% !TeX spellcheck = en_US

Let me tell you a story. A story that I know. Story? No―it is reality,
humans will probably say. They will say it is reality engraved in human
history.

But for me, the deeds of humans are all but stories. At times a comedy,
at times a tragedy; sometimes predictable, sometimes wearisome―nothing
but fabrications.

Yes, humans are always but foolish actors.

They act out a farce, dancing at the mercy of their greed, love, and
emotions. They are foolish, ignorant, and avaricious.... They destroy
with their own hands what they have created. They aspire to rule over
others and become the one and only king of the world.

Why is that, I wonder?

Why are humans the only ones unable to live by the laws of nature,
leaving everything as is? They are such strange creatures.

In the story I am about to tell you now, the main character is also a
human―no. The main character is actually a city. A city-state. People
called it No. 6. Have you ever heard the name before? It is the most
beautiful, yet most fearsome, existence created by human hands. Worthy
of a star role in a farce, don't you think?

But... strange as it is, for some reason, I feel a sort of love towards
that city, No. 6. The story surrounding No. 6, as well those who have
lived in the story itself, are endearing to me. Does that make me the
possessor of a "soul"?

I know of two young boys.

Night and day; light and dark; earth and wind; one who embraces all, and
one who attempts to throw it all away. They are so different, yet they
are very much alike. Both were deeply involved with No. 6. They lived
their lives along with No. 6.

What? When was that, you say?

I wonder. It feels like only yesterday, but at the same time, it feels
like a thousand years ago. I do not feel time the way humans do.

I feel no difference between a single moment or an eternity.

But I have not forgotten about them.

Sometimes I feel that the chronicle of their lives is perhaps the only
one worth telling.

Come hither, now.

Let me tell you a story.

The story of two boys and of No. 6.

\chapter{Inukashi's days}

\lettrine{T}{he ceiling} was spinning. It actually felt like it was whirling.

\emph{Huh? What's going on?}

Inukashi collapsed on the bed and closed his eyes. He felt ill. He was
not only dizzy, he even felt nauseous. He kept his eyes closed as he
took several deep breaths. He inhaled through his nose, let the air sit
in his stomach, and exhaled slowly through his mouth.

Once, twice, three times....

Any ailment, physical or mental, was usually cured by this―whether it be
his agitated heart, his disarrayed thoughts, his throbbing wounds, or
dull headaches. No one had taught him this; it was something he had
learned without even realizing. But as for his empty stomach, there was
nothing he could do. No matter how deeply he inhaled to make his stomach
expand, as soon as he exhaled it flattened back out again. There was
nothing he could do about his body, growing colder from his hunger.

\emph{I hate hunger. It's horrifying.} Inukashi gave himself a shake. Hunger
was like a demon. With its sharp fangs and claws, it uprooted and stole
any will to survive, any hope of living.

But now, he was alright.

Of course, he was still hungry. Inukashi didn't remember the last time
his stomach was full. Empty―that was just how stomachs came. That was
his idea.

He carefully lifted himself up on the bed. He didn't feel dizzy anymore,
but his nausea was still present. He felt heavy, like someone had
attached weights to his arms and legs. \emph{I feel like someone's chained
	metal balls to me, like a prisoner of some country.}

\emph{This is bad.}

He lay back down again, and mentally clicked his tongue. Falling ill in
the West Block was like beckoning Death to your side. Here, there were
underground shamans of questionable nature, or self-proclaimed doctors,
but no one who could give proper medical treatment. Inukashi didn't know
of any, at least.

His body felt heavy. With his eyes closed like this, he felt like he was
being dragged into the watery depths.

\emph{In times like these, I have to think about fun things, he told himself.
	Fun? Have I ever enjoyed myself?}

\emph{You did. Yesterday evening, remember? You were freed from hunger, just a
	little bit. Yeah, see, that was it. That was ultimate happiness.}

\myspace

He'd eaten some meat. There had been a chunk of raw meat in the load of
food scraps from the Correctional Facility. It was not someone's
leftovers: this was a block of meat that had not even been cooked. It
was free of bruising and rot. Upon closer inspection, it was peculiarly
flat. Perhaps the chef at the Facility staff restaurant had dropped it
on the floor, where someone else had stepped on it.

"Oy! You just ruined a perfectly good chunk of meat!"

"Oh, sorry. But you dropped it."

"Well, we can't help it now. Can't use this anymore."

The meat had been tossed into a metal garbage bin and forgotten.
Eventually, it had made its way into Inukashi's hands along with other
trash and food scraps―perhaps that was its journey. \emph{Whatever. I don't
	care what its journey was like, or how it got here. All that matters is
	I'm holding a chunk of meat in my hand.}

What incredible fortune this was.

He quite literally danced for joy. When was the last time he'd had
something this good in his hands? He searched and searched in his
memories, but nothing turned up. Inukashi licked his lips as he held the
hunk of meat, shining with fat. He swallowed hungrily.

He didn't know what kind of meat it was, but he didn't care―as long as
it wasn't human or dog. Inukashi returned to his dwelling in the ruins,
and jumped right into cooking. He selected vegetable cuttings and bones
out of the food scraps, threw them into a pot, and let it simmer. Right
before it finished cooking, he divided the hunk of meat into sections
and threw them in. He considered setting aside half of it to cure, or
take to the market to sell, but in the end he decided against both.
Inukashi was well aware that nonperishable food was a precious
commodity; he also knew that if he took the meat to market, it would
bring him a decent amount of money. \emph{But I think I'll finish this meat
	off in one go.} That was his decision. \emph{I'm allowed to treat myself once
	in a while. I'll enjoy the good fortune that's come to me―the fortune
	that heaven decided to throw my way out of chance.}

\emph{This is the West Block, where I can't even predict what my fate will be
	tomorrow. Even God doesn't guarantee anything for anyone in this place.
	I might as well enjoy the present without thinking about tomorrow.}

Steam rose from the pot.

A mouthwatering smell drifted up. The dogs gathered around, drawn by the
smell.

"I know, I know. You guys'll get some to eat, too. Don't worry."

White, black, patched, tan. Long-haired, short-haired, curly-haired.
Flopped ears, erect ears, one-eared. Inukashi kept twenty or thirty dogs
with him, ranging from one as big as a calf to one smaller than a cat.
For some reason, that number never increased. Puppies were born every
year, so that meant an equal number of dogs probably died or left.

An old female dog died yesterday. She was a great mother, having birthed
many puppies and raised close to half of them successfully. \emph{I remember
	her sons and daughters licking her cold, stiffening body in turn.}

Dogs were deeply loyal. They were warm, and gentle. They had a definite
compassion. They never betrayed their friends or family.

\emph{They're much more decent and trustworthy than human creatures.}

"More fearsome than hunger, than the frozen earth, are humans."

\emph{I remember that was Gramps' line.} Inukashi shook his head as he stirred
the pot with a wooden spatula. \emph{Why did I have to remember him? It's not
	gonna help satisfy my hunger. But, no}―he shook his head even more
fiercely.

\emph{I gotta remember him at least once or twice a year, for his sake. I have
	to remember and recall how dear he was to me. I owe that old man. We
	don't forget the good deeds that people have done for us: that's another
	virtue about us dogs.}

\emph{I don't know how old Gramps was, or why he lived here in the ruins with
	the dogs, or where he came from or where he went. I don't feel like I
	need to know, nor do I intend to find out. But I wouldn't have survived
	if it wasn't for Gramps. I feel the weight of what he did in every inch
	of my bones.}

\emph{It was winter when I met Gramps.}

\emph{I remember the freezing wind and the whiteness of the snow that piled up
	in front of me. So yes, it was winter. Years and years ago.}

He had no memory of his mother, no recollection of his father; yet, he
could remember vividly the frigid wind and the snow dancing. He recalled
the approaching footsteps, a dog's tongue licking his cheek, the warmth
of a human bosom; even the floating feeling he felt for an instant when
he was scooped up.

\emph{How old was I then? Was I still a baby? Probably, huh, because I was
	still getting milk from Mum. Babies sure remember a lot more than we
	give credit for.}

He was an elderly man dwelling in the ruins of the hotel, and he had
picked up Inukashi and raised him. Or perhaps one could say that the man
had picked him up, but the female dog was the one who raised him.

She was young, and had just given birth to a litter. Inukashi suckled at
her breast, and slept nestled up to her belly with the other puppies.
Thanks to her, he had avoided starvation. He had avoided freezing to
death. He had survived.

This intelligent and sweet-mannered dog was Inukashi's one and only
"Mum".

"You're a strange child... or special, I should say." The old man had
made this statement when Inukashi had grown old enough to walk, and was
able to compete with his fellow dogs in lunging for food. The old man
had spoken in a warm, reflective, gentle voice. Inukashi remembered that
well, too.

"Speshal?"

"It means you're different from the others. Until now, I'd never even
heard of, much less seen, a baby who could feed and grow on dog's milk.
When I took you in, to tell you the truth, I figured you wouldn't last
three days. But I still took you in anyway, because I wanted to give you
a proper burial."

"Berry-all?"

"It means digging up the earth and burying you in it. When you died, I
planned to put you underground and give you a burial that way. I
couldn't bring myself to let you waste away in the open air. I didn't
want you to go through what most babies go through on this land, rotting
in the middle of the road, being pecked at by crows, being eaten by
beasts. Normally, I would have... yes, I would have just left you there.
I would have passed you by pretending not to notice. It would be no
different from what I've always been doing. But why did I decide to pick
you off the road... why did I want to bury you in the earth?"

"Why?"

"I don't know." The old man shook his head slowly, twice. "I really
don't know. I don't understand it, myself. Why did I scoop you up that
day and take you home? I've watched many babies, dozens of them, die.
Why did I decide to extend my hand to you? I can't seem to explain it.
That's partly what I meant when I said you were a strange child."

Inukashi shivered. He made a soft strangled noise at feeling his body
grow colder to the tips of his fingers. A cold sweat ran down his back.

He was scared. At the same time, he was overwhelmed with the impulse to
laugh out loud. He wanted to throw his head back and let his laughter
echo to the heavens.

He was alive due to good fortune bordering on mere coincidence. If it
weren't for the old man's impulse, his body, his flesh, his bones would
have been prey to crows and beasts. What a miracle this was, what luck.
Inside his heart was a storm of fear, relief, and the stabbing impulse
to dissolve into hysterical laughter.

By that time, Inukashi had already come to realize how arduous a task it
was to survive every day in the West Block. He sensed that his own
future was full of tribulation and hardship, much like climbing up a
steep cliff with bare hands.

But he wanted to live. He wanted to live, to survive, and stretch the
limits of his life, even for a minute, for a second. For that, he would
do anything, no matter how unsightly, deceitful, or shameful it was. It
was easy to die. All he needed was some rope and a tree with sturdy
branches. He could also jump off a cliff. Or, he could run screaming
into the Correctional Facility―that was an option, too. The soldiers on
patrol would shoot him through the chest or the head without any
hesitation.

He would be finished off in an instant, no matter which method he chose.
He would not suffer for long. At least, he didn't think so. That was why
he knew it was easier to choose death. It was as obvious as the sun
rising from the east.

\emph{But I don't want to.} Inukashi clenched his fist, though it was still
very small. \emph{I won't be finished off so easily. I won't choose death of
	my own will. I'll survive and I'll do whatever it takes.}

\emph{I'll step up to the challenge. I'll challenge the fate which left me
	abandoned on the road in the West Block; I'll challenge the world that
	makes survival such a difficulty; I'll challenge the guys who made the
	world like this―and I'll win. In fact, I'm winning right now by
	continuing to survive.}

As a young child, Inukashi did not know how to speak. He did not know
how to put his heart's resolve into words and tell it to others. But the
old man nevertheless smiled serenely and placed a hand on Inukashi's
head.

"I have a feeling you'd be able to do it," he'd murmured.

It was about a year later, in the onset of winter, when the old man
disappeared. His bed was already empty when Inukashi woke up that
morning, and the old man was nowhere to be seen in the ruins. But
Inukashi didn't particularly go on a frantic search, either. Somewhere
in his heart he had given up, knowing it was no use. He was
disconcerted, but he was not lonely. His dogs were with him. As long as
his dogs were here, he was alright.

\emph{Gramps probably knew that, too. He knew well when he wandered off. Did
	he sense the end of his life coming, or did he find a place he ought to
	go? Whichever it was, he's probably out there somewhere now, a part of
	the earth. People can't turn into the stars in the sky, but they can
	always return to the earth. They can leave their memories behind, too.}

\emph{Thanks, Gramps. I'll never forget everything you did for me. Once in a
	while, I'll be sure to remember you and recall some fond memories. But
	you know, your face is getting blurry lately. I can still remember the
	little things: your scraggly white beard; how your balding forehead was
	shining pink; how your right eyebrow was unusually thick; how you were
	always soft-spoken. I remember those things so clearly, but I can't seem
	to recall your face. I wonder why? But, well, there you have it. I
	remembered you today. That's enough, right?}

He gave the pot another stir with the spatula.

A patched dog barked. The other dogs chimed in and began barking, too.

"I know, I know. Right, let's get this feast started. Gather 'round, you
guys. But you gotta wait 'til it cools down before you eat it. You'll
have a hell of a time later if you end up burning your tongue."

By the time Inukashi had finished doling out the soup into the dog
dishes and begun to sip his own portion of meaty broth, he had
completely forgotten about the old man.

The past tended to get in the way of things. If he kept turning back, he
would not be able to move forward.

Inukashi ate a piece of meat and savoured the taste and sensation of it
in his mouth. He felt like it was a waste to swallow it; he wanted to
savour it forever. But the tiny piece all too easily slid down his
throat and settled in his stomach. By the time he finished the rich,
meaty soup, however, he felt warm down to his very bones. Still
radiating warmth, he lay down on the bed. The puppies squirmed over each
other to climb up, and licked him all over the face. Their small pink
tongues were comforting.

He was happy. He even felt like he had taken all the happiness in the
world for himself. Immersed in bliss, Inukashi dropped off to sleep.

He felt nauseous. He was afraid that the ceiling would start spinning
again if he opened his eyes.

\emph{What's gotten into me?}

A part of his head started throbbing dully. His body felt even heavier.
He was breaking into a sweat. It was an unnatural feverishness, so
different from the warmth of the night before.

The puppies' tongues were no comfort to him, either. His skin only
smarted irritably. He had never once felt his dogs irksome before.

No number of deep breaths seemed to improve his condition.

What's gotten into me?

Right after he questioned himself, he felt a chill run down his back.
Fear ignited deep in his heart.

\emph{This is beyond serious.}

\emph{What if I find I can't get up at all? What if I can't even move?}

It was fatal to fall ill in the West Block. It didn't take much to kill
a West Block dweller, deprived of decent food and living in squalor as
he was. Just a small injury was enough: a deep cut on the pinkie, a hard
scrape along the forefoot. So was a small ailment: dizziness, nausea,
fever―anything to keep one in bed. Someone who had definitely been alive
three days ago could be lying on the road as a corpse today. This kind
of thing happened every day.

\emph{Damnit.}

Inukashi bit his lip, and lifted his upper body up. He leaned against
the wall, and let out a long breath.

\emph{So yesterday's meat was my last supper, huh. Damnit. This isn't even
	funny. I'm not gonna let this take me out.}

He bit his lip harder. The taste of blood spread inside his mouth. He
muttered "damnit" once more to himself for good measure. But no strength
came to him. It was wearisome to lift even one finger. If he forced
himself to get up, he was overcome with simultaneous dizziness and
nausea. He collapsed on the bed again.

His consciousness began to fade.

A chill wind whistled through a crack in the window. The cold drew
Inukashi back to reality. He wanted to scream. He wanted to scream for
help, as loudly as he could.

\emph{Somebody help me... someone, please.}

A dog roused itself in a corner of the room and approached him. It sat
on its haunches at his bedside, and looked up at him. It was a large
brown dog, an offspring of Inukashi's mother's line. It had inherited
her intelligence and deep, dark eyes.

The dog sat still with its ears pricked, as if waiting for Inukashi's
command.

"...I want you to... call them for me..." He pointed out the window.

Beyond was a spread of wintry sky, heavy with snow clouds. The light
struggled to get through the clouds, and barely reached the ground
below. Once more, the West Block would end the day just as frozen as it
had been at the beginning.

The dog pushed open the dilapidated door and left the room. Its rusty
hinges screeched unpleasantly. Inukashi was supposed to be used to the
sound, yet it stabbed at his eardrums and aggravated his nausea.

"Please. Call them..."

\emph{Help me.}

The dog scrambled down the stairs. The puppies huddled together and
whined pitifully.

\myspace

He was dreaming. Dreaming of long ago. \emph{How many years back?}

The old man had long disappeared. Inukashi was alone―but with his dogs.
He'd finally gotten the hang of procuring himself some food scraps, as
well as taught himself how to cook it or sell it off.

He was descending a set of stairs.

They were concrete steps leading underground, not as damaged as the ones
in Inukashi's dwelling. The building was mostly in ruins above ground,
but it looked like the portions beneath were still intact. Once Inukashi
reached the bottom, he was faced with a door. He extended a cautious
hand to grip the handle.

The building was located near the entrance of the West Block. The
surrounding woods nearby were dotted with barracks. Also nearby loomed
the Holy City, No. 6. To be exact, it was No. 6's outer wall. The outer
wall made of special alloy gleamed golden as it loomed before him. The
wall made a clear division between "here" and "there", heaven and hell.
Nothing was lacking within the walls: warm beds, abundant food,
leading-edge medical facilities, comfortable residences. There were no
threats to life, and one could live without even knowing what hunger or
cold was. Inukashi had also heard that suffering and fear didn't even
exist there.

A utopia, worthy of its title of the Holy City.

Inukashi did not hear much of No. 6 in the West Block. Everyone fell
silent, and refused to touch upon the topic as if its very name were
taboo.

\emph{Fishy business}, Inukashi had thought―or rather, felt.

Utopias and Holy Cities simply did not exist in this world. No. 6 was a
city-state founded by humans. As long as humans were involved in it,
something had to come apart. \emph{Your ideal isn't my perfection, and
	happiness for me might be something you can't stand. That's the human
	world for ya. Humans can't create a utopia. The best they'd be able to
	do is quarrel, clash, bend a little for the other person, and then
	settle down somewhere inbetween. That's it.}

\emph{No. 6? That place is so fishy it makes my hair stand on end. The smart
	thing to do is stay the hell away.}

That was why Inukashi never ventured close to this place. He hated
seeing No. 6's wall in his line of sight. If he had experienced a better
harvest that day, he probably wouldn't have gone anywhere near that
place. But an entire day of wandering in the West Block had only gotten
him one or two vegetable ends and a single strip of dried meat. That was
barely enough to nourish himself, much less his dogs. At the time,
Inukashi still did not know how to get his hands on periodic supplies of
leftover food. His only choice was to clutch his empty stomach and
scrounge desperately. At the market, he earned a sound beating from the
butcher's club; at the tavern, the female manager shrieked curses at
him, but he went on unfazed. Inukashi was long used to the abuse, the
insults, and the physical pain.

\emph{I have to do something about this hunger.}

When he came to, he had been standing in the wood. It looked like he had
almost subconsciously walked this way, intending to find even a single
nut to pick up. This was where he found the crumbling abandoned
building. He placed a casual hand on the wall, and it slid aside without
any resistance to reveal stairs leading to the basement.

Inukashi twitched his nose. He squinted his eyes, and strained his ears.

He neither sensed nor smelled the presence of anyone.

\emph{Completely abandoned. huh.}

He carefully descended, step by step.

Inukashi knew that a strange old woman and a boy (her grandson, he
assumed) was supposed to be living here. He had seen them twice before.
The old woman had a harsh look about her eyes, as if she'd never smiled
once in her life.

\emph{I know, I know. I remember.}

\emph{That old lady was funny in the head. She attacked someone important from
	No. 6―the mayor or chairman or whatever. All on her own, at that. She
	hobbled towards him, knife in hand, and was shot to death. Wait―or did
	she get arrested and shot? Whatever it was, she was finished off pretty
	quick. Not much of a surprise, haha.}

Inukashi sneered at her mentally. It was a rumour he'd heard in the
marketplace. He was unsure of its validity.

His stomach growled. It sounded like a cry for help.

\emph{I can't take it anymore. Give me food. Hurry, hurry, hurry, hurry,
	hurry.}

\emph{Damnit, isn't there something? Mouldy bread, rotting meat, I don't care.
	Something to quiet my stomach down.}

He gripped the door handle. The door was unlocked. It was a little
heavy, but with a little push, it opened without much resistance.

"Ho!" A sound not quite resembling a breath or an utterance escaped his
throat. "The heck is this?"

There were piles of books as far as he could see. They were here and
there, everywhere, piled up neatly or scattered carelessly across the
floor. The floor itself was almost indiscernible. The room seemed to
contain nothing but books.

This moment was Inukashi's first encounter with books. He knew words; he
could also write, as long as it wasn't too difficult. The old man had
taught him. But Inukashi had no knowledge whatsoever about books. He had
never heard the word "book", nor did he know that it referred to these
bound sheets of paper with printed words. He had no clue where to begin
understanding them. He perceived instantly that they weren't food. Just
to make sure, he picked a book from a pile near the door, and took a
bite. He had chosen it because the ripe apple pictured on its white
background looked delicious.

\emph{Horrible.}

Inukashi wiped his mouth with the back of his hand, and threw it aside.
\emph{Tough, dry, and definitely not something I can eat.}

He moved forward, kicking the fallen books out of the way. There only
seemed to be books in this place.

\emph{Tsk. All that work gone to waste.} Inukashi clicked his tongue and was
about to turn on his heel when his heart beat a trembling pulse. He had
found something other than books.

It was placed on a shelf (filled with books)―some of the volumes had
been cleared away to make space for it. It was a small silver box,
sitting on top of a towel.

\mybreak

\emph{What is this? Is someone living here?}

He twitched his nose again. Like before, he did not smell anything.
Inukashi took down the small silver box from the shelf. He opened the
lid.

He found himself letting out a whistle.

\emph{Oh, I see. This is quite a treasure. I've found myself some booty.}

The box turned out to be an emergency kit, with bandages, pincers,
gauze, and a number of medicines stored neatly inside. There was even a
scalpel. It looked like something that had been used in No. 6. Inukashi
had no clue about how this ended up here. He had no intentions of
finding out, either. He didn't care about its journey or story. What
mattered was that he was holding it in his own hands. That was all.

Medical items of any kind were coveted in the West Block. Disinfectant,
especially, was traded at a high price. Sometimes a small bottle of
disinfectant could fetch up to two silver coins.

Inukashi brought his nose close.

\emph{This is a hundred-percent pure, with no additives―the good stuff. Look
	at the way it stings my nose. Heh, forget silver―this might just
	transform into a gold coin if I'm lucky. I made a good find. My luck is
	finally turning around.}

Inukashi grinned to himself as he shut the lid of the box. He was about
to lift it up in his arms when he noticed a small table covered with
books.

On top, there was a small mouse. It was not alive. It was skilfully
wrought, but it was clearly man-made. Inukashi leaned forward, still
cradling the box. The belly of the mouse peeled back to reveal its
complex inner parts.

\emph{A robot?}

Inukashi was about to lean further in when he felt a violent chill. He
felt goosebumps forming on his back.

"Don't move," he heard a voice by his ear. This time, the skin on every
inch of his body bristled. It was not because a blade had been pressed
against his neck. It was because the voice was completely void of
warmth. All emotion in it was suspended frozen. Its icy blast chilled
even Inukashi's own emotions.

It was the voice of a murderer.

It was the voice of one who could take a human life with no hesitation,
no sway of emotion.

\emph{And―and on top of that―this guy got behind me.}

If Inukashi could swear on anything, it was his ability to sense the
presence of people. His sixth sense was as good as any dog's. The more
emotional a person was, the more Inukashi could feel the presence on his
skin. Thanks to this ability, he had been able to escape danger and
dispute time and time again. But this time, he had felt nothing. He was
not even able to discern the slightest from the person creeping up
behind him.

\emph{Maybe he's not human? A dead man come crawling out of the depths of
	Hell? A demon? A shapeshifter?}

His teeth refused to come together. His molars chattered, making a
strangely mechanical sound. It echoed deep in his ears.

\emph{Click-click. Click-click.}

\emph{Click-click. Click-click.}

Inukashi gritted his teeth, and clenched his stomach.

"W-Wait a minute here. I was only..."

"Put the box back."

"A-Alright, alright! I'll do as you say." Trembling, Inukashi replaced
the box on the shelf.

"Th... there. I returned it. That's enough, right?"

"Enough? Are you kidding me?"

The blade moved ever so slightly. He felt a jolt of sharp pain. He
struggled to rein in the scream that was about to tear through his
throat. He was sweating in his armpits.

"Theft amounts to death in this place. You should have no complaints
about being killed."

"Y-Yeah, but I mean, I can't complain if I've already been killed,
right? H-Hey, I live in the ruins, by the way... know about it? It's on
the far end of here, the ruins of a hotel. That's my place. I live there
with my dogs. My name is... uh, well, I don't have a name, but you
know―who needs one in a place like this, right? People call me
\emph{inukashi}―the Dogkeeper. Dogs are part of my business. Ha ha, but who
cares about my name, right? I kinda like it, though. Ha ha. So if you
ever wanna call me by name, it's Inukashi."

Inukashi kept talking. He felt like if he closed his mouth, his throat
would be slashed in the silence that fell afterwards.

"Hey, come on. I'm begging ya. I'll apologize, so will you just forgive
me? Please? I'm sorry. I'll never do it again," he tried imploring
pathetically. "Don't kill me. I'm on my knees. Help me, please. I... I
don't wanna die yet. I really don't wanna die. I'm sorry, I'm so sorry.
I'll never touch your stuff again. I promise. Please, just don't kill
me."

Inukashi wasn't putting on an act. He was earnestly pleading for his
life.

\emph{Don't kill me, please. Let me go.}

\emph{Please, please, please, please, please, please.}

The knife was lifted. Suddenly, the base of his neck felt much lighter.
Inukashi let out a long breath. His neck muscles hurt, likely from being
taut this whole time. The spot on his neck throbbed slightly when he
pressed it with his hand, but no blood came off.

The wielder of the knife had made a slight cut, as shallow as the mere
first layer of skin on the neck, to freeze his victim in fear. Not
enough for it to bleed, but just enough to make the victim feel pain.

\emph{I knew it. The guy behind me is no human. He's a dead man, a demon, a
	shapeshifter....}

Inukashi turned around slowly, still holding his neck. The truth was
that he did not want to turn around. He wanted to beeline right out of
the place. But his feet hesitated; he felt like the moment he turned his
back and broke into a run, a knife would be plunged deep into his back.

He slowly, slowly turned around.

\emph{Huh?}

He had to blink. He knew his mouth was hanging open.

The figure in front of him was no dead man, demon, or shapeshifter. It
was a boy wearing a plaid shirt. It might have been a girl. No, it was a
boy. A girl couldn't produce an icy voice like that. The boy only looked
like a girl.

The boy had long hair which came down to his shoulders and hid his
forehead. His small, white face was almost uncannily proportionate.
Inukashi had imagined the boy's eyes to be glittering full of murderous
intent, but they were serene and inscrutable.

The boy had eyes of a strange colour.

An elegant dark grey. It was Inukashi's first time seeing such a colour.

The boy seemed to be taller than Inukashi, but he figured their ages
were about the same. But Inukashi was also unsure of his own age.

The boy sheathed his knife, still wearing a blank expression. Inukashi
felt overwhelming relief. Then, he felt irritation at himself for being
relieved.

\emph{I was being threatened by this twig?} He wanted to click his tongue in
frustration. \emph{Geez, I'd never be able to live that down.}

"You could have picked a better shirt to wear." Inukashi wore a smirk as
he jerked his chin. He intended to look smooth and unruffled. "But the
quality doesn't look half-bad. Not something you'd come across often in
the West Block."

"It's a borrowed shirt."

"Borrowed? Where did you borrow such a good piece of clothing, huh?
Don't tell me you got it from No. 6."

He had meant it as a joke, but once he put it into words, he felt like
that was the only possibility. The shirt's superior quality was evident
from first glance. It looked soft to the touch, warm, and durable. The
emergency kit he had just put back on the shelf was also a product from
inside the walls, no doubt about it.

"Who the hell are you? Don't tell me you came from that―" Inukashi
trailed off. He had just seen the boy pick a strip of dried meat out of
his breast pocket and bite on the end of it.

"Hey... don't tell me that's..." Inukashi scrambled through the bag
hanging from his waist. It was empty. He had most definitely put dried
meat in there, but it was gone.

"I'm taking this", the boy said. "As compensation for your stealing."

"B-Bullshit! Who's the thief now? Give it back, that's my meat! Give it
back!"

\emph{Heh.} The boy laughed. His smile seemed both innocent and carefree.

"Wanna try to take it back by force, Inukashi?"

"Gh..." Inukashi bit his lip. This was not someone he could win against
head-on―his instincts were telling him so.

\emph{Damnit, I shoulda brought my dogs. If I had them with me, I could take
	him down in one bite.}

But his dogs were not here. Inukashi was alone.

"...Fine. Keep it."

"There's a good boy. You should know when to listen. It'll help you live
longer."

"Damnit, stop making fun of me!" \emph{Just watch. I'll get my revenge.}

Inukashi retreated to the door. He grabbed the handle. There was no need
to stay here longer than needed.

The boy sat on top of a pile of books and said nothing. Only his gaze
was fixed on Inukashi. Inukashi's movements were completely surrendered
by that gaze. His arms and legs turned stiff and awkward, and they
refused to move smoothly.

"...What the hell are you...?" He repeated his question from some
moments before. This time, it was more serious. "Do you live here?"

"Yeah."

He did not expect a reply.

"Alone?"

"Yeah."

"This house has been abandoned for ages. There hasn't been anyone living
in it for years―at least, there wasn't supposed to be. Where the hell
did you come from? And why do you have a shirt and emergency kit that's
clearly from No. 6? Oh, and that mouse doll―what is that? It looks like
a robot. Don't tell me you built that thing?"

Inukashi knew he had to run away as soon as possible, but his mouth kept
moving. Question after question escaped his lips.

"You talk a lot, don't you? I'm surprised you haven't bitten your tongue
already from talking so much." The boy shook his head. An amused smile
crossed his face.

Inukashi found himself almost attracted to him. His heart beat faster.

\emph{This guy is dangerous. More dangerous than a murderer, and hell of a lot
	more hassle.} This was another gut instinct of his. And he was sure he
wasn't off the mark.

\emph{Don't associate with him. Get away from here, and never come back
	again}―a voice of warning echoed in his ears. Inukashi usually obeyed the
voice promptly, but this time he ignored it and continued to question
the boy.

"What's your name?"

The boy tilted his head very slightly. "Nezumi."

His name, so unexpectedly and promptly given, seemed unusual for a
human.

"What kind of name is that? Is it your real name?"

"You could say the same about yours, Dogkeeper. It's not a proper name,
for sure."

"Hmph... well, you could say that. Nezumi, huh. At least it's easy to
memorize."

"So you plan on remembering it?"

"Erm... well..." Inukashi felt like he was being toyed with. If he
didn't wrap it up soon, he'd get sucked right into Nezumi's plot. Like
an insect caught in a spider's web, he'd be immobilized and would
eventually wither.

\emph{Danger, danger, danger.}

"Well, see ya, Nezumi. If we're lucky, maybe we'll meet again."

"If we're lucky."

\emph{To hell with luck. I'll make sure I'll never see your face again.}

Inukashi slid his hand behind him and opened the door, and slipped
outside. As soon as he was out, he sprinted up the stairs as fast as he
could. His feet froze halfway. About midway up the stairs, Inukashi
found himself turning around. He could see the rusty door.

"Nezumi, huh," he muttered.

\emph{Would I really be able to get away with not ever seeing you again?}

\emph{If we're lucky.}

The line he'd heard only moments before still echoed inside his head.

\emph{If we're lucky.}

\emph{We probably will meet again.} He had a sudden feeling. It was almost
closer to a firm belief. From hereon, he would see that boy time and
time again. They would form a connection.

His body almost recoiled in disgust. But at the base of that disgust
lurked something slightly tender. He muttered it under his breath again.

"Nezumi, huh."

\mybreak

"Did you call me?"

He heard an uncannily crisp answer.

\emph{Huh?}

"Did you call me, Inukashi?"

He opened his eyes. It was bright.

His room, tucked away in a corner of the ruins, was filled with light.
Beyond the glass pane of the window he could see the blue sky behind a
crack in the clouds.

The blue soaked into his retinas.

Nezumi was peering into his face. Their eyes met. His eyes were the same
elegant dark grey as the time they had first met.

"...What... are you doing here...?"

"Huh? What is this treatment? You're the one who called. Using this guy
as a messenger, remember?" A brown dog wagged its tail from beside
Nezumi.

"C... Called? You? Psh, of course not. I was calling for..."

"Then who were you calling for?"

"I was..."

"Inukashi, are you awake?" A head of white hair peeped out from behind
Nezumi.

"Shion."

"Yep, it's me. You must have had a tough time. It's alright now. We'll
make you better in no time." Shion smiled.

Inukashi came close to tears. He stopped himself in time from clinging
onto Shion and sobbing out loud.

\emph{Shion, I was scared. I thought I was going to die. I was so scared, so
	lonely, and I didn't know what to do. So I called you.}

"Here, drink this." Shion offered him a chipped bowl. It contained a
thick, green liquid. Its dirt-like smell stung his nose.

"What the..."

"It's a medicinal herb. I found a book about oriental medicine in
Nezumi's bookshelf and thought I'd give it a chance. I hunted around in
the woods and found a lot of stuff. This will calm your nausea down, and
it'll also help you recover from exhaustion."

"...Huh? Oriental?"

"It's a type of medicine that was passed down in the East. The book says
it's supposed to heighten your body's overall healing ability. Come on,
just give it a try."

"Pinch your nose. It'll make it bearable," Nezumi said. Inukashi pinched
his nose as he was told, and swallowed the drink in one gulp. He didn't
think it tasted half bad. The bitterness that slid down his throat
seemed to give him strength. He let out a long exhale.

\emph{They actually came for me. They got my SOS. I begged for them without
	offering anything in return.}

Shion placed a hand on Inukashi's forehead. It felt cool and soothing.

"You'd better stay in bed for a while. You haven't got pneumonia, but
you have all the symptoms of a cold. And anemia, as well―"

"If I get trapped in bed, my dogs'll starve to death."

"We'll do something about it. I'll take over your rental duties, and
Nezumi will keep you supplied with food. Right?"

Nezumi shrugged lightly. "Sure, I can do something about it. But you owe
me for this, Inukashi. I'm charging interest."

Inukashi managed a faint smile from where he lay. Nezumi's remarks,
which usually irritated him to no end, sounded unbelievably gentle now.

\emph{There's something seriously wrong with me. If I cry here now, who knows
	how much I'll be made fun of afterwards. If I'm going to cry, it has to
	be when only Shion's around. Hold it in. Tears, don't spill over.}

"Say, Inukashi." Shion smiled even more gently. "I don't think you need
to worry about your cold, judging by your physical strength. But the
wound on your toe is another story."

"Toe? Oh, my right big toe, right? It's been hurting for a while."
Inukashi got injured all the time. Unless it was a considerably large
injury, he usually just licked it better.

"It's festering," Shion pointed out. "If you leave it like this, it'll
swell up with pus and you likely won't be able to walk. So―"

"So?"

"You need an operation."

Shion took out that same emergency kit. It looked no older than when
Inukashi had first seen it.

"Shion, uh, what are you―?"

"I'm going to cut open the wound, extract the pus, disinfect it, and
then sew it back up. That's it. It'll be over in a flash."

Shion was already wearing rubber gloves and holding a scalpel. It was a
small silver blade, sharpened to perfection. Inukashi felt his spine
growing cold.

"C-Cut open? Wait, wait a second, Shion. Hold on. Wh―What about
painkillers? Sleeping gas?"

"I don't have any."

"Whaddoyou mean, you don't―"

"It's alright. It'll be over quickly. Sorry, Nezumi, could you hold
Inukashi down? Make sure he doesn't move."

"Gotcha."

Nezumi held Inukashi's hips down with both hands. Inukashi's lower body
was immobilized completely.

"I think this might be news to you, Inukashi," Nezumi smiled in a
strangely provocative way. "But Shion loves to sew people up. He may
look innocent, but he's a huge sadist."

"Wha―stop it!" Inukashi yelled. "I'm scared! Help!" It was now beyond
Inukashi's power to put on a brave face. He was close to crying.

"Settle down," Nezumi said testily. "Just listen to what he says.
Besides, even I can tell that this wound is pretty serious. You could be
risking your life if you leave it untreated. I know Shion didn't mention
it outright, but maybe this is what's behind your sickness."

"I don't care what's behind it. It hurts! \emph{Stop}," he wailed. "Somebody
help me! Shion, have mercy!"

"It'll be alright. Don't move," Shion said. "Oh, look, see? All this pus
has built up inside. I'm surprised you could walk with this. You must've
turned numb to the pain. Okay, it'll be over soon."

"I'm \emph{not} numb," Inukashi sobbed. "\emph{Owww}, don't sew it! It hurts!"

"Don't cry," Nezumi said. "There's a good boy. I'll give you a reward."

A soft melody flowed forth from Nezumi's lips. It gently rocked
Inukashi's heart. For an instant, Inukashi had turned back into an
infant and was being held in someone's arms. He was freed from fear or
suffering. He was in a place of peaceful sleep.

"There's a good boy. Don't think of anything, just sleep. We'll protect
you with everything we've got. We won't hand you over to the Reaper, no
matter what happens."

\emph{We'll protect you with everything we've got.}

Inukashi opened his eyes and looked at Nezumi. Then, he looked at
Shion's profile as the boy crouched at his feet. Both of their faces
were grave. Numerous streaks of sweat marked Shion's cheek, and formed
droplets at his chin.

\emph{We'll protect you with everything we've got.}

It wasn't a lie.

This world was ridden with lies, but Nezumi's words were true. Even if
everything in this world were a fabrication, Inukashi knew he could
believe those words without fail.

Inukashi could bear no more. His tears spilled over. They kept flowing.
He felt like he was drowning in tears.

\emph{Bastards, making me cry.}

Inukashi pressed both fists against his eyes, and cried silently.

The blue sky was still outside his window.

\chapter{A song from the past}

\lettrine{N}{ezumi lifted} his face. His brow furrowed slightly.

"What? What did you just say, Shion?"

"I said I wanted to see."

Shion sipped the hot water in his cup. The bit of sugar mixed into it
made it taste slightly sweet. Sugar was considered a luxury item in the
West Block. Shion himself had not had flavoured water in a long time.

"I said I wanted to watch you perform onstage."

"Why?"

"Why, well... no particular reason. I just want to see."

Nezumi drew his chin back, and closed the book he was reading with a
rather rough snap.

"That's not an answer. If you're looking for something to kill your time
with, consider other options."

"I don't have enough free time to kill. I have my dog-washing job at
least twice a week, and I've promised to read picture books to Kalan and
the rest of the kids. I've also started working at Rikiga-san's
part-time. I'm actually about to go out now."

"Working part-time? At that old man's place? I hope it's not something
as terribly respectable as taking photos of naked women."

"No, I just run errands and do miscellaneous work. Stuff like sorting
receipts and cleaning the office. Rikiga-san actually runs a pretty wide
variety of businesses. I never knew."

"Well, I bet my mice would sprout wings and fly before that old man
starts running any \emph{decent} trade. Hah! You'd better be careful, Shion.
Who knows when some woman might come attacking you with a knife like she
did to Rikiga."

"I don't think that would be very likely," Shion said sceptically.~

"Rikiga-san has been saying for a while that he's had enough of women."

"That's all talk. He loves his women. It runs in his blood. He can't
live without 'em. But if you were to put alcohol and women in a balance,
he'd probably choose alcohol after a long deliberation and a ton of
griping."

"You certainly don't sugar-coat your words, do you?"

"I just can't whore out my kindness like you do."

Nezumi stood up. A small brown creature hopped up onto his shoulder as
if it had been waiting. It was Cravat, a mouse which Shion had named for
the colour of its fur.

"Is it somehow a bad thing to be nice to everyone?" Shion's words grew
sharp. He felt a restless ripple deep inside his chest. The ripple made
it hard to breathe. This feeling was something he would never have known
if he had remained in No. 6. Various emotions writhed inside him. They
cast one pattern after another like a kaleidoscope.

Since beginning his life in the West Block, Shion found himself startled
by the turbulence and wealth of his own emotions. His heart was shedding
its outer layer. His soul was reviving as it ripped through its tense,
rigid outer shell.

Nezumi put away the book on the shelf, and picked up his cape.

"Kind words that don't hurt anyone―what meaning do they have?" Nezumi
draped the superfibre cloth over his shoulders and donned his gloves.
"Everything that comes out of your mouth is gentle and lukewarm. Like
the chirping of birds or a chorus of insects. It's beautiful, but it
doesn't lodge itself anywhere. Not even in yourself."

"Nezumi―"

"Shion, you're not kind. You just don't want to get hurt yourself.
That's why you take all the thorns out of your words. With no sense of
responsibility, you spew words that do neither harm nor good. Admit
it―I'm right."

Shion could not deny it completely. He could neither show his anger nor
protest that Nezumi was insulting him. Nezumi's words were full of
thorns. If Shion touched them out of carelessness, they would pierce his
fingertips and draw blood. Compared to that, perhaps his own words were
indeed lukewarm.

Shion didn't think that it was an evil thing to avoid hurting anyone.
Nor did he think that gentleness was useless. He also knew that Nezumi
was not criticizing his kindness.

Gentle words that harmed no one, and words that did not carry the weight
of their consequences were rife in No. 6.

\emph{My, how pitiful. Someone should do something about it.}

\emph{It's unfortunate. My heart goes out to them.}

\emph{We will make our utmost efforts with our very hearts and souls.}

\emph{Everyone, we must all be friendly to each other.}

In such an environment, he had unconsciously grown detached from the
meaning and weight of his words. But there was absolutely no value in
superficial kindness and concern, promises and love. They were just
repulsive. Shion had already realized it without Nezumi pointing it out.
He knew, but he wished he could pretend he didn't.

Nezumi had plainly seen the thoughts bubbling from the depths of Shion's
heart. He had felt irritated at Shion's lowliness and artificial
kindness, resulting in his thorny words. Shion knew he deserved to be
pricked by them. But―

"I'm always serious when I'm talking to you."

Nezumi turned around.

"Hm? What did you say?"

"No..." If he muddled his answer now, perhaps it would agitate~

Nezumi's irritation even more. But Shion found his tongue heavy and
unwilling to move.

\emph{I'm standing here and facing you in all seriousness.} Those words were
heavy―so heavy that Shion found them hard to vocalize.

Cravat chirruped from his perch on Nezumi's shoulder.

\emph{Chit-chit! Cheep-cheep-cheep!}

"Oh, crap. I'm late again." Nezumi's tone was calm. There was no sign of
the irritation from moments before.

"See ya, Shion. Like I said, be careful when you're working at that old
man's place." With that, Nezumi left. Shion was left alone―well, perhaps
not so alone. Hamlet and Tsukiyo, the two mice, were asleep in his lap.

Shion stroked their heads with his finger, and took another slow sip of
his sweetened hot water. It was delicious. He figured the expression
"sweet nectar" probably referred to a taste like this.

The days Shion spent in the West Block had honed his senses swiftly, and
without his knowledge: sight, hearing, smell, touch, and taste. Back
when he was in the city of No. 6, he used to eat as much "delicious"
food as he wanted, until he was full. He had been able to. If he should
so desire, he was able to get his hands on any meat, vegetable, fish,
sweets, or fruits with no limitations. Following his move to Lost Town,
his selection of food was narrowed considerably compared to his time in
Chronos, but he seldom felt deprived.

His mother Karan's cakes and freshly-baked breads were simple but
delectable, and he never tired of eating them. But Shion felt that even
that taste did not penetrate as deeply into his heart as the taste of
this hot water.~

He drained his cup. The warmth reached all the way to his~

fingertips, and strength filled his body.

"Alright, now it's time for me to go, too."

Shion cautiously transferred Hamlet and Tsukiyo to the bed and stood up.

"But you know, don't you think I've learned a lot in my own way since I
came here? I can even sort handwritten receipts. And he says I do wipe
the floor and wash the dishes as well as any full-fledged man.
Full-fledged. I'm allowed to be a little proud of myself, right?"

\emph{I'm using my own body and brain to do work and earn its rewards. I'm
	allowed to be proud, no matter what kind of job, no matter how small the
	wages. Right?}

Tsukiyo lifted his head and twitched his ears as if to agree.

\emph{Geez.} Nezumi ground his molars. \emph{Hopeless guy}, he reprimanded mentally.
He was not referring to Shion. He was talking about himself. Cravat
cried softly from within his cape.

\emph{Skreet-skreet! Cheep-cheep-cheep!}

"Shut up. You don't have to tell me; I already know. I just took out my
frustrations on Shion back there. I know."

Sometimes―though it was very rare―Nezumi's emotions grew unstable when
he was around Shion. His self-restraint loosened, and his thoughts
issued unrefined from his lips. They collided, sending sparks and sprays
flying. Nezumi never intended to condemn Shion. He knew that he wasn't
just or strong enough himself to have the right to do so. But he wavered
when he was with Shion.

His heart, which wanted to hate and reject all of No. 6, wavered.

No. 6. The most detestable city-state in this whole world. It was no
utopia or holy city. Those names were but a facade. As soon as he tore
away its thin hide, the monster would show its true figure.

A man-eating monster.

It never hesitated to destroy its surrounding states and massacre entire
tribes if it meant prosperity for itself. It plundered, leeched, and
dominated.

\emph{Someday, I'll take it down.} For Nezumi, No. 6 was an opponent he had to
take down with his own hands, an existence that needed to disappear from
this world.

But inside this grotesque monster lived a boy like Shion. Shion had let
an intruder, a VC―No. 6's term for violent convicts―into his home,
treated his wounds, provided him food and a place to sleep, and as a
result, had lost his secure life as an elite. Shion had lost everything,
and yet still confessed to Nezumi.

\emph{No matter how many times I'd return to that night, I'd do the same
	thing again. I'd open the window, and wait for you.}

They were bare and honest words. They pierced through his heart. For an
instant, Nezumi could not help but stare at Shion without even blinking.
Shion definitely did not use words of superficial kindness, and Nezumi
was sure the people around him were the same.

Shion's mother harboured the unshakable belief that her son would
return, and thought of him constantly while she waited. According to the
mice Nezumi had sent out as messengers, the muffins and bread that she
baked were so delicious, they were enough to make one's cheeks swell in
anticipation. And there was that girl with her unwavering love.

Those were the kind of people around Shion―those who exerted every
effort in living their daily lives. They were honest with their words,
did not condescend on others, and lived without losing their dignity.
Those people lived inside that monster.

If he had not met Shion, he would never even have imagined this. He
would have continued loathing every citizen of No. 6 and wished for the
city's ruin.

But he had met him.

He had come to know.

\emph{Could I still hate, even with that knowledge?}

He wavered. He lost composure. He grew indecisive.

Nezumi paused and turned around. The outer walls of No. 6 reflected the
fading light of dusk. Its reddish glow made him think of fire. Long,
long ago, he had seen this colour, and it had burned an imprint in his
memories. It was neither crimson, burgundy, nor red. It was a mixture of
all of them―a colour that could be described no better than chaos.

The colour still lingered in Nezumi's vision even after he had come out
of the woods and passed through the marketplace. He would probably never
forget it for the rest of his life.

It was burning. Houses, trees, his newborn sister, and his mother who
held her. All burning.

"Run!" his mother had screamed as she burned. Her beautiful hair, her
skin, her body, was a mass of flames. His father had covered his
mother's body with his own, frantically flapping his hands as he tried
to put out the flames. A No. 6 soldier pointed his flamethrower at them.

More fire burst forth.

His father, mother, and younger sister were swallowed up in the flames,
which burned high and fierce. Nezumi himself was overwhelmed with a
shock of heat and pain and was thrown on the ground.

\emph{It hurts. It's hot. I'm scared.}

\emph{Hot, hot, hot, hot, hot, hot, hot.}

"Run!" His father's yell pierced through the flames. "Run! Even if none
of us can, at least you―"

Then, everything fell apart. Nezumi had seen everything. He was supposed
to have seen everything. But he had no recollection. The only things he
remembered were the colour of the raging flames and the roaring―the
sound of whirling flames was just that, a beast's roar―and an old
woman's back.

He was being carried on an old woman's back as she ran. Her back was
bony, and even at his age, Nezumi felt it very small.~

But it was sturdy. Her back and her legs were stout.

The old woman ran, tearing through the flying flames, the winds swept up
by them, and past No. 6 soldiers. She ran through a tangle of bushes
down a wild path and crossed a swift stream.

Nezumi had lived thanks to this old woman. He had survived.

Once Nezumi had recovered from his burns enough to move, the old woman
immediately began making preparations for a journey.

"We must distance ourselves from the devil now," the woman muttered as
if to herself. "But we will return. We will return to exact our
revenge."

While they wandered from the rocky barrens to the lower lands which
would later be known as the West Block, the old woman spoke night and
day.

She spoke, over and over, of the last moments of the Forest~

People, the inhumane acts which would later be engraved forever into the
memories of a select few as an incident called the Mao Massacre. Her
stories continued even after they had settled in a basement vault in the
West Block. Nezumi grew up buried in books, listening to this old
woman's stories. He never felt he lacked anything. But the wound on his
back ached as if in response to the old woman's tales. His mother's
voice and his father's screams echoed in his mind. It was painful for
him.

\emph{Run!}

\emph{Even if none of us can, at least you―}

Each time he recalled it, his wound throbbed harder. It was like his
scar was writhing about. The old woman always looked down at Nezumi in
silence as he gritted his teeth and endured the pain. Her gaze was cool
and sapped of emotion.

The old woman was also reaching her mental limit. Her own hatred,
despair, and anguish was threatening to crush her. She was fighting
dangerously close to the border of giving into death's temptation.
Nezumi could sense with instinct, not logic, the storm of emotions
brewing inside her.

That night, they were sleeping outside on a stretch of wasteland on the
outskirts of the West Block. It was a few days before they ended up
settling there permanently. As usual, they started a campfire and slept
close to it. For a while after their escape, Nezumi's whole body seized
up when he saw fire. That colour, that roar, those screams pierced his
body, and his wound seared him.

But within a year, his fear dissipated.

Fire was essential for warmth and for roasting meat. If he kept on
fearing it, he would freeze to death. Nezumi had also reached an
understanding.

\emph{Humans are the fearsome ones, not fire.}

It was their routine to take turns watching the fire after a few hours
of sleep.

"You may sleep until dawn, when the eastern sky begins to lighten. You
need not feel guilty. We older ones do not need much sleep."

It had been just before Nezumi had gone to sleep. The old woman had
shown a rare smile as she added a withered branch to the fire. The
flames murmured gently. It was more like a mouse's squeak than a roar.

\mybreak

The eastern sky was still inky black when Nezumi awoke. He got up
abruptly, and looked around. He heard quiet sobbing. The voice had woken
him up.

The campfire was still burning. The flames undulated.

"Gran... what's wrong?"

The old woman had curled up into a ball with her face in her hands,
sobbing. Nezumi had never seen her shed tears before. He inched to her
side and placed a hand on her knee.

"What's wrong? Are you hungry? Does it hurt somewhere?"

The woman did not answer him. Her silent sobbing did not stop.

"Come on, tell me what's wrong. Does it hurt? Are you upset?"~

Nezumi shook the woman's knee. She was the only person in this wide
world whom he could trust and lean on.

\emph{I don't want you to cry.}

\emph{Don't be in pain. Don't be sad. Please, gran.}

"I am sorry..." The sobbing stopped. "Shame on me... but I could not
bear it..."

"But what was wrong? Are you alright?"

The woman's hand stretched out to pat Nezumi's head.

"My beloved homeland is so close. But―now, most of the Mao forest is
lost. That demonic city is giving rise in its place. Little remains of
the forest that I grew up in, where your mother and father grew up in,
where you grew up in. We cannot even set foot into that small patch of
forest now. Yet, it is close... so close..."

"Gran..." Nezumi touched the woman's cheek with his fingertips, and
wiped her tears away. They were surprisingly hot. "Don't cry. You can't
cry. It'll weaken your heart."

The old woman nodded and peered into Nezumi's eyes.

"Let me teach you a song."

"A song?"

"Yes. Your mother was the greatest Singer in all of Mao. I was,
too―many, many years ago. I taught your mother how to Sing."

"Are you gonna teach me?"

The old woman looked Nezumi straight in the eye, and nodded deeply once
more. She was not crying anymore. Her dry eyes were darker than the sky
above. Her dark eyes reflected the flames of the campfire.

"You are fit to be a Singer. You often used to go to out to the forest
and sing with your mother. Do you remember?"

Nezumi shook his head.

All of his memories were vague leading up to that day when everything
disintegrated into flames. He had difficulty recalling anything clearly.

"Just... a voice."

"Voice, did you say?"

"I remember a voice. A voice that said―I'll teach you a song that you
will need to keep living."

\emph{Come here.}

\emph{Let me teach you a song. I will teach you a song that you will need to
	keep living.}

Had he not heard a voice say that?

The old woman gave him a startled look, and her mouth twisted.

"Was that... your mother's voice?"

Nezumi fell silent for a moment at her question. He could not remember
his mother's voice. \emph{Run}―only that short cry stuck stubbornly in his
ears, and blotted out her singing voice and her laughter. But even if he
didn't remember, he felt certain about one thing―it was not his mother's
voice.

"No. It wasn't... human."

"...I see." A sigh spilled from her twisted lips. "I see―you~

already know."

"Huh? I don't know anything. I feel like I heard the voice in a dream."
Perhaps it was nothing but a drowsy dream, an illusion in sleep. But the
old woman shook her head slowly.

"It was no dream. You are a Singer. The Forest God has chosen you."

"Forest God..."

"Yes. She is the forest itself. She blesses the Forest People and also
instills them with fear. She is always by our side, watching over us,
blessing us. At times she will hurt, destroy, and obliterate us."

\emph{Destroy and obliterate. Does she mean the fire?} It scorched, thieved,
and banished everything to nonexistence.

"No." The old woman had keenly sensed his unspoken thoughts. She shook
her head vehemently as if to interrupt his words.

"That fire is different. That is made by humans. It is a result of human
malice and greed. It is not the same as the destruction brought on by
the Forest God."

The old woman threw some withered branches into the fire. The flames
swelled slightly. The fire in front of him was gentle. It provided him
warmth and heat for cooking.

"The people of that demonic city burned the forest to the ground. They
turned the Forest God's holy dwelling place into ashes."

"Did the Forest God die that day, too?"

"The Forest God does not die. She will never be killed by human hands.
The people of the demonic city know no God. They do not know her terror.
They do not try to know."

"It's called No. 6."

"What?"

"That city is called No. 6. I heard from someone."

"Who?"

"A traveller. He said he was a bard." Nezumi had met a group dressed in
white while he was collecting branches in the barrens. All of them had
white bags tied to their backs.

They told him that there were six city-states in the world, and people
gathered in and around these places to live. Among them, No. 6 was the
most beautiful and abundant, as well as the most isolated.

"You have a good voice," a bard atop a horse had said to him. The man
had light brown eyes, the same colour as the earth on the barrens. "A
very good voice. If you train it, you could become a first-rate singer.
How about it, kid? Why don't you come along with us?"

Nezumi would be lying if he were to say he wasn't attracted to~

the offer at all.

He would travel the world, with instruments and songs as his companions.
Free from hatred, free from the burden of his memories, he would sing,
play, and dance as his heart desired.

Nezumi was deeply attracted to the idea.

He felt a sort of pleasure as if he had immersed his body in a cold,
clear stream. Yet, he took a step back, and shook his head.

He could not go away and leave the old woman. And more than that―he
could not live on and let that city stand without punishment. He was not
about to throw away his hatred.

"I see. That's too bad," the travelling bard exhaled, and bent over his
horse. "I'm sure we'll come across one another someday. You're the same
as us. You're not stationary―you're the drifting type. Just to let you
know, I \emph{do} have an uncanny eye for seeing people for who they really
are," he chuckled.

His long fingers, suited for playing instruments, touched the horse's
neck. The desert horse neighed. It set off on a trot on its stout, thick
legs.

The group disappeared quickly behind the cloud of dust they raised.

"No. 6," the old woman muttered as she stared into the fire. "The name
does not matter. That city, and all who live in it, will fall someday.
The Forest God will not forgive them."

The branches burned. The old woman's profile was lit up in the darkness
by the flames.

"The Forest God will not forgive. She will bring judgement down upon
them."

"Does that mean we won't have to get our own revenge?" \emph{Could we throw
	away this hatred, the memory of that scream?}

"No, \emph{I} will not forget," the old woman said. "I will not throw my hatred
away. It may be... too late for me. I have grown too old. I will
probably not live to see God's judgement with my own eyes. That is why I
will requite myself. If I could get even one stab―"

And the old woman had kept her word. Knife in hand, she had rushed upon
the mayor, who had come to the Correctional Facility to do an
inspection. The woman did not even manage to slice through his clothes,
much less stab him. She was shot through the chest, knife still in hand,
and died in Nezumi's arms as he rushed to her side. It was almost a
miracle that Nezumi~

was not killed along with her.

He was captured and thrown underground, where he met a man who called
himself Rou. Perhaps Rou had somehow been in contact with the old woman,
for he knew everything about Nezumi and accepted every part of him.

"I will pass down all of my knowledge to you," Rou had said. \emph{Sounds a
	lot like what God's voice said}, Nezumi had thought wryly.

That was two years before he met Shion.

\myspace

Nezumi stopped to look up at the sky. The sun's rays were fast losing
strength and were on the verge of wilting. Days were short in the West
Block, and nighttime came early. Since the sky was blocked out by the
looming figure of No. 6, the sun only shone down on this land for a
brief while.

No. 6 dominated even the skies. It tore apart and devoured a world that
was supposed to belong to no one.

Nezumi gently felt his back. Even now, it still throbbed sometimes. His
burn throbbed as if to command him never to forget.

Never forget. Never forget. Never forget. Never forget. Never forget.
Never forget.

\emph{I will not forget. I couldn't forget, even if I wanted to.}

He despised No. 6. It had killed his father, mother, and the old woman.
It had burned the forest down, and massacred the Forest People. It never
hesitated to crush human lives beneath its heel if it meant prosperity
for itself. It desired not coexistence, but its own sole reign on a
foundation of countless dead bodies.

Only its own prosperity, its own bliss, its own pleasure. What a
terrible existence it was.

He despised it.

The whirlwind of his hatred almost suffocated him. But, yet―

Shion lived in that city, too. For Nezumi, each and every thing in No. 6
had always been a target of his hatred. Not only did he hate the rulers,
he hated the citizens of that city as well who lived undeserved lives,
ignorant and lacking even the will to enlighten themselves.

\emph{Hate? Do you really? Then can you bring yourself to hate Shion as well?}

Nezumi's own self questioned him.

\emph{Could I bring myself to hate Shion completely?}

It was a bitter question every time. The bitter taste that spread in his
mouth was enough to numb his tongue.

\emph{My hatred is so strong, and my wound throbs so painfully, and yet....}

His began to walk, and stopped again. He could hear a melody.~

He strained his ears. He could hear it.

Nezumi quickened his step. He turned a corner and was greeted by a plain
dotted with boulders. On the edge of this plain stood a small
playhouse―his workplace.

A man leaned upon a white boulder, playing a string instrument. Both his
long upper garment and his pants, whose hems were gathered at the
ankles, were faded and dirty. It was impossible to tell what colour they
had been before. But the instrument in his hands was magnificent enough
to turn heads.

Four strings were drawn across an eggplant-shaped body, and that body
caught the rays of the weak evening sun and sparkled. If he squinted,
Nezumi could see that the body was carved with intricate symbols and
decorated with miniscule bits of gold, silver, and hazy silver.

It emitted a strange music. It was quiet yet clear, which added to its
sorrow. It gently stroked the sadness buried in the bottom of one's
heart. It did not agitate the sadness―it only smoothed it gently.

The man looked up. Their eyes met. Was it that bard? The man who had
invited him to join their travels long ago? He looked as if he could be,
yet he also looked like a complete stranger.

The man strummed vigorously. A melody was born.

Nezumi sang a scat along with the melody. He couldn't help it. The man's
music and Nezumi's voice blended together and flowed gently along. Like
the sky which was now beginning to lighten, the song, reminiscent of a
blooming flower, flowed like a large river under a cerulean sky.

It was a comforting feeling.

Nezumi's body felt lighter as a breeze swept through him.~

Floating on the wind, he rose high into the sky.

In the air, he danced high and low, turned over, glided in a wide
circle, and rose up.

The man's fingers stopped. Nezumi also closed his mouth.

"Don't stop," said a woman's voice.

"Keep singing," added a man's voice.

A throng of people had formed around the two.

\emph{I didn't even notice such a huge number of people.} For an instant,
Nezumi felt a chill down his spine. He was usually especially sensitive
to any presence behind him. Even the footsteps of a single child were
enough to make him react. He braced himself even at the sound of a
tumbling rock. Otherwise, he could not survive.

If there was any exception, it was Shion. Shion's presence was the only
one he lost track of at times. For some reason he couldn't figure out,
he could not perceive Shion.

"Let us hear more."

"Sing, sing!"

"Let us hear that song again!"

The man looked up at Nezumi and grinned. "How about it, young'un? Feel
like going for another?"

"Nah, I think my time is up. My nagging boss is here."

"Hey, Eve!" He was grabbed by the arm. Nezumi turned around and
skilfully pried the hand off.

"Hello, Manager. Looking dashing as always."

The stage manager, dressed in a red jacket and bow-tie, placed both
hands on his hips and set his feet apart. He looked to be at the peak of
displeasure.

"What are you thinking, singing in a place like this? These people
haven't paid us a cent! I don't know what you're doing, singing for
people who aren't even our customers. Ridiculous... what? What's so
funny?"

"No. Just wondering if you were enthralled by it too, manager."

"Wh―don't be an idiot!" stammered the manager. "I just came to take a
look, since you were taking so long. And I found you here, having your
nice little outdoor concert. Do work that brings in the money, I tell
ya."

The manager tugged at the ends of his handlebar moustache, then turned
to the man and smoothed his face into a suave smile.

"Say, sir, you have quite an impressive hand at playing. How'd you like
to come work with me? With your playing and Eve's singing, we're sure to
be the talk of the town. We'll draw in a huge crowd."

The man shook his head silently in a gesture of refusal.

"I wish you'd say that line to me."

"Eve, don't give me that crap," snapped the manager. "I pay you a fat
sum all the time."

"Oh, really? There must be some chasm between your perception of 'fat
sum' and mine."

The man stood up quietly. He drew close to Nezumi and whispered into his
ear.

"Are you also the wind?"

\emph{Wind?}

"A wind that blows over this earth as it pleases. It neither dwells nor
sets its roots down in one spot. Like us."

Nezumi stared into the man's eyes. They were light blue. Could he
possibly be that bard?

"You sing, we play," he continued. "That's just who we are. But why do
you dwell here? Why won't you be free, like the wind?~

What has trapped you and kept you here?"

The man drew back. He strummed just one string. Then he~

stowed his instrument in his bag and slung it over his shoulder.

"Best you free yourself soon, young'un."

Nezumi could not answer him. He only watched the man off.

\emph{What has trapped you and kept you here?}

\emph{Would I be able to cut these chains free? Could I cut my chains of
	hatred? And Shion, who binds me? Would I be liberated?}

\emph{Someday, I'll choose to live that way.}

\emph{That day will come.}

\emph{Then it's goodbye, Shion. And goodbye, No. 6.}

"Go home, go home! If you want to hear Eve's singing, come back to the
playhouse with some money. Big concert tonight!"~

The manager's gravelly voice rang out into the crowd.

Nezumi stood rooted to the spot as the wind blew past him, caressing his
hair.

\chapter{Shion's days}

\lettrine{I}{t was} raining. A drizzle―a mist, almost. But rain was rain, and it
drenched the nighttime streets and the people without umbrellas.

Before entering his house, Shion lightly ran his hand through his hair.
Drops of water dripped from his shiny white locks. He was wetter than he
had thought. The cool night air of early spring crept up from his feet.
If he didn't warm up soon, he would probably catch a cold.

Shion knew he would, but he continued to stand in front of the door,
unable to move. He was cold. His spirits were heavy. He felt reluctant
to see his mother Karan's face.

The back door of his house was wooden. The paint was peeling in several
places, and it showed clear signs of its age. A number of times, Shion
had suggested replacing it with a new one. But each time, Karan had
shaken her head.

"This is just fine. It's sturdy and strong. And besides, don't you think
it has its own unique flavour? I think it's much nicer than those awful
glittery metal doors."

His mother was concerned about the cost. But perhaps she really did not
mind the hassle of renovation; perhaps she really did have an attachment
to the worn back door. Shion understood that, so he never spoke of
replacing the door again.~

She was right in a sense. The thick oaken door exuded an ambiance not
quite found in stylish, vividly-coloured steel doors. The round brass
knob was also still firmly in place.

This door had not changed a bit since when Shion and Karan first moved
to Lost Town from their privileged-class residence in Chronos (in truth,
they had actually been exiled and not given any other choice of
residence other than in Lost Town, but strangely, neither Shion nor
Karan felt any lingering attachment to their old days). In fact, this
whole house had not changed much at all.

Over a year had passed since the destruction of the city-state, No. 6.
Confusion still remained, and everyone was still in the midst of groping
at how former No. 6 residents as well as nonresidents could adapt to
their new wall-less surroundings.

The terms "insider" and "outsider" (of the wall) had taken root, and
each regarded the other like a foreigner who spoke a different language.
The Insiders realized that they had been skilfully and rigidly
controlled, and appreciated their liberation from a society of
surveillance. But at the same time, they insisted that they did not want
to let go of their wealth―that they did not want their current lives to
be disturbed. The Outsiders criticized scathingly the crimes of No. 6,
which had built itself and prospered on a parasitic foundation. They
rallied for equal distribution of wealth and compensation for the abuse
they had suffered.

Currently, with the Restructural Committee at its centre, No. 6 (of
course, there were voices that called for a new city name, but no one
could spare the time to consider names. There was also the issue of
inter-city relations; for the sake of convenience, No. 6 was still
called No. 6) sought to restore peace and order; to swiftly establish
governing, judicial, and legislative bodies; and secure lifelines.

For the moment, they would use No. 6's governing institutions.~

They would designate the West Block as a special ward, and fast-track
the establishment of supply systems essential for life. They would
construct a temporary police force to dissolve the army and maintain
peace.

There were twelve members of the Restructural~

Committee―former No. 6 residents, and former representatives from each
Block. Under the Committee were twelve Sub-Committees, with a Committee
member at the helm of each.~

Shion was one of the youngest Committee members.

This past year, everything had changed. Like a crashing wave, like the
torrential waters of a rapid, like an avalanche, everything was
swallowed up, sucked into the spiral, torn asunder, and twisted around.
Things would only get fiercer in the future.

Shion exhaled, and gazed in turn at the old door, the battered brass
knob, and the small window out of which spilled a dim light.

Then, there were things that never changed. No matter what path the
world of mankind took, there were always things that didn't change, both
inside and outside of people.

\emph{Shion, I want you to stay as you are.}

Nezumi's murmur revived inside him.

\emph{Fight it. Fight with yourself.}

It was no order or command. It was a plea.

Nezumi had begged Shion as he spoke those words. \emph{Shion, don't ever
	change.}

\emph{Could I answer to the feelings Nezumi laid bare before me?}

Shion closed his eyes. He visualized the bazaar. It had been restored
into a free market, and it now offered a wealth of options and plenty of
fresh goods, unthinkable in the past. Karan often went shopping there,
too.

"It's twenty to thirty percent cheaper than shops in the city. They
might not be the most attractive, but you couldn't get better-tasting
produce anywhere else." Just yesterday, too, she had laughed as she
proudly laid out her misshapen apples and gnarled cucumbers.

\emph{But mom doesn't know―the Hunt took place in that marketplace. No. 6's
	army ruthlessly fired at those people―shot them through their foreheads,
	their chests―not even batting an eyelash.}

The air had been thick with despair, fear, and anguished screams of the
people; everywhere was stained with the stench of blood as corpses lay
left and right. An arm protruded from fallen debris; an army tank
crushed a torn leg as it passed by; army boots trampled those still
living and begging for help. It was the first volume of the inferno that
Shion was to witness later.

\emph{Mom doesn't know that.} And he was glad that she didn't. When he closed
his eyes, he could recall the sights of that day, no less vivid than the
day he experienced them. It was not only the marketplace. He would never
be able to forget the faces of the people loaded into the cargo hold;
the eyes of the man who had begged Shion to make it better; the stacked
bodies and the smell of death which lingered about him; the walls of the
Correctional Facility, crumbling into flames; the black smoke that rose
from No. 6. He would never forget. These images had branded him for
life, never to disappear.

And the fact that his index finger had pulled a trigger. The fact that
he had wilfully, not incidentally, killed another man.

Shion opened his eyes and looked up at the sky. Of course, he could see
neither the stars nor the moon. A raindrop slid down his cheek. It
touched his lips as it rolled down his face.

\emph{Ah, I'm alive.} Suddenly, he was hit with the realization that life was
within him. He felt it: right now, he was most certainly alive. Its
overwhelming reality almost suffocated him. He wanted to scream.

\emph{I'm alive. I'm alive. I'm alive. I'm alive. I'm alive.}

\emph{Nezumi, I'm alive}, he spoke to the dark sky, void of light. \emph{I'm alive
	and waiting for you. Even in those hellish surroundings, I was drawn to
	your eyes, your words, your gestures, your thoughts―and they supported
	me. Thanks to them, I was able to survive. And right now, I'm still
	alive.}

\emph{Can you hear me, Nezumi? I'm alive.}

A dog barked noisily. It was coming from inside the house.

\emph{What? A dog? Wait, could it be―}

Shion's mind was yanked from the past back into the present. His heart
beat fiercely. He pushed the door open. He was met with an earful of
barking. They were barks of joy and affection, not aggression or
apprehension. A dog with patched fur leapt up and jumped at Shion as it
barked. It wagged its tail fiercely and jabbed its snout against Shion's
thigh. Its black eyes contained even more joy than its voice.

"Dogs just fall at your feet, as always, huh?"

"Inukashi! And Rikiga-san, you too!"

Rikiga made an exaggerated grimace from his spot on the sofa.~

"Hey, Shion. A bit rude of you to notice me after doggy-boy, don't you
think? The proper way to go about it would be to cry,~

'Oh, Rikiga-san!' and pounce on me, like that dog there. And then you'd
add, 'Oh, Inukashi. You're here, too,' as an afterthought."

"Hah!" Inukashi bared his teeth and cackled. "Rude? Who cares? Me 'n'
you don't have no need for manners, old man. Just like how my dog
wouldn't need a fur coat. What do manners do? They certainly don't fill
my belly."

"Shut up," Rikiga snapped. "Don't lump me in with the likes of you.
You're practically half-animal. I'm a right and proper man, and a
gentleman at that."

"Gentleman? Whoa, I didn't know 'gentlemen' referred to guys who can't
live without money, women, and booze. Huh, well, I learned something
new. Since when have meanings changed so much? What has the world come
to?" Inukashi let out a long, doleful sigh.

Shion burst out laughing. It had been a while since he heard Inukashi
and Rikiga bickering like this. He laughed from deep down in his belly
for the first time in a long time.

"You two haven't changed at all."

"He's just got a large attitude for a mutt," grumbled Rikiga. "He has a
complaint ready for everything I do."

"And you're simple-minded for a human, old man. You fly off the handle
and have one of your tempers at everything I say. Dogs are way more
intellectual. Actually, dogs are ten times better than humans in head
and heart, anyway. Besides, I think you're closer to a monkey than a
human, old man."

"Yeah, you're right," Rikiga said angrily. "I am a monkey. Just the
sight of a dog maddens me to no end. Every time I see one, I feel like
tearing it apart with my teeth. \emph{Roar!}" Rikiga raised his arms and lunged
at Inukashi. Inukashi laughed mockingly while he nimbly danced out of
reach.

"My, aren't we full of energy." Karan came in. Rikiga froze. He cleared
his throat purposefully and sat down on a chair. He lightly brushed some
imaginary dust off the vest of his three-piece suit, and smiled amiably
at her.

"But please keep it down a little." Karan lightly rocked the baby in her
arms. It seemed fast asleep.

"Shionn!"

"Shh, Shion, not so loudly. I've just gotten Shionn to fall asleep,
finally―hm, rather confusing now, isn't it?"

Shionn breathed softly, wrapped in an old blanket which was so faded it
was impossible to tell what colour it had formerly been. His long
eyelashes cast shadows on his face, and his plump lips were parted
slightly. If bliss had a physical form, then this sleeping face was it.
It brought happiness to every person who beheld it.

"Looks like he's grown bigger since I last saw him," Rikiga commented.

"That's because he has," Inukashi said. "Now he's big enough to run
around and play with the dogs. Soon, he'll be able to gnaw meat off the
bone." Inukashi beamed and placed a soft kiss on Shionn's forehead.

"You're very good at raising children, Inukashi." Karan smiled.~

"I've seen many babies in my lifetime, but I feel like it's my first
time seeing a baby look so happy when he's sleeping."

"Ya really think so, Momma Karan?"

"I sure do. He trusts you from the bottom of his heart, and you're able
to be there for him and live up to his trust. You two really make an
admirable family."

A faint blush rose in Inukashi's tan cheeks.

"When my dog came home carrying Shionn in its mouth, I was actually
really pissed off," he confessed. "I thought about just abandoning it,
pretending I'd never seen it. Babies only make for baggage. I really
hated Shion that time for leaving his burden with me."

"―I'm sorry. I knew it was irresponsible, but... I had no other choice
but to leave him to you. I knew I could trust you with him."

Inukashi's black eyes turned to Shion.

"Shion, does that mean―"

"Hm?"

"Does that mean you trusted me?"

"Yeah." He nodded. It wasn't a front or a lie. In the confusion of the
Hunt, when he had taken the baby from its young mother, the only person
in Shion's mind had been Inukashi. Indeed, Inukashi was the only option
that he had thought of.

\emph{Inukashi will do something about it. He'll protect this little life with
	everything he's got. Inukashi will.} This was what he had thought.

Inukashi grinned. He raised a finger and twirled it around.

"You trusted me, and I lived up to that trust. That's what you're
sayin', right?"

"Yeah. I think so." \emph{Nezumi was probably the same. He trusted you, so he
	left everything to you.} Shion swallowed his unspoken words and shut his
mouth. He didn't know why, but he didn't feel like saying Nezumi's name
here.

"Hey, wait a minute, Shion. You're not saying you trusted Doggy-boy
above me, are you?"

"Ah, no―that's not what I... I just didn't associate you with babies,
that's all, Rikiga-san."

"Of course not," Inukashi butted in. "Because if you left him to someone
like this old man, the poor little guy would be sold off the next day.
Living babies fetch a pretty good price, ya know."

"What? Are you saying people put up babies for sale?" The blood receded
from Karan's face. Rikiga hastily waved away Inukashi's words.

"N-No―no, no, Karan, it's not like that. I would never do that. It was
just a bad joke. This one here always makes distasteful jokes. You can
imagine the headaches I get. You shouldn't take him too seriously."

"...You're right," Karan said uncertainly. "You would never buy or sell
babies. That's just absurd, isn't it?"

"Absolutely." Rikiga swelled his chest. "Karan, there's one thing I want
you to know: I ran lots of businesses in the old West Block. Among them
there were some that were―ah, not so savoury. Yes. Not savoury at all.
And that's a fact."

Inukashi hunched his shoulders. "Don't you mean 'most'? I think your
porno mag business was the most decent."

"Shut up!" Rikiga snapped. "Why don't you go off and gnaw on a chicken
bone or something? Karan, listen to me," he implored. "I never dared use
children or babies. I never used little ones to make my daily bread.
That's the truth. Please, believe me."

"Of course I believe you," Karan said. "I can't imagine you looking at
the young as a target for profits."

"Karan." Rikiga flushed and stepped closer to Karan. "Thank you. I feel
like your trust in me is all the support I'll ever need."

"My, Rikiga." Karan retreated half a step before smiling serenely. "I
never remember you as someone who could recite such a theatrical line.
You spoke frankly and straightforwardly, and you were careful with your
words."

Inukashi whistled.

"Heh heh, Momma Karan's got a good point. 'Your trust is all the support
I'll need' my ass. You don't even see that line in cheap novels these
days."

"Your mongrel brain has never even read a book before. No one's asking
for your input," Rikiga said sourly.

"My brain is a lot better off than yours. Mine's not swimming in booze."

"What did you say?" Rikiga said menacingly.

"What? Got a problem?" Inukashi shot back.

They glared at each other.

"Stop it, you two," Karan said exasperatedly. "Shion, don't just stand
there laughing."

Karan crouched in the shadow of the sofa and gently placed Shionn down
in a cradle. The cradle was a simple one made of wicker with no
embellishments, but its rounded shape was beautiful in its simplicity.
It looked very old, but showed no signs of wear.

A small golden plaque hung on the side.

\emph{For Shion, my beloved son.}

Just that short phrase was engraved into it.

"Hm? Mom, is this―"

Karan's hand gently rocked the cradle. "Yes. I used to use this when you
were a baby. You probably don't remember."

\emph{Or do I?} Shion thought. \emph{I feel like I remember hearing a gentle
	lullaby while being rocked back and forth, back and forth....}

"I didn't think I'd ever pull it out and use it again like this. I'm
glad I went through the extra trouble to bring it when we moved out."

When they had moved out of Chronos, the furniture and dishes they could
take with them were heavily restricted. Their house, their furniture,
the services, abundance, and their top-class living environment had all
been given to them precisely because~

Shion had been certified as elite.

Once this certification was revoked, they had to return everything that
was given to them from No. 6. The personal belongings that Shion and
Karan brought into Lost Town were surprisingly few.~

Was there a cradle among them? No. Shion would have noticed if there
was.

"I secretly brought it afterwards and stowed it away in the attic,"
Karan said.

"Why did you have to do it secretly?"

Karan's hand stopped.

"Because this... this was handmade by your father."

Shion's breath caught in his throat. It blocked his airway. As he
exhaled, his voice slid out along with it.

"What? My father?"

"Yes. Your father made this cradle for you." Karan pursed her lips and
averted her eyes from Shion.

"Dad was... a craftsman?"

"No. A geologist―that was his main occupation. And I think he was very
good at it. He was chosen to be a member of the revival project team,
after all."

Revival project team―it was a group of individuals chosen to make No. 6
a paradise on Earth, a utopia. The mayor, who desired to become No. 6's
absolute ruler, was a member; Rou, the scientist who schemed to have the
Forest God Elyurias under his control, was a member.

But their aspirations and futures morphed and drifted apart: Rou became
an underground man; No. 6 transformed into a monstrous city, and moved
down the path to destruction.

And Shion's own father had been one of those members. Shion was stunned.
That was all he could say. He was stunned.

"But mom, you said... you said before that my dad was loose with money
and women, a hopeless case and a step away from being an alcoholic. But
then you said he was really kind and sincere."

"I did. Because it's true." Karan pouted even more. She looked like a
sullen child. "He spent all the money that came in, and drank all day.
As soon as he found a girl he liked, he'd start a relationship with her
without even thinking of the consequences... even after we married, he
had girlfriend after girlfriend..."

"To have a lover while being married to \emph{you}, Karan―I don't believe this
man. Unforgivable." Rikiga clenched his fist, his eyebrows arching
angrily.

"You can say that again," Inukashi commented. "He's almost as corrupt as
you, old man."

"Hey, mutt. And what exactly is corrupt about me? I'm single, which is
why I could get away with playi―er, having a good time with women. But
if I got married―" Rikiga glanced furtively at Karan, and took a breath.

"I would love her for as long as I lived. I wouldn't even \emph{look} at other
women. And I would stop drinking. Not to brag or anything, but I think I
would make a good family man. Yeah."

"Bullshit," Inukashi spat. "You being a decent husband is just as likely
as my dog becoming a top chef."

Inukashi faced Karan before Rikiga could say anything in return.

"But Momma Karan, I can't even imagine such a slob being Shion's dad.
Their personalities are way too different."

"You could say that. But he was surprisingly good with his hands, and I
think Shion inherited that from him. Actually, this―" Karan gently
rolled Shionn's blanket back. He was wearing a plain white collared
shirt. The collar and breast pocket of the shirt was embroidered on the
hems with blue thread. A vibrant blue.

"He sewed this by hand. Same with the baby clothes and bib. He finished
it the day before he left us, and left them on the table with a letter
that said he wanted Shion to wear them on his first birthday. So when
you turned one, Shion, I put them on you. They were a little big back
then. But I think they're a perfect fit for this Shionn."

This was really, truly Shion's first time hearing such detailed things
about his father from Karan. Shion had never asked because his mother
never seemed to want to talk about it. He had lived his fatherless life
simply accepting that that was just how it was.

His father was loose with women and money, loved to drink, was a
specialist in geology, a member of the revival project team, had
surprisingly skilled hands, and left his family soon after Shion was
born.

Shion glanced over at the cradle. He gazed at the baby sleeping inside,
with the same name as his. He touched the embroidered shirt.

This was what his father left behind.

Shion sneaked a glance at Karan's profile.

So Karan's acquaintance with the core members of No. 6 had not been
through Rou. And his father, as a member, colleague, and holder of the
same ideals in his heart, had spent his younger days alongside the mayor
and those scientists.

"And Shion's papa left the house because... well, because of those women
problems?" Inukashi leaned forward.

"Hey, don't butt into other people's personal matters," Rikiga said.
"Not a tactful bone in your body, is there?"

"Hah, don't even talk to me about tact. You're dying to hear it
yourself, old man. You're trying \emph{so} hard to impress. Heh, I can't stop
laughing." Inukashi's teeth clattered together.

His comment had apparently hit the mark, for Rikiga blushed crimson and
fell silent. Karan neither appeared offended nor taken aback by
Inukashi's bluntness. She continued calmly.

"Maybe you're right. That might have been an indirect reason. I~

was young and I wanted him to stop being ridiculous. But ever since he
found out that Shion was on the way, he changed a little. All his
attention was on the unborn baby, and he even stopped drinking and
playing around with women, if only for a short while... he picked up
drinking again not long after. But I felt like if he kept on being like
this, maybe he \emph{would} turn into a decent family man. Inside, I was proud.
That's why I know he didn't leave the family because of a woman... he
had another reason..."

"Because No. 6 was changing."

Karan blinked several times at Shion's short utterance.

"You can tell?"

"I had a vague idea."

As No. 6 took shape into a city-state―a totalitarian, authoritarian
state―many members withdrew from the revival project team during the
process. Some were intentionally removed, while others left of their own
will. Strictly in the realm of possibility, perhaps some had been deemed
a hindrance and murdered secretly. It was more than likely.

"He was overwhelmed by the fact that No. 6 was gradually―no, actually,
quite quickly―morphing as it developed its city structure. He was
apprehensive, but he had no idea what he could do about it. Maybe he was
afraid. I remember hearing him say over and over to himself, 'This isn't
possible. This can't be happening.' Then, one day... it hadn't even been
a month since Shion was born... he said to me, 'Let's leave No. 6. We
can still escape now. But soon, we won't be able to leave unscathed from
this city.' His face was so grave when he said it. He must have given up
on No. 6 altogether by that time. He probably thought, 'I can't live
here anymore. One day I'll suffocate, and end up taking my own life, or
get killed if I don't.' That's why he tried to convince me to escape
somewhere far away from No. 6, and start a new life in a strange land,
just the three of us."

"But you said no, mom."

"Yes." Karan let out a long breath. "I said no. I told him clearly that
I wasn't going to go with him. I just couldn't bring myself to believe
what he was saying."

Karan averted her eyes and looked down as if Shion's gaze was too
blinding to bear.

"When I asked him where we would go once we left No. 6, he said he
didn't know. Then he just burst into a joyful laugh and... said it
wouldn't be so bad to wander freely like the wind. But I had a baby that
wasn't even a month old yet. Apart from the six city-states, I knew
there were only barrens and tiny fields left on this earth. I couldn't
bear to think of forcing such an arduous journey on a tiny infant. I
supposed that as long as I stayed inside No. 6, we wouldn't have to
starve or get sick. I couldn't convince myself that he could protect us
better than No. 6. I couldn't trust him."

Yet another sigh escaped Karan's lips.

"I don't know if I made the right decision that day. I certainly don't
regret that I didn't go with him. But the fact is that I had already
become dependent on No. 6. I was trying to live a life of dependence. I
lived for years and years without even realizing.... I was completely
ignorant of No. 6's rotting smell, when he had been one of the first to
detect it. And that―is a very regrettable thing."

"And you have no idea where dad is right now?"

"No, I don't. I don't even know if he's dead or alive. But knowing him,
I have a feeling he's living freely, doing whatever pleases him."

Karan's voice dropped slightly.

"Shion, would you want to meet your father?"

"Well... I've only known you, mom, so I don't really feel any sort of
yearning towards him. I don't really miss him. But I am curious."

"Curious?"

"Curious about why you decided to talk to me about dad so suddenly. You
never talked about him before."

Karan's lips moved, but no words issued from them. A short moment of
silence followed. It was so still that Shionn's slumbering breathing
could be heard crisp and clear.

\mybreak

"K-Karan―"

Rikiga stood up abruptly.

"Ah, um―so, d-do you still have trouble forgetting about, ah, your
former husband? That is to say, um, that you're... waiting for him to
come home, or... is―is that how you still feel now? Or are you, ah, free
of any of that kind of... er, attachment? As in, um, if something were
to happen, would it result in..."

``What the hell kind of language are you speaking, old man?'' Inukashi
jumped in. ``I think a newborn puppy would make a bit more sense than
you. Right?'' A patchy-furred dog that was lying at Inukashi's feet
opened its eyes a crack. It gave a wide yawn.~

Karan smiled.

"I'm not waiting for him, Rikiga," she said. "To me, he's already a man
of the past. Of course I \emph{do} hope he's still alive somewhere, but―"

An unmistakable joy crossed Rikiga's features.

"Can't get any more obvious than that," Inukashi muttered.

"That's absolutely right," Rikiga said enthusiastically. "We can't dwell
on the past forever. If we're going to dwell on something, it should be
the future. Tomorrow is so much more important than yesterday."

"I agree."

"R-Right? You think so too, don't you? So... ah, Karan, wouldn't you
agree that, um... someone with whom you can live in the future is, ah,
more important than someone with whom you lived in the past?"

"Yes, of course. That's why I invited you to dinner this evening. I
wanted to dine with you."

An exclamation issued from Rikiga's lips that sounded like something
between "oh" and "ah".

"K-Karan, is that true? Y―You thought of me, and that's why―"

Inukashi tugged at Rikiga's jacket.

"Old man, old man. Sorry for shattering your dreams, but I've been
invited, too. You're not the only one. Don't you forget that."

Rikiga scowled heartily and made a swatting gesture as if to chase away
flies.

"Shoo! Shoo! Show yourself the door and take that dirty mongrel with
you. You probably asked yourself over with a mind to take advantage of
Karan's cooking."

"As a matter of fact, I \emph{did} get a proper invitation. Right, Momma
Karan?"

"Yes, of course. Both Inukashi and you, Rikiga, are very important
teammates to Shion. And you two are very good friends to me. That's why
I wanted both of you to come. I don't have much, but I do have lots of
freshly-baked bread. I also have homemade jam and stew that's been
simmered nice and long. Just a minute, I'll get it prepared. Shion, can
I get some help?"

"Sure."

Karan opened the door to the kitchen and disappeared beyond. The aroma
of bread and stew wafted into the room. The two distinct smells
stimulated the nose. Inukashi's nose twitched eagerly.

"I'll help, too! Being treated to a free meal goes against my morals."
He chuckled. "Did you hear that? Fresh-baked bread and stew. Just the
sound of it makes me drool, but then you \emph{smell} it, and... oh, this is
the best. My stomach is grumbling like no tomorrow. Aren't you hungry
too, old ma―hm? Old man, what's wrong? Your eyes aren't focused. What're
you spaced out about?"

"...Teammates... friends..."

"Huh?"

"Karan says I was a teammate. A friend. To Karan, I was only ever just a
member of a team, just one of her friends..."

Shion and Inukashi looked at each other. Inukashi tilted his head.

"Hmm. Well, 'let's be good friends' is a pretty typical rejection
phrase. Dogs would be more straight up and tell you they hate your fur
or that your teeth are gross, but humans like to take the long way
around. Hah, but really, old man, were you planning on seriously
proposing to Momma Karan?"

"... I was serious," Rikiga said gloomily. "Work is picking up for me,
and I've got money enough to spare. I was confident that I'd make Karan
happy."

Following the destruction of No. 6, merchandise began to find its way
out of the walls. Rikiga took advantage of the chaos and bought them off
at low prices.

He hoarded artwork and handiwork, electronics, paintings, jewellery,
furniture, medical machines, cars, clothes, office supplies, and even
toys; when things began to settle, he sold them at high prices and made
a handsome profit. Now he directed and managed a publishing company and
printing company, issuing a weekly informational magazine and a daily
paper.

``Well, you \emph{are} a rising star in the entrepreneurial business,
Rikiga-san. Rumour says you're quite the power player.''

"You honestly think so, Shion?"

"Of course I do. You and Inukashi don't need fake compliments from me,
do you?" Shion took his jacket off and rolled up his sleeves.

"I keep telling you to stop lumping me in with doggy-boy," Rikiga said
wearily. "But enough of that. So, Shion, you've acknowledged me, then?
You think I'm fit to be married to Karan?"

"Huh? Oh, I―I didn't mean it like... well, uh, I don't think my mother
ever plans to remarry. She was telling me the other day how satisfied
she was with this life and how she'd like to keep being a baker for as
long as she can."

It was true: Karan's life had not changed much, at least on the outside.
She ran her small bakery tucked away in a corner of Lost Town, chatting
with regulars and kneading dough for the first loaves in the early hours
of the morning.

That was her regular routine, and she repeated it every day. Even in
intense turmoil, Karan continued to fire up the oven, bake bread, and
lay them out at the front of the shop. The people wept through their
mouthfuls of small rolls and muffins.

"The world has crumbled from beneath our feet, but this still tastes the
same. There are still things in this world that haven't changed."

Those were the words of an elderly man, a regular customer. He had
murmured the words over and over, his cheeks wet with tears. Shion
encountered the same sort of murmur many times.

\emph{Something is here which will never change}―for the people, that feeling
of certainty signified hope and a reason to keep living.

"Your mother is an incredible woman," Nezumi had said, with a rare note
of awe in his voice.

It was on the day he had woken up.

On the day that everything had ended―no, began―Shion had dragged his
exhausted and battered body back home to Karan.

After a somewhat brief reunion embrace, he had collapsed into bed with
Nezumi and slept like a log. His slumber was deep enough to cut off all
of his senses, and when he woke, it was already noon of the following
day. It was the time of day when the sun was shining straight from
above, emitting a faint reddish glow.

There was no sign of Nezumi beside him. There was one blanket folded
neatly and placed at the foot of the bed. Shion placed a fist on top of
the folded blanket. A strangled noise subconsciously escaped his throat.

\emph{Nezumi, have you gone? Just like you did four years ago?}

Four years ago, on the morning after the storm, Nezumi had disappeared
from Shion's side. He had disappeared starkly, as if everything from the
night before had been an illusion.

Back then, they had only just met. They barely knew anything about each
other―not a single thing about the pasts they shouldered, the future
they beheld, and the emotions they kept within their souls.

But it was different now.

Yes, there were still things they could not grasp, things they still
could not understand about each other. There was a chasm between him and
Nezumi that he could never fill, no matter how much he struggled to.

\emph{I know. I know. I know. We knew, but we still lived together. Not in the
	past, nor in the future, but in the present. We lived the present
	together.}

\emph{But now you're leaving again without a word?}

Shion's thoughts got as far as that before he shook his head vehemently.

\emph{Of course not.}

\emph{We've spent so much time together, and overcome hell together.
	He wouldn't vanish without a word. That's not what our relationship is
	like. And besides, it would be risky for him to move around with such a
	serious wound. I can't imagine Nezumi being so reckless.}

He caught a whiff of the aroma of coffee and bread. It was the smell of
waking up.

Shion opened the door into the living room.

"Oh, is the prince finally awake?" Nezumi was smiling with a coffee cup
in hand. "I can't say much about you, though. I woke up not too long
ago."

Shion swallowed his sigh of relief, and with great effort feigned a calm
demeanour.

"Nezumi. How do you feel?"

"Couldn't be better. Or, at least I wish I could say so. It's taken its
toll. You?"

"Couldn't be better."

The cup twirled around in Nezumi's hand.

"Confident now that you're on home turf, huh? But it's a good thing that
you've got enough energy to act tough. But might I suggest taking a
shower and spritzing yourself up before you start trying to be a tough
guy? I think even King Lear wandering the wildness would look a little
more put-together than you."

Shion peered into the mirror hanging on the wall. His face and hair were
covered in streaks of blood, dirt, and dried sweat. His shirt was torn
in several places, and his right sleeve looked like it was about to fall
right off.

\emph{He's right. I don't even think King Lear at his maddest would look as
	bad as this.}

He felt a strange urge to laugh.

"So, your Majesty, will you be having a bath first? Or shall I prepare a
cup of the very best coffee for you?"

"What an incredible honour it is to be served coffee by you."

"Your mama just treated me to some delicious bread―the very best, I must
say―and it was so good I felt like my tongue would melt. I think pouring
you a coffee would be a small service compared to that."

"Oh―mom..."

"Your mama has been run off her feet with work since morning." Nezumi
jerked his chin. Shion could feel the muffled buzz from beyond the thin
wall.

"Huh? She's opened shop?"

"Looks like it. Says the only thing she can do is bake bread, so she's
going to keep doing what she can. Even in this chaos, the oven is still
fired up and the danishes are still baking. She says in the evening,
she'll make some cravats for me."

"I see... sounds like what she would do."

Nezumi put his cup down, and his eyes moved towards the white wall.
There was no smile playing on his lips anymore. It was as if his gaze
pierced through the wall, focusing on Karan who bustled about on the
other side. A darkness lurked in the depths of his look.

"Your mother is an incredible woman," Nezumi said. His voice was so low
it was almost a whisper, but there was definitely a note of awe in it.
"She's like the Almighty Mother. I didn't know there was someone like
that inside No. 6. but she is one―and she's lived here as a citizen."

"...You're right."

A person could never be completely dyed into one colour, no matter the
circumstances. He may be dyed temporarily, but he would one day regain
his own colour, and would always attempt to live loyal to himself. He
would try to draw forth many different colours into this world.

Indeed, that was hope itself.

How much could one trust the days that lay before him, the people in his
life, and hope? Eventually, this question would be posed to Shion
himself. He knew that Nezumi would have to take on the same assignment.

\emph{Nezumi, could we ever completely believe in people? Not loathe, not
	condescend upon, not abuse, but believe?}

\emph{Could we do it?}

The aroma of coffee filled the air.

"But first, you need a splendid brunch with the best of bread and the
best of coffee. At least take today to rest and think of nothing at all.
Your mama's gutsy way of living is too much for us youngsters to handle
yet, I think."

"You're pretty modest."

``This is 'away' territory. I'll watch my mouth,'' Nezumi said lightly.~

``And truth be told, I'm a little tired. I haven't the slightest
objection to sleeping, eating good bread, and going back to sleep again.
It's quite a nice vacation.''

"And you'll get to eat cravats in the evening."

"Yes, that." Nezumi snapped his fingers. "I've never had the pleasure of
beholding a pastry shaped like a tie. And baked by your mother's hands.
It must be delicious."

"Once you've had them, you'll be at their mercy. They'll come to haunt
you every night in your dreams."

"I imagine it'll be like how Hansel and Gretel felt when they found the
house made of sweets. It's one of those things where 'pleasure and
trouble come arm-in-arm with each other.'"

"Someone's proverb?"

``I just thought of it now. And you better remember it: it'll illuminate
the path to your fate.''

A cup of coffee was placed down in front of him.

"Drink up. I've made it a little strong with lots of milk, just the way
your Majesty likes it."

"What? We've never had coffee together before. How do you know how I
like it?"

"I just know. I told you before―you're hopelessly easy to read, and yet
also hopelessly hard to understand."

"I could say the same for you."

"But I'm not as difficult as you."

"You're one to talk. You should be the last person to call me
difficult."

"How the hell am I difficult?"

"It would take me until tomorrow morning to list them all."

"Huh," Nezumi huffed. "I'll entertain you with my presence until
tomorrow morning, then, so let us hear all the details."

"See, that's what I'm talking about." Shion sipped his coffee. Its
fragrance, bitter taste, and mildness spread inside his mouth. The rolls
on the table were also delicious. As Nezumi had said, they were so good
he felt his tongue would melt.

The taste soaked into the very core of his body and soul. It was the
unmistakable taste of his mother's cooking.

"One minute you're as stubborn and quick to anger as a child, and the
next minute you've got sound judgment and no attachment to anything
whatsoever. You're constantly changing your mind, and you're in a
different kind of mood from one minute to the next. I can't see how
anyone can be more difficult than you."

"Uh-huh, I see. Not gonna candy-coat anything, are you? Well, let me say
my bit, Shion―"

"Go ahead. You have nothing against me."

Nezumi scoffed. "Only indecent people go on about how decent they are."

"So you're saying you don't think you're decent?" Shion retorted.

"Erm, well... that's not to say I'm not a decent person, because I
always am.... Damnit, you're getting quicker with your comebacks."
Nezumi twisted his mouth and narrowed his eyes.

Shion almost snorted at Nezumi's hilarious scowl.

Everything seemed beautiful―this casual conversation, the gentle
atmosphere, even the rays of the setting sun coming in through the
window.

It was a gem of a moment which had existed between the storm that had
passed and the storm Shion was about to face. It was also a tender
memory that Nezumi had left behind for him.

\myspace

Nezumi set off, and Shion remained. Their tangled and overlapping fates
had separated, and were now drifting apart.

When would they intersect again?

"Hey, Shion." Rikiga's face drew nearer. "I want you to give me a hand."

"Give you a hand?"

"I'd like you to tell... well, hint to Karan―discreetly, mind~

you―how right I am as a marriage candidate for her."

"What? But, well... I'm not so sure I can―"

"I'm serious. I want to propose to her because I'm confident that I can
make her happy. Of course, if Karan wants to keep running her bakery,
she can do it for as long as she likes. I know!'' he exclaimed, ``We can
renovate the entire place. Make the shop bigger, put in a large front
window. Make it glamourous. We'll fix up the living quarters, too, and
add more rooms."

"I don't think that's what my mother would want. She seems pretty
satisfied with what we have already."

Rikiga cradled his head in his hands.

"Oh, Karan. What a virtuous woman, so modest in her wants.~

She's the very embodiment of a goddess."

"I dunno, I think she's a bit on the chubby side to be a goddess,"
Inukashi butted in. "But Momma Karan is pretty, and way too good for
you, old man. And FYI, I think the problem with the kind of women you
hang around with is that they want too \emph{much}. When they look at someone,
they see a gold coin where his face should be. Either way, old man,
Momma Karan only sees you as a friend. The ends of her hair are a more
likely marriage candidate in her mind than you. Hah, just give it up."

"Don't think a brat like you can interfere with adult matters."

"Fine, fine. Mr. Adult can keep putting up a hopeless struggle in his
adult matters. Shion, let's go help Momma out. I'm dying to have
dinner."

"Sure."

They could hear Rikiga let out a troubled sigh behind them.

Dinner was enjoyable. Everyone ate, talked, and laughed plenty.

It was fun―very fun.

\emph{If Nezumi were here}―his heart wavered in uncertainty. If Nezumi were
here, he would have sat across from Shion, praised Karan's cooking, and
sneered coolly as he looked on at Inukashi and Rikiga arguing. He would
have wielded his fork and spoon with elegant grace, and would have made
Karan happy by finishing everything on his plate.

Nezumi, where are you? What are you doing right now?

\emph{I haven't seen you for a year now.}

Three hours later, his companions set off for home into the night.~

Inukashi left in high spirits, his backpack bursting with bread. Rikiga
looked thoroughly depressed.

``Mom,'' Shion called out as he cleaned up. Karan, who was measuring
flour, turned only her head to look at Shion.

``What is it?''

``Why did you invite Inukashi and Rikiga-san over today?''

``Hm? Well... I don't think I really had a reason. I thought it'd be
nice to have some people over for dinner for once. You've been so busy
you haven't even had time to sit down and enjoy a good meal.''

``So you did this out of concern for me?''

Karan turned her whole body towards her son this time, and shook her
head slightly.

``It's not like that. It's just―Shion, have you noticed? You don't~

smile or laugh a lot anymore.''

``Huh?''

``It's been a while since you laughed out loud like you did today.''

Shion touched his own cheek. His skin felt hard and tense beneath his
fingertips. Karan was looking steadily at Shion's fingers.

``Your job at the Restructural Committee must be tough.''

``Yeah. But, I mean, we \emph{are} making an entirely new organization with a
new set of functions. We've got people from all sorts of positions in
one place. It's not like I wasn't prepared to deal with difficulties.''

``Are things not going well with Yoming and his group?'' Karan raised
her chin. Her tone and gaze grew hard, as if she were challenging
someone. ``I imagine you two must... think very differently. Shion, are
Yoming and them giving you a hard time?''

Shion was at a loss for an answer.

``I knew it,'' Karan said. ``I had a bad feeling when I found out Yoming
was selected to be a member of the Restructural Committee.''

``Do you know Yoming-san well, mom?''

A shadow flitted across Karan's eyes.

``I thought I knew him. He's Lili's uncle, after all, and he used to
come to the bakery a lot. He said No. 6 had murdered his wife and son.
He taught me what No. 6 truly was, back when I still had no idea. He
helped me. He's a very intelligent person, isn't he?''

``Yeah. He is smart. He organized the resistance. He's the one who
gathered all the people who opposed No. 6 and made them into an
organization. His actions were one of the things that triggered No. 6's
fall. It's only normal for him to be chosen as a member of the
Committee.''

``Normal? Is it really? Shion, do you really think that Yoming is a
suitable individual for the Restructural Committee? I... I just can't
seem to convince myself that he is.''

``Mom...''

The windows rattled. It seemed like the wind outside was picking up. It
would sweep the clouds away and bring an end to the rain.

Tomorrow, a blue sky would probably open up above them.

``He hated No. 6 with a passion,'' Karan continued. ``And for good
reason, too. It took his most precious family away from him. He wasn't
blinded like the rest of us. He saw No. 6 for what it was precisely
because of his hatred for it. And this was even while he was living
inside the city.''

Karan ran her hand down the bag of flour beside her.

``Hatred was his energy, and it was effective for destroying No. 6.
But... but that energy isn't going to create anything new. That's what I
think, Shion.''

There was a forlorn note in his mother's voice that made his heart ache.

One had to either throw away one's hatred or overcome it in order to
create something new. Loathing could never become a force for revival.

``Just a little before the chaos came to a head in No. 6 because of that
strange disease... when we'd started to see the clear signs of
destruction beginning... he came here, and we had a long talk. And he
said to me, `I've lost faith in you.'''

``Yoming-san told you he lost faith in you, mom?''

``Yes. Shion, there are a lot of things that I don't know or can't
understand. I've never \emph{wanted} to know or understand. And that's a very
shameful thing indeed. If only we adults had been a little smarter,
perhaps we could have saved Safu, too...''

``Mom, let's get back to talking about Yoming-san,'' Shion said in a
firmer tone as if to cut across his mother's mourning words. His
thoughts and feelings for Safu were like a bottomless swamp. No matter
how much he repented or apologized, there would never be an end for him.
No matter how many tens of thousands of words he piled upon, no matter
how much he kept praying, he would never be forgiven.

So at the very least, he would not forget.

He would remember Safu and the wish she had passed onto him until the
hour of his last breath.

Karan blinked, and nodded slightly.

``Yes, he lost all faith in me because I didn't agree with him
wholeheartedly. He was trying to become a hero, a hero who overthrew a
dictator state. I don't know, it wasn't for revenge, or anger at being
oppressed all this time... I felt like he was being taken over by a sort
of―desire?―to become a hero whose name would go down in history. Yoming
said that casualties were inevitable in a world that was changing. He
dismissed all the people bleeding and dying and said it couldn't be
helped.~

For him, if a thousand people had died to save ten thousand, their lives
would not have been lost in vain―but isn't there something wrong about
finalizing it like that? There's something wrong about converting human
lives into numbers. And I think it's wrong for a hero to stand on a
pedestal built on human sacrifice.''

``...Yeah.''

``Shion, can you put up a fight against Yoming?''

\emph{Fight? Is Yoming-san someone I have to fight? Is he an enemy?}

Yoming's group continued to assert that the temporarily-established
Restructural Committee should be dissolved and an entirely new
organization created in its place. It was clear that if they had their
way, the core positions of the Committee would be dominated by members
of Yoming's group. It would be a considerable departure from the
Committee principle, founded upon the idea that the Committee was a
place where members of many backgrounds and affiliations could exchange
opinions freely. But by now, Yoming and his group had stopped listening
at all to the objections and opinions of Shion's group, the minority.

\emph{Something has to be done. I have to do something.}

No. 6 was already a proven example of what resulted when justice lay in
the hands of a few and all others were banished.~

The damage was still raw, still throbbing; why was Yoming's group
attempting to tread the same path?

\emph{I have to do something―}

``Shion, you've gotten so thin.'' Karan's gaze and tone turned to those
of a mother. It was a glimpse of a mother's love, the foolish, fierce,
pure, and selfish love that worried only of her own child's welfare and
wished for only his happiness.

``You should quit the Restructural Committee if it's such a burden on
you. There are so many other ways to make a living. You said yourself
once that you wanted a job that involved kids. Why don't you look for
one?''

``No...'' Shion slowly shook his head. ``I still have things left to
do.''

``But...''

``Mom, he told me not to run away. I have to stay here because I have a
job to finish. He said I can't turn my back on it now. I don't want to
go against those words.''

Karan did not question who ``he'' was. Instead, she silently gazed up at
her son.

The wind grew even fiercer. The windows rattled restlessly.

Karan let out a subdued sigh.

\mybreak

``I suppose life would have been a little less burdensome if you'd been
whimsical like your father.''

``Oh,'' Shion said in realization. ``That's why you suddenly decided to
tell me about dad.''

It was one way to live: taking nothing upon oneself, casting off any
troublesome loads, turning one's back on everything.

\emph{Your father chose to live that way.}

A mother, watching her son struggle with reality, had told him the truth
about his father.

\emph{But I can't. I can't live like dad did.}

\myspace

\emph{Shion... don't run away.}

\myspace

\emph{Nezumi's words are supporting me. Nezumi never ran away. He never
	retreated in the face of fate, or from reality. And I was there beside
	him.}

\emph{Safu passed her legacy on to me.}

\emph{I can't run away.}

\emph{I can't betray them.}

\emph{I have to fight―not for anyone else, but for me to remain as who I am.}

He crouched and kissed his mother on the cheek.

``I'm going to sleep. Good night, mom.''

Karan's fingers gently stroked Shion's white hair.

``Good night.''

Her lips twisted slightly, as if she were forcing herself to smile.

\myspace

A tiny mouse was curled up on the bed.

``Tsukiyo.''

It raised its head at the voice, and squeaked softly. Shion offered some
crumbs of bread and cheese to Tsukiyo, putting them right up to his
nose. Tsukiyo twitched his whiskers two, three times, but did not touch
any of it.

When Shion petted Tsukiyo's back with the tip of his finger,~

Tsukiyo closed his eyes dreamily.

Hamlet, Cravat, Tsukiyo. Out of the three mice Nezumi kept, only this
Tsukiyo remained with Shion. He was a small creature, but possessed both
wisdom and intelligence. He was likely a descendant of the wild mice
that lived deep in the forest alongside the Forest People.

Shion had simply assumed that because this mouse was no ordinary mouse,
it would have the same lifespan as a human.~

But these days, he could see Tsukiyo ageing and beginning to weaken.

The average lifespan of a mouse was anywhere from a year and a half to
two years. Even a pet hamster would live to three years at most.

Tsukiyo was slowly nearing his end.

``Tsukiyo, hang in there. You have to live to see your master come
home.'' Shion stroked him gently with the flat of his finger.

\emph{Cheep-cheep.}

Tsukiyo chirruped contentedly, and closed his eyes.

\mybreak

``What is this?'' Deep creases formed between Yoming's~

eyebrows.

They were on the first floor of the Restructural Committee headquarters,
the former city hall which used to be called the Moondrop.

Shion and Yoming were sitting across the table from one another in a
small meeting room. Shion had called Yoming out.~

An electronic sheet was laid out on the table. Yoming had just glanced
down at the screen and furrowed his brow.

``This is proof that you diverted the funds of former No. 6.''

``What? What are you on about?''

``You have always been, and still are, in the post of managing the
enormous resources of former No. 6. You took advantage of your position
to claim much of that money as your own. I'm talking about
embezzlement.''

``Absurd,'' Yoming sneered. ``I'm busy. I have no time to be playing
along with a little boy's joke.''

``Joke? Is it?'' Shion pressed. ``No. 6's resources were left exposed
for some time because management simply wasn't functioning. In that
time, a third of the funds have disappeared. Gold especially―about sixty
percent has been lost.''

``And you're saying that's my fault?''

``Yes.''

``Don't you dare. Yes, I may be in charge of managing the funds. But how
did you expect me to keep guard over the gold on top of everything else
during that chaos? I shouldn't have to be responsible for that.''

``The gold wasn't simply stolen. It was smuggled out, and it was
premeditated. If it wasn't planned beforehand, how do you explain the
fact that the other forty percent still remains? Thieves would take all
the gold away. Not only that, the gold was in the innermost part of the
underground vault. No matter how bad the confusion, it would have been
exceedingly difficult to carry out several tonnes' worth of gold without
being noticed. Even professional bands of thieves wouldn't have managed
it. In fact, it's outright impossible. Yoming-san, let me say this
again. The gold wasn't stolen. It was smuggled out, and it was
premeditated.''

``And you're saying the smuggler is me?''

``I can't think of anyone else.''

Yoming drew his chin back and smiled blandly. ``Are you calling me a
thief? What an accusation. If you don't take that back soon, I'll sue
for libel.''

``You needed a very large amount of capital to expand and maintain the
power of your group. That's why you turned to No. 6's funds. It was the
easiest, quickest way.''

``Are you really trying to accuse me?''

``This data―'' Shion jerked his chin at the table. ``Is a copy of your
application and authorization forms that you submitted in the
Committee's name to rent out a cargo jet. Both have your own handwritten
signature. This cargo jet was used in a trip to No. 4 and back. And
this―''

Shion swiped the screen with his hand, and new data appeared. Yoming
stared intently at the series of numbers without even blinking.

``This is a list of your personal assets provided by No. 4's bank. Quite
large, isn't it? Fit for a king. I think it's safe to assume that these
assets have all been converted from gold. The numbers add up. And
there's more.''

He moved his fingers.

``These figures are special benefits that you handed out to your group
members. This is also quite a lot. Not even the executives of former No.
6 received this much.''

``...We members placed our lives on the line to fight with No. 6,''
Yoming said quietly. ``We are perfectly entitled to that amount.''

``That is for the Committee to decide, and not for you to make your own
judgements about. Many other people fought with their lives in the
balance. Many did not live through it, either, Yoming-san.''

Shion stood up and began to roll the electronic sheet up.

``You misused public funds by handing out compensation on your own sole
judgement and pocketing money for your own use. It's unmistakable
treason. You've betrayed every single citizen.''

The door burst open. Two men stepped inside. They were second and third
in command in Yoming's group. They were both in their mid-thirties with
dark brown hair.

``You've gone and done it now, Yoming.''

``How could you have perpetrated such evil behind our backs? Shame on
you!''

``Behind your backs?'' Yoming retorted. ``That's ridiculous, you all~

were well aware that...'' Yoming's breath caught. He chewed his lip. The
colour rapidly receded from his face.

``Shion, you tricked me.''

Shion maintained a steady gaze at the man's pale face, and said nothing.
Shion's eyes did not budge.

``...I knew you were dangerous,'' Yoming said softly. ``I underestimated
you because you were still a young boy. That was my mistake.''

``We all make mistakes in life, Yoming-san. But yours just ended up
costing you your life.'' He snapped his fingers. A door slid open
leading to the next room, and two more men came in. They were of such an
enormous stature that one would have to crane his neck to see their
faces.

``What do you suppose you can do with me?'' Yoming said defiantly.
``Give me a public hanging?''

``Of course not. You were a distinguished member in the fall of No. 6. I
won't be so unforgiving. On the basis of the Committee's judgement, we
will grant you a bonus for your deeds, and a public pension until you
die. But we will seize all of your personal assets in No. 4. You are, of
course, dismissed as a member of the Restructural Committee, and you
will be stripped of all of your qualifications. There will be
limitations implemented on your activities and place of residence. You
are prohibited from moving out of your designated residence, regardless
of what the reason may be.''

``If I don't comply―''

``Then, I cannot guarantee your safety.''

``Heh, so it's basically an outwardly-unoffensive imprisonment. A modern
version of exile. If I get shot through the head for acting without
permission, no one will blame you. No one would be able to blame you.''

The gigantic men moved to stand behind Yoming. Yoming strode toward the
door, half-shoving them out of the way. Then he stopped, and turned
around.

``Shion, you have potential to be a leader like no other. I, or even
that mayor, couldn't compare. Someday, you'll try to dominate over all,
try to have everything within your grasp. You'll reign as a cold,
ruthless, and exceedingly good dictator.''

Laughter―dry laughter rang out and echoed inside the room.

``And when that happens, I wonder how Karan would look at you? What kind
of eyes would she behold her son with, the son who's turned into a
monster?''

One of the men placed his hand on Yoming's shoulder. Yoming brushed it
away, and walked out into the hallway. The door closed.

``Can't even go out without a last bitter complaint.''

``He doesn't know when to stop.''

Number 2 and 3 looked at each other and shrugged comically. They
simultaneously turned back to Shion.

``Shion, we've been tricked, too. We didn't even dream that he'd
embezzle public funds.''

``Really? This data lists your two names clearly as the recipients of a
large sum of benefits.''

Shion smiled serenely at the two men, who had begun to turn pale.

``But I've erased that part. Without your co-operation, we would not
have been able to bring Yoming-san's crime to light. I'm grateful.''

``So we're...''

``I myself have nothing to reprimand you about.'' Shion extended his
hand towards the two. ``Please continue to work hard for No. 6. We must
join all our forces to overcome this difficulty. We need your help. I
hope you're willing.''

The colour rose in the cheeks of the two men. They grasped Shion's hand
and nodded enthusiastically.

``See you in this afternoon's meeting, then,'' said Shion. ``I plan to
report this incident in detail from the top. I'm counting on your~

assistance.''

``Yes, we'll testify properly. We'll also show our respect for your
swift response and impressive judgement in the matter. You're really an
incredible leader for the next generation.''

``It's an honour. But it's a little embarrassing to receive such glowing
praise.''

``You don't have to be modest. Not anyone can prepare such detailed data
to prove a misdeed. Even Yoming didn't have anything to argue on.''

``He was underestimating us, I think. He thought once he became the
leader of the Committee, he'd be able to forge and rewrite data as much
as he liked. That was why he fought to get to the top as soon as he
could. His desperation allowed careless blunders to happen left and
right.''

``Ah, now I see. Incredible.''

``Indeed, it was,'' agreed the other man. ``Impressive. Now, I think
we'll wrap up here and get to our jobs. We will see you later, then?''

``Yes.''

The two men lined up and exited. Shion was left alone.

``Detailed data, huh.'' He unravelled the computer and cast his hand
over it. The image on the screen crumbled, and the numbers and words
vanished.

There was no such data that evidenced the crime. It likely existed―but
Shion had neither the method nor the time to acquire it. If it did not
exist, he simply had to create it. Create the data that would leave
Yoming with no choice but to admit his crimes. It was not easy, but it
was not such an arduous task, either.

It went well. He had been able to remove one obstacle from his line of
sight. He would remove, drive away, destroy, his obstacles―and then
what?

Shion glanced out the window.

\emph{What am I doing?}

\emph{Creating a state in this world that is different from No. 6―one that is
	for humans.}

\emph{Make a country where no one kills, and no one is killed.}

\emph{Is that even possible?}

Yoming's derisive laughter burst in his ears.

\emph{What is going to happen to me?}

\myspace

\emph{Tap, tap.} He heard the sound of the wind. No, not the wind―was someone
knocking at the window?

\emph{Nezumi!}

Shion ran to the window and threw it open. The wind tousled his bangs.
There was no one there. It had just been a passing wind. Shion dropped
to the floor and squatted, covering his face with his hands.

\emph{Nezumi... why won't you come home? Why aren't you beside me? I just want
	to look into your eyes and see that I am me, that I can continue to be
	who I am. They are my only anchor.}

\emph{Nezumi, I want to see you.}

There were no tears. A growl escaped through the crack between his lips.
It was an animal growl, in a voice he could hardly call his own.

An alarm went off. It continued to ring. Shion stood up, and
pushed the intercom button.

A young man's voice quietly came through.

``Member Shion, I'd like to hear your orders on the draft of No. 6's new
policies that we will be submitting at today's meeting.''

``Understood. I'll head to Conference Room 3 immediately.''

``Much obliged, Member Shion.''

There was a note of excitement in the young man's voice.

``It's almost coming, isn't it? We're going to clear out the old
political powers and make way to build our ideal state. It's finally
beginning.''

Shion took a breath, and called the man's name.

``Torey, I want you to watch what you say. For us, there is no such
thing as old power or new power. We want to gather the wisdom of each
and every person to progress forward, a little bit at a time. We have no
other way.''

``Oh... right. I'm sorry.''

``You don't need to apologize, but―'' \emph{You should at least be wary of
	wire-taps, Torey.} Shion switched off the intercom, and exhaled one more
time.

He turned around to glance out the window.

A piercing blue sky spread out overhead.

Shion closed the window, and turned his back on the endless expanse of
blue.

\chapter{Nezumi's days}

\lettrine{T}{he clouds} shrouded the sun, and the land cooled quickly in the shadows.
The atmosphere lost heat rapidly and the daytime weather now seemed like
an illusion. The barrens were dotted with low shrubs and no tall trees;
if one stood on higher ground, one could probably look out across the
horizon.

The reddish soil lay exposed, and angular boulders sat here and there
across the land. It was the picture of ruin and fruitlessness itself.
But a number of shrubs harboured natural springs of clean water within
their depths. Those thickets were marked by their green colour, a shade
lusher than the others, and its bushes which yielded red fruit. The
fruit was about the size of an infant's fist and was much too tough to
eat, but its vivid colour was beautiful, and matched well with the
reddish-brown of the land and the green of the shrubbery.

Nezumi crouched by the spring and scooped up some water with his hands.

It was delicious. For someone who had journeyed across dry land, this
water was like a rejuvenating nectar that gave him strength and sped his
recovery.

``Hey, you guys want to take a break, too?'' Two little mice poked their
heads out of his jacket pocket. They climbed down Nezumi's leg, and once
they reached the ground they gave not so much a glance to the spring as
they pounced right onto the red fruit.

The skin of the fruit was too tough to bite for humans, but it seemed to
pose no difficulty for the rodents' incisors. The mice devoured a whole
fruit in moments, making cheerful crunching sounds all the while.

A mouse with light-brown fur―Shion had named it~

Hamlet―looked up and tilted its head as if in inquiry.\\

``No, that's alright,'' Nezumi told him. ``I don't think I can handle
that fruit. You don't have to worry about me; I have a lot to eat.''

Apparently satisfied with its master's answer, Hamlet began nibbling at
the fruit again. Nezumi sipped another mouthful of water, then washed
his face. He shed his clothes and immersed his body in the spring.

It was far from a hot bath, but the cool water felt refreshing. The
spring was deeper than he thought: if he dove underwater, he could see
where the water sprang from the sandy bottom.

Several small fishes were swimming around in the shadows of the algae,
which swayed lazily along with the current and made him think of an
elegant dance.~

Here was a world that was entirely different from the world
above-ground.

``Is it always peaceful underwater?''

How long ago had it been? Shion had murmured those words once, his gaze
hovering in the air.

\myspace

It was in that room in the West Block. It was dawn. He remembered that
the steady rain had finally let up after three days, and the night had
brought a biting chill that blanketed the Block. But it was now starting
to lighten.

Just the day before, not long after the sun had gone down, Rikiga had
made a rare appearance at Nezumi's residence.

``Shion, I brought this for you to eat.'' Rikiga, who had braved the
cold and blustering winds to get here, placed a pointed emphasis on
``for you to eat'' as he handed a paper bag to Shion.

Shion peeked inside and emitted an exclamation of joy.

``Wow, this is amazing! White bread and meat!''

``There are also fresh vegetables and wine. Oh, and cheese. Quite a
feast, don't you think?''

``We can hold a banquet with this!'' Shion said in awe. ``Rikiga-san,
are you giving this all to us?''

Rikiga pursed his lips and shook his head. ``Not `us'. I'm giving it to
\emph{you}. Don't get that part mixed up. Understand, Shion? You're going to
eat this. You have absolutely no need to give it to a certain
serpent-tongued and cunning actor.''

``We'll all eat it together,'' Shion beamed. ``I've promised to have a
read-aloud with the kids tomorrow. I'll make a nice, hearty soup that we
can all eat together. It'll be a splendid lunch.''

Rikiga's face contorted. His expression was like that of someone whose
back itched terribly, but could not reach far enough to scratch it no
matter how hard he tried. Nezumi stifled a laugh behind his book.

``What? What's so funny, Eve?''

``Oh, nothing. I didn't mean to laugh. But if you must hear it out of
me, it was because you made such a cute face, old man, I couldn't help
but smile.''

Nezumi closed his book and stood up. He peered into the paper bag that
Shion held out for him, and gave a high whistle.

``My, my. This is much more than your average wooing gift. If you seek
you shall find, huh? Only a black market trader like you could pull this
off, Mr. Rikiga, sir.''

``Who are you calling a black market trader? I'm a bonafide
businessman.''

``A businessman who traffics women to No. 6 officials and charges
exorbitant amounts for it? Such philanthropic and saintly work you do. I
am ever so humbled.''

Rikiga bared his teeth and made a sour expression.

``Shion, look. You're free to take the meat and vegetables to make soup
or make them part of your interior decor, but whatever you do, don't let
him have a bite. Don't even let him smell it.''

Shion was not listening. His eyes were aglow as he laid out the contents
of the bag on the table.

``Nezumi's soup is top-class,'' he said.

Potatoes, onion, cabbage, carrots. All were fresh. The mice squeaked
incessantly from atop a pile of books.

``He barely uses any seasoning, but it's still so good,'' Shion
continued. ``With this many ingredients, we should be able to make the
best soup ever. Everyone will be so happy. Thank you, Rikiga-san.''

``Ah... but, well, Shion. What I'm saying is that I went out of my way
to―''

``Before our meal, we'll say our graces to you, Rikiga-san. It won't be
a half-hearted ritual. I'm sure everyone will be truly thankful when
they say so. Right, Nezumi?''

``Of course. We'll say, `I am grateful and wish nothing but the best
from the bottom of my heart for this compassionate soul. I pray that his
sublime soul will forever be free of any hurt or pain,''' he said in the
voice of an innocent maiden. Rikiga had a soft spot for innocent, pure,
and unblemished things. Perhaps it was because he had internalized his
own corruption, or perhaps they were simply his fancy, but for whatever
reason, he couldn't help but be attracted to them.

Whether it was an innocent maiden or a prostitute on the corner; a noble
lady or loyal young man; a cunning merchant or an aged philosopher,
Nezumi could become whatever the other person wished. If only for a
short moment, he could show them an illusion of their desire with just
his voice.

Just now, he was certain that Rikiga had seen the countenance of an
untainted girl overlapped on his face. The eyes were connected to the
heart, and so could not help but see what they want to see more than
what is actually there. They also refused to acknowledge what they did
not want to see.

``Damnit! Just a third-rate actor and his tricks. Don't think you can
get away with mocking me, Eve.''

``I would never think of doing such a disgusting thing like manipulating
you to my every whim, old man.'' Nezumi shrugged.

\emph{That sneaky fox. He's as unpleasant as they come. Shion, why don't you
	move in with me before he starts influencing you? Eve, if you don't
	change your ways now, someday you'll pay for it. I know, next time I'll
	bring some butter. For you, I mean, Shion. And I'll bring some fruits.
	Make sure that bastard fox doesn't swipe them from you.}

Rikiga wrapped up a lengthy rant, then went home.

``He never shuts up,'' Nezumi grumbled. ``The right thing to do would be
to deliver his gifts and go straight home. He's the picture of
tactlessness, overstaying his welcome like that.''

``Well, I thought it was nice of him,'' Shion said. ``He came to deliver
all of this expensive stuff to us. It's ungrateful of you to speak ill
of him.''

``Hah,'' Nezumi scoffed. ``Some No. 6 official must have taken a liking
to a woman that the old man arranged for him. Old man got a handsome
load of goods as a reward for arranging that woman, except that stuff
wouldn't have been hard to come by in No. 6, anyway.''

``But he shared it with us instead of hoarding it for himself. He didn't
expect anything in return. I think it was a noble thing.''

``Noble? Are you kidding me?''

``Am I wrong?''

Nezumi smiled with only one side of his face. He found Shion's trusting
nature at once annoying and funny. His frankness and willingness to
trust were foreign to Nezumi. They were as meaningless as the frivolous
embellishments on a piece of clothing.

Rikiga had done it out of guilt.

He was ashamed that he made a business out of selling West Block women
to men from No. 6, and pocketing the money that came from it. On one
hand, it was a sign that Rikiga's heart had not yet been corrupted to
the core, but on the other hand, it was also a sign of his weakness.

Rikiga had wanted to absolve his guilt, his own weakness, by giving
Shion a part of what he had earned. He wanted to see Shion's carefree
smile, feel his joy, and draw some relief for himself. That was all
there was to it. Yet, Shion could not see through this facade.

\emph{Why does he believe in people so easily? How does he do it?
	How does he keep doing it? It's a complete mystery.}

``Nezumi?'' Shion blinked at him uncertainly. ``What're you thinking
about?''

``Nothing, really... oh, the wine wouldn't be a good idea for the kids.
Let's have it ourselves.''

``Sure. We'll have a bit of cheese and bread to go with. How about we
boil some potatoes, too?''

``Sounds great. This is going to be a wonderful night. Let me take back
what I said earlier―I am most sincerely grateful for Rikiga-san's
incredible generosity.''

``You're pretty material.''

``Call me \emph{liberated}. Now, I'll take care of the potatoes, then.''

``Nezumi, we only have mugs to drink out of.''

``Couldn't ask for better.''

``We're gonna drink wine out of mugs?''

``Hey, you don't have to force yourself. I'll have it all if you don't
want it.''

``In your dreams,'' Shion cut in. ``We're going to divide it equally in
half.''

They poured each other wine as they snacked on bread, cheese, and boiled
potatoes. The label on the bottle indicated that the wine was from the
western-most city of No. 3, and was quite an expensive pick. A gentle
sweetness crept up from the depths of its acidity. It was delicious.

Before long, the two had emptied the whole bottle between themselves.

``You can handle alcohol pretty well, can't you?'' Nezumi said.

``Impressed?'' Shion grinned cockily with a flushed face.

``Not impressed, really, just a bit surprised. I didn't know you were a
drinker.''

``This is the first time in my life.''

``...What?''

``This is my first drink ever. I didn't expect it to taste so good,''~

Shion said thoughtfully.

``Huh? Wait, Shion, are you alright? You just had half a bottle of wine.
You must be pretty drunk by now.''

``Mmmm, not really, no,'' Shion said contentedly. ``It just feels nice.
And now I feel so stupid for troubling myself over such little things.''

``What little things were you troubling yourself over?''

``Uh, let me see,'' Shion drawled, then chuckled. ``I can't remember. If
I can't remember, they must've not been that important in the first
place. Ha ha, cheers to no worries! Cheers to wine!''

``Shion―you're pretty drunk.''

``I \emph{am} drunk. I drank wine, didn't I? Of course I'd be drunk. Or is
there some law saying I'm not allowed to be drunk?'' Shion leaned so far
forward that their noses were practically touching.

``Shion... please tell me you don't pick fights with people when you're
drunk.''

``Pick fights with people? What people? You?''

``We're the only two here apart from the mice.''

Shion stood up abruptly and put a hand on his hip.

``'We're the only two here apart from the mice.' Ha ha ha, how was it?
Wasn't that impression spot-on?''

``Impression of who?''

``You.''

``Not even a bit.''

``Liar! I sounded exactly like you.'' Shion stabbed a finger at Nezumi,
and drew a circle with it. ``You know, I think I've awakened to my
talent of doing impressions. Maybe I'm a miming prodigy. I \emph{must} be a
prodigy. The heavens have given me this amazing talent. `We're the only
two here apart from the mice.' Ha ha, see! I \emph{do} sound like you!''

``...Is it fun imitating me?'' Nezumi said exasperatedly.

``It is.'' Shion crouched again and brought his nose right up to
Nezumi's. ``It's unbelievably fun. When I'm with you, everything is such
a joy to experience. Sometimes I wonder why it's so fun to be with
you.''

Nezumi tilted his face away, drew his chin back, and tried to smile
gently like a mother indulging her baby. The muscles around his cheeks
were tense and refused to co-operate.

``I see. Well, that's good for you, isn't it? Just great. But I think
you've let yourself be influenced a little too much by Inukashi's dogs.
We're humans here. We can communicate without having to rub noses.''

``'We're humans here. We can communicate without having to rub noses.'
Heh heh, how was that? Didn't it sound like you? But y'know, Nezumi,
people can't communicate as easily as you make it sound. Compared to the
number of things we understand, there're way more things we wish we
could unnerstan' but can't. A hundred times―a thousan' times more
things. Thas' juss how't is.''

``Shion... you're starting to slur.''

``But iss great for dogs, innit? They juss hafta stick their noses
t'gether `n' go, \emph{sniff sniff} to unnerstan' each other. An' they lick
each other, too.''

``Don't you dare lick my face.''

``I won'. I might bite, though,'' Shion said, stretching out his last
syllable in a singsong voice.

``Knock it off, you drunk. Hurry up and go to sleep. Don't blame me if
you wake up tomorrow morning with a hangover. Besides, have you stopped
to think about how old you are? You're sixteen and you have no inkling
of how to drink... Shion? Hey, Shion, what's wrong?''

Shion was leaning heavily on him. Nezumi could hear the sound of his
soft slumbering breathing.

``Geez, you must be kidding me,'' Nezumi muttered. ``Hey, don't fall
asleep here! I'm not gonna carry you to bed, you know.''

Nezumi shifted his weight. Shion shifted along with him, and they both
tumbled onto the floor. Shion's breathing did not so much as catch. It
continued on, even and regular.

``God,'' Nezumi grumbled. ``You stay awake just long enough to blabber
to your heart's content, then you're out like a light. I don't know if
you could get any more `typical drunk' than this.''

\emph{Cheep cheep cheep!} Cravat looked up from nibbling at a piece of~cheese
and twitched his whiskers.

\emph{He's hopeless}, he seemed to say. He almost seemed to let out a sigh as
well.

Nezumi couldn't hold it in any longer. He burst out laughing.

He continued to laugh by himself, with Shion beside him.

\myspace

He woke up.

He knew it was dawn because the air in the room had gotten even colder.
The chill tended to worsen just as the eastern skies were beginning to
lighten. This was also the hour when the highest number of invalids,
elderly, starving children, and physically weak people drew their last
breath.

Death slipped into the gap between the arrival of morning and the
leaving of night and stole people away. \emph{But even so}, Nezumi thought, \emph{the
	frigid air and starvation are much more merciful servants of Death.
	Much, much more merciful than ruthless violence.}

The scar on his back gave a great throb.

Ruthless―these hostile flames had burnt his back precisely because they
were ruthless. They had swallowed his family and turned everything to
ashes.

\emph{Throb, throb.} The restless pain crawled up his back. Nezumi got up and
regulated his breathing. He took a deep lungful of the frozen air that
summoned death, and exhaled. The cool air that slid down his airway was
a sign that he was alive. He was alive and warm, which was why he could
feel this cold.

\emph{Living people are warm.} Shion had taught him so. Shion had taught him
that living was to feel another's warmth right beside him, and to pass
on one's own warmth to another.

Nezumi raked a hand through his hair, then inhaled and exhaled deeply
one more time. For him, living had always been about revenge and nothing
else. His own survival, the fact that he was alive was revenge towards
No. 6. One day, one day not so far off, he would live and survive to
deliver the fatal blow to No. 6―that had always been the only thing on
his mind. He cared about nothing else. His hatred and loathing towards
No. 6 only mounted, never waned. But he did waver.

Revenge was not the only thing in his heart. There was also something
almost entirely different―something that existed completely unrelated to
No. 6.

Nezumi himself could not grasp what that something was.

\emph{That's why I waver.} He wavered as he wondered about himself after he had
fulfilled his revenge―would he be completely emptied, or would he still
be full? Would there still be a stubborn core of hatred left inside him?
He wavered.

If he wavered, he wandered. Wandering created a vulnerable opening.

Nezumi reached behind him and felt his back. The throbbing had subsided
considerably. Soon it would go away completely.

``Mm...''

Shion rolled over. Last night, Nezumi had dragged him to bed, and Shion
had continued to sleep without a sound, save for his breathing.

``You are \emph{so}―'' he murmured to Shion's sleeping face. ``So
high-maintenance, so hard to take care of... just hopeless.''

Shion rolled over again. His eyelids fluttered, and slowly lifted. There
was no light source save for the dying embers in the stove. In nearly
inky darkness, Nezumi could see a faint white outline of Shion's profile
and hair.

``Nezumi... did you say something?''

Despite the fact that he had just woken up, and that they were immersed
in darkness, Shion's vision had caught Nezumi squarely and his ears had
sensed his words.

``I was giving you my morning greetings. Good morning, your Highness.
How do you feel today? ―Something like that.''

``I feel... not so bad.''

``Oh. Not hung over? Looks like you and booze will get along. If you
don't be careful, you'll turn out like the old man. Don't say I didn't
warn you.''

``You can't get hung over from wine. It's fruit-based, so it's gentle on
the body.''

``Is that true?''

``Yeah. I feel like I heard something along those lines from someone...
maybe it's just me.''

``Not very reliable, are you?''

``I'm not. I'm pretty unreliable―I've finally started to realize that.''

``So you've discovered yourself. Congratulations,'' Nezumi teased
without meaning it.

Shion always explored his own self thoroughly, diligently, and
persistently. He always tried to face off squarely with what was inside
of him.

And that was worthy of awe and praise, was it not?

Nezumi knew right down to his bones how difficult it was not to run away
from oneself. He even felt a sort of reverent fear towards this
high-maintenance, hard-to-take-care-of, hopeless boy.

Shion lifted the upper half of his body up and let his gaze wander in
the air.

``Nezumi.''

``Hm?''

``Do you think it's always peaceful underwater?''

``Wha?''

``Underwater. Like in the sea, or in a river, or in a lake... is it
always peaceful in the water?''

``What're you talking about? Did you dream of something?''

``Yeah. It was the most vivid dream I've had in a while. I wonder if
it's because of the wine?''

``Was it a wine-coloured dream?''

``No... I was swimming underwater, along the bottom. I could breathe
just fine. I just kept swimming on and on.'' Shion shifted and gave a
small sigh.

``And then?''

``That's it. I was just swimming. It was so quiet and beautiful, and I
felt so happy. It seemed like such a peaceful place, with no fighting or
invading....''

``Impossible.'' Nezumi smiled wanly in the dark. \emph{Naive, aren't you?}
``Of course there's fighting underwater. It's just as much of a
dog-eat-dog world as it is above ground. I thought you specialized in
ecology.''

``I was supposed to specialize in it.''

``Either way, it doesn't matter. I thought ecology was a field about the
interaction between organisms and their environment. Didn't you learn
that predation exists underwater, too?''

Shion shook his head. ``I know that. I'm not saying that it's Paradise
underwater. I just thought, since there are no humans...''

``So what?''

``There would be no meaningless fighting. There wouldn't be murder for
the sake of murder, or any atrocious killings.''

``That's what you were thinking about while you were swimming?''

``Yeah. It was so... beautiful. It was sandy on the bottom, and it
stretched on and on. There were jade-coloured stones here and there in
the sand, and they would glimmer from time to time, though I didn't know
how. I reached out to pick one up, but I changed my mind.''

``Why?''

``The stone was so beautiful, I almost felt afraid to touch it. I felt
like if I touched it, the world would fall apart.''

``I didn't know you were such a romanticist,'' Nezumi commented.~

``You sound like a blushing maiden.''

Shion squirmed. ``Yeah, I'm a little embarrassed, too. But I can't
really help it, can I? That's just how I felt. But I kind of regret it
now. If I was going to wake up anyway, I should have picked one up.''

Nezumi almost burst out into a laugh again. He wondered if he was losing
the ability to rein in his emotions.

``You should go back to sleep,'' he said. ``Maybe you'll be able to have
the same dream. Then, you could pick up as many rocks or coins as your
heart pleases.''

``I guess. Hey, Nezumi.''

``Hm?''

``We swam when we escaped No. 6, too, didn't we? But that time, I was
concentrating too much on swimming that I didn't have time to stop and
feel much.''

``We were swimming in sewage. That's completely different from what you
dreamed about.''

``But... it's true that I've seen... so many beautiful things... here in
the West Block...''

Nezumi could hear the other boy lapse into quiet breathing as he fell
asleep. He could feel Shion's warmth. He felt like this warmth was all
he needed to get him through the frigid winter days.

\emph{What am I thinking? That's absurd.} Those who could not live by
themselves, those who could not stand up to fate on their own, simply
did not survive. It was how things worked in the West Block.

\emph{I don't need any warmth.}

Nezumi got up and filled a cup with water from their stores. He drained
it in one draught. The cool water slipped down through his body. Shion
muttered something unintelligible.

``Did you manage to pick one up?'' Nezumi said to him. There was no
answer. Only the heavy groan of the blowing wind echoed in the air.

\mybreak

The algae suddenly rippled. They were not languid movements like those
moments before; now, it bristled like a thin tree being blasted by the
wind.

It was an unsettling movement.

A silver fish burst out of the tangle of algae and sped past~

Nezumi's line of vision. It was but an instant―but Nezumi could clearly
see it swallowing half of a little fish. Predator and prey. The eaters
and the eaten.

The disturbance was brief, and before long the tangle of algae returned
to its normal state and the little fish resumed swimming about as if
nothing had happened.

Nezumi found a blue stone on the waterbed. He picked it up without
hesitation. The stone was neither glittery nor beautiful. It was just a
crude, misshapen rock.

A breath escaped his lips and formed a jet of bubbles. Suddenly, he
couldn't breathe. Unless this was some kind of dream, he knew it was
impossible for a human like him to remain underwater for much longer.

Nezumi paddled the water and aimed for the surface.

The sun was apparently back out, for the surface of the water was
glowing white. A black shadow lay diagonally across the surface.~

It was the shadow of a fallen tree. A dying tree had tipped over at the
roots, and was half-hanging into the water. Nezumi grasped a branch and
pulled himself up. Water rushed past his ears and his hair clung to his
neck and shoulders. He could let out a long exhale now. He filled his
chest with air.

The falling tree was still partly connected to its roots, and perhaps
due to that, its leaves were lush and its branches grew out in all
directions without showing signs of withering. Nezumi swung his leg over
the trunk, and took another breath. He had not expected a tree of this
size to be growing here. This unremarkable oasis in fact hid many
treasures within.

Something moved in the corner of his eye, around the area where he had
tossed his belongings. It seemed like a person.

\emph{Screek, screek!}

\emph{Scritch, scritch, scritch!}

The voices of the little mice turned harsh. They were baring their teeth
in apprehension at the suspicious shadow before them.

``Ow! Stop it! Ouch!'' yelled a voice. It belonged to a man. ``Jesus,
what the hell are these things? Go away! Go on, beat it! Stop biting me!
Damnit, I'm gonna roast you whole and eat you. Ow, my earlobe!''

Apparently the little mice had launched into their attack. The man's
cries grew shriller.

``Ow, ow, ow! Damnit, you bastards!''

The man attempted to flee, leaving curses in his wake. He swung his arm
around to brush off the mice. His hand firmly clutched Nezumi's
belongings.

Nezumi stood on the fallen tree and gripped the rock in his hand.

``Hey, thief.''

The man jumped and whirled around. Nezumi hurled the stone straight
towards his face. At the same time, he himself plunged into the water.
He swam towards the shore.

The man was kneeling on the grass, covering his face with both hands.
Blood was dripping from between his fingertips. Hamlet and Cravat leapt
onto his shoulder as Nezumi swiftly donned his clothes.

The little mice clamoured over each other as if making a passionate
claim.

``Right, I get it, I get it. You two did a good job.'' Nezumi petted
them both on the head with his finger. Cravat then dove into his pocket,
and Hamlet into his mop of wet hair.

``Ugh... it hurts. My eyes... I'm blinded! Help me!'' The man stretched
his bloody hand out into the air and flailed.

``I aimed for the middle of your forehead, and my aim is good. I've
never missed once. I'll go so far as to say I went easy on you.''

The man looked up at Nezumi with a hand still on his forehead.

``Went easy?'' he said incredulously.

``I sure did. I could have lodged that rock into your forehead. I showed
compassion to a thief. You should be thankful.''

The man took his hand away. Blood was spurting out of the centre of his
forehead and running down his face.

``You call this going easy?''

``Of course. No harm done to your skull or your brain. You just got a
little torn flesh there. It's almost too lenient a punishment for
theft.''

``Why, thank you,'' said the man sarcastically. ``I'll be sure to get my
brainwaves checked out at the hospital. Ugh, god, it hurts! It's
stinging!'' The man groaned as he washed his face. Then, he took out an
array of bottles in many sizes from the cloth bag slung over his
shoulder. Inside the bottles were liquids of every colour. The man
skilfully mixed some liquids together to produce a lilac-coloured,
slightly viscous solution which he soaked a cloth with and applied to
his wound.

``Hmm, this should do it. The wound should close up by tomorrow
morning.'' The man then wound the cloth around his forehead and grinned.
He was tanned, and deep creases lined his eyes and his mouth. There were
prominent white streaks in his shaggy head of hair. Yet his voice and
the glint in his eyes were lively―youthful, even.

His age was a mystery. It was hard to tell whether he was young or old,
but he was still a thief nonetheless.

``But let me say, boy―'' Once the man had put away the bottles into his
bag, he turned to Nezumi and began to talk to him with a smile. His tone
was much like that of a teacher lecturing his student on the principles
of higher learning.

``Now that I can get a closer look at you, I can see you're quite the
beauty. A beauty like you shouldn't be swimming naked in a place like
this. This place is dangerous―breeding grounds for vagabonds and rogues.
Swimming in this place with not a thread to clothe your body―why, you're
like a sweet lamb wandering amongst a pack of wolves. Caution is what's
needed, boy, caution.''

``Thank you, I didn't expect to be lectured by a thief. Good to know you
don't even feel guilty about what you did, old man.''

``Old man? Are you calling me an old man?''

``Well, it's not about me, is it? I'm neither an old man nor a thief.''

The man blinked. Twice. Thrice. Four times. Once he stopped~

blinking, he burst out into laughter.

``Ha ha ha! That's funny! Ha ha ha ha! That was a good one! You have a
sharp tongue for such a pretty face. Ha ha ha! Ah, you're an interesting
one!'' he chortled. ``Ha―''

The man's laughter ceased. Nezumi had pressed a knife to his throat.

``What an irritating voice you have,'' Nezumi hissed. ``Why don't you
quiet down for a little―no, forever,'' he whispered into the man's ear
from behind. Nezumi knew well how much fear his whisper instilled to the
person at knifepoint. He also knew how effectively this fear was at
disabling the victim.

The man shuddered.

``Oh... no, c-come on, wait a minute. You don't have to use a knife to
shut me up. Really, I'm honestly sorry. I'll apologize if I've offended
you. I'm sorry.''

Nezumi drew back and put away his knife. The man clutched his throat and
moved his lips. A long exhale hissed from between them.

``God, impatient despite your looks, aren't you? I thought you'd have a
more graceful manner.''

``I reserve my manners and grace for other people who are also graceful.
You're a thief. You tried to sneak away with a stranger's belongings. I
think you deserve a slash across the throat with a knife much more than
graceful manners.''

``Have you ever killed before?'' The man looked up at Nezumi from
beneath his eyebrows. ``Have you killed a man with that knife,
young'un?''

``I don't have any obligation to answer a thief.''

``No, don't misunderstand me. I wasn't trying to steal your things.''

Nezumi looked down at him expressionlessly.

``It's true,'' the man insisted. ``Believe me. Here, this is proof.''

The man thrust his hand into his cloth bag and began to take out one
item after another. There were several vials of medicine, a bag of cured
meat, a water jug, a wrapped loaf of bread, a hunk of cheese, rock salt,
and a small pouch. The man opened the pouch and showed it to Nezumi. It
was full to bursting with gold coins.

``See? Sorry to say this, but I'm a little more well off than you. I
don't \emph{need} to steal your things. I hope you understand now.''

``I don't understand at all.'' Nezumi shrugged just his right shoulder.~

``I don't care how well-off you are. You still tried to walk away with
my stuff. That's the fact of the matter. That was theft and there's no
saying otherwise.''

``I guess it can't be helped if that's what you think I am. So this
wound,''―the man gently touched his forehead―''is my curse and mark of
Cain. I've already been through hell, whatnot with this wound on my
forehead and being bitten by mice. Can't you just take that and say I've
already paid my dues?''

``Awfully in your favour, that interpretation, isn't it?'' Nezumi slung
his load over his shoulder and smiled faintly. Suddenly, everything felt
foolish. Soon the sun would set. He had to secure a spot to sleep for
the night. There was no more time to waste with this smooth-talking
thief.

``Oh, leaving so soon?'' The man stood up. He was wiry and tall. He was
clad from top to bottom in rough, white cloth, and was wearing dirty
leather sandals.

``You bet I am. I'd rather not stay to chat with a thief.''

``I told you I'm not a thief. I just wanted to find something out.''

``Find out?''

``Yes, find out where you came from.''

``And what would you do with that information?''

The man straightened up. ``No, I just thought... just maybe, that you
were from No. 6. It was just a thought.''

No. 6.

He had not expected to hear this name out here.

No. 6.

The artificial city which some called a utopia, which was supposed to
have been the embodiment of humankind's intellect and hopes, had quickly
transformed into a towering monster. The city had crumbled as if
succumbing to the weight of its own horrific ugliness.

\emph{Nezumi, I'll wait here for you. I'll keep waiting.}

Shion's voice echoed deep inside his ears.

``Aha, I see. So you \emph{are} from that city.'' The man jumped up and
attempted to grasp Nezumi's hand.

``Don't touch me.'' Nezumi batted away the arm that was offered to him.
He hadn't meant to do it with much force, but the man staggered back and
plunged one foot into the water.

``No need to be so hostile,'' the man said. ``It's just that if you \emph{are}
a resident of No. 6, there are a lot of things I'd like to ask you.''

``And I have less than a grain of sand's worth to say to you. I'm not a
citizen of No. 6.''

``But you know about it. Is it true that the city is destroyed now?''~

The man's expression showed an obvious tension. The corners of his eyes
were turned up, and they twitched slightly.

``I hear rumours everywhere, but no one knows the truth. And I think you
know. I saw vacuum-packed rations and a lightweight LED~

generator in your pack. That's from No. 6, isn't it? I can't think of
anywhere else you would get it.''

Before the day of Nezumi's departure, Karan and Shion had packed all
manners of things into Nezumi's bags, Karan with the face of a mother
seeing her son off, and Shion in stolid silence.

\emph{We really are saying good-bye.}

Nezumi had finally felt the reality of their parting in his flesh as he
watched Shion's profile, with the boy's lips pursed in a stiff, almost
grumpy, line.

\emph{Tomorrow, I'll be leaving. Shion will stay, and I will leave.}

Their two lives, connected almost miraculously four years ago, were now
parting and going their separate ways. Nezumi and Shion had lived
together for less than half a year. It was a very short period compared
to the days he had spent alone until then, and probably to the days that
were to follow. It was a brief, yet intense, period.

\emph{Would there be any period in the future more intense and finely-defined
	than that period I spent with him?}

Nezumi shook his head. No. 6 had fallen. He had fulfilled what he had
set out for.

\emph{So it's fine.}

Shion was a person of the past. Although he would remain in Nezumi's
memories, never to disappear, he was not involved in Nezumi's present.

He had to draw a line. If he didn't he would not be able to move
forward. He would not be able to live the present if he was trapped in
the past.

He'd had enough. Enough of dragging the past behind him and~

bearing its weight. He wanted no more of it.

``Come on, won't you answer me?'' A pleading tone crept into the man's
voice. ``I hear rumours. Lots of them. I hear that No. 6 has fallen, but
I've also heard that that's all a lie, and that city is still there,
still prospering. I can't tell if either story is true or false.''

``You can always see for yourself.''

The man drew his chin back and let his throat rumble.

``...But No. 6 is such a distant land.''

``It's only about a six-month walk. That's pretty close.''

``Half a year... just thinking about it makes me feel faint.'' The man
gave such a lengthy exhale that his body seemed to shrink a size.

``Aren't you a traveller, too, old man? Or don't tell me you've settled
in this wilderness?''

The man's lip curled revealing a part of his teeth, which were
surprisingly white. His tone and his voice carried none of the
piteousness of before.

``Oh, I wouldn't be so incredulous. It might be a more comfortable place
to live than you think.''

The earth was mostly uninhabitable by humans for the long-term, aside
from the six cities and their surroundings―it had been said so for
years.

People had built the six big cities in search of the right location,
land, and conditions for survival. Those who could not get inside had no
choice but to die, or to cling to their lives by hanging on margins of
the cities.

But after wandering the wilderness, Nezumi realized that not all of it
were badlands that inhibited any chance of survival. There was more
greenery, more oases than he saw back when he had wandered with the old
woman; there were even scattered streams, grassy fields, and marshlands.

It seemed as if the environment was recovering suddenly and rapidly,
though Nezumi could not tell if this improvement was the earth exerting
its inner strength or something that was simply temporary. Nezumi
figured no one would be able to tell.

But he did feel one thing: both the earth and humankind were resilient.

Humans were gathering near bodies of water and establishing small
settlements. They irrigated water and ploughed the fields, planted
seeds, tended cattle, produced children, and were attempting to rear
them. Although they were in extremely harsh conditions, they were
establishing lives that were separate from the six big cities.

\emph{Shion, the world is shifting. It's always moving and changing shape.
	Have your eyes caught this change? Have your ears caught the sound of
	this change, its movements in the womb?}

He spoke mentally to Shion, who was probably still in the midst of a
difficult battle in a newborn city.

``Oh, I know. How about this: why don't you stay over at my house
tonight, young'un? I'll give you a night's lodging as a way to apologize
for my rudeness. Will you sit down with me and tell me your story? It's
a small cottage, but I have a bed and a bath. It's a pretty good lodging
for these parts.''

``I won't take it.''

``Why not? It's a warm bed and a hot bath.''

``You could offer me a marble bathtub and I'd still refuse. I don't even
want to set foot into a thief's lodging.''

``As I said before, I'm not a thief. I'm No.6's―'' the man abruptly shut
his mouth. Nezumi could hear the clear sounds of a horse's neigh and
human footsteps. There were several horses and men. The air suddenly
carried a scent of foreboding.

``Oh, no. They came after us.'' Colour fled from the man's face. In an
attempt to escape, he tripped over his feet and landed on his bottom.

``There, I see him! There he is!'' Three men appeared, wading through
the shrubbery. All three of them were of immense size. One was
tan-skinned, and the other two were fair-skinned with a hint of pink.

``We found you, fraud! Don't think you can get out of this alive.'' The
tan man raised a thick arm. His animal aggression was overwhelming.
``What the hell kind of elixir is this?'' he roared. ``It's just
coloured water! Stop fucking around.''

``Take him down!''

``Finish him off!''

The two fair-skinned men yelled at once. One of them had his grey hair
tied up like a horse's tail, and the other's head was shaven clean.

``You tricked us out of our money. I don't think anybody will have a
problem if you happen to get finished off.''

``W-Wait! Hold on a minute! You misunderstand me. That medicine is
really an elixir. Y-you must have made a mistake while you were
preparing it―''

``Shut up! Still got the balls to lie, huh?'' bellowed one.

``Rip his mouth apart and pull his tongue out so he can never speak
again! While you're at it, break two or three of his teeth!''

``Eeek!'' the man cried. ``P-Please, let's calm down and talk about this
without resorting to violence. I-I'll give you your money back!''

``Money?'' the tan man smirked. It made for a perfect stage villain's
face. ``Of course you'll give it back to us. I'll take my time with the
money after I'm finished with you.''

``Eeeek, help! C-Come on, young'un! Help me!'' The man looked at him
with pleading eyes.

``Hm? Who're you? Are you this fraudster's friend?'' The ponytail man's
eyes bulged as he glared at Nezumi.

``Never. I was just passing by. See ya.'' Nezumi turned his back on the
men. The last thing he wanted to do was get involved in a scuffle, much
less a dispute involving a thief.

``W-Wait! Please, don't leave me!''

``Shut up!''

He heard the dull sound of flesh hitting flesh behind him. He heard
someone collapse to the ground.

``St-Stop.... help me, please.''

``A fraudster like you should just own up to his crime, Shion.''

Nezumi's feet stopped.

``Did you say Shion?'' He turned around.

The man came crawling up to him, bleeding from the corner of his mouth.
He clung to Nezumi, pleading for help over and over.

``Is your name... Shion?''

``I―it's what I call myself, but...''

``It's not your real name.''

``It's my son's name. H-He's an adorable baby, like an aster flower.''

``Your son's name?''

\emph{No way. Can it be?}

``Hey, kid.'' The man with the ponytail strode over to him. ``If you're
just a passerby, you better hand that man over to us and get going. Or
else―''

``Or else, what?''

The ponytail snapped his fingers as his face twisted into a grin.

``Or else you'll be buried in the wild right alongside him.''

``Oh, I think I'd like to decline, if you don't mind. I don't really
like being in the dirt.''

``Hey, fella.'' The tanned man twisted his face into the same kind of
vulgar grin. ``You're actually quite the looker up close. It's a waste
to put you underground. Why don't you come along with us? We'll give you
a good time.''

``What, you didn't realize I was beautiful until you looked at me up
close? I can see eyesight wasn't one of the things you were given, along
with looks.''

``What the hell did you say?''

Nezumi put his pack down and gave a small sigh. \emph{And so it goes in the
	end. Shion, your name always gets me involved in some kind of conflict.
	I hope you're aware of that.}

``Turning against us, huh, little bastard?''

``I wish I didn't have to.''

``Hah, well, that's fine. We'll just beat you up a little until you
quiet down. After we get rid of the fraudster, we'll have all the time
to enjoy with you.''

``Not the face, though. This one brings in the bucks.''

``I know that. Heh heh, we found ourselves a gem.'' The tanned man
licked his lips. Then he clenched his fist and lunged forward.~

His movements were practiced and smooth, like one who was used to
violence and fighting.

Nezumi retreated a step and whistled. Hamlet burst out of his hair and
launched itself at the tanned face in front of it.

``Argh! What is it?!''

Before the tanned man could grasp Hamlet, Nezumi sank his knee into the
man's belly. The man's enormous tanned body fell to the ground without a
sound. Nezumi jumped over the fallen man and drew right up to the
ponytailed man.

``L-Little bastard―''

The ponytail bore down on him, his eyes bulging. Nezumi already had an
idea of the timing. He dodged the blow, slipped close to the man and
hammered the blade of his hand into the man's throat. The ponytail bent
over backwards before collapsing on his back. He, too, was unable to
raise so much as a cry.

``Oh, you've done it―'' The bald man, the last one remaining, drew a
dagger out. ``I'm gonna smash you.''

The bald man's movements were slightly less nimble than the other two.
Nezumi spun around so that he was behind him, and coiled his arm around
the man's neck, tightening his grip.

The dagger fell at his feet. Nezumi kicked it towards the spring. A
moment later, he heard a clear splash.

``A knife isn't something you just swing around. I suggest you get a
little more training.'' Nezumi tightened his headlock even more. All the
strength left the bald man's body. When Nezumi uncoiled his arm, the man
fell to his knees with a muffled gasp.

Hamlet scurried up to Nezumi's shoulder and chirruped softly.

He heard applause.

``Brilliant. I felt like I was watching a stage play. Amazing. Just
stunning. That was good work. Hey, what are you―''

Nezumi snatched the pouch of gold coins from the man's cloth bag and
placed it in the tanned man's hand. The tanned man groaned softly and
raised his head slightly.

``Sorry about that. Can you take this money as an apology for what he
did and write it off? Please.''

The tanned man blinked. He seemed to nod ever so slightly.

``H-Hey! That's too much. It's my money!''

``There'll be no grudges this way. Or would you rather these men follow
you around everywhere? Let me tell you that these types are tenacious.''

The man shrugged, and resumed clapping.

``I see. But anyway, you certainly did a brilliant job of cleaning them
up. I'm humbled.''

``Were you a citizen of No. 6?''

The man's hands froze. Without his smooth talk and clapping, the silence
seemed to ring in Nezumi's ears.

``Answer me. Did you live in that city?''

``...Yes, I did. But I said my goodbyes a long, long time ago.''

``Why?''

``Why? Hmm, let's see. Because that city was fake, young'un. If it's
fake, it will always someday begin to unravel. I knew No. 6 would
probably begin to tighten its surveillance and become even more
domineering in its attempt to keep itself together. I didn't think I
could stand being suffocated like that.''

\emph{I see. So this man saw through No. 6's true form and its destiny.}

``And you escaped from the city alone, leaving your beloved little boy
behind.''

``I couldn't convince my wife to leave. She refused to leave No. 6 with
me. I don't think she could trust me completely.''

``That's shrewd judgement enough. If she had come with someone as
irresponsible as the likes of you, she would've been a pile of bones by
now.''

``Not exactly a polite one, are you? But anyway, is it true? Has No. 6
really been destroyed? It has, hasn't it? An artificial world like that
would never be able to exist in reality for long. It must have crumbled
from its foundations... it's true, isn't it?''

``If it is, what do you plan to do?''

``I'm going home.''

``Home? To No. 6? It's pretty far-off.''\\

``Oh, six months of walking will get me there. It's not a big deal. You
said so yourself.''

``Yearning to see your wife and son again, huh, even after you abandoned
them once? Pretty selfish thing to do, I think.''

``No... that's not all of it.'' The man fell silent for a while, then
raised his face determinedly. ``I owe you. You saved my life. So let me
tell you something. Come here.''

The man invited Nezumi out of the shrubbery. Three horses were tethered
and grazing. They were a dark brown colour.

``No one will overhear us here. Take this.'' The man drew a bag from
under his shirt. He had apparently kept it hanging around his neck. Both
the fabric and string of the bag were worn and faded.

``This...''

Inside was a rock a round smaller than the fruit on the bushes.~

Nezumi did not even have to take a closer look to confirm. This was....

``Is this... gold ore?''

``Yes. Listen to me: there are gold deposits in the area around No. 6. I
don't know how large the area is, but I think there's a considerable
amount of gold hidden there.''

``No way.''

``It's true. I discovered it when I was younger. I might look like this
now, but I was once a geologist. We investigated all soil around No. 6,
and this was part of the discovery.''

``But you put it under wraps and didn't report it.''

``Of course I did. Why would I have to report it, anyway? Gold would
never bring prosperity to No. 6. It would result in a hundred troubles
with not one good thing to make up for it.''

``I can see that.'' Nezumi felt a slight chill.

``As far as I know, the ore hasn't been discovered yet. I haven't heard
any rumours about any discovery. Besides, No. 6 is destroyed now, so the
place must be in the throes of confusion. Which means I can enter and
leave freely. I can even dig up gold in broad daylight and no one would
reprimand me.''

``Wait a minute. Where's this gold mine you're talking about?''

``A strip of land running from the north to the south. Part of it even
reaches the region that used to be called the Land of Mao. None of it is
visible above ground. The gold is slumbering away, deep inside the
earth. Plus―''

The man lowered his voice and continued in a low murmur, as if to build
tension.

``I can't say this is for sure yet, but... there's also a possibility
that there's a huge deposit of rare metals right beneath No. 6. Nickel,
gallium, zirconium, niobium, indium.... I can't say much more, but what
do you think? Great news, isn't it?''

Nezumi's chill worsened slightly.

``...It's great to hear as a fairy tale. This is how you've tricked
people all the way up until now, isn't it? As the fraudster that you
are.''

``I'm not a fraud. I'm the one who waits.''

``The one who waits?''

``Yes, I've been waiting―for No. 6's fall. And it seems like the time
has finally come. I have to make preparations to go back home. Hey, why
don't you come along with me? I couldn't ask for a better partner. Let's
go back to No. 6 and claim that enormous fortune for ourselves.

The man's eyes shone with a disgusting, slimy kind of light. It was not
the lively kind of light that illuminated the way forward. His eyes were
glowing dimly from their depths in an attempt to lure the prey close.

\emph{This man....} Nezumi realized he had gritted his teeth. \emph{This man isn't
	insane, nor is he trying to trick me. He's just telling the truth―at
	least the truth as it appears to him.}

``And what do you plan to do with those riches? Enjoy a luxurious
retirement?'' \emph{No. That isn't what this man wants.}

``I'm going to buy it.''

``Buy what?''

``No. 6.''

For an instant, Nezumi's voice and breath caught in his throat. All he
could do was stare, bewildered, at the man.

``Buy No. 6? What do you mean?''

The man stowed the ore back in its pouch and smiled amiably.

``Listen, young man. If you plan on taking over the world, you won't be
needing armies, commandments, or thorough systems of surveillance and
control. You need wealth. Wealth is the single largest, most significant
weapon. No. 6 didn't quite get that part right. Well, the city was also
unlucky to have a foolish ruler.''

``You plan on becoming the ruler of No. 6 with wealth?''

``Oh, I don't know.'' The man cocked his head to the side. ``Who knows
what fate will bring? I'm not much of an ambitious person. I don't
aspire to be an emperor or a ruler.''

``Then why?''

``For fun. I can make a mess of people's lives with these two hands. It
would be jolly. Just jolly. No game could be better than this.''

``Wh...'' Nezumi stared harder at the man. He was not like Shion.~

Shion never looked at people's lives as something to toy with. He never
manipulated them for fun.

``No. 6―that city is finally on the road to rebuilding. They're trying
to establish a new city-state, and you're just going to make a mess of
it because you feel like it?''

``Rebuild? New? Impossible. It doesn't matter who gets involved and in
what manner. A state is a state. It'll eventually strengthen its
government and attempt to put people under its rule. That's the true
face of a state, and the history of humankind has proven that fact to
us. No. 6 can change its robe as many times as it likes, but it'll still
be No. 6, all the same. If there is any change, it would be whether the
person at the core of No. 6―its ruler―is foolish or intelligent. He'll
set his methods of rule in place: if he's foolish, he'll make it
obvious; if he's intelligent, he'll be nimble and discreet. The fool
would eventually destroy himself, but a man of decent intellect would
gradually gain complete hold of No. 6. Those are the types you should be
the most afraid of. So?''

``...Huh?''

``What kind of person is involved in the rebuilding of No. 6? From your
point of view, is he foolish? Is he intelligent?''

Nezumi shook his head slowly. The base of his neck ached dully.

``He's very bright, and holds substantial intellect. I can't imagine him
becoming the type of ruler you were talking about.''

``Ah, you have high regard for him, I see. And you must know the man―he
is a man, right?―you must know him well?''

\emph{In a sense, I know him more than anyone else. And in a sense, I know
	nothing at all.}

``And you also believe in him.''

\emph{I do believe in him. Nothing in the world would be worth believing if I
	couldn't believe in Shion. I believe in him. But I was also afraid of
	him, wasn't I?}

Nezumi fell silent. The man glanced at him and stepped forward.

``How about it? Come with me. I'm not quite sure about the rare metals,
but there's definitely gold.''

Nezumi took a firm step backwards.

``No thanks. I'll drift to wherever I want to go.''

``I see... that's unfortunate.'' The man grimaced as if he were really
disappointed. ``But I guess there's nothing we can do. I'll be off,
then. I think I'll borrow this horse here. Considering how much gold I
paid back there, I don't think he'll mind if I take one horse.''

The man took hold of the reins of a grey horse and turned around.

``One last thing. People change, boy. That man you believe in will
change, too. Anyone who stands at the top of a state will change. If he
doesn't change, he'll be destroyed. You remember that.''

Nezumi touched the knife attached to his belt. \emph{Maybe if I finish this
	man off here... if I finish him off, I would nip a bud that would
	otherwise bring harm to Shion.}

His fingers itched. Nezumi clasped his itching fingers.

\emph{I'll never forgive you for harming, much less killing, someone for me.}

\emph{Nezumi, don't kill him. Don't commit a crime for my sake.}

Shion was holding his arm back and pleading with him desperately.

\emph{Nezumi, don't kill him.}

\myspace

\emph{That's right. That's what you would say. I know you would say that and
	stop me. You've always been, and always will be, a naive do-gooder.}

\emph{Shion....}

``Well, if the fates bring us together, let us meet again.'' The man
mounted the horse with a sweep, and dug his heels in. The grey horse
gave a whinny and started off. The man and the horse disappeared in a
cloud of dust.

The wind blew, making the bushes sway.

The clouds covered the sky as the land enrobed itself in the
darkness of nighttime.

\emph{Shion.}

A tiny crack appeared in the clouds, revealing deep purple sky.

A solitary star twinkled.

Far off into that sky was No. 6.

Nezumi yielded to the wind as he gazed intently up at that star.