% !TeX spellcheck = en_US

\chapter{Your last embrace}

\myepigraph{O here\\
	Will I set up my everlasting rest\\
	And shake the yoke of inauspicious stars\\
	From this world-wearied flesh. Eyes, look your last.\\
	Arms, take your last embrace!}{Shakespeare, \emph{Romeo and Juliet}, Act V Scene III}

\lettrine{A}{ white} light stabbed at his eyes.

It was blinding.

The light was overpowering.

The place overflowed with light, and glittered.

It was unmistakable―it was the world of No. 6.

\myspace

Yes, No. 6 had always been like this. Brimming with light; releasing it.
\emph{I've returned.} Shion clenched his hand into a tight fist. He was thumped
on the back.

"Take a deep breath," Nezumi said. "Breathe out and get rid of all your
emotions. A split second of hesitation or excitement can cost you your
life. Keep your head."

"Got it. You too. Follow me, and don't fall behind." Suddenly, he felt
the urge to laugh. It tickled in his chest.

"What?" Nezumi drew his chin back. "What're you grinning about?"

"No... just thinking about how great it feels to say 'follow me' to you.
Before, I was always the one to be told that."

"―You know, Shion, you're―" Nezumi closed his mouth mid-sentence, and
shook his head.

The door opened fully. The light hit them head-on.

"Let's go, Nezumi." Shion unclenched his fist, and glided out into the
white light.

\myspace

\emph{He smiled?} Nezumi shook his head, and chewed his lip. He felt
suffocated, though only a little. \emph{How can he smile at a time like this?
	And from the bottom of his heart, like he was really happy.} It wasn't
bravado. It wasn't fake. In a moment they would be stepping into the
Correctional Facility, and yet, Shion had smiled. He had been able to
smile.

\emph{Just thinking about how great it feels to say 'follow me' to you.}

\emph{What the hell? What are we, a couple of students making idle chatter and
	laughing on the way home from school? Why? Why is it that you seem not
	to feel nervous at all? Don't you understand what kind of situation
	you're in right now?}

He could hurl as many insults as he liked. \emph{But}, Nezumi muttered under
his breath, \emph{but it's still amazing}. He couldn't help it; his feeling of
awe was stronger than his desire to insult the boy.

\emph{I can't smile like that. Give an innocent and carefree laugh―it's just
	not gonna happen with me. Right now we're about to step into a danger
	zone that might as well be a minefield. I can't spare the energy to
	laugh.}

He wasn't afraid. He wasn't going to flinch. But he was tense. This
stance prepared him for battle. He needed this shift in mind and body so
that he could manoeuvre himself out of the way of an attacking enemy; so
that he could turn around and sink his fangs into the enemy's throat.
Shion had none of that. He didn't even have the fighting mentality.

Numerous times, Nezumi had felt frustrated at him. \emph{Where did you leave
	your fangs and claws behind?} he would think. He had even slapped Shion's
cheek out of sheer frustration.

He had thought that Shion was frail. He was far weaker, far more fragile
than Nezumi. Like a newly-hatched chick, he was defenseless and
powerless... he had not a single skill to survive in this harsh reality.
But that didn't mean that Nezumi scorned or looked down upon Shion.

On the contrary, he had felt that he needed to protect him. If he didn't
protect him with all the strength he had, Shion would not be able to
survive. He would be crushed. Nezumi had earnestly believed so once.

And he had utterly misunderstood. \emph{I made unfounded assumptions, and that
	was my foolish mistake.} He had realized it long before.

Shion was not weak at all. That was why he had been able to come this
far. He had not been crushed; in fact, he was far from it: he had
survived stoutly. He had come crawling up with his own strength. He had
emerged from this brutal reality, stood on this ground, and even smiled.

\emph{Smiled, huh. That's right. You'll do things your way and I'll do it my
	way, and we'll overcome this.}

He regulated his breathing.

\emph{It starts here, Shion.}

He couldn't predict in the faintest what was going to happen, what was
waiting for them.

\emph{An abyss?}

\emph{Or a miracle?}

\emph{A return alive, or no return at all?}

He couldn't predict what lay a pace away.

\emph{What's going to happen...?}

\emph{When we've run past the finish line, will you still be laughing? Will
	you be smiling as you are, unchanged from now?}

"Let's go, Nezumi." Shion glided into the white light. He had to follow,
so as not to fall behind. Nezumi nodded, and stepped out into the light
after him.

Point X. It was marked as such on the floorplan. It was the door at
location po1-z22. It was the only point where the underground blank was
connected to ground-level.

When the door opened, it made a passage-way between the underground
realm and the Correctional Facility. There was a difference in air
pressure, perhaps, for there was a slight air flow.

Shion ran to the right. The floorplan that Fura had filled in for him
rose in his mind as if he were actually seeing it in front of him.

"Fifteen paces to the right. We're safe until there. There are no
sensors. Beyond that, we've got stairs."

"And there?"

"Laser beams: one on the second step, running 45 degrees; one on the
stairwell, 15 centimetres above the floor, running parallel; one on the
eleventh step running 60 degrees. As long as we don't touch those, the
surveillance won't go off."

"Hm. Pretty lax."

"Only up to here." This was the basement floor of the Correctional
Facility. Excluding Point X, there was no contact to outside areas, so
naturally, there were no windows or doors. Facility workers, personnel,
and visitors who had the appropriate identification chip and didn't need
to worry about the sensors came down by the stairs or elevator―the
legitimate route. But other than that, the only way to get here was
through the underground realm.

Adding to that fact, none of the departments here handled confidential
material, and the risks of infiltration were infinitely close to zero.
It was understandable for security to become lax.

No one had probably predicted that Point X, or location po1-z22 would
ever open.

"Nezumi."

"Hm?"

"How much time do you think we can buy?"

"One―no, at least two minutes."

\emph{Two minutes? Can we buy that much?} The change in Point X had probably
already been registered by the security system. Could they even buy two
minutes until the monitoring staff realized and took appropriate action?

"Inukashi's working his magic," Nezumi said. "It's probably a bit of a
hullabaloo up there."

"Hullabaloo?"

"You'll see in time. The joyous festivities are only beginning. Anyway,
we've got two full minutes. It's ours to use."

"Two minutes, huh."

"Feels like an eternity, doesn't it."

"Sure does," Shion said drily.

Second step, 45 degrees; stairwell, 15 centimetres parallel; eleventh
step, 60 degrees. They emerged at the top of the stairs. It took a bit
of time, since they couldn't just dash up. Approximately 1 minute, 06
seconds left.

From this floor began the ground-level part of the Correctional
Facility. There was an entrance hall, where the largest number of people
came and went. Personnel came through a different gate than that of
prisoners, and gathered on this floor. From here, they dispersed to
their respective workplaces. Everyone was cross-checked minutely at the
entrance, but once they were through, it seemed like inspection on the
rest of the floor wasn't as thorough. The higher the floors, the more
strict it became.

The top floor was where they were headed.

It was the deepest and furthest part of the Correctional Facility,
encircled by many layers of security networks. They were not headed for
the imprisonment facility, which protruded like a bump from the main
tower.

It was the furthest part of the Correctional Facility. That was where
Safu was.

Shion knew in his guts.

Safu was a certified elite. Such chosen ones were furnished with the
best educational environment from a young age. Investing ample time,
money, and labour into developing elites was a fundamental political
policy of No. 6.

Shion couldn't imagine No. 6 taking an elite that they had raised so
carefully to throw her into prison with the rest of the inmates. If she
had been arrested in connection with him, then his mother Karan wouldn't
have been safe, either.

But it had been Safu who had been taken, and not Karan.

Then it must mean that she was arrested not in connection with him, but
on the conditions that she herself fulfilled. The fact that she was
elite, perhaps, and without parents, or perhaps because she was female―

\emph{"Sample Collection Status―I remember there being a section like that in
	the Health and Hygiene Bureau's data,"} Fura had said. Sample. Mock-up.
Specimen.

No. 6 was taking samples from within the city, and apparently in secret.
Citizens were being extracted, unbeknownst, to become specimens. There
was no way this wasn't related to the rumour of agitation and
abnormalities trickling out from inside the city.

Shion knew this too, in his guts.

If Safu was a sample who fulfilled their various requirements, then she
was valuable. They would probably need a suitable facility in which to
handle such a valuable sample.

That was why Safu had to be on the topmost floor, the Special section of
the furthest part of the Facility. He wasn't one-hundred percent sure,
but it was very likely.

Shion felt a violent chill.

Not at No. 6, but at himself.

\emph{How would I treat a valuable sample?} He felt a chill at how he was
turning this over in his mind coolly. He felt goosebumps form at his own
thoughts, which placed Safu in that position.

\emph{I need to be calm and rational. I need to be in this state of mind; it's
	what I need most, especially in danger.}

\emph{Don't get distracted, don't get fooled, don't lose sight.}

Nezumi had taught him.

Being calm meant repressing the furor of his feelings. The restless
tides of his human emotions lurked constantly in his heart; and yet, he
had to suppress them inches from the surface. That was how it was. If he
let himself lose feeling and emotion completely, all that would remain
would be a heartless being.

\emph{But can I say that I'm not heartless? Maybe there's a part of me that's
	gone completely cold, and I'm just mistaking it for calmness.}

He gritted his teeth.

\emph{Don't get distracted, don't get fooled, don't lose sight. And don't
	wander.}

\emph{This isn't the time to be getting lost.}

There were hurried footsteps. Two sets. One was plodding and heavy, and
the other was light.

"Why does it smell so horrible? I can't stand it." Two men clad in white
coats came running down the stairs. Both of them had handkerchiefs held
to their noses. One man was heavyset and in his forties; the other man
was still young and scrawny.

Shion crouched in the shadow of the handrails. The men stopped right
before his eyes, and took deep breaths.

"I feel faint. What in heavens is this smell?" the middle-aged man
grumbled.

"Apparently the cleaning robots broke down. Instead of cleaning, they're
strewing trash everywhere, so I hear," answered the younger man, wiping
his brow. The middle-aged man was clearly not feeling well, for the
colour had receded from his face.

"It's impossible to get any work done in this. I feel like my nose is
going to fall off," complained the older man.

"Unbearable, isn't it? Do you suppose it's because of―you know, that?"

"That?"

"Today's the Holy Celebration. We're probably suffering some kind of
heavenly punishment because we're working on a holiday."

"It can't be helped. When you work for a research organization, you
can't always get your vacations by the calendar. But being rather
unscientific, aren't you, saying things like 'heavenly punishment'?"

"I guess." The man paused. "But these days, I find it suddenly occurs to
me that..."

"Occurs to you? What does?"

"...That maybe someday, the heavens are going to punish us. That if we
keep going like this, we'll eventually pay the penalty."

"What? And who do you suppose would be able to exact punishment on us?
Are you sure the smell hasn't short-circuited your brain?" the older man
said sardonically. "―You listen to me: even if you happen to have
unscientific thoughts, don't say them out loud. You'll earn the brand of
an ineligible citizen. And you can forget about your reputation as a
researcher."

The young man shrugged, and lapsed into silence.

Shion turned and signalled to Nezumi with his eyes. Nezumi acted at
almost the same time. Nezumi twisted the arm of the man in front of him,
and pressed a knife to his throat. Shion also burst out, and twisted the
young man's arm behind him.

"Wh-What―"

"Don't move. Don't make a sound. Make a noise, and I'll kill you."
Nezumi's voice was low, heavy, and cold. It was the voice of a murderer.
It agitated fear inside the person, and sealed any attempt at a
struggle.

Shion was yet again faced with the truth that Nezumi was an incredibly
talented actor.

"You too," he whispered in the young man's ear. It didn't go as well as
Nezumi. But Nezumi's voice and his silver knife played its part well.
The two of them showed no signs of struggling. They stood stock-still,
like wooden poles. Only their bodies trembled slightly.

"The door on the right," Shion said. "Hold the name tag on his chest up
to the sensor."

Nezumi nodded, and positioned the man in front of the door, with his arm
still twisted behind his back. The sensor embedded into the top part of
the door activated, and blinked on and off.

The door slid silently open.

"A change room," Nezumi said.

"Yeah."

"I see. A perfect hiding place for these gentlemen." Even before
finishing his sentence, Nezumi had spun around nimbly and had ground his
fist firmly into the man's stomach. Shion pushed the young man's body
forward. The man tripped over his own feet. The blade of Nezumi's hand
swung down upon his neck. It all happened in the blink of an eye.

The two men crumpled to the floor without uttering a single sound.

They stripped the men of their coats, and shoved them inside the
lockers. \emph{Like highway bandits}, Shion thought fleetingly. He didn't feel
strange about it, nor did he feel guilt. One more upper hand, one more
step forward. That was all he was setting out to do. He slid his arms
through the sleeves of the white coat.

"How do I look?" Nezumi twirled in his white lab coat.

"You look good."

"Thank you. They're a fine set of stage costumes. A little on the big
side, though. So? These name tags function as ID chips, then?"

"Yeah," Shion answered. "The door opened, so I think we can be sure
about that." He figured even No. 6 wouldn't embed each and every single
Facility employee with a chip. Embedding them inside the body would make
them incredibly difficult to retrieve. If they were to go through the
trouble, they would chip people who didn't need to get them retrieved:
first, prisoners; then, those with access to the most confidential
information―those who could access the top floor by their own will.

He had guessed that other personnel would use an identification item
which they could wear and take off easily, and could distinguish at a
glance.

His guess was right.

With these chips, they would go as far as they could go.

Shion and Nezumi made eye contact. No emotions swam in those grey eyes.
He felt somehow relieved. No matter what situation he was in, he would
have these unwavering eyes by his side. They had been like a sturdy
supporting pillar for Shion. All this time, they had supported him.

Shion closed the locker.

\emph{No, Shion. From here on out, you have to be the one to blaze the trail.
	Instead of the stern, you have to be the prow.}

They exited out into the hallway. An odour permeated the place, which
smelled a lot like rotting garbage.

"Hey, what's going on? What's this smell?"

"The whole building is full of it."

"I feel faint. I think I'm going to throw up."

People burst into the hallways, or came clambering down the stairs,
holding their hands or handkerchiefs to their mouths. Some were deathly
pale. Others had a sheen of sweat on their foreheads, and still others
were close to tears.

Shion furrowed his brow, not at the stench, but at the commotion. It was
indeed a bad odour, but was it something to make such a fuss about?

The smell that wafted over the marketplace in the West Block was nothing
like this. It was a more concentrated, more vividly disgusting stench.
And everyone lived in it. They raged, harangued, drank, sometimes
laughed, and cried in it. They lived every day there.

But this, this was merely―

"They haven't any immunity, after all," Nezumi muttered, as if to sense
what was in Shion's heart.

\emph{No immunity. Well, I guess that's true.}

Disinfection, odour removal, humidity control―artificially building a
comfortable environment naturally meant the removal of everything
unpleasant. No. 6 had received its name as the Ideal City, the Holy
City, through purging and exterminating rubbish, refuse, bacteria,
viruses, smells, odours, and noise―all of it.

No. 6 had a standard frame, and did not tolerate anything or anyone who
crossed the boundaries of this frame. It concerned not only smells,
noise, and bacteria; it purged humans as well. It ruthlessly cut them
away. The majority of prisoners in this Correctional Facility were not
criminals in the real sense; they were merely people who had exceeded
the permissible bounds of the Holy City. They had not declared their
loyalty to the city, or they had raised an objection. They had not
complied. They had questioned its ways. There were probably a great
number of people who had been imprisoned on a charge of these crimes.
The rest were those who had committed crimes due to their poverty, or
out of want of food. And underground, the residents of the West Block
were groaning in pain.

Expel all undesirables without an exception.

This was the world of No. 6.

The result of the policy had shown itself in this small scene.

Any faint smell was enough for these sensitive people to react and
panic. It was a sign that the physical tolerance levels of the citizens,
like their city, were becoming dangerously low.

How fragile they were.

Had Nezumi perceived this fragility? It was a slight, almost
unnoticeable crack. But even a crack small enough to be overlooked could
be a trigger for collapse.

This frailty, this defect in its resistance, could be the wound that
would seal No. 6's fate.

Had Nezumi seen through all of this, too?

Shion didn't know.

He realized he barely knew anything about Nezumi. He thought he had
begun to see into his past, into how he had been raised, but―

He didn't know. He knew just as little as when they had first met.

Nezumi was almost like a deep forest.

No matter how far he waded in, he could never gaze out over its
entirety. Here, clumps of flowers bloomed; here, a bowed branch bore
fruits. Here, a spring gushed forth, and he could hear the gentle sound
of its flow. He had definitely seen these various scenes, but they were
mere parts of the deep, vast forest. Perhaps he would emerge from the
dense trees to be faced with a sheer cliff. Perhaps there lurked
man-eating beasts. Perhaps a scene totally unknown to him would stretch
before his eyes. He didn't know.

No matter how far he waded in, Nezumi never revealed his entirety to
him. The further he waded in, the more unfathomable it got.

\emph{I've wandered and gotten lost in an endless forest. I'm drifting, a
	tangle of throbbing pain and dreamy ecstasy.}

\mybreak

There was a cotton handkerchief in Shion's coat pocket. He used it to
cover his nose and mouth. It wasn't to shield against the smell; it was
to hide his face. This way, the risk of being spotted would lessen.
Nezumi also pressed a white handkerchief to his mouth.

They climbed the stairs. The odour gradually grew stronger. Still, the
security alarms didn't go off.

A chime sounded, and his feet froze on the spot. A bead of sweat rolled
down his temple.

"Commencing odour removal. Commencing air filtering. Operational level
8.5. The air quality of the building will return to normal in
approximately two minutes, sixteen seconds."~

The announcement was made by a mechanical voice imitating a female
contralto. A chubby man beside Shion let out a great puff of air. Shion
also breathed out quietly into his handkerchief.

"Good heavens, we're saved. It's torture, this smell."

"I don't think I can stand this for two whole minutes." Behind the man,
an equally chubby woman had twisted her face into a scowl. Her skin was
flawless, and her red pouting lips were strangely alluring. Shion and
Nezumi tried silently to slip by.

"Oh―hey, you there!" The man called at them. Shion's heart skipped a
beat.

\emph{Thump, thump. Thump, thump.}

His pulse was racing painfully. Sweat erupted on his face.

Nezumi twisted his neck around, his handkerchief still clamped over his
mouth.

"Yes?"

"Where are you going?"

"We're going... back to work."

"Third floor?"

"Yes―third floor." Nezumi coughed lightly.

"The stench is horrible up there," the man said. "You'd be better off
going down. I'd suggest you avoid the area entirely for a while. I can't
imagine you could get any work done in that."

"―We can't really afford to leave. We're doing a rush job right now..."

"Rush job? On the third floor?"

"Yes..."

"But the third floor is for resource compilation and management systems.
What section of the third floor are you?"

"Hygiene Management," Shion answered. He traced the floorplan in his
head.

Third floor. He could guess judging by the layout of electric circuitry
that the General floors ended at the third. Starting from the fourth
Special floor, the circuitry spread into a fearfully complicated web.
The fourth floor was connected to the~Surveillance Wing of the
prisoners. Mobile barriers were placed at equal intervals in the
hallways, and the number of sensors were over three times that of the
General floors.

The majority of Facility personnel could only access as far as the third
floor. They had no need to go further. What sections were laid out on
that third floor? The floorplan rose vividly in his mind. If he
remembered correctly, the Hygiene Management department was nestled in a
far corner of the third floor.

"The source of this smell still hasn't been identified," Shion said
hesitantly. "We Hygiene Management employees are in a bit of a panic
right now. We're not getting any data of foreign objects coming in from
outside, so there's a possibility that something has gone wrong inside
the building..."

"Oh, really? According to Management Systems, there was a maintenance
problem with the cleaning robots, and they supposedly broke down and
started strewing trash everywhere. That's not it?"

"Ah, well, that's..." He was at a loss for words. Nezumi answered in a
low, hoarse voice.

"The smell seems too strong for just that. We're doing an emergency
investigation into whether there was something mixed in with the
garbage. We've had no previous cases, after all... we're fumbling, truth
be told."

"Hm. I see. Were there always young'uns like you in that section,
though?"

"We're not―that young," Shion stammered.

The man craned his neck to inspect him. "What happened to your hair?
It's gone all white."

Shion couldn't find any words to say. He had forgotten about his
hair―white, to the point of transparent. No doubt it was extremely
noticeable. If he said he was born with it, people would probably be
suspicious about never having seen him before.

\emph{What to do?}

"I, well... I tried dyeing it..."

"Oh, how pretty," the woman smiled. "It's \emph{very} pretty. So nice and
shiny. What did you use to get it to look like that? Tell me all about
it."

"Sara, stop flirting with him."

"Excuse me? \emph{Flirting?} How rude. I don't know why you can't be a little
more polite. Ugh, this \emph{smell}. I'm sick of it, and I'm sick of you, too."
The woman stalked off down the stairs.

"Wait―hey, Sara! What was that supposed to mean? Hey! Wait up, Sara.
Wait!" The man wiped the sweat off his brow as he~

followed after the woman.

"A romantic spat if I ever saw one. That guy supposedly tries to pick up
ladies in broad daylight. At work, no less." Nezumi shrugged. "Saved our
asses, though."

If the man had questioned them any further, they would have been in
trouble. Shion felt a coldness around his armpits.

"You've gotten pretty good at lying. But not quite polished enough on
the finish."

"Not as nearly as good as you. Looks like I'll need a lot more
training."

"Good call."

The third floor was white-walled and white-floored, and though it was
neat, it was eerily blank.

"So this Management Systems room?" Nezumi said.

"Left-hand side. It's a glass-panelled room. Nezumi, surveillance camera
right above you. Don't look up. Be careful. There's also a 360-degree
camera on the ceiling to your top-right after you enter the room."

"Roger that."

The odour removal and air-conditioning mechanics were well underway,
evidently, for the smell had dispersed considerably, and did not bother
them much. The confusion was beginning to settle.

The glass doors slid automatically open, and a thin man with a jutting
chin came out carrying a vacuum. He looked ill; there was a dead look in
his eyes, and he was horribly pale.

"I've done it... I've actually done it," they heard the man mutter as he
passed them by. "I've done it... but... serves them right... serves them
right..."

"Get out of here quickly," Nezumi whispered to the man's back. The man
stopped in his tracks, and glanced furtively at Nezumi.

"Did you say something?"

"I told you to get out of here. Don't dally."

"You―"

"You've pulled it off admirably. A job well done." His tone was that of
a king congratulating a subject. The man blinked. His Adam's apple
slowly bobbed as he swallowed.

"Who... are you?"

"I'm grateful. Now make a good getaway." Nezumi flashed the man a
seductive smile, and slowly set foot inside the Management Systems room.
He didn't look anything like he was in a rush. He had the footsteps of
an honest employee returning to his work.

The security alarm did not go off.

\emph{We're still good.} Shion clenched his hand into a fist. His palms were
sweaty. \emph{Things are going better than I thought. If they continue like
	this, maybe we'd be able to pull it off.}

\emph{No, don't let your guard down. Even a slight moment of inattention could
	cost us our lives.}

Following in Nezumi's footsteps, Shion also entered the room neither
hastily or cautiously, maintaining a perfectly ordinary step and speed.

It was spacious inside, and the room was sectioned off with clear walls
of reinforced plastic. The booth closest to where Shion and Nezumi had
entered was empty. There was no one there. The booth next to that also
showed no signs of anyone. They had probably fled, unable to bear the
smell. But the smell had now been mostly removed; people would be
returning soon.

"This must be the management division for ventilation. And―"

"The operating button for opening and closing Point X should be here,
too." Nezumi's gaze focused on the right-hand edge of the control panel.
A small, round button. It was a vivid, almost cheap-looking shade of
green. It looked almost out of place amongst the other switches and
touch panels. Shion stood in front of the control panel.

"Oh, yeah," Shion said. "The surveillance and management of all
entrances and openings take place beyond this wall, but the door to
Point X is the only thing that doesn't."

"Is that strange?"

"No. It's just as you said: that door is impenetrable. It will never
open. No. 6 never considered the chance of someone coming in through
that door. Of course, they never considered opening it from their side,
either. So this button for them was actually meaningless. That was why
it didn't matter where they put it. There was no need to keep watch on
it, anyway."

As he spoke, Shion tapped a large screen in the centre of the~

control panel. Of course, he was concerned about his fingerprints being
lifted, but the screen wouldn't function if he didn't touch it directly.
Security measures would take effect, and it would lock itself.

"That's right," Nezumi answered. "It's indulgence. Indulgence that comes
from complacence. No. 6 thinks nothing in the world can threaten them.
Makes you laugh, doesn't it?"

Point X was created when Rou was placed in the underground settlement,
though at the time, it had probably been mere caverns. The caverns
themselves were to be his prison. Then, the Correctional Facility
gradually grew closer to its current form: a new, even more secure
imprisonment facility than the caves.~

The underground caverns, Rou, and the other prisoners were forgotten.
Either that, or they were written off as people who had never existed.

Only the door remained.

The screen changed into a layout of the Correctional Facility's
ventilation system.

"Nezumi, look here." There were stairs leading from the fourth to the
fifth floor, and to the top floor as well.

Each step was 120 millimetres deep, and 240 millimetres high. It was
quite a steep slope. The stairs were also barely wide enough for one
adult to climb. It was more like a ladder than a set of stairs.

Nezumi peered in. "What's this?"

"Stairs for construction and maintenance. Everything is usually
computer-regulated, but once in while they would probably need some
manual labour. The stairs were probably made with that in mind. They
probably haven't been used much, though."

A soft exhale escaped Nezumi's lips.

"I didn't know there was something like this here. Did you know about
these stairs all along?"

"No, I only guessed," Shion said. "I noticed it when I first looked at
the floorplan. It was an unusual blank space."

"I didn't notice."

"It's in the wall. There was a narrow space between the outer and inner
walls. This particular part was wider than the rest."

"So you saw something that I overlooked."

"That's right."

\emph{Tsk.} The sound of a frustrated click of the tongue.

"And is that spot gonna welcome us in like an amusement park? There
aren't any anti-trespassing devices?"

"I don't know. This screen only shows ventilation-related systems. I
can't tell about anything else."

"You said it was a blank. So there's nothing written in there."

"No."

"Then how about a door? If there are stairs, there has to be a door that
leads to them."

"I don't know about that, either. There's nothing written here that
might pertain to that."

"Then we don't have a next move."

They did not have a next move. But they would have to move anyway. If
they couldn't use the central stairs or the elevator, this was the only
route that would take them to the top floor.

Shion had stared at the floorplan long enough until he felt his head
throb, memorizing the interior structure. This was the conclusion that
he had drawn as a result.

Their chips would not take them any higher. They would have to~

set foot on these stairs, using any method they could. If only they
could bound up the steps in one dash. The mother computer was on the top
floor. They had to get there. They had to reach it, no matter what.

This was the only way.

In a way, the Correctional Facility was like a prototype of No. 6. All
information, activities, functions, and monitoring networks led back to
the mother computer. This meant that all the power was in the hands of
the single person who could control the Mother freely.

A perfect hierarchy, in which the king was the absolute summit―that was
what they were trying to create. It was an incredibly vast, yet foolish
ambition.

Humans could control machines. They could develop and refine devices,
and use them in any way they liked. But it was impossible for humans to
dominate other humans. Even empires which had proudly stood for a
thousand years, crumbled after that millennium. Humans could not
dominate other humans. The system would always break down.

Shion had learned this outside No. 6. The ones inside―those reigning
over No. 6―had evidently not. That was why they could continue to
believe in this illusion that they would conquer all.

They were foolish. But foolishness created a vulnerable opening. If they
could make contact with the mother computer, they would be able to find
out Safu's location, and they would be able to halt the Correctional
Facility's functions, if even momentarily.

With a centralized system like this one, where everything concentrated
into this one single point, then all they had to do was attack that one
spot.

No. 6's fragility had also revealed itself here.

Shion's fingers flitted about. The screens changed one after another.

The barriers on the fourth floor. They had to overcome those somehow.
They had to break through the open space before the walls closed in on
them and blocked their route off.

And to do that―

The inside of his head settled into a cold stillness. Only his fingers
kept moving, and finished one task, then another.

"Hey, there's something wrong here," yelled a man in the next booth.
Several workers had already returned. "The activity lamp for Point X is
on."

"Point X?"

"On location po1-z22. The door's been opened and closed. It's recorded
here."

A tall, young man tilted his head in perplexity. "Po1... that's
underground. Did we ever have a door there? Are you sure it's not a
display error on the part of the computer? Maybe the smell was so bad,
even the computer couldn't handle it. Haha."

"This isn't a joking matter," the other snapped. The man closed his
mouth.

"Two minutes and forty seconds ago. That was just now. The door on Point
X opened right in the middle of that commotion."

"Is there something wrong with it opening? Doors are supposed to open,
aren't they?"

"It's not general entrance door. It's not an emergency exit, either. The
staff don't use this door."

"Oh. Then, where's the door supposed to lead?"

"I don't know. I've never heard of it. But this means that a door that
was never supposed to open has opened. This―"

Evidently the sound-proof setting was off, for the boys could hear the
muffled voices of the two men conversing.

"Our time's up." Nezumi undid the buttons of his lab coat. Shion stood
up as well.

Two minutes, forty seconds. It was much longer than they had
anticipated. It looked like Fortune had not abandoned them just yet.

"Oh―hey! You there." A grossly overweight mass of a man was standing in
front of them, blocking their way. "What are you doing there? Who are
you?"

Nezumi flung his coat at the man, which landed on the man's head and
draped over him. The man flailed his arms and staggered. Nezumi swept
his feet out from under him. The man fell sideways with a resounding
crash, and gave a muffled groan.

"Excuse me." Nezumi stepped over the man, and exited into the hallway.
Shion followed suit and hopped over the man's body.

"What was that?"

"Somebody―an intruder! Somebody help!"

"What? Has the emergency bell gone off?"

An agitated buzz rose from behind them.

"Nezumi, run up the stairs."

"Gotcha."

If the sensors caught any intruders, the security shutters would fall
automatically. Could they reach the fourth floor before all the shutters
went down?

The lighting on the stairs turned red. The shutters of special alloy
silently began to close.

They were fast.

"Shion, go in head-first."

Nezumi and Shion dived into the narrow space.

\chapter{If one's human soul}

\myepigraph{If one's human soul should completely disappear, one would
	probably be more likely to find happiness. But even so, the human inside
	oneself feels horror towards it like nothing else. O how so completely
	terrifying, grievous, and painful he thinks it! For one to lose his
	memories as a human.}{Nakajima Atsushi, Sangetsuki}

\lettrine{S}{he had} awakened.

Safu had awakened, and understood everything.

She knew now what had happened to her.

\emph{What have you done... what have you done... what have you done?}

"Goodness, Safu. What's wrong? Look at the fluctuation in your emotions.
How long do you plan on keeping up this agitation for? What a
troublesome child. Your beauty is going to waste." He chuckled. "Ah, no,
that was just a joke. A flat joke. Don't mind me. You are still
beautiful, very beautiful. A huge success. Things are going exactly as
planned so far. And of course, there will be no mistakes in the future,
either." He chuckled again.

The man continued to laugh from his spot beside Safu.

\emph{Devil.}

\emph{So you were the Devil.}

\emph{Why―why―why have you done this to me?}

"You are not only beautiful. You are also resilient. You are my ideal,
Safu, let me confess that. I cannot lie to you, after all. I... at first
only collected you to use you as a specimen. I tried to treat you as I
would any other sample. Oh, I hope you will forgive me. I don't want you
to reproach me like that. I didn't know that you would be so beautiful
and strong. Safu, you captivated me. I could repeat myself a million
times. You are my ideal―you are what I've been looking for. That is why
I will make you queen. No, I will make you into someone close to a
goddess. A perfect existence. You and I, we will rule the world
together. How does it sound? Exciting, isn't it?"

\emph{Devil.}

\emph{You are the Devil.}

\emph{Don't come near me. Don't come near me.}

Safu's voice did not reach the man.

The man continued to talk fervently as if he were possessed. Colour
tinged his cheeks, and he paced in circles, back bent slightly forward.

He was like a fish in an aquarium. He went round and round, round and
round, swimming in an enclosed space. Round and round. Round and round.

The man's feet trod silently on the floor as he continued talking.
Perhaps he was speaking more to himself than Safu.

"I finally have you in my hands. The ideal materials. Oh, Safu, I'm no
believer in fatalism. I don't believe in forces beyond the bounds of
human power, or the heavens being in control of our lives. I have always
laughed in scorn at it, calling it absurd. But―please don't laugh, Safu.
After meeting you, I, well... I feel like I could believe a little bit
in this so-called fate. Perhaps it is true. Perhaps there is a God, and
He is trying to bestow me with an absolute power. If not, what could
explain the fact that I met you like this? That is why I will make you a
goddess. I have the power to do it. Oh, yes. Yesterday, I told you that
you wouldn't need a name. Right, of course, of course. You should throw
away your name from the past. I shall give you a name suitable for a
goddess."

The man's feet and tongue showed no signs of stopping.

He kept walking. He kept talking.

"Yes, how about..." The man's feet stopped abruptly. A slow smile spread
over his face. "How about... Elyurias?"

\emph{Elyurias?}

The man resumed pacing. The blissful smile still hung over his face. "A
splendid name, isn't it? Indeed, a name fit for a queen. Perhaps it is
all the more suitable for someone like you."

\emph{This man...}

Safu's gaze locked onto him. For the first time, she got a good look.

His thin face looked gentle at first glance. His age―it was hard to
tell. Depending on how the light hit him, he either looked very young,
or considerably aged. The man had completely cut himself off from the
external world and was wallowing in his inner realm, staring intently
into the air and soliloquizing his feelings.

Self-intoxication.

This man was completely absorbed in himself. He believed that his
abilities were equal to that of God. He believed he was entrusted with
everything, that he would be forgiven for anything. That... that was why
he could do this.

"Just a little bit more. Just a little more, and my project will be
complete. You were the last piece. Thanks to you, I have all the parts I
need. They're complete, that's no mistake. I just need time. I just need
a little more time. How do you feel? I want you to be comfortable, and
for that, I would do anything. You are one of the most important things
in my life right now, after all."

\emph{Set me...}

"What? Safu, did you say something?"

\emph{Set me free. Change me back to who I was. Let me see him.}

Her emotions reared angrily. A wind roared in her heart, howling loudly.
She wanted to scream from the bottom of her lungs. She wanted to cry.

\emph{I want to see you.}

"Oh, what's the matter? Your numbers are going up. I guess you're having
trouble adjusting to your new environment. Hmm, I thought the transition
would be smoother. Oh, no, I don't mean to blame you for it. I wouldn't
blame you for anything. You are my treasure. Will you sleep a little
more? That should make things better. Hm? ―It looks like Mother agrees
with my judgment. She says she will prescribe you some stabilizers. Oh,
yes. I have to tell you about Mother. You and Mother are directly
connected, you know. Mother will always monitor you to adjust your
conditions for utmost comfort, so that you will have the best
environment possible. So that's why, look, now she's saying that you
need rest―"

A bell sounded shrilly. The tapered ends of the man's eyebrows shot up.

"What is it? An urgent call \emph{now}? How uncouth― yes, it's me. What's the
matter? Today is the Holy Celebration, are you not busy with your
own―what? What's that? What do you mean? In the city? This is happening
in the city... no, that can't be... right, send the video over to me.
The samples, too. Everything you've collected... yes, I'm about to right
now... what? Thirty bodies already? In the space of one day... so that's
what's happened... I understand. That's enough. I'll go over there
myself... yes, immediately. Immediately."

All the blood had receded from the man's profile. His lips were
bloodless, white, and parched. They trembled uncontrollably.

"It's a mistake. It must be a mistake. That... that couldn't have
happened. It just isn't possible," the man practically spat, as he
exited the room. He was agitated to the point of it being unnatural. All
the ease and eloquence he had a minute ago were gone without a trace.

\emph{This is happening in the city}, the man had said. Had something happened
inside No. 6? Something that exceeded that man's predictions...?

\emph{No. 6, where I was born and raised. But there was always unrest
	squirming below the surface. It was such a comfortable and beautiful
	place, and yet it was always precarious... the lingering feeling that
	something was about to happen... at least, I thought so...}

Safu could feel her rage gradually begin to quiet.

She was sleepy. So sleepy, she could melt. Had she been dosed with a
sleeping drug? She was connected to the Mother―what did that mean? The
Mother... \emph{oh, I'm so sleepy.}

Her consciousness blurred. It became hard to think. And in these
moments, there was always a figure which rose in her mind.

\emph{Shion.}

She tried calling his name. Shion smiled, and gave a slight nod. It
wasn't an illusion. He was so vivid, so concrete, as if he were standing
right in front of her.

\emph{Hey, Shion. When was it again? I remember the sun was setting. The wind
	was a little nippy, right? It had snowed for the first time the day
	before, and the path was wet. We were walking side-by-side. Do you
	remember? You haven't forgotten, have you?}

\emph{And I called your name, didn't I?}

\emph{Shion.}

\myspace

She called his name again. And Shion, again, smiled at her.

"What's wrong, Safu?"

"No... I just―"

"Just?"

"I just wanted to call your name. I was giving it some hard thought, and
I actually realized that 'Shion' is a nice name. It's a flower."

"You had to give it a hard thought to notice it was nice?"

She had giggled. "So, what kind of flower is a 'shion'?"

"Uh... a perennial flower that's part of the \emph{Asteraceae} family, if I
remember correctly. The stem grows up to 1.5 metres high, and it blooms
with light purple flower heads..."

"Shion, I don't want to hear an explanation about the flower. I can get
that kind of information easily."

"Then what do you want to know?"

"Something that I can't get easily."

"Can't get easily... hmm, that's almost like a riddle. If you don't want
to hear about the aster flower, then... nope, I have no idea. What do
you want to know, Safu?"

\emph{I want to know about you, Shion.}

\emph{I wanted to know you. Who named you that? Do you like it? When was
	it that I first called you by your name? And when was the first time you
	called me....?}

\emph{Shion, I still don't know anything about you.}

\emph{I know your habits, the food you like, how you talk, your
	gentleness and strength... yes, I do know. I know it very, very well.
	But, Shion―}

\emph{Who were you chasing? Who did you long to be beside? Who were you
	yearning for? Who stands at the other end of your outstretched fingers?
	Couldn't it have been me? Did it have to be that person? I don't know
	anything. So tell me. I wanted you to tell me, Shion.}

\emph{Shion.}

\myspace

Safu.

She heard a voice. Sparks burst in the haze of her consciousness.
Scarlet flowers opened their petals. A wind scattered the fog that hung
over her eyes, and in the same way that the scenery would unfold before
her, Safu's consciousness came back to her. The voice had called it
back.

Safu.

\emph{Who is it? Who called me?}

It wasn't Shion's voice. Nor was it her deceased grandmother, or her
parents. It was a voice she had never heard before―no, sound? Melody? A
breeze in the canopies, the gentle splash of water, the pounding of rain
on the ground―it sounded similar. But it was different. It was a sound
she was hearing for the first time.

\emph{Is it a song―? A beautiful, song-like...}

Safu.

\emph{Who is it? Who's calling me?}

It's me, Safu.

\emph{Who? Who are you?}

I am Elyurias.

\emph{Elyurias...}

\mybreak

"Shionn, stop squirming!" Inukashi clicked his tongue as he lowered the
baby into a large pot full of warm water. The baby grinned. He flapped
his arms and legs, squealing with glee. Warm water splashed everywhere,
wetting the hem of Inukashi's shirt.

"Stop horsing around. Geez, you're really round, aren't ya?"

The baby's hands and feet, his belly, his whole body was plump and soft.
Every finger, every hair was brimming with the energy of life.

\emph{Strange guy. He's different from any baby I know. Way different. So
	different, sometimes he just makes me stop and stare.}

The kind of babies Inukashi knew always had Death curled up and ready to
spring at their feet. Their life was wrenched from them before they even
had a way of protecting themselves. Those were the kind of babies he
knew. Malnutrition, plague, the frigid air; sleeping quarters not much
better than a garbage dump. What was the fraction of babies in the West
Block who lived to turn five? Fifty percent? No, maybe even thirty. Some
kids were killed by their parents so that they would be one less mouth
to feed. Inukashi knew swarms of them whose only purpose in life seemed
to be to come into this world, only to die. For a short time, Inukashi
had done infant burials as a job. But his "burials" literally only
consisted of him digging a hole and burying the baby. It was no
different than digging a grave for a dog. He thought babies who were
sent off with the mourning of a father and the grief of a mother were
still lucky. Oftentimes, Inukashi was the only one to see the baby off.
No one ever left prayers, much less a single flower for the simple
grave, a raised mound of dirt with a rock placed on top. In time, people
forgot that it was a grave in the first place.

Babies usually died with their mouths slightly open. Sometimes, through
their eyelids which had not quite closed, he could see a set of
startlingly clear eyes staring vacantly back at him.

\emph{Of course. They couldn't even stand on their own feet. They'd have no
	way of becoming tainted. Of course they'd still be innocent.}

His heart had never ached as he piled dirt onto the small corpses. He
had never experienced sorrow, nor spilt any tears.

\emph{Good for you to have died early. You're a lucky one. You didn't have to
	suffer any more than this.} These were the only words he's speak to them.

\emph{Hey, little guy, how many months did you get to live for? Two? Three?
	You've lasted half a year? That should be enough, then. Don't even think
	about being reincarnated. You'll just end up with the same fate anyway.
	If you still want to that badly, then come back as a weed that grows on
	the edges of the path, or as a puppy. You'll be a hundred times happier.
	You listen, alright? Never, ever be born again as a human.} That was
another thing he'd say to them.

It was Inukashi's own way of sending the dead off.

Nezumi would sing. He would probably sing a sending-off song, for the
soul that had expired while it was still innocent―though Inukashi didn't
know if such a song existed, he knew Nezumi would sing it. \emph{But you know
	what, Nezumi? Dead people don't need songs. Dying people might, but not
	the dead.}

\emph{The dead return to the land, and turn back into soil. Babies do, and so
	will you and I.}

Inukashi shook his head vigorously when he realized he had been
absent-mindedly thinking about Nezumi. He crossed his left middle and
index fingers. It was his charm to ward off demons.

For Inukashi, Nezumi was something close to a demon. Even more
detestable than Death.

You could avoid Death to a certain extent, as long as you didn't let
your guard down. You could ward it off, you could trick it. \emph{But what
	about him? He thinks nothing of driving people until their backs are
	against the wall. He gets you involved in danger. He doesn't give a damn
	about your convenience or your own matters. He'll make use of dog shit
	if it serves him a purpose. He's cunning, frightfully thorough, and can
	wrap you around his finger as easy as anything. Ugh, enough, enough. If
	Nezumi didn't have his power as a singer, I would never have associated
	with him. Never. Oh―damnit, I'm thinking about him again. I shouldn't
	even devote a second to thinking about that guy, or else I'll be sucked
	in by his evil. I should know this―what's wrong with my head?}

"Come on, Shionn. You do the charm, too. Then the demon won't come
getcha. You're beyond all hope if you end up like your Papa, completely
under his spell. See, stick your fingers together like this."

"Bah-booohh, boo-boo!" Shion raised a joyful cry from his bath. He was
strange―a very strange baby, indeed. Not even a shadow of Death crept up
on him.

In their room in the ruins of the hotel, the walls were crumbling, the
windowpanes were shattered, and a cold draft always blew in. It was a
place only marginally better than outside. Rikiga was able to provide
them somewhat with milk, but it was nearly not enough. Inukashi made up
for what he didn't have with dog's milk and vegetable broth.

The baby was probably more fortunate than most in the West Block, but it
didn't change the fact that he was still severely deprived.

But Shionn was always in high spirits, swinging his hands and feet,
laughing, and babbling to Inukashi. His skin had a healthy glow, and he
was plump, round, and full of energy. Inukashi could even swear that the
baby had grown in these past two, three days.

Those eyes shined with life, his skin was smooth, and his voice was
strong. It was almost like the infant was encased in a transparent
shield that protected him from the many dangers and toxins of this
world.

A strange baby.

"Hey, Inukashi," a gravelly voice called out to him. A deep,
muddy-sounding voice.

\emph{Geez. I'm not asking you to change your face, but can you at least get
	some class into your voice?}

"What the \emph{hell} are you doing? Stop it!" There was scramble of footsteps,
and Shionn was snatched from Inukashi's arms. The pot wobbled, and warm
water spilled out.

"What's your problem?" Inukashi whined.

"You must be kidding me. Stop this!" Rikiga hugged the naked baby to his
body, retreating slowly. "Inukashi―this is going too far. This isn't
what humans do."

"Huh?"

"Aren't you ashamed of yourself? Sure, you might be more dog than human.
But that doesn't mean you don't have a shred of reason in you."

"Reason? That crap isn't gonna do any good for me, will it now? But I
guess I might have a little more of that than you, old man."

Rikiga screwed his drunken flushed face into a scowl, and retreated
another step.

\emph{What the hell is this old man doing?}

"I thought you'd have more decency for a dog boy. Inukashi, I don't know
how hungry you are to want to do this, but eating a baby? You must be a
monster. Have you thrown away your human heart, too?"

"Huh? The hell are you talking about?"

"Don't play dumb with me. You―you were trying to boil Shionn and eat
him."

Inukashi fixed Rikiga with a long stare. He didn't even blink. He could
feel laughter welling up and prodding inside his chest.

"What's so funny? You inhuman bastard."

After Inukashi had bent over double and laughed for a good while, he
wiped his mouth with the back of his hand.

"I laughed so much, I'm drooling. Ah, old man, you missed out. If you'd
come even thirty minutes later, I would've treated you with some good
soup taken from baby broth. As much as you could eat."

"L-Like I would ever eat something like that! I'd rather starve to
death. Besides, what were you―"

"A bath."

"Huh?"

"I was giving Shionn a bath."

"In a pot?"

"Yeah. This is the pot I use to make food for my dogs. It's the best
size for giving a baby a bath. Of course, if you insist on delivering me
a high-quality baby bathtub, old man, I'd be delighted to use that
instead."

"Uh... I, well..."

Inukashi shrugged exaggeratedly.

"But I gotta say, I'm flabbergasted to find out you care so much about
Shionn, old man. I thought you were only nice to your money, your booze,
and young women. What a surprise."

"Of course I care," Rikiga said indignantly. "I'm not like you. I still
have a decent human soul. Don't lump me in with you people."

"You people? Am I part of that group, too?"

"You and Eve. Who else?"

Inukashi shrugged again. "Fine. If you're so bent on it, then take him."

"Huh?"

"Tuck that baby into your coat and take him home. I can just \emph{imagine} the
fine young man he'd grow up to be, raised by such a gentle old man like
you. Just like airheaded Shion, who you love so much."

Rikiga shook his head hastily.

"No can do. I can't do it. Inukashi, I'm sorry. You're not an inhumane
bastard. I'm sorry for lumping you in with Eve, that wiley fox. I
apologize. I'm sorry. There must've been something wrong with me.
Hahaha―I see, yes, a bath. Babies love baths, right? Isn't that nice,
Shionn, aren't you glad to have been picked up by such a nice person?
You lucky guy."

Rikiga rubbed his cheek against Shionn's. Shionn burst into tears. He
opened his mouth wide, and his stretched arms and legs went rigid. An
old dog who had been sleeping underneath the table raised its head and
narrowed its eyes suspiciously.

"Oh―hey, come on, don't cry. Stop flailing around! He'll drop you."

The baby didn't stop crying. He wailed, stretching his hands towards
Inukashi. Inukashi almost reflexively snatched the baby back into his
own arms. He wrapped both arms firmly around the small body. The crying
stopped instantly.

"Geez, he'll catch a cold like this. If he gets sick, it's your fault,
old man. You'll be paying for his medicine bills. Must've been cold,
huh, Shionn? I'll get you inside the bath again. Go on, warm up."

A plump arm reached out, and its fingers touched Inukashi's cheek.

"Mama."

Tears had left their streaked marks on his smooth cheeks.

"Mama."

Inukashi felt like his heart was being wrung. Something twisted deep
inside his body. He almost stopped breathing at this huge, scalding,
twisting emotion that had reared inside him.

"Mama."

\emph{Yeah, I know, Shionn. It was a joke. A lame, stupid joke. Forgive me.
	It's alright, I'm here. I won't give you away to a drunkard like him...
	no, I won't give you away to anyone. I promise. I swear.}

\mybreak

Rikiga peered into the bundle in Inukashi's arms, and exhaled a breath
that reeked of alcohol.

"Mama," he echoed.

"What? You miss your Mama, old man?"

"My mother went six feet under a long time ago. She crawled into that
grave when I was ten, and hasn't tried to crawl back out since."

"She must be really comfortable in there," quipped Inukashi.~

"And she probably wouldn't want to see how much her son has gone
downhill anyway. Maybe she's choosing not to come out."

"Who are you calling downhill? But anyway, about Shionn..."

"What about Shionn?"

"He called you Mama."

"So he did."

"Why 'Mama', huh?"

"Dunno."

"Mama."

"See, there it is again."

Inukashi lowered Shionn back into the bathwater, and warmed him. Shionn
found it very comfortable, apparently, for he gave a relaxed smile. Its
radiance touched upon everything: beautiful things, refreshing things,
exciting things.

\emph{I didn't know babies were such precious beings.}

"Why is it 'Mama', Inukashi?" Rikiga insisted.

"Everything is 'Mama' to babies, old man. Hard to believe, but even you
were crying for you mama some decades ago. Did you stop crying once
someone flashed you a gold coin back then too, huh?"

"You're one to talk," Rikiga shot back. "You're just as attached to
money as I am. Look at the pot calling the kettle black."

"Hah, shut up."

\emph{They're such precious beings. I never knew.}

All the babies Inukashi had buried without feeling―in the frozen ground;
in the sun-beaten and parched soil; in the muddied earth of the rainy
season―now, for the first time, Inukashi cast his thoughts to each and
every one.

\emph{Maybe Shionn wasn't the only one. Was that baby a precious existence? Or
	that baby, or that other baby, too? If they were, then... they shouldn't
	have died like that. It doesn't make sense. It doesn't make sense that
	they have to die so skinny, with their skin so wrinkly you'd think it
	was some old woman. To draw their last breath with such innocent eyes,
	without any hatred for anyone, without even knowing how to hate. Like
	the one I buried at the root of a honeysuckle bush,or the one I dug a
	grave for in red soil, or the one I wrapped in rag before burying, or
	that one, or that one, or that one―they all should have been cherished
	more;. They shouldn't have been forced to die that way.}

\emph{Shionn, don't you die. Live on. Live, and grow big. Learn to hate, learn
	to cherish.}

"Muh-muhhh."

Inukashi scooped the baby up, and briskly put his clothes back on him. A
black female dog got up as if it had been waiting its turn. The mat it
had been sprawled on had cotton stuffing poking out of its ripped seams.
Inukashi had fished it out of the rubble in the marketplace. It was
faded, worn thin in many places, and more like a rag than anything else.
But upon closer examination, one could see an adorable pattern of baby
chicks. Maybe a baby much like Shionn had been using it before. On the
day of the Hunt, maybe he had been put to sleep on this very mat, and
been immersed in a dream.

"He's all yours," Inukashi said to the dog. After Shionn had been laid
down beside the dog, he immediately latched onto the dog's teat. He
suckled eagerly, making gurgling sounds in his throat.

"Rather furry nurse he's got."

"We've got as many furry girls as you'd want," Inukashi said.~

"Black fur, red fur, white fur, spotted fur. Care for a night with a
lady of your choice?"

Rikiga ignored Inukashi's sarcasm, and heaved a sigh.

"A human baby being raised on dog's milk... that's quite something. But
is that alright? God forbid he should start barking next."

"He just said 'Mama', didn't he?"

Rikiga looked down at Shionn, and heaved another sigh.

"Old man."

"What?"

"Have you made the preparations?"

Rikiga's face slowly turned towards Inukashi. "Yeah." He lifted his arm
languidly, and pointed at the black bag on the table.

"Good. Let's go, then." Inukashi lifted the bag. It weighed down heavily
in his hands. Rikiga knitted his brow and made a reluctant face.

"Inukashi... why don't we call it quits?"

"Quit?"

"Let's just forget about the whole thing."

"Forget about it, and then what?"

"We crawl back into our holes and keep quiet. Don't you think it'd be...
better that way?"

"Of course." It would be better, old man. I feel that way hundred times
stronger than you. I want to forget all about it, and crawl back into my
den.

It would be cold tonight, but not enough to freeze. If Inukashi had his
dogs with him, he'd be able to ward off the cold. Just minutes ago, he'd
filled his stomach with stale biscuits and a soup of vegetable rinds. It
was good. \emph{That means right now, I'm more or less fulfilled. If I could
	just lie down with my dogs and fall into a deep, deep sleep...}

\emph{That'd be nice.}

"Right?" Rikiga continued. "Why don't we do that? You have Shionn. You
have to protect him. If something happens to you, who's going to take
care of him? Think about it."

"The dogs are here. The dogs will raise him even without me. Just like
my mum did."

"Yeah, but... Inukashi, let me be straight with you. I value my life as
much as you do. I don't want to do anything dangerous. So," he said
hesitantly, "let's back out of this. Forget it ever happened, hm?"

"And what happens to Nezumi and Shion? You gonna abandon them?"

"Those two are already dead. There's no way they'd be alive. They
couldn't have lived if they've been rounded up by the Hunt, anyway. You
know this as well as I do. That's why it's useless. We're about to put
our lives on the line for something completely useless. Come on, let's
just stop this. It's for the best."

"Old man."

Rikiga drew his chin when he saw Inukashi's gaze.

"―What?"

"That's enough yammering. It's almost time. Let's go."

"Inukashi!"

"I'm going. If you wanna quit, old man, you go do that. I don't care.
The bag comes with me, though."

"Inukashi, why? Why are you so bent on fulfilling your duty to them? You
always acted alone. So have I. I could understand for Shion, but to go
this far for someone like Eve..."

"He's one of us."

"Huh?"

"They're part of our group. I can't abandon them."

Rikiga's dark eyes darted about. His mouth twisted into a scowl, like
someone had force-fed him some bitter herb. He scratched furiously at
the rash on his chin.

"I can't even bring myself to laugh at your joke," Rikiga said
scathingly. "You've got no taste. Just listening to you makes me
nauseous."

"Well, gee, I mean, your stomach is probably already a mess from your
binge-drinking. I'd advise you to give up the booze for you own sake,
though it's probably too late for you. Heheh, but I sounded pretty cool
back there, didn't I? You'd agree I was pretty suave, right?"

"Idiot. I can't believe you could rattle off those embarrassing lines as
if you actually meant it. Maybe you've got potential to be an actor like
Eve. You must be kidding me," he spat, "one fox is enough."

Inukashi bared his teeth on purpose into a vulgar grin. Rikiga's mouth
twisted even more severely.

"The only members of your 'group' are your dogs," he said. "You have as
little trust for humans as the length of your pinky. Keep shooting off
lies like that, and one day your tongue will rot."

"Ooh, I wouldn't want that," Inukashi said sarcastically. "Fine, let's
be frank. You first."

"Me―" Rikiga began. "Well, like I said, I want to back out. I've been
saying this over and over."

"That's honestly how you feel?"

"I'm an honest man. I don't lie."

"I can't even bring myself to laugh at your joke. Forget your tongue.
Watch it before your wang rots and falls off, too. How much money did
you spend to come up with what's inside this bag, huh, old man? I'm sure
you've gotten tons of gold from Nezumi, but at best, that gold'll offset
your expenses and you'll be even... no, you'll probably be down. If you
scamper on back to your hole, you'll be losing all that extra money you
spent for nothing. Could you stand that, really? Of course not. Are you
the kind of humble man to just back down and submit to your loss? Hmm,
even a pure and innocent kid like me finds that hard to believe."

Inukashi whistled. A few dogs that had been laying low near the walls
stood up. He whistled again, this time at a slightly lower pitch than
before.

The dogs surrounded Rikiga. Without so much as a snarl, they formed a
circle with Rikiga at the centre.

"Don't assume they're just normal dogs that are a bit on the big side,"
Inukashi said. "These guys have been trained to be guard dogs since they
were born. I trained them myself, you'll see they're not just any kind
of dog. What would I call them... yeah, like elite troops trained
exclusively for the offense. They'll latch onto human throats―hell, even
a tiger's. It's too bad we don't have any tigers around here. We got
tons of humans, though."

Rikiga clutched his throat, and shrank back. A pronounced fear swam in
his bloodshot eyes.

"Inukashi... cut that out, that's a stupid joke." He knew it was no
joke. Rikiga's voice cracked, and the fear in his eyes deepened.

Inukashi repressed his emotions, and continued speaking in a flat tone.
A cold, inscrutable voice was much more fearsome than a rough and
aggressive manner. He had learned that from Nezumi.

"Only Nezumi was able to escape from these guys. But barely. They
managed to chomp down on his shoulder. Pretty deep. He didn't make a
sound, but I think it must've been painful."

"That Eve, huh... what an accomplishment."

"Hmph," Inukashi sniffed scornfully. "If you've got better moves than
Nezumi, old man, you'd be able to make it through. If not―"

"As if I would be able to scurry around like Eve does. Just climbing the
stairs leaves me out of breath these days, and I know it's nothing to
brag about." Rikiga sighed deeply, and let go of his throat. "Fine,
Inukashi. I lose. This is your kingdom, after all. I could struggle all
I want, but I wouldn't be able to win."

"Feel like coming clean now?"

Rikiga glanced furtively at Inukashi's face as if to gauge his mood.

"Starting to resemble Eve more and more. Don't let him poison you.
Nothing good will come of it. Actually, you might be beyond all help
already."

"That was the most useful piece of advice I've ever gotten from you
since we met, old man. Thanks. But you don't need to worry. Once this
business is over and done with, it's good-bye to him for good."

This was his honest intention.

Inukashi didn't like to be around Nezumi. He couldn't see through Nezumi
at all, nor could he place a finger on him. But despite that, Nezumi had
a strange magnetism about him. Inukashi found himself entangled in
Nezumi's web. Like Rikiga said, he was being poisoned by him.

\emph{Danger, danger. Gotta say good-bye.}

"Good-bye? Are you leaving this place?" Rikiga asked.

"Never. This is my kingdom, I would never leave. I wouldn't even hand
this place over if No. 6's army came crashing in. I'll be saying
good-bye, but I won't be the one leaving. It'll be Nezumi."

"Eve?"

"Yup. The fraudster actor." Inukashi licked his lips. They felt dry.~

The dog that had been nursing Shionn gave a wide yawn.

"He's a wanderer. He appeared in this place out of nowhere, and decided
to stay. Eventually he'll go wandering again. He's like a whimsical
cloud. He'll rain himself out for a bit, and then he'll disappear over
the mountains."

"I see. So that's what you think of him."

"That's what I expect him to do."

\emph{I'll live on this land for the rest of my life. But he'll probably
	disappear.}

It was a gut instinct. He had nothing to prove it. He had heard nothing
from Nezumi himself. It was only something that he, Inukashi, personally
felt. But he felt like he probably wasn't far from the mark.

\emph{Like the clouds travelling across the sky on the wind, like petals
	scattered on the surface of a river, he's going to vanish from our
	sight.}

\emph{I can't wait.}

"Well, enough about Nezumi. Enough about me, too. That leaves you, old
man. So? Why did you try to lead me away from this plan? Why'd you go as
far as to put on a lame act just to make me withdraw?"

Rikiga puckered his lips, like Shionn did often. The gesture on a plump
baby was adorable, but on a middle-aged man flushed with booze, it was
rather revolting. Inukashi averted his eyes.

"You've got it wrong," Rikiga insisted. "I was just scared for my life.
You could say I got cold feet. I was sitting down with a few drinks, and
the more I thought about it, the more afraid I became of what I was
about to do. All I could think of was how much I didn't want to die, and
I just couldn't stand it anymore... I don't know if it's because of the
alcohol, but I feel like these days, once my head gets fixed on a
thought, it just stops working. I just get stuck deeper and deeper in
the rut. You know, Inukashi, maybe I haven't got much longer to live."

Rikiga slumped his shoulders dejectedly. His eyes turned pitiful, like a
sodden puppy. Inukashi had felt pity for sodden puppies before, and
taken them under his wing numerous times. But not humans. He felt even
less inclined when that human was carrying some emotional burden.

Inukashi snapped his fingers.

A larger black dog, which had been standing in front of Rikiga, crouched
into an attack stance. It flashed its canines and gave an intimidating
growl. Its gaze was fixed squarely on Rikiga's throat.

Rikiga gave a terrified whimper. "Hey, stop it."

"I don't have time for your hammy acting, old man. That's it. I've had
enough. Just answer my question. Once you get your throat torn apart,
you wouldn't be able to talk even if you wanted to."

"I-I'm talking right now, aren't I?"

"Old man, you said before―the day before the Hunt. When I said I wanted
out from this plan, you were hell-bent on stopping me. But today, you're
saying both of us should have nothing to do with it. Some 180-degree
change, don't you think?"

"I'm inconsistent. Always been."

The black dog snapped its jaws, opening its mouth wide. Its sharp fangs
showed, and saliva dripped onto the floor. You could almost hear its
steady \emph{pat-pat}.

Rikiga clicked his tongue. "Tsk. I've gotten old, to take threats from a
dog-boy like you. Fine, I'll talk. That's what you want, right?~Fine.
Damnit, this pisses me off."

Rikiga produced a small bottle of whiskey from his jacket pocket, and
drained it in one draught. He let loose a rude burp.

"Pray excuse my lack of manners, Your Majesty," he said sarcastically.
"So, Inukashi―about the strange incidents that are occurring inside No.
6. Looks like they're real. Everything seems to just have erupted all at
once. I didn't expect this turn of events.~

Couldn't even predict it."

"What's happening all at once?"

"Citizens dying right and left inside the walls."

"Holy City residents?"

"Yeah. Today was―what do you call it, the Holy Day, or some festival or
other, that honours the founding of the city, right? People who gathered
for the festivities just collapsed all over the place. And none of them
survived. They died. Each and every one of them."

"Is that―an accident? Like a poisonous gas leak, or something―"

"That would result in a massive death concentrated in one place. But it
looks like the commotion is happening all over the city."

"Then what―terrorists?"

"Terrorists? Have there \emph{ever} been terrorist organizations in No. 6?
That's the most thoroughly-monitored city-state I've ever seen. There's
a city that exterminates undesirables right down to the last cockroach.
It's impossible."

"Then why's it happening?"

"I don't know. I've only skimmed the news from No. 6. It pretty much
said a random accident occurred in the middle of the ceremonies that
resulted in civilian death. The ceremony was cancelled partway through."

"And where do you get 'dying left and right' from that? Are you sure
you're not just being delusional, old man?"

Rikiga's lip curled into a smug grin. "I've had a long relationship with
that city, you know. I've got my own intelligence network. But, well...
not all of them are trustworthy, though. Anyway, if that city's media is
saying 'a few deaths', then there has to be at least a few dozen. When
they say the cause is unclear, it means they have no clue what it is.
But this is No. 6. This city is home to some of the brightest scientific
minds. What in the world is going on that they can't solve?"

\emph{What's going on?} The thought crossed his mind momentarily, but the
answer was still shrouded in a fog. He couldn't even make heads or tails
out of it.

"You know the answer, old man?"

"Me? Obviously not. If I had that much power, I wouldn't be sitting here
being threatened by your dogs. But―think, Inukashi. That high-and-mighty
city is running itself up the wall, unable to deal with the problems
that are occurring inside it. Doesn't it make you excited?"

"Well, yeah..." Inukashi said somewhat dubiously.

Rikiga's grin widened. He looked genuinely happy. Inukashi knew his dogs
usually made that face when they were given a pork rib.

"It's the first time, isn't it, Inukashi? No. 6 has never been this
confused... this is the first time. Maybe it'll turn out as Eve said.
No. 6 won't last much longer. It'll crumble from the inside."

"Yeah..."

"You know, I've never taken that fraud of an actor for his word. Neither
have you."

"No, I haven't."

"But this time around, he might not have been tricking us. That city
might fall apart, just like Eve predicted. The signs were all there.
They're just getting stronger, building up to this. And if that's
true... then next, the big quake will come―"

Rikiga's hands came together noisily as if to squash something
invisible.

"―and flatten it."

"Ahh, I see it now," Inukashi said. "You believe Nezumi, old man. You
believed the Holy City would fall. So would the Correctional Facility.
It might become true, and not just end as a fairy tale. Which means the
gold bullion that's supposedly stored in the basement of the Facility is
starting to sound a lot more real too, along with the chance of stealing
that treasure. The possibility keeps climbing."

Inukashi pointed a finger at the ceiling. Rikiga turned aside.

"But then you started feeling reluctant," Inukashi continued,~

"about sharing it with me. The more you thought about it, the more you
didn't want to hand it over. So to get your full claim over the gold,
you put on this hammy act. You're helpless, old man. Forget booze, all
that greed has probably got to your brain and turned it to mush."\\

"Not much better yourself. You seemed eager about the gold bullion. You
were licking your chops, you were."

"Yeah, I'm eager alright. It still makes me drool. But let me tell you,
until now I've been on the fence. I was pretty suspicious about whether
there was really gold in the basement of the Correctional Facility. But
if you're going so far as to put on an act to snatch it all for
yourself, then... heh heh, I think now I believe it a lot more. You got
your information from a girl named Suru, right?"

"Yeah. No. 6 executives are her best customers. When a guy tells stories
to his prostitute in bed, it's bound to be trustworthy."

"I see. So, No. 6 gets to be wiped out and we get rich at the same time.
Sounds awesome. So great, in fact, I think flowers are going to sprout
on the top of my head."

"If everything goes well."

"What? Don't rain on my parade here. I've had enough of your theatrics."

"That's not it." Rikiga walked over to the windowsill. The dogs silently
made way for him.

"Inukashi..."

"What?" Inukashi snapped. "We gotta get going, or else―"

"Do you think it'll really be destroyed?" It was a dazed murmur. "Is No.
6 really going to disappear entirely?"

"Who knows." That was the only answer he had. Rikiga continued to mumble
as he stared out the window. Inukashi's reply had probably not reached
him.

"But... if that really happens... what'll appear in its place?"

"Huh?"

"A world without No. 6... once that \emph{thing} disappears, what'll happen?
What's going to appear out of it?"

Inukashi felt like someone had bumped him roughly on the shoulder. He
sucked a breath in. He felt like he was breathing in tiny shards of
glass. His chest pricked painfully.

A world without No. 6. The aftermath.

He had never thought of it.

He couldn't even imagine it.

\emph{What would appear?}

He tightened his grip around the handle of the bag.

"I don't have a clue. I just know one thing is for sure."

Rikiga turned around and blinked at him.

"Money is money. No. 6 could disappear tomorrow, or it could~

last for a thousand more years. It doesn't matter. It doesn't matter
what appears. That gold is a hell of a lot of treasure, and that's never
gonna change."

"I see." Rikiga shook his head, grinning. "You're a tough one. Hah. You
might be an even tougher cookie than Eve. I should watch out for the dog
instead of the fox, shouldn't I?"

The ambiguity was now wiped clean from his tone, and Rikiga's face
turned back into the one of the alcoholic that Inukashi knew so well.
This was the countenance of a greedy but cowardly man, indulging in both
booze and women alike, living no dreams―just harsh reality. Inukashi
somehow felt relieved.

"Let's get going, old man."

"Yeah," Rikiga answered promptly this time, and started walking.
Inukashi snapped his fingers, and a few dogs sprang up and bounded ahead
of Rikiga out of the room.

"Are you taking them, too?"

"Yeah. They'll be much more useful than what's inside this bag."

Shionn began to fret. The female dog swung its head around and licked
the tiny body gently with a warm, soft touch. Inukashi remembered it,
too. The baby would probably soon fall fast asleep.

\emph{See ya, Shionn. You wait here. Be a good boy and watch the house with
	the dogs while I'm gone.}

\emph{I'll come home.}

\emph{I'll come home for you someday.}

\emph{Wait for me.}

"Mama, mama, mama," Shionn called, right before he was about to step out
of the room. Inukashi closed his eyes, and slowly pulled the door shut.

\chapter{The arms of reason}

\myepigraph{. . . but he who, provoked and nettled to the quick by an offence,
	should fortify himself with the arms of reason against the furious
	appetite of revenge, and after a great conflict, master his own passion,
	would certainly do a great deal more.}{Montaigne, \emph{Essays} Book 2 Chapter XI}

\lettrine{T}{he shutters} closed.

Shion sprang up, and took in his surroundings. Teal walls and a teal
hallway stretched out before him. The floor was made of a smooth, glossy
material polished to a spotless sheen, and reminded him of the
cleanliness of a hospital.

However, unlike a hospital, there were no windows or doors.

He felt like he had been shut into a durable box. No, it wasn't \emph{like} a
box―this \emph{was} a box, a sealed box. There were three barriers between
where he stood now and the prisoners' wing up ahead. Once all of them
came down, the box would further seal itself into multiple compartments.

These were spaces designed to capture escaped prisoners, if not execute
them on the spot.

The barriers, far from being just walls, were also designed to release
high-voltage current. This beautiful colour, close to indigo dye, was
the colour of the execution grounds.

The alarm went off.

The barriers began to roll down.

"Nezumi, run. We have to make it through."

Nezumi kicked off the ground. They ducked past the first barrier. The
second one was halfway down; the third one was already two-thirds of the
way down.

"Why?"

Shion and Nezumi had reached the end of the hallway by the time the
third barrier had closed completely.

"Why, Shion?" Nezumi asked. "Why are the barriers so slow? Getting
through them is easy, at the speed they're going."

"It might be... easy... for you..." Shion gasped. His heart was
straining in protest from running through the hallway in a single dash.
He couldn't breathe. It was far from easy for him―he was almost at his
limit. If the barriers had fallen a second earlier, Shion would have
been caught between the barrier and the floor, his back snapped in half.

"But this speed doesn't make sense. Why is it?"

"That accident... it's thanks to... the commotion about the smell..."

"What do you mean?"

"I copied and sent... the emergency signal that the third-floor computer
recorded... to the fourth-floor monitoring system. Along with a
deactivation signal, too. Right afterwards, the sensors would register
us... and then notify the system of an emergency again. Activation,
deactivation, and reactivation..."

"I see. And that took up a bit of time. But I don't know how you could
have done it in such a short while. The third and fourth floors operate
on different systems, don't they?"

"...Yeah, well, I managed." Shion had not expected it to go this well.
He had figured it was all or nothing and given it a try, but he himself
was surprised that such a simple deception tactic would work against a
leading, cutting-edge defence system.

\emph{It's almost like God's hand had a part in it.}

\emph{God's hand?}

\emph{Did someone send us help?}

\emph{That's absurd, that would never happen. But...}

Shion.

\emph{I heard a voice call my name. Only for a moment. This voice...}

\emph{Safu?}

\emph{No way, I'm hearing things.}

Nezumi narrowed his eyes. The sharp glint in them condensed.

"And the door we're making for?"

"The wall up ahead, on the far right."

Nezumi ran a hand against the wall.

"Oh, here." It was almost indiscernible from the teal wall, but there
was certainly a slight crack there. "There aren't any handles or
sensors. How do you open it?"

Yes, there were no handles or sensors. And ever since the
computer-operated maintenance system had been completed, this door had
gone out of use and lost all meaning.

"There might be an old-fashioned lock on it," Shion suggested.

"My, my. How careless of them."

No one would be able to get this far without a legitimate ID chip. Even
if they had, no one would take notice of this door. This was No. 6's
judgment, and also its folly.

"―which means we might be able to open it pretty easily. Ah... it's just
like you said. There's a keyhole here. Looks like it'll break easily."

"Can you do it, Nezumi?"

"Probably. I can't let you steal all the spotlight. But before that, I
think we have to deal with those over there."

"Huh?" Shion tried to turn around, and was shoved in the shoulder
instead. He staggered.

\emph{Ping.}

A ray of light whizzed past Shion's eyes. It hit the wall, and left a
small burn.

"Well, well. Look what you've done to the wall, and it's polished up so
nicely, too. That would cost you a written apology, wouldn't it?" Nezumi
hunched his shoulders in mock exasperation.

Three gunmen stood before them. They were clad in military
gear―dirt-coloured combat uniforms and boots. Two barrels were pointed
at Nezumi, and one at Shion.

"Don't move. Put your hands up." The man in the lead stepped forward,
and took aim with his gun.

"Huh?" Nezumi said in mock surprise. "Oh, hey, will you wait a minute?
You gonna shoot me right here? Aren't you getting a little ahead of
yourself? I think I'd like to talk to my attorney first."

The man wordlessly wrapped his finger around the trigger.

"You sure about that? We're valuable samples."

The man stopped mid-movement. He had responded to the word "sample".

"Sample... you say?"

"Yeah. You guys are collecting samples, aren't you? For the Almighty
Mayor's project?"

The men all shifted uneasily, and exchanged furtive glances. For a split
second, there was a moment of vulnerability.

Tsukiyo sprang forth from inside Nezumi's shirt, dashed along the length
of the gun, leapt up, and bit down on the man's nose.

"Whoa!" The man leaned back. Nezumi's knife slashed through his wrist.
Blood splattered everywhere, patterning the wall. Snatching the gun from
the falling man, Nezumi took aim a second ahead of the men behind him,
and pulled the trigger.

He shot one man through the shoulder, and the other through his hand;
both men cried out in pain. Nezumi spun around on one foot as if doing a
dance, and this time shot the laser gun at the wall. He swung a kick
into it next. Tsukiyo scurried up his shoulder.

"It's open."

A space revealed itself, wide enough for an adult to get through if he
crouched. It was pitch-black inside.

"Ugh... it hurts..."

"S-Somebody!"

"Help me... help..." The men were groaning. Shion could hear the sound
of rapid footsteps. More soldiers, each with a gun in hand, were rushing
onto the scene.

There was a curved handle on the inside of the door. Shion pulled it as
hard as he could. The door closed with a screech and a bang. They were
shut into complete darkness.

Just as he had predicted, there was a set of stairs in a steep slope,
almost like a ladder. Shion shed his lab coat and tied one end to the
door handle and the other end to the handrails of the stairs. It wasn't
much of a solution, but it would buy them some time.

Nezumi slung the gun over his shoulder and clambered lightly up the
steps. Shion followed after him. The stairs continued up on their steep
slope, straight into the darkness.

His breathing grew laboured. The sweat stung in his eyes. His feet
threatened to trip him up. Shion pressed on desperately. A moment of
lateness could cost him his life. It would endanger not only his own
life, but Nezumi's as well. He wanted to avoid putting Nezumi into
danger at all costs. He knew he was already a great burden to Nezumi,
but he at least wanted to avoid putting him in harm's way.

Nezumi muttered something.

"What? I didn't hear."

"Nothing. ...Just noticing how you didn't make a fuss."

"Make a fuss?"

"About those soldiers. There was lots of blood flying back there.
Usually you'd rattle off some grand spiel about how we shouldn't harm
others."

"Oh..." \emph{So that's what he meant.}

The screams resounded in his ears. They didn't belong to the soldiers.
They were voices of the people whose lives had been wrenched from them
unfairly in the basement of the Correctional Facility.

\myspace

\emph{It hurts. I can't breathe. Help me.\\
	O God, O God. Why do you make me suffer?\\
	Please, just save my boy. He's only three.\\
	Kill me. Please, release me from my pain...\\
	Help, help, help, help, somebody.}

\myspace

What was a spray of blood on the teal floor compared to this brutality,
this ruthlessness? The soldiers would receive care and medical attention
from their comrades who were rushing onto the scene. But those people...

Those who had been sacrificed in the Hunt, those murdered people did not
even have a way to alleviate the suffering of their dying moments. Their
groans, their gasps, their cries, and their shrieks. It resounded in his
ears.

"We have no choice," he spoke to Nezumi's back in the darkness. "It
can't be helped. We have to defeat the enemy. If you hadn't taken them
down, I would have been killed."

Nezumi stopped. Shion could see a pair of grey eyes. His heart grew
restless. \emph{Even in this darkness, your eyes glow with elegance.}

"It can't be helped... you really feel that way?"

"I do."

"...I see." Nezumi resumed walking. He walked swiftly. Shion could
barely keep up.

"Shion."

"Hm?"

"Back there, we were still able to go easy on them. From now on, we
won't have the chance to be as nice. You were right: we have to defeat
the enemy, or else we'll be killed ourselves."

"Yeah."

"If that happens..." Shion couldn't hear the rest. He snapped his eyes
open in the darkness.

"Nezumi, I can't hear you. Say it a little louder."

"No... never mind." Nezumi breathed out softly in the dark.

\emph{I'm sighing.}

He closed his mouth.

\emph{Never sigh in earnest.}

They were the words of the old woman who had saved him from the flames
that devoured the forest, the village, and their homes. She had raised
him until the age of five.

\emph{Bite your lips to shreds before you let yourself sigh. Throw your head
	back at the pain. Never look down. Look forward. And most of all―}

\emph{Never trust anyone. Never open your heart. Remember that. You must
	engrave these words into your memory in order to survive.}

He had been taught over and over. It wasn't that he had forgotten. Each
word, each letter was deeply carved into his heart―like a mantra, like a
curse.

\emph{Sighing creates an opening, a vulnerability. If you want to stay alive,
	keep your mouth shut. Never let anyone see your weak spot. Let your
	heart warm to no one. Never trust anyone but yourself.}

\emph{You, at least... you at least must survive... you, at least...}

He gripped the handrail.

\emph{Forgive me, gran. I've gone against what you've told me. I've sighed
	many times for another. I believed him, and opened my heart to him. I
	placed the shackles around my own feet. But I couldn't have done
	otherwise. I couldn't cut him away.}

"Nezumi," Shion was calling. He was out of breath. He had probably used
up a considerable amount of energy. "What're you thinking about?"

"You wanna know what I'm thinking about now? Getting to the top of these
stairs safely. Maybe a little wondering about what's waiting to welcome
us at the top, I guess."

\emph{It was you, Shion.}

\emph{I was thinking about you.}

\emph{You said we had no choice. They're enemies, so we had no choice but to
	make them bleed. If we didn't kill them, we'd be killed ourselves.
	That's why we had to take them down.}

\emph{That's what fighting is. We kill, or get killed: those are the only
	choices. And in a melee, there is no such thing as justice or morality.
	I know that. It's been instilled into the marrow of my bones. But,
	Shion, you―are you just going to accept that? Are you able to? Are you
	letting yourself?}

'You put everything into dichotomies. You either love or you hate.
You're either friends or enemies. Outside the wall, or inside the wall.
And you always say you can only ever choose one of them.'

'Don't you think that there could be a third way?'

\emph{I had scoffed at what you'd said. I scorned it as a naive fantasy. But
	you know what? I felt intimidated, too. I felt threatened by your
	naivety, but also your strength to be able to speak of fantasies as if
	they were plausible. When I heard those words, just for an instant―a
	short instant, mind you―I could really see a way. A white path rose up
	behind my eyelids.}

\emph{The third way.}

\emph{The way to seek cohabitation rather than retribution, perhaps?}

\emph{A way that chooses acceptance over revenge?}

\emph{Could such a thing exist, apart from in illusions? Could it exist in the
	hearts of people?}

\emph{I've been thinking about it all this time. I didn't want to think about
	it, but your words always sat adamantly in the middle of my thoughts,
	reminding me constantly. 'Turn your thoughts to this third way,' they
	would tell me, 'don't refuse, don't look away; keep thinking about this
	path.'}

\emph{I haven't found the answer yet. That's why I'm still thinking. I'm still
	fixated on your words, and pondering them.}

\emph{But Shion, now this is what you're saying?}

'We have no choice.'

\emph{If in the future, I end up killing someone―no, if you yourself were to
	harm someone―how about then? Would you still say so?}

'We had no choice.'

\mybreak

They were at the top of the stairs. It was such a cramped space that
they had barely any room to stand.

"Shion, there's no exit."

There was no handle or button to be found. Only a blank wall.

\emph{We've messed up.}

His heart pounded. Cold sweat streamed down his back. If this was a dead
end, then there was no escape for them. They could not fend off the
pursuers coming from below.

"Up," Shion yelled. "Push the ceiling up!"~

Nezumi's body sprang into motion on Shion's orders.

\emph{Bang.} The middle portion of the ceiling opened up like a trap door.
Nezumi kicked off the ground, and launched himself up.~

Just then, he heard a clamour below.

The door had been forced open.

"They're up there! Aim for them!" The unique dry popping sound of
firearms.

"Shion!" He extended his hand, and he could feel Shion latching onto it
tightly. He pulled the other boy up.

"Agh!" Shion let out a small cry.

"Did they get you?"

"―'m alright. Just a graze."

Once they shut the trap door, all noise was cut off, and only an eerie
silence remained. Shion let out a long breath.

"Does it hurt?"

"No―no big deal."

"First time, huh?"

"Hm?"

"It's your first time getting fired at. And a sniper rifle, at that―a
pretty old firearm. Sleek looks, deadly accuracy. That's the kind of
formidable lady you're dealing with."

"I see. Well, attractive as she is, I wouldn't like to go on any future
dates with her." Shion laughed quietly as he bound his calf.

Perhaps he was straining himself. But it meant that he could still push
himself further, and that the wound wasn't so bad that he couldn't move.
Not that it mattered how bad his injury was, anyway: they had to keep
moving. They could not stay in one place.

That was why he would not question Shion further. He would not concern
himself with the boy. They only had to keep moving forward together.

"Shion, where's this?"

"A part of the old air vents. I suppose they used these when this place
was just built. But soon afterwards, they built new external reinforced
walls. They added circulatory filtration devices, and these vents went
out of use."

"Which means they stopped needing them right when the Correctional
Facility was turning into a stronghold. So the old vents must be―here."
Nezumi's extended hand pointed to a rectangular tunnel.

"What's down this way?" he asked.

"Probably a dead end. They've probably blocked it up partway."

"I thought so. I figured it wouldn't be as easy as worming our way right
to the internal core through the vents."

"Yeah. But we'll have to go as far as we can."

He was right. There was no way back. They had no choice but to go as far
as they could go.

"Shion, I'll boost you up. Go on ahead."

"'kay."

Shion dove into the hole more nimbly than Nezumi expected. He felt the
slimy texture of blood as he supported Shion's leg. He clenched his hand
into a fist.

"Hey, this thing opens." The upper body of a soldier peeked into view
along with his voice. As soon as the soldier hoisted himself up, Nezumi
kicked his chin so it snapped back, and swung his rifle butt down on the
man's temple. He dragged the unconscious body up into the vent, aimed
his gun through the opening, and began to fire. He heard bodies tumbling
down the stairs. He closed the trapdoor, and rolled the soldier's body
over it.

"He's got a nice beer gut. That should serve as a good weight."~

Nezumi rifled through the man's pockets and almost whistled.

"Nezumi, what're you doing? Hurry up," Shion called.

"Don't rush me. We gotta get the most we can from them," he answered.

He entered the hole head-first. It was cramped. He had to lie flat on
his belly in order to even move. Tsukiyo hopped out from the folds of
his clothes and scurried down the tunnel.

"It's like a mouse hole in here," Shion reflected idly.

\emph{Still got his wits}, he thought fleetingly. The boy was calmer than he
expected. It wasn't an ignorant kind of calm; Shion understood his
situation well enough. He felt the danger and tension of it, and yet
also had room to be calm on top of it all.

\emph{But why?}

"We couldn't have gotten through here if we were any fatter," Shion said
thoughtfully.

"Well, I guess."

"Inukashi could get through just fine. Rikiga-san might have a bit of
trouble."

"Rikiga? You mean the alcoholic geezer? He wouldn't have been able to
get this far in the first place. He would've tripped and fallen over
when we had to dash down the hall."

"So by now..."

"He would've been charred black. I feel ill just imagining what Roasted
Old Man would look like."

\emph{Cheep-cheep-cheep.}

Tsukiyo answered in place of Shion. Shion stopped moving.

"Dead end?"

"Yeah."

\emph{Dead end. I see. So this is it.}

"It's a dead end. But..." Shion's palm slid along the wall. There was a
soft \emph{clunk} as a part of it fell away. Light seeped through.

"The grate. They must've blocked it from our side."

"What do you see?"

Shion tilted his body sideways to make an opening. Nezumi looked out
through the plastic bars.

It was a tidy and spacious room that looked like a laboratory. Straight
across from them was a large glass window, where several male and female
researchers were huddled together, peering through it and conversing
animatedly. A man said something with a grandiose gesture, and a
long-haired woman gave a toothy grin. They both had steaming mugs in
hand. Apart from them were several other staff busy looking into their
computer screens. There was also a stooped-looking man bustling about on
foot.

"It looks like a comfortable room," Nezumi commented. "Maybe they'd let
me use their shower if I asked. Let's pay them a visit."

"What? We can't get out through such a tiny opening."

"If it's too small, we just have to make it wider."

"Huh?"

"Keep back, Shion. Just retreat as you are."

"Nezumi, what're you gonna do?"

"Just watch."

"Is that... a miniature bomb?" Shion swallowed.

"Yup. A coin-shaped micro-bomb, more like. It even comes with a timer,
and I can control how large the explosion's gonna be. It was a good
buy."

"Where did you buy it? I didn't even realize."

"Are you being dense on purpose?" Nezumi said irritably. "Did we have
\emph{time} to do shopping since we got here? I nicked it from Beer Gut
earlier. But anyway, who cares about that. Shion, get back. A little
more. And take Tsukiyo."

"About here?"

"Perfect. Hold your head with both hands. Once it explodes, we're gonna
jump right out. Be prepared."

Bomb set.

Nezumi shrugged his superfibre cape off, and covered his head with it.
He kept retreating until his foot touched Shion's shoulder.

"Nezumi."

"What?"

"Now it's like you're shielding me. I might end up safe, but you―"

"Idiot. Who the fuck cares about our positions at this point? Stop
wasting your breath."

\emph{How stupid can he get?}

What an idiot. But it was just like Shion. No matter the situation, he
never forgot about others. It was just like him, indeed.

Relief welled up from the bottom of his chest.

\emph{Voom.}

An explosion. And then, wind. A blast of air rushed through the cramped
tunnel. Tsukiyo let out a shrill squeal of terror.

"Shion! You safe?"

"Of course. Tsukiyo and I are both okay."

"Good."

There was no dust, perhaps because the wall was made of a special
material. The bomb was considerably powerful, and despite the fact that
he had set it to make the smallest explosion possible, it had blown
apart a large part of the wall.

They jumped down. Screams rang out all around. Staff began to flee the
room.

"Who are you?" A heavyset man drew a gun from his lab coat. Nezumi
rushed at him and aimed a swift swipe at the base of his neck. The man
fell forward onto his belly.

The security bells were ringing.

\emph{Keep running like this?}

They couldn't stay here for long. In a few dozen seconds, soldiers would
be streaming into the room. They had no choice but to run.~

But to where?

"Shion, what next? Give me orders. Hurry."

There was no answer.

\emph{Shion, what's wrong? Don't tell me...}

A cold sweat trickled down his spine.

He turned around to see Shion at the glass window, looking~

down through it as the staff members had been doing earlier. A dim light
filtered through the highly-polished glass pane.

"What the hell are you doing? Move!"

Shion slowly turned his face towards Nezumi. He was completely ashen.
His features were rigid, almost wooden. Nezumi had never seen Shion with
such a face before.

\emph{What's wrong?}

As soon as the thought passed, he realized that the hem of Shion's pants
was soaked red. The gunshot wound had been deep. \emph{He's fainting from
	blood loss.} That was his first thought.

"Shion, you alright?"

A pair of lips trembled lightly in the deathly pale face.

"Nezumi... this..." Shion trailed off, and swallowed with some
difficulty. "What is this...?"

"Huh?"

There was no time to stop. He knew well enough, but the stricken
expression on Shion's face drew him to stand by his side. His foot
trampled something. It was a wooden photo frame. In the photo was a
woman with a baby in her arms and a boy of about ten. It had probably
been knocked off a staff member's desk. It was an outdated digital
display. Both the woman and the boy were smiling somewhat sheepishly
from the photo.

He lifted his gaze, and looked through the glass in front of him.

The space beyond was a storey lower, as if it were embedded in the
ground. The ceiling was higher, accordingly. It was a room with white
walls.

"Gh―"

He had recoiled without even thinking.

\emph{What―is this?}

\chapter{Are you sad?}

\myepigraph{"Are you sad?"\\
	"Yes, I am."\\
	"You're not really, are you?"\\
	"No, I'm not."}{Hoshi Shin'ichi, "Bokko-chan", \emph{Short Short 1001}}

\lettrine{T}{wo conveyer belts} were running. Humans lay on them. Someone had put
them there.

They were not alive. He could tell clearly even from where he stood
behind the glass.

Bodies. Several dozen, maybe even a hundred, were being carried down. A
half-moon shaped device of enormous size was operating beyond.

The bodies were sucked in one after another into two square openings. It
seemed like the glass was of a special kind, for he could hear nothing
of what was occurring on the other side.

Bodies slipped by continuously in this silent scene.

There were men. Women. Children and adults. Clothed and naked. Their
statures, ages, and sexes ranged broadly.

"Why are their heads... all..." The words stuck in his throat. They
became a lump that blocked his airway.

The top half of the head had been cut away from every corpse. A
translucent plastic dome had been placed on top instead. Men and women,
children and adults―all had been fitted with bowl-shaped plastic from
the forehead up.

"―Samples," Shion said, heaving a breath with his shoulders. "They're
samples."

"What do you mean?"

"Brains... they needed human brains as samples."

"―So these bodies have all had their brains removed?"

"Yeah― I think so. And I think they've all finished serving their
purpose. So―"

"So?"

"They're being disposed of."

This time, Nezumi was the one to swallow hard.

The half-moon-shaped device at the other end of the belt: was that for
disposing the corpses? Did it burn them instantly to ashes? Did it grind
them up and then dry them into dust? Or did it use some special chemical
to melt them right down to their bones?

The bodies were being sucked in.

People who had been alive just moments before―living, speaking, crying,
loving one another―were being disposed of like trash.

\emph{How... how could... No. 6, how could you be so cruel? How could you have
	turned out to be so ruthless?}

"They're not humans." Shion's voice reached his ears. It was no whisper.
It was crisp and clear. "This isn't any human deed." His fist pounded
the reinforced glass.

\emph{This isn't any human deed.}

But the staff clad in white had been standing here conversing only
moments earlier. They had been sipping a warm drink from their mugs.
They had been engrossed in their work.

\emph{Are they all monsters?}

Nezumi's eye caught the photograph at his feet.

The smiling woman, the smiling boy. The sleeping baby.

'Look, look over here. Smile, come on!'

'Daddy, I'll take a picture next.'

'Honey, make sure you get the baby, too.'

He could almost hear the family's conversation―so typical, yet so
precious all the same.

\emph{Is the guy who had this propped up on his desk a monster, too?}

He felt a presence. The enemy approaching.

Nezumi felt like someone had struck him on the cheek. He was wide awake.
He yanked Shion by the arm, and burst out into the hallway.

\emph{We gotta run, Shion. We can't let ourselves die here.}

His whole body reared its arms in order to survive. His thoughts, his
senses, his fingertips, even each hair of his head acted solely for his
survival.

\emph{We cannot die.}

"Right!" Shion's calm orders sliced the air. "Thirty metres to the
right."

Thirty to the right. There was no time to think about what was there.
Strangely, the barriers were not coming down. But he also had no time to
think about why.

\emph{Run. Wait, never mind.}

Soldiers appeared before them.

"Squat down! Curl up!" Nezumi tossed the coin-shaped bomb across the
floor, and fired at it. There was an ear-splitting explosion. Shattered
glass sprayed everywhere.

"We're going in!"

There was no way out if they let themselves be surrounded. In the face
of a firing squad, they had no chance at all. They had no choice but to
charge into the thick.

"Don't leave my side."

A broken sprinkler was spraying water left and right. Nezumi leapt into
the knot of drenched soldiers.

He swung the blade of his hand against a soldier's throat, and stabbed
his knife into another as he spun around. As the soldier clutched his
shoulder and fell forward, Nezumi extracted a military knife from the
man's waist belt and slashed the wrist of another enemy that was coming
his way. A handgun fell and clattered loudly across the floor as blood
and water mixed and flowed together.

None of the soldiers uttered a word. They remained silent and carried
highly harmful military firearms in addition to the laser guns, which
were still in the stages of development. They were silent, swift, and
precise in their kill. They had probably been trained that way.

\emph{But when it comes to handling knives, I'm the better one.}

In hand-to-hand combat, lower-tech firearms would be much more effective
than high-tech weapons. Also, in certain situations, a knife would
probably be much more useful than the most up-to-date gun. Especially if
he could wield the knife as if it were one of his own limbs.

After seeing three of their comrades defeated in the blink of an eye,
the rest of the soldiers lost the fluidity of their movements. This was
a retaliation they had not expected. Stiffness was a weak point, and
Nezumi aimed squarely at it. He twisted the arm of the soldier in front
of him, and pressed his knife to the man's throat from behind.

"Don't move." He licked his lips, and commanded the rest of the
soldiers.

"Throw away your guns, or consider this guy dead."

The soldiers bolted back a step at once.

\emph{Will it go well? Could I make my escape, using this guy as a shield?}

"Shion."

"Yeah."

"You alive?"

"Yeah. You moved so fast, I don't think any of the guys had a chance to
turn on me."

"Perfect. Now use this guy as a shield, and―"

There was a burst of applause.

"Magnificent show. But that's quite enough."

The soldiers immediately parted, as if those words had been a signal. A
man threaded his way in from between them. He stood before the two boys,
and raised his right hand airily.

"Enough fun and games. VC103221 and Shion, was it?"

Shion let out a cry.

"You know him?" Nezumi asked. "Don't tell me he's your uncle or
something."

"He's an Investigating Officer from the Security Bureau―called Rashi."

"So you remembered me," the man said. "An honour. Luck seems to bring us
together quite frequently, doesn't it? You've grown tougher since I saw
you last. I would never have expected you to come infiltrating the
Correctional Facility. I'm shocked, to tell you the truth. However, I am
happy to see you again."

"Why thank you," Shion said guardedly. "I wasn't expecting to see you
here, either. I'm surprised, too."

"Yes, yes, about that. To tell you the truth, my real profession is a
military training instructor. Excuse me for not properly introducing
myself last time."

"Get his business card, Shion. It'll come in handy when you're
job-hunting."

Rashi twisted one side of his mouth into a smile.

"A way with words, as usual, boy. But your way with the knife is even
better than your tongue. Admirable. I would never have expected you to
take control of my subordinates so easily. Ah, simply brilliant. Worthy
of praise. I would even consider recruiting you."

"A tantalizing proposal, but I have to refuse," Nezumi said. "What's
this military training you're talking about, huh? Does target practice
include shooting prisoners?"

Rashi chuckled. "We have that, too. Or we have training sessions where
we exterminate foolish rats that have wandered in."

Nezumi twisted the soldier's arm with even greater force. "Throw away
your guns and clear the way," he said.

Rashi shook his head. "You two are brilliant. Not anyone can get as far
as this. Brilliant, indeed. But unfortunately, you are also young."

Rashi slowly raised his right hand. "Your plan is not well-thought out
to the end."

A gun barrel was pointed their way.

\emph{Huh?}

"Stop!" The soldier twisted desperately. Nezumi let his arm go. A bullet
pierced the soldier as he staggered forward. His wounded body crashed to
the ground. Water poured on him from the ceiling. The soldier raised his
face, and his gaze wandered as if he were searching for something. Then,
he called.

"Mother."

The voice reached Nezumi's ears.

\emph{To kill a subordinate so easily...}

Then a savage pain tore through his shoulder and leg.

"Nezumi!"

Shion's arms caught him from behind. The water caught both their feet,
and they toppled to the floor. Pain raced through his whole body.

"...ts..." Nezumi gritted his teeth. Sweat poured off his body, and his
heart thudded rapidly.

"Come, come. Superfibre may be amazing, but it's useless if you don't
wrap it properly. You can't hold a knife anymore, can you? Nor can you
hop or dart around. Now you're finally quiet. I've had a splendid time,
but the games are over, 103221."

\emph{Over? Does it all end here?}

Rashi furrowed his brow, and sighed.

"I wasn't expecting to be met with so much trouble. A shame, really. A
shame that I must to kill you, but―it cannot be helped. I won't draw it
out longer than it has to be. I will respect your efforts in battle and
I will let you go in peace. A bullet per person should do the job."

"Compassionate... aren't you?" Nezumi said.

"Do you have any last words?"

\emph{Is this really the end?}

Suddenly, the sprinklers stopped. The barriers began to come down at
once. A buzz of anxiety ran through the crowd of soldiers. Rashi's gaze
also roved.

It was their chance. They would take advantage of this opening and steal
that gun. A chance to return from the brink of death―but his body would
not move.

"What's going on?"

"The barriers are just beginning to work."

"That's absurd, why―"

"Run! We'll be trapped!"

Once the barriers came down completely, a high-voltage current would run
through the sealed space. No one would survive.

"Run! Get out of here!"

The soldiers broke into a run, with wounded comrades in their arms.

"Sir, the walls are coming down. Hurry!" A soldier stopped, turned
around, and yelled. "Sir!"

The walls were coming down―coming straight down. Nezumi felt like his
shoulder was on fire. He pressed a hand to his open wound, and smiled
wanly.

"He's calling you. Don't you need to go?"

"After I get rid of you two."

The barrel of his gun was pointed straight at Nezumi's heart. Shion's
arm slid around his chest from behind, as if he were trying to protect
him. Nezumi placed his hand on top. Shion's arm was covered in dirt and
blood.

\emph{I see. So I am going to die with you.}

He leaned back onto Shion and let out a long breath. The tension left
his body.

But he would not close his eyes.

He would behold the world before him with a steady gaze until his last
moments.

Shion's arm tightened around him.

\emph{I won't close my eyes. Not until the last moment―}

He heard a gunshot right beside him. It was a muffled sound, as if he
were underwater. Red flowers bloomed on Rashi's shirt. Petals flew all
around.

\emph{What...?}

Rashi staggered back a few steps before leaning heavily with his back
against the wall. He slid to the ground. Crimson petals also fluttered
from his lips.

Nezumi drew a breath, but could not release it.

\emph{Those aren't flower petals. ―It's blood.}

Blood had sprayed the wall. It was like someone had carelessly hurled
red paint at it. Rashi bowed his head. A startling amount of blood
poured out and dyed his lower body.

\emph{What―? What just happened?}

"Sir!"

A scream. Then, the wall closed it off completely. For a moment, it was
like a soundless void. A brief moment of quiet peace. He could breathe
out now, and he could pull himself up.

"...Shion?" He twisted his head to look at the boy who was cradling him.
"Shion―oh―"

He could breathe out, but no words would come. His heart was beating
harder, more frantic and fast.

Shion's hand was wrapped around a gun. A small-calibre semi-automatic
pistol. It was an official military-issue pistol that could shoot even
through a bullet-proof vest. Just earlier, Nezumi himself had swiped it
out of the soldier's hands and battered it to the ground.

The smoke from the gun wavered in the air. The sharp smell of gunpowder
pricked his nostrils. Sweat stung his eyes. His mouth turned dry, and
his tongue stiffened. He could hear the sound of it tearing as he forced
it to move.

"Shion... what have you..."

Shion withdrew his arm from Nezumi, and stood up. He slowly made his way
towards Rashi.

"Ngh..." Rashi groaned. He lifted his face, and his body trembled
slightly.

"...You amateur..." A barely audible murmur trickled from his lips,
along with a stream of blood. "At least... aim... for a fatal spot..."

"I have something to ask you," Shion said, with gun still in hand. It
was a low voice, stripped of all emotion. "Why didn't you activate the
barriers immediately?"

"...They wouldn't move..."

"So they weren't functioning."

"...Yes..."

"Why not?"

"...I don't know..."

"You and your people would have paused the barrier system temporarily
before coming here, just in case. But this time, they started moving on
their own... am I right so far?"

Rashi quaked as he looked up at Shion imploringly.

"...Please. Put me to rest."

Tears spilled from his eyes.

"Answer me," Shion said.

"...Yes... out of control... cause unknown..."

"Out of control. Cause unknown..." Shion repeated thoughtfully.

"I know... nothing... Shion, I beg you... hurry... put me to rest...
save me..."

"Save you?" Shion's shoulders twitched. "I heard those same words just
earlier. In the basement of this building."

It was then that Nezumi was finally able to stand. Blood streamed from
his shoulder and leg, but he felt no pain.

He had to stand up. He had to grab Shion's arm. He had to stop him.

\emph{Shion, what the hell are you trying to do?}

His legs gave way. He tripped and landed on his knees. A soldier's
corpse was lying right beside him. It was a young man. He had black,
frizzy hair and was wearing a golden necklace. It was glittering.
'Mother'―it was almost like his last word was still plastered to his
lips.

"You people threw this man into the basement. He was a victim of the
Hunt. He couldn't die, so he came begging to me. 'Help me,' he said.
When this man was writhing in agony, what were you doing? Drinking
coffee? Taking a bath? Giving a lecture?"

"...Please... put me... it hurts..."

"I couldn't save him."

"...Help me..."

"I couldn't save anyone."

Shion's right arm rose slowly.

\emph{"Shion, stop!"}

A gunshot rang out.

Nezumi closed his eyes, and turned away. The smell of gunpowder grew
stronger. Mixed with the stench of blood, the air grew thick and
viscous. It was a stench he was used to―almost too used to―and yet, he
still felt like throwing up. He couldn't bear it.

He didn't want to open his eyes.

If he did, he would have to face reality. He wanted to keep his eyes
closed, and escape to a place that was not here.

\emph{I don't want to see it.}

\mybreak

\emph{Whoosh.}

He felt a breeze.

He smelled flowers. The faintly sweet smell of wildflowers.

\emph{Whoosh.}

The breeze touched his cheek, and caressed his bangs.

\emph{Oh, it's that again. It's... that.}

He opened his eyes.

The light stung.

A field stretched out before him.

A field of tender grass. The wind was still somewhat sharp and cold, but
the rays of the sun were strong. Small white flowers bloomed everywhere,
swaying in the breeze, and glowing in the sunlight. There were misty
mountain peaks in the distance. Were those lakes on the mountain-skirts,
white pools reflecting the light of the sun? Lakes and marshes both
large and small dotted the land. The sky was an indigo blue. It was such
a deep azure, it looked like it could colour everything else with its
pale shade. But the flowers still bloomed white on the ground, and the
grasses were a gentle green.

In the sky he saw blue, on the land green, and he saw the forest.

There was a forest beyond the meadow. He could hear the rustling of the
trees. White-backed leaves were fluttering. Birds soared up, and swooped
down again. A fluff ball drifted past Nezumi's line of vision.

He wanted to chase it.

\emph{Can I chase it?}

Nezumi had lifted his face to look up. Looking up at... whom?

"Come here."

There was a gentle voice, and he felt his body being tenderly lifted up.

\emph{Oh, it's that again.}

\emph{It steals my consciousness, and bears my soul away.}

He felt like a little child. He was being carried gently. Like a small,
small child.

Last time, it was summer.

He had smelled the hot air rising from the grass.

Was it springtime now? The scenery was more subdued. The wind, the
light, the smells, the colours were all soft and gentle, encircling
Nezumi in an embrace.

"I will teach you a song."

He shook his head. "I can do it... I can sing."

"You can sing? That song?"

"Yeah." Nezumi straightened his posture, and drew himself up.

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here\\
	Keep everything here, and\\
	Live in this place\\
	O soul, my heart, O love, my feelings true\\
	Return home here\\
	And stay}

The wind stopped. \emph{It's listening to the song}, Nezumi thought. The wind
subsided, and the balls of fluff began to fall slowly to the ground.

"I see. So you can sing."

His hair was caressed. He was gently rubbed on the back.

"Sing some more. Let me hear a little more of your song."

\poem{The wind steals the soul away, humans thieve the heart\\
	But here I will stay\\
	to keep singing\\
	Please\\
	Deliver my song\\
	Please\\
	Accept my song}

His eyelids drooped. All the strength left his body.

"...I'm sleepy."

"Then go to sleep."

\emph{Could I close my eyes like this, and drift off into a slumber?}

"Go to sleep. I will take you there."

"...Where are you going?"

"To the forest."

"To the forest?"

"Go to sleep. Think of nothing, and let yourself rest."

\emph{Is it really alright for me to go to sleep like this?}

His body rocked back and forth. He was comfortable. So comfortable...

"I'm going back!" he heard himself yell.

He had to go back. He could not let himself drift off asleep. He had to
return to reality, where Shion was. It didn't matter what awaited him
there; he couldn't let himself flee on his own.

\emph{Shion.}

\emph{I need to return to you.}

\myspace

He felt a cough coming up. The smoke and the stench of blood filtered
deep into his body. A fit of coughs overtook him. He wiped his mouth,
and stood up.

He could see Shion with his back to him. The boy stood with both arms
dangling at his sides. The pistol was still in his right hand.

"I can't save anyone," Shion said in a muffled voice. He was repeating
it.

\emph{I can't save anyone.}

"―Shion," Nezumi tried calling the boy's name.

\emph{Shion, do you hear my voice?}

"Nezumi."

Shion's eyes focused on Nezumi. Joy ignited within them. A smile spread
widely across his face. A sigh of relief spilled from his lips. The
pistol slid from his hand.

"Thank goodness you're safe. But―you're bleeding a lot. Are you alright?
We have to bind that wound, at least."

Shion took off his sweater and started ripping the sleeve.

"This is all I have, but it might serve as a bandage. Give me your
shoulder, and I'll bind it."

It was the usual Shion. His usual tone, his usual gaze. He was naive and
foolish, ignorant, idealistic, unbelievably honest, and warm.

Nezumi's heart ached. He felt burning at the back of his eyes.

"Shion."

"What? Does it hurt?"

"You protected me."

"Huh?"

"Don't forget that. You... protected me."

"Me?"

Shion closed his mouth, and blinked at him repeatedly. His gaze slid to
and focused on the pistol lying on the floor. Then, it moved to the man
slumped lifeless against the wall. He had been shot between the eyes.

\emph{Quite something}, Nezumi thought fleetingly.

The bullet had pierced the man squarely in the middle of his forehead.
Despite the fact that it was at point-blank range, shooting a target
without a sight was not an easy feat for an amateur.

Shion's breathing quickened. He brought his palms up to his face. He
stared at them intently as if there were some cryptic letters carved
into them. His palms, his arms, his whole body trembled.

"Nezumi―what have I done?"

"You protected me. You saved me with your life―"

"No!" Shion's scream resounded in the confined space. "You're wrong!
You're wrong! You're wrong!"

"I'm not wrong!" Nezumi shot back. "I would've been killed if it weren't
for you. He wouldn't have been sitting there bleeding. It would've been
me."

He pointed at Rashi.

"I would've looked like that."

He grabbed Shion's arms. He shook the boy with all his might. Shion's
head jerked back and forth. He was like a marionette dangling on broken
strings.

"Listen. Listen to what I say. You protected me, do you understand? You
saved me. Shion."

\emph{Listen, Shion. Grasp my words. Believe them.}

"If I were you, I would have done the same. I would definitely have done
it. This is a battlefield. If we don't kill, we get killed. What you did
was justified."

Nezumi chewed his lip. The words crumbled and rotted as soon as they
slipped out of his mouth. This isn't what I really want to say.

Then, what did he want to say? What do I really want to tell Shion right
now?

"Nezumi..." Shion murmured hoarsely. "I... killed him."

He got up, and picked the handgun off the floor.

"I don't know how. But without any hesitation at all, I was able to
just... kill another human being."

Their eyes met.

\emph{What do I have to tell him?}

"Is that forgivable? Is that something... that's allowed to be
forgiven?"

The mere 5.4-mm diameter of the barrel seemed so large to his eyes.

"You said once that No. 6 and I were very similar. I said you were
wrong. But... maybe you were right. I am like that city. It doesn't
matter why I did it. I coldly, ruthlessly, wrenched a man's life from
him. Nezumi―"

Total length: 155 mm. Weight: 460 g. Shots equipped: 8. Rifling: 4
grooves, clockwise.

\emph{How many shots are left?}

"Can I be forgiven...?"

Shion closed his eyes.

\emph{Shion? What are you doing?}

\emph{"Stop―!"}

Nezumi had raised a cry. Not with his voice, but with his whole body. He
lunged at the boy, and punched him as hard as he could. As Shion
crumpled to the ground, Nezumi straddled him.

"Stop fucking around!"

He grabbed the boy by his collar, and struck him across the cheek.

"You must ― be fucking ― kidding me !"

He could feel his palm hitting flesh again and again.

"You bastard, who do you think you are? We've come this far, and now you
think you can run away? Put yourself out of your misery? Fucking
bullshit!"

Shion whimpered softly.

"You traitor," Nezumi snarled. "Are you saying that you can't be
forgiven for killing someone else, but you can be forgiven for killing
yourself? You know that if you go on and commit suicide, you'll be
murdering two people. \emph{Why don't you get it?}" His last words came out
like a pained plea.

Tsukiyo leapt up onto his shoulder and screeched loudly and insistently.
He looked like he was trying to get between them.

Shion didn't resist at all. He looked like he wasn't even breathing. His
eyes were open, but they were sightless. The edge of his mouth was cut
and bleeding, and dried blood was caked on his lips.

\emph{He's totalled ― wounded all over.}

Would it have been better if they had not come? Nezumi knew more than
enough that once they infiltrated the Correctional Facility, it would be
a battlefield. He knew, and he had still dragged Shion in. The rescue of
the girl, Safu, was only an excuse for Nezumi. He wanted Shion's power.
He wanted the boy's power to perfectly memorize the innards of the
Facility, and to give precise orders. He wanted to borrow―no, take
advantage of― Shion's power to destroy the Correctional Facility, and
put a crack in No. 6's core. Shion was a good weapon to serve this
purpose, and this was a happenstance more lucky than anything Nezumi
could ask for.

\emph{Yeah, I used Shion.}

But if the results of it had been this ― \emph{this} ― then, it was better if
they had not come. \emph{We should never have set foot in here.}

He had, of course, been prepared for a brutal struggle. He had
recognized that they were waging a reckless war with less than a
one-percent chance of winning, and yet he had had the resolve that they
would emerge as victors; he had both the eager heart and the restraint
of reason, and he had been so certain that he had it all.

\emph{And that it was we ― not No. 6 ― who controlled the state of things.}

There was no battle without preparation. There was no victory without
solid certainty.

There should have been nothing wrong with what he thought. He was
certain he had not gone astray.

Nezumi gritted his teeth. He felt like he would almost succumb and kneel
to the reality that stood before him. \emph{I never imagined that it would
	turn out like this.}

\emph{We shouldn't have come. We were not supposed to come here. I shouldn't
	have dragged Shion into my battle.}

It had finally dawned on him. But it was too late.

"Shion." \emph{I'm the one who should be asking whether I'll be forgiven. I
	should be the one begging for forgiveness, not you.}

"Shoulder it," he whispered. The words tore through his gritted teeth
and spilled from his lips. Shion's eyes moved slowly. They narrowed
slightly, as if attempting to focus on Nezumi.

"Shoulder it― shoulder it, and live on." They were words for himself,
not Shion.

\emph{Bear your sin, and live.}

\emph{Shion, I'm sorry. I made you bear the burden, one so big it's making
	your spine creak. Would I be forgiven one day? Would you forgive me for
	what I did to you?}

Shion let out a long breath.

An arm reached out, and a set of fingertips touched Nezumi's cheek.

"It's my first time... seeing you cry."

"Huh?"

\emph{Cry? Who?}

"It's alright, Nezumi... don't cry. I get it. I'll do as you say. So
just don't cry, please."

"Idiot," Nezumi said hoarsely. \emph{Really, how idiotic can you get? Still
	caring for others in a situation like this. What's 'alright'? Nothing's
	alright. Besides, I'm not crying. I'm not like you, I don't just let my
	tears fall wherever and whenever I want, without hesitation―}

He had reached his limit. He couldn't hold it in any longer. A wave of
tears overcame him, and they streamed from his eyes. The droplets were
startlingly hot. They rolled down his cheeks, dripped from the point of
his chin, and landed on top of Shion.

\emph{Damnit, why are these tears―damnit.}

He let his body sink on top of Shion's as his sobs spilled out.

\emph{Damnit. Bastard. Bastard.}

"Shion."

"Mm..."

"I don't know how to stop my tears."

"Mm-hmm," Shion murmured.

"I really... don't know. If this keeps going it's gonna be... bad."

"Yeah?" Shion said softly.

"It \emph{would} be. Think about it: if Inukashi saw me like this... he'd make
a fool out of me for the rest of my life."

"―That's for sure." A hand slid around his back, and patted him.

"Nezumi, let's go."

Yes. They would have to go. This wasn't the finish line yet. They had to
move forward. But, how? Was there a way to escape this sealed space?

"Oh!" Nezumi scrambled up. A startled Tsukiyo dove into Shion's shirt.
"Why is that?"

"Why is what?"

"Why isn't anything happening? Weren't they supposed to run an electric
current as soon as the barriers were down?"

"That's right." Shion also got up. He winced in pain, likely from some
wound. But his face soon smoothed into a faint smile.

"It's been almost five minutes since the walls came down completely.
That's kind of a late observation for you, isn't it?"

"The hell is that supposed to mean?" Nezumi replied indignantly. Then,
he closed his mouth. He glanced at Shion's face, which was smeared with
blood.

"Are you saying you knew, then? You knew beforehand that nothing would
happen?"

Shion shook his head.

"I didn't know. There was no way I would have known. It's just that―"

"Just that, what? We've come this far. Don't play hard-to-get."

"Right. Well, you might laugh, but I feel like we're being... invited in
by someone."

"Invited in?"

Shion licked his lips, and continued in his Shion-like, awkward manner.

"Actually, the barriers should have activated the moment we burst into
the hallway. But they didn't move. They only started moving when we were
surrounded by the soldiers. Even though at that time, they would have
been temporarily paused. That doesn't make sense. That's why they were
so flustered."

"Wait a minute, I dunno what you're getting at. So are you saying that
the computer monitoring the security system was buggy? That it
conveniently stopped working for us? ―Well, I dunno whether I'd call
being trapped in here convenient. But we were saved. We were rescued by
a coincidental computer malfunction― is that the deal?"

A No. 6 computer malfunctioning? No, there was no way something like
that would happen.~

Shion shook his head again.

"It's not a coincidence. It was by will."

"Will? You're saying the computer had a will of its own?"

A third refusal.

"No. It could be operated a certain way based on one's will, but the
machine itself wouldn't have one."

"Shion, explain it to me so that I can understand. What're you talking
about? What do you mean by being 'invited in'?"

"I don't know," Shion said slowly. "I can't put it into words very well.
But that's the only way I can explain it. Someone is calling us―"

"And that someone operated the computer and rescued us of their own
will. That's what you figure?"

"Yeah."

"And who's that someone? That girlfriend of yours?"

"Safu―could it be her? But..." Shion dragged his feet to the wall. There
was a part that was a different colour than the rest. It was a shade
lighter.

"That's the elevator, right?"

"Yeah. The only path that leads to the top floor."

Thirty metres to the right. Shion had meant to tell him to run in this
direction. There were no buttons to be found on the wall that would
operate it. There wasn't even a single projecting part. It probably
activated by a sensor responding to a special ID chip.

"How do we get into this thing?"

Shion had turned his face back to stare at something. Nezumi followed
his gaze, and landed on Rashi's body.

"He might have a special chip embedded in his body," Nezumi said
hastily. He put into words what he figured had been on Shion's mind. He
didn't want to let Shion utter any words related to that body. Shion
glanced away, and held his palm up to the sky.

"No― that won't do. This system will activate only if it senses life.
The chip is useless unless it's inside a living, breathing human body. A
corpse won't do."

\emph{I see.} Nezumi muttered silently, and cast his eyes down.

The madness that had driven Shion to nearly shatter his own skull had
already been wiped clean.

\emph{It has to sense life.}

\emph{A corpse won't do.}

How could he say those words so casually after such an intense emotional
disturbance?

Nezumi shifted his eyes to his feet. Maybe I haven't just made him
shoulder it. \emph{Maybe I've also hauled it out―hauled out what was dormant
	in him until now.}

\emph{Shion, what's lurking inside you? What do you really look like, Shion,
	the you that I don't know?}

A chill ran down his spine. The wounds on his shoulder and thigh
throbbed as if in answer. Until now, he had completely forgotten about
his gunshot wounds.

"Is there any other way?" he asked, short and to the point.

"I think someone will come fetch us," came the equally short answer.

"Fetch us?"

He heard a faint mechanical noise. The elevator was coming down. The
door slid open almost soundlessly.

Two shadowy figures stood before them.

Nezumi tensed for a moment, then realized quickly that it was a
reflection of themselves. The entire wall in front of them was a huge
mirror.

"Nezumi―you're getting on, right?"

"You kidding me? Of course. I'm not stupid or rude enough to turn down
such a welcoming."

"Yeah. I figured."

He took one wide step into the elevator. \emph{Throb.} His wounds stirred
again. He would probably not be able to push himself much further,
considering the amount of blood he had lost. And, as Rashi had pointed
out, he could no longer use a knife with this hand.

\emph{No use mulling it over, though.}

He could not predict what lay ahead of them after the elevator stopped.
He couldn't foresee the future, so there was only one choice―to face the
here and now.

He let his gaze wander. There was nothing of note apart from the mirror.
The walls were smooth with not a speck of dirt to be seen. There were no
buttons, switches, or touch screens. It was a sterile, bright, inorganic
space.

The door was closing.

Right in front of them, he could see Rashi with his legs thrown out and
his head tilted to the side. He could see the soles of the soldier's
boots, the soldier who had called his mother in his last moments.

Shion's fingers moved to chest-level.

\emph{Are they going to clasp together in prayer? Nezumi thought.}

But Shion's fingers only clenched into a hard fist.

That was it.

The door closed.

\chapter{A treacherous joy}

\myepigraph{A deep, inexpressible joy filled her heart, a treacherous joy that
	she sought to hide at any cost, one of those things of which one is
	ashamed, although cherishing it in one's soul . . .}{Maupassant, "A Life"}

\lettrine[ante=``]{I}{s Daddy} home yet?'' Lili sighed. "Did Mommy get to see Daddy? Did she
get to say 'welcome back' to him? It's getting so dark. I wonder what
happened? Yuna's daddy and Ei's daddy are already home. They always come
home on the same bus. You know, sometimes me and Yuna and Ei go and meet
them there."

"I see. And Daddy's very happy, isn't he?"

"Yeah. Really. He picks me up, and kisses me on the cheek. But it's kind
of embarrassing. I don't need to get a kiss from Daddy to be happy. I'm
not a little girl, you know. But Daddy still thinks I'm a little girl.
That's why he kisses me in front of all those people. It's kind of a
problem."

Karan smiled at Lili's endearing attempt at sounding like an adult. Lili
sighed again. She cupped her chin in her hands, and let out a long huff.
It was an adult woman's gesture―was she imitating her mother, perhaps?
Usually, Karan would burst out laughing and tease Lili, calling her a
right young little lady, but today she couldn't quite bring herself to.
Her heart felt heavy, as if Lili had transmitted her melancholy to her.
Smiling was the best she could do.

"Ma'am."

"Yes, dear?"

"Daddy'll come home, right?"

"Of course."

Karan stopped in the middle of wiping a tray, and glanced at Lili.
Lili's favourite cheese muffin lay half-eaten on her little plate.

"Getsuyaku-san―your father―is probably very busy at work. I bet he
missed his usual bus. I'm sure he'll come home on the next one."

Karan gave a little sigh as well after finishing her sentence. These
words wouldn't even serve to make Lili feel better. Lili didn't want to
hear these banal words of encouragement.

She felt frustrated and ashamed that she could not even relieve a little
girl's woes.

Lili's eyes, always so lively and full of joy, were now clouded over.

Her father, who usually came home every day at the same time on the
minute, had not come home. She was worried sick.

Karan couldn't bring herself to laugh it off as an exaggerated concern.
Lili had sensed something wrong with Getsuyaku, and it was paining her
heart. Renka―Lili's mother and Getsuyaku's wife―had even gone to the bus
stop to pick him up despite her difficulty moving around. There must
have been something about Getsuyaku that caused his wife and daughter to
feel uncertain and unsettled. It was not only Getsuyaku, either.

This uncertainty―an intangible uncertainty―had by now covered all of
this city of No. 6.

One could call it a looming threat.

Several dozen citizens had already suffered at the hands of death―been
sacrificed. Karan wasn't sure if "sacrifice" was the appropriate term,
but she thought the eeriness and terror that the word invoked matched
perfectly well with the city's atmosphere; of that, she was most
certain. Karan herself was troubled, apart from her thoughts about
Shion, with an uncertainty that dug into her heart.

\emph{Is this really happening?}

\emph{People are dying left and right.}

Without warning, they would collapse and cease to breathe. Karan had yet
to see it for herself, but she had heard that the victims all lost their
hair and teeth, were covered in wrinkles, and died looking a hundred
years older. She had heard that even the most vibrant young man or
beautiful girl ended up in this grisly form. Without exception.

\emph{Why? What's the cause?}

\emph{A new virus? Poison gas? A plague?}

Speculation was rampant, and yet, not one person could give a definite
cause. No one could spot a common trait among all of the victims. Their
ages, body types, environments, workplaces and development histories
ranged widely, and barely overlapped.

Apart from the fact that they were exclusively No. 6 citizens.

One collapsed in the square in front of City Hall; one in the street;
one in his own kitchen. In all cases, the victims were alone. There were
no concentrated outbreaks of casualties in one spot. They all occurred
in pinpoint locations. Many were safe who had seen the victims die right
beside them. Any acquaintance in mid-conversation, any friend walking
beside you, any stranger walking past you, could become a casualty.
Shrieks and wailing voices burst into the air everywhere.

No one could predict who the next casualty was, or when and where it
would occur. That was fear itself. An insurmountable fear.

\emph{My sister collapsed just now. She wasn't even thirty. Now she's
	transformed into an elderly woman.}

\emph{My neighbour just died. We were just having a normal conversation.
	'What's gonna happen now?' 'This is scary, isn't it?', just stuff like
	that. Then she suddenly started to double up in pain―}

\emph{What's going on here?}

\emph{This is a concern for everyone now.}

\emph{Maybe tomorrow I'll be next... no, maybe even in a minute...}

\emph{I might be the next sacrifice.}

\emph{What the hell is the mayor doing? Why doesn't he try to deal with this?}

\emph{Isn't he going to help us citizens?}

Fear became discontent toward the politicians who twiddled their thumbs
in the face of the situation. Discontent became criticism, which turned
into a simmering rage.

The mayor, through various media organizations, called for calm amongst
the citizens, and advised them to take careful action. But even as the
mayor's image flashed across the display, another casualty fell right in
front of it, another among the dozens today. He would convulse again and
again, then age rapidly. It was impossible to remain calm.

\emph{Give us medicine.}

\emph{Tend to the wounded.}

\emph{Give us the truth.}

The cries of the citizens echoed loudly in every corner of the streets.
And on top of this situation, Lili's father had not arrived home. Her
mother had gone out, and not returned.

The girl's tiny chest was probably full to bursting with uncertainty.
Perhaps she was desperately trying to keep herself from crying.~

Karan understood well the suffering and pain of being concerned but
unable to do anything about a family member. She had experienced the
frustration of only being able to wait. It was a pain that had soaked
deep into her bones.

"Lili." She stroked the girl's soft hair. "Have the rest of your
muffin."

"Ma'am..."

"You love your father, right, Lili?"

Lili looked up at Karan, and gave a huge nod.

"Yup. I looove him. I love Daddy lots and lots. I love Mommy, and the
baby in Mommy's stomach, too."

"Yes, and your father loves you too, very very much, right? He kisses
you on the cheek, and he says 'I love you, Lili' while he does, right?"

"Yeah. Daddy always says 'I love you' to me."

"Then everything will be fine. Your father will come straight home to
you, Lili. You know, in the end, people come home to the people they
love most."

Lili blinked. "Is that true, ma'am?"

"Yes. It's true. True as can be."

Lili's mouth relaxed. A smile spread across her face. She picked her
muffin up, and took a bite.

"It's delicious."

"There are still more left. Three, to be exact. One for your mother,
your father, and for you, Lili. You can take them home, if you like."

"Thank you, ma'am."

After finishing her muffin, Lili put her hands together and gave a loud
thanks for her meal.

"Ma'am."

"Yes, dear?"

"I love you, too."

"My, Lili, that's wonderful. Thank you."

"And Shion too... but not as much as Daddy, or Mommy, or you, ma'am."

"Hm?"

"Shion will come home too, right?"

"Lili..."

"People come home to people they love the best, right? So Shion has to
come home to your place, ma'am. Right? He'll come home, right?"

Lili seated herself deep in her chair, and dangled her feet over the
edge.

"When I got hurt once, Shion made it all better."

"Oh? He did?"

"Yeah. I was playing tag with Ei, and I fell down. I fell, and then Ei
came and fell down on top of me, like ― crash! ― and it really hurt.
Ei''s kind of fat. But she's really fast at running, you know. And she's
good at drawing pictures. I like drawing pictures, too. We draw pictures
together a lot."

"You're good friends, then?"

"Yeah. Really good friends. But we fight sometimes, too. Sometimes we
have fights that are so big, I think we're never gonna play again for
the rest of our lives."

"But if you can fight and make up again, that means you're truly good
friends. So you fell down, right, Lili? And Shion made it better?"

"Yeah. My leg was bleeding really bad. And it hurt a lot. I cried lots,
and Ei was crying, too. But then Shion passed by, and he picked me up
and took me to a tap and washed off the blood, and... oh, and then he
put some medicine on it. He said, 'it's stopped bleeding, so you can
stop crying now.' And then he patted my head. He wiped Ei's face for
her, too."

"And... when was this?"

Lili stopped swinging her feet, tilted her head a little, and looked at
Karan.

"Lemme see, ummm... a little before Shion went away. When he was still
going to work at the park. You know, ma'am, Shion is really nice. Mommy
said so, too. She said he's really kind, and handsome, and such a great
person. She said, 'When Shion comes home, you should ask if you could be
his bride'."

"Oh, Lili, you as Shion's bride? That's some happy news."

"But it's just that, well, Ei..."

"What about Ei?"

"Umm, she says she's in 'love at first sight' for Shion. I asked her,
'What's love at first sight mean?' and Ei said, 'It means you get
married, of course'. But if Ei and Shion get married, then I can't be
his bride. Mommy said I can't lose to Ei, but it's really hard."

"Oh, my." Karan laughed out loud. For even just a moment, she was able
to forget the uncertainty and melancholy forming a malignant lump in her
heart.

As far as Karan could remember, Lili had not mentioned Shion's name at
all since the day he had vanished from Karan's sight. Lili had probably
sensed that reflecting on memories of Shion would cause suffering for
Karan. Or perhaps she had been warned by Renka.

'Lili, from now on, I don't want you to talk about Shion in front of
Karan.'

'Why not?'

'Because she'll be sad.'

'Mommy, did Shion do something really bad? Is that why he got caught and
taken away? Everyone says so.'

'What do you think?'

'Me? I think... Shion wouldn't do anything bad. He's so nice. He would
never do anything like that. Ever.'

'And you're right. See, you do know. I'm impressed with you, Lili.
Whatever happened must have been some kind of mistake. Shion is such a
wonderful boy. You wouldn't find anyone nicer. He's kind, handsome, and
just such a great person. I know, Lili, when Shion comes back, why don't
you ask if you can be his bride? Don't lose against Ei.'

Perhaps mother and daughter had had that kind of conversation, and
grinned at each other.

Karan had been surrounded by caring people all along.

Through days of frantic frustration and anguish, she had always thought
she was fighting alone. But it was not so. People around her, people
right by her side, had been quietly expressing their concern all along.

\emph{All this time I was being supported by such a little girl. And―}

\memo[0.45\textwidth]{8}

And by Nezumi's letter.

There were many pillars. The hearts of others held her aloft.

"Lili, thank you." Karan gently embraced the young girl.

The emergency buzzer went off.

A part of the wall turned into a screen, and the face of a young woman
appeared. She was a newscaster directly affiliated with the Information
Bureau.

"This is an urgent broadcast. As of this moment, the authorities have
announced a state of emergency. Citizens are advised to return home
immediately. All subsequent outings of any kind by citizens will hereby
be prohibited. There are no exceptions. If you do not comply, you will
be arrested and taken into custody. I repeat. We are entering a state of
emergency. Citizens are advised to..."

The newscaster had been reading rapidly through her papers, her eyes
cast down, when suddenly she snapped them open wide. She stood up, and
clawed at her throat.

"Help me! No!!" Her shriek rang out.

Karan reflexively put her arms around Lili.

"Ma'am, what's happening to her?"

"No! Don't look!"

The caster's flaxen hair turned white before their eyes. Dark spots
appeared on her cheeks, and spread rapidly.

"Help... me..." Her fingers curled as if trying to grasp something in
the air, and she collapsed behind the desk.

The broadcast cut off abruptly after that.

A state of emergency―it was nothing so tame.

This was an abnormality. A situation far beyond the bounds of common
understanding. It was twisting and rearing before them.

She felt faint.

\emph{No, it's not me. No. 6―this city―is the one that's creaking from the
	stress. It's shrieking, just like that newscaster.}

Confusion. Disaster. Danger. Suffering. And, fear. Plagues that should
have never existed within No. 6 were sprouting furiously.

She heard laughter.

Somewhere far, somewhere far in the distance, she could hear laughter.

\emph{Who? Who's laughing? Whose voice is it?}

Brittle, dead leaves fluttered past her window.

One, two, three...

A wind was blowing. A strong southern wind was blowing against her. It
usually unravelled the rigid cold of winter, and brought with it the
premonition of spring. The southern wind which usually made her heart
feel so lively was carrying that voice to her ears.

"Ma'am, I'm scared." Lili clung to her. "Someone's laughing in the sky."

"Lili, you can... hear it too?"

"I don't know. I don't know, but I'm scared."

Lili began to cry. "I'm scared!" she sobbed.

"It's alright," Karan soothed. "It's alright, Lili. I'll protect you. So
don't be afraid."

\emph{You supported me all this time. You cared for me, you were concerned for
	me. So this time, it's my turn to support you. I won't let people snatch
	you away, so easily like they did Shion and Safu. I'll protect you, you
	just watch.}

Karan bit her lip, embraced Lili still more tightly, and turned to face
the wind that blew outside her window.

\emph{I will protect you to the end.}

\mybreak

\emph{How could this be happening?}

The man was confused. The cause was beyond his grasp. This was the first
time something like this had occurred.

"Why have you let this happen?" he yelled, Fennec, the mayor of No. 6.
"Why have \emph{they} begun to act on their own? I thought you said you were
able to control them perfectly."

\emph{What noise}, the other man thought. \emph{What a noisy lout.} He had always
thought of the other man as a cowardly, yapping dog who knew how to do
nothing else. The years evidently had not changed his character.

"Soon, it will awaken. Then, everything will settle down."

"Really? You \emph{are} telling the truth?"

"Really, Fennec. These are only small precursors to the main event.
Miniscule disturbances."

"Miniscule disturbances―this, you say? The city is in a panic, for
goodness' sake."

"Then, announce a state of emergency."

"I've announced it ," the mayor said shortly. "But if we have any more
deaths, the Security Bureau alone won't be enough to suppress the chaos
among the citizens."

"Mobilize the army."

The mayor froze.

"The army?"

"Yes. Even if there is a possibility of a riot, there would be no
problem with the army there. No cause for concern at all."

"You're telling me to point weapons at my own citizens? These citizens
of No. 6?"

"That's what an army is there for. To neutralize anything that rebels
against No. 6, whether it be from the inside or the outside."

"But―"

"Fennec," the man interrupted. "You are the one to make the decision.
You are the King, after all. It's not something I can intrude into. But
do not forget. You are the sole person who dominates everything on this
land. Rebelling against you is the same as betraying No. 6."

The mayor remained silent for a while, and then gave a resolute nod.

"You're right, in fact. Every word."

"It may have been out of place for me to say this―"

"No, I don't mind. I forgive you."

\emph{Forgive? Forgive me?} The man sneered inwardly.

"I will order the army to mobilize into battle formation and await
further instructions."

"That would be best. It is a grand opportunity to show your foolish
people the extent of your power."

The mayor swept out of the room, his gait stormy. He seemed to be in a
temper.

The man sneered inwardly again, and closed his eyes.

\emph{Soon, it will awaken. And when it does―}

\myspace

Getsuyaku shut off the water flow.

Today, he was going to finish up work early so he could go home.

At the end of every shift, he took a shower and drank a cold glass of
water. It seemed almost too mundane to call it his high point of the
day, but he nevertheless couldn't deny that taking a shower put him into
a good mood.

\emph{Well, that's all the work that needs to be done today. I can go home
	now.}

A smile tugged at his lips every time the thought crossed his mind. He
could see the smiles of his wife and daughter right before his eyes. His
daughter was not of his blood; his wife had brought her from a previous
relationship. There were times when he felt troubled at whether they
could still become father and daughter, even though they weren't
related. Now, he found it funny that he had even bothered to worry.
Blood relations didn't matter. It had nothing to do with how one felt
love. He cared for his daughter so strongly, he could most certainly say
so.

Small and lovable Lili.

Every time he kissed her on the cheek, she would smile sheepishly. In a
year, she might even be rejecting him with a cool "Daddy, don't." But
her gradual blossoming into adulthood made her endearing all the more.
\emph{If I could, I wish she would let me kiss her forever―but that's probably
	not going to happen. But what about today? I wonder if she's come to
	pick me up at the bus stop. If she has, I would be so happy. Lili would
	come dashing up as soon as I get off the bus. She'd say, 'Welcome home,
	Daddy,' and she'd give me a hug. I would pick her up, and give her a
	kiss on the cheek.}

It was his moment of complete bliss.

And he could experience this because Lili, his daughter, was there for
him. His second daughter, too, was almost on her way. He had been told
at the hospital sometime before that the baby was going to be a girl. \emph{My
	second daughter, and Lili's little sister. One more member in the
	family.}

Getsuyaku changed out of his clothes, and smoothed his hair with a hasty
hand.

He had only to think about his wife and daughter. He would not allow his
thoughts to wander and dwell on what he did today, or anything of that
sort.

\emph{Nothing happened today. I didn't do anything. I don't know anything.}

\emph{And that's exactly how it's going to be.}

Tomorrow, Inukashi would give him the rest of his payment. He knew
Inukashi wasn't lying. He was wily, thorough, and miserly, but he kept
his promises. In that sense, Inukashi was someone he could trust. If he
hadn't been such a person, there was no way Getsuyaku would have
co-operated in smuggling, even if it was just garbage or leftover food.

The payment this time around, however, was off the charts compared to
the usual.

Getsuyaku counted on his fingers, curling each one, starting from his
thumb.

\emph{Gold... three gold coins. It's quite a payment. Add that to the previous
	one, and that makes six gold coins. This is enough money to let me live
	like I'm on vacation for a good while. Of course, that's not what I'm
	going to spend it on. I'm going to keep it for Lili, and for the baby
	that's on its way. Renka would be happy for me. But―last time I handed
	her the gold, she looked more worried than happy. She went pale, and
	asked me, 'Where on earth did you get all this money?'. I managed to
	scrape together an excuse, but that was a close call. I made Renka worry
	more than she should. This time, I have to make it good. I have to come
	up with an excuse that'll satisfy her. Maybe something about special
	compensation. I hope I can pull off the lie.}

Six gold coins. A payment off the charts.

After curling all his fingers in, he slowly raised his pinky.

\emph{I want to buy Lili some spring clothes. And Renka, too. Renka is so
	beautiful, but since we don't have the means to be fashionable, she
	always dresses frugally, and it makes her look older. She would look so
	stunning in a brightly-coloured dress, in pink, or blue. And Karan-san.
	She takes care of Lili all the time. And she's so good to her... I have
	to give her something to thank her. Hmm, what should I get?}

His dreary mood began to clear. He felt excited. He could see himself
shopping with Lili, taking her by the hand. He could see Lili turn
around to grin at him. Renka was also smiling.

\emph{Oh, I couldn't be happier.}

He felt it from the bottom of his heart.

He drained his glass of water.

\emph{Alright, let's go home.}

The emergency alarm went off. The lamp flashed.

"What?"

His heart contracted. He could feel the blood receding from his face.

The door connected to the Correctional Facility was beginning to open.
Getsuyaku had passed through the same door only moments before, entered
the Correctional Facility, done his cleaning duties, and returned to
this small room. He had resolved to finish work early that day, and had
taken a shower. He had drank a glass of water.

That was it. That was it.

He shrank bank.

\emph{That's all I've done. I only did my job, did it properly, as usual, and
	tried to go home.}

'Make a good getaway.'

Hadn't a young man who passed him on the stairs said that? Getsuyaku was
almost certain. The youth had a certain severity to him despite his age,
and yet could manage to smile in a very alluring way. \emph{Make a good
	getaway.} Was that a warning? Should he have obeyed those words and made
his escape as swiftly as he could? But he had been afraid of being in a
panic. He had been afraid that he would draw suspicion. \emph{If I run, that's
	like admitting I did something wrong. I didn't want people to be
	suspicious. I still have to come in tomorrow, and the next day. Once
	they're suspicious of me... I―I don't want to lose my job. I was still
	planning on coming into work tomorrow. That's why I ignored him. I
	foolishly pretended that I didn't hear.}

\emph{Make a good getaway.}

\emph{Oh―how wrong I was. I should have listened to that man. I should have
	escaped.}

The door opened.

\emph{I should have escaped.}

Two Security Bureau officials stood there, guns aimed and ready to fire.

"Getsuyaku, is it?"

His legs were shaking. His hands were shaking. His whole body was
shaking.

\emph{No, don't shake. I'll draw even more suspicion. Pretend you don't know.
	Pretend you don't know, and―you haven't done anything.}

"Answer me."

"―Yes, it is."

"We are escorting you. You are to obey."

\mybreak

"E-Escorting me... where?"

There was no answer. The two muscular Bureau officials, alike in height
and shoulder width, remained silent with their guns pointed at
Getsuyaku.

Nothing spoke louder than their lack of words.

Destruction was approaching. Getsuyaku understood that he was in no
position to escape. But he couldn't relent.

\emph{No. No.}

"Wh―why am I... what are you saying I've done...?"~

This time, there was a response.

"You exhibited suspicious behaviour. At the Mannequin."

"S-Suspicious behaviour? That must be some kind of mistake,"~

Getsuyaku stammered. "I... I was just cleaning―it was the robot's fault.
I was summoned because the floor was dirty, and―and so to clean it up,
I―"

"You were responsible for the maintenance of the robot, were you not?"

The muzzle of the gun moved up and down as if to cut off Getsuyaku's
desperate words.

"And you performed it a whole week earlier than was planned."

"That was because―um, they didn't seem to be in very great shape, and...
it happens often, actually, and..."

The officials said nothing more. Their lips were sealed, and no emotion
could be read from their eyes. The two looked like robots themselves.

Only destruction awaited Getsuyaku if he let himself be escorted by
these robots. An inescapable destruction.

\emph{No. No. No.}

\emph{I'm going to go home. I'm going to return to Lili and Renka.}

He threw down the glass in his hand, and dashed outside.

\emph{I have to run. I have to run. I have to get away.}

\emph{If I run straight down this road, and get through the gate, I'll be in
	Lost Town. Once I get on the bus, I'll arrive at the usual bus stop in
	ten minutes. Lili would probably be there to pick me up.}

"Welcome home, Daddy."

"Feels good to be back, Lili."

"Mommy's waiting. Today, we're having your favourite ― stew. We have
bread that Auntie Karan baked, too."

"That sounds terrific. I'm starting to get hungry already. Oh yeah,
Lili, Daddy's going to buy you some brand new clothes soon."

"Really?"

"Really. Let's go shopping on my next break, okay?"

"Yay! Thanks, Daddy."

"Ha ha ha. Alright, let's go home. Mommy's waiting, right?"

A white-hot impact hit him in the chest.

Blood and bits of flesh splattered before his eyes.

\emph{What is it?}

The world teetered off-balance. Darkness closed in on his vision.

\emph{No, no, no. I'm supposed to go home. I'm gonna go home. I'm gonna...}

"Daddy, welcome home."

"It feels great to be back, Lili."

Getsuyaku crumpled as he was shot through the chest.

\myspace

Inukashi averted his eyes, and clenched his hand into a fist.

\emph{What the hell.}

"Hey, that guy just got taken down," growled Rikiga.

They were crouched behind some shrubs that dotted the surrounding area
of the Correctional Facility. The Cleaning Management Room right before
their eyes was the only department that connected the Correctional
Facility directly with the West Block without a set of gates to pass
through. The door that led into the Facility could only be accessed from
the inside, however, so it was not possible to access the Facility from
the side of the Cleaning Management Room. The doors were said to be made
of a special alloy that even a small missile wouldn't be able to damage.
Infiltration was impossible as long as these doors were closed. In that
sense, Getsuyaku's workplace was more similar to the West Block, insofar
as it was completely cut off from No. 6.

For Inukashi, it was no problem if they were cut off. The Facility was
one place he didn't want to step into if he could help it. He had no
interest in it whatsoever, and he would have liked it to stay that way
for the rest of his life.

He was more drawn to the grade and quantity of leftover food and
clothing that Getsuyaku picked out from the waste collection depot
adjacent to the Cleaning Management Room. These were more important to
him than the Facility itself.

He and Getsuyaku had known each other for a while now. It had probably
been at least three years. They were not particularly close or friendly
with each other. They had just used each other as business partners.

Getsuyaku was straight-laced and cowardly, with a decent smattering of
both good morals and greed. A typical man you'd find anywhere. He was
just one of countless many that one could find.

But he did care about his family. Inukashi remembered him saying many
times that he valued them more than anything else in the world. He had
looked truly happy as he smiled and talked about his little daughter,
who was on her way. Inukashi had once asked him, 'Isn't it a pain in the
ass to take care of another human? You can't take care of 'em like
dogs.' Getsuyaku had lapsed into silence, his mouth half-open. He had
looked astonished. Inukashi remembered the look of pity that then
crossed Getsuyaku's face as he closed his mouth.

At that time, he had not understood the reason behind Getsuyaku's
expression. Now, Inukashi felt like he had a better idea. It was thanks
to Shionn―no, it was all his fault.

Inukashi felt like he could understand a little―just a tiny little―of
the kind of love Getsuyaku felt for another tiny soul. And for the
family that awaited its father, its husband, Getsuyaku was definitely
not one of countless many. He was the one and only irreplaceable
existence. Inukashi understood that too.

"I see. So they won't stop at West Block residents. They'll even kill
their own people, too, huh," Rikiga said, wiping the sweat from his
brow. His body was tense despite his airy tone.

"He lived in Lost Town," Inukashi said. "He was probably
practically―trash for those people." Inukashi put up a front of
unruffled calm, but he was also nervous and tense. The nape of his neck
was so taut, it was painful.

\emph{To think they'd actually kill him.}

He hadn't even dreamed that they would kill Getsuyaku. He had, however,
expected the man to blow his cover. There were plenty of possible
instances when Getsuyaku might slip up and give something away. In a
worst-case scenario, he would have been taken into custody and
imprisoned.

But if the Correctional Facility itself would eventually collapse, as
Nezumi said, then it was only a matter of time before Getsuyaku could
get free. They would take advantage of the confusion and rescue him from
his cell.

"God, the amount of trouble I had to go through because I fell for your
smooth talk. That teaches you not to take a dogkeeper's word seriously.
Damnit, I fell right into your trap."

Inukashi wouldn't mind bearing with a complaint or two from the man. In
fact, he wouldn't even mind bowing his head and apologizing. Then, he
would humbly and graciously hand over the promised gold. Three coins,
plus another, "for your trouble," he would say. That was sure to restore
Getsuyaku's spirits.

The demolition of the Correctional Facility meant the end of his
business with Getsuyaku.

\emph{Thanks for all the years of business.}

\emph{No problem. And I think I've had enough risky jobs to last me a
	lifetime.}

They'd shake hands, perhaps, and then part ways. In Inukashi's mind,
that had been his ideal way to say good-bye. But Getsuyaku lay face down
on the arid ground without a single twitch. Only the wind blew over his
body.

\emph{To think he'd get killed.}

\emph{To think he'd get killed so easily, so unceremoniously. Gestuyaku is a
	citizen. He's someone who lived inside the walls. He may have been in
	the dregs of No. 6, but he was still registered as a proper citizen.
	He's different from us. They wouldn't murder him pitilessly. They wouldn't dare.}

He had believed so wrongly all this time.

\emph{I was hopelessly naive. I knew in my head how cold, how brutal No. 6
	could be towards people who betrayed it, refused to obey it, struggled
	against it... I thought I knew, but I didn't know anything. I was naive.
	I should have told him to get his ass out of there as soon as he pressed
	the button. Tell him to get out, and...}

He felt like someone had grabbed his hair and yanked it up. His scalp
hurt from how taut it was. A scream threatened to come up through his
throat.

\emph{I remember now. It said so in Nezumi's letter.}

\emph{Order any collaborators to escape immediately.}

He remembered clearly that single line. Nezumi had predicted this
ruthlessness, this brutality. \emph{But I overlooked it. I was too caught up
	in trying to lure Getsuyaku in to devote any thought to the safety of
	the people I'd be getting help from. It hadn't even crossed my mind
	until now. Until now, when it was too late.}

\emph{I was careless. A careless, fucking naive moron.}

He chewed his lip.

But regretting it now wouldn't undo what he had done.

"Terrible." Rikiga wiped the sweat off his brow again.

Two men who looked like Security Bureau officials were stepping on
Getsuyaku's body with the tips of their boots. They were looking at each
other and nodding. They each took ahold of one of Getsuyaku's legs and
began to drag the body along. The blood flowing from the corpse left red
streaks on the dry ground.

"Are they really human?" Rikiga's voice turned raspy.

The dogs growled lowly beside Inukashi.

\emph{You're sure right about that. These dogs are a hundred times more
	decent. They've got hearts worth a hundred of those men.}

Inukashi gave a quick snap of his fingers. The dogs all sprang to their
feet at once. Rikiga blinked.

"Hey, wait. What're you planning to do?"

"Make them tear those guys' throats apart, obviously. I'm gonna avenge
Getsuyaku."

"Are you stupid?" Rikiga said in disbelief. "Even your dogs couldn't
stand a chance against armed Security Bureau guys. If they find out
where we're hiding, we'll be shot to death, too. Do you think people who
can shoot up their own citizens are going to cut us any slack?"

"But if I don't―"

"If he was alive, you could still flail around and do your thing. But
he's dead. He's gone completely. He's not going to feel anything. He
doesn't feel any anger or suffering now. He's as good as that piece of
dirt. Tell me, should we throw our lives away for a piece of dirt? I
don't know about you, but I'm definitely excusing myself from this one."

Rikiga's bloodshot eyes hardened.

"We can't die yet. We still have an important job to do: save Shion. We
can't do it if we end up as ghosts. That's the most important thing, and
don't you forget that, Inukashi."

"―Fine."

What Rikiga was saying was true. They still had a job to do. And it was
a job that couldn't be done if they weren't alive.

He snapped his fingers again, this time more slowly. The dogs lay back
down on the ground. Rikiga exhaled a long breath.

"Really, I wish you wouldn't act on every emotional whim. This is why
you can't trust young people."

"Old man."

"What?"

"So you \emph{do} say some decent things, once every ten years or so, anyway.
You weren't just a dead weight after all. I see you in a new light now."

"Say what you will."

"And while I'm saying what I will, lemme remind you that we're splitting
the gold even. Don't you forget \emph{that}."

"I know, I know. Even half of the treasure is enough for me to live a
freewheeling life. But if that guy's gotten himself killed, how are we
going to get into the Cleaning Management Room?"

"I have the key." Inukashi held a magnetic card key between his fingers
and thrust it under Rikiga's nose.

"You had a key?"

"Yeah, a spare. In all of the Correctional Facility, the Cleaning
Management Room is the only one that still uses a simple magnetic card
key. There aren't any signsof-life sensors, security systems, object
sensors, or surveillance cameras in there. It's a paradise if you wanna
hide out."

"Well, I guess they wouldn't have a reason to spend money to watch a
place that only collects garbage. So you nicked that key from the poor
guy's pockets, huh?"

"Not his pockets. I took it out of Getsuyaku's small desk, where he eats
his lunch. I borrowed it from his drawer."

\emph{It was an old, worn desk that looked like it'd been picked out of the
	garbage. Getsuyaku used to eat his lunch there by himself. Once, I
	remember him giving me this small, sweet pastry called a muffin. It was
	delicious. I thought my tongue was gonna melt, it was so happy. He said
	he'd bought it from a local bakery.}

"I guess you don't have to return it to him now," Rikiga muttered, with
an unusually heavy tone.

"You're right. I don't have to give it back. So instead, I'm gonna make
as much use of it as I can."

\emph{When I see the Correctional Facility crumble, I'll dedicate the scene to
	you, Getsuyaku. I'll make sure to dedicate something that's worth the
	blood you spilled. I know it probably won't be enough to make up for my
	carelessness, but it'll be the best sending-off to heaven that I'll be
	able to give you.}

Inukashi pressed a hand to his chest. Nezumi's letter was there under
his clothes.

\emph{This time, I won't mess up. I won't overlook anything. I won't let my
	guard down.}

\emph{Their lives are depending on it―Shion and Nezumi's lives. I can't fail
	them again.}

\emph{Cheep-cheep-cheep.}

He hadn't noticed the two mice sitting at his feet. They scurried up his
arm and onto his shoulder. Hamlet and Cravat. \emph{I think those were their
	names.} Two small animals with intellect and their own will.

"You're here," he said to them. "Well, old man, it looks like all the
supporting actors are here."

"Indeed. Now, all we have to do is get the stage perfectly ready, and
then wait for the main actors to make their entrance."

"Yup. The actors of the century. We need a flashy fanfare to welcome
them."

A one-act play, but a massive one nonetheless.

Hope or despair? Success or failure? Heaven or Hell? Life, or death? The
curtains had already risen for this stage without a script.

\emph{It's our turn now. We're waiting for ya, Nezumi.}

\emph{Cheep-cheep, cheep cheep cheep.}

Perched on Inukashi's shoulder, the two mice raised their heads and
squeaked together, as if to call out to someone.

\myspace

"It's stopped."

Nezumi tilted his head slightly in perplexity at Shion's words.

"What're you talking about? It hasn't stopped yet."

The elevator was still ascending. It continued to glide smoothly up.
Shion lightly placed his finger on the edge of his eye.

"No, the tears. Look, they've stopped."

Nezumi's cheeks suddenly emitted a furious glow.

"Idiot. This isn't the time to be making lame observations. If you have
time to be making fun of me, concentrate on the damn door. Once it
opens, we don't know what's gonna hit us."

"I wasn't making fun of you. I just saw that they stopped―"

"Shut up. Just―shut up."

Nezumi turned obstinately aside. His gesture was that of a sullen child.

Shion found it humorous.

Cool, ironic, stronger and more beautiful than anyone else―that was the
kind of person Nezumi had always been, and that never changed. But
behind it all, even he had a childish, emotional side like this. He
still had some immaturity left in him to feel agitated when he was
unable to control his emotions.

Shion had seen Nezumi's tears for the first time. When he saw the boy
choking on the unbearable tumult of his emotions, there was only one
emotion that welled up inside Shion, and it was love. It was neither
friendship nor adoration. Neither romance nor awe. Just love.

He felt an uncontrollable pull of love for the boy's vulnerable tears.
He wanted to protect him with his life.

The howling wind and the sound of rain echoed in his ears.

It was the sound of that storm. The emotions he had felt on that stormy
night when he met Nezumi were revived in himself. And like he had been
so many years ago, he had been stirred to action by these feelings.

\emph{I want to protect him with my life.}

Of course, this was only Shion's self-absorbed and one-sided sentiment.
Nezumi wasn't fragile to the point of needing Shion's protection. He
would learn this the hard way, much later. Shion had been the one being
protected. It had always been this way.

The sounds of the storm showed no signs of dying down. It still roared
vividly.

Shion thought of the boy who had appeared before him that night, his
shoulder drenched with blood much like he was now, except the boy had
been so slender and delicate then. He was so small, and wounded so badly
that he could barely remain standing. But despite that, his eyes had
glowed brilliantly, full of life, and carried no shadow at all. The boy
had neither clung to him, nor begged for his help. On the contrary, he
had coolly scrutinized Shion.

\emph{What kind of person are you?}

Even now, the question still remained sitting before Shion's eyes. He
had not given an answer yet.

\emph{What kind of person am I?}

\emph{My reason, my passion, my folly, my greed, my justice―what shape do they
	take?}

He spread his fingers. There was blood caked on them. Was it his own, or
that man's? His palm and five fingers, dirtied in muddy red.

\emph{Could I stand and look my own self in the eye?}

"I look horrible," Nezumi sighed. He glanced in the mirror, and furrowed
his brow in discontent. "My hair is a mess, my face is dirty―it doesn't
get worse than this. Even the witches from \emph{Macbeth} wouldn't want to come
near me. I can imagine the look of horror on my manager's face if he
were to see me like this."

"You look good enough to me."

"Shion, you don't have to try to make me feel better. Geez, look at me,
my beautiful face is ruined."

"I didn't realize you were so narcissistic."

"I just have an accurate idea of myself. What's beautiful is beautiful.
Unsightly things are unsightly."

"Are you just talking about looks?"

\emph{Or are you talking about how people are deep down, too? Can your gaze
	penetrate even the beauty and ugliness that lies within them?}

\emph{My reason, my passion, my folly...}

Nezumi recited a segment from Macbeth, the witches' line.

"Fair is foul, and foul is fair. Hover through the fog and filthy air."

The elevator stopped. Shion stared at the door.

He was being called―he felt strongly that Safu was calling him.

\emph{Shion.}

The doors glided open noiselessly.

"Don't go running out just yet. Take your precautions." Nezumi's arm
held Shion back as he exited first. He was dragging his foot, though
only slightly. His bleeding had stopped, but it was probably quite a
serious wound. If he moved too much, it would probably begin to bleed
again. Both Nezumi and Shion were nearing their physical limit.

\emph{Shion.}

\emph{Safu. Are you alright? Would I get to see you? I've come to get you so
	we can escape together. Lead us on.}

\emph{Shion...}

A hallway stretched before them, black and glossy. The side where the
elevator was located was just a plain wall. On the opposite side, there
were three evenly-spaced doors. It was deserted. The elevator closed
silently behind Shion.

"Which door is it?" Nezumi turned around to ask. "Right, left, or
middle? Maybe they've got tigers or wolves ready to spring at us if we
open the wrong one."

"No―it's none of these."

Shion walked straight down the hallway. It was neither right, left, nor
middle.

Suddenly, one of the doors opened, and a woman clad in a lab coat
appeared.

"What―" Her electronic tablet slid from her hand. "You―how did you
outsiders get in―?"

They continued past the woman as she stood in stunned silence.

"Wait―where are you―"

"M'lady." Nezumi picked the tablet up, and placed it back in the woman's
hand. "I'm terribly sorry for startling you. We're not suspicious
people―okay, maybe we are―but you don't need to worry. We have no
intentions of harming you. So hush now, please."

Shion stopped where the hall reached a dead end.

\emph{Safu.}

The wall split smoothly in two.

The woman screamed. "How―how did that door open?"

Nezumi whistled. "It's like the caves you see in the \emph{Arabian Nights}.
Shion, what kind of incantation did you use?"

"No―how could it―" The woman squatted to the ground. She was fainting
from shock from the looks of it, for her face was whiter than paper.

There was another door beyond: a crimson door.

"Garish." Nezumi clicked his tongue, and drew up beside Shion.~

"Will it open?"

"Probably." Shion placed a hand on the door. Nezumi trembled. He closed
his eyes, and pursed his lips.

"Nezumi―what's wrong?"

"I heard... a voice."

"You can hear Safu's voice, too?"

"No. This... isn't a human voice. This... whose voice is this?"

"What's it saying?"

"...Finally, you are here." Nezumi made a fist over his chest. He let
out a long breath. "Finally, you are here. I have been waiting for you."

\emph{Finally, you are here. I have been waiting for you.}

\myspace

\emph{I've been called here by Safu. Who's calling you? Who's waiting for you
	beyond this door?}

Shion felt a vibration against his palm. The crimson door opened.

"Gh..." Both Shion and Nezumi made a strangled noise. Their voices stuck
in their throats.

"What―"

There were several transparent pillars filled with clear liquid. These
columns, thick enough for a small child to barely get his arms around,
stood in a neat line.

"Brains." Nezumi swallowed hard.

Brains.

In each column floated a brain. Several clear tubes connected the brain
to the lower part of the column. These tubes glowed bluish-white from
time to time.

It was a bizarre scene. Shion hadn't imagined in the faintest that he
would see something like this. He couldn't have imagined it.

The crimson door closed. Just before it shut completely, he thought he
heard the sound of the wind. Was it an auditory hallucination? It
probably was. But what he was seeing now with his own eyes was no
illusion. It was reality. This scene was concrete. It existed.

His legs quaked. His heart quailed.

Nezumi's hand slid under his arm.

\emph{Oh, here I am again, being supported by you.}

They proceeded slowly through the columns.

\emph{How far do we go? Is there an end?}

"Shion." He heard himself being called. He looked up.

Safu stood there. She was wearing that sweater.

The black sweater which had been hand-knitted by her grandmother. There
were dark pink stripes on the mouths of the sleeves and across the
chest.

"Safu!"

There she was.

He could hear the wind.

Shion stretched his hands straight out before him.