% !TeX spellcheck = en_US

\chapter{Nezumi, dripping wet}

\lettrine{N}{ezumi} was in a tunnel. In the darkness, he drew a quiet breath. The air
smelled faintly of moist dirt. He inched his way forward carefully. The
tunnel was small. It was just big enough for Nezumi to squeeze through,
and it was dark. Light was nowhere to be seen, but it soothed his soul.
He liked dark and small spaces. In these spaces, no large living things
could come to capture him. Momentary relief and tranquility. There was a
dull pain from the wound on his shoulder, but it wasn't enough to
concern him. The problem, rather, was with the amount of blood he had
lost. The wound wasn't deep. It had only grazed a little bit of his
shoulder. By now, the blood should have begun clotting and closed the
open wound. But the wound was still.... He felt a warm and slippery
sensation. It was still bleeding.

――Anticoagulant. They had coated the bullet with it.

Nezumi bit his lip. He wanted something to stop his bleeding. Thrombin,
or aluminum salt. No, not even so much as that. At least, clean water to
wash his wound.

His legs buckled. Dizziness overcame him.

――Not good.

Fainting from lack of blood, maybe. If it was, that would be bad. Soon,
he wouldn't be able to move at all.

――But maybe I wouldn't mind.

He heard a voice inside him.

Maybe it wouldn't be so bad to curl up, unable to move, shrouded in damp
darkness. He would nod off to sleep, a long sleep ― and peaceful death.
It wouldn't hurt, not that much. It might feel a little cold.

No, that would be taking it too lightly. His blood pressure would
plummet, he would have trouble breathing, his limbs would be paralysed
... of course it wouldn't be painless.

――I want to sleep.

He was tired. Cold. Hurting. Unable to move. He only had to suffer for a
little while, he told himself. Stay still, rather than struggle
fruitlessly. There may be people pursuing him, but none who would rescue
him. Then, he should just put an end to living. Curl up here, and just
go to sleep. Just give up.

His feet continued forward. His hands ran along the walls. Nezumi gave a
forced smile. His voice was telling him to give up, but his body still
doggedly carried on. How troublesome it all was.

――An hour left. No, thirty minutes.

Thirty minutes was the time limit for any free movement he had. In that
time, he had to stop his bleeding, and secure a spot to rest. The bare
requirements to keep living.

There was movement in the air. The darkness before him was gradually
becoming lighter. He took each step painstakingly. He emerged from his
dark and narrow side-tunnel to a wider area surrounded by white concrete
walls. Nezumi knew that this was a part of a sewer tunnel that had been
in use until ten and some-odd years ago, the end of the twentieth
century. Contrary to the ground above, No. 6's underground facilities
were not very well-maintained. Much of it had been left in the same
state as they were from the last century. This sewer tunnel was just
another one of those, abandoned and forgotten. Nezumi couldn't have
asked for a better environment. He closed his eyes and visualized the
map of No. 6 that he had extracted from the computer.

There was a good chance that this was the abandoned route K0210. If it
was, then it should extend close to the high-income residence area
called Chronos. Of course, it could very well also lead to a dead end.
But if he had decided to live, then moving forward was his only option.
Nezumi in his current state had neither choice nor time to deliberate.

The air shifted. It wasn't the stale dampness of before, but fresh air
carrying plenty of moisture. He remembered that it was raining hard up
above. This passage was definitely connected to the upper world.

Nezumi inhaled, and smelled the scent of rain.

\mybreak

September 7, 2013 was my twelfth birthday. On this day, a tropical low
pressure-system, or hurricane, that had developed a week ago off the
southwestern area of the North Pacific Ocean, made its way north,
gathering power, until it hit us directly in the city of No. 6.

It was the best present I had ever gotten. I was filled with excitement.
It was only past four in the evening, but already it was getting dark.
The trees in the yard bowed in the winds as leaves and small branches
were torn off. I loved the clamorous noise they made. It was the bare
opposite of this neighbourhood's usual atmosphere, which hardly involved
any loudness.

My mother preferred small trees over flowers, and through her
enthusiastic planting of almond, camellia and maple trees all over the
place, our yard had grown into a small grove. But thanks to that, the
noise today was unlike any other. Each tree made a different groaning
sound. Torn leaves and branches smacked against the window, plastered to
them, and then were whipped away again. Time and time again, gusts of
wind burst against the window.

I itched to open it. Even strong winds like these were not enough to
crack the shatter-resistant glass, and in this atmosphere-controlled
room, humidity and temperature remained stable and unchanged. That was
why I wanted to open the window. Open it, and bring in the air, the
wind, the rain, a change from the usual.

"Shion," called Mother's voice from the intercom. "I hope you're not
thinking of opening the window."

"I'm not."

"Good... did you hear? The lower lands of the West Block are flooding.
Terrible, isn't it?"

She didn't sound like she felt terrible at all.

Outside No. 6, the land was divided into four blocks ― East, West, North
and South. Most of the East and South blocks were farmland or grazing
pastures. They provided for 60\% of all plant-made foods and 50\% of
animal food products. In the north, there was an expanse of deciduous
forest and mountains, under complete conservation by the Central
Administration Committee.

Without the Committee's permission, none could enter the area. Not that
anyone would want to wander into the wilderness, which was completely
unmaintained.

In the centre of the city there was an enormous forest park that took up
more than a sixth of the city's total area. In it, one could experience
the seasonal changes and interact with the hundreds of species of small
animals and insects that inhabited it.

A vast majority of the citizens were content with the wildlife inside
the park. I didn't like it much. I especially disliked the City Hall
building that loomed in the centre of the park. It went five stories
underground and ten stories above, and was shaped like a dome. No. 6 had
no skyscrapers, so maybe "looming" was a little exaggerated.
Nevertheless, it gave off an ominous feeling. Some people called it The
Moondrop from its round, white shape, but I thought it resembled more of
a round blister on the skin. A blister that had erupted in the centre of
the city. As if to surround it, the city hospital and Safety Bureau
building stood close by, and were connected with pathways that looked
like gas pipes. Surrounding that was a green forest. The forest park, a
place of peace and tranquility for the good citizens. All the plants and
animals that inhabited this place were minutely monitored, and all
flowers, fruits and small creatures of each area in every season were
thoroughly recorded.

Citizens could find out the best time and place to watch or gaze at
these through the city's service system. Obedient, perfected nature. But
even it would be raging on a day like this. It was, after all, a
hurricane.

A branch with green leaves still attached smacked into the window. A
gust of wind followed, and its roar resonated for some time. At least, I
thought I could hear it resonate. The soundproof glass cut me off from
any outside noise. I wanted the window out of my way. I wanted to hear,
to feel, the raging wind. Almost without thinking, I threw the window
open. The wind, the rain, came blowing in. The wind rumbled as if coming
from deep within the earth. It was a roar I hadn't heard in a long time.
I too, raised my own hands and let out a yell. It would scatter on the
storming winds, and reach no one's ears. Yet still I shouted, with no
meaning. Raindrops flew into my throat. I knew I was being childish, but
I couldn't stop. It began raining harder. How exciting it would be to
take off all my clothes and burst out into the rain. I tried to imagine
myself naked, running around in the torrential storm. I would definitely
be declared insane. But it was an irresistible temptation. I opened my
mouth wide again, and swallowed the droplets. I wanted to repress this
strange impulse. I was afraid of what lurked inside me. At times, I find
I'm overwhelmed by a tumultuous, savage surge of emotions.

\myspace

\emph{Break it.\\
	Destroy it.\\
	Destroy what?\\
	Everything.\\
	Everything?}

\myspace

There was a mechanical warning sound. It was notifying me that the
atmospheric conditions in the room were deteriorating. Eventually, the
window would close and lock automatically. Dehumidification and
temperature control would commence, and all wet things in the room,
including me, would be dried instantly. I wiped my dripping face on the
curtain and made my way to the door to turn the air control system off.

What if, at that moment, I had obeyed the warning sound? Sometimes, I
still wonder about it. If I had closed the window, and chosen to stay in
the adequately dry comfort of my room, my life would have been entirely
different. It wasn't regret, not anything like that. It was just a
peculiar thought. The one thing that changed my whole world, so
meticulously controlled up until now, happened from that one small
coincidence ― that on September 7, 2013, on a stormy day, I by chance
had opened the window. It was a very peculiar thought.

And though I don't have a particular God I believe in, there are times
when I do feel a certain conviction toward the term 'Divine Hand'.

I turned the switch off. The warning sound stopped. A sudden silence
fell over the room.

\emph{Heh.}

I heard a faint laugh behind me. Instinctively I whirled around, and
gave a small cry. There was a boy standing there, soaking wet. It took
me a while to realize that he was a boy. He had shoulder-length hair
that almost hid his small face. His neck and arms that protruded from
his short-sleeved shirt were thin. I couldn't tell whether he was a boy
or a girl, whether he was very young or older than he looked. My eyes
and conscience were too focused on his left shoulder, which was stained
red, to think about anything else.

It was the colour of blood. I had never seen anyone bleeding as
profusely as he was. Instinctively I was extending my hand out to him.
The intruder's figure vanished at my fingertips. At the same time, I
felt an impact, and I was slammed against the wall with a strong force.
I felt an icy sensation on my neck. They were fingers, five of them,
closing around my throat.

\mybreak

"Don't move," he said.

He was shorter than me. Choked from below, I strained to get a look at
his eyes. They were a dark, yet at the same time, light, grey. I'd never
seen a colour like that before. His fingers clenched. He didn't look
strong at all, yet I was completely unable to move. It wasn't something
a normal person could do.

"I see," I managed to gasp. "You're used to doing this."

\myspace

The pair of grey eyes were unblinking. Their gaze still fixed, they grew
calm like the gentle surface of the ocean, and I could read no colour of
menace, fear or murderous intent from them. They were very quiet eyes. I
could feel my own panic subsiding.

"I'll treat your wound," I said, licking my lips. "You're hurt, aren't
you? I'll treat it."

I could see myself reflected in the intruder's eyes. For a moment, I
felt like I would get sucked into them. I averted my gaze and looked
down, and repeated myself.

"I'll treat the wound. We have to stop the bleeding. Treat. You
understand what I'm saying, right?"

The grip around my neck loosened slightly.

\myspace

"Shion."

My mother's voice carried over from the intercom. "You have the window
open, don't you."

I sucked in a breath. I felt alright. It was alright, I reassured
myself. I could talk with a normal voice.

"The window? ... Oh, yeah, it's open."

"You'll catch a cold if you don't close it."

"I know."

I could hear my mother laughing on the other end.

"You're turning twelve today and you're still acting like a little boy."

"Okay, I get it ... Oh, mom?"

"What?"

"I have a report to write. Can you leave me alone for a bit?"

"A report? Hasn't your Gifted Curriculum just started?"

"Huh? Oh... well, I have a lot of assignments to do."

"I see... don't overwork yourself. Come downstairs at dinnertime."

\myspace

Cold fingers drew away from my throat. My body was free. I stretched my
hand out to restart the air control system. I made sure to leave the
security system off. If I didn't, it would detect the intruder as a
foreign presence, and would set off a piercing alarm. If the person was
recognized as a legitimate resident of No. 6 that wouldn't happen, but I
couldn't imagine that this soaking intruder would have a citizenship.

The window closed, and warm air began to circulate in the room. The
grey-eyed intruder half-collapsed into a kneel, and leaned against the
bed. He let out a long, deep breath. He was weakened considerably. I
took out the emergency kit. First I took his pulse, then tore his shirt
open, and started cleaning the wound.

"This..."

I couldn't help but stare. I wasn't familiar with this type of injury.
It had carved out a shallow ridge in the flesh of his shoulder joint.

"A bullet wound?"

"Yeah." It was a casual answer. "It just missed. What's your term for
this? A graze wound?"

"I'm no specialist. I'm still a student."

"Of the Gifted Curriculum?"

"Starting next month."

"Wow. High IQ, huh?"

There was a tinge of sarcasm in his voice. I lifted my gaze from his
wound, and looked him in the eye.

"Are you making fun of me?"

"Making fun of? When I'm being treated by you? Never. So what's your
specialization?"

I told him I specialized in ecology. I had just been accepted into the
Gifted Curriculum. Ecology. It had the least to do with how to treat a
bullet wound. My first experience. It was a little exciting. Let's see,
what do I have to do first? Disinfect, dress ... oh yes, I had to stop
the bleeding.

"What are you doing?"

He stared as I took a syringe out of the disinfecting kit, and
swallowed.

"Local anaesthesia. Alright, here goes."

"Wait, wait a minute. You're gonna freeze it, and then what?"

"Sew it."

Supposedly I had said this with such a grin that I looked like I
couldn't have been enjoying myself more. It was something I found out
much later on.

"Sew it! Can you get any more primitive than that?"

"This isn't a hospital. I don't have state-of-the-art facilities, and
besides, I think a bullet wound is pretty primitive itself."

The crime rate in the city was infinitely close to zero. The city was
safe, and there was no need for the average citizen to carry a gun. If
they did, it would only be for hunting. Twice a year, rules were lifted
for hunting season. Olden-day firearms slung over their shoulders,
hobbyists would venture into the northern mountains. Mother didn't like
them. She said she didn't understand how people could kill animals for
enjoyment, and she wasn't the only one. In periodic censuses, 70\% of
citizens expressed discomfort at hunting as a form of sport. Killing
poor innocent animals―how violent, how cruel....

But the bleeding figure in front of me was no fox or deer. It was a
human.

"I can't believe it," I muttered to myself.

"Believe what?"

"That there are people who'll shoot at other people... unless... don't
tell me that someone from the hunting club shot you by mistake?"

His lip curled. He was smiling.

"Hunting club, huh. Well, I guess you can call them that. But they
didn't shoot by mistake."

"They knew they were shooting at a human? That's against the law."

"Is it? Instead of a fox, they just happened to be hunting a human. A
manhunt. I don't think it's against the law."

"What do you mean?"

"That there are hunters, and the hunted."

"I don't get what you're talking about."

"I figured you wouldn't. You don't need to understand. So are you
seriously going to give me a needle? Don't you have spray-on anaesthetic
or something?"

"I've always wanted to try giving a needle."

I disinfected the wound, and applied the anaesthetic with three
injections around the wounded area. My hands shook a little from nerves,
but somehow it went smoothly.

"It should start getting numb soon, and then―"

"You're gonna sew it."

"Yeah."

"Do you have any experience?"

"Of course not. I'm not going into medicine. But I do have basic
knowledge of vessel suturing. I saw it in a video."

"Basic knowledge, huh..."

He drew a deep breath, and looked at me directly in the face. He had
thin, bloodless lips, hollowed cheeks, and pale parched skin. He had the
face of someone who had not lived a decent life. He really did look like
an animal prey who had been chased relentlessly, exhausted, with no
place left to run. But his eyes were different. They were emotionless,
but I could feel a fierce power emanating from them. Was it vitality? I
wondered. I had never met anyone in my life with eyes as memorable as
those. And those eyes were staring unblinkingly at me.

"You're strange."

"Why would you say that?"

"You haven't even asked for my name."

"Oh, yeah. But I haven't introduced myself either."

"Shion\footnote{shion / \begin{CJK}{UTF8}{min}紫苑 / シオン\end{CJK}, Japanese for \emph{aster}}, right? Like the flower?"

"Yeah. My mother likes trees and wildflowers. How about you?"

"Nezumi\footnote{nezumi / \begin{CJK}{UTF8}{min}鼠 / ネズミ\end{CJK}, Japanese for \emph{mouse} or \emph{rat}}."

"Huh?"

"My name."

"Nezumi... that's not it."

"Not what?"

That eye colour wasn't that of any rat. It was something more elegant.
Like... the sky just before the crack of dawn ― didn't it look like
that? I blushed, embarrassed at catching myself spouting off like some
lame poet. I purposefully raised my voice.

"Right, here goes."

Remember the basic steps of the suture, I told myself. Set down two or
three stable threads, and use them as support threads to make a
continuous suture ... this must be conducted with utmost care and
precision ... in the case of a continuous suture....

My fingers trembled. Nezumi watched my fingertips in silence. I was
nervous, but a little excited too. I was putting what used to be just
textbook knowledge into action. It was exhilarating.

Suture complete. I pressed a piece of clean gauze onto the wound. A bead
of sweat slid down my forehead.

"So you \emph{are} smart."

Nezumi's forehead was also damp with perspiration.

"I'm just good with my hands."

"Not just your hands. That brain of yours. You're only twelve, right?
And you're going into the Gifted Curriculum of the highest educational
institution. You're super elite."

This time, there was no tinge of sarcasm. Nor any hint of awe. I
silently put away the soiled gauze and instruments.~

Ten years ago, I was ranked highest in the city's intelligence
examination for two-year-olds. The city provides anyone who ranks
highest in skill or athletic ability with the best education they could
wish for. Until the age of ten, I attended classes in an environment
outfitted with the latest facilities amongst other classmates like
myself. Under the eye of a roster of expert instructors, we were given a
solid and thorough education of the basics, after which we were each
provided with our own set of instructors to move into a field of
specialization that was suited for us. From the day that I was
recognized as the highest ranker, my future was promised to me. It was
unshakable. No small force could make it crumble. At least, that was how
it was supposed to be.

\myspace

"Looks like a comfortable bed," Nezumi murmured, still leaning against
it.

"You can use it. But change first."

I dumped a clean shirt, a towel, and a box of antibiotics into Nezumi's
lap. And then, on a whim, I decided to make cocoa. I had enough basic
cooking appliances in my room to make a warm drink or two.

"Not exactly fashionable, is it?" Nezumi sniffed as he plucked at the
plaid shirt.

"Better than a dirty shirt that's ripped and covered in blood, if you
ask me."

I passed him a steaming mug of cocoa. For the first time this evening, I
saw what looked like a flicker of emotion in his grey eyes. Pleasure.
Nezumi sipped a mouthful and murmured softly―good.

"It's good. Better than your suturing."

"It's not fair to compare like that. I think it went pretty well for my
first try."

"Are you always like that?"

"Huh?"

"Do you always leave yourself wide open? Or is it normal for all you
Petri-dish elites to have zero sense of danger?" Nezumi continued,
holding the mug in both hands.

"You guys can get along just fine without feeling any danger or fear
toward intruders, huh?"

"I do feel danger. And fear, too. I'm afraid of dangerous things and I
don't want anything to do with them. I'm also not naive enough to
believe that someone who comes in through my second-floor window is a
respectable citizen."

"Then why?"

He was right. Why? Why was I treating this intruder's wound, and even
giving him hot cocoa? I was no cold-blooded monster. But I also wasn't
teeming in compassion and goodwill enough to extend a hand to anyone who
was injured. I was no saint. I hated dealing with hassles and
disagreements. But I'd taken this intruder in. If the city authorities
found out, I would be in trouble. They might see me as someone lacking
in sound judgment. If that happened...

My eyes met with a pair of grey ones. I felt like I could see a hint of
laughter in them. Like they could see right through me, everything I was
thinking, and laughing at me. I clenched my stomach and glared back at
him.

"If you were some big, aggressive man, I would have set the alarm off
right then and there. But you were short, and looked like a girl, and
was about to fall over. So... So I decided to treat you. And..."

"And?"

\emph{And your eyes were a strange colour that I'd never seen before. And they
	drew me in.}

"And... I wanted to actually see what sewing a vessel was like."

Nezumi shrugged, and drained the rest of his cocoa. Wiping his mouth
with the back of his hand, he ran a palm across the bedsheets.

"Can I really go to sleep?"

"Sure."

"Thank you."

Those were the first words of gratitude I'd heard since he had come into
my room.

\mybreak

Mother was sitting on the couch in the living room, engrossed in the
flat-screen television mounted on the wall. She noticed me coming in,
and pointed at the screen. A female newscaster with long, straight hair
was broadcasting a warning to all residents of Chronos.

A convict had escaped from the Correctional Facility in the West Block,
and was last seen fleeing into the Chronos area. With regards to the
hurricane as well, the area was to be put in a lockdown that night.
Everyone in the area, excluding special cases, was forbidden to go
outside of their homes.

\myspace

Nezumi's face appeared on the screen. Underneath, the words "VC103221"
floated up in red letters.

"VC..."

I lifted a spoonful of cherry cake into my mouth. Every year without
fail, Mother baked a cherry cake for my birthday. It was because Father
had brought home a cherry cake on the day I was born.

From what Mother said, my father was a hopeless case who indulged
lavishly in money-spending and women, but above all, the bottle ― he was
just a step away from being an alcoholic. He had come home one day, in
his drunkenness having bought cherry cakes ― three of them ― that were
so good she couldn't help but remember their taste every time September
7th rolled around. My parents divorced two months after the cherry cake.
So unfortunately, I have no memory of my hopeless case of a father who
was one step away from an alcoholic. But it was no inconvenience. After
being snagged as a top ranker, Mother and I received the right to live
in Chronos, along with complete insurance of our living conditions,
including this modest but well-outfitted house. There was no
inconvenience at all.

"I just remembered, the yard's security system is still turned off. No
harm in leaving it off, right?"

Mother raised herself slowly. She had gained a lot of weight recently,
and it seemed like an effort for her to move.

"It's such a pain in the neck, that thing. Even a cat jumping over the
fence sets the alarm off, and people from the Security Bureau come every
single time to check. What a hassle."

Almost as if in correlation with her gaining weight, she had started to
call things "a pain in the neck" more and more often.

"But look at him, he's still so young. A VC... I wonder what he's done."

VC. The V Chip. It was short for Violence-Chip, and was originally a
term used in America for a semiconductor that was used to censor
television content. With this chip, you could set the television not to
display violent or disturbing scenes. If I remembered correctly, this
term was first used in the 1996 revision of the Telecommunications Act.

But in No. 6, the term VC carried a heavier meaning. Perpetrators of
murder, attempted murder, robbery, assault and other violent crime were
subject to having this chip planted inside their body. This enabled
computers to track every location, condition and even emotional
fluctuations of the convict. VC was a term we used for violent
criminals.

\emph{――But how did he take the chip out?}

If the VC was still inside his body, his location could be instantly
pinpointed with the city's tracking system. It should have been easily
possible to arrest him without any citizens noticing. To make news of
his escape public, and to enforce a lock-down would only mean that they
hadn't been able to find his location.

\emph{――Could that bullet wound have...? No, that can't be.}

I'd never seen a bullet wound on a human before, but I could tell it
definitely came from being shot at a distance. If he had blown the chip
off himself along with the flesh of his shoulder, he would have had a
more serious wound, with burns and all. Much more serious.

"Rather dull, isn't it? A shame, since it's your special day."

Mother sighed as she sprinkled parsley flakes into the pot of stew
sitting on the table. "Dull" was another word Mother used more often
these days.

Mother and I were very similar. We were both a little over-sensitive,
and didn't like to socialize much. The people around us were nice, so
nice there was nothing bad to say about them. My classmates, the
citizens around us, were genial, intelligent, and minded their manners.
No one raised their voice to insult anyone, or treated people with
hostility. There were no strange or devious people. Everyone kept up
such meticulously healthy lifestyles that even slightly plump figures
like my mother's were rare. In this peaceful, stable and uniform world
where everyone looked the same, my mother grew fatter, every other word
"a pain in the neck" or "dull"; and I began to find the presence of
other people oppressing.

\myspace

\emph{Break it.\\
	Destroy it.\\
	Destroy what?\\
	Everything.\\
	Everything?}

\myspace

The spoon slid out of my hand and clattered to the floor.

"What's wrong? You were miles away."

Mother peered inquisitively at me. Her round face broke into a smile.

"That's rare of you, Shion, spacing out like that. Want me to disinfect
that spoon?"

"Oh, no. It's no big deal," I smiled back at her. My heart was racing so
fast it was hard to breathe. I gulped down the mineral water in one go.
Bullet wounds, blood, VC, grey eyes. What were all these things? They
had never existed in my world until now. What business did they have, so
suddenly intruding into my life?

I had a fleeting premonition. A feeling that a great change was coming.
Just like a virus that enters a cell and mutates it or destroys it
altogether, I had a feeling that this impostor would upset the world I
lived in, and destroy it entirely.

"Shion? Really, what's gotten into you?"

Mother peered into my face again, her expression concerned.

"Sorry, mom. That report is bothering me. I'm gonna eat in my room," I
lied, and stood up.

\myspace

"Don't turn on the light."

A low voice commanded me, as soon as I entered the room. I didn't like
the dark, so I usually left the lights on. But now it was pitch-black.

"I can't see anything."

"You don't need to."

But if I couldn't see, I couldn't move. I stood helplessly, with the
stew and cherry cake in my hands.

"Something smells good."

"I brought stew and cherry cake."

I heard a whistle of appreciation in the dark.

"Want some?"

"Of course."

"You're gonna eat it in the dark?"

"Of course."

I carefully inched my foot forward. I could hear a quiet snicker.

"Can't even find your way in your own room?"

"I don't happen to be nocturnal, thanks. Can you see in the dark?"

"I'm a rat. Of course I can."

"VC 103221."

In the darkness, I could sense Nezumi freeze.

"You were all over the news. Famous."

"Hah. Don't I look so much better in real life? Hey, this cake is good."

My eyes were getting used to the darkness. I sat on the bed, and
squinted at Nezumi.

"Can you get away alright?"

"Of course."

"What did you do with the chip?"

"It's still inside me."

"Want me to take it out?"

"Surgery again? No thanks."

"But..."

"It doesn't matter. That thing is useless now anyway."

"What do you mean?"

"The VC is just a toy. Disabling it is like a piece of cake."

"A toy, huh."

"Yup, a toy. And let me tell you something, this city itself is like a
toy, too. A cheap toy that's pretty only on the outside."

Nezumi had polished off the stew and cake. He gave a sigh of content.

"So you're confident that you're going to escape when the city's on
high-alert?"

"Of course."

"But there's a strict security check for trespassers who aren't
registered. There's an entire system in place throughout this area for
people like that."

"You think so? This city's system isn't as perfect as you think it is.
It's full of holes."

"How can you say that?"

"Because I'm not part of the system. You've all been programmed nicely
to believe that this holey fake mess is the perfect utopia. Or, no,
maybe that's what you guys want to believe."

"I don't."

"Huh?"

"I don't think this place is perfect."

The words tumbled out of my mouth. Nezumi fell silent. In front of me,
there was only an expanse of darkness. I couldn't feel his presence at
all. He was right, he was like a rat. A nocturnal rodent, hidden in the
darkness.

"You're strange," he said quietly, in a voice even lower than before.

"Really?"

"You are. That's not something for a super elite to say. Aren't you in
trouble if the authorities find out?"

"Yeah. Big trouble."

"You just took in an escaped VC and didn't report it to the Bureau.
...If they find that out, that's even bigger trouble. They're not gonna
let you off easily."

"I know."

Nezumi suddenly grabbed my arm. His thin fingers dug into my flesh.

"Do you really? I mean, it's not my problem what happens to you, but if
you end up being wiped out because of me, I wouldn't like that. I'd feel
like I did something horrible..."

"That's considerate of you."

"Mama always told me, 'don't cause trouble for other people," he said
lightly.

"Then are you gonna leave?"

"No. I'm tired, and there's a hurricane outside. And I've finally got a
bed. I'll sleep here."

"Make up your mind."

"Papa always told me to separate my public manners from my private
feelings."

"Sounds like a great father."

His fingers withdrew from my arm.

"I guess I was lucky that you were strange," Nezumi said softly.

"Nezumi?"

"Hm?"

"How did you get to Chronos?"

"Not telling."

"Did you break out of the Correctional Facility and get into the city?
Is that even possible?"

"Of course it's possible. But I didn't get into No. 6 on my own. Someone
let me in. Not like I wanted to come here, though."

"Let you in?"

"Yup. I was being escorted, you might say."

"Escorted? By the police? To where?"

The Correctional Facility was located in the West Block, a high-security
zone. Anyone who wanted to enter No. 6 from there had to apply for
permission from the bureau. Those who had special entry permits were
free to go in and out, but new applicants I heard had to wait at least a
month for their form to even be accepted ― and usually only less than
ten percent are admitted. The number of days allowed inside the city
were also severely restricted. Naturally, people began to accumulate in
the West Block. More people waiting for their permits to be processed
meant more accommodation and dining establishments lined the streets to
serve them. Still more people poured in to work or make business there.
I've never been to the West Block myself, but I've heard that it's a
haphazard but lively place. The crime rate there is high. The majority
of VCs that fill the cells in the Correctional Facility are residents of
the West Block. Sentences ranging from one year to life are given based
on age, criminal history, and the degree of violence of the crime. There
is no death penalty. The West Block served as a sort of fortress that
contained all people and things of criminal nature, and prevented it
from entering the city. So for a VC to be escorted from there to within
city walls ― where were they headed? And for what reason?

Nezumi crawled into bed.

"Probably the Moondrop."

"City Hall!" I exclaimed. "The centre of the city? Why?"

"Not telling. You probably shouldn't know, anyway."

"Why not?"

"I'm tired. Let me go to sleep."

"Is it something you can't tell me?"

"Can you guarantee that you can completely forget everything once you've
heard it? Pretend you didn't hear? Outright lie that you don't know
anything? You might be smart, but you're not an adult. You can't lie as
well as that."

"I guess, but..."

"So don't ask me in the first place. In return, I won't tell anyone
either."

"Huh? About what?"

"About how you were yelling out the window."

He had seen me. I could feel my face burning with embarrassment.

"It totally caught me off-guard. I snuck into your yard and was
wondering what to do next, and suddenly the window opened and you stuck
your face out."

"Hey, wait a minute―"

"I was watching for what you'd do next, and then this time you started
screaming. I was caught off-guard again. I don't think I've ever seen
anyone screaming with a face like―"

"Shut up!"

I lunged at Nezumi, but all I felt was the pillow as I fell on top of
it. In a flash, Nezumi was up. He slid a hand under my arm, and with a
quick twist, I was effortlessly flipped over onto my back. Nezumi
climbed over me and pinned both my arms down with one hand. His legs
straddled my hips and pressed them down hard. For an instant, I felt a
tingle of numbness run through my legs all the way down to my toes. It
was impressive. In the space of a split second, I had been trapped,
immobilized, and pinned to my own bed. With his free hand, Nezumi spun
the soup spoon around. He pressed the handle against my throat, and
lightly slid it across. He crouched so that his lips were at my ear.

"If this was a knife," he whispered, "you would be dead."

A muscle in my throat twitched. Amazing.

"That's amazing. Is there a trick to doing that?"

"Huh?"

"How can you immobilize someone so easily? Are there special nerve
points you press down or something?"

The force pinning me down relaxed. Nezumi sank down on top of me,
trembling ― he was laughing.

"I can't believe this. You're hilarious. What a natural," he gasped.

I circled my arms around Nezumi and stuck my hands up the back of his
shirt. It was hot. His burning skin was damp with sweat.

"I knew it... you're catching a fever. You should take those
antibiotics."

"I'm fine... I just wanna sleep."

"If you don't bring your fever down it'll drain you even more. You're
burning up."

"You're pretty warm too."

Nezumi gave a deep sigh, and murmured absent-mindedly.

"Living people are warm."

He became still, and not long after, I could hear quiet, measured
breathing coming from him. With his feverish body still in my arms,
before I knew it, I too was drifting off to sleep.

When I awoke the next morning, Nezumi was gone. The plaid shirt, towel,
and emergency kit were gone with him.

\chapter{A quiet beginning}

\begin{boxed}{Index Case (First Discovered Example)}
	Male, aged 31 years. Employee at a biotechnology firm. Engineer. Already
	dead upon discovery. Confirmed address...
\end{boxed}

\lettrine{T}{he man} sank into a bench in the Forest park, and sighed. He wondered
how many times he had already sighed that morning. He sighed, and looked
at the head of lettuce in his hand. It made him sigh again. Crisp, green
leaves firmly wrapped the head of lettuce ― as far as quality went, it
was first-class. He tore off a leaf, and brought it to his mouth. It had
a delicate taste, and the texture was excellent. First-class, indeed.
Then why wasn't it selling?

The lettuce was this man's piece of work. He had long worked in the
development of biotechnology to produce fresh produce, namely leafy
vegetables. He believed that these safe, affordable and delicious
bio-vegetables were the solution to the rising food crisis, and would
soon become a mainstay in food distribution. He had the confidence it
would. But market sales were not doing as well as he expected, and the
man was losing hope. Buyers seemed to prefer produce trucked in from the
fields of the Southeastern Blocks, rather than his bio-vegetables. The
trend was especially strong for leafy vegetables, like cabbage and
lettuce. If this continued, his boss had told him, he would have to
start thinking about discontinuing production.

The base of his neck itched. It had been itching for a while now. The
man was prone to getting rashes when he was tired. By tonight, a red
rash would probably have spread to his whole body. Too many unpleasant
things were happening today. He sighed again. The lettuce in his hand
felt heavy.

A beeping sound rang from his breast pocket. The mobile telephone screen
on his ID card lit up, and young woman's face appeared.

"Greetings from the Municipal Information System. This is to notify you
of the results of the Children's Examination you have registered for. To
confirm your account, please enter your Citizenship Number..." Before
the woman was even finished speaking, the man began to key in his
number. Today was the day of his two-year-old daughter's Examinations.
She was a bright and adorable little girl. He had never dared to say it
out loud, but he secretly harboured an expectation that she might be
acknowledged as a top ranker.

"Thank you. We have confirmed your fingerprint and registration number.
Your information is as follows..." His daughter's name was displayed,
followed by a set of detailed numbers. Weight, height, bust measurement,
condition of health, condition of nutrition, development stage, ranking
of various skills... all grades ranged in the average A to C. She was
neither overly behind, nor outstandingly brilliant. That was it. The man
gazed at the screen for a moment, and then put his card back into his
pocket. He thought of his daughter's smile.

Oh well.

The man spoke to himself, and grinned at the head of lettuce in his
hand. Gifted or not, his daughter was still his daughter. He cherished
and adored her. And that was good enough.

Suddenly, an idea sparked in his head. Had he, perhaps, been too trapped
in the idea of the best, most perfect? It was true ― there was nothing
to complain about this lettuce. But maybe its perfection was also the
bane of it. If these identical, perfect heads of lettuce were piled up
row after row, consumers might not feel as inclined to buy it. What if
its perfection was actually scaring consumers away?

A cleaning robot was approaching. On its metallic body sat a round head,
and two arms extended to pick up trash, and throw it inside the dust box
located in the middle of its body. Yes. This lettuce was like that
robot. It was clean and orderly, but too artificial. The vegetables that
the consumers wanted were more unique, more natural.... The lettuce
rolled out of his hand. The man quickly bent down to pick it up, and
furrowed his brow.

\emph{Huh?}

His fingers stiffened. His vision blurred. It was hard to breathe. The
robot picked the lettuce up, and paused. A young male voice prompted
him.

"May I dispose of this as trash?"

The man opened his mouth to speak, and was overcome with a fit of
coughing. Along with it, something white spilled out of his mouth.
Teeth. His teeth were falling out.

"Are you sure? I will dispose of it now." The lettuce was thrown into
the dust box, and the robot moved away.

\emph{――Wait, help me....}

The man reached out, and gave a cry of horror. The whole length of his
extended arm was riddled with spots. His body grew heavy. The man
staggered, and collapsed on the ground between the bench and the hedges.

\myspace

"Shion, take a look at this."

It was past six when Shion was called over by his co-worker, Yamase. The
two were the only people at the Park Administration Office. Together
they operated and maintained the three cleaning robots that patrolled
the park. Labour robots such as these were still at the prototype stage,
and even simple cleaning robots were prone to breaking down. Operating
them was a hassle too, because they weren't good at distinguishing
trash. After recording an object as trash in the computer's memory the
first time around, it was supposed to recognize it automatically every
time afterwards. But the robots sent back "indistinguishable object"
errors all the time. There was one half an hour ago, in fact. The image
sent back to him looked like a head of lettuce, and Shion had hesitated
for a moment about what to do. He had encountered other things before
that he wondered if he should call trash, like a baby chick that had
fallen out of a tree, or a hat with a rather extravagant feathered
decoration. Lettuce, though, was a first.

"Something the matter?" He stood behind Yamase, who was sitting at the
operation panel.

"Hmm... Sampo's acting strange."

Yamase liked to call the three robots by their nicknames. Sampo\footnote{three steps, or 'a stroll'} was
Robot No. 3. Today, it was working in a corner in the deeper recesses of
the park. Sampo was also the same one that picked up the head of
lettuce. The screen in front of them displayed a flashing red error
notifying them of an indistinguishable object.

"What's the image like?"

"Yeah, about that. It's not very clear, but... it's strange."

"Strange?"

Yamase was twenty ― four years older than Shion ― and quiet by nature,
seldom ruffled by anything. The calm nature of his co-worker was one of
the two reasons why Shion liked this workplace. The other reason was
that because his job dealt mostly with machines, he didn't have to talk
to people.

"Here, you take a look," Yamase said, switching the screen over to the
camera.

"Can you focus in a little more?"

"Sure," came the answer, and Yamase's hands moved swiftly over the
control panel. The image became clearer.

"What......" Shion leaned in closer, and his breath caught in his
throat. Feet? A pair of trousered legs were protruding from behind the
bench. He could see a pair of brownish shoes outfitting them.

"You think he's sleeping...?" Yamase's voice trembled.

"Any signs of life?"

"Huh?"

"Can you raise Sampo's sensors to the max level?" Sampo was outfitted
with several receptors that could sense heat, sound, and texture.
Yamase's voice shook more violently.

"Oxygen, heat emission.... zero. No signs of life."

"I'll go check," Shion said abruptly.

"I'm coming too."

They leapt on their bicycles, and pedalled as hard as they could.
Bicycles had become explosively popular in the last few years, and
statistics showed that the average citizen owned 1.3 bicycles. Jogging
shoes were also selling well. Rather than convenient and effortless
modes of transportation, it seemed like more people were choosing to
walk, pedal, and otherwise use their own bodies. Popular or not, for a
student like Shion, something this affordable that manoeuvred easily and
didn't cost anything to fuel was more of a necessity.

There were speed limits even for bicycles within the park. Shion
pedalled full-throttle through a path he would usually only stroll down.
Most vehicles nowadays were equipped with a restraint mechanism that
automatically kicked in when the vehicle went over a certain speed.
Bicycles were no exception, and the mechanism was usually built into the
brake lever. But Shion's bicycle was an older model, and wasn't equipped
with speed restraints. He would have to pay a fine if the Transportation
Bureau found out, but right now, he was glad he could go as fast as he
could.

He reached a quiet area secluded by trees. Beneath a canopy of swishing
leaves, Sampo was standing still. His head joint, slightly tilted to the
side, made him look either pensive or baffled.

"Sampo." In response to Shion's voice, its LED eyes lit up green. Shion
peered behind the bench, and froze.

"Shion, what's going on?" Yamase arrived slightly later, and made a
muffled noise in his throat.

The man lay behind the bench, as if to hide behind it. His mouth was
open and his eyes wide and staring. His expression resembled surprise,
rather than fear or pain. He looked like he had seen something shocking
moments before he died. His hair was snowy white, and on his cheeks
there were spots that looked like senile plaque. His wrinkles were
pronounced. He was quite aged.

\emph{――That's a pretty flashy shirt for his age, though.}

Shion remarked inwardly at the light pink shirt the man was wearing.

"Yamase-san, can you contact the Security Bureau?"

"Huh? Oh... oh yeah, of course. Sure. Give me a minute... Hello? Um,
this is the Park Administration Office..." Half-listening to Yamase's
shaky voice as he explained the situation, Shion reached out cautiously
to touch the man. Rigor mortis had spread to his whole body.

"That's impossible," Shion muttered almost automatically in disbelief.

\emph{――It was too soon.}

Rigor mortis usually began taking effect at least an hour after
death―two or three hours, in most cases. It started at the jaw and
spread gradually downwards to end at the legs. Judging by that, this man
would have been dead at least several hours. But 30 minutes ago, this
body wasn't here. If it was, Sampo would have noticed it. He knew that
there had been a living person sitting on the bench. After confirming
the lettuce, Sampo's sensors had registered a living human presence. Of
course, he had no evidence to prove that these two were the same person.
No, there was no way it could be. There was no way a person who was
alive 30 minutes ago could go through complete rigor mortis in this
short time. Then―was someone else sitting on this bench, oblivious to
the dead man?

\emph{―Impossible.}

Shion let go of the man's arm, which felt stiffer and colder than
Sampo's mechanical one. It was impossible. Even if the man had lain dead
without being noticed, Sampo would have picked him up. Indeed, Sampo had
reacted to his presence, and sent an "indistinguishable object" error
just minutes ago. That meant that 30 minutes ago, there was no dead body
here.

Shion thought he saw the body move. Of course, it was just his
imagination. But ― Shion stifled a cry of horror. The jaw of the man,
stiff only minutes ago, was starting to loosen. He thought he could even
smell a faint odour of rot. The man was face-down, and behind his ears
Shion could see a blackish-green stain begin to spread. That was
definitely not there before. Certain not visibly to the naked eye. Shion
leaned in closer.

"They're coming," Yamase sighed in relief. A Security Bureau car was
approaching soundlessly.

\myspace

"So in the space of ten-some-odd minutes, you saw complete rigor
mortis―and it started rotting right afterwards? That's impossible," Safu
concluded simply, after she had swallowed her mouthful of chocolate
doughnut. The fast-food joint where they sat, located near the older
parts of town was bustling with people of every shade and colour.

"And if you're saying you smelled rot, then that means decomposition by
bacteria had already started, right? That can't be. Even in the middle
of the summer, it would take at least 30 hours― right? ― for rigor
mortis to dissipate completely."

"Under a fixed set of conditions, it would take 36 hours in the
summertime, 3-7 days in the winter, and 60 hours in the weather we're
having now. That's what the textbooks say," Shion replied, dropping his
gaze from Safu's face and taking a sip from his cup of tea. He felt
melancholic. And tired.

"Did the Security Bureau give you a hard time?" Safu peered into his
face. Her short, cropped hair framed her delicate face and large eyes,
which gave her a mysterious, androgynous sort of allure. Safu was also
among the top-ranking in intelligence during her Examinations for
Two-Year-Olds. She was one of the several classmates he studied with at
the same school until the age of ten. And presently, at age sixteen, she
was the only one whom Shion shared a close relationship with. She
specialized in physiology, and was set to go on exchange soon to another
city.

"It was an unnatural death after all, they must've been suspicious. They
probably interrogated the heck out of you because of that, didn't they?"

Safu as Shion knew her in the classroom was a small, quiet girl. She was
probably still the same in the lab. But when she was alone with Shion,
Safu smiled often, ate well, and relaxed her formal tone. Shion drained
his tea, and slowly shook his head.

"Nah, it wasn't as bad as I thought." Truth be told, the Security
Bureau's interrogation was surprisingly short. All they did was seize
the data that Sampo had recorded of the body, and demand an explanation
of the situation from each of the two. The official spoke sharply when
he found out that Shion's registered address was located in the old-town
district, close to the West Block, but Shion was used to that kind of
treatment and thought nothing of it.

"Then why do you look so down about it? You're the picture of the
troubled young man right now."

"It... just doesn't seem right."

"The rigor mortis and its dissipation time?"

"Right. You said so yourself, Safu. It's not possible. You're right.
There was no condition present that could have accelerated the rigor
mortis and dissipation to that extent."

"You mean no condition in terms of temperature or humidity, or some
other external influence, right? You won't know until you perform an
autopsy if there might be an internal cause that accelerated it."

"Internal cause, huh... like what?"

"For example, if that person was severely debilitated, he wouldn't have
stiffened up as much, and it wouldn't have lasted as long. In people
with phosphorus poisoning or in infants, they say it's almost
nonexistent..."

"He was definitely not an infant, I can tell you that."

Safu sniffed indignantly and glared at Shion.

"It was just an example. You're as sarcastic as ever, aren't you? That
hasn't changed at all. But I guess there's not much we can make of it if
we don't have any data."

"Yeah...." Shion nodded vaguely, and unconsciously bit his lower lip.
Data, textbooks, manuals... there were times when they became completely
useless. What he once believed to be so certain and absolute would be
overturned ever so easily, and crumble before him. He experienced that
four years ago.

\mybreak

"Shion." Safu put her elbows on the table, and folded her hands over
each other. She placed her chin on them, and gazed at Shion.

"I want to ask you something."

"What?"

"Four years ago ― why didn't you enroll into the Gifted Curriculum?" It
was as if her question saw right through him. Shion broke off a piece of
the blandly sweet apple pie with his hands. The filling oozed out onto
the plate.

\myspace

"Why're you asking now?"

"Because I want to know. Even from an objective point of view, you were
a stellar student. You absorbed information well and knew how to apply
it. All the teachers had high expectations for you."

"You're giving me too much credit."

"It's the truth. The numbers prove it. Do you want me to show you your
Skill Test results again from four years ago?"

"Safu." He had a bitter taste in his mouth. It felt like it was welling
up from the very core of his body.

"What's the point of asking me this now? Four years ago, they decided I
wasn't qualified for the Gifted Curriculum, so I lost all special
privileges. I didn't \emph{choose} to not enroll, I \emph{couldn't}. Now I work for
Park Administration to pay for my tuition, and I'm taking trades courses
from the Labour Bureau. But my attendance hasn't been good so I'm not
even sure if I can graduate. That's reality. That's the truth you're
talking about, Safu."

"And why did you lose your privilege?"

"I don't want to talk about it."

"But I'd love for you to tell me."

Shion finished licking the pie crust from his fingers, and closed his
mouth firmly. He didn't want to talk about it. Or, rather, he couldn't
think of any explanation that would make Safu understand.

The reason was simple. He had taken a VC under his wing for the night,
and let him escape. The Security Bureau had found that out. They had
thought it suspicious that his mother Karan had left the security alarm
off, and Shion had left the foreign-object detection system off in his
own room. The security systems of each house were connected to the
Central Administration Bureau's computer system, and could be easily
tracked.

Not one hour had passed after Nezumi had disappeared when officials from
the Security Bureau were knocking on his door. It was the start of their
long and persistent interrogation.

\emph{You knew that he was a VC, then?}

\emph{Yes.}

\emph{Why didn't you call the police immediately?}

\emph{Well....}

\emph{Answer my question. You don't need to rush. Just give us a clear and
	accurate answer.}

\emph{It was because he looked about the same age as me, and he was seriously
	injured. So I felt sorry for him....}

\emph{So you sympathized with this VC, didn't contact the police, but instead
	treated his wounds and helped him escape.}

\emph{It ended up as so, yes.}

The Security Bureau's Investigations and Interrogations official was
named Rashi. He spoke gently throughout the whole meeting, never once
raising his voice or his fist in violence. When their gruelling two-day
investigation was over and Shion was released, he even gave him a
friendly clap on the shoulder and said, "It's been hard, I know.
Thanks." But Rashi's eyes never smiled once, and Shion had noticed. Even
now, four years later, those unsmiling eyes came into his dreams, their
gaze boring into him. He would awake in the morning, shaken, and soaked
with sweat.

He concealed a criminal and aided his escape. Shion wasn't sentenced for
this crime, but he was deemed severely deficient in appropriate judgment
skill and ability to take action, and as a result all his special
privileges were removed.

When the hurricane passed, Shion and Karan were cast out onto the
streets, under a blindingly blue sky. They had no place to live, nor any
means to make a living. Shion's Gifted Curriculum in ecology had become
something more far away and unreachable than the clouds that floated in
the sky above them.

A certainty, a definiteness he had in his hands only yesterday, only
moments before, had vanished. They had scattered on the winds, more
frail than the leaves he had watched whipped around in the storm. It was
a sense of loss he was feeling for the first time in his life.

No. 6 had no welfare system. There was only a hierarchical insurance
system based on the level of contribution that a select few of the
citizens had to offer to the city. Shion and Karan, far from
contributing to the city, were treated as people who had failed to serve
their responsibility as citizens. They were at the lowest possible rank.
That meant that, apart from being allowed to remain in the city, they
were excluded from any aid or insurance.

Petri-dish elite. Nezumi had used that term that night, and it was true.
He realized the weight of it after he had been thrown out of his
enclosed and sheltered container. No. 6 was none other than a caste
society. The vertical dynamic of the population was neatly ordered into
a pyramid structure. Once you tumbled off the top tiers, it wasn't easy
to crawl back up.

\myspace

"Look at you, so serious." Safu laughed. "I get it. If it's that hard to
explain, then I won't ask."

"Sorry." Shion held up a hand and ducked his head in apology. He was
relieved that she didn't question him further. The events were easy
enough to explain. He did want to tell Safu, for her to know about the
dramatic events that had turned his life upside-down. But what Shion
couldn't grasp, couldn't seem to find the words to explain, were his own
feelings. He even surprised himself with what little regret he felt. He
did feel shock at the fragility of his position, and he did more than
once find himself curled up, unable to grapple with his sense of loss.
But now, after four years of living through it all, he pondered. What
would he do if he could turn back time to that day, on his twelfth
birthday? Would he have called the police? Would he have set his
security alarm off? The answer was always "no".~

Even if he had the chance to return to that night, he would have done
the same thing. He would have taken in the wind and rain, and the
intruder that came with it. He felt it with certainty, and his certainty
put him at unease. It wasn't like he found his life now more satisfying
than before. He still had deep attachments to ecology, his
state-of-the-art learning environment, his comfortable life ― and
shamefully enough, even the accolades, the words of praise and
encouragement, and gazes of admiration that he was the centre of. But
even so, he would have done the same thing. If accepting Nezumi meant
his own destruction, then to destruction he would have trodden again and
again. He had no regrets about what he did. But he couldn't explain why.
Since that night, other hurricanes came and went. Listening to the
excited murmurings of the leaves in the wind, Shion felt not regret, but
a sense of longing. It was a yearning to see him again.

Shion didn't have the confidence that he could explain it to Safu well
enough. He had no other option but to remain silent.

"Shall we go then, Shion?" Safu stood up. The restaurant had become even
more crowded, and now they could barely hear each other's voice.

"I'll walk you to the station," Shion offered.

"Of course. You would have to be really tactless to let a girl go home
by herself, wouldn't you?"

"Oh come on," retorted Shion, "we both know how strong you are, even
though you might look small and skinny. And you're speedy. I always
thought you were more fit for martial arts than physiology, actually."

"You know what, you're right. I've been told off once about how I
emotional I can get all of a sudden, when I'm usually so quiet. Maybe
I'm not meant for lab work after all."

They walked side-by-side down the road to the station. Excluding a few
restaurants, late-night business was banned in the city. In a matter of
hours, the throngs of people walking up and down the streets now would
disappear. Shion gave Safu's back a light push. Her last words had
sounded somewhat dejected to his ears.

"Is that supposed to be the voice of someone who's passed the exams and
is about to go on exchange?"

Safu raised her face, and grinned.

"Jealous, aren't you?"

"Yeah."

"That's awfully truthful of you."

"Be true to yourself, be kind to others. It's been my motto these days."

"Liar."

"Huh?"

"You're not jealous at all."

Shion stopped. Safu was staring at him challengingly. Just as he was
about to call her name, he was suddenly grabbed by the shoulder from
behind.

"Excuse me." Shion turned around. A man was standing there, smiling. He
was about a head shorter than Shion, and was wearing a Security Bureau
uniform. It was navy blue from top to bottom and made of a special
material called superfibre, which had impressive qualities for its
unremarkable appearance. With durability that was tenfold that of steel,
it served the purpose of a bullet-proof vest well enough; at the same
time, it let air pass through easily so the garment could breathe. There
was an increasing number of these uniformed Law Enforcement officers
from the Security Bureau the closer they neared to the West Block. Shion
calmly brushed the man's hand off his shoulder and spoke.

"Can I help you?"

"Ah, well... I just want to ask you two a couple questions... how old
are you?"

"Sixteen."

"The both of you?"

"Yes."

"You do know that those under eighteen are prohibited from being
outdoors after nine?"

"Yes, but it's still before eight."

"Shion," Safu whispered sharply. She was telling him not to argue. But
the Security Bureau uniform standing before him brought back to memory
the eyes of that interrogation officer who called himself Rashi. Instead
of feeling intimidated, Shion was compelled to retaliate.

"Your ID cards, the two of you, please." Perhaps he had taken notice of
Shion's rebellious attitude. The man wiped the smile clean off his face
and demanded their identification cards expressionlessly. Safu passed
her silver card to him. Shion silently did the same.

"Your Citizenship Numbers, in order."

"SSC-000124GJ."

"Qw-55142."

The man pulled the cards out of his portable card-reader, and turned to
give Safu a slight bow.

"A Gifted Curriculum student like yourself shouldn't be roaming these
areas at such a late hour. I advise you to go home."

"I was on my way... I was walking to the station."

"Let me walk you there."

"No thank you. He's going to." Safu clung to Shion's arm.

"I'll take her," said Shion shortly. "That's where we were headed in the
first place. Let's go, Safu."

Snatching the cards from the officer's grasp, Shion grabbed Safu's hand,
and strode swiftly away. When he turned around some moments later, the
man had already disappeared into the bustling crowd.

"That scared me." Safu clutched her chest. "I've never been scolded by
the Security Bureau."~

"It happens all the time," replied Shion. "If you didn't have your
Gifted Curriculum ID, he would have grilled us even more."

"Really?"

"Really," said Shion grimly. "Like the train that you're about to get
on. With that ID card, you can bypass the General car and ride in
Special Class. That's the kind of city we live in. Everyone's sorted out
into categories based on skill, wealth, and all these other factors."

"Don't talk about it like that," Safu protested. "You don't 'sort'
people like you 'sort' garbage and merchandise. People are people.
They're humans."

"Safu, in this city it doesn't matter whether we're people or not. It
matters how useful you are to the city. That's it."

"Shion...."

"Back there you called me a liar. I'm not. Of course I'm jealous. You've
got all your privileges, and you're allowed to study and experiment to
your heart's content. I'm envious, Safu. I resent you, even. You have
everything that I don't have."

Shion paused, and let out a long breath. He had gone too far. It was
shameful. Low. Embarrassing. Pathetic. He clicked his tongue at himself
in frustration.

Safu sighed as well.

"You're still a liar."

"Huh?"

"Did you not hear me? You're. Still. A. Liar. I can add 'big' on top of
that, if you like. You're only pretending to be envious of me. Or do you
not even realize that you're lying? What a dense boy I've got on my
hands."

"Safu, what―" Shion began in exasperation.

"If you were really envious and resentful, you wouldn't be able to stand
going out to eat with me. But you, you're laughing, eating, making
conversation, cracking jokes like it's nothing."

"Hey, I have some pride too. Obviously I'm not going to be openly
jealous."

"Shion," said Safu firmly. "My specialization is in cognitive functions,
brain activity and their relationship with hormones."

"I know."

"Good, because if you didn't, I would've been mad. I haven't told you
this over and over for nothing. Anyway," she continued briskly, "say you
are hiding your resentment and pretending to be enjoying your time with
me. It would be stressful, right?"

"I guess so..." Shion replied dubiously.

"It \emph{would} be stressful. And when you feel stress, your adrenal glands
release steroid hormones called corticosteroids that influence your
brain. And what it does to brain activity is―"

"Okay, Safu, I get it." Shion interrupted. "That's enough. Save your
lecture for next time and I'll listen carefully―"

"Listen to me. You're not feeling any stress. You're not resentful of me
at all. Shion, what is it that you want to do?"

"Huh?"

"If you do want to continue your studies, you can be resentful of me.
But you're not. You said I have everything you don't have. Then what is
it that you have? You can't say you have nothing," she added hastily.
"People who have nothing ― no ― people who \emph{think} they've got nothing
left, can't smile like you do. Or talk like you do. For your emotions
not to have any influence on your actions, to have that level of perfect
control, it takes special training. You're not getting any special
training. I don't think you're an overly emotional person, but I also
don't think you have the ability to control 100\% of your emotions
either. The only reason you can have a regular conversation with me and
laugh around me is because you have a certain level of emotional
security."

"Safu, what you just said is all armchair theory. Humans have complex
emotions. They're not like lab rats. I don't think you can explain how
emotions influence people's actions that easily. It's arrogant to
believe that science can explain everything about human nature."

Safu shrugged. They were approaching the station.

"I didn't know you wanted to become a writer."

"Safu," Shion said wearily.

"Then I'll say this in a literary context. Emotional security... so I'm
talking about hope, or dreams. You have those. That's why you don't feel
the need to resent me. Shion, what is it that you hope for?"

\mybreak

Hope. He repeated the word silently. It was a word he hadn't used for
years. It was neither sweet nor bitter, but it slowly warmed him from
deep inside of his body.

Hope. What do I hope for?

\myspace

His promised future had collapsed. What was left to him now were his
mother, the meager wages from his job, and his own sixteen-year-old
body. What hope resided in those? He wasn't sure. But he was sure that
he hadn't completely lost hope either.

They entered the station. The old-town district where Shion lived was
located adjacent to the West Block and the city border, and functioned
as a sort of buffer zone between the city centre and the West Block. It
was called Lost Town. A far cry from the tranquility of the city centre,
it was a squalid place, dense with people. The station they were in was
also very crowded. The faint smell of deep-fried food and alcohol wafted
in the air.

"I'm fine from here." Safu stopped. There was a black winged insect on
her shoulder. Brushing it away, Shion asked a nonchalant question.

"Be careful. Oh, when are you off for your exchange again?"

"In two days."

"Two days!" Shion exclaimed. "Why didn't you tell me sooner?"

"Because I didn't want to. Would you have thrown me a farewell party if
I did?"

Safu jutted her chin out defiantly.

"Shion, I want to ask something from you."

"Sure, if I can manage to get it to you in time..."

"Your sperm."

Safu looked Shion in the eyes as she said those words. She didn't blink
once. Shion gaped at her open-mouthed.

"Did you hear me? I want your sperm."

"Uh― what? Safu... um―"

"Out of all the people I know, you would probably be the most superior
sperm donor. Your sperm and my ovum. Don't you think it would produce
the most perfect child? I want it, Shion. I want your sperm."

"Artificial insemination needs permission from the city," Shion answered
cautiously.

"Getting permission would be easy. The city encourages artificial
insemination between people who possess excellent DNA and superior
skills."

Shion swallowed, and turned away. The winged insect crossed his line of
vision, buzzing incessantly. Irritation welled up inside him.

"Safu, I don't know if I told you this, but I've never known my father.
I don't know his personality, his stature, or if he had any illnesses."

"I know. But parents don't matter. Ninety-nine percent of the human
genome has been decoded already. I can find out anything I need to know
about your genetic information."

"And then... if you do get the information, and there's something in
there that you don't want, what are you going to do?"

"Well..."

"Safu, what are you trying to get at? Do you think a human being is
entirely what his DNA base sequence tells us he is? Sure, you can look
up my DNA, analyze my genes, but what's that going to tell you about me?
You talk about having kids like it's easy, but―"

"I know a lot more about you than you think!"

Safu's voice cut him off shrilly. People turned their heads as they
passed.

"We've been together since we were two. I know what kind of person you
are, what you like to do... I know. I know, and I'm still telling you
this― you're the one who doesn't know anything."

"What?"

Safu mumbled something, but he couldn't catch it. He bent toward her
slightly so he could hear better.

"I want to have sex with you."

Her words rang clear in Shion's ears.~

"Safu...."

"I don't want your sperm. I don't want artificial insemination. I don't
care about having kids or not. I want to have sex with you. That's it."

"Wait, uh― wait a minute... Safu, I―"

"Right now."

Shion inhaled. The greasy scent of fried food wafted into his nostrils.
The clock chimed eight o'clock.

"Not now."

"Why not? Because you're not interested in me? Or not interested in
sex?"

"I'm interested in both. But... I don't want to do it, not now, with
you."

"So it's because it's with me?"

"No― my body would probably respond no problem. Even now I'm... but― but
that's why I don't want to. I don't want to sleep with you on a spur of
the moment."

"You know that's like saying you've never seen me in that way before."

"Yeah. I always thought of you as a friend."

"I can't believe it."Safu sighed in exasperation. "Why are you such a
kid? Whatever. I'm going home."

"Safu, in two years―"

"Hm?"

"Your exchange is for two years, right? When you come back, I'll ask
this time."

"If I want to have sex?"

"Yeah."

"You're a bonafide idiot if I ever saw one. I don't know how you could
have come this far being that laid-back."

"Stay safe. Don't work too hard."

"Oh, you can count on me working hard. I'll work so hard, it'll keep all
the boys away."

With a casual wave of her hand in farewell, Safu turned around, and gave
a small shriek. A small grey animal darted past Safu's feet and scurried
up Shion's body.

"A mouse!"

A small mouse about the size of Shion's pinky sat on his shoulder,
twitching its nose.

"I'm surprised to see mice in this city. But it \emph{is} kind of cute," Safu
mused.

"Pretty friendly, too."

The mouse brought its face close to Shion's ear.

"Still a natural," it whispered.

He felt an electric shock run through him. He grabbed at the mouse, but
it slipped through his fingers, bounded off his shoulder and shot toward
the station exit. True, this was an older district―but Lost Town was
still within city limits, and mice were rare. The Health and Hygiene
Bureau saw to the complete removal of all pests, animal or insect.
People weren't used to seeing the mouse that sped past their feet.
Shrieks of surprise and bursts of anxious buzzing rose from the crowd.

And at the very end of it, Shion saw a pair of grey eyes. It was for a
fleeting instant. A jolt pierced through his body again.

"Nezumi!"

"Shion, what's wrong?"

"Safu, you can make it home by yourself, right?"

"What? Of course. I was just about to, wasn't I? What's wrong? Why are
you so agitated?"

"Sorry―"

After they parted here, he wouldn't see Safu again for two years. He
knew he had to give her a proper sending-off. At the very least, watch
her retreating back until it disappeared into the jostling crowd.
Whether they were going to have sex or not, didn't change the fact that
Safu was important to him. He knew well that this was nearly not the
proper farewell that she deserved. He knew. But what he thought he knew
so well was swept away instantly. His body moved on its own, defying his
rational thought. Yes, he had experienced this four years ago― even
though he knew reason always had the right answer.

Turn the security system on. Notify the Security Bureau. Remove the
foreign presence. He had defied all of it. It was the same now. He was
letting his emotions control his actions.

It had begun raining outside. Raindrops pelted his cheek. In the crowd
of people briskly walking to and fro, not a familiar face was to be
seen.

"Shion!" Karan greeted her son at the door, and widened her eyes.
"You're soaked through! What were you doing?"

"Walking."

"In this rain? From where?"

"The station."

"And why on earth did you let yourself get this wet?"

"I was cooling off."

"Cooling off, hmm? Laid back as always, aren't you?"

Safu has used the same words only moments before. Shion chuckled to
himself and began towelling off his hair. It had suddenly grown very
cool since it started raining; the old kerosene fan heater was humming
to keep the room warm. Karan yawned. It was already time for her to
sleep. Tucked away in a corner of Lost Town, Karan ran a modest bakery.
It was small, with only one showcase. But people seemed to be drawn to
the aroma of freshly-baked bread that wafted from the doors early each
morning, and business was booming. She opened early, and so slept early
too. It was rounding nine o'clock, which for Karan was like midnight.

"I'm thinking of increasing the batch of butter rolls tomorrow. And
maybe be a little adventurous and try selling some simple cakes, on top
of the muffins that we sell. What do you think?"

"Like cherry cake?"

"That's the one. A little something that people can buy as a snack, but
a little more higher-end than bread or muffins. A small souvenir for a
special day, or something like that."

"That sounds great," Shion enthused.

"Don't you think so? And I think having cakes in the display case would
liven things up a little."

Shion nodded, and began to leave the living room. In this house, they
didn't have the luxury of private bedrooms. Karan slept in a corner of
the living room, and Shion in the storage cellar.

"Shion," his mother called. He turned around.

"Did something happen?"

"Huh?"

"Did something happen to you that would make you need to cool off?"
Karan continued without waiting for Shion's answer. "When you came home,
you seemed a little dazed. You didn't even seem to realize you were wet.
And... even now―"

"Now?"

"You look absent-minded, but then again a little agitated... it's a
strange face you've got on. Do you want me to bring a mirror?"

Shion exhaled shortly.

"Someone died in the park today."

"What? In the Forest Park? There was nothing in the news about that."

Nothing in the news? Did that mean that the man died of natural causes?
Although sudden, maybe it was explainable. Not enough to make the news,
just a normal death ― Shion shook his head. Of course not. The time it
took for that body to become rigid, the expression on his face, the
green stain. It was all too abnormal.

To the Security Bureau he had only explained what he found at the scene.
He pretended that he hadn't noticed the rigor mortis or the stain―he
felt like he had to. He didn't know why, but a voice inside him had told
him to play dumb, to lie. Just as a small animal might sense danger and
hide itself, his instinct had warned him. Instinct -- there it was again.
He was acting not on reason, but on whim. He was turning away from logic
and sense only too easily to succumb to instinctive emotion. Shion
sighed deeply. It was a little hard to breathe.

"And that's why you're agitated?"

"Well, yeah. I've never seen a dead body before."

\emph{I'm lying, mom. I saw those eyes again today. I saw Nezumi. I have a
	feeling that something's going to happen. That's why―}

Karan smiled and wished him good night. It was a gentle smile. He wished
her good night in answer, and left the living room.

Karan's stature was still plump, but she looked much younger than
before. It seemed like she hadn't taken the move from Chronos to Lost
Town too harshly. She often smiled as she talked about how enjoyable it
was to bake bread, and how uplifting it was when people bought them. It
wasn't just out of kindness or a desire to reassure her son. Karan
wasn't despairing at all about their life here. In Chronos, everything
was given to them, but their life in Lost Town was something Karan had
built up with her own hands. That was why Shion didn't want to destroy
it. He didn't want to uproot her entire life as he did four years ago.
He didn't want to get her involved in trouble again.

Shion collapsed into bed. He felt a faint chill, and there was a dull
pain at the back of his head. When he closed his eyes, a flurry of
images rushed past his eyelids. The greenish stain, the abandoned
lettuce, the pink shirt, Safu's face. \emph{I want to have sex.} The mouse that
had scurried up his body. \emph{Still a natural.} The core of his body grew
hot. His heartbeat quickened. It was no dream. It wasn't an illusion.
Nezumi did exist there, in the crowd people at the station. \emph{That was
	some flashy appearance you made back there.} "Jerk," he muttered under
his breath. What was he supposed to expect from that short appearance?
What was Nezumi planning to do?

Shion sat up in bed. Safu aside, were the body in the park and Nezumi
somehow connected? On the same night that he discovered the body, Nezumi
appeared. Was that a coincidence? If they were related, how were they―

A chime interrupted his thoughts. The mobile telephone on his ID card
was ringing. It couldn't be. He knew it couldn't be Nezumi, but his
heart raced. His fingers trembled as he grasped the card. White letters
flashed on the display―Safu. He tapped the Talk button and the screen
switched to Safu's face.

"Shion, were you asleep?"

"Ah―um, no."

He had forgotten. He should be the one calling her back, and to finish
saying the farewell that he had left hanging.

"Safu, I'm sorry about back there. I―"

"That person was that important to you, huh?"

"Huh?"

Safu's face had broken into a wry smile. It was both serene and
beautiful.

"I've never seen you look like that before. Do you know what kind of
expression you had on?"

"Huh? Wait―did I look that bad?"

"It was very interesting indeed. It kept me entertained the whole time.
First, it was astonishment, and then―well, let's see―what could you call
it? Joy? Raptness, maybe. Enough to wipe everything else out of your
mind. And then you beelined out of the station, leaving me behind all by
myself. Sad story, huh? I know."

"I'm so sorry. I can't apologize enough."

"I'll say. You're welcome. At least I got to see a new side of you―I've
never seen you with that face before. So, Shion, who is it that makes
you look like that? Was she\footnote{in Japanese, can be taken as he/she} that important to make you drop everything
and chase after her?"

"Yeah."

He even surprised himself at his prompt affirmation.

"Um, Safu, don't get me wrong. It's not a girlfriend, or anything like
that. Uh―I can't really explain it well, but..."

"Also my first time seeing you stumble over yourself trying to explain
things. That's alright if you have a girlfriend. I don't mind if you've
already got someone on your mind. ―No, that was a lie. Look at me, I
always try to put up a strong face in any situation. It's a bad habit of
mine."

"That's not true," Shion retorted. "You're always truthful to yourself."

"Only in front of you." Didn't you realize? Safu continued, and her
expression grew serious.

"Safu, really, um― take care of yourself. When we meet in two years―"

"I love you, Shion. More than anyone else."

The line died without waiting for his answer. He could hear the
pitter-patter of rain. He thought he saw something move in a corner of
the room.

"Nezumi?"

Amidst the bags of flour and sugar piled in the storage room, only the
sound of rain echoed. Shion hugged his knees and sat silently in the
darkness, lending an ear to its continuous drizzle. The rain showed no
signs of either worsening or letting up, and continued through the rest
of the night.

\chapter{Flight for life}

\lettrine{S}{hion} inserted his ID card into the card reader of the Park
Administration Office. The door opened soundlessly, and the air
filtration system and temperature control started up. There was no one
inside the office yet. It was odd that Yamase was not here already.
Shion turned on the switch of the park administration system. It was the
start of another work day.

"Good morning." An image of City Hall, The Moondrop appeared along with
the greeting. "Your unwavering allegiance to the city―"

He placed his hand on the image of the Moondrop and recited slowly.

"I pledge hereon and ever my unwavering allegiance to the city of No.
6."

"Our gratitude for your loyalty. Engage in your day's labour with
sincerity and pride as a good citizen of the City." The Moondrop
disappeared, and was replaced with a report of the living conditions of
all the organisms in the Park. Shion breathed a sigh of relief. The
daily allegiance rituals had become a source of discomfort for him.
Although it was among the farthest branches, Park Administration Office
was still under direct affiliation with the City. All employees were
required to pledge allegiance to the City every morning. If they
refused, they would lose their job.

It was no big deal. All he had to do was cast his hand over the display,
and recite the same words. Shion tried to brush it aside, but the worn
and banal words of the pledge, and the sheer ridiculousness of the
ritual itself always filled him with disgust. And for repeating this
banal and ridiculous ritual every morning, Shion's injured pride stung.
He remembered Safu complaining of the same thing. The laboratory where
Safu worked also operated under the City, so an allegiance ritual was
mandatory as well.

Shion lightly blew on his palm. It was no use complaining. As long as he
was to be a citizen of No. 6, as long as he was going to continue living
here, it was no use fretting about pride. So he kept telling himself.

The office door opened, and Yamase came in. Behind him stood a woman who
looked about in her twenties. Yamase called over to her softly, but she
shook her head, bowed slightly, and left in a hurry. She was a small
woman with long hair.

"I see..." Shion stopped his hands over the control keys and turned to
stare into Yamase's square, angular face.

"It's rare to see you with a woman, Yamase-san. Could she be―" He went
on to say 'your girlfriend', but promptly shut his mouth. Yamase was
sitting at his control panel, reciting the pledge of allegiance to the
city. His expression was tense. Shion could tell from his face that this
wasn't the right time for teasing.

"Yamase-san, is something the matter?"

"Shion, that lady..." Yamase paused, and turned to Shion. "She's the
wife of yesterday's body."

"Huh?"

That would make them a couple of enormous age difference. No. 6 had no
strict regulations for marriage, as long as it was between two
consenting registered citizens. Even if the couple had not gotten an
official marriage certificate, it was not a problem. The problem was
more with whether they would be able to prepare an appropriate
childrearing environment if they were to have children. Childbirth was
not permitted for people who didn't meet the city's criteria of
standards. Shion didn't know what those criteria were. Nevertheless,
people were free to marry, and a couple or two with this much age
difference was nothing out of the ordinary.

"She says they're only three years apart," said Yamase quietly. Shion
didn't understand. "He was three years older than her," Yamase repeated.

"Three years... but―"

Yamase nodded. "That body was only 31 years old."

"No way!" exclaimed Shion incredulously. "That can't be. That body was
an elderly man, no matter how you look at it."

"Yeah," said Yamase heavily. "I was surprised too. But the body hasn't
come back to the madam since. They're keeping it over at the Bureau."

"Keep? So you're saying an autopsy wasn't enough to find out how he
died?"

"I guess that's what it means."

They couldn't find the cause of death. Shion couldn't imagine a cause of
death that No. 6's front-line medical technology couldn't decode.
Medicine had long had full bearings on organism analysis to the
nanometre scale. An average cell measured approximately 20 micrometres.
A micrometre was 1000 times larger than a nanometre. Any disease at the
cellular level should be more than easy to find and analyze.

Shion felt a chill. Abnormal rigor mortis, its dissipation, and the body
it left that was unmistakably that of an elderly man―what did it all
mean? He didn't know. At present, Yamase's low voice spoke again.

"The madam was told that he died from an accident in the park, and to
wait for further notice until they figure out his cause of death. She
came here today asking if she could at least see where the accident
happened."

"Accident? Bullshit!"

"You're right, it's a load of bull. Them telling her it was an accident
is a huge lie," Yamase replied, and scratched his neck vigorously in
irritation.

"Yamase-san, why does the Bureau have to lie about it? And isn't it
strange that they can't seem to find a cause of death?"

"Yeah... this incident is full of unanswered questions."

"If the Bureau can't explain it, could it be a cause of death that's
never had any previous case?"

"No previous cases?"

"That man died from something that was completely unknown up until now,
something no one's experienced before ― is that possible?"

"Shion! What are you..." Yamase trailed off. His face was pale. Shion
figured his own face must look the same.

"Let's have some coffee, shall we?" Yamase suddenly stood up as if he
couldn't bear the tense atmosphere any longer. Shion hastily stood up
after him.

"Oh, let me―"

"No, I'll do it. You like lots of milk in yours, right Shion?"

"Thanks." Shion paused. "So―but anyone could look at the body and tell
it wasn't an accident, right?"

Yamase turned toward him. His usual gentle face was strangely contorted.

"Yamase-san?"

"Shion, bodies can be modified."

"Huh?"

"I―" Yamase stammered. "Before I started working here, I used to work at
the Municipal Central Hospital. My job was to modify dead bodies."

"Modify―what do you mean?"

"I wasn't planning to tell this to anyone, but..." Yamase hesitated.
"Shion, have you ever seen a dead body before?"

"Once, at a funeral for my grandfather on my mother's side. I saw his
body in a coffin at the viewing."

"How was it?"

"How...? He looked peaceful. Don't they all look like that?"

"You think so?"

"Are you saying they don't?"

Medical technology had made enormous progress not only in the fields of
disease treatment and prevention, but also in the removal of pain.
Technology of the present day could remove anything, whether it be from
accident or illness, ranging anywhere from pain during surgery, to
breathing trouble, severe pain and seizures experienced in the moments
leading up to death. People ended their lives free of suffering, and all
died with peaceful expressions on their faces. That was what Shion had
been told.

Yamase handed him a cup of coffee. He lowered his gaze and bent his neck
to scratch it, as if to avoid Shion's gaze.

"All this about front-line medical technology goes right over my head,"
Yamase said slowly. "But all I know is that... no matter how much
technology develops, it's impossible for everyone to die a peaceful
death. That much I'm sure of." Yamase's face contorted even more. The
hand which held his own mug trembled slightly.

"I worked for a long time in the basement of the Central Hospital. My
job was to modify the bodies that were brought there."

"Yamase-san, so what's this about modifying bodies?"

"It's an easy job. When the body's been confirmed dead and brought down,
I would coat its face with a special chemical and cover it with this
apparatus. And then―"

"Then?"

"Then it would smile. All of them did. They would all look like they
were having some wonderful dream."

Shion almost let out a cry. It was just as Yamase had said. He was nine
years old when he saw his deceased grandfather's face, and he had been
smiling.

"It's almost like he's having a wonderful dream," he remembered his
mother whispering through her tears.

"Of course," Yamase continued, "the majority of people that die don't
need to be modified. They're all people that have been able to get
proper palliative care, and have really died a peaceful death. But it's
still only a majority ― not the entire population. There are a small
number of people, though, that die tragically, their faces all stiffened
up in pain."

"For example―?"

"Huh?"

"What kind of people die like that, Yamase-san?"

Yamase exhaled shortly, and drained the rest of his coffee. "I don't
know. My job was only to coat the faces with the chemical and cover them
with the apparatus. I didn't know why these people had to die with such
suffering and sadness in their faces, and no one would tell me." He
paused. "But― there was this one time, a middle-aged man was brought
in... I usually have to wipe the face before applying the chemical, and
I noticed that the man had tear streaks on his face, and ― and I thought
― maybe he'd been crying right up until he died. I wondered if he'd been
crying the whole time while he was dying. And then I just had this
thought that― maybe this man had killed himself."

"Killed himself? A citizen of this city―?"

"You think it's impossible?" Yamase asked flatly.

"Of all causes of death in the last ten years, suicide has only been
0.05\%. And most have been impulse cases due to temporary psychosis, so
they technically don't even fall into that criteria. According to the
city's statistics, anyway."

"According to what the city has published as statistics, yes," Yamase
rephrased.

Despair did not exist in No. 6. All citizens lead a secure and
hospitable life. There was no starvation, no war, no anguish. Not even
any pain in the moments leading up to death.

\emph{You guys have been programmed to think this holey mess is the ideal
	utopia.} Nezumi had spat these words out four years earlier. Now, Shion
was experiencing its reality word for word. Lost Town was full of people
who had abandoned hope. They had enough to eat, and enough to keep
living. But they had no hopes for the future. Lost Town wasn't the only
place―maybe the same could be said for Chronos. How many people could
die with a real smile on their face, and say they've lived a fulfilling
life?

"Yamase-san, are you saying that the Bureau is manipulating
information?"

"Shion!" Yamase warned, knitting his brow and shaking his head
violently. "Don't say stuff like that out loud. We've been hired by the
City. We've pledged allegiance. We shouldn't be talking about our
suspicions. I don't know what's gotten into me. Forget everything I
said. Just forget it."

"Alright," Shion replied uncertainly.

"Right then, let's get Sampo and the rest moving. Where were the main
regions today?"

"Areas JK02 to ER005. Mainly cleaning up foliage."

"Alright, let's get to work."

"Right you are." They began to tap the control keys for the robots.
Yamase gave a short grunt of pain.

"Yamase-san?"

"Ah, it's nothing. It's just―my fingers are strange."

"Hurt?"

"No, no... it's like they feel stiff..." He stood up unsteadily, and
then suddenly crumpled to the floor, his face in his hands.

"Are you alright?"

"My eyes... I can't see... they're blurry..."

In the midst of reaching out to support Yamase, Shion froze. He couldn't
move. Yamase's hair was turning white. Spots were beginning to spread
over the hands that covered his face.

"Shion... what's―what's happening to me...?"

Frozen in horror, Shion watched as Yamase aged with astonishing speed
before him. He curled up as he lay on the ground, and his back
contracted in violent spasms. He was having trouble breathing. Shion
lunged for the emergency intercom.

"We have an emergency. An ambulance, please. Quickly!"

Yamase coughed weakly. \emph{What was happening? What was going on?} Shion
couldn't believe what was unfolding before him. Everything seemed
surreal. His mind was in a panic ― he didn't know what to do, how to
deal with it. But still another part of him remained unsettlingly calm.
\emph{Observe. Analyze. Watch. Don't take your eyes off of him. Take in
	everything you can and absorb it as knowledge.}

Shion swallowed, and lifted Yamase in his arms. After a few weak spasms,
Yamase's body was still.

"Yamase-san?" His face was unmistakably that of an old man. And it was
no longer that of one who was living. Shion checked his pulse and
pupils. Yamase's body grew colder by the minute. His mouth was open as
if in astonishment, like the man from yesterday.

\emph{Shion, how can this happen? I can't believe it.} Shion could almost
imagine those words tumbling out of his parted lips.

\emph{I have to close his eyes, at least.} Shion pressed his fingers on
Yamase's eyelids. They didn't close. Rigor mortis had already begun to
take its course.

Shion crouched beside Yamase, clenched his fists, and continued staring
at his colleague with whom he was having a conversation only moments
before. Feelings of fear, sorrow, or pain were curiously absent. It was
as if all his feelings had gone numb.

\emph{Observe. Analyze. Watch. Don't take your eyes off of him. Take in
	everything you can and absorb it as knowledge. And memorize it.
	Memorize. Memorize―}

Cessation of respiratory and cardiovascular activity. Decrease in body
temperature. Rigor mortis. Death spots. Dissipation of rigor mortis.
Postmortem phenomena that usually took dozens of hours was taking place
in a mere fifteen, sixteen minutes. It was if he was watching a film on
fast-forward.

Shion watched unmoving, his eyes wide open, biting his lip in
concentration. He could predict what was going to happen next. He was
sweating. A warm bead of perspiration slid from his temple down his
cheek. Its heat reassured him that he was still alive.

\emph{Living people are warm.} You were right, Nezumi. People are warm because
they're alive. Four years ago, you knew this.

A stain appeared on Yamase's neck. It was dark green, almost black.
Shion bit his lip harder. The taste of blood spread inside his mouth.
There it was, it was starting―what was previously unknown, what no one
had ever experienced before. He leaned forward. The stain moved. The
skin over that portion swelled slightly, and stirred.

A buzzer went off. Sampo was sending an Indistinguishable Object signal.
Oblivious to the changes that were happening in the office, it seemed
like Sampo and the rest were going about their cleaning duties as usual.
Shion ignored it. He had no attention to spare. All the nerves in his
body were focused on the stain. His eyes were glued to it, and he
couldn't break his gaze.

Shion let out a muffled cry of horror. He clutched his chest, and felt
his own heartbeat thudding against his palm. He jumped back. An insect
had eaten its way out from under the skin of Yamase's neck, and was
wriggling to get free. It was the same colour as the stain it had come
out of. It had thin silvery wings, six legs, antennae, and a needle-like
ovipositor.

"A bee..."

A bee had just eaten its way out of a human body. How could that―

The insect took flight. He followed it with his gaze, and saw the
Medical Bureau's ambulance pull up in front of the office. A sudden
darkness veiled his eyes.

He was fainting from shock.

The black insect was darting around in his darkening vision. Shion
groaned, and curled up on the floor.

\myspace

Shion awoke to a blinding light stabbing at his eyes. He heard a quiet
male voice speak.

"Awake?"

Light was streaming through the window, and the man had his back to it.
His face was thrown in shadow. The shadow spoke again.

"Get up. I have something to ask you."

It was a voice he'd heard before. Shion came to, and noticed he was
lying on the office sofa. Yamase, wrapped in a white cloth, was being
carried out of the room. It seemed like he had fainted for only a few
minutes.

"Yamase-san."

Shion called the name of his colleague almost without thinking. Yamase's
smiling face crossed his mind. Fragmented memories ― how he loved
coffee, and drank several cups of it a day; his quiet demeanour; his
habit of sheepishly looking at his feet ― all at once burst forth in his
mind.

They weren't particularly close. To Shion, he was just a senior
colleague. He had never confided in Yamase, nor had they ever had a
deeply personal conversation. But Shion had liked Yamase. Yamase never
intruded unheeded into anyone's personal space, but that didn't mean he
was disinterested. He was a good person. But he was no more.

"Yamase-san..." His eyes began to sting. He was tapped lightly on the
shoulder.

"Let's get emotional later, shall we?" The man spoke lazily and without
emotion. Shion's heart jumped unpleasantly.

"Can you explain the situation to us?" This voice, these words. He had
heard them before.

"You're..."

"It's been a while, hasn't it. It's nice to see you still remember me."

It was Rashi, the Interrogations Officer from the Security Bureau. He
had the same gentle tongue and unsmiling eyes as four years before.

"You'll tell us everything you know, won't you?"

Shion found himself nodding automatically. He could feel his mind begin
to unravel slowly. His head and body felt heavy, and his own voice
sounded as if it was coming from far away.

\emph{This is bad.}

A warning signal sounded in a corner of his mind. But he couldn't
regulate himself as well as he could yesterday. Each question that Rashi
asked dragged words forth helplessly from his mouth.

"A bee?" Rashi furrowed his brow. He gazed around the room, and cocked
his head to one side in perplexity. There was no insect, bee or
otherwise, to be found in the room.

"I'm not buying it."

"Check Yamase-san's neck, there should be a scar―" He swallowed his
words. There should be a scar. There should have been one, the same, on
the neck of the man yesterday. The Bureau had investigated that body as
an unnatural death, there was no way they could have overlooked it. They
had noticed, but had told his bereaved wife that it was an accident.
They didn't want the real cause of death to be known ― that was what it
boiled down to.

Shion turned his head to the side, as if to avoid Rashi's gaze. He had
spoken too much. He had divulged everything he knew, which might have
been something that the Bureau intended never to reach outside ears ―
classified information that they were intent on covering up. If that was
the case―

"You used to specialize in ecology, correct?"

"I intended to, but I never did. I have nothing to do with it now."

"And were you interested in the biology of insects as well?"

"Ecology encompasses everything that has to do with interactions of
species with their environment. Insects weren't the only thing I was
interested in."

"Ah, is that so? And specifically, what do you mean in terms of
relationship between organisms and their environment?"

"Well―"

Shion could feel himself breaking into a cold sweat. A thin smile played
on Rashi's lips while he spoke, his words light, his tone
conversational. But his gaze never left Shion once. Two officials of the
Security Bureau came in. One of them whispered in Rashi's ear.
Momentarily, Rashi spoke.

"I hope you won't mind coming down to the Security Bureau for a bit."

"Huh?"

"It's nothing really, we just want to hear more of your story. It'll be
over in minutes. I promise we won't take much of your time if you come
with us."

"I―"

A buzzer sounded. Sampo was sending an Indistinguishable Object error.

"I'm sorry, I have to operate the cleaning robots..."

"Put them away. In any case, you won't get much work done today."

Shion ignored him. He minimized the error display, and switched over to
the camera. A small grey mouse appeared on the screen. It was scurrying
up and down Sampo's arm. Its mouth was open wide, and it was mouthing
something incessantly. Shion brought the earphones to his ear and turned
on the sound sensor.

"Shion." Nezumi's voice flowed through to him. "Get out of there. You're
in trouble."

\emph{What?}

"Get out."

Click. He heard a sound behind him. Shion turned, and found himself
staring down a pair of gun barrels. He couldn't distinguish what model
they were. But he knew that these were no high-tech stun guns, no, none
of that sort ― they were older models, highly effective in the kill.
Sport-hunting hobbyists liked to use these kinds of guns. Shion slowly
flicked Sampo's speaker switch on. Now, Nezumi's end would be able to
hear his voice.

"Are you forcing me under arrest?"

"I guess you could call it something like that. Regardless, you're
coming with us."

"Don't you need a reason to arrest me?"

"A reason? None of that. But if you insist... your bicycle, perhaps?"

"My bike?"

"You were using a bicycle without speed-limiters. That's a breach of the
law, and more than enough reason to put you under arrest."

"What―how―for such a ridiculous reason, without even going through the
proper procedures? Using violence? Is this how you arrest a citizen of
the city? What happens to my rights?"

"A citizen? Rights?" Rashi sneered. A violent chill ran down Shion's
spine.

"You really think you have any of those?"

He could hear Nezumi click his tongue. \emph{Tsk.}

"Guess I didn't make it in time."

Shion exhaled, and began shutting down the operating system. Just before
it turned off, he heard Nezumi's short message ring out clearly.

"Shion, don't panic. I'm coming to help you."

\mybreak

He was right. Don't panic. Calm down. Be of sound mind. He had to buy
more time. Shion relented.

"Please don't use any violence on me."

"We won't, of course. As long as you co-operate with us."

"It wouldn't be any use to retaliate anyway, would it?"

"Is it your policy not to take useless action? There's a good lad, he
knows what he's talking about. It's a waste, really."

"A waste? What is?"

"For you."

"I don't understand what you're talking about."

"You'll know in good time. You've always been smart and quick to
understand, like you were four years ago."

Flanked by two Bureau officials, Shion climbed into the car. Above them
was an expanse of clear, blue autumn sky. The sun was bright. The birds
were chirping. A gentle breeze blew past them. Times of peace and
tranquility they were.

\myspace

The car glided forward.~

"Nice weather today," commented Rashi from the passenger seat, without
turning around. The official sitting on Shion's right side nodded in
response. "It looks like we've been having more warmer days than usual
lately."

Rashi turned to Shion and smiled.

"And yourself? Do you have a car?"

"No. I usually take my bike or walk."

"That's a good thing. Young people like you need to move their bodies
more. By the way, what we're riding right now is a battery-operated car.
Quite comfortable, don't you think?"

"Excellent I would think, if it wasn't for the situation I'm in right
now," Shion replied sarcastically. In means of retaliation, it was the
best he could muster. Rashi shrugged lightly.

"As I was saying, this car runs on fuel-cell batteries. Any idea how
they work? We aren't too well-versed on the scientific side of things,
I'm afraid."

"I don't know much either."

"What sort of things do you know about it?"

"Not much... I mean, I don't really have a lot of scientific knowledge."

The officials on both sides of him moved at once. He was grabbed firmly
by the arms. Rashi's tone changed to that of an interrogator.

"Then just tell us what you do know."

"Like I said, what I know― it's all just general knowledge."

"Such as?"

The conversation was short, clipped and void of frivolity, but Shion
felt a sort of strangling heaviness about it. He felt like someone was
choking him slowly with a soft, damp piece of cloth. He felt nauseous.

"So... through electrolysis, alcohol is separated into oxygen and
hydrogen, and by fusing them together again, energy is―"

"Energy is what?"

"Where are we going?" Shion asked suddenly. He rose, but was yanked back
and shoved into his seat.

"Aren't we going to the Security Bureau? This isn't the way." The Bureau
was located beside City Hall. From the Park Administration Office, one
only had to cut through the park to get there. By car, it was a few
minutes' distance. But the scenery out the window showed him the car was
heading in the opposite direction.

"Where do you think we're going?"

"That's what I'm asking you right now," said Shion testily.

"You're not entitled to ask any questions."

"What―how could you―why―"

"Haven't I told you? You're a top suspect in this case."

"What case?"

"The death that happened today, and the other one from yesterday. You're
on suspicion of murder."

Shion had lost his voice. He could hear the rush of blood in his ears as
it receded from his face.

"You're a dangerous suspect. You have extensive knowledge and an
intelligent brain to put it to use. I could tell just from our
conversation. And to top it off, you're dissatisfied with your situation
and feel a strong resistance against the City. Superior ability and
hostility toward the City. Take either one, and they aren't of concern
by themselves. But you have both. Dangerous, indeed."

"Those are false accusations."

"False? I beg to differ." Rashi's hand extended to a silver button
beside the steering wheel. Shion's and Yamase's voice began to play from
the speakers.

\emph{'Yamase-san, why does the Bureau have to lie about it? And isn't it
	strange that they can't seem to find a cause of death?'}

\emph{'Yeah... this incident is full of unanswered questions.'}

Shion closed his eyes. It was the conversation they'd had only minutes
ago. They were being tapped the whole time. Had a microphone been hidden
in the control panel? But for what purpose?

\emph{'Yamase-san, are you saying that the Bureau is manipulating
	information?'}

\emph{'Shion!'}

Rashi pressed the button lightly again. The voices were cut off. For a
moment, a cold silence fell in the car as if the very air had frozen
over.

"Care to hear a little more?"

"Please... stop... I can't believe this."

"Can't you?"

"I didn't kill anyone," said Shion flatly.

"So you're saying that this \emph{bee} that you were talking about is the real
murderer?"

"Yes."

"Preposterous. A rather contrived story for someone of your
intelligence."

"What reason do I have to kill Yamase-san?"

"That's what we're going to figure out. My guess is that you wanted to
start a commotion."

"―Huh?"

"A commotion. You wanted to start a huge one, enough to shake the very
roots of the city, and bask in its glory. You must have regarded
yourself as some kind of genius fallen upon ill fortune, haven't you? So
you loathed the City for not favouring you as you deserved, and felt
hatred toward its citizens. You believed you deserved more attention, so
you thought of this method of murder, this unnatural death, to take
society by storm. You had the medical and biological knowledge to do it.
It was very well possible that you used some kind of special chemical to
commit murder."

Shion sank deeply into the car seat. All energy had left his body. He
realized it was a trap. He had walked right into its cunning grasp. He
licked his lips. They were parched and dry.

"I see," he said coolly. "So it's all been scripted already. Rather
\emph{contrived} story yourself, maybe even more than mine."

"We'll see how contrived it is once we get through questioning you."
There was a metallic clang. The official on Shion's left had handcuffed
him.

"There's a transmitter on those, and it lets us know where you are. When
we get there, you'll get to take them off." Rashi's words gave Shion an
idea of where he was going. The West Block. The Correctional Facility.
If he was undergoing investigation there, he was sure to be locked up
right afterwards as a convict. In exchange for removing his handcuffs,
he would have a V-chip implanted into him.

\emph{―Nezumi, it's too late. I can't get away.}

He closed his eyes, and took a deep breath.

"There's a good lad. Keep quiet."

Shion remained slumped, and bit his dry bottom lip.

\emph{I'm coming to help you.} Nezumi's voice echoed in his ears. His heart
grew calm. His legs trembled, though not from despair or fear, but rage.
Rage at the people who had tricked him. Nezumi's voice kept that rage
afloat. The car entered Lost Town.

\emph{―Mom.}

"Are you worried about your mother?"

"My mother―what―what'll happen to her?"

"Happen? Nothing. She won't be stripped of her citizenship just because
her son is a convict." Rashi whispered something to the driver. The car
veered to the right. A familiar scenery of the streets came into view.
The car stopped silently at the curb.

"Look."

Rashi pointed. Karan was in the midst of handing a small girl a wrapped
loaf of bread. She said something to her, and the girl nodded. Both
Karan and the girl were smiling. Enveloped in the amber light of autumn,
the two looked as if they were part of a painting, or a scene from a
drama. Shion leaned forward.

"Your mother looks like a gentle lady. Get a good look at her while you
can." Rashi motioned with his chin, and the car began to move. "You may
never see her again."

Rashi chuckled with his back to Shion.

"It's nothing to be so troubled about. Sure, at first your mother will
be shocked, and she'll feel sad. But she'll get over it. That's how life
is. Well, it's not like anything would come of you worrying about her
anyway. Soon you'll find you'll have things more serious to worry
about."

Rashi's words sliced at Shion's heart. His breath caught in his throat.
The rage and rebellion simmering inside him slowly began to dissipate.
He would never be able to return to his his normal life again. He had
been separated from it forever. Seeing his mother etched the feeling of
despair deeper into him.

They had calculated it all. They didn't stop the car near Shion's house
out of pity for him. They had done it to deal him the final blow, the
blow that knocked him down and told him, give up, lose hope, you're
never going back again. It was a cunning and cruel trick to make him
lose the will to retaliate.

"I'm coming to help you. I'm coming to help you."

Shion opened his mouth and repeated the words to himself.

\emph{I'm coming to help you.} Just a short sentence. But Nezumi's voice had
been steady with confidence.

\emph{What did he look like again?} He wondered, and tried to visualize
Nezumi's face. He could only remember a pair of light grey eyes.

\emph{―Will I see you soon, Nezumi?}

"What's that?" Rashi turned around, and furrowed his brow.

"Are you smiling?"

"Smiling? Of course not," Shion replied. "I don't have the courage to
smile in this kind of situation."

"In this situation, huh... you seem rather calm about it. I hope you do
understand exactly what kind of situation you're in right now."

"Almost too well."

"Aren't you calm and collected in spite of that."

"I'm a natural."

"A what?"

"A natural," Shion repeated. "I've been told that by someone once. That
I'm a natural at not getting it."

Rashi stared at Shion in silence. The car was exiting Lost Town and
approaching the western border. It was Shion's first time here, because
regular citizens were not allowed to enter into this area. No. 6 was a
citadel― a wall made of special alloy circled the city and enclosed it.
In most parts if the city, the wall was camouflaged well with trees, but
in the West Block it stood bare. The car bypassed the Access Control
Office.

"Aren't you going to enter the West Block from here?"

"There are two gates. That one was for entering and exiting the city.
The other one is especially for entering the Correctional Facility, it
leads directly into it. The Correctional Facility is a special kind of
facility, even in the West Block. We keep it completely isolated from
all general citizens. I bet you didn't know that."

"No, I didn't."

"You'll find out even more soon enough."

The path narrowed. An increasing number of trees blocked the sunlight.

"Once we're through the woods, there will be nothing but wastelands.
Past the gates it'll be the same. It'll probably be the last time you
see any greenery, so I advise you engrave it into your memory well."

The car stopped.

"What's the matter?" Rashi asked.

"Ah, it's just..." The driver pointed to something in front of them. A
silver-coloured lump was laying across the middle of the road. Slowly,
it raised itself.

"Sampo?" Shion swallowed.

"What's this? What's a cleaning robot doing here?"

"Maybe it has orders to clean the forest area?"

"I haven't heard anything about it."

Sampo was scooping up fallen leaves with his metal arms.

"Keep an eye on the suspect." Rashi ordered the officials, and got out
of the car. He approached Sampo. Sampo swayed, its arms grabbing ahold
of Rashi. Clinging to him, it fell forward.

Rashi gave a short cry, and was dragged by Sampo to the ground amongst
the trees.

"Ah!" The driver raised his own voice in surprise, and opened the door
to lean forward. The next moment, two small shadows darted into the car.
They were two grey mice. In a flash, they each latched onto the throat
of a Bureau official.

"Don't move," a low voice commanded. A person slid into the passenger
seat. A grey cloth covered his head and was wrapped around his
shoulders. From them, a brown mouse sprang onto the base of the driver's
neck.

"These guys have small bombs planted in their bodies. Try anything
funny, and you can count on your heads being blown off."

The driver whimpered in terror.

"Take his handcuffs off. And the three of you, get out of the car."

No one moved.

"Quickly!" he ordered sharply. "I'm impatient. Do you want me to set
them off?" There was a metallic sound from the mice that were latched
onto each throat. Click. Click. Click. The handcuffs fell from Shion's
wrists. The three men tumbled out of the car, bleeding at the neck.

"Nezumi!"

"Greetings later." Nezumi gripped the steering wheel. The car spun
around in a U-turn, and hurtled down the road at full speed.

"Nezumi, are you really going to make them explode?"

"Idiot. You think I would plant bombs into my faithful friends? That was
just to scare them."

"Were those robot mice? They looked just like the real thing. And with
Sampo, how did you―"

"Shut up," Nezumi growled. He yanked the cloth off his head, and threw
it to the backseat. "Wrap that over your head and stay curled up."

"Is this superfibre? Why do I have to wrap up in this?"

"Because I'm going to crash it."

"Crash what?"

"The car."

"What!? Why―"

Nezumi's fist pounded the steering wheel.

"Just shut up, alright? Is asking questions all you're good for?"

"But we can just escape with the car."

"I was planning to, but―"

"But what?"

"It went too well." They were approaching the wall that separated the
West Block from No. 6. The car showed no signs of slowing down. "It
shouldn't have been this easy to rescue you."

"Really?"

"You're naturally dense, you wouldn't know. It doesn't get any more
dangerous when something's gone too well. That's why we're going to dump
this thing. When I tell you to, wrap up in that cloth and jump out of
the car. I'm gonna crash it."

"How about you?"

"I'm used to this kind of thing. No need for the dense boy to worry
about me."

"I can't just leave you!"

The wall was looming closer.

"Get out, open the door!" Nezumi yelled. Almost simultaneously, the
tires screamed as the car screeched to a halt. Shion's body floated up.
The next minute, he was being slammed back against the seat. If it
weren't for its shock-absorbing material, he probably would have broken
a few bones.

"Damnit!" Nezumi kicked the door hard. It didn't move.

"Is it the automatic brake system?" Shion winced at his bruised shoulder
as he asked.

"I disabled that a long time ago. I disabled the alarm system, the
collision sensor system, everything. This car's being controlled
remotely," Nezumi said angrily.

A chuckle resounded throughout the interior of the car. It was Rashi's
voice.

"I won't have you underestimate the Security Bureau. The car that you
boys are riding is actually an escort cruiser, though you might not have
noticed. It's not something you can control so easily."

Nezumi swore.

"I didn't know you had an accomplice. That was something I didn't
expect. It was quite the spectacle, very impressive. Why don't we have a
nice talk, and I can hear all about it."

The car changed directions, and began to move on its own.

"Rather quiet, hmm? Can your friend not talk? Or does talking pose some
kind of problem? Ah, your voice sample must be in the system, which
means you have a criminal record."

"I think \emph{you're} talking a bit too much." Nezumi's hands moved swiftly.
"I'm sorry, but I don't have time for pointless conversations with old
men." Nezumi moved to the back seat and pushed Shion down. "Duck and get
under the cloth. Hold on tight."

"Hey! What are you doing?" There was a note of panic in Rashi's voice.

"See ya, old man. Say goodbye to your high-tech escort cruiser too."

"What―"

There was a blast. A wave of impact slammed into them.

"Get out!" The short command burst at Shion's ear. The door opened. A
gust of hot air swept over them. \emph{Outside. I have to get outside.} Shion
screwed his eyes shut, and leapt into the outside world. He hit the
ground, and rolled. Behind him, he heard an enormous explosion. The car
was on its side, its wheels in the air spinning helplessly.

"Good job," Nezumi whistled. "You rolled pretty well for someone with
such a big head. Not hurt, are you?"

"I scraped my arm pretty badly. You?"

"I told you, I'm used to this."

"What did you do?"

"I destroyed the steering system."

"How?"

"Escort cruisers might be durable on the outside, but they're delicate
on the inside. As long as you set it in the right place, any small bomb
will put it right to sleep."

"You seem to know a lot about it."

"Like I said, I'm used to this. Right, now to get out of here. Can you
run?"

"Of course."

They emerged from the wood to see several Security Bureau cars
approaching in the distance. The area had probably been put under
emergency alert.

"Throw your ID card away," Nezumi ordered quietly. "Hurry up, there's no
time to waste. That thing is only going to be a danger to us."

Shion knew. His ID card carried all his personal information, and it was
connected to and stored in the city's administrative computer system.
The computer could instantly pull up his latest information, or pinpoint
his location from the weak radio waves that his card emitted. Carrying
his ID card was like waving a large flag and telling everyone where he
was. It was a dangerous device for anyone who was on the run, in hiding,
or aiming to go underground. Nezumi was telling him to throw it away.
But― once let go, he would never be able to get it back again. He would
be throwing his whole life in No. 6 away. A card was needed for
everything from shopping, bill payments, and communication to entering
and exiting the workplace or school, and using public transportation.
Those who couldn't prove their citizenship in the city were not allowed
to live there.

"Throw it away," Nezumi repeated, in the same low voice.

If he didn't toss it, there was no chance for them to escape. But if he
did, he would never be able to return. The pair of grey eyes were fixed
on him. They were neither clouded in panic, nor glinting in challenge.
They were calm, and unreadable. Shion let go of his ID card. A grey
mouse appeared, picked up the card in its mouth and disappeared again
into the undergrowth.

"He'll get rid of it for us. That should keep the Bureau busy for a
while trying to find our location. Not much of a distraction, but it
should buy us some time. Let's go."

A Security Bureau car turned right and disappeared into the forest. It
had picked up the radio waves emitted by the ID card. They ran in the
opposite direction.

"Hurry. Once the Bureau switches to their satellite surveillance system,
they'll be able to see everything on land. We have to get away while
they're still on the tail of that ID card."

"Where? How―?"

"Well for starters, we'll use that." A small truck was parked up against
a beech tree. It was a Park Administration truck. A cleaning robot was
loaded on the back.

"Sampo― no, that's Ippo\footnote{one step; first step}."

"Yeah. They said they wanted to help you and wouldn't listen, so I
brought them along. They ended up being pretty useful."

The truck began to move.

"Nezumi, this area's probably under high alert now. If we keep hanging
around here without a card, they'll find us out."

"We have a card."

"Where?"

"He has it," Nezumi jerked his chin at Ippo.

"Ippo? Oh, right." Robots were also required to be registered with the
city. Robots like Ippo and Sampo, which were used by city organizations,
were registered in detail according to their various uses, and implanted
with a chip.

"His chip should get us through the inspection system."

"But Ippo's chip only shows that he's a cleaning robot. If he's found
roaming an area that has nothing to do with it, they'll get suspicious."

"We're roaming an area that has \emph{everything} to do with it."

"Huh?"

They were approaching a pair of silver gates. The moment they passed
through, they would be automatically scanned, and if the contents of the
chip deemed them unfit to pass, the gates would close, and the truck
would be forced to a halt.

The truck sped through the gates without slowing down. The hazard lamps
at the gate remained unlit. Shion let out a breath. Nezumi chuckled.

"Don't get worked up just yet. This is only the beginning."

"Sorry, I'm not used to this kind of thing."

"You'll get used to it in no time. Then you can sit back and enjoy the
ride."

"This isn't really my idea of 'enjoyable'," Shion muttered.

"Oh, really? The look on your face says you're enjoying this quite a
bit."

Shion sighed deeply again, and gazed at Nezumi's profile.

"Admiring my good looks?"

"No, I just noticed you've gotten taller."

"So have you. It's been four years. Our four years is a long time. Gotta
expect some changes. It would be unnatural not to have changed at all."

Four years was a long time. For Shion, it was long and turbulent. But
compared to the dizzying events of these past few hours, he felt like
they were the most peaceful days of his life. A weariness overcame his
body. Nezumi smirked.

"So have you noticed?"

"What?"

"I'm taller than you."

"Lies," Shion objected.

"It's the truth. What have you been eating? You're like a twig. I don't
know how you would be able to get naked in front of your lover with a
body like \emph{that}."

"That's none of your business," Shion replied irritably. "Have you even
seen me naked? Don't go making things up."

"What if I said I have?" The cloth wrapped around Nezumi's shoulders
shook as he continued to laugh. Shion had treated a wound on that same
shoulder four years before. Those shoulders were now broader and more
muscled. His once-long hair was shorter, just covering his ears, and his
jawline and neck were still slender, but not pitifully thin. He carried
no remnant of the weakness that stirred Shion's protective instinct four
years ago.

"Nezumi, have you been keeping watch on me?"

"What're you talking about?" said Nezumi innocently.

"Don't play dumb. You appeared right there as if you knew this was going
to happen to me. What's going on? Were you keeping me under
surveillance?"

"Now, don't think too highly of yourself. I don't have that kind of time
on my hands."

"Then explain why."

"You're always like that, aren't you," Nezumi said. "You can't take any
action unless you understand everything in your head. You need an
explanation and interpretation for everything."

"What do you know?" Shion replied angrily. "Don't act like you know
everything about me. I need to find out why this happened― what's going
to happen. I can't move in this confused state."

The truck came to a halt. Shion was grabbed by the collar and shaken
violently.

"You're going to move," Nezumi hissed. "Don't ever let me hear you
whining about not being able to move again. Those guys don't see us as
human beings. They can get rid of us as easily as crushing an ant under
their feet. You remember that."

Shion caught his breath, and stared into Nezumi's face. His words
clicked into place like puzzle pieces.

\emph{Rights? You really think you have any of those?} The Security Bureau's
Investigations Officer Rashi had said those words, not moving a muscle
on his face. What he had said in meaning was that he could dispose of
Shion as easily as stepping on an ant. Wipe him off the face of the
earth.

"Get out." Nezumi opened the door. "We're walking from here."

The vacated truck made a U-turn and slowly coasted along the way that
they had come. It had switched to auto-pilot and was returning to the
Park Administration Office. On its loading deck sat Ippo, and for a
moment, it looked like its head was bowed in dejection.

They were standing inside what doubled as a waste disposal plant and
Refuse-derived Fuel (RDF) factory. Here, all the garbage gathered from
the city were sorted into those to be turned into RDF, those to be
forwarded to other recycling facilities, and those to be discarded as
waste. 80\% of No. 6's energy supply came from solar power. In Chronos,
every house was equipped with solar panels and its own thermal storage
system. In Lost Town, however, it was more common to use the cheaper
RDFs. RDFs were blocks of solid fuel, about the size of an adult thumb.
Once burned, they emitted a faint odour, which blanketed the town.

"I see. It would be no problem getting into a waste disposal plant with
a cleaning robot's chip." If it had been a nursing robot or pet robot,
they would not have been able to pass.

"Nezumi, was this all part of your plan when you brought Ippo and them
along?"

"More questions?" Nezumi's shoulders hunched slightly in exasperation,
his back to Shion, who trailed behind. Shion noticed that there was now
a grey mouse sitting on Nezumi's shoulder.

"If I had them with me, I wouldn't look suspicious driving around the
city. The inspection system wouldn't catch me as long as I was heading
west in the direction of the waste disposal plant. They were pretty
useful, I'll say. The transport truck was kind of slow, which pissed me
off. But those old guys took a detour to your house, right? That bought
me a little time. But..."

"But?"

"But I would have wanted to get away on the Security Bureau car," Nezumi
sighed. "Well, that just shows you can't get everything you want. Watch
it, things are gonna get a little rough from here."

"Huh?"

There was an explosion. Shion turned to see a cloud of white smoke.
Nezumi furrowed his brow.

"The truck got destroyed at the gate."

"Which means Ippo's chip was read and―"

"Yeah. They must have sent out a destruction order to all the gates.
It's because we left that other robot behind. They figured us out."

\emph{―So Ippo and Sampo are both gone.}

Shion was suddenly grabbed by the wrist.

"They'll find out soon that we're in here. We're gonna make a run for
it. Hurry."

His grip was so strong that Shion's fingers began to go numb.

"Nezumi, it hurts."

"Shut up. Keep close to me."

"I get it, let go. You're gonna break my wrist."

He heard Nezumi \emph{tsk} in frustration.

"That's the problem with delicate little boys like you."

"I'm not a delicate little boy," Shion said indignantly. "I'm different
from four years ago."

"Are you? You know, you can be really irritating sometimes. You might
get killed at any time, you understand that right?"

"Yeah."

"Lies."

"I'm not lying."

Nezumi's tone grew harsh.

"Then what was that face back there, huh? Is this the time to be feeling
sorry for those robots? You don't understand anything. You're just an
oblivious little boy." Nezumi's fingers dug in harder. The grip on his
wrist tightened painfully. Shion gritted his teeth and bore it silently.
He couldn't stand to let himself whimper pitifully after all that Nezumi
had said.

Nezumi's fingers withdrew from his wrist.

"Keep up with me if you don't wanna die. Stay close, no matter what."
Nezumi broke into a run. The waste disposal plant was deserted. There
were surveillance cameras scattered throughout, but most were older
models and didn't seem to be doing their job very well. Shion guessed
that they probably didn't need them because no one would think of
sneaking into the waste disposal plant in the first place. Nevertheless,
Nezumi combed the path cautiously as he searched for a route that kept
them out of view of the cameras.

An enormous funnel-shaped disposal machine was giving off a steady hum.
Waste that could neither be recycled nor used as fuel were turned into
dry chips here to be sent to the incinerator. Wastewater dripped from
the spout of the machine into the pool below. The water flowed slowly
toward the filtration facilities outside. It was murky, like a river
after a bout of heavy rain. But in this river there were no living
things. As they descended the stairs and drew closer to the water, an
acrid smell assaulted Shion's nostrils. The floor beneath their feet was
coated with slime, and threatened to trip him up any time. Nezumi
stopped, and tossed something at Shion.

"Goggles?"

"Yup. They have infrared sensors, so you should be able to see even in
this water."

"In here?"

Nezumi pointed at the sewage. "Happen to like scuba-diving?"

"So we're diving in here, huh...."

"That we are."

Shion took a deep breath. The odour filled his lungs. Without another
word, he put on the goggles.

"Wow, you're picking up quickly," Nezumi remarked in mild amusement. "I
thought you'd whine and stamp your feet."

"I don't wanna die," said Shion firmly. "I'm not going to be stepped on
like some ant. I'll do anything if it'll save me, and that includes
diving into wastewater too."

Nezumi turned to Shion and gave a slight smile.

"Then follow me."

"Of course."

The low hum of the machine stopped. The ceiling lights lit up at once.
The sound of footsteps could be heard above them.

"They're coming." Nezumi extended a hand to the river of sewage. A mouse
scurried down it and leapt into the water.

"He'll be our navigator. Try not to splash. Get into the water slowly."

Shion did as he was told. He sucked in a deep breath before going in.
Just before he hit the water, an image of his mother's face crossed his
mind.

\chapter{Of fathomless terror}

\lettrine{T}{he flow} of sewage was faster and deeper than what Shion had expected.
Indiscernible objects floated past his face. Once in a while, something
would cling to his goggles and block his vision. He could smell an odour
unlike anything he had smelled before. Amidst the overarching smell of
rot was a mix of sickly sweet scents and harsh odours that stung the
nose. In this brownish murk, he could barely follow Nezumi, who swam in
front of him. And more than anything, it was hard to breathe. His heart
thudded, and his chest strained painfully.

Nezumi drifted to the side, and pointed at a handle that was attached to
the wall. Shion reached out and grabbed it. Together, they turned it and
pulled as hard as they could. A round opening appeared.

He couldn't breathe. He was at his limit. His consciousness was fading
away. The next instant, he was sucked into the hole. He was pulled
along, pushed up, and thrown out on dry land. His body was slammed
ashore, and he could feel the shock from it tingle to his toes. But he
no longer felt like he had a wet cloth over his face. He could breathe.
He felt a momentary relief, and then was overcome with a fit of
coughing. He felt nauseous, and the inside of his mouth felt sticky.
Shion yanked off his goggles and closed his eyes. For several moments,
he couldn't move.

"It's a little early for bed-time," Nezumi quipped, but his breathing
was laboured as well. Shion opened his eyes, and saw a bare concrete
surface.

"Where are we?"

"In the sewage pipes. Artifacts of the 20th century. Maybe not
artifacts, since they're still being used." Nezumi shook his head
vigorously from side to side. Water droplets flew from his hair. "When
the amount of sewage goes over capacity, they open that door back there
to flush it down these pipes."

"They flush sewage down here? Without filtering it?"

"Yup. Your beloved City tends to do that sometimes."

"Where does it go?"

"The West Block."

"So they flush dirty water― how could they..." Shion was at a loss for
words. Nezumi stood up.

"The West Block isn't part of the city to him. It's in the margins. He
probably only sees this place as some kind of garbage dump."

"He?"

Nezumi was standing still, staring unblinkingly before him. At the end
of his gaze was the sewage outlet that they had just been washed out of.
Sewage still trickled in thin streams across the concrete.

"Let's go." Nezumi bent down to scoop up the mouse scurrying about his
feet, and turned his back to Shion. Shion stood up hastily. He still
felt nauseous, but he had some strength left in his legs to stand. \emph{I
	still have enough strength. It'll last me. I'll be alright.} Shion
mentally encouraged himself. On Nezumi's shoulder, the mouse that had
been their navigator cheeped amiably.

"Ah!" Shion brought a hand to his neck. He felt something faintly odd.
On the base of his neck, there was a small part that felt numb. Shion
felt the area with his fingers. There was a pea-sized blister growing,
and it was itchy. He scratched it lightly. A chill wind blew through the
centre of his body. Shion could feel his heart contract.

This gesture ― scratching the neck ― he had seen someone do this before.

"Yamase-san." Yamase's image floated up clearly in Shion's mind, pouring
coffee, making conversation, always scratching his neck throughout.
"Don't tell me―"

Nezumi turned around.

"What's wrong?"

"No, nothing."

"You better not be whining that you can't walk anymore."

"On the contrary," said Shion, "I could do with a little more exercise.
Want me to piggy-back you while I'm at it?"

"Nice of you to offer, but no thanks."

The mouse on his shoulder was chirruping. Shion walked faster to catch
up with Nezumi.

He was thinking too much. It was just a blister. The scrape on his arm
and his bruised body were much worse than this. It was a blister, for
goodness sake. Just a blister....

"Why the serious face? Missing your mama?"

"My mother..." Shion murmured. "Nezumi, do you think I'd be able to get
in touch with her?"

"Forget about it."

"How are you so sure?"

"You know well enough. Right now, your house is probably being searched
top to bottom by the Security Bureau, down to the contents of your
garbage can. Unless you have telepathic powers, there's no way you can
get in touch with her."

"I guess you're right."

\emph{―I'm sorry, mom.} He could only apologize. \emph{―I'm safe. I'm alive. So
	please―} He didn't want her to despair. He didn't want her to grieve.

"Bullshit," Nezumi spat.

"What is?"

"You. You're full of it."

It was the first time Shion had been insulted to his face.

"What do you mean?"

"What I'm saying is that you're full of bullshit for carrying this
baggage, this crap, like it's the most precious thing in the world."
Nezumi narrowed his eyes and fixed Shion with a hard gaze. His eyes were
piercing, and filled with an emotion almost leaning toward animosity.

Shion opened his mouth to question him further, but Nezumi had suddenly
begun to scale the wall. Upon a more careful look, Shion could see that
there was a rusted metal ladder fixed to it. When he emerged at the top,
he was greeted with an evening sky. He was above ground again. The sky
was painted vividly in the colours of the sunset, and a chilly air
settled upon him.

The place looked like an entrance to the West Block. In the distance,
the outer walls of No. 6 glittered as it reflected the setting sun.
Because of the West Block's lower elevation, No. 6 loomed even larger
before them. It was breathtaking to see the sprawling city encircled by
shining walls. Shion even thought there was a sort of godly air about
it.

Nezumi began to walk in the opposite direction. They emerged from a
sparse wood and soon came upon the ruins of a house. There was smoke
rising out of it, and voices could be heard inside.

"Are there people living in there?"

"Lots of them," Nezumi replied.

Past the ruined house were a row of several barracks.

"This way." Shion was dragged by the arm to another ruins of a building.
This one looked like it had been a warehouse before. The building had
been quite spacious, but half of it had crumbled away into rubble.

"We're going underground again." Nezumi pressed a section of the wall,
and it soundlessly moved aside to let them through. Beyond, there was a
flight of stairs made of bare concrete like those in the sewage tunnels.
The mouse bounded down the stairs. At the foot of them was a door.
Inside, it was pitch black. There was a click, and the room was bathed
in dim light.

Shion caught his breath and was rooted to the spot.

There were mounds and mounds of books, piled precariously high. Most of
the room was buried in them.

"Are these all... books?"

"Do they look like food to you?"

"I've never seen this many."

"Let me guess, you've only read off electronic paper before."

"Yeah, well, not really, but... but wow, this is amazing."

"And to take another guess, you've probably never read Molière, Racine
or Shakespeare before. And you probably don't know anything about
Chinese classics or myths of the Aztecs."

"I don't." Shion didn't argue otherwise. He was too overwhelmed.

"Then what do you know?" Nezumi asked, running a hand through his wet
hair.

"Huh?"

"What have you studied up until now? Systematic knowledge, front-line
technology, how to decode specialized scholarly papers, and what else?"

"A lot else," Shion replied indignantly.

"Like what?"

"How to bake bread, how to make coffee, park maintenance and cleaning...
not to mention, now I know how to scuba-dive in sewage."

"You forgot 'how to reject someone when she asks you to have sex and
you've only ever thought of her as a friend'. You didn't do a great job
at it, though."

Shion raised his chin defiantly and glared at the pair of grey eyes.

"If you have time to be making fun of me, will you let me wash up?"

"I'm first." Nezumi pulled a towel from in-between some books, and
tossed it at Shion. "Don't be mad," he said. "What I actually meant is
that you've come pretty far since four years ago. You've learned a lot
more useful things other than how to make cocoa."

"I'm humbled by your kind compliments."

"Hey, really, don't be mad."

Nezumi disappeared into the pile of books. Momentarily, Shion could hear
the muffled sounds of a shower. He took a good look around the room.
There were bookshelves on every side, and they were filled to bursting
with books. They didn't look like they were sorted in any order, and
books of all sizes were shoved haphazardly into open spaces on the
shelves. Shion felt from them the same kind of hustle and bustle that he
would from a crowded train station. The faded carpet looked like it had
once been some shade of green, and it was also covered in piles of
books. Nestled amongst them was a bed. There were no windows. There was
no kitchen, and no signs of other furniture.

\emph{Cheep cheep.}

A mouse squeaked at him from atop a book. Shion took the book in his
hands, and flipped open to a page. He smelled the faint scent of paper.
He remembered, long ago, he had smelled the same thing. He was sitting
on top of something soft and warm― his memory wavered. He couldn't
remember it well. The mouse scurried up to his shoulder. It twitched its
whiskers, and chirruped persistently.

"You want me to read this?"

\emph{Cheep cheep.}

There was a bookmark in the middle of the book. Shion turned to it, and
began to read aloud.

\poem{Here's the smell of the blood, still. All the perfumes of Arabia\\
	will not sweeten this little hand. Oh, oh, oh!\\
	―What a sigh is there. The heart is sorely charged.\\
	―I would not have such a heart in my bosom\\
	for the dignity of the whole body.}

Another small mouse had appeared at Shion's feet. It had charming
grape-coloured eyes. The brown mouse that had been sitting on the book
nodded its head vigorously as if to urge him on.

\poem{To bed, to bed, There's knocking at the gate.\\
	Come, come, come, come, give me your hand.\\
	What's done cannot be undone.\\
	― To bed, to bed, to bed!}

Shion felt a presence behind him, and turned around. Nezumi stood with a
towel hanging around his neck. He gave a deep bow.

"To the showers, if it so pleases your Majesty. Your change of
adornments awaits you here."

"Nezumi, this book―"

"It's Shakespeare. \emph{Macbeth}. Ever heard of it?"

"Only the title."

"I figured as much."

"Are all these books classics?"

"Nay, your Majesty. We also have introductory books to ecology, and
scientific journals to please your fancy."

"Are these all your books?"

"Is it interrogation time again?" Nezumi said exasperatedly. "Run along
and take a shower, and then I'll give you something to eat." He ended
abruptly, and obstinately turned his head aside.

\myspace

The shower was old, and it was difficult to control the temperature. The
flow was punctuated with bursts of frigid water, but for Shion it still
felt nice. It had been a long time since he enjoyed a shower this much.
The itch on his neck had miraculously disappeared as well.

\emph{―I'm alive. I've been saved.}

Shion thought to himself as he let the hot water run over his body. He
didn't know about tomorrow. But he was alive right now, and was well
enough to take this shower.

\emph{―I didn't thank him yet.}

He had been rescued, and Nezumi had risked his life to save him. But not
a single word of gratitude had escaped his lips so far. Realization set
in. Soon after exiting the bathroom, one of the mice came scampering up
to him again.

"He's taken a huge liking to your reading." Nezumi was stirring
something in a pot over the kerosene heater. There was steam rising from
it, and it gave the room a feeling of homey warmth.

"Oh!" Shion suddenly exclaimed. He remembered now, what was behind the
nostalgia and warmth he felt when he opened the book.

"What? What're you shouting for?"

"No, I just remembered. A long time ago, my mother used to read to me."

"She read \emph{Macbeth} to you?"

"Of course not. I was really young then. I remember sitting in Mother's
lap, and she'd read to me." \emph{What kind of story was it again?} The page
was being turned slowly. Karan's voice echoed in his ears, first high,
then low; subdued, then full of strength. He could feel the warmth of
her body. He could smell the scent of paper.

"You're going to destroy yourself," said Nezumi quietly. His voice was
cold.

"What?"

"I've said this before. Carry all this useless baggage, and one day
it'll be the end of you. It'll weigh you down until it squashes you
flat."

"Useless? Like what?"

"Memories. Attachments to being a citizen of No. 6. Your comfortable
life, your overestimation of your own skills, your misconceptions of
being some kind of chosen one, pride. The list goes on forever. But the
worst is your mother. Do you have some sort of Oedipus complex? If
you're being haunted by your mother that much, goodness knows what
you're going to do next. Maybe you'll start saying you want to go back
to the city to see your dearest Mama."

It had touched a nerve.

"Is it a useless thing to think about my parents?" answered Shion
tensely. "I know what kind of situation I'm in right now, and I know
there's no way to get in contact with my mother. But I'm free to think
about her, at least. That's not something for you to say anything
about."

"Throw it away." Nezumi's voice has turned even icier, and had almost a
metallic ring to it. "Throw away useless feelings like those."

"Why― Why are you saying..." Shion said in disbelief.

"Because they're dangerous."

"My feelings? Dangerous?"

"Back there, you threw away your citizenship card because it was a
danger to us. So are feelings for other people. You get dragged around,
pulled this way and that, and before you know it, you're in dangerous
territory. Your mama, papa, your grandma, whoever― they're all strangers
now. There's no emotional room in you to be concerned about strangers.
Your hands are full enough trying to keep yourself alive."

"And that's why I should throw everything else away?"

"Toss it. Cut yourself away from all the baggage you've carried until
now."

Shion clenched his fists at his sides. He took a step closer to Nezumi.

"Then what about you?"

"Me?"

"Why did you help me, then? I'm just a stranger, but you stepped into
dangerous territory to save me. You're not exactly practising what you
preach."

"Some personality you've got," retorted Nezumi. "If you really feel that
you've been rescued by me, why don't you try to be a little more modest
when you say things?"

Nezumi's hand extended to grasp Shion's collar. He was pushed against
the bookshelf.

"I owe a debt to you," his low voice hissed at Shion's ear. "Four years
ago, you saved my life. I'm paying back that debt. That's all."

"Then you've paid enough. Too much, even." Shion gripped Nezumi's wrist
to pry it away from his collar. But Nezumi's taut muscles showed no
signs of relaxing.

"Let go."

"Make me, little boy."

"I'll bite your nose off." Shion clicked his teeth. There was a split
second of hesitation. Shion didn't miss it. He slid a hand around the
back of Nezumi's neck.

"Biting noses off is my specialty."

"Huh? Wait a second, that's dirty―"

"I forgot to mention, over these past four years, I've also learned how
to fight."

"Hey, knock it off," Nezumi said nervously, "biting is the worst―whoa―!"

Nezumi lost his footing, and the two fell flailing into the sea of
books. Pile after pile toppled over, and books rained down on them from
above.

"Ow," Nezumi grimaced. "This is the worst. I think I hit my head on an
encyclopedia.... Shion, you alright?"

"Yeah... what's this? \emph{Chumayel's Chilam Balam}?"

"It's a Mayan spiritual text ― a story about gods and humans. You
probably wouldn't be interested in it." Nezumi smiled wanly as he began
to stack the fallen books.

"What's that supposed to mean?"

"It's true, isn't it? Have you \emph{ever} had any interest in other humans, or
gods, or tales before?"

Humans? Gods? Tales? He had never thought deeply about any of those. Not
once. But that was before.

Shion gazed all about him, and breathed in the warm scent that filled
the air. Here was a world that he didn't know. In the days to come, what
would he see, hear, learn, and ponder? His heart raced, but he didn't
know why. For a single moment, his soul had danced with an anticipation,
much like the feeling of seeing the ocean for the first time. Then he
thought of the look he must have on his face. He felt embarrassed for
letting it show, and not wanting Nezumi to see, he bent down and
nonchalantly picked up a book laying at his feet.

"What's this?"

"A collection of Hesse's poems," Nezumi replied.

\poem{My soul, you frightened bird,\\
	Over and over you must ask:\\
	When after so many turbulent days\\
	Comes peace, comes calm?}

"―Heard it before?"

"No."

"I figured as much."

"Don't ask if you already know," said Shion sourly.

"It's your job to learn it if you don't know."

"And these aren't useless things?"

"It'll come in handy one day," Nezumi said casually. "Anyway, enough of
that, the soup's gonna get―" Nezumi swallowed his words. His eyes
widened.

"What's wrong, Nezumi?"

"Shion, your hand."

"Huh?"

"Your hand... when did those spots..."

Shion's shirt sleeve was rolled halfway up his arm. There were dark
spots were beginning to spread over its bare skin. They had not been
there when he was taking a shower. They had definitely not.

"What? What is this?"

He was screaming. At the same time, he felt a vicious pain pierce his
head.

"Shion!"

The pain came in waves. They receded for a moment, then attacked,
bearing ruthlessly down on him. His fingers stiffened. His legs began to
convulse.

"Shion, hang in there, I'll get a doctor―"

Shion willed his uncooperative body to reach as far as it could. He
grabbed ahold of Nezumi by his clothes. There wasn't enough time. It was
useless to call a doctor.

"What should I do? Shion, tell me what―"

"My neck..." Shion said weakly.

"Your neck?"

"The blister... cut it open..."

"But I don't have any anaesthetic."

"I don't need any..." he grimaced. "Hurry..."

He was fading out of consciousness. He could feel his body being lifted.
\emph{Don't pass out. If you do, you'll never wake up again.} He didn't know
what made him feel so strongly, but he was almost sure of it. The pain
ebbed away for a short while, and an image drifted into his mind of
Yamase as he collapsed to the ground and lay still.

\emph{―But Yamase-san didn't suffer.}

He didn't roll around in pain. He aged instantaneously, and passed away
like a withering tree. Yamase's symptoms were different from his. \emph{Maybe
	that means I still have a chance―}

His brain was pierced by smouldering red needles. They were countless,
and came from all directions. His body writhed in pain that he had never
experienced before. His own screaming turned into scorching splinters
that stabbed through him. He began to sweat profusely. He felt a strong
wave of nausea. Blood and stomach fluids welled up inside his mouth, and
spilled over his lips.

\emph{It hurts, it hurts, it hurts.}

Shion no longer wanted to be saved, or to be spared death. He wanted to
be released from this pain, this suffering. He didn't need to open his
eyes. He didn't need to live. He wasn't asking for much. He just wanted
to be released―

He felt like someone had grabbed him by the hair from behind, and was
dragging him into the darkness. He felt relieved. All he had to do was
lend himself to it, and he would be taken to a better place. He would
finally be able to sleep.

A thick, bitter liquid was being poured into his mouth. It was hot. It
slid down his throat, and Shion could feel himself rise up out of the
darkness. But it also meant that he was being pulled back into the
throes of suffering.

"Keep your eyes open." A pair of grey eyes were peering into his face.

"Nezumi... I can't take it..." Shion implored faintly. "Let me go..."

He was slapped sharply across the face.

"Don't bullshit me. You're not going anywhere. Drink up." The strong and
bitter liquid was forcefully poured into his mouth again. The darkness
was lifting. Weak pulses of pain throbbed in his head.

\emph{Nibble nibble nibble... nibble nibble...}

Shion thought he heard a sound― or was it a hallucination? It was the
sound of his brain being eaten alive. There was a mass of countless
black little insects. They crawled all over his brain, making nibbling
sounds,

\emph{Eating. Eating. Eating.}

Was it a hallucination? Or was it... it hurt terribly. He couldn't bear
it. And he was terrified. A scream tore through his throat.

"That's it. Yell. Don't give up. You're still sixteen. It's too early to
throw in the towel just yet."

Shion felt the strength leave his body. He felt heavy, as if he was
being tied to a lead weight. He felt suffocated. But the pain had
receded just a little.

"Keep screaming. Stay conscious. I'm going to cut it open."

There was a silver scalpel in Nezumi's hand.

"I don't have anything fancy like an electronic scalpel, just to let you
know. Don't move."

Whether it was because half of his nerves had gone numb from severe
pain, or because all the strength had left his body, he didn't know, but
Shion didn't move a muscle. He couldn't move.

There were three mice, sitting side-by-side atop a pile of books. Above
them, a round clock was hanging on the wall. It was an analog clock.
Tick, tick, tick. He could hear its sound. It was his first time hearing
the sounds of time passing by. A second passed, then a minute. Time
engraved itself. It passed, gentle, meandering, and vague. The world
before him blurred. His cheeks were hot. A tear slid down, touched his
lips, and was absorbed, still hot, into the sheets.

"It's over." Nezumi let out a long breath. Was the metallic clink the
sound of the scalpel hitting the floor?

"The bleeding isn't too bad. Does it hurt?"

"No... " rasped Shion. "I just wanna go to sleep..."

"Not yet. Hang in there for a little more."

Nezumi's voice faded away. Shion could only hear the sound of the clock
ticking.

"Shion."

He was being shaken.

"Keep your eyes open. Just a little more―please―open your eyes."

Shut up, he wanted to say. \emph{Shut up, shut up. A little more? How long is
	a little more?}

"Don't give me this shit. You put me through all this trouble― you can't
just go off on your own. Shion, you know what that means? Your mama's
going to cry. What're you gonna do about that girl, huh? Safu, or
whatever her name is. Have you ever even slept with a girl before? What
a waste it was to turn down that invitation."

\emph{Shut up. Stop talking. Just stop....}

"You don't know anything yet. About sex, or books, or how to fight
properly. And you still think you don't need to go on living? Shion!
\emph{Open your eyes!}"

He opened his eyes. He saw four pairs of eyes staring back at him. One
pair was grey, and they belonged to a human. The other three pairs were
grape-coloured, and belonged to the mice.

"There's a good kid. I'll praise you for that."

"Nezumi..."

"Hm?"

"I... didn't get your name..."

"My name?"

"Your real... name..."

"Well, there's one more thing you don't know. I'll tell you when you
recover completely, and that'll be your get-well present. Look forward
to it."

He was fed the bitter liquid several more times. He drifted off to sleep
only to be woken up again. Shion felt like he had repeated this
countlessly. He broke into a fever. He perspired heavily, and vomited
again and again. It felt like all the moisture in his body was being
wrung out of him.

"Water...."

He pleaded repeatedly, and each time, a cool draught watered his throat.

"It tastes good..."

"Doesn't it? The world's not such a bad place after all." Nezumi's hand
slowly caressed Shion's hair.

"It's alright now. Go to sleep."

"Can I...?"

"Yeah. You're past the worst of it. You've won. That's quite something."
The fingers that stroked his hair were gentle, as was the tone of
Nezumi's voice. Relief washed over his body. Shion closed his eyes, and
dropped off into a slumber.

\mybreak

With a hand still laid on his hair, Nezumi was checking Shion's
breathing as he slept. It was a little weak, but relaxed. It was not
erratic.

\emph{―You made it through.}

It was quite something. He wasn't exaggerating out of politeness or
encouragement. Shion housed a lot more vitality than his looks gave
away. It was a vitality that was tenacious and strong. Nezumi gazed at
Shion's sleeping face― exhausted and weakened, but still breathing
regularly nonetheless― and realized how tired he himself was as well. He
was mentally, not physically, exhausted. He could neither understand nor
come to terms with what he had just experienced. A sense of unease
consumed his mind and made his very blood tingle.

\emph{―What's happening in there?}

No. 6. Something was beginning to brew in the interiors of what they
called the Holy City. Something that exceeded the depths of human
imagination was being born, and developing slowly but surely. Nezumi dug
into the very back of a shelf and pulled out a petri dish. It contained
something he had removed from under Shion's skin when he had cut the
blister open.

\emph{―I can't believe this.}

Yes, unbelievable things happened sometimes. Reality betrayed people
almost too easily, and yanked people's lives at whim in unexpected
directions. At times, it flung them to the depths of despair. It was
cruel and violent. Absurd, even. It couldn't be trusted. Anything could
happen at any time.

Nezumi knew it well. But he couldn't help being perturbed by this
reality. Was it possible for something like this to happen? ―But the
truth was that it had already happened. It was something that couldn't
be brushed away, and he couldn't turn a blind eye to it now.

Nezumi returned to Shion's bedside. He lightly stroked Shion's hair
again.

\emph{―When you wake up, will you be able to believe this reality?}

Would he be able to handle it? Here was a boy who had been cradled and
sheltered in the Holy City's core until the age of twelve. Until
sixteen, he lived in Lost Town ― the outskirts of the city, but still
part of it nevertheless ― and as a citizen, he was treated as such.
Would someone who had been housed in such a protective shell be able to
handle reality? Was he strong enough?

\emph{―Probably not weak enough to be crushed, though.}

But he didn't know. He didn't know how much strength or weakness resided
in the boy sleeping quietly before him. Whether he would withstand it,
or collapse ―Nezumi didn't know. But Shion had survived, and that was
another reality. To survive, you had to sink your teeth into Life and
hold fast. No matter if it was unsightly or harsh ― those who desired
Life most greedily were the ones that survived. Nezumi, from experience,
was painfully aware of this fact. The boy before him possessed that
avarice. It was far more difficult to survive in an unsightly manner
than to die a beautiful and heroic death. It also held much more value.
Of this fact as well, Nezumi was painfully aware.

\emph{―You'll be alright.}

Nezumi moistened Shion's parched lips with water. Then he quietly opened
the door and slipped outside. Dawn was breaking. The sky was lightening
from black to purple, and a sprinkling of stars winked in the sky.

"No. 6." Nezumi addressed the mammoth city darkly looming in the
distance. "You just wait. Some day, I'll carve out that infection of
yours, and lay it out in the open."

A streak of light shot across the sky. A flock of birds took flight. The
sun was rising. Morning was coming. The West Block was still thrown in
the depths of darkness, but the Holy City, bathed in the light of the
rising sun, glittered as if to laugh in contempt at it. Nezumi stood
still, facing the City in silence.

\mybreak

The streets below were brimming with light. He never tired of gazing out
at the morning scene from this room; that was how magnificent it was.

\emph{―Exquisite.}

The orderly streets, and the lush colours of the abundant trees that
lined them were beautiful. It was a place of full functionality and
vigour. Nowhere could one find anything wasteful or ugly. This was a
product of human hands, the highest possible―

There was a chime. A monitor set into the wall flickered, and displayed
the long, thin face of a man.

"I apologize for disturbing you so early in the morning."

"No need. I've been waiting for you."

"The investigation is complete. I would like to report the results to
you directly, in person."

"In person? That's rather cautious of you. Is there something amiss?"

"The suspect has escaped."

"It seems so― I've heard. But surely that's not of overt importance."

"He was involved in it. He aided in the suspect's escape."

The man on the screen pushed his glasses up his nose. They were rimmed
black, and visibly old-fashioned. Perhaps he was under the impression
that they suited him best, because he had not changed his frames once
for the past ten years.

"Are you sure of that?"

"We've confirmed it. The vocal signatures match."

"Aiding in escape, huh... and his method?"

"I'll report all the details to you shortly."

"Understood. I'll be waiting."

"If you'll excuse me, then."

The image disappeared, and the monitor faded back into the wall. The man
let his gaze wander around him, then out the custom glass panels of his
window to the sky that expanded beyond. It was a deep blue that pierced
his eyes. The seasons were taking their course again.

\emph{―So you've come back.}

What did he return for? Why did show himself again? A single petal
loosened itself from the bunch of roses displayed on his desk, and
fluttered silently to the floor.

\emph{―You should have stayed quietly where you were... idiot.}

He crushed the crimson petal with his foot. It smeared on the lush
carpet, leaving a stain that reminded him of blood.

\mybreak

Yamase was squatted on the floor, hugging his knees, his head bowed. He
looked like a child sulking after being scolded.

"Yamase-san." Shion called over to him. There was no answer.

"Yamase-san, what's wrong?"

Yamase dissolved into tears.

"Yamase-san, don't cry."

Shion placed a hand on Yamase's shoulder. Yamase's anguished sobbing
tore at his heart. It was painful just to listen to him.

"What's making you cry like this? Is there anything I can do?"

"There is." Yamase's hand grasped Shion's ankle.

"Shion, I don't want to be alone. Why did you have to get saved?"

"Huh?"

"Come with me," he pleaded. "You will, won't you?"

"Yamase-san, what―?"

The hand grasping his ankle changed colour. It was beginning to rot.
Chunks of flesh decayed and fell away from Yamase's arm. Shion could see
his bone peeking through.

"We'll go together... right?"

Shion's ankle was being tugged harder. He was being dragged into total
darkness. Yamase's arm continued to rot as it grew in length, and wound
around Shion's torso until it finally reached his neck and began to
choke him.

"No―stop―"

"Shion...."

Shion reached out as far as he could. He felt something firm and
definite, and closed his hand around it, gripping hard. And he screamed.

"\emph{No!}"

Shion awoke with a start. His throat was painfully dry.

"No, what?" Nezumi was peering into his face with a serious expression.

"Nezumi...." Shion murmured dazedly. "Oh... I'm alive...."

"You are. Congratulations on your safe return. And I'm sorry for ruining
your moment, but can you let go of my hand? You're holding on pretty
tight, and it hurts."

He had been grasping Nezumi's hand, so strongly that his fingers were
digging into his flesh. He had clung to this hand to escape from the
darkness.

"Want some water?"

"Yeah," Shion said gratefully.

The water was cold, and quenched every corner of Shion's body.

"I remember you giving me water like this... again and again." Words
formed slowly on Shion's lips, and left them in awkward fragments.

"There's a spring nearby that's not too bad. It's free, so you don't
need to worry."

"You... saved me again."

"I'm not the one that saved you. There aren't any adequate doctors or
medical facilities here anyway, and even if there were, they wouldn't
have done any good. No one could have saved you. You brought yourself
back. You put up quite the fight. I'm a bit impressed, actually. I
promise I won't call you a little boy anymore."

"It's all... thanks to you..."

Shion brought his hand up to his face to gaze at it. It felt somewhat
dry and rough, but there were no spots or wrinkles on it. It was still
the same young hand. He breathed a sigh of relief.

"I had a bad dream...." Shion began softly. "I wanted someone to help
me, and I reached out as far as I could... and I grabbed onto your
hand."

"That frightening, huh?"

"Yamase-san was there― he told me I can't be the only one to be saved...
his arm was wrapping around me, from my torso to my neck..." Shion
trailed off to feel at his neck. It was wrapped in bandages.

"From your torso to your neck?" Nezumi gave a short intake of breath. He
lowered his gaze, and moved away from the bed.

"Yamase-san was never the kind of person to say that..." Shion continued
reflectively. "He would have been happy for me, that I was saved... why
would he come into my dreams and...."

"Because you feel guilty about it," Nezumi said shortly, wrapping the
superfibre cloth around his shoulders. A mouse leapt up onto one
shoulder from a pile of books. "That Yamase guy died, and you survived.
You're feeling guilty over it, and that's why you're having stupid
dreams like that."

"Everything's stupid or useless to you, isn't it...."~

"Whoever lives wins. Don't feel guilty about having survived. If you
have time to be feeling guilty, work on living a day longer, a minute
longer. And once in a while, remember the ones that died before you.
That's good enough."

"Are you saying that to me?" Shion questioned.

"Who else could I be talking to?"

"It sounded like―" Shion hesitated. "Almost like you were telling it to
yourself..."

Nezumi blinked. He stared at Shion for a moment, and then muttered
"ridiculous" under his breath.~

Shion tried to lift himself up on the bed. He still couldn't move his
body as well as he wanted. He noticed that his entire torso was wrapped
tightly in bandages.

"Why are there so many..."

"You were tearing at yourself in pain, that's why. Lie down, it's still
too early to move around. And take the medicine by your pillow. When I
get home, I'll treat you to some soup."

"You're going out?"

"I have work."

Nezumi turned his back to Shion, and briskly left the room.

Shion swallowed the white pill as he was told to. A brown mouse squeaked
at him from beside a glass of water.

"Thanks."

The mouse nodded as if it understood his word of thanks, and perched on
Shion's chest as he lay back down.

"What kind of work does your master do?"

\emph{Cheep cheep.}

"What's his name? What kind of life has he lived until now? Where was he
born, and what...." he trailed off. He was getting drowsy. It seemed his
body was in want of a little more quiet rest. Shion nodded off to sleep.
This time, he had no dreams. When he awoke, the heaviness and lethargy
in his body had disappeared. He didn't feel any discomfort other than a
dull pain from the wound on his neck. His body was recovering quickly.

There was no one else in the room. It looked like Nezumi had not
returned yet. A dim darkness had settled, and it was quiet. Shion turned
his head to see the three mice curled up fast asleep by his neck. He
rose quietly, and put on his shoes. He wanted badly to catch a breath in
the outdoors. He wanted to fill his lungs with fresh air. Shion took
several cautious steps. He was sweating underneath the bandages on his
neck and chest. He unwound the ones around his neck. Now it was much
easier to breathe. His feet were light, and he didn't feel dizzy or
nauseous. Shion opened the door and climbed up the stairs. A cold draft
of air stung him. The world at ground level was bathed in a reddish
light. It was dusk. Coloured leaves were falling from the trees. They
danced in the wind, and with a dry rustling sound, fluttered to the
ground. Looking above, he could see the dark branches of the trees,
mostly bare, cast in stark relief against the sky. In the distance, he
could see No. 6.

Shion felt a hot pricking at the back of his eyes. It wasn't from
nostalgia for the city where he was born and raised. It was the sights
of late autumn, this unremarkable scene, that had tugged at his heart.
The faint rustling of the fallen leaves, the smell of earth, the colour
of the sky, all resonated in his heart deeply as if to coax the tears
from him.

\emph{―He'll have another good laugh if he sees me like this.}

Shion bit his lip to hold back his tears. He inhaled deeply.

He heard the sound of high voices raised in laughter behind him. Shion
turned around, and saw three children amongst the trees, coming up the
slope toward him. There were two girls and one boy. Did these children
live in the ruined house that he had seen earlier? They all had similar
round faces. He didn't know what they were laughing so joyously about,
but Shion felt his own feelings lift just watching them. Karan loved
children, and always used to hold sales that went by names like "Half
Price for Children Under Ten", so the bakery was always filled with the
voices of small children. That was inside No. 6. This was outside No. 6.
But despite how bizarre the world on this side of the wall was, the
sound of children's laughter was still the same.

The girl, who looked the oldest out of all of them, noticed Shion first.
She stopped in her tracks and opened her eyes wide. Her face stiffened.
Shion didn't meant to scare her. He raised his hand in greeting and
spoke first.

"Hi there."

The small boy standing behind the girl burst into tears.

"Huh? Oh, don't cry―" Shion made to take a step closer. The girl's face
contorted.

"Snake!" she shrieked.

Hastily scooping up the boy in her arms and taking the other girl by her
hand, she clambered back down the slope. Her shriek echoed high into the
sunset. Shion stood in stunned silence.

\emph{―Snake? What did she scream for? What snake?}

He didn't understand the girl's words.

\emph{―What did she see?}

He turned around. There was nothing save for the scenery of late autumn.
There were no snakes, or birds. There was no sign of any living thing.

\emph{―Did the shadows of the branches look like a snake to her? ...No, that
	girl was looking straight at me. She was looking only at me.}

Shion shivered. His scalp was tingling. He ran a hand roughly through
his bangs, and pulled hard. It was a habit of his when he was agitated.

"What―"

Shion's breath caught in his throat. There were a few hairs clinging
between his fingers. They were an almost-transparent shade of white.
They caught the light of the setting sun, and glimmered.

"How―what―"

He raked his head, pulling out more hairs. They were all the same. He
felt his face. The skin under his palm was firm. There were no wrinkles
or sags. But he felt a strange sensation on his neck. There was a slight
swell under his skin that was winding around his neck. Shion
half-tumbled down the stairs in haste.

\emph{―A mirror, I need a mirror...}

He knocked over a pile of books. The startled mice darted underneath the
bed. He found a wooden door next the the bathroom. He opened it, and
found a space about big enough for one person to lie down or stand up.
The back wall looked like a mirror. There were various things hanging on
the other walls, but Shion was in no mood to check. He turned on the
light, and moved closer to the mirror. His legs quaked. His hands were
trembling. But he forced himself to gaze into the mirror.

He gave a faint cry of horror.

What was he seeing in the mirror? What was this... this....

\emph{Snake!}

The girl's shriek welled up and echoed in his ears. He needed air, else
he felt like he would suffocate. He couldn't breathe. Shion staggered,
and leaned heavily against the wall. He stared at himself in the mirror.
His eyes were glued to it, and they would not move. He couldn't look
away.

His hair was white and shining. And there was a snake. A red serpent,
about two centimetres wide, was coiled around his neck. That was what it
looked like. He had no doubt about it.

"This can't be..." He shed his clothes. He tried to tear off the
bandages that wrapped his entire body. They had been wound tightly with
care, and they tangled and knotted as if to mock Shion's fumbling hands.
When at last the ends of the bandage had fallen away from his body,
Shion gave a strangled cry. The crimson band that had risen up on his
skin began from his left ankle, coiled up his leg and extended across
his crotch and torso, wound past his armpit and reached up to his neck.
It was, literally, like a snake that was strangling him. It was
slithering over his naked body. A red meander scar. The strength was
leaving his knees. He sank slowly onto the unravelled bandages.

White hair and a red serpent. This was the price he had paid to survive.

"Do you enjoy looking at yourself naked?" a voice spoke, so low it was
almost a whisper. Nezumi was leaning on the door behind him.

"Nezumi― this―"

"It appeared just as your fever went down. The affection is only
skin-deep, it's not because your veins are engorged. Which means there's
been no damage to your circulation system. Isn't that nice?"

"Nice? What's \emph{nice} about this? This is..."

"If you don't like it, you can get rid of it," Nezum said quietly. "Skin
grafting is no big feat in this time and age, right? As for your hair,
you can dye it another colour. I don't see any problem. But just letting
you know―" he shrugged slightly, "we can do something about your hair,
but you won't be able to graft your skin here. We don't have the
technology or facilities for that." His voice was calm and emotionless,
and contained not the smallest hint of sympathy. Shion remained sitting
where he was, absentmindedly gazing at the bandage that was tangled
around his leg.

"Shion."

"...Yeah...."

"Do you regret being alive?"

It took a moment for Shion to respond.

"―What?" he said vaguely. "Oh― did you say something?"

Nezumi sighed and knelt down in front of Shion, hooking a finger on his
chin. He forcefully tilted Shion's face up.

"Stop looking down, and look at me. Snap out of your daze and listen to
what I'm saying. Are you lamenting it?"

"Lamenting...? What?"

"Being alive."

"Lament... you mean... like wishing it didn't happen, right..."

"Obviously. No," said Nezumi sarcastically, "I was speaking French, like
\emph{la menthe}, for mint. Really? Get a grip on yourself. Has
something happened to that gifted brain of yours?"

Regret? Toward living? Was he lamenting the fact that he was alive and
sitting here, looking as he did now? Shion slowly shook his head.

"No, I'm not."

He didn't want to die. Even if he had been struck down, he would have
crawled across the ground to stay alive. He had no clear goals or hopes.
He had no sight of the future. His body had changed startlingly, and his
soul was in turmoil. But he still did not want to die.

Life was in the delicious taste of the water that quenched his throat.
It was in the colour of the sky that spread before his eyes, the
tranquil evening air, freshly baked bread, the definite sensation of
someone's fingers, soft, secretive laughter; 'Shion, what do you hope
for?'; the unexpected confession, uncertainty and hesitation. All these
things were connected to being alive. No matter what his appearance
became, he didn't want to be cut away from any of these.

"Nezumi...." he whispered. "I― I want to be alive."

The tears that he had held back until now gave way. A single droplet
spilled over his cheek. He hastily brushed it away.

"It's no use hiding it, stupid," sighed Nezumi softly. "How can you cry
so openly like that? Aren't you embarrassed?"

"I just let my guard down, okay?" said Shion crossly. "I'm having
trouble controlling myself because I'm not emotionally stable yet. I'm a
recovering patient, so stop making fun of me."

Nezumi silently gazed at Shion's face, and then reached out to gently
grasp at his hair.

"If it bothers you so much, I'll dye it for you later. But it looks
pretty nice on its own. And besides―" Nezumi's fingers moved to trace
the red scar across Shion's chest.

"Think about it, you've got a red snake coiled around your body. Quite
alluring, I'll say."

"I'm not flattered at all."

"Well I don't enjoy seeing you naked either," Nezumi retorted. "Put some
clothes on. I'll treat you to some hot specialty soup and meat."

Come to think of it, it had been a long time since he had eaten any
food. There was a burning sensation around Shion's stomach as hunger
suddenly gnawed at him.

"What kind of soup? Need any help?"

Nezumi blinked.

"You bounce back pretty fast, don't you?"

"Huh?"

Nezumi's voice suddenly dropped low and hoarse.

\poem{Round about the cauldron go.\\
	In the poisoned entrails throw.\\
	Toad, that under cold stone\\
	Days and nights has thirty-one\\
	Sweltered venom sleeping got,\\
	Boil thou first i' the charmèd pot.}

"What's that?"

"\emph{Macbeth}. The scene where the three witches are brewing newt eyes, frog
feet, and bat wings in a cauldron, making their special soup. Charming,
isn't it?"

"If that's your idea of specialty soup, I'll have to say no thanks."

"Instead of bat wings we'll use chicken, and instead of newts we'll toss
in lots of fresh vegetables. We'll substitute the frogs for a clove of
garlic. Just a moment's wait, your Majesty."

Nezumi's specialty soup was piping hot, and more delicious than anything
Shion had ever tasted.

\chapter{The city of light}

\lettrine{A}{fter their} meal, Nezumi placed a petri dish and a pair of tweezers in
front of Shion.

"I extracted this out of your incision. Try opening it up. This is
probably right in your field."

"My field?"

In the petri dish was something black and stringy, about two centimetres
long. Shion plucked it up with the tweezers. The slimy black object
dangled from them, and looked half-melted. Upon closer scrutiny, Shion
could make out evidence of something filmy at the end of it.

"These are― wings?"

"Looks like. I have no idea. There's one other thing I pulled out too,"
Nezumi added. "What do you have to say about this?"

It was another black lump. This one was hard, and resembled a seed.
There was a hole in it as if something had eaten its way out.

"A pupa― I think," said Shion slowly.

"Pupa? Like what moths and butterflies make themselves into? Oh wait,
butterflies make cocoons."

"Cocoons are the outer shell of pupae," Shion explained. "Embryo, larva,
pupa, and imago― most insects go through their development stages in
this order. This one... is probably some kind of bee."

"You can tell?"

"There are signs of wings beginning to form. The membranous qualities,
the fact that there are four of them... and more than anything―" Shion
swallowed. "I saw it with my own eyes― a black bee flying out of
Yamase-san's neck."

"And that bee and this black thing are the same thing?"

"If I'm not mistaken, probably. This one couldn't complete its
metamorphosis in the pupal stage. It managed to eat its way out of the
shell, but it couldn't become a fully grown imago. It failed."

"Why?"

\emph{Why?} He was right, why was that? Why was same bee that had hatched,
undergone metamorphosis and become an imago inside Yamase unable to
break out of its pupal stage here? Was it a coincidence, or― Shion shook
his head.

"I don't know. All I know is that this is a parasitic organism, and it
feeds off humans."

Nezumi stared unblinkingly at the petri dish.

"A parasite bee..." he muttered. "I thought bees only fed off flower
nectar."

"Those are just one species of bee, like the honey bee. Most bees ― or
wasp, in this case ― are hunters, and solitary by nature."

"And there are parasitic wasps too?"

Shion nodded. Nezumi's questions were simple and brief, and were easy to
answer from Shion's knowledge. But none of the questions were off the
mark. They tread lightly but accurately on the point of focus. With each
question he answered, Shion felt a growing uneasiness like he was being
backed into a corner. He felt like he would unwittingly slip and let
something horrific escape from his lips. \emph{But you can't be afraid}, he
told himself. He couldn't turn a blind eye and let things slip past him.
He couldn't pretend that nothing had happened, and refuse to enquire, to
take action. He stood in the position of one who had experienced it. He
had been host to the parasite, fought with it, and prevailed. And like a
symbol of this battle, he bore the red serpent on his body. Yes, this
was his imprint. Nezumi's face was peering into his. Shion returned his
gaze steadily, and spoke.

"There are said to be about 200,000 different species of parasitic
wasps. Hymenoptera such as bees and ants are highly specialized insects,
and there are still tens of thousands of species that are undocumented.
This is particularly so for parasitic wasps― or so I've heard."

"Which means we don't know what we're gonna get."

"We can't say what species for sure."

"But we can still predict."

"If we have any foundation for a basis of prediction," Shion answered.

"Why, \emph{you're} the best foundation there is," said Nezumi with mock
enthusiasm. "So how was it, being a host to a parasite wasp? Could you
tell if it was a new species?"

"You're really disagreeable sometimes, did you know that?" Shion replied
irritably.

"Well, you piss me off \emph{all the time}. 'We can't say what species for
sure', he says. Don't mess around. Don't you have any sense of danger?
These wasps are killing people."

"Most parasitic wasps do."

"What?"

"Wasps that are classified as parasites are actually more parasitoid. To
reach full growth, they only need to attach themselves to one prey...
their host. And ultimately, without fail, they consume and kill it."

Ultimately without fail, they consume and kill the host. It sounded even
more grotesque when put into words.

"Host? Like what kind?"

"There are lots. Moths, butterflies, ant larvae, fruits... a species of
ichneumonoideae called \emph{Rhysella approximator} lays eggs in the larva of
another species, xiphydriida, and makes it its host."

"So a wasp leeches off another wasp."

"Not only that, but another species of the same ichneumonoideae called
\emph{\emph{Pseudorhyssa alpestris}} lays eggs in the same xiphydriida right after the
\emph{Rhysella}, and \emph{its} larva eats both the larva of the \emph{Rhysella} \emph{and} the
xiphydriida."

"So they kill each other even if they're from the same species... wow, I
thought only humans killed their own kind. So?"

"Hm?"

"Are there parasite wasps that attach to humans as hosts?"

"I've never heard of any," replied Shion. "There are other organisms
that are parasitic to humans ― viruses, bacteria, ticks, fleas, and the
like. I've heard once of a warble fly that laid eggs in a boy's head,
and one of them invading his brain, but that was an unusual case, I
think... I've never heard of any wasps doing that. The question is,"
Shion said thoughtfully, "how was it able to lay eggs in a human body in
the first place? How did it pierce the skin with its ovipositor without
being noticed?"

"You have no memory of it?"

"No. I didn't feel any pain or itch. It never crossed my mind that I'd
been stung by a wasp."

"So they can lay their eggs without their host noticing at all."

"Not only that, they also grow with astonishing speed. And when they do,
they must excrete some sort of substance that rapidly accelerates ageing
in the host, and inevitably leads them to death. Even the process of
rigor mortis and dissipation gets sped up. And finally, as a full-grown
imago, the parasite wasp eats its way out of the body and escapes
outside."

There was a moment of silence.

Shion and Nezumi looked at each other, and exhaled at the same time.

"I'm surprised you lived through it."

"Yeah. I'm starting to get the cold sweats just thinking about it."

"There are too many things we don't know," said Nezumi. "Where did this
guy come from? What is it?"

"Hey―" Shion said suddenly. "Have there been any similar incidents like
that here?"

"No. I did a little research because it was nagging me too. There were
guys who got shot to death fighting, or people who got drunk and drowned
in a ditch, but no one who suddenly turned old and died. There's no
media control or censorship here like No. 6," Nezumi added, "so if
anything out of the ordinary happens, it should spread like wildfire."

"Then if it's happened in another Block―" suggested Shion. "The
Southeastern Blocks, maybe? That environment is probably the most suited
for a new species of insect to appear."

Nezumi shook his head slowly.

"I can't imagine that happening. If it did, the city should close all
the gates leading in. But they haven't shown any signs of doing that.
Produce is still being shipped in from the Southeastern Blocks as usual.
The North Block is the same."

"Then the wasp definitely must have come from No. 6.... I can't believe
it," Shion muttered to himself.

"Unbelievable― you're certainly right about that." Nezumi's fingers
lightly tapped the petri dish. His shoulders shook slightly.

"Nezumi?"

Nezumi's head was bowed, and a quiet chuckle escaped his lips. It soon
turned into howling laughter. It echoed in the underground room that
overflowed with books. Nezumi collapsed on the bed, holding his stomach
and laughing harder still. Shion lunged for a pitcher of water, and
emptied it on Nezumi's head.

"Hey!" Nezumi sprang up. "What the hell are you doing?"

"Are you alright?"

"\emph{Alright?} I'm soaking wet here."

"I just― I thought you were undergoing a fit of hysteria or something,
so I..."

"What do I have to throw a hysteric fit for?"

"Well, you started laughing randomly, I just thought..."

"I only laughed because it was funny."

"Funny? What is?"

Nezumi shook his head violently. Shion's face was pelted with water
droplets.

"It's hilarious, isn't it? Where did this thing originate? No. 6.
There's a mysterious man-eating wasp flying around in this utopian model
city, the \emph{Holy City}, if you will. This is city of the future, the
epitome of modern science. And it's being eaten by \emph{bees}. Hilarious."

"It's not something to laugh about. People are dying."

Nezumi stood up. He walked over to Shion, and drew up to him
face-to-face. Nezumi was right, Shion thought. He was tall. He easily
exceeded Shion in height by several centimetres.

"What?" Shion unconsciously took a step backwards. He drew himself up
and squared his shoulders as best he could in spite of the wall of books
behind him. He had seen something flash in Nezumi's grey eyes with a
savage, piercing glint. It was only for a fleeting instant, but he had
not missed it.

"Forgive my foolish question," Nezumi said in an expressionless voice.
At the same time, a set of fingers closed around Shion's throat.

"Have you killed anyone before?" Nezumi's thumb slowly dug deeper into
Shion's neck.

"Never..." Shion said faintly. "Of course I haven't..."

Nezumi's thin lip curled slightly in a cold smile.

"I would've figured. But keep this in mind. The wasp might kill its host
in order to keep itself alive, but humans can kill other humans for much
smaller reasons than that. And \emph{you} were almost killed by another human."

"I know."

"You liar. You don't know anything."

"I do know!" Shion said angrily, clenching Nezumi's wrist. "I know. If
I'd been taken to the Correctional Facility as planned, I would have
been made out to be the murderer in the wasp's place. At best, I would
have gotten a life sentence. At worst, I would have been executed..." He
paused for a moment, then continued determinedly. "The Bureau wanted to
buy more time. They needed time to decode the truth about Yamase-san's
cause of death― and by making me the suspect, they wanted to file it
away as a simple murder case for outside eyes. Am I right?"

Nezumi's fingers withdrew. The spot on Shion's neck burned where
Nezumi's thumb had dug in.

"Good answer, full marks," he said breezily. Then his tone dropped in
mock seriousness. "It seems this unbalanced young man, tumbled from the
ranks of the elite, engaged in this crime out of resentment for the
city. He allegedly concocted a special chemical to use repeatedly in
multiple criminal acts. Thanks to the efforts of the Security Bureau,
however, this young man has been put under arrest. We would like to
reassure the citizens of the city that they are perfectly safe. ―It was
probably scripted somewhere along those lines," he broke off. "What a
ridiculous farce. I'm guessing your knowledge and history fit the role
of 'dangerous criminal' perfectly."

"The City has full access to all the citizens' personal information,"
Shion answered. "It was probably easy to find a person to fit the role
they wanted."

"More like you were being marked from the beginning."

"Huh?"

"Ever since that day you helped me, the city's been marking you as a
cautionary suspect. They've been scrutinizing your daily life down to
every minute detail. Who you met with, what you talked about, what you
ate... so I thought this murder case was something the city devised to
arrest you. I was wrong, though, and we know that now."

"But why? For what purpose―"

"Because you're not a loyal citizen," Nezumi replied as he towelled his
hair off. His profile was delicately chiseled. It looked almost like an
artificial creation. It was all too different from a face that had skin
and blood coursing through it, and carried bodily warmth, with swells
and dimples of flesh or fat, the occasional eczema; a face that changed
with joy, anger, grief or mirth, shone with sweat, or stained with
tears. This was no human face― it looked like a doll that had been
crafted with utmost precision.

But even so, Shion thought, and clenched his fist. The wrist he had
grasped minutes ago had been warm, and throbbing with a steady pulse.

"You're spaced out again. Am I boring you?"

"Huh? Oh, no― of course not. I was just wondering what you meant by...
not loyal." Shion's face flushed, though he didn't know why. Nezumi
sniffed dismissively.

"That city only accepts people who pledge absolute loyalty to them. They
don't allow people who resist, object, or retaliate. They make sure any
foreign object is removed completely. That's how it's thrived up until
now."

"And I'm the foreign object this time."

"You're more than foreign to them― think about it. You housed a VC, you
held suspicions against the city for manipulating information, and you
saw the cruelty behind their fa\c{c}ade. As a citizen, you fail the test.
You're an unwanted candidate. The city was just waiting for the right
opportunity to get rid of you. ―Hey," Nezumi said abruptly. "Tell me,
what does the immune system do when a virus invades a human body?"

"Huh?" Shion was caught off-guard. "Well, first the natural killer
cells― that's a type of lymphocyte― find the cells that have been
infected with the virus, and destroy them. Then the ribonuclease become
active and suppress the spread of the virus. Next―"

"That's enough," Nezumi interrupted. "Geez, I set you off explaining
something, and you don't know when to stop. That's why people get pissed
off at you."

"You're the only one that seems to get irritated at me."

Nezumi ignored him and gave a short, derisive laugh.

"So basically, to the city, you're a virus. And that's why they tried to
erase you."

"I'm a human. I won't be erased that easily."

Nezumi sighed deeply in exasperation.

"It's easy for humans to kill other humans, you know."

Shion clenched his fists tightly again.

"But they can save people too."

"What?"

"You saved me. Nezumi," he said earnestly, "parasite wasps don't help
each other out. But people can save other people. Am I wrong?"

Nezumi smiled briefly, and his gaze slid away from Shion.

"You're as stupid as they come. Hopeless. Where did you think of that
sickening cliché? I told you, I'm only repaying my debt."

"And I told you, you've already paid enough."

"How generous of you to have such low estimations of my debt," said
Nezumi sarcastically.

"Then you must have had pretty high estimations."

Nezumi let out a long breath, and looked up at the ceiling. He bit his
lip in silence as if to grope for the right words. The mice gathered
around his feet.

"You don't understand," he said momentarily. "No amount of words would
probably make you understand. That day, four years ago, I'd mostly given
up. Giving up means the end of you. I knew that. But there was no way
anyone would help me, or lend me a hand― that's what I honestly thought.
I couldn't ask for help, I had nowhere to run.... I snuck into Chronos,
so tired I couldn't move, and I thought about how it was only a matter
of time until I was caught..." he paused, then spoke quietly. "I felt
so― humiliated. I wondered if the whole reason I'd been born was just to
die in humiliation like this.... don't laugh."

Shion would never have been able to. The sounds of that night four years
ago were echoing in his ears. The sounds of the wind, the trees, and the
whipping rain meshed and undulated, rising vivid and sharp in his mind.
And amidst the din and darkness, a sopping wet boy was curled up on the
floor.

"And then the window opened. You threw it open wide, didn't you. And
then you spread your arms open."

"Yeah, I remember. I felt really restless, and I wanted to scream."

"To me, it looked like you were calling, beckoning for me to come in. I
thought― this was unbelievable, and it was happening right this moment.
And you even left the window open when you ducked back inside."

"I was going to turn off the atmosphere control system."

"I don't care for what reason. That window you left recklessly open was
my stroke of luck. And the fact that you didn't call the Security Bureau
on me, but instead treated my wound and even gave me food was another
miracle. I found out for the first time that things like this could
happen. That a helping hand could be extended miraculously like that....
you were the first one that taught me. Like all of these―" Nezumi slowly
looked about his room.

"― These thousands of stories here, you taught me that sometimes we
encounter the most unexpected things. And that's why I was able to
survive...." he lapsed into momentary silence. "So you're right. There
are times when people are saved by other people. And you're the one that
taught me that. You were the only one that taught me that. The debt I
owe for that is high― unfortunately for me."

Nezumi's voice was so quiet it was almost a murmur, but it was deep and
clear, and rang pleasantly in Shion's ears. So that's what it was, Shion
thought, and spread his fingers as he looked as his palm. That night,
when he threw the window open with these hands, he had called in a
miracle along with the wind.

"Don't get too carried away," said Nezumi, his words quickly turning
brusque. "I'm giving you the guest treatment because I owe you. If you
get carried away and start acting cocky, I'm going to kick you out."

"Fine by me," said Shion mildly. "I don't know if you'll take my word
for it, but I'm not the type to get carried away too easily. But how did
you find out I was in danger?" he asked curiously. "It's not like you
were keeping constant watch over me these four years, right?"

Nezumi plucked a grey mouse up and held it out at Shion. It was the
smallest among all the mice.

"Take a close look."

Shion held the mouse in his palm, and brought it close to his face.

"Is this... a robot?"

"Pretty well-made, isn't it? It has a set of built-in sensors. This
thing is small enough that it can slip through the city's surveillance
net and move around quite a bit. Depends on the area, though."

"Did you make this?"

"Well, yeah," he said casually. "While I was away from No. 6, this guy
was the one sending me data about you."

Shion lightly closed his fingers around the mouse in his hand. It had
none of the warmth and softness that was characteristic of living
things. Conversely, he scooped up one of the mice scurrying about his
feet and held it in his palm too. This one had a faint but definite
warmth and pulse.

"I didn't know when or how the city was planning to get rid of you,"
Nezumi continued. "You're smart and young. You still had plenty of usage
value. I couldn't imagine that they would kick you out so easily. I
figured once they discovered how useful you could be, they'd take full
advantage of it. Writing you up as a murderer was probably a piece of
cake for them. You were their scapegoat," he sneered. "They were keeping
you enclosed in a corral until the ceremonial day, when they would drag
you out in front of everyone and make a flashy show of chopping your
head off."

"So I've gone from being a virus to a goat, huh. Not much of an
improvement."

"Hey, goats are cute. More lovable than you, anyway."

"I appreciate the compliment," said Shion unamusedly. "So this little
guy sensed the change going on around me and came to notify you."

"Yup. It started that day when that man died of unnatural causes at the
park where you worked. After that, the Bureau started stepping up their
surveillance on you. And like adding icing to the cake, your co-worker
got killed too. It was the perfect opportunity to put you under arrest."

"Surveillance― I didn't even know I was being watched."

"They do it so you don't notice. Once you do, it's too late."

"That's scary."

"You're noticing \emph{now}?" Nezumi sniffed in derision. Shion raked his bangs
up. He was confused― about what had happened, what was about to happen,
and what he was supposed to do from now on. He knew almost nothing. And
it was terrifying not to know. But there was one idea, although it was a
mere speculation, that had sparked in Shion's mind.

\mybreak

"Nezumi."

"Hm?"

"Could it be the park?"

"The what?"

"The Forest Park in the centre of the city. My workplace― could that be
where the parasite wasp originated?"

"Why?" said Nezumi. "That park is right in the middle of the city. It
might be a forest, but it's still artificial. All the wildlife is
managed and controlled by the city. If a parasite wasp sprung out of
nowhere, they'd notice."

"That's true, but... out of all places in the city, the park would be
the most adequate environment for a new species to appear. And all the
victims so far, including me, were in the park when it happened. Of
course―" Shion hesitated. "I don't know if there's been casualties
anywhere else― but I think part of the reason why the city suspected me
was because the incidents were concentrated in that location. But if
that's the case―"

"That monster must have been born there somehow without being noticed by
the control systems."

"It's plausible, right? And what's more, the park is where lots of
people gather."

"No shortage of hosts," said Nezumi grimly.

It was a park that was beautifully and conveniently crafted for the
citizens. If a species that preyed on humans actually did inhabit it,
then―

"Spring," Shion murmured.

Spring? Nezumi echoed in question.

"Once winter comes, the wasps will cease activity as they enter a
dormant stage. The eggs that have been laid already will probably pass
the winter as they are."

"Inside people's bodies."

"Yeah. And when spring comes, they'll be able to resume activity as an
imago. Then they'll hatch all at once." In a season abundant with
sunlight and flower blossoms, a mass of black wasps would simultaneously
break out of people's bodies to take flight. How many would they be? How
many people would be sacrificed?

"We have to do something."

"And how are you gonna 'do something' about it?" replied Nezumi bluntly.
"Don't even think about going back to the city. You'll be killed. You're
an amateur, you can't pull any fancy tricks like slipping past
surveillance. Ten-to-one, as soon as you step inside the city, you'll be
shot dead. We don't have a trump card to pull out, you know."

"Actually― I think we might."

Nezumi narrowed his eyes.

"I survived that wasp attack. There's a chance that I've developed
antibodies that resist the toxin. If I have, then it'll be possible to
make a serum out of my blood."

Nezumi shot an appalled look at Shion and hunched his shoulders
exaggeratedly.

"And then what're you gonna do? Go waltzing into the city's Health
Bureau and say 'Please check my blood. And if you like, please make a
serum out of it'? That's idiotic. They'll probably suck all your blood
out and throw you in the trash with the rest of their organic garbage.
Sure, what you're saying is impressive, but are you prepared to risk
losing your life for these people?"

"I don't want to die."

"Then don't think about useless things. Whether you have antibodies or
not, once you're caught, you're going to get killed anyway. It's just a
matter of how soon or how late."

"Then what should I do?"

"Don't do anything. Just leave them to fend for themselves."

Shion lifted his face.

"Leave them?" he asked quietly.

"Yeah. What a magnificent stage it'll be," Nezumi sneered. "You can
watch the Holy City crumble into ruin, glowing in the light of spring.
And you'll have the best seats in the house."

"Nezumi!" Shion raised his voice sharply.

"Whoa, don't go dumping water on me again."

"Are you under the impression that the West Block is safe from this?" he
said incredulously. "We're human beings, the same as them. There's no
knowing when the wasps might attack us too."

Nezumi fell silent. A crooked smile played on his lips.

"We're not the same."

"What―"

"The people inside the city sure don't see the residents of the West
Block as the same human beings. You still don't know what kind of place
this is, do you? This is the Holy City's garbage dump. No. 6 has thrived
by throwing everything it doesn't want out here. You should take a good
look and see for yourself."

"Nezumi..."

"This is just my hunch, but listen," he continued. "That monster is
probably only going to choose residents of No. 6 to be its host― the
people who have pushed everything dirty into the hands of others to live
in that perfectly hygienic environment, well-nourished and in excellent
health. Mr. Monster has gourmet tastes."

"How can you be so sure?"

"I have no clue about the biology of insects, Shion. But I'm probably
right in guessing that any bee, wasp, ant or grasshopper will appear
most in places where there's the most food. In terms of population
density, we're much higher than the city. But do you see any sign of the
monster here? No. Which means that there are simply no prey, no hosts
here. Right?"

Shion was at a loss for words. His thoughts were becoming tangled, and
there was a dull pain throbbing at the back of his head. Nezumi's hand
touched his cheek.

"Sorry―" he said softly. "I didn't mean to give you a hard time. I
forgot. You're from the other side, the inside of the wall."

"I don't understand what you mean by inside and outside."

"Of course you wouldn't," Nezumi said gently. "That's normal. You guys
have probably never tried to understand what was going on outside your
walls, have you? You probably weren't even curious about it. Oblivious,
arrogant, blissful people... But you, poor thing," he murmured. "You've
fallen off that pedestal."

\emph{Which means I can no longer be oblivious, arrogant or blissful anymore.
	Is that what you want to say?} Shion let his gaze speak for him as he
looked Nezumi in the eye.

\emph{If arrogance is knowing nothing and never having tried to know, and if
	my blissful life until now has been built upon this arrogance, then
	sure, I don't mind throwing everything away. Falling off my pedestal
	would be the best thing that could have happened to me.}

"Nezumi," he said steadily.

"Hm?"

"I want to know the truth. I want to know what's real, what's happening
to this world I'm living in. I want to see its true face."

Nezumi hunched his shoulders and flashed him a wry smile.

"Such youthful words."

"We're the same age."

"I have more life experience than you. Geez, I don't know who else would
rattle off a line as embarrassing as 'I want to know the truth'. Except
Hamlet, maybe."

"Who's that?"

"A prince of Denmark. I think you should balance out that knowledge bias
before working on knowing the truth. You really know next to nothing
about classics, huh?"

"Well, I've never needed them before..." frowned Shion. "The Arts
weren't encouraged much, so..."

Nezumi reached into the shelves and pulled out two books.~

"If what you're saying is true, then once winter comes, the commotion
will die down. Which means we have a moratorium until spring."

"Probably."

"Then there's no need to get worked up," he said airily. "Nothing will
come of it. So until you recover and you're well enough to move around,
you can read him these."

"Him?"

A brown mouse scurried up onto Shion's knee, and stood on its hind legs.

"He loves \emph{Macbeth}. The other is \emph{Faust}. Ever heard of it?"

"No."

Nezumi grimaced, and heaved an exaggerated sigh.

\poem{If feeling prompt not, if it doth not flow\\
	Fresh from the spirit's depths, with strong control\\
	Swaying to rapture every listener's soul,\\
	Idle your toil; the chase you may forego!}

"―is how it goes. You should give your brain a break and work on
training your soul. Your Mama used to read to you, right?"

"Yeah."

The mouse squeaked insistently.

"Oh, right. Speaking of Mama, I have a message from yours. I almost
forgot."

"Huh?"

A faint colour rose in Nezumi's cheeks as he obstinately turned aside.

"Well, since you managed not to die... I figured it wouldn't hurt to
tell your mother that you're over here now. "

"You went to see my mother?"

"Not me," he said brusquely, "I stayed in the underground tunnel. This
guy―"

The brown mouse tilted its head to one side.

"―He went for me, with the note in his mouth. One of the oldest tricks
in the book, but surprisingly, it got past surveillance without being
noticed."

"Thank you."

"Stop that." Nezumi pulled a face. "Don't give me that teary-eyed look.
Aren't you embarrassed at all?"

"I was talking to this little mouse here."

"Oh― well, then."

Shion really was grateful. Now that he knew how difficult it was to get
past the wall, he felt grateful from the bottom of his heart that Nezumi
had taken the same risk again just to deliver the message to his mother.
\emph{So this is what it means to gain knowledge.}

"Your mom's got some guts," Nezumi remarked. "She managed to give me a
reply without getting caught." Nezumi tossed him a rolled-up strip of
paper that was about half the size of his finger. There was a message
hastily scribbled onto it that he could barely read.

\memo{1}

"What does this mean?" He and Nezumi looked at each other in
bewilderment.

"It's a letter that your Mama wrote to her beloved son," said Nezumi.
"Don't you have any clue what it might be about?"

"Not really," replied Shion doubtfully. "'K' probably stands for my
mother's first name, but this... 'not sure'...?"

"It's probably an address. Not that building numbers would do any good
here.... Latch Building, huh. I guess I'll look into it."

"So that must mean my mother knows someone who lives in the West Block."
It was a surprise to him. He had never heard Karan utter a single word
about anyone who lived here. Nezumi snapped his fingers smartly.

"Oh― I know."

"Huh?"

"Maybe he's your dad."

"Fat chance," retorted Shion. "Look who's had one too many stories to
read. Aren't you embarrassed at all?"

Nezumi \emph{tsk}ed in disappointment.

"You're getting better at your comebacks. ―But, well, I guess you're
right. It's your typical script for a cheap melodrama. A father and son
reunite in tears after sixteen years of estrangement." Nezumi's voice
turned deep and burly.

"I've missed you, son."

"Me too, Father." Shion bounded into Nezumi's widespread arms. They
circled around his back. It was warm. For an instant, the frigid touch
of Yamase's dead body flashed back in his mind. But it was this warmth
here, not that coldness, that he wanted to remember; and Shion vowed
never to forget the heat of the body that was in his arms. He wished all
beings, himself included, could continue to be living beings. He didn't
want his life unfairly wrenched away from him. He could feel it― the
pleasure of living, breathing, and possessing a body of warm flesh― soak
into the depths of his core. Nezumi gently detached himself.

"You're getting better at picking up your cues," he said approvingly.

"I know. I've come pretty far in a short time, haven't I?"

"Quite an excellent pupil. Shall we go, then?"

"Where?"

"Outside."

Darkness had fallen outside. Here in the West Block, night and complete
darkness seemed synonymous. A chill wind nipped at Shion's skin.

"Look," Nezumi pointed. No. 6 was carved out in the darkness, bathed in
light as it glowed in the distance.

"It's always shining like that, morning, day, and night. Pretty, isn't
it."

"Yeah."

"But where you're going to be living from now on is here." The land was
sunken in darkness, with a sparse scattering of lights here and there.
They burned forlornly, and made the surrounding dark look even more inky
black. The clouds above broke, and the moon peeked out. It was a
crescent moon. A thin sliver, almost like a clipped nail, floated in the
empty sky.

Nezumi crouched down to pick something up.

"Look at this." It was a dead wasp.

"This looks like just a regular paper wasp."

"You were right, it looks like the season for wasp activity is over."

"By springtime..." Shion trailed off.

It was possible that the city would hold out somehow until spring. It
gave him a few months' grace period until the fatal judgment would fall.

"If you're serious about fighting the parasite wasps, I won't get in
your way," Nezumi said. "But if that means helping No. 6, I'm backing
out."

"Do you have a grudge against No. 6?"

There was no answer. The wind blew stronger. The canopies above creaked
and rustled as they swayed in the darkness.

"Shion."

"Hm?"

"That city where you were born and raised in― that's the biggest
parasite."

"Huh?"

"It latches onto the host, sucks out all its nutrients, and devours it
whole. That's the kind of city it is. A Parasite City... do you
understand what I'm saying?"

"No."

"You'll find out soon. You said you wanted to know the truth. But once
you know, you'll never be able to go back. I would prepare myself if I
were you."

"I've already come too far to go back anyway, wouldn't you think?"

"I guess so."

Nezumi's quiet laughter carried on the wind. His voice was dry and
hollow, as if to complement it.

"If you find out the truth, and still want to protect No. 6― then,"

In the darkness, Nezumi's face turned to his. Shion could feel his gaze.
He could almost see the grey of his eyes just as vividly.~

"Then you're my enemy too."

\emph{Boy, it's chilly out here. Let's head back in.} Nezumi's tone was light.
It was as if nothing had happened. He turned his back to Shion, and
began whistling as he descended the stairs.

"Nezumi."

The whistling stopped.

"You haven't told me your name yet."

"Nezumi it is, and Nezumi it shall be. Good enough."

"But it doesn't suit you. And it was a promise. You said you'd tell me
your name if I survived."

There was a soft laugh, which quickly turned into whistling again. The
door closed, and a silence settled over the darkness. Shion stood alone,
rooted to the spot. The wind caressed his white hair. He could hear a
dog barking somewhere in the distance.

He gazed up at the city that bejewelled itself in light. The Parasite
City. The city whose name Nezumi had spat with disgust was shimmering
and beautiful.

Shion averted his eyes from the light, and took a deep breath.

Then he descended slowly down the steps to the room below.