% !TeX spellcheck = en_US

\chapter{Inukashi's days}

\lettrine{T}{he ceiling} was spinning. It actually felt like it was whirling.

\emph{Huh? What's going on?}

Inukashi collapsed on the bed and closed his eyes. He felt ill. He was
not only dizzy, he even felt nauseous. He kept his eyes closed as he
took several deep breaths. He inhaled through his nose, let the air sit
in his stomach, and exhaled slowly through his mouth.

Once, twice, three times\el 

Any ailment, physical or mental, was usually cured by this---whether it be
his agitated heart, his disarrayed thoughts, his throbbing wounds, or
dull headaches. No one had taught him this; it was something he had
learned without even realizing. But as for his empty stomach, there was
nothing he could do. No matter how deeply he inhaled to make his stomach
expand, as soon as he exhaled it flattened back out again. There was
nothing he could do about his body, growing colder from his hunger.

\emph{I hate hunger. It's horrifying.} Inukashi gave himself a shake. Hunger
was like a demon. With its sharp fangs and claws, it uprooted and stole
any will to survive, any hope of living.

But now, he was alright.

Of course, he was still hungry. Inukashi didn't remember the last time
his stomach was full. Empty---that was just how stomachs came. That was
his idea.

He carefully lifted himself up on the bed. He didn't feel dizzy anymore,
but his nausea was still present. He felt heavy, like someone had
attached weights to his arms and legs. \emph{I feel like someone's chained
metal balls to me, like a prisoner of some country.}

\emph{This is bad.}

He lay back down again, and mentally clicked his tongue. Falling ill in
the West Block was like beckoning Death to your side. Here, there were
underground shamans of questionable nature, or self-proclaimed doctors,
but no one who could give proper medical treatment. Inukashi didn't know
of any, at least.

His body felt heavy. With his eyes closed like this, he felt like he was
being dragged into the watery depths.

\emph{In times like these, I have to think about fun things, he told himself.
Fun? Have I ever enjoyed myself?}

\emph{You did. Yesterday evening, remember? You were freed from hunger, just a
little bit. Yeah, see, that was it. That was ultimate happiness.}

\myspace

He'd eaten some meat. There had been a chunk of raw meat in the load of
food scraps from the Correctional Facility. It was not someone's
leftovers: this was a block of meat that had not even been cooked. It
was free of bruising and rot. Upon closer inspection, it was peculiarly
flat. Perhaps the chef at the Facility staff restaurant had dropped it
on the floor, where someone else had stepped on it.

"Oy! You just ruined a perfectly good chunk of meat!"

"Oh, sorry. But you dropped it."

"Well, we can't help it now. Can't use this anymore."

The meat had been tossed into a metal garbage bin and forgotten.
Eventually, it had made its way into Inukashi's hands along with other
trash and food scraps---perhaps that was its journey. \emph{Whatever. I don't
care what its journey was like, or how it got here. All that matters is
I'm holding a chunk of meat in my hand.}

What incredible fortune this was.

He quite literally danced for joy. When was the last time he'd had
something this good in his hands? He searched and searched in his
memories, but nothing turned up. Inukashi licked his lips as he held the
hunk of meat, shining with fat. He swallowed hungrily.

He didn't know what kind of meat it was, but he didn't care---as long as
it wasn't human or dog. Inukashi returned to his dwelling in the ruins,
and jumped right into cooking. He selected vegetable cuttings and bones
out of the food scraps, threw them into a pot, and let it simmer. Right
before it finished cooking, he divided the hunk of meat into sections
and threw them in. He considered setting aside half of it to cure, or
take to the market to sell, but in the end he decided against both.
Inukashi was well aware that nonperishable food was a precious
commodity; he also knew that if he took the meat to market, it would
bring him a decent amount of money. \emph{But I think I'll finish this meat
off in one go.} That was his decision. \emph{I'm allowed to treat myself once
in a while. I'll enjoy the good fortune that's come to me---the fortune
that heaven decided to throw my way out of chance.}

\emph{This is the West Block, where I can't even predict what my fate will be
tomorrow. Even God doesn't guarantee anything for anyone in this place.
I might as well enjoy the present without thinking about tomorrow.}

Steam rose from the pot.

A mouthwatering smell drifted up. The dogs gathered around, drawn by the
smell.

"I know, I know. You guys'll get some to eat, too. Don't worry."

White, black, patched, tan. Long-haired, short-haired, curly-haired.
Flopped ears, erect ears, one-eared. Inukashi kept twenty or thirty dogs
with him, ranging from one as big as a calf to one smaller than a cat.
For some reason, that number never increased. Puppies were born every
year, so that meant an equal number of dogs probably died or left.

An old female dog died yesterday. She was a great mother, having birthed
many puppies and raised close to half of them successfully. \emph{I remember
her sons and daughters licking her cold, stiffening body in turn.}

Dogs were deeply loyal. They were warm, and gentle. They had a definite
compassion. They never betrayed their friends or family.

\emph{They're much more decent and trustworthy than human creatures.}

"More fearsome than hunger, than the frozen earth, are humans."

\emph{I remember that was Gramps' line.} Inukashi shook his head as he stirred
the pot with a wooden spatula. \emph{Why did I have to remember him? It's not
gonna help satisfy my hunger. But, no}---he shook his head even more
fiercely.

\emph{I gotta remember him at least once or twice a year, for his sake. I have
to remember and recall how dear he was to me. I owe that old man. We
don't forget the good deeds that people have done for us: that's another
virtue about us dogs.}

\emph{I don't know how old Gramps was, or why he lived here in the ruins with
the dogs, or where he came from or where he went. I don't feel like I
need to know, nor do I intend to find out. But I wouldn't have survived
if it wasn't for Gramps. I feel the weight of what he did in every inch
of my bones.}

\emph{It was winter when I met Gramps.}

\emph{I remember the freezing wind and the whiteness of the snow that piled up
in front of me. So yes, it was winter. Years and years ago.}

He had no memory of his mother, no recollection of his father; yet, he
could remember vividly the frigid wind and the snow dancing. He recalled
the approaching footsteps, a dog's tongue licking his cheek, the warmth
of a human bosom; even the floating feeling he felt for an instant when
he was scooped up.

\emph{How old was I then? Was I still a baby? Probably, huh, because I was
still getting milk from Mum. Babies sure remember a lot more than we
give credit for.}

He was an elderly man dwelling in the ruins of the hotel, and he had
picked up Inukashi and raised him. Or perhaps one could say that the man
had picked him up, but the female dog was the one who raised him.

She was young, and had just given birth to a litter. Inukashi suckled at
her breast, and slept nestled up to her belly with the other puppies.
Thanks to her, he had avoided starvation. He had avoided freezing to
death. He had survived.

This intelligent and sweet-mannered dog was Inukashi's one and only
"Mum".

"You're a strange child\el or special, I should say." The old man had
made this statement when Inukashi had grown old enough to walk, and was
able to compete with his fellow dogs in lunging for food. The old man
had spoken in a warm, reflective, gentle voice. Inukashi remembered that
well, too.

"Speshal?"

"It means you're different from the others. Until now, I'd never even
heard of, much less seen, a baby who could feed and grow on dog's milk.
When I took you in, to tell you the truth, I figured you wouldn't last
three days. But I still took you in anyway, because I wanted to give you
a proper burial."

"Berry-all?"

"It means digging up the earth and burying you in it. When you died, I
planned to put you underground and give you a burial that way. I
couldn't bring myself to let you waste away in the open air. I didn't
want you to go through what most babies go through on this land, rotting
in the middle of the road, being pecked at by crows, being eaten by
beasts. Normally, I would have\el yes, I would have just left you there.
I would have passed you by pretending not to notice. It would be no
different from what I've always been doing. But why did I decide to pick
you off the road\el why did I want to bury you in the earth?"

"Why?"

"I don't know." The old man shook his head slowly, twice. "I really
don't know. I don't understand it, myself. Why did I scoop you up that
day and take you home? I've watched many babies, dozens of them, die.
Why did I decide to extend my hand to you? I can't seem to explain it.
That's partly what I meant when I said you were a strange child."

Inukashi shivered. He made a soft strangled noise at feeling his body
grow colder to the tips of his fingers. A cold sweat ran down his back.

He was scared. At the same time, he was overwhelmed with the impulse to
laugh out loud. He wanted to throw his head back and let his laughter
echo to the heavens.

He was alive due to good fortune bordering on mere coincidence. If it
weren't for the old man's impulse, his body, his flesh, his bones would
have been prey to crows and beasts. What a miracle this was, what luck.
Inside his heart was a storm of fear, relief, and the stabbing impulse
to dissolve into hysterical laughter.

By that time, Inukashi had already come to realize how arduous a task it
was to survive every day in the West Block. He sensed that his own
future was full of tribulation and hardship, much like climbing up a
steep cliff with bare hands.

But he wanted to live. He wanted to live, to survive, and stretch the
limits of his life, even for a minute, for a second. For that, he would
do anything, no matter how unsightly, deceitful, or shameful it was. It
was easy to die. All he needed was some rope and a tree with sturdy
branches. He could also jump off a cliff. Or, he could run screaming
into the Correctional Facility---that was an option, too. The soldiers on
patrol would shoot him through the chest or the head without any
hesitation.

He would be finished off in an instant, no matter which method he chose.
He would not suffer for long. At least, he didn't think so. That was why
he knew it was easier to choose death. It was as obvious as the sun
rising from the east.

\emph{But I don't want to.} Inukashi clenched his fist, though it was still
very small. \emph{I won't be finished off so easily. I won't choose death of
my own will. I'll survive and I'll do whatever it takes.}

\emph{I'll step up to the challenge. I'll challenge the fate which left me
abandoned on the road in the West Block; I'll challenge the world that
makes survival such a difficulty; I'll challenge the guys who made the
world like this---and I'll win. In fact, I'm winning right now by
continuing to survive.}

As a young child, Inukashi did not know how to speak. He did not know
how to put his heart's resolve into words and tell it to others. But the
old man nevertheless smiled serenely and placed a hand on Inukashi's
head.

"I have a feeling you'd be able to do it," he'd murmured.

It was about a year later, in the onset of winter, when the old man
disappeared. His bed was already empty when Inukashi woke up that
morning, and the old man was nowhere to be seen in the ruins. But
Inukashi didn't particularly go on a frantic search, either. Somewhere
in his heart he had given up, knowing it was no use. He was
disconcerted, but he was not lonely. His dogs were with him. As long as
his dogs were here, he was alright.

\emph{Gramps probably knew that, too. He knew well when he wandered off. Did
he sense the end of his life coming, or did he find a place he ought to
go? Whichever it was, he's probably out there somewhere now, a part of
the earth. People can't turn into the stars in the sky, but they can
always return to the earth. They can leave their memories behind, too.}

\emph{Thanks, Gramps. I'll never forget everything you did for me. Once in a
while, I'll be sure to remember you and recall some fond memories. But
you know, your face is getting blurry lately. I can still remember the
little things: your scraggly white beard; how your balding forehead was
shining pink; how your right eyebrow was unusually thick; how you were
always soft-spoken. I remember those things so clearly, but I can't seem
to recall your face. I wonder why? But, well, there you have it. I
remembered you today. That's enough, right?}

He gave the pot another stir with the spatula.

A patched dog barked. The other dogs chimed in and began barking, too.

"I know, I know. Right, let's get this feast started. Gather 'round, you
guys. But you gotta wait 'til it cools down before you eat it. You'll
have a hell of a time later if you end up burning your tongue."

By the time Inukashi had finished doling out the soup into the dog
dishes and begun to sip his own portion of meaty broth, he had
completely forgotten about the old man.

The past tended to get in the way of things. If he kept turning back, he
would not be able to move forward.

Inukashi ate a piece of meat and savoured the taste and sensation of it
in his mouth. He felt like it was a waste to swallow it; he wanted to
savour it forever. But the tiny piece all too easily slid down his
throat and settled in his stomach. By the time he finished the rich,
meaty soup, however, he felt warm down to his very bones. Still
radiating warmth, he lay down on the bed. The puppies squirmed over each
other to climb up, and licked him all over the face. Their small pink
tongues were comforting.

He was happy. He even felt like he had taken all the happiness in the
world for himself. Immersed in bliss, Inukashi dropped off to sleep.

He felt nauseous. He was afraid that the ceiling would start spinning
again if he opened his eyes.

\emph{What's gotten into me?}

A part of his head started throbbing dully. His body felt even heavier.
He was breaking into a sweat. It was an unnatural feverishness, so
different from the warmth of the night before.

The puppies' tongues were no comfort to him, either. His skin only
smarted irritably. He had never once felt his dogs irksome before.

No number of deep breaths seemed to improve his condition.

What's gotten into me?

Right after he questioned himself, he felt a chill run down his back.
Fear ignited deep in his heart.

\emph{This is beyond serious.}

\emph{What if I find I can't get up at all? What if I can't even move?}

It was fatal to fall ill in the West Block. It didn't take much to kill
a West Block dweller, deprived of decent food and living in squalor as
he was. Just a small injury was enough: a deep cut on the pinkie, a hard
scrape along the forefoot. So was a small ailment: dizziness, nausea,
fever---anything to keep one in bed. Someone who had definitely been alive
three days ago could be lying on the road as a corpse today. This kind
of thing happened every day.

\emph{Damnit.}

Inukashi bit his lip, and lifted his upper body up. He leaned against
the wall, and let out a long breath.

\emph{So yesterday's meat was my last supper, huh. Damnit. This isn't even
funny. I'm not gonna let this take me out.}

He bit his lip harder. The taste of blood spread inside his mouth. He
muttered "damnit" once more to himself for good measure. But no strength
came to him. It was wearisome to lift even one finger. If he forced
himself to get up, he was overcome with simultaneous dizziness and
nausea. He collapsed on the bed again.

His consciousness began to fade.

A chill wind whistled through a crack in the window. The cold drew
Inukashi back to reality. He wanted to scream. He wanted to scream for
help, as loudly as he could.

\emph{Somebody help me\el someone, please.}

A dog roused itself in a corner of the room and approached him. It sat
on its haunches at his bedside, and looked up at him. It was a large
brown dog, an offspring of Inukashi's mother's line. It had inherited
her intelligence and deep, dark eyes.

The dog sat still with its ears pricked, as if waiting for Inukashi's
command.

"\el I want you to\el call them for me\el " He pointed out the window.

Beyond was a spread of wintry sky, heavy with snow clouds. The light
struggled to get through the clouds, and barely reached the ground
below. Once more, the West Block would end the day just as frozen as it
had been at the beginning.

The dog pushed open the dilapidated door and left the room. Its rusty
hinges screeched unpleasantly. Inukashi was supposed to be used to the
sound, yet it stabbed at his eardrums and aggravated his nausea.

"Please. Call them\el "

\emph{Help me.}

The dog scrambled down the stairs. The puppies huddled together and
whined pitifully.

\myspace

He was dreaming. Dreaming of long ago. \emph{How many years back?}

The old man had long disappeared. Inukashi was alone---but with his dogs.
He'd finally gotten the hang of procuring himself some food scraps, as
well as taught himself how to cook it or sell it off.

He was descending a set of stairs.

They were concrete steps leading underground, not as damaged as the ones
in Inukashi's dwelling. The building was mostly in ruins above ground,
but it looked like the portions beneath were still intact. Once Inukashi
reached the bottom, he was faced with a door. He extended a cautious
hand to grip the handle.

The building was located near the entrance of the West Block. The
surrounding woods nearby were dotted with barracks. Also nearby loomed
the Holy City, No. 6. To be exact, it was No. 6's outer wall. The outer
wall made of special alloy gleamed golden as it loomed before him. The
wall made a clear division between "here" and "there", heaven and hell.
Nothing was lacking within the walls: warm beds, abundant food,
leading-edge medical facilities, comfortable residences. There were no
threats to life, and one could live without even knowing what hunger or
cold was. Inukashi had also heard that suffering and fear didn't even
exist there.

A utopia, worthy of its title of the Holy City.

Inukashi did not hear much of No. 6 in the West Block. Everyone fell
silent, and refused to touch upon the topic as if its very name were
taboo.

\emph{Fishy business}, Inukashi had thought---or rather, felt.

Utopias and Holy Cities simply did not exist in this world. No. 6 was a
city-state founded by humans. As long as humans were involved in it,
something had to come apart. \emph{Your ideal isn't my perfection, and
happiness for me might be something you can't stand. That's the human
world for ya. Humans can't create a utopia. The best they'd be able to
do is quarrel, clash, bend a little for the other person, and then
settle down somewhere inbetween. That's it.}

\emph{No. 6? That place is so fishy it makes my hair stand on end. The smart
thing to do is stay the hell away.}

That was why Inukashi never ventured close to this place. He hated
seeing No. 6's wall in his line of sight. If he had experienced a better
harvest that day, he probably wouldn't have gone anywhere near that
place. But an entire day of wandering in the West Block had only gotten
him one or two vegetable ends and a single strip of dried meat. That was
barely enough to nourish himself, much less his dogs. At the time,
Inukashi still did not know how to get his hands on periodic supplies of
leftover food. His only choice was to clutch his empty stomach and
scrounge desperately. At the market, he earned a sound beating from the
butcher's club; at the tavern, the female manager shrieked curses at
him, but he went on unfazed. Inukashi was long used to the abuse, the
insults, and the physical pain.

\emph{I have to do something about this hunger.}

When he came to, he had been standing in the wood. It looked like he had
almost subconsciously walked this way, intending to find even a single
nut to pick up. This was where he found the crumbling abandoned
building. He placed a casual hand on the wall, and it slid aside without
any resistance to reveal stairs leading to the basement.

Inukashi twitched his nose. He squinted his eyes, and strained his ears.

He neither sensed nor smelled the presence of anyone.

\emph{Completely abandoned. huh.}

He carefully descended, step by step.

Inukashi knew that a strange old woman and a boy (her grandson, he
assumed) was supposed to be living here. He had seen them twice before.
The old woman had a harsh look about her eyes, as if she'd never smiled
once in her life.

\emph{I know, I know. I remember.}

\emph{That old lady was funny in the head. She attacked someone important from
No. 6---the mayor or chairman or whatever. All on her own, at that. She
hobbled towards him, knife in hand, and was shot to death. Wait---or did
she get arrested and shot? Whatever it was, she was finished off pretty
quick. Not much of a surprise, haha.}

Inukashi sneered at her mentally. It was a rumour he'd heard in the
marketplace. He was unsure of its validity.

His stomach growled. It sounded like a cry for help.

\emph{I can't take it anymore. Give me food. Hurry, hurry, hurry, hurry,
hurry.}

\emph{Damnit, isn't there something? Mouldy bread, rotting meat, I don't care.
Something to quiet my stomach down.}

He gripped the door handle. The door was unlocked. It was a little
heavy, but with a little push, it opened without much resistance.

"Ho!" A sound not quite resembling a breath or an utterance escaped his
throat. "The heck is this?"

There were piles of books as far as he could see. They were here and
there, everywhere, piled up neatly or scattered carelessly across the
floor. The floor itself was almost indiscernible. The room seemed to
contain nothing but books.

This moment was Inukashi's first encounter with books. He knew words; he
could also write, as long as it wasn't too difficult. The old man had
taught him. But Inukashi had no knowledge whatsoever about books. He had
never heard the word "book", nor did he know that it referred to these
bound sheets of paper with printed words. He had no clue where to begin
understanding them. He perceived instantly that they weren't food. Just
to make sure, he picked a book from a pile near the door, and took a
bite. He had chosen it because the ripe apple pictured on its white
background looked delicious.

\emph{Horrible.}

Inukashi wiped his mouth with the back of his hand, and threw it aside.
\emph{Tough, dry, and definitely not something I can eat.}

He moved forward, kicking the fallen books out of the way. There only
seemed to be books in this place.

\emph{Tsk. All that work gone to waste.} Inukashi clicked his tongue and was
about to turn on his heel when his heart beat a trembling pulse. He had
found something other than books.

It was placed on a shelf (filled with books)---some of the volumes had
been cleared away to make space for it. It was a small silver box,
sitting on top of a towel.

\mybreak

\emph{What is this? Is someone living here?}

He twitched his nose again. Like before, he did not smell anything.
Inukashi took down the small silver box from the shelf. He opened the
lid.

He found himself letting out a whistle.

\emph{Oh, I see. This is quite a treasure. I've found myself some booty.}

The box turned out to be an emergency kit, with bandages, pincers,
gauze, and a number of medicines stored neatly inside. There was even a
scalpel. It looked like something that had been used in No. 6. Inukashi
had no clue about how this ended up here. He had no intentions of
finding out, either. He didn't care about its journey or story. What
mattered was that he was holding it in his own hands. That was all.

Medical items of any kind were coveted in the West Block. Disinfectant,
especially, was traded at a high price. Sometimes a small bottle of
disinfectant could fetch up to two silver coins.

Inukashi brought his nose close.

\emph{This is a hundred-percent pure, with no additives---the good stuff. Look
at the way it stings my nose. Heh, forget silver---this might just
transform into a gold coin if I'm lucky. I made a good find. My luck is
finally turning around.}

Inukashi grinned to himself as he shut the lid of the box. He was about
to lift it up in his arms when he noticed a small table covered with
books.

On top, there was a small mouse. It was not alive. It was skilfully
wrought, but it was clearly man-made. Inukashi leaned forward, still
cradling the box. The belly of the mouse peeled back to reveal its
complex inner parts.

\emph{A robot?}

Inukashi was about to lean further in when he felt a violent chill. He
felt goosebumps forming on his back.

"Don't move," he heard a voice by his ear. This time, the skin on every
inch of his body bristled. It was not because a blade had been pressed
against his neck. It was because the voice was completely void of
warmth. All emotion in it was suspended frozen. Its icy blast chilled
even Inukashi's own emotions.

It was the voice of a murderer.

It was the voice of one who could take a human life with no hesitation,
no sway of emotion.

\emph{And---and on top of that---this guy got behind me.}

If Inukashi could swear on anything, it was his ability to sense the
presence of people. His sixth sense was as good as any dog's. The more
emotional a person was, the more Inukashi could feel the presence on his
skin. Thanks to this ability, he had been able to escape danger and
dispute time and time again. But this time, he had felt nothing. He was
not even able to discern the slightest from the person creeping up
behind him.

\emph{Maybe he's not human? A dead man come crawling out of the depths of
Hell? A demon? A shapeshifter?}

His teeth refused to come together. His molars chattered, making a
strangely mechanical sound. It echoed deep in his ears.

\emph{Click-click. Click-click.}

\emph{Click-click. Click-click.}

Inukashi gritted his teeth, and clenched his stomach.

"W-Wait a minute here. I was only\el "

"Put the box back."

"A-Alright, alright! I'll do as you say." Trembling, Inukashi replaced
the box on the shelf.

"Th\el there. I returned it. That's enough, right?"

"Enough? Are you kidding me?"

The blade moved ever so slightly. He felt a jolt of sharp pain. He
struggled to rein in the scream that was about to tear through his
throat. He was sweating in his armpits.

"Theft amounts to death in this place. You should have no complaints
about being killed."

"Y-Yeah, but I mean, I can't complain if I've already been killed,
right? H-Hey, I live in the ruins, by the way\el know about it? It's on
the far end of here, the ruins of a hotel. That's my place. I live there
with my dogs. My name is\el uh, well, I don't have a name, but you
know---who needs one in a place like this, right? People call me
\emph{inukashi}---the Dogkeeper. Dogs are part of my business. Ha ha, but who
cares about my name, right? I kinda like it, though. Ha ha. So if you
ever wanna call me by name, it's Inukashi."

Inukashi kept talking. He felt like if he closed his mouth, his throat
would be slashed in the silence that fell afterwards.

"Hey, come on. I'm begging ya. I'll apologize, so will you just forgive
me? Please? I'm sorry. I'll never do it again," he tried imploring
pathetically. "Don't kill me. I'm on my knees. Help me, please. I\el I
don't wanna die yet. I really don't wanna die. I'm sorry, I'm so sorry.
I'll never touch your stuff again. I promise. Please, just don't kill
me."

Inukashi wasn't putting on an act. He was earnestly pleading for his
life.

\emph{Don't kill me, please. Let me go.}

\emph{Please, please, please, please, please, please.}

The knife was lifted. Suddenly, the base of his neck felt much lighter.
Inukashi let out a long breath. His neck muscles hurt, likely from being
taut this whole time. The spot on his neck throbbed slightly when he
pressed it with his hand, but no blood came off.

The wielder of the knife had made a slight cut, as shallow as the mere
first layer of skin on the neck, to freeze his victim in fear. Not
enough for it to bleed, but just enough to make the victim feel pain.

\emph{I knew it. The guy behind me is no human. He's a dead man, a demon, a
shapeshifter\el }

Inukashi turned around slowly, still holding his neck. The truth was
that he did not want to turn around. He wanted to beeline right out of
the place. But his feet hesitated; he felt like the moment he turned his
back and broke into a run, a knife would be plunged deep into his back.

He slowly, slowly turned around.

\emph{Huh?}

He had to blink. He knew his mouth was hanging open.

The figure in front of him was no dead man, demon, or shapeshifter. It
was a boy wearing a plaid shirt. It might have been a girl. No, it was a
boy. A girl couldn't produce an icy voice like that. The boy only looked
like a girl.

The boy had long hair which came down to his shoulders and hid his
forehead. His small, white face was almost uncannily proportionate.
Inukashi had imagined the boy's eyes to be glittering full of murderous
intent, but they were serene and inscrutable.

The boy had eyes of a strange colour.

An elegant dark grey. It was Inukashi's first time seeing such a colour.

The boy seemed to be taller than Inukashi, but he figured their ages
were about the same. But Inukashi was also unsure of his own age.

The boy sheathed his knife, still wearing a blank expression. Inukashi
felt overwhelming relief. Then, he felt irritation at himself for being
relieved.

\emph{I was being threatened by this twig?} He wanted to click his tongue in
frustration. \emph{Geez, I'd never be able to live that down.}

"You could have picked a better shirt to wear." Inukashi wore a smirk as
he jerked his chin. He intended to look smooth and unruffled. "But the
quality doesn't look half-bad. Not something you'd come across often in
the West Block."

"It's a borrowed shirt."

"Borrowed? Where did you borrow such a good piece of clothing, huh?
Don't tell me you got it from No. 6."

He had meant it as a joke, but once he put it into words, he felt like
that was the only possibility. The shirt's superior quality was evident
from first glance. It looked soft to the touch, warm, and durable. The
emergency kit he had just put back on the shelf was also a product from
inside the walls, no doubt about it.

"Who the hell are you? Don't tell me you came from that---" Inukashi
trailed off. He had just seen the boy pick a strip of dried meat out of
his breast pocket and bite on the end of it.

"Hey\el don't tell me that's\el " Inukashi scrambled through the bag
hanging from his waist. It was empty. He had most definitely put dried
meat in there, but it was gone.

"I'm taking this", the boy said. "As compensation for your stealing."

"B-Bullshit! Who's the thief now? Give it back, that's my meat! Give it
back!"

\emph{Heh.} The boy laughed. His smile seemed both innocent and carefree.

"Wanna try to take it back by force, Inukashi?"

"Gh\el " Inukashi bit his lip. This was not someone he could win against
head-on---his instincts were telling him so.

\emph{Damnit, I shoulda brought my dogs. If I had them with me, I could take
him down in one bite.}

But his dogs were not here. Inukashi was alone.

"\el Fine. Keep it."

"There's a good boy. You should know when to listen. It'll help you live
longer."

"Damnit, stop making fun of me!" \emph{Just watch. I'll get my revenge.}

Inukashi retreated to the door. He grabbed the handle. There was no need
to stay here longer than needed.

The boy sat on top of a pile of books and said nothing. Only his gaze
was fixed on Inukashi. Inukashi's movements were completely surrendered
by that gaze. His arms and legs turned stiff and awkward, and they
refused to move smoothly.

"\el What the hell are you\el ?" He repeated his question from some
moments before. This time, it was more serious. "Do you live here?"

"Yeah."

He did not expect a reply.

"Alone?"

"Yeah."

"This house has been abandoned for ages. There hasn't been anyone living
in it for years---at least, there wasn't supposed to be. Where the hell
did you come from? And why do you have a shirt and emergency kit that's
clearly from No. 6? Oh, and that mouse doll---what is that? It looks like
a robot. Don't tell me you built that thing?"

Inukashi knew he had to run away as soon as possible, but his mouth kept
moving. Question after question escaped his lips.

"You talk a lot, don't you? I'm surprised you haven't bitten your tongue
already from talking so much." The boy shook his head. An amused smile
crossed his face.

Inukashi found himself almost attracted to him. His heart beat faster.

\emph{This guy is dangerous. More dangerous than a murderer, and hell of a lot
more hassle.} This was another gut instinct of his. And he was sure he
wasn't off the mark.

\emph{Don't associate with him. Get away from here, and never come back
again}---a voice of warning echoed in his ears. Inukashi usually obeyed the
voice promptly, but this time he ignored it and continued to question
the boy.

"What's your name?"

The boy tilted his head very slightly. "Nezumi."

His name, so unexpectedly and promptly given, seemed unusual for a
human.

"What kind of name is that? Is it your real name?"

"You could say the same about yours, Dogkeeper. It's not a proper name,
for sure."

"Hmph\el well, you could say that. Nezumi, huh. At least it's easy to
memorize."

"So you plan on remembering it?"

"Erm\el well\el " Inukashi felt like he was being toyed with. If he
didn't wrap it up soon, he'd get sucked right into Nezumi's plot. Like
an insect caught in a spider's web, he'd be immobilized and would
eventually wither.

\emph{Danger, danger, danger.}

"Well, see ya, Nezumi. If we're lucky, maybe we'll meet again."

"If we're lucky."

\emph{To hell with luck. I'll make sure I'll never see your face again.}

Inukashi slid his hand behind him and opened the door, and slipped
outside. As soon as he was out, he sprinted up the stairs as fast as he
could. His feet froze halfway. About midway up the stairs, Inukashi
found himself turning around. He could see the rusty door.

"Nezumi, huh," he muttered.

\emph{Would I really be able to get away with not ever seeing you again?}

\emph{If we're lucky.}

The line he'd heard only moments before still echoed inside his head.

\emph{If we're lucky.}

\emph{We probably will meet again.} He had a sudden feeling. It was almost
closer to a firm belief. From hereon, he would see that boy time and
time again. They would form a connection.

His body almost recoiled in disgust. But at the base of that disgust
lurked something slightly tender. He muttered it under his breath again.

"Nezumi, huh."

\mybreak

"Did you call me?"

He heard an uncannily crisp answer.

\emph{Huh?}

"Did you call me, Inukashi?"

He opened his eyes. It was bright.

His room, tucked away in a corner of the ruins, was filled with light.
Beyond the glass pane of the window he could see the blue sky behind a
crack in the clouds.

The blue soaked into his retinas.

Nezumi was peering into his face. Their eyes met. His eyes were the same
elegant dark grey as the time they had first met.

"\el What\el are you doing here\el ?"

"Huh? What is this treatment? You're the one who called. Using this guy
as a messenger, remember?" A brown dog wagged its tail from beside
Nezumi.

"C\el Called? You? Psh, of course not. I was calling for\el "

"Then who were you calling for?"

"I was\el "

"Inukashi, are you awake?" A head of white hair peeped out from behind
Nezumi.

"Shion."

"Yep, it's me. You must have had a tough time. It's alright now. We'll
make you better in no time." Shion smiled.

Inukashi came close to tears. He stopped himself in time from clinging
onto Shion and sobbing out loud.

\emph{Shion, I was scared. I thought I was going to die. I was so scared, so
lonely, and I didn't know what to do. So I called you.}

"Here, drink this." Shion offered him a chipped bowl. It contained a
thick, green liquid. Its dirt-like smell stung his nose.

"What the\el "

"It's a medicinal herb. I found a book about oriental medicine in
Nezumi's bookshelf and thought I'd give it a chance. I hunted around in
the woods and found a lot of stuff. This will calm your nausea down, and
it'll also help you recover from exhaustion."

"\el Huh? Oriental?"

"It's a type of medicine that was passed down in the East. The book says
it's supposed to heighten your body's overall healing ability. Come on,
just give it a try."

"Pinch your nose. It'll make it bearable," Nezumi said. Inukashi pinched
his nose as he was told, and swallowed the drink in one gulp. He didn't
think it tasted half bad. The bitterness that slid down his throat
seemed to give him strength. He let out a long exhale.

\emph{They actually came for me. They got my SOS. I begged for them without
offering anything in return.}

Shion placed a hand on Inukashi's forehead. It felt cool and soothing.

"You'd better stay in bed for a while. You haven't got pneumonia, but
you have all the symptoms of a cold. And anemia, as well---"

"If I get trapped in bed, my dogs'll starve to death."

"We'll do something about it. I'll take over your rental duties, and
Nezumi will keep you supplied with food. Right?"

Nezumi shrugged lightly. "Sure, I can do something about it. But you owe
me for this, Inukashi. I'm charging interest."

Inukashi managed a faint smile from where he lay. Nezumi's remarks,
which usually irritated him to no end, sounded unbelievably gentle now.

\emph{There's something seriously wrong with me. If I cry here now, who knows
how much I'll be made fun of afterwards. If I'm going to cry, it has to
be when only Shion's around. Hold it in. Tears, don't spill over.}

"Say, Inukashi." Shion smiled even more gently. "I don't think you need
to worry about your cold, judging by your physical strength. But the
wound on your toe is another story."

"Toe? Oh, my right big toe, right? It's been hurting for a while."
Inukashi got injured all the time. Unless it was a considerably large
injury, he usually just licked it better.

"It's festering," Shion pointed out. "If you leave it like this, it'll
swell up with pus and you likely won't be able to walk. So---"

"So?"

"You need an operation."

Shion took out that same emergency kit. It looked no older than when
Inukashi had first seen it.

"Shion, uh, what are you---?"

"I'm going to cut open the wound, extract the pus, disinfect it, and
then sew it back up. That's it. It'll be over in a flash."

Shion was already wearing rubber gloves and holding a scalpel. It was a
small silver blade, sharpened to perfection. Inukashi felt his spine
growing cold.

"C-Cut open? Wait, wait a second, Shion. Hold on. Wh---What about
painkillers? Sleeping gas?"

"I don't have any."

"Whaddoyou mean, you don't---"

"It's alright. It'll be over quickly. Sorry, Nezumi, could you hold
Inukashi down? Make sure he doesn't move."

"Gotcha."

Nezumi held Inukashi's hips down with both hands. Inukashi's lower body
was immobilized completely.

"I think this might be news to you, Inukashi," Nezumi smiled in a
strangely provocative way. "But Shion loves to sew people up. He may
look innocent, but he's a huge sadist."

"Wha---stop it!" Inukashi yelled. "I'm scared! Help!" It was now beyond
Inukashi's power to put on a brave face. He was close to crying.

"Settle down," Nezumi said testily. "Just listen to what he says.
Besides, even I can tell that this wound is pretty serious. You could be
risking your life if you leave it untreated. I know Shion didn't mention
it outright, but maybe this is what's behind your sickness."

"I don't care what's behind it. It hurts! \emph{Stop}," he wailed. "Somebody
help me! Shion, have mercy!"

"It'll be alright. Don't move," Shion said. "Oh, look, see? All this pus
has built up inside. I'm surprised you could walk with this. You must've
turned numb to the pain. Okay, it'll be over soon."

"I'm \emph{not} numb," Inukashi sobbed. "\emph{Owww}, don't sew it! It hurts!"

"Don't cry," Nezumi said. "There's a good boy. I'll give you a reward."

A soft melody flowed forth from Nezumi's lips. It gently rocked
Inukashi's heart. For an instant, Inukashi had turned back into an
infant and was being held in someone's arms. He was freed from fear or
suffering. He was in a place of peaceful sleep.

"There's a good boy. Don't think of anything, just sleep. We'll protect
you with everything we've got. We won't hand you over to the Reaper, no
matter what happens."

\emph{We'll protect you with everything we've got.}

Inukashi opened his eyes and looked at Nezumi. Then, he looked at
Shion's profile as the boy crouched at his feet. Both of their faces
were grave. Numerous streaks of sweat marked Shion's cheek, and formed
droplets at his chin.

\emph{We'll protect you with everything we've got.}

It wasn't a lie.

This world was ridden with lies, but Nezumi's words were true. Even if
everything in this world were a fabrication, Inukashi knew he could
believe those words without fail.

Inukashi could bear no more. His tears spilled over. They kept flowing.
He felt like he was drowning in tears.

\emph{Bastards, making me cry.}

Inukashi pressed both fists against his eyes, and cried silently.

The blue sky was still outside his window.