% !TeX spellcheck = en_US

\chapter{A song from the past}

\lettrine{N}{ezumi lifted} his face. His brow furrowed slightly.

"What? What did you just say, Shion?"

"I said I wanted to see."

Shion sipped the hot water in his cup. The bit of sugar mixed into it
made it taste slightly sweet. Sugar was considered a luxury item in the
West Block. Shion himself had not had flavoured water in a long time.

"I said I wanted to watch you perform onstage."

"Why?"

"Why, well... no particular reason. I just want to see."

Nezumi drew his chin back, and closed the book he was reading with a
rather rough snap.

"That's not an answer. If you're looking for something to kill your time
with, consider other options."

"I don't have enough free time to kill. I have my dog-washing job at
least twice a week, and I've promised to read picture books to Kalan and
the rest of the kids. I've also started working at Rikiga-san's
part-time. I'm actually about to go out now."

"Working part-time? At that old man's place? I hope it's not something
as terribly respectable as taking photos of naked women."

"No, I just run errands and do miscellaneous work. Stuff like sorting
receipts and cleaning the office. Rikiga-san actually runs a pretty wide
variety of businesses. I never knew."

"Well, I bet my mice would sprout wings and fly before that old man
starts running any \emph{decent} trade. Hah! You'd better be careful, Shion.
Who knows when some woman might come attacking you with a knife like she
did to Rikiga."

"I don't think that would be very likely," Shion said sceptically.~

"Rikiga-san has been saying for a while that he's had enough of women."

"That's all talk. He loves his women. It runs in his blood. He can't
live without 'em. But if you were to put alcohol and women in a balance,
he'd probably choose alcohol after a long deliberation and a ton of
griping."

"You certainly don't sugar-coat your words, do you?"

"I just can't whore out my kindness like you do."

Nezumi stood up. A small brown creature hopped up onto his shoulder as
if it had been waiting. It was Cravat, a mouse which Shion had named for
the colour of its fur.

"Is it somehow a bad thing to be nice to everyone?" Shion's words grew
sharp. He felt a restless ripple deep inside his chest. The ripple made
it hard to breathe. This feeling was something he would never have known
if he had remained in No. 6. Various emotions writhed inside him. They
cast one pattern after another like a kaleidoscope.

Since beginning his life in the West Block, Shion found himself startled
by the turbulence and wealth of his own emotions. His heart was shedding
its outer layer. His soul was reviving as it ripped through its tense,
rigid outer shell.

Nezumi put away the book on the shelf, and picked up his cape.

"Kind words that don't hurt anyone---what meaning do they have?" Nezumi
draped the superfibre cloth over his shoulders and donned his gloves.
"Everything that comes out of your mouth is gentle and lukewarm. Like
the chirping of birds or a chorus of insects. It's beautiful, but it
doesn't lodge itself anywhere. Not even in yourself."

"Nezumi---"

"Shion, you're not kind. You just don't want to get hurt yourself.
That's why you take all the thorns out of your words. With no sense of
responsibility, you spew words that do neither harm nor good. Admit
it---I'm right."

Shion could not deny it completely. He could neither show his anger nor
protest that Nezumi was insulting him. Nezumi's words were full of
thorns. If Shion touched them out of carelessness, they would pierce his
fingertips and draw blood. Compared to that, perhaps his own words were
indeed lukewarm.

Shion didn't think that it was an evil thing to avoid hurting anyone.
Nor did he think that gentleness was useless. He also knew that Nezumi
was not criticizing his kindness.

Gentle words that harmed no one, and words that did not carry the weight
of their consequences were rife in No. 6.

\emph{My, how pitiful. Someone should do something about it.}

\emph{It's unfortunate. My heart goes out to them.}

\emph{We will make our utmost efforts with our very hearts and souls.}

\emph{Everyone, we must all be friendly to each other.}

In such an environment, he had unconsciously grown detached from the
meaning and weight of his words. But there was absolutely no value in
superficial kindness and concern, promises and love. They were just
repulsive. Shion had already realized it without Nezumi pointing it out.
He knew, but he wished he could pretend he didn't.

Nezumi had plainly seen the thoughts bubbling from the depths of Shion's
heart. He had felt irritated at Shion's lowliness and artificial
kindness, resulting in his thorny words. Shion knew he deserved to be
pricked by them. But---

"I'm always serious when I'm talking to you."

Nezumi turned around.

"Hm? What did you say?"

"No..." If he muddled his answer now, perhaps it would agitate~

Nezumi's irritation even more. But Shion found his tongue heavy and
unwilling to move.

\emph{I'm standing here and facing you in all seriousness.} Those words were
heavy---so heavy that Shion found them hard to vocalize.

Cravat chirruped from his perch on Nezumi's shoulder.

\emph{Chit-chit! Cheep-cheep-cheep!}

"Oh, crap. I'm late again." Nezumi's tone was calm. There was no sign of
the irritation from moments before.

"See ya, Shion. Like I said, be careful when you're working at that old
man's place." With that, Nezumi left. Shion was left alone---well, perhaps
not so alone. Hamlet and Tsukiyo, the two mice, were asleep in his lap.

Shion stroked their heads with his finger, and took another slow sip of
his sweetened hot water. It was delicious. He figured the expression
"sweet nectar" probably referred to a taste like this.

The days Shion spent in the West Block had honed his senses swiftly, and
without his knowledge: sight, hearing, smell, touch, and taste. Back
when he was in the city of No. 6, he used to eat as much "delicious"
food as he wanted, until he was full. He had been able to. If he should
so desire, he was able to get his hands on any meat, vegetable, fish,
sweets, or fruits with no limitations. Following his move to Lost Town,
his selection of food was narrowed considerably compared to his time in
Chronos, but he seldom felt deprived.

His mother Karan's cakes and freshly-baked breads were simple but
delectable, and he never tired of eating them. But Shion felt that even
that taste did not penetrate as deeply into his heart as the taste of
this hot water.~

He drained his cup. The warmth reached all the way to his~

fingertips, and strength filled his body.

"Alright, now it's time for me to go, too."

Shion cautiously transferred Hamlet and Tsukiyo to the bed and stood up.

"But you know, don't you think I've learned a lot in my own way since I
came here? I can even sort handwritten receipts. And he says I do wipe
the floor and wash the dishes as well as any full-fledged man.
Full-fledged. I'm allowed to be a little proud of myself, right?"

\emph{I'm using my own body and brain to do work and earn its rewards. I'm
allowed to be proud, no matter what kind of job, no matter how small the
wages. Right?}

Tsukiyo lifted his head and twitched his ears as if to agree.

\emph{Geez.} Nezumi ground his molars. \emph{Hopeless guy}, he reprimanded mentally.
He was not referring to Shion. He was talking about himself. Cravat
cried softly from within his cape.

\emph{Skreet-skreet! Cheep-cheep-cheep!}

"Shut up. You don't have to tell me; I already know. I just took out my
frustrations on Shion back there. I know."

Sometimes---though it was very rare---Nezumi's emotions grew unstable when
he was around Shion. His self-restraint loosened, and his thoughts
issued unrefined from his lips. They collided, sending sparks and sprays
flying. Nezumi never intended to condemn Shion. He knew that he wasn't
just or strong enough himself to have the right to do so. But he wavered
when he was with Shion.

His heart, which wanted to hate and reject all of No. 6, wavered.

No. 6. The most detestable city-state in this whole world. It was no
utopia or holy city. Those names were but a facade. As soon as he tore
away its thin hide, the monster would show its true figure.

A man-eating monster.

It never hesitated to destroy its surrounding states and massacre entire
tribes if it meant prosperity for itself. It plundered, leeched, and
dominated.

\emph{Someday, I'll take it down.} For Nezumi, No. 6 was an opponent he had to
take down with his own hands, an existence that needed to disappear from
this world.

But inside this grotesque monster lived a boy like Shion. Shion had let
an intruder, a VC---No. 6's term for violent convicts---into his home,
treated his wounds, provided him food and a place to sleep, and as a
result, had lost his secure life as an elite. Shion had lost everything,
and yet still confessed to Nezumi.

\emph{No matter how many times I'd return to that night, I'd do the same
thing again. I'd open the window, and wait for you.}

They were bare and honest words. They pierced through his heart. For an
instant, Nezumi could not help but stare at Shion without even blinking.
Shion definitely did not use words of superficial kindness, and Nezumi
was sure the people around him were the same.

Shion's mother harboured the unshakable belief that her son would
return, and thought of him constantly while she waited. According to the
mice Nezumi had sent out as messengers, the muffins and bread that she
baked were so delicious, they were enough to make one's cheeks swell in
anticipation. And there was that girl with her unwavering love.

Those were the kind of people around Shion---those who exerted every
effort in living their daily lives. They were honest with their words,
did not condescend on others, and lived without losing their dignity.
Those people lived inside that monster.

If he had not met Shion, he would never even have imagined this. He
would have continued loathing every citizen of No. 6 and wished for the
city's ruin.

But he had met him.

He had come to know.

\emph{Could I still hate, even with that knowledge?}

He wavered. He lost composure. He grew indecisive.

Nezumi paused and turned around. The outer walls of No. 6 reflected the
fading light of dusk. Its reddish glow made him think of fire. Long,
long ago, he had seen this colour, and it had burned an imprint in his
memories. It was neither crimson, burgundy, nor red. It was a mixture of
all of them---a colour that could be described no better than chaos.

The colour still lingered in Nezumi's vision even after he had come out
of the woods and passed through the marketplace. He would probably never
forget it for the rest of his life.

It was burning. Houses, trees, his newborn sister, and his mother who
held her. All burning.

"Run!" his mother had screamed as she burned. Her beautiful hair, her
skin, her body, was a mass of flames. His father had covered his
mother's body with his own, frantically flapping his hands as he tried
to put out the flames. A No. 6 soldier pointed his flamethrower at them.

More fire burst forth.

His father, mother, and younger sister were swallowed up in the flames,
which burned high and fierce. Nezumi himself was overwhelmed with a
shock of heat and pain and was thrown on the ground.

\emph{It hurts. It's hot. I'm scared.}

\emph{Hot, hot, hot, hot, hot, hot, hot.}

"Run!" His father's yell pierced through the flames. "Run! Even if none
of us can, at least you---"

Then, everything fell apart. Nezumi had seen everything. He was supposed
to have seen everything. But he had no recollection. The only things he
remembered were the colour of the raging flames and the roaring---the
sound of whirling flames was just that, a beast's roar---and an old
woman's back.

He was being carried on an old woman's back as she ran. Her back was
bony, and even at his age, Nezumi felt it very small.~

But it was sturdy. Her back and her legs were stout.

The old woman ran, tearing through the flying flames, the winds swept up
by them, and past No. 6 soldiers. She ran through a tangle of bushes
down a wild path and crossed a swift stream.

Nezumi had lived thanks to this old woman. He had survived.

Once Nezumi had recovered from his burns enough to move, the old woman
immediately began making preparations for a journey.

"We must distance ourselves from the devil now," the woman muttered as
if to herself. "But we will return. We will return to exact our
revenge."

While they wandered from the rocky barrens to the lower lands which
would later be known as the West Block, the old woman spoke night and
day.

She spoke, over and over, of the last moments of the Forest~

People, the inhumane acts which would later be engraved forever into the
memories of a select few as an incident called the Mao Massacre. Her
stories continued even after they had settled in a basement vault in the
West Block. Nezumi grew up buried in books, listening to this old
woman's stories. He never felt he lacked anything. But the wound on his
back ached as if in response to the old woman's tales. His mother's
voice and his father's screams echoed in his mind. It was painful for
him.

\emph{Run!}

\emph{Even if none of us can, at least you---}

Each time he recalled it, his wound throbbed harder. It was like his
scar was writhing about. The old woman always looked down at Nezumi in
silence as he gritted his teeth and endured the pain. Her gaze was cool
and sapped of emotion.

The old woman was also reaching her mental limit. Her own hatred,
despair, and anguish was threatening to crush her. She was fighting
dangerously close to the border of giving into death's temptation.
Nezumi could sense with instinct, not logic, the storm of emotions
brewing inside her.

That night, they were sleeping outside on a stretch of wasteland on the
outskirts of the West Block. It was a few days before they ended up
settling there permanently. As usual, they started a campfire and slept
close to it. For a while after their escape, Nezumi's whole body seized
up when he saw fire. That colour, that roar, those screams pierced his
body, and his wound seared him.

But within a year, his fear dissipated.

Fire was essential for warmth and for roasting meat. If he kept on
fearing it, he would freeze to death. Nezumi had also reached an
understanding.

\emph{Humans are the fearsome ones, not fire.}

It was their routine to take turns watching the fire after a few hours
of sleep.

"You may sleep until dawn, when the eastern sky begins to lighten. You
need not feel guilty. We older ones do not need much sleep."

It had been just before Nezumi had gone to sleep. The old woman had
shown a rare smile as she added a withered branch to the fire. The
flames murmured gently. It was more like a mouse's squeak than a roar.

\mybreak

The eastern sky was still inky black when Nezumi awoke. He got up
abruptly, and looked around. He heard quiet sobbing. The voice had woken
him up.

The campfire was still burning. The flames undulated.

"Gran... what's wrong?"

The old woman had curled up into a ball with her face in her hands,
sobbing. Nezumi had never seen her shed tears before. He inched to her
side and placed a hand on her knee.

"What's wrong? Are you hungry? Does it hurt somewhere?"

The woman did not answer him. Her silent sobbing did not stop.

"Come on, tell me what's wrong. Does it hurt? Are you upset?"~

Nezumi shook the woman's knee. She was the only person in this wide
world whom he could trust and lean on.

\emph{I don't want you to cry.}

\emph{Don't be in pain. Don't be sad. Please, gran.}

"I am sorry..." The sobbing stopped. "Shame on me... but I could not
bear it..."

"But what was wrong? Are you alright?"

The woman's hand stretched out to pat Nezumi's head.

"My beloved homeland is so close. But---now, most of the Mao forest is
lost. That demonic city is giving rise in its place. Little remains of
the forest that I grew up in, where your mother and father grew up in,
where you grew up in. We cannot even set foot into that small patch of
forest now. Yet, it is close... so close..."

"Gran..." Nezumi touched the woman's cheek with his fingertips, and
wiped her tears away. They were surprisingly hot. "Don't cry. You can't
cry. It'll weaken your heart."

The old woman nodded and peered into Nezumi's eyes.

"Let me teach you a song."

"A song?"

"Yes. Your mother was the greatest Singer in all of Mao. I was,
too---many, many years ago. I taught your mother how to Sing."

"Are you gonna teach me?"

The old woman looked Nezumi straight in the eye, and nodded deeply once
more. She was not crying anymore. Her dry eyes were darker than the sky
above. Her dark eyes reflected the flames of the campfire.

"You are fit to be a Singer. You often used to go to out to the forest
and sing with your mother. Do you remember?"

Nezumi shook his head.

All of his memories were vague leading up to that day when everything
disintegrated into flames. He had difficulty recalling anything clearly.

"Just... a voice."

"Voice, did you say?"

"I remember a voice. A voice that said---I'll teach you a song that you
will need to keep living."

\emph{Come here.}

\emph{Let me teach you a song. I will teach you a song that you will need to
keep living.}

Had he not heard a voice say that?

The old woman gave him a startled look, and her mouth twisted.

"Was that... your mother's voice?"

Nezumi fell silent for a moment at her question. He could not remember
his mother's voice. \emph{Run}---only that short cry stuck stubbornly in his
ears, and blotted out her singing voice and her laughter. But even if he
didn't remember, he felt certain about one thing---it was not his mother's
voice.

"No. It wasn't... human."

"...I see." A sigh spilled from her twisted lips. "I see---you~

already know."

"Huh? I don't know anything. I feel like I heard the voice in a dream."
Perhaps it was nothing but a drowsy dream, an illusion in sleep. But the
old woman shook her head slowly.

"It was no dream. You are a Singer. The Forest God has chosen you."

"Forest God..."

"Yes. She is the forest itself. She blesses the Forest People and also
instills them with fear. She is always by our side, watching over us,
blessing us. At times she will hurt, destroy, and obliterate us."

\emph{Destroy and obliterate. Does she mean the fire?} It scorched, thieved,
and banished everything to nonexistence.

"No." The old woman had keenly sensed his unspoken thoughts. She shook
her head vehemently as if to interrupt his words.

"That fire is different. That is made by humans. It is a result of human
malice and greed. It is not the same as the destruction brought on by
the Forest God."

The old woman threw some withered branches into the fire. The flames
swelled slightly. The fire in front of him was gentle. It provided him
warmth and heat for cooking.

"The people of that demonic city burned the forest to the ground. They
turned the Forest God's holy dwelling place into ashes."

"Did the Forest God die that day, too?"

"The Forest God does not die. She will never be killed by human hands.
The people of the demonic city know no God. They do not know her terror.
They do not try to know."

"It's called No. 6."

"What?"

"That city is called No. 6. I heard from someone."

"Who?"

"A traveller. He said he was a bard." Nezumi had met a group dressed in
white while he was collecting branches in the barrens. All of them had
white bags tied to their backs.

They told him that there were six city-states in the world, and people
gathered in and around these places to live. Among them, No. 6 was the
most beautiful and abundant, as well as the most isolated.

"You have a good voice," a bard atop a horse had said to him. The man
had light brown eyes, the same colour as the earth on the barrens. "A
very good voice. If you train it, you could become a first-rate singer.
How about it, kid? Why don't you come along with us?"

Nezumi would be lying if he were to say he wasn't attracted to~

the offer at all.

He would travel the world, with instruments and songs as his companions.
Free from hatred, free from the burden of his memories, he would sing,
play, and dance as his heart desired.

Nezumi was deeply attracted to the idea.

He felt a sort of pleasure as if he had immersed his body in a cold,
clear stream. Yet, he took a step back, and shook his head.

He could not go away and leave the old woman. And more than that---he
could not live on and let that city stand without punishment. He was not
about to throw away his hatred.

"I see. That's too bad," the travelling bard exhaled, and bent over his
horse. "I'm sure we'll come across one another someday. You're the same
as us. You're not stationary---you're the drifting type. Just to let you
know, I \emph{do} have an uncanny eye for seeing people for who they really
are," he chuckled.

His long fingers, suited for playing instruments, touched the horse's
neck. The desert horse neighed. It set off on a trot on its stout, thick
legs.

The group disappeared quickly behind the cloud of dust they raised.

"No. 6," the old woman muttered as she stared into the fire. "The name
does not matter. That city, and all who live in it, will fall someday.
The Forest God will not forgive them."

The branches burned. The old woman's profile was lit up in the darkness
by the flames.

"The Forest God will not forgive. She will bring judgement down upon
them."

"Does that mean we won't have to get our own revenge?" \emph{Could we throw
away this hatred, the memory of that scream?}

"No, \emph{I} will not forget," the old woman said. "I will not throw my hatred
away. It may be... too late for me. I have grown too old. I will
probably not live to see God's judgement with my own eyes. That is why I
will requite myself. If I could get even one stab---"

And the old woman had kept her word. Knife in hand, she had rushed upon
the mayor, who had come to the Correctional Facility to do an
inspection. The woman did not even manage to slice through his clothes,
much less stab him. She was shot through the chest, knife still in hand,
and died in Nezumi's arms as he rushed to her side. It was almost a
miracle that Nezumi~

was not killed along with her.

He was captured and thrown underground, where he met a man who called
himself Rou. Perhaps Rou had somehow been in contact with the old woman,
for he knew everything about Nezumi and accepted every part of him.

"I will pass down all of my knowledge to you," Rou had said. \emph{Sounds a
lot like what God's voice said}, Nezumi had thought wryly.

That was two years before he met Shion.

\myspace

Nezumi stopped to look up at the sky. The sun's rays were fast losing
strength and were on the verge of wilting. Days were short in the West
Block, and nighttime came early. Since the sky was blocked out by the
looming figure of No. 6, the sun only shone down on this land for a
brief while.

No. 6 dominated even the skies. It tore apart and devoured a world that
was supposed to belong to no one.

Nezumi gently felt his back. Even now, it still throbbed sometimes. His
burn throbbed as if to command him never to forget.

Never forget. Never forget. Never forget. Never forget. Never forget.
Never forget.

\emph{I will not forget. I couldn't forget, even if I wanted to.}

He despised No. 6. It had killed his father, mother, and the old woman.
It had burned the forest down, and massacred the Forest People. It never
hesitated to crush human lives beneath its heel if it meant prosperity
for itself. It desired not coexistence, but its own sole reign on a
foundation of countless dead bodies.

Only its own prosperity, its own bliss, its own pleasure. What a
terrible existence it was.

He despised it.

The whirlwind of his hatred almost suffocated him. But, yet---

Shion lived in that city, too. For Nezumi, each and every thing in No. 6
had always been a target of his hatred. Not only did he hate the rulers,
he hated the citizens of that city as well who lived undeserved lives,
ignorant and lacking even the will to enlighten themselves.

\emph{Hate? Do you really? Then can you bring yourself to hate Shion as well?}

Nezumi's own self questioned him.

\emph{Could I bring myself to hate Shion completely?}

It was a bitter question every time. The bitter taste that spread in his
mouth was enough to numb his tongue.

\emph{My hatred is so strong, and my wound throbs so painfully, and yet....}

His began to walk, and stopped again. He could hear a melody.~

He strained his ears. He could hear it.

Nezumi quickened his step. He turned a corner and was greeted by a plain
dotted with boulders. On the edge of this plain stood a small
playhouse---his workplace.

A man leaned upon a white boulder, playing a string instrument. Both his
long upper garment and his pants, whose hems were gathered at the
ankles, were faded and dirty. It was impossible to tell what colour they
had been before. But the instrument in his hands was magnificent enough
to turn heads.

Four strings were drawn across an eggplant-shaped body, and that body
caught the rays of the weak evening sun and sparkled. If he squinted,
Nezumi could see that the body was carved with intricate symbols and
decorated with miniscule bits of gold, silver, and hazy silver.

It emitted a strange music. It was quiet yet clear, which added to its
sorrow. It gently stroked the sadness buried in the bottom of one's
heart. It did not agitate the sadness---it only smoothed it gently.

The man looked up. Their eyes met. Was it that bard? The man who had
invited him to join their travels long ago? He looked as if he could be,
yet he also looked like a complete stranger.

The man strummed vigorously. A melody was born.

Nezumi sang a scat along with the melody. He couldn't help it. The man's
music and Nezumi's voice blended together and flowed gently along. Like
the sky which was now beginning to lighten, the song, reminiscent of a
blooming flower, flowed like a large river under a cerulean sky.

It was a comforting feeling.

Nezumi's body felt lighter as a breeze swept through him.~

Floating on the wind, he rose high into the sky.

In the air, he danced high and low, turned over, glided in a wide
circle, and rose up.

The man's fingers stopped. Nezumi also closed his mouth.

"Don't stop," said a woman's voice.

"Keep singing," added a man's voice.

A throng of people had formed around the two.

\emph{I didn't even notice such a huge number of people.} For an instant,
Nezumi felt a chill down his spine. He was usually especially sensitive
to any presence behind him. Even the footsteps of a single child were
enough to make him react. He braced himself even at the sound of a
tumbling rock. Otherwise, he could not survive.

If there was any exception, it was Shion. Shion's presence was the only
one he lost track of at times. For some reason he couldn't figure out,
he could not perceive Shion.

"Let us hear more."

"Sing, sing!"

"Let us hear that song again!"

The man looked up at Nezumi and grinned. "How about it, young'un? Feel
like going for another?"

"Nah, I think my time is up. My nagging boss is here."

"Hey, Eve!" He was grabbed by the arm. Nezumi turned around and
skilfully pried the hand off.

"Hello, Manager. Looking dashing as always."

The stage manager, dressed in a red jacket and bow-tie, placed both
hands on his hips and set his feet apart. He looked to be at the peak of
displeasure.

"What are you thinking, singing in a place like this? These people
haven't paid us a cent! I don't know what you're doing, singing for
people who aren't even our customers. Ridiculous... what? What's so
funny?"

"No. Just wondering if you were enthralled by it too, manager."

"Wh---don't be an idiot!" stammered the manager. "I just came to take a
look, since you were taking so long. And I found you here, having your
nice little outdoor concert. Do work that brings in the money, I tell
ya."

The manager tugged at the ends of his handlebar moustache, then turned
to the man and smoothed his face into a suave smile.

"Say, sir, you have quite an impressive hand at playing. How'd you like
to come work with me? With your playing and Eve's singing, we're sure to
be the talk of the town. We'll draw in a huge crowd."

The man shook his head silently in a gesture of refusal.

"I wish you'd say that line to me."

"Eve, don't give me that crap," snapped the manager. "I pay you a fat
sum all the time."

"Oh, really? There must be some chasm between your perception of 'fat
sum' and mine."

The man stood up quietly. He drew close to Nezumi and whispered into his
ear.

"Are you also the wind?"

\emph{Wind?}

"A wind that blows over this earth as it pleases. It neither dwells nor
sets its roots down in one spot. Like us."

Nezumi stared into the man's eyes. They were light blue. Could he
possibly be that bard?

"You sing, we play," he continued. "That's just who we are. But why do
you dwell here? Why won't you be free, like the wind?~

What has trapped you and kept you here?"

The man drew back. He strummed just one string. Then he~

stowed his instrument in his bag and slung it over his shoulder.

"Best you free yourself soon, young'un."

Nezumi could not answer him. He only watched the man off.

\emph{What has trapped you and kept you here?}

\emph{Would I be able to cut these chains free? Could I cut my chains of
hatred? And Shion, who binds me? Would I be liberated?}

\emph{Someday, I'll choose to live that way.}

\emph{That day will come.}

\emph{Then it's goodbye, Shion. And goodbye, No. 6.}

"Go home, go home! If you want to hear Eve's singing, come back to the
playhouse with some money. Big concert tonight!"~

The manager's gravelly voice rang out into the crowd.

Nezumi stood rooted to the spot as the wind blew past him, caressing his
hair.