% !TeX spellcheck = en_US

\chapter{Shion's days}

\lettrine{I}{t was} raining. A drizzle---a mist, almost. But rain was rain, and it
drenched the nighttime streets and the people without umbrellas.

Before entering his house, Shion lightly ran his hand through his hair.
Drops of water dripped from his shiny white locks. He was wetter than he
had thought. The cool night air of early spring crept up from his feet.
If he didn't warm up soon, he would probably catch a cold.

Shion knew he would, but he continued to stand in front of the door,
unable to move. He was cold. His spirits were heavy. He felt reluctant
to see his mother Karan's face.

The back door of his house was wooden. The paint was peeling in several
places, and it showed clear signs of its age. A number of times, Shion
had suggested replacing it with a new one. But each time, Karan had
shaken her head.

"This is just fine. It's sturdy and strong. And besides, don't you think
it has its own unique flavour? I think it's much nicer than those awful
glittery metal doors."

His mother was concerned about the cost. But perhaps she really did not
mind the hassle of renovation; perhaps she really did have an attachment
to the worn back door. Shion understood that, so he never spoke of
replacing the door again.

She was right in a sense. The thick oaken door exuded an ambiance not
quite found in stylish, vividly-coloured steel doors. The round brass
knob was also still firmly in place.

This door had not changed a bit since when Shion and Karan first moved
to Lost Town from their privileged-class residence in Chronos (in truth,
they had actually been exiled and not given any other choice of
residence other than in Lost Town, but strangely, neither Shion nor
Karan felt any lingering attachment to their old days). In fact, this
whole house had not changed much at all.

Over a year had passed since the destruction of the city-state, No. 6.
Confusion still remained, and everyone was still in the midst of groping
at how former No. 6 residents as well as nonresidents could adapt to
their new wall-less surroundings.

The terms "insider" and "outsider" (of the wall) had taken root, and
each regarded the other like a foreigner who spoke a different language.
The Insiders realized that they had been skilfully and rigidly
controlled, and appreciated their liberation from a society of
surveillance. But at the same time, they insisted that they did not want
to let go of their wealth---that they did not want their current lives to
be disturbed. The Outsiders criticized scathingly the crimes of No. 6,
which had built itself and prospered on a parasitic foundation. They
rallied for equal distribution of wealth and compensation for the abuse
they had suffered.

Currently, with the Restructural Committee at its centre, No. 6 (of
course, there were voices that called for a new city name, but no one
could spare the time to consider names. There was also the issue of
inter-city relations; for the sake of convenience, No. 6 was still
called No. 6) sought to restore peace and order; to swiftly establish
governing, judicial, and legislative bodies; and secure lifelines.

For the moment, they would use No. 6's governing institutions.

They would designate the West Block as a special ward, and fast-track
the establishment of supply systems essential for life. They would
construct a temporary police force to dissolve the army and maintain
peace.

There were twelve members of the Restructural
Committee---former No. 6 residents, and former representatives from each
Block. Under the Committee were twelve Sub-Committees, with a Committee
member at the helm of each.

Shion was one of the youngest Committee members.

This past year, everything had changed. Like a crashing wave, like the
torrential waters of a rapid, like an avalanche, everything was
swallowed up, sucked into the spiral, torn asunder, and twisted around.
Things would only get fiercer in the future.

Shion exhaled, and gazed in turn at the old door, the battered brass
knob, and the small window out of which spilled a dim light.

Then, there were things that never changed. No matter what path the
world of mankind took, there were always things that didn't change, both
inside and outside of people.

\emph{Shion, I want you to stay as you are.}

Nezumi's murmur revived inside him.

\emph{Fight it. Fight with yourself.}

It was no order or command. It was a plea.

Nezumi had begged Shion as he spoke those words. \emph{Shion, don't ever
change.}

\emph{Could I answer to the feelings Nezumi laid bare before me?}

Shion closed his eyes. He visualized the bazaar. It had been restored
into a free market, and it now offered a wealth of options and plenty of
fresh goods, unthinkable in the past. Karan often went shopping there,
too.

"It's twenty to thirty percent cheaper than shops in the city. They
might not be the most attractive, but you couldn't get better-tasting
produce anywhere else." Just yesterday, too, she had laughed as she
proudly laid out her misshapen apples and gnarled cucumbers.

\emph{But mom doesn't know---the Hunt took place in that marketplace. No. 6's
army ruthlessly fired at those people---shot them through their foreheads,
their chests---not even batting an eyelash.}

The air had been thick with despair, fear, and anguished screams of the
people; everywhere was stained with the stench of blood as corpses lay
left and right. An arm protruded from fallen debris; an army tank
crushed a torn leg as it passed by; army boots trampled those still
living and begging for help. It was the first volume of the inferno that
Shion was to witness later.

\emph{Mom doesn't know that.} And he was glad that she didn't. When he closed
his eyes, he could recall the sights of that day, no less vivid than the
day he experienced them. It was not only the marketplace. He would never
be able to forget the faces of the people loaded into the cargo hold;
the eyes of the man who had begged Shion to make it better; the stacked
bodies and the smell of death which lingered about him; the walls of the
Correctional Facility, crumbling into flames; the black smoke that rose
from No. 6. He would never forget. These images had branded him for
life, never to disappear.

And the fact that his index finger had pulled a trigger. The fact that
he had wilfully, not incidentally, killed another man.

Shion opened his eyes and looked up at the sky. Of course, he could see
neither the stars nor the moon. A raindrop slid down his cheek. It
touched his lips as it rolled down his face.

\emph{Ah, I'm alive.} Suddenly, he was hit with the realization that life was
within him. He felt it: right now, he was most certainly alive. Its
overwhelming reality almost suffocated him. He wanted to scream.

\emph{I'm alive. I'm alive. I'm alive. I'm alive. I'm alive.}

\emph{Nezumi, I'm alive}, he spoke to the dark sky, void of light. \emph{I'm alive
and waiting for you. Even in those hellish surroundings, I was drawn to
your eyes, your words, your gestures, your thoughts---and they supported
me. Thanks to them, I was able to survive. And right now, I'm still
alive.}

\emph{Can you hear me, Nezumi? I'm alive.}

A dog barked noisily. It was coming from inside the house.

\emph{What? A dog? Wait, could it be---}

Shion's mind was yanked from the past back into the present. His heart
beat fiercely. He pushed the door open. He was met with an earful of
barking. They were barks of joy and affection, not aggression or
apprehension. A dog with patched fur leapt up and jumped at Shion as it
barked. It wagged its tail fiercely and jabbed its snout against Shion's
thigh. Its black eyes contained even more joy than its voice.

"Dogs just fall at your feet, as always, huh?"

"Inukashi! And Rikiga-san, you too!"

Rikiga made an exaggerated grimace from his spot on the sofa.

"Hey, Shion. A bit rude of you to notice me after doggy-boy, don't you
think? The proper way to go about it would be to cry,
'Oh, Rikiga-san!' and pounce on me, like that dog there. And then you'd
add, 'Oh, Inukashi. You're here, too,' as an afterthought."

"Hah!" Inukashi bared his teeth and cackled. "Rude? Who cares? Me 'n'
you don't have no need for manners, old man. Just like how my dog
wouldn't need a fur coat. What do manners do? They certainly don't fill
my belly."

"Shut up," Rikiga snapped. "Don't lump me in with the likes of you.
You're practically half-animal. I'm a right and proper man, and a
gentleman at that."

"Gentleman? Whoa, I didn't know 'gentlemen' referred to guys who can't
live without money, women, and booze. Huh, well, I learned something
new. Since when have meanings changed so much? What has the world come
to?" Inukashi let out a long, doleful sigh.

Shion burst out laughing. It had been a while since he heard Inukashi
and Rikiga bickering like this. He laughed from deep down in his belly
for the first time in a long time.

"You two haven't changed at all."

"He's just got a large attitude for a mutt," grumbled Rikiga. "He has a
complaint ready for everything I do."

"And you're simple-minded for a human, old man. You fly off the handle
and have one of your tempers at everything I say. Dogs are way more
intellectual. Actually, dogs are ten times better than humans in head
and heart, anyway. Besides, I think you're closer to a monkey than a
human, old man."

"Yeah, you're right," Rikiga said angrily. "I am a monkey. Just the
sight of a dog maddens me to no end.\footnote{In Japanese folklore, monkeys and dogs never get along.} Every time I see one, I feel like
tearing it apart with my teeth. \emph{Roar!}" Rikiga raised his arms and lunged
at Inukashi. Inukashi laughed mockingly while he nimbly danced out of
reach.

"My, aren't we full of energy." Karan came in. Rikiga froze. He cleared
his throat purposefully and sat down on a chair. He lightly brushed some
imaginary dust off the vest of his three-piece suit, and smiled amiably
at her.

"But please keep it down a little." Karan lightly rocked the baby in her
arms. It seemed fast asleep.

"Shionn!"

"Shh, Shion, not so loudly. I've just gotten Shionn to fall asleep,
finally---hm, rather confusing now, isn't it?"

Shionn breathed softly, wrapped in an old blanket which was so faded it
was impossible to tell what colour it had formerly been. His long
eyelashes cast shadows on his face, and his plump lips were parted
slightly. If bliss had a physical form, then this sleeping face was it.
It brought happiness to every person who beheld it.

"Looks like he's grown bigger since I last saw him," Rikiga commented.

"That's because he has," Inukashi said. "Now he's big enough to run
around and play with the dogs. Soon, he'll be able to gnaw meat off the
bone." Inukashi beamed and placed a soft kiss on Shionn's forehead.

"You're very good at raising children, Inukashi." Karan smiled.

"I've seen many babies in my lifetime, but I feel like it's my first
time seeing a baby look so happy when he's sleeping."

"Ya really think so, Momma Karan?"

"I sure do. He trusts you from the bottom of his heart, and you're able
to be there for him and live up to his trust. You two really make an
admirable family."

A faint blush rose in Inukashi's tan cheeks.

"When my dog came home carrying Shionn in its mouth, I was actually
really pissed off," he confessed. "I thought about just abandoning it,
pretending I'd never seen it. Babies only make for baggage. I really
hated Shion that time for leaving his burden with me."

"---I'm sorry. I knew it was irresponsible, but\el I had no other choice
but to leave him to you. I knew I could trust you with him."

Inukashi's black eyes turned to Shion.

"Shion, does that mean---"

"Hm?"

"Does that mean you trusted me?"

"Yeah." He nodded. It wasn't a front or a lie. In the confusion of the
Hunt, when he had taken the baby from its young mother, the only person
in Shion's mind had been Inukashi. Indeed, Inukashi was the only option
that he had thought of.

\emph{Inukashi will do something about it. He'll protect this little life with
everything he's got. Inukashi will.} This was what he had thought.

Inukashi grinned. He raised a finger and twirled it around.

"You trusted me, and I lived up to that trust. That's what you're
sayin', right?"

"Yeah. I think so." \emph{Nezumi was probably the same. He trusted you, so he
left everything to you.} Shion swallowed his unspoken words and shut his
mouth. He didn't know why, but he didn't feel like saying Nezumi's name
here.

"Hey, wait a minute, Shion. You're not saying you trusted Doggy-boy
above me, are you?"

"Ah, no---that's not what I\el I just didn't associate you with babies,
that's all, Rikiga-san."

"Of course not," Inukashi butted in. "Because if you left him to someone
like this old man, the poor little guy would be sold off the next day.
Living babies fetch a pretty good price, ya know."

"What? Are you saying people put up babies for sale?" The blood receded
from Karan's face. Rikiga hastily waved away Inukashi's words.

"N-No---no, no, Karan, it's not like that. I would never do that. It was
just a bad joke. This one here always makes distasteful jokes. You can
imagine the headaches I get. You shouldn't take him too seriously."

"\el You're right," Karan said uncertainly. "You would never buy or sell
babies. That's just absurd, isn't it?"

"Absolutely." Rikiga swelled his chest. "Karan, there's one thing I want
you to know: I ran lots of businesses in the old West Block. Among them
there were some that were---ah, not so savoury. Yes. Not savoury at all.
And that's a fact."

Inukashi hunched his shoulders. "Don't you mean 'most'? I think your
porno mag business was the most decent."

"Shut up!" Rikiga snapped. "Why don't you go off and gnaw on a chicken
bone or something? Karan, listen to me," he implored. "I never dared use
children or babies. I never used little ones to make my daily bread.
That's the truth. Please, believe me."

"Of course I believe you," Karan said. "I can't imagine you looking at
the young as a target for profits."

"Karan." Rikiga flushed and stepped closer to Karan. "Thank you. I feel
like your trust in me is all the support I'll ever need."

"My, Rikiga." Karan retreated half a step before smiling serenely. "I
never remember you as someone who could recite such a theatrical line.
You spoke frankly and straightforwardly, and you were careful with your
words."

Inukashi whistled.

"Heh heh, Momma Karan's got a good point. 'Your trust is all the support
I'll need' my ass. You don't even see that line in cheap novels these
days."

"Your mongrel brain has never even read a book before. No one's asking
for your input," Rikiga said sourly.

"My brain is a lot better off than yours. Mine's not swimming in booze."

"What did you say?" Rikiga said menacingly.

"What? Got a problem?" Inukashi shot back.

They glared at each other.

"Stop it, you two," Karan said exasperatedly. "Shion, don't just stand
there laughing."

Karan crouched in the shadow of the sofa and gently placed Shionn down
in a cradle. The cradle was a simple one made of wicker with no
embellishments, but its rounded shape was beautiful in its simplicity.
It looked very old, but showed no signs of wear.

A small golden plaque hung on the side.

\emph{For Shion, my beloved son.}

Just that short phrase was engraved into it.

"Hm? Mom, is this---"

Karan's hand gently rocked the cradle. "Yes. I used to use this when you
were a baby. You probably don't remember."

\emph{Or do I?} Shion thought. \emph{I feel like I remember hearing a gentle
lullaby while being rocked back and forth, back and forth\el }

"I didn't think I'd ever pull it out and use it again like this. I'm
glad I went through the extra trouble to bring it when we moved out."

When they had moved out of Chronos, the furniture and dishes they could
take with them were heavily restricted. Their house, their furniture,
the services, abundance, and their top-class living environment had all
been given to them precisely because Shion had been certified as elite.

Once this certification was revoked, they had to return everything that
was given to them from No. 6. The personal belongings that Shion and
Karan brought into Lost Town were surprisingly few.

Was there a cradle among them? No. Shion would have noticed if there
was.

"I secretly brought it afterwards and stowed it away in the attic,"
Karan said.

"Why did you have to do it secretly?"

Karan's hand stopped.

"Because this\el this was handmade by your father."

Shion's breath caught in his throat. It blocked his airway. As he
exhaled, his voice slid out along with it.

"What? My father?"

"Yes. Your father made this cradle for you." Karan pursed her lips and
averted her eyes from Shion.

"Dad was\el a craftsman?"

"No. A geologist---that was his main occupation. And I think he was very
good at it. He was chosen to be a member of the revival project team,
after all."

Revival project team---it was a group of individuals chosen to make No. 6
a paradise on Earth, a utopia. The mayor, who desired to become No. 6's
absolute ruler, was a member; Rou, the scientist who schemed to have the
Forest God Elyurias under his control, was a member.

But their aspirations and futures morphed and drifted apart: Rou became
an underground man; No. 6 transformed into a monstrous city, and moved
down the path to destruction.

And Shion's own father had been one of those members. Shion was stunned.
That was all he could say. He was stunned.

"But mom, you said\el you said before that my dad was loose with money
and women, a hopeless case and a step away from being an alcoholic. But
then you said he was really kind and sincere."

"I did. Because it's true." Karan pouted even more. She looked like a
sullen child. "He spent all the money that came in, and drank all day.
As soon as he found a girl he liked, he'd start a relationship with her
without even thinking of the consequences\el even after we married, he
had girlfriend after girlfriend\el "

"To have a lover while being married to \emph{you}, Karan---I don't believe this
man. Unforgivable." Rikiga clenched his fist, his eyebrows arching
angrily.

"You can say that again," Inukashi commented. "He's almost as corrupt as
you, old man."

"Hey, mutt. And what exactly is corrupt about me? I'm single, which is
why I could get away with playi---er, having a good time with women. But
if I got married---" Rikiga glanced furtively at Karan, and took a breath.

"I would love her for as long as I lived. I wouldn't even \emph{look} at other
women. And I would stop drinking. Not to brag or anything, but I think I
would make a good family man. Yeah."

"Bullshit," Inukashi spat. "You being a decent husband is just as likely
as my dog becoming a top chef."

Inukashi faced Karan before Rikiga could say anything in return.

"But Momma Karan, I can't even imagine such a slob being Shion's dad.
Their personalities are way too different."

"You could say that. But he was surprisingly good with his hands, and I
think Shion inherited that from him. Actually, this---" Karan gently
rolled Shionn's blanket back. He was wearing a plain white collared
shirt. The collar and breast pocket of the shirt was embroidered on the
hems with blue thread. A vibrant blue.

"He sewed this by hand. Same with the baby clothes and bib. He finished
it the day before he left us, and left them on the table with a letter
that said he wanted Shion to wear them on his first birthday. So when
you turned one, Shion, I put them on you. They were a little big back
then. But I think they're a perfect fit for this Shionn."

This was really, truly Shion's first time hearing such detailed things
about his father from Karan. Shion had never asked because his mother
never seemed to want to talk about it. He had lived his fatherless life
simply accepting that that was just how it was.

His father was loose with women and money, loved to drink, was a
specialist in geology, a member of the revival project team, had
surprisingly skilled hands, and left his family soon after Shion was
born.

Shion glanced over at the cradle. He gazed at the baby sleeping inside,
with the same name as his. He touched the embroidered shirt.

This was what his father left behind.

Shion sneaked a glance at Karan's profile.

So Karan's acquaintance with the core members of No. 6 had not been
through Rou. And his father, as a member, colleague, and holder of the
same ideals in his heart, had spent his younger days alongside the mayor
and those scientists.

"And Shion's papa left the house because\el well, because of those women
problems?" Inukashi leaned forward.

"Hey, don't butt into other people's personal matters," Rikiga said.
"Not a tactful bone in your body, is there?"

"Hah, don't even talk to me about tact. You're dying to hear it
yourself, old man. You're trying \emph{so} hard to impress. Heh, I can't stop
laughing." Inukashi's teeth clattered together.

His comment had apparently hit the mark, for Rikiga blushed crimson and
fell silent. Karan neither appeared offended nor taken aback by
Inukashi's bluntness. She continued calmly.

"Maybe you're right. That might have been an indirect reason. I
was young and I wanted him to stop being ridiculous. But ever since he
found out that Shion was on the way, he changed a little. All his
attention was on the unborn baby, and he even stopped drinking and
playing around with women, if only for a short while\el he picked up
drinking again not long after. But I felt like if he kept on being like
this, maybe he \emph{would} turn into a decent family man. Inside, I was proud.
That's why I know he didn't leave the family because of a woman\el he
had another reason\el "

"Because No. 6 was changing."

Karan blinked several times at Shion's short utterance.

"You can tell?"

"I had a vague idea."

As No. 6 took shape into a city-state---a totalitarian, authoritarian
state---many members withdrew from the revival project team during the
process. Some were intentionally removed, while others left of their own
will. Strictly in the realm of possibility, perhaps some had been deemed
a hindrance and murdered secretly. It was more than likely.

"He was overwhelmed by the fact that No. 6 was gradually---no, actually,
quite quickly---morphing as it developed its city structure. He was
apprehensive, but he had no idea what he could do about it. Maybe he was
afraid. I remember hearing him say over and over to himself, 'This isn't
possible. This can't be happening.' Then, one day\el it hadn't even been
a month since Shion was born\el he said to me, 'Let's leave No. 6. We
can still escape now. But soon, we won't be able to leave unscathed from
this city.' His face was so grave when he said it. He must have given up
on No. 6 altogether by that time. He probably thought, 'I can't live
here anymore. One day I'll suffocate, and end up taking my own life, or
get killed if I don't.' That's why he tried to convince me to escape
somewhere far away from No. 6, and start a new life in a strange land,
just the three of us."

"But you said no, mom."

"Yes." Karan let out a long breath. "I said no. I told him clearly that
I wasn't going to go with him. I just couldn't bring myself to believe
what he was saying."

Karan averted her eyes and looked down as if Shion's gaze was too
blinding to bear.

"When I asked him where we would go once we left No. 6, he said he
didn't know. Then he just burst into a joyful laugh and\el said it
wouldn't be so bad to wander freely like the wind. But I had a baby that
wasn't even a month old yet. Apart from the six city-states, I knew
there were only barrens and tiny fields left on this earth. I couldn't
bear to think of forcing such an arduous journey on a tiny infant. I
supposed that as long as I stayed inside No. 6, we wouldn't have to
starve or get sick. I couldn't convince myself that he could protect us
better than No. 6. I couldn't trust him."

Yet another sigh escaped Karan's lips.

"I don't know if I made the right decision that day. I certainly don't
regret that I didn't go with him. But the fact is that I had already
become dependent on No. 6. I was trying to live a life of dependence. I
lived for years and years without even realizing\el I was completely
ignorant of No. 6's rotting smell, when he had been one of the first to
detect it. And that---is a very regrettable thing."

"And you have no idea where dad is right now?"

"No, I don't. I don't even know if he's dead or alive. But knowing him,
I have a feeling he's living freely, doing whatever pleases him."

Karan's voice dropped slightly.

"Shion, would you want to meet your father?"

"Well\el I've only known you, mom, so I don't really feel any sort of
yearning towards him. I don't really miss him. But I am curious."

"Curious?"

"Curious about why you decided to talk to me about dad so suddenly. You
never talked about him before."

Karan's lips moved, but no words issued from them. A short moment of
silence followed. It was so still that Shionn's slumbering breathing
could be heard crisp and clear.

\mybreak

"K-Karan---"

Rikiga stood up abruptly.

"Ah, um---so, d-do you still have trouble forgetting about, ah, your
former husband? That is to say, um, that you're\el waiting for him to
come home, or\el is---is that how you still feel now? Or are you, ah, free
of any of that kind of\el er, attachment? As in, um, if something were
to happen, would it result in\el "

``What the hell kind of language are you speaking, old man?'' Inukashi
jumped in. ``I think a newborn puppy would make a bit more sense than
you. Right?'' A patchy-furred dog that was lying at Inukashi's feet
opened its eyes a crack. It gave a wide yawn.

Karan smiled.

"I'm not waiting for him, Rikiga," she said. "To me, he's already a man
of the past. Of course I \emph{do} hope he's still alive somewhere, but---"

An unmistakable joy crossed Rikiga's features.

"Can't get any more obvious than that," Inukashi muttered.

"That's absolutely right," Rikiga said enthusiastically. "We can't dwell
on the past forever. If we're going to dwell on something, it should be
the future. Tomorrow is so much more important than yesterday."

"I agree."

"R-Right? You think so too, don't you? So\el ah, Karan, wouldn't you
agree that, um\el someone with whom you can live in the future is, ah,
more important than someone with whom you lived in the past?"

"Yes, of course. That's why I invited you to dinner this evening. I
wanted to dine with you."

An exclamation issued from Rikiga's lips that sounded like something
between "oh" and "ah".

"K-Karan, is that true? Y---You thought of me, and that's why---"

Inukashi tugged at Rikiga's jacket.

"Old man, old man. Sorry for shattering your dreams, but I've been
invited, too. You're not the only one. Don't you forget that."

Rikiga scowled heartily and made a swatting gesture as if to chase away
flies.

"Shoo! Shoo! Show yourself the door and take that dirty mongrel with
you. You probably asked yourself over with a mind to take advantage of
Karan's cooking."

"As a matter of fact, I \emph{did} get a proper invitation. Right, Momma
Karan?"

"Yes, of course. Both Inukashi and you, Rikiga, are very important
teammates to Shion. And you two are very good friends to me. That's why
I wanted both of you to come. I don't have much, but I do have lots of
freshly-baked bread. I also have homemade jam and stew that's been
simmered nice and long. Just a minute, I'll get it prepared. Shion, can
I get some help?"

"Sure."

Karan opened the door to the kitchen and disappeared beyond. The aroma
of bread and stew wafted into the room. The two distinct smells
stimulated the nose. Inukashi's nose twitched eagerly.

"I'll help, too! Being treated to a free meal goes against my morals."
He chuckled. "Did you hear that? Fresh-baked bread and stew. Just the
sound of it makes me drool, but then you \emph{smell} it, and\el oh, this is
the best. My stomach is grumbling like no tomorrow. Aren't you hungry
too, old ma---hm? Old man, what's wrong? Your eyes aren't focused. What're
you spaced out about?"

"\el Teammates\el friends\el "

"Huh?"

"Karan says I was a teammate. A friend. To Karan, I was only ever just a
member of a team, just one of her friends\el "

Shion and Inukashi looked at each other. Inukashi tilted his head.

"Hmm. Well, 'let's be good friends' is a pretty typical rejection
phrase. Dogs would be more straight up and tell you they hate your fur
or that your teeth are gross, but humans like to take the long way
around. Hah, but really, old man, were you planning on seriously
proposing to Momma Karan?"

"\el I was serious," Rikiga said gloomily. "Work is picking up for me,
and I've got money enough to spare. I was confident that I'd make Karan
happy."

Following the destruction of No. 6, merchandise began to find its way
out of the walls. Rikiga took advantage of the chaos and bought them off
at low prices.

He hoarded artwork and handiwork, electronics, paintings, jewellery,
furniture, medical machines, cars, clothes, office supplies, and even
toys; when things began to settle, he sold them at high prices and made
a handsome profit. Now he directed and managed a publishing company and
printing company, issuing a weekly informational magazine and a daily
paper.

``Well, you \emph{are} a rising star in the entrepreneurial business,
Rikiga-san. Rumour says you're quite the power player.''

"You honestly think so, Shion?"

"Of course I do. You and Inukashi don't need fake compliments from me,
do you?" Shion took his jacket off and rolled up his sleeves.

"I keep telling you to stop lumping me in with doggy-boy," Rikiga said
wearily. "But enough of that. So, Shion, you've acknowledged me, then?
You think I'm fit to be married to Karan?"

"Huh? Oh, I---I didn't mean it like\el well, uh, I don't think my mother
ever plans to remarry. She was telling me the other day how satisfied
she was with this life and how she'd like to keep being a baker for as
long as she can."

It was true: Karan's life had not changed much, at least on the outside.
She ran her small bakery tucked away in a corner of Lost Town, chatting
with regulars and kneading dough for the first loaves in the early hours
of the morning.

That was her regular routine, and she repeated it every day. Even in
intense turmoil, Karan continued to fire up the oven, bake bread, and
lay them out at the front of the shop. The people wept through their
mouthfuls of small rolls and muffins.

"The world has crumbled from beneath our feet, but this still tastes the
same. There are still things in this world that haven't changed."

Those were the words of an elderly man, a regular customer. He had
murmured the words over and over, his cheeks wet with tears. Shion
encountered the same sort of murmur many times.

\emph{Something is here which will never change}---for the people, that feeling
of certainty signified hope and a reason to keep living.

"Your mother is an incredible woman," Nezumi had said, with a rare note
of awe in his voice.

It was on the day he had woken up.

On the day that everything had ended---no, began---Shion had dragged his
exhausted and battered body back home to Karan.

After a somewhat brief reunion embrace, he had collapsed into bed with
Nezumi and slept like a log. His slumber was deep enough to cut off all
of his senses, and when he woke, it was already noon of the following
day. It was the time of day when the sun was shining straight from
above, emitting a faint reddish glow.

There was no sign of Nezumi beside him. There was one blanket folded
neatly and placed at the foot of the bed. Shion placed a fist on top of
the folded blanket. A strangled noise subconsciously escaped his throat.

\emph{Nezumi, have you gone? Just like you did four years ago?}

Four years ago, on the morning after the storm, Nezumi had disappeared
from Shion's side. He had disappeared starkly, as if everything from the
night before had been an illusion.

Back then, they had only just met. They barely knew anything about each
other---not a single thing about the pasts they shouldered, the future
they beheld, and the emotions they kept within their souls.

But it was different now.

Yes, there were still things they could not grasp, things they still
could not understand about each other. There was a chasm between him and
Nezumi that he could never fill, no matter how much he struggled to.

\emph{I know. I know. I know. We knew, but we still lived together. Not in the
past, nor in the future, but in the present. We lived the present
together.}

\emph{But now you're leaving again without a word?}

Shion's thoughts got as far as that before he shook his head vehemently.

\emph{Of course not.}

\emph{We've spent so much time together, and overcome hell together.
He wouldn't vanish without a word. That's not what our relationship is
like. And besides, it would be risky for him to move around with such a
serious wound. I can't imagine Nezumi being so reckless.}

He caught a whiff of the aroma of coffee and bread. It was the smell of
waking up.

Shion opened the door into the living room.

"Oh, is the prince finally awake?" Nezumi was smiling with a coffee cup
in hand. "I can't say much about you, though. I woke up not too long
ago."

Shion swallowed his sigh of relief, and with great effort feigned a calm
demeanour.

"Nezumi. How do you feel?"

"Couldn't be better. Or, at least I wish I could say so. It's taken its
toll. You?"

"Couldn't be better."

The cup twirled around in Nezumi's hand.

"Confident now that you're on home turf, huh? But it's a good thing that
you've got enough energy to act tough. But might I suggest taking a
shower and spritzing yourself up before you start trying to be a tough
guy? I think even King Lear wandering the wildness would look a little
more put-together than you."

Shion peered into the mirror hanging on the wall. His face and hair were
covered in streaks of blood, dirt, and dried sweat. His shirt was torn
in several places, and his right sleeve looked like it was about to fall
right off.

\emph{He's right. I don't even think King Lear at his maddest would look as
bad as this.}

He felt a strange urge to laugh.

"So, your Majesty, will you be having a bath first? Or shall I prepare a
cup of the very best coffee for you?"

"What an incredible honour it is to be served coffee by you."

"Your mama just treated me to some delicious bread---the very best, I must
say---and it was so good I felt like my tongue would melt. I think pouring
you a coffee would be a small service compared to that."

"Oh---mom\el "

"Your mama has been run off her feet with work since morning." Nezumi
jerked his chin. Shion could feel the muffled buzz from beyond the thin
wall.

"Huh? She's opened shop?"

"Looks like it. Says the only thing she can do is bake bread, so she's
going to keep doing what she can. Even in this chaos, the oven is still
fired up and the danishes are still baking. She says in the evening,
she'll make some cravats for me."

"I see\el sounds like what she would do."

Nezumi put his cup down, and his eyes moved towards the white wall.
There was no smile playing on his lips anymore. It was as if his gaze
pierced through the wall, focusing on Karan who bustled about on the
other side. A darkness lurked in the depths of his look.

"Your mother is an incredible woman," Nezumi said. His voice was so low
it was almost a whisper, but there was definitely a note of awe in it.
"She's like the Almighty Mother. I didn't know there was someone like
that inside No. 6. but she is one---and she's lived here as a citizen."

"\el You're right."

A person could never be completely dyed into one colour, no matter the
circumstances. He may be dyed temporarily, but he would one day regain
his own colour, and would always attempt to live loyal to himself. He
would try to draw forth many different colours into this world.

Indeed, that was hope itself.

How much could one trust the days that lay before him, the people in his
life, and hope? Eventually, this question would be posed to Shion
himself. He knew that Nezumi would have to take on the same assignment.

\emph{Nezumi, could we ever completely believe in people? Not loathe, not
condescend upon, not abuse, but believe?}

\emph{Could we do it?}

The aroma of coffee filled the air.

"But first, you need a splendid brunch with the best of bread and the
best of coffee. At least take today to rest and think of nothing at all.
Your mama's gutsy way of living is too much for us youngsters to handle
yet, I think."

"You're pretty modest."

``This is 'away' territory. I'll watch my mouth,'' Nezumi said lightly.

``And truth be told, I'm a little tired. I haven't the slightest
objection to sleeping, eating good bread, and going back to sleep again.
It's quite a nice vacation.''

"And you'll get to eat cravats in the evening."

"Yes, that." Nezumi snapped his fingers. "I've never had the pleasure of
beholding a pastry shaped like a tie. And baked by your mother's hands.
It must be delicious."

"Once you've had them, you'll be at their mercy. They'll come to haunt
you every night in your dreams."

"I imagine it'll be like how Hansel and Gretel felt when they found the
house made of sweets. It's one of those things where 'pleasure and
trouble come arm-in-arm with each other.'"

"Someone's proverb?"

``I just thought of it now. And you better remember it: it'll illuminate
the path to your fate.''

A cup of coffee was placed down in front of him.

"Drink up. I've made it a little strong with lots of milk, just the way
your Majesty likes it."

"What? We've never had coffee together before. How do you know how I
like it?"

"I just know. I told you before---you're hopelessly easy to read, and yet
also hopelessly hard to understand."

"I could say the same for you."

"But I'm not as difficult as you."

"You're one to talk. You should be the last person to call me
difficult."

"How the hell am I difficult?"

"It would take me until tomorrow morning to list them all."

"Huh," Nezumi huffed. "I'll entertain you with my presence until
tomorrow morning, then, so let us hear all the details."

"See, that's what I'm talking about." Shion sipped his coffee. Its
fragrance, bitter taste, and mildness spread inside his mouth. The rolls
on the table were also delicious. As Nezumi had said, they were so good
he felt his tongue would melt.

The taste soaked into the very core of his body and soul. It was the
unmistakable taste of his mother's cooking.

"One minute you're as stubborn and quick to anger as a child, and the
next minute you've got sound judgment and no attachment to anything
whatsoever. You're constantly changing your mind, and you're in a
different kind of mood from one minute to the next. I can't see how
anyone can be more difficult than you."

"Uh-huh, I see. Not gonna candy-coat anything, are you? Well, let me say
my bit, Shion---"

"Go ahead. You have nothing against me."

Nezumi scoffed. "Only indecent people go on about how decent they are."

"So you're saying you don't think you're decent?" Shion retorted.

"Erm, well\el that's not to say I'm not a decent person, because I
always am\el Damnit, you're getting quicker with your comebacks."
Nezumi twisted his mouth and narrowed his eyes.

Shion almost snorted at Nezumi's hilarious scowl.

Everything seemed beautiful---this casual conversation, the gentle
atmosphere, even the rays of the setting sun coming in through the
window.

It was a gem of a moment which had existed between the storm that had
passed and the storm Shion was about to face. It was also a tender
memory that Nezumi had left behind for him.

\myspace

Nezumi set off, and Shion remained. Their tangled and overlapping fates
had separated, and were now drifting apart.

When would they intersect again?

"Hey, Shion." Rikiga's face drew nearer. "I want you to give me a hand."

"Give you a hand?"

"I'd like you to tell\el well, hint to Karan---discreetly, mind
you---how right I am as a marriage candidate for her."

"What? But, well\el I'm not so sure I can---"

"I'm serious. I want to propose to her because I'm confident that I can
make her happy. Of course, if Karan wants to keep running her bakery,
she can do it for as long as she likes. I know!'' he exclaimed, ``We can
renovate the entire place. Make the shop bigger, put in a large front
window. Make it glamourous. We'll fix up the living quarters, too, and
add more rooms."

"I don't think that's what my mother would want. She seems pretty
satisfied with what we have already."

Rikiga cradled his head in his hands.

"Oh, Karan. What a virtuous woman, so modest in her wants.
She's the very embodiment of a goddess."

"I dunno, I think she's a bit on the chubby side to be a goddess,"
Inukashi butted in. "But Momma Karan is pretty, and way too good for
you, old man. And FYI, I think the problem with the kind of women you
hang around with is that they want too \emph{much}. When they look at someone,
they see a gold coin where his face should be. Either way, old man,
Momma Karan only sees you as a friend. The ends of her hair are a more
likely marriage candidate in her mind than you. Hah, just give it up."

"Don't think a brat like you can interfere with adult matters."

"Fine, fine. Mr. Adult can keep putting up a hopeless struggle in his
adult matters. Shion, let's go help Momma out. I'm dying to have
dinner."

"Sure."

They could hear Rikiga let out a troubled sigh behind them.

Dinner was enjoyable. Everyone ate, talked, and laughed plenty.

It was fun---very fun.

\emph{If Nezumi were here}---his heart wavered in uncertainty. If Nezumi were
here, he would have sat across from Shion, praised Karan's cooking, and
sneered coolly as he looked on at Inukashi and Rikiga arguing. He would
have wielded his fork and spoon with elegant grace, and would have made
Karan happy by finishing everything on his plate.

Nezumi, where are you? What are you doing right now?

\emph{I haven't seen you for a year now.}

Three hours later, his companions set off for home into the night.

Inukashi left in high spirits, his backpack bursting with bread. Rikiga
looked thoroughly depressed.

``Mom,'' Shion called out as he cleaned up. Karan, who was measuring
flour, turned only her head to look at Shion.

``What is it?''

``Why did you invite Inukashi and Rikiga-san over today?''

``Hm? Well\el I don't think I really had a reason. I thought it'd be
nice to have some people over for dinner for once. You've been so busy
you haven't even had time to sit down and enjoy a good meal.''

``So you did this out of concern for me?''

Karan turned her whole body towards her son this time, and shook her
head slightly.

``It's not like that. It's just---Shion, have you noticed? You don't
smile or laugh a lot anymore.''

``Huh?''

``It's been a while since you laughed out loud like you did today.''

Shion touched his own cheek. His skin felt hard and tense beneath his
fingertips. Karan was looking steadily at Shion's fingers.

``Your job at the Restructural Committee must be tough.''

``Yeah. But, I mean, we \emph{are} making an entirely new organization with a
new set of functions. We've got people from all sorts of positions in
one place. It's not like I wasn't prepared to deal with difficulties.''

``Are things not going well with Yoming and his group?'' Karan raised
her chin. Her tone and gaze grew hard, as if she were challenging
someone. ``I imagine you two must\el think very differently. Shion, are
Yoming and them giving you a hard time?''

Shion was at a loss for an answer.

``I knew it,'' Karan said. ``I had a bad feeling when I found out Yoming
was selected to be a member of the Restructural Committee.''

``Do you know Yoming-san well, mom?''

A shadow flitted across Karan's eyes.

``I thought I knew him. He's Lili's uncle, after all, and he used to
come to the bakery a lot. He said No. 6 had murdered his wife and son.
He taught me what No. 6 truly was, back when I still had no idea. He
helped me. He's a very intelligent person, isn't he?''

``Yeah. He is smart. He organized the resistance. He's the one who
gathered all the people who opposed No. 6 and made them into an
organization. His actions were one of the things that triggered No. 6's
fall. It's only normal for him to be chosen as a member of the
Committee.''

``Normal? Is it really? Shion, do you really think that Yoming is a
suitable individual for the Restructural Committee? I\el I just can't
seem to convince myself that he is.''

``Mom\el ''

The windows rattled. It seemed like the wind outside was picking up. It
would sweep the clouds away and bring an end to the rain.

Tomorrow, a blue sky would probably open up above them.

``He hated No. 6 with a passion,'' Karan continued. ``And for good
reason, too. It took his most precious family away from him. He wasn't
blinded like the rest of us. He saw No. 6 for what it was precisely
because of his hatred for it. And this was even while he was living
inside the city.''

Karan ran her hand down the bag of flour beside her.

``Hatred was his energy, and it was effective for destroying No. 6.
But\el but that energy isn't going to create anything new. That's what I
think, Shion.''

There was a forlorn note in his mother's voice that made his heart ache.

One had to either throw away one's hatred or overcome it in order to
create something new. Loathing could never become a force for revival.

``Just a little before the chaos came to a head in No. 6 because of that
strange disease\el when we'd started to see the clear signs of
destruction beginning\el he came here, and we had a long talk. And he
said to me, `I've lost faith in you.'''

``Yoming-san told you he lost faith in you, mom?''

``Yes. Shion, there are a lot of things that I don't know or can't
understand. I've never \emph{wanted} to know or understand. And that's a very
shameful thing indeed. If only we adults had been a little smarter,
perhaps we could have saved Safu, too\el ''

``Mom, let's get back to talking about Yoming-san,'' Shion said in a
firmer tone as if to cut across his mother's mourning words. His
thoughts and feelings for Safu were like a bottomless swamp. No matter
how much he repented or apologized, there would never be an end for him.
No matter how many tens of thousands of words he piled upon, no matter
how much he kept praying, he would never be forgiven.

So at the very least, he would not forget.

He would remember Safu and the wish she had passed onto him until the
hour of his last breath.

Karan blinked, and nodded slightly.

``Yes, he lost all faith in me because I didn't agree with him
wholeheartedly. He was trying to become a hero, a hero who overthrew a
dictator state. I don't know, it wasn't for revenge, or anger at being
oppressed all this time\el I felt like he was being taken over by a sort
of---desire?---to become a hero whose name would go down in history. Yoming
said that casualties were inevitable in a world that was changing. He
dismissed all the people bleeding and dying and said it couldn't be
helped.

For him, if a thousand people had died to save ten thousand, their lives
would not have been lost in vain---but isn't there something wrong about
finalizing it like that? There's something wrong about converting human
lives into numbers. And I think it's wrong for a hero to stand on a
pedestal built on human sacrifice.''

``\el Yeah.''

``Shion, can you put up a fight against Yoming?''

\emph{Fight? Is Yoming-san someone I have to fight? Is he an enemy?}

Yoming's group continued to assert that the temporarily-established
Restructural Committee should be dissolved and an entirely new
organization created in its place. It was clear that if they had their
way, the core positions of the Committee would be dominated by members
of Yoming's group. It would be a considerable departure from the
Committee principle, founded upon the idea that the Committee was a
place where members of many backgrounds and affiliations could exchange
opinions freely. But by now, Yoming and his group had stopped listening
at all to the objections and opinions of Shion's group, the minority.

\emph{Something has to be done. I have to do something.}

No. 6 was already a proven example of what resulted when justice lay in
the hands of a few and all others were banished.

The damage was still raw, still throbbing; why was Yoming's group
attempting to tread the same path?

\emph{I have to do something---}

``Shion, you've gotten so thin.'' Karan's gaze and tone turned to those
of a mother. It was a glimpse of a mother's love, the foolish, fierce,
pure, and selfish love that worried only of her own child's welfare and
wished for only his happiness.

``You should quit the Restructural Committee if it's such a burden on
you. There are so many other ways to make a living. You said yourself
once that you wanted a job that involved kids. Why don't you look for
one?''

``No\el '' Shion slowly shook his head. ``I still have things left to
do.''

``But\el ''

``Mom, he told me not to run away. I have to stay here because I have a
job to finish. He said I can't turn my back on it now. I don't want to
go against those words.''

Karan did not question who ``he'' was. Instead, she silently gazed up at
her son.

The wind grew even fiercer. The windows rattled restlessly.

Karan let out a subdued sigh.

\mybreak

``I suppose life would have been a little less burdensome if you'd been
whimsical like your father.''

``Oh,'' Shion said in realization. ``That's why you suddenly decided to
tell me about dad.''

It was one way to live: taking nothing upon oneself, casting off any
troublesome loads, turning one's back on everything.

\emph{Your father chose to live that way.}

A mother, watching her son struggle with reality, had told him the truth
about his father.

\emph{But I can't. I can't live like dad did.}

\myspace

\emph{Shion\el don't run away.}

\myspace

\emph{Nezumi's words are supporting me. Nezumi never ran away. He never
retreated in the face of fate, or from reality. And I was there beside
him.}

\emph{Safu passed her legacy on to me.}

\emph{I can't run away.}

\emph{I can't betray them.}

\emph{I have to fight---not for anyone else, but for me to remain as who I am.}

He crouched and kissed his mother on the cheek.

``I'm going to sleep. Good night, mom.''

Karan's fingers gently stroked Shion's white hair.

``Good night.''

Her lips twisted slightly, as if she were forcing herself to smile.

\myspace

A tiny mouse was curled up on the bed.

``Tsukiyo.''

It raised its head at the voice, and squeaked softly. Shion offered some
crumbs of bread and cheese to Tsukiyo, putting them right up to his
nose. Tsukiyo twitched his whiskers two, three times, but did not touch
any of it.

When Shion petted Tsukiyo's back with the tip of his finger,
Tsukiyo closed his eyes dreamily.

Hamlet, Cravat, Tsukiyo. Out of the three mice Nezumi kept, only this
Tsukiyo remained with Shion. He was a small creature, but possessed both
wisdom and intelligence. He was likely a descendant of the wild mice
that lived deep in the forest alongside the Forest People.

Shion had simply assumed that because this mouse was no ordinary mouse,
it would have the same lifespan as a human.

But these days, he could see Tsukiyo ageing and beginning to weaken.

The average lifespan of a mouse was anywhere from a year and a half to
two years. Even a pet hamster would live to three years at most.

Tsukiyo was slowly nearing his end.

``Tsukiyo, hang in there. You have to live to see your master come
home.'' Shion stroked him gently with the flat of his finger.

\emph{Cheep-cheep.}

Tsukiyo chirruped contentedly, and closed his eyes.

\mybreak

``What is this?'' Deep creases formed between Yoming's eyebrows.

They were on the first floor of the Restructural Committee headquarters,
the former city hall which used to be called the Moondrop.

Shion and Yoming were sitting across the table from one another in a
small meeting room. Shion had called Yoming out.

An electronic sheet was laid out on the table. Yoming had just glanced
down at the screen and furrowed his brow.

``This is proof that you diverted the funds of former No. 6.''

``What? What are you on about?''

``You have always been, and still are, in the post of managing the
enormous resources of former No. 6. You took advantage of your position
to claim much of that money as your own. I'm talking about
embezzlement.''

``Absurd,'' Yoming sneered. ``I'm busy. I have no time to be playing
along with a little boy's joke.''

``Joke? Is it?'' Shion pressed. ``No. 6's resources were left exposed
for some time because management simply wasn't functioning. In that
time, a third of the funds have disappeared. Gold especially---about sixty
percent has been lost.''

``And you're saying that's my fault?''

``Yes.''

``Don't you dare. Yes, I may be in charge of managing the funds. But how
did you expect me to keep guard over the gold on top of everything else
during that chaos? I shouldn't have to be responsible for that.''

``The gold wasn't simply stolen. It was smuggled out, and it was
premeditated. If it wasn't planned beforehand, how do you explain the
fact that the other forty percent still remains? Thieves would take all
the gold away. Not only that, the gold was in the innermost part of the
underground vault. No matter how bad the confusion, it would have been
exceedingly difficult to carry out several tonnes' worth of gold without
being noticed. Even professional bands of thieves wouldn't have managed
it. In fact, it's outright impossible. Yoming-san, let me say this
again. The gold wasn't stolen. It was smuggled out, and it was
premeditated.''

``And you're saying the smuggler is me?''

``I can't think of anyone else.''

Yoming drew his chin back and smiled blandly. ``Are you calling me a
thief? What an accusation. If you don't take that back soon, I'll sue
for libel.''

``You needed a very large amount of capital to expand and maintain the
power of your group. That's why you turned to No. 6's funds. It was the
easiest, quickest way.''

``Are you really trying to accuse me?''

``This data---'' Shion jerked his chin at the table. ``Is a copy of your
application and authorization forms that you submitted in the
Committee's name to rent out a cargo jet. Both have your own handwritten
signature. This cargo jet was used in a trip to No. 4 and back. And
this---''

Shion swiped the screen with his hand, and new data appeared. Yoming
stared intently at the series of numbers without even blinking.

``This is a list of your personal assets provided by No. 4's bank. Quite
large, isn't it? Fit for a king. I think it's safe to assume that these
assets have all been converted from gold. The numbers add up. And
there's more.''

He moved his fingers.

``These figures are special benefits that you handed out to your group
members. This is also quite a lot. Not even the executives of former No.
6 received this much.''

``\el We members placed our lives on the line to fight with No. 6,''
Yoming said quietly. ``We are perfectly entitled to that amount.''

``That is for the Committee to decide, and not for you to make your own
judgements about. Many other people fought with their lives in the
balance. Many did not live through it, either, Yoming-san.''

Shion stood up and began to roll the electronic sheet up.

``You misused public funds by handing out compensation on your own sole
judgement and pocketing money for your own use. It's unmistakable
treason. You've betrayed every single citizen.''

The door burst open. Two men stepped inside. They were second and third
in command in Yoming's group. They were both in their mid-thirties with
dark brown hair.

``You've gone and done it now, Yoming.''

``How could you have perpetrated such evil behind our backs? Shame on
you!''

``Behind your backs?'' Yoming retorted. ``That's ridiculous, you all
were well aware that\el '' Yoming's breath caught. He chewed his lip. The
colour rapidly receded from his face.

``Shion, you tricked me.''

Shion maintained a steady gaze at the man's pale face, and said nothing.
Shion's eyes did not budge.

``\el I knew you were dangerous,'' Yoming said softly. ``I underestimated
you because you were still a young boy. That was my mistake.''

``We all make mistakes in life, Yoming-san. But yours just ended up
costing you your life.'' He snapped his fingers. A door slid open
leading to the next room, and two more men came in. They were of such an
enormous stature that one would have to crane his neck to see their
faces.

``What do you suppose you can do with me?'' Yoming said defiantly.
``Give me a public hanging?''

``Of course not. You were a distinguished member in the fall of No. 6. I
won't be so unforgiving. On the basis of the Committee's judgement, we
will grant you a bonus for your deeds, and a public pension until you
die. But we will seize all of your personal assets in No. 4. You are, of
course, dismissed as a member of the Restructural Committee, and you
will be stripped of all of your qualifications. There will be
limitations implemented on your activities and place of residence. You
are prohibited from moving out of your designated residence, regardless
of what the reason may be.''

``If I don't comply---''

``Then, I cannot guarantee your safety.''

``Heh, so it's basically an outwardly-unoffensive imprisonment. A modern
version of exile. If I get shot through the head for acting without
permission, no one will blame you. No one would be able to blame you.''

The gigantic men moved to stand behind Yoming. Yoming strode toward the
door, half-shoving them out of the way. Then he stopped, and turned
around.

``Shion, you have potential to be a leader like no other. I, or even
that mayor, couldn't compare. Someday, you'll try to dominate over all,
try to have everything within your grasp. You'll reign as a cold,
ruthless, and exceedingly good dictator.''

Laughter---dry laughter rang out and echoed inside the room.

``And when that happens, I wonder how Karan would look at you? What kind
of eyes would she behold her son with, the son who's turned into a
monster?''

One of the men placed his hand on Yoming's shoulder. Yoming brushed it
away, and walked out into the hallway. The door closed.

``Can't even go out without a last bitter complaint.''

``He doesn't know when to stop.''

Number 2 and 3 looked at each other and shrugged comically. They
simultaneously turned back to Shion.

``Shion, we've been tricked, too. We didn't even dream that he'd
embezzle public funds.''

``Really? This data lists your two names clearly as the recipients of a
large sum of benefits.''

Shion smiled serenely at the two men, who had begun to turn pale.

``But I've erased that part. Without your co-operation, we would not
have been able to bring Yoming-san's crime to light. I'm grateful.''

``So we're\el ''

``I myself have nothing to reprimand you about.'' Shion extended his
hand towards the two. ``Please continue to work hard for No. 6. We must
join all our forces to overcome this difficulty. We need your help. I
hope you're willing.''

The colour rose in the cheeks of the two men. They grasped Shion's hand
and nodded enthusiastically.

``See you in this afternoon's meeting, then,'' said Shion. ``I plan to
report this incident in detail from the top. I'm counting on your
assistance.''

``Yes, we'll testify properly. We'll also show our respect for your
swift response and impressive judgement in the matter. You're really an
incredible leader for the next generation.''

``It's an honour. But it's a little embarrassing to receive such glowing
praise.''

``You don't have to be modest. Not anyone can prepare such detailed data
to prove a misdeed. Even Yoming didn't have anything to argue on.''

``He was underestimating us, I think. He thought once he became the
leader of the Committee, he'd be able to forge and rewrite data as much
as he liked. That was why he fought to get to the top as soon as he
could. His desperation allowed careless blunders to happen left and
right.''

``Ah, now I see. Incredible.''

``Indeed, it was,'' agreed the other man. ``Impressive. Now, I think
we'll wrap up here and get to our jobs. We will see you later, then?''

``Yes.''

The two men lined up and exited. Shion was left alone.

``Detailed data, huh.'' He unravelled the computer and cast his hand
over it. The image on the screen crumbled, and the numbers and words
vanished.

There was no such data that evidenced the crime. It likely existed---but
Shion had neither the method nor the time to acquire it. If it did not
exist, he simply had to create it. Create the data that would leave
Yoming with no choice but to admit his crimes. It was not easy, but it
was not such an arduous task, either.

It went well. He had been able to remove one obstacle from his line of
sight. He would remove, drive away, destroy, his obstacles---and then
what?

Shion glanced out the window.

\emph{What am I doing?}

\emph{Creating a state in this world that is different from No. 6---one that is
for humans.}

\emph{Make a country where no one kills, and no one is killed.}

\emph{Is that even possible?}

Yoming's derisive laughter burst in his ears.

\emph{What is going to happen to me?}

\myspace

\emph{Tap, tap.} He heard the sound of the wind. No, not the wind---was someone
knocking at the window?

\emph{Nezumi!}

Shion ran to the window and threw it open. The wind tousled his bangs.
There was no one there. It had just been a passing wind. Shion dropped
to the floor and squatted, covering his face with his hands.

\emph{Nezumi\el why won't you come home? Why aren't you beside me? I just want
to look into your eyes and see that I am me, that I can continue to be
who I am. They are my only anchor.}

\emph{Nezumi, I want to see you.}

There were no tears. A growl escaped through the crack between his lips.
It was an animal growl, in a voice he could hardly call his own.

An alarm went off. It continued to ring. Shion stood up, and
pushed the intercom button.

A young man's voice quietly came through.

``Member Shion, I'd like to hear your orders on the draft of No. 6's new
policies that we will be submitting at today's meeting.''

``Understood. I'll head to Conference Room 3 immediately.''

``Much obliged, Member Shion.''

There was a note of excitement in the young man's voice.

``It's almost coming, isn't it? We're going to clear out the old
political powers and make way to build our ideal state. It's finally
beginning.''

Shion took a breath, and called the man's name.

``Torey, I want you to watch what you say. For us, there is no such
thing as old power or new power. We want to gather the wisdom of each
and every person to progress forward, a little bit at a time. We have no
other way.''

``Oh\el right. I'm sorry.''

``You don't need to apologize, but---'' \emph{You should at least be wary of
wire-taps, Torey.} Shion switched off the intercom, and exhaled one more
time.

He turned around to glance out the window.

A piercing blue sky spread out overhead.

Shion closed the window, and turned his back on the endless expanse of
blue.