% !TeX spellcheck = en_US

\chapter{Flowers for beautiful days}

\lettrine{H}{is hand} stopped where it had extended to sort out the shelf.

"What's this?" he found himself murmuring.

"Shion, you've worked hard enough. That's fine for now, so take a break. I made some coffee. I also have some cookies, though they're a bit stale."

Rikiga was calling out to him with a tray in hand. Coffee and cookies were items that one hardly came across in the West Block.

A pleasing aroma filled the air.

"Hiring you was the best decision I ever made," Rikiga said. "You do everything, from sorting out my bills to cleaning up the room. A worker like you is hard to come by."

"I might not be so good as a bodyguard, though," said Shion wryly.

"Rest assured, I'll never give you a dangerous job like that. Dirty work is more suited for a certain third-rate actor."

"Are you talking about Nezumi?"

"Who else could I be talking about? He's the very man, a cunning, treacherous, and fraudulent bastard."

"Harsh as always when it comes to Nezumi, aren't you?"

"I have to be," Rikiga said matter-of-factly. "Once you let your guard down around a guy like him, he'll suck you dry and gnaw at your bones. Now go on, your coffee's going to get cold."

"Oh, sorry. Thank you. What a treat. It's been a while."

"I can see you're in rough times," Rikiga said sympathetically. "If you're willing, I'm more than happy to let you stay here. You'd have a much more decent life than if you lived with Eve."

"No thank you\el I'm fine."

"Are you really satisfied?"

"Yes. Very much. Nowhere else is more comfortable for me than that basement room."

"That room? Where there's nothing but books?"

"Yes."

It was a beautiful place. That place had everything. Several thousand volumes; vast amounts of knowledge; stories; words at times gentle, at times thorny; nonchalant conversation; secretive whispers; a trembling heart; new discoveries; piping hot soup; and beautiful deep grey eyes.

That room had all of the things that Shion desired.

Rikiga sighed.

"You're not a greedy one, that's for sure."

\emph{Aren't I? No one is greedier than I am. I'm sure no one desires another as strongly as I do.}

"Isn't there anything you want? I'll do anything within my power." Rikiga leaned forward.

"No, really, I don't want any\el oh, but---"

"Hm? What is it? Bread? Meat? Or a warm coat?"

"No, I\el I was wondering if I could possibly see a play\el "

"A play?"

"Yes. I've always wanted to see Nezumi perform onstage\el "

Rikiga drew his chin back. "Eve's performance, huh. I do remember the playhouse manager babbling on about premium tickets and whatnot. Hah, what a joke!"

"Would it be difficult?"

"Of course not!" Rikiga said crossly. "The manager and I are old friends. I can get a hundred tickets for the likes of Eve. Piece of cake."

"Really, Rikiga-san?"

"Yes. I'll take you wherever you want to go. You can even invite your friends along, too, ha ha ha! And besides, you know\el " Rikiga cleared his throat awkwardly. "I guess you could say Eve's performance is worth a look. It's decent for a shoddy run-down place like this, I mean."

"Can I bring Inukashi?"

"Of course, if that's what you want to---what? Who?"

"I want to invite Inukashi along."

"Why do I have to take a mongrel brat like him?"

"Inukashi's my friend, and I don't really have any other ones. Besides, Inukashi loves to hear Nezumi sing. I want to give him a chance to really enjoy it."

"\el Good god. It's a bit too late to be saying this, Shion, but you haven't exactly surrounded yourself with the best bunch. You should start getting yourself some decent friends."

"Both you and Inukashi are the most interesting, wonderful people I've met, in my opinion," Shion said firmly. It was his honest opinion. Those two were the kind of people he would never have met inside No.~6. They were the most interesting company he'd ever had.

"Like I said, don't lump me in with the mutt. But, well, fine. I got it. I'll take you and the dog."

"Thank you. I'm really grateful, Rikiga-san."

"Don't worry about it. I just can't seem to say no to you. Well, finish up that cookie. I'll have a sandwich ready so you can take it home when you leave. Of course, that's on top of the wages you'll get. You don't need to feel obliged; just think of it as a cleaning fee. This room looks a lot neater thanks to you."

"Oh, which reminds me---" Shion showed him the cover of an old magazine he found on the shelf. There was a crowd of people on the cover and across the spread. A decked-out maiden; a youth wearing a feathered hat; an elderly woman wearing a silver shawl; an elderly man wrapped in a magnificently-embroidered cape; men, women, children. Everyone was smiling. Some were dancing; one had a stringed instrument in hand; another looked like he was singing. The photo was lively and joyous, yet faded with age.

"Oh, this is the Festival of Flowers," Rikiga said.

"Festival of Flowers?"

"Yeah. We used to have this festival when this area was still a quaint, beautiful town. It took place when spring was at its finest. We prayed to the gods and thanked them for the blessings they'd bestow on the land."

"Everyone looks like they're having a great time. I couldn't help but gaze at it."

"You're right. People back then still hadn't forgotten their respect and gratitude to the gods. Oh, this brings back memories. A group of singers would come out from far away, just for that one festival. They sang a song for God in the most beautiful voices. There they are on the cover, the women decorated in flowers."

"These women\el where did they come from?"

"I'm not sure where. I remember hearing that they came from the deepest part of the woods, but I was never sure. They appeared for the festival, and were gone the next day. Come to think of it, they were strange people. But by the time No.~6's wall was complete, the festival and the singing troupe were gone."

Rikiga gave a hefty sigh. His gaze wandered the air as if searching for something. Shion looked at the beautiful singers in their white costumes and white ornamental flowers.

They looked like Nezumi somehow.

\mybreak

"Festival?"
Nezumi uncrossed his legs.

They were in the basement room. The stove was burning, and the little mice were scurrying about.

"Yeah. I borrowed this. It's a photo of the festival." Shion put the magazine down beside Nezumi. Nezumi only glanced at it, and showed no signs of picking it up.

"What about it?" he said.

"This woman looks like you."

"Me? I don't know about that. She's chubby compared to me, and her nose is flat."

"You might be better-looking, but she looks like she's enjoying herself. It's almost as if you can hear the singing and the crowd buzzing. Festival of Flowers," he murmured to himself. "I wonder what it was like."

"It's all from the past." Nezumi closed the book he was reading and stood up. "The lost past, faded days, a festival that only remains in vague memories. What good is it to me? Only a certain sentimental sheltered boy would find any use for it. To play with, like a toy."

"\el I thought maybe you could sing it."

"What?"

"I had a feeling you would know how to sing the song of the festival."

"Me? Why? For your information, Shion, I know next to nothing about the Festival of Spring."

"Festival of \emph{Flowers}."

"Flowers. Whatever. Either way, it has nothing to do with me."

"Yeah, but\el "

Nezumi suddenly yanked at Shion's hair.

"Ow! What was that for?" Shion protested.

"What kind of song would you make it?"

"Huh?"

"The festival song. What kind of song do you think it was?"

"Huh? Well, I guess it would be, like, you know\el "

"Like what?"

"\el A song of joy, I guess. The long winter is finally ending, and the season of blossoms is on its way. The sky will turn blue, and the breezes will soften. The air will taste fresher, and the birds and insects will start becoming active. Doesn't it make your heart feel lighter?"

Nezumi sat down and crossed his legs again.

"I see. So it would celebrate the beautiful season."

"Yeah. The world, once closed off, would open up with the coming of spring. Farmers would begin their intensive fieldwork, and the children would be able to start playing outside again. It's\el how should I say it\el a season that would want to make you believe in hope."

"The future might just hold despair. The chances of that are much higher."

"That's why they held a festival." \emph{People want to change despair into hope, ill luck into fortune, anguish into happiness. People have hope. That's why they pray to God. That's why they offer their songs, plead with Him, and seek His protection.}

"They clung pathetically to God," Nezumi said shortly.

"They tried to live in harmony with Him," Shion corrected.

Nezumi lapsed into silent thought for some moments.

"Shion."

"Hm?"

"There aren't any festivals in No.~6, are there?"

"No. Only the Holy Celebration, but it's nothing like a festival. There's no singing, dancing, or joy. Nezumi, I think only festivals are born if people's hearts are free. They aren't born if people are trapped, dominated\el am I wrong?"

Nezumi did not answer him.

All he did was close his eyes and repeatedly take quiet breaths.

\mybreak

It was unbearably stuffy inside the playhouse with the heat of the throng.

"What a turnout," Shion said. "It's beyond what I imagined."

"Ugh, booming business as always," Rikiga said sourly as he clicked his tongue. "I'm sure the manager is raking in the money. He sure knows where the business is. Damnit!"

"Just lure Eve over to your side," Inukashi cackled, his shoulders shaking with his laughter. "They're all here for him, anyway. Then you'll be the one rolling in the dough, old man."

"What? You're telling me to team up with that wily fox? Lay off the jokes, will you? There's nothing I hate more in this world than that guy. He and I are practically archenemies."

"What lies!" Inukashi howled. "You're practically a fan boy. I know you come for almost every showing."

"Shut up! I haven't even turned my nose in this direction since finding out who he really was. I'm here tonight because Shion said he absolutely wanted to go, no matter what, and so I had no choice\el "

"So you jumped at the opportunity and rushed over."

"I'd say you're the one jumping at the opportunity, Inukashi," Rikiga retorted loudly. "You were itching to see Eve perform." The man in front of him turned around at his voice. He was bearded and intimidating.

"Shut the hell up back there."

"Oh---terribly sorry." Rikiga ducked his head. The stage lights went out as if on cue. A spotlight shone down on centre stage. There appeared Nezumi---no, Eve.

The stage had only one spotlight. There were no microphones, no orchestra, or any stage equipment.

A draft was coming in from somewhere, and Shion could feel the cold creeping up from his feet. A quiet song rang out through it all.

"It's 'The Shimmering Things'," someone whispered. It was a faithful maiden's love song. It was clear and soft, yet it exuded a heated passion.

Shion could only listen in awe. His heart was stolen away from the very first song. He felt as if he existed solely to listen to Eve's singing.

Once Eve finished, a moment of silence was followed by thunderous applause. It was enough to make the run-down playhouse shake.

Eve smiled graciously and slowly bowed his head.

Then came the second song.

\poem{O soul, O soul\\
	From where do you come? Whither do you go?\\
	I want to keep holding you in my arms, and yet\\
	Will you fly away\\
	With the wind, to the high skies?\\
	Will you soak through\\
	With the rain, into the earth?}

"The song of burial." Inukashi trembled. "He sang this when my Mum died\el "

\poem{Will you envelope me warmly\\
	With the light?\\
	O soul, before you become the wind\\
	Before you turn into the rain\\
	Before you glow as the light\\
	Just once more\\
	Come back into my arms\\
	One day, I will also become the wind\\
	Become the rain, become the light\\
	And embrace you\\
	Embrace you.}

Someone was sniffling. The giant man in front of Shion was weeping.

The third song took a brighter turn with a lighthearted dance piece. For the fourth, a song of lost love between young lovers. Eve unveiled one song after the next.

Then, the last song.

"A song for the far past and far future. A song for those who believe in what's to come," Eve announced. He regulated his breathing, then began to sing.

\poem{Spring is coming\\
	The flowers bloom\\
	The skies are blue, the breezes sweet\\
	Come, everyone, come outside\\
	Let us sing\\
	Let us gather\\
	Let us dance\\
	Today is the Festival of Flowers; tonight the Flower Ball\\
	A festival for those who believe in tomorrow}

Eve gave a wide sweep with his hand. Flower blossoms danced in the air. Petals of all colours and shapes, in the thousands, in the ten thousands, showered down from above. It was, of course, an illusion. But Shion could definitely see those illusory blossoms.

\poem{Let us live and celebrate\\
	Let us love another\\
	And stretch our hands to tomorrow\\
	Today is the Festival of Flowers; tonight the Flower Ball\\
	A beautiful day for God and His people}

"Hey, is this---" Rikiga held his breath. It was. The song of the Flower Festival. A song celebrating hope.

\emph{You did sing it, Nezumi.} Shion closed his eyes and placed a hand on his chest. \emph{Nezumi, some day with you\el }

He mentally spoke to the boy onstage.

\emph{Some day, I want to create a real festival with you. When real peace finally prevails in this land, we'll create the Festival of Flowers once more. We will.}

\emph{You won't mind if I call this hope, would you?}

The song ended.

Eve lowered his head gracefully in a deep bow.