% !TeX spellcheck = en_US

\chapter{Days in the West Block}

There was not a cloud in the sky that day in the West Block, and it was
bright and clear. It was truly a cerulean sky.

But of course, since the West Block lay in the shadow of No. 6, daylight
hours were always short no matter how sunny it was. In the winter, it
was especially so.

Shion looked up at the sky, and gave a huge stretch. The suds on his
hands turned into small bubbles that floated into the air above.

They reflected the light and sparkled in rainbow-coloured hues.

"It's such a nice day today."

The blue of the sky and the light from the bubbles stung his eyes.

"Hey, Shion. Get a move on." Inukashi looked up from making soap suds in
a bucket to glare at Shion. The light on his raven hair made it look
even more black.

"Take your sweet time, and the sun'll be down before you know it. We
gotta finish washing the dogs by afternoon. 'Cause if they don't get
washed by then, we'll have to burn a whole extra fire just to dry them
off. It's a waste of firewood."

"Oh, right. Yeah. Sorry about that."

"Well\el you don't have to apologize, or anything." Inukashi sniffed his
nose. "You're just way too thorough. You just gotta wash 'em quick,
rinse 'em off quick, and you're done. My dogs aren't princesses."

"But if you don't rinse them off properly, they're going to get skin
infections."

"Skin infections? That true?"

"Yeah. I've started reading more animal-related books since I started to
work here. Nezumi's got all sorts of books in his house."

Inukashi wrinkled his nose. He flapped his hand in front of his face as
if to wave away an odour.

"Do me favour and don't mention his name around me, will ya? Makes me
feel sick. If you're gonna read something, at least read something like
'How to Exterminate Sneaky Rats'."

Shion couldn't help but smile wryly.

"I remember seeing a book on how to exterminate regular rats."

"Heh, regular methods aren't gonna work on someone like him. But that's
enough of that. Why did you hafta bring up the world's most obnoxious
guy on such a nice day?"

"Do you hate Nezumi that much?"

"Damn right I do." Inukashi spread his arms widely. "Even if someone
gave me a hundred gold coins to like him, I couldn't. If it was
possible, I'd avoid associating with him for my whole life."

"Inukashi, I think that's being a bit harsh."

"Heh, harsh? You must be kidding me. I haven't even said half of what I
wanna say. That old man's a fake, but compared to Nezumi, he's as
innocent and harmless as a newborn baby. Shion, lemme tell ya something:
there's nobody more dangerous, disagreeable, and a pain in the ass than
Nezumi."

Shion stopped midway through washing a dappled brown dog.

\emph{He's more dangerous, troublesome, strong, and beautiful than anyone else
in the world. That's Nezumi.}

He caught Inukashi looking at him. He felt like Inukashi had seen right
through his thoughts, and his cheeks burned. Shion looked down to hide
his flushed face, and scratched the dappled dog on the back. The dog
seemed to enjoy it, for he narrowed his eyes and let out a quiet growl
of pleasure.

"And?" Inukashi pressed.

"Hm?"

"That skin infection you were talking about earlier. So it's bad if I
don't rinse them properly?"

"Oh---yeah, that's right. When there's soap residue left on the skin, it
could cause rashes and the fur can fall out. You have to wash the soap
off properly."

"You serious? I can't afford my dogs getting any skin infections, man. I
wouldn't even be able to rent 'em out at the hotel. Shion," he said
briskly, "rinse 'em good. Get all the soap out. Be extra careful about
the ones with long fur."

"Alright, but I don't think I'd be able to get through all the dogs by
sunset. Should I finish the rest off tomorrow?"

"Tomorrow, huh." Inukashi looked up at the sky, and squinted at the rays
that shone down upon him.

"Shion, wanna know something else, while I'm at it? No one makes
promises about 'tomorrow' here in the West Block. Doesn't matter how
important that person is to you, or anything. There's no such thing as a
'tomorrow' here. Sure, today might be the sunniest, warmest, most
beautiful day ever. But no one knows if it's gonna be the same tomorrow.
Actually, the weather usually takes a turn for the worse after days like
this. A cold wind comes, and you start seeing flurries of snow. Then the
ground freezes over, along with your feet, the water from the spring,
and everything else around you. Starving kids and old people start
dying. Same for young, brawny guys, too. They're not free from death.
Say, for example\el he's walking down the street one day, with a loaf of
bread that he's worked all day to get. He could get attacked from behind
by a group of kid thugs who are after his food, get his skull cracked
open, and it's off to heaven for him. These cases aren't uncommon. Oh
yeah, you've experienced it before too, right? Some starving brats
mugged you and took your bread in the marketplace?"

"Ah---yeah, that's happened before."

"Knowing you, you probably didn't even put up much of a struggle when
they tried to steal your bread. That's 'cause you don't know how much a
slice of bread is worth in these parts. My dog told me you practically
gave your bread and meat away. He wasn't very impressed."

"Your dog was watching?"

"You bet he was. I sell information, man, it's my business. My dogs are
everywhere in the West Block, sniffing stuff out. Your airheaded antics
aren't worth much in terms of information, though, just to tell ya."

"I can see that."

Inukashi shrugged, and sighed impatiently.

"Well, you got your bread stolen because you were quiet---or spaced out,
more like. It's embarrassing, but you might call it lucky. If you
struggled like no tomorrow, they'd try harder to take it away from you.
Who knows, worst-case, you might've been whacked from behind with a
metal bar and had your brained splattered on the street."

Shion clutched his head reflexively. Inukashi curled up, cackling
lightheartedly.

"I hear you've got some good brains, but they'd be no use if they were
splattered all over the place, huh?"

"You're giving me the chills."

The smile vanished from Inukashi's face. He gazed at Shion with a stony
expression.

"No one knows about tomorrow. Not a single soul here is absolutely sure
that they can live to see it, Shion."

Shion directed his gaze to the sky once again.

Under this cerulean sky, there existed tragic life and death. There
existed lives easily wrenched away. There were people who had to claw
and struggle to even see a faint image of tomorrow. It was his own
affair as much as everyone else's. \emph{There's nothing ensuring me whether
I'll even be alive tomorrow.}

\emph{That's reality.}

\emph{The reality of the world I live in.}

\emph{I can't avert my eyes from it. I can't turn a blind eye, or simply let
it slide. I have to face, and accept this reality.}

"Hey-hey, Shion." Inukashi clapped his hands. The sound echoed crisply
in the clear sky. "If you got time to be spaced out, get a move on.
That's one of your biggest flaws, eh---thinking too much about everything.
Before you start mulling over this or that, get your body moving and get
some work done. That's a hundred times more useful."

"Another of your teachings, huh, Inukashi."

"Yeah. I'm a gold mine of the kind of wisdom you need to live well. I
gave you some advice for free, so you better be thankful."

"I am. Thank you."

Inukashi visibly shuddered. "Shion, I'm begging you, don't be so frank
about saying thanks. It makes my skin crawl."

"But I really did feel thankful---" Shion protested.

"Geez, I don't think I've ever met someone as honest and simple as you.
I can't see how you can live with such an unfathomable, shifty,
difficult, and twisted guy like Nezumi. Is it true what they say about
how opposites do well together?"

"Inukashi, you're being harsh again. Nezumi isn't shifty or twisted. I
know he can be\el difficult sometimes, or hard to see through, but\el "

"Dumb ass! That's what I'm saying when I say you're naive. Nezumi is as
shifty as it gets, just as much as you with your airheadedness. You
should get a certificate for that, by the way. Hah, I guess if you think
about it that way, you two \emph{are} actually kind of alike."

"Bit rude, that, Inukashi."

Inukashi bolted up. He snapped his eyes open wide, and whirled around.
Shion also twisted around to look, his hands still covered in suds.

Nezumi was standing there, catching the soft winter rays. His
shoulder-length hair glowed and shimmered in the sun. His lips were
curled sardonically, but mirth sparkled in his eyes.

"How long have you been there?" Inukashi swallowed hard.

"Just a little while."

"What do you mean, just a little while?"

"Right about when you were saying you wanted to know about How to
Exterminate Sneaky Rats."

Inukashi sighed. He turned to face Shion, and gave a great scowl.

"See what I mean, Shion? This guy sneaked up from behind us, and made
sure we didn't even notice as he eavesdropped on our conversation. You
can't trust yourself to do anything around this guy."

"Rude again, Inukashi. I wasn't eavesdropping. You weren't even talking
about anything worth listening to. You guys were too into your animated
little chat to notice my presence, that's all."

"What do you want?" Inukashi said brusquely.

"Don't get so worked up over it, Inukashi," Nezumi drawled. "I just
thought I'd swing by. I wasn't expecting to be treated to tea or lunch,
or anything like that."

"Damn right you weren't," Inukashi said with bared teeth. "I wouldn't
give you a single bowl of soup if I could help it. If you want me to
empty it over your head, that's another story."

"Oh dear, see how the boy hates me. But not to worry, I'd turn down the
soup anyway. God knows what you'd put into it."

"Say what you will." Inukashi clicked his tongue irritably, and resumed
washing his dog with even greater zeal. "Hey, Shion. Never mind Nezumi.
The dogs are the ones that need attention. Twenty-one left, and we're
gonna finish washing them by sunset."

"Got it. Oh, Nezumi."

"What?"

"Can you help us?"

"What?" Nezumi said incredulously.

"You're off work today, aren't you?"

"Well, yeah, but\el "

"Then help us. We're short-staffed here."

"You're telling me to wash a dog?"

"Yup."

"No thanks. Nothing is worse than inferior soap, water, and dog hair,
especially if they're combined. The state it would put my hands in\el "
Nezumi clenched his fingers softly. Just that gesture was elegant enough
to make one's breath catch.

"Then I want you to towel down the dogs after I finish washing them,"
Shion said promptly. "Get as much moisture out of their fur as you can."

"Like I said, why do I have to associate with these mutts---"

"Please. Help out." Shion held out a bunch of rags toward Nezumi. Nezumi
drew his chin back in disgust.

"Hey, Shion---"

"This dog first. Wipe him down thoroughly. Quickly, though. He's an old
dog, so if you leave him wet for too long, he might catch a cold.
Careful about that. Come on, boy, you have to ask him nicely too," he
added to the dog.

The dappled dog shook his coat vigorously at Nezumi's feet. Water
droplets flew in all directions.

"Hey---stop that! You're drenching \emph{me}," Nezumi complained.

"So wipe him down. Come on."

"Geez, why do \emph{I} have to take care of the dogs\el "

Nezumi nevertheless began to towel the dog off with a rag.

"Nezumi, you can't scrub like that. You have to wrap it gently, and let
the cloth suck up the moisture. I know that rag is tattered, but it
absorbs water well."

"Shut up. I know how to wipe a dog without getting instructions from
you."

"See, the dog doesn't like it. You're being too rough."

"I know that. God, are you my mother or what?"

Inukashi hunched his shoulders and chuckled.

"You guys are hilarious as always. The way you two go on about it is
just \emph{classic}. You know, you guys could probably enter a stand-up
competition. Eh, Eve? Maybe you're more fit for comedy instead of
singing onstage."

Just as Nezumi opened his mouth to reply, Rikiga peeped out from between
the ruins. His entire face was red.

"Holy, you stink of booze," Inukashi complained loudly. "You in Drunkard
Mode already, old man? It's still morning." He pinched his nose.

"Ha ha, big deal. Like they say, God's in his heaven, and all's right
with the world. Cheers t' a peaceful morning! Oh, morning t'you, too,
Shion. How're you?"

"Good morning, Rikiga-san. You're in a good mood."

"Just seeing your face puts me in a good mood, y'know. \emph{Whoa}--- Eve, what
are \emph{you} doing here?"

"It's not like I want to be here."

"I jus' came to see Shion's face---" Rikiga slurred, "why do I hafta see
you or Doggy Boy? This is \emph{highly unpleasant}---"

"Cut the crap," Inukashi snapped. "This is \emph{my} hotel. You invited
yourself here, you've got no right to complain."

Rikiga ignored Inukashi completely.

"Shion, I brought you something real good. Have it for lunch. Here!"

Rikiga offered him a paper bag. Shion peered inside, and gave a small
shout.

"Whoa, muffins!"

"Muffins?" Inukashi swiped the bag from him. "Whoa, cool! So these are
what they call muffins, huh? I've never seen them before. It smells
awesome." His tan nose twitched busily.

Nezumi gave a short, appreciative whistle.

"Where'd you nick so many, old man?"

"Idiot, the Great Mr. Rikiga would never steal. I'm not like you.
Someone gave them to me. Heh heh," he chortled proudly. "These muffins
are from No. 6. One of my customers brought them as a small gift. So how
do you like 'em? They're from a bakery that's supposedly famous for
their muffins. Hah, see? Even though I'm all the way in the West Block,
I can still get my hands on muffins from No. 6. Pretty amazing, aren't
I? Heh heh."

"What, so you came to brag? Give me a break. I didn't think you were
\emph{that} pathetic, old man Rikiga."

"So Doggy-boy thinks he can be a smartmouth now?" Rikiga replied
indignantly.

"Rikiga-san, do you have time right now?" Shion cut in.

"Huh? Me? Well, I am a successful businessman. Men of property like me
don't have to slave the day away like poor people."

"Then I'm sure you could help us with washing the dogs."

"Huh? Washing the dogs? Wait a minute, Shion. I only came to drop off
these muffins for you, and---"

"Please, if you could pour water over them with this bucket here.
Slowly, and evenly."

"No, what I'm saying is, Shion---"

"You're a great help. Now, we should be able to get everything done by
evening."

"Yes, but Shion, I never said I would---"

"Give it up, old man." Nezumi gave a small smile. "Do as you're told and
get it over with."

Then he turned to Shion and pointed his thumb up.

"You've gotten awfully good at getting people to do your bidding,
Shion."

"Well, you trained me, so\el "

Rikiga punctuated the air with a single sigh. Then, mumbling something
under his breath, he lifted the bucket.

\mybreak

The sun had begun to dip and darkness had begun to settle on the West
Block by the time they had finished washing the dogs.

"Good work, everyone. Tonight, I'll give you guys a special treat of
soup and drinks. You're welcome." Inukashi stared around with his hands
on his hips at the three sitting down on the ground.

"This is a joke!" Rikiga grumbled. "You wore us down to the ground
without even any lunch to eat. Give me my muffins." Rikiga shook his
fist in the air.

"So like I said, I'm gonna let you guys eat now. \emph{With} soup and drinks."

"You mean water, right?" said Rikiga sourly. Nezumi smiled wryly.

"Water, properly boiled," he added. "It's still warm. Come on, everyone,
let's dig in. It's a feast."

Two muffins each, hot water in tin cups, and thin soup seasoned with
salt. In the West Block, it definitely fell into the category of a
feast.

\emph{This taste---}

Shion's heart thudded loudly as he took a bite of his muffin,

It tasted like his mother's baking. They tasted just like Karan's
muffins.

\emph{Can it be---}

\emph{Where did you---?}

Shion swallowed his words a moment shy of posing Rikiga the question.

There was a wall between his mother and him.

Right now, it was a wall over which he had no way to climb.

He could not ask a question if he knew the answer would do him no good.

His gaze met Nezumi's.

You're right, Nezumi.

\emph{That's it, Shion. Keep silent, not because you've given up, but because
you've made the decision. You have to shoulder the weight of your
silence.}

I know.

\emph{Do you? Maybe you just think you know.}

Nezumi's gazed pierced through him. Those grey eyes gave Shion the
impression that they knew everything. He wondered why every time he was
held by this gaze, he felt a shiver of bliss rather than pain.

"Ah, but I have to say, nothing tastes better than a meal after a hard
day's work." Rikiga gave a great yawn.

"From now on, you should vow to dedicate yourself to honest labour more
often, old man."

"Heh, I don't want to hear the word 'honest' come from the likes of
you."

Half-listening to Inukashi and Rikiga bickering, Shion slowly brought
his muffin to his mouth. Up above in the sky, the stars were beginning
to twinkle.