% !TeX spellcheck = en_US

\chapter{Who did see him die?}

\myepigraph{Who did kill cock Robbin?\\
	I, said the sparrow,\\
	With my bow and arrow,\\
	And I did kill cock Robbin.\\
	Who did see him die?\\
	I, said the fly,\\
	With my little eye,\\
	And I did see him die.}{Mother Goose}

\lettrine{T}{he man} was gazing at the gold coin Inukashi had given him with
fascination.

"It's real," Inukashi whispered to the man's profile, with its thin and
jutting chin. He dropped his voice into a hush to make himself sound as
intimidating as possible.

"It's real gold... is it?" The man's Adam's apple bobbed up and down.

"Look at it for as long as ya need to. It's the real thing, no matter
which way ya look at it."

"Y-Yeah... you're right, it's real..."

"It's yours." This time, Inukashi spoke a little quicker, like he was
thrusting the words onto him. The man's chin trembled.

"Mine?"

"Yeah. Yours. I'll give it to ya."

"What? But―ah―a whole gold coin, it's so much money―"

"Of course, I'm not saying it's for free. I'm not a do-gooder with money
to spare. I'll give this to you as payment for a job. How about it?"

"Job?"

The man's eyes shifted from the gold coin to Inukashi. His eyes were
round, like some frightened pet animal. A shade of suspicion flitted
across them.

\emph{Here it comes.}

Inukashi clenched his fist.

\emph{This is the crucial moment. I won't give this guy any room to think. I
won't let any suspicion sneak into his thoughts. I'll wave the gold in
front of him, and tantalize him. It's gold, man, gold. Not something
he'd be able to lay his eyes on often. Not to mention, this guy wants
money, \emph{needs} money... but then, I don't know who \emph{wouldn't} want money,
unless they were dying.}

You just had to dangle the other's most desired object in front of his
nose. You had to ensnare him with crafty words. You would chase him into
a corner so he wouldn't be able to escape. You would do it thoroughly,
and with skill. All he had to do was trace Nezumi's way of doing it.
\emph{He's done it to me enough times for me to get sick of it.}

\emph{Heh.}

He felt like he could hear Nezumi chuckle. He could even see Nezumi's
unique ironic smile.

\emph{See, you \emph{can} do it just as I taught you. Good boy. I'll give you a treat
later.}

Shut up, Nezumi. Just to let you know, I'm not undertaking this to help
you. It's for the gold bullion. I'm crossing the perilous bridge so I
can lay my hands on that gold bullion.

He shook his head to dispel the illusion.

\emph{Stop popping into my head like that, asshole.}

"Job... what do you mean?"

"A job is a job. I'm asking you to do a job. For a gold coin."

Inukashi snapped his fingers smartly. The man blinked. The shade of
suspicion in his eyes grew more pronounced.

The man was called Getsuyaku. His job was managing the cleaning duties
at the Correctional Facility. He was Inukashi's acquaintance. A while
had passed since Inukashi had first started receiving his stock of
Facility waste and leftover food from Getsuyaku. Of course, it was an
under-the-table transaction; it was smuggling. About once every three
days, Inukashi received a portion of leftover food and waste, and handed
Getsuyaku an amount that was appropriate for the load. It was usually a
few copper coins. If there was a considerable find, a silver coin.

But this was probably the first time they had exchanged so many words
with each other. It was always only a couple words, things like: "This
is it"; "Thanks. Your payment, then"; "Right"; they didn't even count as
conversations, and they didn't make eye contact either. It had always
been this way.

Getsuyaku was in charge of managing and incinerating the waste produced
by the Correctional Facility, as well as operating the cleaning robots
inside. In a small room adjacent to the waste collection area and the
incinerator, he spent the whole day alone, operating machines.

"When I'm here, I don't say a word all day. I don't see anyone, I don't
talk to anyone. It's really lonely. Sometimes I can't tell if I'm still
a human, or becoming a machine myself." One day, on a rare occurrence,
Getsuyaku had loosed a string of complaints. Inukashi had given him
offhanded answers. \emph{That must be hard}, he had nodded, but had responded
scathingly in his mind.

\emph{Stop acting like a baby.}

The monitoring room for the disposal of leftover food and other trash
was located in the most remote part of the Correctional Facility. All of
the trash produced in the facility was collected here. The machines
sorted through it and carried it to the incinerator; machines adjusted
the temperature of the incineration, and disposed of the ashes. Almost
the entire procedure was completed automatically. Getsuyaku's only job
was monitoring and tuning the machines. One person was enough for the
job. Sure, a workplace without anyone to talk to was probably lonely. So
what? You wouldn't die from not speaking for a day.

\emph{Try living a life where you're so, so hungry that all you can think
about all day is food. Try spending your days licking pebbles on the
road to stave off your hunger. Loneliness? That's just a luxurious toy
for you people who don't have to worry about filling your bellies.}

But Inukashi only remarked in his mind. Out loud, he feigned pity,
saying things like, "that must be hard". Getsuyaku was an important
partner in trade. Nothing good would come out of getting on his bad
side.

Although the sorting, incineration, and cleaning of the incinerating
chamber were all automated, the step before the sorting required human
hands. It was the task of transferring the trash from the collection
area to the conveyor belt. For some reason, this step was the only one
that was not automated. Getsuyaku had to operate a small power shovel
himself to lift the trash onto the conveyor belt. Sometimes he even had
to use an archaic tool like the shovel to scrape it out by hand. At this
step, he would swiftly set aside raw garbage, or clothes that still
looked wearable, and hide them. Inukashi bought the lot off of him: that
was how it worked. Inukashi distributed his wares to the food vendors
and secondhand clothes merchants in the West Block, and made a decent
amount of money.

For Inukashi, it was a heaven-sent fortune that there was a manual task
before the automated process. It was thanks to this that he was even in
business.

Getsuyaku's workplace was equipped with neither surveillance cameras nor
security systems. If anything happened, Getsuyaku himself had to flick
the emergency switch on the corner of his control panel.

"I don't imagine they would actually come to help, even if I did flick
it." Inukashi remembered Getsuyaku muttering as if to himself, gazing at
the red switch.

Although facility employees were normally taken from the general gates
to their respective sections by shuttle bus, Inukashi had heard that
Getsuyaku was the only one being crammed into an outdated compact
automobile.

"Being treated like that makes me feel ashamed of myself. I don't have
pride in myself anymore."

This was probably another one of his complaints. These days, Getsuyaku's
complaints had increased noticeably.

\emph{Pride? Hah, first loneliness, and now pride? So you're pulling out
another luxurious toy to show off, huh? Geez, the least you could do is
talk about something that would fill my stomach.}

These were, of course, remarks confined to his mind.

He didn't care about Getsuyaku's loneliness or pride. What mattered was
that this was the one and only place that was off the dense map of
surveillance criss-crossing far and wide throughout the Correctional
Facility. It was also the one and only place which was connected
directly to both the West Block and No. 6 without any barriers. He could
naturally see why Nezumi had set his sights here. However, it was
impossible to go beyond and get inside the Correctional Facility from
here. The hallway leading into the main parts were blocked by double
doors, and they were made so that they could not be opened from
Getsuyaku's end.

Whoever designed this stout building had made it into a kind of dungeon
where infiltration and escape were both exceedingly difficult; maybe
this guy had poured so much life's blood into the effort that he didn't
have attention to spare for the waste disposal system. Or, maybe he
never had any consideration for the people managing the waste. Even in
the Security Bureau, which presided over the Correctional Facility,
there would probably be no officials at all who were concerned about
Getsuyaku's working conditions. If an accident happened during the
operation, and Getsuyaku suffered a life-threatening wound, not in a
thousand chances would the Facility doors open from the inside to admit
paramedics. The doors would remain closed, and Getsuyaku would be left
to die.

It felt strange, to think of it this way.

As a resident of Lost Town, Getsuyaku was a semi-citizen. But it didn't
change the fact that he lived inside the city. He may be poor, but he
could live without fearing starvation and the pain of freezing in the
cold. He was fortunate enough to be able to complain of loneliness. To
people of the West Block like Inukashi, his lifestyle was equivalent to
heaven.

Inukashi could tell even from their sparse exchange of words that
Getsuyaku was an honest and amiable man. But even Getsuyaku's gaze
sometimes carried a hint of scorn or superiority when he looked at
Inukashi, the West Block resident.

\emph{I'm still higher than him.}

\emph{I can eat 'til I'm full.}

\emph{I don't have to freeze in the dead of winter.}

\emph{I am a citizen of No. 6.}

\emph{That's why I'm higher than him.}

\emph{It was a funny story.}

People put other people into classes. Those who were looked down upon
and slighted turned around and looked down upon others and slighted
them. This was not a mechanism of society that forced them; people
established such order in their own hearts, of their own will.

Getsuyaku, who was treated like less than a machine by the upper class
of No. 6, who lamented this treatment, and even complained about it,
showed a superior attitude to Inukashi, because he lived in a corner of
the West Block. He condescended upon him.

It was a funny story. And it was strange.

Sometimes he thought humans were even more foolish animals than dogs.
Dogs also had a social order, but it was based on their strength. Dogs
didn't rank themselves based on pedigree, the state of their coat, or
where they were born.

Humans weren't bothered at all at doing something even dogs didn't do.
Humans― what ridiculous―

\emph{We're all the same.}

He suddenly recalled a voice. It rang faintly deep inside his ears. It
wasn't Nezumi's. Nezumi's voice was vivid too, but it wasn't as soft as
this.

\emph{Shion....}

\emph{He's a weird, pampered boy with white hair. Not to mention he's a
most-wanted criminal on the run. Top-class criminal. That's something
you can't just wake up and decide to be one day. Leaves me in awe,
really. But on the other hand, he did turn out to be an airhead with a
capital A.... just baffles me. He's such a weirdo.}

But he'd said this once.

\emph{They're the same humans as us, Inukashi.}

And then I asked him.

Are you and I the same humans?

\emph{Yeah.}

Are the people of No. 6 the same humans as us? The answer had come back,
clearly, with not a hint of hesitation.

\emph{Yeah.}

Shion. He was a weirdo, through and through.

\emph{Hey, Shion. Don't you have any sense of hierarchy in your heart? Don't
you draw lines between groups of people at all? Don't you ever feel
contempt towards other people, and then feel you're better because of
it?}

Shion, as humans, are we really all equal?

"What do you mean by... job?" A hoarse voice questioned him. Inukashi's
mind, which had been deeply immersed in thought, took a while to
respond.

"Eh?"

"The gold-coin job... what do I have to do?"

"Oh! Right, that." \emph{He sure swallowed the bait easier than I imagined.
This old man must really need the money.}

"Just to let you know, I'm not taking any dangerous jobs," Getsuyaku
said hastily. "My baby is due in the spring. I've still got to work and
keep earning a solid wage into the future. Under no circumstances
whatsoever will I take a job that endangers my life."

\emph{I see. Fine, fine. You don't want to get yourself in danger. But you
still need money desperately, enough to do almost anything. I see.}

Inukashi narrowed his eyes and let a slow smile spread across his lips.
This was also an expression he had picked up from Nezumi. When you
wanted to entice someone, you smiled at them gently, like this. If
possible, so beautifully that the other's breath would catch in his
throat...

\emph{Fat chance I'd be able to pull it off. I'm no actor. I can't put people
under a spell as easily as Nezumi does.}

He tried smiling anyway. \emph{And then... then what next, Nezumi?}

He felt his heart racing. His heart pounded against his chest. He heard
the thudding in his ears. His palms were sweating as he clenched his
hands into fists. Sweat streamed down his back. His throat was dry, and
his tongue felt like sandpaper.

Inukashi realized he was almost nervous out of his wits.

He realized he had to lure this man into his trap using any method he
could get his hands on. He had to get the man to do what he wanted, no
matter what it took. He had to make him do it. If he failed, Nezumi and
Shion's escape route would be completely closed off. He would never be
able to see them again.

They had made a reckless bet from the beginning, anyway. There was less
than a one-percent chance of them escaping the Correctional Facility.
Those two had embarked anyway. He thought they were stupid to do so.
Fools of fools. It was logical for fools to perish. They were reaping
the rewards for what they had sown.

\emph{I know that's how it is, I know. But―}

\emph{But I'm still wishing they'd return. I find myself still wanting to see
them again. Yeah, sure, I've got my sights set on the gold bullion, too.
My eyes are dazzled by the mountain of gold. But I want to see them too.
I want to hear with these ears again, Nezumi's sarcasm and laugh,
Shion's awkward way of speaking.}

'Oh, you're back.'

'So I am. I told you I'd come back. I don't make empty promises.'

'Egh, stop trying to act cool. Does that mean I get to hear you prattle
on forever again? Gee, I can hardly wait.'

'Inukashi, I'm sorry for worrying you.'

'Worry? Hah, Shion, are you still dreaming? I haven't been worried even
a teeny―'

'You were worried about us, right?'

'Idiot.'

He wanted to have that sort of conversation with them. He wanted to
exchange words with them. \emph{I... I'm actually, seriously, praying that you
guys will survive, and that you guys will come back still living. I
won't pray to God. I won't cling to Him. I'll pray to myself, and cling
to myself. I'll do whatever I can push myself to manage. Without ever
giving up... I'll keep on believing in myself and in you guys.}

\emph{Isn't that what praying is, Nezumi?}

Getsuyaku saw Inukashi's smile, and drew his chin back. So it didn't go
as well as with Nezumi. Go figure. There was probably something awkward
about it. And that had made Getsuyaku feel apprehensive.

Inukashi cleared his throat, and pursed his lips.

"Isn't that nice. Congratulations. Don't worry, I'm not gonna ask you
something as idiotic as your life in exchange for pay. It's an easy job.
Very easy. But it's also something only you can do. That's why it's
worth one gold coin."

"It's easy, but worth one gold coin," Getsuyaku repeated suspiciously.

"I told you, it's something only you could do. I have no choice but to
cling to you, Getsuyaku-san. Really. Only you can do it. And I know
you'd be able to do it."

Getsuyaku's face relaxed very slightly.

\emph{Only you can do it.}

\emph{And you \emph{would} be able to do it.}

You had to tickle his pride. Caress him gently with words. It would no
doubt soothe his battered and stinging self-respect.

"I'm begging you. Work with me, Getsuyaku-san."

"It's not that easy... what are you saying I have to do?"

"I want you to send the cleaning robots haywire."

"Huh?"

"You monitor the cleaning robots as well as doing waste disposal, don't
you?"

"Ah―well, yeah. Monitoring goes as far as me pressing the control switch
on the robots that are on standby, though. The robots start moving on
their own, and commence cleaning. I'm only in charge of monthly
tune-ups."

"When's the next tune-up?"

"In a week."

"Couldn't you make it tomorrow?"

"Tomorrow? Tomorrow is the Holy Celebration."

"It is, isn't it? It's a holiday in No. 6."

"It―it's a holiday, which means most workers are off... including me."

"You don't get the day off," Inukashi replied. "You told me before
yourself. You only have three days off a month, and even the Holy
Celebration isn't part of that. You were mumbling complaints about it."

"Well―B-but..."

"It should be easy. You come up with some excuse like you're noticing
something weird in their movements, and push the maintenance a week
earlier. That's all there is to it."

"No, there's no way―"

"You \emph{could} do it. You must've had a lot of similar cases in the past."
Shion had told him once.

"Cleaning robots are actually required to perform more complicated
motions than you'd expect. If they were like Ippo and the rest―(here
Inukashi had unwittingly blurted out a question as to what Ippo was. He
was exasperated to hear it was the robot's name. Supposedly Shion's dead
colleague had named him. \emph{Said he named them Ippo, Niho, and Sampo.
One-step, Two-step, and Three-step. Hah, I can't believe how placid this
guy was.} He had found it funny that the airheaded boy even called the
robots' names lovingly, like he did to the mice)―and only had to clean
the park, they would only have to make relatively simple movements,
because there's no strict sorting of trash. But they're operating inside
a building, and not the average household either: you've got trash from
various sections all coming together. One simple type of movement isn't
gonna be enough. The type of trash and how soiled it is is going to vary
according to what section it comes from, so I'm pretty sure the
mechanisms are much more complicated too."~

"Which means it needs meticulous maintenance. And you can't rule out
them breaking down."

\emph{That was Nezumi's line, if I remember. And Shion had nodded.}

"Judging from my experience, I'm pretty sure they experience a lot of
petty trouble. Their distinguishing functions decline, or their
movements turn sluggish, or something like that."

"I see."

\emph{Then Nezumi put on that wan smile of his, and glanced at me. It wasn't a
gaze I liked. It was a meaningful glance, and somewhat suggestive.
Nothing good ever comes out of him making eyes like that. I broke eye
contact in a hurry. It was already too late, though.}

\emph{Back then, I didn't understand fully what his gaze meant. Now I know.}
'Inukashi, this is your chance to shine. It's a key role. Play it well.'

\emph{I know. You just watch, Nezumi. I'll pull it off so well, it'll blow
your hammy acting away.}

"I heard the cleaning robots break down a lot. Am I wrong?"

Getsuyaku knitted his brow. He answered grudgingly. "Well, it doesn't
happen \emph{that} often."

"So what about speeding up the maintenance day, hm? It's not unnatural
at all."

"Well, I mean... it's not something I can't do, but..."

Inukashi had to keep himself from bursting out laughing. \emph{This guy is way
too truthful.}

He found it hilarious that Getsuyaku couldn't help giving him straight
answers, even though he was supposed to be apprehensive towards
Inukashi. But this wasn't the time to be laughing, and he didn't have
the concentration to spare. Inukashi set his jaw. He had to pull this
man onto their side, even if he had to take advantage of the man's
straight-laced and honest nature.

"If you can't not do it, it means you can, right, Getsuyaku-san?"

"Scheduling the maintenance earlier isn't... well, it isn't impossible.
But what do you mean by making the robots go haywire?"

"Just that. I want you to do a little rigging so that it does the
opposite of cleaning."

"Opposite?"

"Make it spit out trash, all the trash that it's accumulated in itself.
And I want you to mix this in with it."

Inukashi took out a jar with a small capsule inside, and showed it to
him.

"What's this?"

"It's nothing dangerous, you can relax. It just releases a bit of an
odour. It's not even that strong. This capsule starts melting when it
touches the air. Very gradually, though."

"Why do I have to mix this in? Not to mention making the robot spit it
back out."

"It's a prank." Inukashi shrugged, and gave a show of chuckling. But he
didn't find it funny at all. His whole body was damp with sweat. He was
in no state to be laughing.

But he still did. He showed Getsuyaku a smile like one of a child
devising a little prank. Getsuyaku wasn't laughing. His face made it
clear that he wasn't believing a word of what Inukashi said.

\emph{Geez, talk about ingrained suspicions. He must be made up of a lot of
Coward.}

"If a robot starts spewing trash and odours everywhere, it's gonna cause
a commotion. No mistake about that, right?" Inukashi continued
nevertheless.

Getsuyaku nodded. His fingers were still clenched around the gold coin.

"No mistake about a commotion. Those guys inside the Facility, prisoners
aside, are always working in comfortable and immaculate rooms. They most
likely haven't even gotten dirty before. Yeah―I'm pretty sure they
haven't even touched trash in their life."

"Right? No one thinks about how tough and important your job is. So this
is why you're gonna pull a little prank. The cleaning robot goes
haywire, and starts strewing trash everywhere. Those guys inside will
make a big deal, and what'll they do first―?"

"Order me to stop the robot."

"Exactly. And you'll do that. Then―then, you'll probably be called
inside the building."

"To repair the robot? Mm, well, that would happen, I guess."

"And cleaning up the aftermath. You'll be ordered to clean the garbage
that was spilled. No one else can do the cleaning job. You'll be
summoned. And it'll open."

"What?"

"The doors. The doors which you could never open from your side will
open up to you. You'll go through them, carrying your outdated cleaning
equipment. Around that time, the capsule is gonna start to melt, and the
odour will start spreading. If it's not melting properly, step on it a
bit. That might be more effective, yeah," Inukashi murmured to himself.

"And oh, you don't needa worry. Like I said, it doesn't smell that bad.
The smell sensors might activate, but the danger level is still gonna be
zero. My nose is probably too used to it to even pick it up. But those
guys on their cushy perches are gonna take it \emph{hard}. The commotion will
get even worse. Then, you'll pretend to be in a rush to clean up the
trash, and―"

\emph{Now, this is the real deal.}

Inukashi lowered his voice, and whispered into Getsuyaku's ear.

One, two words.

Getsuyaku's whole body went rigid. His mouth fell half-open, and a set
of strong-looking white teeth peeked through.

"Th... There's absolutely no way I could do that."

"Why not? It's so easy. I think using a power shovel is harder than
this."

"And if anyone finds out? I'll get fired―no, probably worse. I'll be
arrested by the Security Bureau, and... oh, no, stop," he moaned. "Just
the thought of it is scaring me enough to give me goosebumps. No thanks.
That's a resounding No. Go home, Inukashi. I'll give this back to you."

Getsuyaku thrust the gold coin back at him. It was a real one; it
glimmered faintly. Inukashi twisted his lips into a smile. He felt like
this one was a little better than the last one.

"Give it back, huh. I see. Not tempted by material desires?"

"My life is more important than material desires."

Inukashi gently placed his own tan hand on Getsuyaku's upturned palm.

"Ooh―" Getsuyaku gulped his breath. The gold coin in his hand had turned
into two. "Hey, Inukashi, I'm not―"

"One more." He placed a third gold coin onto his palm. "Three gold
coins. How about it?"

"Why―why are you―offering so much..."

"The job I'm asking you is worth this much. If it goes well, I'll give
you three more as your compensation."

"Inukashi, what are you getting at? This isn't just any old prank, is
it? It can't be. And where did you come across this much money?"

"No need for questions. This is what I'm asking―do you take it or leave
it? Actually, you can't really turn it down anymore."

"W-Why not? \emph{I will} turn it down. See: I won't take it," Getsuyaku said
stubbornly.

"No can do. You sold me inside information. Did you already forget?" He
tried licking his bottom lip. It was dry and sandy. The palpitations in
his chest had settled down. Watching the blood recede from Getsuyaku's
face, Inukashi widened his smile.

\emph{I'm alright. I'm calm. I won't panic and end up messing up the finishing
touch. I'm alright.}

"You told me the other day, where the electric circuitry was inside the
Correctional Facility."

"That was―well... it was only a broad idea of what I knew."

"But you still told me. No, you sold it to me. Two silver coins that
time, I think it was. You sold me information about your workplace to me
for two silver coins. If that gets found out, it's gonna be worse than
getting fired, it's gonna be―"

"I-I needed money!" Getsuyaku protested. "My wife fell ill, and I had to
take her to the doctor's."

"Yeah. You're a good guy, a family man. But you think the authorities
are gonna take that reason? \emph{I sold information for two silver coins to a
West Block resident so I could feed my family.} I'm sorry. What're the
guys at the Security Bureau gonna do if you confess that, huh? Are they
gonna give you a pat on the back and say, 'that must have been tough on
you'? No way. That would never happen, you know that. Even you
understand your own position and how dangerous the Security Bureau can
be, don't you? Oooh, terrifying. I'm getting goosebumps just thinking
about it."

Inukashi rubbed his bare arms. Getsuyaku's face turned even more
colourless and flat, and looked like a sad caricature drawn on a piece
of paper.

"A-Are you blackmailing me?"

"I just told you the truth. For free."

Getsuyaku made a strangled noise in his throat. Inukashi patted him
lightly on the shoulder.

"It's alright, man. No danger is gonna swoop down on you. I'll ensure
it. Think about it: you've been a hard-working man up until now. You're
registered legitimately as a citizen. Who's gonna be suspicious of you?
No one. It's because no one's paying attention to you. No one is
watching you."

"But the surveillance cameras―"

"If you make suspicious movements, you'll be caught. But if you move
naturally and unnoticeably, then fooling the camera is a piece of cake.
Machines might be able to send you clear images, but they can't display
what's inside your mind. Either way, it doesn't change the fact that
you've already set one foot in."

Inukashi put the gold coins back in his hand and made him clasp it.

"You'll take the job for me, won't you, Getsuyaku-san?"

"Uh... only once. Just this once."

"Thank you," Inukashi said graciously. "Tomorrow, then. Right before
your shift ends."

"Right... and you'll really give me the rest of the gold?"

"This is where humans and dogs are different. We don't lie. Once we make
a promise, we always carry it out."

"But―huh?"

"What?"

"Didn't you hear a baby crying?"

"Baby? I didn't hear nothin'."

"I could swear I heard―"

"Maybe you thought you heard it. Isn't your baby coming soon? That's why
you think the wind howling is a baby crying. But, see, I'm right: once
the baby's born, you'll need even more money. You'll need a warm bed for
him, and nutritious milk."

Getsuyaku moved his lips as if to say something. Instead, he promptly
closed the door of the monitoring room without a word.

Once the light that spilled from the room was cut off, a heavy darkness
wrapped around Inukashi. The frozen night air whistled past his feet.

\emph{Phew.} He let out a great sigh. Even in this frigid weather, his whole
body was dripping with sweat. His shoulders felt heavy, probably because
his muscles had been tense.

\emph{Phew.} This time, he intentionally let out his breath. As he breathed
back in, cold air slid deep down into his chest, and swirled around.

\emph{Did it go well? Was I able to tie their lifeline down properly?}

\emph{I'm not confident I did.}

Getsuyaku, that fearful and goodhearted man, would probably worry. He
would waver. He would probably hum and haw until the last minute, unable
to make up his mind.

\emph{What'll I do? What should I do? Keep going? Call it off? Oh, what should
I do. What should I do.}

What last-minute decision would Getsuyaku make? Would he act as Inukashi
hoped? He wasn't confident of the answer.

\emph{Human minds are like the ends of a thin branch.}

\emph{They get shaken by the wind so easily.}

\emph{I guess I just have to believe.}

Not Getsuyaku. He had to believe his own fortune. Shion's face rose in
his mind. Nezumi's profile did, too.

\emph{Guess I just have to believe in them.}

He walked briskly through the darkness. A dark shadow shifted beside the
cart holding leftover food. He heard hiccoughing sobs.

"Stop making him cry," Inukashi said with a sharp click of his tongue.
He pulled his face into a scowl. "What good are you as babysitter? Take
care of him properly. At least just make sure he doesn't wail like that,
I'm begging you, old man."

"I'm the one that wants to cry here, geez," Rikiga rejoined with a click
of his own tongue while holding the baby. He was probably scowling, too.
Inukashi just couldn't see through the darkness that shrouded him.

"Look, Shionn. Your mama's back. Isn't that nice."

"Who're you calling mama?"

"Who cares? I'm certainly not the mama. Here." Inukashi was handed the
baby, wrapped in a soft blanket. The blanket was something Rikiga had
gotten. Inukashi could feel the baby's warmth and weight in his arms.
The baby felt a little heavier.

\emph{Could it be? No way. It's probably just me.}

The baby he had picked up out of the rubble suckled at a dog's nipple,
flailed his arms and legs, laughed often, and cried all the time. He had
large, roving eyes and plump cheeks.

"Mama," the baby stretched his arms out to Inukashi. It looked like he
was searching, longing, or calling for something.

"See, he's calling you Mama," Rikiga said. "He did miss his mummy."

"He probably couldn't stand your boozy breath, old man. Ooh, there
there. Poor thing. That must've sucked, Shionn."

"So?"

"Hm?"

"How did it turn out?"

"Dunno. I did everything I could. I did what Nezumi told me to."

Rikiga sniffed.

"Eve, huh. What an insolent little bastard. He's off getting himself
tossed into the Correctional Facility, and he still has the gall to give
orders to us. Who does he think he is?"

"Nezumi is Nezumi, man. He doesn't 'think' he's anything. Besides, they
didn't get tossed in there. They went through those gates of their own
will."

"The gates of Hell."

"Hey, old man."

"What?"

"Do you think they'll come back?"

"When they've gone through the gates of Hell? Impossible. It would take
a miracle for that to happen."

"I hear miracles happen pretty easily. Nezumi said so before."

"Eve is a fraud. You couldn't find any truth in his words that's bigger
than a fly's head. You know, Inukashi, I―I really do want Shion to come
back, though."

"How about Nezumi?"

"I don't care about Eve. I wouldn't mind not seeing him for the rest of
my life. Actually, I couldn't be happier if I didn't have to see him.
Brighter prospects for me, at least. Hmph."

Inukashi laughed silently. Rikiga was in a terrible mood. He found it
funny. He knew the reason why, and that made it funnier.

"Tsukiyo." Inukashi lowered his voice and called the little mouse's
name. Shion had named this one too. Hamlet, Cravat, Tsukiyo... it was a
strange thing. Once he knew their names, he found he could distinguish
between each of them, when they had only been "just the mice" to him
before.

It was strange, indeed.

\emph{Chit.}

A black mouse appeared from under the belly of a similarly black dog,
which was sprawled out on the ground.

"A message for your master: I've done what you told me to do. Tomorrow
evening, everything springs into action."

\emph{Chit.}

"I'll pray so you can reach your master safely, Tsukiyo."

\emph{Cheep-cheep-cheep!}

The mouse disappeared swiftly into the darkness.

"Does it know where Eve is?"

"I reckon."

"Does he understand what you say?"

"He can probably understand you too, old man. As long as you're sober,
he'll understand what you're trying to say."

"Why? He's just a mouse."

"He's not just a mouse. Ordinary mice don't understand human words.
Those mice are unusually smart. They can understand words, and the
intention we put behind them. It's no wonder Nezumi treats them so
preciously."

"Why aren't they ordinary mice?"

"How the hell am I supposed to know that?"

"Are they microrobots?"

"No. Completely natural living things. They just have intellect. Shion,
you know, he was even \emph{reading} to the mice. Some classic called
Whachamacallit. I bet you've never read any classics before, have ya,
old man?"

"Never read any classic called Whachamacallit before," Rikiga responded
sarcastically. "So why do these mice have intellect?"

"I said I dunno. They're Nezumi's, after all. I wouldn't find it strange
if they were somehow extraordinary."

"Of course it's strange. Where did Eve get those mice?"

"Old man."

"What?"

"Why are you so hung up about them? What, you wondering if you can make
a little extra cash by using those mice?"

"Of course not," Rikiga said crossly. "Like I would have anything to do
with Eve's mice. I wouldn't touch them even if they had gold coins in
their mouths."

Inukashi found it hard to believe that Rikiga would let a mouse with a
gold coin go uncaptured, but he only shrugged in response, and didn't
say anything.

\emph{Mice that understand human language....}

One of those mice had delivered Inukashi a letter during the day. It was
from Nezumi. The words were scrawled with a thin pen.

\memo{7_nezu}

The letter began with no~formal opening or seasonal greeting, and read
rather standoffishly.

\emph{Doesn't he even know how to write a proper letter? Or does he think I'm
not good enough for a greeting? If that's so then, well, what a rude
prick.}

Nevertheless, a letter from Nezumi was unexpected and unusual, and his
eyes were glued to the letter even while he complained. He read, and he
growled.

On the letter were detailed instructions for those left behind in the
West Block. Only after reading the letter did Inukashi finally realize
what meaning was behind the meaningful and suggestive look in Nezumi's
eyes.

\emph{I see. This is what you want me to do. What a touching love letter
you've given me.}

\emph{This guy is just rotten. Not that it's anything new.}

He took a deep breath. He had to decide: whether to crush the letter in
his hand and pretend he never saw it, or act on Nezumi's orders.

A short moment of hesitation came and went. Inukashi folded the letter
neatly, and exhaled a long breath.

Apart from instructions for Inukashi, there were also detailed orders
for Rikiga as well. That was the source of Rikiga's discontent.

"The brat thinks he can order me around. Damnit, I feel like that
despicable rat is remote-controlling me. Pisses me off."

"Then you'll ignore it?"

"I can't just do that. Shion's life is on the line."

"The mountain of gold bullion is also on the line."

"Exactly."

Love and greed. These two conditions were often all it took to get most
people moving. For the amount of continuous complaints that streamed
from Rikiga's mouth, he moved surprisingly swiftly and efficiently. He
had brought in a stock of micro-bombs. He had probably had them prepared
a while ago in advance.

He had said he had spent ungodly amounts of money. But if they were
going to get that gold bullion, it was a small sacrifice.

Both Inukashi and Rikiga had accomplished half of Nezumi's orders. Now
there was the other half. This was the critical moment.

"We know for sure that Tsukiyo and the rest are on our side. Isn't that
enough peace of mind for now?" Inukashi voiced his honest thoughts.
Whether it be a human, dog, or little mouse, as long as they weren't
enemies, it was something to be thankful for. He wished Rikiga would
worry about this "strangeness" and "mystery" business later, when they
weren't in such a tight situation.

\emph{It's been obvious since, like, a hundred years ago that Nezumi is
someone you just can't figure out, old man.}

"Abah, abah, abah." Shionn babbled animatedly.

"Congratulate us, Shionn." Inukashi lifted the tiny body up to the night
sky, where the stars were winking. "Celebrate for us. For our present,
and our future."

"Babhuh." Shionn suddenly lifted his arms, wrapped in a tattered cloth.
He reached straight up as if to indicate at something.

"What?" Inukashi looked up to see the golden city. The Holy City of No.
6, glittering, tore through the inky darkness.

Shionn's tiny fingers were stopped right on that golden light.

"It's No. 6. What about it? Did it catch your eye?"

Shionn wasn't smiling. He wasn't crying, either. With his purple-tinted
eyes opened wide, all he did was stare intently at No. 6.