% !TeX spellcheck = en_US

\chapter{The arms of reason}

\myepigraph{\el but he who, provoked and nettled to the quick by an offence,\\
should fortify himself with the arms of reason against the furious
appetite of revenge,\\ and after a great conflict, master his own passion,\\
would certainly do a great deal more.}{Montaigne, \emph{Essays} Book 2 Chapter XI}

\lettrine{T}{he shutters} closed.

Shion sprang up, and took in his surroundings. Teal walls and a teal
hallway stretched out before him. The floor was made of a smooth, glossy
material polished to a spotless sheen, and reminded him of the
cleanliness of a hospital.

However, unlike a hospital, there were no windows or doors.

He felt like he had been shut into a durable box. No, it wasn't \emph{like} a
box---this \emph{was} a box, a sealed box. There were three barriers between
where he stood now and the prisoners' wing up ahead. Once all of them
came down, the box would further seal itself into multiple compartments.

These were spaces designed to capture escaped prisoners, if not execute
them on the spot.

The barriers, far from being just walls, were also designed to release
high-voltage current. This beautiful colour, close to indigo dye, was
the colour of the execution grounds.

The alarm went off.

The barriers began to roll down.

"Nezumi, run. We have to make it through."

Nezumi kicked off the ground. They ducked past the first barrier. The
second one was halfway down; the third one was already two-thirds of the
way down.

"Why?"

Shion and Nezumi had reached the end of the hallway by the time the
third barrier had closed completely.

"Why, Shion?" Nezumi asked. "Why are the barriers so slow? Getting
through them is easy, at the speed they're going."

"It might be\el easy\el for you\el " Shion gasped. His heart was
straining in protest from running through the hallway in a single dash.
He couldn't breathe. It was far from easy for him---he was almost at his
limit. If the barriers had fallen a second earlier, Shion would have
been caught between the barrier and the floor, his back snapped in half.

"But this speed doesn't make sense. Why is it?"

"That accident\el it's thanks to\el the commotion about the smell\el "

"What do you mean?"

"I copied and sent\el the emergency signal that the third-floor computer
recorded\el to the fourth-floor monitoring system. Along with a
deactivation signal, too. Right afterwards, the sensors would register
us\el and then notify the system of an emergency again. Activation,
deactivation, and reactivation\el "

"I see. And that took up a bit of time. But I don't know how you could
have done it in such a short while. The third and fourth floors operate
on different systems, don't they?"

"\el Yeah, well, I managed." Shion had not expected it to go this well.
He had figured it was all or nothing and given it a try, but he himself
was surprised that such a simple deception tactic would work against a
leading, cutting-edge defence system.

\emph{It's almost like God's hand had a part in it.}

\emph{God's hand?}

\emph{Did someone send us help?}

\emph{That's absurd, that would never happen. But\el }

Shion.

\emph{I heard a voice call my name. Only for a moment. This voice\el }

\emph{Safu?}

\emph{No way, I'm hearing things.}

Nezumi narrowed his eyes. The sharp glint in them condensed.

"And the door we're making for?"

"The wall up ahead, on the far right."

Nezumi ran a hand against the wall.

"Oh, here." It was almost indiscernible from the teal wall, but there
was certainly a slight crack there. "There aren't any handles or
sensors. How do you open it?"

Yes, there were no handles or sensors. And ever since the
computer-operated maintenance system had been completed, this door had
gone out of use and lost all meaning.

"There might be an old-fashioned lock on it," Shion suggested.

"My, my. How careless of them."

No one would be able to get this far without a legitimate ID chip. Even
if they had, no one would take notice of this door. This was No.~6's
judgment, and also its folly.

"---which means we might be able to open it pretty easily. Ah\el it's just
like you said. There's a keyhole here. Looks like it'll break easily."

"Can you do it, Nezumi?"

"Probably. I can't let you steal all the spotlight. But before that, I
think we have to deal with those over there."

"Huh?" Shion tried to turn around, and was shoved in the shoulder
instead. He staggered.

\emph{Ping.}

A ray of light whizzed past Shion's eyes. It hit the wall, and left a
small burn.

"Well, well. Look what you've done to the wall, and it's polished up so
nicely, too. That would cost you a written apology, wouldn't it?" Nezumi
hunched his shoulders in mock exasperation.

Three gunmen stood before them. They were clad in military
gear---dirt-coloured combat uniforms and boots. Two barrels were pointed
at Nezumi, and one at Shion.

"Don't move. Put your hands up." The man in the lead stepped forward,
and took aim with his gun.

"Huh?" Nezumi said in mock surprise. "Oh, hey, will you wait a minute?
You gonna shoot me right here? Aren't you getting a little ahead of
yourself? I think I'd like to talk to my attorney first."

The man wordlessly wrapped his finger around the trigger.

"You sure about that? We're valuable samples."

The man stopped mid-movement. He had responded to the word "sample".

"Sample\el you say?"

"Yeah. You guys are collecting samples, aren't you? For the Almighty
Mayor's project?"

The men all shifted uneasily, and exchanged furtive glances. For a split
second, there was a moment of vulnerability.

Tsukiyo sprang forth from inside Nezumi's shirt, dashed along the length
of the gun, leapt up, and bit down on the man's nose.

"Whoa!" The man leaned back. Nezumi's knife slashed through his wrist.
Blood splattered everywhere, patterning the wall. Snatching the gun from
the falling man, Nezumi took aim a second ahead of the men behind him,
and pulled the trigger.

He shot one man through the shoulder, and the other through his hand;
both men cried out in pain. Nezumi spun around on one foot as if doing a
dance, and this time shot the laser gun at the wall. He swung a kick
into it next. Tsukiyo scurried up his shoulder.

"It's open."

A space revealed itself, wide enough for an adult to get through if he
crouched. It was pitch-black inside.

"Ugh\el it hurts\el "

"S-Somebody!"

"Help me\el help\el " The men were groaning. Shion could hear the sound
of rapid footsteps. More soldiers, each with a gun in hand, were rushing
onto the scene.

There was a curved handle on the inside of the door. Shion pulled it as
hard as he could. The door closed with a screech and a bang. They were
shut into complete darkness.

Just as he had predicted, there was a set of stairs in a steep slope,
almost like a ladder. Shion shed his lab coat and tied one end to the
door handle and the other end to the handrails of the stairs. It wasn't
much of a solution, but it would buy them some time.

Nezumi slung the gun over his shoulder and clambered lightly up the
steps. Shion followed after him. The stairs continued up on their steep
slope, straight into the darkness.

His breathing grew laboured. The sweat stung in his eyes. His feet
threatened to trip him up. Shion pressed on desperately. A moment of
lateness could cost him his life. It would endanger not only his own
life, but Nezumi's as well. He wanted to avoid putting Nezumi into
danger at all costs. He knew he was already a great burden to Nezumi,
but he at least wanted to avoid putting him in harm's way.

Nezumi muttered something.

"What? I didn't hear."

"Nothing\el Just noticing how you didn't make a fuss."

"Make a fuss?"

"About those soldiers. There was lots of blood flying back there.
Usually you'd rattle off some grand spiel about how we shouldn't harm
others."

"Oh\el " \emph{So that's what he meant.}

The screams resounded in his ears. They didn't belong to the soldiers.
They were voices of the people whose lives had been wrenched from them
unfairly in the basement of the Correctional Facility.

\emph{It hurts. I can't breathe. Help me.\\
	O God, O God. Why do you make me suffer?\\
	Please, just save my boy. He's only three.\\
	Kill me. Please, release me from my pain\el \\
	Help, help, help, help, somebody.}

What was a spray of blood on the teal floor compared to this brutality,
this ruthlessness? The soldiers would receive care and medical attention
from their comrades who were rushing onto the scene. But those people\el 

Those who had been sacrificed in the Hunt, those murdered people did not
even have a way to alleviate the suffering of their dying moments. Their
groans, their gasps, their cries, and their shrieks. It resounded in his
ears.

"We have no choice," he spoke to Nezumi's back in the darkness. "It
can't be helped. We have to defeat the enemy. If you hadn't taken them
down, I would have been killed."

Nezumi stopped. Shion could see a pair of grey eyes. His heart grew
restless. \emph{Even in this darkness, your eyes glow with elegance.}

"It can't be helped\el you really feel that way?"

"I do."

"\el I see." Nezumi resumed walking. He walked swiftly. Shion could
barely keep up.

"Shion."

"Hm?"

"Back there, we were still able to go easy on them. From now on, we
won't have the chance to be as nice. You were right: we have to defeat
the enemy, or else we'll be killed ourselves."

"Yeah."

"If that happens\el " Shion couldn't hear the rest. He snapped his eyes
open in the darkness.

"Nezumi, I can't hear you. Say it a little louder."

"No\el never mind." Nezumi breathed out softly in the dark.

\emph{I'm sighing.}

He closed his mouth.

\emph{Never sigh in earnest.}

They were the words of the old woman who had saved him from the flames
that devoured the forest, the village, and their homes. She had raised
him until the age of five.

\emph{Bite your lips to shreds before you let yourself sigh. Throw your head
back at the pain. Never look down. Look forward. And most of all---}

\emph{Never trust anyone. Never open your heart. Remember that. You must
engrave these words into your memory in order to survive.}

He had been taught over and over. It wasn't that he had forgotten. Each
word, each letter was deeply carved into his heart---like a mantra, like a
curse.

\emph{Sighing creates an opening, a vulnerability. If you want to stay alive,
keep your mouth shut. Never let anyone see your weak spot. Let your
heart warm to no one. Never trust anyone but yourself.}

\emph{You, at least\el you at least must survive\el you, at least\el }

He gripped the handrail.

\emph{Forgive me, gran. I've gone against what you've told me. I've sighed
many times for another. I believed him, and opened my heart to him. I
placed the shackles around my own feet. But I couldn't have done
otherwise. I couldn't cut him away.}

"Nezumi," Shion was calling. He was out of breath. He had probably used
up a considerable amount of energy. "What're you thinking about?"

"You wanna know what I'm thinking about now? Getting to the top of these
stairs safely. Maybe a little wondering about what's waiting to welcome
us at the top, I guess."

\emph{It was you, Shion.}

\emph{I was thinking about you.}

\emph{You said we had no choice. They're enemies, so we had no choice but to
make them bleed. If we didn't kill them, we'd be killed ourselves.
That's why we had to take them down.}

\emph{That's what fighting is. We kill, or get killed: those are the only
choices. And in a melee, there is no such thing as justice or morality.
I know that. It's been instilled into the marrow of my bones. But,
Shion, you---are you just going to accept that? Are you able to? Are you
letting yourself?}

'You put everything into dichotomies. You either love or you hate.
You're either friends or enemies. Outside the wall, or inside the wall.
And you always say you can only ever choose one of them.'

'Don't you think that there could be a third way?'

\emph{I had scoffed at what you'd said. I scorned it as a naive fantasy. But
you know what? I felt intimidated, too. I felt threatened by your
naivety, but also your strength to be able to speak of fantasies as if
they were plausible. When I heard those words, just for an instant---a
short instant, mind you---I could really see a way. A white path rose up
behind my eyelids.}

\emph{The third way.}

\emph{The way to seek cohabitation rather than retribution, perhaps?}

\emph{A way that chooses acceptance over revenge?}

\emph{Could such a thing exist, apart from in illusions? Could it exist in the
hearts of people?}

\emph{I've been thinking about it all this time. I didn't want to think about
it, but your words always sat adamantly in the middle of my thoughts,
reminding me constantly. 'Turn your thoughts to this third way,' they
would tell me, 'don't refuse, don't look away; keep thinking about this
path.'}

\emph{I haven't found the answer yet. That's why I'm still thinking. I'm still
fixated on your words, and pondering them.}

\emph{But Shion, now this is what you're saying?}

'We have no choice.'

\emph{If in the future, I end up killing someone---no, if you yourself were to
harm someone---how about then? Would you still say so?}

'We had no choice.'

\mybreak

They were at the top of the stairs. It was such a cramped space that
they had barely any room to stand.

"Shion, there's no exit."

There was no handle or button to be found. Only a blank wall.

\emph{We've messed up.}

His heart pounded. Cold sweat streamed down his back. If this was a dead
end, then there was no escape for them. They could not fend off the
pursuers coming from below.

"Up," Shion yelled. "Push the ceiling up!"

Nezumi's body sprang into motion on Shion's orders.

\emph{Bang.} The middle portion of the ceiling opened up like a trap door.
Nezumi kicked off the ground, and launched himself up.

Just then, he heard a clamour below.

The door had been forced open.

"They're up there! Aim for them!" The unique dry popping sound of
firearms.

"Shion!" He extended his hand, and he could feel Shion latching onto it
tightly. He pulled the other boy up.

"Agh!" Shion let out a small cry.

"Did they get you?"

"---'m alright. Just a graze."

Once they shut the trap door, all noise was cut off, and only an eerie
silence remained. Shion let out a long breath.

"Does it hurt?"

"No---no big deal."

"First time, huh?"

"Hm?"

"It's your first time getting fired at. And a sniper rifle, at that---a
pretty old firearm. Sleek looks, deadly accuracy. That's the kind of
formidable lady you're dealing with."

"I see. Well, attractive as she is, I wouldn't like to go on any future
dates with her." Shion laughed quietly as he bound his calf.

Perhaps he was straining himself. But it meant that he could still push
himself further, and that the wound wasn't so bad that he couldn't move.
Not that it mattered how bad his injury was, anyway: they had to keep
moving. They could not stay in one place.

That was why he would not question Shion further. He would not concern
himself with the boy. They only had to keep moving forward together.

"Shion, where's this?"

"A part of the old air vents. I suppose they used these when this place
was just built. But soon afterwards, they built new external reinforced
walls. They added circulatory filtration devices, and these vents went
out of use."

"Which means they stopped needing them right when the Correctional
Facility was turning into a stronghold. So the old vents must be---here."
Nezumi's extended hand pointed to a rectangular tunnel.

"What's down this way?" he asked.

"Probably a dead end. They've probably blocked it up partway."

"I thought so. I figured it wouldn't be as easy as worming our way right
to the internal core through the vents."

"Yeah. But we'll have to go as far as we can."

He was right. There was no way back. They had no choice but to go as far
as they could go.

"Shion, I'll boost you up. Go on ahead."

"'kay."

Shion dove into the hole more nimbly than Nezumi expected. He felt the
slimy texture of blood as he supported Shion's leg. He clenched his hand
into a fist.

"Hey, this thing opens." The upper body of a soldier peeked into view
along with his voice. As soon as the soldier hoisted himself up, Nezumi
kicked his chin so it snapped back, and swung his rifle butt down on the
man's temple. He dragged the unconscious body up into the vent, aimed
his gun through the opening, and began to fire. He heard bodies tumbling
down the stairs. He closed the trapdoor, and rolled the soldier's body
over it.

"He's got a nice beer gut. That should serve as a good weight."

Nezumi rifled through the man's pockets and almost whistled.

"Nezumi, what're you doing? Hurry up," Shion called.

"Don't rush me. We gotta get the most we can from them," he answered.

He entered the hole head-first. It was cramped. He had to lie flat on
his belly in order to even move. Tsukiyo hopped out from the folds of
his clothes and scurried down the tunnel.

"It's like a mouse hole in here," Shion reflected idly.

\emph{Still got his wits}, he thought fleetingly. The boy was calmer than he
expected. It wasn't an ignorant kind of calm; Shion understood his
situation well enough. He felt the danger and tension of it, and yet
also had room to be calm on top of it all.

\emph{But why?}

"We couldn't have gotten through here if we were any fatter," Shion said
thoughtfully.

"Well, I guess."

"Inukashi could get through just fine. Rikiga-san might have a bit of
trouble."

"Rikiga? You mean the alcoholic geezer? He wouldn't have been able to
get this far in the first place. He would've tripped and fallen over
when we had to dash down the hall."

"So by now\el "

"He would've been charred black. I feel ill just imagining what Roasted
Old Man would look like."

\emph{Cheep-cheep-cheep.}

Tsukiyo answered in place of Shion. Shion stopped moving.

"Dead end?"

"Yeah."

\emph{Dead end. I see. So this is it.}

"It's a dead end. But\el " Shion's palm slid along the wall. There was a
soft \emph{clunk} as a part of it fell away. Light seeped through.

"The grate. They must've blocked it from our side."

"What do you see?"

Shion tilted his body sideways to make an opening. Nezumi looked out
through the plastic bars.

It was a tidy and spacious room that looked like a laboratory. Straight
across from them was a large glass window, where several male and female
researchers were huddled together, peering through it and conversing
animatedly. A man said something with a grandiose gesture, and a
long-haired woman gave a toothy grin. They both had steaming mugs in
hand. Apart from them were several other staff busy looking into their
computer screens. There was also a stooped-looking man bustling about on
foot.

"It looks like a comfortable room," Nezumi commented. "Maybe they'd let
me use their shower if I asked. Let's pay them a visit."

"What? We can't get out through such a tiny opening."

"If it's too small, we just have to make it wider."

"Huh?"

"Keep back, Shion. Just retreat as you are."

"Nezumi, what're you gonna do?"

"Just watch."

"Is that\el a miniature bomb?" Shion swallowed.

"Yup. A coin-shaped micro-bomb, more like. It even comes with a timer,
and I can control how large the explosion's gonna be. It was a good
buy."

"Where did you buy it? I didn't even realize."

"Are you being dense on purpose?" Nezumi said irritably. "Did we have
\emph{time} to do shopping since we got here? I nicked it from Beer Gut
earlier. But anyway, who cares about that. Shion, get back. A little
more. And take Tsukiyo."

"About here?"

"Perfect. Hold your head with both hands. Once it explodes, we're gonna
jump right out. Be prepared."

Bomb set.

Nezumi shrugged his superfibre cape off, and covered his head with it.
He kept retreating until his foot touched Shion's shoulder.

"Nezumi."

"What?"

"Now it's like you're shielding me. I might end up safe, but you---"

"Idiot. Who the fuck cares about our positions at this point? Stop
wasting your breath."

\emph{How stupid can he get?}

What an idiot. But it was just like Shion. No matter the situation, he
never forgot about others. It was just like him, indeed.

Relief welled up from the bottom of his chest.

\emph{Voom.}

An explosion. And then, wind. A blast of air rushed through the cramped
tunnel. Tsukiyo let out a shrill squeal of terror.

"Shion! You safe?"

"Of course. Tsukiyo and I are both okay."

"Good."

There was no dust, perhaps because the wall was made of a special
material. The bomb was considerably powerful, and despite the fact that
he had set it to make the smallest explosion possible, it had blown
apart a large part of the wall.

They jumped down. Screams rang out all around. Staff began to flee the
room.

"Who are you?" A heavyset man drew a gun from his lab coat. Nezumi
rushed at him and aimed a swift swipe at the base of his neck. The man
fell forward onto his belly.

The security bells were ringing.

\emph{Keep running like this?}

They couldn't stay here for long. In a few dozen seconds, soldiers would
be streaming into the room. They had no choice but to run.

But to where?

"Shion, what next? Give me orders. Hurry."

There was no answer.

\emph{Shion, what's wrong? Don't tell me\el }

A cold sweat trickled down his spine.

He turned around to see Shion at the glass window, looking
down through it as the staff members had been doing earlier. A dim light
filtered through the highly-polished glass pane.

"What the hell are you doing? Move!"

Shion slowly turned his face towards Nezumi. He was completely ashen.
His features were rigid, almost wooden. Nezumi had never seen Shion with
such a face before.

\emph{What's wrong?}

As soon as the thought passed, he realized that the hem of Shion's pants
was soaked red. The gunshot wound had been deep. \emph{He's fainting from
blood loss.} That was his first thought.

"Shion, you alright?"

A pair of lips trembled lightly in the deathly pale face.

"Nezumi\el this\el " Shion trailed off, and swallowed with some
difficulty. "What is this\el ?"

"Huh?"

There was no time to stop. He knew well enough, but the stricken
expression on Shion's face drew him to stand by his side. His foot
trampled something. It was a wooden photo frame. In the photo was a
woman with a baby in her arms and a boy of about ten. It had probably
been knocked off a staff member's desk. It was an outdated digital
display. Both the woman and the boy were smiling somewhat sheepishly
from the photo.

He lifted his gaze, and looked through the glass in front of him.

The space beyond was a storey lower, as if it were embedded in the
ground. The ceiling was higher, accordingly. It was a room with white
walls.

"Gh---"

He had recoiled without even thinking.

\emph{What---is this?}