% !TeX spellcheck = en_US

\chapter{In falsity's company}

\myepigraph{In days of old, the Buddha\\
	was but a mortal;\\
	in the end, we ourselves\\
	will be buddhas too.\\
	How grievous that distinctions\\
	must separate those\\
	who are alike in sharing\\
	the Buddha-nature!}{Tales of Heike: Giou}

\lettrine{S}{hion slowly} raised himself off the floor.

Only a few dying embers remained in the heater, and the room was
freezing cold. Cravat, who had been curled up against Shion's body,
raised his head and chirruped softly.

"Shh---" Shion drew his blanket around the little mouse. "Here, you sleep
in this. Just \emph{please} don't make any noise, okay?"

Shion had gotten so used to this room that he could find his way even in
the dark. He padded stealthily to the door. He unlatched it, and before
opening it, he turned back again. He listened carefully. There was not a
noise.

It looked like the pain from Nezumi's wound hadn't kept him from
sleeping. \emph{I guess a wound that small wouldn't be enough to keep him
awake.} There were so many things he still needed to tell Nezumi. The joy
of meeting him, the gratitude for everything he had done for him, and
the profound respect he had for him --- Shion had not been able to get any
of these adequately across.

\emph{I'm glad I met you.}

\emph{That was all I was able to say.}

Shion inhaled the air of the room deeply, just once, before quietly
opening the door.

\mybreak

The lamp flashed, signalling a call from a direct extension to City
Hall. The man lifted his face from the research documents he had been
perusing, and lightly clucked his tongue in irritation. The document,
which had been printed decades ago on paper, was very intriguing, and he
wished to read a little further. But the lamp was flashing red,
signalling an emergency situation. The man clucked his tongue again, and
put the documents away in a folder.

When he pressed the switch, the familiar face of a man appeared
on-screen. He was a man who used to be called Fennec.

Fennec --- the desert fox. Who was it that had first started calling him
that?

"What's the matter, Fennec?"

"We have an emergency. Two samples have been brought into the Central
Hospital."

"Something the matter with that?"

"Both of them aren't registered as representative samples in the data."

"What?"

"They're different from the samples you've requested from us. Things are
happening on their own, outside of our control."

"Perhaps it's too early to conclude that they're samples. Couldn't
something else be the cause?"

Fennec shook his head. The screen promptly changed to another image. An
audio clip read out the two bodies' personal information.

Name, age, address, occupation, history of illness, physical
measurements, citizenship number\el 

A man and a woman. Two bodies. Both their faces were contorted in
suffering, and were aged and shrivelled. It if weren't for their facial
expressions, their cause of death would easily have passed as old age.
But the documented age of one of them was in the twenties, the other in
his late thirties.

"You're right, \emph{they} must have done it," the man muttered. The screen
flickered again, and Fennec's scowl was displayed largely. The man
exhaled quietly.

"\el What could this all mean?"

"I think \emph{I} would like to know that!" Fennec raised his voice, and his
ears twitched indignantly. Ah, yes. This was a habit of his. Since he
was young, he had always had the habit of twitching his ears when his
emotions were agitated. That was why he was called Fennec. A fennec fox
was a small fox with the longest ears of its kind, reaching up to
fifteen centimetres.

"But how could something unexpected like this happen?" Fennec continued.
"I don't believe it. What's going on?"

"Something must have gone wrong somewhere," the man answered. "But it's
insignificant. It's nothing you should be worried about."

Fennec's throat contracted as he swallowed at the man's words.

"Are you sure?"

"Of course."

"You have the highest responsibility in this project, you know."

"Not officially," the man added. "Well, but then again, nothing about
this project has been publicized officially."

"But if this succeeds, then No. 6's City Project will finally be perfect
and complete. Right?"

"Yes."

"Then even minor slip-ups can't be permitted."

"I know. I'll launch an investigation immediately looking into the
cause. I want you to send the bodies over to the Special Autopsies Room,
Section V."

"I've already got it underway."

"Then I'll get to work straightaway."

"Please do. I'll be waiting for the report."

"Roger."

"Oh, yes," Fennec added. "Once this mess has quieted down somewhat, I'm
planning another clean-up."

"Clean-up? That's something I haven't heard in a long time. Say, it's
almost the Holy Celebration, isn't it?"

"Yes, the same reverent day is coming again. If you need any for your
experiments, I can arrange for as many as you need. What say you?"

"I am most humbled by the kind considerations of His Excellency."

"None of that embellished formality, if you will."

"But you'll eventually become the absolute ruler of this land," the man
said. "The one and only King. I'd have to start calling you Your
Highness."

"And what would you have me call you?"

"I'll stay as I am. If I'm still provided with the same top-notch
research facilities and environment as I am now, then I have nothing
more to ask."

"Sparse in your wants as always, I see. Then I trust you'll have the
work done."

The screen silently went blank. The man let his gaze flit over the
documents he had only partially read. Unfortunately, it looked like he
would not be able to read through the rest of it today.

They were documents concerning a species of ants called \emph{Eciton
burchelli}, which inhabited Central and South Americas. These ants, which
formed colonies numbering up to 500,000, did not live in one static
place, but instead repeated cycles of temporary encampment and migration
until their life was spent. There was only one queen ant that reigned
over the colony of 500,000. But the queen's sole purpose in the colony
was to lay eggs, and she was not necessarily in control of its members.
Warrior ants and worker ants, large and small, all moved accordingly to
their instinct, and as a result, the colony functioned seamlessly as if
they were governed by a great common intellect.

Ants, and bees too, had created the ideal social system.

There was no way that humans could not do what insects already did. Each
would obediently fill his role. Without thinking, without being
interrupted by suspicions, they would take to their task. Brains were
unnecessary. Souls were of no use.

A colony of 500,000, and a single one to reign over all.

\emph{You say I'm sparse in my wants, do you? You're right, Fennec, I desire
nothing. I have no need for desire. I never have to suffer from being
dominated by my desires, like you do.}

The man smiled discreetly, and pushed the button for the elevator
leading directly to the Special Autopsies Room.

\mybreak

A frost had fallen. The frozen grass underneath his shoes made crunching
sounds as he trod over them. When the sun rose, the frost would sparkle
white, and the barren expanse would be enveloped in light for a fleeting
instant. But it was too early --- the sun had yet to rise for a while
longer. Shion stopped in his tracks, and lifted his face to the northern
sky. He wanted to reach the Correctional Facility before dawn. He had no
idea what he would do once he arrived. But he had to go. It was all he
could think about. Why had Safu been impounded in the Correctional
Facility, when she was supposed to be abroad? Was it in connection with
him? If it was, then would Karan's safety also be compromised?
Uncertainty and fretful misgivings coursed through his body, blocked his
airway, and pressed against his heart. He didn't want to lose anyone,
neither his mother, Safu, nor Nezumi. He would do anything to protect
them. But he was frustrated at himself for not being able to come up
with how he would do so.

Even now, as he was walking, Safu was probably alone and frightened. He
had to do something. He had to save her and get her out. But what was he
to do? How could he---

\emph{Cheep-cheep.}

A soft cry. His feet stopped. His eyes, which had gotten used to the
darkness, trained on a small rodent poking its face out from the grass.

"Cravat?"

He scooped up the tiny mouse in his hands.

"Did you follow me out here? Go home, you shouldn't be---" He realized as
soon as he had said it out loud, that this mouse was not Cravat. It
wasn't Hamlet, either. It wasn't even alive. This mouse carried no sign
of the warmth that living animals did.

"This is--- a robot---?"

"He's the navigator." There was a voice behind him. He didn't have to
turn around to know who the voice belonged to. Shion took a few measured
breaths, and slowly turned his body around.

Nezumi was also approaching him slowly. He plucked the miniscule robot
from Shion's hands, and tossed it into a pouch.

"It's a simple navigator robot with three-dimensional mapping functions.
It was warning you because you were going in the wrong direction."

"The wrong direction---"

"Weren't you going to Inukashi's place? You were gonna give those
long-haired dogs a trim because their skin was getting inflamed, weren't
you? Leaving awfully early, huh? How diligent of you. But this isn't the
way."

Shion inhaled the frigid air of dawn yet to come.

"This has nothing to do with you," he said bitingly. "It's none of your
business what I do, or where I go. I'm sick and tired of you trying to
act like my guardian. I'm not a helpless baby. Just leave me alone. You
know what," he said, "it's enough. If you still think of four years ago
as a debt, then let me tell you now, it's paid back. You've given more
than enough already. From now on, I'm going to be free. I'm going to do
as I please, without being strapped down by you. That's my decision, so
don't get in my way."

He ran out of breath, and lapsed into silence. It was too dark to see
the expression on Nezumi's face. His shadowy figure shifted slightly,
and he could hear a soft applause.

"That's quite some recitation for an amateur. Maybe you do have a talent
for acting after all. Certainly better than yesterday's kiss, at least."

"Nezumi, what---"

He thought he saw Nezumi's right hand swing upwards, and then a hard
blow struck his cheek. Shion staggered, and fell backwards. The taste of
blood spread inside his mouth.

"---what was---!"

"Get yourself up if you have the time to be asking questions. The next
one's coming."

The tip of Nezumi's boot swung straight toward him. Shion instinctively
rolled to the side.

"Don't just stop there. Keep moving, keep the flow."

A kick landed firmly in Shion's ribs. His breath caught in his throat.
He blindly grasped at a handful of pebbles that littered the grassy
patch.

"Don't close your eyes. Don't look away from your opponent's attacks.
Move!"

Shion twisted around to whip the pebbles at Nezumi, and at the same
time, kicked off the ground and tried to ram into him with his shoulder.
His feet were swept from under him, and he was slammed to the ground.
This time, he could not get up again. He could see the stars. The stars
that scattered across the sky yet untouched by dawn twinkled almost
frightfully bright.

He was grabbed by the arm, and pulled up off the ground.

"Shion, this is punishment."

"Punishment for what?"

"You lied to me."

"Well---"

"You'll admit that, won't you?"

"Yeah\el I guess."

"Your second crime. You belittled me."

"I never did that."

"Lying to someone means you're belittling him. Did you think I would
fall for your lame excuse? If that's not an insult to me, I don't know
what the hell is."

"It was my best attempt," Shion protested feebly.

"Well, you'd make a horrible politician or writer, seeing how you can't
even conceive a realistic lie."

"Was it that bad?"

"Atrocious. But this is what pisses me off the most, Shion---"

"Yeah?"

"That you must've figured I was some brat who couldn't tell one kind of
kiss from the other. What good-night kiss, huh? Bullshit."

Nezumi knelt in front of Shion, and gripped his collar tightly.

"You hear me? Never give me a farewell kiss again. Ever."

"I'm sorry."

"And never lie to me again."

"I won't."

"Swear it."

"I swear."

The hand released him. Nezumi settled into a sitting position, and
looked up at the heavens.

"I've heard there are strange things happening inside No. 6."

"Strange?"

"I don't know the details, but Inukashi is gathering information for me.
If we do it well, maybe we can use old man Rikiga and get some
information through his customers, too. And it looks like stuff is going
on in the Correctional Facility as well. There's commotion happening
both inside and outside of No. 6 at the same time. A little weird, don't
you think?"

"Correctional Facility? Nezumi, are you saying---"

"Your important friend, or whatever --- you called her your best friend,
right? --- I've known about her for a while."

He handed Karan's memo to Shion. Shion's fingers began to tremble after
he had read the note.

"Your Mama is safe for now. I'm not so sure about your bestie. But don't
panic. Right now, we have to gather all the information we can and set
down a plan. Inukashi says he'll help. This is all preparation so that
we can infiltrate the Correctional Facility as soon as possible.
Understand? We're not going in there to get killed. We're going in there
to save her. Be calm."

Shion nodded.

"So I've finally dragged you into the mess, too."

"It's not your fault. Inukashi says he smells something, and frankly, I
have my own suspicions too. Why would they need to imprison a precious
member of their elite? There's a chance that it might have to do with
the wasp incidents."

"The parasite wasps, huh\el but they're not active this time of year."

"That's why something must've happened, something unexpected. And if it
has, then it might be worth risking the danger. Whatever the case,
whenever Inukashi gets into contact with me is when we make our next
move. Until then, we have to gather our own information and start making
preparations."

Nezumi stood up, and spoke in a beautiful voice that rang out
crystalline.

"Cheer up. Things will work out. We'll make them work out."

"Thanks. You've saved me again."

"Things are just getting started."

Shion stood up as well, and called the name of the boy who stood beside
him.

"Nezumi."

"Hm?"

"Mind if I---"

"Huh? What?"

As Nezumi turned to peer inquisitively at him, Shion slapped him across
the face as hard as he could. Nezumi, of course, didn't so much as
stagger --- but he was certainly startled. After drawing a breath, he
yelled,

"---the hell was that for?"

"It's punishment."

"Punishment?"

"You hid things from me. You didn't even mention a word to me about this
memo."

"What would telling you do, anyway? I couldn't have you wandering off by
yourself like you did tonight. I did you a favour and looked out for
you. Or what, are you saying I don't have the right to be worried about
--- wait, I've heard this line somewhere before."

"Worrying about me and hiding things from me are two completely
different issues. It's not like I want to be sheltered by you. I don't
want to coast along living the easy life, always being protected by you.
I want---"

Shion softly clenched his fingers around his palm, on which he could
still feel the sensation of Nezumi's cheek.

"I want to be equals with you."

Nezumi hunched his shoulders, and lifted his right hand in a pledge.

"I admit my mistake. I won't do it again."

"Do you swear it?"

"I swear herewith upon my battered cheek."

In the distance, a cock was crowing. Even in this darkness, it could
sense the coming of dawn, and heralded it loudly and shrilly. In
moments, the eastern skies would lighten, and the light of the sun would
wipe the darkness away. The first day of their battle was about to
begin.

\mybreak

Safu was trying to wake up. She could feel her consciousness gradually
beginning to return. But her physical sensations were still murky.

\emph{Where am I?\\
	What am I doing here?\\
	Am I dreaming?\\
	I have to remember.\\
	Remember what?\\
	My very precious person.\\
	Precious person.}

"Safu."

She could hear a voice very close by, a man's voice.

\emph{No.\\
	It's not this voice.\\
	The voice I'm waiting for\\
	isn't this voice.}

"How are you feeling? I daresay you must be feeling a little different
from what you're used to? But you'll get used to it in no time. I hope
you like this special suite. It's the best you could ask for, and it's
especially for you, Safu."

\emph{I don't like this voice.\\
	Don't call my name.\\
	Don't call my name\\
	with that voice.}

"Safu, you are quite beautiful. Even more than I imagined. Beautiful,
indeed. I'm very satisfied."

\emph{I don't like this voice, and\\
	I don't like this smell.\\
	It smells like --- blood.\\
	The smell of blood.}

"I'm rather busy today. I'll come again, Safu. You should relax and rest
a little as well."

The footsteps faded away, and so did the stench of blood. She was
relieved.

\emph{But why\\
	Why is everything so\\
	hazy?\\
	But I}

From the margins of her consciousness, which was not completely
recovered yet, a flash of a figure emerged vividly.

Those eyes, those nails, that mouth, the faraway gaze, the energetic
smile, or that clouded expression, the long fingers --- and oh, she could
hear his voice.

"I always thought of you as a friend."

He was always such a child. He had never even realized her feelings for
him. But there he was, desperately searching and yearning for someone
else. She had loved that childish, but intent soul of his. She had loved
him like she could love no other. Even now---

She was fading out of consciousness. The darkness gently draped over
her.

\emph{I'll never see you again\el \\
	Shion.}

\mybreak

Shion spent the majority of the day taking care of the dogs. There had
been no sign of Inukashi in the morning, so Shion had had to prepare
food for and groom ten some-odd dogs all by himself. He had barely any
time to rest, but he didn't feel the labour to be onerous. On the
contrary, he was actually grateful for it. Immersed in his work, he
could forget his agitation, even for a short while.

\emph{Don't rush, and wait patiently. Act calmly.}

Nezumi's words were certainly persuasive, and he had no choice but to
nod his head, but still he couldn't help his agitation. He could not
remain calm.

\emph{Even while I'm going about this now, Safu is\el }

Every time the thought crossed his mind, his emotions would be thrown
into disarray, he would panic, and he would bite his lip until it bled.

A dog whined forlornly. It was one from a litter of puppies that had
been born at the start of fall. Shion realized he had been staring off
into space in the middle of making their meal.

"Oh, sorry."

He hastily scooped the stewed leftovers into their food bowls. The
puppies fiercely wagged their identical tails as they dipped their faces
into the food. In the kind of circumstances where even humans starved to
death, Inukashi managed to provide for his dogs with enough so that they
did not starve.

The leftover food was shipped into the ruins in the middle of the night,
and was sorted into food for humans, which would be shipped to the
market, and the rest, which was used for dog feed. Shion finally knew
where it came from now. Inukashi was probably tracing this route.
Nezumi, too, had disappeared in an early part of the morning.

What could he do?

The more he thought about it, the more he came face-to-face with his own
powerlessness. It agitated him. He could not stay calm. And he would
bite his lip again, and try to endure.

There was a warm sensation on the back of his hand. He looked down to
see a puppy intently licking his hand. Cravat poked his head out from
the breast-pocket of his sweater, and ducked back inside again.

He wanted to show Safu this puppy, and this little mouse. He wanted to
let her touch them, and let her feel the warmth of their little tongues
and bodies.

Safu was dear to him. She was precious to him. But it was different from
the amorous sense --- it was more serene, more deeply connected. He loved
her like family, like a close friend. Whatever kind of love it was made
no change to the fact that he cared about her.

He closed his eyes. He called her name.

\emph{Safu.}

\mybreak

"You want me to co-operate with you?" Rikiga made a clearly distasteful
expression.

"Yeah," Nezumi answered. "I want you to glean information from your
customers." Nezumi seated himself snugly into the chair, and put his
feet up on the table.

"Information? You mean about the Holy City?"

"Yeah."

"What's in it for me?"

"Enormous riches."

Rikiga stood up, and strode over to Nezumi. They were in a room of the
building Rikiga used as his workplace. It was a room littered with
magazines and empty bottles, and it reeked of alcohol. Looking down at
Nezumi, Rikiga twisted his mouth in a scowl.

"Some long legs you've got, huh. Showing off?"

"What an honour to be complimented by you. These are the money-makers, I
gotta keep them in shape."

Rikiga's hand rapped sharply on the pair of legs flung out onto the
table.

"Get your feet off my table. It's obvious what kind of upbringing \emph{you've}
had," he said scornfully. "Don't even know your basic manners, do you?"

"I use my manners with people who deserve them."

"Not to mention your filthy language," Rikiga continued. "And this
favour you're asking for, is this some kind of act? Are you practicing
for some new part you've got?"

"It's a real issue."

"A real issue, huh. Enormous riches, you say? Ridiculous."

Nezumi glanced at Rikiga's face, and flashed a faint smile.

"What's wrong?" he said. "This is about making a fortune --- you love this
kind of stuff. Not feeling up for it?"

"What makes you think I'm gonna believe what some third-rate, fraud of
an actor tells me?"

"Then who would you listen to? Shion?"

Rikiga's gaze wavered.

"Shion? Does Shion have something to do with this?"

"He has a lot to do with it."

"Did you get him involved, Eve?"

"No. Shion sowed the seeds, they're just growing in my yard."

"What do you mean?"

"If you agree to help me, I'll tell you."

"Spit it out."

"First, I want you to show me your customers' stats. When's the next
time a high official from No. 6 is gonna come to have a good time? I
want to know his name, and position."

Rikiga exhaled shortly, and folded his arms.

"Eve, how old are you?"

"Younger than you, old man."

"You must be young enough to be my son. I've been meaning to say this
for a while, but a brat like you has no right to look down on adults
like this. You're bound to serve the consequences."

With his eye still trained on Nezumi, Rikiga called out, "Conk," in a
loud voice. The door to the next room opened, and a large man walked in.

"He's my new bodyguard," Rikiga said. "Just got him hired. He used to be
a wrestler, and people used to bet on the matches. He's nearly killed
several people with his bare hands. On the ring, and off the ring too."

The man silently gazed down at Nezumi. He was so large, he made the
dirty room seem a size smaller just by walking in.

"Conk, I want you to give this little prince here a proper welcome. You
don't have to kill him. Just enough so that he'd never be able to make
another smart comeback again."

"Huh?" Conk stuttered. "Uh---"

"Don't 'uh' me, I'm telling you to teach this kid what a punch from a
real adult is like," Rikiga said irritably.

Conk licked his lips, and took a step forward. And another step. Nezumi
stood up. Rikiga smiled contemptuously.

"This is the punishment you deserve, Eve. The full extent of it."

Conk's feet stopped.

"Eve --- is it really you, Eve?"

Nezumi smiled, and proffered his hand in a delicate gesture. His sensual
smile made even Rikiga blink.

"So your name is Conk? Pleased to meet you, Conk. Thank you for always
coming to see me on stage. I would never have dreamt that I'd be able to
meet you here. I'm so happy."

"Oh --- Eve, me too."

Conk blushed crimson, and gently clasped the hand that was offered to
him.

"I've always been a fan of yours ---\\I've seen almost all of your
performances---"

"I know. You stood out, so I always knew whenever you came to my shows.
You'd even send me gifts sometimes. I've always wanted to thank you
directly."

"Really? You --- you could really tell when --- when I---"

"Of course. And last time, you even cried. I was watching you from
on-stage, too, you know."

"Watching? You were watching me?"

"Watching you."

"Eve --- I don't know how to say --- I ---"

"You're overwhelmed?"

"Yeah, overwhelmed. With happiness. I've never been so happy. I feel
like I'm floating on air."

"Thank you, Conk," Nezumi said pleasantly. "And I hate to disturb you,
but I'd like to have a nice, long talk with Rikiga-san. Would you be so
kind and pour me a cup of coffee?"

"Of course. Anything to eat?"

"That would be nice. Do you have meat pie, by any chance?"

"Yeah. I'll bring it rightaway."

Conk disappeared into the next room with amazing swiftness for his
stature. Rikiga shook his head.

"Coffee and pie, huh? That stuff is all mine, you know," Rikiga
grumbled.

"Don't complain, or he'd probably punch you. You said so yourself.
Ex-wrestler. Nearly killed several people. Right?"

"I can see why his wife kicked him out of the house," Rikiga said
bitterly. "He's completely useless when you need him the most."

"He's a good guy. Probably makes excellent coffee."

Rikiga clucked his tongue three times.

"That's quite something, Eve. Not only can you handle a knife, can you
also use sex appeal to your advantage too?"

"Both make good weapons."

"Then use that weapon you've got."

Nezumi lowered himself into a chair and crossed his legs.

"Eve, you're no rat," Rikiga continued. "You're a cunning white demon
fox, great at manipulating people. Now, I don't know how many tails\footnote{The number of tails a demon has signifies how powerful it is.}
you've got, but I've got a man who likes that kind of thing. He's an
elite, works at the Central Administration Bureau. He's my best
customer."

"Does that mean you're co-operating with me?" Nezumi's face was sombre.
Rikiga's face was also grave.

"I've also heard that there's been commotion recently inside No. 6."

"News reaches you quick, huh. I'm impressed."

"Don't try to flatter me with things you don't mean. Staying on top of
the news is what keeps my business running. But really," he said
bemusedly. "This is the first time I've heard about anything out-of-line
coming from that place. And that's how many decades since the Holy City
came to be? It's probably about time things started fraying at the
seams. And if that's the case, then I want to know more. I'm still
concerned about these things, Eve. And if Shion's involved --- then I
don't want to turn a blind eye."

"Is he precious to you?"

"He reminds me of Karan. And unlike you, he's truthful and kind. He's a
good kid. Karan raised him well. She probably showered him with love."

"What's wrong, old man?"

"What?"

"Why so solemn? You sick or something?"

"Leave me alone," Rikiga snapped. "When I'm with Shion, I just feel at
peace. I'm not sure why --- but anyway, I'll show you my customers' data
files. Once that's done, let's hear your story. I'm not sure if it'll
amount to 'enormous riches', but it might be of some interest to me."

"That's what you're really after, isn't it?"

"Say what you will."

The aroma of coffee wafted over to him.

Nezumi thought about Shion.

Showered with love --- he probably very well had been. His recklessness,
his liberality, his straightforwardness, his wide acceptance, were
probably all tokens of the ample amount of love he had been given. Shion
had probably never experienced what it was like to grovel for love. That
was fortunate of him. But love could sometimes be reversed into its
opposite. Love could attract hatred, and bear the banner for
destruction.

Hopefully, the love that had raised Shion, the love that resided within
Shion, would not become the chains that bound him, nor the hand that led
him to death---

Nezumi deeply inhaled the fragrant smell, barely managing to prevent a
sigh from escaping his lips.

Inukashi trudged along the path, cocking his head ever so often in
perplexity.

He didn't know how to sort through the information he had gathered. It
was like sorting through ore, separating the gems from the rocks. From
the reams of information, he had to select those that mattered, build
the parts into a structure, and draw a conclusion. He wasn't very good
at these processes.

\emph{Oh well. They'll figure the rest out. My job is just to dump all the ore
out in front of them. But I can't help thinking---}

He stopped his feet on a whim, and craned his neck. In the distance, he
could see the fortress walls of No. 6. The special alloy reflected the
light of winter. Inukashi had never thought about that land deeply. It
was just an entirely different world, glittering in the distance. That
was it. His only concern had been to survive the day's deprivation, and
managing not to starve. He had never linked his ordeal with the shining
Holy City. But Nezumi was different. He was constantly occupied with No.
6 itself.

Why did he insist on concerning himself? What bound him to it?

Love and hatred were no different in that they were both entrapments.

There was a gust of wind. It was chilly. Sometime tomorrow, the weather
would probably change.

Inukashi curled up, and gave a small sneeze.

He'd been taken ahold of, he knew it. He'd been taken ahold of firmly by
Nezumi's persistent intentions, and Shion's resolution.

\emph{No, that's not it. Half of it is me sticking my own foot in.}

It wasn't because he had been threatened by Nezumi, or because he felt
pity for Shion. He had stepped in on his own will.

\emph{But why?}

He questioned himself, but did not receive an answer.

\emph{Why? Why have I---}

He craned his neck again to survey the Holy City.

\emph{Over there, the Holy City of No. 6 glitters, and over here is where we
spend our daily lives. The amount of leftovers that No. 6 spits out in a
single day is enough to easily satisfy the hunger of all the people
here. Just leftovers. Half-eaten food, for god's sakes.}

Gluttony and starvation, extravagance and poverty, rejoicing of life and
fear of death, arrogance and debasement---

Would he be able to change it?

Inukashi walked briskly in the wind. His hair rippled and streamed out
behind him.

Would he be able to change the reality he had resigned himself to, the
days he had struggled to survive, his life which had long been stripped
of any dignity as a human being?

\emph{Ridiculous. It's just a fairy tale. Besides, what can we do now that---}
But Nezumi had, and so had Shion. Nezumi and Shion believed. They
believed that they would be able to change things with their own power.

Inukashi couldn't bring himself to laugh at them for it. The thought,
the possibility, had crossed his mind.

\emph{This is bad.}

One misstep, and he probably wouldn't live to see spring.

\emph{This is bad. This is very bad.}

But he was lighthearted. He felt so buoyant he felt like breaking out
into song.

As he whistled a light tune, the wind hitting his body, Inukashi found
himself breaking into a run.

\mybreak

Shion finished neatly combing the last dog, and sank down on the spot.
He had to admit that he was exhausted. The whole day today he had
devoted to taking care of the dogs. He felt like he'd become a dog
himself. It was already dusk.

The puppies nudged at him playfully.

"Alright, alright. Come along, then, all your fleas should be gone now."
He had just scooped one of them up when Cravat gave a squeak from his
pocket. Shion lifted his face.

Nezumi was standing right in front of him. He had not realized it. He
had felt no presence at all. But of course, by this time, it was no
surprise to him either.

Shion put the puppy down, and stood up without a word. Nezumi, also
silent, jerked his chin. He began walking straight toward the ruins.

"Nezumi --- you got word from Inukashi?"

"The two of them are waiting for us."

"Two?"

They climbed the crumbling stairs, and opened the door at the end of the
hall. On top of the small, round table, a candle was burning. Inukashi
and Rikiga were seated.

"They've graciously offered their help. Let's be thankful, Shion."

"Graciously?" Inukashi scoffed, and gave an exaggerated sigh. "I don't
think you call getting threatened, bribed, or tricked into doing
something is 'gracious', Nezumi."

Shion took a step forward, and bowed his head deeply. He had no words to
say. He felt like no words would be able to express how grateful he
felt.

"Thank you --- all of you." This typical statement was all he could say.

"Shion, no need to be serious about it," Nezumi quipped. "They've all
got ulterior motives. They're only here because they were attracted to
the sweet scent of personal profit."

"Eve, one of these days, that cheeky tongue of yours is gonna rot and
fall off. That much I'm sure of." Rikiga had a bottle of whisky in his
right hand, one that he had evidently brought along with him. He took a
swig, and swallowed it slowly.

Nezumi indicated with his gaze for Shion to sit, and then lowered
himself into a chair as well. Inukashi was the one who stood up.

"Can I start, Nezumi?"

"Yeah. Go ahead."

Shion made a tight fist in his lap. \emph{I've gotten all these people
involved. I'm the one that did it. I can't let myself forget that.}

A hand suddenly reached over to him. It was Nezumi's. It gently pried
Shion's fist open, finger by finger, gently, as if toying with it.

"We're just getting started. Tense up like that, and you won't last."

With his gaze fixed on the fluttering flame of the candle, Nezumi spoke
as if to himself. There was probably a draft coming in from somewhere,
for the flame kept flickering. It was already completely dark outside. A
long day was coming to a close. No, things were just starting. They were
starting right here.

"This week, the number of prisoners escorted into the Correctional
Facility was three. Among them\el " Inukashi trailed off while staring at
the candle, then resumed. The darkness edged in on them. The flame
flickered. "Among them, there were no women. There were no escorts from
within the city. All three of them were men from the West Block."

Nezumi questioned him in a low voice.

"Are you sure about that?"

"Yeah. I heard it directly from the guy who's in charge of preparing the
prisoner's clothes. There were three of them recorded in the Prisoner
Registration data. They tried to break into the Access Control Office to
steal money. They were either hungry enough to do it, or they were funny
in the head. Either way, there were no women."

"That can't be!" Shion sprang up from his seat.

There was no way that could be. But at the same time, his heart softened
just for an instant. What if Safu was actually safe? \emph{Maybe that coat was
just my mistake, and it didn't belong to Safu. Maybe---}

"If that's true, then things are gonna be complicated." Nezumi furrowed
his brow. His voice was cold, like the draft that made the flame
flicker.

"Complicated?"

"It means that she's probably not a legitimate prisoner. I know it's
weird to call a prisoner legitimate, but if she's not registered as one
in the Correctional Facility, then--- Shion, it means she doesn't even
exist as a prisoner. She's been erased."

"Erased\el "

"The moment your friend got captured by the Security Bureau, all of her
data as a citizen would have been erased. In normal circumstances, it
would've just been forwarded to the Correctional Facility's main
computer, and been filed as prisoner data. Then, once inside the
Facility, all her personal information would be re-collected and added
to, along with photos from all sides, height, weight, fingerprint, vocal
signature, iris, and her finger vein. Only after these procedures do
prisoners really become prisoners. It wouldn't matter so much for
thieves from the West Block, but if their subject is a former citizen of
No. 6, then they would definitely be thorough about these things. But
this time, it wasn't done at all. Why? So as not to leave any trace that
your friend ever existed."

"Hey, Nezumi." Rikiga noisily placed his bottle on the table. "Can't you
go about things a bit more delicately? All this talk about erasing and
leaving traces\el it's almost like you're saying the girl\el uh, Safu,
was it? You make it sound like this Safu girl has already been
murdered."

"I think you're more lacking in delicacy than me, old man."

Shion swallowed hard while he listened to the two speak. He didn't feel
well. He felt like he was in a nasty bout of drunkenness. But now wasn't
the time to slump over the table and go to sleep.

\emph{Safu\el }

"Safu was an outstanding human resource," Shion said evenly. "The city
has spent a lot of money and time on her raising her from childhood.
They've been raising her to have a future career in the upper echelons
of the city. Why would they erase her? It would be a huge loss to the
city, too, if they did."

His own voice sounded like a stranger's to his ears. It was a hoarse and
irritating voice.

"Yeah, that's the problem," Nezumi agreed. "Why were they so willing to
wipe out an elite they've kept domesticated with all this time and
money? It's not likely she's gone and done something idiotic, like you
did when you were twelve."

Inukashi's nose twitched.

"What idiotic thing? Does it have something to do with why Shion got
kicked out of No. 6?"

"It does. But that's not relevant right now. Shion."

"Yeah\el "

"What's your friend's family structure?"

"Safu didn't have any parents. I think the only relative she had was her
grandmother. She said she'd been raised by her."

"Just her grandmother, huh. Which means if Grandma dies, then Bestie is
left without relatives."

"Yeah\el "

Shion lifted his face, and his gaze met with a pair of grey eyes. He
could finally understand what Nezumi was trying to get at.

"Even if Safu disappears, there would be no relatives to make a big deal
about it. And not only that---"

"What else?"

"Safu was supposed to be living in another city for two years on
exchange. Even if she went missing from No. 6, no one would find it
strange."

"That probably about sums it up, then. She's an elite, has no relatives,
and wouldn't raise suspicions if she went missing for a long time. Your
best friend filled those requirements. That's why she was apprehended
and imprisoned in the Correctional Facility. Not as a prisoner, but---"

"Not as a prisoner--- then what for?"

"I don't know." Nezumi shook his head. Inukashi leaned forward.

"Hey, does that have something to do with the rumours? The one about the
weird disease going around inside No. 6."

"Do you have the details on that?"

"No," Inukashi said promptly. "It's not that easy to get information
about what's going on inside that city, you know. This might be more of
a job for Mr. Alcoholic."

Rikiga drained the rest of the contents of his bottle, and glared at
Inukashi with bloodshot eyes.

"I don't think Doggy-boy has any right to call me an alcoholic. As for
inside information about the city, I can't get it rightaway. Earliest
would be the day after tomorrow. But I'm warning you, Eve, just because
you have all the information you need, it doesn't mean things are going
to go well. How do you plan on infiltrating the Correctional Facility?"

There was no answer. Rikiga hunched his shoulders.

"What're you gonna do? Attack the Access Control Office like those three
lunatics, and get arrested on purpose?"

"Can't do that," Nezumi said brusquely. "All my personal information is
recorded on their main computer."

"Oh? So it was true that you'd once been in the Correctional Facility.
Ah, so there is a way to get out of that place alive, huh. What a
surprise. Give me an autograph, will you, I'll hang it on my wall. Of
course, with your real name."

Nezumi ignored Rikiga's joke. The flame flickered violently. The wind
had probably gotten stronger.

"Inukashi --- how about the security system?"

"I couldn't get anything too specific. I've got the main points down.
And there seems to be a new facility that's been built underground."

"New facility? For what?"

"I dunno. Even the custodians aren't allowed to go in there. Supposedly
there's an elevator that leads directly to the top floor, but it also
has an elaborate physical recognition system that only a fraction of
people can log into."

"Top-secret and confidential, huh\el and this facility is located in the
Correctional Facility, and not the Moondrop. I see."

Nezumi lapsed into his thoughts. Shion fixed his gaze on Nezumi's
profile.

"Nezumi."

"What?"

"Getting arrested would be the easiest and most surefire way, right?"

"In a sense. But once you get inside like that, there'd be no room for
free movement at all."

"Is it impossible to rescue Safu? Isn't there even a single percent of
possibility that we can save her?"

Nezumi gazed at Shion with a mixture of cold indifference and pity.

"You're in the same boat as me," he said. "They've got all your personal
information on file. Say we get arrested and they scan through your
data. It wouldn't even take them a second to match you up with the
first-class criminal on the run. If fortunes work in your favour, you'd
be sent to a solitary cell. If they don't, you'd be executed on the
spot."

Rikiga erupted into a fit of coughs. Inukashi drew his chair back with a
large screech.

"First-class criminal on the run? This dense boy here? Wait a minute,
Nezumi. I haven't heard a word of this."

"Because I haven't told you."

Ignoring Inukashi and Rikiga's rapt gaze, Shion persisted with Nezumi.
There had to be something. Somewhere, there had to be a possibility.
Even if it was slimmer than one percent, thinner than a spider's thread,
he had to grasp it and draw it toward him. Despair was not permissible.

"If we get arrested as prisoners, does everyone get searched
immediately? Isn't there any way to avoid the data-matching in the time
between getting imprisoned until we get Safu out?"

"No," Nezumi answered. "As soon as we get arrested, they'd pull up all
our personal information, and scan it through their files. They won't
let a single mole go unnoticed. And then we'd get implanted with a
V-Chip. Prisoners are bound and placed under surveillance for the whole
time. We won't even get a second of free movement."

"No exceptions?"

"No exceptions. Not a single---"

Nezumi abruptly swallowed his words. His face froze.

"Nezumi?"

At his sudden silence, Shion, Inukashi, and Rikiga held their breaths
and unconsciously trained their ears. A voice spilled out into the
silence.

"There is."

"Huh?"

"There's just one exception."

Shion widened his eyes, and stared intently at Nezumi's candlelit
profile. Nezumi's lips moved.

"The Hunt." His voice was raspy, and very low.

Inukashi's body tensed in his chair. Rikiga dropped his gaze from
Nezumi, and gripped his liquor bottle.

"Hunt? What's that?" Shion looked around at the other three faces. There
was no answer from any of them. The darkness in the room thickened.
Inukashi sighed.

Nighttime was approaching.

No. 6, glittering golden, would reign over the night. In a corner of the
West Block, in a room carved out amongst the ruins, at the very bottom
of the deep of the night, the four of them silently sat surrounding a
flickering flame.

There was the sound of the wind. It moaned as if it called to someone,
as if in yearning. And the night enveloped it all.

The wind whistled. The flame flickered, and went out as if it had spent
the last of its energy. Nezumi's whisper echoed in the darkness. It was
no longer hoarse.

"The Hunt --- that's the only exception."