% !TeX spellcheck = en_US

\chapter{Of life and death}

\myepigraph{Thou livest; report me and my cause aright\\
	To the unsatisfied.}{\emph{Hamlet}, Act V Scene II}

\lettrine{S}{hion closed} the book. He could hear the sound of rain.

This underground room was cut off from most outside sounds. But for some
reason, the sounds of the wind and the rain always seemed to seep
through the walls.

A mouse scurried up Shion's leg and perched on his knee. It twitched its
whiskers and rubbed its front paws together as if in request.

"You want me to read this book to you?"

\emph{Cheep.}

"You really like tragedies, don't you. Why don't you pick something more
fun?"

The mouse looked up at him and blinked its grape-coloured eyes. Shion
adjusted himself in his chair and crossed his legs, with the mouse still
on his knee.

The chair had once been quite a fine piece of furniture. It was evident
from its sturdy build and the delicate patterns carved into the
chair-back. But now, it was worn and old; the colour was peeling in
various places, and the cushion had faded so much it was impossible to
tell what colour it had been before. Still, it was one of the few pieces
of furniture that this room had. A week ago, Shion had dug it out from
among the books that covered two-thirds of the room's floor space.

"There might be an even bigger treasure hidden in these books, if you
sorted them out." Shion had meant to sound serious, but Nezumi scoffed.

"Why don't you worry about building up some strength before thinking
about stupid stuff like that? You're a little boy who's probably never
had to do any physical labour since the day you were born. You're pale
and skinny enough as it is."

"I was in charge of cleaning duties at the park. I had to do physical
labour all the time."

Nezumi's shoulders hunched. His voice was tinged with contempt.

"Cleaning duties? Does cleaning count as physical labour in No. 6? All
you had to do was operate the robots that did the maintenance and
cleaning. What physical labour is, little boy---"

Nezumi grabbed Shion's arm and dug his fingers in so hard that he
winced. Nezumi's fingers, slender at first glance, had a surprisingly
strong grip.

"---is using these arms, your legs, and putting your back into it. Using
your own body. Remember that."

Nezumi's biting and sarcastic way of speaking didn't bother Shion much
anymore after he had gotten used to it. In its harshness and cynicism,
there was often a truth that he couldn't help but agree with, and
oftentimes he would come away more persuaded than offended. It was true,
the work that Shion did in the Holy City of No. 6 was just to tap the
keys of the control panel. He had never experienced the kind of labour
that made his own body creak under its burden. He had no experience of
what it was like to be damp with sweat, to have the skin of his hands
blister and tear, to have his muscles ache from exhaustion; to be
famished unbearably, and to fall into a comfortable slumber after a
day's work.

He had never experienced it once.

"That's why I'm going to do this," Shion said determinedly, pointing at
the mountains of books that piled high all over the room. "I'm going to
organize them, sort them out, and shelve them in order. If that's not
physical labour, I don't know what is."

"It'll take you a hundred years."

"I'll do it in a week."

Nezumi shrugged his shoulders again. "As you wish," he sighed.

"Do what you want. But stick with the books and bookshelves. Don't touch
anything else."

"You don't have much other than books and bookshelves in here."

"Like you said, you might find some amazing treasure. To tell you the
truth, even I don't know what's buried under these books."

The mice were chattering to each other from the nooks and tiny spaces
between the books. Shion picked up a small, light-green volume.

"Nezumi."

"Hm?"

"How long have you been living here?"

These bare concrete walls, thousands of books, this underground room--- it
didn't seem well-suited to be a human dwelling.

"You didn't grow up here, did you? Where were you---"

He closed his mouth. He noticed that Nezumi's grey eyes were harbouring
a steely glint.

"I'm--- I'm sorry."

Nezumi snatched the book out of Shion's hand and threw it aside.

"If you plan on staying here---" he wrapped his shoulders in the
superfibre cloth, and gave an impatient sigh. "Then do something about
that interrogation habit of yours. I don't know how much more I can take
of you nosing around every little part of my life."

"I'm not nosing around. I just wanted to know."

"Sniffing around and questioning people for every piece of information
you want is called nosing around. Remember that too."

Shion felt a jab of irritation at the way Nezumi's words seemed to push
him away. Indignation welled up inside him. He wasn't nosing around. He
grabbed Nezumi's arm as he made to leave the room.

"I barely know anything yet. That's why I wanted to know."

"And I'm saying that's called---"

"If it was something I could get by without knowing," Shion interrupted,
"I wouldn't want to know about it. But I do want to know. To me, this is
something I need to know. I want to know, and that's why---\emph{ach}---" He bit
his tongue. He clamped a hand over his mouth and squatted on the floor
in pain. Tears stung at his eyes and the pain smarted in his mouth.
Nezumi burst out laughing.

"Geez, does clumsiness come naturally to you too? I never get tired of
looking at you. ---You alright?"

"Somewhat. Biting your tongue is really painful." When he had been in
No. 6 --- that was from when he was born, to the age of sixteen--- Shion had
never once tripped over his words enough to bite his tongue. And it was
the first time, too, that he had grabbed someone's arm without thinking,
out of desire to say what his heart raced to tell, his words unable to
keep up with his thoughts.

"So?"

Nezumi knelt down, and peered into Shion's face. The light in his eyes,
which had the sheen of finely-woven cloth, had subsided to a gentle
glow.

"What do you want to know?"

"You---" Shion answered. "I want to know about you."

Nezumi's mouth fell open. He blinked several times.

"Shion, have you been reading any strange books lately?"

"Strange?"

"Like romance novels, the kind that are cliché and over the top. You
know, where a prince comes to rescue a damsel in distress, or when
lovers who are torn apart overcome trials and tribulations to reunite
again."

"I don't think I've read any of those."

"Then where the hell did you come up with that line? '\emph{I want to know
about you}'," Nezumi echoed in disbelief.

"I don't have to learn that from anywhere to say it."

"Are you serious about what you just said?"

"Of course. Nezumi---" Shion wiped his lips, and looked directly into his
grey eyes. "I want to know. I want to know because there are still so
many things I don't know. All I know about you is that you've saved me.
I don't know your real name, or how you grew up, or why you're living
here alone--- or what you're thinking of now, or what you're planning to
do --- I have no idea. I don't know a single thing about you."

He was grabbed by the wrist. Nezumi's fingers were always cold, and
rigid.

"Then I'll tell you something. Put your hand here." Shion did as he was
told, and placed his hand on Nezumi's chest.

"What do you feel?"

"Feel---? Well, it feels like a man's chest, for one. It's hard, and
flat."

"I know, I know. Too bad for you, I don't have big breasts. What else?"

"Well\el "

What did he feel on his palm through the rough fabric of Nezumi's shirt?
It was his heartbeat, his warmth, and the firmness of his flesh. Shion
hesitated to put it into words. He didn't know why. He withdrew his
hand, and curled his fingers over his palm. Nezumi chuckled quietly.

"My heart was beating, and it was warm. Right?"

"Of course. You're alive. It's normal for your heart to be beating and
for you to feel warm."

"It is. I'm alive, and I'm right here in front of you. That's all you
need to know. What more do you want?"

Nezumi stood up, and looked down at Shion. His gaze, like his fingers,
was cold.

"What you want is information," he said icily. "My birth date, my
development history, my height, weight, index of my intelligence, DNA
data. You just want information that you can convert into numbers.
That's the only way you ever try to understand other humans. That's why
you can't understand the living people that are standing right in front
of you."

Shion stood up as well. He clenched his fist harder.

"You're big on sarcasm, and love to make fun of people. You don't like
fish, and you're a restless sleeper."

There was a moment of silence.

"---Huh?"

Shion continued.

"You have an enormous amount of knowledge, and a wide range of it too---
but none of it is systematic. Sometimes you're fickle and
over-sensitive, but other times you're lazy and careless about the
details. You adore piping-hot soup, and you get really grumpy when it
doesn't have the right amount of salt. And last night, you kicked me
three times in your sleep."

"Hey Shion, wait a minute---"

"Since coming here, this is what I've learned about you. They're not
numbers. I would never substitute you for numbers. That's not what I
want to do."

Nezumi's gaze slid away from him.

"I'm just a stranger to you," he said. "You shouldn't be interested in
strangers. Four years ago, you saved my life, and I owe you a big debt
for that. So that's why, this time, I helped you out. So if you want,
you can stay here for as long as you wish and do what you want to do.
But never think of wanting to know more about another stranger."

"Why not?"

"Because it gets in the way."

"Gets in the way? Knowing things gets in my way?"

"Yes, for people like you. You're good at cramming knowledge, but you
give in easily to your emotions. You're quick to trust in people, and
try to attach yourself to them. I told you before, didn't I? Cut
yourself off, and throw away everything you don't need."

"Yeah, but\el "

"But what you're doing right now is just the opposite. You're starting
to take interest in me and want to know more. You're trying to add even
more to your burden. You're hopelessly stupid, just hopeless."

Shion couldn't understand what Nezumi was saying. It was more
confounding and difficult to grasp than any scholarly book he had read.

"Nezumi, I don't understand what you're talking about." He voiced his
feelings truthfully. Nezumi shrugged slightly.

"The more you know, the more emotionally attached you'll get. Then we
can't be strangers anymore. And that'll be trouble for you."

"For me? Why?"

"When we become enemies, you won't be able to kill me." There was a hint
of a laugh in his voice. Shion dug his feet firmly into the worn carpet.

"While you're busy being caught up in your emotions, I can go ahead and
stab a knife into your heart. You know, a knife is a really ancient
weapon, but it can come in handy sometimes."

"Why do you and I have to become enemies? That's just absurd. \emph{That's}
what's stupid, if anything."

"Really? I think it's pretty plausible."

"Nezumi!" Shion said heatedly.

There was a loud toppling noise as a pile of books fell over. A mouse
hopped onto Nezumi's shoulder.

"Well, if you're really gonna organize these books, you better get
cracking. One week will be over in no time. I'm going to work." Nezumi
turned nimbly on his heel and walked out the door. Shion felt all the
tension leave his body. He was cold and clammy. Conversations with
Nezumi sometimes made him so wrought with nerves that he broke out in a
cold sweat. Shion licked his dry lips.

"I don't even know what kind of job it is that you do," he muttered to
himself. "I only wanted to know. Who's the stupid one here?" He let his
words hang for a moment, then set out to organize the stacks of books.

"Shion." The door opened, and Nezumi's voice called him. A pair of work
gloves were tossed his way.

"You'll crack a nail if you use your bare hands." The door closed before
Shion could say thanks, and silence settled over the room again. This
casual act of kindness, or those cold, dispassionate words from a few
minutes ago--- which one was he to believe? Shion couldn't grasp him. That
was why he wished could reach out and take firm hold. Shion pulled the
gloves over his hands, and lifted some books off the floor.

\emph{Of course. It's good to wear gloves when doing this kind of work. That's
another thing I didn't even know.}

\emph{You just want information that you can convert into numbers. That's the
only way you ever try to understand other humans.} The words that had
been slapped in his face minutes before still remained stubbornly in his
ears. This method of analyzing people through their data was something
Shion had learned all his life in No. 6, ever since he had been deemed
top-ranking in the Childrens' Examinations and was given a top-class
learning environment.

The human body is made up of 274 different types of cells, numbering 60
billion in total. He remembered perfectly the names, shapes, and
functions of each. He knew the locations and functions of each organ,
and had also learned about the transmission paths of signals between the
amygdala, perirhinal cortex and the hippocampus.

But it was no use to him. No matter how much he put his knowledge to
work, he was unable to understand the person with whom he'd been living
for almost a month.

Was Nezumi honestly thinking that they were going to become enemies some
day? That they would end up killing each other--- was that possible?
Nezumi's words and actions were always shrouded in mystery, and confused
Shion greatly.

He couldn't grasp him. That was why he wished could reach out and take
firm hold. He wanted to know the part of Nezumi that couldn't be
substituted for numbers or symbols. Shion shook his head. The mice
scampered busily about his feet. \emph{I have to stop. Brooding over it isn't
gonna help. Right now, I have to wage war with these books.}

He was soon damp with perspiration. His back ached, and his arms felt
heavy. But what interrupted Shion in his work was not in his bodily ache
or exhaustion, but in the pages of the books he went through. He would
casually flip to a story, and find himself sinking to the floor to read
the rest. Wholly engrossed, he would soon lose track of the hour. And
each time, a little mouse hopped up onto the page in stern reprimand.

"Give me one more minute. I'll put it away as soon as I'm finished
reading this part."

"\emph{Cheep cheep!}"

"Alright, alright. I'm getting on it, okay? Are you satisfied now?"

And on the third day, he found it, under an old copy of a science
journal. A small, silver box. His emergency kit.

On that stormy night four years ago, Nezumi had appeared, sopping wet, a
sudden intruder in Shion's home. His shoulder stained with blood, the
dripping boy before him looked as if he was about to collapse. Shion had
extended his hand without thinking. His protective instinct had stirred
so strongly in him that he had even forgotten to feel fear toward the
intruder. Even after finding out that he was a VC--- considered a violent
and dangerous criminal in No. 6--- that feeling did not change. Shion took
Nezumi under his wing, and provided treatment for his wound and a
momentary respite. He didn't hesitate to. He couldn't help but do what
he did. As a result, Shion lost most of what he had, as well as a large
part of his secure and privileged life.

That night, Shion had treated the wound, painfully evident of the bullet
that had caused it, with the tools and medication in this emergency kit.
The next morning, there were four things missing in Shion's presence---
the red checkered shirt, the towel, the emergency kit, and Nezumi
himself. Of them, two were back in his hands. Or, rather, emergency kit
aside, perhaps it wasn't right to say that Nezumi had "come back" into
his hands. Shion was the one who had fallen into a trap, and was about
to be hauled to the Correctional Facility by the Security Bureau--- Nezumi
was the one who had saved him, and brought him outside No. 6.

\emph{He wasn't the one that came back. I was the one that burst in and took
refuge here.} That was the reality of it. He had fallen from the Utopian
City--- even called Holy by some---into this underground room, where no
sunlight shone. He would probably never be able to return to No. 6
legitimately again. He had left his mother there. Was Karan still
thinking of him, even after he had been cast as an escaped criminal?
Shion knew it was fruitless to think about it, but his heart ached
nonetheless.

He couldn't throw it all away like Nezumi. He couldn't cut himself off.
He couldn't live without. He had to cling to something, else he would
crumble and fall. He had to have someone in his heart always, else he
would go insane.

Shion opened the lid of the box. It looked like the automatic sterilizer
was still functioning. A scalpel and a roll of gauze glowed dimly under
the faint reddish light of the sterile lamp. A nostalgic feeling welled
up in his chest as if he was meeting an old friend.

"\emph{Cheep-cheep! Chit-chit-chit!}"

"What? I know, I know. I'm getting there. Geez, you're strict." Shion
laughed. As if in response, the mouse raised its front paws and
chittered.

\mybreak

By the time a week rolled around, Shion had managed to organize almost
all of the books that had been dominating most of the floor. Of course,
it was impossible to find shelf space for all of them, and many piles of
books still remained on the floor --- but it had cleared up a considerable
amount of living space.

"So what do you think?" Shion puffed out his chest proudly. Nezumi was
draped lazily over the chair. He yawned.

"The emergency kit, a couple blankets, a mug, and an old heater. Is that
all you managed to find?"

"That's a lot," Shion replied indignantly.

"Too bad you couldn't find an entry permit into No. 6."

Shion moved in front of Nezumi, and looked him directly in the eye. If
he was going to speak in earnest, he mustn't avert the other's gaze. It
was one of the things he had learned in his one month of living with
Nezumi. Shion bent over, and clasped each hand around the armrests of
the chair.

"What?"

Shion was now blocking Nezumi from the front. Nezumi shifted uneasily in
his seat.

"Nezumi, my mother is still in No. 6. She's my only blood relative. I
don't care how much you laugh at me for it, but I'll never be able to
cut her off. But--- but let me say this. I have no attachments to life in
that city anymore. Even if someone told me I could go back in time, I
wouldn't want to go back to when I had the privilege to live in No. 6 as
its legitimate citizen. I'm serious--- I wouldn't want to return one bit."

The grey eyes on the other end of Shion's gaze didn't blink once.

"You said that my life in No. 6 was fake. Now I've experienced it for
myself. And I never, ever want to return to a life that's fake, and only
peaceful and privileged in appearance."

"So you're prepared to live life outside of the Holy City, is that what
you're telling me?"

"Yeah."

"Do you know what kind of place this is?"

He hesitated to answer. Nezumi's lips twisted into a cold smile.

"You don't know anything," he said softly. "You don't know what it's
like to starve, to shiver in the cold, to groan from a wound that's
festered because it's been left untreated too long; you don't know the
suffering that follows when that wound becomes infested with maggots,
and you start rotting alive; you don't know how it feels to watch
someone die in front of you, while there's nothing you can do to help
them. You don't know a single thing. You're just rattling off pretty
words. You've experienced it for yourself, you say? You've only peeled
the surface of that city and sniffed at it, and already you're acting
like you know everything about it. It might be a city of lies, but in
No. 6 you have a warm bed, plenty of food and clean water. You have
fully-equipped medical facilities, recreational facilities, educational
institutions. Everything that residents here would never be able to
have, no matter how hard they wished. And you say you have no
attachments to those? That's arrogant of you. So arrogant it makes my
skin crawl. Either that, or you're a liar."

Shion drew a breath. He tightened his grip on the armrests.

"It might be arrogant--- but I'm not lying. Regardless of what kind of
place is, I still want to continue living here. It's not because I got
chased out of No. 6 as a criminal. Even if I wasn't--- no matter how
horrible this environment turns out to be, I want to stay here."

"What's your reason?" Nezumi shot back. "If you're not lying, and if
you're not trying to impress me with a model answer, what lead you to
make that decision?"

"I'm drawn to you."

"Huh?"

"You know things that I don't know. You've taught me things that no one
has ever taught me before. I can't say it well, but---" he hesitated. "I'm
drawn to you. A lot. That's why I want to stay here. I want to see what
you see, eat what you eat, and breathe the same air as you. I want to
hold in these hands what I would never have been able to get in No. 6."

Nezumi slowly blinked twice. Then, he placed a palm on his forehead and
shook his head slowly in exasperation.

"Shion, I've been noticing this for some time now, but---"

"Yeah?"

"Your language ability is worse than a chimpanzee."

"I've heard before that the genome of a human and chimpanzee are only
different by 1.23\%," said Shion, unfazed. "I don't think you should
mock chimpanzees."

"I'm mocking \emph{you}. Idiot. Don't you have any idea what proper expressions
to use?"

"Was there something weird about what I said?"

"Don't use words like 'drawn to' so easily. It's a very weighty,
important word. You're only supposed to use it for a special,
irreplaceable person in your life."

"Then how am I supposed to say it? Do I say I love you?"

Nezumi heaved a long, exaggerated sigh. "Never mind," he muttered. "It
messes me up when I talk to you. Here," he pushed a thick book into
Shion's hands, and stood up. "\emph{Hamlet}. Read it."

"I already have."

"Then read it again. Give that crippled language ability of yours some
good, hard training. Learn some words."

"Was I off-the-mark that badly?"

Nezumi's words quickened.

"You're just fascinated by new and unusual things. You're like a scholar
who's discovered a new planet, or a new kind of bacteria. You're just
itching with curiosity because you've met someone who's different from
all the people that used to surround you. That's it. You're not drawn to
me, and you're not in love with me. You're just excited about the exotic
animal you've discovered. Can't you even tell the difference?"

They were harsh words. They became sharp thorns that stabbed at Shion's
eardrums.

"I don't trust you," Nezumi said.

Shion raised his face, and his gaze collided with Nezumi's. He had been
biting his lip without thinking.

"I don't trust anything you say. You're someone who's been living in
artificial abundance since you were born. And you're arrogant enough to
be able to say you can throw away that fortune easily. ---Shion," he said
suddenly. "When you used to do that cleaning job at the park, you had to
do that ritual every morning, didn't you?"

The ritual was always the first task in Shion's work day. He had to lay
a palm on the image of the City Hall --- or Moondrop, informally --- that
was displayed on monitor of the maintenance system, and pledge his
allegiance.

"I hereon and ever pledge my unwavering allegiance to the City of No.
6."

"Our gratitude for your loyalty. Engage in your day's labour with
sincerity and pride as a good citizen of the City."

That was it. Every morning, he had repeated the same task. It had been a
sore discomfort for him. His youthful pride stung for having to repeat
these banal and grandiose words, and for this ritual itself, which
seemed foolish.

Nezumi gave a short laugh.

"You hated it, didn't you."

"Yeah."

"Felt suffocated, didn't you, being forced to declare your loyalty."

"Yeah\el now that you mention it."

"But you put up with it," Nezumi said. "Instead of retaliating, you
recited this pledge every morning, not meaning a single word of it, and
pretended it didn't bother you. Let me tell you something, Shion: words
aren't things that you can toss around casually. You can't let yourself
be forced to say something, and just put up with it. But you don't know
that. So that's why I'm not going to trust you."

Nezumi's hand suddenly extended toward him. His palm touched Shion's
cheek.

"Did that hurt?" he asked gently.

"Quite a bit."

"---I don't have any grudge against you. And I don't hate you, either."

"I know\el " Shion answered quietly. "That much I can tell."

"Shion."

"Hm?"

"Feel like going outside?"

His fingers caressed Shion's hair.

"You're fully recovered, now, aren't you? Feel like seeing for yourself
the place you've decided to continue living in?"

Nezumi's hand slowly drew away. Several strands of white hair clung to
his long fingers. Shion's hair still had some lustre despite being
drained of its colour, and to certain eyes he figured it might look
pretty. But he felt its beauty to be cruel. In a single night, the
colour had faded from his hair, and he had been scarred with a red band
that slithered like a serpent over his entire body. He had been seen by
children, who had shrieked at the sight of him. He couldn't forget the
look in their eyes. They were filled with dismay and horror like the
eyes of one who beheld a deformed monster. But he had to go outside. He
wanted to see the world he was going to live in with his own eyes, hear
the sounds with his own ears, smell with his nose, and feel it on his
own skin. Then, maybe, he would speak to Nezumi about it again.

\emph{No matter what kind of place this is, I want to keep living here. Rather
than being surrounded by falsities, and being forced to swallow banal
words, I want to live here--- even if it means I have to struggle---}

"We can dye your hair, if it'll make you feel better at all," Nezumi
said. "Black, brown, green--- whatever colour you wish. What do you wanna
do?"

"No, it's fine."

"You're going to keep it?"

"Yeah, I'll keep my hair like this. White hair isn't so bad. I figure
it's better than being completely bald."

Nezumi lowered his face. His shoulders were trembling.

"You're really funny, you know that?" he said, his voice shaking from
holding back a laugh. "Seriously. I mean, really."

"Am I?" said Shion dubiously. "No one's ever really told me I'm
funny\el "

"You're a natural comedian. You should toss the theory books and study
comedy instead."

"I'll think about it."

"You should. Right--- tomorrow, then, I'll show you around."

"Alright," Shion agreed.

"And there's one place you definitely need to go to."

"Latch Building," Shion answered for him.

\memo{\karan}{Arnd LK-3000. Latch Bl. 3F. Not sure. -K}

It was a memo from Karan, and it was a cryptic one--- Shion didn't know
where it pointed to, or who was going to be there.

"Did you find out where Latch Building is?"

"Nope," Nezumi replied. "We don't have any fancy numberings for our
buildings here. But once upon a time this place used to be a decent
town, and I was able to get a map from then. And there's a region that's
marked LK-3000."

"You looked all of this up\el " Shion murmured in awe.

"Just to kill some time."

"I didn't think you had time to kill. You always seem so busy---"

"Oh, and write a letter," Nezumi interrupted nonchalantly.

"Huh?"

"To your Mama. But keep it within 15 words. Just a simple note. The
mouse here says he misses your mother's homemade bread."

"You'll deliver the letter for me?"

"More like a memo," he said brusquely. "Under 15 words. I can't
guarantee it'll get there safely."

"Nezumi."

"What?"

"Thank you."

Nezumi shrank away from Shion and fixed him with an appalled stare.

"Please, can you not look at me like that? It gives me the willies.
What'll happen tomorrow will happen tomorrow. I'm gonna take a shower.
Oh, and before you write a letter to your mama, read the poor little guy
a story. He's been waiting all this time."

Nezumi disappeared into the bathroom. Shion curled up in a chair, and
opened the book he had been passed earlier. There was a faint whiff of
the smell of paper. He was drawn in instantly, and soon lost himself in
its pages.

\poem{If thou didst ever hold me in thy heart,\\
	Absent thee from felicity awhile,\\
	And in this harsh world draw thy breath in pain\\
	To tell my story.}

Hamlet drew his last breath in the arms of his friend. Shion slowly
closed the book. There was the sound of rain. He wondered why it always
seemed to seep through the walls into this underground room. It seeped
through and reverberated, like the soft sound of music.

And in this harsh world, draw thy breath in pain--- maybe that's what
living on in this world meant--- to suffer in pain. And Nezumi knew this.
It had been ingrained into his body. A mouse chirruped at his foot.

"Oh, sorry about that. Which one do you want me to read?"

The mouse climbed up onto his knee, and rubbed its front paws together.

"You want me to read this book to you?"

\emph{Cheep.}

"You really like tragedies, don't you. Why don't you pick something more
fun?"

He crossed his legs, with the mouse still perched on his knee.

"Read him the tragedy," Nezumi's voice spoke from behind him. He hadn't
even noticed Nezumi coming out of the bathroom. He hadn't heard a sound
or felt any presence.

"You have a good voice. This little guy loves to be read to. And he
loves to listen to you read tragedies."

"Really?"

The mouse blinked its grape-coloured eyes at him. Shion guessed it was
his way of saying yes.

"Okay, okay. Then from the top of Act Five---"

"Shh---" Nezumi's damp hand pressed over Shion's mouth. "I hear
something."

"Huh?"

Before Shion could ask what it was, it reached his own ears. The sound
of footsteps clambering down the steps. The heavy door was being banged.
Someone was knocking on the centre of the door, and its sound was frantic, though not altogether strong.

A child.

A child was knocking desperately on the door. Shion stood up, and made
for the entrance.

"Not so fast." Nezumi stopped him. Under his wet bangs, his grey eyes
beheld the door warily.

"Don't open the door yet."

"Why not?"

"It's dangerous. Don't open the door without any defense."

"It's a child knocking. And it's urgent. Something must have happened."

"How can you be so sure? An armed soldier can knock on the bottom half
of the door, no problem."

Shion's gaze travelled from Nezumi's face to the door.

\emph{Help me.}

He thought he heard a weak voice cry out in plea. He swallowed. He
unlatched the door, and gripped the handle.

"Shion!"

He opened the door. A cold draft blew into the room. It was getting dark
outside, and a chill wind was blowing.

A girl was standing in the gathering dark. Her eyes were filled with
tears as she looked up at Shion. He had seen her before. She lived in
the barracks in the hollow under the slope. She was the girl he had not
been able to forget--- the girl who had shrieked at Shion's whitened hair
and red scar that snaked up his neck. For the first time, in this gaze,
he had been beheld like a deformity. But now, her large eyes were
brimming with tears, and contained no hint of terror. Instead, they were
bright with frantic urgency.

"Help me--- please--- he's dying."

Shion swiftly took the girl by her hand, and began to clamber up the
stairs. He hastily yelled over his shoulder.

"Nezumi, bring the emergency kit, and some blankets!"

Then he burst outside, into the wood of bare branches and fallen leaves.