% !TeX spellcheck = en_US

\chapter{Hidden danger}

\myepigraph{The first day or so we all pointed to our countries.\\
	The third or fourth day we were pointing to our continents.\\
	By the fifth day, we were aware of only one Earth.}{Sultan bin Salman Al-Saud, astronaut}

\lettrine{A}{fter Shion} had finished reading the picture book, Kalan gave a sigh of
satisfaction.

"That was a good story."

Rico blew out of his flared nostrils sullenly. He fiddled with the
newly-changed bandages on his neck and complained.

"Well, \emph{I} didn't think it was good. Stories about rabbits are boring."

"Then what kind of story do you want to hear, Rico?" Shion asked.

"Ummmm---" Rico paused for a moment of thought. "Oh, a story about bread.
And--- and one about soup and fried sweet potatoes."

"You must be hungry, Rico."

Kalan turned to Shion and nodded.

"He's hungry all the time. Rico gets more hungry than anyone else."

"Just a minute, then. I think I've got some soup\el " Was there any soup
left for him? A bowlful of soup that could sate Rico's empty stomach for
a short while---

Kalan stood up.

"No, thank you. It's okay. We have to go home now." She took her little
brother by the hand and made for the door. She stopped, turned, and
spoke in a small voice. "Thank you for reading to us."

"You're very welcome."

"Can we come again tomorrow?"

"Of course."

"Okay." A smile spread across Kalan's face, and she half-dragged Rico
out the door. Nezumi stretched in the shadow of a pile of a books.

"Stupid as always, aren't you."

"Stupid? Me?"

"They say the biggest idiots are the ones who don't realize they're
idiots. I think there was a proverb like that." Nezumi stood up, and
draped the superfibre cloth around his neck. "You tried to give a
handout to the kids. You tried to give them leftover soup."

"Is that a stupid thing to do?"

"Those kids came here to be read to. They didn't come to beg. If you can
ensure that Rico will never starve again, that would be fine and dandy.
But if you give him leftover soup on a whim one day, what're you gonna
do the next time he starves? You wouldn't be able to take care of him
all the time. If you're going to be irresponsible and abandon him
halfway, it would be better not to give him anything at all in the first
place. Kalan has a better idea of how things work. That girl is bright
and dignified. She knew to refuse your half-hearted and reckless
charity."

Shion sank into a chair. Nezumi's words always inflicted him with pain.
It felt like his skin was being torn from his very body. He could almost
hear the sound of his flesh being ripped from him. His foolishness, his
arrogance, his heedlessness. His outward vanity stripped from him, he
was left naked: superficial and pretentious--- his real self. Nezumi
strode in front of him and continued to speak while he pulled on a pair
of gloves.

"There's a second example of your stupidity. Wanna hear it?"

"Sure. Tell me."

"You made a promise for tomorrow."

"Is there something wrong with that?"

"There's no guarantee that there's gonna be a tomorrow."

Shion took a deep breath.

"So you're saying that I can't be sure that I'll be alive tomorrow to
read a book to those children?"

"Yeah. See, you're starting to pick up on things more quickly. You're on
the Bureau's Wanted list, and you went wandering around outside
yesterday. I wouldn't be surprised if the tracking satellites have got
you already. Maybe the guys who have nothing better to do over at the
Security Bureau's Law Enforcement division are heading over here right
now. If they are, then you can forget having a read-aloud tomorrow. At
best you'd be in a solitary cell in the Correctional Facility; at worst,
you won't even be able to speak, because you'll be dead."

Shion was gazing at Nezumi's leather-gloved hands. Even when he was
speaking crudely, his movements were still graceful. Shion wanted to
imitate him if he could.

"What?" Nezumi said. "You're spaced out again."

"Oh\el uh, sorry."

"You really have no sense of danger, do you? I think even a newborn fawn
would be more cautious than you."

"Nezumi."

"I don't want to hear it," he said abruptly. "I'm going to work."

"Do the city authorities really intend to capture me?"

Nezumi stopped.

"This place is adjacent to No. 6," Shion continued. "If they really set
out to catch me, it wouldn't be hard for them at all\el no, not even
just me. You're a VC on the run too, aren't you? And unlike me, you go
walking around outside all the time. No. 6's tracking satellites are
able to keep detailed surveillance on one location from their stationary
orbit."

"Uh-huh, so?"

"So I'm wondering why. The authorities aren't serious about trying to
catch us. They certainly haven't gotten desperate about it, to say the
least."

Nezumi shrugged his shoulders.

"Shion, in both good and bad ways, the city you were born in isn't
interested in things outside of it. For them, everything's complete
within those walls of special alloy. The West Block is their garbage
can. Here, they throw away their waste, their pus. If you're pus to
them, they probably think the West Block is an appropriate place for
you. They've squeezed the pus out of their tiny wound, and thrown it
away in the garbage. They're not going to come back looking for it."

"So I'd be safe as long as I stayed here."

"Who knows? It probably won't go that well, but there's a chance you
will be. ---You said you wanted to go on living here, didn't you? Maybe
your dream will come true."

"Until spring, at least."

He had a moratorium until spring. Once spring came, and the wasps
entered their activity period, what would happen in the interior of the
Holy City? Would the parasite wasps sweep the city with their dread? He
had to do something before it got warmer, before spring arrived. He had
to come up with a plan before they passed the winter through.

"The man-eating wasps have finally shown themselves," said Nezumi
airily. "You should just sit back and watch. It'll be an interesting
stage, to see what happens to No. 6. Our wasp will be the star of the
stage. A tragedy like no other--- or a comedy like no other. I wonder
which one it'll be?"

"Mother is still inside that city. I can't stand by and be a spectator."

"What, you're planning on going home?"

"Once, before spring comes. I'm going to see if I can make a blood serum
by then."

"Using your own blood?"

"Yeah. It would be impossible to make a perfect one, of course, but it's
worth giving it a try."

"Hey, you might be a genius, but what can you do without any beakers or
syringes? You sure can't get them here."

"I'm going to try asking Rikiga-san. He might be able to get his hands
on at least the bare minimum of equipment I'll need."

"The man won't do anything unless it's going to put money in his
pocket," Nezumi said flatly. "You might be the son of a girl he used to
love, but try to get him to do free labour, and he'll turn away as fast
as anything."

"You think so?" Shion said dubiously. "---But we'll still need a serum.
Yeah, I'll tell him if it goes well, he could make some money off of it.
I'll convince him someh---"

Nezumi's foot moved. Shion, chair and all, went flying across the floor.
A pile of books collapsed. The mice darted away.

"What was that for?" He tried to get up. Before Shion could move,
Nezumi's knee was on his chest, and his hand was holding his shoulder
down.

"Shion." Looking down into Shion's face from above as he lay on his
back, Nezumi moved his fingers from Shion's shoulder to his throat.
Through the leather of his gloves, Shion could feel the sensation of
five fingers at his neck. They tightened their grip slowly.

"Aren't you gonna resist?"

"No. It wouldn't be any use. You'd agree," Shion said calmly.

"Giving up pretty easily, huh? Don't you care about your life?"

"Of course I do."

"Or are you thinking that I'd never kill you?"

"Yeah."

Nezumi smiled. His grey eyes, his thin lips, and well-shaped nose formed
a beautiful but cruel and pitiless smile.

"Don't think too highly of yourself," he said softly. A knife appeared
in Nezumi's hand as if by magic. "I remember doing something like this
four years ago too. I was holding you down like this on your bed."

"I remember too," Shion said. "That time, I was the one that went
lunging at you. You dodged it like it was nothing, and then the next
moment, you were pinning me down and I couldn't even move."

That stormy night. He remembered the wind howling outside his window. He
remembered the sensation of Nezumi's skinny body, feverish and hot. It
had been four years since then.

\emph{It's been four years, and I still have neither skill nor the heart to
push this body aside.}

"That time, I was holding a spoon. And I said--- do you remember? --- that
if this was a knife, you'd be dead."

"Yeah."

"Wanna give it a try?" His fingers moved away from Shion's throat. In
their place, the blade of a knife was pushed under his chin. It was
cold. Shion felt a prick of pain.

"I won't let you make a blood serum," Nezumi whispered. "I didn't save
you so you could go around doing something like that. Keep your nose out
of things you have no business in. Stay holed up here until the time
comes."

"'Til the time comes? When's that gonna be?"

"When I strike No. 6 with its fatal blow, that's when."

"When you strike No. 6\el "

"Yeah. I'm going to choke its last breath out of it."

The weight lifted off Shion's chest. Nezumi put away his knife, and
wiped the cruel smile off his face. He pulled a glove off, and stroked
Shion under the chin with his bare finger. A small red smudge came off
on his fingertip.

"This is your blood. Don't even think of doing something foolish like
making a serum. Put it to better use."

"Nezumi." Shion grabbed his wrist. "Why do you loathe No. 6 so much?"

There was no answer.

"What happened between you and No. 6? Why do you have so much hatred for
it?"

Nezumi exhaled shortly. The muscles of his wrist flexed.

"Shion, do you still not understand what kind of place No. 6 is? It
sucks the nutrients from the places around it, and while they grow lean,
it only become more engorged. It's a hideous---"

"Parasite City."

"Yeah. So you do know what I'm talking about. Humankind is becoming more
and more intent on expelling parasitic organisms. What I'm doing is the
same thing. I'm going to exterminate and wipe No. 6 off the face of the
earth. Once that place is gone, the people here won't have to live in a
garbage can anymore."

"But what I want to hear is your personal reason," Shion persisted.

"I don't have one."

"You're lying. You're the one who told me only to fight for myself."

Nezumi fell silent, and shrugged his shoulders.

"Is it revenge?"

Silence. Nezumi didn't even bother to shake Shion's wrist off, and gazed
at him as they stood face-to-face.

"Do you want revenge on No. 6? If you do--- then what happened?"

"I don't need to tell you."

"I want to hear it." Shion clenched his fingers around Nezumi's wrist.
"I want to know, Nezumi."

Suddenly, Nezumi started laughing. It sounded like a laugh that was
genuinely full of mirth.

"Geez, you're like a brat throwing a tantrum. Alright, Shion."

"Mm-hmm?"

"If I tell you, would you co-operate with me?"

"Huh?"

"Would you aid me as I stab a knife into the heart of the city you were
born and raised in? Would you help me bring destruction--- not salvation---
unto that city? I don't need any blood serum. If parasite wasps do
exist, then I'll use them. I want to wreak havoc on No. 6 from the
inside. I want to watch as the people that have always lived in safety
fall into a panic, flee in confusion, and lead themselves to
destruction. That's the kind of thing I have in mind. Will you aid me,
Shion?"

Shion shook his head from side to side. He dropped his gaze from the
pair of grey eyes.

"I can't do that."

Shion's fingers were shaken off.

"You're always like that," Nezumi spat. "You babble on about how you
want to know, but you're never prepared to handle it. To know means to
be prepared to know. Once you find out the truth, there's no going back.
You can't ever go back to being the way you were, blissful and
unconcerned. Why can't you understand that? ---Shion, let me ask another
question."

Nezumi squatted, and hooked a finger under Shion's chin.

"Me, or No. 6 --- which one do you choose?"

Shion's breath caught in his throat. He knew he would be faced with this
decision one day. He had felt it coming.

Which would he choose? If he chose one, he would lose the other. He
didn't want to go back to No. 6. In that sense, he had no attachments
whatsoever left for that city. But with people, it was different. His
mother, and Safu, who was off in another city now, and the residents of
Lost Town were all within those walls. Within those walls were familiar
scenery and fond memories.

If Nezumi harboured hatred toward the entirety of No. 6, its people,
scenery, memories and all, then he couldn't sympathize with that hatred.

Nezumi's fingers withdrew from his chin.

"You love No. 6, and I hate it. That's why--- one day, we're going to be
enemies."

It was a murmur. A murmur that stabbed at his heart.

"I have a feeling that we will," Nezumi said quietly.

He had said something similar before. That time, too, Shion had said
that he wanted to know. He had wanted to know how Nezumi grew up. I want
to know about you, he had said. And now he was receiving the same answer
as he did that time. \emph{We're going to be enemies.} But that time, there had
still been laughter in Nezumi's eyes, and his voice had been light with
jest. But now, it was heavy. A darkness hung over the statement, and its
weighty reality sank deeper into Shion. It was Nezumi's honest answer.

\emph{Some day, we'll be enemies.}

Nezumi rose to his feet, and looked up at the clock on the wall.

"Crap, I'm late," he said to himself. "The manager's probably pissed
off." He turned his back to Shion. His voice and his eyes were wiped
clean of any shadow of murderous intent. His grey eyes were bright, and
his tone of voice was casual.

"Nezumi."

"Yes, yes," Nezumi said unconcernedly. "Mama is going to work now.
Little lamb, you are in charge of the house while I'm gone. A scary wolf
is going to come by, but whatever you do, you aren't allowed to open the
door. Okay?"

"Don't underestimate me," Shion said quietly.

Nezumi's expression hardened. He drew his chin back a little, and
knitted his brow.

"What did you just say?"

"I said, don't underestimate me too much."

"Are you offended because I called you a little lamb? Then why don't I
give you the role of the Little Red Riding Hood? Cute and innocent Red
Riding Hood. Oblivious to doubts and caution, she ends up being eaten by
the wolf. A perfect role for you."

\emph{I'm not going be provoked. You can condescend me all you like. But I
have something I need to tell you.}

"Sometimes there are things I can see that you can't."

"I don't understand what you're saying," Nezumi said bluntly. "Oh wait,
that's supposed to be your usual line, right?"

"You put everything into dichotomies," Shion continued, ignoring
Nezumi's comment. "You either love or you hate. You're either friends or
enemies. Outside the wall, or inside the wall. And you always say you
can only ever choose one of them."

"Of course. If I stood there at the fork in the road wasting time trying
to decide what to do, I'd wither away. That's what cowards and traitors
do. You can't run away forever. Some day you'll have to choose one over
the other."

"Don't you think that there could be a third way?"

"Third way?"

"Yeah."

"Shion, what you're saying is incomprehensible," Nezumi said irritably.
"What 'third way'?"

"Instead of destroying No. 6, what if you made it disappear? Don't you
ever think about that?"

Nezumi put a hand to his cheek, and took a deep breath. He was
restraining himself from letting it show on his face, but Shion could
tell he was agitated. Shion took a step forward.

"Tear the walls down. Get rid of them."

"You mean No. 6's barriers?"

"Yeah. Without its walls, No. 6 as a place will no longer exist.
Everyone will be able to come and go freely. Take away the walls and
gates. Then there will be nothing dividing No. 6 and the Blocks from
each other, and---"

Nezumi burst out laughing. He bent over, holding his stomach. His hollow
laughter echoed in the basement room. The mice huddled together
fearfully and curled up into balls, making them smaller yet.

"Is it that funny to you?" Shion said tensely.

"It's hilarious. It's so funny, it's bringing me to tears. You're not
just a little airheaded, are you? Do you also have delusionary
tendencies? What \emph{third way}, huh? Those are just pretty words, an
unrealistic fairy tale."

"Nezumi, I was serious when I said---"

"I'll have none of it." There was not a remnant of a smile left in his
face as Nezumi said those words. "We can't have that place disappear so
easily just yet. We have to let it keep being the way it is, let it
dress itself up and eat a bellyful of good food, let it grow fat. I can
just imagine how great it must feel to slice that belly open with one
blow. I'm going to pull out all of its gorged innards and expose it to
the light. I can't wait. Yeah, spring is going to be great. I'm quite
excited."

Shion lifted his chin, and clenched both hands into fists at his sides.

"I don't care if you laugh at me, I still think it can be done," he said
defiantly. "I want to believe that it's possible."

"You're just looking for an escape route," Nezumi shot back. "You're
looking for a way to avoid getting hurt. Say if you do get rid of the
walls: you won't get any kind of heaven. It'll be hell. Tumult,
disorder, fighting, looting--- you don't know how much these people have
been oppressed until now. You don't know how many people have been
sacrificed so that city can be where it is. You don't know, and that's
why you can spin fairy tales like that. Shion, it can't be done. It's
not like mixing paint, you can't mingle them together and make them one.
Either one will have to destroy the other, that's the only solution.
That's what fate has set out. Love and hatred, friends and enemies,
those within and those outside the wall--- and you and I. They can never
be as one, and neither can we."

"You don't know until you try. For one thing\el "

"For one thing?"

"---I know I wouldn't become your enemy. Ever. No matter what happens,
even if I'm killed, I would be on your side."

"Just pretty words."

"It's my resolve."

It was his will, and it was unwavering. In order to know, you had to try
it first. He believed that human souls, when faced with a dilemma, would
ultimately choose peace over war, songs and scriptures over weapons, and
love over hatred. It wasn't a fantasy. It was hope. \emph{I still haven't
abandoned hope. I want to find a road that you can't see, and point it
out for you.}

Nezumi averted his gaze. He kicked the chair leg with the tip of his
shoe.

"It pisses the hell out of me sometimes, when I'm with you. Your head's
full of naive and idealistic theories, and you talk as if you're
actually serious about them."

"You wouldn't listen if I wasn't serious about it."

"That's enough," said Nezumi curtly. "Just shut up." He began working at
setting upright the chair that he had kicked over, and lightly thumped
the faded cushion seat. "An idealistic armchair theorist like you should
just sit here all day long. Ignore the world outside, and mull over this
and that all inside your head. Don't talk to me anymore. Don't make me
any angrier than this."

"Nezumi---" Shion began.

"I don't want to hear it. Listening to you makes me sick. Sick and
tired. Damnit, if I knew you were such a chatterbox, I would never have
brought you here in the first place."

"I'm not a chatterbox. I actually don't like speaking to people much."

"Then all the more reason for you to shut up."

\emph{But I can't just shut up. I can't sit here, close myself off in my own
world and sever myself from the world outside. I have to talk to you,
listen to your story, and search for a way that we can go on living
together.}

\emph{I don't want to live like this anymore--- plugging my ears, keeping my
mouth shut, closing my eyes. Nezumi, you were the one that made me feel
that way. Pry your hands away from your ears, you said, open your mouth,
and will your eyes to see. Those were your words. And now you're telling
me to shut up? You're telling me you don't want to hear it?}

"Who's the coward now?" He muttered out loud without thinking. Nezumi's
expression hardened.

"What did you say?"

\emph{Is this gonna end in a fight?} The thought flitted in a corner of his
mind. Then he decided he wouldn't mind if it did. Nezumi would probably
easily wrestle him to the ground. Four years ago, and even now, this
hadn't changed. Shion had no chance against him. But it wasn't about
winning or losing.

He wanted to charge at Nezumi with his own body, his own flesh. He
wouldn't mind if he were to be pushed to the ground, punched, or pinned
so that he couldn't breathe. If even for a moment, he wanted to collide
with Nezumi as equals.

But Nezumi averted his gaze again. He made for the door without even
looking at Shion. But before Nezumi's hand closed around the doorknob,
there came a muffled scratching sound from outside. Something was
tearing at the door. A moment later, there was a bark. Nezumi and Shion
looked at each other.

"Sounds like a dog."

Nezumi opened the door. A large, dark brown dog was sitting in the
doorway, wagging its tail. It had a white parcel in its mouth.

"You're from Inukashi's---something happen to him?" Nezumi retrieved the
package from the dog's mouth. It was a letter. Nezumi read it, and the
corners of his mouth relaxed.

"Shion, there's a job request for you."

Shion ran his eyes through the letter that was passed to him. It was
nearly illegible. The paper itself was yellowed, old, and wet with dog
saliva, and the handwriting meandered all over the place. But it
thrilled Shion's heart more than any other letter he had received.

\memo{\inukashi}{
	hey shion, feel like working? Its a dog-washing job.\\
	i need some help. If you wanna do it, follow this guy.\\
	As long as hes with you, the Disposers wont do\\
	anything funny. see ya\\
	Oh PS: this guy said your made for dog-washing.}

"What's dog-washing?"

"It's just how it reads. You wash dogs--- the ones that Inukashi lends out
for heating. They're the big, quiet ones with long fur. There must be
about twenty of them altogether. He gets customers sometimes that don't
pay because they complain the dogs are smelly or have fleas, so once a
week on a sunny day he takes them out for a wash. So what are you gonna
do?"

"I'll go, of course," Shion glowed. "He's asking me if I want to come
work. It's my first job. I actually have a job now."

"Will you stop gushing?" Nezumi said with a grimace. "Man, you really
are easy to please, aren't you?"

"Nezumi, should I take anything with me? Do you think I'll need soap?"

"You probably won't need anything. Just beware of men and women who
might pull you into alleyways, I guess. If that dog is with you, I don't
think you need to worry. I'll go with you partway."

"Speaking of which, I do want to see your workplace one day. And see you
on the stage."

"Don't get your hopes up."

The dog barked.

"Thank you," Shion told him. "Thanks to you, I've been able to get my
hands on my first job. I'm all yours, take me there."

The dog wagged its tail as Shion crouched down toward it, and licked him
under the chin.

"You're licking my wound for me? You're a nice boy."

"Dumbass, he only licked it because he smelled blood."

"I don't think so. He did it because he was concerned about me. But
whatever the reason, he's certainly nicer than you," Shion said wryly.

"Don't compare me with a mutt," Nezumi said sullenly. He looked
genuinely disgruntled. The way he stuck his lip out brought back a
fleeting image of his face four years ago. It somehow made Shion want to
laugh, and for some reason, made him feel nostalgic.

"What?" Nezumi said. "What're you grinning about?"

"Nothing," Shion said mildly. "Just noticing you've still got a childish
part left in you. It made me kind of happy."

"Huh?"

"Never mind. Alright, then," he said briskly, "lead the way." He petted
the dog lightly on the back. Picking up the cue, the dog bounded up the
stairs. Shion followed after it and exited the basement room.

The sun was bright in his eyes.\emph{ I see--- a day like this would be perfect
for washing dogs.} He tilted his face up to the sky and breathed in
deeply.

\mybreak

It looked like Shion's figure was being sucked into the light. Whenever
Nezumi crawled out of his dark hole, the light always stabbed at his
eyes. He didn't like bright places. Places filled with light always
turned easily into areas of danger. He knew this well from experience.
He couldn't be like Shion and fully accept the light without hesitation.

Friends and enemies. Outside the wall, and inside the wall. Love and
hatred. Light and dark.

\emph{I told you, didn't I? They can never co-exist. I've told you so many
times, and you still don't seem to get it.}

He swallowed a sigh that was halfway up his throat. The lump sank deep
down into his chest again.

As Nezumi was about to lock the door, a mouse came rubbing itself
against his foot.

"You're back." He scooped it up in his hand. The mouse seemed exhausted.
Its grape-coloured eyes were bleary.

"You've worked hard. Rest up." The mouse shook its head, and spat a
capsule onto Nezumi's palm. There was a light blue piece of paper
inside.

"A reply, huh." If it was, Shion would rejoice. Today must be a lucky
day for letters.

Just for an instant, a blackness flitted across his heart. A black
thing. It had no form--- it was only dark. Uncertainty, a bad premonition.
A dull pain throbbed in the back of his head.

His ability to smell impending danger or calamity was something he had
had since birth. Thanks to this ability, he had been able to escape
numerous times, in some instances by a mere hair. The contents of this
capsule carried a bad smell. It smelled like the first step toward
something that would chase him into destruction\el 

He opened the capsule. The paper was scribbled with what looked like
Karan's handwriting.

\memo{\karan}{
	Safu was taken away by the Security Bureau.\\
	Help. -K}

The pain got worse. Nezumi screwed his eyes shut, and leaned heavily
against the door.

Safu--- it was that girl. \emph{Why was she--- wasn't she an elite? Just like
Shion\el just like Shion\el which means--- she was taken in place of him?
The second scapegoat?} But he didn't know for what reason. \emph{Why do they
need a sacrifice? Shion was framed as a murderer to cover up what the
parasite wasp did. They should only need one perpetrator. So why--- why
did the authorities want another sacrifice? Why---}

\emph{Either way, if that girl is the second sacrifice, she hasn't been taken
to the Security Bureau. She's headed for the Correctional Facility. A
mouse takes half a day to get back from No. 6. There's no more time.
She's probably been imprisoned in the Correctional Facility already.}

Why were they eliminating so easily a Gifted Curriculum student that
they had measured, carefully selected, and spent considerable funds and
time to raise?

\emph{Why? Why--- what was going on? What are they hiding? What's about to
happen?}

Nezumi slowly brought himself upright.

He didn't know. It was a mystery. But now was not the time to be solving
puzzles. He had an important decision to make.

\emph{What to do with this?}

If he showed this scribbled note to Shion, he would probably head right
for the Correctional Facility, without even knowing what kind of place
it was. He would go, with the single intention of rescuing Safu. A
sheltered simpleton of a little boy like him would never be able to let
a friend's death go unheeded. If he could prevent it, it was reason
enough for him to go diving head-first into a nest of venomous snakes.
He would willingly embark to his own death.

\emph{Or do I crush it?}

It was very easy to do. This girl, Safu, had nothing to do with Nezumi.
She was a stranger. It wasn't any of his business what should happen to
her. He could leave things be, and it wouldn't matter. Nothing would
change.

But if Shion died, something within him would change greatly. He didn't
want to see Shion die. He would probably suffer. Not Shion, but he---
Nezumi--- would suffer, from having to live and stand before Shion's
corpse. He would be experiencing the same suffering again, of being
broiled alive in hellfire.

\emph{You've gotta be kidding me. I've had enough of this already.}

He didn't want to lose him. He didn't want to experience the remorse of
having been the one that lived.

\emph{I don't want to lose him? I would suffer?}

He was clicking his tongue in frustration.

So this was what he had come to. He almost felt like curling up on the
ground.

He had rescued Shion from the hands of the Security Bureau to return the
debt that he owed him. That was it. He never wished to be attached to
him. Shion wasn't the only one--- he had never wished to be attached or to
share his heart with any other person. Feelings for others were even
more dangerous than the light. He was not to share a connection with
anyone. Whether it be with a man or a woman, he was only to develop
relationships that could be severed easily.

\emph{Never open your heart to anyone. Don't believe in anyone but yourself.}

The last words of the old woman. He was turning against them again.

\emph{I don't want to lose him. I would suffer.}

Nezumi carefully folded Karan's memo again and stuffed it inside the
capsule.

He was used to loss, he was used to suffering. Wasn't he? Even if Shion
did die, perhaps he wouldn't moan in agony over his gaping loss. Even if
he did, perhaps it would only be for a short while.

He would be able to use his bed and shower freely. He wouldn't have to
worry about making enough soup. He wouldn't be pelted incessantly with
questions, or be spoken to. He would be released from having to look up
halfway through a book to lend an ear to the other's words, and to give
an answer while trying to restrain his irritation.

He would go back to his normal life. That was it. He should just pass
the memo, capsule and all, to Shion, and then turn his back on him.

On a whim, Nezumi opened his door again.

Before him was his room, filled with books and sparse furniture. The
basement chamber, surrounded by thick walls, was a nest that suited a
rat like him well.

The room looked barren and dark, and larger than usual. Its coldness,
darkness and vacant space seeped into his bones.

That was what being attached to someone meant. He would no longer be
able to live alone anymore. It was one of many artfully-set traps that
lurked at every corner of his life. And to this one, he had fallen
victim.

\emph{Have I still got a chance?}

"Nezumi, what's wrong?" Shion called from the top of the stairs, the
entrance that led to ground-level. "The dog's pulling at me. Hurry and
come on up." His shadowy figure floated up against the glare of noon.

Have I still got a chance? Shion, will I still be able to live without
you? After some amount of suffering, would I be able to detach myself
from the trap you've become?

\emph{Would I be able to sever you?}

"Nezumi?" The voice from above dropped apprehensively.

"Nothing--- I'm coming." He closed the door. He heard the dog bark. There
was light. The rustle of a breeze.

Nezumi wrapped the superfibre cloth around his neck again, and ascended
the stairs step by step. He kept ascending to the ground above.