% !TeX spellcheck = en_US

\chapter{The beautiful ones...}

\myepigraph{Away, and mock the time with fairest show:\\
	False face must hide what the false heart doth know.}{\emph{Macbeth} Act I Scene VII}

\lettrine{T}{he sky} was blue and bright. The sun's rays, approaching noon, were
gentle and warm. It was a temperate afternoon that made the frigidness
of a few days ago seem like a dream.

Shion lifted his face, and narrowed his eyes as he looked up at the
azure sky.

He thought it was beautiful.

The sky was beautiful. The blinding whiteness of the crumbled ruin as it
reflected the sunlight was beautiful. The odd bubble that floated up as
if by magic from the soapsuds was beautiful. The sheen on the fur of a
freshly-washed dog was beautiful.

All the little things that surrounded him were beautiful. A lone bubble
floated up again and drifted on the gentle breeze.

"Hey, stop slacking off," Inukashi's voice called over to him. "There
are still tons of dogs left. Space out every other minute like that, and
the sun's gonna set before you're even halfway through."

As if in agreement with Inukashi's reprimand, a large white dog covered
in suds gave a low growl.

"Oops, sorry."

Shion stuck his hands back into the suds and washed the dog thoroughly
with his fingertips. The dog evidently found it very pleasing, for its
eyes were closed and its mouth lolled half-open. Today was only Shion's
second time at his dog-washing job, but already he had learned that dogs
had many different facial expressions. They also varied in personality
and tendency: some were lazy, others diligent; some high-strung, others
laid-back; they could be mild, impatient, rambunctious--- all of this was
new to him.

The white dog that he was washing now was a female that was quite old.
It was gentle and intelligent, and reminded him of the wise old woman
that often appeared in tales.

"Shion, you're spending way too much time on each dog. How long is it
taking you to wash just one?" Inukashi, with his long hair tied at the
back and soapsuds on his nose, pulled a face at him.

"You lend these dogs out to serve as blankets, don't you?" Shion
answered. "They need to be cleaned properly, then."

"A quick wash is good enough. The customers are all like dirty strays
anyway, the bastards."

In a building mostly reduced to rubble, there was a part that still
somewhat retained a semblance of the hotel that it used to be. Inukashi
lent space there as overnight accommodation for those who had nowhere to
stay. He lent out dogs in preparation for the coming winter. Boarders
spent the night buried amongst several dogs, and by doing so were able
to avoid freezing to death. Shion had been hired to wash these dogs.

"Inukashi, I don't think that's a nice thing to say about your
customers."

"Huh? What'd you say?"

"It's not good to call your customers bastards, or call them dirty."

Inukashi rubbed his nose with the back of his hand, and gave a small
sneeze.

"Are you my Mum or what, Shion?"

"No. I've been hired by you to wash your dogs."

"Then that makes me the employer and you the employee. And your job is
to shut up and do what you're told."

Inukashi yanked the white dog out of Shion's hands, and began vigorously
rinsing the dog by dumping water over it, which he had drawn from the
stream.

At the back of the ruins, there ran a small, clear river. Not long after
Shion had escaped from No. 6 to this West Block, he had nearly died from
a parasite wasp that had planted itself in his body. Although he was
unconscious most of the time from severe pain and high fever, he still
remembered clearly the taste of the cold, delicious water that had slid
down his throat numerous times.

When he had thanked Nezumi for giving him water and treating him, he had
gotten a gruff answer that there was a decent spring nearby. Perhaps
this stream originated from that spring.

"Inukashi, don't do that. All the soap is getting into the river." Shion
hastily restrained Inukashi's hands. Soapsuds bobbed on the stream as
they drifted away from them.

"So what?"

"Everyone drinks from this stream, don't they?"

"Well, yeah, of course. We don't have any fancy facilities that give you
sanitized and temperature-controlled water at the push of a button.
Everyone draws water directly from the river or spring."

"Then you can't get it dirty. It's bad for the people downstream."

Inukashi stared into Shion's face for a brief moment.

"And why should I care about the people downstream?"

"Well, I mean\el " Shion faltered. "If you know that the people
downstream are going to be drinking from here, you wouldn't want to make
it dirty for them. That's normal, right?"

"Normal? By whose standards are we talking about, Shion? This is the
West Block. You wouldn't be able to survive here if you went around
putting everyone else first."

"Yeah, but there's no need to go out of the way to make it dirty," Shion
protested. "We can do what we did yesterday, and put water in steel
drums and wash the dogs there."

"Yesterday we only had small dogs. FYI, Shion, we were supposed to get
through all the dogs yesterday. You taking your sweet time is costing
us. You understand that, right?"

"Yeah."

"Not only are you horribly slow, the dogs we're washing today are all
big. And that's not it--- wait for it--- \emph{there are shitloads of them}. Are
you getting the picture? If we drew a bath each and every single time,
it would take forever."

Then Inukashi stopped, and shrugged slightly.

"But if you wanna draw water from the river on your own, I'm not gonna
get in your way."

"Fine. I'll do it."

"It's heavy labour, man."

"I know."

"By the way, I'm only paying you to wash the dogs. Carrying the water is
something you're doing entirely on your own."

"I don't mind."

"Well then, get cracking. I'm gonna have lunch."

The white dog shook itself vigorously, and water droplets flew in all
directions. Shion grabbed the pail that Inukashi had tossed at him, and
drew a pailful of water from the river.

"Shion," Inukashi said abruptly.

"Hm?"

"Why?"

"Why what?"

"Why shouldn't I badmouth my customers? Why do I have to bother about
the people downstream?"

Shion looked up into Inukashi's tan face as he sat perched atop a pile
of rubble.

"Because we're the same."

"Same?"

"They're the same humans as us. So---"

Inukashi suddenly threw his head back and laughed. His voice rang out
and was sucked into the bright blue sky. Several dogs began barking in
agitation.

"Same humans, huh? Ha ha, you nearly bowled me over. I've never heard
those words before in my life. Shion, is that honestly what you think?"

"Yeah, is there a problem?" Shion said stoutly.

Inukashi leapt down from the rubble and drew up to him. He had a small
frame, and only reached up to around Shion's shoulders in height. His
thin arms and legs protruded from his black clothes, and his skin was
the shade of tanned leather.

"So my filthy customers, and the brats that come here to draw water are
the same humans as us?"

"Yeah."

"Are you and I the same humans?"

"Yeah."

Inukashi lifted his arm and extended it upwards to the noon sun above.

"Are the people of No. 6 the same humans as us?"

Shion nodded slowly, and answered.

"Yeah."

Inukashi's smooth, tan skin glowed in the sunlight, and his long bangs
cast a shadow over his forehead and eyes. Under its veil, the same
tan-brown eyes blinked a few times at him.

"Shion, you're gonna die."

"Huh?"

"Is your head up in the clouds or something? If you keep
believing in that fantasy of yours, you'll never survive here."

"Nezumi tells me the same thing," Shion said. "That I've got my head up
in the clouds."

"The clouds wouldn't be high enough, actually. Your head must be in
space, or something. I don't know what space is supposed to be like, but
it's really high up, right? And sometimes you burn up, just like that,
before you even get there."

"I've never been to space, but yeah, I guess it is really high up."

Inukashi climbed nimbly up the ruins, and sat down with the blue sky at
his back. He dangled his legs over the edge, and spoke quietly as if to
himself.

"I wonder why Nezumi even puts up with you. He hates people that are all
talk, and unrealistic."

"Inukashi, are you close with Nezumi?"

"Close? What do you mean by close?"

Shion heaved the pail up the path of withered grass and rubble, and
dumped the water into the steel drum.

"It means you know a lot about each other."

"Oh, if that's the case, then no. I know less than the tip of that guy's
tail, and I wouldn't want to know." As he spoke, Inukashi pointed at the
light brown puppy that was tumbling about at Shion's feet. Its tail was
tipped with white.

"I thought you were friends, but I guess I was wrong\el "

"Friends!" Inukashi exclaimed incredulously. "There's another word I
don't hear often. Friends. Hah, ridiculous. Nezumi only comes here when
he wants information that me or my dogs have collected. I give him
information, and he gives me money. That's it, that's everything."

Inukashi fell silent. His gaze wandered, collided with Shion's, and slid
away.

"It's not just information and money that you guys trade," Shion said. A
statement, not a question.

"Uh--- well, once in a while, he--- sings for me."

"Sings?"

"He has a good voice. So I\el I get him to sing. Sometimes when my dogs
die--- it's alright when you wake up and they're already dead, but---
sometimes, they're sick or hurt, and don't die as easily, and they\el 
they suffer. It hurts them so much, they whimper all night long. That's
when I get him to sing. I don't know what the song's called. But it--- I
don't know how to describe it--- I dunno, what would it be?" Inukashi
murmured to himself.

"What does it sound like?"

"Huh?"

"Nezumi's song. Nezumi's voice. If you were to compare it to something,
what would it be?"

Inukashi tilted his head to the side, and pondered in silence. Shion
also silently continued carrying pailfuls of water. He made several
trips between the river and the steel drum, and when more than half of
it had been filled, Inukashi opened his mouth again.

"The wind, maybe\el ?" he said hesitantly. "A wind that comes blowing
from far away\el yeah, his song steals away souls that are struggling
because they can't die. Just like how the wind scatters flower petals,
his song cuts the soul away from the body. Any dog, no matter how much
he's suffering, closes his eyes and becomes quiet. You think he's just
settled down, but he's actually not breathing. They all die quietly,
like all their suffering was just a dream or something." He paused. "It
was like that with my Mum, too."

"Your mother's passed away?"

"Yeah. She got killed by a couple of brats that live downstream, the
ones you said I shouldn't make the water dirty for. She got rocks thrown
at her, and was clubbed to death with an oak stick. But my Mum was at
fault for that, too. She tried to steal their only supper. She snuck
into their hut, and got caught holding their dried meat in her mouth.
When she finally got away and managed to come back, both her front legs
and ribs were broken, and she was bleeding from her mouth. There was
nothing we could do."

Having finished filling the drum with water, Shion wiped the sweat off
his brow. He couldn't understand Inukashi's words.

"Inukashi, by front legs\el you mean your mother's, right?"

"Yeah. She's a dog."

"A dog?"

Shion could feel his jaw drop. Inukashi looked at him and gave a laugh.
His voice was high and rang out clearly into the air.

"I was dumped here when I was still a baby," he explained. "The old man
that picked me up was a weirdo who lived here with his dogs, and he
raised me together with them. My Mum gave me milk. She licked me, and
curled up with me to sleep. When it got cold, she huddled close to me
and my siblings--- her puppies--- and kept us warm. She always used to say,
you poor thing, you have no fur--- but at least you're cool in the summer,
and you don't get fleas. She'd tell me that over and over again, and
lick me until I was clean."

"She must have been a great mother," Shion said softly. "Gentle and
caring."

Inukashi blinked several times.

"You really think so, Shion?"

"I do. She cherished you. Since you didn't have fur, she protected you
and made sure you didn't freeze."

"Yeah. Mum was always really nice. I still remember how her tongue felt.
It was warm, and wet\el funny, I can never seem to forget about it."

"It's a gift of memory."

"Huh?"

"It's a gift of memory from mother to son. Memories that your mother's
left behind for you."

Inukashi stopped dangling his legs, and drew his chin back.

"I've never thought of it like that\el " he said pensively. "A gift of
memory, huh\el "

Shion knelt at the river's edge and sipped a mouthful of water.

It was cold. It soaked through his entire body, and it was delicious.

\emph{Ah yes, it's this water.}

It was the water that had quenched his exhausted body like an elixir
after his battle with the parasite wasp. Not only his body--- it was from
the moment the water had slid down his throat and he had found it
delicious, that Shion's entire being was revived again. He believed it
so.

This water was connected to what it meant to be alive. This coldness,
this deliciousness. It was connected to the voice that called to him,
telling him, \emph{don't die, live, come crawling back up again.}

That was why he would remember it forever. There was no way he could
forget it. Deep within Shion, this water and that voice had set its
roots down, and would continue to thrive, never to wither. And at times,
it would float to the surface of his conscious, and each time, it would
whisper to him.

\emph{Don't die. Live. Come crawling back up again.}

It was a gift of memory, indeed.

"I'll bring ya some lunch." Inukashi stood atop the rubble, and spoke in
a tone that sounded more like a command. "You better be finished with
that black one by the time I get back. I won't let you have it until
you're finished."

"Wow, I even get lunch? That's nice of you."

"I don't just serve this to anyone, you know. It's a full-course meal.
And by full I mean two: bread and dried fruit."

"That's more than enough."

Running a brush through the black dog's fur, Shion grinned at Inukashi.
Months had passed since escaping to the West Block, and chronic hunger
gnawed at Shion persistently. At times he wished he could eat his fill
of dishes with plenty of meat, fish, and eggs, and he yearned for the
bread and cakes that his mother Karan baked. But in contrast, things
that he had never even acknowledged as food before--- soup made with bits
and ends of vegetables, and bread that was beginning to mould--- made his
mouth water, and satiated his appetite.

\emph{Being able to eat is enough.}

Here, everyone was starving. They starved, froze, and passed away. Shion
knew in his own way how precious the single slice of bread was that
Inukashi was about to give him.

He looked up to the sky. The sun was bright. This light was also shining
down on No. 6. His former workplace at the Forest Park, the high-end
residential area of Chronos, Lost Town, where his mother lived, and
here, West Block, were bathed in the same light. But things were so
different. Too different.

Divided by a wall of special alloy, prosperity and poverty stood in
opposition to each other. Life and death. Light and dark. At the same
hour that an extravagant party was being hosted in the interior of No.
6, while people smacked their lips at the numerous elaborate and
delectable dishes, in a corner of the West Block, an elderly person clad
in rags would starve to death. While the boys and girls of No. 6 would
crawl into their beds in their air-conditioned rooms, the children in
the barracks of the West Block would huddle close to each other to avoid
freezing to death.

It was the truth that Shion had seen with his eyes. There were far too
few things which were like the sunlight, equally and amply distributed
among all.

"Get working, then," Inukashi spat, and disappeared in the shadows of
the ruin.

\myspace

All that remained of the entranceway, which had probably once been
flanked by thick, wooden doors, were pairs of rusted hinges. Every time
the wind blew in, their screeching noise assaulted the ears. Inukashi
passed through that entrance to climb the stairs to the second floor.
Some sort of architectural consideration had left this particular part
of the building, which used to be a hotel, withstanding against the
elements. Durable though it was, plaster still peeled from the walls,
and the hallways and ceilings were webbed with countless cracks.

Buildings too possessed a life. From the moment they were abandoned,
buildings began to decay. They began to die. This hotel, which had
become a ruin, continued crumbling and decaying still. It marched
steadily toward destruction, neither loathing the heartlessness of its
human owners, nor lamenting its fate.

Inukashi occasionally wondered what he would do once this building had
completely collapsed into rubble.

The old man that had picked him up, given him dog's milk, and taught him
speech and the written word was no longer here. He had wandered outside
one snowy day, never to return again.

\emph{Snow? Was it snowing? Maybe it was thundering that day. Or it might have
been a morning with chapped winds\el either way, the old man
disappeared. He vanished, without even leaving any words of farewell.}

He wasn't lonely, because he had his dogs. From that day until now, he
had lived here with them. He knew no other home. He also knew of no
other human company. Nezumi was probably the same. He may have been to
more places than Inukashi, but he probably lived alone, not knowing
anyone else, nor ever having the need to know. Inukashi had assumed so,
for no particular reason. He had no grounds for his argument, but he
figured he wasn't entirely wrong. Inukashi had a sharp sense of smell.
Nezumi always only carried the smell of loneliness. When that scent
blurred, and Inukashi had begun to notice a mingled scent of another,
Shion had appeared before him.

He was a weirdo. He was very strange. His hair was snowy-white, and he
had a red scar. Though Inukashi wasn't sure, he'd heard that the raised
scar covered Shion's whole body like a coiled snake. But in terms of
appearance, there were tons more people who were weirder than him. His
appearance wasn't the only thing--- Shion was also weird on the inside. He
said not to dirty the water for the brats downstream. \emph{He said the people
inside the Holy City and people like us were the same. And he talked
about the gift of memory. Not as any kind of joke or sarcasm, but in all
seriousness.}

\emph{He was weird. Very weird. Why is Nezumi hanging around a weirdo like
him?}

Inukashi walked down the hall, and opened the door at the very end of
it.

"Nezumi."

Nezumi was sitting in a chair with his feet up on the table.

"Can't you even knock before entering the room?" Inukashi said
irritably. "Someone didn't learn proper manners from Mama. Geez." He
then swung a blow as hard as he could toward the pair of long legs
resting on the table. Nezumi sniffed lightly in derision, and took his
legs off.

"I called out before coming in. That dog gave me permission to enter." A
dog with black patches on its fur was lying in a corner of the room. It
cocked its head to the side, and gave a wide yawn.

"If you're here to pick up Shion, you're early. If he keeps going at
this pace, he probably won't be done 'til evening."

"Pick up? Never."

"But he scuffled with the Disposers, din' he? Isn't it dangerous to let
him walk by himself? I'll send him with a dog on the way home, either
way."

"That's good enough."

"But the Disposers don't give up easily. That guy stands out, and if he
gets caught, who knows what they might do to him."

Nezumi's grey eyes sparkled, and a slight smile played on his lips.

"Does it matter to us what the Disposers do to Shion? What's up,
Inukashi? You're being awfully nice. Not like you at all."

Inukashi glared at Nezumi silently.

The small playhouse was one of the few entertainment facilities in the
West Block. And as one who stood upon its stage, Nezumi made his
audience pay--- or rather, made them want to pay--- out of what little money
they had for a show that provided them no physical nourishment. It was
Nezumi's beautiful countenance and deep, clear voice that made them want
to. His voice laid trapped and dying souls to rest, gently detaching
them from the body. His appearance made it impossible to discern whether
he was male or female, human or demon, God or the Devil. His audience,
in a brief slice of the evening, could forget the day's hardships and
the next day's sorrows, and let themselves be immersed and intoxicated
by his voice.

Once the outside the shabby doors of the playhouse, reality waited for
them--- no money in their pockets; children crying for food at home--- but
despite that, the people's faces were always filled with drunken
contentment as they scattered hither and thither into the darkness.

\emph{It's all an illusion. He's just a big fraud.}

Every time he met with Nezumi, Inukashi mentally spat these words from
the pit of his stomach. Nezumi was like the beautiful mistress who
manipulated men and milked them of all that they were worth. Inukashi
had been through that experience once, too.

\emph{Mum was suffering so much, I didn't know what else to do but to call
him. I asked him to let my Mum's soul go peacefully. That was still
good. His song was impressive, and my Mum was released from suffering.
But what he did before that--- the sheer amount of money he demanded while
my Mum lay there suffering--- it was enough money for me to live a whole
month without working. With other dogs, I would've given up. I would
slit their throat, or smash their skull with my own hands, and let them
die a quick and easy death. But I couldn't do that to my Mum. I could
never do that to her with my own hands. He knew that, and that's why he
demanded that sum. After burying Mum in her grave, me and the dogs had
to work for three days without any food. He's a fraud. He captures
people's souls, clamps down on them, and shows them a fleeting dream. It
might be vivid, but it's still fake. Dreams are dreams. You can't live
on them.}

Inukashi unlocked the cabinet and retrieved the bread and a bag of dried
fruits.

"If you're not here to pick Shion up, what're you here for?"

"Can you treat me to some lunch? I'm starving."

"\emph{You jest,}" Inukashi said in a mocking voice. "I don't have anything
fitting for a star actor like you. But if you pay me one silver coin, I
can give you bread, fruits, and water."

"One silver coin for mouldy bread, rock-hard dried fruits and water from
the stream? That's stretching it, Inukashi."

"Way cheaper than how much it costs for your singing."

Nezumi chuckled softly.

"You still holding a grudge about that?"

"Damn right, I am."

"I sang for your dogs so many times after that. It might as well have
been charity, for the amount I took as payment."

"That's what pisses me off even more. You took advantage of me. I got
gypped out of all the money I had that time. I was this close to
starving to death."

"Well, if that happens again, feel free to call me," Nezumi said
amiably. "I'll sing you a song about food, and see you off."

"Just teeming with compassion, aren't you?" Inukashi retorted. He
hunched his shoulders, and stood directly in front of Nezumi. He posed
his question once more.

"What do you want?"

Nezumi, still deeply seated in the chair, tossed a single coin onto the
table. Inukashi's eyes widened.

"Gold\el " he whispered.

"It's real. See for yourself."

Inukashi pinched the shiny coin between his fingertips, and gazed at it.

"You're right--- it's real. Yeah. It's the real thing."

"I want you to do a job for me," Nezumi said in an expressionless voice.

"Job? A job that's worth a whole gold coin?"

"That's down payment. After the job is done, I'll give you another gold
coin."

"Big spender, aren't you? But I won't take it." Inukashi flung the coin
out onto the table.

"You're going to refuse a job worth two gold coins without even hearing
about it?"

"I'm refusing it \emph{because} it's a job worth two gold coins. I can just
smell the stench."

"Stench?"

"The smell of danger. My nose is warning me--- it's saying, don't go
there, or else you'll get killed. I don't care how much money you're
gonna pile on. If I die, it's all over. Either way, any job that
involves a Rat and is worth two gold coins is like sticking my hand into
a nest of poisonous snakes. I don't wanna die just yet."

"That's why you get the money without dying--- isn't that what doing a job
is all about? Avoiding danger isn't gonna turn you a profit."

"It depends on the level of danger. \emph{All} your jobs are dangerous and
tricky. This is two whole gold coins we're talking about here. If anyone
else came to me with that deal, I'd have taken it in a split second.
Damnit," Inukashi grumbled. "I feel ripped off already."

Nezumi stood up, and pocketed the gold coins.

"That's too bad. I guess it can't be helped."

"No hard feelings. Things are just too risky with you. To be honest, I
don't even wanna have much to do with you."

"Then it's mutual," Nezumi said airily. "Fine. Let's not meddle with
each other anymore. I'll never come to you with a job again. As for you,
no matter how much you suffer, be sure you don't come to me about it."

Inukashi hastily grabbed Nezumi's arm as he turned his back. He had
lunged so suddenly that he almost tripped over himself.

"W-Wait a minute, Nezumi. What do you mean, no matter how much I
suffer?"

"I just told you. If you end up like your mother someday and you're
suffering because you can't die, it won't have anything to do with me.
You can call me, but I won't come."

"What're you going on about\el ?" Inukashi said shakily. "Me, going
through a painful death? That would never happen\el Besides, I'm younger
than you, aren't I? I think so, at least."

Nezumi lazily brushed Inukashi's hand off.

"Inukashi, age doesn't matter in this place. You know that, don't you?
Death can never be predicted. It just comes. And how many people here
are lucky enough to die painlessly, huh? The majority suffer, suffer,
and die writhing. Tomorrow, someone might stab a knife into your
stomach. You might crack your skull open on a falling piece of debris.
You might get bacteria into a wound, have it fester, and rot alive. You
might come down with a serious illness. Can you guarantee that none of
that is going to happen to you? Huh, Inukashi? Can you say with
certainty that you, above all people, will die without suffering?"

The pair of grey eyes bore into him. They had the lustre of fine cloth,
and glowed dimly like the clouds when they shrouded the sun. His voice
reverberated deep in his ears.

Inukashi sucked a breath in, and took a step backwards.

It was a trick. An illusion. \emph{He's trying to suck me in.}

"Suffer all you may because you can't die. I won't get involved. Fine
with you, right?"

Inukashi sank into a chair.

He knew death. He had seen it countless times. Not one of them could be
called decent. That was why--- that was why he wanted to stay alive. He
felt like as long as he survived, he would be able to experience a
more-or-less better death. Although much too insignificant to call it
hope, Inukashi admitted feeling a sort of longing for peaceful death.

\emph{Damnit.}

He gritted his teeth. Nezumi's lips curled thinly into a smile.

\emph{This is a threat. I can easily turn Nezumi down now. But after that, if
I were to get into the same fix as Mum did--- my bones broken, my insides
crushed, blood spurting from my mouth--- and I had to die that way\el If
there was nothing to ease my pain, numb it even just a little--- if I had
no choice but to moan and plead for someone to kill me, quickly, please,
until death came to claim me---} Just thinking about it sent a chill down
his spine. He broke into a sweat.

"Sit down," Inukashi uttered weakly. "I'll listen to what you have to
say, first."

Nezumi's gloved hand extended toward him and caressed his cheek.

"Good boy."

"Fuck you."

Inukashi glared at the face that still smiled wanly at him. "Lemme tell
you something, Nezumi. Don't think this shebang is gonna work every
time."

"Shebang? I only want you to do a job for me. A rude way to treat a
customer, don't you think, Inukashi?"

"Is this your idea of a decent customer? Taking advantage of someone's
weakness, threatening him, and then forcing a dangerous job on him? I
think even fleas are a little nicer to the dogs they infest, compared to
you."

"Wouldn't you say," Nezumi said, "that the fault lies with that person
for having a weakness that can be taken advantage of in the first place?
In these parts, exposing your weakness can cost you your life. Not news
to you, I hope?"

Nezumi once more gently stroked Inukashi's cheek as he fell silent, and
murmured sympathetically.

"You're afraid of death. More than anything, you're afraid of the
suffering that leads up to it. You'd do anything to be spared from it. I
know that, and I'm able to ease that pain for you, am I not? I don't
want to blackmail and wring things out of you. I'm taking the proper
steps, paying you money in exchange for a job."

"That's enough!" Inukashi slammed the table with his fist. Two puppies
that were playing under the table shot out from under it and fled.

"You fraud, you sophist, you third-rate actor! I hope you choke on rat
poison and die." Out of breath, Inukashi inhaled raggedly.

"Are you finished?" Nezumi said momentarily. His calm and unruffled tone
further stirred Inukashi's wrath. But it was no use getting irritated.
Nezumi was right. He was at fault for exposing his weakness and leaving
himself vulnerable. These were the rules of this land.

Inukashi sighed, and adjusted himself in his seat.

"Let's hear what you have to say. I don't have much time. Keep it short
and sweet."

Nezumi lowered himself into a seat as well. He was no longer smiling.

\mybreak

"I want information."

"I figured as much," Inukashi said simply. "Even \emph{you} wouldn't be foolish
enough to come to me looking for groceries. So? Information about what?"

"The Correctional Facility."

Inukashi almost fell over.

"Correctional Facility!" he exclaimed. "You mean the one the Security
Bureau presides over?"

"Is there some other Correctional Facility that no one knows about?"
Nezumi said sarcastically.

Inukashi ignored him.

"So you want information\el what kind of information?"

"Any kind, no matter how unimportant." Nezumi fished a white mouse out
of his pocket. It was about the size of an adult thumb. Inukashi's eyes
narrowed.

"Is that a robot? It's smaller than the one you gave me last time."

Pulling off his gloves, Nezumi gently pressed the mouse's head. Its back
split open, and a yellow shimmer of light flickered momentarily before
an image floated up into it.

"What's this?"

"A hologram. The mechanism embedded in this mouse uses light to
reproduce objects."

"I know what a hologram is," Inukashi said irritably. "It's my first
time actually seeing one, though," he said as an afterthought. "But I'm
asking about what's displayed there. What is this? A blueprint?"

"It's a floor plan of the Correctional Facility's inner structure, but
it's pretty outdated. The structure itself might not have changed, but
their administrative system has probably been improved."

Inukashi scowled at him in a way that said, 'you must be kidding me'.

"No can do. I don't care what kind of information you want, I won't be
able to get it for you."

"Why?"

"\emph{Why?} Don't ask me stupid questions. Do you know what kind of place that
is? Of course you wouldn't," he said flatly, "I don't know either. No
one knows, because there hasn't been a single person who came out of
that place alive. ---Not even dead bodies can make it out of there. Once
they pass through the Special Gates, they disappear. They vanish off the
face of the earth. That's the kind of place it is, right? That's what
the rumours say."

Inukashi gulped, and shuddered. Nezumi echoed his words back to him
expressionlessly.

"Rumours?"

"Rumours say---" Inukashi began hesitantly, "there's a huge incinerator in
the basement, and all the prisoners get thrown in there. They get burned
like garbage. And the ashes that come out of there are scattered on the
farm fields of the South Block, instead of going to waste disposal. They
say it's good for the soil. ---Here, in this place."

Inukashi pointed at the bottom-most floor, presumably the basement, on
the diagram that floated above the table, and shuddered again. It was a
blank white space, and there was nothing written in it. This curiously
empty space gave him an eerie feeling.

"There's no incinerator there," Nezumi muttered.

"What makes you so sure?" Inukashi said accusingly. "Have you seen it?
How can you say that without even---"

Inukashi clipped his words halfway through and found himself staring at
Nezumi.

"You know---?"

There was no answer.

"You know what it's like inside the Correctional Facility? When---"
Inukashi's hand thrust into the light, and clenched into a fist. The
image jittered and warped.

"When did you record this?" he demanded. "This is internal data."

"Inukashi, I'm not paying you gold to answer \emph{your} questions. I want
whatever you can manage --- find any latest information about the interior
of the Correctional Facility, and add it to this data. Specifically, if
I were to be picky, I'd want accurate information about the operations
and security systems."

"You stupid or something? Operations system? Only people in the highest
classes have access to that, it's top secret. Tough luck if I can even
get my hands on it."

"That's why I'm not being picky. Gather whatever you can manage. Any
information that has to do with the Correctional Facility, and I want it
ASAP. I'll leave you with this."

Nezumi turned off the switch, and tossed the small projector mouse to
Inukashi. Inukashi wrinkled his nose at it as if it were a rotting
corpse.

"Should I use the mini-mouse I got from you last time?" he asked.

"No, that won't work. The Correctional Facility is full of security
sensors. Any robot, no matter how small, is gonna get blown up if it's
caught scurrying around without proper recognition."

"Then use real mice," Inukashi continued. "They'll be able to get in
much easier than dogs. A small living organism isn't a problem for the
sensor, is it?"

"Not so fast. Forget mice, even flies or cockroaches would be
exterminated automatically. Lasers burn them up so that there's nothing
of them left. They don't let a single fly intrude into that place. And
that's how it is."

"Then what am I supposed to do?" Inukashi said in frustration. "How am I
supposed to sneak in and gather information from some place that's all
computer-managed?"

"You don't have to sneak in. You're right --- pretty much all of the
Facility's interior is managed to the tee. But there are still lots of
areas that involve people, too. And information usually leaks through
the mouths of people. If there's anything computers can't control, it's
a man's tongue."

Inukashi hunched his shoulders exaggeratedly. He was beginning to make
out, though vaguely, what Nezumi was trying to get at. He didn't want to
see any more clearly if he could help it.

"Of course," he agreed promptly. "You need people operating the
computers and humanoid robots. The guards would have to be human, and
officials from the Bureau would be coming in and out of there. And we
can't forget the prisoners, they're human too, right? But apart from
them, the only people that can come and go from the Correctional
Facility are people inside No. 6. You need an IC card to get through the
Special Gates. It's impossible to create a fake No. 6 IC card. Which
means no one from the West Block can get near that building unless
they're prisoners. Not that anyone would wanna get near it, anyway. So
---" He was talking rather fast. "Well --- if we jump to the conclusion,
pretty much it's impossible for us to interact with people inside the
Correctional Facility because they're residents of No. 6, and that makes
it an impossible case, right? You should know better than anyone. Those
guys live in a completely different world from us. It's just \emph{different}."

"Inukashi."

"What?"

"You're talkative today."

Inukashi dropped his gaze. He knew that lowering his eyes signalled
defeat, but he had no energy to glare back at the pair of grey ones that
stared at him. He knew already who would win and who would lose.

Nezumi stood up and drew close to Inukashi, who was staring at the
floor. He whispered in a voice raspy and low, but sensual --- a woman's
voice.

"That's how you always are. When you've got something to hide, you
suddenly become more eloquent. And then I realize the truth that lies in
your heart --- that underneath that tongue of yours, flapping like a leaf
in the wind, a furtive secret is curled up."

His fingertips stroked Inukashi's chin, slid up his jawline, and lightly
pinched his earlobe. Inukashi shivered. The brief moment of ecstasy was
followed quickly by a small, sharp pain. His earlobe had been yanked.

"Ow!" he said indignantly. "The hell was that for?"

"Don't underestimate me, Inukashi."

"What're you talking about? I wasn't---"

"Stop playing dumb. I know what you're using your dogs for. That's why I
came here."

Inukashi tsked loudly, and roughly shoved Nezumi's hand away. Nezumi
chuckled amusedly.

"You use your dogs to smuggle, don't you? You've been transporting
leftover food and garbage from the Correctional Facility into the West
Block. For years now."

"I am," Inukashi answered defiantly. "So what? Transporting goods is
also part of my trade. A rat like you has no business telling me what to
do."

"The Correctional Facility has full waste disposal functions," Nezumi
continued. "They can dispose of everything inside that building. You
just said that not even corpses can make it out of there. You're right.
They even dispose of dead bodies inside that place. Which means there
shouldn't even be a speck of dust escaping from there, much less
leftover food. From that same Correctional Facility, you somehow manage
to get periodical loads of leftover food, and sell it to the food stalls
in the West Block. Makes good money, doesn't it? Maybe even more than
your hotel-running business?"

"Is it not to your liking that I'm operating in the black market?"
Inukashi said scathingly. "You must be kidding me. Since when did you
become a Bureau lackey, huh, Nezumi?"

"Machines don't trade with black-market merchants. Once programmed with
a set of rules, they'll never break them. If anyone's going to break the
rules, it's the humans. There's someone in the interior of the
Correctional Facility that's selling you leftover food, isn't there? No,
not just food. He's probably passing prisoner rations and other
belongings your way too. Anyway, the fact is, you have a contact inside
the Correctional Facility. Sniff out a lead from him. Lure the
information out of him."

Inukashi shook his head. The young man in front of him was trying to get
him involved in more danger than he had expected. Inukashi broke out
into a cold sweat.

"It's impossible---" he muttered. "The guys I deal with are the lowest of
the low. They pretty much do the cleaning and waste disposal right
alongside the robots. There's no way they would have any sort of useful
information."

"That's exactly why you wanna ask them. The guys on the top tier are
strictly overseen by the authorities. They can't risk the danger of
letting any secrets slip. But management is lax with people in lower
positions. And if their job is to clean the place, they've probably been
everywhere inside the Facility. Who knows, they might have more
information than you think. Your job is to sniff it out. Your nose is as
good as a dog's, isn't it?"

Inukashi heaved a sigh, and vainly attempted at a last act of
retaliation.

"I need money. To get any information from them, I'd need money. Two
gold coins isn't gonna cut it."

Nezumi nodded, and passed a small leather pouch to Inukashi. In it,
there were a considerable number of gold coins.

"I only have this much right now." Nezumi suddenly squatted down and
peered into Inukashi's eyes.

"Inukashi, work with me. I'm begging you."

\emph{Begging? Nezumi, are you \emph{begging} me?}

"If you take the job, I promise I'll always rush to your side if you're
overcome with unbearable pain one day. No matter where you are, I'll
deliver a song to your soul. I promise."

"Who's gonna count on a promise between a dog and a rat?"

No one could guarantee it. But yet --- Nezumi \emph{would} keep his promise.
Almost instinctively, the feeling apprehended Inukashi's soul.

\emph{No matter where or how I died, if it was accompanied with suffering, he
would always appear and put my soul to rest. He could be hard to
understand as hell, but he would never break a promise.}

Inukashi believed strongly in his own instincts. He extended his hand,
and closed it around the leather pouch.

"I'll take the job."

"I owe you one." Nezumi breathed out shortly, and wound the superfibre
cape around his shoulders. Then, he put a finger to his lips.

"I shouldn't need to tell you, but none of this---"

"I know. I won't let anyone get wind of the job. It's the cardinal rule
for my work. I'll gather the information as quickly as I can, and
contact you before anyone else can find out."

"I'm counting on you."

"Nezumi, I wanna ask you something."

"What?"

"What are you doing this for?"

Silence. It was impossible to read a single expression from Nezumi's
face. Inukashi licked his bottom lip, and continued.

"With this much money, you could live the easy life for a pretty good
while. I knew you were a star actor and making quite a bit of money, but
even for that, this is a lot. Putting this much money forward, and
threatening me---"

"I'm not threatening you. I only came to you with a job."

"Hmph---whatever. Then, going as far as to \emph{request a job from me} --- what
makes you want to poke your nose into the Correctional Facility so
badly? What's your reason?"

Nezumi didn't answer. He only made a slight half-smile. It was an
artificial one, made for the stage.

"You don't need to know to do the job, do you, Inukashi?"

"Well, obviously," Inukashi said testily. "But diving into this kind of
risky job without even knowing why is kinda harsh, man."

"Finding out why isn't gonna change how risky it is."

\emph{Tsk. This guy and his fondness of twisting arguments around --- I'm no
match for him when it comes to verbal arguments.}

"Fine," he said finally. "That's enough from you. Get outta here
already." Inukashi flapped his hand to shoo Nezumi away. He caught a
whiff of soap. The image of a face crossed his mind. It was the face of
someone who was washing the dogs, covered in suds. The nonchalant
question tumbled out of his mouth.

"Nezumi, this has nothing to do with Shion, does it?"

For a brief moment, the grey eyes wavered. Inukashi's eyes didn't miss
their slight hesitation. The tip of his nose twitched. He could smell
something.

"Shion?" Nezumi raised his shoulders slightly. "Where does Shion come
into this? This has nothing to do with him."

"Just now, you told me not to divulge information about this job to
anyone else. Do you mean that I can't tell Shion either?"

"Of course. There's no need to involve people that have nothing to do
with this."

"Dear, dear, aren't you the gentle one?" Inukashi mocked. "Who knows how
many dangerous jobs you've shoved into my hands, but when it comes to
Shion, \emph{oh no, I can't get him involved}. Hah, I see. I guess even you
warm up to people if you've lived with them long enough. Is that
white-headed weirdo of a little boy that precious to you?"

Nezumi vanished from before his eyes. Before he could even utter a cry,
Inukashi's body was being pushed up against the wall, and a set of
fingers were digging into his throat.

"That's enough smart-mouthing from you," Nezumi hissed. "Any more, and
I'll make sure you can never speak again."

"Let's see you try," Inukashi said boldly. "These guys won't let you off
for it."

Several dogs which were sprawled on the floor got to their feet,
snarling menacingly as they surrounded Nezumi. Just as one of them bared
its teeth, a small grey shadow darted out of a corner of the room.

A strangled yelp.

The large dog that had bared its teeth raised its voice in pain. A small
mouse was latched onto its neck. The dog writhed, violently shaking its
head from side to side, but soon collapsed forepaws-first. Its four
limbs convulsed. The other dogs retreated fearfully. Inukashi shoved
Nezumi aside, and cried out in the same strangled way his dog did.

"My dog, my dog!" He lifted the dog's body in his arms. A cold voice
showered over his head.

"If you don't want to end up like him, settle your other dogs down."

"Nezumi, you fucking---"

\emph{Cheep-cheep.}

The soft cry of a mouse. Inukashi lifted his face, and his breath caught
in his throat. He looked about the room, and he was rooted to the spot.
From the top of the cabinets, from underneath the table, from the shadow
of the door, from various places in the room, countless small grey mice
were staring silently at him. All their eyes were red, and glowed from
deep within.

"Down," Inukashi commanded hoarsely. The dogs did as they were told.
They returned to their spots, and lay low on their stomachs.

"He's not dead," Nezumi said. "He's just paralysed a little bit. Give
him twenty, thirty minutes and he'll be fine. He's breathing properly,
right?"

It was just as Nezumi had said. The dog's breathing was laboured, but
consistent. It was struggling to get to its feet, but it looked like it
had no strength to. It gave a pitiful whimper.

"You'll pay for doing this to my dog." Just as Inukashi clenched his
fist, the door flew open with a bang. Shion came bursting in.

"Inukashi!" Shion stood frozen, still holding the doorknob. His gaze
slid from Inukashi, who was hugging his dog, to Nezumi.

"Nezumi, what are you doing here?"

"What are \emph{you} doing here? You shouldn't be abandoning your workplace
like that."

"Well, I heard a dog howling, and I thought I heard Inukashi's voice too
--- I thought something had happened --- Inukashi, what's wrong with that
dog?"

"He's just paralysed," Nezumi answered for him. A brown mouse poked its
head out from Nezumi's shoulder. It jumped down on the floor, and
scurried up Shion's body.

"Hamlet, did you come along too?" Shion said to it.

"Hamlet? What're you talking about?"

"It's his name. Because he likes to be read \emph{Hamlet} out loud."

Nezumi's face contorted.

"Don't go naming my mice without permission."

"Well, you wouldn't name them yourself," said Shion, unfazed. "---He seems
to like it a lot. Right, Hamlet?"

The mouse nodded its head up and down.

"Ridiculous," Nezumi spat. "So if this guy's Hamlet, what's the other
one? Othello? Macbeth?"

"Cravat."

"Cravat? Was there a name like that in Shakespeare?"

"It's the name of a fried pastry. The colour of his fur looks just like
one. It means 'tie', because of the shape. The dough has powdered
almonds in it, and you twist it into a tie-shape to fry---"

"I get it, that's enough," Nezumi interrupted. "You go dream of filling
your belly with those cravats, or whatever, when you go to sleep
tonight. I'm going home. Talking with you gives me a headache."

"Are you sure it doesn't have something to do with your nerves? You're
always irritated. Maybe you're tired."

"Whose fault is it that I'm irritated all the time? Besides, you---"

Feeling Inukashi's bewildered gaze on him, Nezumi shut his mouth. He
re-wrapped his superfibre cloth, and strode out of the room without
another word. Hamlet nudged Shion on the cheek and chirruped once before
bounding after its master.

The grey mice that had been all over the room had mysteriously
disappeared. Inukashi let a long breath escape his lips, and sank to the
floor. The dog gave a low growl in his arms. Shion bent down on one knee
and began inspecting the dog thoroughly.

"He looks like he's been paralysed with some sort of drug\el but his
heart's beating normally, and he's not vomiting. He should be fine."

"Really? He won't die?"

"He'll be fine. He's only mildly paralysed. We should give him clean
water to drink. I'll go get some." Shion filled the pail that he had
been using to carry water from the river, and brought it to the dog. The
dog gulped the water down eagerly.

"See, it looks like the numbness is almost all gone. But this dog --- how
did he get paralysed?"

"Nezumi did it."

"Nezumi? To the dog? No way."

"Yes way," Inukashi said angrily. "He did it. That bastard paralysed my
dog. He wouldn't hesitate to do something like that. He's ruthless,
cunning, and cruel. I'd watch out if I were you. If you let his pretty
face fool you into thinking he's going to be gentle and kind like your
Mum, you're in for a nasty surprise."

"I don't think he's my mother, but I do think he's kind."

Inukashi made circles with his index finger in front of Shion's face.

"Idiot. That's what I'm talking about when I say he's fooled you. You're
too naive to notice how heartless he is."

"Nezumi isn't heartless. He's saved my life more than once. If it
weren't for him, I wouldn't have been able to survive."

"Nezumi, help a stranger? Without anything in return?"

"For nothing in return. On the contrary," Shion said reflectively, "I
think he's brought a nuisance upon himself. It might sound weird coming
from me, but I think I'm being quite a bit of a burden on him. After
all, I don't know anything about how to live here."

Inukashi pursed his lips. He let his gaze hover over Shion's profile as
he washed the dog's wound with water.

A nuisance? He was quite right. In these parts, someone who was as naive
and gullible as he was, and was kind to everyone, was none other than a
nuisance. And a nuisance often became the shackles that binded the hands
and feet.

But Nezumi was living with this weirdo of a nuisance, looking for
nothing in return. He wasn't chasing Shion out of his nest --- on the
contrary, he was sheltering him there.

\emph{Why?}

"Hey, Shion."

"Hm?"

"Do you two always talk like that to each other?"

"Huh? Well --- yeah, I guess. Why?"

"Because Nezumi's usually not like that. He doesn't let his emotions
show."

Shion cocked his head to the side quizzically, as if to say, 'really?'.
The dog licked the back of his hand. It was its way of expressing
gratitude for treating the wound.

Inukashi wiggled his nose and grinned. He was onto a scent.

Shion and that job concerning the Correctional Facility were somehow
connected. For this kid, Nezumi was willingly stepping into dangerous
territory.

Inukashi had no proof. He wasn't sure of any clear reason for why Nezumi
was doing this. But he had grasped Nezumi's weakness now, and that was
certain. \emph{My nose doesn't lie.}

\emph{Nezumi, so this oblivious weirdo is your weakness, your Achilles' heel,
huh? Heh, then things should be interesting. You said so. Let anyone
find out your weakness, and it could cost you your life. You're damn
right. And I've got your lifeline in my hands right now. I'll make sure
you get rewarded handsomely for what you did to me. You can count on
that.}

"I might be wrong, but\el " Shion's voice reached his ears. He was
petting the dog, which had gotten to its feet and was wagging its tail
energetically, apparently fully recovered from paralysis.

"Huh? Did you say something?"

"This dog --- is he related to you, by any chance?"

"Oh ---" Inukashi paused. "Yeah, he is. He's the last one that my Mum gave
birth to. She had him, and got beaten to death shortly afterwards."
There was a lapse before he said, "How'd you know?"

"I just had a feeling," Shion said. "He has really intelligent and
compassionate eyes. It kind of reminded me of what you said about your
mother, so I wondered if I was right."

Shion's hand stroked the dog's neck. The dog's eyes drooped half-closed,
and a quiet sigh escaped from its mouth. From its peaceful expression it
was hard to imagine that the same dog had bared its teeth at Nezumi
earlier.

"Shion, you didn't laugh."

"Huh? About what?"

"About my Mum. Usually when I talk to people about my Mum being a dog,
they laugh, or make fun of me, or treat me like a freak\el but you --- you
said my Mum was kind and loving. You're the only one who's listened to
me without laughing or making fun of my Mum, apart from---"

Inukashi clipped his words, and swallowed hard. He had just noticed this
fact. Simultaneously, he was overcome with a wave of agitation that
threatened to suffocate him.

Shion, still on one knee, looked up at him with a concerned expression.
Inukashi licked his dry lips, and slowly formed the rest of his words as
if tracing the thread of his memory.

"You're the only one --- apart from Nezumi."