% !TeX spellcheck = en_US

\chapter{The place of the gods}

\myepigraph{Then the goddess Hannahanna decided to use her last resort. She
gathered not several, but hundreds, thousands of bees, and said, "You
are small and nimble, and fly as swift as the light, so you shall surely
be able to find the god Telepinu. Now, go."}{The Disappearance of Telipinu, Hittite Myth}

\lettrine{T}{here was} a person collapsed at the foot of a spindly tree whose bark
was whiter than the rest. He was a little boy, even smaller than the
girl in size. He was writhing in pain. Shion took him in his arms and
sat him up. Even in the settling dusk, he could tell that the boy was
deathly pale. He was clawing at his throat, and his mouth was open, but
his lips were bloodless.

\myspace

Suffocation. He was choking from something stuck in his throat. There
was no time to waste. Supporting the boy's belly with one arm, Shion
thumped his back with the palm of his other hand.

"Spit it out. Come on," he urged. Twice, then a third time, he kept
hitting the boy's bony back. Four times, five times...

The boy wretched, and vomit spilled out of his mouth. There was a dark,
round object mixed in with it. The boy twitched slightly.

"Water! Bring water!" Shion commanded Nezumi again. He lay the boy down,
and brought his own cheek to the boy's mouth. He could feel definite
breathing. \emph{He's alright, he's breathing.} He didn't need to clear the
boy's airway, or give him artificial resuscitation. But his
consciousness---

"Call his name."

The girl responded quickly to Shion's words. She bent over the boy,
bringing her face close to his, and called his name.

"Rico, can you hear me? Rico."

"Rico, can you breathe?" Shion called after her.

The boy's chest swelled largely. His eyelids fluttered and opened. A
tear spilled over and rolled down his cheek.

"---Sis---"

"Rico!" Shion gently restrained the girl as she tried to throw her arms
around the boy. He slowly raised Rico's upper body off the ground, and
brought a cup of water to his mouth.

"Can you drink this?"

"Yeah."

"Good boy. Drink it slowly. So your name is Rico, huh?"

"Yeah."

"Rico, can you hear your sister's voice and my voice clearly? Can you
see us just fine?"

"Yeah--- and the water tastes good."

"You're a good boy," Shion enthused. "You've done a really great job.
Does your stomach feel alright? Does your chest hurt at all?"

"My throat..."

"Hm?"

"My throat hurts..."

Rico had probably torn at his throat in pain, for it was covered in
scratches which were beginning to bleed. Shion retrieved some gauze and
rubbing alcohol from the emergency kit. They were four years old, but
now, this was all they had.

"This is going to sting. Don't cry."

"I won't."

He swabbed the wounds, pressed a fresh piece of gauze to them, and
wrapped Rico's neck with a bandage. Shion could only give him the most
basic of emergency procedures. This was the best he could do. If he had
said anything along the lines of 'to the hospital', Nezumi would have
laughed in his face. Shion knew very well that in this area, the West
Block of No. 6, there was no such thing as a decent medical facility.
From what Rico had vomited out, Shion picked out what appeared to have
been blocking his airway.

"A nut?" It was small and round. "Why would this be---"

Rico hung his head. Nezumi folded his arms as he stood, and gave a short
sigh.

"He was hungry."

"Huh?"

"He was probably so hungry he couldn't bear it anymore. That nut--- if you
grind it into flour, it's--- well, it's edible. He was probably in the
middle of gathering them when he got hungry. He got so hungry he decided
to put one in his mouth, which was all good until he swallowed it by
mistake--- is my guess of what probably happened."

"Rico's always hungry," the girl said. "Even if Mum gives him part of
her bread, he's still hungry."

"It's such a tiny piece of bread," Rico protested. "One bite, and it's
all gone." He dissolved into a fit of coughs. His voice was raspy, and
his face was still pale. Shion wrapped his body in a blanket.

"Keep warm. If your neck still hurts, I'll treat it for you. Come again
anytime."

"Take them home."

Shion raised his face at Nezumi's words.

"Me?"

"Yeah, you. You helped them, so finish your job and see them through.
They live in the house down this slope, it's not too far. Their mother
is probably getting worried right about now."

That meant he would have to show himself to an adult. Shion stood up. He
didn't know why, but he had started to shake.

"But I---"

"You'll have to go out there one day anyway. If you're getting scared
now, you'll never be able to walk the streets. ---Well, not that it's any
of my business. But if we stay out here in the rain any longer,
someone's going to catch pneumonia."

He had forgotten that it was raining. Shion finally noticed its
coldness. It seeped right into his bones, and reminded him that winter
was approaching.

"Well, I'm off. The prince can do as he pleases." Nezumi turned his back
to them and descended down the steps below. Rico sneezed. The girl
extended her small hand and grasped Shion's fingers.

"Thank you."

"Huh?"

"Thanks for saving my little brother."

"Oh--- no, I--- It's not---" Shion stammered. "You don't have to thank me.
What's your name?"

"Karan."

"Karan? That's the same name as my mother."

"Really?"

"Yeah."

The girl smiled. Shion could feel the warmth of the girl's hand as she
clasped his fingertips. He scooped Rico up, blankets and all.

"I'll take you two home. Kalan\footnote{spelling changed to distinguish her from Shion's mother}, lead the way."

\myspace

There was steam rising out of the pot on the kerosene heater. Inside it
was soup. As he stirred the broth of vegetables and meat, Nezumi gave a
sigh. He flinched when he realized he had sighed without thinking. A few
droplets of soup splashed out of the pot, and hissed as they hit the RDF
heater.

He hated sighing. Sighing on purpose was a different matter--- but this
kind of sighing, the kind that escaped his lips without his knowing,
irritated him.

"Never sigh in earnest. Never cry. You'll be taken advantage of by
demons." He had been told that by an old woman, so far in her years that
age seemed not to matter. "Sighing creates an opening, a vulnerability.
If you want to stay live, keep your mouth shut. Never let anyone see
your weak spot. Let your heart warm to no one. Never trust anyone but
yourself."

They were her dying words. She had been shot through the chest and was
frothing bloodily at the mouth, but her words had rung clearly in his
ears. Nezumi didn't think of ever forgetting them. Even if he did, her
voice would not let him. It clung tenaciously to his mind, and refused
to let go.

But he had turned his back on it. He had let an unheeded sigh escape his
lips without even realizing. \emph{All thanks to him.} He \emph{tsk}ed his tongue in
frustration.

Maybe it was a mistake to bring Shion here. He seriously thought so.
Shion had opened the door without hesitation. He had thrown it open
wide, without even checking what was on the other side, or concealing
himself in shadow. If they had been unlucky, he would have lost his
life. Even if the visitor had not been an armed soldier, it may as well
have been an armed robber using a child as bait. Here in the West Block,
it would not be an uncommon thing. But that was something Shion didn't
know. He didn't know how to be suspicious or cautious, or to be afraid.
It was the ignorance and recklessness of one who had grown up in safety
and security.

He honestly felt that he had taken a dangerous and troublesome burden
under his wing. No one had forced him to. He had born the burden of his
own will, because he wanted to return the favour he owed. There was no
way he could have let him die --- Shion, who had saved his life, expecting
nothing in return.

There was no way of returning a favour to the dead, and Nezumi didn't
want to carry a debt that he would never be able to repay. That was why
he rescued and brought Shion here. But now he thought it may have been
careless for him to do so. Maybe he had brought with him a bigger risk
than he had imagined. An oblivious and careless, dangerous and
troublesome---

He threw a glance at the door.

But if Shion had not opened the door that time, Rico would not have been
saved. It didn't take a lot of time for a choking young child to lose
his life. Swift action and appropriate treatment --- thanks to that,
Nezumi hadn't had to see a small body with its face permanently
contorted in pain. A life had been saved. It was the same as the stormy
night four years before. That time, it was him--- this time, it was Rico.
Shion, both times, had taken them in recklessly and as a result, saved
them.

Shion knew the world only through theorems and rationales. He was naive
and hadn't even learned how to doubt the trustworthiness of others. He
was naturally oblivious, he was clueless, idiotic, and didn't even know
who Hamlet was. But Shion was also definitely above him in some ways.
Not in knowledge or skill, but --- but what?

\emph{"I'm drawn to you."}

Was it the power to attempt at this embarrassing confession, and to
believe that his sincere feelings would actually get across? Was it the
power to lend a hand to a total stranger without thinking of the risk it
reflected on himself?

He didn't know. All he knew was that Shion was, indeed, dangerous and
troublesome. He was very--- there were footsteps. Knocking. The door
opened soon afterwards. Shion had come home.

"If you're gonna knock, wait for an answer before opening the door,"
Nezumi said curtly.

"Not like you would answer anyway, right?" replied Shion lightly. "But I
noticed you left the door unlocked for me."

"Huh?"

"The lock. I thought you'd lock the door, but you kept it open."

He was right. He hadn't locked the door. How reckless of him.

"Look at me, I've fallen under your horrible influence," Nezumi said
woefully.

"What's that? ---Hey, look, I got some grapes as a thank-you gift."

The grapes were small and the whole bunch was rather pitiful.

"She offered me dried fish too, but I told her no thanks."

"Oh?" said Nezumi sardonically. "So even you felt bad about receiving
handouts from the poor."

"No. It was because you don't like fish."

"Me? I'll eat fish. I'm not fortunate enough to be picky about my food."

"But you told me once you didn't like it much."

"What I said was that I can't eat raw fish. Meaning, this place is way
too unhygienic to even think about eating fish raw."

Shion blinked, and put a hand to his hair.

"Oh. Oh well. ---But I'm glad, though."

"About what?"

"Kalan's family--- oh, Kalan is the girl's name, by the way---"

"I know."

"Oh, you knew? It's the same name as my mother's."

"Your mother's name isn't any of my concern, but.... So? Did it bring
back memories of your Mama and bring you to tears? Poor thing."

He had meant it as a sarcastic remark, but Shion shook his head gravely.

"No, that's not it. There was another child there, a girl, younger than
Rico. I think that fish was supposed to be their supper. One dried fish,
for the three of them. It would have been alright not to accept that,
right? But their mother insisted that I accept the grapes. She was
really grateful. It kind of made me happy."

"You really think so?"

"Huh?"

"If that kid had died, there would be more to eat for Kalan and the
other girl. Even for Rico--- wouldn't you have thought it would be better
for him to die rather than grow up in constant hunger? Maybe you haven't
actually done them a favour at all."

Shion sat down in front of the heater. His white hair, leaning more on
transparent, was tinged red with the colours of the flame. His youthful
hair had lost its colour, but still retained its shine. \emph{It's beautiful},
Nezumi thought.

Shion's head of hair glimmered as it reflected the light of the things
around it, and Nezumi extended his fingertips to touch it. His hair felt
slightly coarse, but ran through Nezumi's fingers easily. It felt like
ordinary hair, no more, no less.

"You told me to live," Shion said quietly, his face still turned to the
flames. "Nezumi--- you said there's meaning to being alive, and that's why
I should live. That's what you said."

"I just said whoever lives wins."

"That's the same thing, isn't it?"

"How should I know?"

The dead could not speak. All they could do was lay there as a corpse,
and return to the earth from which they came. They had no way to speak
of the hatred, the cruelties, anguish, loathing or grief they went
through. That was why he had to live. He would live, preserving
everything in his memory, and pass it on.

No. 6.~

It was like an artificial flower that left no seeds behind. It bloomed
on the blood and corpses of a countless number. \emph{I'll pull you right out
of the ground one day. Then you'll have no choice but to hear the voices
of the dead, their hatred, their hardship, their anguish, their
loathing, as it wells up out of the very ground and soaks the earth.
I'll make sure you hear, even if you plug your ears. Until then, I'll
live and remember. To forget is not a choice.} His own self didn't allow
him to.

"I got complimented." Shion looked up at Nezumi, and grinned.

"Complimented? For what?"

"My hair. Kalan's mother said it was nice. She said it was really
unique, and really pretty."

Nezumi shrugged.

"Well, it's unique, for sure. There are tons of kids around here that
have white hair from malnutrition, but no one with a whole head of snowy
hair like you."

"She didn't just say it was unique. She said it was pretty."

"Are you \emph{gushing} about how someone complimented your hair? What are you,
a girl?"

"But--- well, you know, it gives me a bit of confidence," said Shion
happily. "For when you show me around town tomorrow."

"Who said I was going to show you around?"

"You said so."

He did say so. He had said that he was going to show Shion around.
Nezumi felt like a sullen child. He averted his gaze from Shion.

"I'm going to go about my own business. You go about yours."

"Okay. I'll mind my own business and tag along. Oh, and one more thing---"

"What now?"

"I promised Kalan and Rico I'd read to them when I have time. I found a
lot of picture books in your stash, so---"

"You're gonna read to them here?"

"If it's sunny, I can take them outside."

Nezumi came close to sighing again, but he caught himself in time to
seal his lips and hold it in.

"Are you trying to make this place a kindergarten?"

"Are there that many children around here?"

"Oh yeah, tons. But this is my place. Don't go around doing things
without my permission, and don't think you're entitled to everything."

His words turned crude. There was a stinging irritation within his
chest. Being with Shion irritated him. He felt like his restraint would
snap any minute. It wasn't because Shion was being reckless or imposing,
he admitted that Shion wasn't--- it was because he couldn't see through
him. There was no way to predict what Shion was thinking or what he
would do. His actions and words always seemed to hit Nezumi out of the
blue. It was tiring.

Shion was setting plates out on the table. The soup was finished, and
its gentle aroma filled the room.

"I wasn't thinking I was entitled to anything--- it's just that, since
Kalan, Rico and I are friends now---"

"Huh?"

"Friends," Shion repeated. "They're the first friends I've made since
coming here. Well, not that I had many friends back in No. 6," he added
as an afterthought. "I think Safu was the only one."

"She said she wanted to sleep with you. You don't call that 'friends'."

He remembered the ends of her short hair that draped prettily on the
back of her neck.

\emph{Shion, I want to have sex with you.}

She had put her all into this confession, and Shion had not been able to
handle it. \emph{What a guy you've fallen for, huh}, he remarked in his mind to
the girl he barely knew. For some reason, he was suddenly overcome with
the urge to laugh.

"What?"

Shion cocked his head to the side. Two mice sitting atop a pile of books
tilted their heads too, as if to imitate him. Nezumi burst out laughing.
He squatted to the ground, and gave in fully to the wave of mirth that
bubbled up inside him.

\mybreak

The rain let up before noon but the clouds still lingered, and the
ground remained cold as dusk approached. Nezumi was walking briskly
through the throng. Shion was doing his best to keep up behind him. He
was out of breath. He was jostled, bumped, and yelled at; he felt the
gaze of countless curious eyes raining down on his head; the smell of a
dozen things reached his nose, so mingled and melded into each other
that he couldn't tell what they originally were; the muddy ground
tripped up his feet; a sprawl of barracks and tents lined the road, and
from them, thick smoke billowed rudely into the passerby; in the air,
angry bellows, seductive coos, and merchants' cries clashed clamorously.
He felt dizzy.

The older district of Lost Town, which was where he took up residence
after being forced from Chronos, was also bustling and lively. But
compared to what he was seeing now, it seemed like a tranquil getaway.

In No. 6, there were designated roads and paths for both people and
vehicles going in each direction, and as a fundamental rule, stopping
suddenly or going the opposite way was prohibited. Everyone walked in
the same direction, in the same orderly fashion. It was rare to ever
bump into anyone, or be stopped by an acquaintance. Nothing occurred
suddenly or unexpectedly. Everything was managed to prevent such things
from occurring. No. 6 was that kind of place.

A roar of voices suddenly erupted close by. Shion was shoved violently
aside. He lost his footing, and fell forward onto his knees in the mud.
Several men thundered past him. Something fell from one of their arms,
rolled, and came to a stop in front of Shion. It was an orange.

"Thief!"

A man burst out of one of the shops in the barracks, holding a gun. He
was towering, and very fat.

"Them thieves!" he roared. "Someone catch 'em!"

No one moved. Some smirked as they looked on, others showed no interest
at all, others were shouting unintelligibly; and all the while, the
so-called thieves were retreating further away into the crowd.

Shion's breath caught in his throat. The gigantic man was taking aim
with his gun. Passers-by who saw him squatted hastily to the ground to
take cover.

\emph{Is he nuts?} Shion couldn't imagine this man being in his right mind to
open fire into this crowd of people. But the man's face was set in
determination. The long muzzle of his outdated firearm was pointed
straight before him. The fleeing men bumped into an old woman and pushed
her aside as they continued running. She yammered something at them,
then returned to hobbling down the centre of the road. She was oblivious
to the gun that was pointed her way. The giant's thick finger wrapped
around the trigger.

Shion threw himself at the man just before his hairy knuckle jerked to
fire the gun. With as much strength as he could muster, he knocked the
muzzle of the gun upwards.

He felt a heavy impact slam his hand, and a shot blasted in his
eardrums. The muzzle of the gun spewed fire into the darkening sky.
Shion staggered. His feet were swept from under him, and he was slammed
to the ground. His breath died on his lips.

"The hell do you think yer doin'?"

The man towered over him with his gun raised, filling every inch of his
vision. Shion rolled quickly to the side. The giant moved nimbly for his
appearance, and Shion was met with a firm kick in the ribs.

Shion grunted in pain. He couldn't speak. His stomach lurched.

"One of their little friends, eh?" the giant snarled. "Little fucker,
takin' a swipe at my merchandise."

The man's boot gave off a greasy, animal smell. And it was swinging
straight toward his stomach again.

"I'm not one of them!" Shion screamed, barely dodging the blow.\emph{ I have
to scream, or else he'll really kick me to death.} There was no hint of
hesitation in the blows that showered down upon him.

"I'm not--- I'm not one of them," Shion persisted.

"Shut up!" the giant bellowed. "Now those bastard thieves 're gone.
Thanks to yer gettin' in the way."

"If I didn't intervene, someone could have been killed," Shion
protested. "Opening fire in a place like this --- what if you'd hit
someone?"

To his astonishment, the man started laughing. Laughter rose from the
crowd that lined the streets as well.

"And so what if I did?" the man roared, emanating his beastly odour.
"What's that got to do with me, eh?" His expression suddenly darkened,
and he roughly grabbed Shion by his hair. "You and yer strange mop o'
yers. I don't like the looks o' you."

He was pulled to the ground forcefully. His scalp burned with pain, and
it felt like it was being torn off. But even stronger than the aches on
his body were the feelings of wrath and humiliation that seethed within
him.

"Stop it!" Shion yelled.

\emph{Stop it. Let go of me. How dare you treat me like cattle.}

Shion threw himself at the man again, and slammed his body into him as
hard as he could. He felt his elbow dig firmly into the man's swollen
gut. The man let out a muffled groan and fell on his knees. The crowd
had formed a ring around them. Clapping, whistling and raucous laughter
erupted periodically.

"That's the spirit, young'un. Give 'im what he deserves!"

"Kill 'im off, ol' man! There's no use wastin' time here!"

No one tried to stop them. Everyone was enjoying the spectacle from a
safe distance. Shion searched the jeering crowd for a pair of grey eyes.
He couldn't find them.

"You little---"

He heard a booming roar that sounded more animal than human. Then he
felt a blow bludgeon his cheek. Sparks burst before his eyes, and his
vision went dark for a short instant. Something warm was filling his
mouth. Unable to bear it, he spat it out. Saliva mixed with blood
splattered and oozed over the dirt.

"Playin' funny tricks!" The man's face was flushed red, and he was
shaking in rage. His eyes were bloodshot, and his veins were raised and
throbbing over his skin like a crimson web. The murderous intent that
radiated from him was unmistakable.

"Yer gonna pay for this," he growled. The gun was aimed right between
Shion's eyes. Shion couldn't close his gaping mouth. He felt like his
heart was going to burst out of his chest. And still, no one stopped
him. In this crowd of people that surrounded them, not a single one
stepped in to stop the man. He felt nauseous. He couldn't tell whether
the muzzle before his eyes was real or just an illusion.

"Hey," a deep voice punctuated the din. It belonged to a man who was
roasting meat at the front of his store. Pieces of blackened meat
covered the grill, which was billowing thick, sooty smoke. "Don't be
makin' a mess in front of my store," he said.

"I en't makin' a mess," the man growled.

"You were 'bout to, you were. If you go blowin' brains and blood all
over the place, everyone's gonna lose their appetites, they is. Take it
somewhere else."

The giant scoffed. "No one's gonna have any appetite for yer half-rotten
meat anyway."

"Whassat?" The man shot back. "Rotten meat? You's the one selling rotten
fruits and vegetables, you's sure one to talk."

"Our produce is fresh."

"You must be kiddin' me! Even i' this season, theys flies swarmin' all
over 'em. If they's not rotten, theys must be right withered."

"What? You little---"

The men lunged at each other. Shion raised himself off the ground and
started running.

"Hey! Damnit, you come back 'ere!" The man bellowed angrily. Shion had
no time to turn around to check. His body bristled in fear of being shot
from behind at any second. He tripped.

"This way."

He was grabbed by the arm.

"This way, quickly."

He was dragged into a narrow alleyway between two buildings. Shion
leaned back heavily against the wall, and drew several deep breaths.

"Doing alright there?"

He lifted his face. A woman was smiling at him. Her red painted lips
floated up vividly in the dim gloom. The lips parted wide again.

"Oh, dear. You've cut your lip, it's bleeding. Looks like you had a hard
time back there. Poor thing."

The strong smell of her perfume filled Shion's nostrils.

"Thank you for helping me," Shion said to her, after his breathing had
returned somewhat back to normal. There was a few seconds of silence,
after which the woman suddenly burst into laughter.

"I wonder how long it's been since someone last thanked me," she
chuckled. "It feels like years. By the way, you've got interesting hair,
sweetie."

"Huh---? Oh... I've been through a lot of, er, things..."

"We've all been through a lot of things. And so have I, here---"

Despite the biting cold, the woman was clad only in a thin dress that
bared her shoulders. She pulled her neckline down to show him, and a
pair of voluptuous breasts appeared. Their whiteness stood out even more
than her red lips. Shion's eyes stung.

"Look, you see there's a burn mark? A man did that to me with a hot
metal rod, a long time ago. It was hell, I'm telling ya. But look, see,
doesn't it kind of look like a snake? Like a snake is slithering over my
chest."

\emph{I've got a snake too, and it's coiled around my whole body.}

He thought so, but he didn't put into words. The woman continued
giggling softly.

"Sweetie, don't you have any experience with women?"

"Huh?"

"Shall I give you a lesson? My place is just up ahead. Why don't you
come over, and we can have a good time. How's that sound?"

"What?" Shion repeated dumbly.

"I'm asking if you if you want to come over and have a good time."
Irritation crept into the woman's voice. "I haven't got anything to do
until nighttime either. Don't worry, it won't cost too much. So why
don't we enjoy ourselves, hmm?"

The woman's arms reached around Shion's neck. He was pushed back against
the wall. Her lips pressed firmly against his. The strong scent of her
makeup washed over him. He felt faint. Her warm tongue glided in between
his teeth and mingled with his own. Shion found himself reflexively
pushing the woman away.

"What was that for?" she said indignantly.

"No, I--- Well--- this isn't..."

"What're you mumbling on about? I helped you, didn't I? Being my
customer is the least you can do."

"Customer? But... I---"

"I'm not gonna force you if you don't want to. But you still owe me
money for the kiss."

"What?" Shion asked incredulously.

The woman's lips twisted, and her voice turned sugary sweet.

"Now, don't be disagreeable," she purred. "You're a man, aren't you?
Come on, let's take it easy. I'll make sure you have a good time, so
come on over to my place, sweetie."

"N---No thanks, it's really..."

Her white arms came clinging onto him again. Shion was frozen rigid even
more than when the gun had been pointed at him. He couldn't move.

"Would you mind?" a voice spoke. "That one belongs to me."

Nezumi was standing at the entrance of the alleyway. The woman furrowed
her brow.

"What?"

"He's mine. Could I get him back?" Nezumi extended his hand as if to
beckon Shion over. The woman drew her chin up and smiled thinly in
realization.

"I see. No wonder I was getting such a slow reaction. Sweetie here isn't
interested in women."

"What? Actually that's not true, I'm---"

Nezumi pressed a hand over Shion's mouth and smiled at the woman.

"That's right. He's so head-over-heels for me, even the most beautiful
girl couldn't attract his attention right now."

The woman hunched her shoulders as if to say 'oh well'. She glanced at
Shion. "Money," she said.

"I don't care which way sweetie swings, but I still need payment for
that kiss. One silver coin."

Nezumi laughed softly.

"One whole silver for that kiss? That's pretty expensive."

"That's how much it's worth. If sweetie can't pay for it, you better pay
up for him. You're his lover, aren't you? Footing the bill once isn't
gonna do any harm."

"I guess you're right. Yeah, sure. Could I get change, then?"

"Change?"

Nezumi leaned in toward the woman. He grabbed her arm as she tried to
back away, and drew her close.

"What---"

The woman's lips, parted in mid-sentence, were met by Nezumi's. It
happened right before Shion's eyes. The woman resisted for a moment,
then was still. Only her bare and exposed throat contracted slightly as
she swallowed. A dog was barking somewhere in the distance. A sewer rat
scurried its way past Shion's feet and disappeared. Nezumi drew away
from the woman.

"How was it?" he asked.

"Not bad," the woman replied. "But not enough to give you change."

"That's unfortunate," Nezumi said ruefully. "Then this here, for
m'lady." Nezumi placed an orange in the woman's hand, and turned his
back to her. He pulled Shion by the arm. "Right, let's get going."

The woman called after them with her arms crossed.

"Sweet-cheeks, don't let yourself get too involved with that man. It's a
waste, you know. Make sure you get a taste of what it's like to have fun
with a girl."

They weaved back into the crowd. The bustle and mixture of smells that
had agitated Shion only moments before were now a source of relief.

"Why?" he muttered to himself. Nezumi drew up by his side.

"Why what?"

"Why am I 'sweet-cheeks' when you're 'that man'?"

"Must be because I have more life experience."

"And she said I was slow," Shion grumbled.

"You are slow. And dense. Especially concerning women. I hope I didn't
ruin your first experience by walking in on you," Nezumi snickered.

"Nezumi."

"Hm?"

"How long were you watching for?"

"Probably sometime around when you started attacking the fat guy."

Shion stopped in his tracks. He was bumped into from behind, and yelled
at angrily.

"Why didn't you come help me?"

"I did. You were this close to being eaten alive by a witch.
\emph{Gobble-gobble}, head-first, too."

"But before that, I was being held at gunpoint---"

"That's your fucking mess," Nezumi said scathingly. His grey eyes
glittered harshly like the blade of a sharp knife. Nezumi's smile always
seemed to fade instantaneously.

"Let me tell you something, Shion. If you're going to keep being naive
and think that someone will always jump in to help you, you'll never
survive here. Depending on other people isn't gonna keep you alive. You
make sure you get that straight."

Nezumi turned his face away and started walking faster. Shion could feel
the heat rising in his cheeks. Nezumi was right, he was being naive. He
had thought it was only natural that Nezumi would come to help him.
Shion had been leaning on him all this time, an insolent burden that was
dragging him down. Here he was, hoping to be treated equally, yet at the
same time expecting to be defended as if it was something he was
entitled to. Shion was overcome with shame.

He trailed close behind Nezumi, who had his superfibre cloth wrapped
around his shoulders like a cape.

"But you did manage to defend yourself back there," Nezumi said, slowing
his gait slightly.

"Back there?"

"With the fat guy. You waited for the right chance to get away."

"Oh, that," Shion said. "No, I was just desperate that time. He looked
like he was seriously about to shoot."

"He probably was. If you were unlucky, you probably would've had half
your head blown off, and you'd be lying there on the street."

"I don't even want to imagine. It's giving me the chills."

He really was shaking. There was mud smeared over the knees of his
pants, and the hem of his sweater. He tried to brush it off, and tripped
over something.

"Whoa---!"

He fell forward, but managed to regain his balance in time to turn
around. There were a pair of legs. Their feet were bare. The upper half
of the body was lying face down, swallowed up by the darkness of the
alleyway. \emph{Is he sleeping? Here?}

"Um--- hello? Can you hear me?" Shion called over to him. He was yanked
from behind.

"Will you stop doing that?" Nezumi said in annoyance. "If we don't hurry
up, it'll get dark in no time. Geez, do you have a thing for making
detours?" Nezumi clicked his tongue.

"But this man--- he's going to catch a cold if he sleeps out here like
this."

"He isn't gonna get any colder than that. He's dead."

"\emph{What?}"

A woman called over to them nearby from her clothing shop.

"Oy, are ya two acquaintances with this here? If you are, mind cleanin'
it up? It's blockin' the way, makin' a mighty nuisance outta itself."

Nezumi shook his head slightly.

"Of course not. I've never even seen this old man before."

"It's a woman, an old beggar lady. Out of all places, she bloody had to
snuff it right in front of my store, the git."

"My deepest sympathies," Nezumi said solemnly. "Make sure you get her
cleaned up."

"That's enough o' yer cheeky attitude, little bugger!" The woman
bleated, swinging around a red piece of cloth. Her arm was as thick as
Shion's thigh. \emph{I'd go flying if I got punched by that}, Shion thought to
himself.

He was yanked along by Nezumi. The sight of those legs, like withered
twigs, overlapped with another pair of legs, wrapped in a fine pair of
trousers and wearing leather shoes. They were the legs that protruded
from behind the bench, in a secluded corner of the Forest Park inside
No. 6. It was the first dead body that Shion had born witness to, and
the first victim that \emph{it} had claimed.

"He wasn't killed by it," Nezumi smiled wanly, as if to read Shion's
thoughts. "That old man--- or woman, was it? She wasn't eaten by any
parasite wasp. It was either hunger, or the cold --- maybe a combination
of both --- that carted her off to heaven. There's a whole season for
that, and it's coming soon."

"Season for what?"

"Where people freeze to death. Old people, children, the infirm... the
weak ones die out first. It's the season of Natural Selection."

"Natural selection..." Shion murmured the words. They were cold, like a
frozen confection. But they were neither sweet nor delicious like one.
They were just cold. The tip of his tongue felt numb.

"Shion, you said there would be lots of casualties in the Holy City when
the parasite wasps become active again in the spring, right?"

"Yeah."

"Well, here, people die every day, especially in the winter. Which one
do you think is easier to go through, being devoured by a wasp, or
starving and freezing to death?"

Shion had put a hand to his neck without thinking. There was a scar at
the base of it, where the incision had been made. Underneath was \emph{the
thing}. It had failed in hatching, and was half-melted when it was found,
but it had been struggling to eat its way out from this spot. The
vicious pain, the suffering and despair from that time was still fresh
in his mind. He never wanted to go through the same thing again. But he
had no way of comparing this with the elderly woman's death. He had no
idea what it was like to starve or freeze.

"Nezumi, what's going to happen to her?"

"Her?"

"That--- body. It's not just gonna get left there, is it?"

"Of course not. It might get cold out here, but bodies will still rot if
they're left out like that. Then wild dogs and crows will come to pick
at them until it's impossible to do anything, so they usually get
cleaned up before then."

"So there must be a communal cemetery, or something?"

"Cemetery? There's no land here that we can put aside for dead people.
The Disposers come. See, over there. The guys that are sitting there
eating meat. See them?"

In the direction where Nezumi pointed, there was a ripped tent under
which there were several burly men sitting, talking loudly and devouring
meat glistening with fat. A scraggly, pitifully thin dog was lapping
desperately at the juices that dripped from them onto the ground.

There was a strange vehicle parked beside the tent. It was a bicycle,
strapped to a flat cargo bed on wheels. Sitting on top of it was a large
basket.

"They're the Disposers. In exchange for money, they get rid of dead
bodies. It's people like that old hag back there that eventually cough
up the money to get it done. They don't want a body lying around their
store, but they're too disgusted to pick it up and toss it onto someone
else's property, or they feel guilty about doing it. So they dismiss it
as their unlucky day, and call up the Disposers to get rid of it. I hear
it's a pretty lucrative business. I guess it would be, since there are
people that die all the time on the road who have no friends or
relatives."

"Do they bury the bodies properly?"

"They burn them. They gather them all in one place, and set them on
fire. I guess you can call it some sort of cremation, if you want. They
don't get anything fancy like a requiem or prayer of repose, though,
that's for sure."

Shion's eyes met with a man who was in the midst of ripping a chunk of
meat off the bone with his teeth. He grinned widely, and grease dripped
from his sparse whiskers. Then he stood up, and started making his way
toward them. He tossed the bone carelessly on the ground, and the
scraggly dog pounced on it.

"Hey fellas, how'd you like to join us?"

His arm reached out, and before Shion could dodge it, he was grabbed
roughly by his hair.

"So it's real, huh. I thought it was a wig. Pretty interesting hair you
got."

"Stop it," Shion yelled. "Let me go."

"Hmm, not bad. I never seen this kinda hair myself. Kinda pretty,
actually. You almost look like a doll of some sort, little fella."

Vulgar laughter erupted from his group of companions sitting behind him.
Shion turned to look beside him. There was no sign of Nezumi, who had
been there moments before.

"Let go," he repeated loudly.

"No need to make a ruckus, now. Why don'tcha join us for some drinks? We
got meat too."

"I said let go," Shion said through clenched teeth.

The bulky man showed no signs of loosening his grip. Shion could feel
the man's breath on his cheek, putrid with the smell of alcohol and
meat. He turned his face away.

\emph{Nezumi}. He bit his lip hard, and resisted the urge to call out his name.
He had to try to defend himself first, or no one would come to help him.
Shion let his body relax.

"Fine."

"Hm?"

"I give in. I'll join you just for one drink."

"That so? There's a good fella. This way."

The man's arm relaxed just slightly. Shion lifted his leg, aimed at the
man's groin, and kicked as hard as he could.

\emph{Ngh}. The man let out a muffled groan, and doubled over as he collapsed
to the ground. Shion leapt over his curled back and broke into a sprint.

\emph{Running away is all I've been doing today.} The fleeting remark crossed
his mind, but soon disappeared. He tore through the street as fast as
his legs would carry him. There were less people milling about, which
made it easier for him to thread his way through. \emph{No more alleyways for
me}, he thought, and concentrated on keeping straight to the road. If he
stopped, he felt like he would be grabbed by the collar from behind.

"---Agh!---"

His foot slipped, and his body floated up momentarily. Then he was
slammed to the ground. The pain jolted through his body from head to
toe.

"Whoa---" Now he was sliding downwards. He was on a slope of grey
concrete, though now it felt like more of a steep slide. He hurtled
downwards. Shion closed his eyes, and brought his arms over his head to
protect it. The action made him lose his balance, and he tumbled forward
in a somersault.

His vision went dark. Just as he was about to scream, the smell of moist
dirt reached his nostrils. He was thrown out onto the ground. Clods of
dirt flew into his mouth. Shion lay coughing for several moments, and
then stretched out on his back. His heart was thudding frantically, and
it was hard to breathe. Dull and sharp pains alternately throbbed all
over his body.

The taste and sensation of dirt still remained in his mouth. He had
never imagined that dirt could taste this sweet and fragrant.

He could see the stars: they were winking in the settling dusk. The sky
was neither black nor blue, but closer to indigo, with a wash of purple---
it was stunningly beautiful. He felt his soul getting sucked into its
beauty. He had never thrown himself out on the ground like this to stare
up at the sky. Had something as beautiful as this always existed above
him?

He heard quiet footsteps padding toward him. A wistful whimper. A warm
tongue slowly licked his forehead and his hair.

"You---"

It was the dog, the skeletal dog that had been hanging about the group
of men. It lapped at his head persistently.

"Are you worrying about me?" As soon as the words were out of his mouth,
Shion noticed something else. When he had been grabbed by the man, his
hair had been smeared with grease and meat juices. The dog was licking
that spot with enormous concentration.

"Okay, that's enough, that's enough," Shion said. "I don't want your
slobber all over my hair instead." Shion propped himself up off the
ground, and stood up carefully. He didn't feel any severe jabs of pain.
It looked like he had managed not to sprain anything or break any bones.
He let his gaze take in everything around him. He inhaled sharply.

"This---"

He was in the midst of a ruin.