% !TeX spellcheck = en_US

\chapter{To the evening breeze}

\myepigraph{For more than a thousand years sad Ophelia\\
	Has passed, a white phantom, down the long black river;\\
	For more than a thousand years her sweet madness\\
	Has murmured its romance to the evening breeze.}{Arthur Rimbaud, \emph{Ophelia}}

\lettrine{N}{ezumi fell} very slowly and quietly. It was like watching a slow-motion
film. An ancient, monochromatic film\el 

A dull impact hit his chest. Nezumi had fallen on him. Shion caught the
boy's weight and heat in his arms. Suddenly, the black-and-white screen
regained its repulsive colours of reality.

Nezumi collapsed in Shion's arms, letting his whole body weigh down on
them. The stench of blood assaulted Shion's nose.

\emph{Nezumi\el }

But no voice came out. He could not understand what had happened. He
just could not. \emph{What is it? What just happened?} Soldiers were pointing
their guns at them. Rifles. The bayonets attached to them shone starkly
white. One of the soldiers let his tongue peek out from between his
lips.

A new wave of prisoners came in a torrent down the stairs. They formed a
blockade between the soldiers and Shion. Of them, a bald, gigantic man
gave a short cry. He staggered, clutching his chest.

"Damnit\el you've done it now." The giant took two, three steps towards
a soldier and suddenly let out a great roar. "Goddamnit!"

The giant lunged at the soldier. At the same time, there was an
explosion. Smoke and flames burst from the monitoring room near the
stairs. Shion saw the soldier being flung to the wall by the blast.
White smoke rapidly filled the corridor. Like a giant white snake, it
slithered up the stairs and crawled down the hall.

Shion hoisted Nezumi up, and made for the end of the hallway. In regards
to the movement of the smoke, the typical way to escape was probably
downstairs. But down this hall was the Hygiene Management department.

The Hygiene Management Department. From the layout, Shion guessed that a
simple medical examination room had been built adjacent to it. He
stepped in through the door, which had been left flung open. He closed
it to prevent further smoke and flames from filtering in.

He tripped. Nezumi's body nearly slipped from his grasp. Shion attempted
to catch him, but fell down with him in a tangle. He instinctively
thrust his palms out, and noticed they had left red hand prints on the
floor. His palms were dyed with blood---with Nezumi's blood.

"Nezumi!"

He couldn't help but raise his voice. Words were tearing through his
throat and streaming forth.

"Nezumi, can you hear me? Nezumi!"

Nezumi's eyes remained closed, and he remained unresponsive. The blood
had spread from his shoulder, stained his chest, streamed down his arm,
and was dripping from his fingertips.

"No, how---how can this---" He knew that he could not lose his wits. He had
to be rational. He had to calmly carry out what he had to do.

\emph{I know. Of course I do. But I can't move. My mind and my body are frozen
still.}

"Nezumi, Nezumi. Please, open your eyes." He gritted his teeth.

\emph{You dumbass.} He heard a scolding voice. \emph{You're a helpless idiot.
Useless, good-for-nothing. You're bigheaded and slow and cowardly.}

Inukashi? Is that you?

\emph{Can't you even protect your most precious person? Can you only cry
without even trying to save him? What do you have to show for being with
Nezumi all this time, then? Are you still the same spoiled elite as you
were in No. 6?}

He could not tell if it was Inukashi's voice or his own, but someone was
giving him a severe reprimand.

\emph{Shion, are you sure? Would you be indifferent if you lost Nezumi? Would
you even be able to bear it?}

Shion drew a deep breath. The smell of blood reached all the way into
his chest. He brought his ear close to Nezumi's lips and checked his
breathing. He took Nezumi's pulse by placing his fingers on the boy's
wrist. He felt blood throbbing against his fingertips, but it was a
faint pulse that seemed close to disappearing anytime now.

Shion stood up and glanced around the room. Thin flames and smoke issued
from the instrument panel in the centre. There was a cabinet against the
wall beyond with glass doors. The glass had been broken, and plastic
bottles lay tipped over. Some had loosened caps, or the bottles
themselves had been damaged, for the contents were leaking. Shion drew
closer, but smelled nothing strange. Hand-written labels were fixed to
each bottle with the name of the drug. Shion would perhaps have smiled
at the rounded handwriting if he had seen them in a normal situation. He
would have smiled unwittingly at the idea of someone handwriting labels
in such an inhuman-like place like the Correctional Facility, instead of
using printed labels.

But now, he had no room in his thoughts for that.

Shion went through all the labels one by one. He suppressed his agitated
heart, and told himself to calm down over and over, like a mantra.

Disinfectant; hemostatic agent; painkillers; purified water; general
syringe; hemostatic clamp; gauze; absorbent cotton pads\el in a corner
of the shelf, there was an emergency flashlight tipped over on its side.
As he expected, there was an adequate range of drugs and apparatuses for
simple medical treatment.

Would he be able to manage something with these? A minor injury would
have been no problem; but would he be able to treat a wound so severe it
had caused the patient to suffer massive blood loss and loss of
consciousness?

Most of Shion's medical knowledge was theoretical. He had almost no
practical experience. In this situation, furthermore, how well could he
give emergency treatment? Could he do it? He felt like the bayonet he
had seen just now was being held to his throat.

Can you do it?

\emph{I've got to. There's no time to hesitate. I can't just sit idle and
trouble myself over it. I can't let Nezumi be stolen from me so easily,
without a struggle. I won't hand him over to you.}

"Nezumi, you can hear me, right? I know my voice is getting to you."

\emph{There's no way you can't hear me. There's no way my voice won't reach
you. No matter when or what situation, you always caught my words
firmly, You heard me through the noise, you grasped my words, and you
answered me. You came back to me. This time, I'm going to bring you
back. I'll take you back by force.}

"Nezumi!"

Shion tore the other's clothes. The bullet had pierced him below the
left shoulder through his upper arm. If the shot had been a little
further inwards, the bullet would have pierced his heart and he would
have died instantly.

\emph{Live. Cling onto life. Heaven left that possibility for you. I won't let
it go to waste. First things first, I have to stop the bleeding. My
priority right now is to stop this blood. Then, I have to take him to a
place where he can get proper treatment. Quickly, even a second sooner.
Just that.}

He illuminated the affected spot with a flashlight. He sprinkled
disinfectant on the wound. He washed the wound from the inside outwards,
and he examined the inside with his naked eye. The artery was not
severed completely. He applied pressure on Nezumi's collarbone and
temporarily controlled the bleeding. His fingertips were trembling.

\emph{Calm down calm down, calm down. I have to calm down. Banish all your
emotions, and focus only on the bullet wound that's penetrated him.}

He pinched the artery with the hemostatic clamp, placed gauze on it, and
pressed over it with an absorbent cotton pad. He wrapped a bandage
tightly around it.

\emph{This is the best treatment I can give him right now.}

He had broken into a sweat, which formed droplets and streamed down his
face. They seeped into his mouth, and left a bitter taste on his tongue.

\emph{How long will he last with this? Three hours---no, more like two,
considering how much he's bled. If Nezumi doesn't get proper treatment
within two hours from now, he won't make it.}

Time limit: 120 minutes.

"Ugh\el " Nezumi groaned softly. His eyelids fluttered slightly.

"Nezumi! Can you hear me? Nezumi!"

"\el Shion\el " he mumbled.

"Just a little longer. I need you to bear with me. I'm taking you to the
hospital. Hang in there, and stay with me." He instilled as much
strength as he could into his words.

"\el Shion\el I can't\el move\el "

"No problem. I'll carry you." \emph{I'm here. I'm right here. So you'll be
alright.} Shion slung Nezumi's arm around his neck, and hoisted him up.
He circled his arm around the boy's waist to secure him, and stepped out
into the hallway.

The smoke stung his eyes. He dissolved into a fit of coughs. Pain raced
through his throat, and his airway clogged up.

He had no survival knowledge, but he had the will, and his heart was
prepared to do whatever it took. Nezumi had taught him plenty about
that.

Shion crouched, and dragged Nezumi almost at a crawl. Heat and smoke
swirled around them on the stairs. It was too dangerous to jump into
this. But there was no time to survey other escape routes. If they
dallied here, they would be engulfed by the smoke, and die of
suffocation.

\emph{What do I do? What should I do?}

His mounting agitation and the smoke that crept into his body almost
made him lose his calm. \emph{Don't panic. Whatever you do, don't panic. There
is always a way.}

"Shion\el "

Nezumi shifted his body. "Get out\el through the garbage chute\el "

His voice reached Shion in fragments. He could tell that Nezumi was
clinging desperately onto his consciousness. Once he lost it, it would
be more difficult than ever to wake up again; Nezumi knew this all too
well.

\emph{Garbage chute. Right, there was that option.}

In the lower floors like the first to third, a garbage chute was
installed in the middle of the hallway on each floor. It looked like
small apparatuses were discarded there along with everyday waste, for
the chute was quite wide. The first time Shion had found this out, the
idea of using the chute to infiltrate the Facility had crossed his mind.
But the idea was short-lived. It was impossible to climb up a chute
almost perpendicular to the ground with no footholds whatsoever. Also,
the chute was programmed to sense and set alarms off at any strange
objects protruding from the openings. Infiltration was impossible. But
it was possible to use it as an escape route.

He and Nezumi had talked about it before. It was---two days before the
Hunt.

The day of the Hunt had been a cold winter day with a blustering wind,
but two days before, it had been sunny with milder weather. A blue sky
spread out above the West Block instead of snow clouds, and the rays
that shone down were so warm that it was hard to believe it was winter.
People seemed to be making the most of this short bout of pleasant
weather, and strolled down the marketplace at a leisurely pace. Old
beggars and starving children still overflowed in the streets as usual,
but they seemed to breathe easier than most days. The shopkeepers, who
would usually drive them away in a spiteful and unforgiving way,
narrowed their eyes at the sun and let their faces relax. They didn't go
so far as to give hand-outs, but they seemed to be willing to turn a
blind eye to the beggars as long as they didn't steal any of their
goods. Some even joked with familiar beggars.

Out of them, how many could have foreseen the hell that unfolded two
days later? How many could have escaped the inferno of the Hunt?

Nezumi and Shion had been dining on hard bread they had bought at the
market, soaking it in hot water first. Perhaps Nezumi's smile had done
the trick; the female head baker had given them some cheese for free. It
was superb cheese, free of mould.

There was no sound in the basement room except for the voices of the two
boys. Strangely, even the howl of the north wind which had begun to blow
around sunset did not find its way here. Had the wind died down during
that time? Or had Shion been so engrossed in the conversation that his
ears had refused to catch anything other than Nezumi's voice?

"Shion, the garbage chute could be an escape route. Is it doable?"
Nezumi asked, turning his cup of hot water in his hands.

"The garbage chute, huh\el I see, it's like having a road that leads
straight from the third floor to the meeting place in the basement."

"Yeah. From the blueprint, I'm guessing the entire chute apart from the
openings probably isn't integrated into the object-detection and
disposal system. Heh, seems like No. 6 is lax all over the place when it
comes to its waste disposal facilities."

"You're right," Shion had replied. "And it's bigger than a typical
chute. Technically, we should be able to get through."

"Exactly. Aren't you glad we both happened to be skinny? If any of us
had been around old man Rikiga's size, we'd get stuck in the middle.
Oversized garbage, indeed."

"That sounds a bit severe."

"You're welcome. I'm just telling the truth. \emph{You} tell me if you can
imagine that beer-bellied geezer hurtling down the chute like it's
nothing."

"Well---I guess you're right." The image of Rikiga with his fleshy
underbelly rose in Shion's mind, and he almost burst out laughing. He
swallowed it back down, and pursed his lips. Nezumi's question was not
the kind he could answer with a smile.

Was the garbage chute a plausible escape route or not? After some
moments of thought, Shion spoke.

"To tell you the truth, I have no idea if we can really do it. But
there's a possibility. All theory, just saying," he answered. Nezumi put
his cup down, and sank deeply into his seat.

"Possibility, huh."

"Yeah."

"There is a possibility, then." Nezumi crossed his legs, and closed his
eyes. Shion also leaned back against the bookshelf and hugged one knee.
It was then that Shion noticed the sound of the wind for the first time.
It was a raspy sound, similar to an old woman's hushed weeping.

The room dimly lit by a lamp; Nezumi's meditating profile; the low
rumble of the wind---he felt like he was looking at a scene from a play.

Shion was sitting in the audience, eyes fixed to the silent tableau on
the darkened stage before him. A fulfilled comfort, a wistfulness, and
an emotion close to awe, along with others he couldn't name, mixed,
tangled with each other, and filled Shion to the brim.

\emph{If only this moment could last forever. If only time would stop right at
this moment. If only my entire world consisted of the things right here.
The wish rose suddenly in his heart.}

\emph{"Life's but a walking shadow, a poor player."} A line from \emph{Macbeth}
suddenly rose in his mind.

\emph{"Out, out, brief candle."}

\emph{"Life's but a walking shadow, a poor player."}

Nezumi opened his eyes. His gaze tangled with Shion's own.

"What?"

"Huh? No, nothing\el " Shion shifted his body, and backed away slightly
from the lamplight. He did not want Nezumi to see his cheeks, which were
probably flushed red.

"Shion, do you know what I was thinking about just now?"

"You? Well\el the garbage chute, probably?"

"Of course not. I'm not gonna trouble myself over trash forever.
Besides, we solved that problem. It's possible, which means it's worth a
shot. So far so good?"

"Right." It didn't matter if it was only theory. No matter if the idea
was nothing more than speculation; if it's possible, you have to drill
it into your mind--- that was what Nezumi was telling him. Shion nodded
slowly as a sign that he understood.

"Good. But if you ask me, I'd rather make my gracious exit at the front
door, complete with all the accompaniments. But that's a luxury I
probably won't have."

"Probably not. I'd warn you not to expect VIP treatment. So, if you
weren't thinking about the garbage chute, what were you thinking about?
Other ways to escape?"

Nezumi re-crossed his legs, and let out a doleful sigh.

"I was thinking about food."

"Huh?"

"Food. F-o-o-d. I was thinking about what I'd order if I could stuff
myself with whatever I liked."

"---Materialistic of you, huh?" Shion commented.

"Food is important. Sometimes, a roll that an old baker man has slapped
together is much more meaningful than an eternal truth discovered by an
esteemed philosopher. That's the nature of life. Anyway, right now I'm
so hungry I'm starting to feel sorry for myself. I probably won't be
able to sleep if I went to bed now."

"You just ate. You ate two rolls."

"Rock-hard, withered bread, hot water and a piece of cheese is not
nearly enough."

"Don't be greedy," Shion said sternly. "Thanks to that madam at the
bakery, we were able to get our hands on some good cheese. It was a
pretty decent dinner."

"If only you'd been a bit more friendly, and we probably could have
gotten some canned lamb or a bottle of milk on top. Shame."

"Me? I've got nothing to do with it."

"What're you saying? You've got everything to do with it. You should
have seen the way that lady was looking at you. I thought you were
ignoring her on purpose. Don't tell me you actually didn't notice!"

"I had no idea."

Nezumi grimaced at him and shook his head. "Shion, you need to brush up
a little---no, forget that, \emph{a lot}--- on your perceptions of the other sex.
If you don't do it soon, things'll get pretty bad."

"What do you mean, bad?"

"So bad I can't put it into words. You won't hear anything from me, at
least. Oh, but geez, that's serious. Just thinking about it gives me the
goosebumps."

"What are you talking about?" Shion asked in annoyance. "Now you're
making me curious. It would probably keep me up if I went to bed now. My
curiosity and your hunger would make a good contest."

Nezumi laughed out loud, which was unusual for him. His laughter was
carefree and full of delight. It entered into Shion quietly, and deeply.

"Nezumi."

"What?"

"Can you recite \emph{Macbeth}?"

"Macbeth? Which part?"

"Act Five Scene Five, right after Macbeth is told about his wife's
death."

"Why \emph{Macbeth}?"

"I dunno," Shion replied. "I wonder why. I just suddenly wanted to hear
you do \emph{Macbeth}. Won't you?"

"Well, I don't mind."

Hamlet and Tsukiyo climbed up onto Shion's shoulder. Nezumi's voice,
serene yet wrung with sorrow, reached Shion's ears.

\poem{Tomorrow, and tomorrow, and tomorrow,\\
	Creeps in this petty pace from day to day,\\
	To the last syllable of recorded time,\\
	And all our yesterdays have lighted fools\\
	The way to dusty death. Out, out, brief candle.\\
	Life's but a walking shadow, a poor player\el}

Shion and the mice listened entranced with bated breath. The flame of
the lamp wavered, and their shadows wavered also. Shadows also etched
themselves into Nezumi's voice and expression, and Shion felt himself
being lifted out of reality and taken up to the heights. A fleeting
levity; eternal fulfilment. How rich, how plentiful and beautiful were
these hours that passed.

Two days before the Hunt, in that room was the scene which left an
impression like no other in Shion's life. What took place only a while
ago felt like something of days long past.

Tears spilled over.

It was the smoke, and not because his heart had been torn in nostalgia.

\emph{Cheep-cheep, cheep-cheep, chit chit chit.} Tsukiyo alighted on the floor,
and squeaked incessantly. The superfibre had fallen to the ground. Shion
stooped abruptly to pick it up. The strength left Nezumi's body, and his
weight bore down on Shion's shoulder.

"Nezumi, hang in there. Stay awake."

"\el Get out of here\el hurry\el "

"I know. Even I wouldn't take a rest here. Nezumi, we're almost there.
Bear with me for a bit longer."

"Shion\el we can't. Not\el with two of us."

"Huh? What're you talking about?"

"Run\el on your own\el just run."

"Idiot!" Shion snapped. "Don't give me that crap!" Anger reared inside
him. It was wrath toward Nezumi. He felt like his white hair was
standing on end. Scorched air blew not only from outside, but from
within Shion as well.

\emph{Telling me to leave without you? That I should just escape by myself?
Don't give me that. Don't you dare. Is that how much you look down on
me? How little you think of me? I'm not so weak that I'll leave you and
choose the path of my own survival. I can protect us, you know. I have
enough strength to protect you and me.}

"Don't underestimate me, damnit," he said angrily.

Anger swiftly transformed into energy to press forward. He willed
strength into his arms, and glared ahead. The place was void of any
human presence. Shion felt a slight breeze. The flames began to lick the
ceiling. Some chemical had apparently caught fire, for there was a small
explosion, followed by a characteristic sharp odour.

"Tsukiyo, come on."

Tsukiyo dove into his pocket. He poked his head out, and emitted
high-pitched squeaks. To Shion, it sounded like the orders of a
navigator, and he felt encouraged. He had to escape even a second
sooner, also for the sake of this tiny creature who kept up its cries
even through its shortness of breath.

He tripped on something and almost fell over. A giant of a prisoner was
lying face-down on the floor. He had died with his face in a pool of his
own blood. Shion stepped over his body, and continued forward.

\emph{Stairs here, which means the location of the garbage chute is\el } He
recalled the accurate details of the floorplan which he had drilled into
his mind. He traced it in his memory. It was in a corner of the hall,
where the smoke was billowing now. He nudged Tsukiyo's head back into
his pocket with the tip of his finger.

"Nezumi." \emph{We're going in.} Shion held his breath, and plunged into the
smoke. He had neither time nor way to check the opening of the chute.
His field of vision in this smoky corridor was close to zero metres. A
slight hesitation, and he would meet his end through suffocation.

\emph{Believe. Believe in yourself. If you're gonna cling, cling to yourself.}

His feet stopped. He could see the opening of the garbage chute. A
soldier was slumped against it as if to block his way. His legs were
thrown out, and he lay still with his eyes half-open. His neck was
twisted at a queer angle. His rifle, which he had apparently held fast
onto even while being blasted by the explosion, sat in his lap. The same
rifle which had shot Nezumi.

Shion did not feel any sort of emotion rise toward this soldier. No
hatred, nor ire, nor pity. Not even respect for one who had died. The
thing in front of him was not a human body; it was but an obstacle.
Shion had to think that way, or else he could not survive. \emph{It's just an
obstacle.}

He kicked the soldier.

The soldier's body rolled over, its neck still bent at an odd angle. The
opening revealed itself fully. \emph{It hurts. I can't breathe. My throat is
burning. I want air.} His veins swelled. His heart was wreaking havoc in
his chest. Strength began to leave him. \emph{Damnit, I've come this far; I
won't give in now. I've come so far\el }

\emph{Nezumi. What? Can you recite \emph{Macbeth}? \emph{Macbeth}? Which part? Act Five
Scene Five\el }

\emph{The wind was howling. The flame was flickering. And I desperately wanted
to hear you recite that line. I don't know why. Maybe I just wanted to
lend my ears to your voice, and immerse myself in your breathing. As I
listened to Macbeth tread the path to destruction, I felt elevated; I
was fulfilled.}

\emph{"Out, out, brief candle."}

\emph{"Life's but a walking shadow, a poor player\el"}

\emph{Nezumi, we're going home. We're going back to that room. We can't turn
back time, but we can create it anew.}

Usually, the garbage chute was programmed to open automatically when it
sensed someone standing it front of it. Of course, right now it did not
move at all. Once Shion laid Nezumi down, he grabbed a rifle and fired
the whole round of shots into the opening of the chute. The lid blew
into smithereens.

A black square void yawned at him. Triumph pierced his body.

\emph{Nezumi, we're almost there. Almost there.} He wanted to call out to
Nezumi, but he couldn't speak out loud anymore. He wrapped Nezumi in his
superfibre cloth. If he could, he wanted to slide down the chute while
holding Nezumi, but the chute was too narrow. It was wide enough for
just one person.

Shion heaved Nezumi up, and stuck him into the chute feet-first. Shion
slid in after him, and he gripped the opening with his left hand while
he secured Nezumi's head to his belly with his right. He could feel
vibrations from the explosions. The wind roared.

Shion closed his eyes and released the grip on his left hand. Two bodies
slid down the perpendicular chute.

\mybreak

"Ow!" Inukashi yelled. He had been bitten on the earlobe. "The hell was
that? That hurt. You freaking rats."

With a hand to his ear, Inukashi glared at the two mice perched
side-by-side.

"I guess calling you guys rats doesn't make for much of an insult.
You're close enough. Damnit, that hurts."

He had evidently fallen fast asleep, slumped over the desk. \emph{I guess I've
got some guts to fall asleep in this situation. Heh heh.} He mentally
congratulated himself while he massaged his earlobe. In reality, he had
probably lost consciousness from exhaustion, but it didn't feel bad to
compliment himself like this.

He heard snoring. Rikiga was curled up on the floor at his feet, snoring
liberally. Even a legendary monster couldn't produce such a horrifying
noise.

"Tsk, looks like old man here has got more guts," Inukashi clicked his
tongue. The little mice scurried up his arm.

"Hey, stop that. I just clicked my tongue. I wasn't inviting you to
play. I don't have food, either. Hey, don't bite my ear! I'm hungry,
too!"

\emph{Chit-chit-chit. Chit-chit-chit.}

\emph{Screek! Screek! Screek!}

The mice scurried up and dashed down Inukashi's arm in turn. Their
actions and cries were clearly out of the ordinary.

"What is it? Is something wrong?"

His nose twitched. It smelled like something was burning. Smoke was
seeping through the door, which was slightly ajar. It was burning inside
the Correctional Facility.

"Shit\el " Inukashi muttered to himself.

The smoke would probably fill this room in no time. They had to escape
before then.

\emph{This is serious. And it's amazing. If the smoke has gotten this far, it
must be a serious fire. What about the fire-extinguishing devices? Did
they not work? Devices not working in the Correctional Facility? Is that
even possible?}

Inukashi swallowed. \emph{Is it their doing? Did Nezumi and Shion stop all the
systems? Did they pull this miracle off?}

\emph{"You can make miracles happen more easily than you think, Inukashi." Are
you telling me you weren't lying or putting on a front when you were
saying that?}

The smoke streamed in with even greater speed, along with a burning
smell and heat. His spine froze. \emph{Wait. Wait a second. Are they still in
here?}

This smoke, this stench, this heat. He could not imagine people
surviving in this. His spine grew even colder.

\emph{Nezumi, you better know that you're only allowed to call it a miracle if
you come back alive to say it. If you die in there, that's not a
miracle. You won't even get a memorial. If you don't end up coming home
after giving me all that big talk, I'll laugh. I'll laugh my ass off.}

Rikiga choked on the smoke and started coughing. The mice screeched. It
looked like they were roaring with all their might.

"What is it? What do I do? What happened to your masters?" Inukashi felt
like screaming too. \emph{What the hell am I supposed to do?}

One of the mice---he couldn't tell if it was Cravat or Hamlet---dashed into
the collection area. It darted madly around the very bottom of the
garbage chute, where a square opening had been cut out. The other joined
it, and they both ran in dizzying circles around it.

\emph{Garbage chute? Wait a minute, why did Nezumi make us wait here in the
first place? The garbage chute\el }

Inukashi roused himself, and kicked Rikiga's hind quarters.

"Help me out, old man."

"Wh-What? What's going on?"

"They're coming back. Help out."

In a corner of the collection area, there were a few old and worn mats.
Getsuyaku had supplied them to prevent further damage to apparatuses as
they came falling down the chute. The less damaged the goods were, the
higher the price he could resell them at. Getsuyaku made considerable
money from garbage that came falling down this chute.

There were bits of broken glass strewn in the waste heaps in the
collection area, and the bare concrete floor was exposed in some parts.
If the boys came falling down here, their bones would shatter. \emph{I can let
that happen to unwanted machines, but they're human. I can't let their
bones break.}

"Hurry up, old man. Stop loafing."

"R-Right." Rikiga waddled over, and grabbed a mat.

"We're gonna line these up. Stack them. Hurry!"

"Right\el but Inukashi, are Shion and them really coming back? How are
they---"

"Shut up and get a move on! Quickly!"

Inukashi strained his ears while moving the mats. \emph{Come back, Nezumi.
Come back, Shion.}

"Inukashi, the smoke is getting bad!" Rikiga yelled. The small room was
being swallowed up in white smoke.

\emph{Just come back, Nezumi, Shion.}

\emph{Please, just come home.}

He heard the wind rumbling through the chute.

\emph{Come home.}

\emph{Please, come home.}

\emph{O Lord, watch over them.} Inukashi clasped his hands together, and prayed
to God for the first time in his life. \emph{O Lord---}