% !TeX spellcheck = en_US

\chapter{Sin and sanctity}

\myepigraph{Humans are shapeshifters; there's naught that's not in this
world.}{Ihara Saikaku, 'Saikaku's Tales from Various
Provinces'}

\lettrine{T}{he slope} that Shion had skidded down turned out to be an enormous
pillar tipped over on its side. Upon closer inspection, he could see
that the base was carved out with the figures of several women robed in
thin, translucent cloth. Rusty metal foundations were all that remained
of what probably used to be an arched ceiling, and several withered
vines feebly clung to them. The wall had collapsed entirely, and chunks
of stone in all sizes were scattered hither and thither.

If he had accidentally struck his head on one of those--- Shion shuddered.

The scene before his eyes was something Shion was seeing for the first
time. Naturally, there were no such dilapidated buildings to be found in
No. 6. All buildings were built accordingly to their purpose, with
efficiency and functionality prioritized above all. Remains such as
these, which had drifted through time, exposed to the wind and rain,
were synonymous to illusion, and were not a product of reality.

He drew a breath, and let his gaze wander about him again. The wind
whipped about in a fierce dance. As if continuing its journey toward yet
a more ruinous state, a portion of the wall made a dry, crackling sound
as it crumbled right before Shion's eyes.

"Nezumi," he called. It wasn't a plea for help. He had just wanted to
call his name. "You're there, aren't you? Come out already."

"You're getting sharper," said a voice somewhere from above. Shion
looked up to see Nezumi sitting on a window ledge several metres up.
Nothing remained of the window itself except for the frame. The
rectangular void, which was bordered in black, looked like a yawning
mouth on the face of the crumbling wall, opened wide to let out a
scream.

Nezumi jumped down from his spot several metres up. He landed squarely
on the soft dirt.

"You're light on your feet," Shion commented.

"I am most humbled by your gracious compliments, your Highness."

"Quite something," Shion quipped. "Not to mention how amazingly fast you
seem to disappear when you get into a tight spot."

Nezumi shrugged his shoulders slightly, and gave a soft chuckle.

"You've even learned how to be sarcastic. Quite something, yourself.
Grown up a bit, haven't you?"

"I must've gotten ten years' worth of experience from walking through
that market."

Nezumi's hand waved languidly in front of Shion's face.

"So you nearly got mowed down by a gun, got seduced by a woman, tripped
over a dead body, and got hit on by an old man. Well, I guess for a
little boy like you, that counts for about ten years. But---"

"Hm?"

"You really \emph{have} gotten better at running away," Nezumi said
approvingly. "Way better than your last try with the fat guy."

"The Disposers, you mean?"

"Yup. It looked like that geezer was seriously into you. To be honest, I
thought you'd be good as gone if you managed to get dragged inside."

"You disappeared awfully fast for that."

"I don't get involved in more trouble than I need to," Nezumi laughed
silently. "But you did a good job of making a getaway. Let me tell you,
though, those guys don't give up easily. And you stand out on your own
as it is. I'd be careful if I were you."

"It is with utmost gratitude that I accept your words of advice, your
Majesty."

"Oh dear, and your comebacks have gotten better too," Nezumi laughed out
loud this time, but softly. The thin dog was sprawled out on the ground,
wagging its tail from side to side. The squalor of the market felt like
a dream. A silent stillness pervaded the place as if the mountains of
debris were absorbing all the sound around them.

"Nezumi, where are we?"

"Take a guess."

"I don't have a clue--- looks like it used to be a pretty big building\el "

"It's a hotel. There used to be a hospital across from here. Beside that
was a playhouse, I think--- I don't know much about this place, either."

A hotel, a hospital, a playhouse\el 

"So this really used to be a decent town."

"I guess so. I mean I don't really know what a decent town is supposed
to look like, but there probably weren't bodies everywhere, to say the
least. At least back then."

"Back then?"

"Before No. 6 was established."

Shion wasn't surprised. He had expected as much. He closed his fingers
lightly over his palm.

"I've learned about the history of No. 6, and how it came to be. It was
one of the very first classes we took."

"Mm-hmm," Nezumi replied offhandedly.

"A series of large-scale wars erupted all over the world as the last
century was coming to a close. It was before neither of us were born. As
a result of the massive amount of bombs and biological weapons that were
used, the land was utterly destroyed and the climate deteriorated
severely. The majority of all landmasses, with just a few tiny
exceptions, lost all ability to sustain human life. There were an
enormous amount of casualties. The people that remained vowed never to
war again, and in those regions that were spared destruction, they
founded six utopian cities. And No. 6 was one of them."

"That's what you learned."

"Yeah."

"And you've always believed it to be true?"

"That's the truth that we were taught to believe."

"You remember what you said on the day we first met?" Nezumi said. "You
said you didn't think No. 6 was perfect."

"I did."

"Was that a lie?"

"No," Shion answered. "I honestly thought so. But before I met you, I
didn't realize that was how I really felt. I met you--- and that's when I
finally knew."

He had met Nezumi, and realized. He had finally heard the sound of his
own conscience creak as it strained against its shackles. He had always
felt suffocated. In No. 6, he had everything. He had plenty of food, a
warm bed, and full access to medical care at his fingertips. And it
didn't stop there--- at the age of two, when he had been acknowledged as a
top-ranking individual in his Examinations, he had acquired the
privilege to live in the luxury neighbourhood of Chronos. All its
residents were provided a first-class environment on many facets.

Before he had met Nezumi on that stormy night of his twelfth birthday,
he had been surrounded by everything he could wish for, all of
first-class quality. But that day, gazing at the wind and rain that
rumbled out his window, what Shion had felt was a destructive impulse
that seared him to the very core.

He had felt unbearably suppressed. Like a corralled animal that
instinctively rams itself against the fence, Shion had wanted to be
released from the invisible cage that trapped him. At the very bottom of
the deepest part of Shion's subconscious, a voice had been resounding.

\myspace

\emph{This is a facade.\\
	Here, everything is given to you.\\
	But there is nothing here.\\
	You can't live here anymore.\\
	So escape.}

\myspace

\emph{Break it.\\
	Destroy it.\\
	Destroy what?\\
	Everything.\\
	Everything?}

\myspace

When the voice within him had overlapped with Nezumi's words, Shion had
finally understood. \emph{I don't know the truth. I don't know anything.}

Nezumi's gaze slid away from Shion as he turned his back to him. Shion
grabbed his arm.

"Nezumi, tell me."

\emph{Tell me the truth. Not a lie, or a haphazard excuse. Tell me its true
form--- of the Holy City, of No. 6.}

His fingers were shaken off roughly.

"I'm not your nanny. If you want to know, then find out for yourself."

He was shaken off again. No matter how many times he tried to grasp at
Nezumi, he was always pushed away. Rejected ruthlessly. But still, Shion
kept extending his hand.

The dog was pressing its body against him. It was so thin its ribs
jutted out, but it was still warm. Very warm. It had the warmth of
something who was alive.

"Are you feeling sorry for me, by any chance?"

The dog twitched its drooping, light-brown ear. For a moment, it looked
like it grinned at him. Then it lumbered ahead of him to Nezumi's side.
Nezumi's hand slowly and gently petted the dog's head.

"So you're nice to dogs, huh."

"Dogs don't act like babies."

"But dogs can't sew."

"What?"

"Dogs can't suture a wound. I noticed the suturing kit was still in tact
in the emergency case. If you ever get hurt again, I'll sew that wound
right up for you."

"Why, thank you," Nezumi said sarcastically. "Your offer is so great
it's sending chills down my back. That face came into my dreams for
quite a while after that day, you know."

"Did I look that great?"

"You were grinning. You had this look on your face like you were having
the time of your life. Every time I dreamt about it I had nightmares."

"Well, it was the first time in my life doing a suture. I remember being
really excited. Say," said Shion enthusiastically. "So did you take out
the stitches yourself?"

"Of course. It was easier than making soup."

"Did it leave a scar?"

"Yeah. But I won't show you."

Shion stuck out his lip.

"Don't be stingy."

Watch your feet, Nezumi interrupted loudly.

"The stairs start here. We're going up."

The sun was setting lower, and darkness was setting in thickly. A large
part of the stairs had crumbled away like the wall, and what was left of
it wound upwards in a wide clockwise curve. Here, the ceiling was still
in tact. It looked like it had originally been painted white, and
although most of it had peeled away, there were white flecks of paint
still left over here and there. A chandelier was hanging over the
stairwell, and to Shion's surprise, it was relatively undamaged.

"So this place really was a hotel."

"It still is."

"Huh?"

"This place is still used as a hotel."

"No way."

They emerged at the top of the stairs and were greeted by a large,
vacant chamber. It had probably been the lobby. There walls were set in
glass from floor to ceiling. The panes in the top half had been
shattered and strewn over the floor, but the bottom panes still remained
unbroken. Ripped and faded drapes hung lifelessly over them. Vines that
had probably intruded through the broken windows clung densely to the
walls, criss-crossed like a network of capillaries. Leaves were falling
from them, adding to the thick layer that had already carpeted the
floor.

It was thanks to a dim light in the room that Shion had been able to
decipher this much despite the settling darkness. It came from a candle
that was burning on top of a stone table.

"Nezumi, do you smell something?"

"The candle burning, maybe?"

"No, it's not wax. It smells--- almost like some animal\el "

Nezumi gave a laugh.

"You really have come a long way. Your nose has gotten sharper. Now
let's try working on your eyesight. Look."

"Ah---"

A shadow moved in the darkness where the light could not reach. It was
not a human. It had four legs, two pointed ears, and was growling
menacingly.

"A dog," he whispered.

It was a large dog, covered in short, dark-brown fur, with a fierce
glint in its eye. Its throat was rumbling in a low growl. Shion took a
step backwards.

"He's not the only one," Nezumi added.

There was a note of amusement in his voice--- he was enjoying Shion's
reaction. Shion resisted the urge to turn and give Nezumi a glare. He
had no attention to spare for that.

With the first dog in the lead, several dogs of all shapes, sizes, and
colours were emerging from the darkness. They were far from what would
be called pets. They were dirty, their eyes glinted viciously, and their
teeth were bared.

"Is this a nest for wild dogs?"

"Might be. What do you wanna do? Run away? If you don't decide soon,
you'll get your throat torn out."

The dark-brown dog approached him warily. It wasn't growling anymore. It
silently but steadily drew up to him, without ever lowering its gaze.

Shion gazed back into the set of caramel eyes that were the same colour
as its fur. Behind the savage light in its eyes, there resided something
surprisingly gentle. Shion could feel its presence there.

\emph{Intellect?}

Shion lowered himself into a kneel. The shattered glass crunched
underneath his denim-clad knee. Nezumi fidgeted. Shion didn't move.
Crouched on the ground, he stared straight at the dog.

The dog stopped. It stood still in front of him. It opened its mouth,
lolling its pink tongue, and licked the tip of Shion's nose. Then it lay
down on the spot, and gave a yawn. All the other dogs began moving about
on their own. Some began to groom each other, others sprawled out on the
floor; still others began sniffing at their surroundings, and none of
them seemed to have any concern for Shion's presence.

"I passed the interview," Shion grinned as he looked up at Nezumi.
Nezumi clicked his tongue, and turned away.

"Didn't the wild dogs scare you at all?" he said sourly.

"They did. But wild dogs don't light candles."

Nezumi sniffed in derision. "You've never even seen a candle before."

"I just did for the first time. It was brighter than I imagined it to
be. Hey, Nezumi, does someone live here?"

Laughter rang out. It echoed off the ruins, and faded into the darkness.

"Pleased to have ya, guest."

It was a human voice, but he couldn't see who it belonged to. The voice
was echoing from so many directions that he couldn't tell from whence it
came. It ricocheted and overlapped in countless layers. Just listening
to it made him feel dizzy.

"Stop shitting around." Nezumi bent down. He picked up a piece of
debris, and flung it straight into the darkness where the dogs had come
from. It was sucked into the gloom, but he could hear a definite sound
in the distance as it hit the floor.

"Watch it." The focus of the voice settled to one point in the darkness.
It was a young voice. A light flickered in the inky-black pool.

"That's some violent way to greet someone, Nezumi. You've got no
manners."

"You could use some manners yourself, if that was what you call the
proper way to welcome a guest."

A figure was weaving through the dogs toward them with a candleholder.
Even by the candle's flame, the person looked like he was thrown in
shadow.

His waist-length hair, his eyes, his trousers that were ripped at the
knees, and his baggy sweater were all black. He had tan skin.

Was he a boy? A girl?\footnote{Japanese pronouns make no gender distinction; Shion assumes Inukashi is male}

Shion couldn't make the distinction. The stranger's pointed chin and
round eyes reminded him of a small rodent. He was very small and thin,
and reached only up to about Shion's shoulders in height.

"He lives here," Nezumi said. "I don't know his real name. We just call
him Inukashi."

"Like--- dog lender\footnote{\jp{犬貸し}; literally}?"

"That's the one," the stranger answered. "Lending dogs is my trade. Nice
to meet ya, Shion." Inukashi grinned. Shion was taken by surprise.

"You know my name."

"I'm quick to catch onto things around here. As long as I have my dogs,
getting any information about these parts is a piece of cake. I know
your name, and I know that you kicked the Disposer guy in the nuts
before you came running here. This guy told me everything."

The emaciated dog wagged its tail from its place beside Inukashi.

"You can speak with dogs?"

"I'll hold conversations with anyone, as long as they're not human.
Whenever you want any information, feel free to come to me." Inukashi
extended his hand with a smile. He was wearing a thick, silver ring. It
matched well with his tan skin.

"Nice to meet you, too." Shion also extended his own hand.

It had been a while since he had shaken hands with someone. So far, his
experiences had only consisted of running away, yelling, or rolling
around. Inukashi's face was open and affectionate, and reminded him of a
puppy.

A sharp pain ran through his palm.

"Agh!"

Shion withdrew his hand hastily. At the base of his index finger, there
was a small wound about the size of a pinprick. Blood was already
starting to well up from it. It ran down the palm of his hand in a
single, red stream. He thought he felt the tips of his fingers go numb.

Inukashi threw his head back and cackled.

"What was that for?" Shion said in disbelief.

"'What was that for' he says!" Inukashi crowed. "Haha, what a surprise!
You fell right into that handshake, and you're turning on \emph{me} and asking
me 'what was that for'? Classic."

Inukashi showed his palm to Shion, and bent his fingers slightly. A tiny
needle-tip poked out of the middle of the ring. When he straightened his
fingers, it retracted again.

"It's been used as an assassination weapon for ages. Well, the proper
way to use it would be to coat the needle-tip with poison. But I haven't
done anything to these, so you can relax."

Shion pressed hard on the base of his finger. He licked his dry lips,
and opened his mouth in question.

"Why would you do that?"

"Oh dear," said Inukashi exaggeratedly. "Now he's asking me, \emph{why would
you do that?}"

Inukashi's gaze moved to Nezumi, who stood by silently.

"Haven't you taught this guy \emph{anything} about how to live here?"

"That's not my responsibility."

"You picked him up and brought him home, didn't you? If you're gonna
pick up a stray, you gotta take care of him properly. He'll make himself
useful one day."

"I'm not so sure about that."

Inukashi laughed again.

"If he doesn't, just eat him. Or is he---" Inukashi's gaze travelled to
Shion's hair. "He's got interesting hair. Has he got issues, or what?"

Nezumi turned up the corner of his mouth and answered shortly.

"As many issues as the dogs you have. Too many to count."

"Uh-huh. So the rumours were true. You really are keeping a young boy as
a pet." Inukashi's face turned serious as he stared at Shion from head
to toe. It was a bold and insolent gaze. The thin dog suddenly raised
itself off the floor, and barked once. Two furry brown balls came
tumbling out of the darkness. They were puppies, probably a month or two
old. Their noses and tails were tipped with white. The skinny dog lay
down again, showing its belly. Its teats drooped pitifully. The puppies
eagerly latched themselves onto them. Their round bottoms wagged from
side to side.

"Wow, puppies!" Shion exclaimed. He gently petted their backs so not to
get in the way of their feeding. "Wow, Nezumi, look. They're so soft.
Why don't you try petting them too?"

"No thanks."

"But look, they're puppies. So you're a mom, huh. It must be tough for
you, raising all these kids."

Inukashi furrowed his brow and retreated half a step away from Shion.

"What's up with this guy? What's he doing having a serious conversation
with a dog? Is he unbalanced or something?"

Nezumi pointed to his temple.

"He's a little vacant up here. It comes naturally to him."

"Comes naturally, huh? Why are you taking care of this weirdo?"

"Like I said, he's got issues. And he might not look it, but he's pretty
good with his hands. He can even pull off a simple surgery."

"I don't care what he can do, I wouldn't have any of it. He'd never be
anything more than a dead weight."

"Couldn't have said it better myself," replied Nezumi. "So have you
looked up what I asked you to?"

"Of course. A job's a job. Let's go upstairs." Inukashi took his candle
holder in his other hand and disappeared back into the darkness. There
were more stairs. Like the ones before, they wound upwards in a gentle
curve. These ones weren't crumbled as badly. The rubble was cleared with
a space just wide enough for a person to walk through.

"Oh---" Shion murmured in surprise as they emerged at the top of the
stairs.

A narrow hallway ran straight before them. There was a person curled up
at the edge of the hall. Beside him were a pair of dogs. They had long
white fur, and they were nestled closely against the person as if to
protect him. Shion squinted his eyes, and he could make out several more
of these groups of people and dogs curled up together.

"What are these people doing?"

Inukashi answered over his shoulder.

"They're my customers."

"Customers?"

"This place used to be a hotel, and it still is now. Rumour says this
place used to be quite grand, but now it's just somewhere people can
bunk for a bit of money if they have nowhere to stay for the night. We
have beds, too. If you can cough up the cash, I can get them ready for
ya."

"What about those dogs?"

"I rent them out for heating. It can get pretty cold at night, but it's
not so bad if you curl up with a dog or two like them. You won't freeze
to death, at least."

"So that's where 'dog-lender' comes from."

"Dogs are useful for other things too. They'll collect information,
guard your property, or carry your stuff. They'll do anything. They're
probably much more useful than a natural airhead like you."

Nezumi clucked his tongue.

"That's my line."

At the very end of the hall was a wooden door. Beyond it was a small
room, with a low ceiling and no windows. A round table stood in the
centre of it. Inukashi placed the candle holder down, and spread an old
map over the surface of the table.

"This map that Nezumi got his hands on is from around twenty years ago.
This is my hotel here, and LK-3000 should be somewhere around here."

"Latch Building isn't marked on this map," Nezumi added. "I asked
Inukashi to look into that."

He ran a finger lightly over the map. It was a casual gesture, but one
of understated elegance. It was a movement calculated and honed to
perfection, fully aware of watching eyes.

"What?" Nezumi tilted his head at Shion's gaze.

"No--- I just thought that sometimes you move really elegantly."

"Huh?"

"Sometimes your gestures are really captivating. I couldn't help but
stare."

Inukashi looked up at them, his gaze alternating between Nezumi and
Shion's face.

"How can you say something like that in front of his face?" he asked in
disbelief. "Nezumi, this guy really \emph{is} naturally oblivious. How do you
put up with him?"

"I manage somehow."

"Shion, haven't you heard what this guy does for a job?"

"No."

Inukashi thrust his open palm toward Shion.

"If you pay up, I can tell you. Selling information is another one of my
trades."

"I don't have any money."

"What? You don't? Nezumi, you're taking care of a penniless bum?"
Inukashi's eyes narrowed. "So he has weird hair, he's an airhead, shakes
hands without a second thought, and has no money--- Nezumi, where did you
bring him from?"

"Where do you think?"

"I'm asking the question here."

"If you pay me, I can tell you."

"Don't mess around," Inukashi snapped. "You're the one who should be
paying up."

Nezumi took out a small leather pouch from his pocket.

"There you go."

The contents of the pouch fell on top of the map. It was a small, grey
mouse.

"It's a mico-robot. It has audio and video recognition and recording
sensors, and it's mounted with a solar-powered micro-battery. One charge
will make it last for thirty-six hours. It can move around freely to
gather information. You'll find plenty of use for the places your dogs
can't get into. You were telling me you wanted one, right?"

Inukashi nodded wordlessly. He moved his head up and down in an
exaggerated way, much like how a small child would nod.

"Are you really going to give this to me?" he asked.

"Yeah. If your information is worth it."

Nezumi put the mouse back into the pouch again, and clenched it lightly.
Inukashi's tone of voice sped up.

"Fine. I'll jump right to the conclusion. Latch Building doesn't exist."

"Is that all you've got?"

"Of course not. It doesn't exist, but there's something that goes by
that name."

"Latch Building?"

"Latch Bill, and it's the name of a newspaper. A long time ago, there
used to be a newspaper company by that name, right behind this hotel. It
went bankrupt and got torn down to be made into a parking lot for this
place. It happened before this map was made, which is why it doesn't
exist."

"So Latch Bill 3F means---"

"If it means the 3rd floor of that newspaper company, then---"

"Then?"

"I have no idea," Inukashi said abruptly. "There's no way for me to know
what could have been on the 3rd floor of a newspaper that went out of
business twenty-something years ago. You should meet up directly with
the guy who has ties to that place."

"There's someone with ties to it?"

"Yeah. I got the location of one guy who had ties to Latch Bill. And
said guy also has interesting connections to No. 6. Listen carefully---"

Nezumi leaned forward. Shion swallowed.

\mybreak

No. 6 was shrouded in the red glow of the sunset. Nothing was more
exquisite than the sunset of late autumn. The man let out a satisfied
sigh.

What beauty this was, what a tranquil scene. The Forest Park only days
ago had been showing a vivid contrast between turning leaves and those
that were still green, but now most of the trees had lost their leaves.
It was a peaceful kind of beauty, of nature that was quietly preparing
for the approaching winter.

He had gathered here the pinnacles of modern science; he had nature
under his management, and the ultimate utopian city was nearing its
completion. People were fortunate to be able to be born, raised, and
live to an old age here. They were the chosen ones.

There was no such thing as misfortune here. Even the occasional
hurricane that came upon them was an abundant source of natural
irrigation that watered the agricultural and farming pastures that
spread from East to Southern Blocks.

All it needed was a little more. A little more, and the land of the gods
would finally be complete. A utopia, where only the chosen ones would
reside. It only needed a little more.

"You really must love the view from here." A voice said behind him, with
the hint of a laugh.

"Wouldn't you agree that it's excellent?"

The man that had laughed silently shook his head in an expression of
refusal. He was wearing a white lab coat.

"I prefer the micro-universe. The world of bacteria, microbes, neurons,
macrophages, viruses. When you get to something like viruses, you're at
the nanometre scale. You could only see them through an electron
microscope. They're very beautiful, you know. The really beautiful
things are things you can't see with the naked eye. There's only so much
that your eyes can show you as is."

"That's always been your mantra, hasn't it. You've been saying that for
as long as I can remember."

"It's my unchanging mantra."

"And you also still drink strong coffee before and after supper."

"That's another unchanging habit of mine."

The men looked at each other and chuckled quietly. They had known each
other for decades. They knew well what part of the other had changed,
and what remained the same.

"So what now? I think it's about time." The man raised his custom-made
coffee cup. The coffee in it remained steaming and fragrant as if it had
just been poured, thanks to the adjustment mechanism built into the cup.
The man robed in the lab coat licked his bottom lip. It was his habit
when he was immersed in thought.

"You're talking about collecting more samples," he said.

"Live ones."

"Yes, we've already collected a few dead sample bodies. But we can't say
they're nearly enough, though. We want a few more."

"If you want, I can find ways to go about it. How many do you need?"

"I'll report to you later with how many we want for each condition based
on sex, age, and history of illness."

"That would be great. So how about the live ones? Do you want me to go
into collection preparation?"

"No, I need more time."

"Why?"

"The data from the collected samples is still incomplete. We're still
running analyses and uploading it to the database. I want to flesh that
out first."

"It's taking unusually long for you. How rare."

"If we were able to do it publicly, things would go much more smoothly.
But doing this much under wraps is going to take double the time. I want
you to keep that in mind. Besides, we should have entered the live
samples stage only after the dead sample database was complete. That was
an unexpected occurrence--- we have to investigate as to why that happened
in this stage. It'll all take time\el "

"I know," the man conceded. "I'm not rushing you. Make sure that
everything gets carried out carefully, thoroughly, and perfectly. This
is all connected to No. 6's future roots. Yes--- and this is the final
piece."

"The final piece to make this place a Holy City in the actual sense,
hmm." The lab coat chuckled. "Cheers to the Great Leader." He raised his
coffee cup lightly.

"And cheers to the Great Brain behind it all." The man lifted his cup as
well. There was a moment of silence. The man in the lab coat spoke with
a slightly lowered voice.

"But is it really good to go?"

"What?"

"Collection of the living sample. I heard a certain Rat is with him."

The man placed his coffee cup down, and wiped his lips with his fingers.

"It's just one rat. It should barely be an obstacle at all."

"If you could get him alive as well--- I'm interested in him."

"You want to cut him open?"

"An autopsy, hmm. That would be rather nice. I would like to investigate
every corner of his body. But before that--- we need more samples."

The man in the lab coat suddenly stood up, and began soundlessly pacing
on the thick carpet. He strode impatiently, taking large steps with his
hands behind his back. It was a bad habit of his that he had since he
was young. Following the movements of the tall lab-coated man with his
gaze, the man reclined deeply into his desk chair.

"Yes that's the main issue," the lab coat continued. "The total number
of samples is severely lacking. We need more, Fennec." Fennec was a
nickname that had been given to the man when he was young. A desert fox.
It had the smallest body and largest ears of its kind. Its ears, which
could reach up to fifteen centimetres long, was not only well-suited for
releasing body heat effectively, but possessed keen hearing ability that
could detect even a grasshopper hopping in the sand. He had also heard
that, contrary to its cute appearance, it had a vicious personality.

It was not a nickname that he liked very much. He had not used it, nor
been called by it for quite some time now. He had almost forgotten about
it. But he didn't feel the same repulsion toward it as he did in his
younger days. He even felt somewhat fond about it now.

Fennec. The desert fox. Not bad.

"We don't have enough living samples either. I'd want at least two, no,
three more on hand. But that could be difficult\el "

The man in the lab coat continued muttering to himself, and paced
increasingly quickly. He was completely oblivious to everything else
around him. He had probably not even realized that he had called the man
Fennec. He had been like that since he was young. His research and
experiments, his speculation, his satisfaction. It was only ever about
him. He had never shown any interest toward things external to him. He
showed no attachments to power, money or women. He had no need for
faith, philosophy or morals in his life. A brain of rare intelligence
and a vacant soul\el 

\emph{---Which is why he's useful all the more.}

The man trained his gaze on the pacing figure clad in the lab coat, and
smiled.

\emph{---You would have no use for a soul. If you did, it would only be to
declare your loyalty to me.}

The lab coat stopped pacing.

"Fennec, let's make another living sample. I want a female this time. It
might be difficult. Yes, at this stage it will be very difficult\el but
that's why we should prepare one ahead of time."

"Let's do it."

"There's a great risk of failure, however---"

"Failure and sacrifice are all things we must go through in order to
gain progress. Don't worry, we'll be able to overcome it to hold the
final piece in our hands."

"I guess you're right," the lab coat agreed.

"Let's have supper then, shall we? This probably won't pique your
interest much, but I've had it all prepared, and the main course will be
lamb. I've also a remarkable wine to go with."

"And coffee after the meal?"

"Of course. But I beg you, at least take off that lab coat while we
eat."

The man lightly clapped the lab coat on the shoulder. Then he gave a
sidelong glance at the scene out his window. Beyond the pane of thick,
spotless glass, the stars were beginning to twinkle.

\mybreak

"We're here."

Nezumi's feet stopped. They were standing in front of a three-storey
building. At least, it resembled more of a building than the ruins that
constituted the hotel, but in the sense that it was also falling apart,
they were none too different.

The arched entranceway and the red brick walls had probably once carried
an air of pomp, but were now strangled by vines, crumbled in places, and
radiating an aura of dilapidation. Nezumi jerked his chin upwards.

"Someone's home."

\myspace

There was a light in the third-floor centre window. From its brightness,
it was most likely an electric lamp. That meant there was electricity
running in this building.

They pushed the wooden doors open, and entered inside. There were no
signs of people on the first or second floors. The stairs, which were
also wooden, creaked loudly with each step they took.

If Inukashi's tip was a good one, a former reporter from the Latch Bill
newspaper was supposed to be living here.

They climbed up to the third floor. There was light spilling out from a
crack of the open door into the wooden hallway, which was carpeted with
a thick layer of dust. In the pool of light, there were several empty
glass bottles. It was easy to tell what these bottles used to hold.
Shion didn't have to pick one up to check, for the strong smell of
alcohol filled the air around them. In a darkened corner of the hallway,
there were towering piles of bundled papers, and empty cans littered
about it. Only the door from which the light was spilling was neither
dirty nor broken, though it was very old. Shion raised his hand to
knock, but Nezumi held him back.

"What's wrong?"

"No, it's just--- the air is strange."

"Air? What do you---"

Before Shion could finish his sentence, he heard a yell from inside the
room. It belonged to a man. There was the sound of furniture being
knocked over. A high-pitched voice screaming angrily. He could hear the
sound of glass being smashed.

"Sounds serious. What now, Shion?"

"What do you mean, what now?"

"It looks like they're busy at the moment. Should we come back another
day?"

"As if."

"Thought so."

There was a loud noise again. A man's deep voice yelled out for help.
Shion tried to burst into the room, but Nezumi restrained him and opened
the door.

The room was well-lit by a large lamp. It was the brightest light Shion
had seen since coming to the West Block. The light was illuminating
clearly every corner of the room. By the window there was a large desk,
and against the wall was a rather unimpressive textile sofa. The floor
was covered, again, with bundles of paper and books that were piled up
or scattered haphazardly. But these were all things he had noticed when
he had taken a good look around the room much later on. What Shion saw
immediately over Nezumi's shoulder were two people entangled with each
other. It was a man and a woman. The man was wearing pants, but his
upper body was naked. The woman was clad all in black. Her hair, cut
straight across at the shoulders, was also black. She was straddling the
man. The hem of her slitted skirt had flipped up to reveal her thigh.
She had well-endowed, curvy body. She had a round face, round nose and
round eyes. Her face was tense.

The woman swung her right hand up.

"Help!" The man yelled. Shion realized that there was a knife in the
woman's hand. Nezumi \emph{tsk}ed his tongue shortly.

"You good-for-nothing!" The woman shouted. Nezumi moved at the same
time. Soundlessly and in a flash, he was holding the woman's wrist
mid-swing. Without a word, he twisted it.

The knife clattered to the floor. Shion hastily picked it up. He spotted
a red knife pouch in the corner of his vision. He grabbed it
reflexively, and sheathed the blade. He felt relieved.

"What the hell are you doing?" The woman screeched shrilly. She had
fallen backwards on her bottom from being dragged by Nezumi.

"I don't think you should be swinging around a toy like this, Miss. It's
dangerous," Nezumi said softly.

"Leave me alone. What's any of this got to do with you? This
good-for-nothing, shitbag of a womanizer deserves to die."

The woman dissolved into tears on the floor. Still holding the knife,
Shion looked down at her hunched back. He didn't know what to do. There
was nothing in Shion's manual that told him how to deal with this kind
of situation. Nezumi knelt down, and gently stroked her back as it shook
with her sobs. He lowered his voice into a quiet murmur.

"Don't cry. No--- you \emph{should} cry. Cry to your heart's content. You'll feel
better that way. Go on, cry---"

It was like a lullaby. His whisper was deep and soothing, and soaked
into Shion's soul like the sound of the rain that seeped into the
basement room. He could see the woman's agitation subside as its
gentleness and tranquility washed over her. But there was no gentleness
or tranquility in Nezumi's gaze. After taking a quick glance around the
room, his gaze stopped at the middle-aged man who was gasping,
half-naked on the floor. Then his eyes flicked up to Shion, who was
stock-still, rooted to the spot. Shion took a step forward.

"Um--- are you Rikiga-san? The one who used to work for the Latch Bill
newspaper?"

The man raised himself unsteadily and began to put his arms through a
shirt that had been draped over the sofa. Though not exactly obese, he
was rather fleshy around the shoulders and waist. There was a white scar
that ran diagonally across under his right shoulder blade.

"Uh--- have we gotten the wrong person?" Shion asked uncertainly. "We've
come here today because we heard we could meet a Rikiga-san here---"

"You've got the right one."

It was the woman who had answered. Her face was a sopping mess of tears,
sweat and snot, but she was not crying anymore.

"This good-for-nothing liar goes by that name. Once upon a time he was a
newspaper reporter, but now this shitty excuse for a man is reduced to
making shitty porno magazines to pay for his liquor habit."

"And who's the one who had a hysteric fit when she got dumped by said
excuse for a man, huh?" retorted the man who had been called Rikiga.

"What're you talking about?" the woman shot back. "You're the one who
said you wanted to get married!"

"And I'm telling you, issues have come up, and I can't get married to
you anymore."

"What issues?"

"Well--- ah, um--- you see\el "

"If you're gonna try to trick me, at least take the time to think up a
proper lie. I'm not one to be messed with."

Sparked to anger by her own words, the woman's wrath threatened to boil
over again. She suddenly lunged a Shion, breathing fast.

"Give me my knife back!"

"No---I can't do that---" Shion resisted. "Stop, please. It's dangerous."

"I said give the damn thing back. What 'issues', huh? Let's hear your
excuse. I can't believe I'm being shitted like this. I'm gonna kill
you."

"Stop, watch it---"

Nezumi stood up. With one step, he strode to Rikiga's side and put a
hand on his shoulder.

"Father, is she going to be our new mother from now on?"

The woman froze. Her mouth gaped open, and her eyelid twitched.

"Father?"

Nezumi nodded with an affectionate smile.

"Yes. We're his sons."

"You--- you had kids? I've never heard anything about that before."

The woman's voice turned hoarse. Rikiga blinked.

"Father and Mother separated a long time ago," Nezumi explained. "But
Mother passed away just last month, and so we came back to live with
Father. We've already heard before that Father has someone he loves. But
he said he would give up getting married so that we could live together
as a family again, the three of us. Right, Shion-niisan\footnote{suffix, older brother}?"

"Huh?"

"We came all the way here searching for Father, right?"

"What? Oh--- yes, we have. We're his sons. Nice to meet you."

Rikiga cleared his throat a few times.

"---That's how it is. They're my sons. I've had to take them into my care
now\el raise these two on my own. Living will become much more
difficult. I couldn't put you through that, honey. I love you, I love
you so much. But these kids need their father\el I couldn't burden you
by asking you to be their mother. I had no choice but to ask you to
break up with me."

"So that was what came up\el "

"Well--- pretty much."

The woman ran a hand through her hair, and sighed. "So that's how it
is."

"That's how it is."

The woman ran a hand through her hair again, and picked up her coat and
purse, which were lying on the floor. She looked at Shion, and drew her
chin back slightly.

"You have strange hair. Is it a wig?"

"Oh, um--- stuff happened\el "

"More issues? Like father like son, you guys must love your issues. Oh
well, fine. If that's what's going on, I'll break up with you. As if I
would want a middle-aged man with kids anyway."

The woman gave an energetic wave of her hand.

"Good-bye, then. It was fun while it lasted."

The door closed. Shion let the knife in his hand drop to the floor. His
palms were sweaty from nerves.

Rikiga lifted the chair and placed it upright on the floor, and began to
gather the pieces of broken glass. There had probably been some kind of
drink in it, for its contents had made a stain on the carpet that
emitted such an overpowering smell of alcohol that it made Shion feel
ill.

"Good god, she certainly let herself go," grumbled Rikiga. "It was fun
while it lasted, huh? Putting on a cool face at the last minute. Geez."

Rikiga looked alternately at Shion and Nezumi, and grinned.

"You saved me from the gallows. First, let me give you my thanks."

He had strong, broad shoulders and considerable height. The bridge of
his nose was high, and it suited his moustache well. His face was
neither handsome nor ugly. It was a face that was both energetic with
optimism and worn with hardship; it was a face of cunning, and steely,
resilient willpower.

"Your acting could have been better, though. Especially for a star of
the show like you, Eve."

Nezumi scooped the knife off the floor and smiled thinly.

"You know about me?"

"I'm your fan. I went to see your show last week."

"That's nice to hear, but I didn't appear in any shows last week."

"Really? Well, anyway, we wanted to do a special feature in our magazine
about you. We asked your manager to get an interview with you, but he
turned us down."

"He probably would, for a magazine like this." Nezumi's fingers flipped
casually through the pages. The cover was a photo of a naked woman. On
the whole, she was rather blurry. All the other pages were somewhat
similar. Naked women, half-naked men. Lewdness and provocation
overflowed in the flimsily-bound pages of the magazine.

"It's the go-to for young people," Rikiga said. "Teaches them everything
from birth control to picking up women."

"You should do a feature about the right way to dump a woman next, old
man."

Nezumi tossed the magazine aside. Rikiga raised his hands in an
exaggerated gesture.

"Ouch Eve, that was pretty harsh. I thought you'd be more of a pansy."

"Nice to hear that coming from someone who was pinned on the floor by a
woman just a minute ago."

"I was drunk, alright? And she suddenly just jumped at me--- but I never
would've guessed that she had a knife on her. Scary things, those
women."

Shion took half a step forward.

"Eve\el is that your real name, Nezumi?"

"No way. It's just for work."

"Your work\el so you're a stage actor."

"Nothing half as classy as that. Maybe a couple steps above this
magazine."

"But--- oh," Shion murmured in realization. "So that's why you speak and
move so gracefully."

\emph{A spotlight shines on a dark stage, illuminating a single actor as he
floats up out of the darkness. Captivating the eyes, ears, and souls of
all who watch, his voice rings out--- at times, with a soaring, elegant
air; at times, with a pained tremor like a wind that whistles low to the
ground.}

Nezumi snorted.

"What're you imagining, Shion? We're talking about a playhouse here, in
the West Block. People who've got a little spare cash to spend come out
to forget their worries for a little while. We haven't got any
embroidered drop curtains, decent costumes, or stage props. It's mostly
impromptu song or dance. That's it."

"But it still makes people forget their worries, right?"

"Huh?"

Shion was gazing unblinkingly at Nezumi. In these past few hours, he had
experienced almost as much as--- no--- perhaps even more than what he had
seen and heard his entire life. Of course, this was still only just a
glimpse. But he had caught a glimpse of how harsh and brutal it was just
to live a day, an hour, even a moment, in this world. If these people,
in their brief moment of respite, chose to go to this place of their own
free will, and that was where Nezumi was, then he thought it was
amazing. It neither filled their bellies, nor quenched their thirst. But
people still yearned for this crude stage and the tales told on it, and
immersed in them, they forgot their melancholy. They clapped, wept,
laughed, and bustled with noise. There was no way of telling when death
might come sweeping down upon them. But in this moment, they could still
live and enjoy life. They could live and enjoy life all the more because
of it.

"I think it's amazing, Nezumi."

Nezumi sighed, caught himself hastily, and grimaced.

"Knock it off. It's not as rosy as you make it out to be. You've
probably never even seen a stage."

"You're right--- In No. 6, students weren't allowed to watch plays."

"I would've thought so. Especially for top-rankers like you, Mr. Elite.
Everything you watched or read would be strictly limited--- though you
probably never even realized it was being withheld from you."

"No. 6?"

Rikiga stopped mid-gesture as he was bringing a cigarette to his lips.
"Hey, wait a minute. Are you saying this wig-boy is from No. 6? You
gotta be kidding me."

"This is no joke, old man. And he isn't wearing a wig."

"Then is it some kind of new hat? Is that what's popular in fashion
these days?"

"No, it's my real hair," Shion answered. "Just--- a lot of things have
happened due to--- uh, issues."

"Oh?" Rikiga said. "There's nothing I love more than issues. If you've
really tumbled out of No. 6, you must have issues like no other. I want
to hear your story. And the reason behind that hair."

Nezumi hoisted himself up on the desk, and let his legs dangle.

"Does it smell, old man?"

"What?"

"Your nose twitched. Did you sniff out an interesting scoop, or what?"

Rikiga clapped a hand to his nose. Nezumi continued laughing softly.

"It's the same nose wild dogs make when they smell food. It twitched,
then your nostrils flared."

Rikiga's brow furrowed, and an expression of clear distaste spread over
his features.

"I've mentioned this before, Eve. I think I've had misconceptions about
you. I thought you'd be more gentle and refined. I would never have
imagined such a rude and brash kid. I'm disappointed, frankly."

"I thought you were my fan?"

"You can count me out from now on. Good god, I don't know what you enjoy
so much about taunting adults like this."

"Karan," Nezumi spoke quietly. Rikiga froze. "Do you know a woman that
goes by that name?"

Rikiga's body, beginning to show the signs of middle-aged weight gain,
teetered dangerously. His throat contracted as he swallowed.

"You know Karan\el ? Are you acquaintances with her?"

"She's my mother."

Rikiga appeared not to understand Shion's words immediately. He sucked
in a deep breath.

"Mother?"

"I'm--- oh, my name is Shion. I'm Karan's son."

"Son\el Karan's son, huh\el who's the father?"

"I couldn't say."

"You couldn't--- don't you know who he is? Is he deceased?"

"No--- I've heard from my mother that they separated shortly after I was
born. It's just been the two of us all my life. I've never met my
father."

Nezumi continued to laugh.

"Are you telling me there's a possibility he might be \emph{your} son?"

"No--- that can't be--- wait a minute, er, what was your name again?"

"Shion."

"Shion--- aster, huh. Karan did like that flower a lot. Uh--- Shion, will
you hold on for a minute? I'll get you a drink--- ah, I mean, a
non-alcoholic one, of course\el what would you like? I have everything.
Oh yes, here--- let's move somewhere more comfortable where we can talk."

Rikiga knocked the wall behind the sofa, and pressed his right hand on
it. The wall soundlessly slid to the side.

"Wow," Nezumi whistled. "Fingerprint recognition? You've got fancy
gimmicks on this place. Guess it's not as shabby as it looks."

Beyond the wall appeared a rather extravagant room. The floor was lined
with a luxurious carpet, and there were leather chairs, a leather sofa,
and a table. There was a fire burning in the fireplace set into the
wall.

"Come in, this way. I'll pour some coffee. Are you hungry? I have some
excellent pie."

Shion had forgotten that he was starving. His empty stomach ached.

"What kind of pie?" Nezumi said. "I prefer meat."

"You can shut up." Rikiga waved his hand irritably at Nezumi.

"You're horrible, treating us so differently like that."

Rikiga ignored him and disappeared into a small adjacent room. The aroma
of coffee soon wafted over to them.

"Coffee and pie, huh. I don't believe it." Shion had barely tasted any
such savoury foods since escaping from No. 6. Nezumi let his gaze wander
about the room.

"You're right. They're luxury items, for sure. And seeing how this room
is outfitted\el it looks like Inukashi's information was spot-on after
all."

"If that's the case\el " Shion said pensively. "No, that can't be\el "

"What can't be?"

"Mother once told me that my father was fast and loose with money and
women, and was one step away from becoming an alcoholic, a hopeless---"

"Good-for-nothing?"

"Yeah. A hopeless good-for-nothing\el but she said he was really gentle,
honest and straightforward."

"What's that supposed to mean? Is your Mama still attached to him?"

"I have no idea\el but it fits his image, right?"

Nezumi threw a glance at the entrance to the small room, and pulled a
face.

"I dunno the part about gentle, honest and straightforward, but he sure
is fast and loose with women, and halfway there to being an alcoholic.
Now that you mention it, I guess you guys look kind of similar around
the eyes. Well, we don't have DNA testing here, so there would be no way
to know for sure. ---Shion, you don't look too well."

"Ah, no\el I'm probably just hungry\el "

"Don't worry. Just the idea of that being \emph{my} father would make me feel
ill too. I'd probably break out into a fever."

"You've got a fever? Are you alright?" Rikiga set a tray down on the
table. On it was coffee, pie, and a glass of whisky. Shion's mouth
watered.

"Karan liked pie, too," Rikiga said reflectively. "She also liked bread
and cakes."

"She still loves them," Shion replied. "She bakes bread for a living
now."

"Baking, huh\el mm-hmm. I see."

An idea sparked in Shion's mind.

"Do you remember about the cherry cake?"

"Cherry cake? I'm not too sure\el what, do you want to eat cherry cake?"

"No, it's just\el my mother told me once that the day I was born, my
father came home with three boxes, each with a whole cherry cake inside.
And the two of them ate it together."

Rikiga lifted the glass of amber liquid and squinted.

"Is that so\el one of Karan's fond memories, huh? But unfortunately I
have no recollection of that. I've never bought cherry cake or eaten it
with Karan. I was never even a resident of No. 6. Shion, I'm not your
father."

Nezumi swallowed his mouthful of pie and nudged Shion's shoulder.

"So he says. What a relief, huh, Shion?"

"What's that supposed to mean, Eve?"

"It means exactly what it means."

Shion fished out Karan's memo.

\memo{\karan}{Arnd LK-3000. Latch Bl. 3F. Not sure. -K}

"We relied on this memo to get us here."

Rikiga stared intently at Karan's scribbled writing. Shion spoke.

"Shortly after I\el escaped from No. 6, my mother sent this to me. She
must have thought you were still here. I'm just wondering how you---"

'Know my mother' was what Shion planned to say afterwards, but his words
caught in his throat. A tear had spilled from Rikiga's eye.

"Karan\el she hadn't forgotten about me\el she remembered me\el her
writing\el still the same as I remember it\el "

His bowed head and broad shoulders were trembling slightly. Nezumi
nudged Shion on the shoulder again.

"Egh, will you look at that. This old man is a teary drunk. At this age
too--- talk about embarrassing, hah."

"Shut up. What's wrong with getting a little teary? You're always
wailing and yelling on the stage."

"That's all acting. What, are you saying yours is an act too, old man?"

Rikiga glared at Nezumi with watery eyes, and raise himself heavily. He
extracted a folder from the back of a sturdy bookshelf. He drew a single
photo from it and placed it in front of Shion.

"This is Karan and I."

An image of his mother was smiling back at him, young, beautiful and
wearing a sleeveless one-piece dress. Beside her stood Rikiga, much
thinner and well-proportioned than now, even with a hint of boyishness
in his features.

"It was taken decades ago, not long after we met each other. Karan was
still a student, and she was interested in the columns I wrote, and came
to visit me. The third floor of the company building was my workplace,
and when I'd just gotten back from an interview, she was sitting there.
It was a rainy day, and thundering outside, but she came all the way out
here to see me\el "

Rikiga sniffled. Shion and Nezumi looked at each other. Nezumi gave a
long, exaggerated sigh.

"You used to be a reporter, didn't you, old man? Can you summarize it a
little more efficiently? So basically what you're saying is that you and
Shion's Mama first met on the third floor of the Latch Bill company
building, am I right?"

"That's right. We got along great\el I enjoyed spending time with Karan.
I think it must've been love. Back in those days, No. 6 wasn't as closed
off as it is now. People were more or less free to come and go. I'd just
started my career as a journalist, and one of the things I was sniffing
out was about No. 6."

"Sniffing out? So you had some suspicions about that city, huh, old man?
You must've had a decent nose back then. Too bad it's useless now."

Rikiga fixed Nezumi with a glare again, and contorted his face in an odd
half-grimace.

"Eve, I wasn't kidding when I said I was your fan. When I first went to
see you, you were standing centre-stage and reciting a poem. Arthur
Rimbaud, I think it was\el I was captivated by your appearance, and your
voice."

Nezumi licked the grease from the pie off his fingers, and crossed his
legs.

\poem{But, in truth, I have wept too much! Dawns are heartbreaking\\
	Every moon is atrocious and every sun bitter\\
	Acrid love has swollen me with intoxicating torpor\\
	O let my keel burst! O let me go into the sea!}

"---Shion, know what this is?"

"A stanza from 'The Drunken Boat', if I'm not mistaken."

Nezumi chuckled. "Racing up that learning curve, aren't you? I can treat
you to a little more fan service if you want, old man. How about it?"

"No thanks. But let me say this, you were brilliant on that stage. I
almost can't believe that it was the same person as this insolent brat
that's in front of me. So do me a favour and stop talking."

"Don't be mad," Nezumi drawled. He uncrossed his legs, and his face
turned serious. Expression vanished from his voice. It became flat and
heavy. It was a voice that was startlingly different from moments
before.

"In the beginning, six cities were founded, including No. 6, as model
cities for the future. They were models created in the search for a way
humankind could live comfortably in a land that was reduced to rubble,
riddled with abnormal weather patterns mostly due to the carbon dioxide
from massive consumption of fossil fuels during the wars. That was what
it was, at first. The plan was that each city would take part in the
research and development of things like safe energy that could be
mass-produced to replace fossil fuels and nuclear power, and scientific
technology that ranged from the nanometre to cosmic scales, in a way
that was appropriate for the conditions of each city. This was in hopes
that some day, everyone on this earth would be free of any threat to
their life--- whether it be war, catastrophe, or plague--- and this first
step toward a world of threat-free life, the cornerstone of hope, was
No. 6. In all respects, this was the objective at first. Wasn't it, old
man?"

Rikiga drained the rest of his glass of whisky in one gulp. He coughed
lightly.

"So I guess classics weren't the only thing you could recite off by
heart, Eve. Your manager told me he didn't know your real name, age, or
where you were born. He said you were a wanderer that just appeared out
of nowhere. But I'm not buying it--- you're not just any travelling
entertainer. What's your real identity?"

"Nose around my business afterwards. So during the time this picture was
taken, No. 6 was still seen as the hope for all humankind, right? But
you had doubts. A fine nose you must've had to smell something fishy
there."

"When I became a journalist, No. 6 was already in the process of
change," Rikiga said. "Research organizations were gathering all sorts
of skilled labour, and their departments flourished; but on the other
hand, release of information and free speech were becoming more and more
restricted. I thought, is this really going to become a utopian city? I
had my doubts. You and your smart mouth are right. Back then, I had a
nose that could sniff out something that I couldn't see. While I was
scrambling around, the barriers spread further and grew more secure, and
going to and fro from outside parts became much more difficult. Soon,
you couldn't even enter or exit without a permit from the city. It
happened in no time. Since I was a journalist, they made sure I could
never set foot in that place again. They stamped out the freedom of the
press, just like that. Of course, that meant I couldn't see Karan
anymore either. To tell you the truth, I think that hit me harder than
not being able to do my work.

A decade and some later\el you get what you're seeing now. The
surroundings of No. 6 became places whose sole purpose was to service
the one, central city. Agricultural lands, cattle pastures, recreational
forest--- and this is their garbage can. Destitution, dispute, disease,
violence--- the rubbish that No. 6 spits out all ends up here. You two
probably don't know this, but this town used to be a small, but much
more decent place than it is now. At least, not a place that's been
classified and shelved away with an impersonal label like the West
Block. But they've turned this place into a garbage can. What's this
\emph{hope} they're speaking of now? Some Holy City this is--- they're doing the
name a disgrace. It's more like a devil that releases toxins everywhere
it goes."

"I guess humans and cities are similar, then," Nezumi remarked. "In time
they forget the ambitions they set out with, and corrupt themselves to
no end."

Nezumi drained the rest of his coffee, and threw a glance at the man who
had just finished talking.

"What's that supposed to mean? Are you saying that I've been corrupted?"

"Can you say that you aren't?"

Shion let his eyes flit to Nezumi's profile. He felt that Nezumi was
provoking Rikiga. Rikiga responded to that provocation. No--- maybe he had
just been lead into the skilful trap.

"You're criticizing me about how I've become a drunk, huh? How I've been
reduced to making magazines full of naked pictures, drinking as much
booze as I could bathe in, and to top it off, nearly getting killed by a
woman."

"You sound bitter, old man. But using pretty words instead isn't gonna
help you survive here."

"Everyone knows that."

"What I'm curious about is how decked-out this room is. A warm room, and
good food. You can't get those things easily. I can't see all your
income for this coming from those porno mags. Which means--- you've got
ahold of someone's purse strings. Am I right?"

Nezumi smiled. It was a haughty, but elegant smile, like of one passing
divine judgment.

"I heard high officials from No. 6 come here secretly ever so often."

Rikiga's mouth made a chewing motion.

"Old man, I heard you take orders from these men and bring them the kind
of women they want, like the middleman in a deal. I guess your
connections from your journalist days ended up being pretty useful. And
the enormous payment you get from these guys pays for this luxurious
lifestyle. You suck up to the guys who are pretty much at the core of
the city that you just called the Devil, and leech off the good parts
while you live off women who have no choice but to sell their bodies to
avoid cold and starvation. You don't call that corruption?"

All expression vanished from Rikiga's face. It had no light or shadow,
and looked strangely flat. The flames from the fireplace were lighting
the right half of his face.

"\el Where did you hear about that?"

"From a dog."

"Dog?"

"A dog told me he heard you and some man whispering under the stairs.
Afterwards, the man got in his car and drove right through the special
gates of the Access Control Office, and got into No. 6 without any
difficulty. The kind of people that can go between No. 6 and the West
Block freely are limited. Only High Officials who have a special
identification card with them can. Everyone else would get destroyed at
the gates."

Shion gulped. He felt like he was watching a stage play. He could read
nothing from the man's face, which was coloured crimson by the flames.
Suddenly, its mouth twisted.

"How would you like to join, then?"

"Join?"

"No. 6 is a boring place. You're not allowed to have a disorderly
lifestyle. Beggars and prostitutes aren't allowed to exist. Everyone's
listless. So they come here to stretch their wings. They come, laugh at
the women who sell themselves for whatever meagre cash that'll take
them. The men reconfirm that they're a specially privileged class, and
take joy in that again. After their short moment of fun, they go back to
their boring home. Those kind of people are the ones that keep coming
back."

"So business is booming, huh? That's good for you."

"Thankfully, yes. But their demands seem to have no end. They give me
different orders, every time. First they want a dark-skinned girl, next
they want a young girl with a tattoo all down her back. It gets
stressful sometimes."

Shion had his head bowed. It pained him to listen to Rikiga talking. No.
6 was a beautiful city on its surface. Now he was hesitant whether to
call that real beauty, but nevertheless, it was orderly. Its nature and
buildings maintained a delicate balance, neither one over-asserting
itself, and all its people were gentle and polite. Behind all of that
was the truth that he was hearing now. His eyes met with Karan's in the
photograph.

\emph{Mom, the place where we lived, the place where you still live now, was
just a monster wearing a mask of beauty. Mom\el }

"And you're inviting me to join you in head-hunting for women?"

It was Nezumi's dry, brittle voice. Rikiga laughed. It was vulgar and
insulting to the ears.

"Never. That would be a waste of good labour that could be put to better
use. I've actually been thinking about it ever since I first saw you on
that stage. You could rake in as much money as you want. It should be a
piece of cake for you to sweet-talk those bored stiffs into showering
you with money. What do you think? It'll pay way more than that shabby
hut of a playhouse."

"Are you telling me to take customers? Has the alcohol gotten to your
brain, old man?"

Rikiga sneered. "Don't try to play cool with me. God knows where you've
come from and where you've been--- a wandering actor like you has probably
had experience with it anyway. It's no use pretending you're an
innocent---"

"Shut up!"

It was Shion who had yelled. He whipped the coffee cup and its contents
at Rikiga. He leapt over the table, grabbed him by the shirt, which was
soaked through, and leaned in with all his weight. Rikiga gave a short
cry as he fell to the floor.

"That's enough!" Shion yelled angrily. "How dare you say something so
degrading! Apologize--- apologize to him!"

Shion straddled Rikiga and shook him roughly. The back of Rikiga's head
banged against the floor repeatedly. Still holding him by the collar,
Shion closed his hands around Rikiga's throat.

"Can't--- breathe---" Rikiga gasped. "Shion, please--- I really can't---I'll
apologize\el so stop---"

"Shut up! You shameless--- shame on you---"

A pair of hands slid under his armpits, and he was dragged backwards.

"Shion, that's good enough. Any more, and the old man's gonna pass out."

Rikiga curled up and coughed.

"That was a surprise," Nezumi murmured, still holding Shion from behind.
He really sounded stunned. "I never imagined you'd resort to violence. I
guess even \emph{you} let the blood get to your head sometimes, huh. Enough to
go attacking people like that."

"\el First time in my life\el " said Shion, slightly out of breath.

"I can tell. Your heart is going a mile a minute."

Shion turned and impatiently brushed Nezumi's hand away.

"Why aren't you angry?"

"Angry? If I let a joke like that get to me every time, I'd be going mad
all year round. I'm used to it. It's no big deal."

"Idiot!"

"Idiot? Shion, what're you getting all worked up for?"

"You're an idiot. What he said wasn't a joke. Don't say you've gotten
used to it. Don't---"

His eyes burned. A tear spilled before he could screw his eyes shut.

"Shion--- come on, don't cry. Why would you\el ---I can't believe you're
crying," Nezumi said exasperatedly.

"He\el insulted you."

"Huh?"

"He insulted you. He said horrible things--- lumped you in with the filthy
officials of No. 6. But you say it's no big deal. You weren't even angry
about it\el and that made me feel even more helpless and angry--- so
angry\el I don't even know what to do anymore\el "

Nezumi opened his mouth to say something, then closed it again. He
yanked the tablecloth and thrust the end of it toward Shion.

"This is all I've got, but you can wipe your face on it."

"Okay."

"Shion, the one who got insulted was me, and not you. Don't cry for
other people. Don't get into fights for other people. Fight and cry only
for yourself."

"I don't understand what you're saying."

"I guess you wouldn't--- sometimes it's like we speak different languages.
Look, there's snot coming out of your nose. Wipe it, come on."

"Mm-hmm."

"I always find it impossible to understand you. Even if we spent our
whole lives together, I probably still wouldn't understand you. You're
right in front of me, but at the same time, it's like you're far away.
That's probably why---"

Rikiga rose to his feet behind Shion.

"I'm sorry for interrupting your moment, but I want to let you know that
that tablecloth is silk. I had a hard time coming across that thing, so
I'd appreciate if you didn't wipe your nose on it."

He peered into Shion's face.

"Your angry face looked just like Karan's. I felt like I was being
scolded by Karan herself. Though with her, I've never been yelled at
that violently."

Then he turned to Nezumi, and lowered his head in apology.

"I'm sorry. I went too far. I deserved to be punched. Looks like my
morals have rotted right through."

"They haven't rotted. They're just pickled in alcohol, that's all."

Nezumi gave Shion a light push on the back.

"I think we can call it a day. Let's go home."

"Sure. But I have to clean up first."

Nezumi laughed.

"You really are a well-behaved little boy, aren't you?"

"Make fun of me all you want, but I'm still going to clean up."

Shion bent to retrieve the coffee cup. Nezumi also reached for the
folders and plates scattered on the floor. His body stiffened. His
breath was caught in his throat, and he was frozen.

"Nezumi, what's wrong?"

"This---"

Nezumi's fingertips were trembling slightly as they held a single
photograph. It had probably fallen out of one of the folders. Rikiga
narrowed his eyes.

"What's the matter? Oh, that."

There were several men and women in the picture, with Karan at the
centre.

"It's a photo from the last time I entered No. 6. It's a picture of
Karan and her friends."

"This man\el "

Nezumi pointed at the tall man standing at Karan's side.

"That guy, huh," said Rikiga absentmindedly. "Who was he again? I think
he said he was in an institution for biological research--- looks like a
bright fellow, doesn't he? I can't remember much about him, though. He
didn't really stand out. Eve, you know this guy?"

"I might."

"How do you know him?"

Nezumi drew a breath, and answered quietly.

"He's my godfather."