% !TeX spellcheck = en_US

\chapter{Act one scene two}

\myepigraph{No, you've got it all wrong.\\
	We flee\\
	because we want to live.}{Tezuka Osamu, \emph{Grand Dolls}}

\lettrine{T}{he sighs} of the wind grew louder. High-pitched and somewhat plaintive,
it whistled through the ruins. The man awoke to hear the sound of the
wind around him. He hadn't lost much of his composure. Bound and sitting
on the floor, he let his gaze roam around the room.

"What's going on?" He questioned hoarsely. No one answered. "What's
going on, Rikiga? You understand what you're doing, don't you?"

"Unfortunately, I do." Rikiga gave a sigh, one of several he had already
heaved that day. "I understand it so well, it makes me sick to the
stomach. I never asked for this, anyway."~

"Let me go." The man twisted in his bonds. But he realized that the more
he struggled, the more the ropes dug into his body, and he soon quieted
down. He let his gaze wander about again, and cleared his throat. He
remained unruffled.

"What are you after?" he said calmly. "Money? Surely you don't think
you'll be let off easily for doing something like this?"

"Our point is not to be let off at all." Nezumi knelt down in front of
the man. The man widened his eyes in surprise, and murmured
appreciatively.

"You're a beauty." A smile spread across the man's face. "Rikiga, this
one's a much finer gem."

"If it pleases you to have me," Nezumi said, hooking a leather-gloved
finger on the man's chin, "then you can have me to your heart's content.
But it'll be expensive. Five gold coins isn't nearly gonna cut it."

"Hmph," the man sneered. "So it \emph{is} money you're after. How much do you
want?"

"I don't want money."

The contemptuous smile vanished from the man's face. He tried to draw
his chin back, but Nezumi's fingers held fast and didn't let him.

"If it's not money---then what?"

"Information."

"What?"

"Information," Nezumi repeated. "I'm going to have you spit out every
piece of information you have, right here."

"What preposterous---"

"And after that, I'll give you plenty of my company. I think it's a good
deal, don't you?"

"Don't make me laugh," the man retorted. "Mere West Block residents,
having the audacity to ask for \emph{information}? And what will filth like you
do with information about the Holy City, hm? What use would it be to
you? You ought to go back to crawling around in the dirt where you
belong."

There was a slap. Nezumi's right hand had struck a fierce blow across
the man's cheek. The man fell to the floor on his side. Nezumi yanked
him upright by his hair, and sharply slapped the other cheek. Once more.
Twice. The man never so much as raised a groan, and only crumpled to the
floor each time.

Shion stood frozen and staring with his breath caught in his throat. Lit
in the glow of the candle, Nezumi's profile had no expression.
Blank-faced, as if wearing a mask, he continued to abuse the man.

"Nezumi---" His body shook.

\emph{Please. No more. Stop---}

As Shion took a step forward, a tan arm barred him.

"Inukashi."

"Shut up and watch, little boy," Inukashi hissed quietly, licking his
lips with the tip of his tongue. "The fun's just getting started. Don't
get in the way."

"But this---this is too much."

"Shion, remember what you said before?"

"Huh? What?"

"You said to me once that Nezumi was kind. I think it was in this room,
actually. Have you forgotten?"

"I remember."

A quiet chuckle escaped Inukashi's lips.

"It's just getting started, Shion. Make sure you get a good look at
exactly how \emph{kind} your dearest Little Mouse is."

There was a cut on the side of the man's mouth. It looked like he had
cut the inside of it too; a mix of saliva and blood oozed from his lips.

"Stop it---please---" the man moaned. Nezumi's hand stopped.

"Feel like speaking truthfully now?"

"I... don't know... anything..."

"A high official of the Central Administration Bureau like yourself,
know nothing, sir? That doesn't even make a good joke."

"All information is managed and processed by computers... there isn't...
much that I know..."

Shion thought that he had a point. Even if he was a high official, it
didn't mean he would have access to all internal information about No.
6. The more classified the information, the more barriers there would
be, so that only a select handful of people would know its entirety.
Only a select handful---

Who were they? he wondered. It was a question he had never considered up
until now. In No. 6's City Hall, inside the oval-shaped dome of the
Moondrop, a certain man reigned.

\emph{The mayor?}

He was a figure who was at the centre of the citizens' overwhelming
support and admiration for building up the prosperity of No. 6. Apart
from the first one, all mayoral elections had been without any other
competitors.

\emph{Could it be him?}

The image of the mayor's face on television rose in his mind. It was
wearing a gentle smile. He had seen it in no other expression. He had
not been able to. The more steps the city took toward prosperity, the
less he began to see the mayor's unmediated face in public. And at the
same time, enormous support and political power were beginning to
concentrate around this one man. The mayor, as he spoke to the citizens
through the media, was always a mild-mannered gentleman, full of
intellect and compassion.

"I don't like him."

Shion's mother Karan had said so once, and turned off the television
soon afterwards. Shion was not yet ten, but he nevertheless remembered
being surprised at the harsh tone of his mother's voice, and the fact
that she had spat out those words about the mayor, whom everyone else
praised.

"Why don't you like him?"

"I don't like his ears. They're so vulgar."

"His ears?"

"They twitch. Like some kind of beast that's after his prey."

Was the mayor twitching his ears as he was being broadcast? Shion had
tilted his head, perplexed. Then Karan's face had grown serious, and she
had said, \emph{that's a secret}. By that time, there had been a generally
discouraging air throughout the city towards people who criticized the
mayor, and it was best to keep criticisms to yourself. It had been
nearly ten years since then, and the mayor was still sitting at his post
of highest power in No. 6, while Shion was here, outside the wall.

"Answer my question." Nezumi's low voice reached his ears as if crawling
stealthily across the ground. "This new facility that's been built
inside the Correctional Facility---what is it? What's it for?"

The man shook his head.

"I don't know."

"Then which Bureau is it under?"

"I don't know."

"A few days ago, a young woman---an elite candidate---was taken into custody
by the Security Bureau. She's been imprisoned in the Correctional
Facility, but that's as far as we know. Does her case have something to
do with that new facility?"

"I don't... know..."

"I've heard that lately there have been patients sprouting up inside the
city with an unidentifiable illness. Is that true? What are the
symptoms? How many patients are there?"

There was no answer. Nezumi straightened up, and shrugged slightly.

"You don't have much of a vocabulary for a high official. Didn't you
have to be a little smoother than that to pick up girls?"

"Untie me."

The inside of the man's mouth was probably swelling, for his voice came
out strangely muffled. "Untie me, and let me go. If you do, I'll forget
about this incident. I'll do you a favour and pretend it never
happened."

"Why, thank you. A judgment of clemency. I'm so grateful---Inukashi," he
said abruptly.

"Uh?" Inukashi answered lazily.

"Keep him still."

"A'ight." Inukashi quickly stepped in behind the man, and held his
shoulders and arms down. Nezumi unsheathed his knife.

"What are you doing?" the man cried frantically. His forehead was moist
with sweat.

"Quiet down. I'm just granting your wish."

The white blade flashed in the hazy light. The knife, clean of any
ornament or decoration, was eerily beautiful. The ropes fell away.
Nezumi, with an almost languid air, took the man's hand in his own. He
held it by the wrist, and peered into the man's face. The man stayed
frozen and unmoving, although he had long been freed. Perhaps he was not
able to move. The pair of grey eyes had arrested and trapped him in his
spot.

Leather-gloved fingertips stroked the man's palm.

"I figured a high official of No. 6 like you would only need a little
pain before he started bawling and spilling the beans. Looks like I
underestimated you by a lot."

Nezumi traced the man's hand, finger by finger, and gave a small sigh.
It was almost almost like a loving caress.

"You've got guts. It's quite something. Let me give you a reward."

A shard of glass was placed on the man's hand. It was a piece from the
shattered liquor bottle.

"And one more."

The pointed end of the shard shone dully.

"What---what are you doing---?" The man shook his head, his voice and body
quaking uncontrollably. "Stop---stop it, please---"

"Why? The reward's all ready for you. Take it."

Nezumi's hands cupped around the man's, and closed it firmly.

The wind grew still. For a brief moment, a bloodcurdling scream rang out
in the silent room. Rikiga's face contorted as he averted his gaze.
Inukashi also closed his eyes, and bit his lip while he held the man
down.

"Answer me!" Nezumi commanded, still clenching the man's hand closed.
"Answer everything I've asked you, or else I'll make sure you can never
use any of your five fingers again."

"Nezumi!" No sooner had Shion yelled his name than he found himself
springing forward. He rammed himself into Nezumi. Bloodstained shards of
glass fell out of the man's hand onto the floor.

"Stop---stop, please." Nezumi showed neither surprise nor anger, and
remained expressionless as if he had expected Shion to act this way all
along. The only thing he did was to click his tongue lightly in
irritation.

"Don't get in my way."

"You can't. You can't do this. This... this is torture."

"What other way do I have? If I bow my head and say \emph{will you please}, is
this guy gonna tell me everything?"

"Well---but---but this isn't right. I don't want you to do something like
this."

"Shion, get over yourself and your indulgent thoughts, or else we're
never gonna get anywhere. We aren't playing house. This is a war."

Shion knew. He knew very well. He was aware of the hardships that
awaited him in the future. But---

"But---it's not right. Torture isn't right. Don't do it."

"Why not?"

"He's a human. We can't make him suffer."

Nezumi snorted. He turned aside, and laughed silently with his mouth
closed. The man was sobbing pitifully, his hand bloody and shaking. \emph{Poor
guy}, Inukashi muttered under his breath. Nezumi nudged the man's thigh
with the tip of his boot, and looked Shion straight in the eye.

"You heard what he said. Us West Block people are filth to guys like
him. Like bugs that scuttle across the ground. He's probably never even
thought of us as humans, with blood running through our veins, and
emotions like everyone else. Whether we bleed, or starve to death---or
writhe in pain, it has nothing to do with him. That's what he thinks. So
why do we have to treat him like a human? If we're insects to them, then
these guys aren't even---"

"I don't want to see it!" Shion found himself yelling, more loudly than
his last outburst. He yelled to block out Nezumi's voice.

"Huh?"

"I don't want to see it. I don't want to see you harm someone like
this." He felt nauseous. At himself. A thick, black self-hatred coiled
within his body. \emph{Don't want to see? Then drop your gaze. You're always
like this. You've always averted your eyes from everything you don't
want to see, and pretended you didn't notice. For whose sake is Nezumi
exercising this brutality? Isn't it all for you? Didn't you force him to
do this? Haven't you burdened Nezumi with a sin that should have been
your own---and now you're crying saintly things? They're just pretty
words, Shion. Everything you say and do, just a pretty facade. You never
dirty your own hands, never bear a wound on your soul, never get hurt,
and yet, \emph{you mustn't hurt others,} you say, brandishing justice.}

\emph{This self-righteousness, this arrogance, this falseness, superficiality,
your unsightly and hideous nature.}

\emph{It's all you.}

None other than his own voice was speaking to him. Shion felt nauseous.
The hatred slithered and twisted inside him.

But he didn't want to see it. Despite everything, he didn't want to see
it. He could be certain of that much.

"I don't---want to see you like that." \emph{Nezumi, I don't want to see you
cold and ruthless. Because it's a lie. Everything you've taught me has
always led to rebirth and creation. You told me to live, and you told me
to think. You taught me to love another, to understand another, to seek
a connection, to yearn---and yes, everything you've taught me is the bare
opposite of ruthlessness. I don't want to see you as someone you're not.}

"Eve." Rikiga swayed and stepped forward. "Shion's right. Leave it at
that. Fura's grown up as an elite since he was a kid. He probably has no
resistance at all against pain. Put him through any more, and who knows,
you might finish him off with a cardiac arrest."

Nezumi shrugged. Expressionless eyes flitted between the wailing man and
Shion. Without another word, he withdrew a step. Then, he slowly pulled
off his bloodstained gloves.

\emph{I'll step down and leave the spot free for you. Do as you would, until
you're satisfied.}

Shion knelt down on the blood-spattered floor. He spoke to the man.

"Fura-san. I want you to listen to me. The girl that was apprehended by
the Security Bureau is my very precious friend. I'm willing to do
anything it takes to save her. And to do that, I need information from
you."

"It hurts... it hurts... so much blood..."

"If you speak to us, then I'll treat your wound."

"Please, stop the blood," Fura implored. "Stop the pain. Hurry!" The man
offered his palm. He thrust it out, with tears streaming down his face.
There were bleeding cuts in various places, but the wounds themselves
were not that deep. As long as they didn't get infected, they were
surely of no threat to his life.

"A couple licks from a dog, and it'd be gone in a night," Inukashi
cackled, showing his teeth.

"Rikiga-san, can you bring me some clean water and alcohol?" said Shion.

"Don't have much to disinfect with except my booze."

"That's fine."

"And the water---I can just draw it from the stream?"

"Yes."

"Alright, I'll bring some." Rikiga sighed in relief, and left the room.
His footsteps were light, as if he couldn't wait to get out of the
place. Shion renewed his composure, and turned back to the man's
exhausted face.

"I'll treat you, so talk to me. I don't have time. I want you to answer
me truthfully."

"Oh---" the man whimpered. "Fine---hurry, just make the pain stop---please,
quick---"

"What's the facility that's been newly built inside the Correctional
Facility?"

"I---I really don't know."

"So even someone of your rank doesn't know---does that mean it's
top-secret information for the city? As classified as it gets?"

"Yeah---there's a project team that's directly beneath the mayor, and
everything happens between them... we have no involvement in it... we
aren't allowed."

"You aren't allowed to be involved. But you know that some project or
other exists, am I right?"

"The city's---in-invested a lot of money into it," the man stammered. "It
was declared in the budget on the pamphlet we got at the assembly...
and..."

"Was it a problem at the assembly?" Shion asked. If it was, then
naturally, a question would be raised from the assembly, and the mayor
would have no choice but to give an answer. For what reason was this
enormous budget set aside? What was this project for? If there had been
a diet member who had raised the issue---

"Of course not," the man's mouth twisted in derision. "There's no way
anyone could object or question a project proposed by the mayor himself.
The budget was simply printed in the document---until seeing this, we
hadn't known about it... and by that time, it was already---"

"The facility had already been built in the Correctional Facility."

"Yes."

"Anything about the project team members?"

"I don't know... I don't know names... even how many there are. No
one... should know."

Inukashi whistled.

"That's amazing. No one knows anything about it, there's no explanation,
and yet just because it's the mayor's project, he gets free reign with
the funds. And no one complains? Yeesh, I'm so jealous, I could topple
over from envy. Wish I could get a piece of that." True to his word,
Inukashi promptly hugged his knees and flopped backwards on the bed.

Rikiga entered, carrying a pail of water. The stream that ran by the
ruins apparently traced back to a natural spring in the wood, and it was
constantly brimming with clear, cold water. Come spring, clusters of
little blush-pink flowers would line the edges of the river---a girl
called Kalan, who went by the same name as his mother, had told Shion.

The clear water lapped inside the worn pail.

"We're going to clean the wound. Put your hand in the water---Inukashi, do
we have clean cloth?"

"Clean? Not a word I have a close relationship with. This is the West
Block, you know. The cleanest thing here is probably a dog's tongue."

Rikiga silently handed him a roll of gauze. It was a little old and
yellowed, but nevertheless unused. It was a luxury item in the West
Block.

"I figured something like this would happen," Rikiga said. "So I had
some ready. I don't have anything fancy like antiseptic, though. Use
this, if it'll do."

A small liquor bottle was tossed into Shion's lap. There was a
colourless liquid inside.

"Gin, from my precious stash."

"Thank you." Shion dipped the man's hand in water. Streams of blood
ribboned and swayed in the water like crimson seaweed.

"This will sting a bit." Shion pressed a piece of gauze soaked in gin
against the wound. The man grunted in pain, but didn't struggle. Shion
wrapped the gauze around his hand, and knotted it tightly.

"You haven't cut any nerves or tendons. If you re-dress the wound
properly later, it shouldn't pose a huge problem."

"It still... hurts..." the man protested feebly.

"We don't have painkillers here. You'll have to bear with it."

The man's gaze beheld Shion steadily for the first time.

"---How old are you?"

"Sixteen."

"How did your hair turn like that?"

"Oh, this---" Shion brought a hand to his hair, now almost entirely
drained of its colour. He had been so busy trying to live each day in
the West Block, and these past days he had thought of nothing except
Safu. It had been a long time since he had bothered to think about his
hair colour. He had forgotten about it. His hair still held its shine,
and Nezumi had said that some would perhaps find it beautiful. But
Shion's white hair was still a mismatch for his young age of sixteen,
and seemed to appear odd to some people.

"There's a slew of reasons behind this. I didn't bleach it on purpose,"
Shion explained.

"You're not a resident of this place, are you?"

"No."

"Where did you come from?"

"From within the wall."

"From within the city? Impossible!"

"I was living in No. 6 until recently."

"What's a city resident doing here?"

"That---well, there are a lot of reasons for that, too."

Shion had moved from inside the wall to outside of it. In numbers, it
was not a considerable distance. But if he were to explain why he had
crossed the border between two distinctly separate worlds, to be where
he was now---he felt like no amount of words would be enough.

"What did you used to do inside?"

"I did cleaning duties at a park. I was a student as well---that was my
main occupation."

"Hey, hey," Inukashi butted in. "That's enough. What're you doing
answering \emph{his} questions? Isn't it supposed to be the other way around?"

"Oh yeah."

"How can you be so slow?" Inukashi said exasperatedly. "Buck up a
little, I'm begging ya. You're making me start to feel bad for you,
man."

"Uh---right, okay. Sorry."

"Apologizing to me isn't gonna help. Geez, talk about unfit for
interrogation. It's like trying to teach a mole how to swim. My dogs
would probably do a better job."

Inukashi raked a hand through his black hair, scratched impatiently, and
gave an exaggerated sigh. Shion turned red. Inukashi was right---he'd
never even known how to interrogate someone, and he couldn't see himself
doing it well. Still kneeling, he looked up at Nezumi.

In a dim patch of darkness out of light's reach, Nezumi was leaning back
against the wall with his arms folded. His expression was indiscernible.

Shion knew there was simply no time to be complaining that he would
rather not, or that he couldn't do it. He bit his lip.

"Fura-san, so basically you're saying that you don't know anything about
the Correctional Facility."

"Yes."

"Then what do you think it is?"

"Huh?"

"Why do you personally think those facilities are there?"

"Why do I personally---"

"Yes. I want to know from your personal perspective---what sort of thing
would the mayor build that he would keep in secret, and not let anyone
else interfere with?"

"Th-There's no way I would know. I don't have any information---I don't
have any files or resources."

"Then just make a prediction. Imagine what it would be, even."

\emph{Imagine.} The man enunciated the word slowly. He let it roll off his
tongue cautiously, like tasting a fruit that he had never seen before.

"Imagine..."

The stench of alcohol and blood mingled together in the air. The wind
renewed its forceful gusts, and whistled high-pitched and forlorn.

The man's bloodless lips moved.

"I reckon---the Health and Hygiene Bureau might have something to do with
it."

"Health and Hygiene Bureau? Not the Security Bureau?"

The Bureau of Health and Hygiene singly managed the city's hygiene and
the health of its citizens. It presided over all hospitals and health
clinics in the city. This Bureau administered the Children's
Examinations to select elites at an early stage, and also ran the yearly
physical assessments that were mandatory for every citizen. It was an
important bureau, but from Shion's knowledge, it didn't have a close
connection with the core of the city as much as the Security and Central
Administration Bureau did. Since his former workplace at the Park
Administration Office had been a distant branch of the Health and
Hygiene Bureau, he had a little knowledge about the Bureau's activities
from the information that trickled in.

The Correctional Facility and the Health and Hygiene Bureau---two
organizations that seemed to be most disconnected with each other in
fact turned out to be closely entangled.

"Fura-san, why do you think so?"

"It's just what I imagine. You told me I could."

"Yes, I did."

"Just my imagination. But..."

"But?"

"At the Municipal Hospital---" The man broke off, and swallowed hard. He
wasn't keeping Shion hanging on purpose---he was hesitating. He was
hesitating whether he could talk about something like this.

Shion waited. He waited for the man to speak to him, to put into words
what was in his heart. He could do nothing but wait. So he waited. That
was his way.

The man lifted his gauze-wrapped hand and wiped his mouth with the back
of it. His lips had swollen and turned a reddish-purple colour.

"A few months ago, there was a transfer of posts at the Municipal
Hospital. Doctors---all highest-ranking in work ethic and skill---a few of
them, along with some nurses, were transferred out. I don't know where
they were transferred to."

"You don't know?"

"It's not recorded anywhere. All data of the citizens are collected at
the Central Administration Bureau. Every action taken in the day is
recorded without fail to the database. Anything as big as a workplace
transfer, even more so for doctors and nurses that work for the
Municipal Hospital, would be recorded strictly and with detail."

"But it was missing."

"Right. It wasn't there. I thought it was strange. I thought---but that
was all I did."

"Did you look into it?"

"I didn't even think about it. Even if I wanted to, it would be
impossible. And if I slipped and somehow ended up with confidential
information, I would be in huge trouble."

\emph{I can't believe you've asked me such a stupid question}, the man seemed
to say, as he turned his face aside.

The Health and Hygiene Bureau; talented and skilled doctors and nurses;
the Correctional Facility---an idea flared in Shion's mind.

"I've heard that there have been strange incidents inside No. 6. Do you
think it has anything to do with the Correctional Facility?"

"What?"

"There have been people struck ill. Am I right?"

"You've done your research," the man observed. "Where did you get that
information?"

Rikiga swayed, and exhaled a stench of liquor.

"You're not my only customer who comes from No. 6," he said, "though
none of them are the kind of big-shot you are. The lackeys give me their
own kind of information. Like when they're giving bedtime stories to the
girls they've slept with---just spills out."

"You call that information? They're probably just rumours."

"Rumours usually happen to be closer to the truth than what public
organizations shove in your face. But speaking of which---" Rikiga knitted
his brow, and narrowed his eyes.

"These days the authorities seem to be getting stricter on their
regulations. It's almost over the top. Apart from big-shots in your
rank, it's becoming harder and harder for the lower ranks to sneak their
way out here. I've even heard that soon, it's just going to be banned
outright. Poof, there goes half of my business."

"And look what you've done to your best customer," Inukashi chimed in.
"Forget half of your business, you're going completely bankrupt, old
man," he cackled. Rikiga glared at him, and tsked his tongue irritably.

"Either way, it's all over. For me, and for you."

Inukashi retracted his laugh and fell silent.

"If someone fell ill, they'd naturally be taken to the Municipal
Hospital, right?" Shion continued. "But what happens to them
afterwards?"

"I don't know."

"It's not a contagious illness, is it?"

"There's been no public announcement from the city. Besides, there would
be no way a contagious illness could spread in No. 6."

"True."

Shion lowered his eyes, and looked at his own hands. They were scarred,
the skin was rough, and on the whole, they had become rather bony. They
had lost all their softness and smoothness that they had when he was
inside the city, but he thought his hands now showed more strength. They
were hands that were alive and trying to get a firm grasp on things. On
these hands, stains would spread, fingers would bend out of shape, and
they would age at the blink of an eye. He could still clearly visualize
how Yamase had died.

"The patients wouldn't have survived---I'm thinking it would have been an
unnatural death. They would age rapidly until they finally died---maybe
that's how---"

The man drew his chin back, and narrowed his eyes suspiciously.

"What are you talking about?"

Shion stared at the man, and then slid his gaze to Nezumi. The darkness
was spreading, growing thicker, and trying to shroud the boy who stood
as still as a statue.

This man did not know. He really didn't know a thing, about the parasite
wasps, or the queer incidents, or the grisly deaths. Even someone like
him, in the post of a high official, did not know a single thing.

"Samples," the man suddenly muttered.

"Samples?"

"Sample Collection Status---I remember there being a section like that in
the Health and Hygiene Bureau's data."

\mybreak

"Samples of what?"

"I don't know. I just know it said something about their collection
status---you needed a special password to access it. The only thing I know
is that this and the mayor's project..."

"Are connected."

"I imagine they are."

Sample. What a cold, desolate word. Shion felt a chill.

\emph{Safu.} He cast his thoughts to her, and his chill got worse.

"Shion," Nezumi called. The darkness shifted. "That's about it. We can't
get anything else out of this guy." His words also had a cold, desolate
ring. The man perceived their coldness and stiffened.

"Are you going to---k-kill me?"~

"Of course." Nezumi's boot stepped over the blood splatters, now
beginning to congeal.

"I-I've told you everything I know. I talked. This isn't what we
promised."

"We didn't promise anything. Promises or agreements don't exist between
people like you and I."

"Stop, please---I don't want to die!"

"Nezumi, that's enough." Shion stood between him and the man. "There's
no need to scare him like that. You've done enough. We have to take him
back and drop him off somewhere near the gates. Rikiga-san---"

"Yeah, I know. I gotcha. I'll bring the car around."

"He's our enemy." The unsheathed knife spun around in Nezumi's hand.
"Are we just gonna let him slip through our hands like that?"

"It's not necessary at this point. We don't need to kill him."

\emph{Heh.} Lending the upper-half of his body to the darkness, Nezumi gave a
quiet laugh.

"And when would you say it \emph{is} necessary? Do you think this guy will go
back to No. 6 and keep quiet about us?"

"Yeah."

Shion lifted his chin, and looked straight through the darkness. He
aligned his gaze with the pair of grey eyes at the other end. \emph{Have you
noticed, Nezumi? No matter how dark or blindingly bright it is, I'm
never led astray---my eyes always find yours.}

"He won't tell anyone. If he did, he would be threatening his own life.
Just think---a high official of the Central Administration Bureau,
entering a prohibited area like the West Block for no apparent
objective, with no official permission. What would happen if people
found out? He's more than aware of the risks. There's no way he would
give us away. You should know this already."

"How the hell should I know?" Nezumi stepped soundlessly forward.
"There's no guarantee that this guy won't slip and mention a... certain
group in the West Block sniffing around about the Correctional
Facility."

"He won't talk."

"Shion." Nezumi's voice lowered slightly. "I'm gonna ask you again. Do
you plan on letting him go home alive?"

"Yeah."

An arm stretched towards him. In less than a blink of an eye, Shion was
trapped in Nezumi's embrace. Nezumi's arms were thin, and certainly
didn't seem to be that strong at a glance---but it only took a single arm
for him to arrest Shion's movements completely. Shion felt an icy
sensation at his neck---the blade of a knife.

"I've had enough of your half-assed justice and fake goodwill," Nezumi
said quietly. "It makes me sick. I've been meaning to tell you this,
Shion---you won't survive unless you tear off that self-righteous,
artificial mask. I could care less if you went off to die by yourself,
but don't get the rest of us involved. We don't have time to be fooling
around trying to decide if it's 'necessary' to do something or not.
Enemies are enemies. We kill or get killed. That's all there is to it."

The blade slid along his neck. Shion felt a small, sharp pain. His eyes
were transfixed to Nezumi. For just a brief moment, a sweet thrill
stirred in the core of his body. To take one in his arms, and slit his
throat---

An embrace of death.

This was, indeed, the feat of a devil.

Nezumi withdrew. When Shion brought a hand to his neck, and felt it
pulsing with heat. His palm was smeared with blood. With his gaze still
on Nezumi, Shion clenched his fingers.

"Rikiga-san, the car."

"Huh?"

"If you could take him home by car, please."

"Oh---right, yeah."

Shion turned to the man, and gave him a smile.

"I'm sorry we've done such horrible things to you. But it was the only
way we had."

"Shion..." The man blinked several times as he studied Shion's face. "I
remember there was a first-degree criminal by that name. He was a fallen
elite who'd gone insane. He poisoned his co-worker, then fled to the
West Block---is that you?"

"Been blown out of proportion pretty badly, hasn't it?" Shion couldn't
help but give a wry smile. Karan's face rose into his mind. He thought
of the hardships she must be facing, living in a society where rumours
of her son constantly flooded her ears---her son, the murderer. His heart
ached. But no matter how much it did, there was nothing he could do. He
could do nothing other than say, \emph{Mom, I'm sorry.} But Nezumi had
delivered his plea for forgiveness to his mother. He had passed on his
one-line note. Those scribbled words had pulled Karan a step out of the
depths of her despair. It was all thanks to Nezumi. For now, he knew
that Karan was not exposed to any danger. So he would suppress the pain
in his heart, and forget about his mother. He would not think of her. He
would think only of Safu.

Instead of scattering his heart hither and thither, he would carefully
select where to put it, and discard all other thoughts. He needed the
power to do it, or else he would not survive. Shion had acquired this
power long before he realized he had.

The man slowly shook his head.

"I don't believe it." He jerked his chin at Shion. "Your face is totally
different from the first-degree criminal I saw on the screen. It's like
you two are different people."

"Well, my hair colour's changed. And I've lost a bit of weight, I
think."

"No, that's not what I mean---ah, well, I guess you can say the shape of
your face, your facial features are the same... but it's different. Your
demeanour is totally different. He had really deranged eyes. He looked
aggressive---even my co-worker was saying he looked like he would kill
someone. And he was right. His eyes weren't so---gentle like yours. You
two are totally different. Total strangers."

"It's more than easy to modify someone's face," Rikiga said, through a
mouthful of the remainder of his gin. "And not just his face. If the
authorities wish it, they can conjure or twist around any information to
their advantage. Hardly something you should be surprised about,
Fura-san. Isn't it part of your job to manipulate information at the
authorities' beck and call?"

"Rather rude of you, Rikiga."

"Because it's the truth." Rikiga shook the last droplet onto his tongue,
and sighed deeply. "And that just makes it all the more difficult to
bear. Is there such a thing as real truth in No. 6?"

"I've never taken part in such lowly activities like manipulating
information. I've only handled its management and release."

"And have you ever doubted where the information was coming from?"

"What?"

"All you've been doing is receiving information from the city, and
passing it along to the media. You've never doubted the truth of that
information, have you?"

"Of course not. How could I ever doubt---"

Rikiga's thick hand rested on Shion's shoulder.

"This kid that's here in front of you, and the criminal with deranged
eyes. That gap is the gap between false information and the truth."

The man opened his trembling lips to say something, and made a guttural
noise in his throat. Though the room had no heat, beads of sweat were
forming on his forehead. After a silence that lasted for almost a
minute, the man's lips finally stopped trembling as he called out
Shion's name.

"Shion."

"Yes."

"You said you wanted information about the Correctional Facility."

"Yes."

"And you said it was to help a friend."

"Yes. The Security Bureau suddenly put her under arrest, and sent her to
the Correctional Facility."

"Her name?"

"Safu. She was supposed to be on exchange abroad, as an elite
candidate."

"Do you know her citizenship number?"

"Citizenship number..."

They had eaten together the day before Safu was to fly out on her
exchange. On their way to the station, they had been stopped by a law
enforcement officer from the Security Bureau, and asked to display their
ID cards. The number that Safu had recited was it. He closed his eyes,
and shuffled through his memory. Although he was no computer, he had
considerable ability to memorize and accumulate information, to sort and
apply it. This skill had been developed and polished from a young age.
For him, it was not difficult to instantly recall a series of letters
and numbers, even if it had only been uttered once.

"It's SSC-000124GJ."

"SSC-000124GJ," the man repeated twice. "I don't know any incident of a
citizen by that number being apprehended by the Security Bureau."

"The incident has happened, in secret. You just don't know about it."

"And you all are planning to save her?"

"Yes."

"You're going to help a criminal break out of the Correctional
Facility," the man said in disbelief. "---You're not serious?"

"Safu isn't a criminal. She hasn't committed any crime. If anyone has,
it's whoever captured her."

Inukashi yawned widely.

"Hey, you know, this is great and all, but would anyone mind if I
excused myself and went to bed? I gotta get up early tomorrow morning to
take care of the dogs."

"You're right," Rikiga agreed. "If we keep him too late, even Mr.
Big-Shot's ID card wouldn't be enough to get him back through the gates.
Shall we go, Fura-sama?"

The man ignored Rikiga, and remained stiff and unmoving. A bead of sweat
rolled down his face, mingled with blood, and dripped from the tip of
his chin. Just as the droplet hit the back of his hand, the man
whispered faintly.

"I have the latest."

"Huh?"

"I have the latest. But the portion where the new facility has been
built is still blank."

Shion widened his eyes in disbelief, and knelt on both knees in front of
the man. His voice was hoarse from excitement.

"You're going to tell us about the inside of the Correctional Facility?"

The man remained silent. He wiped his streaming sweat, and nodded.
Inukashi slipped forth. He fished out a white mouse-shaped robot, and
held its small head firmly. The robot split open at its back, and a beam
of reddish-yellow light fanned out upwards. An image appeared in it. The
man's Adam's apple bobbed as he swallowed.

"A hologram, huh."

"That's what they call it. I don't know much myself. The red circles are
where the security devices are, according to what I've gathered. So, how
is it? No mistakes, are there, old man?"

Inukashi peered into the man's face, twitching the tip of his nose. The
man continued staring at the floorplan of the Correctional Facility as
if glued to it.

"Electronic pen?" Nezumi offered a silver pen to him.

"No. I'll use my own." The extracted a pen from his inner coat pocket,
and inserted the tip of it into the light. The gauze on the back of his
hand was beginning to bleed through; the expression on his face was
tense, and his fingertips were shaking---but nevertheless, the pen swept
smoothly through the air, drawing countless complicated lines onto the
diagram.

"Whoa---awesome," Inukashi raised his voice amazement. Rikiga was looking
down at the man with a pitying gaze.

The pen slipped from the man's hand and fell onto the floor.

"This... is about all I know."

The number of security devices had grown to three times more than what
Inukashi had originally put down. In contrast, the number of cells
housing prisoners had shrunk to two-thirds. Automatic barriers were
placed in the hallways at intervals, perhaps to prevent prisoners from
escaping, or intruders from entering the premises. Once activated, they
would come down and trap any runaway or intruder. Or rather, they would
dispose of them.

Shion swallowed hard. Judging by the layout of the electrical circuits,
it looked like the barriers were made to release high-voltage current.
Once the walls blocked the intruder and cut him off from any means of
escape, the chamber would instantly become an electric chair. The
hallway would become an execution ground.

"It's like a citadel." Shion exhaled.

"It's a place of holocaust." Nezumi picked the pen up, and put it back
in the man's pocket. "Eventually it'll become a brilliant monument of
genocide."

"Genocide---" Shion repeated. "How many people have been killed here?"

Nezumi slowly shook his head.

"Shion, it's not 'have been'. It's not a thing of the past yet. People
are still being killed right now. The cells have decreased, but it's not
because there are less prisoners. There are just less of them that are
being put into the cells. You understand what I'm saying, right?"

"Yeah."

They would dispose of prisoners before they even got to their cells.
They would simply be discarded, like garbage.

Rikiga gave a short groan, and put a hand to his mouth. Sweat glistened
on his pale face.

"Stop that," he said. "It's making me feel ill."

"You must be kidding me," Inukashi said indignantly. "Don't even think
about throwing up in my room." He swung his thin arms around wildly.

"I have a question." Nezumi, still on one knee, pointed at the hologram.
"Why do you know so much? How can you remember the inside of the
Correctional Facility in such detail?"

"I had a look at it just recently---there was a section in the top-secret
files about the Correctional Facility. I skimmed through the ones about
the interior layout."

"And what exactly are these top-secret files about the Correctional
Facility?"

"Well---"

"It can't be the mayor's project. It has to be top-secret information
that's still accessible to high officials of your rank---what is it?"

The man gritted his teeth. The cut inside his mouth seemed to bother
him, and he gave a scowl.

"Is it about the Hunt?"

As soon as Nezumi said the word, both Inukashi and Rikiga looked at each
other, then looked away. Shion felt uneasy. No one had given him a
satisfactory explanation of what "The Hunt" was supposed to be. The man
remained silent as his vacant gaze wandered in space.

"Is there going to be a Hunt soon?"

"It's called a Clean-up."

"Clean-up? Oh, right. That's what you guys call manhunting. Cleaning up
garbage, right? So when is it?"

"I don't know. No set date has been decided yet. But it will probably be
before the Holy Celebration."

Holy Celebration. This was something Shion was familiar with. On this
day, all of No. 6 would be full of festivities celebrating the birth of
the city. Fireworks would be launched, and the city flag---a golden oval
symbolizing the Moondrop, set on a white background---would be hung
everywhere. Citizens would celebrate their fortuitous privilege of being
a resident of the Holy City, and would shower 'our mighty No. 6' with
praise. A year ago, Shion had been in the midst of the clamour. He could
still remember it clearly. He had been on his way home to Lost Town when
a slightly aged gentleman had stopped him. The man had reprimanded him,
and asked him why he wasn't waving the city flag and celebrating the
Holy Day. And it wasn't just that man. In the mere space of an hour's
walk from the Central Station to his home, he had been met with the same
kind of indignant rhetorical question from several people---among them a
young woman, an elderly person, and a middle-aged matron. The matron who
approached him last had even pushed a flag forcefully into his hands,
saying, "Fulfil your responsibilities as a citizen. Come on, wave your
flag." Shion remembered his discomfort, the displeasure, and his unease
at the mass of waving flags, and the voices of the crowd chanting "our
almighty City". The Holy Celebration was that kind of day.

Nezumi flashed a crooked smile.

"So they're gonna do some major housecleaning before the big day."

"The population in the West Block has grown too large. These days, it's
been burgeoning with displaced people. Violent crimes are increasing,
like the ambush at the Access Control Office that happened the other
day. It's about high time for... for a clean-up."

"And exactly how many \emph{other} places are left on this earth where people
can still live safely? If people see a place that looks more suitable to
live, they'll try to move there. Is that a crime?"

"We allow certain numbers, up to a degree."

"Up to a degree? Hah," Nezumi laughed shortly, "you mean until they
start becoming a threat to No. 6."

"Yes. If frustration builds, and the starving people of the West Block
decide to start a riot, it's just more trouble for us. We're helping to
alleviate overcrowding by doing this, you know. It should be good news
to you."

"Well, well. How considerate of you." Nezumi hunched his shoulders
exaggeratedly. Shion gripped Nezumi's shoulder firmly.

"Nezumi, you're not telling me the Hunt is---"

"The Hunt is what?"

"No way---how can it..." Shion trailed off, then began again. "Tell me.
What's going to happen here before the Holy Celebration?"

"Think for yourself!" Shion's hand was roughly shaken off. Nezumi's
voice was like a slap in the face.

"I'm not your personal tutor. If you think everyone will just hand you
your answers, you're wrong. Use your own head. Imagine." Nezumi sucked
in a breath, and softened his tone.

"I reckon your flimsy imagination would be no match for reality,
though." He dusted his hands off, and stood up.

"I'm going home," the man muttered, and raised himself unsteadily to his
feet as well. "I'm going home. Let me go."

"Fura-san, thank you for everything." The words of gratitude were out of
Shion's mouth before he knew it. His thoughts were tangled, and his
heart was still distraught from hearing the conversation between Nezumi
and the man. But he was still grateful for what Fura had given them. A
man who had been living as an elite all his life had purposely committed
a treasonous act towards the city. Shion could understand the sort of
pressure and fear that Fura was feeling right now.

"I know it's odd to say thanks after everything we've done to you, but
I'm grateful. Really, thank you very much."

The man stopped in front of the door, and turned around.

"And you?"

"Huh?"

"Aren't you going back?"

Unable to comprehend the sudden question, Shion focused his eyes on the
man's swollen lips instead.

"Do you mean to No. 6?"

"Yes. You're not considering going back to the city at all?"

"I'm not."

"You're going to stay here."

"Yes."

"Why? Don't you feel homesick for the Holy City? Don't you want to go
back?"

"I do miss some people. There are people I'd like to meet again. But I
have no intention of going home."

"Why not?"

"Because it's not a place where I ought to return. And because I've
realized that, I guess."

The man put a hand on the doorknob, and opened the door.

"You're a... a fool."

"Am I? I don't think so."

"You're a fool."

The man left the room. Rikiga followed after him. The door closed, and
the candle flickered from the breeze. The three that were left in the
room looked down at the diagram the man had left behind.

"I just remembered something." Inukashi sat down on the bed. "An old
tale my Mum used to tell me. About the northern wind and the sun. Know
about it?"

"Yeah," Shion answered. "It was in one of Nezumi's books. It was a
picture book. It's the one where the wind and the sun compete to see who
could get a journeyman's coat off first, right?"

"Yeah yeah, that one. No matter how much the wind blows and blows at the
journeyman, the guy only holds onto his coat tighter so it doesn't get
blown away. But as soon as the sun shines down on him, he takes it off
because he's hot."

"Inukashi, what're you getting at?" Nezumi knitted his eyebrows in
displeasure.

"I just thought it was like the two of you. Too bad, Nezumi. Shion was
able to get the coat off much more easily."

"Say what you will," Nezumi said dismissively. "---Shion."

"Hm?"

"Do you think we can trust this floorplan?"

"Yeah."

"You're being naive."

"You think he went out of his way to write in fake information?"

"What if he had? Maybe you just think you've gotten his coat off
successfully, but he's actually just wearing armour underneath."

"He didn't have a reason to lie. He would have known that we'd let him
go home, even if he hadn't told us anything. But he took the trouble to
give us top-secret information."

"Maybe he's set a trap for us."

"You think so? You honestly think so?"

"I'm just saying there's the possibility and the risk. But knowing that
doesn't do anything for us. What he's left us is the best information we
have. We don't have the method or the time to figure out if it's real or
not."

"So you're saying we have no choice but to believe it."

"Unfortunately."

Inukashi sprawled out on the bed and barked out a laugh. "Look at him,
trying to act cool. \emph{Unfortunately} my ass! You know, Shion, Professor
Nezumi here is actually impressed that the guy gave away top-secret
information so easily. He didn't even imagine you'd do so well. He sees
you in a new light now---he's just not showing it. Stubborn boy," Inukashi
sighed in mock exasperation. "If he's impressed, he should just admit
that he is."

"Inukashi!" Nezumi said angrily.

"Don't get mad at me. It's the truth." Inukashi's face turned serious,
and he glanced at Nezumi and Shion while he lay on his stomach.

"But what're you gonna do now, Nezumi? You serious about using the Hunt
to get into the Correctional Facility?"

"Yeah. And lucky for us, it looks like a Hunt is scheduled to happen
soon."

"Lucky, huh," Inukashi echoed. "Just to tell you, I'm opting out of
this. I don't want anything to do with something this risky, and I don't
have any obligation to be involved."

"Your chance to shine is just coming up," Nezumi said. "I've got work
for you to do outside of the Facility. The alcoholic said so too: we're
in this together until the end. There's no way you can take your two
gold coins and run. You know that, don't you, Inukashi? More than anyone
else."

Inukashi stuck his lip out, and pulled his face into a scowl. Nezumi
cast a hand over the hologram, and called Shion's name.

"Shion."

"Hm?"

"Memorize this entire floorplan. We won't be able to take any
micro-robots into the Correctional Facility. Any machine that's not
equipped with a recognizable chip will be destroyed, no matter how
small. Take one wrong step, and whoever's holding the machine will
probably be blown up along with it. And we won't have the time to pull
out a map and check our bearings every time we get lost."

"You want everything from this?"

"Everything. Commit it to memory perfectly. I want every sensor
location, security system layout, and the location of every garbage bin
memorized, without any errors. Even a tiny incongruity can cost us our
life."

"Alright."

Nezumi tossed the micro-robot to Shion.

"We don't have much time. Commit everything to memory perfectly---that's
your assignment."

"That's a more difficult assignment than anything I've gotten before."

"How confident do you feel?"

"Confident."

\emph{Huh.} Nezumi blinked and gave a huff. It seemed like he had not expected
Shion's definite answer.

"I guess I should have known you'd be good at doing brain-work, huh?"

"It's not a question of whether I'm good at it or not. It doesn't matter
whether I can or can't---it's something I have to do."

Lives depended upon it. Safu's, Nezumi's, his own; Inukashi's and
Rikiga's irreplaceable lives depended upon it.

He clenched his hand around the white micro-robot. Even if he squeezed
hard enough to crush it, the man-made machine never screeched in alarm
like Hamlet or Cravat, nor did it feel warm and soft in his hand like
them. It was merely stiff and cold. Nezumi's lips relaxed into a smile.
He chuckled softly.

"Looks like you've learned to grasp the situation a little, at least."

"You trained me."

Nezumi pursed his lips.

"---Stay close to me," he muttered.

"Huh?"

"The Hunt is coming soon. Stay close to me, and don't wander off.
Wherever you go, keep in sight of me. If we lose sight of each other in
the middle of the Hunt, we'll probably never see each other again. Your
chances of living will go down drastically, to say the least."

"Got it," Shion said heavily.

"I think the chances are low enough without you losing sight of him,"
Inukashi's whole body shook as he laughed. The rusty bed-springs creaked
and made an irritating noise. "When people get captured during the Hunt,
they get thrown into the Correctional Facility where most of them die or
go insane. It'd be a miracle if you could live through it and manage to
come back out. It'd be as miraculous as the sun splitting in two."

"You can make miracles happen more easily than you think, Inukashi.
Hasn't your mom told you?" Nezumi threw the superfibre cloth around his
shoulders, and headed for the door. Inukashi called after him.

"Nezumi, there's more."

"More? More what?"

"Mum didn't say anything about miracles, but she told me this after the
story of the wind and the sun. 'No wind or sun can take our hides off
us,' she said. 'You may not have a coat of fur, but don't you ever give
in to the wind or sun.' And then she licked me all over."

"Admirable mother you've got."

"She's the best." Inukashi leapt off the bed, and glided to Nezumi's
side. "I've been raised by my Mum. I still remember how her fur used to
feel, her scent, and what she told me. I remember, and that's why---"

"What?"

"That's why I'm going to survive. I'm going to keep on living here with
my dogs. Even if you guys die, even if you never come back out of the
Correctional Facility again, I'll still keep living. I'm going to live,
and tell the rest of the dogs about my Mum."

"A fine vow. Your deceased mother would probably be overjoyed to hear
that." Nezumi's hand stretched forth to stroke Inukashi's tan cheek.

"Good night, my boy. May God bless you with sweet dreams to give you
strength for tomorrow," he said gently, in a woman's voice. Before
Inukashi could open his mouth, Nezumi had disappeared out the door.
Inukashi spoke to the darkness.

"Just watch me---I'll live through it without you all."

"We'll all live through it," Shion said quietly. Death was not in their
plan. They would act, think, and fight to live. To survive---together.

"Oh, I forgot to say something." Nezumi's breezy voice echoed from the
darkness. "Inukashi, if you want a good-night kiss, I suggest you get
one from Shion. He would give you a very adroit and passionate kiss,
indeed."

"Nezumi!" Shion said indignantly.

Nezumi's laughter faded into the distance. It became one with the sound
of the wind, and was sucked into the darkness.