% !TeX spellcheck = en_US

\chapter{Flight for life}

\lettrine{S}{hion inserted} his ID card into the card reader of the Park
Administration Office. The door opened soundlessly, and the air
filtration system and temperature control started up. There was no one
inside the office yet. It was odd that Yamase was not here already.
Shion turned on the switch of the park administration system. It was the
start of another work day.

"Good morning." An image of City Hall, The Moondrop appeared along with
the greeting. "Your unwavering allegiance to the city---"

He placed his hand on the image of the Moondrop and recited slowly.

"I pledge hereon and ever my unwavering allegiance to the city of No.
6."

"Our gratitude for your loyalty. Engage in your day's labour with
sincerity and pride as a good citizen of the City." The Moondrop
disappeared, and was replaced with a report of the living conditions of
all the organisms in the Park. Shion breathed a sigh of relief. The
daily allegiance rituals had become a source of discomfort for him.
Although it was among the farthest branches, Park Administration Office
was still under direct affiliation with the City. All employees were
required to pledge allegiance to the City every morning. If they
refused, they would lose their job.

It was no big deal. All he had to do was cast his hand over the display,
and recite the same words. Shion tried to brush it aside, but the worn
and banal words of the pledge, and the sheer ridiculousness of the
ritual itself always filled him with disgust. And for repeating this
banal and ridiculous ritual every morning, Shion's injured pride stung.
He remembered Safu complaining of the same thing. The laboratory where
Safu worked also operated under the City, so an allegiance ritual was
mandatory as well.

Shion lightly blew on his palm. It was no use complaining. As long as he
was to be a citizen of No. 6, as long as he was going to continue living
here, it was no use fretting about pride. So he kept telling himself.

The office door opened, and Yamase came in. Behind him stood a woman who
looked about in her twenties. Yamase called over to her softly, but she
shook her head, bowed slightly, and left in a hurry. She was a small
woman with long hair.

"I see\el " Shion stopped his hands over the control keys and turned to
stare into Yamase's square, angular face.

"It's rare to see you with a woman, Yamase-san. Could she be---" He went
on to say 'your girlfriend', but promptly shut his mouth. Yamase was
sitting at his control panel, reciting the pledge of allegiance to the
city. His expression was tense. Shion could tell from his face that this
wasn't the right time for teasing.

"Yamase-san, is something the matter?"

"Shion, that lady\el " Yamase paused, and turned to Shion. "She's the
wife of yesterday's body."

"Huh?"

That would make them a couple of enormous age difference. No. 6 had no
strict regulations for marriage, as long as it was between two
consenting registered citizens. Even if the couple had not gotten an
official marriage certificate, it was not a problem. The problem was
more with whether they would be able to prepare an appropriate
childrearing environment if they were to have children. Childbirth was
not permitted for people who didn't meet the city's criteria of
standards. Shion didn't know what those criteria were. Nevertheless,
people were free to marry, and a couple or two with this much age
difference was nothing out of the ordinary.

"She says they're only three years apart," said Yamase quietly. Shion
didn't understand. "He was three years older than her," Yamase repeated.

"Three years\el but---"

Yamase nodded. "That body was only 31 years old."

"No way!" exclaimed Shion incredulously. "That can't be. That body was
an elderly man, no matter how you look at it."

"Yeah," said Yamase heavily. "I was surprised too. But the body hasn't
come back to the madam since. They're keeping it over at the Bureau."

"Keep? So you're saying an autopsy wasn't enough to find out how he
died?"

"I guess that's what it means."

They couldn't find the cause of death. Shion couldn't imagine a cause of
death that No. 6's front-line medical technology couldn't decode.
Medicine had long had full bearings on organism analysis to the
nanometre scale. An average cell measured approximately 20 micrometres.
A micrometre was 1000 times larger than a nanometre. Any disease at the
cellular level should be more than easy to find and analyze.

Shion felt a chill. Abnormal rigor mortis, its dissipation, and the body
it left that was unmistakably that of an elderly man---what did it all
mean? He didn't know. At present, Yamase's low voice spoke again.

"The madam was told that he died from an accident in the park, and to
wait for further notice until they figure out his cause of death. She
came here today asking if she could at least see where the accident
happened."

"Accident? Bullshit!"

"You're right, it's a load of bull. Them telling her it was an accident
is a huge lie," Yamase replied, and scratched his neck vigorously in
irritation.

"Yamase-san, why does the Bureau have to lie about it? And isn't it
strange that they can't seem to find a cause of death?"

"Yeah\el this incident is full of unanswered questions."

"If the Bureau can't explain it, could it be a cause of death that's
never had any previous case?"

"No previous cases?"

"That man died from something that was completely unknown up until now,
something no one's experienced before --- is that possible?"

"Shion! What are you\el " Yamase trailed off. His face was pale. Shion
figured his own face must look the same.

"Let's have some coffee, shall we?" Yamase suddenly stood up as if he
couldn't bear the tense atmosphere any longer. Shion hastily stood up
after him.

"Oh, let me---"

"No, I'll do it. You like lots of milk in yours, right Shion?"

"Thanks." Shion paused. "So---but anyone could look at the body and tell
it wasn't an accident, right?"

Yamase turned toward him. His usual gentle face was strangely contorted.

"Yamase-san?"

"Shion, bodies can be modified."

"Huh?"

"I---" Yamase stammered. "Before I started working here, I used to work at
the Municipal Central Hospital. My job was to modify dead bodies."

"Modify---what do you mean?"

"I wasn't planning to tell this to anyone, but\el " Yamase hesitated.
"Shion, have you ever seen a dead body before?"

"Once, at a funeral for my grandfather on my mother's side. I saw his
body in a coffin at the viewing."

"How was it?"

"How\el ? He looked peaceful. Don't they all look like that?"

"You think so?"

"Are you saying they don't?"

Medical technology had made enormous progress not only in the fields of
disease treatment and prevention, but also in the removal of pain.
Technology of the present day could remove anything, whether it be from
accident or illness, ranging anywhere from pain during surgery, to
breathing trouble, severe pain and seizures experienced in the moments
leading up to death. People ended their lives free of suffering, and all
died with peaceful expressions on their faces. That was what Shion had
been told.

Yamase handed him a cup of coffee. He lowered his gaze and bent his neck
to scratch it, as if to avoid Shion's gaze.

"All this about front-line medical technology goes right over my head,"
Yamase said slowly. "But all I know is that\el no matter how much
technology develops, it's impossible for everyone to die a peaceful
death. That much I'm sure of." Yamase's face contorted even more. The
hand which held his own mug trembled slightly.

"I worked for a long time in the basement of the Central Hospital. My
job was to modify the bodies that were brought there."

"Yamase-san, so what's this about modifying bodies?"

"It's an easy job. When the body's been confirmed dead and brought down,
I would coat its face with a special chemical and cover it with this
apparatus. And then---"

"Then?"

"Then it would smile. All of them did. They would all look like they
were having some wonderful dream."

Shion almost let out a cry. It was just as Yamase had said. He was nine
years old when he saw his deceased grandfather's face, and he had been
smiling.

"It's almost like he's having a wonderful dream," he remembered his
mother whispering through her tears.

"Of course," Yamase continued, "the majority of people that die don't
need to be modified. They're all people that have been able to get
proper palliative care, and have really died a peaceful death. But it's
still only a majority --- not the entire population. There are a small
number of people, though, that die tragically, their faces all stiffened
up in pain."

"For example---?"

"Huh?"

"What kind of people die like that, Yamase-san?"

Yamase exhaled shortly, and drained the rest of his coffee. "I don't
know. My job was only to coat the faces with the chemical and cover them
with the apparatus. I didn't know why these people had to die with such
suffering and sadness in their faces, and no one would tell me." He
paused. "But--- there was this one time, a middle-aged man was brought
in\el I usually have to wipe the face before applying the chemical, and
I noticed that the man had tear streaks on his face, and --- and I thought
--- maybe he'd been crying right up until he died. I wondered if he'd been
crying the whole time while he was dying. And then I just had this
thought that--- maybe this man had killed himself."

"Killed himself? A citizen of this city---?"

"You think it's impossible?" Yamase asked flatly.

"Of all causes of death in the last ten years, suicide has only been
0.05\%. And most have been impulse cases due to temporary psychosis, so
they technically don't even fall into that criteria. According to the
city's statistics, anyway."

"According to what the city has published as statistics, yes," Yamase
rephrased.

Despair did not exist in No. 6. All citizens lead a secure and
hospitable life. There was no starvation, no war, no anguish. Not even
any pain in the moments leading up to death.

\emph{You guys have been programmed to think this holey mess is the ideal
utopia.} Nezumi had spat these words out four years earlier. Now, Shion
was experiencing its reality word for word. Lost Town was full of people
who had abandoned hope. They had enough to eat, and enough to keep
living. But they had no hopes for the future. Lost Town wasn't the only
place---maybe the same could be said for Chronos. How many people could
die with a real smile on their face, and say they've lived a fulfilling
life?

"Yamase-san, are you saying that the Bureau is manipulating
information?"

"Shion!" Yamase warned, knitting his brow and shaking his head
violently. "Don't say stuff like that out loud. We've been hired by the
City. We've pledged allegiance. We shouldn't be talking about our
suspicions. I don't know what's gotten into me. Forget everything I
said. Just forget it."

"Alright," Shion replied uncertainly.

"Right then, let's get Sampo and the rest moving. Where were the main
regions today?"

"Areas JK02 to ER005. Mainly cleaning up foliage."

"Alright, let's get to work."

"Right you are." They began to tap the control keys for the robots.
Yamase gave a short grunt of pain.

"Yamase-san?"

"Ah, it's nothing. It's just---my fingers are strange."

"Hurt?"

"No, no\el it's like they feel stiff\el " He stood up unsteadily, and
then suddenly crumpled to the floor, his face in his hands.

"Are you alright?"

"My eyes\el I can't see\el they're blurry\el "

In the midst of reaching out to support Yamase, Shion froze. He couldn't
move. Yamase's hair was turning white. Spots were beginning to spread
over the hands that covered his face.

"Shion\el what's---what's happening to me\el ?"

Frozen in horror, Shion watched as Yamase aged with astonishing speed
before him. He curled up as he lay on the ground, and his back
contracted in violent spasms. He was having trouble breathing. Shion
lunged for the emergency intercom.

"We have an emergency. An ambulance, please. Quickly!"

Yamase coughed weakly. \emph{What was happening? What was going on?} Shion
couldn't believe what was unfolding before him. Everything seemed
surreal. His mind was in a panic --- he didn't know what to do, how to
deal with it. But still another part of him remained unsettlingly calm.
\emph{Observe. Analyze. Watch. Don't take your eyes off of him. Take in
everything you can and absorb it as knowledge.}

Shion swallowed, and lifted Yamase in his arms. After a few weak spasms,
Yamase's body was still.

"Yamase-san?" His face was unmistakably that of an old man. And it was
no longer that of one who was living. Shion checked his pulse and
pupils. Yamase's body grew colder by the minute. His mouth was open as
if in astonishment, like the man from yesterday.

\emph{Shion, how can this happen? I can't believe it.} Shion could almost
imagine those words tumbling out of his parted lips.

\emph{I have to close his eyes, at least.} Shion pressed his fingers on
Yamase's eyelids. They didn't close. Rigor mortis had already begun to
take its course.

Shion crouched beside Yamase, clenched his fists, and continued staring
at his colleague with whom he was having a conversation only moments
before. Feelings of fear, sorrow, or pain were curiously absent. It was
as if all his feelings had gone numb.

\emph{Observe. Analyze. Watch. Don't take your eyes off of him. Take in
everything you can and absorb it as knowledge. And memorize it.
Memorize. Memorize---}

Cessation of respiratory and cardiovascular activity. Decrease in body
temperature. Rigor mortis. Death spots. Dissipation of rigor mortis.
Postmortem phenomena that usually took dozens of hours was taking place
in a mere fifteen, sixteen minutes. It was if he was watching a film on
fast-forward.

Shion watched unmoving, his eyes wide open, biting his lip in
concentration. He could predict what was going to happen next. He was
sweating. A warm bead of perspiration slid from his temple down his
cheek. Its heat reassured him that he was still alive.

\emph{Living people are warm.} You were right, Nezumi. People are warm because
they're alive. Four years ago, you knew this.

A stain appeared on Yamase's neck. It was dark green, almost black.
Shion bit his lip harder. The taste of blood spread inside his mouth.
There it was, it was starting---what was previously unknown, what no one
had ever experienced before. He leaned forward. The stain moved. The
skin over that portion swelled slightly, and stirred.

A buzzer went off. Sampo was sending an Indistinguishable Object signal.
Oblivious to the changes that were happening in the office, it seemed
like Sampo and the rest were going about their cleaning duties as usual.
Shion ignored it. He had no attention to spare. All the nerves in his
body were focused on the stain. His eyes were glued to it, and he
couldn't break his gaze.

Shion let out a muffled cry of horror. He clutched his chest, and felt
his own heartbeat thudding against his palm. He jumped back. An insect
had eaten its way out from under the skin of Yamase's neck, and was
wriggling to get free. It was the same colour as the stain it had come
out of. It had thin silvery wings, six legs, antennae, and a needle-like
ovipositor.

"A bee\el "

A bee had just eaten its way out of a human body. How could that---

The insect took flight. He followed it with his gaze, and saw the
Medical Bureau's ambulance pull up in front of the office. A sudden
darkness veiled his eyes.

He was fainting from shock.

The black insect was darting around in his darkening vision. Shion
groaned, and curled up on the floor.

\myspace

Shion awoke to a blinding light stabbing at his eyes. He heard a quiet
male voice speak.

"Awake?"

Light was streaming through the window, and the man had his back to it.
His face was thrown in shadow. The shadow spoke again.

"Get up. I have something to ask you."

It was a voice he'd heard before. Shion came to, and noticed he was
lying on the office sofa. Yamase, wrapped in a white cloth, was being
carried out of the room. It seemed like he had fainted for only a few
minutes.

"Yamase-san."

Shion called the name of his colleague almost without thinking. Yamase's
smiling face crossed his mind. Fragmented memories --- how he loved
coffee, and drank several cups of it a day; his quiet demeanour; his
habit of sheepishly looking at his feet --- all at once burst forth in his
mind.

They weren't particularly close. To Shion, he was just a senior
colleague. He had never confided in Yamase, nor had they ever had a
deeply personal conversation. But Shion had liked Yamase. Yamase never
intruded unheeded into anyone's personal space, but that didn't mean he
was disinterested. He was a good person. But he was no more.

"Yamase-san\el " His eyes began to sting. He was tapped lightly on the
shoulder.

"Let's get emotional later, shall we?" The man spoke lazily and without
emotion. Shion's heart jumped unpleasantly.

"Can you explain the situation to us?" This voice, these words. He had
heard them before.

"You're\el "

"It's been a while, hasn't it. It's nice to see you still remember me."

It was Rashi, the Interrogations Officer from the Security Bureau. He
had the same gentle tongue and unsmiling eyes as four years before.

"You'll tell us everything you know, won't you?"

Shion found himself nodding automatically. He could feel his mind begin
to unravel slowly. His head and body felt heavy, and his own voice
sounded as if it was coming from far away.

\emph{This is bad.}

A warning signal sounded in a corner of his mind. But he couldn't
regulate himself as well as he could yesterday. Each question that Rashi
asked dragged words forth helplessly from his mouth.

"A bee?" Rashi furrowed his brow. He gazed around the room, and cocked
his head to one side in perplexity. There was no insect, bee or
otherwise, to be found in the room.

"I'm not buying it."

"Check Yamase-san's neck, there should be a scar---" He swallowed his
words. There should be a scar. There should have been one, the same, on
the neck of the man yesterday. The Bureau had investigated that body as
an unnatural death, there was no way they could have overlooked it. They
had noticed, but had told his bereaved wife that it was an accident.
They didn't want the real cause of death to be known --- that was what it
boiled down to.

Shion turned his head to the side, as if to avoid Rashi's gaze. He had
spoken too much. He had divulged everything he knew, which might have
been something that the Bureau intended never to reach outside ears ---
classified information that they were intent on covering up. If that was
the case---

"You used to specialize in ecology, correct?"

"I intended to, but I never did. I have nothing to do with it now."

"And were you interested in the biology of insects as well?"

"Ecology encompasses everything that has to do with interactions of
species with their environment. Insects weren't the only thing I was
interested in."

"Ah, is that so? And specifically, what do you mean in terms of
relationship between organisms and their environment?"

"Well---"

Shion could feel himself breaking into a cold sweat. A thin smile played
on Rashi's lips while he spoke, his words light, his tone
conversational. But his gaze never left Shion once. Two officials of the
Security Bureau came in. One of them whispered in Rashi's ear.
Momentarily, Rashi spoke.

"I hope you won't mind coming down to the Security Bureau for a bit."

"Huh?"

"It's nothing really, we just want to hear more of your story. It'll be
over in minutes. I promise we won't take much of your time if you come
with us."

"I---"

A buzzer sounded. Sampo was sending an Indistinguishable Object error.

"I'm sorry, I have to operate the cleaning robots\el "

"Put them away. In any case, you won't get much work done today."

Shion ignored him. He minimized the error display, and switched over to
the camera. A small grey mouse appeared on the screen. It was scurrying
up and down Sampo's arm. Its mouth was open wide, and it was mouthing
something incessantly. Shion brought the earphones to his ear and turned
on the sound sensor.

"Shion." Nezumi's voice flowed through to him. "Get out of there. You're
in trouble."

\emph{What?}

"Get out."

Click. He heard a sound behind him. Shion turned, and found himself
staring down a pair of gun barrels. He couldn't distinguish what model
they were. But he knew that these were no high-tech stun guns, no, none
of that sort --- they were older models, highly effective in the kill.
Sport-hunting hobbyists liked to use these kinds of guns. Shion slowly
flicked Sampo's speaker switch on. Now, Nezumi's end would be able to
hear his voice.

"Are you forcing me under arrest?"

"I guess you could call it something like that. Regardless, you're
coming with us."

"Don't you need a reason to arrest me?"

"A reason? None of that. But if you insist\el your bicycle, perhaps?"

"My bike?"

"You were using a bicycle without speed-limiters. That's a breach of the
law, and more than enough reason to put you under arrest."

"What---how---for such a ridiculous reason, without even going through the
proper procedures? Using violence? Is this how you arrest a citizen of
the city? What happens to my rights?"

"A citizen? Rights?" Rashi sneered. A violent chill ran down Shion's
spine.

"You really think you have any of those?"

He could hear Nezumi click his tongue. \emph{Tsk.}

"Guess I didn't make it in time."

Shion exhaled, and began shutting down the operating system. Just before
it turned off, he heard Nezumi's short message ring out clearly.

"Shion, don't panic. I'm coming to help you."

\mybreak

He was right. Don't panic. Calm down. Be of sound mind. He had to buy
more time. Shion relented.

"Please don't use any violence on me."

"We won't, of course. As long as you co-operate with us."

"It wouldn't be any use to retaliate anyway, would it?"

"Is it your policy not to take useless action? There's a good lad, he
knows what he's talking about. It's a waste, really."

"A waste? What is?"

"For you."

"I don't understand what you're talking about."

"You'll know in good time. You've always been smart and quick to
understand, like you were four years ago."

Flanked by two Bureau officials, Shion climbed into the car. Above them
was an expanse of clear, blue autumn sky. The sun was bright. The birds
were chirping. A gentle breeze blew past them. Times of peace and
tranquility they were.

\myspace

The car glided forward.

"Nice weather today," commented Rashi from the passenger seat, without
turning around. The official sitting on Shion's right side nodded in
response. "It looks like we've been having more warmer days than usual
lately."

Rashi turned to Shion and smiled.

"And yourself? Do you have a car?"

"No. I usually take my bike or walk."

"That's a good thing. Young people like you need to move their bodies
more. By the way, what we're riding right now is a battery-operated car.
Quite comfortable, don't you think?"

"Excellent I would think, if it wasn't for the situation I'm in right
now," Shion replied sarcastically. In means of retaliation, it was the
best he could muster. Rashi shrugged lightly.

"As I was saying, this car runs on fuel-cell batteries. Any idea how
they work? We aren't too well-versed on the scientific side of things,
I'm afraid."

"I don't know much either."

"What sort of things do you know about it?"

"Not much\el I mean, I don't really have a lot of scientific knowledge."

The officials on both sides of him moved at once. He was grabbed firmly
by the arms. Rashi's tone changed to that of an interrogator.

"Then just tell us what you do know."

"Like I said, what I know--- it's all just general knowledge."

"Such as?"

The conversation was short, clipped and void of frivolity, but Shion
felt a sort of strangling heaviness about it. He felt like someone was
choking him slowly with a soft, damp piece of cloth. He felt nauseous.

"So\el through electrolysis, alcohol is separated into oxygen and
hydrogen, and by fusing them together again, energy is---"

"Energy is what?"

"Where are we going?" Shion asked suddenly. He rose, but was yanked back
and shoved into his seat.

"Aren't we going to the Security Bureau? This isn't the way." The Bureau
was located beside City Hall. From the Park Administration Office, one
only had to cut through the park to get there. By car, it was a few
minutes' distance. But the scenery out the window showed him the car was
heading in the opposite direction.

"Where do you think we're going?"

"That's what I'm asking you right now," said Shion testily.

"You're not entitled to ask any questions."

"What---how could you---why---"

"Haven't I told you? You're a top suspect in this case."

"What case?"

"The death that happened today, and the other one from yesterday. You're
on suspicion of murder."

Shion had lost his voice. He could hear the rush of blood in his ears as
it receded from his face.

"You're a dangerous suspect. You have extensive knowledge and an
intelligent brain to put it to use. I could tell just from our
conversation. And to top it off, you're dissatisfied with your situation
and feel a strong resistance against the City. Superior ability and
hostility toward the City. Take either one, and they aren't of concern
by themselves. But you have both. Dangerous, indeed."

"Those are false accusations."

"False? I beg to differ." Rashi's hand extended to a silver button
beside the steering wheel. Shion's and Yamase's voice began to play from
the speakers.

\emph{'Yamase-san, why does the Bureau have to lie about it? And isn't it
strange that they can't seem to find a cause of death?'}

\emph{'Yeah\el this incident is full of unanswered questions.'}

Shion closed his eyes. It was the conversation they'd had only minutes
ago. They were being tapped the whole time. Had a microphone been hidden
in the control panel? But for what purpose?

\emph{'Yamase-san, are you saying that the Bureau is manipulating
information?'}

\emph{'Shion!'}

Rashi pressed the button lightly again. The voices were cut off. For a
moment, a cold silence fell in the car as if the very air had frozen
over.

"Care to hear a little more?"

"Please\el stop\el I can't believe this."

"Can't you?"

"I didn't kill anyone," said Shion flatly.

"So you're saying that this \emph{bee} that you were talking about is the real
murderer?"

"Yes."

"Preposterous. A rather contrived story for someone of your
intelligence."

"What reason do I have to kill Yamase-san?"

"That's what we're going to figure out. My guess is that you wanted to
start a commotion."

"---Huh?"

"A commotion. You wanted to start a huge one, enough to shake the very
roots of the city, and bask in its glory. You must have regarded
yourself as some kind of genius fallen upon ill fortune, haven't you? So
you loathed the City for not favouring you as you deserved, and felt
hatred toward its citizens. You believed you deserved more attention, so
you thought of this method of murder, this unnatural death, to take
society by storm. You had the medical and biological knowledge to do it.
It was very well possible that you used some kind of special chemical to
commit murder."

Shion sank deeply into the car seat. All energy had left his body. He
realized it was a trap. He had walked right into its cunning grasp. He
licked his lips. They were parched and dry.

"I see," he said coolly. "So it's all been scripted already. Rather
\emph{contrived} story yourself, maybe even more than mine."

"We'll see how contrived it is once we get through questioning you."
There was a metallic clang. The official on Shion's left had handcuffed
him.

"There's a transmitter on those, and it lets us know where you are. When
we get there, you'll get to take them off." Rashi's words gave Shion an
idea of where he was going. The West Block. The Correctional Facility.
If he was undergoing investigation there, he was sure to be locked up
right afterwards as a convict. In exchange for removing his handcuffs,
he would have a V-chip implanted into him.

\emph{---Nezumi, it's too late. I can't get away.}

He closed his eyes, and took a deep breath.

"There's a good lad. Keep quiet."

Shion remained slumped, and bit his dry bottom lip.

\emph{I'm coming to help you.} Nezumi's voice echoed in his ears. His heart
grew calm. His legs trembled, though not from despair or fear, but rage.
Rage at the people who had tricked him. Nezumi's voice kept that rage
afloat. The car entered Lost Town.

\emph{---Mom.}

"Are you worried about your mother?"

"My mother---what---what'll happen to her?"

"Happen? Nothing. She won't be stripped of her citizenship just because
her son is a convict." Rashi whispered something to the driver. The car
veered to the right. A familiar scenery of the streets came into view.
The car stopped silently at the curb.

"Look."

Rashi pointed. Karan was in the midst of handing a small girl a wrapped
loaf of bread. She said something to her, and the girl nodded. Both
Karan and the girl were smiling. Enveloped in the amber light of autumn,
the two looked as if they were part of a painting, or a scene from a
drama. Shion leaned forward.

"Your mother looks like a gentle lady. Get a good look at her while you
can." Rashi motioned with his chin, and the car began to move. "You may
never see her again."

Rashi chuckled with his back to Shion.

"It's nothing to be so troubled about. Sure, at first your mother will
be shocked, and she'll feel sad. But she'll get over it. That's how life
is. Well, it's not like anything would come of you worrying about her
anyway. Soon you'll find you'll have things more serious to worry
about."

Rashi's words sliced at Shion's heart. His breath caught in his throat.
The rage and rebellion simmering inside him slowly began to dissipate.
He would never be able to return to his his normal life again. He had
been separated from it forever. Seeing his mother etched the feeling of
despair deeper into him.

They had calculated it all. They didn't stop the car near Shion's house
out of pity for him. They had done it to deal him the final blow, the
blow that knocked him down and told him, give up, lose hope, you're
never going back again. It was a cunning and cruel trick to make him
lose the will to retaliate.

"I'm coming to help you. I'm coming to help you."

Shion opened his mouth and repeated the words to himself.

\emph{I'm coming to help you.} Just a short sentence. But Nezumi's voice had
been steady with confidence.

\emph{What did he look like again?} He wondered, and tried to visualize
Nezumi's face. He could only remember a pair of light grey eyes.

\emph{---Will I see you soon, Nezumi?}

"What's that?" Rashi turned around, and furrowed his brow.

"Are you smiling?"

"Smiling? Of course not," Shion replied. "I don't have the courage to
smile in this kind of situation."

"In this situation, huh\el you seem rather calm about it. I hope you do
understand exactly what kind of situation you're in right now."

"Almost too well."

"Aren't you calm and collected in spite of that."

"I'm a natural."

"A what?"

"A natural," Shion repeated. "I've been told that by someone once. That
I'm a natural at not getting it."

Rashi stared at Shion in silence. The car was exiting Lost Town and
approaching the western border. It was Shion's first time here, because
regular citizens were not allowed to enter into this area. No. 6 was a
citadel--- a wall made of special alloy circled the city and enclosed it.
In most parts if the city, the wall was camouflaged well with trees, but
in the West Block it stood bare. The car bypassed the Access Control
Office.

"Aren't you going to enter the West Block from here?"

"There are two gates. That one was for entering and exiting the city.
The other one is especially for entering the Correctional Facility, it
leads directly into it. The Correctional Facility is a special kind of
facility, even in the West Block. We keep it completely isolated from
all general citizens. I bet you didn't know that."

"No, I didn't."

"You'll find out even more soon enough."

The path narrowed. An increasing number of trees blocked the sunlight.

"Once we're through the woods, there will be nothing but wastelands.
Past the gates it'll be the same. It'll probably be the last time you
see any greenery, so I advise you engrave it into your memory well."

The car stopped.

"What's the matter?" Rashi asked.

"Ah, it's just\el " The driver pointed to something in front of them. A
silver-coloured lump was laying across the middle of the road. Slowly,
it raised itself.

"Sampo?" Shion swallowed.

"What's this? What's a cleaning robot doing here?"

"Maybe it has orders to clean the forest area?"

"I haven't heard anything about it."

Sampo was scooping up fallen leaves with his metal arms.

"Keep an eye on the suspect." Rashi ordered the officials, and got out
of the car. He approached Sampo. Sampo swayed, its arms grabbing ahold
of Rashi. Clinging to him, it fell forward.

Rashi gave a short cry, and was dragged by Sampo to the ground amongst
the trees.

"Ah!" The driver raised his own voice in surprise, and opened the door
to lean forward. The next moment, two small shadows darted into the car.
They were two grey mice. In a flash, they each latched onto the throat
of a Bureau official.

"Don't move," a low voice commanded. A person slid into the passenger
seat. A grey cloth covered his head and was wrapped around his
shoulders. From them, a brown mouse sprang onto the base of the driver's
neck.

"These guys have small bombs planted in their bodies. Try anything
funny, and you can count on your heads being blown off."

The driver whimpered in terror.

"Take his handcuffs off. And the three of you, get out of the car."

No one moved.

"Quickly!" he ordered sharply. "I'm impatient. Do you want me to set
them off?" There was a metallic sound from the mice that were latched
onto each throat. Click. Click. Click. The handcuffs fell from Shion's
wrists. The three men tumbled out of the car, bleeding at the neck.

"Nezumi!"

"Greetings later." Nezumi gripped the steering wheel. The car spun
around in a U-turn, and hurtled down the road at full speed.

"Nezumi, are you really going to make them explode?"

"Idiot. You think I would plant bombs into my faithful friends? That was
just to scare them."

"Were those robot mice? They looked just like the real thing. And with
Sampo, how did you---"

"Shut up," Nezumi growled. He yanked the cloth off his head, and threw
it to the backseat. "Wrap that over your head and stay curled up."

"Is this superfibre? Why do I have to wrap up in this?"

"Because I'm going to crash it."

"Crash what?"

"The car."

"What!? Why---"

Nezumi's fist pounded the steering wheel.

"Just shut up, alright? Is asking questions all you're good for?"

"But we can just escape with the car."

"I was planning to, but---"

"But what?"

"It went too well." They were approaching the wall that separated the
West Block from No. 6. The car showed no signs of slowing down. "It
shouldn't have been this easy to rescue you."

"Really?"

"You're naturally dense, you wouldn't know. It doesn't get any more
dangerous when something's gone too well. That's why we're going to dump
this thing. When I tell you to, wrap up in that cloth and jump out of
the car. I'm gonna crash it."

"How about you?"

"I'm used to this kind of thing. No need for the dense boy to worry
about me."

"I can't just leave you!"

The wall was looming closer.

"Get out, open the door!" Nezumi yelled. Almost simultaneously, the
tires screamed as the car screeched to a halt. Shion's body floated up.
The next minute, he was being slammed back against the seat. If it
weren't for its shock-absorbing material, he probably would have broken
a few bones.

"Damnit!" Nezumi kicked the door hard. It didn't move.

"Is it the automatic brake system?" Shion winced at his bruised shoulder
as he asked.

"I disabled that a long time ago. I disabled the alarm system, the
collision sensor system, everything. This car's being controlled
remotely," Nezumi said angrily.

A chuckle resounded throughout the interior of the car. It was Rashi's
voice.

"I won't have you underestimate the Security Bureau. The car that you
boys are riding is actually an escort cruiser, though you might not have
noticed. It's not something you can control so easily."

Nezumi swore.

"I didn't know you had an accomplice. That was something I didn't
expect. It was quite the spectacle, very impressive. Why don't we have a
nice talk, and I can hear all about it."

The car changed directions, and began to move on its own.

"Rather quiet, hmm? Can your friend not talk? Or does talking pose some
kind of problem? Ah, your voice sample must be in the system, which
means you have a criminal record."

"I think \emph{you're} talking a bit too much." Nezumi's hands moved swiftly.
"I'm sorry, but I don't have time for pointless conversations with old
men." Nezumi moved to the back seat and pushed Shion down. "Duck and get
under the cloth. Hold on tight."

"Hey! What are you doing?" There was a note of panic in Rashi's voice.

"See ya, old man. Say goodbye to your high-tech escort cruiser too."

"What---"

There was a blast. A wave of impact slammed into them.

"Get out!" The short command burst at Shion's ear. The door opened. A
gust of hot air swept over them. \emph{Outside. I have to get outside.} Shion
screwed his eyes shut, and leapt into the outside world. He hit the
ground, and rolled. Behind him, he heard an enormous explosion. The car
was on its side, its wheels in the air spinning helplessly.

"Good job," Nezumi whistled. "You rolled pretty well for someone with
such a big head. Not hurt, are you?"

"I scraped my arm pretty badly. You?"

"I told you, I'm used to this."

"What did you do?"

"I destroyed the steering system."

"How?"

"Escort cruisers might be durable on the outside, but they're delicate
on the inside. As long as you set it in the right place, any small bomb
will put it right to sleep."

"You seem to know a lot about it."

"Like I said, I'm used to this. Right, now to get out of here. Can you
run?"

"Of course."

They emerged from the wood to see several Security Bureau cars
approaching in the distance. The area had probably been put under
emergency alert.

"Throw your ID card away," Nezumi ordered quietly. "Hurry up, there's no
time to waste. That thing is only going to be a danger to us."

Shion knew. His ID card carried all his personal information, and it was
connected to and stored in the city's administrative computer system.
The computer could instantly pull up his latest information, or pinpoint
his location from the weak radio waves that his card emitted. Carrying
his ID card was like waving a large flag and telling everyone where he
was. It was a dangerous device for anyone who was on the run, in hiding,
or aiming to go underground. Nezumi was telling him to throw it away.
But--- once let go, he would never be able to get it back again. He would
be throwing his whole life in No. 6 away. A card was needed for
everything from shopping, bill payments, and communication to entering
and exiting the workplace or school, and using public transportation.
Those who couldn't prove their citizenship in the city were not allowed
to live there.

"Throw it away," Nezumi repeated, in the same low voice.

If he didn't toss it, there was no chance for them to escape. But if he
did, he would never be able to return. The pair of grey eyes were fixed
on him. They were neither clouded in panic, nor glinting in challenge.
They were calm, and unreadable. Shion let go of his ID card. A grey
mouse appeared, picked up the card in its mouth and disappeared again
into the undergrowth.

"He'll get rid of it for us. That should keep the Bureau busy for a
while trying to find our location. Not much of a distraction, but it
should buy us some time. Let's go."

A Security Bureau car turned right and disappeared into the forest. It
had picked up the radio waves emitted by the ID card. They ran in the
opposite direction.

"Hurry. Once the Bureau switches to their satellite surveillance system,
they'll be able to see everything on land. We have to get away while
they're still on the tail of that ID card."

"Where? How---?"

"Well for starters, we'll use that." A small truck was parked up against
a beech tree. It was a Park Administration truck. A cleaning robot was
loaded on the back.

"Sampo--- no, that's Ippo\footnote{one step, first step}."

"Yeah. They said they wanted to help you and wouldn't listen, so I
brought them along. They ended up being pretty useful."

The truck began to move.

"Nezumi, this area's probably under high alert now. If we keep hanging
around here without a card, they'll find us out."

"We have a card."

"Where?"

"He has it," Nezumi jerked his chin at Ippo.

"Ippo? Oh, right." Robots were also required to be registered with the
city. Robots like Ippo and Sampo, which were used by city organizations,
were registered in detail according to their various uses, and implanted
with a chip.

"His chip should get us through the inspection system."

"But Ippo's chip only shows that he's a cleaning robot. If he's found
roaming an area that has nothing to do with it, they'll get suspicious."

"We're roaming an area that has \emph{everything} to do with it."

"Huh?"

They were approaching a pair of silver gates. The moment they passed
through, they would be automatically scanned, and if the contents of the
chip deemed them unfit to pass, the gates would close, and the truck
would be forced to a halt.

The truck sped through the gates without slowing down. The hazard lamps
at the gate remained unlit. Shion let out a breath. Nezumi chuckled.

"Don't get worked up just yet. This is only the beginning."

"Sorry, I'm not used to this kind of thing."

"You'll get used to it in no time. Then you can sit back and enjoy the
ride."

"This isn't really my idea of 'enjoyable'," Shion muttered.

"Oh, really? The look on your face says you're enjoying this quite a
bit."

Shion sighed deeply again, and gazed at Nezumi's profile.

"Admiring my good looks?"

"No, I just noticed you've gotten taller."

"So have you. It's been four years. Our four years is a long time. Gotta
expect some changes. It would be unnatural not to have changed at all."

Four years was a long time. For Shion, it was long and turbulent. But
compared to the dizzying events of these past few hours, he felt like
they were the most peaceful days of his life. A weariness overcame his
body. Nezumi smirked.

"So have you noticed?"

"What?"

"I'm taller than you."

"Lies," Shion objected.

"It's the truth. What have you been eating? You're like a twig. I don't
know how you would be able to get naked in front of your lover with a
body like \emph{that}."

"That's none of your business," Shion replied irritably. "Have you even
seen me naked? Don't go making things up."

"What if I said I have?" The cloth wrapped around Nezumi's shoulders
shook as he continued to laugh. Shion had treated a wound on that same
shoulder four years before. Those shoulders were now broader and more
muscled. His once-long hair was shorter, just covering his ears, and his
jawline and neck were still slender, but not pitifully thin. He carried
no remnant of the weakness that stirred Shion's protective instinct four
years ago.

"Nezumi, have you been keeping watch on me?"

"What're you talking about?" said Nezumi innocently.

"Don't play dumb. You appeared right there as if you knew this was going
to happen to me. What's going on? Were you keeping me under
surveillance?"

"Now, don't think too highly of yourself. I don't have that kind of time
on my hands."

"Then explain why."

"You're always like that, aren't you," Nezumi said. "You can't take any
action unless you understand everything in your head. You need an
explanation and interpretation for everything."

"What do you know?" Shion replied angrily. "Don't act like you know
everything about me. I need to find out why this happened--- what's going
to happen. I can't move in this confused state."

The truck came to a halt. Shion was grabbed by the collar and shaken
violently.

"You're going to move," Nezumi hissed. "Don't ever let me hear you
whining about not being able to move again. Those guys don't see us as
human beings. They can get rid of us as easily as crushing an ant under
their feet. You remember that."

Shion caught his breath, and stared into Nezumi's face. His words
clicked into place like puzzle pieces.

\emph{Rights? You really think you have any of those?} The Security Bureau's
Investigations Officer Rashi had said those words, not moving a muscle
on his face. What he had said in meaning was that he could dispose of
Shion as easily as stepping on an ant. Wipe him off the face of the
earth.

"Get out." Nezumi opened the door. "We're walking from here."

The vacated truck made a U-turn and slowly coasted along the way that
they had come. It had switched to auto-pilot and was returning to the
Park Administration Office. On its loading deck sat Ippo, and for a
moment, it looked like its head was bowed in dejection.

They were standing inside what doubled as a waste disposal plant and
Refuse-derived Fuel (RDF) factory. Here, all the garbage gathered from
the city were sorted into those to be turned into RDF, those to be
forwarded to other recycling facilities, and those to be discarded as
waste. 80\% of No. 6's energy supply came from solar power. In Chronos,
every house was equipped with solar panels and its own thermal storage
system. In Lost Town, however, it was more common to use the cheaper
RDFs. RDFs were blocks of solid fuel, about the size of an adult thumb.
Once burned, they emitted a faint odour, which blanketed the town.

"I see. It would be no problem getting into a waste disposal plant with
a cleaning robot's chip." If it had been a nursing robot or pet robot,
they would not have been able to pass.

"Nezumi, was this all part of your plan when you brought Ippo and them
along?"

"More questions?" Nezumi's shoulders hunched slightly in exasperation,
his back to Shion, who trailed behind. Shion noticed that there was now
a grey mouse sitting on Nezumi's shoulder.

"If I had them with me, I wouldn't look suspicious driving around the
city. The inspection system wouldn't catch me as long as I was heading
west in the direction of the waste disposal plant. They were pretty
useful, I'll say. The transport truck was kind of slow, which pissed me
off. But those old guys took a detour to your house, right? That bought
me a little time. But\el "

"But?"

"But I would have wanted to get away on the Security Bureau car," Nezumi
sighed. "Well, that just shows you can't get everything you want. Watch
it, things are gonna get a little rough from here."

"Huh?"

There was an explosion. Shion turned to see a cloud of white smoke.
Nezumi furrowed his brow.

"The truck got destroyed at the gate."

"Which means Ippo's chip was read and---"

"Yeah. They must have sent out a destruction order to all the gates.
It's because we left that other robot behind. They figured us out."

\emph{---So Ippo and Sampo are both gone.}

Shion was suddenly grabbed by the wrist.

"They'll find out soon that we're in here. We're gonna make a run for
it. Hurry."

His grip was so strong that Shion's fingers began to go numb.

"Nezumi, it hurts."

"Shut up. Keep close to me."

"I get it, let go. You're gonna break my wrist."

He heard Nezumi \emph{tsk} in frustration.

"That's the problem with delicate little boys like you."

"I'm not a delicate little boy," Shion said indignantly. "I'm different
from four years ago."

"Are you? You know, you can be really irritating sometimes. You might
get killed at any time, you understand that right?"

"Yeah."

"Lies."

"I'm not lying."

Nezumi's tone grew harsh.

"Then what was that face back there, huh? Is this the time to be feeling
sorry for those robots? You don't understand anything. You're just an
oblivious little boy." Nezumi's fingers dug in harder. The grip on his
wrist tightened painfully. Shion gritted his teeth and bore it silently.
He couldn't stand to let himself whimper pitifully after all that Nezumi
had said.

Nezumi's fingers withdrew from his wrist.

"Keep up with me if you don't wanna die. Stay close, no matter what."
Nezumi broke into a run. The waste disposal plant was deserted. There
were surveillance cameras scattered throughout, but most were older
models and didn't seem to be doing their job very well. Shion guessed
that they probably didn't need them because no one would think of
sneaking into the waste disposal plant in the first place. Nevertheless,
Nezumi combed the path cautiously as he searched for a route that kept
them out of view of the cameras.

An enormous funnel-shaped disposal machine was giving off a steady hum.
Waste that could neither be recycled nor used as fuel were turned into
dry chips here to be sent to the incinerator. Wastewater dripped from
the spout of the machine into the pool below. The water flowed slowly
toward the filtration facilities outside. It was murky, like a river
after a bout of heavy rain. But in this river there were no living
things. As they descended the stairs and drew closer to the water, an
acrid smell assaulted Shion's nostrils. The floor beneath their feet was
coated with slime, and threatened to trip him up any time. Nezumi
stopped, and tossed something at Shion.

"Goggles?"

"Yup. They have infrared sensors, so you should be able to see even in
this water."

"In here?"

Nezumi pointed at the sewage. "Happen to like scuba-diving?"

"So we're diving in here, huh\el "

"That we are."

Shion took a deep breath. The odour filled his lungs. Without another
word, he put on the goggles.

"Wow, you're picking up quickly," Nezumi remarked in mild amusement. "I
thought you'd whine and stamp your feet."

"I don't wanna die," said Shion firmly. "I'm not going to be stepped on
like some ant. I'll do anything if it'll save me, and that includes
diving into wastewater too."

Nezumi turned to Shion and gave a slight smile.

"Then follow me."

"Of course."

The low hum of the machine stopped. The ceiling lights lit up at once.
The sound of footsteps could be heard above them.

"They're coming." Nezumi extended a hand to the river of sewage. A mouse
scurried down it and leapt into the water.

"He'll be our navigator. Try not to splash. Get into the water slowly."

Shion did as he was told. He sucked in a deep breath before going in.
Just before he hit the water, an image of his mother's face crossed his
mind.