% !TeX spellcheck = en_US

\chapter{Nezumi, dripping wet}

\lettrine{N}{ezumi} was in a tunnel. In the darkness, he drew a quiet breath. The air
smelled faintly of moist dirt. He inched his way forward carefully. The
tunnel was small. It was just big enough for Nezumi to squeeze through,
and it was dark. Light was nowhere to be seen, but it soothed his soul.
He liked dark and small spaces. In these spaces, no large living things
could come to capture him. Momentary relief and tranquility. There was a
dull pain from the wound on his shoulder, but it wasn't enough to
concern him. The problem, rather, was with the amount of blood he had
lost. The wound wasn't deep. It had only grazed a little bit of his
shoulder. By now, the blood should have begun clotting and closed the
open wound. But the wound was still\el He felt a warm and slippery
sensation. It was still bleeding.

------Anticoagulant. They had coated the bullet with it.

Nezumi bit his lip. He wanted something to stop his bleeding. Thrombin,
or aluminum salt. No, not even so much as that. At least, clean water to
wash his wound.

His legs buckled. Dizziness overcame him.

------Not good.

Fainting from lack of blood, maybe. If it was, that would be bad. Soon,
he wouldn't be able to move at all.

------But maybe I wouldn't mind.

He heard a voice inside him.

Maybe it wouldn't be so bad to curl up, unable to move, shrouded in damp
darkness. He would nod off to sleep, a long sleep --- and peaceful death.
It wouldn't hurt, not that much. It might feel a little cold.

No, that would be taking it too lightly. His blood pressure would
plummet, he would have trouble breathing, his limbs would be paralysed
\el of course it wouldn't be painless.

------I want to sleep.

He was tired. Cold. Hurting. Unable to move. He only had to suffer for a
little while, he told himself. Stay still, rather than struggle
fruitlessly. There may be people pursuing him, but none who would rescue
him. Then, he should just put an end to living. Curl up here, and just
go to sleep. Just give up.

His feet continued forward. His hands ran along the walls. Nezumi gave a
forced smile. His voice was telling him to give up, but his body still
doggedly carried on. How troublesome it all was.

------An hour left. No, thirty minutes.

Thirty minutes was the time limit for any free movement he had. In that
time, he had to stop his bleeding, and secure a spot to rest. The bare
requirements to keep living.

There was movement in the air. The darkness before him was gradually
becoming lighter. He took each step painstakingly. He emerged from his
dark and narrow side-tunnel to a wider area surrounded by white concrete
walls. Nezumi knew that this was a part of a sewer tunnel that had been
in use until ten and some-odd years ago, the end of the twentieth
century. Contrary to the ground above, No. 6's underground facilities
were not very well-maintained. Much of it had been left in the same
state as they were from the last century. This sewer tunnel was just
another one of those, abandoned and forgotten. Nezumi couldn't have
asked for a better environment. He closed his eyes and visualized the
map of No. 6 that he had extracted from the computer.

There was a good chance that this was the abandoned route K0210. If it
was, then it should extend close to the high-income residence area
called Chronos. Of course, it could very well also lead to a dead end.
But if he had decided to live, then moving forward was his only option.
Nezumi in his current state had neither choice nor time to deliberate.

The air shifted. It wasn't the stale dampness of before, but fresh air
carrying plenty of moisture. He remembered that it was raining hard up
above. This passage was definitely connected to the upper world.

Nezumi inhaled, and smelled the scent of rain.

\mybreak

September 7, 2013 was my twelfth birthday. On this day, a tropical low
pressure-system, or hurricane, that had developed a week ago off the
southwestern area of the North Pacific Ocean, made its way north,
gathering power, until it hit us directly in the city of No. 6.

It was the best present I had ever gotten. I was filled with excitement.
It was only past four in the evening, but already it was getting dark.
The trees in the yard bowed in the winds as leaves and small branches
were torn off. I loved the clamorous noise they made. It was the bare
opposite of this neighbourhood's usual atmosphere, which hardly involved
any loudness.

My mother preferred small trees over flowers, and through her
enthusiastic planting of almond, camellia and maple trees all over the
place, our yard had grown into a small grove. But thanks to that, the
noise today was unlike any other. Each tree made a different groaning
sound. Torn leaves and branches smacked against the window, plastered to
them, and then were whipped away again. Time and time again, gusts of
wind burst against the window.

I itched to open it. Even strong winds like these were not enough to
crack the shatter-resistant glass, and in this atmosphere-controlled
room, humidity and temperature remained stable and unchanged. That was
why I wanted to open the window. Open it, and bring in the air, the
wind, the rain, a change from the usual.

"Shion," called Mother's voice from the intercom. "I hope you're not
thinking of opening the window."

"I'm not."

"Good\el did you hear? The lower lands of the West Block are flooding.
Terrible, isn't it?"

She didn't sound like she felt terrible at all.

Outside No. 6, the land was divided into four blocks --- East, West, North
and South. Most of the East and South blocks were farmland or grazing
pastures. They provided for 60\% of all plant-made foods and 50\% of
animal food products. In the north, there was an expanse of deciduous
forest and mountains, under complete conservation by the Central
Administration Committee.

Without the Committee's permission, none could enter the area. Not that
anyone would want to wander into the wilderness, which was completely
unmaintained.

In the centre of the city there was an enormous forest park that took up
more than a sixth of the city's total area. In it, one could experience
the seasonal changes and interact with the hundreds of species of small
animals and insects that inhabited it.

A vast majority of the citizens were content with the wildlife inside
the park. I didn't like it much. I especially disliked the City Hall
building that loomed in the centre of the park. It went five stories
underground and ten stories above, and was shaped like a dome. No. 6 had
no skyscrapers, so maybe "looming" was a little exaggerated.
Nevertheless, it gave off an ominous feeling. Some people called it The
Moondrop from its round, white shape, but I thought it resembled more of
a round blister on the skin. A blister that had erupted in the centre of
the city. As if to surround it, the city hospital and Safety Bureau
building stood close by, and were connected with pathways that looked
like gas pipes. Surrounding that was a green forest. The forest park, a
place of peace and tranquility for the good citizens. All the plants and
animals that inhabited this place were minutely monitored, and all
flowers, fruits and small creatures of each area in every season were
thoroughly recorded.

Citizens could find out the best time and place to watch or gaze at
these through the city's service system. Obedient, perfected nature. But
even it would be raging on a day like this. It was, after all, a
hurricane.

A branch with green leaves still attached smacked into the window. A
gust of wind followed, and its roar resonated for some time. At least, I
thought I could hear it resonate. The soundproof glass cut me off from
any outside noise. I wanted the window out of my way. I wanted to hear,
to feel, the raging wind. Almost without thinking, I threw the window
open. The wind, the rain, came blowing in. The wind rumbled as if coming
from deep within the earth. It was a roar I hadn't heard in a long time.
I too, raised my own hands and let out a yell. It would scatter on the
storming winds, and reach no one's ears. Yet still I shouted, with no
meaning. Raindrops flew into my throat. I knew I was being childish, but
I couldn't stop. It began raining harder. How exciting it would be to
take off all my clothes and burst out into the rain. I tried to imagine
myself naked, running around in the torrential storm. I would definitely
be declared insane. But it was an irresistible temptation. I opened my
mouth wide again, and swallowed the droplets. I wanted to repress this
strange impulse. I was afraid of what lurked inside me. At times, I find
I'm overwhelmed by a tumultuous, savage surge of emotions.

\myspace

\emph{Break it.\\
	Destroy it.\\
	Destroy what?\\
	Everything.\\
	Everything?}

\myspace

There was a mechanical warning sound. It was notifying me that the
atmospheric conditions in the room were deteriorating. Eventually, the
window would close and lock automatically. Dehumidification and
temperature control would commence, and all wet things in the room,
including me, would be dried instantly. I wiped my dripping face on the
curtain and made my way to the door to turn the air control system off.

What if, at that moment, I had obeyed the warning sound? Sometimes, I
still wonder about it. If I had closed the window, and chosen to stay in
the adequately dry comfort of my room, my life would have been entirely
different. It wasn't regret, not anything like that. It was just a
peculiar thought. The one thing that changed my whole world, so
meticulously controlled up until now, happened from that one small
coincidence --- that on September 7, 2013, on a stormy day, I by chance
had opened the window. It was a very peculiar thought.

And though I don't have a particular God I believe in, there are times
when I do feel a certain conviction toward the term 'Divine Hand'.

I turned the switch off. The warning sound stopped. A sudden silence
fell over the room.

\emph{Heh.}

I heard a faint laugh behind me. Instinctively I whirled around, and
gave a small cry. There was a boy standing there, soaking wet. It took
me a while to realize that he was a boy. He had shoulder-length hair
that almost hid his small face. His neck and arms that protruded from
his short-sleeved shirt were thin. I couldn't tell whether he was a boy
or a girl, whether he was very young or older than he looked. My eyes
and conscience were too focused on his left shoulder, which was stained
red, to think about anything else.

It was the colour of blood. I had never seen anyone bleeding as
profusely as he was. Instinctively I was extending my hand out to him.
The intruder's figure vanished at my fingertips. At the same time, I
felt an impact, and I was slammed against the wall with a strong force.
I felt an icy sensation on my neck. They were fingers, five of them,
closing around my throat.

\mybreak

"Don't move," he said.

He was shorter than me. Choked from below, I strained to get a look at
his eyes. They were a dark, yet at the same time, light, grey. I'd never
seen a colour like that before. His fingers clenched. He didn't look
strong at all, yet I was completely unable to move. It wasn't something
a normal person could do.

"I see," I managed to gasp. "You're used to doing this."

\myspace

The pair of grey eyes were unblinking. Their gaze still fixed, they grew
calm like the gentle surface of the ocean, and I could read no colour of
menace, fear or murderous intent from them. They were very quiet eyes. I
could feel my own panic subsiding.

"I'll treat your wound," I said, licking my lips. "You're hurt, aren't
you? I'll treat it."

I could see myself reflected in the intruder's eyes. For a moment, I
felt like I would get sucked into them. I averted my gaze and looked
down, and repeated myself.

"I'll treat the wound. We have to stop the bleeding. Treat. You
understand what I'm saying, right?"

The grip around my neck loosened slightly.

\myspace

"Shion."

My mother's voice carried over from the intercom. "You have the window
open, don't you."

I sucked in a breath. I felt alright. It was alright, I reassured
myself. I could talk with a normal voice.

"The window? \el Oh, yeah, it's open."

"You'll catch a cold if you don't close it."

"I know."

I could hear my mother laughing on the other end.

"You're turning twelve today and you're still acting like a little boy."

"Okay, I get it \el Oh, mom?"

"What?"

"I have a report to write. Can you leave me alone for a bit?"

"A report? Hasn't your Gifted Curriculum just started?"

"Huh? Oh\el well, I have a lot of assignments to do."

"I see\el don't overwork yourself. Come downstairs at dinnertime."

\myspace

Cold fingers drew away from my throat. My body was free. I stretched my
hand out to restart the air control system. I made sure to leave the
security system off. If I didn't, it would detect the intruder as a
foreign presence, and would set off a piercing alarm. If the person was
recognized as a legitimate resident of No. 6 that wouldn't happen, but I
couldn't imagine that this soaking intruder would have a citizenship.

The window closed, and warm air began to circulate in the room. The
grey-eyed intruder half-collapsed into a kneel, and leaned against the
bed. He let out a long, deep breath. He was weakened considerably. I
took out the emergency kit. First I took his pulse, then tore his shirt
open, and started cleaning the wound.

"This\el "

I couldn't help but stare. I wasn't familiar with this type of injury.
It had carved out a shallow ridge in the flesh of his shoulder joint.

"A bullet wound?"

"Yeah." It was a casual answer. "It just missed. What's your term for
this? A graze wound?"

"I'm no specialist. I'm still a student."

"Of the Gifted Curriculum?"

"Starting next month."

"Wow. High IQ, huh?"

There was a tinge of sarcasm in his voice. I lifted my gaze from his
wound, and looked him in the eye.

"Are you making fun of me?"

"Making fun of? When I'm being treated by you? Never. So what's your
specialization?"

I told him I specialized in ecology. I had just been accepted into the
Gifted Curriculum. Ecology. It had the least to do with how to treat a
bullet wound. My first experience. It was a little exciting. Let's see,
what do I have to do first? Disinfect, dress \el oh yes, I had to stop
the bleeding.

"What are you doing?"

He stared as I took a syringe out of the disinfecting kit, and
swallowed.

"Local anaesthesia. Alright, here goes."

"Wait, wait a minute. You're gonna freeze it, and then what?"

"Sew it."

Supposedly I had said this with such a grin that I looked like I
couldn't have been enjoying myself more. It was something I found out
much later on.

"Sew it! Can you get any more primitive than that?"

"This isn't a hospital. I don't have state-of-the-art facilities, and
besides, I think a bullet wound is pretty primitive itself."

The crime rate in the city was infinitely close to zero. The city was
safe, and there was no need for the average citizen to carry a gun. If
they did, it would only be for hunting. Twice a year, rules were lifted
for hunting season. Olden-day firearms slung over their shoulders,
hobbyists would venture into the northern mountains. Mother didn't like
them. She said she didn't understand how people could kill animals for
enjoyment, and she wasn't the only one. In periodic censuses, 70\% of
citizens expressed discomfort at hunting as a form of sport. Killing
poor innocent animals---how violent, how cruel\el 

But the bleeding figure in front of me was no fox or deer. It was a
human.

"I can't believe it," I muttered to myself.

"Believe what?"

"That there are people who'll shoot at other people\el unless\el don't
tell me that someone from the hunting club shot you by mistake?"

His lip curled. He was smiling.

"Hunting club, huh. Well, I guess you can call them that. But they
didn't shoot by mistake."

"They knew they were shooting at a human? That's against the law."

"Is it? Instead of a fox, they just happened to be hunting a human. A
manhunt. I don't think it's against the law."

"What do you mean?"

"That there are hunters, and the hunted."

"I don't get what you're talking about."

"I figured you wouldn't. You don't need to understand. So are you
seriously going to give me a needle? Don't you have spray-on anaesthetic
or something?"

"I've always wanted to try giving a needle."

I disinfected the wound, and applied the anaesthetic with three
injections around the wounded area. My hands shook a little from nerves,
but somehow it went smoothly.

"It should start getting numb soon, and then---"

"You're gonna sew it."

"Yeah."

"Do you have any experience?"

"Of course not. I'm not going into medicine. But I do have basic
knowledge of vessel suturing. I saw it in a video."

"Basic knowledge, huh\el "

He drew a deep breath, and looked at me directly in the face. He had
thin, bloodless lips, hollowed cheeks, and pale parched skin. He had the
face of someone who had not lived a decent life. He really did look like
an animal prey who had been chased relentlessly, exhausted, with no
place left to run. But his eyes were different. They were emotionless,
but I could feel a fierce power emanating from them. Was it vitality? I
wondered. I had never met anyone in my life with eyes as memorable as
those. And those eyes were staring unblinkingly at me.

"You're strange."

"Why would you say that?"

"You haven't even asked for my name."

"Oh, yeah. But I haven't introduced myself either."

"Shion\footnote{shion / \jp{紫苑} / \jp{シオン}, Japanese for \emph{aster}}, right? Like the flower?"

"Yeah. My mother likes trees and wildflowers. How about you?"

"Nezumi\footnote{nezumi / \jp{鼠} / \jp{ネズミ}, Japanese for \emph{mouse} or \emph{rat}}."

"Huh?"

"My name."

"Nezumi\el that's not it."

"Not what?"

That eye colour wasn't that of any rat. It was something more elegant.
Like\el the sky just before the crack of dawn --- didn't it look like
that? I blushed, embarrassed at catching myself spouting off like some
lame poet. I purposefully raised my voice.

"Right, here goes."

Remember the basic steps of the suture, I told myself. Set down two or
three stable threads, and use them as support threads to make a
continuous suture \el this must be conducted with utmost care and
precision \el in the case of a continuous suture\el 

My fingers trembled. Nezumi watched my fingertips in silence. I was
nervous, but a little excited too. I was putting what used to be just
textbook knowledge into action. It was exhilarating.

Suture complete. I pressed a piece of clean gauze onto the wound. A bead
of sweat slid down my forehead.

"So you \emph{are} smart."

Nezumi's forehead was also damp with perspiration.

"I'm just good with my hands."

"Not just your hands. That brain of yours. You're only twelve, right?
And you're going into the Gifted Curriculum of the highest educational
institution. You're super elite."

This time, there was no tinge of sarcasm. Nor any hint of awe. I
silently put away the soiled gauze and instruments.

Ten years ago, I was ranked highest in the city's intelligence
examination for two-year-olds. The city provides anyone who ranks
highest in skill or athletic ability with the best education they could
wish for. Until the age of ten, I attended classes in an environment
outfitted with the latest facilities amongst other classmates like
myself. Under the eye of a roster of expert instructors, we were given a
solid and thorough education of the basics, after which we were each
provided with our own set of instructors to move into a field of
specialization that was suited for us. From the day that I was
recognized as the highest ranker, my future was promised to me. It was
unshakable. No small force could make it crumble. At least, that was how
it was supposed to be.

\myspace

"Looks like a comfortable bed," Nezumi murmured, still leaning against
it.

"You can use it. But change first."

I dumped a clean shirt, a towel, and a box of antibiotics into Nezumi's
lap. And then, on a whim, I decided to make cocoa. I had enough basic
cooking appliances in my room to make a warm drink or two.

"Not exactly fashionable, is it?" Nezumi sniffed as he plucked at the
plaid shirt.

"Better than a dirty shirt that's ripped and covered in blood, if you
ask me."

I passed him a steaming mug of cocoa. For the first time this evening, I
saw what looked like a flicker of emotion in his grey eyes. Pleasure.
Nezumi sipped a mouthful and murmured softly---good.

"It's good. Better than your suturing."

"It's not fair to compare like that. I think it went pretty well for my
first try."

"Are you always like that?"

"Huh?"

"Do you always leave yourself wide open? Or is it normal for all you
Petri-dish elites to have zero sense of danger?" Nezumi continued,
holding the mug in both hands.

"You guys can get along just fine without feeling any danger or fear
toward intruders, huh?"

"I do feel danger. And fear, too. I'm afraid of dangerous things and I
don't want anything to do with them. I'm also not naive enough to
believe that someone who comes in through my second-floor window is a
respectable citizen."

"Then why?"

He was right. Why? Why was I treating this intruder's wound, and even
giving him hot cocoa? I was no cold-blooded monster. But I also wasn't
teeming in compassion and goodwill enough to extend a hand to anyone who
was injured. I was no saint. I hated dealing with hassles and
disagreements. But I'd taken this intruder in. If the city authorities
found out, I would be in trouble. They might see me as someone lacking
in sound judgment. If that happened\el 

My eyes met with a pair of grey ones. I felt like I could see a hint of
laughter in them. Like they could see right through me, everything I was
thinking, and laughing at me. I clenched my stomach and glared back at
him.

"If you were some big, aggressive man, I would have set the alarm off
right then and there. But you were short, and looked like a girl, and
was about to fall over. So\el So I decided to treat you. And\el "

"And?"

\emph{And your eyes were a strange colour that I'd never seen before. And they
drew me in.}

"And\el I wanted to actually see what sewing a vessel was like."

Nezumi shrugged, and drained the rest of his cocoa. Wiping his mouth
with the back of his hand, he ran a palm across the bedsheets.

"Can I really go to sleep?"

"Sure."

"Thank you."

Those were the first words of gratitude I'd heard since he had come into
my room.

\mybreak

Mother was sitting on the couch in the living room, engrossed in the
flat-screen television mounted on the wall. She noticed me coming in,
and pointed at the screen. A female newscaster with long, straight hair
was broadcasting a warning to all residents of Chronos.

A convict had escaped from the Correctional Facility in the West Block,
and was last seen fleeing into the Chronos area. With regards to the
hurricane as well, the area was to be put in a lockdown that night.
Everyone in the area, excluding special cases, was forbidden to go
outside of their homes.

\myspace

Nezumi's face appeared on the screen. Underneath, the words "VC103221"
floated up in red letters.

"VC\el "

I lifted a spoonful of cherry cake into my mouth. Every year without
fail, Mother baked a cherry cake for my birthday. It was because Father
had brought home a cherry cake on the day I was born.

From what Mother said, my father was a hopeless case who indulged
lavishly in money-spending and women, but above all, the bottle --- he was
just a step away from being an alcoholic. He had come home one day, in
his drunkenness having bought cherry cakes --- three of them --- that were
so good she couldn't help but remember their taste every time September
7th rolled around. My parents divorced two months after the cherry cake.
So unfortunately, I have no memory of my hopeless case of a father who
was one step away from an alcoholic. But it was no inconvenience. After
being snagged as a top ranker, Mother and I received the right to live
in Chronos, along with complete insurance of our living conditions,
including this modest but well-outfitted house. There was no
inconvenience at all.

"I just remembered, the yard's security system is still turned off. No
harm in leaving it off, right?"

Mother raised herself slowly. She had gained a lot of weight recently,
and it seemed like an effort for her to move.

"It's such a pain in the neck, that thing. Even a cat jumping over the
fence sets the alarm off, and people from the Security Bureau come every
single time to check. What a hassle."

Almost as if in correlation with her gaining weight, she had started to
call things "a pain in the neck" more and more often.

"But look at him, he's still so young. A VC\el I wonder what he's done."

VC. The V Chip. It was short for Violence-Chip, and was originally a
term used in America for a semiconductor that was used to censor
television content. With this chip, you could set the television not to
display violent or disturbing scenes. If I remembered correctly, this
term was first used in the 1996 revision of the Telecommunications Act.

But in No. 6, the term VC carried a heavier meaning. Perpetrators of
murder, attempted murder, robbery, assault and other violent crime were
subject to having this chip planted inside their body. This enabled
computers to track every location, condition and even emotional
fluctuations of the convict. VC was a term we used for violent
criminals.

\emph{------But how did he take the chip out?}

If the VC was still inside his body, his location could be instantly
pinpointed with the city's tracking system. It should have been easily
possible to arrest him without any citizens noticing. To make news of
his escape public, and to enforce a lock-down would only mean that they
hadn't been able to find his location.

\emph{------Could that bullet wound have\el ? No, that can't be.}

I'd never seen a bullet wound on a human before, but I could tell it
definitely came from being shot at a distance. If he had blown the chip
off himself along with the flesh of his shoulder, he would have had a
more serious wound, with burns and all. Much more serious.

"Rather dull, isn't it? A shame, since it's your special day."

Mother sighed as she sprinkled parsley flakes into the pot of stew
sitting on the table. "Dull" was another word Mother used more often
these days.

Mother and I were very similar. We were both a little over-sensitive,
and didn't like to socialize much. The people around us were nice, so
nice there was nothing bad to say about them. My classmates, the
citizens around us, were genial, intelligent, and minded their manners.
No one raised their voice to insult anyone, or treated people with
hostility. There were no strange or devious people. Everyone kept up
such meticulously healthy lifestyles that even slightly plump figures
like my mother's were rare. In this peaceful, stable and uniform world
where everyone looked the same, my mother grew fatter, every other word
"a pain in the neck" or "dull"; and I began to find the presence of
other people oppressing.

\myspace

\emph{Break it.\\
	Destroy it.\\
	Destroy what?\\
	Everything.\\
	Everything?}

\myspace

The spoon slid out of my hand and clattered to the floor.

"What's wrong? You were miles away."

Mother peered inquisitively at me. Her round face broke into a smile.

"That's rare of you, Shion, spacing out like that. Want me to disinfect
that spoon?"

"Oh, no. It's no big deal," I smiled back at her. My heart was racing so
fast it was hard to breathe. I gulped down the mineral water in one go.
Bullet wounds, blood, VC, grey eyes. What were all these things? They
had never existed in my world until now. What business did they have, so
suddenly intruding into my life?

I had a fleeting premonition. A feeling that a great change was coming.
Just like a virus that enters a cell and mutates it or destroys it
altogether, I had a feeling that this impostor would upset the world I
lived in, and destroy it entirely.

"Shion? Really, what's gotten into you?"

Mother peered into my face again, her expression concerned.

"Sorry, mom. That report is bothering me. I'm gonna eat in my room," I
lied, and stood up.

\myspace

"Don't turn on the light."

A low voice commanded me, as soon as I entered the room. I didn't like
the dark, so I usually left the lights on. But now it was pitch-black.

"I can't see anything."

"You don't need to."

But if I couldn't see, I couldn't move. I stood helplessly, with the
stew and cherry cake in my hands.

"Something smells good."

"I brought stew and cherry cake."

I heard a whistle of appreciation in the dark.

"Want some?"

"Of course."

"You're gonna eat it in the dark?"

"Of course."

I carefully inched my foot forward. I could hear a quiet snicker.

"Can't even find your way in your own room?"

"I don't happen to be nocturnal, thanks. Can you see in the dark?"

"I'm a rat. Of course I can."

"VC 103221."

In the darkness, I could sense Nezumi freeze.

"You were all over the news. Famous."

"Hah. Don't I look so much better in real life? Hey, this cake is good."

My eyes were getting used to the darkness. I sat on the bed, and
squinted at Nezumi.

"Can you get away alright?"

"Of course."

"What did you do with the chip?"

"It's still inside me."

"Want me to take it out?"

"Surgery again? No thanks."

"But\el "

"It doesn't matter. That thing is useless now anyway."

"What do you mean?"

"The VC is just a toy. Disabling it is like a piece of cake."

"A toy, huh."

"Yup, a toy. And let me tell you something, this city itself is like a
toy, too. A cheap toy that's pretty only on the outside."

Nezumi had polished off the stew and cake. He gave a sigh of content.

"So you're confident that you're going to escape when the city's on
high-alert?"

"Of course."

"But there's a strict security check for trespassers who aren't
registered. There's an entire system in place throughout this area for
people like that."

"You think so? This city's system isn't as perfect as you think it is.
It's full of holes."

"How can you say that?"

"Because I'm not part of the system. You've all been programmed nicely
to believe that this holey fake mess is the perfect utopia. Or, no,
maybe that's what you guys want to believe."

"I don't."

"Huh?"

"I don't think this place is perfect."

The words tumbled out of my mouth. Nezumi fell silent. In front of me,
there was only an expanse of darkness. I couldn't feel his presence at
all. He was right, he was like a rat. A nocturnal rodent, hidden in the
darkness.

"You're strange," he said quietly, in a voice even lower than before.

"Really?"

"You are. That's not something for a super elite to say. Aren't you in
trouble if the authorities find out?"

"Yeah. Big trouble."

"You just took in an escaped VC and didn't report it to the Bureau.
\el If they find that out, that's even bigger trouble. They're not gonna
let you off easily."

"I know."

Nezumi suddenly grabbed my arm. His thin fingers dug into my flesh.

"Do you really? I mean, it's not my problem what happens to you, but if
you end up being wiped out because of me, I wouldn't like that. I'd feel
like I did something horrible\el "

"That's considerate of you."

"Mama always told me, 'don't cause trouble for other people," he said
lightly.

"Then are you gonna leave?"

"No. I'm tired, and there's a hurricane outside. And I've finally got a
bed. I'll sleep here."

"Make up your mind."

"Papa always told me to separate my public manners from my private
feelings."

"Sounds like a great father."

His fingers withdrew from my arm.

"I guess I was lucky that you were strange," Nezumi said softly.

"Nezumi?"

"Hm?"

"How did you get to Chronos?"

"Not telling."

"Did you break out of the Correctional Facility and get into the city?
Is that even possible?"

"Of course it's possible. But I didn't get into No. 6 on my own. Someone
let me in. Not like I wanted to come here, though."

"Let you in?"

"Yup. I was being escorted, you might say."

"Escorted? By the police? To where?"

The Correctional Facility was located in the West Block, a high-security
zone. Anyone who wanted to enter No. 6 from there had to apply for
permission from the bureau. Those who had special entry permits were
free to go in and out, but new applicants I heard had to wait at least a
month for their form to even be accepted --- and usually only less than
ten percent are admitted. The number of days allowed inside the city
were also severely restricted. Naturally, people began to accumulate in
the West Block. More people waiting for their permits to be processed
meant more accommodation and dining establishments lined the streets to
serve them. Still more people poured in to work or make business there.
I've never been to the West Block myself, but I've heard that it's a
haphazard but lively place. The crime rate there is high. The majority
of VCs that fill the cells in the Correctional Facility are residents of
the West Block. Sentences ranging from one year to life are given based
on age, criminal history, and the degree of violence of the crime. There
is no death penalty. The West Block served as a sort of fortress that
contained all people and things of criminal nature, and prevented it
from entering the city. So for a VC to be escorted from there to within
city walls --- where were they headed? And for what reason?

Nezumi crawled into bed.

"Probably the Moondrop."

"City Hall!" I exclaimed. "The centre of the city? Why?"

"Not telling. You probably shouldn't know, anyway."

"Why not?"

"I'm tired. Let me go to sleep."

"Is it something you can't tell me?"

"Can you guarantee that you can completely forget everything once you've
heard it? Pretend you didn't hear? Outright lie that you don't know
anything? You might be smart, but you're not an adult. You can't lie as
well as that."

"I guess, but\el "

"So don't ask me in the first place. In return, I won't tell anyone
either."

"Huh? About what?"

"About how you were yelling out the window."

He had seen me. I could feel my face burning with embarrassment.

"It totally caught me off-guard. I snuck into your yard and was
wondering what to do next, and suddenly the window opened and you stuck
your face out."

"Hey, wait a minute---"

"I was watching for what you'd do next, and then this time you started
screaming. I was caught off-guard again. I don't think I've ever seen
anyone screaming with a face like---"

"Shut up!"

I lunged at Nezumi, but all I felt was the pillow as I fell on top of
it. In a flash, Nezumi was up. He slid a hand under my arm, and with a
quick twist, I was effortlessly flipped over onto my back. Nezumi
climbed over me and pinned both my arms down with one hand. His legs
straddled my hips and pressed them down hard. For an instant, I felt a
tingle of numbness run through my legs all the way down to my toes. It
was impressive. In the space of a split second, I had been trapped,
immobilized, and pinned to my own bed. With his free hand, Nezumi spun
the soup spoon around. He pressed the handle against my throat, and
lightly slid it across. He crouched so that his lips were at my ear.

"If this was a knife," he whispered, "you would be dead."

A muscle in my throat twitched. Amazing.

"That's amazing. Is there a trick to doing that?"

"Huh?"

"How can you immobilize someone so easily? Are there special nerve
points you press down or something?"

The force pinning me down relaxed. Nezumi sank down on top of me,
trembling --- he was laughing.

"I can't believe this. You're hilarious. What a natural," he gasped.

I circled my arms around Nezumi and stuck my hands up the back of his
shirt. It was hot. His burning skin was damp with sweat.

"I knew it\el you're catching a fever. You should take those
antibiotics."

"I'm fine\el I just wanna sleep."

"If you don't bring your fever down it'll drain you even more. You're
burning up."

"You're pretty warm too."

Nezumi gave a deep sigh, and murmured absent-mindedly.

"Living people are warm."

He became still, and not long after, I could hear quiet, measured
breathing coming from him. With his feverish body still in my arms,
before I knew it, I too was drifting off to sleep.

When I awoke the next morning, Nezumi was gone. The plaid shirt, towel,
and emergency kit were gone with him.