% !TeX spellcheck = en_US

\chapter{A quiet beginning}

\begin{boxed}{Index Case (First Discovered Example)}
	Male, aged 31 years. Employee at a biotechnology firm. Engineer. Already
	dead upon discovery. Confirmed address\el 
\end{boxed}

\lettrine{T}{he man} sank into a bench in the Forest park, and sighed. He wondered
how many times he had already sighed that morning. He sighed, and looked
at the head of lettuce in his hand. It made him sigh again. Crisp, green
leaves firmly wrapped the head of lettuce --- as far as quality went, it
was first-class. He tore off a leaf, and brought it to his mouth. It had
a delicate taste, and the texture was excellent. First-class, indeed.
Then why wasn't it selling?

The lettuce was this man's piece of work. He had long worked in the
development of biotechnology to produce fresh produce, namely leafy
vegetables. He believed that these safe, affordable and delicious
bio-vegetables were the solution to the rising food crisis, and would
soon become a mainstay in food distribution. He had the confidence it
would. But market sales were not doing as well as he expected, and the
man was losing hope. Buyers seemed to prefer produce trucked in from the
fields of the Southeastern Blocks, rather than his bio-vegetables. The
trend was especially strong for leafy vegetables, like cabbage and
lettuce. If this continued, his boss had told him, he would have to
start thinking about discontinuing production.

The base of his neck itched. It had been itching for a while now. The
man was prone to getting rashes when he was tired. By tonight, a red
rash would probably have spread to his whole body. Too many unpleasant
things were happening today. He sighed again. The lettuce in his hand
felt heavy.

A beeping sound rang from his breast pocket. The mobile telephone screen
on his ID card lit up, and young woman's face appeared.

"Greetings from the Municipal Information System. This is to notify you
of the results of the Children's Examination you have registered for. To
confirm your account, please enter your Citizenship Number\el " Before
the woman was even finished speaking, the man began to key in his
number. Today was the day of his two-year-old daughter's Examinations.
She was a bright and adorable little girl. He had never dared to say it
out loud, but he secretly harboured an expectation that she might be
acknowledged as a top ranker.

"Thank you. We have confirmed your fingerprint and registration number.
Your information is as follows\el " His daughter's name was displayed,
followed by a set of detailed numbers. Weight, height, bust measurement,
condition of health, condition of nutrition, development stage, ranking
of various skills\el all grades ranged in the average A to C. She was
neither overly behind, nor outstandingly brilliant. That was it. The man
gazed at the screen for a moment, and then put his card back into his
pocket. He thought of his daughter's smile.

Oh well.

The man spoke to himself, and grinned at the head of lettuce in his
hand. Gifted or not, his daughter was still his daughter. He cherished
and adored her. And that was good enough.

Suddenly, an idea sparked in his head. Had he, perhaps, been too trapped
in the idea of the best, most perfect? It was true --- there was nothing
to complain about this lettuce. But maybe its perfection was also the
bane of it. If these identical, perfect heads of lettuce were piled up
row after row, consumers might not feel as inclined to buy it. What if
its perfection was actually scaring consumers away?

A cleaning robot was approaching. On its metallic body sat a round head,
and two arms extended to pick up trash, and throw it inside the dust box
located in the middle of its body. Yes. This lettuce was like that
robot. It was clean and orderly, but too artificial. The vegetables that
the consumers wanted were more unique, more natural\el The lettuce
rolled out of his hand. The man quickly bent down to pick it up, and
furrowed his brow.

\emph{Huh?}

His fingers stiffened. His vision blurred. It was hard to breathe. The
robot picked the lettuce up, and paused. A young male voice prompted
him.

"May I dispose of this as trash?"

The man opened his mouth to speak, and was overcome with a fit of
coughing. Along with it, something white spilled out of his mouth.
Teeth. His teeth were falling out.

"Are you sure? I will dispose of it now." The lettuce was thrown into
the dust box, and the robot moved away.

\emph{------Wait, help me\el }

The man reached out, and gave a cry of horror. The whole length of his
extended arm was riddled with spots. His body grew heavy. The man
staggered, and collapsed on the ground between the bench and the hedges.

\myspace

"Shion, take a look at this."

It was past six when Shion was called over by his co-worker, Yamase. The
two were the only people at the Park Administration Office. Together
they operated and maintained the three cleaning robots that patrolled
the park. Labour robots such as these were still at the prototype stage,
and even simple cleaning robots were prone to breaking down. Operating
them was a hassle too, because they weren't good at distinguishing
trash. After recording an object as trash in the computer's memory the
first time around, it was supposed to recognize it automatically every
time afterwards. But the robots sent back "indistinguishable object"
errors all the time. There was one half an hour ago, in fact. The image
sent back to him looked like a head of lettuce, and Shion had hesitated
for a moment about what to do. He had encountered other things before
that he wondered if he should call trash, like a baby chick that had
fallen out of a tree, or a hat with a rather extravagant feathered
decoration. Lettuce, though, was a first.

"Something the matter?" He stood behind Yamase, who was sitting at the
operation panel.

"Hmm\el Sampo's acting strange."

Yamase liked to call the three robots by their nicknames. Sampo\footnote{three steps, or 'a stroll'} was
Robot No. 3. Today, it was working in a corner in the deeper recesses of
the park. Sampo was also the same one that picked up the head of
lettuce. The screen in front of them displayed a flashing red error
notifying them of an indistinguishable object.

"What's the image like?"

"Yeah, about that. It's not very clear, but\el it's strange."

"Strange?"

Yamase was twenty --- four years older than Shion --- and quiet by nature,
seldom ruffled by anything. The calm nature of his co-worker was one of
the two reasons why Shion liked this workplace. The other reason was
that because his job dealt mostly with machines, he didn't have to talk
to people.

"Here, you take a look," Yamase said, switching the screen over to the
camera.

"Can you focus in a little more?"

"Sure," came the answer, and Yamase's hands moved swiftly over the
control panel. The image became clearer.

"What\el " Shion leaned in closer, and his breath caught in his
throat. Feet? A pair of trousered legs were protruding from behind the
bench. He could see a pair of brownish shoes outfitting them.

"You think he's sleeping\el ?" Yamase's voice trembled.

"Any signs of life?"

"Huh?"

"Can you raise Sampo's sensors to the max level?" Sampo was outfitted
with several receptors that could sense heat, sound, and texture.
Yamase's voice shook more violently.

"Oxygen, heat emission\el zero. No signs of life."

"I'll go check," Shion said abruptly.

"I'm coming too."

They leapt on their bicycles, and pedalled as hard as they could.
Bicycles had become explosively popular in the last few years, and
statistics showed that the average citizen owned 1.3 bicycles. Jogging
shoes were also selling well. Rather than convenient and effortless
modes of transportation, it seemed like more people were choosing to
walk, pedal, and otherwise use their own bodies. Popular or not, for a
student like Shion, something this affordable that manoeuvred easily and
didn't cost anything to fuel was more of a necessity.

There were speed limits even for bicycles within the park. Shion
pedalled full-throttle through a path he would usually only stroll down.
Most vehicles nowadays were equipped with a restraint mechanism that
automatically kicked in when the vehicle went over a certain speed.
Bicycles were no exception, and the mechanism was usually built into the
brake lever. But Shion's bicycle was an older model, and wasn't equipped
with speed restraints. He would have to pay a fine if the Transportation
Bureau found out, but right now, he was glad he could go as fast as he
could.

He reached a quiet area secluded by trees. Beneath a canopy of swishing
leaves, Sampo was standing still. His head joint, slightly tilted to the
side, made him look either pensive or baffled.

"Sampo." In response to Shion's voice, its LED eyes lit up green. Shion
peered behind the bench, and froze.

"Shion, what's going on?" Yamase arrived slightly later, and made a
muffled noise in his throat.

The man lay behind the bench, as if to hide behind it. His mouth was
open and his eyes wide and staring. His expression resembled surprise,
rather than fear or pain. He looked like he had seen something shocking
moments before he died. His hair was snowy white, and on his cheeks
there were spots that looked like senile plaque. His wrinkles were
pronounced. He was quite aged.

\emph{------That's a pretty flashy shirt for his age, though.}

Shion remarked inwardly at the light pink shirt the man was wearing.

"Yamase-san, can you contact the Security Bureau?"

"Huh? Oh\el oh yeah, of course. Sure. Give me a minute\el Hello? Um,
this is the Park Administration Office\el " Half-listening to Yamase's
shaky voice as he explained the situation, Shion reached out cautiously
to touch the man. Rigor mortis had spread to his whole body.

"That's impossible," Shion muttered almost automatically in disbelief.

\emph{------It was too soon.}

Rigor mortis usually began taking effect at least an hour after
death---two or three hours, in most cases. It started at the jaw and
spread gradually downwards to end at the legs. Judging by that, this man
would have been dead at least several hours. But 30 minutes ago, this
body wasn't here. If it was, Sampo would have noticed it. He knew that
there had been a living person sitting on the bench. After confirming
the lettuce, Sampo's sensors had registered a living human presence. Of
course, he had no evidence to prove that these two were the same person.
No, there was no way it could be. There was no way a person who was
alive 30 minutes ago could go through complete rigor mortis in this
short time. Then---was someone else sitting on this bench, oblivious to
the dead man?

\emph{---Impossible.}

Shion let go of the man's arm, which felt stiffer and colder than
Sampo's mechanical one. It was impossible. Even if the man had lain dead
without being noticed, Sampo would have picked him up. Indeed, Sampo had
reacted to his presence, and sent an "indistinguishable object" error
just minutes ago. That meant that 30 minutes ago, there was no dead body
here.

Shion thought he saw the body move. Of course, it was just his
imagination. But --- Shion stifled a cry of horror. The jaw of the man,
stiff only minutes ago, was starting to loosen. He thought he could even
smell a faint odour of rot. The man was face-down, and behind his ears
Shion could see a blackish-green stain begin to spread. That was
definitely not there before. Certain not visibly to the naked eye. Shion
leaned in closer.

"They're coming," Yamase sighed in relief. A Security Bureau car was
approaching soundlessly.

\myspace

"So in the space of ten-some-odd minutes, you saw complete rigor
mortis---and it started rotting right afterwards? That's impossible," Safu
concluded simply, after she had swallowed her mouthful of chocolate
doughnut. The fast-food joint where they sat, located near the older
parts of town was bustling with people of every shade and colour.

"And if you're saying you smelled rot, then that means decomposition by
bacteria had already started, right? That can't be. Even in the middle
of the summer, it would take at least 30 hours--- right? --- for rigor
mortis to dissipate completely."

"Under a fixed set of conditions, it would take 36 hours in the
summertime, 3--7 days in the winter, and 60 hours in the weather we're
having now. That's what the textbooks say," Shion replied, dropping his
gaze from Safu's face and taking a sip from his cup of tea. He felt
melancholic. And tired.

"Did the Security Bureau give you a hard time?" Safu peered into his
face. Her short, cropped hair framed her delicate face and large eyes,
which gave her a mysterious, androgynous sort of allure. Safu was also
among the top-ranking in intelligence during her Examinations for
Two-Year-Olds. She was one of the several classmates he studied with at
the same school until the age of ten. And presently, at age sixteen, she
was the only one whom Shion shared a close relationship with. She
specialized in physiology, and was set to go on exchange soon to another
city.

"It was an unnatural death after all, they must've been suspicious. They
probably interrogated the heck out of you because of that, didn't they?"

Safu as Shion knew her in the classroom was a small, quiet girl. She was
probably still the same in the lab. But when she was alone with Shion,
Safu smiled often, ate well, and relaxed her formal tone. Shion drained
his tea, and slowly shook his head.

"Nah, it wasn't as bad as I thought." Truth be told, the Security
Bureau's interrogation was surprisingly short. All they did was seize
the data that Sampo had recorded of the body, and demand an explanation
of the situation from each of the two. The official spoke sharply when
he found out that Shion's registered address was located in the old-town
district, close to the West Block, but Shion was used to that kind of
treatment and thought nothing of it.

"Then why do you look so down about it? You're the picture of the
troubled young man right now."

"It\el just doesn't seem right."

"The rigor mortis and its dissipation time?"

"Right. You said so yourself, Safu. It's not possible. You're right.
There was no condition present that could have accelerated the rigor
mortis and dissipation to that extent."

"You mean no condition in terms of temperature or humidity, or some
other external influence, right? You won't know until you perform an
autopsy if there might be an internal cause that accelerated it."

"Internal cause, huh\el like what?"

"For example, if that person was severely debilitated, he wouldn't have
stiffened up as much, and it wouldn't have lasted as long. In people
with phosphorus poisoning or in infants, they say it's almost
nonexistent\el "

"He was definitely not an infant, I can tell you that."

Safu sniffed indignantly and glared at Shion.

"It was just an example. You're as sarcastic as ever, aren't you? That
hasn't changed at all. But I guess there's not much we can make of it if
we don't have any data."

"Yeah\el " Shion nodded vaguely, and unconsciously bit his lower lip.
Data, textbooks, manuals\el there were times when they became completely
useless. What he once believed to be so certain and absolute would be
overturned ever so easily, and crumble before him. He experienced that
four years ago.

\mybreak

"Shion." Safu put her elbows on the table, and folded her hands over
each other. She placed her chin on them, and gazed at Shion.

"I want to ask you something."

"What?"

"Four years ago --- why didn't you enroll into the Gifted Curriculum?" It
was as if her question saw right through him. Shion broke off a piece of
the blandly sweet apple pie with his hands. The filling oozed out onto
the plate.

\myspace

"Why're you asking now?"

"Because I want to know. Even from an objective point of view, you were
a stellar student. You absorbed information well and knew how to apply
it. All the teachers had high expectations for you."

"You're giving me too much credit."

"It's the truth. The numbers prove it. Do you want me to show you your
Skill Test results again from four years ago?"

"Safu." He had a bitter taste in his mouth. It felt like it was welling
up from the very core of his body.

"What's the point of asking me this now? Four years ago, they decided I
wasn't qualified for the Gifted Curriculum, so I lost all special
privileges. I didn't \emph{choose} to not enroll, I \emph{couldn't}. Now I work for
Park Administration to pay for my tuition, and I'm taking trades courses
from the Labour Bureau. But my attendance hasn't been good so I'm not
even sure if I can graduate. That's reality. That's the truth you're
talking about, Safu."

"And why did you lose your privilege?"

"I don't want to talk about it."

"But I'd love for you to tell me."

Shion finished licking the pie crust from his fingers, and closed his
mouth firmly. He didn't want to talk about it. Or, rather, he couldn't
think of any explanation that would make Safu understand.

The reason was simple. He had taken a VC under his wing for the night,
and let him escape. The Security Bureau had found that out. They had
thought it suspicious that his mother Karan had left the security alarm
off, and Shion had left the foreign-object detection system off in his
own room. The security systems of each house were connected to the
Central Administration Bureau's computer system, and could be easily
tracked.

Not one hour had passed after Nezumi had disappeared when officials from
the Security Bureau were knocking on his door. It was the start of their
long and persistent interrogation.

\emph{You knew that he was a VC, then?}

\emph{Yes.}

\emph{Why didn't you call the police immediately?}

\emph{Well\el }

\emph{Answer my question. You don't need to rush. Just give us a clear and
accurate answer.}

\emph{It was because he looked about the same age as me, and he was seriously
injured. So I felt sorry for him\el }

\emph{So you sympathized with this VC, didn't contact the police, but instead
treated his wounds and helped him escape.}

\emph{It ended up as so, yes.}

The Security Bureau's Investigations and Interrogations official was
named Rashi. He spoke gently throughout the whole meeting, never once
raising his voice or his fist in violence. When their gruelling two-day
investigation was over and Shion was released, he even gave him a
friendly clap on the shoulder and said, "It's been hard, I know.
Thanks." But Rashi's eyes never smiled once, and Shion had noticed. Even
now, four years later, those unsmiling eyes came into his dreams, their
gaze boring into him. He would awake in the morning, shaken, and soaked
with sweat.

He concealed a criminal and aided his escape. Shion wasn't sentenced for
this crime, but he was deemed severely deficient in appropriate judgment
skill and ability to take action, and as a result all his special
privileges were removed.

When the hurricane passed, Shion and Karan were cast out onto the
streets, under a blindingly blue sky. They had no place to live, nor any
means to make a living. Shion's Gifted Curriculum in ecology had become
something more far away and unreachable than the clouds that floated in
the sky above them.

A certainty, a definiteness he had in his hands only yesterday, only
moments before, had vanished. They had scattered on the winds, more
frail than the leaves he had watched whipped around in the storm. It was
a sense of loss he was feeling for the first time in his life.

No. 6 had no welfare system. There was only a hierarchical insurance
system based on the level of contribution that a select few of the
citizens had to offer to the city. Shion and Karan, far from
contributing to the city, were treated as people who had failed to serve
their responsibility as citizens. They were at the lowest possible rank.
That meant that, apart from being allowed to remain in the city, they
were excluded from any aid or insurance.

Petri-dish elite. Nezumi had used that term that night, and it was true.
He realized the weight of it after he had been thrown out of his
enclosed and sheltered container. No. 6 was none other than a caste
society. The vertical dynamic of the population was neatly ordered into
a pyramid structure. Once you tumbled off the top tiers, it wasn't easy
to crawl back up.

\myspace

"Look at you, so serious." Safu laughed. "I get it. If it's that hard to
explain, then I won't ask."

"Sorry." Shion held up a hand and ducked his head in apology. He was
relieved that she didn't question him further. The events were easy
enough to explain. He did want to tell Safu, for her to know about the
dramatic events that had turned his life upside-down. But what Shion
couldn't grasp, couldn't seem to find the words to explain, were his own
feelings. He even surprised himself with what little regret he felt. He
did feel shock at the fragility of his position, and he did more than
once find himself curled up, unable to grapple with his sense of loss.
But now, after four years of living through it all, he pondered. What
would he do if he could turn back time to that day, on his twelfth
birthday? Would he have called the police? Would he have set his
security alarm off? The answer was always "no".

Even if he had the chance to return to that night, he would have done
the same thing. He would have taken in the wind and rain, and the
intruder that came with it. He felt it with certainty, and his certainty
put him at unease. It wasn't like he found his life now more satisfying
than before. He still had deep attachments to ecology, his
state-of-the-art learning environment, his comfortable life --- and
shamefully enough, even the accolades, the words of praise and
encouragement, and gazes of admiration that he was the centre of. But
even so, he would have done the same thing. If accepting Nezumi meant
his own destruction, then to destruction he would have trodden again and
again. He had no regrets about what he did. But he couldn't explain why.
Since that night, other hurricanes came and went. Listening to the
excited murmurings of the leaves in the wind, Shion felt not regret, but
a sense of longing. It was a yearning to see him again.

Shion didn't have the confidence that he could explain it to Safu well
enough. He had no other option but to remain silent.

"Shall we go then, Shion?" Safu stood up. The restaurant had become even
more crowded, and now they could barely hear each other's voice.

"I'll walk you to the station," Shion offered.

"Of course. You would have to be really tactless to let a girl go home
by herself, wouldn't you?"

"Oh come on," retorted Shion, "we both know how strong you are, even
though you might look small and skinny. And you're speedy. I always
thought you were more fit for martial arts than physiology, actually."

"You know what, you're right. I've been told off once about how I
emotional I can get all of a sudden, when I'm usually so quiet. Maybe
I'm not meant for lab work after all."

They walked side-by-side down the road to the station. Excluding a few
restaurants, late-night business was banned in the city. In a matter of
hours, the throngs of people walking up and down the streets now would
disappear. Shion gave Safu's back a light push. Her last words had
sounded somewhat dejected to his ears.

"Is that supposed to be the voice of someone who's passed the exams and
is about to go on exchange?"

Safu raised her face, and grinned.

"Jealous, aren't you?"

"Yeah."

"That's awfully truthful of you."

"Be true to yourself, be kind to others. It's been my motto these days."

"Liar."

"Huh?"

"You're not jealous at all."

Shion stopped. Safu was staring at him challengingly. Just as he was
about to call her name, he was suddenly grabbed by the shoulder from
behind.

"Excuse me." Shion turned around. A man was standing there, smiling. He
was about a head shorter than Shion, and was wearing a Security Bureau
uniform. It was navy blue from top to bottom and made of a special
material called superfibre, which had impressive qualities for its
unremarkable appearance. With durability that was tenfold that of steel,
it served the purpose of a bullet-proof vest well enough; at the same
time, it let air pass through easily so the garment could breathe. There
was an increasing number of these uniformed Law Enforcement officers
from the Security Bureau the closer they neared to the West Block. Shion
calmly brushed the man's hand off his shoulder and spoke.

"Can I help you?"

"Ah, well\el I just want to ask you two a couple questions\el how old
are you?"

"Sixteen."

"The both of you?"

"Yes."

"You do know that those under eighteen are prohibited from being
outdoors after nine?"

"Yes, but it's still before eight."

"Shion," Safu whispered sharply. She was telling him not to argue. But
the Security Bureau uniform standing before him brought back to memory
the eyes of that interrogation officer who called himself Rashi. Instead
of feeling intimidated, Shion was compelled to retaliate.

"Your ID cards, the two of you, please." Perhaps he had taken notice of
Shion's rebellious attitude. The man wiped the smile clean off his face
and demanded their identification cards expressionlessly. Safu passed
her silver card to him. Shion silently did the same.

"Your Citizenship Numbers, in order."

"SSC-000124GJ."

"Qw-55142."

The man pulled the cards out of his portable card-reader, and turned to
give Safu a slight bow.

"A Gifted Curriculum student like yourself shouldn't be roaming these
areas at such a late hour. I advise you to go home."

"I was on my way\el I was walking to the station."

"Let me walk you there."

"No thank you. He's going to." Safu clung to Shion's arm.

"I'll take her," said Shion shortly. "That's where we were headed in the
first place. Let's go, Safu."

Snatching the cards from the officer's grasp, Shion grabbed Safu's hand,
and strode swiftly away. When he turned around some moments later, the
man had already disappeared into the bustling crowd.

"That scared me." Safu clutched her chest. "I've never been scolded by
the Security Bureau."

"It happens all the time," replied Shion. "If you didn't have your
Gifted Curriculum ID, he would have grilled us even more."

"Really?"

"Really," said Shion grimly. "Like the train that you're about to get
on. With that ID card, you can bypass the General car and ride in
Special Class. That's the kind of city we live in. Everyone's sorted out
into categories based on skill, wealth, and all these other factors."

"Don't talk about it like that," Safu protested. "You don't 'sort'
people like you 'sort' garbage and merchandise. People are people.
They're humans."

"Safu, in this city it doesn't matter whether we're people or not. It
matters how useful you are to the city. That's it."

"Shion\el "

"Back there you called me a liar. I'm not. Of course I'm jealous. You've
got all your privileges, and you're allowed to study and experiment to
your heart's content. I'm envious, Safu. I resent you, even. You have
everything that I don't have."

Shion paused, and let out a long breath. He had gone too far. It was
shameful. Low. Embarrassing. Pathetic. He clicked his tongue at himself
in frustration.

Safu sighed as well.

"You're still a liar."

"Huh?"

"Did you not hear me? You're. Still. A. Liar. I can add 'big' on top of
that, if you like. You're only pretending to be envious of me. Or do you
not even realize that you're lying? What a dense boy I've got on my
hands."

"Safu, what---" Shion began in exasperation.

"If you were really envious and resentful, you wouldn't be able to stand
going out to eat with me. But you, you're laughing, eating, making
conversation, cracking jokes like it's nothing."

"Hey, I have some pride too. Obviously I'm not going to be openly
jealous."

"Shion," said Safu firmly. "My specialization is in cognitive functions,
brain activity and their relationship with hormones."

"I know."

"Good, because if you didn't, I would've been mad. I haven't told you
this over and over for nothing. Anyway," she continued briskly, "say you
are hiding your resentment and pretending to be enjoying your time with
me. It would be stressful, right?"

"I guess so\el " Shion replied dubiously.

"It \emph{would} be stressful. And when you feel stress, your adrenal glands
release steroid hormones called corticosteroids that influence your
brain. And what it does to brain activity is---"

"Okay, Safu, I get it." Shion interrupted. "That's enough. Save your
lecture for next time and I'll listen carefully---"

"Listen to me. You're not feeling any stress. You're not resentful of me
at all. Shion, what is it that you want to do?"

"Huh?"

"If you do want to continue your studies, you can be resentful of me.
But you're not. You said I have everything you don't have. Then what is
it that you have? You can't say you have nothing," she added hastily.
"People who have nothing --- no --- people who \emph{think} they've got nothing
left, can't smile like you do. Or talk like you do. For your emotions
not to have any influence on your actions, to have that level of perfect
control, it takes special training. You're not getting any special
training. I don't think you're an overly emotional person, but I also
don't think you have the ability to control 100\% of your emotions
either. The only reason you can have a regular conversation with me and
laugh around me is because you have a certain level of emotional
security."

"Safu, what you just said is all armchair theory. Humans have complex
emotions. They're not like lab rats. I don't think you can explain how
emotions influence people's actions that easily. It's arrogant to
believe that science can explain everything about human nature."

Safu shrugged. They were approaching the station.

"I didn't know you wanted to become a writer."

"Safu," Shion said wearily.

"Then I'll say this in a literary context. Emotional security\el so I'm
talking about hope, or dreams. You have those. That's why you don't feel
the need to resent me. Shion, what is it that you hope for?"

\mybreak

Hope. He repeated the word silently. It was a word he hadn't used for
years. It was neither sweet nor bitter, but it slowly warmed him from
deep inside of his body.

Hope. What do I hope for?

\myspace

His promised future had collapsed. What was left to him now were his
mother, the meager wages from his job, and his own sixteen-year-old
body. What hope resided in those? He wasn't sure. But he was sure that
he hadn't completely lost hope either.

They entered the station. The old-town district where Shion lived was
located adjacent to the West Block and the city border, and functioned
as a sort of buffer zone between the city centre and the West Block. It
was called Lost Town. A far cry from the tranquility of the city centre,
it was a squalid place, dense with people. The station they were in was
also very crowded. The faint smell of deep-fried food and alcohol wafted
in the air.

"I'm fine from here." Safu stopped. There was a black winged insect on
her shoulder. Brushing it away, Shion asked a nonchalant question.

"Be careful. Oh, when are you off for your exchange again?"

"In two days."

"Two days!" Shion exclaimed. "Why didn't you tell me sooner?"

"Because I didn't want to. Would you have thrown me a farewell party if
I did?"

Safu jutted her chin out defiantly.

"Shion, I want to ask something from you."

"Sure, if I can manage to get it to you in time\el "

"Your sperm."

Safu looked Shion in the eyes as she said those words. She didn't blink
once. Shion gaped at her open-mouthed.

"Did you hear me? I want your sperm."

"Uh--- what? Safu\el um---"

"Out of all the people I know, you would probably be the most superior
sperm donor. Your sperm and my ovum. Don't you think it would produce
the most perfect child? I want it, Shion. I want your sperm."

"Artificial insemination needs permission from the city," Shion answered
cautiously.

"Getting permission would be easy. The city encourages artificial
insemination between people who possess excellent DNA and superior
skills."

Shion swallowed, and turned away. The winged insect crossed his line of
vision, buzzing incessantly. Irritation welled up inside him.

"Safu, I don't know if I told you this, but I've never known my father.
I don't know his personality, his stature, or if he had any illnesses."

"I know. But parents don't matter. Ninety-nine percent of the human
genome has been decoded already. I can find out anything I need to know
about your genetic information."

"And then\el if you do get the information, and there's something in
there that you don't want, what are you going to do?"

"Well\el "

"Safu, what are you trying to get at? Do you think a human being is
entirely what his DNA base sequence tells us he is? Sure, you can look
up my DNA, analyze my genes, but what's that going to tell you about me?
You talk about having kids like it's easy, but---"

"I know a lot more about you than you think!"

Safu's voice cut him off shrilly. People turned their heads as they
passed.

"We've been together since we were two. I know what kind of person you
are, what you like to do\el I know. I know, and I'm still telling you
this--- you're the one who doesn't know anything."

"What?"

Safu mumbled something, but he couldn't catch it. He bent toward her
slightly so he could hear better.

"I want to have sex with you."

Her words rang clear in Shion's ears.

"Safu\el "

"I don't want your sperm. I don't want artificial insemination. I don't
care about having kids or not. I want to have sex with you. That's it."

"Wait, uh--- wait a minute\el Safu, I---"

"Right now."

Shion inhaled. The greasy scent of fried food wafted into his nostrils.
The clock chimed eight o'clock.

"Not now."

"Why not? Because you're not interested in me? Or not interested in
sex?"

"I'm interested in both. But\el I don't want to do it, not now, with
you."

"So it's because it's with me?"

"No--- my body would probably respond no problem. Even now I'm\el but--- but
that's why I don't want to. I don't want to sleep with you on a spur of
the moment."

"You know that's like saying you've never seen me in that way before."

"Yeah. I always thought of you as a friend."

"I can't believe it."Safu sighed in exasperation. "Why are you such a
kid? Whatever. I'm going home."

"Safu, in two years---"

"Hm?"

"Your exchange is for two years, right? When you come back, I'll ask
this time."

"If I want to have sex?"

"Yeah."

"You're a bonafide idiot if I ever saw one. I don't know how you could
have come this far being that laid-back."

"Stay safe. Don't work too hard."

"Oh, you can count on me working hard. I'll work so hard, it'll keep all
the boys away."

With a casual wave of her hand in farewell, Safu turned around, and gave
a small shriek. A small grey animal darted past Safu's feet and scurried
up Shion's body.

"A mouse!"

A small mouse about the size of Shion's pinky sat on his shoulder,
twitching its nose.

"I'm surprised to see mice in this city. But it \emph{is} kind of cute," Safu
mused.

"Pretty friendly, too."

The mouse brought its face close to Shion's ear.

"Still a natural," it whispered.

He felt an electric shock run through him. He grabbed at the mouse, but
it slipped through his fingers, bounded off his shoulder and shot toward
the station exit. True, this was an older district---but Lost Town was
still within city limits, and mice were rare. The Health and Hygiene
Bureau saw to the complete removal of all pests, animal or insect.
People weren't used to seeing the mouse that sped past their feet.
Shrieks of surprise and bursts of anxious buzzing rose from the crowd.

And at the very end of it, Shion saw a pair of grey eyes. It was for a
fleeting instant. A jolt pierced through his body again.

"Nezumi!"

"Shion, what's wrong?"

"Safu, you can make it home by yourself, right?"

"What? Of course. I was just about to, wasn't I? What's wrong? Why are
you so agitated?"

"Sorry---"

After they parted here, he wouldn't see Safu again for two years. He
knew he had to give her a proper sending-off. At the very least, watch
her retreating back until it disappeared into the jostling crowd.
Whether they were going to have sex or not, didn't change the fact that
Safu was important to him. He knew well that this was nearly not the
proper farewell that she deserved. He knew. But what he thought he knew
so well was swept away instantly. His body moved on its own, defying his
rational thought. Yes, he had experienced this four years ago--- even
though he knew reason always had the right answer.

Turn the security system on. Notify the Security Bureau. Remove the
foreign presence. He had defied all of it. It was the same now. He was
letting his emotions control his actions.

It had begun raining outside. Raindrops pelted his cheek. In the crowd
of people briskly walking to and fro, not a familiar face was to be
seen.

"Shion!" Karan greeted her son at the door, and widened her eyes.
"You're soaked through! What were you doing?"

"Walking."

"In this rain? From where?"

"The station."

"And why on earth did you let yourself get this wet?"

"I was cooling off."

"Cooling off, hmm? Laid back as always, aren't you?"

Safu has used the same words only moments before. Shion chuckled to
himself and began towelling off his hair. It had suddenly grown very
cool since it started raining; the old kerosene fan heater was humming
to keep the room warm. Karan yawned. It was already time for her to
sleep. Tucked away in a corner of Lost Town, Karan ran a modest bakery.
It was small, with only one showcase. But people seemed to be drawn to
the aroma of freshly-baked bread that wafted from the doors early each
morning, and business was booming. She opened early, and so slept early
too. It was rounding nine o'clock, which for Karan was like midnight.

"I'm thinking of increasing the batch of butter rolls tomorrow. And
maybe be a little adventurous and try selling some simple cakes, on top
of the muffins that we sell. What do you think?"

"Like cherry cake?"

"That's the one. A little something that people can buy as a snack, but
a little more higher-end than bread or muffins. A small souvenir for a
special day, or something like that."

"That sounds great," Shion enthused.

"Don't you think so? And I think having cakes in the display case would
liven things up a little."

Shion nodded, and began to leave the living room. In this house, they
didn't have the luxury of private bedrooms. Karan slept in a corner of
the living room, and Shion in the storage cellar.

"Shion," his mother called. He turned around.

"Did something happen?"

"Huh?"

"Did something happen to you that would make you need to cool off?"
Karan continued without waiting for Shion's answer. "When you came home,
you seemed a little dazed. You didn't even seem to realize you were wet.
And\el even now---"

"Now?"

"You look absent-minded, but then again a little agitated\el it's a
strange face you've got on. Do you want me to bring a mirror?"

Shion exhaled shortly.

"Someone died in the park today."

"What? In the Forest Park? There was nothing in the news about that."

Nothing in the news? Did that mean that the man died of natural causes?
Although sudden, maybe it was explainable. Not enough to make the news,
just a normal death --- Shion shook his head. Of course not. The time it
took for that body to become rigid, the expression on his face, the
green stain. It was all too abnormal.

To the Security Bureau he had only explained what he found at the scene.
He pretended that he hadn't noticed the rigor mortis or the stain---he
felt like he had to. He didn't know why, but a voice inside him had told
him to play dumb, to lie. Just as a small animal might sense danger and
hide itself, his instinct had warned him. Instinct --- there it was again.
He was acting not on reason, but on whim. He was turning away from logic
and sense only too easily to succumb to instinctive emotion. Shion
sighed deeply. It was a little hard to breathe.

"And that's why you're agitated?"

"Well, yeah. I've never seen a dead body before."

\emph{I'm lying, mom. I saw those eyes again today. I saw Nezumi. I have a
feeling that something's going to happen. That's why---}

Karan smiled and wished him good night. It was a gentle smile. He wished
her good night in answer, and left the living room.

Karan's stature was still plump, but she looked much younger than
before. It seemed like she hadn't taken the move from Chronos to Lost
Town too harshly. She often smiled as she talked about how enjoyable it
was to bake bread, and how uplifting it was when people bought them. It
wasn't just out of kindness or a desire to reassure her son. Karan
wasn't despairing at all about their life here. In Chronos, everything
was given to them, but their life in Lost Town was something Karan had
built up with her own hands. That was why Shion didn't want to destroy
it. He didn't want to uproot her entire life as he did four years ago.
He didn't want to get her involved in trouble again.

Shion collapsed into bed. He felt a faint chill, and there was a dull
pain at the back of his head. When he closed his eyes, a flurry of
images rushed past his eyelids. The greenish stain, the abandoned
lettuce, the pink shirt, Safu's face. \emph{I want to have sex.} The mouse that
had scurried up his body. \emph{Still a natural.} The core of his body grew
hot. His heartbeat quickened. It was no dream. It wasn't an illusion.
Nezumi did exist there, in the crowd people at the station. \emph{That was
some flashy appearance you made back there.} "Jerk," he muttered under
his breath. What was he supposed to expect from that short appearance?
What was Nezumi planning to do?

Shion sat up in bed. Safu aside, were the body in the park and Nezumi
somehow connected? On the same night that he discovered the body, Nezumi
appeared. Was that a coincidence? If they were related, how were they---

A chime interrupted his thoughts. The mobile telephone on his ID card
was ringing. It couldn't be. He knew it couldn't be Nezumi, but his
heart raced. His fingers trembled as he grasped the card. White letters
flashed on the display---Safu. He tapped the Talk button and the screen
switched to Safu's face.

"Shion, were you asleep?"

"Ah---um, no."

He had forgotten. He should be the one calling her back, and to finish
saying the farewell that he had left hanging.

"Safu, I'm sorry about back there. I---"

"That person was that important to you, huh?"

"Huh?"

Safu's face had broken into a wry smile. It was both serene and
beautiful.

"I've never seen you look like that before. Do you know what kind of
expression you had on?"

"Huh? Wait---did I look that bad?"

"It was very interesting indeed. It kept me entertained the whole time.
First, it was astonishment, and then---well, let's see---what could you call
it? Joy? Raptness, maybe. Enough to wipe everything else out of your
mind. And then you beelined out of the station, leaving me behind all by
myself. Sad story, huh? I know."

"I'm so sorry. I can't apologize enough."

"I'll say. You're welcome. At least I got to see a new side of you---I've
never seen you with that face before. So, Shion, who is it that makes
you look like that? Was she\footnote{in Japanese, can be taken as he/she} that important to make you drop everything
and chase after her?"

"Yeah."

He even surprised himself at his prompt affirmation.

"Um, Safu, don't get me wrong. It's not a girlfriend, or anything like
that. Uh---I can't really explain it well, but\el "

"Also my first time seeing you stumble over yourself trying to explain
things. That's alright if you have a girlfriend. I don't mind if you've
already got someone on your mind. ---No, that was a lie. Look at me, I
always try to put up a strong face in any situation. It's a bad habit of
mine."

"That's not true," Shion retorted. "You're always truthful to yourself."

"Only in front of you." Didn't you realize? Safu continued, and her
expression grew serious.

"Safu, really, um--- take care of yourself. When we meet in two years---"

"I love you, Shion. More than anyone else."

The line died without waiting for his answer. He could hear the
pitter-patter of rain. He thought he saw something move in a corner of
the room.

"Nezumi?"

Amidst the bags of flour and sugar piled in the storage room, only the
sound of rain echoed. Shion hugged his knees and sat silently in the
darkness, lending an ear to its continuous drizzle. The rain showed no
signs of either worsening or letting up, and continued through the rest
of the night.