% !TeX spellcheck = en_US

\chapter{Of fathomless terror}

\lettrine{T}{he flow} of sewage was faster and deeper than what Shion had expected.
Indiscernible objects floated past his face. Once in a while, something
would cling to his goggles and block his vision. He could smell an odour
unlike anything he had smelled before. Amidst the overarching smell of
rot was a mix of sickly sweet scents and harsh odours that stung the
nose. In this brownish murk, he could barely follow Nezumi, who swam in
front of him. And more than anything, it was hard to breathe. His heart
thudded, and his chest strained painfully.

Nezumi drifted to the side, and pointed at a handle that was attached to
the wall. Shion reached out and grabbed it. Together, they turned it and
pulled as hard as they could. A round opening appeared.

He couldn't breathe. He was at his limit. His consciousness was fading
away. The next instant, he was sucked into the hole. He was pulled
along, pushed up, and thrown out on dry land. His body was slammed
ashore, and he could feel the shock from it tingle to his toes. But he
no longer felt like he had a wet cloth over his face. He could breathe.
He felt a momentary relief, and then was overcome with a fit of
coughing. He felt nauseous, and the inside of his mouth felt sticky.
Shion yanked off his goggles and closed his eyes. For several moments,
he couldn't move.

"It's a little early for bed-time," Nezumi quipped, but his breathing
was laboured as well. Shion opened his eyes, and saw a bare concrete
surface.

"Where are we?"

"In the sewage pipes. Artifacts of the 20th century. Maybe not
artifacts, since they're still being used." Nezumi shook his head
vigorously from side to side. Water droplets flew from his hair. "When
the amount of sewage goes over capacity, they open that door back there
to flush it down these pipes."

"They flush sewage down here? Without filtering it?"

"Yup. Your beloved City tends to do that sometimes."

"Where does it go?"

"The West Block."

"So they flush dirty water--- how could they..." Shion was at a loss for
words. Nezumi stood up.

"The West Block isn't part of the city to him. It's in the margins. He
probably only sees this place as some kind of garbage dump."

"He?"

Nezumi was standing still, staring unblinkingly before him. At the end
of his gaze was the sewage outlet that they had just been washed out of.
Sewage still trickled in thin streams across the concrete.

"Let's go." Nezumi bent down to scoop up the mouse scurrying about his
feet, and turned his back to Shion. Shion stood up hastily. He still
felt nauseous, but he had some strength left in his legs to stand. \emph{I
still have enough strength. It'll last me. I'll be alright.} Shion
mentally encouraged himself. On Nezumi's shoulder, the mouse that had
been their navigator cheeped amiably.

"Ah!" Shion brought a hand to his neck. He felt something faintly odd.
On the base of his neck, there was a small part that felt numb. Shion
felt the area with his fingers. There was a pea-sized blister growing,
and it was itchy. He scratched it lightly. A chill wind blew through the
centre of his body. Shion could feel his heart contract.

This gesture --- scratching the neck --- he had seen someone do this before.

"Yamase-san." Yamase's image floated up clearly in Shion's mind, pouring
coffee, making conversation, always scratching his neck throughout.
"Don't tell me---"

Nezumi turned around.

"What's wrong?"

"No, nothing."

"You better not be whining that you can't walk anymore."

"On the contrary," said Shion, "I could do with a little more exercise.
Want me to piggy-back you while I'm at it?"

"Nice of you to offer, but no thanks."

The mouse on his shoulder was chirruping. Shion walked faster to catch
up with Nezumi.

He was thinking too much. It was just a blister. The scrape on his arm
and his bruised body were much worse than this. It was a blister, for
goodness sake. Just a blister....

"Why the serious face? Missing your mama?"

"My mother..." Shion murmured. "Nezumi, do you think I'd be able to get
in touch with her?"

"Forget about it."

"How are you so sure?"

"You know well enough. Right now, your house is probably being searched
top to bottom by the Security Bureau, down to the contents of your
garbage can. Unless you have telepathic powers, there's no way you can
get in touch with her."

"I guess you're right."

\emph{---I'm sorry, mom.} He could only apologize. \emph{---I'm safe. I'm alive. So
please---} He didn't want her to despair. He didn't want her to grieve.

"Bullshit," Nezumi spat.

"What is?"

"You. You're full of it."

It was the first time Shion had been insulted to his face.

"What do you mean?"

"What I'm saying is that you're full of bullshit for carrying this
baggage, this crap, like it's the most precious thing in the world."
Nezumi narrowed his eyes and fixed Shion with a hard gaze. His eyes were
piercing, and filled with an emotion almost leaning toward animosity.

Shion opened his mouth to question him further, but Nezumi had suddenly
begun to scale the wall. Upon a more careful look, Shion could see that
there was a rusted metal ladder fixed to it. When he emerged at the top,
he was greeted with an evening sky. He was above ground again. The sky
was painted vividly in the colours of the sunset, and a chilly air
settled upon him.

The place looked like an entrance to the West Block. In the distance,
the outer walls of No. 6 glittered as it reflected the setting sun.
Because of the West Block's lower elevation, No. 6 loomed even larger
before them. It was breathtaking to see the sprawling city encircled by
shining walls. Shion even thought there was a sort of godly air about
it.

Nezumi began to walk in the opposite direction. They emerged from a
sparse wood and soon came upon the ruins of a house. There was smoke
rising out of it, and voices could be heard inside.

"Are there people living in there?"

"Lots of them," Nezumi replied.

Past the ruined house were a row of several barracks.

"This way." Shion was dragged by the arm to another ruins of a building.
This one looked like it had been a warehouse before. The building had
been quite spacious, but half of it had crumbled away into rubble.

"We're going underground again." Nezumi pressed a section of the wall,
and it soundlessly moved aside to let them through. Beyond, there was a
flight of stairs made of bare concrete like those in the sewage tunnels.
The mouse bounded down the stairs. At the foot of them was a door.
Inside, it was pitch black. There was a click, and the room was bathed
in dim light.

Shion caught his breath and was rooted to the spot.

There were mounds and mounds of books, piled precariously high. Most of
the room was buried in them.

"Are these all... books?"

"Do they look like food to you?"

"I've never seen this many."

"Let me guess, you've only read off electronic paper before."

"Yeah, well, not really, but... but wow, this is amazing."

"And to take another guess, you've probably never read Molière, Racine
or Shakespeare before. And you probably don't know anything about
Chinese classics or myths of the Aztecs."

"I don't." Shion didn't argue otherwise. He was too overwhelmed.

"Then what do you know?" Nezumi asked, running a hand through his wet
hair.

"Huh?"

"What have you studied up until now? Systematic knowledge, front-line
technology, how to decode specialized scholarly papers, and what else?"

"A lot else," Shion replied indignantly.

"Like what?"

"How to bake bread, how to make coffee, park maintenance and cleaning...
not to mention, now I know how to scuba-dive in sewage."

"You forgot 'how to reject someone when she asks you to have sex and
you've only ever thought of her as a friend'. You didn't do a great job
at it, though."

Shion raised his chin defiantly and glared at the pair of grey eyes.

"If you have time to be making fun of me, will you let me wash up?"

"I'm first." Nezumi pulled a towel from in-between some books, and
tossed it at Shion. "Don't be mad," he said. "What I actually meant is
that you've come pretty far since four years ago. You've learned a lot
more useful things other than how to make cocoa."

"I'm humbled by your kind compliments."

"Hey, really, don't be mad."

Nezumi disappeared into the pile of books. Momentarily, Shion could hear
the muffled sounds of a shower. He took a good look around the room.
There were bookshelves on every side, and they were filled to bursting
with books. They didn't look like they were sorted in any order, and
books of all sizes were shoved haphazardly into open spaces on the
shelves. Shion felt from them the same kind of hustle and bustle that he
would from a crowded train station. The faded carpet looked like it had
once been some shade of green, and it was also covered in piles of
books. Nestled amongst them was a bed. There were no windows. There was
no kitchen, and no signs of other furniture.

\emph{Cheep cheep.}

A mouse squeaked at him from atop a book. Shion took the book in his
hands, and flipped open to a page. He smelled the faint scent of paper.
He remembered, long ago, he had smelled the same thing. He was sitting
on top of something soft and warm--- his memory wavered. He couldn't
remember it well. The mouse scurried up to his shoulder. It twitched its
whiskers, and chirruped persistently.

"You want me to read this?"

\emph{Cheep cheep.}

There was a bookmark in the middle of the book. Shion turned to it, and
began to read aloud.

\poem{Here's the smell of the blood, still. All the perfumes of Arabia\\
	will not sweeten this little hand. Oh, oh, oh!\\
	---What a sigh is there. The heart is sorely charged.\\
	---I would not have such a heart in my bosom\\
	for the dignity of the whole body.}

Another small mouse had appeared at Shion's feet. It had charming
grape-coloured eyes. The brown mouse that had been sitting on the book
nodded its head vigorously as if to urge him on.

\poem{To bed, to bed, There's knocking at the gate.\\
	Come, come, come, come, give me your hand.\\
	What's done cannot be undone.\\
	--- To bed, to bed, to bed!}

Shion felt a presence behind him, and turned around. Nezumi stood with a
towel hanging around his neck. He gave a deep bow.

"To the showers, if it so pleases your Majesty. Your change of
adornments awaits you here."

"Nezumi, this book---"

"It's Shakespeare. \emph{Macbeth}. Ever heard of it?"

"Only the title."

"I figured as much."

"Are all these books classics?"

"Nay, your Majesty. We also have introductory books to ecology, and
scientific journals to please your fancy."

"Are these all your books?"

"Is it interrogation time again?" Nezumi said exasperatedly. "Run along
and take a shower, and then I'll give you something to eat." He ended
abruptly, and obstinately turned his head aside.

\myspace

The shower was old, and it was difficult to control the temperature. The
flow was punctuated with bursts of frigid water, but for Shion it still
felt nice. It had been a long time since he enjoyed a shower this much.
The itch on his neck had miraculously disappeared as well.

\emph{---I'm alive. I've been saved.}

Shion thought to himself as he let the hot water run over his body. He
didn't know about tomorrow. But he was alive right now, and was well
enough to take this shower.

\emph{---I didn't thank him yet.}

He had been rescued, and Nezumi had risked his life to save him. But not
a single word of gratitude had escaped his lips so far. Realization set
in. Soon after exiting the bathroom, one of the mice came scampering up
to him again.

"He's taken a huge liking to your reading." Nezumi was stirring
something in a pot over the kerosene heater. There was steam rising from
it, and it gave the room a feeling of homey warmth.

"Oh!" Shion suddenly exclaimed. He remembered now, what was behind the
nostalgia and warmth he felt when he opened the book.

"What? What're you shouting for?"

"No, I just remembered. A long time ago, my mother used to read to me."

"She read \emph{Macbeth} to you?"

"Of course not. I was really young then. I remember sitting in Mother's
lap, and she'd read to me." \emph{What kind of story was it again?} The page
was being turned slowly. Karan's voice echoed in his ears, first high,
then low; subdued, then full of strength. He could feel the warmth of
her body. He could smell the scent of paper.

"You're going to destroy yourself," said Nezumi quietly. His voice was
cold.

"What?"

"I've said this before. Carry all this useless baggage, and one day
it'll be the end of you. It'll weigh you down until it squashes you
flat."

"Useless? Like what?"

"Memories. Attachments to being a citizen of No. 6. Your comfortable
life, your overestimation of your own skills, your misconceptions of
being some kind of chosen one, pride. The list goes on forever. But the
worst is your mother. Do you have some sort of Oedipus complex? If
you're being haunted by your mother that much, goodness knows what
you're going to do next. Maybe you'll start saying you want to go back
to the city to see your dearest Mama."

It had touched a nerve.

"Is it a useless thing to think about my parents?" answered Shion
tensely. "I know what kind of situation I'm in right now, and I know
there's no way to get in contact with my mother. But I'm free to think
about her, at least. That's not something for you to say anything
about."

"Throw it away." Nezumi's voice has turned even icier, and had almost a
metallic ring to it. "Throw away useless feelings like those."

"Why--- Why are you saying..." Shion said in disbelief.

"Because they're dangerous."

"My feelings? Dangerous?"

"Back there, you threw away your citizenship card because it was a
danger to us. So are feelings for other people. You get dragged around,
pulled this way and that, and before you know it, you're in dangerous
territory. Your mama, papa, your grandma, whoever--- they're all strangers
now. There's no emotional room in you to be concerned about strangers.
Your hands are full enough trying to keep yourself alive."

"And that's why I should throw everything else away?"

"Toss it. Cut yourself away from all the baggage you've carried until
now."

Shion clenched his fists at his sides. He took a step closer to Nezumi.

"Then what about you?"

"Me?"

"Why did you help me, then? I'm just a stranger, but you stepped into
dangerous territory to save me. You're not exactly practising what you
preach."

"Some personality you've got," retorted Nezumi. "If you really feel that
you've been rescued by me, why don't you try to be a little more modest
when you say things?"

Nezumi's hand extended to grasp Shion's collar. He was pushed against
the bookshelf.

"I owe a debt to you," his low voice hissed at Shion's ear. "Four years
ago, you saved my life. I'm paying back that debt. That's all."

"Then you've paid enough. Too much, even." Shion gripped Nezumi's wrist
to pry it away from his collar. But Nezumi's taut muscles showed no
signs of relaxing.

"Let go."

"Make me, little boy."

"I'll bite your nose off." Shion clicked his teeth. There was a split
second of hesitation. Shion didn't miss it. He slid a hand around the
back of Nezumi's neck.

"Biting noses off is my specialty."

"Huh? Wait a second, that's dirty---"

"I forgot to mention, over these past four years, I've also learned how
to fight."

"Hey, knock it off," Nezumi said nervously, "biting is the worst---whoa---!"

Nezumi lost his footing, and the two fell flailing into the sea of
books. Pile after pile toppled over, and books rained down on them from
above.

"Ow," Nezumi grimaced. "This is the worst. I think I hit my head on an
encyclopedia.... Shion, you alright?"

"Yeah... what's this? \emph{Chumayel's Chilam Balam}?"

"It's a Mayan spiritual text --- a story about gods and humans. You
probably wouldn't be interested in it." Nezumi smiled wanly as he began
to stack the fallen books.

"What's that supposed to mean?"

"It's true, isn't it? Have you \emph{ever} had any interest in other humans, or
gods, or tales before?"

Humans? Gods? Tales? He had never thought deeply about any of those. Not
once. But that was before.

Shion gazed all about him, and breathed in the warm scent that filled
the air. Here was a world that he didn't know. In the days to come, what
would he see, hear, learn, and ponder? His heart raced, but he didn't
know why. For a single moment, his soul had danced with an anticipation,
much like the feeling of seeing the ocean for the first time. Then he
thought of the look he must have on his face. He felt embarrassed for
letting it show, and not wanting Nezumi to see, he bent down and
nonchalantly picked up a book laying at his feet.

"What's this?"

"A collection of Hesse's poems," Nezumi replied.

\poem{My soul, you frightened bird,\\
	Over and over you must ask:\\
	When after so many turbulent days\\
	Comes peace, comes calm?}

"---Heard it before?"

"No."

"I figured as much."

"Don't ask if you already know," said Shion sourly.

"It's your job to learn it if you don't know."

"And these aren't useless things?"

"It'll come in handy one day," Nezumi said casually. "Anyway, enough of
that, the soup's gonna get---" Nezumi swallowed his words. His eyes
widened.

"What's wrong, Nezumi?"

"Shion, your hand."

"Huh?"

"Your hand... when did those spots..."

Shion's shirt sleeve was rolled halfway up his arm. There were dark
spots were beginning to spread over its bare skin. They had not been
there when he was taking a shower. They had definitely not.

"What? What is this?"

He was screaming. At the same time, he felt a vicious pain pierce his
head.

"Shion!"

The pain came in waves. They receded for a moment, then attacked,
bearing ruthlessly down on him. His fingers stiffened. His legs began to
convulse.

"Shion, hang in there, I'll get a doctor---"

Shion willed his uncooperative body to reach as far as it could. He
grabbed ahold of Nezumi by his clothes. There wasn't enough time. It was
useless to call a doctor.

"What should I do? Shion, tell me what---"

"My neck..." Shion said weakly.

"Your neck?"

"The blister... cut it open..."

"But I don't have any anaesthetic."

"I don't need any..." he grimaced. "Hurry..."

He was fading out of consciousness. He could feel his body being lifted.
\emph{Don't pass out. If you do, you'll never wake up again.} He didn't know
what made him feel so strongly, but he was almost sure of it. The pain
ebbed away for a short while, and an image drifted into his mind of
Yamase as he collapsed to the ground and lay still.

\emph{---But Yamase-san didn't suffer.}

He didn't roll around in pain. He aged instantaneously, and passed away
like a withering tree. Yamase's symptoms were different from his. \emph{Maybe
that means I still have a chance---}

His brain was pierced by smouldering red needles. They were countless,
and came from all directions. His body writhed in pain that he had never
experienced before. His own screaming turned into scorching splinters
that stabbed through him. He began to sweat profusely. He felt a strong
wave of nausea. Blood and stomach fluids welled up inside his mouth, and
spilled over his lips.

\emph{It hurts, it hurts, it hurts.}

Shion no longer wanted to be saved, or to be spared death. He wanted to
be released from this pain, this suffering. He didn't need to open his
eyes. He didn't need to live. He wasn't asking for much. He just wanted
to be released---

He felt like someone had grabbed him by the hair from behind, and was
dragging him into the darkness. He felt relieved. All he had to do was
lend himself to it, and he would be taken to a better place. He would
finally be able to sleep.

A thick, bitter liquid was being poured into his mouth. It was hot. It
slid down his throat, and Shion could feel himself rise up out of the
darkness. But it also meant that he was being pulled back into the
throes of suffering.

"Keep your eyes open." A pair of grey eyes were peering into his face.

"Nezumi... I can't take it..." Shion implored faintly. "Let me go..."

He was slapped sharply across the face.

"Don't bullshit me. You're not going anywhere. Drink up." The strong and
bitter liquid was forcefully poured into his mouth again. The darkness
was lifting. Weak pulses of pain throbbed in his head.

\emph{Nibble nibble nibble... nibble nibble...}

Shion thought he heard a sound--- or was it a hallucination? It was the
sound of his brain being eaten alive. There was a mass of countless
black little insects. They crawled all over his brain, making nibbling
sounds,

\emph{Eating. Eating. Eating.}

Was it a hallucination? Or was it... it hurt terribly. He couldn't bear
it. And he was terrified. A scream tore through his throat.

"That's it. Yell. Don't give up. You're still sixteen. It's too early to
throw in the towel just yet."

Shion felt the strength leave his body. He felt heavy, as if he was
being tied to a lead weight. He felt suffocated. But the pain had
receded just a little.

"Keep screaming. Stay conscious. I'm going to cut it open."

There was a silver scalpel in Nezumi's hand.

"I don't have anything fancy like an electronic scalpel, just to let you
know. Don't move."

Whether it was because half of his nerves had gone numb from severe
pain, or because all the strength had left his body, he didn't know, but
Shion didn't move a muscle. He couldn't move.

There were three mice, sitting side-by-side atop a pile of books. Above
them, a round clock was hanging on the wall. It was an analog clock.
Tick, tick, tick. He could hear its sound. It was his first time hearing
the sounds of time passing by. A second passed, then a minute. Time
engraved itself. It passed, gentle, meandering, and vague. The world
before him blurred. His cheeks were hot. A tear slid down, touched his
lips, and was absorbed, still hot, into the sheets.

"It's over." Nezumi let out a long breath. Was the metallic clink the
sound of the scalpel hitting the floor?

"The bleeding isn't too bad. Does it hurt?"

"No... " rasped Shion. "I just wanna go to sleep..."

"Not yet. Hang in there for a little more."

Nezumi's voice faded away. Shion could only hear the sound of the clock
ticking.

"Shion."

He was being shaken.

"Keep your eyes open. Just a little more---please---open your eyes."

Shut up, he wanted to say. \emph{Shut up, shut up. A little more? How long is
a little more?}

"Don't give me this shit. You put me through all this trouble--- you can't
just go off on your own. Shion, you know what that means? Your mama's
going to cry. What're you gonna do about that girl, huh? Safu, or
whatever her name is. Have you ever even slept with a girl before? What
a waste it was to turn down that invitation."

\emph{Shut up. Stop talking. Just stop....}

"You don't know anything yet. About sex, or books, or how to fight
properly. And you still think you don't need to go on living? Shion!
\emph{Open your eyes!}"

He opened his eyes. He saw four pairs of eyes staring back at him. One
pair was grey, and they belonged to a human. The other three pairs were
grape-coloured, and belonged to the mice.

"There's a good kid. I'll praise you for that."

"Nezumi..."

"Hm?"

"I... didn't get your name..."

"My name?"

"Your real... name..."

"Well, there's one more thing you don't know. I'll tell you when you
recover completely, and that'll be your get-well present. Look forward
to it."

He was fed the bitter liquid several more times. He drifted off to sleep
only to be woken up again. Shion felt like he had repeated this
countlessly. He broke into a fever. He perspired heavily, and vomited
again and again. It felt like all the moisture in his body was being
wrung out of him.

"Water...."

He pleaded repeatedly, and each time, a cool draught watered his throat.

"It tastes good..."

"Doesn't it? The world's not such a bad place after all." Nezumi's hand
slowly caressed Shion's hair.

"It's alright now. Go to sleep."

"Can I...?"

"Yeah. You're past the worst of it. You've won. That's quite something."
The fingers that stroked his hair were gentle, as was the tone of
Nezumi's voice. Relief washed over his body. Shion closed his eyes, and
dropped off into a slumber.

\mybreak

With a hand still laid on his hair, Nezumi was checking Shion's
breathing as he slept. It was a little weak, but relaxed. It was not
erratic.

\emph{---You made it through.}

It was quite something. He wasn't exaggerating out of politeness or
encouragement. Shion housed a lot more vitality than his looks gave
away. It was a vitality that was tenacious and strong. Nezumi gazed at
Shion's sleeping face--- exhausted and weakened, but still breathing
regularly nonetheless--- and realized how tired he himself was as well. He
was mentally, not physically, exhausted. He could neither understand nor
come to terms with what he had just experienced. A sense of unease
consumed his mind and made his very blood tingle.

\emph{---What's happening in there?}

No. 6. Something was beginning to brew in the interiors of what they
called the Holy City. Something that exceeded the depths of human
imagination was being born, and developing slowly but surely. Nezumi dug
into the very back of a shelf and pulled out a petri dish. It contained
something he had removed from under Shion's skin when he had cut the
blister open.

\emph{---I can't believe this.}

Yes, unbelievable things happened sometimes. Reality betrayed people
almost too easily, and yanked people's lives at whim in unexpected
directions. At times, it flung them to the depths of despair. It was
cruel and violent. Absurd, even. It couldn't be trusted. Anything could
happen at any time.

Nezumi knew it well. But he couldn't help being perturbed by this
reality. Was it possible for something like this to happen? ---But the
truth was that it had already happened. It was something that couldn't
be brushed away, and he couldn't turn a blind eye to it now.

Nezumi returned to Shion's bedside. He lightly stroked Shion's hair
again.

\emph{---When you wake up, will you be able to believe this reality?}

Would he be able to handle it? Here was a boy who had been cradled and
sheltered in the Holy City's core until the age of twelve. Until
sixteen, he lived in Lost Town --- the outskirts of the city, but still
part of it nevertheless --- and as a citizen, he was treated as such.
Would someone who had been housed in such a protective shell be able to
handle reality? Was he strong enough?

\emph{---Probably not weak enough to be crushed, though.}

But he didn't know. He didn't know how much strength or weakness resided
in the boy sleeping quietly before him. Whether he would withstand it,
or collapse ---Nezumi didn't know. But Shion had survived, and that was
another reality. To survive, you had to sink your teeth into Life and
hold fast. No matter if it was unsightly or harsh --- those who desired
Life most greedily were the ones that survived. Nezumi, from experience,
was painfully aware of this fact. The boy before him possessed that
avarice. It was far more difficult to survive in an unsightly manner
than to die a beautiful and heroic death. It also held much more value.
Of this fact as well, Nezumi was painfully aware.

\emph{---You'll be alright.}

Nezumi moistened Shion's parched lips with water. Then he quietly opened
the door and slipped outside. Dawn was breaking. The sky was lightening
from black to purple, and a sprinkling of stars winked in the sky.

"No. 6." Nezumi addressed the mammoth city darkly looming in the
distance. "You just wait. Some day, I'll carve out that infection of
yours, and lay it out in the open."

A streak of light shot across the sky. A flock of birds took flight. The
sun was rising. Morning was coming. The West Block was still thrown in
the depths of darkness, but the Holy City, bathed in the light of the
rising sun, glittered as if to laugh in contempt at it. Nezumi stood
still, facing the City in silence.

\mybreak

The streets below were brimming with light. He never tired of gazing out
at the morning scene from this room; that was how magnificent it was.

\emph{---Exquisite.}

The orderly streets, and the lush colours of the abundant trees that
lined them were beautiful. It was a place of full functionality and
vigour. Nowhere could one find anything wasteful or ugly. This was a
product of human hands, the highest possible---

There was a chime. A monitor set into the wall flickered, and displayed
the long, thin face of a man.

"I apologize for disturbing you so early in the morning."

"No need. I've been waiting for you."

"The investigation is complete. I would like to report the results to
you directly, in person."

"In person? That's rather cautious of you. Is there something amiss?"

"The suspect has escaped."

"It seems so--- I've heard. But surely that's not of overt importance."

"He was involved in it. He aided in the suspect's escape."

The man on the screen pushed his glasses up his nose. They were rimmed
black, and visibly old-fashioned. Perhaps he was under the impression
that they suited him best, because he had not changed his frames once
for the past ten years.

"Are you sure of that?"

"We've confirmed it. The vocal signatures match."

"Aiding in escape, huh... and his method?"

"I'll report all the details to you shortly."

"Understood. I'll be waiting."

"If you'll excuse me, then."

The image disappeared, and the monitor faded back into the wall. The man
let his gaze wander around him, then out the custom glass panels of his
window to the sky that expanded beyond. It was a deep blue that pierced
his eyes. The seasons were taking their course again.

\emph{---So you've come back.}

What did he return for? Why did show himself again? A single petal
loosened itself from the bunch of roses displayed on his desk, and
fluttered silently to the floor.

\emph{---You should have stayed quietly where you were... idiot.}

He crushed the crimson petal with his foot. It smeared on the lush
carpet, leaving a stain that reminded him of blood.

\mybreak

Yamase was squatted on the floor, hugging his knees, his head bowed. He
looked like a child sulking after being scolded.

"Yamase-san." Shion called over to him. There was no answer.

"Yamase-san, what's wrong?"

Yamase dissolved into tears.

"Yamase-san, don't cry."

Shion placed a hand on Yamase's shoulder. Yamase's anguished sobbing
tore at his heart. It was painful just to listen to him.

"What's making you cry like this? Is there anything I can do?"

"There is." Yamase's hand grasped Shion's ankle.

"Shion, I don't want to be alone. Why did you have to get saved?"

"Huh?"

"Come with me," he pleaded. "You will, won't you?"

"Yamase-san, what---?"

The hand grasping his ankle changed colour. It was beginning to rot.
Chunks of flesh decayed and fell away from Yamase's arm. Shion could see
his bone peeking through.

"We'll go together... right?"

Shion's ankle was being tugged harder. He was being dragged into total
darkness. Yamase's arm continued to rot as it grew in length, and wound
around Shion's torso until it finally reached his neck and began to
choke him.

"No---stop---"

"Shion...."

Shion reached out as far as he could. He felt something firm and
definite, and closed his hand around it, gripping hard. And he screamed.

"\emph{No!}"

Shion awoke with a start. His throat was painfully dry.

"No, what?" Nezumi was peering into his face with a serious expression.

"Nezumi...." Shion murmured dazedly. "Oh... I'm alive...."

"You are. Congratulations on your safe return. And I'm sorry for ruining
your moment, but can you let go of my hand? You're holding on pretty
tight, and it hurts."

He had been grasping Nezumi's hand, so strongly that his fingers were
digging into his flesh. He had clung to this hand to escape from the
darkness.

"Want some water?"

"Yeah," Shion said gratefully.

The water was cold, and quenched every corner of Shion's body.

"I remember you giving me water like this... again and again." Words
formed slowly on Shion's lips, and left them in awkward fragments.

"There's a spring nearby that's not too bad. It's free, so you don't
need to worry."

"You... saved me again."

"I'm not the one that saved you. There aren't any adequate doctors or
medical facilities here anyway, and even if there were, they wouldn't
have done any good. No one could have saved you. You brought yourself
back. You put up quite the fight. I'm a bit impressed, actually. I
promise I won't call you a little boy anymore."

"It's all... thanks to you..."

Shion brought his hand up to his face to gaze at it. It felt somewhat
dry and rough, but there were no spots or wrinkles on it. It was still
the same young hand. He breathed a sigh of relief.

"I had a bad dream...." Shion began softly. "I wanted someone to help
me, and I reached out as far as I could... and I grabbed onto your
hand."

"That frightening, huh?"

"Yamase-san was there--- he told me I can't be the only one to be saved...
his arm was wrapping around me, from my torso to my neck..." Shion
trailed off to feel at his neck. It was wrapped in bandages.

"From your torso to your neck?" Nezumi gave a short intake of breath. He
lowered his gaze, and moved away from the bed.

"Yamase-san was never the kind of person to say that..." Shion continued
reflectively. "He would have been happy for me, that I was saved... why
would he come into my dreams and...."

"Because you feel guilty about it," Nezumi said shortly, wrapping the
superfibre cloth around his shoulders. A mouse leapt up onto one
shoulder from a pile of books. "That Yamase guy died, and you survived.
You're feeling guilty over it, and that's why you're having stupid
dreams like that."

"Everything's stupid or useless to you, isn't it...."~

"Whoever lives wins. Don't feel guilty about having survived. If you
have time to be feeling guilty, work on living a day longer, a minute
longer. And once in a while, remember the ones that died before you.
That's good enough."

"Are you saying that to me?" Shion questioned.

"Who else could I be talking to?"

"It sounded like---" Shion hesitated. "Almost like you were telling it to
yourself..."

Nezumi blinked. He stared at Shion for a moment, and then muttered
"ridiculous" under his breath.~

Shion tried to lift himself up on the bed. He still couldn't move his
body as well as he wanted. He noticed that his entire torso was wrapped
tightly in bandages.

"Why are there so many..."

"You were tearing at yourself in pain, that's why. Lie down, it's still
too early to move around. And take the medicine by your pillow. When I
get home, I'll treat you to some soup."

"You're going out?"

"I have work."

Nezumi turned his back to Shion, and briskly left the room.

Shion swallowed the white pill as he was told to. A brown mouse squeaked
at him from beside a glass of water.

"Thanks."

The mouse nodded as if it understood his word of thanks, and perched on
Shion's chest as he lay back down.

"What kind of work does your master do?"

\emph{Cheep cheep.}

"What's his name? What kind of life has he lived until now? Where was he
born, and what...." he trailed off. He was getting drowsy. It seemed his
body was in want of a little more quiet rest. Shion nodded off to sleep.
This time, he had no dreams. When he awoke, the heaviness and lethargy
in his body had disappeared. He didn't feel any discomfort other than a
dull pain from the wound on his neck. His body was recovering quickly.

There was no one else in the room. It looked like Nezumi had not
returned yet. A dim darkness had settled, and it was quiet. Shion turned
his head to see the three mice curled up fast asleep by his neck. He
rose quietly, and put on his shoes. He wanted badly to catch a breath in
the outdoors. He wanted to fill his lungs with fresh air. Shion took
several cautious steps. He was sweating underneath the bandages on his
neck and chest. He unwound the ones around his neck. Now it was much
easier to breathe. His feet were light, and he didn't feel dizzy or
nauseous. Shion opened the door and climbed up the stairs. A cold draft
of air stung him. The world at ground level was bathed in a reddish
light. It was dusk. Coloured leaves were falling from the trees. They
danced in the wind, and with a dry rustling sound, fluttered to the
ground. Looking above, he could see the dark branches of the trees,
mostly bare, cast in stark relief against the sky. In the distance, he
could see No. 6.

Shion felt a hot pricking at the back of his eyes. It wasn't from
nostalgia for the city where he was born and raised. It was the sights
of late autumn, this unremarkable scene, that had tugged at his heart.
The faint rustling of the fallen leaves, the smell of earth, the colour
of the sky, all resonated in his heart deeply as if to coax the tears
from him.

\emph{---He'll have another good laugh if he sees me like this.}

Shion bit his lip to hold back his tears. He inhaled deeply.

He heard the sound of high voices raised in laughter behind him. Shion
turned around, and saw three children amongst the trees, coming up the
slope toward him. There were two girls and one boy. Did these children
live in the ruined house that he had seen earlier? They all had similar
round faces. He didn't know what they were laughing so joyously about,
but Shion felt his own feelings lift just watching them. Karan loved
children, and always used to hold sales that went by names like "Half
Price for Children Under Ten", so the bakery was always filled with the
voices of small children. That was inside No. 6. This was outside No. 6.
But despite how bizarre the world on this side of the wall was, the
sound of children's laughter was still the same.

The girl, who looked the oldest out of all of them, noticed Shion first.
She stopped in her tracks and opened her eyes wide. Her face stiffened.
Shion didn't meant to scare her. He raised his hand in greeting and
spoke first.

"Hi there."

The small boy standing behind the girl burst into tears.

"Huh? Oh, don't cry---" Shion made to take a step closer. The girl's face
contorted.

"Snake!" she shrieked.

Hastily scooping up the boy in her arms and taking the other girl by her
hand, she clambered back down the slope. Her shriek echoed high into the
sunset. Shion stood in stunned silence.

\emph{---Snake? What did she scream for? What snake?}

He didn't understand the girl's words.

\emph{---What did she see?}

He turned around. There was nothing save for the scenery of late autumn.
There were no snakes, or birds. There was no sign of any living thing.

\emph{---Did the shadows of the branches look like a snake to her? ...No, that
girl was looking straight at me. She was looking only at me.}

Shion shivered. His scalp was tingling. He ran a hand roughly through
his bangs, and pulled hard. It was a habit of his when he was agitated.

"What---"

Shion's breath caught in his throat. There were a few hairs clinging
between his fingers. They were an almost-transparent shade of white.
They caught the light of the setting sun, and glimmered.

"How---what---"

He raked his head, pulling out more hairs. They were all the same. He
felt his face. The skin under his palm was firm. There were no wrinkles
or sags. But he felt a strange sensation on his neck. There was a slight
swell under his skin that was winding around his neck. Shion
half-tumbled down the stairs in haste.

\emph{---A mirror, I need a mirror...}

He knocked over a pile of books. The startled mice darted underneath the
bed. He found a wooden door next the the bathroom. He opened it, and
found a space about big enough for one person to lie down or stand up.
The back wall looked like a mirror. There were various things hanging on
the other walls, but Shion was in no mood to check. He turned on the
light, and moved closer to the mirror. His legs quaked. His hands were
trembling. But he forced himself to gaze into the mirror.

He gave a faint cry of horror.

What was he seeing in the mirror? What was this... this....

\emph{Snake!}

The girl's shriek welled up and echoed in his ears. He needed air, else
he felt like he would suffocate. He couldn't breathe. Shion staggered,
and leaned heavily against the wall. He stared at himself in the mirror.
His eyes were glued to it, and they would not move. He couldn't look
away.

His hair was white and shining. And there was a snake. A red serpent,
about two centimetres wide, was coiled around his neck. That was what it
looked like. He had no doubt about it.

"This can't be..." He shed his clothes. He tried to tear off the
bandages that wrapped his entire body. They had been wound tightly with
care, and they tangled and knotted as if to mock Shion's fumbling hands.
When at last the ends of the bandage had fallen away from his body,
Shion gave a strangled cry. The crimson band that had risen up on his
skin began from his left ankle, coiled up his leg and extended across
his crotch and torso, wound past his armpit and reached up to his neck.
It was, literally, like a snake that was strangling him. It was
slithering over his naked body. A red meander scar. The strength was
leaving his knees. He sank slowly onto the unravelled bandages.

White hair and a red serpent. This was the price he had paid to survive.

"Do you enjoy looking at yourself naked?" a voice spoke, so low it was
almost a whisper. Nezumi was leaning on the door behind him.

"Nezumi--- this---"

"It appeared just as your fever went down. The affection is only
skin-deep, it's not because your veins are engorged. Which means there's
been no damage to your circulation system. Isn't that nice?"

"Nice? What's \emph{nice} about this? This is..."

"If you don't like it, you can get rid of it," Nezum said quietly. "Skin
grafting is no big feat in this time and age, right? As for your hair,
you can dye it another colour. I don't see any problem. But just letting
you know---" he shrugged slightly, "we can do something about your hair,
but you won't be able to graft your skin here. We don't have the
technology or facilities for that." His voice was calm and emotionless,
and contained not the smallest hint of sympathy. Shion remained sitting
where he was, absentmindedly gazing at the bandage that was tangled
around his leg.

"Shion."

"...Yeah...."

"Do you regret being alive?"

It took a moment for Shion to respond.

"---What?" he said vaguely. "Oh--- did you say something?"

Nezumi sighed and knelt down in front of Shion, hooking a finger on his
chin. He forcefully tilted Shion's face up.

"Stop looking down, and look at me. Snap out of your daze and listen to
what I'm saying. Are you lamenting it?"

"Lamenting...? What?"

"Being alive."

"Lament... you mean... like wishing it didn't happen, right..."

"Obviously. No," said Nezumi sarcastically, "I was speaking French, like
\emph{la menthe}, for mint. Really? Get a grip on yourself. Has
something happened to that gifted brain of yours?"

Regret? Toward living? Was he lamenting the fact that he was alive and
sitting here, looking as he did now? Shion slowly shook his head.

"No, I'm not."

He didn't want to die. Even if he had been struck down, he would have
crawled across the ground to stay alive. He had no clear goals or hopes.
He had no sight of the future. His body had changed startlingly, and his
soul was in turmoil. But he still did not want to die.

Life was in the delicious taste of the water that quenched his throat.
It was in the colour of the sky that spread before his eyes, the
tranquil evening air, freshly baked bread, the definite sensation of
someone's fingers, soft, secretive laughter; 'Shion, what do you hope
for?'; the unexpected confession, uncertainty and hesitation. All these
things were connected to being alive. No matter what his appearance
became, he didn't want to be cut away from any of these.

"Nezumi...." he whispered. "I--- I want to be alive."

The tears that he had held back until now gave way. A single droplet
spilled over his cheek. He hastily brushed it away.

"It's no use hiding it, stupid," sighed Nezumi softly. "How can you cry
so openly like that? Aren't you embarrassed?"

"I just let my guard down, okay?" said Shion crossly. "I'm having
trouble controlling myself because I'm not emotionally stable yet. I'm a
recovering patient, so stop making fun of me."

Nezumi silently gazed at Shion's face, and then reached out to gently
grasp at his hair.

"If it bothers you so much, I'll dye it for you later. But it looks
pretty nice on its own. And besides---" Nezumi's fingers moved to trace
the red scar across Shion's chest.

"Think about it, you've got a red snake coiled around your body. Quite
alluring, I'll say."

"I'm not flattered at all."

"Well I don't enjoy seeing you naked either," Nezumi retorted. "Put some
clothes on. I'll treat you to some hot specialty soup and meat."

Come to think of it, it had been a long time since he had eaten any
food. There was a burning sensation around Shion's stomach as hunger
suddenly gnawed at him.

"What kind of soup? Need any help?"

Nezumi blinked.

"You bounce back pretty fast, don't you?"

"Huh?"

Nezumi's voice suddenly dropped low and hoarse.

\poem{Round about the cauldron go.\\
	In the poisoned entrails throw.\\
	Toad, that under cold stone\\
	Days and nights has thirty-one\\
	Sweltered venom sleeping got,\\
	Boil thou first i' the charmèd pot.}

"What's that?"

"\emph{Macbeth}. The scene where the three witches are brewing newt eyes, frog
feet, and bat wings in a cauldron, making their special soup. Charming,
isn't it?"

"If that's your idea of specialty soup, I'll have to say no thanks."

"Instead of bat wings we'll use chicken, and instead of newts we'll toss
in lots of fresh vegetables. We'll substitute the frogs for a clove of
garlic. Just a moment's wait, your Majesty."

Nezumi's specialty soup was piping hot, and more delicious than anything
Shion had ever tasted.