% !TeX spellcheck = en_US

\chapter{The angel of the netherworld}

\myepigraph{I love him, love him. He's a millstone round my neck ---\\
	he'll take me to the bottom with him. But I love this millstone of mine ---\\
	I can't live without it.}{Chekhov, \emph{The Cherry Orchard}, Act III}

\lettrine{T}{he girl} came just as Karan was about to close the blinds of the store.

"Ma'am, are there any muffins left?" She was an adorable child with a
round face, probably not yet ten.

"We're all out of cheese, but if you like raisin muffins, we've got one
of those left."

"I'll have it, please."

"Alright, Lili. Just a second." Karan picked the leftover muffin off the
tray, and put it in a bag with two doughnuts.

"The doughnuts are a little something extra."

"Thank you, Ma'am." Lili dropped a few copper coins into Karan's hand.
She had probably held them tightly in her hand her whole way here, for
although no blood coursed through the coins, they held the warmth of a
human body.

Lili peeked inside the bag, and her face glowed as she observed aloud
that there were two whole doughnuts inside.

"You're one of my regular customers after all, Lili. Next time, I'll
bake some extra cheese muffins for you."

"Ma'am, you won't quit running this store, will you?" Lili raised her
face from the bag, and questioned Karan with a sombre expression.

"I would never. Why would you think so?"

"Mama said that you might close your store. But I'm glad you're not." A
relieved grin spread across her round face. Karan squatted down and
wrapped her arms around the girl's small frame.

"Thank you for worrying about me, Lili."

Her soft body, her warm presence--- she was so small, yet she provided
Karan with definite encouragement.

"Mama and Papa were both worried," Lili said. "They were saying, 'what
if we can't eat the bread or cakes from your bakery again?'. Because you
know, the cake shop in front of the station is bad-tasting, and
expensive, and mean," she said huffily.

"Are they?"

"Yeah. Because the other day, there was a huge white cake on display,
and it was like a toy castle. And me and Ei--- oh, do you know who Ei is?"

"No, I don't."

"He's my friend. He's really good at blowing bubbles. So Ei and me were
looking at it together, because it was so pretty."

"So you two were looking into the shop window?"

"Yeah. And the old man in the store started yelling at us. He said,
don't touch the glass with your dirty hands. We were just looking. We
weren't even touching the glass," Lili said indignantly.

"That's awful."

"So Ei yelled at him back, and said 'you stupid stingy old man!' and so
I yelled at him too, and said 'you stupid bald old man!'. And then we
both ran away."

Karan found herself bursting into laughter. It had been a while since
she had laughed out loud. She kissed Lili on the cheek.

"I can't make anything as big as a castle, but for your birthday, Lili,
I'll bake a nice, all-white cake for you."

"Really?"

"Really. Make sure you share with Ei, too."

"Thank you, Ma'am," said Lili happily. "I like cherry cake."

\emph{Cherry cake---} Shion had liked it too.

Lili waved her hand, and walked out of the store. Karan watched her
retreating back until it melted into the dusk, then lowered the blinds.
She sank into a chair.

After Shion had left her, she found it hard to bear when evening set in
each day. Evening trapped her in the deep disappointment that another
day had passed without Shion coming home. The feeling turned into heavy
exhaustion that made it feel troublesome to lift a single finger.

"Shion\el "

At times a murmur, at times unvoiced; at times as if in conversation, at
times coming close to screaming--- she wondered how many times she called
her son's name each day.

When she heard that the Security Bureau had taken Shion into custody on
charges of civil disturbance and murder, she thought she would go
insane.

"Please be aware that you will likely never meet with the suspect
again."

The night that she had been given the news by a Security Bureau
official, Karan had a premonition that her son would die. She knew more
certainly than anyone that Shion would never take part in a murder. But
a mother's desperate feelings would never get across to the Bureau--- she
knew that well too. In No. 6, where the crime rate was almost zero
percent, there was no judicial system. Merely being arrested and taken
into custody by the Security Bureau confirmed the suspect's guilty
status. Pleading guilty or not guilty was not allowed, nor was raising a
formal objection.

He has already been impounded into the Correctional Facility. Soon, as a
first-class VC he will be sentenced for life; or under special law, be
sentenced to death penalty. The Security Bureau official's words were
neither exaggerated nor twisted in any way--- they were the bare truth.
They had always been. The next time this uniform would appear at her
door would be after the sentence had been handed down to her son. At
this moment, Karan experienced for herself what despair physically felt
like. All sounds disappeared from around her, and all colours faded. She
couldn't smell or feel anything. Darkness was the only thing she could
see before her. It was an inky-black darkness that would never see the
light of dawn. Was this bottomlessness what people called despair---?

\emph{I've lost everything.}

Suddenly, a certain man's face crossed her mind. \emph{If I beg him for help,
could something be done?} But the crack of light that had shone into her
heart soon flickered and vanished. \emph{No--- there's no time.} She didn't even
know where that man was right now. She had no time to search him out and
beg for her son's life.

Suddenly overcome with nausea, Karan vomited all the contents of her
stomach. She broke out into a sweat. She half-crawled to the storage
room, and collapsed on Shion's bed. Most of Shion's belongings had been
confiscated as evidence by the Security Bureau.\emph{ I can just die too, in a
corner of this storage room. I'll close my eyes, and follow after him.}

\emph{Rather than live this brutal life, I can choose the peace of death
that'll come after short suffering. I'm not strong enough to go on
living alone in this darkness.}

"Cheep-cheep!"

She thought she heard something squeak at her ear as she lay there. It
was probably just her imagination. It might not be my imagination. \emph{But
it doesn't matter, I'm already\el }

Something bit her earlobe. A dull pain raced through it. She lifted her
upper body. A small mouse scurried away into a corner of the storage
room.

\emph{---What was a mouse doing here?}

She swallowed. She touched her earlobe. A little blood came off on her
finger. Lost Town may be in the older parts of town, but it was still
rare for animals, excluding pets, to be running around. Even more so for
mice---

"Nezumi." Her heart thumped loudly.

Nezumi. Hadn't Shion murmured that word more than once? While he was
drinking cocoa; while he gazed at the trees swaying in the wind; while
he looked up at the evening sky, he had murmured that word. Ever since
that day, when they had been evicted from Chronos and moved to Lost Town
because of that incident--- it was the day that Shion had undergone an
investigation and received a stern warning for guarding a VC, regarded
as a violent criminal in No. 6. Concealing and aiding in the escape of a
VC normally classified as a serious crime, but with regards to his young
age of twelve and his emotional state, he had been let off with only the
removal of his special privileges.

Karan, for some reason, didn't feel much of an attachment to Chronos,
nor did she find her life in Lost Town harsh. Though others may have
reprimanded Shion's actions for lacking common sense, she was able to
believe that there was something in Shion's feelings and beliefs that
lead him to do what he did. Although the city gave him preferred
treatment as a gifted child because of his level of intellect, perhaps
she had begun to realize somewhere inside that her son would take
emotion over knowledge, and take a future that he could grasp of his own
free will over a future that was already promised to him. That was why
she chose not to question him much about that incident. But she had
asked him once about Nezumi.

"So what's this Nezumi? Who is he?"

"Huh?"

"It's someone's name, isn't it?" She had thought so because of the
tender way her son said the word. Nostalgically, lovingly, at times
strained--- it even carried a tone of longing. He would definitely not use
that tone of voice to call a regular mouse or rat.

"Did you get your heart broken by that person?"

"Never. What're you saying, Mom?"

"Well, it sounded like that."

"No, it's not like that. You've got it all wrong."

It was then that Shion would become unusually agitated, blush crimson,
and do things like drop his spoon. Yes, she remembered it now. Nezumi\el 

She stood up. Her heartbeat returned to normal, and her body felt
lighter. Hope--- though she didn't know why--- flickered inside her. She
could breathe, and the willpower to move on revived within her again.

A small mouse was curled up next to a box of flour. It made eye contact
with Karan, and swung its face around in a wide circle. It spat a
capsule out of its mouth. Then it disappeared into the back of the
storage room. There was a memo inside the capsule.

\memo{\nezumi}{
	Shion is safe, worry not. Escaped to West Block.\vspace{-2ex}\\
	Be wary of Bureau surveillance.\vspace{-2ex}\\
	Any replies to this mouse. Brown brings news of safety,\vspace{-2ex}\\
	black brings news of change or abnormal occurrence. -Nezumi}

The light that flickered in her became a roaring flame. She pressed a
hand firmly to her mouth. She felt if she didn't, she would cry out in
joy.

\emph{He's alive. My child is alive. I'll be able to see him again.}

Karan breathed in, and furtively looked about her.

If the memo was true, and Shion had escaped alive to the West Block,
then this house was probably under heavy surveillance by the Bureau.
Pinhole cameras. Audio tapping. Wireless signal tapping. She would not
be able to act recklessly.

She moved further into the storage room. Beside a crate of jam, she
scribbled on a piece of wrapping paper. The word 'West Block' brought to
mind a hazy figure. \emph{What was his name again?} He worked for the Latch
Bill\el he was a good person. She remembered that much. \emph{Perhaps he
would--- but---}

She had an endless amount of things she wanted to tell Shion.

\emph{Shion, stay alive. No matter what you do, stay alive. Your mother is
fine. As long as you're alive, I'll be fine. So please, don't die.}

But there was no use in spilling her heart out now.

"Cheep cheep!"

The small mouse appeared at her feet. It twitched its whiskers as if to
urge her on. She couldn't stay in one spot like this for long---
especially because she didn't know where the surveillance cameras would
be located. She scribbled hastily, rolled the paper up, and tossed it on
the floor. In an instant, the small mouse picked it up in its mouth and
disappeared.

\emph{If I follow it, will it lead me to Shion?}

It was a fleeting thought. She waved it away, and took a step forward.

\emph{I'll wait here, until my child comes back to me. I'll stay here, and
I'll wait. It's an easy thing to do. He's alive, and he's in the West
Block. If he's alive, I can wait. Hope hasn't been cut off from me. I
haven't lost yet.}

\emph{I haven't lost? Who am I fighting with, anyway?}

Karan smiled slightly to herself, lifted her face, and strode out of the
storage room.

It had been almost a month since then. Just once, a small mouse
appeared. It was brown, which meant that Shion was still safe. She felt
relieved, but at the same time, distressed. Next time, a black mouse
might appear. There was nothing ensuring Shion's safety.

She wanted to see him again. Lately, she had been having frequent
dreams. In them, Shion was still young, and she would became afraid if
they weren't clasping hands with each other. \emph{I won't let this hand go.}
But no matter how strongly she thought so, the little boy's hand would
always slip from hers as he began running ahead of her.

"Shion, wait."

\emph{Don't go there. It's dangerous over there, there's a horrible danger---}

"Shion!"

She would awake to her own scream. These sort of mornings had been
continuing for some time. She had often moaned with dizziness, shortness
of breath and headaches. But she still continued to bake, and continued
to open her store for people like Lili.

Even after news of Shion's arrest and imprisonment had been broadcasted,
the attitudes of the people around her hadn't changed.

The factory worker who always stopped by on his way to work to buy
raisin bread and a sandwich for lunch--- the college student who came once
a week to buy a walnut cake--- the housewife who came every morning to buy
a freshly-baked loaf of bread--- all rejoiced that Karan was still
continuing her business.

"Whenever I eat your cakes, Madam, it fills me with a happy feeling. I
don't know why, but it just makes me feel happy."

"Not being able to eat your raisin bread'll take all the fun outta my
day. It's one of the things I look forward to, so don't ya take it away
from me, Karan-san."

"You're a baker, aren't you? It's your job to bake, no matter what
happens. We're all waiting, you know. Every morning, we all wait for the
aroma of baking bread to waft into the streets."

These, and so many other countless words had supported her. Although
they were still far from strong, the words of others made her soul hold
ground as it threatened to collapse from the distress of not being able
to confirm her son's well-being.

She had borrowed their shoulders to stand, clench her teeth, and
continue to bake bread and cakes.

But evenings were still unbearable. If the people that passed her
storefront on their way home were youths, it was unbearable all the
more. It made her want to weep her heart out.

She sank into a chair, and covered her face with her hands.

"Cheep-cheep!"

She lifted her face. Under the glass display case, a small mouse was
twitching the tip of its nose. It was brown.

"You came."

The mouse looked around, then spat a capsule out of its mouth. She
instinctively knew what would be inside the transparent capsule case.

\memo{\shion}{Mom, I'm sorry. Alive and well.}

The writing was slightly slanted, and distinctive in style. It was none
other than Shion's hand.

\emph{Mom.} The words became his voice as it echoed in her ears. Right then, at
this moment, her son was living. He was alive as he wrote these words to
his mother. He had written on this tiny piece of paper, a message just
several words long. But it was enough to make Karan cry. She couldn't
stop the tears that streamed down her face. She traced the words over
and over again with her fingers.

Shion was probably in a dire situation. He may well be suffering in
uncertainty. But he was not in utter dejection. His cramped but
energetic handwriting expressed that.

\emph{Mom, I'm alright. I'm not unhappy. I really haven't despaired.}

Karan wiped her tears on her apron. She vowed them to be her last. The
next time she would cry would be when she was holding Shion again in her
arms. Until that day, she would weep no more. Despair no more. \emph{I'll bake
bread every day, sell it, manage my money, clean my shop, put out some
flowers, and go on living. I'm going to do my job.}

"Starting tomorrow, I'll put out a few more kinds of muffins. I know,
I'll make it a Kids' Special day."

Karan nodded at her own words, and reached into the glass case to take
out a round savoury roll. The bread, which was sprinkled with powdered
cheese, was still fragrant and tasty even after it had gotten cold. With
its affordable price to boot, it was a popular choice at her bakery.
This one was the last of the batch that she had baked today.

"Thank you. Thank you so much, Mr. Mouse." She broke off a piece and
tossed it in front of the little mouse. The dark brown mouse stared
warily at the bread for a little while, sniffed it, and began to nibble
at it cautiously.

"Is Nezumi your master? Will you tell him that I'm very, very grateful?
And please tell him to come by one day to have a bite to eat. I'll treat
him to as much bread as he can eat. And plenty of bread for you too, of
course."

There was knocking at the door. It wasn't rough-sounding; on the
contrary, it was quiet and almost hesitant. But Karan's heart shrank in
fear.

\emph{Oh no.} There was the possibility that this house was now a part of the
Bureau's surveillance net. She had been so preoccupied with Shion's note
that she had completely forgotten.

\emph{Is it the Security Bureau? Have they come to collect this letter---?}

There was no complete security system here like in Chronos. There was no
security alarm or camera, nor an auto-lock with a built-in recognition
sensor. There was only a door paned with thin glass, blinds that covered
them, and an outdated manual lock. One powerful man would be able to
force his way in easily.

Karan crumpled the note into a ball in her hand. If worse came to worst,
she was prepared to swallow it whole. The knocking still continued. She
stood up slowly. She clenched her hand into a tight fist.

"Excuse me." It was a young woman's voice. "Excuse me\el is anyone
home---?"

The voice trailed off feebly. For an instant, the face of the college
student who liked walnut cakes rose into her mind. But it wasn't her.
Karan pressed the button to open the blinds.

Beyond the glass panes of the door stood a slender girl. She was wearing
a thigh-length grey coat that seemed to melt into the dusk. Karan
remembered the face that looked up and smiled at her.

"Why, it's Safu." Karan hastily opened the door. The girl stepped into
the store along with the evening breeze, and commented on the tasty
aroma. Then she bowed her head.

"Madam, it's been a long time."

"It has. How many years has it been now? You've grown so beautiful. I
was so surprised."

"I did used to be mistaken for a boy a lot," Safu smiled, dimples
showing in both her cheeks. Her smile was still the same as before. Like
Shion, she had placed in the top rank for her intelligence in the city's
Children's Examinations. She had been studying with him as a classmate
in the Gifted class until the age of twelve. Karan remembered hearing
that Safu had lost her parents at a young age, and was living with her
grandmother.

After Karan and Shion had been banished from Chronos, Safu was the one
classmate that continued to treat Shion as she had before. She had also
come to this store once. That time, her face had still harboured some of
its girlish innocence.

But the Safu now, who had unwound her light pink scarf, had silky skin
and a gentle mouth. She showed hints of the beautiful woman she would
eventually grow into.

"But hadn't you gone away on exchange to another city? I remember
hearing something like that from Shion," Karan said.

"I've come back. My grandmother passed away. I received word not long
after I arrived there, so I packed up and came right back."

"Your grandmother? Oh, dear\el "

\emph{This girl has lost the last of her blood relatives.}

"Safu\el I don't know what to say. My heart goes out to you."

This girl had also experienced the same despair. She had experienced the
loneliness of standing by herself in neverending darkness. And she was
so young.

"Is there anything I can do? Safu, is there any way I can help?"

"There is." Safu stood in front of Karan, and looked her straight in the
eyes. She was not wrought with grief. She wasn't anguished, or spent in
exhaustion. She had a resilient and defiant gaze. The kind of eyes that
one could only have in her girlhood.

"I came here because I have a favour to ask you, Madam."

"What is it?"

"Please tell me where Shion is."

Karan drew a breath, and gazed back into Safu's eyes.

"Please, tell me," Safu persisted. "He's alive, isn't he? He's not
incarcerated in the Correctional Facility. He's alive--- where is he?"

Her tone of voice was anxious for an answer. Karan clenched her fist
harder around the small scrap of crumpled paper.

"Safu, you know about Shion, then?"

"I only know what's been broadcasted by the Bureau. Which means I don't
know anything. They're all lies, aren't they?"

"Safu."

"What they said about Shion planning indiscriminate murder from twisted
hatred--- that's a huge lie. Shion wasn't twisted, and he didn't harbour
any grudges toward anyone."

Karan tugged the girl by her hand and led her into the storage room.

"It looks like this room doesn't have any surveillance cameras or
recording devices. Though I'm not sure how safe it is---"

Safu's eyes sparkled.

"If you're being spied on, that means Shion hasn't been captured, right?
He's escaped somewhere, hasn't he? He's been able to escape safely, and
he's still out there alive--- Madam, you're sure of it, aren't you?"

"Why would you say that?"

"Because you're so calm about it\el Just one look at you, and I could
tell. You looked thin and worn, but you hadn't given up completely. It
wasn't the face of a mother who's lost her son."

"I'm blown away, Safu. You'd make an excellent detective."

"Madam, Shion's alive, isn't he? He's doing well, right?"

Karan continued to hold Safu's gaze with her lips firmly shut.

Was there a possibility that Safu had been requested by the Bureau to
come here to seek Shion's whereabouts? Karan thought for a moment. The
answer was no. If the Bureau really intended to, there was no need to
use Safu. It would be easy enough to extract information from Karan
herself using a confession serum.

Was the Bureau actually pursuing her son in earnest?

The thought suddenly crossed her mind. All this time she had been too
swayed by emotional exhaustion and confusion to even think about it, but
if the Bureau were to actually pursue him with all their might, a mere
young boy like him would not be difficult to put under arrest. Even if
Shion had thrown his ID card away, tracking satellites would be able to
confirm his location. As long as he didn't remain eternally underground,
it was nearly impossible to escape the highly-refined tracking
satellites.

"Madam."

Safu's hand grasped Karan's arm.

"Shion's outside of No. 6, isn't he?"

"Yes."

"I knew it\el but it's only natural, isn't it? Within the city,
surveillance would be in effect everywhere. It would be impossible to
hide\el "

"Safu, what's the image resolution of tracking satellites nowadays?"

"The newest ones would be under fifty centimetres. I heard it's possible
to zoom in now by sending commands from the ground. Which means, it's
possible to get an image of a person on ground-level with clarity."

The shrewd girl had guessed Karan's next thought. Safu swallowed, and
continued talking.

"If they input Shion's data into the system, the satellites would start
tracking him automatically. If he's above ground, it would be impossible
for him not to be found."

"Then I wonder if he's gone underground. Or---"

Or has his appearance changed greatly from the recorded data--- was that
even possible?

"Madam\el I think as long as Shion is outside the city, he'll be safe."

"Safe?" Karan repeated Safu's words in question. She didn't understand
what Safu meant.

"I can't say it very well. It's just a hunch I have\el we've never
learned to put things like feelings and hunches into words. But after
spending time outside the city, I've come to feel something\el "

Safu's words became awkward and stumbling. She was desperately searching
for words that described not theory, but something that resided within
herself.

"Ah\el I feel like this city is really closed--- like it's shut itself in.
Like it's just withdrawn completely into itself, solved everything
within itself\el and it's not interested or intrigued by anything
outside of it."

"And you're talking about this city, here."

"Yes. That's how I feel. So if Shion is outside the city, I figure the
Bureau would leave him alone, no matter if he's the suspect of a serious
crime. If he were to come back to the city, though, they would probably
arrest him immediately."

"That would mean Shion would never be able to come back, right?"

"As long as the city itself doesn't undergo some kind of change--- I feel
like that's how it would continue to be."

"That's such a cruel thing to say, Safu."

Safu shook her head, and grasped Karan's arm again.

"Madam, where is Shion?"

"In the West Block. That's all I know."

"West Block--- is that so?" A breath escaped Safu's lips. For an instant,
her gaze wandered in the air. Then she bowed her head deeply toward
Karan.

"Thank you. I'm glad I was able to see you, Madam."

This time, Karan was the one to grab Safu's arm.

"Wait," she said. "What are you going to do, now that you've heard
Shion's whereabouts?"

"I'm going to see him."

\mybreak

Karan was at a loss for words. She couldn't let go of the arm she was
grasping. The slender sixteen-year-old girl stood silently before her.

"Safu\el what on earth are you saying? Do you know what kind of place
the West Block is?"

"I don't. I've only heard that it's a terrifying place. But I'm still
going."

"But--- but--- you said so yourself just now. It might be possible to exit
the city, but getting back in\el "

"It doesn't matter to me," Safu said determinedly. "Even if I could
never come back here again, I wouldn't regret it. If Shion is in the
West Block, that's where I'm going."

"Safu."

"I want to see him. I want to see Shion." Safu's eyes welled up with
tears. She bit down on her lip.

\emph{She's a strong girl}, Karan thought. \emph{At this young age, she's already
learned how to stop her tears.}

Karan reached out and embraced the girl to her bosom.

"Thank you, Safu."

"Madam\el "

"You know, I always thought I was alone. I thought I had to carry this
burden all by myself\el but you were right there with me. You had a
place in your heart for Shion too--- thank you."

"I\el I love him," Safu said, her voice trembling. "From the bottom of
my heart, I've always, always, loved only him."

"Mmhmm," Karan murmured in assent.

"I don't want to lose him. I want to be by his side."

"I know." She stroked Safu's back.

\emph{In the distant past, I'd said the same thing once. I'd met a man I cared
about more than anyone else, and I never wanted to lose him. I wished I
could be by his side forever.}

But they had separated. The only thing he left in her hands was her
newborn baby. 'Shion' was a name that the man had given to his son. It
was his last and only gift to her.

"Women can go on living without a man, you know."

It had come out as a whisper. Perhaps Safu had not heard, for she raised
her face and blinked at her as if in question. As she blinked, a single
tear spilled over and rolled down her smooth cheek.

"Safu, can I ask you to believe in him?"

"Huh?"

"Believe in him. He'll come home one day. Somehow, I just know he will.
He's not as weak as he looks."

"I know that, very well."

"So please, wait for him," Karan implored. "Take some time to see how
the situation unfolds. I don't think it would be good for us to act
rashly."

Safu's shoulders raised and dropped as she took a deep breath.

"Madam, can I ask you one more thing?"

"Sure."

"Who's by his side right now?"

It was an unexpected question. Someone who was with Shion--- unseen, but
by his side nonetheless. Who was it?

"Is it Nezumi, I wonder?"

"Nezumi?"

"Yes, Nezumi. That's the only person I can imagine."

"I wonder if he's a very important person to Shion?" Safu asked.

"I think so. Maybe even as much as you and I are to him."

Safu smiled, and announced that she was going to go home.

"Wait, Safu," Karan said urgently. "Promise me you won't do anything
rash. You'll wait until he comes home, won't you? Right?"

The girl's smile didn't fade. But the light in her eyes was defiant, and
harboured a clear intention.

"I don't like to wait."

"Safu\el "

"I've always been like this. I can't just sit still and do nothing while
I wait. This morning, I went to do all the paperwork to get my exchange
cancelled. I'm free now. So I'm going to go. I'm going to get to where
Shion is, no matter what it takes."

Karan shook her head. She felt like no matter what she said, it would be
of no use now. But she had to stop Safu. She couldn't let her make the
foolish choice to walk right into the spider's web.

"Safu, I may be Shion's mother, but I don't know every single thing
about him. There are probably more things I \emph{don't} know. But--- but you
see, I know that surely he wouldn't want you to put yourself in danger
just to see him. If something happened to you because of that, then he
would suffer for his whole life. This much, I know for sure. So
please\el "

Safu raised her chin. She pursed her lips firmly.

"This has nothing to do with how Shion feels."

"Huh?"

"I'm doing this because I want to. I'm being selfish, I know. But I
can't just sit and wait for Shion in this state. I want to see him so
badly. That's why I'm going. That's all there is to it\el I'm not a
mother, Madam--- I can't be strong like you. I can't keep waiting out of
faith. I don't want to regret anything. If--- if by some chance, he ends
up never coming back\el I'm going to be the one to suffer for my whole
life. I don't want that. I don't want to lose him."

"But Safu\el " Karan said the same words again softly, in her heart.

\emph{But Safu, you know, women can go on living without a man. It'll be
painful, and it might feel like your limb has been torn away, but you'll
still be able to live on carrying that wound. Even with that burden, one
day you'll be able to laugh again. That's why--- please, don't put your
life on the line for any man. Please, live for your own sake.}

How could she respond to this girl's stubborn and fiercely devoted
feelings? How could she convince her? Karan awkwardly but desperately
struggled to find the right words. But already, Safu was turning her
body away from her.

"Madam, I'm glad I was able to see you. Good-bye."

\emph{No, Safu--- never say words of farewell like that.}

"Next time, come by before noon," Karan called out. She willed her words
to reach the back of the figure clad in grey.

"Before noon?"

"Yes. I bake bread from early morning right up to before noon. Earlier
in the morning, I bake mostly rolls and loaves, but closer to noon I
bake sweet breads and cakes. I'm going to bake three kinds of muffins.
Do come and have a bite. I have delicious black tea to go with it, too."

There was a moment of silence between the two.

"I know," Karan continued, "Safu, if you're willing, would you be able
to help me with this shop? I'll teach you how to bake bread. I've been
very lonely all this time. If you would come and work here, I would be
so happy."

She knew she was being foolish. \emph{But what else could I have said? How
else could I distract her heart from Shion? How can I protect her from
danger?}

"Thank you, Madam. I love muffins. I'll look forward to the day I can
taste them."

The girl once more said her words of farewell, and stepped out into the
nighttime streets. Karan silently watched her back disappear. Her arms
and legs felt heavy. One sigh after another escaped her lips.

Why were girlhood loves so fluttering, anxious, and blindly devoted?
Girls at this age couldn't even wait patiently with faith. Their
feelings were so turbulent, so passionate with longing, and so painful.

\emph{I'd completely forgotten how it was to feel like that.}

Karan sighed again.

It was after she had locked up and was about to turn off the lights that
Karan noticed the baby-pink scarf. The forgotten scarf. She could almost
feel Safu's agitation.

Yes, Safu was still wavering in her decision. If she had even a little
bit of uncertainty, she may be able to stop her from going. It might not
be too late after all.

Karan clutched the scarf in both hands, and opened the door of her shop.

\mybreak

She was about to exit the alleyway into the main street when she
realized she had forgotten her scarf. It was a piece that was
hand-knitted by her grandmother.

Right now, hand-knitted scarves and sweaters had come back into fashion
because many people found the woolly texture pleasing on the skin. But
back when Safu had been small, no one wore scarves in No. 6. Most people
wore undergarments made of special fibre under their clothes, and all
parts that touched the skin were kept at a level temperature. People
didn't need to wear scarves, nor even a thin sweater or gloves.

Safu's grandmother knitted as a hobby, and she was always knitting
sweaters and scarves for her granddaughter. Safu was often laughed at by
classmates for them. Even though they were in the same Elite curriculum,
the kids would find any small difference and mock or put others down
because of it. The hand-knitted scarves and sweaters she wore became a
target of ridicule.

"Wow, is that an artifact from the last century?"

"I've only seen that in a museum before."

No one understood what consideration for others was, or anything about
people's souls, or people's dignity. It was because they had never
learned about it. Everyone thought they were the chosen ones. The chosen
ones were permitted to do anything. People belonged to classes: the
chosen ones, and those who were not. Apart from an enormous amount of
theoretical knowledge, in the classrooms which were outfitted with
state-of-the-art equipment, that was all they had learned.

But Shion was different. He knew to treat others with as much respect as
he treated himself. He put himself neither above nor below others. He
was an oddity. That was how Safu had felt about him.

\emph{This person is different from the others.}

She didn't remember when anymore, but he had once complimented a black
sweater that Safu was wearing. The sweater had had a reddish-pink trim
across the chest and around the mouth of the sleeves.

"It looks really nice on you."

Safu had been checking the day's class schedule on the EL display on her
desk. She hesitated a little at being spoken to so suddenly.

"That sweater looks really nice. I can tell just by looking at it that
it's really warm."

"Th--- thank you."

"No worries. But now I've learned something new."

"Huh?"

"Black and pink go pretty well together. I had no idea they did."

It wasn't anything like a proper conversation. It was abrupt, and
one-sided. But at that moment, in Safu's soul, the gentle-faced boy had
risen and left an imprint.

\emph{What a strange person\el }

\emph{He was a strange person. He was different from the rest. So one day,
he'll probably go a different way from the rest of us too. He'll
probably leave, throwing away without a second thought everything we've
clung onto, everything that we've been taught to prize most importantly.}

She had had the feeling before.

So when Shion had passed the selection examinations for the High
Institute's Gifted Curriculum, only to lose his privilege shortly
afterwards to move away to Lost Town, Safu wasn't surprised. Her
premonition had just come true. There was nothing to be surprised about.
But she wanted to know why. She wanted to know the meaning behind the
eyes Shion made ever so often.

\emph{What are you looking at? Who are you looking for?}

\emph{Don't let your eyes wander so far away. Look at me. I'm right in front
of you.}

They were such simple words, but she could never bring herself to say
them. They were such strong feelings, but they showed no sign of getting
across. Communications devices were progressing in quality day by day,
and card-type mobile phones, wearable computers and electronic paper all
existed and were used in the real world--- but all of them were useless to
her. They served no function to communicate her soul to the one that
stood beside her. It riddled her with anxiety.

She was frustrated at herself for not knowing any words of confession,
and at Shion for not even trying to sense her feelings. But even so, she
had bared her soul just before departing on exchange. She was
embarrassed at herself for being so direct, but it was the only way she
could say it.

\emph{I want you. I've always wanted you.}

Simple and direct words. It was the best confession she could muster.
But it had been brushed away all too easily.

\emph{I always thought of you as a friend.}

What an Oscar-award-winning answer. It was so ridiculous she had wanted
to dissolve into peals of laughter. So funny, it was almost painful.

\emph{You numbskull, idiot, grow up a little, won't you?}

She criticized him in her mind. But she had still been able to tell him
what she wanted to say. That was good enough. Her load was one millstone
lighter. \emph{In two years, when I get back from my exchange, I'll start over
again. I'll look at him face-to-face again, when I'll be two years more
mature.} Her soul would remain unchanged. She still ached for him with
longing.

But Shion for the most part, had not even been looking at Safu. His soul
had been captured by something else, and he had forgotten about her. For
the first time, she had seen this calm and serene boy of few words being
ruffled right before her eyes.

Shion's emotions had lost their equilibrium, and he had been in
agitation.

She had tried to follow Shion's gaze, through the station, through the
crowd of people, but she had not been able to see anything. Whoever it
was that she couldn't see had probably been the person Shion had been
searching for. And right now, that person was probably by his side.
Although she had no evidence, she was certain it was true. It was no use
wondering who that person might be. He was an unknown persona.

\emph{Is it Nezumi, I wonder?} That was what Karan had said.

A mouse?

There was. There had been a mouse. Before they had parted at the
station, a small mouse had climbed up onto Shion's shoulder.

"Nezumi." She tried saying it out loud. Only the image of a lab rat came
to mind. The wind blew. She felt cold around the neck. \emph{Should I go back
to get my scarf?} Right as she was about to change direction, a dark
shadow appeared before her.

"Are you Safu-san\footnote{An honorific suffix, here similar to \emph{Miss}.}?" She was called by her name. A faint chill ran down
her spine. These uniforms--- they were law enforcement officers of the
Security Bureau.

\emph{Why were Bureau officials---?}

"Safu-san, am I right?" One of the men repeated his question. It was a
question he already knew the answer to.

"Yes."

"May I see your ID card?" After confirming the card that Safu showed
them, the officials looked at each other and nodded. Their tone of voice
was courteous, but were not friendly in any way. It was mechanical, with
no human warmth. Her chill got worse.

"If you don't mind, we'd like for you to come to the Security Bureau
with us."

"What?"

By the time she had raised a small cry, she had already been flanked by
officials on both sides and taken by the arms.

"Please get in the car."

"No, let me go!" She struggled. Their grip didn't loosen.

"Stop it! What are you taking me for? Tell me why," Safu demanded.

"Get the hell in there and you'll find out soon." Their words became
rough. It looked like they intended to forcibly escort her. Safu let her
body relax.

"Alright. Please, just don't use violence on me." She took a step
forward.

"Ah---!"

She pretended to trip, and let her body fall forward. The men's hands
loosened. She rammed herself into the man to her right. He staggered
back a few steps. Safu swung her bag around, and whipped it at the other
man. She sped through the space between them.

She had to get away. If she got captured, she would never be able to see
Shion again.

What it meant to be forcibly escorted by the Security Bureau--- she knew
by instinct, not logic. \emph{I'll never be able to see him again.}

She saw a shadow at the end of the alleyway. It was too far away to make
out clearly, but she could see that it was holding something
light-coloured in its hands.

Her baby-pink scarf.

"Madam."

Her feet stopped.

\emph{Madam, no. Don't come this way.}

She tried to whirl around, but she was grabbed by the shoulder. Her
wrist was wrenched and twisted behind her back. A shooting pain. Her
mouth was covered as she opened it to scream.

\emph{Stop.}

The men didn't speak a single word anymore. Silently, they proceeded to
capture Safu. A feeling of terror raced through her whole body.

\emph{I'm scared. No. Help me.} She struggled to get free. She heard the sound
of her coat ripping. A button tore off and rolled onto the street.

\emph{Help me. No---help---}

She felt a shock in her neck. Her body went numb, and she couldn't move
as she wanted to.

"No\el help me\el " She was fading out of consciousness. The night scene
before her blurred.

\emph{Shion.}

Before she could murmur the name, Safu was dragged into the darkness.

\mybreak

Karan saw the shadowy figures tangled in a struggle. She heard a small
cry. She instantly recognized it as Safu's voice. She hesitated for a
moment, then broke into a run. But her legs didn't move as she willed
them to, and she tripped and fell, and struck her knee hard on the
pavement.

By the time Karan had gotten back up, the men were dragging Safu's limp
body into a car. It was like a silent shadow play performed on an empty
street. But what was unfolding before her under the evenly-spaced street
lamps was none other than reality. The men were not acting in a fiction---
they were carrying out their assigned mission, without a single word.

Security Bureau.

Her breath caught in her throat. Curled up on the pavement, she was
unable to move. It was not pain, but fear, that prevented her feet from
stepping forward.

One of the men glanced this way. Or at least she thought he did. Her
body shrank in horror. Karan was curled up outside of where the light
shone, so in this darkness it would be difficult to see her. But with
night-vision goggles, the time of day was of no concern. They could see
into the darkness as if it were midday. They could probably see Karan
crystal-clear.

She was terrified.

But the men swiftly got into the car. The black station wagon silently
glided forward, and disappeared from Karan's sight within seconds. Karan
lifted herself up and clenched the scarf in her hands.

"Safu."

She said her name out loud, and the real terror of it finally set in.
Her hands shook. She staggered home, and locked the door. The faint
smell of bread soothed her a little.

Safu had been taken away by the Security Bureau. It had almost been like
a kidnapping.

\emph{Why? Why did she have to get captured? Is it because of Shion? If it is,
then why is it Safu, and not me? Why on earth---}

She didn't know. She didn't know anything.

\emph{Cheep.}

A small mouse poked its head out from under the glass case. It was
holding a morsel of cheese bread in its paws.

"Nezumi."

Would Nezumi be able to help her? Would he bring her salvation? Would he
take the hand she extended out to him?

Toward the small animal with grape-coloured eyes, Karan extended her
palm.