% !TeX spellcheck = en_US

\chapter{Tranquil scenes}

\myepigraph{I am the one without hope, the word without echoes,\\
    he who lost everything and he who had everything.\\
    Last hawser, in you creaks my last longing.\\
    In my barren land you are the final rose.}{Neruda, \emph{Twenty Love Poems and a Song of Despair}}

\lettrine{I}{n No. 6}, those under forty years of age consisted the majority of the
age demographic. It was a young city. Because of this, the odd elderly
person she passed on the street stood out all the more sorely.

\emph{I'd do anything to avoid growing old.}

She was sick of seeing obese, white-haired women; knobbly, wrinkly old
men and the like.~

The woman worked as a nurse in the Municipal Central Hospital, which was
directly managed by the Health and Hygiene Bureau. She was currently in
charge of the elderly wing. Despite the fact that she loathed them, she
had to deal with the elderly every day.

\emph{Why do they bother even staying alive?}

The woman swept a hand through her long, chestnut-brown hair which she
prided herself upon. She couldn't bear the thought of this hair turning
white, and having wrinkles and spots appear on her face. \emph{I'd rather die
before I end up looking like that.}

She was serious. No. 6 had top-notch terminal care. Some said that no
other city could compare.

Once the elderly reached a certain age and received a notification from
the city, they were entitled to live in a place called the Twilight
Cottage, regardless of their social class, sex, or personal history.

The Twilight Cottage was an ideal facility that the city had built so
that the elderly could spend the rest of their lives in abundance and
comfort. People said it was like heaven for them: medical facilities for
palliative care were a given; all things that threatened to hurt them,
whether it be pain, suffering, or distress, were removed. It was a
facility under direct control of the city, and from the woman's
workplace at the Central Hospital, a few elderly people would be
escorted to Twilight Cottage each week. It was not disclosed what age or
what criteria determined when people were sent to the Cottage. Though
not many, there were still some elderly who died from illness or
unfortunate accident even before obtaining the right to live in the
Twilight Cottage. That was why the elderly unanimously rejoiced upon
receiving news of residency.

It was the same with the woman whose application for residency had
passed yesterday. She was ill with a disease that had been declared
incurable even by No. 6's stellar medical technology.

"I'm so glad. Now I can spend the rest of my few years in peace. I give
my gratitude to God and the city for their compassion."

The woman, who had said she was a strong believer in God, had clasped
her hands at her breast, and had murmured words of prayer before leaving
the hospital wing.

The Twilight Cottage. The woman didn't know where it was located. The
city had also not disclosed its address. But the woman had no interest
whatsoever in the Twilight Cottage.

The woman hated elderly people. Her disgust was a side of the same coin
of fear that she felt toward growing old herself. The woman was young
and beautiful. She wanted to stay young and beautiful forever. Through
her work, she had heard rumours that the city was focusing more than
ever its medical research on understanding the mechanism of life. She
had also heard that amongst that, the city was investing considerable
funds in molecular research having to do with ageing.

If a drug to suppress ageing were to be developed --- if she could stay
like this, and never grow old --- how splendid it would be. She wanted
them to succeed soon, as soon as possible.

She was almost at the station. Her parents were waiting at home, in a
little house in a town two stations away. A man and woman just entering
their senior years, they were both harpy, neurotic, and pretentious.
They still complained that their daughter had not been ranked highest by
the city in any field. She didn't want to grow old like that.

The woman stepped into view of the reflective shop window. \emph{I'm on my way
home from work, so I guess it can't be helped that I look a little
tired. But, still beautiful. My hair, my skin --- still youthful, still
beautiful.}

She would do some shopping before going home. In the shop window, she
could see the lavish dresses, tasteful shoes, and practical pantsuits
that lined the store. In this city, she could attain whatever she
desired. Of course, they were limited to things within her financial
range.

Excluding the small part of the population that wallowed piteously in
Lost Town, city residents had no problem obtaining everything they
needed, as long as they weren't after the most premium-class things.
They could obtain clothes, food, and residence without difficulty.

It wasn't nearly as good as it was for Chronos residents, but it was
much better than the people of Lost Town. She lived a relatively
comfortable life.

The woman was satisfied with her position. She wanted to enjoy more of
her youth, her beauty, comfort, and the life that lay ahead of her.

Her feet stopped. A pair of shoes displayed in the window had caught her
eye. They were light-pink pumps. Winter had just begun, but the spring
collection was already being put out. The pink pumps glowed: there they
were, earlier than any other store; faster than anyone else; ahead,
ahead; forward, forward, they invited her.

The Holy Celebration was next week. It was a day that marked the
founding of the city. Parties and celebratory events would be held all
over town. The woman, too, was planning to attend two parties.

\emph{I'll buy these shoes. And I'll buy a light-peach dress to match. It'll
look splendid on me, I just know it.}

Just as a satisfied smile spread over her face, she was struck with a
sudden dizziness. After her brief bout, the base of her neck grew hot.

\emph{What's wrong with me? --- I feel tired --- My body feels heavy.}

Her legs felt weak. She felt nauseous.

\emph{I have to rest somewhere\el }

She entered an alleyway between two shops. There was supposed to be a
clinic run by the Central Hospital through this alley.

\emph{I just have to get there\el }

Her neck was burning. She felt like there was something wriggling
underneath her skin. She felt the unfamiliar and disturbing sensation of
her body being wrung dry.

\emph{What---?}

She staggered, and collapsed. Her purse flew open, and its contents
scattered. The woman extended her hand to pick her things up, and
screamed when she realized what she saw.

Spots --- black spots, like senile plaque, and several of them, were
appearing. Her skin rapidly lost moisture and began to crack.

\emph{This can't be---what---what's happening---?}

The woman snatched her mirror, and peered into it. She shrieked again.
But her voice was hoarse, and what came out was barely a whisper.

\emph{My face--- my face---}

Her face, which had been so beautiful moments before, was changing
rapidly before her eyes. Wrinkles creased her skin, spots marred it, and
her hair began falling out.

Something wriggled at the base of her neck. There was something living
inside her body. The woman, seized by fear, realized that her body was
being taken over by something else.

\emph{No, help me--- Mom---Dad--- save me---}

The faces of her mother and father appeared before her eyes.

\emph{Mom, Dad\el }

Her fingers, extended in plea, grasped thin air. Unconsciousness
overcame her.

\mybreak

Karan sat on the bench, and heaved a sigh, one of many she had heaved
today. She knew sighing was useless. She could cry out, she could throw
herself on the ground, but reality would not budge. It would not change.
Then, at least, she would remain defiant. She would square her
shoulders, hold her head high, and be unashamed.

That was what she thought, but shortly afterwards, a sigh would escape
her lips.

\emph{I can't do anything. I'm powerless\el }

Karan tried opening both hands palm-up in her lap. The gentle rays of
the winter sun shone down on her white palms. She felt another sigh
about to come.

Karan had closed her small bakery in a corner of Lost Town today, and
spent half of the day walking around. She had embarked to visit Safu, in
her and her grandmother's house in the luxury neighbourhood of Chronos.

If residents were acknowledged by the city as being of highest rank in
one of various fields, they were permitted to live in Chronos,
regardless of sex, upbringing, or family structure. The city provided
housing, as well as an ideal environment suited for the growth and
development of each skill.

When her son Shion had been ranked top-level for intelligence in his
Two-Year-Olds' Examinations, Karan had also been given a residence in
Chronos. Comfortable living arrangements, and a lifetime of insurance ---
as an elite, thanks to her son, who would probably eventually work his
way up to the upper echelons of No. 6, Karan was in a position that many
envied and desired.

A position that many envied and desired --- it was a life of comfort, free
of the need to worry of tomorrow's sorrows; free whatsoever of hunger or
violence; a life where indoor environment, security, hygiene, and
physical conditions were all monitored.

Karan slowly clenched her hand. Her fingers, which were smooth and soft
when she had lived in Chronos, had become rough and worn from her work
in Lost Town, and her skin sometimes cracked and bled.

\emph{But until I lost Shion, I was happier than when I was at Chronos. Much
happier.}

Karan had never adjusted well to a life where every minute aspect was
managed and checked upon, and had begun to feel a sort of terror that
her nerves were unravelling. That was why, when Shion had committed a
taboo and engaged in the unbelievable act of sheltering an escaped
convict, she had felt --- more than surprise, more than despair --- a sense
of release, even. She even found herself enjoying it.

Of course, she knew in her rational mind that it meant all of their
special privileges would be revoked, as well as the right to live in
Chronos, and that the path to Shion's future would be closed forever.
But she had still enjoyed it.

She wanted to praise rather than reprimand the actions of her son, which
were so foolish for one with such a level of intelligence. Shion had
thrown away his life in Chronos so easily. Rather than his stable and
insured life, he had chosen the road to protect one who had fled into
his room one stormy night. It was a blunder, if anything. But he had not
been wrong in committing it.

It meant that Shion had also not seen much meaning in life at Chronos.
To him, it was something he could throw easily away. He had only
discarded what was meaningless to him. And that was not wrong at all.

"Mom, I'm sorry."

On their first night moving into Lost Town, twelve-year-old Shion had
hung his head as he apologized to his mother.

"Sorry for what?"

"Because\el Mom, you\el you have to go out and work now."

Shion's crime had been assisting in hiding and aiding the escape of a
violent criminal, called a VC in No. 6. With regards to his age, he had
been let off only with exile from Chronos. But in turn, he was forbidden
to live anywhere other than the city's lowest-class residential area of
Lost Town. Mother and son had slid from the crest of the mountaintop to
valley-bottom in a mere night. First things first, they had to think of
a means of living for the future.

"I'm sorry."

His drawn chin, which still carried a semblance of boyishness, trembled.
Karan wrapped her arm around her son's shoulders in a firm embrace.

"What a stupid thing to say," she said softly. "You shouldn't be
apologizing for something like that."

"But---"

"Shion, are you Mommy, or am I? I think you've got your roles mixed up,"
she scolded in mock sternness. "I'm a lot tougher than you might think.
I bet you didn't know that, did you?"

"No."

"Then that's something you can look forward to. You'll see how tough
your mommy can be, real soon. It'll blow you away."

In her arms, Shion gave a quiet laugh.

How many years had it been since she had last embraced her son like
this? That day, in the dark, damp room that had once been storage for
building materials, what Karan had felt was neither despair nor woe. It
was the joy of her child's warmth in her arms, and the sense of
fulfilment only motherhood could bring.

"What kind of person was he?"

"Huh?"

"The person you took under your wing. I was just wondering what he was
like. I'm curious to know --- but you wouldn't tell me, right?"

Shion's body shrank away from her as if he had been stung. His pout and
his flushed cheeks struck her as so humorous that Karan couldn't help
but smile.

"G'night," Shion mumbled, and with the expression still on his face,
hastily trotted out of the room. Even after the rickety door had closed
with a loud noise, Karan was still smiling.

She wondered what kind of boy he had been. What kind of boy had made
Shion leave Chronos behind? What about this boy was Shion drawn to, and
dazzled by?

She wanted to know, but Shion would probably never put it into words.
Children learned to hide their feelings, or encountered something that
made them, and that was how they grew up. Maybe she would never be able
to draw her son close again like this, without hesitation.

Just as how a fully-fledged bird spreads its young wings to leave its
nest, Karan knew that she would have to part with Shion someday. She was
prepared. If she could see her son off as he took flight, she figured it
would be a joyous thing as a mother. So starting tomorrow, she would
pour herself into work.

True to her vow, for four years at Lost Town, Karan worked tirelessly.
She started with baking bread and selling it out on the street;
eventually, she outfitted a corner of their abode into a bakery, and
increased the variety of her goods. Her affordable and tasty breads and
cakes enjoyed popularity in Lost Town, where there were few such
luxuries. The business grew, and supported their household of two.

Small children showed up to buy muffins, out of breath and with coins
clasped tightly in their little fists. An elderly labourer came to buy a
cake to give as a gift to his grandchildren. There were customers that
came first thing in the morning to buy fresh loaves of bread.

Karan was satisfied with her life in Lost Town. It was not bravado; nor
was she trying to fool herself. She hadn't a thread of attachment left
for Chronos. She was working, and reaping its rewards. It was a life
that they had built up with their own hands, with their feet firmly
planted on the ground. She desired nothing more.

Karan was, in her own way, happy --- until that day had come.

One day, Shion had simply disappeared. He had left in the morning for
his workplace at the Forest Park Administration Office, never to return
home. This was far from the kind of parting she had steeled herself to
face as a mother. This was no natural way to part --- it was so irregular,
so sudden, so cruel. She realized how naive and dreamy she had been in
thinking that she would see her son off as he took flight from the
parental nest.

He had been put under arrest as a suspect of a violent crime, and been
incarcerated in the Correctional Facility.

When she had received word from the Security Bureau, Karan experienced
the full extent of the ugliness of despair. Despair meant being spun
into the folds of deepest darkness. The darkness slithered its way into
her body, and numbed her hands and feet. How irresistible death had
seemed then.

But there was someone who had given her hope to live. Nezumi. He had
contacted her to let her know that Shion was alive and in the West
Block. He had delivered Shion's short letter to her. How beautiful was
the small light that had glittered in the midst of her dark despair.

\memo{\shion}{Mom, I'm sorry. Alive and well.}

The hasty scribble of just a few words had become a streak of light that
tore through the darkness, and became the voice that whispered life into
her ear.

Karan opened her store, and continued to bake bread. Until Shion came
home, she would grit her teeth and wait. She would keep waiting. Nezumi
had brought her the strength to do it. At times, she was still
overwhelmed with anxiety and the urge to scream, but Karan's daily life
was gradually regaining its stability. It was around this time that Safu
had appeared at her door.

Safu, like Shion, had also been acknowledged as highest-ranking in
intelligence. She was a girl whose large, black eyes stood out defined
on her face; and she had an honest gaze. Safu, with few words but a
strong will, had spoke of her love for Shion, and had proclaimed that
she was going to the West Block to see him.

"It doesn't matter to me. Even if I could never come back here again, I
wouldn't regret it. If Shion is in the West Block, that's where I'm
going."

"I want to see him. I want to see Shion."

"I\el I love him. From the bottom of my heart, I've always, always,
loved only him."

The sixteen-year-old girl had formed these words, fighting back her
tears; and for their simplicity and awkwardness, they had touched
Karan's heart all the more. But moved as though she was, she could not
let Safu go to the West Block. As Shion's mother, and as grown adult,
she had to stop her.

Safu left her store, and Karan had followed shortly afterwards. What she
witnessed was the kidnapping of Safu by Security Bureau officials.

It had already been three days since then.

"Safu\el " At her wit's end, Karan let another sigh escape her lips. She
had not the faintest idea what she was to do next. She had passed a memo
to the small messenger mouse. That was all she had done.

Would Nezumi save the girl as he did with Shion? If she was already
imprisoned in the Correctional Facility, it seemed almost impossible to
save her. If Shion found out, and set out to the Correctional Facility
to save Safu, perhaps this time he would really be killed. \emph{Maybe I've
done something rash---} There was no way Nezumi would take such a risk to
save a complete stranger. Her feelings shredded into little ribbons, and
made her fingers tremble.

Karan had spent these past three days hardly sleeping or eating. She was
physically and mentally exhausted, and yet was unable to stay still, and
had come all the way here, close to where Safu used to live.

The luxury neighbourhood of Chronos.

Abundant greenery, and a tranquil environment. A fully-functioning
security system. Various facilities, for medical care, entertainment,
and shopping were provided in full, and residents could use them freely
with only their ID card. Even within the Holy City of No. 6, Chronos was
of a different class still, a residence beyond anyone's wildest dreams.

Although Karan had been a resident here only a few years ago, this time
she was prevented from even entering the streets. As soon as she had
stepped onto the cobblestone path that led into Chronos, the gates had
closed.

\emph{We are very sorry. Due to concerns for safety, the area past this point
is accessible to Chronos residents only. Thank you for your
understanding. Further, anyone who passes the gates without a Entrance
Permit for Special Residential Districts issued by the authorities is
subject to removal from the premises and punishable by municipal law
Article 203 Clause 42. I repeat --- Due to concerns for safety\el }

A gentle female voice flowed forth. The surveillance camera attached to
the chalk-white gates silently captured Karan as she stood with her feet
rooted to the ground. If she remained unmoving here, the soft voice
would turn into a shrill alarm, and Security Bureau officials would
burst onto the scene. Karan had no choice but to turn her back on the
gate, bite her lip, and go back the way she had come.

And now, in a corner of the Forest Park, she was sitting on a bench
under a large tree that had lost all of its leaves. She sat, staring
absently down at her hands.

"Shion\el Safu\el "

\emph{Why am I so powerless? I've been living for decades, I'm a parent, I'm
an adult, and I can't even help two young people who are in the middle
of a crisis. I've been alive for so long, and yet---}

Karan lifted her face. An emotion quite different from dread or anxiety
flitted across a corner of her heart. In the years that No. 6 shaped
itself and began maturing as an independent city, Karan lived in its
interior as a resident.

Six cities were founded in this world, building upon the numerous
blunders that humankind had caused. It was a place free of war or
hunger, and people could live here in peace and freedom. Here, the
people could live from birth to death in safety, bliss, and tranquility.
That was how it was supposed to be. She had never thought deeply about
it. Everyone thought that as long as they stayed in No. 6, they would be
promised a fulfilling life.

They thought --- they had thought --- they had been taught into thinking.

She clenched her fingers, and bit her lip harder.

\textbf{\emph{This is all a lie. Everything--- it's all just an appearance.}}

She whispered without putting it into words. Though it was on the verge
of winter, she was starting to perspire.

They were divided into countless classes by their ID chips so that they
weren't even free to travel inside the city. Her son had been taken
forcibly into custody, and she was not permitted even to make a formal
objection. She couldn't even confirm the safety of another resident who
had been seized by the authorities. Where was freedom? Where was peace,
safety, and a life of fulfilment? It was nowhere.

\emph{If that's true, then what have we been doing all this time? Why have we
created a city like this? What have we done --- where have we gone wrong?}

"Excuse me---"

Karan was jolted abruptly back to reality by a voice.

"I'm sorry. Did I surprise you?" An elderly lady wearing a small,
light-blue hat was smiling at her. It was a face she didn't know.

"Ah---oh no, it's nothing," Karan said hurriedly. "I'm sorry, I was just
lost a little in thought\el is there something---?"

"Would you mind if I sat down beside you?"

"Not at all--- please."

The woman, still smiling, lowered herself into her seat beside Karan.

"What splendid weather it is, don't you think? So nice."

"Yes, it is." The weather was the last thing on her mind. For the past
few days, she had felt nothing in the colour of the sky, the sound of
the wind, or the sight of the trees.

"You must have thought me a rather rude old crone for suddenly speaking
to you like that, I suppose?" the woman said mildly.

"No no, of course not. I was just a little surprised. I was thinking
about something, and I hadn't noticed that you were standing there."

The madam pushed her round spectacles up her nose, and her face turned
serious.

"You see, that's exactly why I decided to speak to you."

"I'm sorry?"

The woman was wearing a silver ring. Her fingers extended to clasp
around Karan's hand.

"Please, I don't want you to be offended. I know very well that I'm
being meddlesome." She hesitated. "But you had such a forlorn look on
your face, I just couldn't go without doing something."

\emph{Oh}, Karan said softly, her hands still clasped in the woman's.

"And that was why you took the time to speak to me?"

"Oh yes. There you were, on such a fine day, on such a splendid
afternoon, looking as troubled as ever. You were sitting alone, limp on
the bench, with your head bowed. There was no way I couldn't go without
saying something."

The elderly woman tightened her fingers around Karan's hands, and
wrapped them tenderly in her own hands.

"Why is a lady so young and beautiful as you, sitting with such a face?
Has something happened?"

The pair of eyes behind the spectacles were soothing and gentle. Above
their heads, the branches of a beech tree were swaying.

"Thank you for your concern. I've just been going through a bit of
trouble\el "

"Yes, I understand," the woman said sympathetically. "There was a time
in my life, too, when I was burdened terribly with troubles." Her aged
but dignified countenance clouded slightly. Karan's heart leapt for an
instant.

Were there other people brooding like her? Were other people suffering
like her? Had other people realized the city's contradictions as well?

"It was devastating, even though it happened decades ago. ---I lost my son
to an illness."

"My, an illness," murmured Karan.

"Yes, and he was only three. When he died, I still remember crying
uncontrollably when I saw how small his coffin was. You would
understand, wouldn't you, the feelings of a mother who's lost her son?"

Karan tried to nod, and drew her chin back just in time. Shion was still
alive. \emph{I haven't lost my son yet.}

"I can't quite say that I do understand---" she said slowly, "but you must
have suffered so."

"Indeed, I did. Words couldn't describe what I went through. Many times,
I thought how much better it would be if I were dead. But now, I'm glad
I'm alive. I couldn't be happier, living in such a brilliant city,
surrounded by my children and grandchildren."

The woman smiled, and cast her gaze around her.

"I would've wanted my son to experience growing up here. No--- if medical
care at No. 6 had been what it is now, I'm sure he wouldn't have had to
die."

Karan softly drew her hand back. The elderly madam's gaze wandered into
the sky as she continued talking. Her lips were still turned up in a
vague smile.

"I really do think this place is a utopia. You know, I say this to my
grandchildren very often. I say, you must be grateful for being born
here. They just look puzzled, of course --- but that's when I tell them
about the West Block."

"The West Block?" Karan's heart quickened again, for an entirely
different reason this time.

"Yes, the West Block. Do you know what sort of place it is?"

Karan leaned forward. She wanted to know. The West Block was where Shion
was, and she wanted to know the details, what sort of place it was.

"I haven't the faintest idea. Please tell me."

The lady furrowed her brow, and shook her head.

"I don't know much about it, myself. But my nephew works at the Access
Control Office, and I hear stories from him sometimes. It's a horrible
place, I hear."

Karan restrained her impatient heart, and murmured in assent. She wanted
to encourage the madam to continue her story.

"The hygiene there is absolutely atrocious, and I hear the children have
to drink contaminated water."

"Contaminated\el "

"Yes, isn't it just horrid? I feel such pity for them, my heart aches.
Compared to that, the children in this city couldn't be happier.
Wouldn't you agree?"

"What? I mean--- yes, but\el "

"That's why over there, they're plagued with contagious diseases all the
time, ones we could never imagine within No. 6. Crime is a daily
occurrence, and safety is almost nonexistent. The residents of that
Block are all uneducated, savage, and most will even kill a man without
batting an eye if it means money for them. Just recently, I heard a
group of violent men tried to force their way into the Control Office.
Of course, since their security system was perfect, they were arrested
before they even set foot inside. It's frightening, really."

The lady wrapped her arms around herself and shivered.

"My nephew told me the place is like a hell, the basest, worst possible
environment. It must be ever so different from here. We must rejoice
too, that we're residents of No. 6 --- not just our children. As for
myself, I'm not afraid to tell my grandchildren how fortunate they are
as No. 6 residents, compared to the West Block."

The West Block. The basest, worst possible environment.

Karan closed her eyes. Shion's handwriting floated up in her mind. It
was a mere scribble, and only one line long. It was a slightly slanted,
distinctive hand.

\memo{\shion}{Mom, I'm sorry. Alive and well.}

The letters were brimming with energy. It was writing that radiated
youthful vigour for life. He was alive in the West Block. Ever so
strongly, even now, he was continuing to live on.

"Is something the matter?"

She opened her eyes at the elderly lady's words.

"Are you feeling ill? Shall I contact the Health and Hygiene Bureau?"

Karan slowly shook her head.

"I don't think so."

"Pardon me?"

"I don't think the West Block is the basest, nor the worst."

"Why, what---"

"And I don't think---"

\emph{I don't think this city is a utopia, either.}

Just as she was about to say those words, there was a sound, a flurry of
beating wings, and a black object came flying at her from above.

\mybreak

The elderly woman gave a small cry.

"Heavens, a crow!"

A crow with glossy black wings had alighted on the ground at Karan's
feet.~

"How disturbing," the woman said uneasily. "Were there ever any crows in
the Forest Park?" She furrowed her brow.

"This is a natural environment after all. There are crows, though
probably not many of them," Karan replied. The crow took flight again.
She thought it would fly away, but instead, it flapped its wings busily
and alighted again, onto a man's shoulder.~

It was Karan who gave a cry of surprise this time. She had not noticed
at all that there was somebody standing this close by. During her
conversation with the elderly woman, there had been other passerby: an
elderly man with his dog; a girl stooping to pick up a coloured leaf; a
group of what looked to be students --- but no one with a crow on their
shoulder. When had he gotten so close? How long had he been there? It
was a little unnerving.

The man was tall and wiry, and clad in a light-brown jacket, with
trousers of the same colour. He had a full head of hair, but with
streaks of grey that stood out. His moustache was also flecked with
grey. Apart from the fact that he had a crow perched on his shoulder, he
seemed like an ordinary middle-aged man. And he was a complete stranger.

But the man extended both his hands toward Karan with a smile on his
face. He even called her name as he spoke.

"Karan, I missed you."

"Huh?"

Before she could give a decent answer, the man grabbed Karan by the arm,
and drew her toward him. Karan's small stature nestled easily into the
man's long arms as they encircled her. He was holding her so tight, she
couldn't breathe.

"Forgive me," he pleaded. "It's all my fault. I'll never do anything
that'll make you feel bad again. I promise. You'll be the only one I
love for the rest of my life."

"Sorry, what---?" Karan stammered in alarm. "What are you doing?"

"I didn't realize how much I loved you until you were gone. Please, I'm
begging you. Say you'll start over with me again, Karan."

\emph{Why, he's gone mad.}

Her first thought was that he was out of his mind. But if someone was
insane, they wouldn't be able to roam on city premises. Just as the
thought crossed her mind, she noticed the man's heartbeat. They were so
close to each other that she could feel his heart beating on her own
chest. It was beating with a steady rhythm. The man was neither insane,
nor nervous with excitement. He was very much coolly and calmly rattling
off these clichéd lines.

"I don't believe this. I've had enough!" Karan thrust her arms in front
of her, and pushed the man away. "I've had enough of your sweet-talking.
I'm leaving you. I never want to see you again."

"Karan, I love you. I'm really, seriously, in love with you." The crow
on the man's shoulder cawed shrilly, as if to mock them. The man cleared
his throat awkwardly, and bowed his head to the elderly lady, who was
staring at them with her mouth gaping open.

"I'm very sorry for having to show you such an ugly scene."

"Oh--- ah, you don't need to---" the woman said falteringly. "So, er, you
two are---?"

"We're lovers," the man answered. "I was a fool, and I caused her a lot
of pain. I just wanted to apologize to her, and start over again."

"I see. Well, that's\el "

"We've got some important things to discuss, so if you'll excuse us---"

The man grabbed Karan's arm, and she was half-dragged away from the
scene. The crow cawed loudly again. They took a back route behind the
Park Office --- Shion's former workplace --- and exited through the back of
the park, the man uttering not a single word the whole way. Karan also
remained silent as she was pulled along by the arm.

There was a white car parked at the curb. It was a rather old model,
seldom seen on city streets anymore. The man opened the door, and spoke
quite without any hesitation.

"Get in."

"No, thank you."

"Get in," the man repeated. "I have something I want to talk to you
about." With a great swoosh of its wings, the crow swooped noisily from
the man's shoulder to the back seat of the car. Then, it looked at Karan
and jerked its head, as if to invite her to follow.

"He looks like a smart bird," Karan observed.

"He's a little too smart for his own good." The man's long-suffering
tone was telling of how much trouble the bird must have caused him. The
crow opened its beak widely and made a cackling sound. It sounded like
it was laughing. Karan, found herself laughing a little, too. Only after
she finished laughing did she realize how she had gone these past few
days without laughing, or even smiling at all.

Karan continued holding the crow's gaze as she slid into the passenger
seat. The electric-gasoline hybrid car glided forward soundlessly. When
they merged onto the highway, the man pressed the switch on auto-drive
and took his hands off the steering wheel.

"Did you know? A new bylaw is being put into place, and we won't be able
to use gasoline starting as early as next year. Which means I won't be
able to drive this car anymore either."

"I've heard that fossil fuels have nearly been depleted, except for
coal," said Karan. "I guess we wouldn't have any other choice but to
switch to another energy source."

"Who did you hear that from?"

"Who---? Well, it's been announced in the city's energy policy---"

"Exactly. An announcement by the authorities. The mayor's speech on his
administrative policy, word-for-word." The man twitched his moustache in
a cynical smile. "No one questions it. Everyone accepts what the city
announces as it is, and agrees to it without a thought. God, everyone in
this damn city is so obedient and naive. Doubting their superiors is the
last thing on their minds. They probably can't even imagine doing that,
or want to. Having suspicions takes energy. It's easier just to sit back
and say, yes yes, I agree, to everything."

Karan threw a sidelong glance at the man's face.

\emph{Then are you saying that you have suspicions? Instead of nodding
obediently, are you saying you're stopping to question it?}

She resisted the urge to ask him. It wasn't wise to say such reckless
things to someone she barely knew. She had to be cautious, like a
cowering herbivore.

Karan drew herself up, and tried to change the direction of the
conversation.

"May I ask you a question?"

"Fire away."

"Who are you, and how do you know my name? What made you go so far as to
stage that half-baked act to pull me out here?"

"Half-baked is a little harsh, no?" said the man wryly. "I thought I
pulled it off quite well. You played along nicely, too. That's Best
Actress Award material."

"Why, thank you," Karan said pleasantly. "The role of romantic heroine
isn't one I get to play often at this age."

"Well, I don't see why not. You're young and beautiful enough, quite,
quite. You could play any heroine you wanted, Karan."

"Where did you learn my name?"

"From my niece."

"Niece?"

"Says she's a fan of yours," said the man. "Or I should probably say, a
fan of your muffins."

A small, round face floated up in Karan's mind --- the girl who always
came to the store with coins clenched in her fist.

"Ma'am, you won't close this bakery, would you?" --- The girl who had
shown sincere concern for Karan. She, along with the words and gazes of
encouragement from others, had supported her in her dark days after
Shion had been taken into custody by the Security Bureau.

"Lili."

"That's the one," the man affirmed. "Lovable Lili. She's my younger
sister's daughter. Says she likes your cheese muffins a hundred times
more than ol' Uncle here. She told me last time I saw her."

"Oh, dear."

"I was ticked off, so I was going to put in my own two-cents about these
muffins of yours, and took a bite out of one to taste\el " The man's
mouth made a chewing motion. He poked the tip of his tongue out, and
licked his lips.

"They were good, weren't they?"

"They were. I hate to admit it, but they were delicious. Guess it can't
be helped that Lili would like them more than some old uncle who only
pops by once in a while."

"Well," said Karan, "at least now I know that you're Lili's uncle, and
that you learned my name from that adorable niece of yours."

"Thanks for understanding. Did you think I was someone suspicious, by
any chance?"

"I still do. What was that act back there? Did you want to pull me away
from that respectable madam that badly?"

"You bet. She was dangerous."

"Dangerous?"

The car turned slowly. It was going into Lost Town. It seemed safe to
believe that this man intended to take her home.

The old car went back along the same path she had taken this morning,
deep in thought. She had taken a day off from the bakery today. Was Lili
disappointed?

"You were a hair away from voicing your dissatisfaction toward the city.
Am I right?"

\emph{I don't think this city is a utopia.}

Indeed, she had been about to voice those words. But she had been
interrupted at that very moment by the sound of the crow's beating
wings.

"That was dangerous?"

"There's a possibility it might've been. What would you have done if
that lady decided you were trouble?"

"Trouble? What do you mean?"

"What I'm saying is, she would've gone to the authorities and told them
that the women sitting on the park bench has a dissatisfaction with the
city."

"You mean she would secretly turn me in?"

"Finding it hard to believe?"

"Of course," Karan blurted. "That's nonsense. That madam was concerned
about me. She spoke to me out of kindness."

"Exactly, because you looked so depressed. In this utopia, in No. 6,
everyone has to be happy. Even seriously ill or injured people have
almost all of their pain removed by leading-edge medical technology.
People who are troubled, or who contemplate, or who lose themselves in
thought --- those kinds of people don't exist. They aren't \emph{allowed} to
exist."

"That's not---" Karan protested. "I mean, there are always people on the
bench who seem to be lost in thought."

The man shook his head, and tapped a corner of the small monitor on the
dashboard that was displaying road information. Small digits expressing
the time popped up on the screen.

"Do you remember how long you were sitting on that bench for?"

Karan gazed at the numbers, and shook her head. She had forgotten
completely about the time. She had sat on that bench, contemplating,
wrestling with her thoughts, and unable to find an answer. She had lost
the will to stand up and keep walking.

"Your time limit is thirty minutes," the man muttered.

"Huh?"

"Citizens are allowed to space out for thirty minutes, at the most. If
they're thinking deeply or losing themselves in thought for longer than
that, the flags come up and someone'll jump in to check."

"So you're saying --- that madam approached me to investigate, because I
was brooding for such a long time?"

"I couldn't say," the man answered. "All I know is that there was a
possibility. Maybe she was just a little old woman who thought she was
being kind and generous --- the kind that won't mind doing something nice,
as long as it's not too much trouble for them."

"What a horrible way to put it."

"It's the truth. This city is teeming with those kind of self-proclaimed
good Samaritans. There are so many of them, it gets pretty hard to
distinguish the ones that are actually good. Still, if that madam was
one of those, it wouldn't be a problem. But what if she was a snitch?
That would've been a close call for you, wouldn't it?"

Karan didn't answer him. She didn't want to be suspicious of the elderly
madam. She wanted to believe that the woman had been a kind soul who had
spoken to her, a stranger, out of genuine concern.

She had had such gentle eyes, smiling behind her spectacles---

Karan drew a sharp breath.

"Those glasses\el "

"You've finally noticed? They were a little big and clunky for a
sophisticated madam like her, don't you think? Maybe they were built in
with a microphone and recording device."

Karan closed her eyes, and let out a long breath.

Thirty minutes was her time limit. She was not allowed any more.

To contemplate deeply; to wrestle with one's thoughts; to immerse
oneself in the realm of one's mind; and from there, to find one's own
answer --- it was all prohibited.

The same question welled up inside her breast again.

\emph{What have we been doing all this time? Why have we created a city like
this? Where have we gone wrong?}

She swallowed her sigh. She felt exhausted, and felt as if the mental
will to retaliate, and the strength to become angry, had all withered
within her.

"I've probably been tracked by the authorities all this time," she said
quietly. "They must have been keeping me under surveillance, and not
only because I was lost in thought. I \emph{am} the mother of a convicted
murderer, after all."

"There'll be none of that," the man said sharply. "No putting yourself
down." His tone was that of a father scolding his daughter. "Do you
really think your son is a criminal, like the authorities have told
you?"

Karan lifted her gaze off the floor, and shook her head. She had not
believed for an instant that her son had murdered someone.

"This is also something I heard from Lili," continued the man. "She says
your son --- name's Shion, right? --- says he's really nice. When she'd
break her toys, he'd always fix them for her. Says she likes him a lot
more than Uncle here, though not as much as your muffins. She was
wondering if he had a girlfriend."

"\emph{Was} she? Oh, dear," Karan said, with a hint of a smile in her voice.

"Cheeky, huh? Acting older than her age. But for all it's worth, she
can't seem to realize how attractive her own uncle can be. Don't know
how my sister raised her, for her to turn out like that."

"And if I ask Lili, would I be able to find out what name this
attractive uncle of hers goes by, and what he does?"

The man laughed at Karan's words, and tapped the panel lightly again.

"God knows what might happen if you asked Lili. She'd probably tell you
that Uncle Yoming is a weird man who wanders by the house once in a
while, eats 'til he's full, and scoots out of the place."

"Yoming. That's your name."

"Yeah. And this is my job."

The panel filled with images of bread, cakes and other light fare,
followed by caloric content and nutritional information, price, and name
of the stores that served them.

"I run an electronic newsfeed for all sorts of entertainment in the
areas, all of them except Chronos. Which isn't much, I mean, apart from
dining and seasonal events, which is mostly what I do. Since the city
oversees all the plays, concerts and print publishing, there's not much
we can write about other than food and drink. The Food Bureau's out of
the question, no way I could get inside that place --- so it's just stuff
like where to eat good cakes, or good places to have lunch, or things
like that. I do the best I can. It's actually quite popular. I mean,
after all, in Lost Town, there's not much to do for fun other than eat
or drink, so everyone's eager for information."

"Then by any chance, are you---"

"Right on," the man said energetically. "I want to run a feature on your
bakery's breads and cakes, with a spotlight on the muffins. Will you let
me interview you?"

"Are you sure you want to write about my shop?" Karan said worriedly.
"Won't the authorities turn their eye on you too?"

"I don't care if the authorities turn their eye on me, or want to trip
me up, what-have-you. I can't let those delicious muffins go without any
publicity." He paused. "Though Lili probably wouldn't be too happy if a
crowd of customers came and cleaned out your muffins. \emph{Uncle, you never
do anything right}, she'd probably say."

"Never," smiled Karan. "---But my bakery's been on the news before, with
my son's incident, and all. People from Lost Town might still come --- but
what about people from other areas?"

Yoming shrugged his shoulders, and erased the image on the touch-panel
screen.

"Karan, the people of this city aren't very good at remembering things."
His voice was hoarse, and hard to catch.

"They forget everything at the blink of an eye. No matter how serious an
incident. Gone. What's more, they don't even see the possibility that
there might be something underneath the surface. Remembering, doubting,
contemplating. It's hard for them to do. But they don't even have to do
it --- the day still goes on, and peacefully, too. It's a terrifying
place, this."

Yoming's words sounded so much like an open criticism of the present
condition that Karan found herself straightening in her seat. If this
conversation reached outside ears, that would be more terrifying than
anything. As if perceiving Karan's agitation, Yoming relaxed his face in
a smile and waved his hand nonchalantly.

"Don't worry. This car is equipped with an anti-tapping device. But who
knows, maybe all the new cars rolling out next year will have tapping
devices built right into them."

"Yoming, why are you so critical of the city? How can you be so certain
that this is a frightening place?"

After a brief silence, Yoming tapped the touch-screen three times.

The image of a young, delicate-faced woman appeared. A baby was sleeping
in her arms, bundled in a white blanket. The woman's smile was filled
with the bliss of motherhood. Her chestnut hair, cropped in a short bob,
framed her alert and energetic face, and her gentle smile was memorable.

"My wife. That's our son in her arms. This picture is from a long time
ago."

"Did something happen to your---?"

"Same as with your son, she left the house one day and never came back.
The only thing that's different from your case is that she disappeared
along with our son, and that she was filed away as a missing person."

Karan's breath caught in her throat. Yoming's calm and levelled way of
speaking made the fact even more shocking.

\emph{It's the same as Shion--- there's someone who's been through the same
thing---}

"She was a school teacher," Yoming said quietly. "She taught art and
music to kids like Lili. Said no other job could suit her better. She
always told the kids to cherish what they felt in their hearts. Whether
it be for drawing a picture, or writing a song, she said the most
important thing was to look straight at your feeling and emotions, and
express them truthfully."

"That's beautiful," Karan breathed. "I don't think I've heard such
touching words in a long time."

"Yeah. She was an admirable woman, touched a lot of people. She had firm
beliefs, and taught her children based on those. But she started getting
more and more stern warnings and directions from the Education Bureau\el 
they told her to teach the kids strictly by the book. The book that
they'd published, of course. Naturally, she resisted--- and she got fired
from her workplace. She got her license revoked too, because they deemed
her as unfit for teaching. I think during that time, there were quite a
few teachers like her who were removed from their jobs. You didn't know,
did you?"

"I had no idea--- I can't even remember\el "

"No need to be ashamed. It's natural you shouldn't know," Yoming said
grimly. "It didn't make the news. The authorities were already starting
to manipulate information by that time. There you had the seeds of a
system that would eventually prevent anything inconvenient from being
publicized as tangible information."

The car was already entering Lost Town. This district was always the
least-maintained and the last to be updated in its facilities, and was
an area of haphazard mish-mash. Amidst its restless buzz, Karan found
herself sighing a breath of relief.

"She was planning to build a school for children, with other exiled
teachers --- she was trying to teach in a place where the authorities
would have less influence. She'd left for a meeting to discuss plans for
the school that day --- and she never came back."

Yoming clenched his fist, and pounded the steering wheel. The crow cried
plaintively in the back seat.

"I'll never forget," he said through clenched teeth. "No matter what
happens, I'll never forget. I'll keep it alive in my memory. It was
cloudy that morning, and it looked like it would rain any minute. I'd
gone to the dentist because my toothache was getting unbearable. I was
off work that day, so I should have been the one babysitting our son at
home. But she took him with her so I wouldn't have to. She put him on a
stroller with a blue hood, and she was wearing a beige jacket. There
were small embroidered flowers on the chest. We promised that if my
toothache settled down in the afternoon, and it didn't rain, we'd go out
to the Forest Park to take a walk. At the door, we kissed and said
goodbye. I kissed my son on the cheek, too. He laughed, and kicked his
feet. He was wearing tiny little white socks. There were flowery
patterns sewn on them too. They were purple violets. I still remember. I
still haven't forgotten a single thing. I could never forget."

"Yoming\el "

The car stopped.

\emph{You have arrived at your destination}, announced the car navigator. They
were in front of Karan's bakery.

"I'm sorry, I got a little worked up," Yoming said. "Rude of me, since
we've only just met."

"No---" Karan said softly. "Thank you for bringing me home."

She paused uncertainly. She questioned herself whether it would be
alright to tell him about Safu. She was unable to decide whether she
could completely trust the man in front of her.

"Ma'am!"

Someone rammed full-speed into Karan's waist as she got out of the car.

"My, Lili."

"Ma'am, why did you take a day off today? Are you sick?"

Yoming called over from inside the car.

"Lili, she's fine. Madam here just had some errands to run. She'll bake
muffins for you tomorrow, I'm sure."

Lili blinked, and her mouth gaped open.

"Hey, is that you, Uncle Yoming? Did you come to eat dinner again? Why
do you always come when we're having chicken and mushrooms?"

"See, this is what I get. Horrible, isn't it?" Yoming smiled wryly, and
leaned forward to peer into Karan's face. "If you can, open your bakery
again tomorrow. And keep on at it. You've got a job to do, Karan."

"Of course."

"Never despair. You can't give up, no matter what. It's only when you
despair and decide that there's nothing you can do, that you really
lose. It might seem easier to just give up---"

Karan placed a hand on top of Lili's head, and shook her head firmly.

"No, I won't give up. I have my responsibilities."

"Responsibilities?"

"Yes. I'm a grown adult, and I've been living alongside this city for a
long time. I've done my best to live respectably, but if the result of
that is what this city has become --- then we've made a huge mistake
somewhere along the way. I'm not sure where we've made it --- but I know
I've got to take responsibility for it. We can't let children like Lili
suffer because of a crime that's not their own, right?"

"Shh---!" Yoming lifted a warning finger. A young woman on a bicycle sped
past the car. "I understand how you feel, but don't say those kind of
things out loud here. You don't know who might be listening."

Lili giggled, and pulled at Karan's skirt.

"Uncle Yo's always being cautious. He's a scaredy-cat, even though he's
a grown-up."

"When you grow up, Lili, you'll start to understand what the really
scary things are."

"Well, I think Mommy is the scariest when she's angry," Lili said
matter-of-factly. "She's really scary, you know. Daddy says he's scared
of Mommy the most, too."

"Ah, that's right, of course," Yoming replied gravely. "I agree, your
Mommy can be very scary."

Karan burst out laughing. Lili's mother would often scold her children
in a booming voice that was hard to imagine coming from her slender
frame.

"Lili, Yoming, and Mr. Crow, too --- if you have time to spare, how would
you like to stop by for a bit? I wouldn't be able to serve you muffins,
but I could whip up some pancakes."

"Really? Yay!" Lili clasped Karan's hand tightly. Her hands were soft.
Karan's heart swelled with an outpouring of love.

\emph{I can't let this little girl go through what Shion and Safu did. And I
must save those two, somehow. Yes --- we have a responsibility to fulfill.}

Her eyes met with Yoming's. They stared back at her, the colour of
crow's feathers. Karan nodded, and unlocked the door.

"Lili, come in. You too, Yoming. I still have things to speak to you
about."

Just then, a small black spot flitted across her vision. She heard the
buzz of wings.

"What's wrong?" Yoming followed Karan's gaze and glanced around as he
got out of the car.

"There was an insect --- I thought I saw a bee flying around."

"Bee? It might be warm still, but I don't think they should be active
anymore."

"I guess you're right."

It was winter. There was no way bees would be flying around. Even if
there were, it was probably a single insect that had wandered out into
the air, drawn by the sunlight and warmth. But she could not shake the
foreboding feeling in her heart.

"Ma'am?"

Lili stared up at her from below as she stood still in the doorway.

"Oh, sorry about that. Come on in."

\emph{My nerves are just on-edge. I must be tired.} Karan reassured herself,
and opened the door. She stepped inside, and shook her head violently,
as if brushing away the buzzing sound that had lodged itself in her
ears.