% !TeX spellcheck = en_US

\chapter{Cease from the struggle of war's impartial contention}

\myepigraph{"Zeus-sprung son of Laërtes, Odysseus of many devices,\\
	hold back, cease from the struggle of war's impartial contention,\\
	lest wide-thundering Zeus son of Kronos be angry against you."}{Homer, \emph{The Odyssey}}

\lettrine{T}{he door} of the elevator was open by a crack. Nezumi hooked his hand on
it.

\emph{Give me strength. Please.} He prayed, but not to God. He prayed to the
girl with the wilful gaze. \emph{Safu, give us strength. A little more, just a
little strength for us...}

The door opened, but not by enough. They could not escape yet. Nezumi
heard laboured breathing behind him.

"Shion..."

Shion was getting to his feet. He silently stretched his hands out, and
his fingers grasped the door. They looked at each other. Tsukiyo poked
his face out of the folds of superfibre and cried once, loudly.

\emph{Cheep!}

Nezumi and Shion took that as their signal to push the door with all
their might. The gap widened so that one person could slip through with
some effort.

The elevator careened. His feet stumbled unsteadily.

"Hurry, get out!" Nezumi pushed Shion out before squeezing through the
gap. The elevator gave an irritating screech, which turned into a
rumble. It hurtled downwards as if it had been waiting for the two to
escape before setting off.

Nezumi closed his eyes for a moment. \emph{My gratitude, Safu.} Sweat poured
down his cheeks. The wound on his leg throbbed. His heart pounded
against his pectoral muscles from the inside.

He was in pain.

His mental and physical strength was whittled down, crumbling off, and
barely remaining. He was in pain, yet―this pain, this throbbing, this
heartbeat was nothing less than proof that he was alive. He was still
alive. Still alive.

He opened his eyes and took in his surroundings.

He saw scattered glass shards and a wet corridor. Two men lying dead.
The black-haired soldier and Rashi were unchanged from how Nezumi and
Shion had left them.

One was lying in the corridor covered in blood, and another was thrown
out on the ground near the wall. The barriers were gone. The sprinklers
were off. There was no human shadow or presence.

Nothing. Only Nezumi and Shion's breathing could be heard, almost too
loudly.

\emph{Whoom.} Something exploded. He spun around and saw smoke coming out of a
room at the end of the hall. It was the room they had fallen into after
destroying the ventilation duct. Flames soon licked through the door
left ajar.

It was burning.

A similar-sounding explosion rocked them from the floor below. He could
hear the commotion and people screaming.

The computer systems on each floor were executing the same program of
exploding and bursting into flames. Like loyal subjects, all devices
within the Correctional Facility were following after the mother
computer.

Were these machines following in their master's footsteps, despite the
fact that they had no soul? No; they had only been programmed to do so.
The mother's failure meant death for all systems within the Correctional
Facility. They were configured to self-detonate as soon as they stopped
receiving signals from the mother. It was nothing as lax as the
information being wiped or deleted, or the device itself going out of
operation. They were forcibly destroyed.

So were they following the master to her grave after all? It was forced
suicide. The system ended everything along with itself. It allowed
nothing to survive. Had the creator of this system directly applied the
dictator's logic?

The flames had crawled into the corridor. The heat attacked them. Smoke
filled the air thickly. None of the extinguishing devices were
operating. Neither smoke extraction devices nor air filtration devices
were working. A system which had been so flawlessly tuned to eradicate
unwanted objects was completely useless.

"Shion, go down. We have to escape downwards."

They clambered down the stairs. Hot air blew at them here as well.
Personnel were screaming and rushing to escape.

"Fire! It's a fire!"

"No, it was an explosion! Suddenly I couldn't control the thing anymore.
Oh, look at this mess!"

"Help me! My arm, it's been blown off―a doctor―"

"Oh, I'm so scared―we have to escape, quickly!"

"What's going on? What's the matter? Nothing seems to work. The
automatic doors aren't opening. What's wrong with the lights?"

"Someone, this person's covered in blood. Someone, please!"

"The smoke... it's choking me."

"We can't use the elevator. The stairs―only the stairs are left."

It was truly a pandemonium. A mob of lab coats stormed the stairs as
each one tried to get down before the other. Some slipped and fell on
top of others. Some tried to help their friends; others stepped over the
fallen ones and fled; some wept; some cried out directions for the
emergency route. A woman helped a bleeding man to his feet; a man shoved
a staggering woman out of his way as he ran past her―each one showed his
true colours in this tragic scene.

An even louder explosion shook the air.

It had evidently blown a hole somewhere, for the air began to move in a
current. The smoke cleared somewhat. If even for a moment, they could
catch their breath.

Again, the same sound, and the faint roar of a crowd.

Nezumi turned around and confirmed that it had come from the direction
of the prison wing. The trapped prisoners were causing a commotion. But
if all of the prisoners' wing had been computer-monitored, then every
door should be unlocked by now. Perhaps that noise was the sound of the
prisoners cheering and roaring at being set free.

But if that was so...

They reached the third floor. The flames, smoke, and confusion were more
subdued than the fourth. Some people had caught a breath on the
stairwell, restored their reason and were attempting to escape this hell
by supporting each other.

\emph{Can we keep at it and escape?} Hope flared. A ray of light pierced the
darkness.

All systems had died. The Correctional Facility was being reduced to a
mere building, an empty shell with no function. With the addition of the
prisoners, the chaos was bound to get worse.

\emph{And when that happens....} Perhaps it would be easy to take advantage of
this situation to escape. There was not much blocking their way.

"Shion, let's go." Nezumi restrained his over-eager heart, and grabbed
Shion's wrist. Shion did not move. "Shion!" he said urgently. "What is
it? We have to get out of here."

"Why did you kill her?" Shion muttered, barely moving his lips. It
sounded almost like a gasp. Nezumi let his hand go, and met Shion's
gaze. He could feel his blood turning cold. He was freezing over
gradually from his extremities.

"Nezumi, answer me. Why did you kill Safu?" Shion's voice caught in his
throat, and took on an unnatural murky tone. Nezumi felt like he was
listening to static-filled music through outdated speakers.

"We― I came here to save Safu. Save her... not kill her." Shion's whole
body began to tremble, but no emotion could be read from his face. Not
agitation, nor wrath, nor sadness, nor anguish.

"Shion, we were too late. She was already―"

"Safu was alive." Shion's murky voice jolted him sharply. He felt like
he had been slapped on the cheek. "She was living, and standing right in
front of me."

"That was an illusion. You should have known yourself. That wasn't her.
It was just an illusion."

"No! No! No!" Shion yelled. "Safu was alive. She was alive, and that was
why she could appear in front of me. Nezumi, I don't care what form she
took. Safu was definitely alive."

"...No matter what form, huh."

"Yeah. Safu may have lost her body, but she was alive. She was alive and
waiting for me. I needed to save her. I should have stayed here with
her. Isn't that right, Nezumi?"

\emph{Safu was alive.} Was she? Had she really been? Nezumi ground his teeth.
She had been alive and waiting for Shion. She had been waiting
devotedly, just for him. She had been alive just to see Shion once
again. And her wish had been granted.

\emph{Safu, Shion overcame hardship and danger to come to you. You were able
to meet your most beloved person. But what you wished for next was to
disappear from Shion's sight. Yes, you wished for it.}

\emph{You didn't want Shion to see you.}

\emph{That was why...}

"Shion, we couldn't have saved her. She and the mother were fused
together. And she... she chose to die with it."

"Is that your reason? Your reason for murdering Safu?"

"Then what should I have done?" Nezumi yelled. His blood, which was
supposed to be frozen, boiled and raced through his body in a hot
stream. "Don't you understand how she felt? She summoned us because she
wanted to see you. And―and couldn't you see it was because she wanted to
be saved? I don't mean escaping from the Correctional Facility. She'd
already known it was impossible. That was why she wanted you at least to
save her from that wretched situation. You were the last person whom she
wanted to see her like that. I mean, wouldn't you feel the same? You
understand, right?"

Nezumi's breathing was erratic. Shion's expression did not change. Not
even a twitch of an eyebrow. The smoke stung at Nezumi's eyes.

\emph{We have to run. We can't waste any more time here. His thoughts were
clear, but his feet would not move. They quaked at Shion's eyes.}

"Shion, I can't think of it as you do. We \emph{were} too late. Safu was
already dead." They were his true thoughts. "You aren't looking at
reality. It would have been impossible to separate her from the mother.
She even said so herself: she had no body, but she was still trapped.
She said it hurt, that she wanted you to set her free. She wished to be
set free from that situation, from her humiliation."

He was not wrong. Shion was the one with the wrong idea. He was unable
to accept the reality of losing Safu. He was trying to avert his eyes
from the truth.

"You used her." A low, low mutter. Nezumi did not catch it.

"What?"

"You used Safu to destroy the mother. Isn't that right?" Shion's eyes
shifted slowly from right to left. Tsukiyo peeked out from the
superfibre, but soon ducked back inside again.

"Destroying the Correctional Facility was your purpose from the very
beginning. Your object was never to save Safu, it was to destroy the
Correctional Facility, and to use it as a gateway to destroy No. 6. You
were waiting for that chance all along. That was why you didn't hesitate
to destroy the mother. You didn't hesitate at all. You used her for your
own purposes. You sacrificed her."

Nezumi stared at Shion. \emph{Used her? Didn't hesitate at all? Sacrificed
her? Shion, you really think so?}

But is he wrong?

He heard a voice questioning him back. It was not Shion's. It was his
own voice. \emph{Did you not use her? Did you not sacrifice her? Did you not
prioritize your own wishes over saving another life?}

\emph{Didn't you? Didn't you? Didn't you?}

Roar. Roar.

A knot of people wearing dark green shirts came storming down the
stairs, screaming. They were prisoners. Their loud cheering hit the
walls around them, bounced, and echoed clamorously.

Roar. Roar. \emph{Get out, get out.}

"Stop! I said stop!" The Security Bureau official's orders were drowned
out by the din. Suddenly, a gunshot rang out. A man trying to run past
Nezumi careened backwards and fell onto the floor in the corridor. He
had been shot through the head.

"Stop! Stop, or I will shoot!"

"Run! Get outta here!" the prisoners yelled. "Don't stop! Escape! Hurry,
hurry and get outta here!"

All the prisoners had bloodshot eyes. Some were foaming at the mouth.
Every one of them roared like beasts as they ran.

To become a prisoner of the Correctional Facility meant death. Whether
guilty or not, regardless of the severity of the crime, as soon as they
were imprisoned, they were on death row.

\emph{We're going to get killed anyway, so why not cling to this miracle?
We'll latch onto this one-in-a-million chance, and be free.}

\emph{To the outside world. To the outside world. Run to the light.}

Gunshots. Sprays of blood. A white-haired prisoner crumpled over the
railing. Gunshots, explosions, smoke, fire.

"Shion, it's dangerous here." Nezumi grabbed Shion's arm and yanked. He
met no resistance. Shion staggered and bumped his shoulder on the wall.
He slid to the ground, still leaning on the wall.

"Nezumi... I'm sorry." A whimper spilled from his bloodless lips. "I'm
sorry. I―I―" Shion covered his face with his hands, and drew several
ragged breaths.

"I know," Shion said. "I know we had no choice but to do it. You granted
Safu's wish... I have no reason nor right to blame you. It was me... I
should have been the one to do it. It was my job to set Safu free. But I
couldn't. I was scared... and I couldn't do it. I leaned on you again,
thrust everything onto you, and made you do the dirty work. I didn't
want to acknowledge my cowardice, so I blamed you, ran you to the
ground..."

Nezumi looked down at Shion's snowy hair. Despite having been through
such a hellish ordeal, it had not lost any of its lustre. Every single
hair shimmered elegantly.

"I got you involved, and even dragged Rikiga-san and Inukashi into it...
and if the result was this.... Nezumi, we didn't come here for
destruction. We came here to give salvation. But look―"

"We came for destruction."

Shion lifted his face. It was smeared with sweat and blood.

"You're right. I had only one purpose, and it was to destroy the
Correctional Facility. I never had plans to save Safu from the
beginning."

"Nezumi..."

Nezumi looked away from Shion. He couldn't hold the other boy's gaze.

"I needed you. I knew that without your memory and judgment skills, it
would be impossible to get around inside the Facility. You were my last,
and my best trump card. I thought for a long time how I would use you,
and... this is the answer. The thing about Safu was just an excuse. I
just... used you and her to satisfy my own purposes."

\emph{Yes, Shion, you aren't wrong. I betrayed you. I was tricking you all
along. You didn't get me involved; it was the other way around. I set
the cunning trap.}

"My plan was a success. Look at this confusion. The Correctional
Facility is crumbling. Shion, I―I directed things to proceed according
to my intentions. Frankly, I didn't expect it to turn out so well. You
served your purpose a hundred times better than I expected. You were...
really useful to me."

Shion stood up unsteadily.

"Nezumi, what are you talking about?"

"I never believed that Safu would be safe. The moment she was
imprisoned, I knew the possibility of her escape was close to nil.
Shion― saving Safu never mattered to me. When I planted the bomb in the
mother, I was only thinking of destroying it and getting out of there as
soon as possible. That was it."

The superfibre cloth slid from his neck and fell at his feet. Had he
been bowing his head unwittingly? Nezumi stooped to pick the fabric up,
and stared intently at the boy in front of him.

"I'm not asking you to forgive me. It's not something I can apologize
for and be done with."

"What are you talking about?" Shion said loudly. "I'm not getting a
single word."

\emph{Really? Can you really not understand?}

\emph{You're a liar, Shion. You do get it. You understand every single word.
And you'll never forgive me. You'll lose faith in me and loathe me. Or
would you―}

\emph{Cheep!}

Tsukiyo squeaked sharply. Nezumi felt his spine tense. He felt like
transparent arrows were stabbing into him. It was murderous intent.

He turned around. A man stood there, aiming a gun at him. He was not a
Security Bureau official. He was one of the soldiers who had been under
Rashi's command.

Nezumi had noticed him too late.

"Shion, duck!" He shoved Shion as hard as he could. Immediately, the
impact came. A beam of light seemed to pierce his entire body.

It scorched him.

He tried to scream.

\emph{Escape, Shion. Hurry}, he thought, but no voice came out. Somewhere―
somewhere in his body, he was burning. It was hot.

"Nezumi!"

He could see Shion, wide-eyed. He could see clearly the boy's screaming
mouth, his extended hand, and the shape of his fingers. The image was so
vivid, it seemed hardly real.

The vivid scene blurred, and darkness closed in.

All colour faded.

\mybreak

\emph{Raugh!}

The black dog was thrown out across the floor. Its limbs convulsed as it
foamed at the mouth. The Bureau official had propped himself up and was
holding a small gun in his hand. The black dog eventually stopped
moving. Despite its aggressive nature, it had loved to nap in the sun.
It would often lie in the sunlight much like it was doing now,
stretching its legs out. It had a temperamental disposition, but it was
loyal to Inukashi,

\emph{I'm sorry.}

Inukashi cast a glance over the dog, and apologized inside his heart.
\emph{I'm sorry for putting you through this. Forgive me.}

He could see down the barrel of the gun. He could see the hollowed
cheeks of the thin-faced man who held it. Inukashi did not flinch. He
did not stop. A moment of hesitation, a moment of confusion could cost
him his life. Once he started to move, he had to keep moving. With the
enemy before him, he had no option to cower.

He aimed his gun and fired blindly in furious succession.

\emph{Damnit, damnit, you bastards. You arrogant murderers. You're all cruel,
dirty thieves. Give back everything you've stolen from us. You guys have
trampled over everyone in the West Block for this whole time. You killed
people indiscriminately. You cold-blooded murderers. Have some shame.
That's right. You shameful, despicable people. Damnit.}

He mentally hurled as many insults at them as he could. He could not
voice his vilification. If only his wrath could turn into bullets and
shatter that blue-grey weapon.

\emph{Can't you give us a miracle like that for once, God? You were quick to
turn your back on the West Block, like a mother abandoning her infant on
the barren plains. Doesn't your moral conscience bother you at all? So
give me a miracle, at least, to make up for it. Hand over that miracle
so we can survive.}

His foot slipped. He lost his balance and landed on his bottom. Bullets
bounced at his feet. If he had not fallen, he would have been shot
cleanly through.

\emph{Phew, I still have some luck left.}

"Don't move, filthy sewer rats." Bureau officials pointed guns at them.
Simultaneously, a nerve-racking bass rumbled.

"We'll exterminate you well. Be prepared."

\emph{Sewer rats? Don't you dare put me on the same level as those lowly
animals.}

Inukashi tried to pull the trigger, but realized the gun was out of
bullets. He glanced at the power shovel.

\emph{What the hell are you doing behind there, old man?} The baritone rumble
was issuing from the somewhat comically wide mouth of the shockwave
cannon. Preparations seemed to be set.

\emph{What? No way. Is this it? A frigid wind blew up at him. Is this the end?
Am I gonna die here? That can't happen. You gotta be kidding me. Nezumi,
this isn't what you promised. The whole show is gonna be ruined before
the main actors even appear. What the hell do I do now? Do something, do
anything, Nezumi!}

Suddenly, the lights went out. An alarm sounded.

"What? What is it?"

"I don't know. Something's happened inside."

"Hey! Did you hear an explosion?"

"Huh? Oh, now that you mention it―"

Inukashi could feel strongly the agitation of the officials.

"I can't see! I can't see anything in here!"

Shrill screams, almost shrieks, echoed in the darkness. \emph{It's the same as
with the smell. They're really, really weak.} Inukashi smirked.

The people of No. 6 were so unbelievably, so laughably weak when even a
small change occurred in their clean and comfortable environment.
Perhaps soldiers would have had a little more resistance. But the
Security Bureau officials were cowering, clearly exposing their
fragility.

\emph{Look at what a loss you're all at. You build that murder weapon with a
cool face, but you're afraid of the dark. Disgusting.} Inukashi hurled
abuse at them, still sitting on his bottom. He restrained himself from
rushing out.

"Not yet. Don't rush it," he told himself.

The alarm grew louder. Its enormous volume rattled his eardrums.

\emph{Emergency alert. Emergency alert.}

\emph{Level 5, Level 5.}

\emph{Emergency evacuation. Emergency evacuation.}

\emph{All personnel, evacuate immediately.}

\emph{Level 5, Level 5.}

"Level 5!? What is it, what's going on?"

"I don't know, but we should evacuate. We have to get out of here, or
we'll be in danger."

"Hey, there it is again. I heard it. Things are exploding everywhere.
Get out!"

"I-I wish I could, but it's so dark... why aren't the backup lights
coming on?"

"This is a trash depot. Do you think they have backup lights?"

\emph{Now!} Inukashi leapt to his feet, using his whole body for leverage. \emph{I'm
used to the dark. You'll see how different I am from all of you.}

"Bastards!" He yelled as swung his gun around. It hit something. The
dogs snarled and pounced. Inukashi started yanking out all the pipes and
cables attached to the cannon.

\emph{Bastards. Bastards. Making crap like this. You guys made a monster
that's good for nothing but killing people.}

\emph{Level 5, Level 5.}

\emph{Emergency evacuation. Emergency evacuation.}

"Outside! Get outside! It's dangerous in here!"

"Yeah, get out! We have to evacuate!"

The Security Bureau officials fled through the door leading outside.

Inukashi stood, breathing heavily. Sweat poured off his whole body. But
he was shaking. He could not stop. His teeth chattered. His heart was
palpitating so badly, he had trouble catching his breath.

He fell to his knees as the strength left him. His dogs approached. One
with a patched coat pushed its nose up against him. Inukashi latched on
to its furry collar and buried his face in its soft fur. It smelled like
dog. He had known this scent for as long as he could remember. It was
the scent of his mother, his siblings, and his friends. It smelled more
sweetly than any flower.

Tears spilled over. They streamed down one after another. \emph{We're saved.
We've been saved.} The dog licked away the tears on his cheeks. \emph{It's
warm. Oh, it's so warm. I'm still alive.}

"I owe it to you guys. Thank you. Thanks so much."

"Inukashi..." Rikiga came crawling out through the door of the waste
collection area. "Looks like they ran off."

"Yeesh, old man," he gave a purposely long sigh. "What good are you
gonna be now? Were you off shopping for today's dinner or something?"

He gently brushed his tears away so Rikiga wouldn't see them. Rikiga
shrugged, and laughed softly in the dark.

"I told you, I'm a philanthropist. I'm also a born and bred gentleman.
No one is more ill-suited for killing than me. Fortune could turn every
which way, but I would never be able to go wild and let loose like you."

"Well, \emph{you} can turn right back around and never come back again. You're
just a useless drunkard even when you're around, anyway. You'd only hold
me up."

"Nothing to be angry about," Rikiga said lightly. "Ah, but I have to say
that was an impressive fight. I have a new regard for you now. If I were
a girl, I'd have fallen for you right there. Bravo, bravo."

Inukashi wrinkled his nose at Rikiga's applause.

"You falling for me, old man? What a horror story. You just gave me the
goosebumps. I just came out of deadly territory, alright? I'd appreciate
it if you could lay off that stuff, it's bad for my heart. The last
thing I wanna do is keel over from fright here."

Rikiga paid no attention to Inukashi's insults. He cupped his hand
around his ear and listened intently. The alarm stopped as abruptly as
it had started.

Inukashi also pricked his ears.

He could hear something like the distant rumble of the sea, or distant
thunder.

\emph{What is it? What is that sound?}

"Something's exploding inside the Correctional Facility," Rikiga said in
a queerly languid voice. "And that's not it... I can hear screaming in
there, too. It's in there. Yeah, I can hear it."

The door connecting the Correctional Facility to the waste processing
area was still open, which was why they could hear what was going on
inside. Two spaces which had always been firmly divided were now
connected.

"Hey, Inukashi. Is this a precursor? Is this the beginning?" His voice
quavered as it tapered off. Inukashi could not see his face, but he knew
that Rikiga was probably flushed with excitement. He did not even need
to look. \emph{My face is probably that colour, too}, Inukashi thought. \emph{I'm
excited. I'm restless.}

\emph{It's beginning. It's finally beginning. It's actually beginning.}

\emph{Nezumi, Shion, you guys actually did it. I don't know what the hell you
did, but you did it. You set the alarms off throughout the Correctional
Facility. Level 5. Is that the highest hazard level? If it was... hah,
this is getting interesting. This is gonna be fun.}

\emph{Those must be gun salutes in the distance.}

Inukashi had been licking his lips unwittingly.

\emph{Nezumi, that fraudulent bastard wasn't just a talker. He did what he
promised.}

"You think the Correctional Facility's going to come tumbling down?"
Rikiga murmured, his voice still trembling.

Suddenly, the lights flashed. They went out again, and the room sank
into darkness. The door closed, opened, tried to close again, but
stopped at about two-thirds of the way.

"What is it? Is it practicing a dance?" Rikiga cracked a lame joke.
Inukashi didn't even feel like laughing.

"Go dance along with it, old man." He was licking his lips again. \emph{This
isn't a dance. These are its last spasms. Its last struggles before its
life gives out. Just like that black dog, the Correctional Facility is
writhing in pain at the brink of death.}

\mybreak

"Don't tell me the whole building is going to collapse." The excitement
faded from Rikiga's voice, and uncertainty crept in.

"All's good and well if it collapses," Inukashi replied. "Once this
place becomes a mountain of rubble, I'll be the first to plant a
memorial tree." \emph{I'll plant one for Getsuyaku, my black dog, and the
countless people who were murdered here. A tree that'll grow huge and
bloom with pure white flowers.}

"You sounded so happy the other day wishing this place would come
falling down, old man," he added.

"That was a form of expression. I don't mind the Correctional Facility
falling down, but I have a bit of a problem with this building becoming
a pile of rubble."~

"Why?"

"Inukashi, think \emph{really} hard about it. If this building collapses
completely, the gold bullion underground will be buried along with it.
It's going to be a hell of a lot of work digging it back up."

Inukashi stared at Rikiga. The man's face was earnest.

"Old man... did you really believe that?"

"What?"

"The story about the gold bullion. Do you actually believe it's down
there?"

Rikiga's eyes wandered. His throat contracted.

"Inukashi, what are you joking about now? Of course it's there. My
information sources are trustworthy. There's no room for doubt."

"Okay, if you say so," Inukashi said indifferently. "Who was your source
again? Ann or Oon or something like that, right?"

"Sulu, the redheaded beauty. She heard it directly from a high official
of No. 6, in bed. No doubt about it. This tip isn't a dud."

"Is that how it goes?"

"Yeah. You might not know, since you're still a snot-nosed kid and all
you deal with are dogs. The thing about men is that they can't lie to
women after the deed. Wives are a different story, but men don't lie to
women they buy. They don't need to."

"That's why they accidentally spill the beans about confidential stuff
they'd never talk about."

"That's right. So you do understand."

"And can you trust this Sulu woman?"

"I sure can. I pressed her over and over about whether this story was
true. Sulu said she definitely heard it. She's sure of it, and so am I."

"Are you two together, old man?"

"None of your business, kid. Inappropriate subject matter for children.
As a well-meaning adult, I refuse to answer. No comment."

"Anything that comes out of your mouth is inappropriate, old man,"
Inukashi retorted. "Any well-meaning intentions of yours are probably
dissolved in alcohol by now. You're as inappropriate as adults get. I
would never want my baby around you."

"Back to the topic," Rikiga said impatiently. "How does my relationship
with Sulu have anything to do with what we're talking about?"

"To get straight to the point, I'll just say that between you and
Nezumi, Nezumi would get girls a lot more easily. Yeah, I think
ninety-nine out of a hundred... no, all hundred girls would rather sleep
with Nezumi than you. Of course. And I don't think Sulu is an
exception."

Rikiga's brows furrowed theatrically.

"Inukashi, what are you trying to say? Stop trying to beat around the
bush. Do me a favour and be clearer about it."

"Clearer, huh. Well, there's not much to say, anyway. Say I'm Sulu, and
I love to watch plays, and I get totally hooked onto this good-looking
actor called Eve. If he whispered into my ear with that sultry voice of
his, what would I do? I think I'd be pretty eager to feed false
information to a certain beer-bellied old man, no matter if he was my
ex-boyfriend or not. Just a thought," Inukashi said offhandedly.

Rikiga swallowed hard. He opened his mouth and started panting like a
dog in scorching heat.

"How―no, how―why would Eve ask Sulu to do that? Th―there's no plausible
reason―"

"To manipulate you, old man. Actually, maybe I was part of the plan,
too. He wanted to draw us in by hinting to us about some gold bullion.
It's the easiest and most effective way. Doesn't it sound like something
he'd think of? He's unbeatable when it comes to being wily. He's
astonishingly smart. I'm actually really impressed."

Rikiga stood still and speechless for a good while.

"Inukashi... when did you realize that?"

"When? I dunno. I think from the moment I heard you got the tip from a
pretty girl, Nezumi was in the back of my mind. Hah, I guess that means
I know a little bit more than you about Nezumi's true identity, huh? Not
much to brag about, though."

"If you knew, why did you still come? Why are you putting your life in
danger to do this?"

"Because there's gold bullion."

"Huh?"

"I actually don't know why I'm not curled up quietly in my nest right
now. I really don't know. It's just―something I thought would never
break is breaking. Something I thought would never change is gonna be
turned upside down. It's almost as amazing as a mountain of gold. And
God's not making that miracle―humans are. An airheaded boy and the fraud
of the century. Doesn't it give you a thrill? It gave me a thrill.
That's why I decided to act on my own. I wasn't gonna wait 'til someone
changed things. I'm gonna go ahead and do it. I wanna think that I have
a role in changing the world. Nezumi and Shion threw that opportunity
down right in front of me. They said, 'How long do you plan on curling
up there and pretending you don't notice?' and tossed the bait in front
of me. Bait that's bigger than gold."

"And you latched onto it knowing you were being tricked."

"I guess you can say that."

"I see... so you got in on it and tricked me, too. What a shameful day
for Almighty Mr. Rikiga. I've been strung along by a couple of brats.
I've grown old. I think it's really hitting home now that my life is
entering its retirement stage."

"Hey man, don't be so down about it. It's just my guess. I think it's
about ninety-percent right, though. There's always the possibility that
Sulu seriously had the hots for you, and she gave you the gift of juicy
information."

"Serious about me, huh... impossible." Rikiga gave a great sigh, and
slumped his shoulders. True to his word, he suddenly looked like he had
aged by many years. "So what do you plan to do now?" he looked up at
Inukashi, and exhaled again.

"Me? I'm gonna wait."

"For Eve and Shion?"

"Yeah. Nezumi told me to wait here. What other choice do I have?"

"Like a loyal dog waiting for its master."

"More like a cunning fox preying on a field mouse."

"Where are they coming back from? From that half-open door?"

"Who knows? I can't read that far into it. I don't think even Nezumi
would know. They're gambling for all or nothing―there's no way they can
foresee that far. Climaxes are best left in the dark, anyway. So what
are you gonna do, old man?"

Rikiga sighed yet another time. His back was hunched and his posture was
truly that of an old man, though Inukashi wasn't sure if he was doing it
on purpose.

"I'll wait," he replied. "Feeling like a loyal dog."

"Even if the gold bullion was a lie?" Inukashi was a little surprised.
He had been almost certain that Rikiga would beeline right out of this
room as soon as he found out that the gold bullion was an illusion.

\emph{Here, you don't know what's gonna happen next. There's no way of
guessing what kind of danger is coming, and when it'll come.}

\emph{Anyone with some smarts would get the hell outta here and go back home.
And Rikiga's not stupid. He might be prone to wandering off, blinded by
greed, but he's got the smarts it takes to survive. If not, he wouldn't
be able to hoard money in a place like the West Block.}

Rikiga only got involved in things that benefited him. Emotions and
sense of duty were not in his criteria for taking action―only potential
wealth was. This was Rikiga's philosophy of life, and Inukashi agreed
with it. That was why he was taken by surprise.

"Why're you gonna wait, old man?" he questioned sincerely. He was truly
curious.

"Because I can't move."

"Can't move? Doesn't look like you're hurt to me."

"I'm out of breath, and my heart is palpitating. My legs and back are
shot. I have no choice but to rest here. Besides, there's nothing to
prove that you're a hundred percent right. Sulu's tip might be a good
one after all."

"You're saying Mr. Gold Bullion is just sitting on his ass under our
feet."

"Yeah. I've come this far believing in it. There's no way I'm going to
leave with nothing. If it comes to this, I'll clean out the Correctional
Facility of anything that's worth money. And I'll get you and Eve to
help. For free. I'm not taking complaints."

Inukashi shrugged, and turned aside. He wasn't convinced that Rikiga was
telling the truth. What was he waiting for? What was he staying behind
for? Inukashi was sure even Rikiga himself did not know the answer. He
knew at least that it was probably not because of his palpitating heart,
his shortness of breath, or the gold bullion, which was nothing but an
illusion.

\emph{So whaddaya know, the old man actually believes that they're coming
back.} Inukashi meant to sneer, but ended up compressing his lips.

\emph{Changes are happening inside the Correctional Facility. It's almost
time. They're almost coming back.}

In the dark, Inukashi quietly balled his hand into a fist.

\mybreak

"It's delicious," Renka sighed. "I didn't know hot tea could taste so
nice."

"More sugar? They say sweet tea soothes you when you're tired." Karan
placed the pot of sugar in front of Renka. It was something she had
bought to celebrate the opening of her store. It was a small and cheap
pot, but it was Karan's favourite.

Renka pinched her tear ducts.

"Karan―thank you. I'm so glad you're here. Thank you."

"Oh, Renka, don't cry." Karan placed a hand on Renka's knee, and added
strength to her tone. "You have Lili. Don't cry. Be strong."

Lili, who had been looking up at her mother with concern, gripped the
cup in her hands tightly. Karan knew how harsh it was to reprimand Renka
and tell her to be strong when she was so overwhelmed with uncertainty
and exhaustion. "Be strong"; "smarten up"; "try your hardest"―at times,
words of encouragement from others hurt the soul much more brutally than
insults.

\emph{I'm at my limit. What am I supposed to try harder at?}

Karan herself had come close to screaming so. How ruthless, how shallow,
how crude they were―such superficial words of encouragement or reproach.
\emph{I know. But I have to say them.}

"Renka, you have Lili and the baby in your womb. You're a mother―you
have to be strong. You could cry any other time. But now isn't the time
to let your feelings go, is it? You have to pull yourself together."

Renka blinked, and swallowed her breath. Then, she straightened her
back.

"Yes, senpai."\footnote{Senpai means "upperclassman", which also functions as a respectful address to someone who is older and/or more experienced.}

"As long as you understand. Be careful next time."

"Of course."

Lili's gaze darted between her mother and Karan.

"Ma'am, you're Mommy's senpai?"

Renka gently drew her daughter's shoulder close. "Yes, she is. My senpai
in life. I'd want her to teach me a lot more things in the future."

"Ma'am, you must be really old."

Karan and Renka looked at each other, and burst out laughing almost
simultaneously.

"How mean of you, Lili," Karan exclaimed. "That's not true. Your mommy
and I are only―oh, we're eight years apart. I guess I am pretty old."

"Oh, Karan!" Renka laughed, and softly brushed the tears from her eyes.
"No, Karan, I really am thankful. Who knows what would have happened if
I was alone. I would probably be bawling from anxiety."

"You're not that weak," Karan said firmly. "You would have gotten your
strength back as a mother without me telling you to. And―you know,
Renka, this might seem like a temporary fix, but why don't we wait a
little longer for Getsuyaku-san? I feel like it's too soon to give up
hope."

Perhaps it was really just a temporary fix, something to disguise the
truth. But sometimes, you needed that something to ease your conscience,
something to mask the grim truth. Like a spoonful of sugar in a cup of
tea.

Renka put her cup down, and nodded slowly.

"Yes, yes... you're right. It's too soon to give up hope... absolutely
right. I'll wait for him a little longer. Maybe he'll come home
tomorrow."

"Right." Karan almost sighed. As long as Renka could not confirm
Getsuyaku's safety, she would have to keep waiting for her husband, and
Lili for her father.

It was too soon to lose hope. Yet hope without direction was a painful
thing.

Karan felt Renka clasp her hand. Renka's fingers were warm and soft.

"Karan, I won't be defeated. Even if by some chance, he
doesn't―Getsuyaku doesn't come home... the two of us will live―no, the
three of us will live together. I'm going to give birth to Getsuyaku's
child. I'll have his baby, and I'll raise it proper."

Strength shone in Renka's gaze. No hint of her previous tears remained.

"I have people like you who support me, so I'll be alright. I'll do what
I have to do. I'm a mother, after all."

"Renka!" Karan circled her arms around Renka's slender neck. "You're an
incredible mother. The best."

\emph{Look at us, Fate. Look how strong we can be. We won't be swallowed up.
We'll hold our ground and keep on living. O Fate, No. 6, we won't
submit; we won't be trampled on.}

"Karan, there's one other person I'm actually concerned about." Renka's
tone turned heavy.

"Yoming, isn't it?"

"Yes, it's my brother... I'm wondering what he's trying to do. I just
have this nagging feeling that―has he come here?"

"Yes, he has."

"What was he like?"

"Well, let me see... he seemed to be worked up."

They heard a scream. It was from outside; it came from the direction of
the front entrance. It was followed by what sounded like someone falling
down. Karan stood up and hastened to the door. She peered through the
blinds. A group of men were squatting under a street lamp. A chubby
woman was cradling one of the men in her arms. Karan remembered her. Her
name was Koka, and she ran a tavern. The young man in her arms looked
like her second son. He was a boisterous youth and a spitting image of
his mother, and was dedicated to his job at the tavern and helping his
mother out. Once in a while, he dropped by Karan's shop. Last time, he
had bought all the butter rolls on the shelf, laughing and saying it was
because his mother adored them. Karan did not know his real name, but
she remembered hearing him being called "Good Guy Appa".

Half of Appa's face was covered in blood, and he was slumped against his
mother's arm with his eyes closed. He did not stir. He did not seem to
be breathing.

Karan burst out into the street.

"Koka, what's the matter?"

"Oh, Karan! My son―they got my son."

"Who did it?"

One of the men swung his fist in the air. "The army. The army shot at us
with guns."

Karan felt a jolt as if she had been hit by lightning. She thought for a
minute that she had been the one to collapse noisily on the road. But in
reality, she had clasped her hands tightly together, willed her legs to
stand fast, and was holding her ground.

\emph{I knew it. I knew it. I knew it.}

"Army? What are you talking about? There's no such thing as an army!"
Koka wailed through her tears.

"There wasn't supposed to be, but there was. They weren't dressed like
Security Bureau officials. They were in military gear. And―and those
guys, they... they started firing at us..."

"Wait!" Karan said sharply. "Give me more details. You went to city
hall, didn't you?"

"Yeah. There was a summons through the Internet. We were on the move
because of it."

"A summons..."

"It was about this scary, mysterious illness. All these citizens are
dying, and yet the authorities aren't doing anything. And get this―the
mayor and all the big-shots have vaccinated themselves already, and plan
to abandon the rest of us. How could we let that pass? That's why we
stormed the Moondrop. You should have seen the amount of people there.
It looked like they came out from all over the city. Even Chronos
residents. We formed one huge mob and headed for the Moondrop. Our plan
was to get inside and see the mayor. That's what the message told us to
do. It told us to protect our own lives, and get our hands on that
vaccine. And that wasn't the only thing."

The man swallowed, and shook his fist even more furiously.

"We've been mistreated all this time. Our living conditions aren't even
half as good―no, even a tenth as good―as people living in Chronos. Even
though we're the same citizens. All this time we'd given up, thinking it
couldn't be helped. We all thought we had no choice but to bear with it.
But I've had enough of that. A horrible disease is going around right
now; I'm not gonna be left behind with no means of dealing with it."

Another man got to his feet. Blood soaked through the cloth wrapped
around his forehead.

"Yeah, that's right! Some consideration they must have for us!"

"Let me hear your story properly," Karan said. "So you all stormed the
Moondrop. There were a lot of people, and the army suddenly materialized
there. Is that what you're saying?"

"That's right. I was surprised, I tell ya. They even had tanks. It was a
weird kind of vehicle with a dull gold colour. I think they're called
tanks, at least. First time in my life I've seen them... but I'm pretty
sure. And in front of them, a huge row of armed soldiers were lined
up... lined up, saying, 'This is a warning. Vacate this area
immediately.' And they repeated it a couple times. 'This is a warning.
Vacate this area immediately.'"

Fear flashed in the man's eyes.

"We didn't leave, though, obviously. Some people tried to escape, but a
lot of others were screaming to keep pressing forward. So we just―I
mean, we never expected to be attacked. We're citizens. And like I said,
the people there weren't only from Lost Town or other districts; Chronos
residents were there as well. Elites, and their families. I never even
considered... that the city would use military force against its
people."

"But the city did," Karan said softly. All too easily, it had pulled the
trigger at its citizens.

\emph{Judgment for those who do not obey.}

\emph{Punishment for those who do not submit.}

No. 6 had exposed its true colours. It had flung off the costume it had
been donning so cleverly until now.

\emph{Death to those who are not meek.}

\emph{A penalty to those who rebel.}

"Appa was beside me when he was shot, right through the head. He didn't
even make a noise, he just fell... everyone fell into a panic, and
started trying to get out of there all at once. Oh, you wouldn't
believe. We took turns carrying Appa... and we ran out of there as fast
as we could. When we came to, we were sitting here..."

Koka lifted her face to the heavens and cried out.

"Oh, my son is going cold! Why! Why did this have to happen? My son!"
Her anguished cries did not ring out, but were sucked into the night
sky.

"Hey! It looks like people are gathering in front of the Moondrop
again." A man who had been staring at his mobile computer raise a bellow
like a battle cry. Everyone except Koka glanced back at him.

"Looks like there are two―no, three times as many people this time.
They're all coming out to get the vaccine. With this many people,
neither the Security Bureau nor the army would be able to do anything.
They can't just massacre all the citizens. Now is the time to ask the
mayor to come out of the Moondrop so we can hold a discussion."

"Everyone is gathering... is that true?"

"Yeah. The people are coming together again, and this time they're going
to use force to drag the mayor out. This is our first chance, and our
last. Now is the time. This is it." The man's voice cracked, and his
eyes roved over the computer screen.

"Yes, now."

"Let's head out one more time. We can't let Appa's death go to waste. If
we withdraw now, what would Appa have given up his life for?"

"It's not only Appa. My cousin and my mother are dead, too, from that
disease. We can't let the souls of the dead go unrequited."

"My younger sister died, too. She was gone so fast. Can you imagine how
angry I was? If only I had the vaccine, if only the city had dealt with
this faster, she wouldn't have had to die."

"Right, let's go."

"Yeah!"

The men rose at once. They looked at each other, then broke into a run.
Only the woman and the dead man remained.

"My son is dead. He's left on a journey alone without me," Koka
continued to lament. Her voice travelled across the ground and crawled
up Karan's feet.

\emph{I knew it. I knew it. I knew it. People have died. Even more people will
die in the near future.}

"Karan," Renka said in a trembling voice from behind. "What's going to
happen? The summons over the Internet... is that what my brother is
doing?"

Karan turned around and gripped Renka's shoulder.

"Renka, how do I get in contact with Yoming? Is there any way?"

Renka promptly shook her head. "No. I can't get through to his cell
phone or e-mail. I think he's refusing contact."

"I see..."

"Mommy? Ma'am?" Lili extended her hand straight out, and pointed down
the path. Shadowy figures appeared from alleyways everywhere, and were
forming a black mob.

"To city hall, to the Moondrop."

"We have to get the vaccine."

"They can't just watch us die."

"Yeah! Is that what they're expecting from us?"

"Come on, everyone. Get together!"

Yelling and footsteps clashed and mingled, and became a roar. Where in
the city had this energy lain dormant?

\emph{God, everyone in this damn city is so obedient and naive}, Yoming had
once muttered. They did not even have the energy to doubt orders from
higher-ups. \emph{They don't try to think. They just go with the path of least
resistance}, he had spat, his words full of frustration and contempt.

But now, the ground radiated with heat from the people, and was a step
away from exploding. Such enormous energy had lain hidden inside them
all along. No. 6 was not supposed to have any hint of unrest,
discontent, or anxiety. But this was what had been swirling in its
depths. What had flowed hidden deep underground was about to erupt. It
was like a miracle.

\emph{Maybe this world will really change. Maybe―but no. This isn't it. It's
different. Not right. A miracle wrapped in blood and anguish is no
miracle.}

Yoming had predicted No. 6's fall. He had cried for the Holy City's
destruction. But he had not spoken a single word about creation. He had
not expressed a specific vision for what kind of world he wanted to
realize here, what he aimed to create after No. 6 had ceased to exist.
Not a single word.

Karan put her hand to her heart, which was pounding frantically.

Koka's cry of mourning was swallowed up in the din, and shattered to
pieces. It reached no one's ears.

"Renka, go back inside the shop, please. Lock the door and stay in the
back room with Lili."

"How about you, ma'am?"

Karan crouched in front of Lili.

"I'm going to take Koka home. I'll be back soon. You take care of your
mother while I'm gone, alright?"

"Alright!"

She kissed Lili on the cheek. Then, for a moment, she closed her eyes. A
vision of Shion's smile graced the back of her eyelids. Karan drew a
breath of the nighttime air deep into her chest, and opened her eyes.