% !TeX spellcheck = en_US

\chapter{A treacherous joy}

\myepigraph{A deep, inexpressible joy filled her heart, a treacherous joy that
she sought to hide at any cost, one of those things of which one is
ashamed, although cherishing it in one's soul . . .}{Maupassant, "A Life"}

\lettrine[ante=``]{I}{s Daddy} home yet?'' Lili sighed. "Did Mommy get to see Daddy? Did she
get to say 'welcome back' to him? It's getting so dark. I wonder what
happened? Yuna's daddy and Ei's daddy are already home. They always come
home on the same bus. You know, sometimes me and Yuna and Ei go and meet
them there."

"I see. And Daddy's very happy, isn't he?"

"Yeah. Really. He picks me up, and kisses me on the cheek. But it's kind
of embarrassing. I don't need to get a kiss from Daddy to be happy. I'm
not a little girl, you know. But Daddy still thinks I'm a little girl.
That's why he kisses me in front of all those people. It's kind of a
problem."

Karan smiled at Lili's endearing attempt at sounding like an adult. Lili
sighed again. She cupped her chin in her hands, and let out a long huff.
It was an adult woman's gesture---was she imitating her mother, perhaps?
Usually, Karan would burst out laughing and tease Lili, calling her a
right young little lady, but today she couldn't quite bring herself to.
Her heart felt heavy, as if Lili had transmitted her melancholy to her.
Smiling was the best she could do.

"Ma'am."

"Yes, dear?"

"Daddy'll come home, right?"

"Of course."

Karan stopped in the middle of wiping a tray, and glanced at Lili.
Lili's favourite cheese muffin lay half-eaten on her little plate.

"Getsuyaku-san---your father---is probably very busy at work. I bet he
missed his usual bus. I'm sure he'll come home on the next one."

Karan gave a little sigh as well after finishing her sentence. These
words wouldn't even serve to make Lili feel better. Lili didn't want to
hear these banal words of encouragement.

She felt frustrated and ashamed that she could not even relieve a little
girl's woes.

Lili's eyes, always so lively and full of joy, were now clouded over.

Her father, who usually came home every day at the same time on the
minute, had not come home. She was worried sick.

Karan couldn't bring herself to laugh it off as an exaggerated concern.
Lili had sensed something wrong with Getsuyaku, and it was paining her
heart. Renka---Lili's mother and Getsuyaku's wife---had even gone to the bus
stop to pick him up despite her difficulty moving around. There must
have been something about Getsuyaku that caused his wife and daughter to
feel uncertain and unsettled. It was not only Getsuyaku, either.

This uncertainty---an intangible uncertainty---had by now covered all of
this city of No. 6.

One could call it a looming threat.

Several dozen citizens had already suffered at the hands of death---been
sacrificed. Karan wasn't sure if "sacrifice" was the appropriate term,
but she thought the eeriness and terror that the word invoked matched
perfectly well with the city's atmosphere; of that, she was most
certain. Karan herself was troubled, apart from her thoughts about
Shion, with an uncertainty that dug into her heart.

\emph{Is this really happening?}

\emph{People are dying left and right.}

Without warning, they would collapse and cease to breathe. Karan had yet
to see it for herself, but she had heard that the victims all lost their
hair and teeth, were covered in wrinkles, and died looking a hundred
years older. She had heard that even the most vibrant young man or
beautiful girl ended up in this grisly form. Without exception.

\emph{Why? What's the cause?}

\emph{A new virus? Poison gas? A plague?}

Speculation was rampant, and yet, not one person could give a definite
cause. No one could spot a common trait among all of the victims. Their
ages, body types, environments, workplaces and development histories
ranged widely, and barely overlapped.

Apart from the fact that they were exclusively No. 6 citizens.

One collapsed in the square in front of City Hall; one in the street;
one in his own kitchen. In all cases, the victims were alone. There were
no concentrated outbreaks of casualties in one spot. They all occurred
in pinpoint locations. Many were safe who had seen the victims die right
beside them. Any acquaintance in mid-conversation, any friend walking
beside you, any stranger walking past you, could become a casualty.
Shrieks and wailing voices burst into the air everywhere.

No one could predict who the next casualty was, or when and where it
would occur. That was fear itself. An insurmountable fear.

\emph{My sister collapsed just now. She wasn't even thirty. Now she's
transformed into an elderly woman.}

\emph{My neighbour just died. We were just having a normal conversation.
'What's gonna happen now?' 'This is scary, isn't it?', just stuff like
that. Then she suddenly started to double up in pain---}

\emph{What's going on here?}

\emph{This is a concern for everyone now.}

\emph{Maybe tomorrow I'll be next... no, maybe even in a minute...}

\emph{I might be the next sacrifice.}

\emph{What the hell is the mayor doing? Why doesn't he try to deal with this?}

\emph{Isn't he going to help us citizens?}

Fear became discontent toward the politicians who twiddled their thumbs
in the face of the situation. Discontent became criticism, which turned
into a simmering rage.

The mayor, through various media organizations, called for calm amongst
the citizens, and advised them to take careful action. But even as the
mayor's image flashed across the display, another casualty fell right in
front of it, another among the dozens today. He would convulse again and
again, then age rapidly. It was impossible to remain calm.

\emph{Give us medicine.}

\emph{Tend to the wounded.}

\emph{Give us the truth.}

The cries of the citizens echoed loudly in every corner of the streets.
And on top of this situation, Lili's father had not arrived home. Her
mother had gone out, and not returned.

The girl's tiny chest was probably full to bursting with uncertainty.
Perhaps she was desperately trying to keep herself from crying.~

Karan understood well the suffering and pain of being concerned but
unable to do anything about a family member. She had experienced the
frustration of only being able to wait. It was a pain that had soaked
deep into her bones.

"Lili." She stroked the girl's soft hair. "Have the rest of your
muffin."

"Ma'am..."

"You love your father, right, Lili?"

Lili looked up at Karan, and gave a huge nod.

"Yup. I looove him. I love Daddy lots and lots. I love Mommy, and the
baby in Mommy's stomach, too."

"Yes, and your father loves you too, very very much, right? He kisses
you on the cheek, and he says 'I love you, Lili' while he does, right?"

"Yeah. Daddy always says 'I love you' to me."

"Then everything will be fine. Your father will come straight home to
you, Lili. You know, in the end, people come home to the people they
love most."

Lili blinked. "Is that true, ma'am?"

"Yes. It's true. True as can be."

Lili's mouth relaxed. A smile spread across her face. She picked her
muffin up, and took a bite.

"It's delicious."

"There are still more left. Three, to be exact. One for your mother,
your father, and for you, Lili. You can take them home, if you like."

"Thank you, ma'am."

After finishing her muffin, Lili put her hands together and gave a loud
thanks for her meal.

"Ma'am."

"Yes, dear?"

"I love you, too."

"My, Lili, that's wonderful. Thank you."

"And Shion too... but not as much as Daddy, or Mommy, or you, ma'am."

"Hm?"

"Shion will come home too, right?"

"Lili..."

"People come home to people they love the best, right? So Shion has to
come home to your place, ma'am. Right? He'll come home, right?"

Lili seated herself deep in her chair, and dangled her feet over the
edge.

"When I got hurt once, Shion made it all better."

"Oh? He did?"

"Yeah. I was playing tag with Ei, and I fell down. I fell, and then Ei
came and fell down on top of me, like --- crash! --- and it really hurt.
Ei''s kind of fat. But she's really fast at running, you know. And she's
good at drawing pictures. I like drawing pictures, too. We draw pictures
together a lot."

"You're good friends, then?"

"Yeah. Really good friends. But we fight sometimes, too. Sometimes we
have fights that are so big, I think we're never gonna play again for
the rest of our lives."

"But if you can fight and make up again, that means you're truly good
friends. So you fell down, right, Lili? And Shion made it better?"

"Yeah. My leg was bleeding really bad. And it hurt a lot. I cried lots,
and Ei was crying, too. But then Shion passed by, and he picked me up
and took me to a tap and washed off the blood, and... oh, and then he
put some medicine on it. He said, 'it's stopped bleeding, so you can
stop crying now.' And then he patted my head. He wiped Ei's face for
her, too."

"And... when was this?"

Lili stopped swinging her feet, tilted her head a little, and looked at
Karan.

"Lemme see, ummm... a little before Shion went away. When he was still
going to work at the park. You know, ma'am, Shion is really nice. Mommy
said so, too. She said he's really kind, and handsome, and such a great
person. She said, 'When Shion comes home, you should ask if you could be
his bride'."

"Oh, Lili, you as Shion's bride? That's some happy news."

"But it's just that, well, Ei..."

"What about Ei?"

"Umm, she says she's in 'love at first sight' for Shion. I asked her,
'What's love at first sight mean?' and Ei said, 'It means you get
married, of course'. But if Ei and Shion get married, then I can't be
his bride. Mommy said I can't lose to Ei, but it's really hard."

"Oh, my." Karan laughed out loud. For even just a moment, she was able
to forget the uncertainty and melancholy forming a malignant lump in her
heart.

As far as Karan could remember, Lili had not mentioned Shion's name at
all since the day he had vanished from Karan's sight. Lili had probably
sensed that reflecting on memories of Shion would cause suffering for
Karan. Or perhaps she had been warned by Renka.

'Lili, from now on, I don't want you to talk about Shion in front of
Karan.'

'Why not?'

'Because she'll be sad.'

'Mommy, did Shion do something really bad? Is that why he got caught and
taken away? Everyone says so.'

'What do you think?'

'Me? I think... Shion wouldn't do anything bad. He's so nice. He would
never do anything like that. Ever.'

'And you're right. See, you do know. I'm impressed with you, Lili.
Whatever happened must have been some kind of mistake. Shion is such a
wonderful boy. You wouldn't find anyone nicer. He's kind, handsome, and
just such a great person. I know, Lili, when Shion comes back, why don't
you ask if you can be his bride? Don't lose against Ei.'

Perhaps mother and daughter had had that kind of conversation, and
grinned at each other.

Karan had been surrounded by caring people all along.

Through days of frantic frustration and anguish, she had always thought
she was fighting alone. But it was not so. People around her, people
right by her side, had been quietly expressing their concern all along.

\emph{All this time I was being supported by such a little girl. And---}

\memo[0.45\textwidth]{8}

And by Nezumi's letter.

There were many pillars. The hearts of others held her aloft.

"Lili, thank you." Karan gently embraced the young girl.

The emergency buzzer went off.

A part of the wall turned into a screen, and the face of a young woman
appeared. She was a newscaster directly affiliated with the Information
Bureau.

"This is an urgent broadcast. As of this moment, the authorities have
announced a state of emergency. Citizens are advised to return home
immediately. All subsequent outings of any kind by citizens will hereby
be prohibited. There are no exceptions. If you do not comply, you will
be arrested and taken into custody. I repeat. We are entering a state of
emergency. Citizens are advised to..."

The newscaster had been reading rapidly through her papers, her eyes
cast down, when suddenly she snapped them open wide. She stood up, and
clawed at her throat.

"Help me! No!!" Her shriek rang out.

Karan reflexively put her arms around Lili.

"Ma'am, what's happening to her?"

"No! Don't look!"

The caster's flaxen hair turned white before their eyes. Dark spots
appeared on her cheeks, and spread rapidly.

"Help... me..." Her fingers curled as if trying to grasp something in
the air, and she collapsed behind the desk.

The broadcast cut off abruptly after that.

A state of emergency---it was nothing so tame.

This was an abnormality. A situation far beyond the bounds of common
understanding. It was twisting and rearing before them.

She felt faint.

\emph{No, it's not me. No. 6---this city---is the one that's creaking from the
stress. It's shrieking, just like that newscaster.}

Confusion. Disaster. Danger. Suffering. And, fear. Plagues that should
have never existed within No. 6 were sprouting furiously.

She heard laughter.

Somewhere far, somewhere far in the distance, she could hear laughter.

\emph{Who? Who's laughing? Whose voice is it?}

Brittle, dead leaves fluttered past her window.

One, two, three...

A wind was blowing. A strong southern wind was blowing against her. It
usually unravelled the rigid cold of winter, and brought with it the
premonition of spring. The southern wind which usually made her heart
feel so lively was carrying that voice to her ears.

"Ma'am, I'm scared." Lili clung to her. "Someone's laughing in the sky."

"Lili, you can... hear it too?"

"I don't know. I don't know, but I'm scared."

Lili began to cry. "I'm scared!" she sobbed.

"It's alright," Karan soothed. "It's alright, Lili. I'll protect you. So
don't be afraid."

\emph{You supported me all this time. You cared for me, you were concerned for
me. So this time, it's my turn to support you. I won't let people snatch
you away, so easily like they did Shion and Safu. I'll protect you, you
just watch.}

Karan bit her lip, embraced Lili still more tightly, and turned to face
the wind that blew outside her window.

\emph{I will protect you to the end.}

\mybreak

\emph{How could this be happening?}

The man was confused. The cause was beyond his grasp. This was the first
time something like this had occurred.

"Why have you let this happen?" he yelled, Fennec, the mayor of No. 6.
"Why have \emph{they} begun to act on their own? I thought you said you were
able to control them perfectly."

\emph{What noise}, the other man thought. \emph{What a noisy lout.} He had always
thought of the other man as a cowardly, yapping dog who knew how to do
nothing else. The years evidently had not changed his character.

"Soon, it will awaken. Then, everything will settle down."

"Really? You \emph{are} telling the truth?"

"Really, Fennec. These are only small precursors to the main event.
Miniscule disturbances."

"Miniscule disturbances---this, you say? The city is in a panic, for
goodness' sake."

"Then, announce a state of emergency."

"I've announced it ," the mayor said shortly. "But if we have any more
deaths, the Security Bureau alone won't be enough to suppress the chaos
among the citizens."

"Mobilize the army."

The mayor froze.

"The army?"

"Yes. Even if there is a possibility of a riot, there would be no
problem with the army there. No cause for concern at all."

"You're telling me to point weapons at my own citizens? These citizens
of No. 6?"

"That's what an army is there for. To neutralize anything that rebels
against No. 6, whether it be from the inside or the outside."

"But---"

"Fennec," the man interrupted. "You are the one to make the decision.
You are the King, after all. It's not something I can intrude into. But
do not forget. You are the sole person who dominates everything on this
land. Rebelling against you is the same as betraying No. 6."

The mayor remained silent for a while, and then gave a resolute nod.

"You're right, in fact. Every word."

"It may have been out of place for me to say this---"

"No, I don't mind. I forgive you."

\emph{Forgive? Forgive me?} The man sneered inwardly.

"I will order the army to mobilize into battle formation and await
further instructions."

"That would be best. It is a grand opportunity to show your foolish
people the extent of your power."

The mayor swept out of the room, his gait stormy. He seemed to be in a
temper.

The man sneered inwardly again, and closed his eyes.

\emph{Soon, it will awaken. And when it does---}

\myspace

Getsuyaku shut off the water flow.

Today, he was going to finish up work early so he could go home.

At the end of every shift, he took a shower and drank a cold glass of
water. It seemed almost too mundane to call it his high point of the
day, but he nevertheless couldn't deny that taking a shower put him into
a good mood.

\emph{Well, that's all the work that needs to be done today. I can go home
now.}

A smile tugged at his lips every time the thought crossed his mind. He
could see the smiles of his wife and daughter right before his eyes. His
daughter was not of his blood; his wife had brought her from a previous
relationship. There were times when he felt troubled at whether they
could still become father and daughter, even though they weren't
related. Now, he found it funny that he had even bothered to worry.
Blood relations didn't matter. It had nothing to do with how one felt
love. He cared for his daughter so strongly, he could most certainly say
so.

Small and lovable Lili.

Every time he kissed her on the cheek, she would smile sheepishly. In a
year, she might even be rejecting him with a cool "Daddy, don't." But
her gradual blossoming into adulthood made her endearing all the more.
\emph{If I could, I wish she would let me kiss her forever---but that's probably
not going to happen. But what about today? I wonder if she's come to
pick me up at the bus stop. If she has, I would be so happy. Lili would
come dashing up as soon as I get off the bus. She'd say, 'Welcome home,
Daddy,' and she'd give me a hug. I would pick her up, and give her a
kiss on the cheek.}

It was his moment of complete bliss.

And he could experience this because Lili, his daughter, was there for
him. His second daughter, too, was almost on her way. He had been told
at the hospital sometime before that the baby was going to be a girl. \emph{My
second daughter, and Lili's little sister. One more member in the
family.}

Getsuyaku changed out of his clothes, and smoothed his hair with a hasty
hand.

He had only to think about his wife and daughter. He would not allow his
thoughts to wander and dwell on what he did today, or anything of that
sort.

\emph{Nothing happened today. I didn't do anything. I don't know anything.}

\emph{And that's exactly how it's going to be.}

Tomorrow, Inukashi would give him the rest of his payment. He knew
Inukashi wasn't lying. He was wily, thorough, and miserly, but he kept
his promises. In that sense, Inukashi was someone he could trust. If he
hadn't been such a person, there was no way Getsuyaku would have
co-operated in smuggling, even if it was just garbage or leftover food.

The payment this time around, however, was off the charts compared to
the usual.

Getsuyaku counted on his fingers, curling each one, starting from his
thumb.

\emph{Gold... three gold coins. It's quite a payment. Add that to the previous
one, and that makes six gold coins. This is enough money to let me live
like I'm on vacation for a good while. Of course, that's not what I'm
going to spend it on. I'm going to keep it for Lili, and for the baby
that's on its way. Renka would be happy for me. But---last time I handed
her the gold, she looked more worried than happy. She went pale, and
asked me, 'Where on earth did you get all this money?'. I managed to
scrape together an excuse, but that was a close call. I made Renka worry
more than she should. This time, I have to make it good. I have to come
up with an excuse that'll satisfy her. Maybe something about special
compensation. I hope I can pull off the lie.}

Six gold coins. A payment off the charts.

After curling all his fingers in, he slowly raised his pinky.

\emph{I want to buy Lili some spring clothes. And Renka, too. Renka is so
beautiful, but since we don't have the means to be fashionable, she
always dresses frugally, and it makes her look older. She would look so
stunning in a brightly-coloured dress, in pink, or blue. And Karan-san.
She takes care of Lili all the time. And she's so good to her... I have
to give her something to thank her. Hmm, what should I get?}

His dreary mood began to clear. He felt excited. He could see himself
shopping with Lili, taking her by the hand. He could see Lili turn
around to grin at him. Renka was also smiling.

\emph{Oh, I couldn't be happier.}

He felt it from the bottom of his heart.

He drained his glass of water.

\emph{Alright, let's go home.}

The emergency alarm went off. The lamp flashed.

"What?"

His heart contracted. He could feel the blood receding from his face.

The door connected to the Correctional Facility was beginning to open.
Getsuyaku had passed through the same door only moments before, entered
the Correctional Facility, done his cleaning duties, and returned to
this small room. He had resolved to finish work early that day, and had
taken a shower. He had drank a glass of water.

That was it. That was it.

He shrank bank.

\emph{That's all I've done. I only did my job, did it properly, as usual, and
tried to go home.}

'Make a good getaway.'

Hadn't a young man who passed him on the stairs said that? Getsuyaku was
almost certain. The youth had a certain severity to him despite his age,
and yet could manage to smile in a very alluring way. \emph{Make a good
getaway.} Was that a warning? Should he have obeyed those words and made
his escape as swiftly as he could? But he had been afraid of being in a
panic. He had been afraid that he would draw suspicion. \emph{If I run, that's
like admitting I did something wrong. I didn't want people to be
suspicious. I still have to come in tomorrow, and the next day. Once
they're suspicious of me... I---I don't want to lose my job. I was still
planning on coming into work tomorrow. That's why I ignored him. I
foolishly pretended that I didn't hear.}

\emph{Make a good getaway.}

\emph{Oh---how wrong I was. I should have listened to that man. I should have
escaped.}

The door opened.

\emph{I should have escaped.}

Two Security Bureau officials stood there, guns aimed and ready to fire.

"Getsuyaku, is it?"

His legs were shaking. His hands were shaking. His whole body was
shaking.

\emph{No, don't shake. I'll draw even more suspicion. Pretend you don't know.
Pretend you don't know, and---you haven't done anything.}

"Answer me."

"---Yes, it is."

"We are escorting you. You are to obey."

\mybreak

"E-Escorting me... where?"

There was no answer. The two muscular Bureau officials, alike in height
and shoulder width, remained silent with their guns pointed at
Getsuyaku.

Nothing spoke louder than their lack of words.

Destruction was approaching. Getsuyaku understood that he was in no
position to escape. But he couldn't relent.

\emph{No. No.}

"Wh---why am I... what are you saying I've done...?"~

This time, there was a response.

"You exhibited suspicious behaviour. At the Mannequin."

"S-Suspicious behaviour? That must be some kind of mistake,"~

Getsuyaku stammered. "I... I was just cleaning---it was the robot's fault.
I was summoned because the floor was dirty, and---and so to clean it up,
I---"

"You were responsible for the maintenance of the robot, were you not?"

The muzzle of the gun moved up and down as if to cut off Getsuyaku's
desperate words.

"And you performed it a whole week earlier than was planned."

"That was because---um, they didn't seem to be in very great shape, and...
it happens often, actually, and..."

The officials said nothing more. Their lips were sealed, and no emotion
could be read from their eyes. The two looked like robots themselves.

Only destruction awaited Getsuyaku if he let himself be escorted by
these robots. An inescapable destruction.

\emph{No. No. No.}

\emph{I'm going to go home. I'm going to return to Lili and Renka.}

He threw down the glass in his hand, and dashed outside.

\emph{I have to run. I have to run. I have to get away.}

\emph{If I run straight down this road, and get through the gate, I'll be in
Lost Town. Once I get on the bus, I'll arrive at the usual bus stop in
ten minutes. Lili would probably be there to pick me up.}

"Welcome home, Daddy."

"Feels good to be back, Lili."

"Mommy's waiting. Today, we're having your favourite --- stew. We have
bread that Auntie Karan baked, too."

"That sounds terrific. I'm starting to get hungry already. Oh yeah,
Lili, Daddy's going to buy you some brand new clothes soon."

"Really?"

"Really. Let's go shopping on my next break, okay?"

"Yay! Thanks, Daddy."

"Ha ha ha. Alright, let's go home. Mommy's waiting, right?"

A white-hot impact hit him in the chest.

Blood and bits of flesh splattered before his eyes.

\emph{What is it?}

The world teetered off-balance. Darkness closed in on his vision.

\emph{No, no, no. I'm supposed to go home. I'm gonna go home. I'm gonna...}

"Daddy, welcome home."

"It feels great to be back, Lili."

Getsuyaku crumpled as he was shot through the chest.

\myspace

Inukashi averted his eyes, and clenched his hand into a fist.

\emph{What the hell.}

"Hey, that guy just got taken down," growled Rikiga.

They were crouched behind some shrubs that dotted the surrounding area
of the Correctional Facility. The Cleaning Management Room right before
their eyes was the only department that connected the Correctional
Facility directly with the West Block without a set of gates to pass
through. The door that led into the Facility could only be accessed from
the inside, however, so it was not possible to access the Facility from
the side of the Cleaning Management Room. The doors were said to be made
of a special alloy that even a small missile wouldn't be able to damage.
Infiltration was impossible as long as these doors were closed. In that
sense, Getsuyaku's workplace was more similar to the West Block, insofar
as it was completely cut off from No. 6.

For Inukashi, it was no problem if they were cut off. The Facility was
one place he didn't want to step into if he could help it. He had no
interest in it whatsoever, and he would have liked it to stay that way
for the rest of his life.

He was more drawn to the grade and quantity of leftover food and
clothing that Getsuyaku picked out from the waste collection depot
adjacent to the Cleaning Management Room. These were more important to
him than the Facility itself.

He and Getsuyaku had known each other for a while now. It had probably
been at least three years. They were not particularly close or friendly
with each other. They had just used each other as business partners.

Getsuyaku was straight-laced and cowardly, with a decent smattering of
both good morals and greed. A typical man you'd find anywhere. He was
just one of countless many that one could find.

But he did care about his family. Inukashi remembered him saying many
times that he valued them more than anything else in the world. He had
looked truly happy as he smiled and talked about his little daughter,
who was on her way. Inukashi had once asked him, 'Isn't it a pain in the
ass to take care of another human? You can't take care of 'em like
dogs.' Getsuyaku had lapsed into silence, his mouth half-open. He had
looked astonished. Inukashi remembered the look of pity that then
crossed Getsuyaku's face as he closed his mouth.

At that time, he had not understood the reason behind Getsuyaku's
expression. Now, Inukashi felt like he had a better idea. It was thanks
to Shionn---no, it was all his fault.

Inukashi felt like he could understand a little---just a tiny little---of
the kind of love Getsuyaku felt for another tiny soul. And for the
family that awaited its father, its husband, Getsuyaku was definitely
not one of countless many. He was the one and only irreplaceable
existence. Inukashi understood that too.

"I see. So they won't stop at West Block residents. They'll even kill
their own people, too, huh," Rikiga said, wiping the sweat from his
brow. His body was tense despite his airy tone.

"He lived in Lost Town," Inukashi said. "He was probably
practically---trash for those people." Inukashi put up a front of
unruffled calm, but he was also nervous and tense. The nape of his neck
was so taut, it was painful.

\emph{To think they'd actually kill him.}

He hadn't even dreamed that they would kill Getsuyaku. He had, however,
expected the man to blow his cover. There were plenty of possible
instances when Getsuyaku might slip up and give something away. In a
worst-case scenario, he would have been taken into custody and
imprisoned.

But if the Correctional Facility itself would eventually collapse, as
Nezumi said, then it was only a matter of time before Getsuyaku could
get free. They would take advantage of the confusion and rescue him from
his cell.

"God, the amount of trouble I had to go through because I fell for your
smooth talk. That teaches you not to take a dogkeeper's word seriously.
Damnit, I fell right into your trap."

Inukashi wouldn't mind bearing with a complaint or two from the man. In
fact, he wouldn't even mind bowing his head and apologizing. Then, he
would humbly and graciously hand over the promised gold. Three coins,
plus another, "for your trouble," he would say. That was sure to restore
Getsuyaku's spirits.

The demolition of the Correctional Facility meant the end of his
business with Getsuyaku.

\emph{Thanks for all the years of business.}

\emph{No problem. And I think I've had enough risky jobs to last me a
lifetime.}

They'd shake hands, perhaps, and then part ways. In Inukashi's mind,
that had been his ideal way to say good-bye. But Getsuyaku lay face down
on the arid ground without a single twitch. Only the wind blew over his
body.

\emph{To think he'd get killed.}

\emph{To think he'd get killed so easily, so unceremoniously. Gestuyaku is a
citizen. He's someone who lived inside the walls. He may have been in
the dregs of No. 6, but he was still registered as a proper citizen.
He's different from us. They wouldn't murder him pitilessly. They wouldn't dare.}

He had believed so wrongly all this time.

\emph{I was hopelessly naive. I knew in my head how cold, how brutal No. 6
could be towards people who betrayed it, refused to obey it, struggled
against it... I thought I knew, but I didn't know anything. I was naive.
I should have told him to get his ass out of there as soon as he pressed
the button. Tell him to get out, and...}

He felt like someone had grabbed his hair and yanked it up. His scalp
hurt from how taut it was. A scream threatened to come up through his
throat.

\emph{I remember now. It said so in Nezumi's letter.}

\emph{Order any collaborators to escape immediately.}

He remembered clearly that single line. Nezumi had predicted this
ruthlessness, this brutality. \emph{But I overlooked it. I was too caught up
in trying to lure Getsuyaku in to devote any thought to the safety of
the people I'd be getting help from. It hadn't even crossed my mind
until now. Until now, when it was too late.}

\emph{I was careless. A careless, fucking naive moron.}

He chewed his lip.

But regretting it now wouldn't undo what he had done.

"Terrible." Rikiga wiped the sweat off his brow again.

Two men who looked like Security Bureau officials were stepping on
Getsuyaku's body with the tips of their boots. They were looking at each
other and nodding. They each took ahold of one of Getsuyaku's legs and
began to drag the body along. The blood flowing from the corpse left red
streaks on the dry ground.

"Are they really human?" Rikiga's voice turned raspy.

The dogs growled lowly beside Inukashi.

\emph{You're sure right about that. These dogs are a hundred times more
decent. They've got hearts worth a hundred of those men.}

Inukashi gave a quick snap of his fingers. The dogs all sprang to their
feet at once. Rikiga blinked.

"Hey, wait. What're you planning to do?"

"Make them tear those guys' throats apart, obviously. I'm gonna avenge
Getsuyaku."

"Are you stupid?" Rikiga said in disbelief. "Even your dogs couldn't
stand a chance against armed Security Bureau guys. If they find out
where we're hiding, we'll be shot to death, too. Do you think people who
can shoot up their own citizens are going to cut us any slack?"

"But if I don't---"

"If he was alive, you could still flail around and do your thing. But
he's dead. He's gone completely. He's not going to feel anything. He
doesn't feel any anger or suffering now. He's as good as that piece of
dirt. Tell me, should we throw our lives away for a piece of dirt? I
don't know about you, but I'm definitely excusing myself from this one."

Rikiga's bloodshot eyes hardened.

"We can't die yet. We still have an important job to do: save Shion. We
can't do it if we end up as ghosts. That's the most important thing, and
don't you forget that, Inukashi."

"---Fine."

What Rikiga was saying was true. They still had a job to do. And it was
a job that couldn't be done if they weren't alive.

He snapped his fingers again, this time more slowly. The dogs lay back
down on the ground. Rikiga exhaled a long breath.

"Really, I wish you wouldn't act on every emotional whim. This is why
you can't trust young people."

"Old man."

"What?"

"So you \emph{do} say some decent things, once every ten years or so, anyway.
You weren't just a dead weight after all. I see you in a new light now."

"Say what you will."

"And while I'm saying what I will, lemme remind you that we're splitting
the gold even. Don't you forget \emph{that}."

"I know, I know. Even half of the treasure is enough for me to live a
freewheeling life. But if that guy's gotten himself killed, how are we
going to get into the Cleaning Management Room?"

"I have the key." Inukashi held a magnetic card key between his fingers
and thrust it under Rikiga's nose.

"You had a key?"

"Yeah, a spare. In all of the Correctional Facility, the Cleaning
Management Room is the only one that still uses a simple magnetic card
key. There aren't any signsof-life sensors, security systems, object
sensors, or surveillance cameras in there. It's a paradise if you wanna
hide out."

"Well, I guess they wouldn't have a reason to spend money to watch a
place that only collects garbage. So you nicked that key from the poor
guy's pockets, huh?"

"Not his pockets. I took it out of Getsuyaku's small desk, where he eats
his lunch. I borrowed it from his drawer."

\emph{It was an old, worn desk that looked like it'd been picked out of the
garbage. Getsuyaku used to eat his lunch there by himself. Once, I
remember him giving me this small, sweet pastry called a muffin. It was
delicious. I thought my tongue was gonna melt, it was so happy. He said
he'd bought it from a local bakery.}

"I guess you don't have to return it to him now," Rikiga muttered, with
an unusually heavy tone.

"You're right. I don't have to give it back. So instead, I'm gonna make
as much use of it as I can."

\emph{When I see the Correctional Facility crumble, I'll dedicate the scene to
you, Getsuyaku. I'll make sure to dedicate something that's worth the
blood you spilled. I know it probably won't be enough to make up for my
carelessness, but it'll be the best sending-off to heaven that I'll be
able to give you.}

Inukashi pressed a hand to his chest. Nezumi's letter was there under
his clothes.

\emph{This time, I won't mess up. I won't overlook anything. I won't let my
guard down.}

\emph{Their lives are depending on it---Shion and Nezumi's lives. I can't fail
them again.}

\emph{Cheep-cheep-cheep.}

He hadn't noticed the two mice sitting at his feet. They scurried up his
arm and onto his shoulder. Hamlet and Cravat. \emph{I think those were their
names.} Two small animals with intellect and their own will.

"You're here," he said to them. "Well, old man, it looks like all the
supporting actors are here."

"Indeed. Now, all we have to do is get the stage perfectly ready, and
then wait for the main actors to make their entrance."

"Yup. The actors of the century. We need a flashy fanfare to welcome
them."

A one-act play, but a massive one nonetheless.

Hope or despair? Success or failure? Heaven or Hell? Life, or death? The
curtains had already risen for this stage without a script.

\emph{It's our turn now. We're waiting for ya, Nezumi.}

\emph{Cheep-cheep, cheep cheep cheep.}

Perched on Inukashi's shoulder, the two mice raised their heads and
squeaked together, as if to call out to someone.

\myspace

"It's stopped."

Nezumi tilted his head slightly in perplexity at Shion's words.

"What're you talking about? It hasn't stopped yet."

The elevator was still ascending. It continued to glide smoothly up.
Shion lightly placed his finger on the edge of his eye.

"No, the tears. Look, they've stopped."

Nezumi's cheeks suddenly emitted a furious glow.

"Idiot. This isn't the time to be making lame observations. If you have
time to be making fun of me, concentrate on the damn door. Once it
opens, we don't know what's gonna hit us."

"I wasn't making fun of you. I just saw that they stopped---"

"Shut up. Just---shut up."

Nezumi turned obstinately aside. His gesture was that of a sullen child.

Shion found it humorous.

Cool, ironic, stronger and more beautiful than anyone else---that was the
kind of person Nezumi had always been, and that never changed. But
behind it all, even he had a childish, emotional side like this. He
still had some immaturity left in him to feel agitated when he was
unable to control his emotions.

Shion had seen Nezumi's tears for the first time. When he saw the boy
choking on the unbearable tumult of his emotions, there was only one
emotion that welled up inside Shion, and it was love. It was neither
friendship nor adoration. Neither romance nor awe. Just love.

He felt an uncontrollable pull of love for the boy's vulnerable tears.
He wanted to protect him with his life.

The howling wind and the sound of rain echoed in his ears.

It was the sound of that storm. The emotions he had felt on that stormy
night when he met Nezumi were revived in himself. And like he had been
so many years ago, he had been stirred to action by these feelings.

\emph{I want to protect him with my life.}

Of course, this was only Shion's self-absorbed and one-sided sentiment.
Nezumi wasn't fragile to the point of needing Shion's protection. He
would learn this the hard way, much later. Shion had been the one being
protected. It had always been this way.

The sounds of the storm showed no signs of dying down. It still roared
vividly.

Shion thought of the boy who had appeared before him that night, his
shoulder drenched with blood much like he was now, except the boy had
been so slender and delicate then. He was so small, and wounded so badly
that he could barely remain standing. But despite that, his eyes had
glowed brilliantly, full of life, and carried no shadow at all. The boy
had neither clung to him, nor begged for his help. On the contrary, he
had coolly scrutinized Shion.

\emph{What kind of person are you?}

Even now, the question still remained sitting before Shion's eyes. He
had not given an answer yet.

\emph{What kind of person am I?}

\emph{My reason, my passion, my folly, my greed, my justice---what shape do they
take?}

He spread his fingers. There was blood caked on them. Was it his own, or
that man's? His palm and five fingers, dirtied in muddy red.

\emph{Could I stand and look my own self in the eye?}

"I look horrible," Nezumi sighed. He glanced in the mirror, and furrowed
his brow in discontent. "My hair is a mess, my face is dirty---it doesn't
get worse than this. Even the witches from \emph{Macbeth} wouldn't want to come
near me. I can imagine the look of horror on my manager's face if he
were to see me like this."

"You look good enough to me."

"Shion, you don't have to try to make me feel better. Geez, look at me,
my beautiful face is ruined."

"I didn't realize you were so narcissistic."

"I just have an accurate idea of myself. What's beautiful is beautiful.
Unsightly things are unsightly."

"Are you just talking about looks?"

\emph{Or are you talking about how people are deep down, too? Can your gaze
penetrate even the beauty and ugliness that lies within them?}

\emph{My reason, my passion, my folly...}

Nezumi recited a segment from Macbeth, the witches' line.

"Fair is foul, and foul is fair. Hover through the fog and filthy air."

The elevator stopped. Shion stared at the door.

He was being called---he felt strongly that Safu was calling him.

\emph{Shion.}

The doors glided open noiselessly.

"Don't go running out just yet. Take your precautions." Nezumi's arm
held Shion back as he exited first. He was dragging his foot, though
only slightly. His bleeding had stopped, but it was probably quite a
serious wound. If he moved too much, it would probably begin to bleed
again. Both Nezumi and Shion were nearing their physical limit.

\emph{Shion.}

\emph{Safu. Are you alright? Would I get to see you? I've come to get you so
we can escape together. Lead us on.}

\emph{Shion...}

A hallway stretched before them, black and glossy. The side where the
elevator was located was just a plain wall. On the opposite side, there
were three evenly-spaced doors. It was deserted. The elevator closed
silently behind Shion.

"Which door is it?" Nezumi turned around to ask. "Right, left, or
middle? Maybe they've got tigers or wolves ready to spring at us if we
open the wrong one."

"No---it's none of these."

Shion walked straight down the hallway. It was neither right, left, nor
middle.

Suddenly, one of the doors opened, and a woman clad in a lab coat
appeared.

"What---" Her electronic tablet slid from her hand. "You---how did you
outsiders get in---?"

They continued past the woman as she stood in stunned silence.

"Wait---where are you---"

"M'lady." Nezumi picked the tablet up, and placed it back in the woman's
hand. "I'm terribly sorry for startling you. We're not suspicious
people---okay, maybe we are---but you don't need to worry. We have no
intentions of harming you. So hush now, please."

Shion stopped where the hall reached a dead end.

\emph{Safu.}

The wall split smoothly in two.

The woman screamed. "How---how did that door open?"

Nezumi whistled. "It's like the caves you see in the \emph{Arabian Nights}.
Shion, what kind of incantation did you use?"

"No---how could it---" The woman squatted to the ground. She was fainting
from shock from the looks of it, for her face was whiter than paper.

There was another door beyond: a crimson door.

"Garish." Nezumi clicked his tongue, and drew up beside Shion.~

"Will it open?"

"Probably." Shion placed a hand on the door. Nezumi trembled. He closed
his eyes, and pursed his lips.

"Nezumi---what's wrong?"

"I heard... a voice."

"You can hear Safu's voice, too?"

"No. This... isn't a human voice. This... whose voice is this?"

"What's it saying?"

"...Finally, you are here." Nezumi made a fist over his chest. He let
out a long breath. "Finally, you are here. I have been waiting for you."

\emph{Finally, you are here. I have been waiting for you.}

\myspace

\emph{I've been called here by Safu. Who's calling you? Who's waiting for you
beyond this door?}

Shion felt a vibration against his palm. The crimson door opened.

"Gh..." Both Shion and Nezumi made a strangled noise. Their voices stuck
in their throats.

"What---"

There were several transparent pillars filled with clear liquid. These
columns, thick enough for a small child to barely get his arms around,
stood in a neat line.

"Brains." Nezumi swallowed hard.

Brains.

In each column floated a brain. Several clear tubes connected the brain
to the lower part of the column. These tubes glowed bluish-white from
time to time.

It was a bizarre scene. Shion hadn't imagined in the faintest that he
would see something like this. He couldn't have imagined it.

The crimson door closed. Just before it shut completely, he thought he
heard the sound of the wind. Was it an auditory hallucination? It
probably was. But what he was seeing now with his own eyes was no
illusion. It was reality. This scene was concrete. It existed.

His legs quaked. His heart quailed.

Nezumi's hand slid under his arm.

\emph{Oh, here I am again, being supported by you.}

They proceeded slowly through the columns.

\emph{How far do we go? Is there an end?}

"Shion." He heard himself being called. He looked up.

Safu stood there. She was wearing that sweater.

The black sweater which had been hand-knitted by her grandmother. There
were dark pink stripes on the mouths of the sleeves and across the
chest.

"Safu!"

There she was.

He could hear the wind.

Shion stretched his hands straight out before him.