% !TeX spellcheck = en_US

\chapter{Are you sad?}

\myepigraph{"Are you sad?"\\
	"Yes, I am."\\
	"You're not really, are you?"\\
	"No, I'm not."}{Hoshi Shin'ichi, "Bokko-chan", \emph{Short Short 1001}}

\lettrine{T}{wo conveyer belts} were running. Humans lay on them. Someone had put
them there.

They were not alive. He could tell clearly even from where he stood
behind the glass.

Bodies. Several dozen, maybe even a hundred, were being carried down. A
half-moon shaped device of enormous size was operating beyond.

The bodies were sucked in one after another into two square openings. It
seemed like the glass was of a special kind, for he could hear nothing
of what was occurring on the other side.

Bodies slipped by continuously in this silent scene.

There were men. Women. Children and adults. Clothed and naked. Their
statures, ages, and sexes ranged broadly.

"Why are their heads... all..." The words stuck in his throat. They
became a lump that blocked his airway.

The top half of the head had been cut away from every corpse. A
translucent plastic dome had been placed on top instead. Men and women,
children and adults―all had been fitted with bowl-shaped plastic from
the forehead up.

"―Samples," Shion said, heaving a breath with his shoulders. "They're
samples."

"What do you mean?"

"Brains... they needed human brains as samples."

"―So these bodies have all had their brains removed?"

"Yeah― I think so. And I think they've all finished serving their
purpose. So―"

"So?"

"They're being disposed of."

This time, Nezumi was the one to swallow hard.

The half-moon-shaped device at the other end of the belt: was that for
disposing the corpses? Did it burn them instantly to ashes? Did it grind
them up and then dry them into dust? Or did it use some special chemical
to melt them right down to their bones?

The bodies were being sucked in.

People who had been alive just moments before―living, speaking, crying,
loving one another―were being disposed of like trash.

\emph{How... how could... No. 6, how could you be so cruel? How could you have
turned out to be so ruthless?}

"They're not humans." Shion's voice reached his ears. It was no whisper.
It was crisp and clear. "This isn't any human deed." His fist pounded
the reinforced glass.

\emph{This isn't any human deed.}

But the staff clad in white had been standing here conversing only
moments earlier. They had been sipping a warm drink from their mugs.
They had been engrossed in their work.

\emph{Are they all monsters?}

Nezumi's eye caught the photograph at his feet.

The smiling woman, the smiling boy. The sleeping baby.

'Look, look over here. Smile, come on!'

'Daddy, I'll take a picture next.'

'Honey, make sure you get the baby, too.'

He could almost hear the family's conversation―so typical, yet so
precious all the same.

\emph{Is the guy who had this propped up on his desk a monster, too?}

He felt a presence. The enemy approaching.

Nezumi felt like someone had struck him on the cheek. He was wide awake.
He yanked Shion by the arm, and burst out into the hallway.

\emph{We gotta run, Shion. We can't let ourselves die here.}

His whole body reared its arms in order to survive. His thoughts, his
senses, his fingertips, even each hair of his head acted solely for his
survival.

\emph{We cannot die.}

"Right!" Shion's calm orders sliced the air. "Thirty metres to the
right."

Thirty to the right. There was no time to think about what was there.
Strangely, the barriers were not coming down. But he also had no time to
think about why.

\emph{Run. Wait, never mind.}

Soldiers appeared before them.

"Squat down! Curl up!" Nezumi tossed the coin-shaped bomb across the
floor, and fired at it. There was an ear-splitting explosion. Shattered
glass sprayed everywhere.

"We're going in!"

There was no way out if they let themselves be surrounded. In the face
of a firing squad, they had no chance at all. They had no choice but to
charge into the thick.

"Don't leave my side."

A broken sprinkler was spraying water left and right. Nezumi leapt into
the knot of drenched soldiers.

He swung the blade of his hand against a soldier's throat, and stabbed
his knife into another as he spun around. As the soldier clutched his
shoulder and fell forward, Nezumi extracted a military knife from the
man's waist belt and slashed the wrist of another enemy that was coming
his way. A handgun fell and clattered loudly across the floor as blood
and water mixed and flowed together.

None of the soldiers uttered a word. They remained silent and carried
highly harmful military firearms in addition to the laser guns, which
were still in the stages of development. They were silent, swift, and
precise in their kill. They had probably been trained that way.

\emph{But when it comes to handling knives, I'm the better one.}

In hand-to-hand combat, lower-tech firearms would be much more effective
than high-tech weapons. Also, in certain situations, a knife would
probably be much more useful than the most up-to-date gun. Especially if
he could wield the knife as if it were one of his own limbs.

After seeing three of their comrades defeated in the blink of an eye,
the rest of the soldiers lost the fluidity of their movements. This was
a retaliation they had not expected. Stiffness was a weak point, and
Nezumi aimed squarely at it. He twisted the arm of the soldier in front
of him, and pressed his knife to the man's throat from behind.

"Don't move." He licked his lips, and commanded the rest of the
soldiers.

"Throw away your guns, or consider this guy dead."

The soldiers bolted back a step at once.

\emph{Will it go well? Could I make my escape, using this guy as a shield?}

"Shion."

"Yeah."

"You alive?"

"Yeah. You moved so fast, I don't think any of the guys had a chance to
turn on me."

"Perfect. Now use this guy as a shield, and―"

There was a burst of applause.

"Magnificent show. But that's quite enough."

The soldiers immediately parted, as if those words had been a signal. A
man threaded his way in from between them. He stood before the two boys,
and raised his right hand airily.

"Enough fun and games. VC103221 and Shion, was it?"

Shion let out a cry.

"You know him?" Nezumi asked. "Don't tell me he's your uncle or
something."

"He's an Investigating Officer from the Security Bureau―called Rashi."

"So you remembered me," the man said. "An honour. Luck seems to bring us
together quite frequently, doesn't it? You've grown tougher since I saw
you last. I would never have expected you to come infiltrating the
Correctional Facility. I'm shocked, to tell you the truth. However, I am
happy to see you again."

"Why thank you," Shion said guardedly. "I wasn't expecting to see you
here, either. I'm surprised, too."

"Yes, yes, about that. To tell you the truth, my real profession is a
military training instructor. Excuse me for not properly introducing
myself last time."

"Get his business card, Shion. It'll come in handy when you're
job-hunting."

Rashi twisted one side of his mouth into a smile.

"A way with words, as usual, boy. But your way with the knife is even
better than your tongue. Admirable. I would never have expected you to
take control of my subordinates so easily. Ah, simply brilliant. Worthy
of praise. I would even consider recruiting you."

"A tantalizing proposal, but I have to refuse," Nezumi said. "What's
this military training you're talking about, huh? Does target practice
include shooting prisoners?"

Rashi chuckled. "We have that, too. Or we have training sessions where
we exterminate foolish rats that have wandered in."

Nezumi twisted the soldier's arm with even greater force. "Throw away
your guns and clear the way," he said.

Rashi shook his head. "You two are brilliant. Not anyone can get as far
as this. Brilliant, indeed. But unfortunately, you are also young."

Rashi slowly raised his right hand. "Your plan is not well-thought out
to the end."

A gun barrel was pointed their way.

\emph{Huh?}

"Stop!" The soldier twisted desperately. Nezumi let his arm go. A bullet
pierced the soldier as he staggered forward. His wounded body crashed to
the ground. Water poured on him from the ceiling. The soldier raised his
face, and his gaze wandered as if he were searching for something. Then,
he called.

"Mother."

The voice reached Nezumi's ears.

\emph{To kill a subordinate so easily...}

Then a savage pain tore through his shoulder and leg.

"Nezumi!"

Shion's arms caught him from behind. The water caught both their feet,
and they toppled to the floor. Pain raced through his whole body.

"...ts..." Nezumi gritted his teeth. Sweat poured off his body, and his
heart thudded rapidly.

"Come, come. Superfibre may be amazing, but it's useless if you don't
wrap it properly. You can't hold a knife anymore, can you? Nor can you
hop or dart around. Now you're finally quiet. I've had a splendid time,
but the games are over, 103221."

\emph{Over? Does it all end here?}

Rashi furrowed his brow, and sighed.

"I wasn't expecting to be met with so much trouble. A shame, really. A
shame that I must to kill you, but―it cannot be helped. I won't draw it
out longer than it has to be. I will respect your efforts in battle and
I will let you go in peace. A bullet per person should do the job."

"Compassionate... aren't you?" Nezumi said.

"Do you have any last words?"

\emph{Is this really the end?}

Suddenly, the sprinklers stopped. The barriers began to come down at
once. A buzz of anxiety ran through the crowd of soldiers. Rashi's gaze
also roved.

It was their chance. They would take advantage of this opening and steal
that gun. A chance to return from the brink of death―but his body would
not move.

"What's going on?"

"The barriers are just beginning to work."

"That's absurd, why―"

"Run! We'll be trapped!"

Once the barriers came down completely, a high-voltage current would run
through the sealed space. No one would survive.

"Run! Get out of here!"

The soldiers broke into a run, with wounded comrades in their arms.

"Sir, the walls are coming down. Hurry!" A soldier stopped, turned
around, and yelled. "Sir!"

The walls were coming down―coming straight down. Nezumi felt like his
shoulder was on fire. He pressed a hand to his open wound, and smiled
wanly.

"He's calling you. Don't you need to go?"

"After I get rid of you two."

The barrel of his gun was pointed straight at Nezumi's heart. Shion's
arm slid around his chest from behind, as if he were trying to protect
him. Nezumi placed his hand on top. Shion's arm was covered in dirt and
blood.

\emph{I see. So I am going to die with you.}

He leaned back onto Shion and let out a long breath. The tension left
his body.

But he would not close his eyes.

He would behold the world before him with a steady gaze until his last
moments.

Shion's arm tightened around him.

\emph{I won't close my eyes. Not until the last moment―}

He heard a gunshot right beside him. It was a muffled sound, as if he
were underwater. Red flowers bloomed on Rashi's shirt. Petals flew all
around.

\emph{What...?}

Rashi staggered back a few steps before leaning heavily with his back
against the wall. He slid to the ground. Crimson petals also fluttered
from his lips.

Nezumi drew a breath, but could not release it.

\emph{Those aren't flower petals. ―It's blood.}

Blood had sprayed the wall. It was like someone had carelessly hurled
red paint at it. Rashi bowed his head. A startling amount of blood
poured out and dyed his lower body.

\emph{What―? What just happened?}

"Sir!"

A scream. Then, the wall closed it off completely. For a moment, it was
like a soundless void. A brief moment of quiet peace. He could breathe
out now, and he could pull himself up.

"...Shion?" He twisted his head to look at the boy who was cradling him.
"Shion―oh―"

He could breathe out, but no words would come. His heart was beating
harder, more frantic and fast.

Shion's hand was wrapped around a gun. A small-calibre semi-automatic
pistol. It was an official military-issue pistol that could shoot even
through a bullet-proof vest. Just earlier, Nezumi himself had swiped it
out of the soldier's hands and battered it to the ground.

The smoke from the gun wavered in the air. The sharp smell of gunpowder
pricked his nostrils. Sweat stung his eyes. His mouth turned dry, and
his tongue stiffened. He could hear the sound of it tearing as he forced
it to move.

"Shion... what have you..."

Shion withdrew his arm from Nezumi, and stood up. He slowly made his way
towards Rashi.

"Ngh..." Rashi groaned. He lifted his face, and his body trembled
slightly.

"...You amateur..." A barely audible murmur trickled from his lips,
along with a stream of blood. "At least... aim... for a fatal spot..."

"I have something to ask you," Shion said, with gun still in hand. It
was a low voice, stripped of all emotion. "Why didn't you activate the
barriers immediately?"

"...They wouldn't move..."

"So they weren't functioning."

"...Yes..."

"Why not?"

"...I don't know..."

"You and your people would have paused the barrier system temporarily
before coming here, just in case. But this time, they started moving on
their own... am I right so far?"

Rashi quaked as he looked up at Shion imploringly.

"...Please. Put me to rest."

Tears spilled from his eyes.

"Answer me," Shion said.

"...Yes... out of control... cause unknown..."

"Out of control. Cause unknown..." Shion repeated thoughtfully.

"I know... nothing... Shion, I beg you... hurry... put me to rest...
save me..."

"Save you?" Shion's shoulders twitched. "I heard those same words just
earlier. In the basement of this building."

It was then that Nezumi was finally able to stand. Blood streamed from
his shoulder and leg, but he felt no pain.

He had to stand up. He had to grab Shion's arm. He had to stop him.

\emph{Shion, what the hell are you trying to do?}

His legs gave way. He tripped and landed on his knees. A soldier's
corpse was lying right beside him. It was a young man. He had black,
frizzy hair and was wearing a golden necklace. It was glittering.
'Mother'―it was almost like his last word was still plastered to his
lips.

"You people threw this man into the basement. He was a victim of the
Hunt. He couldn't die, so he came begging to me. 'Help me,' he said.
When this man was writhing in agony, what were you doing? Drinking
coffee? Taking a bath? Giving a lecture?"

"...Please... put me... it hurts..."

"I couldn't save him."

"...Help me..."

"I couldn't save anyone."

Shion's right arm rose slowly.

\emph{"Shion, stop!"}

A gunshot rang out.

Nezumi closed his eyes, and turned away. The smell of gunpowder grew
stronger. Mixed with the stench of blood, the air grew thick and
viscous. It was a stench he was used to―almost too used to―and yet, he
still felt like throwing up. He couldn't bear it.

He didn't want to open his eyes.

If he did, he would have to face reality. He wanted to keep his eyes
closed, and escape to a place that was not here.

\emph{I don't want to see it.}

\mybreak

\emph{Whoosh.}

He felt a breeze.

He smelled flowers. The faintly sweet smell of wildflowers.

\emph{Whoosh.}

The breeze touched his cheek, and caressed his bangs.

\emph{Oh, it's that again. It's... that.}

He opened his eyes.

The light stung.

A field stretched out before him.

A field of tender grass. The wind was still somewhat sharp and cold, but
the rays of the sun were strong. Small white flowers bloomed everywhere,
swaying in the breeze, and glowing in the sunlight. There were misty
mountain peaks in the distance. Were those lakes on the mountain-skirts,
white pools reflecting the light of the sun? Lakes and marshes both
large and small dotted the land. The sky was an indigo blue. It was such
a deep azure, it looked like it could colour everything else with its
pale shade. But the flowers still bloomed white on the ground, and the
grasses were a gentle green.

In the sky he saw blue, on the land green, and he saw the forest.

There was a forest beyond the meadow. He could hear the rustling of the
trees. White-backed leaves were fluttering. Birds soared up, and swooped
down again. A fluff ball drifted past Nezumi's line of vision.

He wanted to chase it.

\emph{Can I chase it?}

Nezumi had lifted his face to look up. Looking up at... whom?

"Come here."

There was a gentle voice, and he felt his body being tenderly lifted up.

\emph{Oh, it's that again.}

\emph{It steals my consciousness, and bears my soul away.}

He felt like a little child. He was being carried gently. Like a small,
small child.

Last time, it was summer.

He had smelled the hot air rising from the grass.

Was it springtime now? The scenery was more subdued. The wind, the
light, the smells, the colours were all soft and gentle, encircling
Nezumi in an embrace.

"I will teach you a song."

He shook his head. "I can do it... I can sing."

"You can sing? That song?"

"Yeah." Nezumi straightened his posture, and drew himself up.

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here\\
	Keep everything here, and\\
	Live in this place\\
	O soul, my heart, O love, my feelings true\\
	Return home here\\
	And stay}

The wind stopped. \emph{It's listening to the song}, Nezumi thought. The wind
subsided, and the balls of fluff began to fall slowly to the ground.

"I see. So you can sing."

His hair was caressed. He was gently rubbed on the back.

"Sing some more. Let me hear a little more of your song."

\poem{The wind steals the soul away, humans thieve the heart\\
	But here I will stay\\
	to keep singing\\
	Please\\
	Deliver my song\\
	Please\\
	Accept my song}

His eyelids drooped. All the strength left his body.

"...I'm sleepy."

"Then go to sleep."

\emph{Could I close my eyes like this, and drift off into a slumber?}

"Go to sleep. I will take you there."

"...Where are you going?"

"To the forest."

"To the forest?"

"Go to sleep. Think of nothing, and let yourself rest."

\emph{Is it really alright for me to go to sleep like this?}

His body rocked back and forth. He was comfortable. So comfortable...

"I'm going back!" he heard himself yell.

He had to go back. He could not let himself drift off asleep. He had to
return to reality, where Shion was. It didn't matter what awaited him
there; he couldn't let himself flee on his own.

\emph{Shion.}

\emph{I need to return to you.}

\myspace

He felt a cough coming up. The smoke and the stench of blood filtered
deep into his body. A fit of coughs overtook him. He wiped his mouth,
and stood up.

He could see Shion with his back to him. The boy stood with both arms
dangling at his sides. The pistol was still in his right hand.

"I can't save anyone," Shion said in a muffled voice. He was repeating
it.

\emph{I can't save anyone.}

"―Shion," Nezumi tried calling the boy's name.

\emph{Shion, do you hear my voice?}

"Nezumi."

Shion's eyes focused on Nezumi. Joy ignited within them. A smile spread
widely across his face. A sigh of relief spilled from his lips. The
pistol slid from his hand.

"Thank goodness you're safe. But―you're bleeding a lot. Are you alright?
We have to bind that wound, at least."

Shion took off his sweater and started ripping the sleeve.

"This is all I have, but it might serve as a bandage. Give me your
shoulder, and I'll bind it."

It was the usual Shion. His usual tone, his usual gaze. He was naive and
foolish, ignorant, idealistic, unbelievably honest, and warm.

Nezumi's heart ached. He felt burning at the back of his eyes.

"Shion."

"What? Does it hurt?"

"You protected me."

"Huh?"

"Don't forget that. You... protected me."

"Me?"

Shion closed his mouth, and blinked at him repeatedly. His gaze slid to
and focused on the pistol lying on the floor. Then, it moved to the man
slumped lifeless against the wall. He had been shot between the eyes.

\emph{Quite something}, Nezumi thought fleetingly.

The bullet had pierced the man squarely in the middle of his forehead.
Despite the fact that it was at point-blank range, shooting a target
without a sight was not an easy feat for an amateur.

Shion's breathing quickened. He brought his palms up to his face. He
stared at them intently as if there were some cryptic letters carved
into them. His palms, his arms, his whole body trembled.

"Nezumi―what have I done?"

"You protected me. You saved me with your life―"

"No!" Shion's scream resounded in the confined space. "You're wrong!
You're wrong! You're wrong!"

"I'm not wrong!" Nezumi shot back. "I would've been killed if it weren't
for you. He wouldn't have been sitting there bleeding. It would've been
me."

He pointed at Rashi.

"I would've looked like that."

He grabbed Shion's arms. He shook the boy with all his might. Shion's
head jerked back and forth. He was like a marionette dangling on broken
strings.

"Listen. Listen to what I say. You protected me, do you understand? You
saved me. Shion."

\emph{Listen, Shion. Grasp my words. Believe them.}

"If I were you, I would have done the same. I would definitely have done
it. This is a battlefield. If we don't kill, we get killed. What you did
was justified."

Nezumi chewed his lip. The words crumbled and rotted as soon as they
slipped out of his mouth. This isn't what I really want to say.

Then, what did he want to say? What do I really want to tell Shion right
now?

"Nezumi..." Shion murmured hoarsely. "I... killed him."

He got up, and picked the handgun off the floor.

"I don't know how. But without any hesitation at all, I was able to
just... kill another human being."

Their eyes met.

\emph{What do I have to tell him?}

"Is that forgivable? Is that something... that's allowed to be
forgiven?"

The mere 5.4-mm diameter of the barrel seemed so large to his eyes.

"You said once that No. 6 and I were very similar. I said you were
wrong. But... maybe you were right. I am like that city. It doesn't
matter why I did it. I coldly, ruthlessly, wrenched a man's life from
him. Nezumi―"

Total length: 155 mm. Weight: 460 g. Shots equipped: 8. Rifling: 4
grooves, clockwise.

\emph{How many shots are left?}

"Can I be forgiven...?"

Shion closed his eyes.

\emph{Shion? What are you doing?}

\emph{"Stop―!"}

Nezumi had raised a cry. Not with his voice, but with his whole body. He
lunged at the boy, and punched him as hard as he could. As Shion
crumpled to the ground, Nezumi straddled him.

"Stop fucking around!"

He grabbed the boy by his collar, and struck him across the cheek.

"You must ― be fucking ― kidding me !"

He could feel his palm hitting flesh again and again.

"You bastard, who do you think you are? We've come this far, and now you
think you can run away? Put yourself out of your misery? Fucking
bullshit!"

Shion whimpered softly.

"You traitor," Nezumi snarled. "Are you saying that you can't be
forgiven for killing someone else, but you can be forgiven for killing
yourself? You know that if you go on and commit suicide, you'll be
murdering two people. \emph{Why don't you get it?}" His last words came out
like a pained plea.

Tsukiyo leapt up onto his shoulder and screeched loudly and insistently.
He looked like he was trying to get between them.

Shion didn't resist at all. He looked like he wasn't even breathing. His
eyes were open, but they were sightless. The edge of his mouth was cut
and bleeding, and dried blood was caked on his lips.

\emph{He's totalled ― wounded all over.}

Would it have been better if they had not come? Nezumi knew more than
enough that once they infiltrated the Correctional Facility, it would be
a battlefield. He knew, and he had still dragged Shion in. The rescue of
the girl, Safu, was only an excuse for Nezumi. He wanted Shion's power.
He wanted the boy's power to perfectly memorize the innards of the
Facility, and to give precise orders. He wanted to borrow―no, take
advantage of― Shion's power to destroy the Correctional Facility, and
put a crack in No. 6's core. Shion was a good weapon to serve this
purpose, and this was a happenstance more lucky than anything Nezumi
could ask for.

\emph{Yeah, I used Shion.}

But if the results of it had been this ― \emph{this} ― then, it was better if
they had not come. \emph{We should never have set foot in here.}

He had, of course, been prepared for a brutal struggle. He had
recognized that they were waging a reckless war with less than a
one-percent chance of winning, and yet he had had the resolve that they
would emerge as victors; he had both the eager heart and the restraint
of reason, and he had been so certain that he had it all.

\emph{And that it was we ― not No. 6 ― who controlled the state of things.}

There was no battle without preparation. There was no victory without
solid certainty.

There should have been nothing wrong with what he thought. He was
certain he had not gone astray.

Nezumi gritted his teeth. He felt like he would almost succumb and kneel
to the reality that stood before him. \emph{I never imagined that it would
turn out like this.}

\emph{We shouldn't have come. We were not supposed to come here. I shouldn't
have dragged Shion into my battle.}

It had finally dawned on him. But it was too late.

"Shion." \emph{I'm the one who should be asking whether I'll be forgiven. I
should be the one begging for forgiveness, not you.}

"Shoulder it," he whispered. The words tore through his gritted teeth
and spilled from his lips. Shion's eyes moved slowly. They narrowed
slightly, as if attempting to focus on Nezumi.

"Shoulder it― shoulder it, and live on." They were words for himself,
not Shion.

\emph{Bear your sin, and live.}

\emph{Shion, I'm sorry. I made you bear the burden, one so big it's making
your spine creak. Would I be forgiven one day? Would you forgive me for
what I did to you?}

Shion let out a long breath.

An arm reached out, and a set of fingertips touched Nezumi's cheek.

"It's my first time... seeing you cry."

"Huh?"

\emph{Cry? Who?}

"It's alright, Nezumi... don't cry. I get it. I'll do as you say. So
just don't cry, please."

"Idiot," Nezumi said hoarsely. \emph{Really, how idiotic can you get? Still
caring for others in a situation like this. What's 'alright'? Nothing's
alright. Besides, I'm not crying. I'm not like you, I don't just let my
tears fall wherever and whenever I want, without hesitation―}

He had reached his limit. He couldn't hold it in any longer. A wave of
tears overcame him, and they streamed from his eyes. The droplets were
startlingly hot. They rolled down his cheeks, dripped from the point of
his chin, and landed on top of Shion.

\emph{Damnit, why are these tears―damnit.}

He let his body sink on top of Shion's as his sobs spilled out.

\emph{Damnit. Bastard. Bastard.}

"Shion."

"Mm..."

"I don't know how to stop my tears."

"Mm-hmm," Shion murmured.

"I really... don't know. If this keeps going it's gonna be... bad."

"Yeah?" Shion said softly.

"It \emph{would} be. Think about it: if Inukashi saw me like this... he'd make
a fool out of me for the rest of my life."

"―That's for sure." A hand slid around his back, and patted him.

"Nezumi, let's go."

Yes. They would have to go. This wasn't the finish line yet. They had to
move forward. But, how? Was there a way to escape this sealed space?

"Oh!" Nezumi scrambled up. A startled Tsukiyo dove into Shion's shirt.
"Why is that?"

"Why is what?"

"Why isn't anything happening? Weren't they supposed to run an electric
current as soon as the barriers were down?"

"That's right." Shion also got up. He winced in pain, likely from some
wound. But his face soon smoothed into a faint smile.

"It's been almost five minutes since the walls came down completely.
That's kind of a late observation for you, isn't it?"

"The hell is that supposed to mean?" Nezumi replied indignantly. Then,
he closed his mouth. He glanced at Shion's face, which was smeared with
blood.

"Are you saying you knew, then? You knew beforehand that nothing would
happen?"

Shion shook his head.

"I didn't know. There was no way I would have known. It's just that―"

"Just that, what? We've come this far. Don't play hard-to-get."

"Right. Well, you might laugh, but I feel like we're being... invited in
by someone."

"Invited in?"

Shion licked his lips, and continued in his Shion-like, awkward manner.

"Actually, the barriers should have activated the moment we burst into
the hallway. But they didn't move. They only started moving when we were
surrounded by the soldiers. Even though at that time, they would have
been temporarily paused. That doesn't make sense. That's why they were
so flustered."

"Wait a minute, I dunno what you're getting at. So are you saying that
the computer monitoring the security system was buggy? That it
conveniently stopped working for us? ―Well, I dunno whether I'd call
being trapped in here convenient. But we were saved. We were rescued by
a coincidental computer malfunction― is that the deal?"

A No. 6 computer malfunctioning? No, there was no way something like
that would happen.~

Shion shook his head again.

"It's not a coincidence. It was by will."

"Will? You're saying the computer had a will of its own?"

A third refusal.

"No. It could be operated a certain way based on one's will, but the
machine itself wouldn't have one."

"Shion, explain it to me so that I can understand. What're you talking
about? What do you mean by being 'invited in'?"

"I don't know," Shion said slowly. "I can't put it into words very well.
But that's the only way I can explain it. Someone is calling us―"

"And that someone operated the computer and rescued us of their own
will. That's what you figure?"

"Yeah."

"And who's that someone? That girlfriend of yours?"

"Safu―could it be her? But..." Shion dragged his feet to the wall. There
was a part that was a different colour than the rest. It was a shade
lighter.

"That's the elevator, right?"

"Yeah. The only path that leads to the top floor."

Thirty metres to the right. Shion had meant to tell him to run in this
direction. There were no buttons to be found on the wall that would
operate it. There wasn't even a single projecting part. It probably
activated by a sensor responding to a special ID chip.

"How do we get into this thing?"

Shion had turned his face back to stare at something. Nezumi followed
his gaze, and landed on Rashi's body.

"He might have a special chip embedded in his body," Nezumi said
hastily. He put into words what he figured had been on Shion's mind. He
didn't want to let Shion utter any words related to that body. Shion
glanced away, and held his palm up to the sky.

"No― that won't do. This system will activate only if it senses life.
The chip is useless unless it's inside a living, breathing human body. A
corpse won't do."

\emph{I see.} Nezumi muttered silently, and cast his eyes down.

The madness that had driven Shion to nearly shatter his own skull had
already been wiped clean.

\emph{It has to sense life.}

\emph{A corpse won't do.}

How could he say those words so casually after such an intense emotional
disturbance?

Nezumi shifted his eyes to his feet. Maybe I haven't just made him
shoulder it. \emph{Maybe I've also hauled it out―hauled out what was dormant
in him until now.}

\emph{Shion, what's lurking inside you? What do you really look like, Shion,
the you that I don't know?}

A chill ran down his spine. The wounds on his shoulder and thigh
throbbed as if in answer. Until now, he had completely forgotten about
his gunshot wounds.

"Is there any other way?" he asked, short and to the point.

"I think someone will come fetch us," came the equally short answer.

"Fetch us?"

He heard a faint mechanical noise. The elevator was coming down. The
door slid open almost soundlessly.

Two shadowy figures stood before them.

Nezumi tensed for a moment, then realized quickly that it was a
reflection of themselves. The entire wall in front of them was a huge
mirror.

"Nezumi―you're getting on, right?"

"You kidding me? Of course. I'm not stupid or rude enough to turn down
such a welcoming."

"Yeah. I figured."

He took one wide step into the elevator. \emph{Throb.} His wounds stirred
again. He would probably not be able to push himself much further,
considering the amount of blood he had lost. And, as Rashi had pointed
out, he could no longer use a knife with this hand.

\emph{No use mulling it over, though.}

He could not predict what lay ahead of them after the elevator stopped.
He couldn't foresee the future, so there was only one choice―to face the
here and now.

He let his gaze wander. There was nothing of note apart from the mirror.
The walls were smooth with not a speck of dirt to be seen. There were no
buttons, switches, or touch screens. It was a sterile, bright, inorganic
space.

The door was closing.

Right in front of them, he could see Rashi with his legs thrown out and
his head tilted to the side. He could see the soles of the soldier's
boots, the soldier who had called his mother in his last moments.

Shion's fingers moved to chest-level.

\emph{Are they going to clasp together in prayer? Nezumi thought.}

But Shion's fingers only clenched into a hard fist.

That was it.

The door closed.