% !TeX spellcheck = en_US

\chapter{If one's human soul}

\myepigraph{If one's human soul should completely disappear,\\
	one would probably be more likely to find happiness.\\
	But even so, the human inside oneself feels horror towards it like nothing else.\\
	O how so completely terrifying, grievous, and painful he thinks it!\\
	For one to lose his memories as a human.}{Nakajima Atsushi, \emph{Sangetsuki}}

\lettrine{S}{he had} awakened.

Safu had awakened, and understood everything.

She knew now what had happened to her.

\emph{What have you done\el what have you done\el what have you done?}

"Goodness, Safu. What's wrong? Look at the fluctuation in your emotions.
How long do you plan on keeping up this agitation for? What a
troublesome child. Your beauty is going to waste." He chuckled. "Ah, no,
that was just a joke. A flat joke. Don't mind me. You are still
beautiful, very beautiful. A huge success. Things are going exactly as
planned so far. And of course, there will be no mistakes in the future,
either." He chuckled again.

The man continued to laugh from his spot beside Safu.

\emph{Devil.}

\emph{So you were the Devil.}

\emph{Why---why---why have you done this to me?}

"You are not only beautiful. You are also resilient. You are my ideal,
Safu, let me confess that. I cannot lie to you, after all. I\el at first
only collected you to use you as a specimen. I tried to treat you as I
would any other sample. Oh, I hope you will forgive me. I don't want you
to reproach me like that. I didn't know that you would be so beautiful
and strong. Safu, you captivated me. I could repeat myself a million
times. You are my ideal---you are what I've been looking for. That is why
I will make you queen. No, I will make you into someone close to a
goddess. A perfect existence. You and I, we will rule the world
together. How does it sound? Exciting, isn't it?"

\emph{Devil.}

\emph{You are the Devil.}

\emph{Don't come near me. Don't come near me.}

Safu's voice did not reach the man.

The man continued to talk fervently as if he were possessed. Colour
tinged his cheeks, and he paced in circles, back bent slightly forward.

He was like a fish in an aquarium. He went round and round, round and
round, swimming in an enclosed space. Round and round. Round and round.

The man's feet trod silently on the floor as he continued talking.
Perhaps he was speaking more to himself than Safu.

"I finally have you in my hands. The ideal materials. Oh, Safu, I'm no
believer in fatalism. I don't believe in forces beyond the bounds of
human power, or the heavens being in control of our lives. I have always
laughed in scorn at it, calling it absurd. But---please don't laugh, Safu.
After meeting you, I, well\el I feel like I could believe a little bit
in this so-called fate. Perhaps it is true. Perhaps there is a God, and
He is trying to bestow me with an absolute power. If not, what could
explain the fact that I met you like this? That is why I will make you a
goddess. I have the power to do it. Oh, yes. Yesterday, I told you that
you wouldn't need a name. Right, of course, of course. You should throw
away your name from the past. I shall give you a name suitable for a
goddess."

The man's feet and tongue showed no signs of stopping.

He kept walking. He kept talking.

"Yes, how about\el " The man's feet stopped abruptly. A slow smile spread
over his face. "How about\el Elyurias?"

\emph{Elyurias?}

The man resumed pacing. The blissful smile still hung over his face. "A
splendid name, isn't it? Indeed, a name fit for a queen. Perhaps it is
all the more suitable for someone like you."

\emph{This man\el }

Safu's gaze locked onto him. For the first time, she got a good look.

His thin face looked gentle at first glance. His age---it was hard to
tell. Depending on how the light hit him, he either looked very young,
or considerably aged. The man had completely cut himself off from the
external world and was wallowing in his inner realm, staring intently
into the air and soliloquizing his feelings.

Self-intoxication.

This man was completely absorbed in himself. He believed that his
abilities were equal to that of God. He believed he was entrusted with
everything, that he would be forgiven for anything. That\el that was why
he could do this.

"Just a little bit more. Just a little more, and my project will be
complete. You were the last piece. Thanks to you, I have all the parts I
need. They're complete, that's no mistake. I just need time. I just need
a little more time. How do you feel? I want you to be comfortable, and
for that, I would do anything. You are one of the most important things
in my life right now, after all."

\emph{Set me\el }

"What? Safu, did you say something?"

\emph{Set me free. Change me back to who I was. Let me see him.}

Her emotions reared angrily. A wind roared in her heart, howling loudly.
She wanted to scream from the bottom of her lungs. She wanted to cry.

\emph{I want to see you.}

"Oh, what's the matter? Your numbers are going up. I guess you're having
trouble adjusting to your new environment. Hmm, I thought the transition
would be smoother. Oh, no, I don't mean to blame you for it. I wouldn't
blame you for anything. You are my treasure. Will you sleep a little
more? That should make things better. Hm? ---It looks like Mother agrees
with my judgment. She says she will prescribe you some stabilizers. Oh,
yes. I have to tell you about Mother. You and Mother are directly
connected, you know. Mother will always monitor you to adjust your
conditions for utmost comfort, so that you will have the best
environment possible. So that's why, look, now she's saying that you
need rest---"

A bell sounded shrilly. The tapered ends of the man's eyebrows shot up.

"What is it? An urgent call \emph{now}? How uncouth--- yes, it's me. What's the
matter? Today is the Holy Celebration, are you not busy with your
own---what? What's that? What do you mean? In the city? This is happening
in the city\el no, that can't be\el right, send the video over to me.
The samples, too. Everything you've collected\el yes, I'm about to right
now\el what? Thirty bodies already? In the space of one day\el so that's
what's happened\el I understand. That's enough. I'll go over there
myself\el yes, immediately. Immediately."

All the blood had receded from the man's profile. His lips were
bloodless, white, and parched. They trembled uncontrollably.

"It's a mistake. It must be a mistake. That\el that couldn't have
happened. It just isn't possible," the man practically spat, as he
exited the room. He was agitated to the point of it being unnatural. All
the ease and eloquence he had a minute ago were gone without a trace.

\emph{This is happening in the city}, the man had said. Had something happened
inside No. 6? Something that exceeded that man's predictions\el ?

\emph{No. 6, where I was born and raised. But there was always unrest
squirming below the surface. It was such a comfortable and beautiful
place, and yet it was always precarious\el the lingering feeling that
something was about to happen\el at least, I thought so\el }

Safu could feel her rage gradually begin to quiet.

She was sleepy. So sleepy, she could melt. Had she been dosed with a
sleeping drug? She was connected to the Mother---what did that mean? The
Mother\el \emph{oh, I'm so sleepy.}

Her consciousness blurred. It became hard to think. And in these
moments, there was always a figure which rose in her mind.

\emph{Shion.}

She tried calling his name. Shion smiled, and gave a slight nod. It
wasn't an illusion. He was so vivid, so concrete, as if he were standing
right in front of her.

\emph{Hey, Shion. When was it again? I remember the sun was setting. The wind
was a little nippy, right? It had snowed for the first time the day
before, and the path was wet. We were walking side-by-side. Do you
remember? You haven't forgotten, have you?}

\emph{And I called your name, didn't I?}

\emph{Shion.}

\mybreak

She called his name again. And Shion, again, smiled at her.

"What's wrong, Safu?"

"No\el I just---"

"Just?"

"I just wanted to call your name. I was giving it some hard thought, and
I actually realized that 'Shion' is a nice name. It's a flower."

"You had to give it a hard thought to notice it was nice?"

She had giggled. "So, what kind of flower is a 'shion'?"

"Uh\el a perennial flower that's part of the \emph{Asteraceae} family, if I
remember correctly. The stem grows up to 1.5 metres high, and it blooms
with light purple flower heads\el "

"Shion, I don't want to hear an explanation about the flower. I can get
that kind of information easily."

"Then what do you want to know?"

"Something that I can't get easily."

"Can't get easily\el hmm, that's almost like a riddle. If you don't want
to hear about the aster flower, then\el nope, I have no idea. What do
you want to know, Safu?"

\emph{I want to know about you, Shion.}

\emph{I wanted to know you. Who named you that? Do you like it? When was
it that I first called you by your name? And when was the first time you
called me\el ?}

\emph{Shion, I still don't know anything about you.}

\emph{I know your habits, the food you like, how you talk, your
gentleness and strength\el yes, I do know. I know it very, very well.
But, Shion---}

\emph{Who were you chasing? Who did you long to be beside? Who were you
yearning for? Who stands at the other end of your outstretched fingers?
Couldn't it have been me? Did it have to be that person? I don't know
anything. So tell me. I wanted you to tell me, Shion.}

\emph{Shion.}

\mybreak

\elyurias{Safu.}

She heard a voice. Sparks burst in the haze of her consciousness.
Scarlet flowers opened their petals. A wind scattered the fog that hung
over her eyes, and in the same way that the scenery would unfold before
her, Safu's consciousness came back to her. The voice had called it
back.

\elyurias{Safu.}

\emph{Who is it? Who called me?}

It wasn't Shion's voice. Nor was it her deceased grandmother, or her
parents. It was a voice she had never heard before---no, sound? Melody? A
breeze in the canopies, the gentle splash of water, the pounding of rain
on the ground---it sounded similar. But it was different. It was a sound
she was hearing for the first time.

\emph{Is it a song---? A beautiful, song-like\el }

\elyurias{Safu.}

\emph{Who is it? Who's calling me?}

\elyurias{It's me, Safu.}

\emph{Who? Who are you?}

\elyurias{I am Elyurias.}

\emph{Elyurias\el }

\mybreak

"Shionn, stop squirming!" Inukashi clicked his tongue as he lowered the
baby into a large pot full of warm water. The baby grinned. He flapped
his arms and legs, squealing with glee. Warm water splashed everywhere,
wetting the hem of Inukashi's shirt.

"Stop horsing around. Geez, you're really round, aren't ya?"

The baby's hands and feet, his belly, his whole body was plump and soft.
Every finger, every hair was brimming with the energy of life.

\emph{Strange guy. He's different from any baby I know. Way different. So
different, sometimes he just makes me stop and stare.}

The kind of babies Inukashi knew always had Death curled up and ready to
spring at their feet. Their life was wrenched from them before they even
had a way of protecting themselves. Those were the kind of babies he
knew. Malnutrition, plague, the frigid air; sleeping quarters not much
better than a garbage dump. What was the fraction of babies in the West
Block who lived to turn five? Fifty percent? No, maybe even thirty. Some
kids were killed by their parents so that they would be one less mouth
to feed. Inukashi knew swarms of them whose only purpose in life seemed
to be to come into this world, only to die. For a short time, Inukashi
had done infant burials as a job. But his "burials" literally only
consisted of him digging a hole and burying the baby. It was no
different than digging a grave for a dog. He thought babies who were
sent off with the mourning of a father and the grief of a mother were
still lucky. Oftentimes, Inukashi was the only one to see the baby off.
No one ever left prayers, much less a single flower for the simple
grave, a raised mound of dirt with a rock placed on top. In time, people
forgot that it was a grave in the first place.

Babies usually died with their mouths slightly open. Sometimes, through
their eyelids which had not quite closed, he could see a set of
startlingly clear eyes staring vacantly back at him.

\emph{Of course. They couldn't even stand on their own feet. They'd have no
way of becoming tainted. Of course they'd still be innocent.}

His heart had never ached as he piled dirt onto the small corpses. He
had never experienced sorrow, nor spilt any tears.

\emph{Good for you to have died early. You're a lucky one. You didn't have to
suffer any more than this.} These were the only words he's speak to them.

\emph{Hey, little guy, how many months did you get to live for? Two? Three?
You've lasted half a year? That should be enough, then. Don't even think
about being reincarnated. You'll just end up with the same fate anyway.
If you still want to that badly, then come back as a weed that grows on
the edges of the path, or as a puppy. You'll be a hundred times happier.
You listen, alright? Never, ever be born again as a human.} That was
another thing he'd say to them.

It was Inukashi's own way of sending the dead off.

Nezumi would sing. He would probably sing a sending-off song, for the
soul that had expired while it was still innocent---though Inukashi didn't
know if such a song existed, he knew Nezumi would sing it. \emph{But you know
what, Nezumi? Dead people don't need songs. Dying people might, but not
the dead.}

\emph{The dead return to the land, and turn back into soil. Babies do, and so
will you and I.}

Inukashi shook his head vigorously when he realized he had been
absent-mindedly thinking about Nezumi. He crossed his left middle and
index fingers. It was his charm to ward off demons.

For Inukashi, Nezumi was something close to a demon. Even more
detestable than Death.

You could avoid Death to a certain extent, as long as you didn't let
your guard down. You could ward it off, you could trick it. \emph{But what
about him? He thinks nothing of driving people until their backs are
against the wall. He gets you involved in danger. He doesn't give a damn
about your convenience or your own matters. He'll make use of dog shit
if it serves him a purpose. He's cunning, frightfully thorough, and can
wrap you around his finger as easy as anything. Ugh, enough, enough. If
Nezumi didn't have his power as a singer, I would never have associated
with him. Never. Oh---damnit, I'm thinking about him again. I shouldn't
even devote a second to thinking about that guy, or else I'll be sucked
in by his evil. I should know this---what's wrong with my head?}

"Come on, Shionn. You do the charm, too. Then the demon won't come
getcha. You're beyond all hope if you end up like your Papa, completely
under his spell. See, stick your fingers together like this."

"Bah-booohh, boo-boo!" Shion raised a joyful cry from his bath. He was
strange---a very strange baby, indeed. Not even a shadow of Death crept up
on him.

In their room in the ruins of the hotel, the walls were crumbling, the
windowpanes were shattered, and a cold draft always blew in. It was a
place only marginally better than outside. Rikiga was able to provide
them somewhat with milk, but it was nearly not enough. Inukashi made up
for what he didn't have with dog's milk and vegetable broth.

The baby was probably more fortunate than most in the West Block, but it
didn't change the fact that he was still severely deprived.

But Shionn was always in high spirits, swinging his hands and feet,
laughing, and babbling to Inukashi. His skin had a healthy glow, and he
was plump, round, and full of energy. Inukashi could even swear that the
baby had grown in these past two, three days.

Those eyes shined with life, his skin was smooth, and his voice was
strong. It was almost like the infant was encased in a transparent
shield that protected him from the many dangers and toxins of this
world.

A strange baby.

"Hey, Inukashi," a gravelly voice called out to him. A deep,
muddy-sounding voice.

\emph{Geez. I'm not asking you to change your face, but can you at least get
some class into your voice?}

"What the \emph{hell} are you doing? Stop it!" There was scramble of footsteps,
and Shionn was snatched from Inukashi's arms. The pot wobbled, and warm
water spilled out.

"What's your problem?" Inukashi whined.

"You must be kidding me. Stop this!" Rikiga hugged the naked baby to his
body, retreating slowly. "Inukashi---this is going too far. This isn't
what humans do."

"Huh?"

"Aren't you ashamed of yourself? Sure, you might be more dog than human.
But that doesn't mean you don't have a shred of reason in you."

"Reason? That crap isn't gonna do any good for me, will it now? But I
guess I might have a little more of that than you, old man."

Rikiga screwed his drunken flushed face into a scowl, and retreated
another step.

\emph{What the hell is this old man doing?}

"I thought you'd have more decency for a dog boy. Inukashi, I don't know
how hungry you are to want to do this, but eating a baby? You must be a
monster. Have you thrown away your human heart, too?"

"Huh? The hell are you talking about?"

"Don't play dumb with me. You---you were trying to boil Shionn and eat
him."

Inukashi fixed Rikiga with a long stare. He didn't even blink. He could
feel laughter welling up and prodding inside his chest.

"What's so funny? You inhuman bastard."

After Inukashi had bent over double and laughed for a good while, he
wiped his mouth with the back of his hand.

"I laughed so much, I'm drooling. Ah, old man, you missed out. If you'd
come even thirty minutes later, I would've treated you with some good
soup taken from baby broth. As much as you could eat."

"L-Like I would ever eat something like that! I'd rather starve to
death. Besides, what were you---"

"A bath."

"Huh?"

"I was giving Shionn a bath."

"In a pot?"

"Yeah. This is the pot I use to make food for my dogs. It's the best
size for giving a baby a bath. Of course, if you insist on delivering me
a high-quality baby bathtub, old man, I'd be delighted to use that
instead."

"Uh\el I, well\el "

Inukashi shrugged exaggeratedly.

"But I gotta say, I'm flabbergasted to find out you care so much about
Shionn, old man. I thought you were only nice to your money, your booze,
and young women. What a surprise."

"Of course I care," Rikiga said indignantly. "I'm not like you. I still
have a decent human soul. Don't lump me in with you people."

"You people? Am I part of that group, too?"

"You and Eve. Who else?"

Inukashi shrugged again. "Fine. If you're so bent on it, then take him."

"Huh?"

"Tuck that baby into your coat and take him home. I can just \emph{imagine} the
fine young man he'd grow up to be, raised by such a gentle old man like
you. Just like airheaded Shion, who you love so much."

Rikiga shook his head hastily.

"No can do. I can't do it. Inukashi, I'm sorry. You're not an inhumane
bastard. I'm sorry for lumping you in with Eve, that wiley fox. I
apologize. I'm sorry. There must've been something wrong with me.
Hahaha---I see, yes, a bath. Babies love baths, right? Isn't that nice,
Shionn, aren't you glad to have been picked up by such a nice person?
You lucky guy."

Rikiga rubbed his cheek against Shionn's. Shionn burst into tears. He
opened his mouth wide, and his stretched arms and legs went rigid. An
old dog who had been sleeping underneath the table raised its head and
narrowed its eyes suspiciously.

"Oh---hey, come on, don't cry. Stop flailing around! He'll drop you."

The baby didn't stop crying. He wailed, stretching his hands towards
Inukashi. Inukashi almost reflexively snatched the baby back into his
own arms. He wrapped both arms firmly around the small body. The crying
stopped instantly.

"Geez, he'll catch a cold like this. If he gets sick, it's your fault,
old man. You'll be paying for his medicine bills. Must've been cold,
huh, Shionn? I'll get you inside the bath again. Go on, warm up."

A plump arm reached out, and its fingers touched Inukashi's cheek.

"Mama."

Tears had left their streaked marks on his smooth cheeks.

"Mama."

Inukashi felt like his heart was being wrung. Something twisted deep
inside his body. He almost stopped breathing at this huge, scalding,
twisting emotion that had reared inside him.

"Mama."

\emph{Yeah, I know, Shionn. It was a joke. A lame, stupid joke. Forgive me.
It's alright, I'm here. I won't give you away to a drunkard like him\el 
no, I won't give you away to anyone. I promise. I swear.}

\mybreak

Rikiga peered into the bundle in Inukashi's arms, and exhaled a breath
that reeked of alcohol.

"Mama," he echoed.

"What? You miss your Mama, old man?"

"My mother went six feet under a long time ago. She crawled into that
grave when I was ten, and hasn't tried to crawl back out since."

"She must be really comfortable in there," quipped Inukashi.

"And she probably wouldn't want to see how much her son has gone
downhill anyway. Maybe she's choosing not to come out."

"Who are you calling downhill? But anyway, about Shionn\el "

"What about Shionn?"

"He called you Mama."

"So he did."

"Why 'Mama', huh?"

"Dunno."

"Mama."

"See, there it is again."

Inukashi lowered Shionn back into the bathwater, and warmed him. Shionn
found it very comfortable, apparently, for he gave a relaxed smile. Its
radiance touched upon everything: beautiful things, refreshing things,
exciting things.

\emph{I didn't know babies were such precious beings.}

"Why is it 'Mama', Inukashi?" Rikiga insisted.

"Everything is 'Mama' to babies, old man. Hard to believe, but even you
were crying for you mama some decades ago. Did you stop crying once
someone flashed you a gold coin back then too, huh?"

"You're one to talk," Rikiga shot back. "You're just as attached to
money as I am. Look at the pot calling the kettle black."

"Hah, shut up."

\emph{They're such precious beings. I never knew.}

All the babies Inukashi had buried without feeling---in the frozen ground;
in the sun-beaten and parched soil; in the muddied earth of the rainy
season---now, for the first time, Inukashi cast his thoughts to each and
every one.

\emph{Maybe Shionn wasn't the only one. Was that baby a precious existence? Or
that baby, or that other baby, too? If they were, then\el they shouldn't
have died like that. It doesn't make sense. It doesn't make sense that
they have to die so skinny, with their skin so wrinkly you'd think it
was some old woman. To draw their last breath with such innocent eyes,
without any hatred for anyone, without even knowing how to hate. Like
the one I buried at the root of a honeysuckle bush,or the one I dug a
grave for in red soil, or the one I wrapped in rag before burying, or
that one, or that one, or that one---they all should have been cherished
more;. They shouldn't have been forced to die that way.}

\emph{Shionn, don't you die. Live on. Live, and grow big. Learn to hate, learn
to cherish.}

"Muh-muhhh."

Inukashi scooped the baby up, and briskly put his clothes back on him. A
black female dog got up as if it had been waiting its turn. The mat it
had been sprawled on had cotton stuffing poking out of its ripped seams.
Inukashi had fished it out of the rubble in the marketplace. It was
faded, worn thin in many places, and more like a rag than anything else.
But upon closer examination, one could see an adorable pattern of baby
chicks. Maybe a baby much like Shionn had been using it before. On the
day of the Hunt, maybe he had been put to sleep on this very mat, and
been immersed in a dream.

"He's all yours," Inukashi said to the dog. After Shionn had been laid
down beside the dog, he immediately latched onto the dog's teat. He
suckled eagerly, making gurgling sounds in his throat.

"Rather furry nurse he's got."

"We've got as many furry girls as you'd want," Inukashi said.

"Black fur, red fur, white fur, spotted fur. Care for a night with a
lady of your choice?"

Rikiga ignored Inukashi's sarcasm, and heaved a sigh.

"A human baby being raised on dog's milk\el that's quite something. But
is that alright? God forbid he should start barking next."

"He just said 'Mama', didn't he?"

Rikiga looked down at Shionn, and heaved another sigh.

"Old man."

"What?"

"Have you made the preparations?"

Rikiga's face slowly turned towards Inukashi. "Yeah." He lifted his arm
languidly, and pointed at the black bag on the table.

"Good. Let's go, then." Inukashi lifted the bag. It weighed down heavily
in his hands. Rikiga knitted his brow and made a reluctant face.

"Inukashi\el why don't we call it quits?"

"Quit?"

"Let's just forget about the whole thing."

"Forget about it, and then what?"

"We crawl back into our holes and keep quiet. Don't you think it'd be\el 
better that way?"

"Of course." It would be better, old man. I feel that way hundred times
stronger than you. I want to forget all about it, and crawl back into my
den.

It would be cold tonight, but not enough to freeze. If Inukashi had his
dogs with him, he'd be able to ward off the cold. Just minutes ago, he'd
filled his stomach with stale biscuits and a soup of vegetable rinds. It
was good. \emph{That means right now, I'm more or less fulfilled. If I could
just lie down with my dogs and fall into a deep, deep sleep\el }

\emph{That'd be nice.}

"Right?" Rikiga continued. "Why don't we do that? You have Shionn. You
have to protect him. If something happens to you, who's going to take
care of him? Think about it."

"The dogs are here. The dogs will raise him even without me. Just like
my mum did."

"Yeah, but\el Inukashi, let me be straight with you. I value my life as
much as you do. I don't want to do anything dangerous. So," he said
hesitantly, "let's back out of this. Forget it ever happened, hm?"

"And what happens to Nezumi and Shion? You gonna abandon them?"

"Those two are already dead. There's no way they'd be alive. They
couldn't have lived if they've been rounded up by the Hunt, anyway. You
know this as well as I do. That's why it's useless. We're about to put
our lives on the line for something completely useless. Come on, let's
just stop this. It's for the best."

"Old man."

Rikiga drew his chin when he saw Inukashi's gaze.

"---What?"

"That's enough yammering. It's almost time. Let's go."

"Inukashi!"

"I'm going. If you wanna quit, old man, you go do that. I don't care.
The bag comes with me, though."

"Inukashi, why? Why are you so bent on fulfilling your duty to them? You
always acted alone. So have I. I could understand for Shion, but to go
this far for someone like Eve\el "

"He's one of us."

"Huh?"

"They're part of our group. I can't abandon them."

Rikiga's dark eyes darted about. His mouth twisted into a scowl, like
someone had force-fed him some bitter herb. He scratched furiously at
the rash on his chin.

"I can't even bring myself to laugh at your joke," Rikiga said
scathingly. "You've got no taste. Just listening to you makes me
nauseous."

"Well, gee, I mean, your stomach is probably already a mess from your
binge-drinking. I'd advise you to give up the booze for you own sake,
though it's probably too late for you. Heheh, but I sounded pretty cool
back there, didn't I? You'd agree I was pretty suave, right?"

"Idiot. I can't believe you could rattle off those embarrassing lines as
if you actually meant it. Maybe you've got potential to be an actor like
Eve. You must be kidding me," he spat, "one fox is enough."

Inukashi bared his teeth on purpose into a vulgar grin. Rikiga's mouth
twisted even more severely.

"The only members of your 'group' are your dogs," he said. "You have as
little trust for humans as the length of your pinky. Keep shooting off
lies like that, and one day your tongue will rot."

"Ooh, I wouldn't want that," Inukashi said sarcastically. "Fine, let's
be frank. You first."

"Me---" Rikiga began. "Well, like I said, I want to back out. I've been
saying this over and over."

"That's honestly how you feel?"

"I'm an honest man. I don't lie."

"I can't even bring myself to laugh at your joke. Forget your tongue.
Watch it before your wang rots and falls off, too. How much money did
you spend to come up with what's inside this bag, huh, old man? I'm sure
you've gotten tons of gold from Nezumi, but at best, that gold'll offset
your expenses and you'll be even\el no, you'll probably be down. If you
scamper on back to your hole, you'll be losing all that extra money you
spent for nothing. Could you stand that, really? Of course not. Are you
the kind of humble man to just back down and submit to your loss? Hmm,
even a pure and innocent kid like me finds that hard to believe."

Inukashi whistled. A few dogs that had been laying low near the walls
stood up. He whistled again, this time at a slightly lower pitch than
before.

The dogs surrounded Rikiga. Without so much as a snarl, they formed a
circle with Rikiga at the centre.

"Don't assume they're just normal dogs that are a bit on the big side,"
Inukashi said. "These guys have been trained to be guard dogs since they
were born. I trained them myself, you'll see they're not just any kind
of dog. What would I call them\el yeah, like elite troops trained
exclusively for the offense. They'll latch onto human throats---hell, even
a tiger's. It's too bad we don't have any tigers around here. We got
tons of humans, though."

Rikiga clutched his throat, and shrank back. A pronounced fear swam in
his bloodshot eyes.

"Inukashi\el cut that out, that's a stupid joke." He knew it was no
joke. Rikiga's voice cracked, and the fear in his eyes deepened.

Inukashi repressed his emotions, and continued speaking in a flat tone.
A cold, inscrutable voice was much more fearsome than a rough and
aggressive manner. He had learned that from Nezumi.

"Only Nezumi was able to escape from these guys. But barely. They
managed to chomp down on his shoulder. Pretty deep. He didn't make a
sound, but I think it must've been painful."

"That Eve, huh\el what an accomplishment."

"Hmph," Inukashi sniffed scornfully. "If you've got better moves than
Nezumi, old man, you'd be able to make it through. If not---"

"As if I would be able to scurry around like Eve does. Just climbing the
stairs leaves me out of breath these days, and I know it's nothing to
brag about." Rikiga sighed deeply, and let go of his throat. "Fine,
Inukashi. I lose. This is your kingdom, after all. I could struggle all
I want, but I wouldn't be able to win."

"Feel like coming clean now?"

Rikiga glanced furtively at Inukashi's face as if to gauge his mood.

"Starting to resemble Eve more and more. Don't let him poison you.
Nothing good will come of it. Actually, you might be beyond all help
already."

"That was the most useful piece of advice I've ever gotten from you
since we met, old man. Thanks. But you don't need to worry. Once this
business is over and done with, it's good-bye to him for good."

This was his honest intention.

Inukashi didn't like to be around Nezumi. He couldn't see through Nezumi
at all, nor could he place a finger on him. But despite that, Nezumi had
a strange magnetism about him. Inukashi found himself entangled in
Nezumi's web. Like Rikiga said, he was being poisoned by him.

\emph{Danger, danger. Gotta say good-bye.}

"Good-bye? Are you leaving this place?" Rikiga asked.

"Never. This is my kingdom, I would never leave. I wouldn't even hand
this place over if No. 6's army came crashing in. I'll be saying
good-bye, but I won't be the one leaving. It'll be Nezumi."

"Eve?"

"Yup. The fraudster actor." Inukashi licked his lips. They felt dry.

The dog that had been nursing Shionn gave a wide yawn.

"He's a wanderer. He appeared in this place out of nowhere, and decided
to stay. Eventually he'll go wandering again. He's like a whimsical
cloud. He'll rain himself out for a bit, and then he'll disappear over
the mountains."

"I see. So that's what you think of him."

"That's what I expect him to do."

\emph{I'll live on this land for the rest of my life. But he'll probably
disappear.}

It was a gut instinct. He had nothing to prove it. He had heard nothing
from Nezumi himself. It was only something that he, Inukashi, personally
felt. But he felt like he probably wasn't far from the mark.

\emph{Like the clouds travelling across the sky on the wind, like petals
scattered on the surface of a river, he's going to vanish from our
sight.}

\emph{I can't wait.}

"Well, enough about Nezumi. Enough about me, too. That leaves you, old
man. So? Why did you try to lead me away from this plan? Why'd you go as
far as to put on a lame act just to make me withdraw?"

Rikiga puckered his lips, like Shionn did often. The gesture on a plump
baby was adorable, but on a middle-aged man flushed with booze, it was
rather revolting. Inukashi averted his eyes.

"You've got it wrong," Rikiga insisted. "I was just scared for my life.
You could say I got cold feet. I was sitting down with a few drinks, and
the more I thought about it, the more afraid I became of what I was
about to do. All I could think of was how much I didn't want to die, and
I just couldn't stand it anymore\el I don't know if it's because of the
alcohol, but I feel like these days, once my head gets fixed on a
thought, it just stops working. I just get stuck deeper and deeper in
the rut. You know, Inukashi, maybe I haven't got much longer to live."

Rikiga slumped his shoulders dejectedly. His eyes turned pitiful, like a
sodden puppy. Inukashi had felt pity for sodden puppies before, and
taken them under his wing numerous times. But not humans. He felt even
less inclined when that human was carrying some emotional burden.

Inukashi snapped his fingers.

A larger black dog, which had been standing in front of Rikiga, crouched
into an attack stance. It flashed its canines and gave an intimidating
growl. Its gaze was fixed squarely on Rikiga's throat.

Rikiga gave a terrified whimper. "Hey, stop it."

"I don't have time for your hammy acting, old man. That's it. I've had
enough. Just answer my question. Once you get your throat torn apart,
you wouldn't be able to talk even if you wanted to."

"I-I'm talking right now, aren't I?"

"Old man, you said before---the day before the Hunt. When I said I wanted
out from this plan, you were hell-bent on stopping me. But today, you're
saying both of us should have nothing to do with it. Some 180-degree
change, don't you think?"

"I'm inconsistent. Always been."

The black dog snapped its jaws, opening its mouth wide. Its sharp fangs
showed, and saliva dripped onto the floor. You could almost hear its
steady \emph{pat-pat}.

Rikiga clicked his tongue. "Tsk. I've gotten old, to take threats from a
dog-boy like you. Fine, I'll talk. That's what you want, right? Fine.
Damnit, this pisses me off."

Rikiga produced a small bottle of whiskey from his jacket pocket, and
drained it in one draught. He let loose a rude burp.

"Pray excuse my lack of manners, Your Majesty," he said sarcastically.
"So, Inukashi---about the strange incidents that are occurring inside No.
6. Looks like they're real. Everything seems to just have erupted all at
once. I didn't expect this turn of events. Couldn't even predict it."

"What's happening all at once?"

"Citizens dying right and left inside the walls."

"Holy City residents?"

"Yeah. Today was---what do you call it, the Holy Day, or some festival or
other, that honours the founding of the city, right? People who gathered
for the festivities just collapsed all over the place. And none of them
survived. They died. Each and every one of them."

"Is that---an accident? Like a poisonous gas leak, or something---"

"That would result in a massive death concentrated in one place. But it
looks like the commotion is happening all over the city."

"Then what---terrorists?"

"Terrorists? Have there \emph{ever} been terrorist organizations in No. 6?
That's the most thoroughly-monitored city-state I've ever seen. There's
a city that exterminates undesirables right down to the last cockroach.
It's impossible."

"Then why's it happening?"

"I don't know. I've only skimmed the news from No. 6. It pretty much
said a random accident occurred in the middle of the ceremonies that
resulted in civilian death. The ceremony was cancelled partway through."

"And where do you get 'dying left and right' from that? Are you sure
you're not just being delusional, old man?"

Rikiga's lip curled into a smug grin. "I've had a long relationship with
that city, you know. I've got my own intelligence network. But, well\el 
not all of them are trustworthy, though. Anyway, if that city's media is
saying 'a few deaths', then there has to be at least a few dozen. When
they say the cause is unclear, it means they have no clue what it is.
But this is No. 6. This city is home to some of the brightest scientific
minds. What in the world is going on that they can't solve?"

\emph{What's going on?} The thought crossed his mind momentarily, but the
answer was still shrouded in a fog. He couldn't even make heads or tails
out of it.

"You know the answer, old man?"

"Me? Obviously not. If I had that much power, I wouldn't be sitting here
being threatened by your dogs. But---think, Inukashi. That high-and-mighty
city is running itself up the wall, unable to deal with the problems
that are occurring inside it. Doesn't it make you excited?"

"Well, yeah\el " Inukashi said somewhat dubiously.

Rikiga's grin widened. He looked genuinely happy. Inukashi knew his dogs
usually made that face when they were given a pork rib.

"It's the first time, isn't it, Inukashi? No. 6 has never been this
confused\el this is the first time. Maybe it'll turn out as Eve said.
No. 6 won't last much longer. It'll crumble from the inside."

"Yeah\el "

"You know, I've never taken that fraud of an actor for his word. Neither
have you."

"No, I haven't."

"But this time around, he might not have been tricking us. That city
might fall apart, just like Eve predicted. The signs were all there.
They're just getting stronger, building up to this. And if that's
true\el then next, the big quake will come---"

Rikiga's hands came together noisily as if to squash something
invisible.

"---and flatten it."

"Ahh, I see it now," Inukashi said. "You believe Nezumi, old man. You
believed the Holy City would fall. So would the Correctional Facility.
It might become true, and not just end as a fairy tale. Which means the
gold bullion that's supposedly stored in the basement of the Facility is
starting to sound a lot more real too, along with the chance of stealing
that treasure. The possibility keeps climbing."

Inukashi pointed a finger at the ceiling. Rikiga turned aside.

"But then you started feeling reluctant," Inukashi continued,
"about sharing it with me. The more you thought about it, the more you
didn't want to hand it over. So to get your full claim over the gold,
you put on this hammy act. You're helpless, old man. Forget booze, all
that greed has probably got to your brain and turned it to mush."

"Not much better yourself. You seemed eager about the gold bullion. You
were licking your chops, you were."

"Yeah, I'm eager alright. It still makes me drool. But let me tell you,
until now I've been on the fence. I was pretty suspicious about whether
there was really gold in the basement of the Correctional Facility. But
if you're going so far as to put on an act to snatch it all for
yourself, then\el heh heh, I think now I believe it a lot more. You got
your information from a girl named Suru, right?"

"Yeah. No. 6 executives are her best customers. When a guy tells stories
to his prostitute in bed, it's bound to be trustworthy."

"I see. So, No. 6 gets to be wiped out and we get rich at the same time.
Sounds awesome. So great, in fact, I think flowers are going to sprout
on the top of my head."

"If everything goes well."

"What? Don't rain on my parade here. I've had enough of your theatrics."

"That's not it." Rikiga walked over to the windowsill. The dogs silently
made way for him.

"Inukashi\el "

"What?" Inukashi snapped. "We gotta get going, or else---"

"Do you think it'll really be destroyed?" It was a dazed murmur. "Is No.
6 really going to disappear entirely?"

"Who knows." That was the only answer he had. Rikiga continued to mumble
as he stared out the window. Inukashi's reply had probably not reached
him.

"But\el if that really happens\el what'll appear in its place?"

"Huh?"

"A world without No. 6\el once that \emph{thing} disappears, what'll happen?
What's going to appear out of it?"

Inukashi felt like someone had bumped him roughly on the shoulder. He
sucked a breath in. He felt like he was breathing in tiny shards of
glass. His chest pricked painfully.

A world without No. 6. The aftermath.

He had never thought of it.

He couldn't even imagine it.

\emph{What would appear?}

He tightened his grip around the handle of the bag.

"I don't have a clue. I just know one thing is for sure."

Rikiga turned around and blinked at him.

"Money is money. No. 6 could disappear tomorrow, or it could
last for a thousand more years. It doesn't matter. It doesn't matter
what appears. That gold is a hell of a lot of treasure, and that's never
gonna change."

"I see." Rikiga shook his head, grinning. "You're a tough one. Hah. You
might be an even tougher cookie than Eve. I should watch out for the dog
instead of the fox, shouldn't I?"

The ambiguity was now wiped clean from his tone, and Rikiga's face
turned back into the one of the alcoholic that Inukashi knew so well.
This was the countenance of a greedy but cowardly man, indulging in both
booze and women alike, living no dreams---just harsh reality. Inukashi
somehow felt relieved.

"Let's get going, old man."

"Yeah," Rikiga answered promptly this time, and started walking.
Inukashi snapped his fingers, and a few dogs sprang up and bounded ahead
of Rikiga out of the room.

"Are you taking them, too?"

"Yeah. They'll be much more useful than what's inside this bag."

Shionn began to fret. The female dog swung its head around and licked
the tiny body gently with a warm, soft touch. Inukashi remembered it,
too. The baby would probably soon fall fast asleep.

\emph{See ya, Shionn. You wait here. Be a good boy and watch the house with
the dogs while I'm gone.}

\emph{I'll come home.}
\emph{I'll come home for you someday.}
\emph{Wait for me.}

"Mama, mama, mama," Shionn called, right before he was about to step out
of the room. Inukashi closed his eyes, and slowly pulled the door shut.