% !TeX spellcheck = en_US

\chapter{Out, out, brief candle}

\myepigraph{Tomorrow, and tomorrow, and tomorrow\\
	Creeps in this petty pace from day to day,\\
	To the last syllable of recorded time,\\
	And all our yesterdays have lighted fools\\
	The way to dusty death. Out, out, brief candle.\\
	Life's but a walking shadow, a poor player\\
	That struts and frets his hour upon the stage . . .}{Shakespeare, \emph{Macbeth} Act V Scene V}

\lettrine{J}{ust once}, he heard footsteps approach. Someone was trying to run up the
stairs. But the footsteps died along with a gunshot, a scream, and
someone tumbling down the stairs. He didn't have to see it to know what
happened. The same stairs that Shion had flown up moments ago was
probably spattered with someone's blood.

Not only the stairs. The floor, the entrance, and the consultation room
were probably smeared with blood and littered with broken objects in a
horrific scene. A body or two probably lay on the floor.

\emph{What about the doctor?} What had become of the man who saved Nezumi's
life?

"Don't move." Nezumi restrained his arm. "Don't move yet."

Shion, Inukashi, and Rikiga all held their breaths and tensed as if they
were bound by his words. Even the dogs lay low to the floor, unmoving
like boulders, save to growl softly at the footsteps.

One minute, two minutes, three minutes\el 

"Freedom for No. 6! Freedom for all of us!" A hoarse, high-pitched
scream resounded, its gender indiscernible. Right afterwards, angry
voices and the sound of fierce beatings were heard through the window.

\emph{It's the same.} Shion made a fist. His palm was damp with perspiration.

It was the same---no different from the Hunt in the West Block. The
brutality he had seen under the thick snow clouds was taking place again
right here.

Stealthily within the walls, openly outside of them---that was the only
difference.

The sweat stung the countless cuts on his palm and made it throb
slightly. Sweat streamed down his cheek, and entered his mouth.

In No. 6, he used to feel trapped and suffocated, like being forced to
wear clothes that didn't quite fit. But until Nezumi had saved him and
they had begun to live in the West Block, he had never had much
difficulty dealing with these vague doubts and feelings of suffocation.
Not until he was given a chance to look at No. 6 from the outside. In
fact, he had taken comfort in No. 6's cleanliness and abundant
lifestyle. It was true. He had been devouring this comfort and taking it
for granted. Back then, the Security Bureau's existence hardly crossed
his mind. It never had to; the days still went by. On the surface, time
passed peacefully without incidence.

When had it all begun?

Shion was wheeling his bike across the park after his shift. He was
allowed to ride his bicycle in the park, as long as he didn't go over
the speed limit. But the spring sunset was so beautiful that Shion had
felt like taking a stroll to take it all in.

The sky was divided into dark pink, red, and carmine. The streaming
clouds caught the sun, their edges glittering golden. The sweet
fragrance of the flowers blended with the refreshing scent of new
leaves, enveloping the passersby.

"Ah, the end of another day."

"It was wonderful, wasn't it?"

"All's right with the world, as they say. What do you say to topping it
all off with a mouthwatering meal and some excellent wine?"

"Oh, how splendid. That sounds great."

He could hear the lighthearted conversation of a young man and
woman---were they lovers, husband and wife, or good friends?

\emph{They're right. It's a perfect evening to enjoy wine over a nice meal in
the company of someone close}, Shion had thought, feeling a comfortable
sort of weariness and hunger himself.

\emph{All's right with the world.}

Neither Shion nor that man or woman had any clue about what lurked in
the depths of that day. Most people didn't. It wasn't because of the
dreamy spring evening. Through hot summer days, sleety mornings, in
autumn sunsets, they had never noticed.

The majority of the citizens were neither concerned nor interested about
the Security Bureau. They probably had no idea that it would bare its
fangs so ferociously at the slightest voice of protest from the
citizens. They thought of the Security Bureau as an organization that
maintained and protected their safety---an organization for the
people---were they not? And they believed in this clause---

\emph{No. 6 exists for its citizens. It exists to ensure a plentiful and
comfortable life for its citizens. No one shall be permitted to threaten
the safety, activities, and lives of the citizens in any way whatsoever.}

They believed the city would also abide by this clause of its own City
Charter. The people relied upon the city, left everything in its hands,
and unwittingly allowed themselves to be pulled along by its flow.

And this was the result.

The sweat stung in his wounds. Nezumi's hand was still restraining
Shion's arm.

\emph{If this was the result, then Nezumi---where did we go wrong? Do you know
the answer?}

\emph{No---I'm the one that needs to know the answer, not you. I was born as a
No. 6 citizen, reaped all of its benefits, and lived without any concern
for the outside or inside. I'm the one who has to reach out and grasp
the answer, in exchange for always choosing the comfort of lending
myself to the least resistant path, rather than struggling against the
current.}

\emph{I know. Meeting you has taught me, and so have the words we exchanged
and the days we spent together. I need an answer that I've grasped with
my own hands, rather than one that's been prepared for me.}

\emph{Mine, and not someone else's.}

\emph{Or else I'll end up with the same result again.}

"They weren't after us, then." Shion sensed Inukashi twitching his nose
in the dark. "I was totally under the impression that\el the doctor
tipped the Bureau off. Looks like that wasn't it."

"No, it definitely wasn't."

\emph{Traitors.} That was what the Bureau officials had said. The target of
their sting had not been Shion, but the others---the doctor, and Yoming.

Inukashi twitched his nose again. "Nezumi\el aren't we safe now?"

"Wait. It's still too early."

"Tsk, paranoid as always."

One minute, two minutes, three minutes\el 

"Hey, Nezumi."

"Don't rush. But---alright, it should be fine now. Don't turn on the
lights. Leave them off, and move quietly."

Nezumi pushed the door slightly ajar, and whistled softly. Hamlet poked
his head out from Shion's pocket, alighted on the floor, and dashed
through the open crack.

Momentarily, a lighthearted squeak greeted them.

\emph{Cheep cheep, chit-chit-chit.}

\emph{Cheep cheep, chit-chit-chit.}

"Alright, let's go downstairs. Avoid the elevator, just in case." Nezumi
swiftly wrapped the superfibre cloth around himself, and slipped into
the hallway.

"What the hell was that?" Shion saw Rikiga's mouth gaping open by the
light that spilled in from the hallway. "Wasn't he unconscious just now?
Or was that an act, too? Playing the part of a prince on his deathbed?"

Inukashi shrugged.

"He ain't no prince. He's an animal. Like a savage beast. No way he can
sleep in the face of oncoming danger. He sensed the Security Bureau guys
before my nose could sniff them out, damnit. Pisses me off."

"I see. Now I have a good idea of how Eve could have survived this far.
With instincts as sharp as those, and that cautiousness to boot\el "

"Falling in love all over again, old man?"

"I just confirmed my notion that he doesn't have an ounce of good in
him."

The humans, dogs, and mice crept down the stairs cautiously, step by
step. There was a pool of blood in the stairwell. At the bottom of the
stairs was the owner of that blood, a man in his forties or fifties
lying on his back.

The lower floor was just as grisly as Shion imagined. Blood had sprayed
the walls and the floor. There was broken glass and furniture strewn
about, all soiled with dirt and blood. At the end of the hall, a
blue-grey door was half-open. The room was dark and the air inside
cold---a basement room, perhaps.

A man lay slumped against the door, and the nurse at his feet. A figure
clad in a lab coat lay a few metres away. The three of them were
perfectly still.

"Doctor!" Shion ran to him and lifted him up in his arms. The chest of
the man's lab coat was dyed in blood. "Doctor, answer me, please."

His words felt painfully empty as they escaped his lips.

The doctor was clearly almost dead. There was no hope for him.

"Doctor, doctor! Open your eyes, please," Shion continued to implore
with empty words. That was all he could do.

The door to the consulting room opened, and Aria appeared, evidently
from the elevator.

{\sffamily "Vital signs: none. Vital signs: none. Vital signs---minimal. Minimal."}

The doctor's eyelids slowly lifted.

{\sffamily "Vital signs: minimal. Commencing treatment."}

Several tubes extended from Aria's torso, and connected to the doctor's
body.

"Aria\el don't. It's no use\el "

{\sffamily "No use. No use\el cannot comprehend. Continuing treatment."}

"Doctor, what\el why did this happen?"

"\el He\el broadcasting\el from the basement of this clinic\el calling\el 
on his comrades to defeat No. 6 together\el "

{\sffamily "Vital signs: minimal. Probability of recovery: one percent. One
percent."}

"I wanted revenge\el on No. 6\el revenge\el "

"Doctor," Shion pleaded.

"I wanted to\el destroy this world\el and build it\el anew."

Suddenly the doctor dug his fingers into Shion's arm.

"Shion," the man called his name in a clear, strong voice. "I leave this
in your hands."

His eyes were open wide, fixed intently on Shion.

"I leave it\el in your hands. Don't ever make\el No. 6\el this kind of
city\el again. Please. I'm leaving it to you."

The doctor's fingers slipped out of his own. The light went out of his
eyes as they glazed over. His whole body convulsed.

Then, it was over.

{\sffamily "Vital signs: minimal. Minimal. Unable to register. Unable to register.
Aborting treatment."}

"Doctor\el "

Shion laid the man down, and put a hand over his eyelids. With his eyes
closed, the doctor looked peaceful and relaxed.

"Leave it to you, huh." Inukashi let out a long sigh. "You guys are the
ones who built No. 6 in the first place," he said to the doctor's body.
"But once something goes wrong and it spins out of control, you just
shove it off onto someone else? Not exactly a friendly gift to leave to
someone, is it? A little selfish, don't you think, doctor? I guess it's
none of my business, though."

"Inukashi, what good is it to mouth off at a dead man? He's not going to
hear any of it. Poor guy." Rikiga clasped his hands in front of his
chest and bowed his head.

"The hell are you doing?" Inukashi asked.

"I'm praying to God, can't you tell? O God, please forgive this sinful
man. May you bless his soul and let him rest in peace by your side."

"Hah, you don't even believe in God. What an act. Oh, wait---you must be
praying to God Moneybags Almighty, right, old man?"

"Rotten kid," spat Rikiga. "You never get tired of spewing insults, do
you? Once this settles down, you're in for it. You remember that."
Rikiga unclasped his hands and rolled his shoulder joints.

"So, what now?" he said. "We've accomplished our big goal of destroying
the Correctional Facility. As for me, I'm in the mood for heading back
to the West Block and crawling into bed. I feel like curling up and
dreaming about digging up gold from underneath the Correctional
Facility. I'd wake up to the best morning ever. It puts me in a good
mood already."

"Old man, you can be sarcastic all you want, but Nezumi's not gonna
respond. I'd get a better response out of complaining to that corpse
over there." Inukashi chuckled spiritedly, his shoulders shaking with
his laughter.

"But truth be told, I'm all for crawling into bed myself. And, well,
there are a lot of things that I want to mull over. It doesn't help that
it's kinda creepy being inside No. 6. It gives me a bad vibe, makes my
skin crawl. Shion, don't you wanna go home, too? It's not too far from
here, is it? Your mum must be waiting for you."

"Yeah\el " Shion's house was within walking distance from here.

"Don't you wanna see your mum again?"

"Yeah, I do."

"Karan, huh. I'd like to see her too," Rikiga murmured wistfully.

\emph{Mom, there's no telling how much I've probably made you worry. I want
you to see that I'm doing well. I want you to see that I'm safe. I want
to say sorry. I want to apologize from the bottom of my heart. Mom, I'm
sorry.}

Shion was overwhelmed with nostalgia and love for his mother. He
remembered the scent of freshly-baked bread. Yearning. Love. \emph{I wish I
could see you.}

But the only place he wanted to return to was that basement room
littered with books. He wanted to go back to that room and its countless
volumes, the bed, the stove, and the tattered chair.

\emph{I want to go home.}

Shion burned with longing.

\emph{I want to bring back those days, those moments I spent with Nezumi in
that room. I would give up anything.}

But he would not return. Those days had long passed, never to come
within his grasp again.

Ever.

It was a premonition---a premonition which he almost certainly believed
would come true. Shion purposely averted his eyes from it. He knew well
it was a sign of weakness, but he did it anyway.

Shion stood up and turned to face Nezumi.

"Can you move?"

"Somewhat."

Nezumi lifted himself up from where he was leaning on the wall, and let
out a long breath. A thin sheen of sweat covered his forehead.

"Aria, can you measure his blood pressure, pulse, and body temperature?
Based on that, tell me what an appropriate treatment for him would be."

{\sffamily "Understood. Understood. Blood pressure, pulse, body temperature,
commencing measurements. Commencing measurements."}

"No need." Nezumi shook his head in refusal. "It's a waste of time."

He brushed off Aria's extended pipes, and sighed again.

"M'lady, with all due respect, allow me to politely decline your offer.
We don't have time for treatment."

Aria blinked, and her eyes turned yellow.

{\sffamily "Due respect, decline, time. Cannot comprehend. Cannot comprehend.
Aborting measurements."}

"Nezumi, you plan to go?"

"Of course."

Inukashi and Rikiga looked at each other.

"Go where?" Rikiga asked. Inukashi scowled in silence.

"To city hall," Shion answered.

"City hall? You mean the Moondrop?"

"Yes."

"Wh---do you know what state that place is in right now?" Rikiga
exclaimed. "I mean, I don't know myself, but\el it's sure to be chaos.
The Security Bureau is cracking down on citizens left and right---shot
some of them, even. They've probably gotten word of what happened to the
Correctional Facility. The rest of the people will find out about it
soon---No. 6 doesn't have the power to suppress the spread of information
like it used to. The confusion is only going to get worse. It'll be
completely out of control."

"That's why we're going." Nezumi smiled wanly. Nezumi had countless deft
ways to smile. This one was a cold smile with a hint of mockery.

"It's our once-in-a-lifetime chance to see No. 6 perform its last dying
shriek on stage. We better hurry, or we won't even get standing seats."

"With the state you're in?" Rikiga replied incredulously. "You can't do
it, Eve. Sure, you might be stronger than you look, but you're human.
You have limits. Don't do it. No. 6 will play its star role even if
we're not in the audience. It'll pull off its role of the wretched,
self-destructing giant with flying colours."

"You're telling me to throw away this chance and retreat with my tail
between my legs?"

"Yes. You two destroyed the Correctional Facility, and that definitely
helped trigger the demise of No. 6. That's amazing, and you've done
enough. More than enough. Eve, Shion, don't go further than this. Back
off and let nature take its course. It's time for you two to retreat
backstage."

"Being backstage staff is not my style," Nezumi said. "Neither is
throwing away a chance that's already in my hands."

"Your greed is bottomless," Rikiga said in disgust. "Listen to me, don't
make me say this again. Your part is over. It's not worth it to risk
your lives to stand onstage."

Shion stood in front of Rikiga and shook his head.

"Rikiga-san, we have to go. We have to go, no matter what."

"Shion, you too? Why? What for? You were able to escape the Correctional
Facility, a damn miracle it was. Why won't you retreat to where it's
safe? Doesn't your life mean anything to you?"

"We're not going because we want to die," Shion said firmly. "We're
going because he's the only one who can stop Elyurias."

"Elyurias?" Rikiga's eyes darted about. "What is that? Someone's name?"

"She's the queen who once ruled over this land. I don't know if 'queen'
is the right name for her---she never tried to dominate her subjects or
drain their wealth like humans do. She only protected the rules of the
forest, and the workings of nature."

"Shion\el what are you talking about?" Rikiga drew his chin back. A bead
of sweat rolled along his jawline, across his five-o'clock shadow.

"Humans---the humans who attempted to build No. 6 on this land trampled
Elyurias' land and tried to reign over everything within it. They burnt
the forests, massacred the Forest People, and tried to build a world
that was solely for themselves. Only their own abundance, their own
wealth, their own safety and prosperity was their concern. They built a
disconnected utopia on a foundation of others' sacrifices."

"Shion," Nezumi called. It was a quiet, beautiful voice. "You know
everything?"

"No. What I know is probably only a small part. I only read what was in
Rou's chip."

Nezumi sank to the floor. He curled up, and muttered, "I see."

"Hey, keep going," Rikiga said. "I still have no idea what you're
talking about. Sounds like complete gibberish. So how is
Elyuri-what's-her-face related to what's happening to No. 6? What do you
mean when you say Eve is the only one who can stop her? Shion, give me
the details."

"I'd love to hear all about it, too." Inukashi clicked his tongue
lightly. His hands were full with numerous bags.

"What---where did you go? What is all that?"

"Clothes and food. Bland soup and bread just doesn't do it for me. And
besides, if we're going to watch a play, I think we need to look a
little more decent. They wouldn't even let us in the standing seats."

Inukashi dug out a chunk of meat and a roll from the bag, and tossed it
at the dogs. The dogs promptly pounced without even raising their
voices. The mice skilfully stopped a tumbling roll, and lined up to
nibble at it.

"Good. Eat," Inukashi said proudly. "Eat as much as you want. You guys
worked hard. You did a good job. This is your reward. Heh heh, that's
the amazing thing about No. 6. Even a clinic in the middle of nowhere
like this has a kitchen full of food. Not to mention expensive-looking
clothes. Heh heh, heh heh heh heh, this place is full of top-notch
items. I could get a good price for this in the West Block."

"You've come this far and you're still thieving?" Rikiga said.

"Who cares? The doctor is dead. Dead people don't need food or clothes."

"Well\el I guess you're right. Hey, pass me some ham, bread, and those
blue pants."

"I'll sell them to you for one silver piece."

"Inukashi, you bastard, you just said goodbye to your ride," Rikiga
snarled. "You can walk back to the West Block."

"I was kidding, yeesh! Old man has no sense of humour. That's why all
the women trick you out of your money. Anyway, come on, let's eat. We
gotta prepare for the road ahead."

Inukashi turned a bag upside down. Ham, apples and bread tumbled out.

"Let's have a banquet while we listen to the story Shion The Great has
got to tell. Sounds like an interesting one."

Inukashi's eyes glittered from underneath his long bangs. His pink
tongue flitted across his lips again and again.

"Maybe he'll tell us who Nezumi really is. This is bound to be
interesting. In fact, I'm way more interested in this than a drama
starring No. 6, to be honest."

Shion scooped up an apple.

"Nezumi, can you eat?"

"Ah, I haven't recovered to that point yet. I'm not hungry."

"I figured as much. Aria, can you give him some glucose solution?"

{\sffamily "Understood. Understood. Commencing glucose transfusion."}

"I'd like a transfusion of wine," Rikiga chimed in.

"You'll have to settle with grape juice. There were two bottles in the
fridge." Inukashi handed a bottle of reddish-purple liquid to Rikiga.

"Alright, Shion. We're all ready. Spit out everything you know." His
pink tongue flitted across his lips again. Shion peered at Nezumi, apple
still in hand.

"Nezumi\el is it alright?"

Nezumi inclined his head very slightly. He propped his knees up, and put
his face down on his arms. He looked like he was either crying, or
bearing a wind that was blowing against him.

Shion took a bite of the apple. Its tart juice burst inside his mouth.

Inukashi and Rikiga leaned forward, Inukashi clutching a piece of bread
and ham in each of his hands, and Rikiga gripping a bottle of grape
juice.

The two had put their lives in the balance for Shion and Nezumi. They
had acted on Shion and Nezumi's word with next to no knowledge of what
they were doing. In other words, they had believed in the two boys. They
had invested their lives into their belief. Telling them everything was
the only way to match the leap of trust they took, and to answer to
their dedication.

He knew Nezumi must feel the same.

Shion began to speak.

\myspace

"I don't think I need to tell you about how No. 6 was created. Humankind
tried to build a utopia once again on this planet, which was half
destroyed by human hands.

Before No. 6 was born, this area was a miraculously preserved stretch of
beautiful, abundant forest. I said miraculous, but this land---its
forests, woods, and lakes--- was actually meant to survive. Elyurias and
the Forest People protected this realm. It was because of her that this
land's wildlife was spared damage.

No one can explain who or what Elyurias is. Even the name Elyurias was
given to her by a researcher. ---I met him, in the basement of the
Correctional Facility."

"Basement of the Correctional Facility?" Rikiga choked on his juice and
had a coughing fit. "So there was a basement in there, after all!"

"There was."

"How about gold bullion? Was there gold bullion in there, Shion?"

"Gold? No. There were people living underground. Back when the
Correctional Facility wasn't such a brutal and vigilant incarceration
facility, people who escaped but couldn't return above ground began to
build their own underground world in secret. The leader of this group
was called Rou."

"\el So there was no gold, after all." Rikiga hunched over, clearly
crestfallen. Inukashi guffawed, baring his teeth.

"Rou was a member of a revival project team chosen to design and build
No. 6 on this land. Before No. 6 was created, there used to be a small,
pretty town at the edge of the forest. People who survived through the
waste and decay lived modestly here in a tightly-knit community. This
town was the mother of No. 6.

Bright young people were chosen from that town to form a team to build a
utopian city."

"My town." Rikiga drew himself up. "That's the town I was born and
raised in. It used to be called the Town of Roses---that's how beautiful
it was. Karan also used to live there."

"No one asked you, old man." Inukashi bared his teeth even more. "If
you're not gonna shut up, I'll tear apart your throat for you."

"I'd like to see you try. You can rip my throat out, but I'll still keep
talking. Oh, yes, that revival project team. I heard about them. Back in
those days, I was still a pimply youngster chasing after girls and
blushing at their ankles. They were holding some kind of selection exam
to gather skilled young people from the science fields to make a
brighter future for humankind. Yes, yes, I remember."

Rikiga folded his arms and nodded enthusiastically.

"That was how No. 6 began. And not long after that, No. 6 was born as
the sixth and best, most optimal utopian city. It grew at an astonishing
speed."

"And before you knew it, you dropout failures were shoved outside the
walls. Pity," Inukashi said nastily.

"You should be the one keeping your mouth shut, Inukashi. I'll yank out
that long tongue of yours and turn it into mincemeat. In those days, I'd
just become a journalist. The fact that the city-state was walling
itself in, trying to build a barrier around itself, just seemed really
shady to me. I wrote a whole slew of articles that talked about it. It
was natural that I was thrown out of the city. It was around that time
that No. 6 became more and more intolerant and domineering."

"It was precisely that.

No. 6 grew at a stunning rate. Its infrastructure, governing bodies and
regulations were swiftly and skilfully laid out. In the midst of it all,
Rou met Elyurias.

Rou himself wasn't able to define Elyurias well---was she a forest spirit?
Or a species of animal unknown to humankind?

The only thing he knew for sure was that Elyurias existed long before
the birth of humankind, protecting this land. The Forest People
worshipped her, revered her, and lived in harmony with her."

"Right, so who are these 'forest people' that you keep talking about?"

"Will you shut up, old man? Can't you listen quietly for once? Geez."
Inukashi gave an exaggerated sigh.

Shion turned and glanced at Nezumi slumped against the wall. His eyes
were closed. His profile was beautiful, but it looked somewhat
artificial.

{\sffamily "Glucose transfusion, 50\% complete. 50\% complete. Continuing
transfusion."} Aria's eyes blinked green.

Nezumi said nothing. His eyes remained meditatively shut, his body
perfectly still.

\mybreak

"According to Nezumi, the Forest People are those who have made the
forest their home. Since ancient times, they've lived in harmony with
the wind, the earth, lakes and rivers, and the sky.

To borrow Rou's words, the forest is a place both of their birth and
upbringing. They nurtured, respected, and continued to protect the
forest. They lived peacefully within the bounds of nature without
desiring prosperity or development. Even those who lived in the Town of
Roses had no idea about their existence.

Elyurias' power wasn't what allowed the abundant forest to survive on
this land. It was because the Forest People protected it. Through the
long, perpetual flow of time, they continued to protect the forest.

Nezumi is a descendant of those Forest People."

Inukashi shifted.

Rikiga let his empty juice bottle roll across the floor. It continued to
roll until it hit the doctor's arm, and stopped.

\enquote{Nezumi is a descendant of the Forest People. He's also a descendant of
the \enquote{Singers}.}

"Singers?"

"Yes, Singers---those who had the power to appease Elyurias and converse
with her. There were always a number of Singers among the Forest
People.

Neither Elyurias nor nature were embodiments of pure compassion and
generosity. On the contrary, they could easily turn terrifying. The
Forest People knew this.

Both nature and Elyurias could bare their fangs and attack suddenly at
any time. Their power was absolute---no human could compare. That made
them all the more dreadful.

Yes, the Forest People knew fear. They knew how to fear as well as
revere. Singers could appease Elyurias' wrath with their voices, and
were able to exchange words with her. They had the ability to mediate
between humans and nature. Nezumi had this ability, and so did his
mother.

Rou ventured deep into the forest, met Elyurias and the Forest People,
and reported their existence to No. 6. He had no idea that this had
planted the seed for the Mao Massacre."

"The Mao Massacre?" Creases appeared between Rikiga's eyebrows.

"Yes. 'Mao' apparently refers to the area near the lakeshore where the
Forest People lived. They had a settlement there. It's where the airport
is now. Apparently the lake was drained to build the airport. I had no
idea."

"I didn't know, either," Rikiga said. "I was already kicked out when
they started building it. A massacre, huh\el which means No. 6 must have
invaded the Mao area and tried to wipe out its residents?"

"Yes."

"What for? Did they need land for the airport?"

"No. What they really wanted was Elyurias."

"What for?"

\emph{What for.} Rikiga kept repeating the same question.

What for, what for. Really, what was this for? What made people this
brutal, this ruthless?

Shion looked down at the doctor's body. It had lost all its human warmth
and was now a cold corpse. The nurse lay beyond it, and beyond her lay
an unnamed man.

What made them capable of taking the lives of others so easily?

In the short instant that he closed his eyes, he could see the Hunt
unfold again behind his eyelids. He could hear the groans of the people
loaded onto the truck's cargo bed. In his ears rang the screams of the
people who had died, piled on top of each other in the basement of the
Correctional Facility.

\emph{What for?}

Perplexity---not anger---snagged Shion and would not release him. Also,
fear.

What set him apart from the central figures of No. 6? Hadn't Rou said so
himself? Everyone was young; everyone had hopes to build a utopian city.

It had taken mere decades for these hopes and ideals to mutate. Mere
decades. Shion swallowed his breath.

\emph{What kind of person will I be in a few decades? Would I still be able to
hold the same hopes and ideals that I have now, at age sixteen? Would I
be connected in any form with this kind of brutality?}

The terror was enough to make him shiver.

"What did they want Elyurias for? Her special powers."

"Special powers?" Inukashi's mouth fell open as he stared at Shion.

"Yeah. Elyurias embodies the form of a wasp."

"Wasp? Like those things that fly around flowers and stuff?"

"Those would be honeybees. Elyurias is a parasitic wasp. She lays eggs
in her hosts."

Inukashi's mouth fell open wider. No words came out.

"The eggs hatch inside the host's body. They grow without the host's
knowledge, become pupae, and emerge as adults. They tear through the
host's body to escape, leaving him behind like an empty shell. This is
what's happening to No. 6 right now.

Elyurias' children are all beginning to hatch. They're children who fed
off No. 6 citizens in order to grow.

I told you earlier that Elyurias looks like a wasp. But she isn't one.
No one knows who or what she really is. Rou has recorded that he thinks
she might be between a human and a god. That's why she---since she lays
eggs, I'll call her a 'she', but I don't think there's much meaning to
distinguishing her sex. Maybe she's taken the form of a wasp because it
was a convenient form for her to lay eggs inside the hosts. Maybe she
only appears as a wasp to human eyes.

She has an enormous intellect---and intellect that far surpasses that of
humankind. And she had the power to exert perfect control over the
hosts.

Because of that power, the hosts were programmed to take actions that
were favourable to the children of Elyurias, oblivious to the fact that
they were being leeched from. For example, their instincts for sensing
danger were honed, and they became increasingly sensitive to their
nutrition. They were controlled to take every effort to maintain a
healthy body; their personalities turned gentle; they began to avoid
disputes. It makes sense that No. 6 citizens were the only targets.
Think about how malnourished the West Block people are, coupled with
their substandard environment\el as hosts, they were out of the
question. Nezumi mentioned before that the parasitic wasps have gourmet
tastes. He turned out to be right."

"Ironic, ain't it," Inukashi muttered. "We starved, we froze, we didn't
know when we would die\el but because of that, we West Block residents
were spared."

"These were the absolutely necessary conditions for the eggs: the host
needed to be alive when they hatched, and the host needed to be healthy.
Even Elyurias couldn't turn the West Block into a paradise. But she
didn't need to."

"You've already got the best hosts you could ask for in No. 6."

"That's right."

"The wasps controlled the humans?" This time, it was Rikiga who opened
his mouth. He breathed raggedly.

"Yes. They can make people act according to their every whim. It's not
unusual for parasitic organisms. A certain schisotome blindfolds the
human immune system and makes it think that it's harmless. A species of
parasitic wasp injects its DNA into the caterpillar that it chooses as
its host, and disables the caterpillar's immune system completely. But I
don't think there's any other example of a highly-functional parasitic
organism like Elyurias, who chooses humans as her host and controls them
completely without the host's knowledge."

"\el And No. 6 wanted that power---the power to completely control and
dominate over humans." Rikiga made a choked noise in his throat. It was
a dry, brittle sound, similar to the frigid winter wind.

"No. 6 had tried to attain Elyurias' power.

They came to know of this mystical power through Rou's investigative
reports, and tried to use it in building their government.

Elyurias' characteristics remained a mystery; however, everyone in No. 6
thought of her as a mere insect, a mutant species. They did not think of
her as a being halfway between man and god, like Rou did. Not one of
them saw her as such. Every person believed firmly that no being more
superior than man existed.

Elyurias was nothing but a queen bee with an unusually large intellect.
It would be no large task training her and controlling her according to
their needs---that was what they believed.

An investigative squad was formed for the capture of Elyurias, and they
set foot into the forest. There, they met adamant resistance by the
Forest People.

Elyurias did not constantly reside in the forest. She appeared once
every few years, or once every few decades---always unexpectedly.
Everything about her---what the necessary conditions were for her
appearance, when she laid eggs, and how long she lived afterwards---was a
mystery. After she laid her eggs, Elyurias always disappeared. She
withdrew from human eyes. A new queen bee emerged from one of the eggs
she laid. It was never clear whether that was going to be a few years or
decades later.

No one has seen Elyurias' body. From the time this forest appeared on
this land, Elyurias had been repeating the same routine, but not a
single person had ever seen her corpse.

Among the Forest People, it was said that Elyurias was immortal, that
she revived endless times---that her corpse decayed somewhere where no eye
could see, and became the forest itself.

When Elyurias appeared, the Forest People appeased her with song. They
prayed and pleaded with her that they would not become hosts. They
carried out rituals, and offered a Godly Bed. The Godly Bed was a type
of man-made host, prepared from animal brains. It was an offering for
implantation. Led on by the song, Elyurias would lay her eggs there.
After the eggs were laid, the Godly Bed never seemed to rot or dry out;
instead, it maintained an adequate level of moisture and freshness until
it rotted away with the emergence of the adult wasp.

Yes, it was the same---the same way in which human hosts aged and died
within the blink of an eye immediately after the adult wasps emerged.

The Forest People protected the Godly Bed with their bodies and souls.
It was part of their promise with her. This rule had been passed on for
ages. As long as the Forest People continued to protect the Godly Bed,
Elyurias did not inflict any harm on them. She not only protected the
people, but the forest and its land.

That was the rule.

No. 6 had burst onto the scene and wrenched everything from them. They
had burned down the settlement of the Forest People when they resisted;
they had massacred women, children, and the elderly indiscriminately.
They had taken the Godly Bed back to No. 6.

The Mao Massacre---the demise of the Forest People.

This incident took place just twelve years ago."

Shion sucked in a huge breath, and exhaled. He felt like there was no
other way to let the air reach every corner of his body.

"From here on is my guesswork, not Rou's records. I'm positive that it's
true."

Rikiga leaned forward as if to encourage him. Inukashi, on the other
hand, shrank back. He grimaced as if he had smelled some unbearable
stench.

"The upper echelons of No. 6 probably attempted to hatch Elyurias' eggs
artificially in the Godly Bed that they'd brought back, and failed. They
had no Singers, and therefore couldn't maintain the Godly Bed.
Nonetheless, they refused to acknowledge anything other than scientific
proof. But through their countless failures, one thing they realized was
that the most suitable place for the eggs to hatch and grow was inside
the human brain."

"Brain?" Rikiga grabbed his head.

"Yes. Not a cow's, pig's, or monkey's. They got as far as determining
that Elyurias' eggs hatched if they used a human brain, and that one of
them would be born the queen bee, as another Elyurias."

"And then, what\el ?"

"They implanted eggs inside a number of citizens secretly---just like a
wasp would use its ovipositer to lay eggs inside its host. It was easy
enough to give a needle during scheduled check-ups, saying it was only
part of the procedure. They chose sample citizens who differed in
gender, age, build, and environment. I was one of them. Rou was also
chosen as a host, but it seems Elyurias' will had some influence in this
case. Both of us survived because the parasite's development was
incomplete. The host always dies if the adult emerges successfully. That
means Elyurias' eggs were effective also as assassination weapons. The
upper echelons would do anything to have Elyurias in their power. They
were desperate to have her under control. Maybe they already had a faint
premonition that cracks would start to form in No. 6. Maybe they knew
that their selective and exclusive government would some day break down,
no matter how skilfully it was camouflaged. That was why they wanted
definite control over others. They wished to be the queen bee, and to
reign as the absolute, sole ruler."

"Were front-line research facilities set up in the Correctional Facility
to, um, research those\el wasps?"

"Yes. They couldn't figure out what kind of conditions Elyurias required
to emerge as an adult. I think any human effort would have been
fruitless---it would always be a mystery. But they built a research
facility anyway, to unravel a mystery that couldn't be unravelled. In
it\el there were rows of countless brains, contained in special cases.
I'm sure eggs were planted in every one."

It came back to him.

The rows of brains trapped in cylindrical cases; Safu, trapped in its
innermost depths---it all came back to him.

"I see." Rikiga stroked his chin. "In the Correctional Facility, you
could have as many brains as you wanted. Couldn't ask for a better
place."

"Makes me sick." Inukashi clutched his chest. He looked truly nauseous:
all the colour had receded from his face. He tossed his piece of bread
aside.

"I've been starved enough to eat grass and caterpillars off the ground,
but I've never felt this sick before. I don't see whatever it is you're
seeing. So---was this Hunt a massive harvest of human brains?"

"Yes. They probably wanted to experiment on human brains that have
survived harsh conditions. They wanted brains affected by various
things, like large amounts of stress, or the will to live, or fear, or
excitement."

"I\el I think I'm really going to be sick." A dog nuzzled up to
Inukashi. He buried his face in its coat and sniffed.

"These guys are\el are a hundred times, a thousand times, ten thousand
times better than humans. Shion, I'm glad I've got dogs on my team
instead of humans. I really am."

"Yeah." \emph{You're right, Inukashi. Dogs are a hundred times, a thousand
times, ten thousand times better than humans. I can see why you'd feel
that way.}

Inukashi sneezed softly. He sniffled.

"So, what, Nezumi? Are you really a surviving descendant of the Forest
People or whatever?"

Nezumi raised his face. The colour had returned to his cheeks, perhaps
thanks to Aria's care. It made Nezumi into a glowing, living being
rather than a beautiful doll.

"Yes."

"So you survived that Mao Massacre, or whatever it is. Looks like your
lucky streak takes you way back, huh."

"Sure."

Nezumi's eyes focused on Shion. Shion returned his gaze without
blinking. After a moment of hesitation, Nezumi began to speak.

"I was really young then. To tell you the truth, there's not much I
remember about the Mao area. I just remember Gran carrying me on her
back as she ran frantically through the flames. I don't know if Gran was
my real grandmother, or if she was a total stranger. But she rescued me
and raised me. After we escaped from the forest, we moved constantly
around in what's now called the West Block."

Nezumi's tone was brisk and seemed to contain no emotion.

"Gran taught me a lot of things. She was also the one who found a room
that used to be a library vault, and suggested that I live in it. I
buried myself in those books, and I grew up listening to Gran tell tales
of the Forest People. These guys---"

Nezumi snapped his fingers. The three mice scurried up to him,
squeaking.

"---were born in that room. They're intelligent and can feel emotion. So
could their parents, and their grandparents. Those kinds of animals just
seemed to gather around the Forest People. These guys and Elyurias were
both---well, we didn't call it Elyurias. We just called it the Forest God.
But I was too young to know what the Forest God was, anyway. I was
taught that only Forest People like us had a connection to these little
mice and the Forest God. But they seem completely used to having Shion
around, and they seem overjoyed that they've been given names. It was
the same with the rats in the underground realm. I was surprised, to
tell you the truth."

"Same with my dogs, come to think of it. They've taken such a liking to
Shion. They didn't even bark at him."

Nezumi smiled serenely.

"You're a mysterious one, Shion. I thought so since the first time we
met---you're a mystery."

"You're talking about the night of the storm."

"Yeah. The night we first met. But let's go back to the topic for now. I
was ten when the special gates of the Correctional Facility were
completed. The mayor was scheduled for a visit. Gran said it was our
first and last chance for revenge. Revenge---Gran said it was the only
thing she'd been living for. But a ten-year-old kid and an old woman
were no match for him. Gran had a knife hidden on her, but she was shot
on the spot trying to get near the mayor. I was caught along with
captives of the Hunt and thrown into the basement of the Correctional
Facility. It was a miracle that I didn't die. I climbed the wall of rock
as if my life depended on it, and I got to those caverns. That was where
I met Rou. Maybe that was a miracle, too. Rou gave me even more
knowledge than Gran, and when I turned twelve, he ordered me to leave
the underground realm and face a new world. At the time, Rou still had a
thread,---a thin one, mind you---of communication leading to the core of No.
6. Once in a while, No. 6 delivered just enough food and living supplies
for us to survive. I guess in the back of their minds, their conscience
still nagged them to help the man who was once their colleague. Through
that route, Rou sent in a suggestion that I be transferred to the
Moondrop. He proposed to have me examined in detail as one of the last
surviving Forest People. The mayor and his associates agreed. They'd
probably reached a roadblock in their research about the Forest God.
They were eager for any potential lead, so they jumped on the chance. On
the day of my transfer, Rou handed me a special knife that wouldn't get
caught by the metal detectors. He told me to find my own path. I
wouldn't survive if I let myself be taken into the Moondrop. There was a
good chance that I'd be dissected there. My only path of survival was to
break free and run before I reached the Moondrop. As for the rest---I
don't think I need to go into details. I was able to survive, thanks to
you rescuing me."

Nezumi looked up at the ceiling and exhaled a long breath.

"Like I said before, on that stormy night, you threw open the window and
welcomed me in. It was a real miracle. To me, you were more of a miracle
than the Forest God ever was. I felt like I was being told to live---to
live on, not give up\el If you hadn't been there, I wouldn't have been
able to survive that night. Shion, you---only you---were the one who saved
me. This time, too."

Nezumi stood up carefully.

{\sffamily "Glucose infusion completed. Infusion is complete."} Aria retreated
silently like a meek maiden.

"You saved my life," Nezumi said.

"It goes both ways. If it hadn't been for you, I wouldn't be alive,
either." Shion stood up as well.

"Hey, hey, wait a minute here. If you're gonna overwhelm yourselves with
gratitude, it should be for us. Right, old man?"

"Of course. Eve, you've just made yourself a hell of a debt. You better
be prepared."

Inukashi and Rikiga nodded in unison.

"Practically finishing each other's sentences now, aren't you? You've
sure gotten close." Nezumi smirked as he wrapped himself in the
superfibre cloth.

"If you're going to keep tabs on my debt anyway, mind giving me a ride
and dropping me off close to the Moondrop?"

"Are you really going to go?" Rikiga said in disbelief.

"Yes, we are," Shion answered. "We have to. Nezumi is the only one who
can stop Elyurias."

"Don't get ahead of yourself. We don't even know if my singing is going
to work on her yet."

"It will. Even on that cargo bed on the way to the Correctional
Facility, people still wanted to hear you sing."

Rikiga swung his arm around. His weary and bloodshot eyes blinked
repeatedly.

"Why, Eve? I thought you were going to sit back and enjoy the show as
part of the audience. Weren't you going to laugh the whole way through
while you watched No. 6 give its last dying shriek?"

"I was planning to, but it looks like my career as an actor will be the
death of me," Nezumi said ruefully. "Seems I can't stand being out of
the spotlight for more than a short while. I guess I'm not made to sit
in the audience, after all."

"This isn't the time to be showing off," Rikiga said bitingly. "Take it
seriously. I thought you loathed No. 6. Just leave it alone, and it'll
destroy itself. There's nothing more you have to do except sit back,
watch, and laugh."

Nezumi's face contorted for an instant. It did not look like an act.

"I would if I could. But Rou told me---what about the children within the
walls? What are they guilty of? He said those who twiddle their thumbs
while they watch children die are no better than the murderers
themselves."

A sigh. All emotion vanished from Nezumi's face.

"Old man, I do loathe No. 6. This destruction is what I've been longing
for. In fact, it's everything I could have wished for. If I ended up
bloodying my hands to attain it, so be it---that's what I used to think,
and I still think that way. But I want to avoid killing children at all
costs. I'm a survivor of the Mao Massacre. The last thing I want to do
is be on the side of the murderers. I don't want to become like No. 6."

Rikiga fell silent. He sighed like Nezumi, and took out his car keys.

"Inukashi, what are you doing to do?"

"I'll go. Don't got a choice, do I? I've got my own baby to worry about.
I can understand what Nezumi's trying to say. Heh, but I didn't expect
to be completely convinced. I must be getting old."

"Oh---Inukashi, by baby, do you mean the one I entrusted---"

"Shut up. He's my baby, and it's none of your business. A little slow to
notice, huh, uncaring prick? You can beg on your knees asking to see
him, but you won't get a chance." Inukashi neatly gathered up all the
leftover food and stuck his long tongue out at Shion.

\myspace

Confusion was reaching its peak around the Moondrop. The army had fired
further shots into the knots of people, resulting in even more deaths.
At the same times, several soldiers also fell to the ground, growing old
and dying within minutes.

A roar of fear erupted from the soldiers. As some threw their guns aside
and attempted to run, their superiors shot them dead from behind.

"Obey your orders. Suppress the rioters. Disperse them."

"No! Our lives are precious to us, too!"

"Don't even think about fleeing. Desert the battlefield---the penalty is
death," a senior officer barked. Suddenly, he bent backwards and
collapsed. Blood spurted from his forehead. A bullet had ricocheted and
hit him, perhaps---or had someone shot him? Even while his body convulsed,
the soldiers trampled him with their military boots in an attempt to
escape.

The crowd swarmed into the Moondrop. In their midst, each gate of the
city exploded and dissolved in flames. Cracks appeared in the special
alloy barrier as it, too, fell apart. The Correctional Facility was
already half-demolished in a cloud of black smoke.

The bigscreen monitors in the square displayed each of these scenes.

"Shion, what the hell is going on there? Why are they playing that? Is
No. 6 showing everyone its demise on purpose?" Inukashi asked with a
shiver.

"That must be surveillance footage from the cameras installed in each
part of the city\el But that should be playing on the screens in the
monitoring room of the Security Bureau. This footage is being forwarded
to public screens\el which means the computer's controls have gone
completely haywire."

"And that must be\el "

"Yeah, you're right. Only she can scramble No. 6's controls like this."

\emph{Chuckle, chuckle, chuckle.}

\emph{Chuckle, chuckle, chuckle.}

He could hear lighthearted laughing. It reached his ears, threading its
way through the roar of the mob, footsteps, screams, and the sound of
something being beaten like a drum.

\emph{Chuckle, chuckle, chuckle.}

\emph{Chuckle, chuckle, chuckle.}

\myspace

\emph{She's laughing. She's trying to destroy No. 6, laughing all the while.}

"Nezumi, can you sing?"

"\el Not here. It's too packed with people. I'll be out of breath before
long, especially in this condition." Nezumi looked up at the night sky,
his face shining with perspiration.

"She's laughing," he muttered.

"You hear it?" Shion asked.

"Yeah. She sounds like she's enjoying herself. Arrogant humans thought
they were the rulers of the world, and now look how easily they destroy
themselves---she's relishing every minute of it."

"Is she punishing human hubris?"

"Or it might be fate," Nezumi answered. "No. 6 was fated to become like
this. A balloon will always burst if it's blown up too much. Maybe she
just sped up those cogwheels of fate a little bit."

\emph{Chuckle, chuckle, chuckle.}

\emph{Chuckle, chuckle, chuckle.}

A man clutching a boy of about five ran past Shion.

"Help me, help me!" he cried through his tears.

"Nezumi, let's go to the top floor of the Moondrop."

"The mayor's office?"

"Yeah. Your voice will reach the entire square from there. Not only will
Elyurias hear your song, so will the rest of the people."

"A song won't calm the confusion."

"It'll be more effective than guns. That much is for sure."

They went along with the flow of people and entered the Moondrop.

"Where's the mayor? Bring him out!"

"This is the end of No. 6! We're done for!"

"The wall has crumbled! The gates have been broken!"

"Bring out the vaccines! Mayor! \emph{Mayor!}"

Suddenly, one man dashed up the stairs. With a megaphone in hand, he
bellowed in the stairwell.

"Comrades, I am here! I am Yoming! I once urged you to rise for
freedom!"

The crowd buzzed.

"It's Yoming! Yoming!"

"Yes! Comrades, just moments ago, I was attacked by the security squad
and I was almost killed. But yet I still stand here in front of you. I
will not die until I finish rebuilding No. 6 with my own two hands. I
will not die---I am immortal!"

The buzz grew louder. A mass of fists were raised triumphantly towards
the man.

"Yoming! Yoming! Our hero!"

"Comrades. No. 6's destruction is near. We're almost there. Let us
defeat No. 6, come together as one, pool our strength, and build a new
utopia. We will make our bright future a reality, with our hands,
comrades!"

"Yeah! That's right!"

"Three cheers for Yoming! Three cheers for a new No. 6!"

"Comrades, let us drag the mayor and his people out before us. Here we
will sentence and obliterate them. Let that be the first step towards a
new world!"

Cries of assent melded together into one roar. It shook the very air.

"No!"

Shion also dashed up the stairs to stand beside Yoming. "That's wrong.
What he's saying isn't right."

Yoming's eyes bulged as he gritted his teeth.

"Everyone, listen to me: there is no vaccine here. What's happening
right now isn't going to be stopped by the likes of any vaccine."

"Hey, what are you---"

"I survived." Shion took off his shirt and flung it aside, exposing his
red banded scars. "This is proof of my survival. Everyone, please. Give
us a little bit---ten minutes---of your time. Don't worry, we'll settle this
somehow. I survived. There's nothing stopping you from surviving, too.
But for that to happen, we need time."

\mybreak

"What are we supposed to do?" A voice questioned weakly from the crowd.
It was a female voice. "Tell us what we're supposed to do."

"Keep waiting," Shion answered. "Wait just a little bit longer, and
everything will come to an end. No one has to die anymore."

\emph{Wait, he says.}

\emph{So we just wait here.}

\emph{For half an hour or so.}

Like a breeze blowing ripples across the surface of a lake, a silent
wave spread throughout the crowd. Everyone gradually began to sit down
on the spot. People in the square also squatted on the ground, hugging
their knees.

"Thank you, everyone." Still holding the megaphone, Shion also spoke to
the dumbfounded man before him. "You, too, Yoming. Wait here."

Yoming was speechless.

"I'm going ahead." Nezumi broke into a run, passing behind Shion.

"How on earth did you\el " Yoming murmured as he gazed at Shion.

\myspace

There was no one in front of the mayor's office. The guards had likely
fled as well. What used to be the safest and most comfortable place in
No. 6 was now highly dangerous territory.

Shion knocked on the door.

"Come in," a calm voice answered through the intercom beside the door.

The door slid aside soundlessly.

The room was warm, tranquil, and luxurious. The mayor was standing in
front of a wide writing desk near the wall. He had a smaller frame than
what Shion had imagined. And he was young.

\emph{This man\el is the ruler of No. 6.}

There was a leather sofa beside the mayor, and another man sat at the
end of it. He was wearing a white lab coat. His neck was bent at an odd
angle, and his arms dangled lifelessly. His hair had turned white before
Shion's eyes, and his mouth hung open, having already taken its last
breath. A tooth dislodged itself from the man's mouth and landed on the
floor.

"Oh\el "

A wasp was sitting on the nape of the man's neck, moving its antennae
busily.

"It's a newborn," the mayor whispered. He sounded like someone who was
trying not to wake a sleeping baby. "I had no idea it was living inside
his body, either. But I think he was the most surprised. He died without
even getting over his astonishment. 'It can't be'---" the mayor smiled
faintly. "Those were his last words. 'It can't be'. Hah, it must be
decades since I heard something like that come out of his mouth. He
believed that everything in the world could be explained by science."

"Mayor. Please open the window. We're going to use your balcony."

"What do you intend to do?"

"We want to speak with Elyurias. We need to meet her, and it's urgent."

"You kids know about Elyurias?"

"Yes."

The mayor's gaze shifted from Shion to Nezumi.

"Window, you say\el " he muttered, and pushed a button on his desk. The
window slowly opened out.

"Nezumi."

"Yeah."

Nezumi stepped out onto the balcony. A wind blew up at them, ruffling
Nezumi's hair.

A song flowed forth.

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here\\
	Keep everything here, and\\
	Live in this place\\
	O soul, my heart, O love, my feelings true\\
	Return home here\\
	And stay}

Nezumi's singing was picked up by the wind, and seemed to reach every
corner of the square---and every corner of No. 6. The people sat perfectly
still and listened in a trance.

It was like a voice that stole the soul away and thieved the heart.

\myspace

\emph{Safu.} Shion spoke to the girl in his heart. \emph{Just once---just once more,
lend me your strength. Deliver this song to Elyurias. Safu, please. Lend
us your power.}

\poem{The wind steals the soul away, humans thieve the heart\\
	But here I will stay\\
	to keep singing\\
	Please\\
	Deliver my song\\
	Please\\
	Accept my song}

\emph{Safu.}

\myspace

The wind grew stronger. Nezumi staggered.

"Ah!"

Inukashi stood still, rooted to the spot.

"Wh---What the hell---"

A golden ring appeared in the sky, squarely in front of Nezumi. The ring
shrank until it became a blinding light. The light shimmered as it
wavered, and turned into the figure of a wasp.

\myspace

\emph{It has been a while, Singer.}

\myspace

"It really has." Nezumi turned around and beckoned to Shion.

\myspace

\emph{Come closer.}

\myspace

Shion stepped out onto the balcony and drew up beside Nezumi. The crowd
filling the square looked up all at once.

"Elyurias. Do you mind if I call you by this name?"

\myspace

\emph{As you please. A name given by a human means nothing to me.}

\myspace

"Elyurias. We beg you. We want you to grant us one more chance---just
once."

Shion heard the beating of wings. Four transparent wings glimmered as
they beat the air.

"Please don't give up on us humans yet. Just once. Give us one more
chance, Elyurias."

\myspace

\emph{Foolish creatures.}

\emph{Creatures full of arrogance and deceit.}

\emph{You are telling me to believe you?}

\myspace

"Humans are capable of both upholding ideals and succumbing to
corruption. There are those who cling onto their power, and there are
those who are pushed along by the majority. But there are those who
uphold their ideals, live for others, and continue to fight against
their own foolishness, deceit, and arrogance. Elyurias, hear our plea.
Believe in us, just once more."

\myspace

\emph{Is that what you wish for yourself, Singer?}

\myspace

Nezumi gave a slight nod.

\myspace

\emph{As one of the Forest People, you will believe in the residents of No. 6?}

\myspace

"I won't believe the people of No. 6. The only one I believe is him.
No---that's not it. It's not that I believe him. It's just---"

\myspace

\emph{Just?}

\myspace

"I want to see what Shion will become. I want to see what he's going to
build on the ruins of No. 6. I want to see with my own eyes what he'll
create."

\myspace

\emph{You want to see.}

\myspace

"O God---Forest God, you yourself aren't omnipotent. You can't see
everything. There's no way you could predict whether he'll create a
future that's different from No. 6, or follow in its footsteps. It's
something to look forward to, isn't it? How far will humans fall? Where
would they be able to dig in their heels and resist? See where it'll
take them---that's just another way to enjoy it. I think you're jumping
the gun if you think humans are hopeless because of a small example like
No. 6."

\myspace

\emph{The tiny infant I remember seems to have grown into an insolent one.}

\myspace

"People grow up. For better or for worse."

\myspace

\emph{Singer, are you sure? You do not need to keep loathing No. 6?}

\myspace

"No. 6 doesn't exist anymore. You destroyed it. But if No. 6 were to
appear here again, I'd hate it with my heart and soul, and wage another
war."

Elyurias' antennae quivered left and right. Golden powder scattered from
them.

\myspace

\emph{Shion.}

\myspace

"Yes."

\myspace

\emph{I have a message from Safu. She says, "I leave everything in your
hands".}

\myspace

\emph{Everything in your hands.} They were the same as the doctor's dying
words. Shion clenched his hand into a fist, and nodded.

"Please tell Safu that I've gotten her message. And please tell her that
I'll never forget her for as long as I live."

\myspace

\emph{Understood.}

\emph{Now, then.}

\myspace

"Elyurias, wait! Please, for us---"

\myspace

\emph{Just once. This one single time, Shion.}

\myspace

The golden light disappeared. The wind ceased.

\myspace

Shion went back inside the room, and sank onto the carpeted floor.

"It's finally over."

"Over? This is just the start, Shion. Your battle is beginning, and it's
going to be an arduous one."

"Nezumi\el "

"What kind of world will you build here in the place of No. 6? Would you
be able to build a real town, where humans can live as humans---and not
some parasitic city wearing the mask of a utopia? Shion, your battle has
just begun. You haven't finished. The one whose end is nigh is---"

Nezumi turned around and stared at the mayor.

"I know." The mayor sat down in his chair, and quietly closed his eyes.
"Could you excuse yourselves? I would like to be alone."

"Going to think about what to do with yourself, Mayor?" Rikiga growled.

"That has already been decided. I'll put an end to my own affairs. So,
please, if you will."

"Let's go. Everyone deserves to have their last wishes respected."
Nezumi started to walk out.

"You have my thanks." The mayor raised his hand.

The door closed.

A gunshot rang out almost at the same time. Rikiga shook his head
slowly.

Hamlet squeaked from Shion's pocket.

\emph{Cheep-cheep-cheep!}

\myspace

A cerulean sky.

The sky that unfolded over the small hill in the North Block was crystal
clear.

"Nice weather. Perfect for travelling." The wind tousled Nezumi's hair,
and he smoothed it down with his hand.

"Shion, right here is fine. You didn't have to come out to see me off."

"\el You're set on going?"

"I have to."

"When are you coming back?"

"Coming back? I don't have a place to return to."

"Nezumi, can't I\el can't I go with you?"

"You and I are different. I'm a drifter; you're stationary. That's what
it boils down to. When you're incompatible, you can't live together. You
should know this already."

Nezumi let his gaze wander over the scene that spread below him.

Here was a city once called No. 6. From where he stood, it seemed no
different than how it had always been.

"Shion."

"What?"

"Are you crying?"

"I'm not---geez, I'm not a girl---"

"I'm afraid of you."

"What?"

"I can't seem to grasp anything that's inside you, that's why. You're a
mystery. You had the power to put all the people at the Moondrop in the
palm of your hand in two seconds flat, yet here you are crying like a
girl. You can be utterly ruthless, courageous, and noble all at once.
And that's all part of who you are, isn't it? I can't understand it, and
that's why it's terrifying for me. Maybe sometime in the future, it
wouldn't be so bad for me to drop by to see\el yeah, to see what kind of
person you've become. Your mama's muffins are also hard to resist. But I
didn't expect to get a hug from her right after being introduced."

"Nezumi."

Shion grasped Nezumi's arm. He felt like he could endure no more.

"Don't go, Nezumi. I want to be by your side. I want you to be by my
side. That's all I wish for."

"It can't happen."

"Why not?"

"How many times are you going to make me repeat myself? You have to stay
here. You have a job to do."

"I can just let someone else---"

"You can't let anyone else do it. Shion, \emph{you} have to do this. Did you
forget your promise with Safu? What about the doctor's last words? You
said you'd take it. Shion, don't run away. You have a battle to fight.
You have a job to do here. You can't turn your back on it."

Shion looked at his feet.

He tightened his grip around Nezumi's arm.

\emph{I know. I understand. But---}

"Nezumi, the world means nothing to me without you. Nothing."

A finger hooked on his chin, and yanked it upwards.

A set of dark grey eyes were right in front of him.

"Won't you listen, my stubborn child? Act your age." It was a woman's
voice, softened with laughter.

"Nezumi, I'm serious---"

Their lips overlapped. It was a searing, but gentle, passionate kiss.

"Was that a\el goodbye kiss?"

"A vow." Nezumi smiled. "Reunion will come, Shion."

Nezumi turned his back to him. Hamlet and Cravat hopped onto his
shoulder, and chirruped at each other.

\emph{Cheep-cheep-cheep. Cheep-cheep-cheep.}

The wind blew.

The clouds panned out.

Nezumi's figure grew smaller and smaller.

He never turned around once.

"Nezumi." \emph{I never found out your real name. But---I don't need to know.}

To Shion, Nezumi had always been Nezumi. His one and only, irreplaceable
person.

\emph{Nezumi, I'll keep waiting. No matter how many years it takes, no matter
how old I get, I'll keep waiting for you right here, on this land.}

The drifter and the stationary one---their paths were bound to intersect
again. And when they did, Shion would not let him go again so easily.

\emph{Nezumi, I'll keep waiting for you.}

\myspace

The wind blew.

Sunlight streamed down---on Shion; on the city about to be reborn; on
Nezumi's vestige.

The light streamed down, and encompassed everything.