% !TeX spellcheck = en_US

\chapter{'Twere best not know myself}

\myepigraph{To know my deed, 'twere best not know myself.\\
Wake Duncan with thy knocking! I would thou couldst!}{\emph{Macbeth} Act II Scene II}

\lettrine{H}{e heard} the sound of the wind. It was a dry, sorrowful sound.

\emph{It can't be...}

Shion stopped his feet, and blinked slowly. It was dark. Even when his
eyes were accustomed to darkness, the gloom only reflected into his eyes
as gloom, and was entirely painted black. And of course, there was no
wind blowing.

Here, they were at the bottom of the earth.

A place in the bosom of No. 6---precisely, a place of darkness. The
basement of the Correctional Facility. Of course there would be no wind
blowing. There was no way he could have even heard its sound. Yet he had
definitely heard a high-pitched whistling. It was for a mere instant,
but he had heard it.

It wasn't a sound he had heard before in No. 6, where he had been living
only a short while ago. It wasn't a breeze that gently shook the
abundant canopies, nor was it something that wafted the sweet fragrance
of flowers to him. It was---

The wind of the ruins.

It was the cry of the wind that whistled through the remains of the
dilapidated hotel in a corner of the West Block. It was a cold wind.
Every time he felt it against his body, he remembered feeling like he'd
been chilled to the marrow of his bones. And indeed, people like the
elderly who collapsed on the road, unable to move, or children who had
been depleted of energy from starvation, were whipped by this frigid
wind and eventually froze to death. It was a cruel and ruthless winter
wind.

But he missed it.

He yearned many times more for the chilling wind that swept through the
ruins over the gentle, harmless breezes in No. 6.

What was Inukashi doing now? Was he simmering leftovers in the big pot,
briskly making food for his dogs? Was he busy tallying up his earnings
for the day? Inukashi, with his tan skin, ink-black hair and wiry body.

He had left a baby in Inukashi's care. He had thrust a small infant boy
upon him against his will.

\emph{Cut the crap, Shion. I'm operating a business here, my hotel. I'm not
running a non-profit orphanage.}

Shion could imagine his face, scowling in disgust.

Sorry, Inukashi. I didn't have anyone else to depend on. I had no other
choice but to cling and beg for your help.

\emph{Tsk.}

Inukashi clicked his tongue.

\emph{Pain in the ass wherever you go, aren't ya? Fine, I'll take it. Even I
have the heart to feel a bit of compassion. But it's a tiny one, and
even a dog would turn its nose up at it. No choice, though. This baby's
someone my own dog has risked its life to protect. I can't just throw
him away.... Look at me, I'm a pushover. Makes me sick of myself, even.}

Inukashi, my gratitude.

\emph{Doesn't make me happy one bit to have any of your gratitude. Doesn't
give me any gain. Shion, I'll take the baby \emph{for now}. Got it? Only for
now. You better come pick him up. You decided to take this guy in. You
gotta raise him. Understand? You better come pick...}

"Shion."

Nezumi turned around, and called his name. He could clearly see the pair
of lustrous grey eyes. Even in this darkness, Nezumi's eyes both sucked
light in, and released it. \emph{Or---} Shion let his thoughts wander.

\emph{Or could I still render those eyes, even if there was no light, even if
I was in complete darkness without a single ray to illuminate my way?}

"Don't stop walking. Keep right behind me."

"Oh---right. Sorry, I was spaced out a bit."

"Spaced out?"

"I thought I heard the wind blowing. Like the wind that used to blow
against Inukashi's ruins... I know I'm just hearing things, but---Nezumi."

"Hm?"

"I wonder what Inukashi's doing right now."

Nezumi blinked. Shion could make him out catching a breath.

"You've got guts."

"Huh?"

"Not just anyone can space out in a situation like this. There are
probably tons of people who go into shock from nerves, but to be able to
hear the wind blowing, or casually think about other people---that's
colossal. The amount of guts you have probably puts you in ranks with
the gods. You will let me worship you every day, won't you, once in the
morning and in the evening?"

"Are you being sarcastic?" Shion said flatly.

"Why, never," Nezumi said. "I haven't got the courage to smart-mouth a
god. I'm genuinely impressed. But---"

Shion was grabbed by the arm. It hurt. He felt Nezumi's fingers digging
into him. He knew how much strength those fingers held, despite how
slender and almost delicate-looking they were. So many times Nezumi had
clenched his arm, making him wince in pain. So many times he had grabbed
his arm and pulled him up. Again and again, countless times---from death
to life, from despair to hope, from fiction to reality, Shion had been
able to crawl up and out thanks to these fingers.

"From now on, be a bit more of an earthly coward. Don't give a damn
about Inukashi. Only think about protecting yourself."

"Got it."

"---Do you really get it?"

"I do---probably."

"Probably, huh. Nothing reassures me less." Nezumi gave a sudden laugh.
It was small, but it was lighthearted and filled with mirth. "Look at
the conversation we're having, in this place, in this situation. The
epitome of flippancy, I think, both you and me. Maybe I'd be able to
join the gods if I hang around you more."

Then his tone suddenly changed, into one that was heavy and severe. His
fingertips dug in with even more force.

"No matter what happens, don't stray from me. Keep up with your own
strength. I told you before. I won't say it again."

Shion nodded. Nezumi turned his back and resumed walking, either having
seen or felt the slight inclination of Shion's head in reply. The figure
before him wouldn't turn back around as easily. Shion knew that well,
too.

If he wasn't desperate enough to live, if he didn't greedily latch onto
life, then Nezumi would not turn to him.\footnote{turn to him: The expression "turn around to face someone" is often used in the romantic sense to mean "requiting someone's feelings". The way it's phrased seems to stand out here. I may be reading too much into this, but I wouldn't put it past Asano.}

Nezumi would never revere a flippant and unobservant god. Shion inhaled
a breath of darkness, and placed his foot forward.

A small path continued up a slight slope in the crack between the
boulders. It was just wide enough for an adult to get through. It might
even be narrower than the former passageway, cased in concrete with
small light bulbs at equal intervals. It wasn't a long journey, but
twists and turns made it that much harder to walk through.

\emph{But at least---}

Shion wiped his sweat with the back of his hand.

\emph{But at least it doesn't smell like blood here.}

The air was absent of the bloody stench that had filled the other
passageway. There were no screams or groans of the dozens of people
dying---being murdered.

There was only darkness.

Even if this were only to last for a short moment; even if there was a
reality beyond Shion's imagination waiting for him beyond the darkness,
as it had always done, he would not have to breathe the stench of people
being unfairly and pitilessly obliterated.

He was grateful. As if he had encountered an oasis in a desert---he was
grateful.

\emph{You're naive.}

He chewed his bottom lip.

Nezumi didn't even have to tell him. He was so very much naive.

\emph{I just can't smell it. I just can't hear it. I just can't see because of
the wall that divides us.}

\emph{But it's still happening right beside me.}

The reality that dozens of people---including newborns---were being unfairly
and pitilessly obliterated, still existed on the same stretch of land
that Shion stood on, right here, right now.

Just because he couldn't smell it, just because he couldn't hear, just
because he didn't see, didn't mean that it didn't exist. Just because he
had arrived at an oasis, it didn't mean the desert had disappeared.

\emph{I'm naive; I'm idealistic.} He couldn't help but make excuses. He
couldn't help but try to forget the wrath he had felt when he had
witnessed the brutality. He wanted to avert his eyes from grisly things.
He was trying to curl up and lend himself fully to the comfort of
falling into an ignorant slumber.

\emph{I am naive. And I am weak.}

He traced the rocky wall with his hand, and did his best to keep up with
Nezumi.

What was important right now was to follow him. \emph{And I've always followed
him}. He had walked down a nighttime path for the first time in the West
Block. He had torn through it, even. If it weren't for that experience,
he would probably not be able to walk through the oppressive darkness
now that seemed to crush his very eyeballs.

\emph{In that sense, I've toughened up a bit}, he told himself. \emph{Believe. You've
got your own kind of strength stored up inside you. Believe yourself
wholeheartedly.} It was easy to fall back to self-loathing, and wallow in
defeat---but it was meaningless. Believing yourself was strength. With
this strength as fuel, as a weapon, one could overcome innumerable
difficulties.

Shion funnelled his concentration into the soles of his feet, and moved
forward one step at a time. He met a light. It was dim. It was gradually
beginning to lighten before his eyes.

Nezumi's figure glided into that dim light as he watched from behind.
Shion quickened his pace.

"Oh---" his breath caught in his throat.

They had emerged into a spacious chamber. It was much more spacious than
where Nezumi and the sand-coloured man had fought. The ceiling was
lofty. It looked almost three storeys high. The same rugged boulders
jutted out from all around.

\emph{This place is a naturally-occurring series of caves, huge and complex.}
Nezumi had told him. Then this must be a chamber that nature had
created. Candles were lit here and there in the crevices, and they were
not the only thing: lamplight also winked in some places. They were all
dim, but warm, sources of light. They were beautiful, too---like small
flame-coloured flowers blooming in the alcoves of rock.

Alcoves?

Shion squinted. He baited his breath, and squinted as hard as he could.
He baited his breath more.

A shadow moved.

One, two, three, four.... They were not mice; those were not small
animals. Numerous shadows were moving around. They stood on two legs,
and were whispering to each other. On two legs, whispering....

\emph{Humans!}

The lump he had swallowed stuck in his throat. His heart raced.

\emph{Humans. There are humans here. They're peering out at us from the
alcoves. Humans.} If he squinted even more, he could see a large cavern
yawning its large mouth from behind the lit candles in the crevices. So
there were tunnels even further on inside these caves. The people had
probably crawled out from there.

Shion couldn't make out each individual figure with his eyesight, but he
could tell that they varied in height and build.

Were there men and women, both adults and children? All of them
identically leaned forward, and were gazing down upon them. Shion felt
like he could see each person's eyes glinting dully if he stared long
enough.

"Nezumi, these people..."

"Who do you think they are?"

"Oh---survivors. They must be people like us, who've managed to escape the
execution grounds."

"Wrong." Nezumi shook his head. It was a languid gesture, unusual for
him. "They've lived here way before that."

"Way before... what do you mean?"

"You'll see in a bit."

\emph{'You'll see in a bit'---I guess you're right.}

\emph{You will see. As long as you have the will and the strength.}

Shion clenched his fist. It was easy to question. He had always been
asking questions up until now. He had always instantly, so easily,
begged Nezumi for the right answer without trying to decode the reality
that appeared before his eyes.

\emph{It won't work anymore.}

He would find the answer himself. He would grasp it. He would decode it.
Other people were other people, even someone as close as Nezumi. He
would not be able to render the truth if he kept leaning on other
people's words. He would not be able to face off with a reality that
surpassed his imagination. He would not be able to stay equals with
Nezumi.

He had to render it himself.

Nezumi dropped his gaze from Shion. His grey eyes clouded over. Clearing
it away with a blink, Nezumi swept his hand aside in a smooth gesture.
It was a graceful move unique to him.

"Look, isn't it spectacular? Everyone has turned out for the welcoming
parade."

"Famous even in a place like this, aren't you?"

"---Idiot. Shion, this is your welcoming."

"Mine?"

"You're the spectacle here. It's unheard-of for an outsider to come
bursting in. And a No. 6 resident at that."

"\emph{Former} resident," Shion corrected. "I'm not one anymore. I threw my ID
card away a long time ago. I'm not a citizen of that city."

"Don't get hung up about it. It was just a form of expression."

"I \emph{will} be hung up," Shion said stubbornly. "It isn't 'just' an
expression. I'm not as weak as you think. I'm not attached to No. 6."

Maybe it was bravado. But Shion squared his shoulders the best he could.

\emph{I am weak. My mind and body are all too fragile. But nothing can shake
my resolve. Nothing can confuse my feelings. My resolve to live not
within, but outside the city; my feelings of wanting to live together
with you; nothing can shake them, nothing can muddle them.}

"Who said you were weak?"

"You always say so."

"Never. You're a superpower. You just overwhelmed me with your
brilliance back there. It's quite something... I'm even more impressed
now. I certainly am." Nezumi shrugged. "And I would never have thought
you would trip me up at every petty word and start complaining about it.
In this situation much less."

\emph{Skrit, skrit, skrit.}

A sewer rat crawled up Shion's body, and sat on his shoulder. It was
quite heavy compared to Hamlet or Cravat. And it smelled rotten. But it
twitched its nose and tilted its head to the side in the same way.
Another one crawled onto his other shoulder. It stuck its head into
Shion's snowy hair, and nuzzled its face into it. Yet another one---this
time, a baby rat---rubbed itself against his feet. One more came, and
still another.

The rats scurried up and down Shion's body, chirruping affectionately.

\emph{Skrit, skrit, skrit, cheep cheep cheep.}

\emph{Chit chit chit. Chit chit chit.}

"Hey, cut that out," said Shion, suppressing a laugh. "I'm not a
playground slide. Stop that, it tickles!" Shion gave his body a shake.

The air buzzed. The darkness rippled uneasily. Shion could feel the
presence of the rock dwellers: breaths sucked in, inaudible whispering,
shifting bodies, furtive glances.

"An intriguing child."

A voice came raining down from above. It was a low voice, but it rang
out clearly. It wasn't quite the level of Nezumi's singing, but it was
deep, soothing, and flowed into his ears comfortably. Was it the same
voice as a few moments ago? The voice that had come floating down from
the black painted void?

\emph{'Let us hear your story.'} Was it the same voice as that?

He looked up.

He saw a figure of a man seated in a chair in the middle of an alcove,
in a spot that was jutting out like a balcony. At least... he thought it
was a man. It looked like... an elderly man with long white hair and a
long white beard, clad in a long gown-like garment. It was too dark to
get a good look at his face.

"An intriguing child. You haven't stirred any animosity or apprehension
in the mice. Shall I ask you your name? What are you called?"

"I'm Shion."

"Shion---ah, a beautiful name."

"Th---Thank you. For, um, complimenting me," Shion stammered. "And you
are?"

"Me? What about me, Shion?"

"What is your name?"

\emph{Buzz.}

The darkness rippled even more fiercely. The rats chattered on his
shoulders. Laughter rose. From alcoves in every direction, various kinds
of laughter rose, and showered down upon Shion.

\emph{Giggle, giggle, giggle.}

\emph{Name, he says.}

\emph{Giggle, giggle, giggle.}

\emph{He asked for his name.}

\emph{Giggle, giggle, giggle. Giggle, giggle, giggle. Giggle, giggle, giggle.
Giggle, giggle, giggle.}

He had no idea why he was being laughed at. He had only asked for the
man's name. Why was that a cause for such derision?

\emph{Giggle, giggle, giggle. Giggle, giggle, giggle.}

The laughter didn't cease. Shion turned to look at Nezumi, who was
standing at his side.

Nezumi stood unmoving. He wasn't smiling. Naturally. No expression
adorned his face. He was like a statue.

"Rou." A deep voice pierced through the rippling darkness. The noise in
the caverns was silenced immediately. An almost painful stillness fell,
like one you encountered in a forest when all the winds had died. In
this stillness, only the elder's words unfolded leisurely.

"Rou. That is what I am called."

"Rou---that's your name?"

"Perhaps, perhaps not. It may only mean \emph{old person}\footnote{the character 'rou' \begin{CJK}{UTF8}{min}老\end{CJK} literally means 'elder'}."

"So this is not your real name?"

Some moments of silence.

"Young one. No one here places importance on names. No one. Has Nezumi
not taught you that?"

\emph{Come to think of it---}

Shion exhaled.

\emph{Come to think of it, I still don't know Nezumi's real name.}

"Rou." Nezumi moved. He had taken a step forward. "I want you to hear
our story."

"Let us hear it." The elder straightened his posture in his chair. "You
have returned. We were never supposed to meet again, yet you have
appeared again before my eyes. Let us hear the reason."

"I'm grateful."

"Grateful? Nezumi, I see you have been grown weak and cowardly from
being buffeted by the wind outside. But no matter how weak and cowardly
you have become, I hope you have not forgotten the rules."

"Of course not."

"Those who have left this place must never return. You have broken that
taboo. You must recompense."

"I know. I'll pay the penalty. So listen to me, please."

The elder snapped his fingers. Although Shion had not noticed this
before, two long poles were attached to the legs of the elder's chair.
It was perhaps better called a palanquin than a chair.

Two men held the poles and hoisted the elder along with the palanquin.

\emph{His legs?}

There was nothing filling out the lower part of the elder's gown. The
hem hung lifelessly. The elder had lost his legs from the knees down.
Both of them.

The palanquin with the elder in it began to descend from the boulders
slowly, as if slithering down the wall. A shadowy figure, whose long
hair was bound in a ponytail---a woman, evident from the outline of her
body---was sweeping the path in front of the palanquin with what looked
like a broom. She was like a forerunner for a procession.

There was a path. A path just wide enough for people to brush shoulders
as they passed. The slope was steep, yet the men walked steadily down
it, without missing a step.

It was not something naturally-occurring. Walkways had been carved into
the boulders by human hands. If he looked closely, paths spanned all
along the rocky walls; perhaps it was structured so that people could
come and go freely.

\emph{Is this... a settlement?}

Shion took in his surroundings anew. At the same time, he set his brain
to work. Caverns, which were no doubt residences; paths on the boulder
walls; this chamber; the dark space that continued beyond this
chamber---and he could almost smell something being boiled or stewed. And
faintly, very faintly, he could feel a wind. Which meant the air was
moving, and this place was connected to ground-level. Here was a
settlement of humans.

An underground settlement?

He restrained his thoughts, which threatened to stray every which way.
He organized them, and searched for a coherent thread.

Nezumi had said that these residents of the dark were not people who had
survived the Hunt. It was perhaps so. An underground world, where no
sunlight would reach, would be too harsh of a condition for people to
live in. Humans were organisms that were adapted to life above ground.
It seemed implausible that one could keep living in a place where there
was barely any change in amount of sunlight, air current, and natural
surroundings. But before his eyes were those very people themselves, and
the signs of human residency.

The scene before him was clearly not something that had been created
overnight. He could gather that much. Had these people lived underground
for a long, long time, having established their settlement, and
gradually adapted this way? It was the only guess he could come up with.

Shion unconsciously let out a long sigh.

\emph{Remember this place. The basement of the Correctional Facility. What is
a settlement doing here? Is it a coincidence?}

\emph{Maybe...}

Shion's thoughts emitted frustrated sparks inside his head. No matter
how much he thought about it, he wasn't able to grasp it. He couldn't
set foot outside of the boundaries of speculation. But that was also why
he thought harder. He speculated. He devised theories of "what-if"s.
Desperately.

What if people had been living in this place for much longer---this place
that had been a series of large caves from the very beginning?

Aboriginals...

What if there had been people living on this land long before the birth
of the nation-state of No. 6?

The West Block area had once been a small but beautiful town. Many kinds
of people, Rikiga included, had resided there. His mother had been
there. And his father---though he had no memory of him or his face---had
also been there. The town had mutated, and became the mother from which
No. 6 was born. Except it wasn't the town that had changed, it was the
people. Under human hands, the massive walls of special alloy and the
enormous city-state had been born. Outside of the walls, the remnants of
the town became a barren wasteland known as the West Block. But that was
only the west side.

Was the western town the only place No. 6 had destroyed? What about the
northern mountains, the forests, the grassy plains that stretched from
south to east, the lakes and marshes that dotted the land from eastern
to western edge? Considering No. 6's geographical area, it was logical
to think that it had enlarged in all four directions, proliferating and
expanding...

A chill ran down his spine.

In the northern mountains, the southern plains, the eastern marshes.
Somewhere, a race of peoples unknown to Shion had once lived. And not
only one race. In the mountains, forests, and plains, people had carried
on their lives. In these caverns, too....

Aboriginals. A people who had taken up residence in the caves from a
time dating far back.

They had been people of a different kind of world than the town Rikiga
and his mother had lived in; they had probably stayed in their own
territory, as the "town people" lived in theirs, and had not had any
contact with them. Perhaps neither group was even aware of the other's
existence.

This stretch of land had once been a sprawling forest. On this planet,
there were only six regions which fulfilled the conditions adequate for
human life.

People built towns in those regions, and those towns eventually grew
into city-states. Learning from history's moral lesson, they had
abolished civil wars between the states. They agreed that a ban on all
military power was the bottom line for the continued survival of
mankind, and so, they had acted in accordance with the Babylon Treaty,
which called on the abandonment of all armies and weapons. Also in
accordance, each city had discarded its unique name, and adopted a
simple number as its title---from No. 1 to No. 6.

The six cities, while still respecting the uniqueness and independence
of each, nevertheless maintained strong ties, and were acknowledged to
be part of one nation; both political leaders and the populace agreed
that this was the mindset each and every one should have.

\emph{These lands are the only things left to us. Further destruction is not
permissible. War is evil. It leads everything to extinction. It
threatens our very existence. We must abandon all weaponry for the
future of humankind.}

\emph{Under this ideology, we shall found six cities linked in friendship and
understanding.}

\emph{From No. 1, to No. 6.}

The sixth region had been blessed with natural conditions more
favourable than any other. Everything was utilized to the
fullest---nature's bounties, human intelligence, and scientific
technology---to build this utopian city, one rarely found throughout
history.

This was the birth of the Holy City of No. 6.

That was an outline of the history Shion had learned as an elite
candidate in his perfectly-equipped classroom.

His chill had gotten worse. He felt like he was frozen right down to his
fingertips.

If he closed his eyes---but even with them open---he could see images of the
Hunt flashing in the back of his mind. It was reality. Those were scenes
he had seen with his own eyes.

Barracks had been blown apart; tents had been torn down. Frantic,
fleeing people had been ruthlessly murdered. Men and women, both elderly
and young, and even infants had been indiscriminately vaporized. The
most modern weapons had attacked people who could only retaliate by
throwing rocks. It was a massacre if anything.

'Abandon all weaponry' indeed.

He had been biting his lip without thinking. The bloody taste spread
inside his mouth. He swallowed it with his spit. He did not know about
the other cities. But---but...

At the very least, he knew that No. 6 was on its way to becoming an
armed state with overwhelming military power.

\emph{Since when?}

He swallowed his bloody saliva again.

\emph{When did that city start to change? When did it begin to stray
from the policies and ideals of the Babylon Treaty? Since when... since
the beginning?}

\mybreak

Shion felt a gaze on him. His eyes met with Nezumi's. He felt like he
was being wrapped in an elegant grey cloth. The core of his body
pulsated. All the thoughts that had been swirling around in his head
came to a full stop.

A moment of pleasure.

It was strange. Just the kind of light in Nezumi's eyes was enough to
make him feel like he was being pushed away or being embraced.

But now was not the time to be giving himself up to selfish and
indulgent emotions. People were easily swayed once they ceased to think.
They were too easily led along by the flow of other people's words and
the mindset of the times.

Nezumi would never embrace and protect anyone who avoided thinking, who
let himself simply be pushed along with the flow.

\emph{And besides}, Shion thought as he lifted his chin. \emph{I don't want to be
protected by him. I haven't abandoned my thoughts. I'll keep decoding
the world around me and its workings in my own way. I will confront the
world in its true form, and look reality in the eye. That's probably
something you would call a battle, Nezumi.}

Shion dropped his gaze from Nezumi, and meditated. He set his thoughts
in motion again.

\emph{Since when?}

\emph{From the beginning?}

Yes, from the beginning. Perhaps No. 6 had been removed from ideologies
of peace and co-existence from the very moment of its birth.

On this land, there had once been a people that had lived here long
before. No. 6 had invaded them. They had tried to dominate them in the
same way a starving beast devoured its prey and gnawed on its bones. By
doing so, it had expanded its boundaries, and established its
foundations as a city-state. Peace? Co-existence? It had laughed
contemptuously in face of these words, and with brute force, made the
surrounding areas its own.

Just as it had destroyed the West Block. Just as it had massacred its
people. Using overwhelming military force.

\emph{But still... what about the other thing? LEDs---light-emitting diodes.}
LEDs lit up when electric current was applied to the joint between two
special semiconductors. They were man-made lights that didn't exist in
the natural world. Scientifically manufactured lights. Were they not
things that No. 6 had created? Or---or, rather, had some scientific
civilization existed which was at par with, or even more advanced than
No. 6? But if that was so, the civilization would probably not have been
invaded so easily. He did know that science was neither all-solving nor
almighty, however....

He didn't know. It was like walking in a fog. No matter how much he
pondered and contemplated, no matter how far he stepped in, he never
reached the truth. The more he thought, the further he ventured, the
more lost he felt. He couldn't get out of the labyrinth. His thoughts
wandered aimlessly.

He was frustrated.

\emph{Cheep.}

The rat jumped down from Shion's shoulder. The little mice also hid
themselves in the boulder cracks.

\emph{What's wrong?}

As Shion's gaze started to follow the little mice, he was suddenly
attacked from behind. A shadow twisted his arm up behind him. His mouth
was gagged. In the blink of an eye, he was bound up with rope. He was
shoved from behind. He fell with his hands still tied behind his back.
He rammed his shoulder on the ground.

"What was that for?" he shouted.

"Shion, keep quiet." Nezumi, also kneeling in ropes, shook his head at
him. "Don't resist. Stay quiet."

"But why---ow! The rope really hurts!"

"Let your body relax. Breathe out and loosen up. It'll feel a bit
better."

He did as he was told. Nezumi was right---he felt a bit better. \emph{Pretty
amazing, though. Capturing and binding us in a matter of seconds---oh, but
still---}

"Not as good as you."

"What?"

"You'd have a better handle on it. Whether it be a rope, or a knife."

"Why, thanks for the compliment. I'm undeserving of the privilege,
really, to be complimented by you."

"I'm always in awe at your---\emph{gh}." The rope dug into his neck. His breath
caught in his throat.

"Do not speak." A flat voice hissed at his ear.

Was it that man? The man with sandy-grey hair, skin, and eyes?

"Any more idle chatter, and I will wring your neck."

The rope tightened. He really felt like his neck was being wrung. His
airway caved in from the pressure. He felt like he was suddenly swelling
from the neck up. He couldn't breathe. It was painful.

"Knock it off," Nezumi said quietly. "Revenge for what happened back
there? Taking your frustrations out on an unresisting human? I see
you've picked up some low habits while we haven't seen each other,
Sasori."

The rope loosened. For an instant, Shion didn't know what was happening.
He threw himself out on the ground, and dissolved into a fit of
coughing. He heard the sound of flesh hitting the ground as if it were
crawling across it. He raised himself.

Nezumi was crumpled beside him. The man's foot landed on his shoulder.
He was wearing sandals that were woven out of what looked like thin
strips of bark.

"You too, Nezumi." The man's voice grew leaden. "Enough of your insolent
complaints. Do you not understand your place? Then it is only a matter
of making you understand."

The man's foot moved to kick Nezumi's shoulder.

"You are the ones who have trespassed from outside. You have no right to
protest if you get killed."

"Stop!" Shion twisted and yelled. Nezumi lifted his face, and shook his
head as if to tell him to shut his mouth. But he could not.

"You coward! You're just as Nezumi says. Tying us up and making it so
that we can't fight back, and then beating us---it's low, it's filthy!"

"Shion." Nezumi grimaced. Several streams of blood ran from his temple
down his cheek. Shion clenched his stomach, and stared up at the man.

"What is this place? No. 6?"

"No. 6, you say?" The man's whole body quivered. His sand-coloured eyes
glinted sharply. The light seemed almost murderous. But Shion was not
about to be silenced. He was also trembling, but not with fear. It was
with wrath. Wrath boiled within him.

"It's true. You're just the same. What you're doing is no different from
No. 6. You oppress the weak by force. You inflict pitiless violence. How
are you guys any different?"

"I'm not really weak, just saying," Nezumi shrugged with his hands still
tied behind his back. "Shion, I get what you're trying to say. Just
leave it at that. Say any more, and you'll be kicked to death. Kicking
is this old man's specialty."

"I will kill you," the man growled. "You are a demon. A wicked bringer
of misfortune. If I do not dispose of you now, you will only bring
catastrophe upon us."

"A sharp eye, Sasori," Nezumi sighed exaggeratedly. "You're spot on. A
catastrophe, indeed. Of the highest class."

"Nezumi, what do you mean 'catastrophe'? ...You mean I am?"

"You are," Nezumi chuckled lightheartedly.

"He is evil," the man continued. "He wears a demonic aura like a cloak,
and carries misfortune wherever he goes. I can tell. Nezumi, you said he
was a resident of No. 6."

"Former resident, to correct you. He was inside the city up until just
recently."

"That must be why he is so evil. He is... like No. 6 itself."

Nezumi narrowed his eyes. The tip of his tongue licked the blood on his
lips.

"No. 6 itself, huh.... I see. That's how he appears to you."

"I know," the man answered. "I can tell. I must kill him. I must dispose
of him before it is too late. If not..." The man took a step forward.
Shion shrank back without thinking. The man was radiating such a
murderous intent that he could not help but recoil.

\emph{He's serious....}

\emph{This man is serious about killing me.}

The man took another step forward, but suddenly spun in a somersault and
crashed to the ground. Nezumi had tripped him.

Nezumi was up in a flash. The ropes slid to the ground. It was like a
magic trick. In his hand was a small knife.

The man tried to get up, but was stopped by Nezumi's knee digging into
his stomach. The man let out a muffled groan. He bent backwards from the
pain, leaving his throat defenseless; a blade was soon pushed up on it.

"We worked hard to get here. I won't have you disposing of him that
quickly."

"Why... did you bring... such catastrophe?" choked the man. "Do you plan
to destroy us all?"

"The opposite." Nezumi's lips curled. "I want to send \emph{No. 6} to its
grave. That's why I brought him."

"No. 6? Does that boy have the power to?"

"Who knows. We don't know until we try. I can't let you kill him before
we even test it out. That jealousy of yours, by the way: a little
embarrassing, don't you think?"

"Jealousy?"

"Yeah. You're jealous of Shion. He's got your rats in the palm of his
hand like it's nothing. You're jealous. Am I right?"

There was a heavy grinding sound. The man was gnashing his teeth.

"Nezumi... just as unpleasant as you used to be. It irritates me. I will
strangle you to death first."

"What a splendid promise. I can't wait. But before that---" The wan smile
disappeared from Nezumi's mouth. A drop of blood that had slid down his
chin dripped on the man's chest, and coloured it red. "Let's have you
swear, Sasori. Swear that you'll never lay a finger on Shion again."

The blade of the knife jerked. The man's throat contracted as well.

"Swear it."

The man fell stubbornly silent.

"That is enough." A gentle voice rang out. It even held a hint of a
laugh. "You have not changed, Nezumi. Neither your skill with the knife
nor your sarcastic way with words has deteriorated. I daresay it seems
to have become even more polished."

The elder on the palanquin was smiling with the same benign air as his
voice. The palanquin was lowered steadily.

"Rou."

"You have grown. I can barely recognize you. I would never have thought
I could encounter you as a grown man."

Nezumi released the man and knelt down. The knife spun once in his hand
before disappearing. This too, was like witnessing a magic trick. The
man muttered something, and gnashed his teeth some more. Rats raced over
Shion's lap.

"I believed that you had left long ago for a land far away. Did I not
command you to do so? To leave this place behind, forget everything,
throw everything away, and to live freely?"

"Rou, please listen to me."

"You should never have returned. Regardless of what happened, you should
never have come back."

"I can't be free." Nezumi clenched his fingers hard. "As long as No. 6
exists, I can't be free. I can't forget it, nor can I throw it away."

"Nezumi."

"You should know. No. 6 still exists. It's still here. How can I be the
only free one? It's impossible."

"I have told you not to become trapped. I have told you to live
unfettered. If you did not, you would not be able to survive; I
understood this well. That was why I released you into the outer world.
But to think that you would come back..."

"I've realized."

"Realized?"

"I've realized your words were nothing but white lies."

The air wavered in agitation. Voices which were barely voices traversed
between the people nestled in the rocky walls, looking down at them.

"Your words were white lies. False. There was no way I could live
without being trapped. On the contrary, I \emph{had} to be trapped. Even if I
deceived myself, pretending I was free, I would still be in chains
anyway. From now on, I'll acquire real freedom with my own hands. I'll
set myself free. That's why I came back."

"Is this freedom you speak of fighting with No. 6?"

"It means fighting and winning. Erasing it clean from this land. The day
I see the Holy City arrive at its end is when I'd be free for the first
time. I'd be able to live a truly free life. I would be able to leave
this place... of my own will."

"Nezumi!" Shion yelled without thinking. As he yelled, grabbed Nezumi's
shoulder. "What do you mean by that? Leave this place? What---"

"Shion." Nezumi's eyes blinked rapidly. "The rope... how did you---?"

"Huh?"

"The ropes. How did you get out of them? You don't have a knife on you."

"What? Oh, the rats chewed them apart for me."

"The rats? No way, you must be---"

Shion thrust an end of the rope to Nezumi, and waved it before his eyes.

"Look. They all chewed at it together. It happened in no time.
Impressive, isn't it?"

Nezumi's eyes flitted to the jagged end of the chewed rope before
furrowing his brow.

"You have that much control over those rats?"

"Me? No, of course not. I couldn't pull tricks like that. The rats did
it on their own. They're all very kind and intelligent," Shion said
proudly.

"Kind and intelligent, huh. So your rats chew apart the ropes their
master has tied. He's right; they \emph{are} kind and intelligent. You've
trained them to be very well-behaved, Sasori."

The man---the sand-coloured man called Sasori---only fidgeted a little, and
didn't reply. Instead, the elder let out a short breath.

"Enough sarcasm, Nezumi. It is a bad habit of yours. It seems your
tendencies have not changed, despite how much you have grown physically.
A problem, indeed."

There was warmth in the elder's tone. He was like a father smiling
exasperatedly over his child's antics. His voice radiated with the
source of its warmth---love.

This man felt tenderness for Nezumi.

Shion gazed at the elder on his palanquin. \emph{This is my first time}, he
thought. It was his first time meeting someone who expressed a peaceful
and warm attitude to Nezumi.

Nezumi had always been alone. He had always lived alone. There was never
anyone by his side. He didn't let anyone approach him. Shion yearned for
Nezumi in his own way, and he was also entranced by Nezumi's resilience,
litheness and beauty. He hoped to remain by Nezumi's side. These
feelings certainly existed inside him as unmovable fact; however, it was
also fact that he was uncertain of what name to give those feelings.

Admiration, friendship, deference, love.... He was uncertain; he
couldn't help it.

But what he felt from the elder on the palanquin was definite affection.
It was like a parent bestowing affection upon a child.

\emph{To think Nezumi had someone like this.}

"Shion," the elder called.

"Yes."

"Come here."

"Yes, sir."

"Wait," Sasori stepped forward and grabbed Shion's arm. "Rou, this boy
is dangerous. He is cloaked in evil. You cannot let him near you."

"Evil---this boy?"

"He is not just a boy. He is a demon. He will destroy everything. I can
see it. Why can you not, Rou?"

It was hard not to get angry when this much was being said about him.
Shion tried to shake off the hand that held his arm. Sasori's fingers
showed no signs of moving, and squeezed even harder, choking its hold.

"I see no problem. Bring Shion here."

"Rou."

"I see no problem. Good and evil, virtue and wickedness, truth and
lies---they are all very similar. So similar, in fact, that it is often
hard to tell them apart. True, is it not, Nezumi?"

"I see what you're saying."

"It is a boy whom you have brought. Surely he is neither entirely
wicked, nor entirely virtuous. Now, Shion: here, if you will."

The fingers drew away from his arm. Sasori retreated a few steps,
growling lowly. His sand-coloured limbs blended into the darkness. Shion
approached the palanquin slowly. Several rats scurried around his feet.~

The elder had clear, dark eyes. They harboured a twinkling light as he
gazed unflinchingly at Shion.

\emph{This man....}

Shion felt like this man was younger than he had originally thought. He
had assumed---from the man's name as "elder" and the white hair that
framed his face---that he was an aged man. But the strength of the light
in his eyes was not that of an ageing person.

The elder raised his hand. It was thin and pale.

"Your head."

"I'm sorry?"

"Will you let me touch your hair? It is a rather odd colour."

Shion crouched, and bowed his head forward. The elder reached and gently
ran a hand through his hair in a circular motion. It tickled a little.
Shion felt a little sheepish, like he was being patted on the head.

"Why?" the elder said, with added heaviness to his voice. His voice
trailed off hoarsely. Its gentleness was gone; now it sounded tense.

"Why has your hair---"

"It's not only his hair." Nezumi strode purposefully forward. "Shion,
show him your red snake."

"Huh? No way."

"Why not?"

"I'd have to take off my clothes. I don't want to be naked in front of
so many people."

"Dumbass," Nezumi clicked his tongue. "What kingdom are \emph{you} from,
Princess? This isn't the time to be a blushing maiden. Quickly! Show him
what you've had to endure."

Nezumi's fingers flipped his shirt up. Shion hastily recoiled.

"I get it! I'll do it myself. I don't need help undressing."

"Is that so? I'm impressed. Worthy of praise."

Nezumi's eyes were not as buoyant as his voice. They were tense and
sharp. Shion cast his shirt aside, and took another half-step towards
the elder.

The elder drew a breath. His trembling fingers traced the crimson band
that had scarred his chest.

"These... these scars..."

Nezumi jerked his chin as if to encourage Shion.

\emph{Can I tell him?}

"These marks, why---" the elder said. "No, it couldn't be..."

"They're from a parasite wasp."

"Parasite wasp," the elder repeated.

"They feed off humans. They ultimately kill their host before hatching.
I---was able to survive. The result of it are these scars, and my blanched
hair."

The elder's mouth twisted. His eyes, set in his face among countless
wrinkles, glittered unnaturally bright. Nezumi grabbed Shion's shoulder
roughly.

"Rou, No. 6 will disintegrate. One day, it'll crumble not only from the
outside, but from its own powers working inside. These are the first
signs."

"A parasite wasp which lodges in humans... I see... they have begun to
appear inside the city."

"Yeah. And apparently out of sudden coincidence. They appeared
unexpectedly; even the guys holding the reins of No. 6 couldn't predict
it. Several citizens have died in strange ways. The authorities haven't
been able to prevent it. I don't see them desperately trying to, either.
Maybe they don't have a grasp of how serious the situation is yet.
They've become complacent."

"Complacent..."

"They're complacent because they think the world will run according to
their plans. They're arrogant enough to believe that they can be a
universal and omnipotent ruler... they've been blinded by their own
delusions, and can't see the truth of reality. They're losing the
eyesight to see through the facade."

Even when it seemed to scrape across the ground, Nezumi's voice
nevertheless reached the ears of his listeners crystal clear. In the
darkness, only his low, resounding voice filled the air.

"Things are still quiet inside the city. They're still managing to
maintain peace and daily routine. But it's like a cup that's been filled
to the brim with water, about to spill over any second. It's maintaining
its balance, but barely."

"One has only to stimulate it slightly, and everything will spill
over... is that what you mean?"

"It would burst. It would destroy the cup and come gushing out."

The elder muttered something softly. Then, he locked his fingers
together as if in prayer.

"Let us hear it, then---everything, from the beginning."

A pair of glittering eyes trained steadily on Shion.