% !TeX spellcheck = en_US

\chapter{Into the unknown light}

\myepigraph{In the heavens, black clouds gathered\\
	On the earth, blustering winds blew\\
	For seven months and seven nights, the storm clouds covered the
	sky\\
	For nine months and nine nights, violent gusts buffeted the land.\\
	The waters of Yangtze swelled up to the top,\\
	and river waters spread to every corner of the land.}{Chinese myth -- Creation Story of the Lisu}

\lettrine[ante=``]{M}{a'am}, can I have some muffins, please?'' Lili came bursting into the
store.

"Huh?" She stopped abruptly, and blinked quizzically, still clenching
the coins in her fist. Karan couldn't help but smile at how adorable she
was.

"You're here again, Uncle?"

Yoming smiled wryly at his niece's frank attitude.

"Lili, I'm here to do my job. You understand, right?"~

"What job?"

"You know Ms. Karan's muffins, the ones you love so much? I'm going to
write a feature on them. An impressive job, don't you think?"

"What's a feature gonna do?"

"It'll make the muffins famous. Ms. Karan will have lots and lots of
customers."

"I don't want that," Lili said, puffing out her cheeks sulkily as she
glared at her uncle. "If everyone buys her muffins, there won't be any
left for me."

"Don't worry," Karan said as she took two muffins out of the display
case. "You're my important customer. I'll always set aside some for you.
Cheese and raisin, one of each. The raisin one is a present from me."

"Really? Thank you," Lili glowed. "Can I eat it now?"

"Sure you can," Karan said. "It's right about tea time, anyway. Why
don't we make some hot cocoa for Lili, hmm?"

"Yay! You're the best," Lili grinned.

\emph{How lovable she is.}

Karan's heart warmed. It always happened when she saw children smile. A
warm, gentle feeling rose up inside her heart each time.

As a resident of Lost Town, an older district of No. 6, Lili was
certainly not in the most plentiful of environments. In a city like
this, where elites sat at the pinnacle and a complete hierarchy ruled,
no matter how hard Lili tried, she would never be able to climb to the
upper echelons. Lost Town was a residential district for people who sat
at the bottom of the hierarchy. Among adults, there were many people who
showed listlessness or angry abandon at their defeat, but children were
not infected by this. They raced down alleyways, laughed at the smallest
things, and set their eyes aglow at tasty foods. Perhaps this was an
easier place to live for them compared to Chronos, where they would be
placed under strict management and thorough instruction.

\emph{I want them to be happy.}

Karan thought in her heart while she gazed at Lili's carefree smile.

\emph{I want the children, at least, to be happy.}

\emph{But what should I do so that they can? As an adult, what am I able to
do? I can't even save my only son, or even the girl that loved him---}

"Karan, what's the matter?"

Yoming lifted his face from photographing the muffins and croissants.

"Oh, no, I was just---"

"Were you thinking about your son?"

"I guess you can say that... But I'm always thinking about Shion," Karan
said. "I haven't forgotten about him for a single second. He appeared in
my dreams last night, too."

"Of course," Yoming said softly. "Of course---you're a mother. I'm sorry,
that was inconsiderate of me."

Karan turned to face Yoming, and shook her head firmly.

"He looked very well."

"What?"

"My son. He was smiling. He looked a little thinner, but he had such a
nice smile on his face. I thought, my, this boy must be happy. I was
happy, too. Even my heart felt a little lighter when I woke up."

"Happy, huh," Yoming said thoughtfully. "Karan, whatever state he's in,
your son is out there alive. That's for sure."

"And I'm grateful for it."

\emph{As long as you're alive, I won't ask for anything more.}

\emph{Shion, live---and come back to me once more.}

She placed a cup of cocoa down in front of Lili, and a cup of coffee in
front of Yoming.

"Huh? Are you eating too, Uncle?" Lili asked sternly. "Don't you think
you're overstaying your welcome?"

Yoming choked on his coffee. Karan burst out laughing.

"Both you and your uncle are my special customers. It's on the house,"
she reassured her.

"Okay," Lili replied, somewhat unconvinced. "You know, Mommy thinks
Uncle Yo might be making moves on you, ma'am. What's 'making moves'
mean?"

"Oh dear," Karan said with a smile.

Yoming broke into a fit of coughing.

"Th-That's absurd," he sputtered. "Tell Renka---tell your mother, that
Uncle Yo was very, very angry about that."

"I don't think Mommy's gonna be scared of you even if you get mad," Lili
said boldly. "You won't get dinner next time you come to our house,
Uncle."

Karan was so amused by the sour expression on Yoming's face that she
knelt down behind the display case to succumb to laughter. As she
laughed, she remembered what Yoming was saying to her before Lili came
in.

\emph{Karan, do you think we ought to keep on being this way?}

That was how Yoming had started the conversation.

\emph{Do you think this city, No. 6, should keep being the way it is?
You might not know much, but you do know enough. You know that this
place is built on lies.}

\emph{Yes, I know.}

\emph{Both you and I have had our sons stolen from us. You still have
hope, but my son will never come back again. Nor my wife. This city eats
people up like a demon.}

\emph{Yes.}

\emph{Karan. Don't you think we can change this place?}

\emph{Pardon me?}

\emph{Don't you think we could change the Holy City so it can be reborn
again into a place of human beings?}

\emph{Us... change...?}

\emph{Not only the two of us. There are others who have realized the
true nature of the Holy City. We're---}

That was when Lili had come bursting in.

Karan lapsed into thought.

\emph{Instead of just waiting, just praying, or just crying the days
away, what can I do to embrace Shion again? What can I do to save Safu?}

\emph{Cheep-cheep.}

There was a small squeak. A cry she had long awaited. A small mouse was
curled up under the display case. Its long tail and grape-coloured eyes
shone in Karan's vision like diamonds. In the long hours after Shion had
disappeared, what strong support this tiny creature had given her at
times when she felt like she would be washed away by her despair,
loneliness, and hopelessness.

She gently placed a morsel of cheese muffin on the floor.

\emph{Thank you. Thank you so much.}

"You came again."

A pea-sized capsule dropped into her outstretched palm. It was a letter
from Shion. She had been told at the beginning that if anything
out-of-place happened, a black mouse would come to notify her. It was a
brown mouse this time, like the last. Shion was still safe. He was still
alive. Perhaps he was even breaking out into joyous laughter now and
then.

\emph{Shion.}

She spread open the contents of the capsule with trembling fingers. It
was a folded scrap of paper. On it was just a single line.

\memo{\shion}{Mom, thank you. I'll love you always.}

That was all it said. It was Shion's writing, without a doubt. It was
his letter, which she had long hoped for. But a sense of unease rippled
through Karan's heart. This---

\emph{Mom, thank you. I'll love you always.}

These were almost like words of farewell. Like a last kiss, a last
embrace, the last words.

\emph{Mom, thank you. I'll love you always.}

\emph{Goodbye.}

The last unwritten line swirled inside her head.

She stood up. She felt faint. The ceiling, the floor, was spinning.

"Karan!"

"Ma'am!"

She heard Yoming and Lili calling her from far away.

\emph{Shion, wait.}

She reached out and yelled.

\emph{Where are you going? What do you plan to do? Don't tell me---Don't
say you're---}

The Correctional Facility.

She couldn't stop shaking. Karan was seized by the horror of what her
actions had brought about.

She had told him about Safu. Shion was intending to help her escape. He
was the kind of boy who would do something like that. It was something
Karan would have known he would do. She should have known more than
anyone else.

Her ego as a mother emerged fully exposed.

\emph{I shouldn't have told him. Out of all people, I should never have
told Shion.}

\emph{No, Shion. You can't go. You can't be the one that dies.}

\emph{Wait, wait.}

She fell to her knees. In front of her was a small mouse. It was holding
the muffin morsel in both paws, and nibbling at it.

\emph{Nezumi---}

Uncertainty weighed heavily upon her chest, and her heart felt like it
was being wrung.

\emph{Where are you? Are you by his side? If you are, then please don't leave
him. I'm begging you. Protect him. Protect him.}

\emph{Nezumi!}

\myspace

The air was thick with the stench of blood, refuse, and sweat. The
people had been crowded into a windowless cargo container, squeezed so
much they could barely move, and they were gasping amidst the stench of
blood, refuse, and sweat. He couldn't breathe. It was hot and humid in
this confined space, and there was no light. It was like they were not
even permitted to breathe.

Beside Shion, a man entering his senior years gave a short gasp. After
several sharp breaths, his head lolled forward. Shion could feel the
man's body begin to convulse repeatedly through his own shoulder, which
was pushed up against him. Shion managed to squirm enough to get his
hand free and place it on the man's mouth.

"Nezumi," he said.

"What?"

"This man---he just died."

"I see," Nezumi responded flatly. "Did he have a heart attack or
something?"

"It might be."

"I see. Well, if he was able to go quickly, maybe it was all the more
lucky for him."

Maybe it was luckier to be able to die here, rather than not being able
to die here. Nezumi's words weren't sarcastic or joking. It was probably
the truth.

As Shion withstood the weight of the deceased man, he thought about the
baby---the small baby he had left along with a dog in the shadows of the
rubble. Would the baby survive?

"Inukashi's probably in a rage right about now." A smile spread thinly
across Nezumi's lips.

"Huh?"

"He'd be flying off the handle because you dumped that baby into his
care. I can just imagine him holding that wailing baby in his arms and
cursing you to high heaven."

"He'd take care of the baby somehow, wouldn't he?"

"Who knows? It's probably already taking everything he's got to take
care of himself and his dogs. Though he probably won't go as far as to
feed the baby to them."

"Inukashi's kind," Shion said firmly. "He wouldn't abandon a helpless
baby."

"Wouldn't he, now?"

"He wouldn't, because he's been raised by a compassionate mother."

"I see. So you're taking advantage of his compassion and kindness to
dump that baby on him, huh?"

"Oh---well, I guess if you put it that way, I have. I didn't realize."

"It might be hard to imagine for Little Mr. Naive, but it's tough.
Babies and puppies are different. Humans take ten times more hassle.
Poor Inukashi, he has to cut back on his own food income to care for
someone else's baby."

"I'll apologize," Shion said simply.

"What?"

"I'll apologize next time I see him."

\emph{If you ever do}, Nezumi muttered as he shrugged his shoulders.

"But how could you tell?" Shion asked. "How did you know I was thinking
about the baby?"

"We've been together long enough to get sick of each other. I can tell
most of the time. You're pretty easy to read, and---no---" Nezumi cut off
abruptly, and touched his neck. \emph{That's not it}, he muttered. "I can't
read you at all."

Suddenly, they heard muffled sobbing from somewhere. It was a feeble
voice, belonging to a woman.

"Oh... oh... oh..."

As if dragged along by her weeping, there came an eruption of sobbing
from all over. Some belonged to women, others to men. No one was strong
enough to raise their voice in an anguished cry. Seized by despair,
exhaustion, and fear, they could only weep softly, in a voice that was
barely audible.

As he squatted on the floor hugging his knees, Shion felt the tearful
sniffling of the people soaking into his body.

\emph{Oh, oh, oh...}

\emph{Oh, oh, oh...}

He wanted to cover his ears, but he knew he could not. Even if he did,
it would come seeping in through his skin. It would seep in through his
nostrils, the tips of his hair.

\emph{Oh, oh, oh...}

\emph{Oh, oh, oh...}

Nezumi lifted his chin, and shifted his body slightly.

A song rang out. It was a song Shion had never heard before.

\poem{On the mountaintop far away, the snows are melting\\
	Becoming the stream that colours green in the beech wood\\
	The fields are now brimming with blossoms\\
	And a maiden more beautiful than they\\
	Makes a vow of love in the beech wood\\
	O youth\\
	Wet your feet in the green waters\\
	And gallop to me like a deer\\
	Before the blossoms fall, come and kiss the maiden's hair}

It was a strange voice. Inukashi had once said that his song was like
the wind, and that it stole the soul away like a wind scattering flower
petals. He was right---Shion could feel his heart being enveloped by the
song, and his soul being beckoned away. In this hopeless space without a
ray of light, for just an instant, flowers bloomed, water babbled, and
the lovers glowed.

The sobbing ceased. The people were enchanted by the song.

Here, in this hellish place, they had heard a beautiful song. It was
like they had encountered a miracle. And it meant that these things
could happen. \emph{Even if we've been cast down into the pits of hell, it
doesn't mean we've been torn away whole from beautiful things.}

Nezumi caught his breath, and gave a dry cough.

"That was a stretch. There's just not enough air in here. My voice won't
last."

"That's more than enough," Shion reassured him. "It's amazing... I don't
know how to describe it... this is my first time hearing you sing."

"Well, the acoustics here aren't the greatest. There's no orchestra, and
no spotlight. On the stage it would look a little better."

"I'd love to hear it."

"Then let me extend you an invitation. Box seats, the best in the house.
You should bring Inukashi and his baby too."

"I will. I bet even a crying baby would quiet down after hearing you
sing."

"Shion, I was kidding," Nezumi said flatly. "Don't take it seriously."

"Eve." Someone raised his voice in the darkness. "Sing for us, Eve.
Don't stop singing."

"Yeah, Eve. Sing for us."

Shion touched Nezumi's shoulder.

"Everyone wants to hear your song."

"I'm being put through slave labour now, am I?"

"You can save people with your singing. Nezumi, you're amazing." Even
Shion himself knew how inept his words of praise sounded. He was
embarrassed. But he did mean what he said.

\emph{Nezumi, you're amazing.}

"Shion, you can't save people with songs or tales," Nezumi said coldly.
"It'll make them forget their suffering for a little while. But that's
about all it can do. They can't save people in any of the real sense of
the word."

"Eve, sing us 'All the Shimmering Things'," a woman's voice pleaded.

"Geez," Nezumi muttered. "If the Manager finds out I've got fans even in
a place like this, he'd probably burst into tears of joy."

\emph{Sing for us, Eve. In this moment, give us your song.}

The truck slackened its speed just a little.

"We've passed through the gates," Nezumi muttered, in a voice low enough
that only Shion could hear. Then he began to sing softly again. This
song had a loping tempo, with a touch of melancholy.

\poem{The pearls at the bottom of the sea\\
	The stars winking in the night sky\\
	And the love that rests in my heart\\
	All the shimmering things I surrender to you\\
	The sea grows stormy---the pearls disappear\\
	The sky grows stormy---the stars disappear\\
	But my love will never change\\
	Through generations of time\\
	Things that shimmer for eternity are just}

The truck stopped. The song cut off abruptly, and atmosphere in the
cargo container froze over again.

"Shion, you hear me?" Nezumi whispered quietly. His voice was heavy now,
completely different from when he was singing. "No matter what happens,
don't get separated from me."

Shion nodded. He clenched his fists.

\emph{No matter what happens, I'll never leave you.}

The truck doors opened.

\emph{"Get off the truck."}

The crowd swarmed off the truck as they were told. Shion followed the
throng. Nezumi nudged him in the ribs.

"That's the Correctional Facility. The place \emph{thy breast hath ached
longingly for}."

Shion swallowed. He swallowed, and stared at the building before him. It
was a building of white walls. This piece of architecture, almost devoid
of any embellishments and clearly designed to prioritize efficiency, was
something Shion was used to seeing in No. 6.

Apart from the fact that it had very few windows, this building looked
perfectly normal. Its height was about the same as that of the Moondrop,
and four wings about two storeys high protruded from it in different
directions, like arms. The protrusions were perhaps unusual, but not
something that gave off an oppressive or foreboding air.

Shion had expected something more hideous. He had believed it to be
something so hideous, he would not be able to lay his eyes on it.~

The Correctional Facility, which was coloured crimson in the rays of the
setting sun, could easily pass as a medical building. It appeared a
sterile and functional place to the eye.

It was far from what he had imagined.

This was the Correctional Facility---and this was where Safu was.

"This would be the back of the building," Nezumi said. "The front
doesn't look much different, though. So, how is it? Looks a lot more
decent than you imagined, doesn't it?"

"A lot more decent," Shion agreed. "It almost looks like a normal
building."

"Yup. But maybe 'normal' is the scariest thing about it."

\emph{"Walk forward."}

The mob lurched forward. The line fell slightly out of array few metres
ahead of Shion. Someone had collapsed. A soldier approached, and dragged
the person away from the line. It was an old woman wrapped in a tattered
shawl. She was thrown out onto the ground like a rag doll.

"Nezumi, what's gonna happen to her?"

"Don't worry yourself with other people's problems. Even if you knew
what would happen, it's not like you'd be able to do anything."

Another person fell. It was a young woman. Her clothes were torn, and
she buckled to her knees, with her arms covering her bare breasts. One
of the soldiers out of the evenly-spaced line dragged her out promptly.
The same thing was occurring both behind and in front of Shion.

\emph{Are they sorting us?}

Saliva welled up inside his mouth.

\emph{They put us in a confined space, so crowded we couldn't breathe;
put us through confusion, despair, terror... but even after that brutal
experience, now they're selecting those who can still manage to walk in
a straight line?}

"Yeah," Nezumi nodded. "They're sorting us. They're disposing of the
ones who've gotten weak or died during the transport."

"What's the sorting for?"

"I don't know. I still don't know what they're planning to use us for."

"Funny you wouldn't know, huh, even though you seem to know everything
I'm thinking about."

"\emph{Heavens}," Nezumi exclaimed in mock surprise. "To think you can
still be sarcastic in these conditions! That's quite something. Worthy
of praise, my boy."

"I was trained by you---I've toughened up."

"But the real sorting is only starting."

"Just starting, huh..."

They trudged in the blustering wind. In that time, several people
collapsed, and were removed from the line.

Among them were those who lay still, those who shook in the cold, and
those groaning in pain. Without exception, they were all dragged out and
herded into one spot.

\emph{What's going to happen to them? What's going to happen, what's
going to happen? I don't know. Even if I did, there would be nothing I
could do to help it.}

His emotions began to grow numb, starting from the extremities. He was
getting used to atrocity. He was becoming unperceptive to brutal murder.
His thoughts slowed and became sluggish. The death of others no longer
fazed him.

Shion reached out and grabbed Nezumi's arm. He made sure he could feel
the body of flesh at his fingertips.

\emph{Nezumi, keep me as the human I am.}

"There's a chance---" Nezumi dropped his gaze. "---that you might change."

"Huh?"

"Here---in this Correctional Facility, you might change."

"What're you talking about?"

"Maybe the time will come when I'll finally realize---I never knew a thing
about you."

"Nezumi, what are you saying?"

Nezumi clamped his mouth shut, and fell silent.

The people were ordered to stop in front of a set of black doors.

\emph{"Begin entering, starting with the ones at the front. Do not make
any noise."}

The line was divided into three groups, and the first group disappeared
beyond the other side of the door. There was not a sound. A few minutes
later, the door opened again.

\emph{"Next."}

It was Shion and his group's turn.

\emph{We're going in there?}

Into the interior of the Correctional Facility.

He had steeled himself. He had already made the decision. But he could
not help shrinking back a little. His heart was expanding so much, he
felt like it would burst through his pectoral muscles.

"This was the only way," Nezumi said softly, his gaze staring steadily
ahead. "This was the only way we had, Shion."

"Nezumi..."

"Let's go."

"Yeah."

A gust of wind blew past them. The doors swung open on each side.

"Eve," someone yelled suddenly from somewhere behind. "A song for us. A
song---"

A soldier wordlessly fired his gun. There was the heavy \emph{thud} of a body
crumpling on the ground. The voice was cut off mid-scream, and the roar
of the wind grew stronger.

\emph{Damnit.}

Nezumi's lips moved to form the words.

\emph{Damnit. Someday, someday surely I'll---}

\emph{"Move forward."}

Beyond the door was a world of darkness.

It was too dark to decipher how large the space was. Like the cargo
container, they were squeezed in well past the capacity of people it
could hold.

The doors closed.

\emph{Lurch.} The whole room began to shake. And it began to move. They
were moving down at a considerable speed.

"An elevator, huh." The floorplan of the Correctional Facility emerged
in Shion's mind. The blank space underground. \emph{This is it. We're
moving down into that place.}

They were descending. Descending. It was like they were falling into the
abyss.

Nezumi's arm slid around his waist.

"Hold onto me. No matter what happens, never let go."

"Nezumi, what---"

"We're going to hell together."

The arm around his waist grew tighter.

"But we're coming back alive. Don't forget that, Shion."

"Of course."

The elevator stopped. The darkness wavered.

"We're gonna fall."

Nezumi's voice echoed into a world cloaked in darkness.