% !TeX spellcheck = en_US

\chapter{Those whose buds bloom}

\myepigraph{Then shall I speak of the two primal Spirits of existence, of whom
	the Very Holy thus spoke to the Evil One: neither our choices nor words
	nor acts, not our inner selves nor our souls agree.}{Zarathushtra's Gathas, Yasna 45.2}

\lettrine{T}{he baby} started crying. Lying atop a grimy blanket filled with holes,
it flailed wildly, raising a voice loud enough to echo off the ceiling.

\emph{Geez, enough of you already.}

Inukashi clicked his tongue, and put the coins he was counting back into
the bag. It was his profit for the day, and it was a hefty sum.

A night had passed since the Hunt, and the West Block was still in the
throes of confusion and anguish. Nobody knew how many had been killed,
kidnapped, or had escaped, and no one had the energy or the means of
finding out.

Early this morning, Inukashi took a dog with him to walk down the
bazaar. More accurately, it was what had been the bazaar---the patch of
land where it had once been until yesterday.

Most of the buildings---though it was doubtful whether those barracks even
deserved such a name---had been destroyed, and were reduced to rubble.
This Hunt had been particularly large and sweeping compared to the ones
before. No, that was an understatement. Although they had destroyed
homes before, even razed them completely for the sake of capturing
people, they had never been in the habit of being bent on destruction
like this. If Inukashi could get a bird's-eye view from the sky, he
would probably have seen a strange scene---a crater in the middle of the
market, with debris forming a ring around the edges.

The bazaar had once been filled with a raucous, though lively bustle,
lined with store barracks of questionable nature, with prostitutes,
pickpockets, starving children, old beggars, cockroaches and rats
roaming about. But in mere minutes, it had all but vanished from this
land.

\emph{It's mindblowing.}

Inukashi stood atop the ruins, and sighed. It was not a sigh of despair.
He was not so innocent anymore to feel anguish towards this catastrophe.
Rather, he was astonished.

\emph{This is how far they're gonna go.}

The people of the West Block were not enemies. They had not retaliated.
They had merely gathered there, without power or weapons. What reason
did they have to be crushed to this extent?

Rather than feel anguish, or wrath, he found himself simply astonished.

This destructive power, such thorough ruthlessness. It amazed him.

He bent to pick up a piece of debris at his feet. Although it was
crumbled badly, it had no burn marks. So No. 6 had not used firearms in
the Hunt this time around. Usually they used outdated high-calibre
weapons like cannons or howitzers; sometimes they simply burned
everything to the ground with flamethrowers.

Inukashi twitched his nose. Even with his olfactory senses, he could not
smell the distinctive smoky smell of firearms. Only the overwhelming
stench of dead bodies wafted over to him. An odourless weapon. It would
leave nothing in the wake of its destruction.

\emph{Acoustic shockwaves?}

He tried saying it out loud. He remembered hearing a little about it
before from Nezumi. They had been talking about whales. He didn't
remember how they got to talking about them. Inukashi had neither
touched nor seen a whale before. He didn't even know what the ocean was
like. The world that Inukashi knew was limited to the ruined hotel and
its surroundings. For as long as he could remember, he had lived within
those boundaries. He had never thought of travelling outside of the West
Block. He was satisfied with his segment of the world, with the ruins,
his dogs, and the market at the centre. He had no intention of going
anywhere. But Nezumi was a wanderer. He was the kind to appear on a
whim, and disappear on a whim. He would never settle in one place.
Inukashi didn't trust wanderers, and he didn't want anything to do with
them if he could help it. But he was attracted to the the tales of the
world that were spun from his mouth. They were stories of worlds he had
never seen and would probably never see. The ocean was one of these. A
wide, blue expanse brimming with saltwater, and the enormous animals
that lived within it---Inukashi's heart quickened with excitement just
hearing about them. Although he had no intention of going anywhere, his
heart was drawn to the unknown world that Nezumi told of. It was
probably because of his skilful storytelling, and his beautiful
voice---though "beautiful" was far from adequate in describing it,
"beautiful" was often the only word he seemed to be able to come up
with. And out of desire to hear his voice and singing, the residents of
the West Block would scrape their meagre wages together, and would flock
to the shabby playhouse.

\emph{Everyone falls into his trap so easily. But I'm not like that. Sure, I
listened to his stories as if I were in a trance, but I wasn't tricked.
I noticed. I still had enough wits to.}

Inukashi threw his chest out, although there was no one to boast to on
this pile of rubble.

But he had not missed it.

Inukashi had noticed Nezumi's tone of voice change slightly during his
story about whales. It had grown flat, losing all of his softness that
usually stroked the listener gently as if with a feather. It was just
when Inukashi had picked a flea from one of his dog's furry collars and
tossed it into his mouth.

"Acoustic shockwaves?" Inukashi licked his fingers, and echoed Nezumi.
"What's that?"

"A sound beam. They turn sound waves into shockwaves to numb the prey
and capture it."

"Those... spleen whales, or whatever?"

"Sperm whales."

"Hah," Inukashi ejected. "Catching food with sound waves, huh. That's
pretty impressive. If there was a sperm whale in front of me right now,
I think I'd want an autograph."

"Humans might do it too."

"Uh?"

"I'm saying humans might start using it too."

"Those acoustic shock-whatcha-ma-callits?"

"Yeah."

"To catch food?"

"For destruction."

To destroy with sound waves? Inukashi didn't understand. But then again,
more than half of what Nezumi usually said was incomprehensible to him.
Nor did he want to understand. But it was also true that many of those
words he could not understand left a mark in his mind.

For destruction.

"Did he..."

Inukashi clenched a piece of debris in his hand.

\emph{Was he predicting that this would occur? Did he know that this
destruction, this catastrophe was coming?}

The wind was blowing. As if to mock what had happened, today was a
bright, sunny day, and a beautiful blue sky spread out over his head.
How alluring the colour was. It stung at his eyes.

Inukashi took a deep breath. His body trembled at the joy that he was
alive, right this moment, and breathing. Many had died. Nezumi and Shion
were missing. They were either buried under this rubble, or had
succeeded in sneaking into the Correctional Facility---either way, they
would never meet again. He was sure they wouldn't.

\emph{Everyone's dead. Everyone's disappeared. But I'm still here, and I've
survived.} He licked his bottom lip. He was smiling, though at no one in
particular.

\emph{I'm alive.}

A triumphant glory raced through his body and made him want to let out a
cry; it shook his body and soul with an even greater force. Loss?
Listlessness? He had no time to be feeling those. \emph{Those who live are the
winners. I lived. I win. Aren't I right, Nezumi?}

A dog barked. It dug at the rubble with its front paws, nudged at it
with its nose, and scrabbled at it again.

"Find anything?"

The dog, which had a grey coat and drooping ears, gave a proud bark, and
trotted over to Inukashi to drop the contents of its mouth onto his
palm. It was a silver coin.

"Good boy." He patted the dog on the head. "Now dig some more. We gotta
find more cash."

The dog's tail wagged furiously at being complimented by its master.

"Listen. This is where the meat shop used to be. Dig, and you'll find
meat. That'll be your dinner tonight. Meat and money. Make sure you find
both."

This time, a small white dog gave a bark. In its mouth was a cloth
pouch.

"Whoa, nice!"

There were no gold coins, but there were several silvers and plenty of
loose change. Inukashi felt like jumping up and down. Frankly, he had
not expected to find this much booty this easily.

\emph{I'm lucky today. Might be the best luck I've had yet.}

He encouraged his dogs to dig more, find more.

He had already heard that the owner of the meat shop had a fat sum of
money stored away. He had just confirmed that owner of the meat shop was
lying lifeless underneath the rubble. A familiar hairy arm had been
poking out from a gap in a crumbled wall. It was the same arm that used
to throw twigs and stones at kids loitering in front of the store, or at
beggars. Inukashi himself had nearly been punched by that arm once. The
man had worn large golden rings on his thumb and index finger, and every
time he swung his arm up for a blow, they used to glitter. Inukashi made
away with the ring on his index finger. It didn't go as well for his
thumb, for it had been blown off entirely.

\emph{He was a stingy, greedy bastard. But too bad. Once you're a corpse, you
can't spend your money, much less save it.}

After the meat shop, Inukashi planned to dig up the used-clothing stall
next door. If he did it well, maybe he could get his hands on two, three
wearable pieces of clothing. He wanted a thick jacket preferably, but he
would take even a single shirt, a single cape. After that was the food
stall. If he could find the large soup pot that they used to stir
leftovers in over the fire, it would come in handy.

Inukashi felt a presence. His eyes darted around, and he clicked his
tongue quietly. Quite a number of people had appeared out of nowhere,
and were beginning to dig up the piles of rubble as well. Some unearthed
something and raised a cry, like Inukashi had just done. A gaggle of
dirty children were fighting over a piece of cloth, presumably a
blanket. For the time being here in the West Block, physical items would
probably be more cherished than money. Money was useless in a destroyed
place like this. But within a month, this place would turn back into a
market again, unchanged from before. It would be lined with the same
haphazard shops, people would come and go, and the place would fill with
bellows, cheers, laughs, and smells of every kind. Prostitutes would
stand in the dim alleyways, and beggars would wander about. Gold and
silver would speak, and speak loudly.

More and more people flocked to the debris. They seemed to spring up out
of the destroyed buildings themselves. If Inukashi dawdled any longer,
all the valuable items would be carried off. He had countless
competitors.

\emph{What pain-in-the-asses.}

Inukashi clicked his tongue again before laughing voicelessly. He lifted
his face, and threw a glance at the dim outline of No. 6's fortress
walls in the distance, the walls of special alloy.

\emph{No. 6, this is who we are. No matter how many times you step on us,
we'll raise our heads again. We'll never be destroyed. We'll crawl
across the ground, we'll set our roots down, and we'll live. We're a lot
tougher than you think.}

He narrowed his eyes. The special alloy caught the streams of light
coming from the sky, and glittered. Inukashi had always averted his eyes
from that light. It had been too blinding for his eyes. But not today.
The glittering wall looked as cheap and flimsy as the rings on the meat
shop owner's hand.

"Maybe \emph{you're} the one that's fragile." He startled himself. He glanced
around, wondering if someone else had muttered it, but there was no one
else around, other than his dogs, within hearing distance. Inukashi was
the only one who spoke a human language.

He pressed a hand to his mouth, and scowled.

He wasn't supposed to think about No. 6. He wasn't supposed to have
anything to do with it. The Holy City had always reigned over their
heads. It was a tyrant. It possessed absolute strength, and crushed the
West Block beneath its feet. But on the other hand, it was also true
that people and merchandise trickled out of the city into the West Block
through smuggling routes. It was also true that Inukashi himself gained
a share of the profits that came from it.

He would latch onto No. 6 like a flea or tick, and live on. After all,
their existence was nothing more than fleas and ticks to No. 6---though
city residents had probably never seen a flea or tick before.

That was what he had thought all along.

\emph{The Holy City reigns; as for us, we're as good as insects.}

Thinking like that did him no harm. He had long discarded any pride or
shame. Once he did away with useless things, and told himself that was
just how things were, he could live anywhere.

This was Inukashi's philosophy, which he had built up during his life.
He had lived by it, with his dogs, and done decently more or less.

But these days, he felt a little strange. The axis of his philosophy was
beginning to wobble. The fortress walls of the Holy City, which were
supposed to be absolute, sometimes looked to him like a cheap toy. Here
he was, mumbling things like, 'maybe you're the one that's fragile'.
There was something wrong with this. It was clearly odd.

He thought maybe---what if---but shook his head.

It was an absurd story. Absurd, indeed. A tick was a tick. As long as he
minded not to get squished and could manage to suck a little blood in
the process, it was good. It was wise not to even think about whether he
could tear through the other's vulnerable spot.

Inukashi told himself so, and grimaced again. His mind was frantic,
urging him to dig out things of worth instead of leaving it all to his
dogs, but his hands remained still.

With his hands dangling, Inukashi furrowed his brow, and turned his
scowling face to the city walls.

\emph{The Holy City reigns.}

\emph{As for us, we're as good as insects.}

But too late, the thought had occurred to him: he could shake the
foundations of that relationship. He could tear through that artificial
wall, and lay No. 6 exposed and naked. It was their fault. \emph{Those
two---Shion and Nezumi---poisoned my mind.}

Suddenly, Shion's face flashed in his memory. It was so sudden, Inukashi
arched his back and stumbled over, almost touching the ground behind him
with his hand.

Shion. The boy whom Nezumi had brought with him. He was a resident of
No. 6, hopelessly dense, and---hard to believe---a first-rate criminal.

It was utterly unbelievable. Speaking of fleas and ticks, could he even
bring himself to kill any? And that hair. Despite being young, his hair
was pure white. It was too weird. Well, maybe his hair wasn't so bad. It
was shiny, and not the kind of hair you'd see anywhere. If Inukashi
could somehow manage to peel his scalp off, perhaps it would sell for a
good price---but never mind, his appearance wasn't the only weird thing
about him; in fact, he was weirder than his appearance.

"Yeah." Shion's clear answer reverberated in his ears. \emph{Are the people of
No. 6 the same humans as us?} Inukashi had asked. Shion had given a clear
answer.

"Yeah."

Inukashi had scoffed at him, but the instant he had heard those words,
his chest had thumped loudly.

The same humans. So the people who lived on this side and that side of
the wall were the same?

\emph{Yeah.}

Inukashi could tell more than easily that Shion wasn't just saying this
for the sake of saying it; he honestly believed it. According to Shion,
it didn't matter where you lived, what colour skin or hair you had; any
person fell into the category of "human". It was weirder than anything
he could believe. \emph{I should've asked him where he learned that.}

And Nezumi. He was no good, either. He was mysterious, much more
dangerous than Shion. Some day, he was planning to utterly destroy No.
6. He was planning to slash No. 6 and tear it apart, like he would slit
open a person's belly and drag out their organs with his skilful knife.

Inukashi rubbed his arms. He had goosebumps. It wasn't because of the
cool air. Every time he thought of Nezumi, he got these. He was afraid.
He would've rather died than admit it, but Inukashi felt a horror
towards Nezumi. From the first time they'd met, he had been afraid of
him. Those grey eyes, that soul-snatching voice, his way with the knife:
it wasn't normal. It was impossible to get a big picture of him. He
couldn't place a finger on him. For some reason, it was horrifying. But
what was strange was that Nezumi was afraid of Shion. Inukashi wasn't
completely sure, but he could feel it. Inukashi trusted his instincts.

Nezumi was afraid of Shion. The reason was beyond him, but this was no
mistake. Both of them were weirdos. Odd. \emph{But I---I let myself get poisoned
by those two. And I believed them---that we could one day shatter those
walls, and bring them down.}

A dog barked. It had apparently found some meat. Drool was dripping from
the sides of its mouth. It looked up at Inukashi in a pleading way.

"Eat." Inukashi jerked his chin. The three dogs pounced on the hunk of
meat. A hollow-cheeked boy was was staring at them intently. Inukashi
sniffed loud enough for him to hear.

\emph{Too bad, kid. Here, you gotta find your own food. No one's gonna give
you a handout.}

The boy left. The dogs latched onto the meat, and sunk their teeth into
it. The sky was blue, and there was not a single cloud in the sky.

\emph{Shion, Nezumi.}

He looked up at the heavens.

\emph{Have you really gone away? Will we really never see each other again?
Have you guys really left? Am I the only one here?}

The glory that had raced through his body only moments before showed no
sign of bubbling up again.

\emph{How am I supposed to face that wall here in this West Block, without you
guys here?}

\emph{Awooo.}

A dog whined. It wasn't any of the dogs he had brought with him.
Inukashi could distinguish each of his dogs by their bark.

This voice was---

Inukashi leapt off the wreckage, and gave a short whistle. A large, tan
dog came bounding out of the shadows of what remained of the meat shop
from yesterday. It pounced on Inukashi.

"You made it alive, huh."

If the Hunt was close, it would be dangerous to roam the bazaar. But if
he shut himself up in the ruins, he wouldn't be able to do business. So
Inukashi had ordered this dog to scout the bazaar out. Since it had not
come home last night, he had given up, assuming that the dog had been
rounded up in the Hunt. Inukashi hadn't expected it to be alive.

"Good job, you pulled through it. But why didn't you come straight home?
Hm? You hurt or somethin'?"

Inukashi ran his hands quickly over the dog's body. No blood came off on
his hands. It didn't seem to be in pain. It was dirty, but not hurt.

"Well then, what were you up to?" he said sternly. "If you were alive,
you should've come straight---" he stopped mid-sentence. He could hear
crying. It wasn't the dog. It was--- a human? And it sounded like a baby.
The dog clamped its jaws on Inukashi's sleeve, and yanked.

"What?"

The dog was telling him to follow. Inukashi had a bad feeling. He never
had good feelings about anything, and if he did they often weren't
right, but he always had bad feelings. And they often turned out to be
right.

\emph{Oh come on, don't tell me....}

The dog led its master between the ruins of the meat shop and clothing
store. It turned back, and flicked its ears proudly. Inukashi stood
still, and stared at the thing that was nestled in the crack between a
crumbled wall and the ground. His gaze wandered for an instant once,
then he blinked, and scrutinized the space between the wall and the
ground.

It was a baby. No matter how he looked at it, it was a human baby.
Wrapped in a dark cloth, it was wailing. It was a clamorous, energetic
voice, almost unsuited for this place.

"Were you here with this kid the whole night? Warming him up so he
wouldn't freeze?"

\emph{You bet}, the dog's impressive brown tail seemed to say, as it wagged
side to side.

"Idiot," Inukashi snapped at him. "What are you gonna do, picking up a
human baby? What good is he, if you can't even sell or eat him? What
were you thinking?"

Although probably not due to Inukashi's bellow, the baby's wailing
escalated to a shrill scream. It was a voice loud enough to make
Inukashi wonder for a second if the wall would collapse from its sheer
volume. He hastily turned his back to it.

Nothing good came out of mingling with babies. Pigs and goats served as
meat, and produced milk as well. There was nothing to lose in taking
care of them. But human babies were nothing but hassle, and useless
baggage. But then again, it was also possible to sell him off after
raising him to a certain age. Indeed in the West Block, there were
merchants who bought and sold children.

\emph{No thanks for me, though.}

Inukashi usually never turned things down if it brought him money. He
dirtied his hands with almost any trade. This place wasn't nice enough
to let you live on pretty ideologies. Yes. He did anything to stay
alive, and he would continue doing so. But trafficking children was one
thing he didn't want to do. Only those who had stooped to the lowest of
the low laid their hands on that business. Inukashi wasn't trying to
preach morals. But he didn't want to fall that low. But that didn't mean
he was going to save the baby that was wailing behind him. He liked to
think he wasn't prone to the kind of softness that would make him extend
a hand out of pity or sympathy, especially if he knew it would be
nothing but a burden.

If he left this child as is, without a doubt, it would die. The flighty
sky was already starting to turn cloudy. Perhaps it would snow in the
afternoon. The ground would freeze over along with the coming of night,
and would easily nip the life of that powerless bundle.

But what was it to him? If the baby was going to die, it may as well be
sooner than later. If it could leave the world without having to know
what suffering was like, maybe that was happiness in a sense. He would
make a grave for the baby, at least. It would only take a small hole to
bury it. It would be much easier than burying a dog.

\emph{Woof!}

The dog barked, and rammed into Inukashi, almost making him fall over.

"Hey, stop! That's enough fooling around," Inukashi shouted at it. Their
eyes met. Even among the other dogs that lived in the ruins, this one
was particularly smart. It was also a descendant of the female dog that
had raised Inukashi.

\emph{He has the same eyes as my Mum.}

\emph{Peaceful, intelligent eyes.}

\emph{If only all the humans had eyes like my Mum's....}

At times, those thoughts crossed Inukashi's mind.

\emph{If everyone had eyes like my Mum's, maybe the world would be a somewhat
better place.}

The dog was dragging the baby out from under the wall. It pawed the
ground lightly.

"What the... hell..." Inukashi gulped. He recognized the cloth that the
baby was wrapped in. He picked the baby up, and realized that the cloth
was a coat. It was second-hand, but of considerable quality.

"Shion..." It was what Shion had been wearing. It was a coat that Rikiga
had bought and forced onto him. "Why did Shion...."

The dog lay down at his feet. Inukashi remembered now, that this dog had
loved Shion. Shion had loved it too, and would brush its fur almost
every day. Both of them were smart; maybe like minds got along.

"Did Shion leave this baby to you?"

Just a single bark---\emph{woof}---an affirmative.

"Th-This must be some kind of joke," Inukashi said, flustered. "Why do I
have to end up with some baby? No way in hell am I gonna take care of
this. Geez, you must be kidding me."

The baby wriggled in his arms. It wasn't crying anymore. Two watery eyes
were fixed on Inukashi. They were black, with a tinge of purple.
Depending on the way the light hit them, the purple shone through more
strongly. Maybe it was the tears: those eyes reminded him of the surface
of a lake at night, brimming with still water. He thought they looked a
lot like Shion's eyes. They were similar. Maybe exactly the same.

"Hey, you wouldn't be Shion's kid, would you? He probably doesn't even
know how to have children." Inukashi found himself speaking to it. The
baby suddenly broke into a grin. Still looking up at Inukashi, it had
raised its voice in an ecstatic giggle. Inukashi felt like something had
reached into his chest yanked violently. He felt like he was going to
cry.

\emph{What the hell, man.}

Inukashi was agitated at the laughing infant, and also at himself, about
to cry. He didn't know what to do.

A shadow crossed the sun. Clouds were coming in. The wind whipped around
his body. He felt something icy on the nape of his neck. Inukashi
finally realized that he'd been sweating.

\emph{I'm gonna go home.}

Inukashi firmly dug his heels into the ground. The gravel beneath his
feet crunched.

\emph{I gotta get home. Uh---so what do I do now... yeah, I'll throw this baby
back where it belongs, and I'll wave goodbye. And then, and then... I
gotta hurry back to the ruins... oh, before that, I gotta dig out what I
can find at the clothing shop...}

He glanced at the rubble beside him, and almost raised a cry. Almost
three times as many people from a few minutes ago were swarming around
the rubble, digging through the remains of the buildings with their bare
hands. They didn't care if their hands bled, or their fingernails peeled
off. In this season of brutal cold, warm garments were next to food in
necessity. They didn't carry the risk of breaking like dishes, or being
crushed, like fruit; if they dug out, washed, and mended the clothes,
they could be resold.

\emph{Got a late start.}

Inukashi clicked his tongue. Even if he joined that crowd now, he
probably wouldn't be able to find anything much. Could he use his dogs
to chase them away? The thought flitted across Inukashi's mind, and he
quickly brushed it away. It was too dangerous. The residents of the West
Block were always on the edge as they clung to their lives, but today
they were even more desperate. No. 6 had, along with the marketplace,
blown away the little morals and order that had set their roots down on
this land.

If Inukashi set his dogs on them, the people would disperse temporarily.
But what would happen afterwards? He would be surrounded and lynched.
People didn't forgive people who tried to monopolize living necessities
amidst destruction and confusion. If they allowed it to happen, their
own portion would not come around. There was no way they would tolerate
anyone who endangered their own lives. The kind of people who did were
not to be tolerated.

Inukashi knew very well how violent someone could become if cornered. It
was no different from a hungry wolf. But Inukashi also knew that once
the confusion settled, order would be restored as well, at least to the
minimal level. Order existed even within wolf packs.

But with all that aside, today's work was done. He would have to be
satisfied with what he had managed to reap from the meat shop. It was
idiotic to risk getting lynched for instant gratification.

Knowing when to make a clean break was also a skill you needed to have
in order to survive here.

"A-bah," the baby sputtered, stretching its hands toward him. Its soft
palms touched his cheek. Perhaps it wanted milk: the baby puckered its
lips and started making suckling sounds. It had been brought up more or
less with care, and was not pitifully thin. For a baby in the West
Block, this was a rarity.

He felt a definite warmth and weight in his arms as he held the baby.

Inukashi sighed, and gazed at it. He had taken it in his arms. They had
made eye contact. He had felt this warmth and weight in his arms, and
now there was no going back.

\emph{Oh, geez.}

He wanted to throw his head back and cry anguish into the heavens.

\emph{What am I gonna do with even more baggage? What the hell am I gonna do?}

Clouds began to cover the sky above him. The wind grew even more chilly.

\emph{What am I gonna do, Shion?}

The dog at his feet gave a great swing of its tail, as if to encourage
him.

Inukashi had no experience with raising babies. But as for puppies, he
had raised a countless number of them. He told himself he would manage
it somehow.

Humans and dogs weren't all that different.

From his experience, Inukashi felt it was true. The only difference
between them was whether one had two legs or four legs, whether one had
a tail or not.

\emph{I've taken it on myself to do it. I'll raise it.}

He had picked it up in his arms, and carried it home---there was no
abandoning the baby now. He would raise it, in his own way. If he was
lucky, it would grow. If it wasn't... well, that was not much to worry
about. It would only die.

Two of his dogs had given birth out of season. Births in the wrong time
of the year were often stillborn. Each dog had four puppies, and half
the litter of each had already been dead when they came out of the
mother.

"Well, hang in there, little guy. It's up to how lucky you are, whether
you'll live or not. If you're unlucky, then don't blame me. You got God
to---no, you got Shion to thank for that. Got it?"

He laid the baby down beside a female dog with black fur, so that it
nestled against the dog's belly. The mother dog, which had lost its
puppies recently, gave a great sigh as it lay on the ground. The baby
was looking up at Inukashi wide-eyed.

They were eyes like a lake surface at nighttime. They reflected nothing,
but they looked like they would suck everything in. Inukashi averted his
gaze, and swiftly backed away. He had to go over what he had collected
today. Inukashi was soon engrossed in the silver coins that were piled
on his table.

It was more than he had expected. He still regretted that he hadn't
gotten any clothes or a pot, but he had no complaints with this amount
of profit.

\emph{One, two, three... that meat shop geezer, I can see how greedy he really
was, look how much he's saved up. Don't worry, I'm in charge of all of
it now. You have nothing to worry about in your afterlife.}

When he had the silver coins between his fingers, shining dully, he
couldn't help but grin. \emph{I sure wish that baby came with his own pouch of
money.}

\emph{But}---he thought, as he clenched the coin in his fist. \emph{I've sure gone
soft.}

He was sighing again. He sighed, and lapsed into thought. \emph{Why? Why did I
bring it here?}

Inukashi swept up the coat that had been flung onto the floor. It was
Shion's coat. He had heard the rough gist of things from the dog. Shion
had wrapped the baby in his coat, and left it in the dog's care. Or,
rather, he had left it in Inukashi's care.

\emph{Inukashi, please take care of him.}

Even before hearing it from the dog, as soon as the baby had gazed at
him, Shion's voice had echoed in his head.

\emph{Inukashi, please take care of him.}

He could almost see the figure of the white-haired boy in the midst of
the Hunt, in the midst of utter chaos in the market, hiding the baby
underneath the rubble. That was why Inukashi could not resist. He could
not abandon what Shion had left him at the border of his own life and
death. If Inukashi let this baby die, then Shion...

\emph{Shion probably wouldn't blame me}, he thought. He would only be
crestfallen. The purple of his eyes would deepen, and a heavy sorrow
would cross his face. Seeing him like that pained Inukashi. \emph{I don't...
want that to happen.}

He drew a breath. The silver coin rolled out of his hand onto the table.
\emph{Hey}, he scolded himself sharply. \emph{Are you supposing you can see them
again? See them alive?}

His own self answered.

\emph{No, I... no, of course not.}

Yeah. It's impossible. Right? As impossible as waking up tomorrow
morning to see the whole ruins in full bloom.

\emph{Yeah... you're right... that might be true, but....}

But? Hey, what're you thinking? This is the Hunt we're talking about.
You saw the mountain of rubble, right? How can you be sure that Shion
and Nezumi are buried somewhere in there? Well, I can't imagine them
being buried so easily if Nezumi's around. The meat shop geezer is the
one who got flattened under his own house, haha. But still---if they
escaped being buried alive, then what? They probably got rounded up and
carted off. To the Correctional Facility.

\emph{Taken to the... Correctional Facility.}

Yeah. Correctional Facility. Once you get through the gates, you can
never get out again. They passed through those gates of death, man.
They've gone to hell. They won't come back. There's no way they could.
They'll never appear in front of you again.

Inukashi bit his lip. He thumped his chest hard, with his fist.

People who went through the gates of death never returned to the world
of life. He knew. Of course he knew.

His mind knew. But this---this here, refused to comply.

He opened his palm now, and rubbed his thin chest.

His heart was raising an objection. It was screaming that it wasn't
convinced.

They had said so many times. \emph{We're going to hell, but we'll come back
alive.} Nezumi with Nezumi's own ways, and Shion with his own, they had
said they would definitely return. Yes, and---and besides, Nezumi had
promised.

\emph{If you're overcome with unbearable pain one day, I promise I'll always
rush to your side. No matter where you are, I'll deliver a song to your
soul.}

Inukashi couldn't forget his serious tone as he had whispered those
words. Although he resented it heartily, those words had supported him.
If he could be wrapped by that beautiful singing voice, all suffering
would disappear, and the peaceful death he had always hoped for would
come. To be unfearing of death meant he could be unfearing of life.
Thanks to Nezumi, Inukashi was able to be relatively unafraid of life or
death.

\emph{He made a promise. I'm gonna believe it.}

One was an airheaded little boy, and the other was a highly dangerous
fraud, but neither of them ever went back on their word.

They would come home.

He stood up, and turned around. He realized it had been unusually quiet
behind him.

The baby had brought its lips to the dog's nipple, and was suckling. The
black dog raised its head and was staring curiously at the human child
clinging onto its nipple.

"Wow," Inukashi mused. He had to admit he was surprised. "You're a tough
one."

He had not expected the baby to be able to feed from a dog so well. But
it had been one to escape the carnage of the Hunt: perhaps it was
blessed with a strong and good fortune.

Fate decided between life or death. God presided over it. But the
ability to cling to life and snatch it came from human power.

"Well, good luck giving life a try." Inukashi nudged the baby's bottom
with his toe. He hadn't kicked it. He had really only poked at it as if
to tickle it. But the baby began to cry. It flailed its limbs, and broke
into sobbing. And soon, that turned into a full-out wailing.

"Huh? Hey hey, what's wrong?" Inukashi hastily picked it up in his arms,
and the crying instantly stopped. "Don't cry, stupid. I still got money
to count. I'm busy. I have no time to be playing with you."

He put the baby down, and it instantly erupted into tears again. When he
picked it back up, it stopped, and even smiled.

So Inukashi had to roam about the room with the baby in his arms. The
baby remained in a splendidly good mood as long as it was being held.
Eventually, it began to lapse into quiet breaths as it fell asleep in
Inukashi's arms.

He gently laid the baby down on a blanket, and covered it with Shion's
coat. The tan-coloured dog nestled alongside it. After a moment of
hesitation, the black female dog also sprawled out beside the baby, as
if to hold it to its belly.

\emph{What's up with him? He's just a kid, and the dogs are already starting
to like him.}

The dogs around Inukashi were midway between wild and domesticated. They
lived in the world of humans alongside them, but they did not trust
humans. They were apprehensive, fearful, and even attacked humans at
times. They were cautious and aggressive. It was highly unlikely for
them to accept any human apart from Inukashi so easily. Sure, it was a
defenseless baby, but Inukashi couldn't believe that they had taken it
under their wing so promptly. He had even been prepared for the baby to
receive two, three bites at least....

\emph{Geez, what's up with this kid? Maybe he really has some of Shion's blood
in him. Don't tell me he's gonna grow up to be an airhead like him, too.}

It was kind of funny when he tried to imagine it, and he laughed. But
now, the baby had no fear of freezing. It had filled its belly, and was
now able to sleep, free of the cold. It was something to be thankful
for. For Inukashi, this would have been the most fortunate circumstances
he could ever be in, But yet the baby still cried. Whatever it was that
made him unhappy, made him start crying not even five minutes after
being laid down. If he carried it, it stopped crying and went to sleep;
if he put it down, it woke up and cried. This repeated itself. Counting
money was the last thing he could do.

"You idiot. I'm the one that wants to cry here. If you don't knock it
off soon, I'm gonna throw you in a pot and make you into dog food," he
griped. It had apparently not gotten across to the baby, for it squealed
and giggled enthusiastically, its voice bouncing off the walls.

\emph{If this was Nezumi, he'd probably sing it a gentle lullaby}, he thought.
A super-special one that would lull the baby into a deep sleep that
would not make him wake until morning.

Inukashi didn't know a single lullaby. Raised by dogs, only thing that
lingered in his ears was the sound of the wind and the growling of the
dogs. Both of them stirred unsettling feelings rather than invite sleep.

\emph{Could I get my hands on food tomorrow?}

\emph{Could I avoid freezing to death tomorrow?}

\emph{Could I avoid getting beaten up too badly tomorrow?}

\emph{Could I still be alive tomorrow?}

The wind brought snow, and growling brought news of danger. It had
always been like that.

Danger, danger. Be careful. Don't let your guard down for even a second.
See, that vulnerable moment could cost you your life. Look out, it's
dangerous. Look out, be careful.

The dogs and the wind had always whispered those words. No one ever sang
to him, told him, \emph{relax and rest, sleep peacefully}.

Inukashi stopped pacing, and rocked the baby in his arms.

\emph{When I see Nezumi next time, I'll request a lullaby for this baby. Of
course, for free. This kid is Shion's business anyway, he wouldn't be
able to say no.}

\emph{I'd want to hear it too}, he thought. \emph{I'd want to hear Nezumi sing a
lullaby, even just once.}

He touched the baby's cheek. It felt plump. It wasn't hard or taut, and
had a smooth elasticity. It was comforting to the touch.

\emph{Might be tasty to eat.}

The thought crossed his mind, half-serious. His stomach, empty save for
leftover food, contracted, squealing insistently. His mouth watered. In
the end, it was meat over lullabies. He needed a full stomach more than
sleep. He swallowed his saliva.

\emph{Geez, am I hungry.}

The air shifted. The air that surrounded the ruins hummed. The barking
of dogs resounded throughout.

\emph{Who is it?}

\mybreak

Someone was coming. The dogs lying down outside were now raising their
voices in apprehension. But there was nothing to be agitated about. The
barking of the dogs, both large and small, was not overly wrung in alarm
or threat.

It was not an enemy. No stranger had wandered in; no thief had snuck in
either. It was someone unwelcome, but of low risk.

Inukashi raised his face and quivered his nose. He caught the smell of
alcohol. At the same time, a puppy with a torn right ear burst into the
room. It yapped insistently, reporting who the visitor was. Inukashi
gave a light wave of his hand to shut it up. See, dogs were great. You
told them to shut up, and they did.

"I know, I know. I could smell it from here. The alcoholic old man,
yeah?"

His eyes fell on the coins sitting on his table.

"Oh, crap." He shoved the baby onto the dog, and hurriedly shovelled the
coins into a bag. The moment he stuffed the bag into his pant pocket, he
heard footsteps clambering up the stairs.

The door burst open violently.

"Will you knock, at least?" Inukashi seated himself in a chair, and
scowled exaggeratedly. "What if I was changing?"

"How many---times---in your life---do you ever--- change your clothes?" Rikiga
panted heavily, his shoulders rising and falling with every breath. He
leaned against the wall.

"Hey old man, you better not run around so much. Your lungs are probably
half-melted from the booze. Watch you don't suffocate and die."

Rikiga thrust his right hand out, still gasping.

"What? You want a handshake?" Inukashi said.

"Get me a... glass of water."

"One copper coin."

\emph{"What?"}

"You want something to drink, you trade me one copper coin for it."

"Inukashi... you little..."

"Hey, this is a ruins. I don't have any running water like your place,
old man. I draw the water from the stream. Precious stuff. One copper,
no change."

Rikiga clicked his tongue. His forehead was damp with sweat, despite the
biting cold. He must have been in a great hurry, for his breathing took
a while to return to normal. Wheezing raggedly, Rikiga sank into a
chair, and quipped in a sarcastic voice:

"You're not... charging for seating, are you?"

"This time it's on the house. So, on what visiting business, sir?"

"So the Hunt has actually come, huh."

"Uh-huh."

"Shion's been taken away."

"Looks like it."

"I'm... worried, so worried... I can't sit or stand still."

"So that's why you decided to run a marathon here? Kudos to you."

Rikiga's fist pounded the table. A copper coin that Inukashi had
forgotten to put away fell to the floor and rolled. He stopped it with
his foot, and picked it up.

"No matter how much you worry, it isn't gonna do any good, old man.
Besides, things just went according to plan, didn't they? They managed
to slip into the Correctional Facility, just as they wanted. We should
congratulate them."

He blew on the copper coin, and shined it with his sleeve. "If they make
it out alive, it'd be a cause for celebration."

A deep sigh escaped from Rikiga's stubbly mouth. It stank of alcohol.

"Shion... poor boy... when I imagine what horrible things he must be
going through right now... a good boy, such a good boy... please be
safe."

"Old man."

"What?"

"Not that I really care or anything, but---aren't you forgetting
something?"

"Forgetting? What?"

"Shion didn't sneak into the Correctional Facility alone. Well, they
didn't 'sneak in' really... more like 'captured'," he added as an
afterthought. "But anyway, he's not alone. He's got a partner. Aren't
you worried about him?"

Rikiga's face contorted. If someone were to thrust a rotting corpse
under his nose, his face would probably not be as twisted as it was now.
It was an expression of blatant dislike.

"Are you talking about Eve? I don't care about him. It'd be a load off
my chest if he could get himself caught in a mouse trap while he's at
it."

"I do agree," Inukashi said amiably. "Just imagining Nezumi flailing
around in a mouse-trap box makes me giddy. But you were his fan, old
man. I heard you used to go see him at the playhouse all the time."

Rikiga sniffed dismissively, and turned aside.

"I was being tricked. Who could imagine that personality from a face
like that, a voice like that? Goodness, he's as deceitful as a female
fox."

"He's a guy."

"Either way, it doesn't change the fact that he's a trickster fox
demon."

\emph{Fox demon, huh. That's a good description. More suitable for him than
Rat, though he's probably closer to a wolf than a fox.}

Inukashi shrugged, and closed one eye. "Shion's got a demon fox with
him, then. He'll be fine."

Rikiga leaned forward and grabbed Inukashi's arm. Inukashi almost let
out a cry: Rikiga's grip was that strong. He instinctively clapped a
hand over his pocket. He felt like silver was going to be stolen from
him.

"Really?" Rikiga had his bloodshot eyes open wide. "You really think
so?"

"Th-Think what? Holy crap, old man, that hurts. Leggo of me."

"You really think Shion is okay?"

"How the hell should I know?" He withdrew his arm. Rikiga began mumbling
to himself.

"Eve is a knave, a trickster, a fraud, but he's there when you need
him."

"Are you insulting him or complimenting him?"

Rikiga ignored him, and continued mumbling.

"Yeah. I can count on him. Eve would probably protect Shion just fine.
Am I right, Inukashi?"

"I told you, I dunno." He closed his mouth, and directed his gaze at the
ceiling.

Nezumi was a knave, a trickster, a fraud, no mistake, and that was
putting it mildly. But you could count on him in any situation too, to
put it mildly. This was also no mistake. Nezumi was more cunning and
cautious than anyone Inukashi knew. He was also level-headed, nimble,
and tough. He was like a wolf that didn't conform to a pack.

He had never seen a real wolf before. But he had heard about them from
his mother.

\emph{They're terrifying creatures. They don't open their hearts to humans
like we dogs. Never. They would rather die than be taken care of by a
human. They're prideful. But they're also treacherous and always on the
prowl for a profit. They're greedy and ruthless. They don't carry a tiny
bit of sympathy in their hearts. That's the difference between dogs and
wolves. Now you listen, you're a dog. You're not a human, or a wolf.
You're a dog. Don't you forget that.}

A prideful and heartless creature. In Inukashi's mind, the image of the
wolf he'd been told about so many times overlapped perfectly with that
of Nezumi. He was dangerous if he turned against you. But as a guard, he
was cut out for the job.

If Nezumi seriously tried to defend Shion, maybe they would be able to
return from the Correctional Facility alive. It was a slim chance, but
it wasn't zero.

Nezumi would probably defend Shion seriously, and with all he had. He
would. As long as Shion didn't trip him up, they would probably return
alive like they'd promised.

Inukashi's heart grew calm. \emph{Yeah. Yeah, that's right}, he told himself.

Evidently reading something from Inukashi's expression, Rikiga adjusted
himself in his chair, and nodded resolutely.

"If that's the case, then we should get moving as well."

"Huh? If what's the case?"

"We have to help them from the outside, so Shion can come home. What
else?"

"When did we decide that? I'm staying outta this," Inukashi said
hastily. "I already agreed to be bait once. I've contributed way more
than my share."

"You're acting like you did volunteer work," scoffed Rikiga. "You did
receive your pay for that, if I'm not mistaken."

"That doesn't even amount to pocket money. Whatever. I have no plans of
having anything to do with them or the Correctional Facility again.
None. Zip, I tell ya."

"You're not going to help Shion?"

"Lemme tell you something, old man. I don't got any debts or favours to
repay to that airhead. We're not friends, or brothers, or relatives, or
a parent and kid."

"But he's part of our group."

"Our group?" Inukashi drew his chin back. He had not expected to hear
the words "our group" from the kind of alcohol-pickled example of a
corrupted man who published lewd magazines and made his money off of
selling women's bodies. What a surprise.

Group mates?

"We're all in it together. Am I wrong?"

Wrong he most certainly was. \emph{In it together?} The tip of his nose tensed.
Inukashi remained silent, not knowing whether he should laugh or be
exasperated. Rikiga, on the other hand, seemed to turn more eloquent by
the minute.

"Shion is part of our group. Nobody could ever replace him. Come on,
Inukashi, you like him too, don't you?"

"Not---well---I don't hate him."

"He's like an angel. Untainted. You can't find people as pure as those
just anywhere."

"Uh-huh, is that so?" Inukashi said flatly. "So sorry, for being the
\emph{tainted} one in your company."

"Nobody said you were tainted. See, Shion would never twist people's
words around like that. He accepts things openly, honestly, and as they
are. His heart is rooted in the same place as his mother. Oh, Karan, I
wonder what she's doing now," Rikiga said forlornly. "What if she's
fallen ill from worrying about her son?"

"Who's Karan? Aren't we talking about Shion here? Besides, old man, all
you've been talking about so far is Shion-this and Shion-that. What
about Nezumi? If Shion's part of our group, then Nezumi has to be too,
doesn't he?"

"Eve, part of us? Give me a break. I'd rather welcome a slug into my
extended family than be in the same group as a deceitful fox like him."

"You sure treat him differently from Shion, huh." Inukashi glanced up
into Rikiga's liquor-flushed face. \emph{Pure and angelic? Is this old man
really serious about that?}

Just like how he didn't know what Nezumi really was, he didn't know what
lay inside Shion either. If he peeled off a layer, what would this
angelic and pure figure reveal? Maybe he would be more horrendous and
fierce than he ever expected. Maybe within Shion, there existed some
dark pit of truth that even Nezumi feared.

Rikiga favoured Shion too much. Angel? That was absurd. People could
become devils, but never angels. Besides, sometimes angels could be much
more brutal than devils. A man like Rikiga, who was thoroughly versed in
wiles through his life experience, should know best.

\emph{It stinks.}

There was a stench, other than alcohol. But it wasn't a smell Inukashi
disliked. He preferred the smell of rotting meat over the perfume of
flowers.

Catching Inukashi's gaze, Rikiga smiled vaguely.

"So selfless, don't you think Inukashi?"

"Who? Me?"

"Please tell me where the hell I can find a trait like 'selfless' inside
you. I was talking about Shion. He infiltrated the Correctional
Facility, risking his own life, to save his friend. He's putting his
life on the line for someone else."

"Around these parts, we call those kinds of people Huge Idiots."

"Inukashi, knock it off. If we don't help them out, who will? Shion
believes in us, and he's waiting for our help."

"Old man."

"Hm?"

"I can help you, depending on the event and circumstance."

"Now that's more like it, Dogkeeper of the Ruins. Admirable decision."

"Stop buttering me up, and let's hear your real story."

"Real story?"

"Your aim, old man. What're you after in the Correctional Facility?"

Rikiga blinked.

"What am I after... what're you talking about? I just wanted to help
Shion, that was the only---"

"How much profit is it gonna make you?" Still holding his pocket with
his hand, Inukashi leaned forward. In response, Rikiga slid back, chair
and all.

"Geez, look at you. Every other word out of your mouth is 'profit'.
Money, money, money. Don't you have anything else to think about?"

"Lots. My brain is always going full-throttle. And you too, old man.
Your gears are still turning in there, your greed is still going strong.
The only thing that's gotten sluggish is probably the blood in your
veins, from the alcohol. There's no way you'd stick your hands into a
job that didn't carry profits, am I right, old man? And we're talking
against the Correctional Facility, a direct affiliate of No. 6's
Security Bureau. Enemies don't get any more dangerous than that. Both
you and I helped Nezumi sneak in, either because we were tricked or
because we got talked into it. But this is where it ends, usually. We
get however much money we deserve for that job, and go back to our own
nests. Whatever happens afterwards isn't any of our business... right?
That's usually how it is."

"Inukashi, listen---"

"But this time, old man, you're crawling out of your nest on your own,
even saying you wanna stick your nose into dangerous territory. For
Shion? Of course not. I'd never believe it. If my dogs started baa-ing
like sheep, I'd believe that over you."

"Like I said, it's---"

Inukashi waved his hand impatiently. He was sick of excuses and
justifications. He found himself a little irritated. More and more he
felt like he had had enough of wasting words, trying to make excuses to
each other. He was beyond weary of coating his honest words with lies,
and trying to read the other's intentions.

\emph{At the very least...}

Inukashi inhaled through his nose. The frigid air of the room, which had
no heater, coursed through his body.

\emph{At least those two never made excuses to each other.}

He didn't think Nezumi and Shion had bared all to each other. Nezumi,
especially, probably hadn't. But they never made excuses to each other.
They didn't try to manipulate each other, or shroud their honest
opinions. They lived for each other, not out of give-and-take, nor
greed, nor calculation.

Inukashi had never encountered that sort of relationship. There were
mothers who threw away their lives for their children. He knew a girl
who had sold her body to support her family. But \emph{those two} weren't in
such a sacrificial relationship. One of them didn't have to destroy
himself for the other to be saved.

Friendship, love, group mentality, pity, sympathy, empathy---it didn't
matter what name it was given, but none of them seemed to fit their
relationship.

Both could live for the other, without the give-and-take, without greed,
without calculation, without sacrifice. Perhaps he was tired. Inukashi
found himself envying that relationship---just a little.

He inhaled again.

\emph{But I don't have to be jealous of them. I've got my dogs. Humans will
always betray you one day. They'll never give back to you with their
whole body and soul, like dogs do. Dogs are enough for me.}

"Fine." Rikiga's shoulders shook. A smug smile spread across his lips.
What a hideous grin it was. He committed almost any crime for money. He
had nothing against tricking, threatening, or swindling people.

\emph{Yeah, that face is more like it. The day you put on some mask of a
kind-hearted good Samaritan is the day I stop talking to you.}

"You know, Inukashi, I don't think there's much time left."

"For you? Oh, really? What a shame. I thought so too. The alcohol's
poisoned you, old man. If you've got anything to leave behind, give it
to me before it's too late."

"Who said I was talking about myself? I was talking about No. 6."

"No. 6?"

"Yeah. The oh-so-beautiful Almighty Holy City."

"Not much time left? Give me the details."

Rikiga's grin widened. \emph{Got you biting the bait}, his smile said. There
were times when you had to swallow the bait, even if you could see the
hook. It was bait that was too attractive to ignore.

"Is there something strange happening in No. 6?"

"Yeah. I've been seeing strange movements around the city that are
really standing out."

It looked like Rikiga was serious about his talk: the smile vanished
from his face, and the sarcasm disappeared from his voice. "First: there
have been several cases of a strange disease reported inside the city.
Now, what it is, or whether it's contagious, we don't know yet. But you
remember Fura saying this, don't you? The Correctional Facility, that
other facility that's just been built, and the Health and Hygiene Bureau
are connected. Health and Hygiene Bureau, you hear? Now what does it
do?"

"It monitors the health and manages treatment of all citizens..."

"Exactly. Which means now, that strange disease is also connected to the
Correctional Facility too. You understand what I mean so far, right?"

"More or less. I got a good earful during that farce we did."

"Apparently, Shion's friend was pretty much kidnapped and taken to the
Correctional Facility. And this is still unconfirmed information, but...
someone who was involved in the construction of the facility inside the
Correctional Facility supposedly died a sudden death. He was a resident
of the city, of course."

"Was he killed?"

"Not quite sure about that. But it reeks of death, and it's coming from
the city. And then we have the acoustic shockwaves. Went all-out, didn't
they? One blast, and the whole market's gone. They used a brand-new
weapon to blow up barracks. That's like eating leftovers on a silver
platter."

"Good simile. It just screams education."

"Why, thank you," Rikiga said unconcernedly. "So that means the city was
developing weapons in secret, which is prohibited by the Babylon Treaty.
And now they've started using it openly in public. The Hunt that
happened this time was probably to test-drive their new weapon."

Inukashi swung his neck around in a wide circle.

Rikiga had run all the way here, out of breath, worried about Shion---or
feigning it---but had managed to collect information about the Hunt, and
investigated the remains of the destruction on the way. Maybe he had
rifled through the debris and picked out things that might make him
money while he was at it.

\emph{You can't trust this guy around anything, the tough cookie}, Inukashi
snickered silently in his mind.

"Don't you think it's been hectic in there lately?" Rikiga continued.
"And too many people are dying. Not in the West Block, either---in No. 6,
the ideal city, the Holy City, as it's been paraded as. I've had a long
relationship with that city. It always used to perch prim and composed,
never ruffling its demeanour as a utopia. But it reeks these days. I've
never smelled death come from it so freely, without restraint. Of
course, there have been people killed, people committing suicide,
but..."

"Not this blatantly."

"Yeah. Every death they put under wraps, and disposed of it as a calm
and peaceful death. Do you know about the Twilight Cottage?"

"Whas' that?"

"Outwardly it's a facility for palliative care. A hospice, you might
call it. Ill patients who don't have long to live---mostly the
elderly---have all suffering removed, and can die a peaceful death, not
much different from a deep sleep. That's what they say the Twilight
Cottage is for."

Inukashi purred in his throat. He felt like he would salivate. A death
not much different from sleep: it was something he'd wished for, harder
than anything. He would be embraced in softness, warmth, and he would
softly close his eyes. He would never wake up. His heart would slowly
stop beating, and his breathing would grow few and far between. But his
brain would keep dreaming. Sleep would gently coast over to death. He
would live his last without being shut into darkness. He would be
smiling.

Rikiga peered into Inukashi's eyes.

"Geez, don't make those begging eyes. You're sure easy to understand.
What I was talking about was the Twilight Cottage as it's publicized by
the authorities."

"---which means?"

"Things are different, apparently."

"Different?"

"The Twilight Cottage isn't a hospice; it's an execution grounds."

"Execution grounds? Does that even exist inside the Holy City?"

"Of course, it's nothing like the Correctional Facility. It's not as
obvious... all the patients brought to the Twilight Cottage don't live
out their lives and die a natural death... as soon as they've been
transported, they're drugged, put to sleep, and---"

Perhaps even Rikiga felt resistance towards saying it out loud; he only
twitched his mouth, and then gave a long sigh.

"But why do they do that to the citizens? What for?"

"Because they're useless," Rikiga said promptly, as if he had been
expecting Inukashi's question. "No. 6 is that kind of city. It's
ruthless against people who are useless to it. If that person's only got
his death to wait for, then why not let him go quickly and easily with
drugs? Less waste that way. That's how they think."

Inukashi shuddered. He was getting goosebumps.

He had seen his share of grisly deaths. He had seen so many, the fingers
on both his hands weren't enough, even if he counted over them twice. He
had committed to his heart, and resigned himself to the fact that in the
West Block, you had to accept many different kinds of deaths. That life
and death were different within the walls and outside. But did grisly
deaths pervade inside the walls just like they did outside?

"Old man, who'd you hear that from?"

"My customers. Fura isn't the only one who sneaks out here from No. 6 in
search of our ladies. The tight restrictions they're making these days
is enough to put me out of business now, but I've still got a couple
returning customers. Among them, some work at a direct affiliate of the
city, though not in a position as high as Fura's. Those guys babble to
the girls. Spill the beans. Why do you think?"

"Why---well---because they feel talkative after finishing, or something..."
Inukashi said awkwardly.

"No, no. It's because they don't think of the West Block's prostitutes
as humans. They don't even think that the girls might have brains and
hearts like they do. They don't think the girls can think, or can feel
sadness in their hearts. So they spill the beans. To them, it's probably
like talking to a rock lying on the road. That's why they can go on
divulging workplace secrets. Humans are talkative animals; they can't
shut up. 'I can't talk inside the city, so why not talk to the
prostitutes in the West Block? They probably can't even understand
language anyway.' That's what they think. But those girls listen.
Sometimes they even flatter the guys, in order to draw out more."

"And you take that information and sell it, or use it to threaten people
to make money, huh, old man."

"Well, you have a mix of good and bad information. Most of it is
useless. But my customers from No. 6 these days are more talkative than
ever. Before, it was mostly bragging or exaggerated lies... but now we
have complaints, discontent... uncertainty. All we're getting are
stories about uncertainty. See, Inukashi, No. 6 is no utopia. It's only
trying to keep a skilful hold over its citizens to dominate them. And
that's starting to get obvious. It's starting to fray at the seams.
Those citizens are starting to get suffocated in that interior. They're
living in the ideal city, and yet, they can't even breathe. And they've
started to wonder why. I've heard of a customer who lay in bed all
night, mumbling 'why? Why do you think this is?'."

"I see." Inukashi could finally see where this was going. \emph{So that's how
it is.} "Strange illnesses, the new equipment at the Correctional
Facility, all that information leakage, and the mounting complaints,
dissatisfaction, uncertainty. You're saying gas is building up within
the walls of No. 6?"

"Yeah, gas. It might still be thin now, but what happens when the
density increases?" Rikiga spread the fingers of both his hands, making
a bursting gesture.

"Explode? You're saying No. 6 is gonna collapse from the inside?"

"If everything goes as planned. Before the city-state of No. 6 wields
overwhelming military force---before it can dominate over the world and
its citizens with its power, we have to set the gas alight. And the
Correctional Facility is where we'll start. Most of the mysteries are
focused on that place. We try prodding it for information. Aren't you
excited to find out what we'll find?"

"---and that's what Nezumi said."

"Idiot. How could a kid like him come up with an advanced theory like
this?"

"Advanced, indeed. No alcoholic brain would be able to come up with
that. What happened to the talk about making money, huh? Is the treasure
gonna get blown up along with it, and come raining down on our heads?"

"It won't come raining down. We have to dig it up."

"Dig?"

"There's supposedly a secret safe in the basement of the Correctional
Facility."

"Secret safe? In that blank space?"

"I don't have bearings on the exact location. But rumour says the head
honchos of No. 6 have hidden a total of several tens of thousands of
tonnes of solid gold bullion."

"Gold... gold bullion, didja say?"

"Tens of thousands of tonnes of gold bullion. They might be bars, I
don't know. So? Don't you feel blinded just imagining that brilliance?"

"But... I mean, where did you get that information?"

"From a girl, of course. A red-headed one named Sulu, who has a
returning customer who works at the Finance Bureau. Quite pretty."

Inukashi didn't care about the red-headed woman. His interest was piqued
many times more by the gold bullion than human flesh.

"So you got it from her."

"Yeah. It was a bed-time story, though, so I'm not one-hundred percent
sure about its credibility. But it's plausible, isn't it? A mountain of
gold in a place where infiltration and escape is impossible. Safer for
hiding than anywhere else. Pretty believable, I would say."

"Are we gonna be able to get it?"

"We \emph{will} get it. Once No. 6 begins to crumble, the whole place will be
chaos. If we take advantage of it... what do you think?"

Inukashi growled softly. It sounded like a dream. Should he simply laugh
and call it a stupid story, or play along with this fairy tale, just for
the sake of it?

"Does Nezumi plan to destroy the Correctional Facility?"

"Eve? He might do it. He can't create much, but he can sure destroy. No,
why don't we have him do it? Let's have him make a spectacle out of it."

The Correctional Facility---the very embodiment of fear itself---would
crumble. Inukashi's heart danced just imagining its destruction unfold.

The collapsing Correctional Facility and the glittering mounds of gold.
He would receive two of the best compensation he could ever get, in
these two hands. Perhaps it was worth the challenge. However---

Inukashi licked his lips. He inhaled, filling his nostrils with the
odour of dogs that permeated the room.

However, if he had to invest his own life in this capital, he would
decline. He would rather remain in the ruins starving, but living, with
his dogs, rather than die buried in gold.

"What do I needa do? If it's anything risky, I'm not in."

"I know, I know. I wouldn't put you in danger. I just need your
connections."

"Connections?"

"There's a man who passes on leftover food to you from the Correctional
Facility, am I right?"

Inukashi narrowed his eyes, and clenched his jaw lightly. Behind the
drink-drowned middle-aged man, Nezumi was wearing his signature ironic
smile. He could see it.

\emph{Good job, Nezumi. You softened this tough cookie up. Nice cooking
skills.}

Many different feelings and desires were mingling, melting, and writhing
within Rikiga: genuine compassion for Shion, destructive impulses, a
strong desire to see No. 6 crumble before his eyes; and more than
anything, an attachment for gold bullion. Nezumi had used this to his
advantage. He had very artfully used this in his favour, had given
orders to him, and was controlling him this way. It was quite something.
But it was also possible that Rikiga was fully aware that he was being
controlled, and had agreed to play the marionette for Shion and for gold
bullion; for greed and love.

Inukashi found himself sighing. They were like a raccoon dog and
fox trying to out-trick each other. Suddenly he began to miss
Shion. He was a mystery, sure, but he was a hundred times better than an
old raccoon dog and demon fox. Inukashi missed those awkward, naive
actions of his; his earnest and foolishly straightforward way of saying
things; his carefree smile. He wanted to see Shion.

"You're receiving a substantial amount of leftovers, aren't you? That
route hasn't been cut off, has it?"

"No." It wasn't cut off yet. The man who was in charge of waste disposal
not only resold leftovers, but also the clothes and belongings of
prisoners through secret routes. He had even once complained that he was
assigned to dispose of dead bodies. It was the department where all of
the facility's garbage and corpses were gathered. It was located inside
the Correctional Facility, and it was regarded with the least
importance, and for that reason the management was also lax. But it
would probably be impossible to use him as a foothold to sneak into the
Facility, much less get back out of it. The man had said he was not
allowed even a single step inside the Facility from the waste disposal
site. The door that led inside simply didn't open.

"Would he be useful at all...?" Inukashi said dubiously.

"He will be. Every knife, no matter how dull, has its uses."

"Did Nezumi say that too?"

"Who cares? You clearly have something against Nezumi, and it's over the
top. Look, Inukashi, keep the line open with that man. It'll come in
handy. If you can, get him wrapped around your finger."

"Got it." \emph{What was his name again?} The man had a thin, long face with
drooping eyebrows, and sighed a lot. He cared about his family---and he
had complained that he wasn't even allowed to tell them that he was
working at the Correctional Facility, and that he would be instantly
fired if he did. 'It gets you down, really, not even being able to tell
your own daughter what you do for a job,' he had said. Daughter? Oh yes,
he had one daughter. He had also said that a baby was coming soon... and
he was in need of money. He wanted a good amount to sustain his
family---\emph{yeah, it might not be that hard to soften him up}.

"I need money. You gonna set me up with some, right, old man?"

"I know, I know. I won't force you to dig into the savings that are
loading your pocket down right now." Rikiga scratched his chin, and
grinned. "Going after the meat shop man's savings, huh? You've got a
sharp eye. I have renewed admiration for you, Inukashi."

"Same for you. Who woulda known you'd find about it so fast? Pretty
amazing. I'm in awe."

\emph{Geez, the raccoon dog. Nothing goes unnoticed when it comes to him.}

Inukashi had just shrugged when the baby began to cry. Rikiga stood up
from his chair.

"What's that?"

"What's what?"

"That voice. It's a baby crying."

"Huh? I don't hear anything," Inukashi said nonchalantly. "You having
auditory hallucinations now, old man? My heart goes out to you."

After throwing a glance at Inukashi, Rikiga took big strides toward the
dogs laying in a corner of the room. They instantly rose and began to
growl menacingly at him.

"Inukashi, what's this?"

"My dogs."

"This crying one too, the one that's lodged in between the dogs? New
breed? Because it has no tail."

The wailing renewed itself with even greater volume. Inukashi
reluctantly picked the baby up in his arms. Rikiga shook his head.

"What did you pick it up for? Planning to sell it?"

"I didn't pick it up, it was thrust onto me," Inukashi said obstinately.
"By your little angel."

"Shion?"

Inukashi gave a brief explanation. Rikiga nodded in assent with a solemn
expression on his face.

"Sounds like something Shion would do. It probably came to him instantly
to hide the baby. When his own life was in danger, too... he's a living
angel."

"Angels don't thrust babies on other people. Geez, nice burden he's
given me."

"Don't complain. Think of how Shion must have felt. The little guy's got
a cute face. It's a boy, huh. What's his name?"

"Shionn\footnote{'Shion', but spelling changed to distinguish the two}."

"Huh?"

"He dumped the thing in my care, so he can have the same name too. Hey,
old man, don't you think this kid's eyes look just like Shion's?"

"Hmm, now that you mention it, they're the same colour," Rikiga said
thoughtfully. "And they're clear, like his. Beautiful eyes."

"Right? He's an angelic child. So take him home, will ya?" He proffered
the baby in his arms. Rikiga backed away, shaking his head.

"No, sorry, I'm a bachelor."

"Well, so am I. But you've got tons of women with big boobs, old man."

"Yeah, but none of them can give breast milk. Here, on the other hand,
you don't even need diapers because the dogs will lick the baby clean.
They'll even warm him. You grew up like this too, didn't you? Brilliant
childrearing environment... oh, I know, I'll get my hands on some
powdered milk and deliver it to you."

"\emph{Shion} left the baby, you know," Inukashi said pointedly.

"I'll get some soft and clean blankets for you, too. And not just
one---two or three. Well, see you then, Inukashi. I'll come by again
soon."

With a scramble of hurried footsteps, Rikiga all but sprinted out of the
room. Apparently his knack for making speedy getaways hadn't
deteriorated yet.

The baby smiled in Inukashi's arms. It grabbed at his long hair, and
grinned happily.

"Hey Shionn, that hurts. Don't get carried away." Inukashi prodded the
baby's nose. A wide grin spread over the tiny face. "You happy that you
have a name now? You gotta stay alive until Papa comes back, then,
alright?"

A wind blew into the room. The sky was completely covered in grey
clouds.

\emph{Stay alive, Shion. Live to come pick this little guy up.}

As Inukashi turned his face up to the snow clouds drifting by, he found
himself murmuring those words as if in prayer.