% !TeX spellcheck = en_US

\chapter{Curtain up}

\myepigraph{Howl, howl, howl! O, you are men of stones!\\
	Had I your tongues and eyes, I'd use them so\\
	That heaven's vault should crack! She's gone fore ever.}{King Lear Act V Scene III}

\lettrine{B}{eyond} the gate was a world of darkness.

It was freezing. The man shivered, and flipped the collar of his jacket
up. His coat was woven of the finest cashmere, and it was lightweight
and warm. It was also equipped with an automatic sensor that registered
the temperature of the body and outside air to adjust the temperature
inside the coat accordingly. The sensor itself was smaller, lighter, and
slimmer than a postage stamp.

He could feel the biting coldness of the air on his partially-exposed
face, but the rest of his body was enveloped comfortably in the warmth
of his coat. So when the man shivered, it was not because of the cold.

It was the darkness. It was too dark.

No. 6, where the man lived, was a city of light. It sparkled and brimmed
with it, regardless of whether it was day or night. Light wasn't the
only thing he had access to freely: thanks to leaps in biotechnology, a
steady supply of food was always available, independent of seasonal or
weather conditions, and he had access to any manner of foodstuffs. It
was the same with energy supply. As long as they were inside the city,
people were able to lead an abundant, secure and hygienic life. Apart
from them, there were five other city-states in the world, but no other
place had an environment as perfect as theirs. This was the reason
behind No. 6's second name of the Holy City.

The man held an important position in the governing body of the Holy
City. Inside the Central Administration Bureau, he held what was
equivalent to the third most powerful spot. He was an elite of the
elites. His son, who was turning three this year, had also scored
highest in intelligence in the past Children's Examinations. The man was
already receiving childrearing instruction through a Special Curriculum.
If no problems arose ― no problems would arise, naturally, because in no
way would anything unpredictable happen inside the Holy City ― then his
son, as an elite as well, would be able to acquire a life which lacked
nothing. It was promised to him.

The man couldn't stop shivering. How dark it was. How foreboding it was.
He had no idea that nighttime could bring such fathomless darkness. He
had had no idea, until he had stepped into this West Block.

\emph{What the hell is he doing?}

The man who was supposed to be there to fetch him, wasn't. He was
usually waiting for him in the cover of darkness, but tonight, there was
no sign of him at all.

\emph{Has something happened?}

\emph{Maybe something has come up.}

\emph{If so... then it isn't very good.}

The man exhaled in the darkness.

It was best not to dawdle here any longer. He must pass back through the
gates, and return to the Holy City. He must.

His reason commanded him to return, to turn on his heel, and go back
into comfort and light. But the man could not move.

\emph{Just a little longer. I'll wait for five more minutes.}

It was a lingering attachment. It was his attachment for the few hours
of pleasure and decadence that he was about to enjoy. This attachment,
for the few hours he spent fooling around with women in the West Block,
weighed his feet down and prevented him from walking away. How enticing
it was to spend the hours in a drunken stupor, in the company of women
with hair and eyes in every colour. It was almost a year now since he
had first been irresistibly drawn into this enticement. There was no way
out of it.

The City's management was getting stricter. General citizens were
restricted, naturally; but even the upper echelons, which had had
considerable freedom, were being imposed with limitations. Travel
between the city and the West Block was one of the things which limits
had been placed upon.

\myspace

All travel between other Blocks were prohibited unless with a clear
reason and an application to do so.

When the man had seen that section of the city's notice, he remembered
giving a small sigh. The Central Administration Bureau was a department
that singularly managed all of the city's information. All personal
files of the citizens were naturally gathered here as well. Each
citizen's name, sex, birth date, family structure, intelligence index,
physical characteristics, physical measurements, history of illness,
curriculum vitae, were all contained here. The daily actions of each and
every individual were recorded without fail and internalized as data by
the Central Administration Bureau, through the numerous surveillance
cameras and sensors placed throughout the city, as well as the
data-collection chips embedded in their ID cards. This system was
already well-established.

Thorough management and centralization of data ― and whether for better
or for worse, this man was near the heart of the system. He used his
position to his advantage to overwrite his personal records numerous
times. He had rewritten his file to say he had never entered the West
Block. He had destroyed his records.

It was a crime, he was well aware. He was nervous of what would happen
to him if this was exposed, and at the same time, he was confident that
he would never be found out. He drowned himself in euphoric ecstasy. At
the same time, he wanted to protect his secure life and cowered at its
destruction. And underneath was the confident reassurance that he was an
irreplaceable member of the elite core, and that he would not be
persecuted so easily. Many emotions jostled inside the man.

But in the end, he had given into his desires and passed through the
gates again tonight.

\emph{He's late, a little too late....}

The man chewed his lip lightly.

\emph{I should probably give up for tonight.}

Nothing was more dangerous than standing still like this for a prolonged
time, wrapped in the darkness of the West Block. As the man turned to go
back the way he had come, a low voice called his name.

"Fura-sama\footnote{honorific suffix, like 'Mr.' but more polite}." That was the man's name. The low voice carried over to him
in the darkness. "I apologize for keeping you waiting."

Fura furrowed his brow, and hunched his shoulders slightly.

"Is it you, Rikiga?"

"Yes. I've come to fetch you."

"You're late."

"I'm terribly sorry. There was a slight delay."

"Delay? What happened?"

He could sense the darkness shift slightly as Rikiga shook his head.

"Nothing to worry yourself about. No trouble for you in the slightest
sense, Fura-sama... actually ― ah ― you could say I was delayed for the
purpose of your further enjoyment―"

"Which is to say?"

He could hear a vulgar laugh.

"It's taken me a bit of time to prepare a woman to your liking." The
vulgar laugh continued, and the darkness coiled slimily. "But rest
assured, it shall more than make up for the time I've kept you waiting.
I'm most certain you'll be satisfied."

"Is she that good?"

"Exquisite specimen."

He swallowed. If he could, he would have raised his own vulgar chuckle
like Rikiga, but he restrained himself.

His position was like the heavens in relation to Rikiga as the lowly
earth. a resident of the West Block. He could not bring himself down to
that level.

For Fura, although the West Block was place that provided him with lewd
and luscious pleasures, those who lived there ― Rikiga, or the women ―
were not the same humans as he. He saw them as insects, perhaps. No,
that was too harsh ― they were rather close to cattle. Humans and
cattle, the dominator and dominated. No. 6's surrounding regions existed
to serve the city ― that was what he had been taught since childhood.

"―Shall we go, then?" Rikiga began to walk. Silently, he followed
behind.

\mybreak

The outdated gasoline automobile was uncomfortable to ride, and bumped
and jerked ever so often. The road itself was full of potholes. Once in
a while, the car teetered dangerously. When Fura had first begun
frequenting the West Block, he had more than once raised his voice in
complaint, but now, he thought nothing of it. As one who was used to the
immaculately-paved roads of No. 6 and hybrid cars fully equipped with
shock-absorption, the sudden bumps and sways were new and refreshing.
And more than anything, it tickled his heart with the anticipation for
things to come.

"So?"

Fura leaned forward in the back seat and questioned him.

"What kind of girl is she?"

"I daresay she's a perfect match for your tastes. I'm sure you'll like
her."

"The last girl wasn't so great."

"I know. But this girl, she's exactly as you like them, Fura-sama. Small
frame, slender ― and very young."

"Young, huh."

"Yes. Of course, this being the place it is, we're not sure of her real
age, but she's very young, for certain. So she ― hasn't had experience
with men yet."

"Are you sure?"

"Absolutely. And not only that, it looks like she has the blood of the
southern lands in her veins. She has that sort of appearance."

"Ah."

"We've many women with ripe bodies, but it's a little difficult to find
the younger ones. I could never send you a scrawny, dirty brat to
service you, Fura-sama, nor would I be able to just pluck one off the
street. And besides ― to give this kind of job to a girl so young, and
with no experience, it is quite ― well, it certainly doesn't bode well
with my conscience, to say the least."

\emph{Liar.} Fura retorted in his head. \emph{For money, you'd do anything.
Conscience, you say? Don't make me laugh.}

Although he was no doubt deaf to Fura's words, Rikiga let a dry chuckle
escape his lips.

The car stopped. Inky-black darkness still surrounded them outside.

"This is―?" It was different from the usual place Rikiga prepared.

"It's a hotel."

"Hotel?"

"A long time ago, this used to be quite a fashionable one." Rikiga got
out of the car, and lit a lamp. "The girl and her family have made this
place their home. The girl said she'd only take customers if it was in
her room, and she wouldn't have it any other way ― she's still a child,
she's probably afraid of going to strange places."

"But―"

"It's nothing to worry about. We've had her family removed temporarily.
Tonight, you and the girl are the only ones here, Fura-sama. ―Ah, no,
that would be wrong. She also has her dogs."

"What?"

"Dogs. The girl's father runs a business that deals with dogs. There are
swarms of them here."

Fura couldn't imagine what kind of business would deal with dogs. A pet
shop was certainly out of the question. Were the dogs skinned and sold
as meat?

"If you'll follow me, then. I would advise you to watch your feet."
Rikiga swung the lamp over. Fura glanced at his profile, and carefully
put his foot forward.

He did not trust this man, Rikiga. He had not a thread of trust for him.
But Fura knew for certain that he was a regular and highly valued
customer for Rikiga. There was no way a man like him, who loved, prized,
and trusted money above all, would harm his best source of income. In
that sense, Fura had never felt any apprehension toward the man that was
now walking a few steps before him.

This building that Rikiga had said was once a fashionable hotel, was now
half-crumbled and mostly ruin. Countless pieces of rubble littered the
ground, and there were puddles everywhere. The floor was slippery, but
whether it was because the flooring was rotting, or because moss was
growing on it, he didn't know. He was unsteady on his leather-shoed
feet. The wind nipped at his cheeks. They ascended the stairs. He
smelled a faint, strange odour. It was an odour he had never smelled
inside No. 6, and he had no idea what it could be. They crossed a bare,
spacious area that looked like it had been a lobby, and ascended further
still.

"Oh―"

He spoke without thinking. His feet were rooted to the spot. It was what
looked like a narrow hallway that stretched straight before him. At
least, it looked like it ran straight into the darkness, but he had no
idea what was beyond the darkness that shrouded it; Fura's eyesight,
unused to darkness, could not make it out.

Lit by the dim light of the lamp, he could see shadowy figures hunched
over here and there.

"Dogs?"

"Yes."

"Why are there so many? For what purpose...?"

"Ah, well, there are many reasons, but nothing to do with high officials
of No. 6 like yourself," Rikiga said. "It's nothing to be concerned
about. These dogs are quiet, they won't bite or attack you. ― Alright,
here we are. The girl is inside this room."

Just as Rikiga had said, the dogs remained curled up on the ground,
perfectly still, without growling or baring their teeth.

"Right here, this way. After you," Rikiga ushered him in.

There was a shabby wooden door before him. Perhaps it was the lamplight
that did it ― the aged door looked warm and gentle to his eyes. It was
like a prim old madam. There she was, sitting in a pool of sunlight,
beautiful, with snowy hair. She had knitting needles in her hands, and a
white ball of yarn in her lap―

Fura turned aside, and cleared his throat a few times. He had long
hidden this bad habit of his to lapse into daydreams. If any of the
higher officials at the Central Administration Bureau found out that he
had this tendency, it would mean dire consequences for him.

In No. 6, imagining, weaving stories, speaking of dreams, and
daydreaming were frowned upon and avoided like the plague. There were no
official rules or prohibiting laws, but among common citizens, it was
the object of ridicule and contempt; in central organizations, it was
seen as inappropriate, and a valid reason for job termination. You would
be removed.

The door opened. Its silver knob was manually-operated, of course, and
the door screeched stubbornly as it opened inwards.

It was a low-ceilinged room, and it was dark. The only lighting came
from Rikiga's lamp and a single candle in a stand on the table. It
wasn't too cold, probably owing to the fact that there were no windows.
But the muffled howling of the wind still echoed in the room. Various
whistlings and moanings overlapped in layers like a symphony, tangled
with each other, and reached his ears. He wondered how this place had
been built.

The only pieces of furniture in the room were the table that held the
candle, a rather shabby partition, and a similarly pitiful bed in a
corner of the room. A figure was sitting on the edge of it with a
blanket over his head, curled up as if to shrink into himself.

Rikiga was right, she was small. The legs that protruded from the
blanket were pitifully thin. But they were shapely. They were slender
from the knee-down, and if they had a little more flesh on them, they
would probably have been a beautiful set of legs, indeed.

"How is she?" Rikiga whispered at his ear. "A gem, wouldn't you agree,
Fura-sama?"

"Maybe. I can't tell yet."

Fura lowered himself onto the bed, and slid a hand around the small body
wrapped in the blanket. He could feel her trembling slightly.

"Are you afraid? ―Don't worry, there's no need to be." He took off his
coat, and drew her closer, blanket and all. He could feel the trembling
becoming more violent in his hands. The blanket fell away from her head,
and her hair, black as night, and delicate neck exposed itself to Fura's
eyes. Since she had her face turned away in defiance, her neck showed
even more. Fura could tell even in this darkness that the skin was
smooth and supple. And it was tan-coloured.

\emph{I see. This one may be a gem after all.}

He brushed the long hair aside and let his lips travel up her neck.
There was a faint smell. It was the same scent as what he had
encountered on the stairs. It was the smell of a dog, a beast. But
instead of diminishing Fura's desire, the smell spurred it on even more.
It was a smell he wouldn't have gotten in No. 6 even if he had wanted
to, because of its perfect hygiene. This body was thoroughly soaked in
this scent, and it excited him.

"Well, then," Rikiga said, "I guess I'll excuse myself. Enjoy." Rikiga
made for the exit with an absent smile on his face. Fura stopped his
hand, which had been in the middle of stroking the girl's thin leg. For
the first time, a suspicion flitted in his breast.

"Wait," he commanded shortly, to the man who had his back turned to him.
Rikiga swung around lethargically.

"Something the matter?"

"Don't you find it strange?"

"Strange? What, may I ask?"

"Why haven't you asked for my payment first?"

Rikiga's face tensed. Then, after a while, he muttered \emph{ah, yes, payment},
to himself.

"You always ask me to pay beforehand. Why haven't you brought it up
tonight?"

"Oh, yes, of course. I'd forgotten."

"Forgotten? You? About money?"

The suspicion grew inside him. This man? Forget about money? He, who was
more greedy and miserly than anyone, forget ― he found it hard to
believe.

His doubt and suspicion grew into unease. Things were different from
usual. Why? Why―

The small body leapt up out of Fura's arms. The blanket slid to the
floor.

"Cut this shit out, you bastard," he snarled. "I've had enough of this.
You must be fucking kidding me." Fura gaped open-mouthed at the boy who
had whipped his hair around and was baring his teeth, pelting him with
profanities.

"Rikiga, who's this?"

"He is who he is, sir."

"You told me you 'd prepared a young girl."

"Young girls, young boys, it doesn't make much of a difference. I
thought perhaps you had those kind of preferences hidden somewhere
within, Fura-sama, and you just hadn't realized."

The black-haired youth bared his teeth even more. He was almost like a
wild dog.

"You can stop making shit up, alcoholic old man," he growled. "Why
didn't you follow the plan? I'm gonna turn all three of you into
mincemeat and throw you to the dogs. You're paying for this, bastards."

Plan? Three of you? What was he talking about?

Fura gathered his coat, and stood up. He put his arms through the
sleeves and glanced around the room. The four corners were dark, and the
darkness was eerie.

Either way, it was dangerous to remain here.

"Where to?" Rikiga stood in front of the door, barring him with a wan
smile.

"I'm going home. Get out of the way!"

"Please, please, do calm down," Rikiga said silkily. "It isn't like you
to be so uncouth, Fura-sama."

"Out of the way, or else―" Fura clenched his hand around the small
handgun in his pocket. It was an electric gun, not very effective as a
killing weapon, but enough to defend himself. He pulled it out and aimed
it between Rikiga's eyes. If he was going to retaliate any further, he
would shoot without batting an eyelash. It may be for self-defense, but
a gun was still a gun. Any unarmed human, if shot between the eyes,
would die. But he didn't mind. These people didn't even qualify as
humans anyway.

"But the fun's just getting started, you'd be missing out if you went
home."

The voice came from behind him. At the same time, his mouth was covered,
and his wrist was gripped tightly. The gun slipped through his fingers.
He was only being held at the mouth and hand from behind, but his whole
body was trapped. He could not move at all. A cold breath caressed his
earlobe. A whisper flowed into his ear.

"Why don't you hang out with us a little longer? We'd give you such a
good time, you'd melt on the spot." It was a tender voice, and not
clouded at all. It was sweet, clear, and beautiful. Fura couldn't tell
whether it was a man's voice or woman's voice. Perhaps, if he obeyed
this inviting voice, he \emph{would} be able to melt in ecstasy. It was a
thought that lasted a mere blink of an eye.

His feet were swept from under him, and he was slammed to the floor. His
breath caught in his throat, and he faded out of consciousness.

\mybreak

"Nezumi!" Inukashi yelled, stomping on the blanket. "This isn't what you
promised. What the hell were you doing?"

"Hush, stop barking." Nezumi rummaged through the coat of the man he had
just tied up, and extracted a leather pouch out of one of its pockets.
"Take a cue from your dogs, Inukashi. Lie down and shut up."

"Stop shitting me," Inukashi snarled. "Why didn't you come out sooner?"

"I forgot my line, so I was re-reading my script," Nezumi replied
mildly. "Sorry about that."~

"You must be kidding me. Fucking. Kidding. Me. You half-assed fraud, you
third-rate actor. You're more cunning than a fox, and more shameless
than a pig. I'm never gonna trust you again. I hope you get bitten by
fleas, and get all the blood sucked out of you so you wither and die."

"Stop yapping already, will you? It's not even something to get that
angry about. Alright, I was two, three minutes late coming out. That's
it."

"And in those two, three minutes I got licked on the neck and molested
on my leg."

Nezumi flashed a gentle, wry smile, like one of a mother directed toward
her whining child.

"Inukashi, it's the benefit of the experience. You've just had the
precious experience of getting your neck licked by a high official of
No. 6. You can store it away as a good memory."

Inukashi's clenched fist trembled. His black eyes glittered in his tan
face.

"Besides," he said, "why me? Why couldn't you have done it instead?"

"Why do I have to do it?"

"Because you'd make the perfect prostitute. You lure men in, and make
them completely weak and helplessly infatuated. A liar, a wanton, with a
nasty personality to boot. You wouldn't even have to put on an act."

It was then that Shion finally spoke to Inukashi. Until now, he had been
watching everything unfold in a daze, unable to keep up.

"Inukashi, that's going too far. Don't say any more."

"Same goes for you, Shion," Inukashi turned on him next. "Why didn't you
come rushing out the moment that man sat on the bed? That was how we
planned it, right?"

"Yeah, but―" He was right. In their briefing before the event, they had
agreed to wait until Fura, the high official from the Central
Administration Bureau, had been brought in by Rikiga. When he sat on the
bed, they were to burst out from behind the partition and apprehend him.
That was the plan, and Shion had intended to act on it.

But Nezumi had stopped him. He had grabbed him by the shoulder as if to
say, "don't burst out yet." The bed was creaking unpleasantly. The man
had inched closer to Inukashi. Shion could almost feel Inukashi's panic
as if it were his own. But Nezumi still did not move. He remained
crouched in the darkness, so silent that not even his breathing could be
heard.

"I'm going home. Get out of the way!"

The man's hand drew something out of his pocket. And in the same
soundless way, Nezumi's body glided forward. Shion was not able to sense
Nezumi's movements at all. Although he had been squatting right beside
him, he had not even been able to sense the air around him move as he
shifted.

"Why don't you hang out with us a little longer? We'd give you such a
good time, you'd melt on the spot."

Once he heard Nezumi's voice pierce through the multitude of layered
wind-whistles, Shion finally stepped out from behind the partition and
stood beside Inukashi. By this time, the man was already groaning
quietly on the floor.

Inukashi clicked his teeth, with his nose wrinkled in a menacing scowl.

"'Yeah but'? 'Yeah but' what, huh? Is taking care of dogs all you're
good for? You useless, airheaded idiot!"

Shion couldn't talk back. He was well aware of how unskilled and useless
he was, once he had been cornered. Nothing was quite as painful as an
insult that hit the mark with its grain of truth.

Nezumi bent down and picked the handgun off the floor. He moved it
around on his palm as if to check its weight.

"It's a self-defense gun, latest model. It's pretty small, but if you
got hit point-blank, it would be fatal. I just thought it'd be more
trouble if we risked letting him swing this thing around."

"And that's why you decided to take your sweet time, and wait until this
pervert took out his gun."

"It reduces the risk of danger."

"Risk? Why, isn't that just splendid," Inukashi said sarcastically.
"While I was dealing with this perverted bastard over here, you two were
busily discussing the \emph{risks}. Guess great minds are just different from
us, huh? I almost want to ask you to give a special lecture to my dogs,
next time."

"Don't be sarcastic. Here, look."

Nezumi turned the leather pouch upside-down, and shook it lightly. Five
golden coins spilled out onto the table.

"Five golds, huh. Loaded himself down quite a bit for just one night of
fun, didn't he, old man."

"Actually, not really," Rikiga opened his mouth. His voice was heavy and
hoarse, a startling difference from his earlier cavalier tone.

"I told him I had a woman that was unusual, different from the
prostitutes he usually has. I had to charge him considerably more than
usual, or else he'd be suspicious. He's a cautious one."

"I see."

Nezumi plucked a gold coin up.

"Here, Inukashi. Your share."

The coin was tossed into the air, bounced off Inukashi's fingers as he
snatched at it, and fell on the floor at Shion's feet. Shion picked it
up and handed it to Inukashi. His tan fingers were trembling.

"Inukashi?"

His lips were pursed, and he looked like he was about to cry at any
minute. Shion had never seen this expression on him before. His
shoulders and arms were shaking slightly as well.

\emph{He must've been really scared.}

Inukashi, who had several dozen dogs at his command, lived in ruins, and
with fierceness and strength survived each day, was not able to restrain
his shaking body. Shion tried to imagine just how much fear and
humiliation he had gone through.

Shion didn't know how old Inukashi was. Inukashi himself probably didn't
know either. Most of the West Block's residents were not certain of
their age, parents, birthplace, nor whether they had a life to live
tomorrow. But he could imagine that Inukashi was very young, much
younger than himself at sixteen years. He knew that Inukashi engaged in
fraudulent activities, theft, and even extortion without batting an
eyelash. Inukashi was seldom bothered by being railed at or having
insults hurled his way. But he had not been able to bear playing the
bait in this farce, staged on the bed in a dimly-lit room.

He was still that young.

Inukashi's angry bellows and profanities were but the other side of the
fear he really felt.

"I'm sorry," Shion found himself saying softly. "I've done a horrible
thing to you. I'm really, really sorry, Inukashi."

Inukashi's brown eyes blinked. Their rims were red. His lips moved
soundlessly. Shion placed a hand on his bony shoulder. He didn't think
the gesture was nearly enough to soothe the other boy's anger or
confusion. He knew he would not be forgiven. But he had remembered one
thing. When he was still young, his mother Karan would often put a hand
on his shoulder like this. He had remembered the comforting warmth that
soaked into his body from that gentle hand, wordlessly placed. That was
all.

Inukashi didn't resist. He shifted a little, and pressed his forehead
against Shion's arm.

"Bastards... I hate you all."

"Mm-hmm," Shion murmured.

"I hated... hated it, so much..."

"I know."

"I tried so hard not to scream ― scream for you guys, ask why you
weren't coming out... I tried as―as hard as I could, you know."

\emph{Sorry}, Shion murmured again, and gripped his shoulder firmly.

\emph{Huh?}

Agitation raced through him. He had felt in his fingertips, a softness
of the flesh he had not expected at all. The shoulder was thin and bony,
but soft. It was not hard, taut and bulging with muscle, but soft and
rounded in a curve.

It reminded him of Safu's shoulders in the few times they had touched
his own.

\emph{Could it be ― but how ―}

At almost the same time that Shion gazed at Inukashi, Inukashi detached
himself from Shion's arm, and Nezumi tossed another gold coin. This
time, Inukashi's hand securely snatched it.

"Bonus allowance."

"How nice. Most \emph{honourable} of you, Nezumi."

"You haven't done the work for free. You agreed to be the bait in
exchange for money."

"No need to tell me, I already know."

"Then don't go yammering on about it now. Two gold coins for less than
ten minutes of work. Can't find a job like this just anywhere."

"I told you, I know!" Inukashi repeated loudly. "But you can count me
out of any future roles like this. You can step in for me, or this
airheaded young master here."

"There won't be a next time."

Nezumi shoved the rest of the three gold coins in Rikiga's direction.
"The rest is for the old man's taking."

"How about you guys?"

"Don't need it."

"Modest in your desires, aren't you?"

"You can say that."

"Or are you saying that because money's gonna be useless from here on
anyway?"

"Probably will be."

"I see..."

Nezumi's grey eyes studied Rikiga's alcohol-flushed face.

"What's wrong?" he said. "Why the grave face?"

Rikiga didn't answer.

"Gold coins, old man. Your favourite. Why aren't you accepting them? Not
like they're smeared with poison, at least I don't think so."

"Probably not smeared with poison. We've got something much more
troublesome."

The brown liquid sloshed around in his glass. The sharp smell of alcohol
drifted into the air and assaulted the nose. Rikiga took another swig of
the cheap liquor, and coughed weakly.

"It's money we've stolen from a high official of the Holy City, tricking
him and tying him up. Get our hands on that, and it could cost us our
lives."

Nezumi laughed softly.

"You're starting to get scared \emph{now}?"

"I am," Rikiga nodded promptly. He wiped his mouth with the back of his
hand. "We're already knee-deep, but I'm starting to get scared. We've
really done it, now we've ― we've really turned No. 6 against us."

"They've always been against us. That city has always been an enemy to
us. Are you saying you haven't realized, or have you just pretended not
to? Which one is it, old man?"

Rikiga drained the last of his liquor in one swig, and sighed deeply.
The candle flame flickered, and their four shadows, half-blended in
darkness, also shifted slightly.

"Eve." Rikiga called Nezumi by his stage name. The alcohol seemed to be
working on him, for his speech was beginning to slur.

"―Aren't you afraid to die?"

"Die? Well, that question just came out of nowhere, didn't it."

"You're turning the whole Holy City against you. You don't possibly
think you can brazenly keep living? You're not that naive."

"Old man." Nezumi's hand stroked the tabletop. The gold coins
disappeared like magic. "Sorry, but I have no intention of bracing
myself for death. The ones who live are the ones who win. \emph{They're} the
ones that are going to perish. We're gonna be the ones that survive. Are
we not?"

"Are you serious about that?"

"Of course."

"You're mad. You've gone mad, and you're living in your delusions, Eve.
There's no chance of us winning. Not even a fraction of possibility."

"You may be right."

"It's completely unfounded. Everything you're saying and trying to do,
completely unfounded. Babblings of a madman. It's one percent. 0.01.
You're willing to bet on this tiny fraction?"

"It's a tiny fraction, but it's not zero. Which means you don't know
until you try."

"Eve!"

"Your hand."

"Huh?"

"Prithee lend me your hand, your Majesty." Nezumi forcibly grabbed
Rikiga's wrist and turned his palm upwards. He placed his own hand on
top. Three gold coins appeared.

"Your share, old man. Don't forget to claim it."

The empty liquor bottle slid out of Rikiga's hand, and smashed messily
on the floor. Drops of liquor flew in all directions, and stained the
floor.

"Be more like Inukashi, and accept it humbly. We're in motion now. We
can't turn back. \emph{None of us.}"

"None of us, huh..." Rikiga looked down at the gold coins in his hand,
and his mouth twisted. "Accomplices to the very end, you might say."

"Right. Important \emph{partners}. We each have our own role, and the curtain's
long risen. You better not be thinking of ducking out now, old man,
because it's way too late for that."

"What if I said I surrender my role? Would you kill me?"

"If you wish."

"Knowing you, you'd probably execute the kill beautifully," Rikiga said
bitterly. "What, would you slit my throat with a knife? Give me a stab
through the heart?"

"Don't give me too much credit. It's harder to wield a knife than an
amateur might think, you know." Nezumi turned to Rikiga and smiled.
Rikiga drew his chin back, and grew stone-faced.

"My hand might slip and miss the fatal spot. It happens every now and
then. Pretty gruesome for the victim, huh? He has to writhe around and
suffer because he can't die quickly. Gruesome, indeed. I'd hate to see
one of my precious friends die that way."

Rikiga made a low strangled noise in his throat, and dropped the gold
coins into his pocket. Then, he spat out one word.

"Devil."

Inukashi sniffed dismissively from his spot beside Shion.

"We've always known what a devil he is. No use throwing a fit about it
now."

\emph{No.}

Shion balled his hand into a fist.

Nezumi was no devil. He knew this more certainly than anyone else. Again
and again, his life had been saved, and been rescued from pressing
danger. He had clung to the hand that was extended to him, and it had
pulled him up. His life was not the only thing that had been saved ― his
soul, in the form that it was meant to be ― had also been saved. He
believed so.

Nezumi had pulled Shion up to the heights, and taught him how to gaze at
the world from there. In contrast to a world circled by fortress walls,
isolated and complacent, he had shown him a world which expanded to
limitless horizons, where many forms of human life jostled in one place,
where lifestyles, values, gods, and justice were never the same for
everyone. If he had not met Nezumi, he would have continued living
without knowing a thing about it, and gone on to grow old. He would have
lived peacefully in the Holy City of No. 6, privileged with artificial
vivacity and abundance , never casting a single thought to the world
outside the wall.

\emph{Look.}

Nezumi had told him. \emph{Crawl out of your artificial world, and come over
here.} He had told him to see with his own eyes. To think for himself.
\emph{Think. Think with your own head what's right, what's meaningful, what
you want, what you believe ― not the values, morals, and justice that
have been fed to you, imposed upon you.}

He had been told countless times. At times passionately, at times
coldly, with his voice, his gaze, and his actions, Nezumi had told him
again and again.

Since meeting Nezumi, he had thought about all these things. His
feelings, his desires, his thoughts, his sensations, his hopes, his
beliefs, what he desired to believe. There were many things he could
still not grasp, but to wrestle with his thoughts, and to keep
pondering, had revived Shion's soul and pumped living blood back into
it.

That was what living meant.

To make one's soul one's own. Not to hand it over to anyone else. Not to
be dominated. Not to fall into submission.

This was what it was to live.

Nezumi had taught him this. He had injected new blood into his soul.

And―

And Shion himself was the one who had gotten everyone involved. It
wasn't Nezumi. Shion had gotten the other three involved, solely for the
purpose of rescuing Safu, who had been apprehended by the Security
Bureau and imprisoned in the Correctional Facility. He had dragged them
into a dangerous battle, where the chances of winning were less than one
in a hundred, as Rikiga had said.

"What's up, Shion? You look kinda scary ― not like yourself," Inukashi
cocked his head in a puzzled way. Shion shook his head.

"That's not it."

"Huh?"

"That's not it, Inukashi. Rikiga-san, too. All this, it's all my―"

His eyes met with Nezumi's. Or, rather, it was more like his eyes had
been pulled at and forced to meet the other's strong gaze. Nezumi's
lustrous, dark grey eyes always glittered with energy, and were
beautiful. But despite that, they never showed any hint of emotion. They
had not changed at all from when Shion had first met him. They were
still the same as the pair of eyes he had peered into once, pushed up
against the wall with a set of cold fingers at his throat. Nezumi slowly
dropped his gaze, and murmured as if in song.

"I am the spirit that denies. Yes, I am all things which you call Sin,
Destruction, or Evil."

"What's that?" Inukashi twitched his nose. "Shion, what the hell is this
deranged actor saying?"

"Mephistopheles."

"Huh? What's that? Is it edible?"

"He appears in the book \emph{Faust}. He's ― a demon."

"So a devil is just reciting a devil's lines. Perfectly fitting."

"No, like I said, Nezumi isn't―"

The man suddenly groaned. His bound body gave a twitch.

"Looks like our guest has awakened from his slumber." Nezumi extracted
his leather gloves, and flapped them nonchalantly. A faint smile played
on his lips.

"Let us begin Act One Scene Two, then, shall we?"

Rikiga looked up at the ceiling, and exhaled. Inukashi gave an
exaggerated shrug of his shoulders. He glanced at Shion.

"Shion," he said.

"Hm?"

"He \emph{is} the devil."

"Huh?"

"He's the devil, and you're the one who doesn't know the real deal. At
least, that's what I think."