% !TeX spellcheck = en_US

\chapter{A Stage of calamity}

\myepigraph{Adorable ladies, just as our pity is commended, so is our cruelty
severely punished by divine justice. And in order to prove this to you,
as well as to give you an incentive for banishing all cruelty from your
hearts, I should like to tell you a story as delightful as it is full of
pathos.}{Boccaccio, \emph{The Decameron}}

\lettrine{H}{e was} walking amidst the blades of grass, in a hot and humid haze. He
could see his own feet. They were very small. The grass grew high, and
reached up to his shoulders.

He realized that he was almost buried in the mass of vigorous grasses
because he was still very young. He looked up to see the cerulean sky,
which was far and high up. The winds were quiet, and it was very hot.~

He was called by his name.

His real name. It had been a long time since he was called by this name.
The air shifted. The breeze swayed the branches above. The scent of
greenery grew stronger.

Who had called him? Who knew his name?

He could hear a song. And the beating of insect wings. A black shadow
crossed his vision. First one, then another, and yet another. Across a
cerulean background, countless insects flew to and fro, making a ring.
As he approached closer, they scattered in all directions, and came back
together in one spot.

A dance.

They were dancing to the song.

\emph{Come here.}

He could hear a gentle voice.

\emph{Let me teach you a song. I will teach you a song that you will need to
keep living. Come here.}

He was called by his name, and beckoned over. It was a voice that
stirred nostalgic feelings. But he could not move.

The beating of wings grew louder. It buzzed incessantly in his ears, and
the air was humming with it. Black shadows danced around fiercely.

\emph{Oh, this scene---}

"Nezumi!"

He was pulled back, strongly, with a definite force. The song, the
beckoning voice, the buzzing of wings, and the smell of lush greenery,
all vanished into thin air.

"Answer me, Nezumi!"

A dim light stung at his eyes. A cold cloth was being pressed to the
nape of his neck. It was very soothing.

"Shion\el "

"Are you awake? Can you see me?"

"Somewhat."

"And you do know where you are?"

"On the bed\el " Nezumi said at length. "Did you carry me here?"

"What's three plus seven?"

"Huh?"

"Addition. If you add three to seven, what do you get?"

"What's this about? Are you quizzing me?"

"Just answer me seriously. What's three plus seven?"

"Ten\el " Nezumi answered apprehensively.

"Yes. Correct. Next---what's three times seven?"

"Shion, listen---"

"Three multiplied by seven. Answer me."

"Twenty one."

"Correct. Okay then, what did you eat for dinner today?"

"Gee, I wonder if that even constitutes as a dinner? I had two strips of
dried potatoes and a bit of goat's milk. I stole a bag of stale crackers
from Inukashi. Almost got bitten in the process."

"Do you feel dizzy?"

"Not at all."

"Nausea?"

"I feel fine."

"No headache, either?"

"No."

"Can you tell me what---when you fell, can you explain to me how it felt?"

Shion was studying him intently. There was a tense, determined light in
his eyes. It made him think of the surface of a frozen lake.

"A wind\el was blowing," Nezumi began hesitantly.

"A wind?"

"The wind blows, and steals souls away."

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here}

Hadn't the voice sung something like this? Nezumi couldn't remember
clearly. But his throat was dry. So dry, it was painful. A white cup was
handed to him. It was full of clear water. He drained it. Like showers
that quenched a parched land, the water that was offered to him flowed
into his body, and soaked through its every extremity. It was a
deliciousness he could not put into words. He was now able to take a
deep breath, and pose a question.

"Shion, are you worrying about whether I might have brain damage?"

"Well, you fainted so suddenly. I had to take all precautions."

Nezumi put a hand to the base of his neck. With the same hand, he felt
his own chest through his open shirt. There were no abnormalities. At
the least, there were no changes that could be seen by the naked eye.

"It's not the parasite wasp," Shion said as he exhaled. "There's no
change in your hair or your skin. It wasn't them."

"That's too bad. It wouldn't seem so bad to have hair like yours."

"Don't even joke about it," Shion said sharply. "It may have only been
for a few minutes, but you were unconscious. It's not something you can
laugh off."

"It was just a fainting spell."

"A fainting spell? You're saying you just \emph{fainted}?"

"You have a problem with that?"

"Nezumi." Shion sat down on the bed, and exhaled again.

"Don't overestimate yourself."

"What?"

"Don't overestimate yourself. You're a human being. There'll be times
where you fall ill, or get hurt. Don't forget that. I'm no doctor, and I
don't have medical knowledge either---but even I could tell that the way
you collapsed just now wasn't from a simple fainting spell."

"Thanks for worrying about me. Maybe I should go to the hospital
tomorrow and get myself checked out more carefully. If I end up having
to be charged at the hospital, I'll make sure to get the VIP room on the
top floor, so make sure to come visit me."

"Nezumi, I wasn't kidding when I said---"

"Shut up!"

He was yelling, but he couldn't tell why. His temper wasn't out of
control, nor did he hate the person in front of him. But he couldn't
help the harshness in his tone.

He did not want someone to be so earnestly concerned about his
well-being like this. He did not want anyone to be seriously worried. He
did not want to be cared about. Feelings like concern, worry, and care
fell all too easily into the frame of "love". He didn't feel like he
needed anything like that. He could live without it. He always had. It
was unnecessary.

But Shion didn't know that. Here he was, burdened with all sorts of
useless baggage. Maybe it was Shion's ignorance and stubborn
truthfulness that irritated him.

"No numbness in your fingertips, right?" Shion continued, "Doesn't look
like there's any swelling, either\el " His fingers took ahold of Nezumi's
hand, which was flung out on the sheets. Shion's fingertips felt along
his hand, and pressed down lightly at intervals. He was still calmly and
intently searching for the presence of any numbness or edema. It was
like Nezumi's yelling hadn't affected him at all.

So not only was he oblivious and stubborn---he was dense, to top it off.

Nezumi brushed Shion's fingers away, and jumped down from the bed.

"Nezumi, you shouldn't be getting up so suddenly---"

"I'll teach you."

"Huh?"

"I'll teach you a dance."

"What're talking about? You should be getting some quiet rest---"

"Over here, come on." Nezumi grabbed Shion's arm, and forced him to
stand. He slid his hand around his waist.

"See, I knew it," he said.

"What?"

"I'm taller than you."

"Liar," Shion retorted. "There's barely any difference."

Nezumi chuckled.

"So, honourable Prince. Have you any experience with dancing?"

"No."

"I figured as much. Then first, we'll begin with the basic steps. Come
on---back straight, chin up. Don't look down."

"Aw, come on, stop it," Shion protested. "We can't dance in here.
Besides, it's too dangerous. If we move around in a small space like
this, we'd knock all the books over."

"There'll be none of that kind of clumsiness. Alright, turn here. Step
back. Once more, and turn. See, you can do it," Nezumi encouraged.

"You're just pulling me along."

"You're still doing pretty well. Your movements are light. Step out and
turn. Good, you're staying on the beat. And repeat the first steps
again. Keep dancing---dance, Shion."

Shion opened his mouth to say something, then shut it again and lent his
body fully to Nezumi's movements. He tilted an ear to the lighthearted
melody that spilled from Nezumi's lips, and traced his steps. The flame
from the heater cast a shadow of two figures. The little mice huddled
together, and looked down at them from atop their lofty perch on a pile
of books.

"Whoa---!" Shion tripped on his feet, and fell backwards on top of the
bed. His breaths came out in pants, and his forehead was damp with
perspiration.

"That was a workout. It takes your whole body to dance, doesn't it,
huh."

"You didn't know?"

"I didn't. Guess I'm that much smarter now. So?"

"Hm?"

"I'm all out of breath, but you're not tired at all. Is that the point
you wanted to make?"

"You could say that."

"You have far more energy, athletic skill, and resilience than me.
You're not the one I should be worrying about---that's what you're saying,
right?"

"I wouldn't be \emph{that} blatant, but---"

Shion stood up. He stood in front of Nezumi, and reached out. It was a
brief gesture, lasting only for a split second.

\emph{Huh?}

Nezumi was being held at the base of his neck. Not even held---Shion's
fingers were merely resting on it. But a violent chill ran through him.
It was a piercing shiver like what a beast felt when it had fallen into
a trap.

"I thought \emph{it}\el was going to come out of here," Shion whispered
hoarsely, as if his voice were caught in his throat. "When you
collapsed, that's what I thought. I---I thought you were going to die.
Nezumi, it's not for you."

"Huh?"

"I'm not worrying about you for your sake. I'm only concerned about you
for my own sake---to be free of my own fears." Shion's fingers drew away.
Nezumi realized he had been holding his breath the whole time.

"Nezumi, there are still a lot of things out there that I don't know.
But I do know," he hesitated. "---How terrifying it would be for me to
lose you. I'm probably more afraid to lose you than anyone---anybody else.
I'm so scared, it's unbearable. I want to make sure you'll never
disappear from my side. I don't care if you ridicule me, or sneer at
me---these are my real feelings."

It was none other than a straightforward and simple confession of love.

\emph{I can't live without another---without you.}

How direct, how blatant, how foolish of a confession it was. Shion was,
at this moment, committing the enormous mistake of revealing his
foolishness, feminine weakness, his fragility. But Nezumi found himself
unable to ridicule or sneer at him. It wasn't because he had been
overwhelmed by Shion's sincerity, nor was it because his heart had been
moved by Shion's heartfelt confession.

\emph{Who\el is he\el ?}

"Good night." Shion cast his eyes down, and slipped past Nezumi.

"I'll sleep on the floor. Just get some good rest tonight, alright?
You've sweated a lot. You're probably more drained than you think you
are."

"Yeah---" Nezumi was barely able to choke out an answer. Once Shion's back
had retreated into the shadows of the books, he clutched at his throat,
his shoulders rising and falling as he breathed raggedly.

\emph{I couldn't avoid it.}

He wasn't able to avoid Shion's hand. The neck was one of the most fatal
points for a human. Even a small wound or impact could cost him his
life. But he wasn't able to brush away the hand that reached out to grab
it. Shion had no murderous intent. But Nezumi hadn't let his guard down
either, and he hadn't meant to comply to Shion's fingers as they reached
out to touch him.

\emph{I couldn't avoid it. I, out of all people, let myself get caught.}

He couldn't predict, avoid, or reject Shion's gesture. He had been
captured completely. If Shion had been an enemy, if he had had the
intent to kill, if he had been holding a knife---Nezumi would most
certainly have been killed. Without even a cry, unable to scream, he
would have fallen lifeless to the floor. He would have been killed.

\emph{I'm going to get killed.}

Among the feelings that stirred inside him when Shion's fingers had held
his neck, not a single one of them had any hint of love or yearning. It
was fear. He was terrified. Nezumi had been through numerous dangers
before. He couldn't count how many times he had been cornered and almost
given up. But he had never stood before someone who made him cower like
this, stiff and unable to move.

\emph{Those eyes, those movements, that oppressive feeling.}

\emph{What was that?}

He gritted his teeth.

He could hear the little mice skittering across the floor.

"Cravat, Tsukiyo, quiet down. Come on over here."

Shion was calling the mice. Once the shuffling of blankets and the soft
squeaking of the mice quieted down, there ceased to be any sound or
movement beyond the stack of books. Silence surrounded them.

\emph{I can't live without another---without you.}

His cloyingly sweet but sincere confession, along with the movements
that had trapped Nezumi completely---they lasted for only an instant, but
in that time, all emotion had vanished from Shion's eyes. Those were not
the eyes of one who was baring one's soul in a confession of love. They
were the eyes of one who had delivered an accurate and fatal stab, and
was twisting the knife in the wound. Shion himself was probably not
aware.

\emph{Am I the one who hasn't known anything all along?}

Shion was a sheltered boy with a stellar intellect and gentle heart. He
had never known to hate, to rebel, or to fight. He could embrace people,
but not hurt them. He could protect people, but not attack them. He was
one who had nothing to do with brutality or cold ruthlessness. He was
one who could only ever become the sun. Wasn't that what he was supposed
to be? If he wasn't, then---

He had no idea of Shion's true nature.

Nezumi had saved his life, had his own life saved, and they had lived
and spent their days together. They were connected more closely, more
intimately to each other than anyone else. He had been avoidant and
apprehensive towards this relationship, but nevertheless he could never
completely sever it; somewhere in his heart he had desired it, and
perhaps he had made it into a kind of haven for himself.

\emph{I'm more afraid to lose you than anyone else.}

Shion's words were also his own feelings. He didn't like admitting it,
but it was the truth, and he had no other choice. But still, even so,
for the first time since they had met, he was losing sight of who Shion
was.

Nezumi ground his teeth once more. They made a thick, heavy noise like
the sound of rusty cogwheels turning. The sound resonated deep within
his body.

It wasn't that he had lost sight---he had probably never seen him properly
from the beginning. He had only looked at the brighter parts of Shion,
illuminated by the spotlight. Until now, Nezumi had always looked at the
root of the plant instead of the flowers that bloomed above-ground,
focusing always on the parts that were sunken in darkness rather than
exposed to light---and he was confident that he had the ability to render
them clearly.

But he had been blinded.

He had been too blinded by Shion's carefree smile, his defenselessness,
and his earnest gaze, to be able to see anything else.

He had not lost sight---he had never seen him from the beginning.

Nezumi began to get goosebumps.

\emph{Shion, exactly what are you?}

In his heart, he questioned the boy who was lying curled up in a blanket
with the mice.

\emph{What are you?}

\myspace

The news came one day, out of the blue.

The sky was already cloudy in the morning, forecasting snow later on.
The ground was frozen over, and showed no signs of melting even after
noon. Snow came in scattered flurries, and a chilly wind whistled
through the West Block bazaar.

It was on that kind of day.

An old dog passed away at Inukashi's place.

"He was siblings with my Mum," Inukashi mumbled as he dug a hole in the
frozen earth.

"Then he would be your uncle?"

"I guess so. Now that's one dog less who I can share memories of my Mum
with."

"He was---quite old, though, right?" Shion said quietly.

"Yeah. Probably close to a hundred in human years. So he probably didn't
suffer much. Yesterday he was still going around licking the puppies.
But when I woke up this morning, he was already cold. No one noticed.
The puppies that were sleeping with him freaked out because he was so
cold, and they came whining to let me know. He lived a full life."

"He must've lived admirably."

"He lived admirably," Inukashi repeated.

The ground was frozen solid, and they were not making much progress with
the pitiful hand-shovels and scraps of wood they were digging with.

"Nezumi," Shion called as he looked up to where Nezumi was sitting on a
portion of a crumbling wall. "Help us out if you've got nothing else to
do."

"Me? Why do I have to dig a dog's grave? Ridiculous."

Inukashi sniffed.

"Shion, leave him alone. I don't want him touching my dog's grave."

"But we have to get him to sing a song."

"A funeral song, huh."

"Yeah, to send his spirit off," Shion said. "You'll do it, right,
Nezumi?"

"Dirges are expensive, just to let you know. Three silver coins."

Inukashi flung his spade aside, and bared his teeth, growling.

"Get the fuck down here. You greedy, fraudulent bastard. I'll rip your
throat apart."

"With your teeth, the best you could manage would probably be a piece of
mouldy bread," Nezumi replied. "Oh yeah, speaking of which, weren't
there some crackers left in your cabinet? Maybe I'll have those for
lunch."

"Hey, you must be fucking kidding me," Inukashi snarled. "You better not
lay a single finger on those crackers, Nezumi!"

Inukashi bounded over the ruins after him. Nezumi was nowhere in sight.

"Hey, wait a minute, you two!" Shion called after them. "Nezumi, didn't
you tell me not to get out of your sight? Inukashi, are you just gonna
leave your uncle here?"

There was no answer from either of them. In the end, Shion ended up
digging the rest of the hole by himself, into which he laid the aged dog
to rest.

\myspace

By the time Inukashi burst into the room out of breath, Nezumi was
already sitting on the table, dangling the bag of crackers in his hand.

"Give it back." Inukashi mustered the most intimidating glare he could.
He didn't think it would be effective, but the bag of crackers was
tossed back to him promptly. He was caught a little off-guard.

"What? Aren't you hungry?"

"What, would you treat me if I said I was?"

"Stop kidding yourself," Inukashi snapped. "I might have food for my
dogs, but I don't have a single cracker to give you."

Inukashi put the bag back in the cabinet. It was old and rickety, but he
still kept it locked. However, he could see the lock had been
effortlessly picked.

\emph{Geez, I can't even relax or let my guard down around this guy. Not that
I would ever, anyway.}

Inukashi relocked the cabinet, and turned around. Nezumi was still
sitting in the same position. Inukashi bent to pick a pebble off the
floor. This room was relatively durable as opposed to the rest of the
hotel, which had mostly crumbled away into ruin. The wall and the floor
were still intact. It not only blocked out the wind and rain, as a
living space it fell into one of the best that the West Block had to
offer. But even this room was beginning to show signs of dilapidation.
The pebbles that had evidently been set into the walls as decoration
were beginning to fall out.

If he squinted at the pebble in his hand, he could almost make out the
blue paint on it. He clenched it lightly in his palm.

"Nezumi."

As Nezumi turned to look at him, Inukashi hurled the pebble straight at
his face. Nezumi tilted his head just slightly to dodge it, and furrowed
his brow.

"Nezumi." Inukashi called him again. This time, he didn't throw
anything. "What's wrong, hey?"

"What do you mean, 'what's wrong'?"

"You got troubles or something?"

"Troubles?"

"I'm asking you if there's something on your mind."~

"Huh?"

The two boys looked at each other, and snorted nearly at the same time.
Then, they fell silent. Nezumi was the first to open his mouth.

"I don't think I've ever had something on my mind in my life. Ever."

"I'da figured."

"Same for you, isn't it?"

"Me? I've always got something on my mind. Food for my dogs, tomorrow's
wages. The worrying never ends. I've got my dogs to take care of. They
can be a great help, but a burden too. I can't let them starve to death.
It's not as worry-free for me as it is for you."

"Worry-free, huh." Nezumi paused. "Hey, Inukashi."

"What?"

"The Hunt is coming. I think it's gonna come in a day or two."

"You mean you \emph{feel} it coming, right?"

"Yeah, I feel it. I'm wondering if I should tell them."

"Who?"

"The other West Block residents."

Inukashi blinked, and fixed Nezumi's profile with a stare.

"You mean tell them to run away because the Hunt is coming?"

"Yeah."

"Where would they run?"

Nezumi didn't answer. His eyes were cast down, his gaze fixed on the tip
of his boot. At a glance, it looked like his mind was racing with
thoughts; then again, it also looked like he was hesitating to give an
answer.

"If the nice folks over in No. 6 are gonna put up a bulletin saying 'We
will begin the Hunt at so-and-so day from this time until that time',
you go on ahead and tell everybody," Inukashi said. "If that's the only
time the Hunt is gonna occur, they can run. But you don't know, do ya?
You say you think it's in a day or two, but that's just your hunch. It
can happen in five minutes. It can happen in a week. If a tip as
unreliable as that was enough to make people run away, they wouldn't be
living here in the first place. They have nowhere to run. They have
nowhere else they can live. That's why everyone's hanging onto this
place like their life depended on it."

While he spoke, Inukashi thought to himself that Nezumi should know this
already down to the marrow of his bones.

On this earth, there were a precious few places that satisfied all the
conditions for human life. There were probably no other places left,
apart from the six city-states. Although Inukashi didn't know this, No.
6 was situated in a considerably more favourable environment compared to
the other five cities. People gathered here in order to live. Leaving
this place was synonymous to death. The people sensed this, not from
learned knowledge or information, but from instinct.

They could not escape it. They had no place to escape to. The Hunt
occurred once every few years. \emph{If we're lucky, we'll be spared. So let's
stay here.} That was the only way.

Whether it was out of resignation or for survival, in the end, everyone
remained on this land. This was the only place they could live. And that
was why it was hell.

"I shouldn't even have to say this," Inukashi gave an exaggerated huff.
\emph{You're right}, Nezumi muttered.

\emph{What the hell has gotten into him?}

\emph{Is he scared about what's gonna happen?}

\emph{Nezumi? Afraid?}

Inukashi found himself vigorously shaking his head from side to side.
His long hair flopped as it bounced against his back.

\emph{Impossible.} Inukashi didn't see Nezumi in a favourable light. On the
contrary, he saw him as a danger to deal with. Nezumi never revealed the
most important part of his thoughts, and he could be extremely callous
at times. Every time Inukashi saw the impressive skill with which he
wielded his knife, he wondered if Nezumi had perhaps sent several people
to the grave like this.

Inukashi didn't want to deal with him if he could help it---that was his
honest opinion. But even so, he knew that Nezumi was someone who was
neither underhanded nor deceitful; and although he was extremely
cautious, he was not a coward. Inukashi knew that much.

\emph{He's decided to sneak into the Correctional Facility. If he's decided
it, he'll do it. And now that he's made his decision, he shouldn't have
anything to fear or be intimidated by.}

Perhaps Nezumi had noticed Inukashi's apprehensive stare. He shrugged
his shoulders nonchalantly in response.

"You're right. You shouldn't even have to say this. It's just---"

"Just what?"

"Shion hasn't mentioned it."

"Mentioned what? About letting everyone know so they can escape?"

"Yeah."

"Well, it sure sounds like something the airhead would say---but I mean,
Shion doesn't know much about the Hunt, does he?"

"He's catching on."

Nezumi got down from the table, and picked up a pebble that was lying
near the wall.

"He's slow to get the hint sometimes, but he's not stupid. He's probably
realized exactly what kind of hunt the Hunt is. Though it probably
hasn't sunk in for him yet."

"Uh-huh," said Inukashi dubiously. "Well, then, that means he's gotten
smarter. Maybe he finally gets the picture about what the West Block is
actually like."

"Probably."

Nezumi was twirling the pebble in his fingers. The question was out of
Inukashi's mouth before he knew it.

"What's nagging at you?"

A shadowy veil fell over the pair of beautiful dark-grey eyes. There was
a tremulous flicker. Inukashi remembered seeing the same kind of shadow
and flicker. Many, many times. It was what you saw in the eyes of a
dying child. They were eyes wide open and staring, filled with
suffering, agitation, and fear, unable to understand why it hurt so
much, and what was going to happen next. They were not the same, but
they were very similar.

"You scared of something?" Another question spilled from his lips.

\emph{So you really are scared of something? It's not about the Correctional
Facility or the Hunt. Those might pose a danger to Nezumi's life, but
wouldn't instill fear in him. Then what---}

\emph{Shion?}

Inukashi scowled, and sneezed softly.

"What did you say I was scared of?" Nezumi said.

"No---" Inukashi said nonchalantly.

He didn't quite know what kind of relationship Shion and Nezumi had or
what kind of connection they shared, nor did he ever wish to know. He
didn't care. But he was sure that Shion would never become Nezumi's
enemy. That was one thing that would never happen. Besides, what kind of
damage would there be if a single airheaded, oblivious boy turned
against them?

Inukashi sucked in a breath.

\emph{Oh well, it doesn't matter. Whatever it is, I don't wanna get more
involved with these two than I already am.} He shooed Nezumi away with
his hand.

"Go home."

"Some greeting."

"I wouldn't even give you one, if I could help it. ---Nezumi?"

Nezumi was covering his face with his hands. He staggered, and leaned
heavily against the wall. He slid down with his back against the wall
until he was squatting on the floor. He propped his knees up, and bowed
his head.

"Nezumi, what's wrong?"

There was no answer.

"Hey, Nezumi. Stop fooling around. You practicing for your play or
something? I'm not gonna give you any acting tips, just saying."

"Singing---"

"Huh?"

"I hear singing---again---" Nezumi's voice was trembling as he trailed off,
and Inukashi could hear his laboured breathing. It turned into a faint
murmur.

\emph{The wind\el steals the soul away\el humans thieve\el the heart.}

"Nezumi, what're you saying? Get a grip on yourself."

\emph{So he has some disease.}

Inukashi crouched down, and laid a hand on Nezumi's shoulder.

"You hang in there. I'm gonna get Shion."

He was grabbed by the wrist. It was such a powerful grip, Inukashi
almost cried out in pain. Nezumi put his other hand to his forehead, and
slowly stood up. He exhaled slowly.

"Hey, Nezumi."

"I'm fine."

"You don't look fine at---whatever," he cut off abruptly. "None of my
business what happens to you, anyway."

"Right back at ya."

Nezumi released Inukashi's hand, and took a few steps. His feet were
steady.

"Oh yeah." Nezumi turned back at the door, and fluttered his fingers.
In-between them was a silver coin.

"Wha---hey, don't tell me you---"

"And I'm telling you I did. Hidden compartment in the back of your
cabinet, huh? Pretty nifty gimmicks you've got in this room, Inukashi."

"W-Wait. You---you opened it?"

"Of course. One silver coin. I'm taking it to pay for Shion's day of
work. And the bag of crackers, too."

"The crackers too!?" Inukashi howled. "You must be fucking kidding me."

"They're not stale or mouldy. Superb bag of crackers. I'll have a
splendid afternoon tea with these. Thanks."

Inukashi lunged at Nezumi, only to have the door shut firmly in his
face.

\myspace

He had buried an aged and emaciated dog.

Shion threw dirt over the grave, and placed upon it a rock which
Inukashi had chosen from the rubble as a makeshift tombstone. He brought
his palms together in prayer. Several puppies sat at Shion's side, and
wagged their tails at the newly-made grave.

He felt a presence behind him. Since he had not heard any footsteps
approaching, he knew who was standing there without having to turn
around.

"What're you doing?" Nezumi asked.

"I'm giving my condolences."

"You're praying for a dog."

"He lived a full life on this land. I think it's admirable."

Nezumi kicked at the pebbles with the tip of his boot, and nodded.

"Yeah, I guess you're right. It's almost like a miracle for him to be
able to die of old age here. He was able to die a peaceful death in a
world that doesn't give it to those who deserve it. Yeah. It's worthy of
admiration."

"Will you pray for him too?"

"No thanks. If you're done, let's go home already. You're finished your
work for today, aren't you?"

"Did you nick those crackers from Inukashi?"

Nezumi lifted a finger at him and wagged it disapprovingly.

"Tut, tut. A royal prince like yourself shouldn't be using such crude
words like 'nick'."

"You nicked them, didn't you."

"It's for the work you've done. Compensation for your grave-digging. And
this, too." A silver coin appeared between Nezumi's fingertips.

"A silver coin and a bag of crackers. Don't you think that's ripping him
off just a little?"

"It's fine. I hooked him up with a job worth two gold coins. Think of
the silver as commission. Alright, let's get some dried meat at the
market and then head home."

Shion walked shoulder-to-shoulder with Nezumi. The puppies followed him
around at his feet, and saw the two of them off at the outskirts of the
ruins.

"Where's Inukashi? I don't see him anywhere."

"He's crying."

"Did you make him cry?"

"He cries at anything. He talks like he's tough, but he's a crybaby.
He's probably bawling his eyes out right now because he can't believe he
let himself get nicked of his silver and crackers."

"That's horrible," Shion said worriedly. "Hey, Nezumi."

"Hm?"

"About Inukashi\el uh---by any chance, is he---"

"What about him?"

"Uh---no, never mind. Sorry."

They climbed a set of crumbling stone steps, and headed to the
marketplace lined with barracks. The wind was blowing at them head-on.
It seemed to steal away every little bit of their body heat. \emph{I wonder
what Safu's doing now. I hope she's not freezing in the cold. I hope
she's not going hungry.}

\emph{I love you, Shion. More than anyone else.}

He was not able to return the girl's feelings. He would probably never
be able to. He could not love Safu in the way that she wanted him to.
But he could love her another way.

\emph{Safu, stay alive. And be waiting for me. Please.}

The wind got stronger. He shrank from the cold.

"What're you thinking about?" Nezumi glanced at him, his hair streaming
in the wind.

"About Safu."

"I'd say don't get worked up---but it's probably hard not to. But no
good'll come out of it. Just remember that."

"I know."

"Pull your hat down lower. The Disposers are here. It's gonna be a pain
in the ass if they decide to talk to us."

Before Nezumi finished his sentence, a burly man approached them from
the gang drinking at the barracks.

"Hold on a minute, fellas."

It was, without a doubt, the same man that had run into Shion last time.
Shion remembered the snake tattoo on his arm.

"Hey, if it ain't those cheeky brats from last time. Nice meetin' ya
fellas again, huh? I'll make sure you guys have a good time."

\emph{Tsk.} Nezumi clicked his tongue. At the same time, his right arm moved
lithely. A blue pebble struck the man right between the eyes. The man
cried out as he bent backwards. Shion waded through the crowd of people,
and broke into a run.

"This way." He followed Nezumi, skidded into an alleyway, and squatted
hastily down. The Disposers thundered past them, yelling angrily.

"That's pretty serious," Nezumi commented. "If you get caught next time,
you probably won't get away with just a beating. You better prepare for
it."

"Am I the only one who has to prepare?"

"I'm gonna make a run for it."

"So will I."

Nezumi looked furtively around before crawling out of the alleyway.
Apparently it was an everyday occurrence for men to be bellowing and
running around, for people were walking down the street as if nothing
had happened.

"But you've gotten faster at running away, that's for sure. You've made
some nice progress since last time."

"You trained me. ---Oh, I said this last time too, didn't I?"

Nezumi smiled. It wasn't one of exasperation, scorn, or cold cruelty. It
was a sensual smile. Shion found himself entranced by it.

"Eve!" Someone yelled from further down the alley. "What the hell are
you doing here?"

A small-framed man wearing a white shirt and black pants was standing
there, his face fuming. He was wearing a dark, wide-brimmed hat, and a
scarf of the same colour. Although it wasn't very becoming on him, his
outfit had a flair that one never saw in the West Block.

"Oh---Manager. It's been a while."

"It's been a while, indeed," the man said indignantly. "I've been
looking for you. Why haven't you shown up at the playhouse? We can't get
anything started without you on the stage. What's going on?"

"Ah---well, a lot of issues have come up, and\el I was wondering if I
could take time off from performing for a while."

"Take time off?" said the man incredulously. "Are you insane? Most of
our audience comes to see you. Planning to put my playhouse out of
business, are you?"

The manager then suddenly smoothed his face over with a meek smile, and
his voice took on a wheedling tone.

"Come on, Eve," he said pleadingly. "Let's talk it out, one man to
another. If you've got any complaints, I'm always here to listen."

"Complaints, huh\el that's kind of hard."

"Don't have any? Then---"

"I've got so many, if I were to list them off, it would take me until
tomorrow morning."

"Eve, I'm begging you. If it's about your compensation, we can work
something out. If you can't come in tonight, maybe starting tomorrow---"

There was a noise. It was a sound that would linger in Shion's ears, be
engraved in his memory, and haunt him incessantly in his dreams in the
days to come.

The sound of destruction. The sound of genocide. The sound of death. The
sound of despair. Screaming, yelling, crying, footsteps. Everything
melted together, tripping over each other, tangling with everything
else, writhing, rising in pandemonium. Hell had materialized before
Shion's eyes.

People began to flee frantically in every which way. The barracks began
to collapse, and tents were being torn down.

"It's the Hunt!" someone bellowed.

\myspace

\emph{It's the Hunt.\\
It's the Hunt.\\
It's the Hunt.}

\myspace

Even the howling of the wind was drowned out.

An elderly person tripped and fell. Shion had no chance to help him up.
Countless feet stepped on the fallen as they stormed past.

"It's begun." Nezumi swallowed. He turned around and gave a curt command
to the manager.

"Run!"

There was a deafening explosion above their heads. The air rippled with
it. A numbing impact came slamming into them. A barrack that used to be
a meat shop was blasted to bits.

"Shion!" He felt himself being knocked over. Nezumi's body overlapped
his own. As he was pushed against the ground, Shion choked on his own
breath. He could hear Nezumi's voice at his ear.

"Shion, you alright?"

"Of course."

This was no time to fall unconscious. It had started. Everything was
starting now.

Nezumi drew away. Shion lifted himself up, and gave a small groan. He
saw the sky. A grey expanse of sky spread above him. The whole second
floor of the barrack which had previously been blocking his vision was
blown off and gone. The air was thick with dust.

"What about that man?"

"Who?"

"Your manager, or whoever."

"Oh, he probably got away. If he's lucky, he'll make his escape. If
not---he'll end up like that." Nezumi jerked his chin. There was a bloody
arm protruding from under a collapsed wall. It was thick and hairy.

"Probably the old guy from the meat shop."

\myspace

\emph{It's the Hunt.\\
	Help.\\
	O dear God.\\
	Damnit.\\
	We're gonna get killed.\\
	Run, run, run.\\
	Ahh, ahh, ahh.}

\myspace

Voices clashed together in an unintelligible din. Shion squatted down in
the shadows of the ruined remains of a wall, trying to avoid being
caught up in the moving mass of people. Less than a step away was the
arm of the man from the meat shop.

"Nezumi, is this---"

"Look." Shion's gaze roved to where Nezumi was pointing.

"Oh---" His breath and his voice were stuck in his throat.

Two armoured vehicles were travelling side-by-side down the road, almost
blocking it entirely. They made their way into the marketplace at a
crawling speed. The barracks were no match for them. They were like
paper-craft, crackling as they were crushed beneath the wheels.

"Nezumi, those armoured trucks---"

"Yeah. Old models, by the looks of it. But it looks like their ammo is
still in working shape. They used acoustic shockwaves to blast the
second floor off the meat shop. When did they start putting it to use?"
Nezumi muttered to himself. "Or did they use this place to test it out?"

"That's not what I'm asking. I meant---do those belong to No. 6?"

"Well, they don't belong to me, that's for sure."

The fact that No. 6 had an army was something entirely new to Shion.

Before he was born, the six city-states that dotted the earth had
conferred together to sign a peace treaty that clearly denoted their vow
to abandon their armies and forbid the possession, development and use
of any weapons. From the past they had learned that warfare between the
states only caused environmental destruction and deterioration of the
motherland, endangering the existence of humankind itself. As a means to
escape their own extinction, all cities had signed the treaty and vowed
to honour it.

It was called the Babylon Treaty, after the ancient castle in which the
signing was held.

But Shion was no longer surprised by any of it. If No. 6 was a fictional
utopia, then it was only appropriate for the city to have an army,
soldiers, and weapons in order to oppress, dominate, and erase its
people.

Shion beheld the approaching armoured truck warily, and regulated his
breathing. Nezumi gave a soft chuckle.

"I thought you'd panic a little more. You've toughened up."

"You trained me."

"You were a nice pupil to coach. But game time is just starting."

"Yeah, I know."

The mob of people rippled. The flow was pushed back. The same armoured
truck had appeared in front of them this time, blocking their way. The
screams of the crowd grew louder. People jostled each other, toppling
over like dominoes, and as they screamed and shrieked tearfully, they
became one churning mass herded into the centre of the marketplace. It
was in the area where Shion and Nezumi had taken cover, right in front
of the destroyed meat shop. The meat shop, the tavern across, the
used-clothing store beside it, and the store selling dried goods were
all destroyed. Perhaps they had been blown up purposely to make the
capture easier. Soldiers had appeared with guns in hand to surround the
mob.

\emph{"Quiet down."} A low, booming voice of a man issued forth from the
armoured vehicle.

"Help! Please, just save my baby." A mother with an infant in her arms
was raising her voice in plea to anyone who would listen. No one
answered her.

"Please, he's not even one yet. Don't kill him!" As if sparked by her
agitation, the baby began to wail in her arms.

"Please\el don't kill him\el "

Shion bit down on his lip. His whole body was shaking.

\emph{What should I do. What can I do? What---I can't do anything.}

A whimper.

A voice. It was a dog's voice. As Shion whirled around, his eyes met
with a dog who was poking its head out of the rubble. It was one of
Inukashi's dogs---the one that had delivered Shion his letter. Just the
other day, Shion had given him a caring and thorough wash as his way of
expressing his gratitude. It was a large, dark brown dog. Shion extended
his arms to the mother.

"Give me the baby."

The mother widened her eyes, clutching the crying baby to her breast.

"Hurry, give him to me."

"What will you do with my baby?"

"We might be able to save him. Hurry." He half-wrenched the baby from
the mother's arms. He shed his coat, wrapped the tiny body in it, and
laid him down in a space among the rubble. The dog lay down beside it,
and licked the baby's face. The crying stopped instantly. The dog's
brown fur blended perfectly with the crumbled wall, which was the same
colour. He was unnoticeable.

\emph{Maybe he'll make it. Maybe---}

"I'm counting on you."

The dog swung its tail softly.

"My baby---my son---" The young mother covered her face with her hands.

"If you're able to make it through, go to the hotel ruins," Shion said
to her.

"Hotel?"

"Hotel ruins. The baby will be kept there. Don't worry, he'll be taken
care of. So make sure you make it out. Alive. And please be there to
pick him up."

The mother nodded, and closed her eyes as if in prayer.

"I'll be damned if I die at yer hands!" a burly voice roared. "We ain't
gettin' killed by the likes o' you!"

Along with the voices, several small rocks whizzed at the soldiers. An
agitated buzz ran throughout the crowd. Rocks and pebbles flew one after
another from the mob, aimed at the soldiers.

"Shit," Nezumi grimaced. "Shion, get down!"

"Huh?"

"Hold your head and duck!"

Shion did as he was told, covered his head with both hands, and squatted
down. At almost the same time, the soldiers opened fire with a torrent
of electric bullets. The beams of the electric guns pierced people's
foreheads, chests, and stomachs. Men, women, the elderly, and the young
all fell without even raising a cry. They convulsed, and were still.

\emph{"If you rebel, you shall be killed. There are no exceptions."}

It was a low voice. It was not a threat. Everyone understood. The
clamour in the bazaar, or what used to be, died down at once. People
even stopped moving. They were frozen in fear, and rigid with despair.

Shion stood up cautiously. There was a corpse in front of him. It had a
wound between the eyes, but it wasn't fatal. It was only red and
swollen. The fatal wound was a little bit above it. The person had been
shot straight through the middle of his forehead. It was the Disposer.
His mouth was gaping open, and his lifeless eyes were staring at the
sky. Beside him, an elderly woman was squatting on the ground, chanting
something under her breath. Her vacant gaze roamed aimlessly.

The scene before him lost all colour. Shion was never able to give
colour to this scene that had permanently burned an image in his memory.
Although faded, he knew the people there had clothes and hair of various
colours; he knew that the rubble was not just one shade; he remembered
for certain that the dog had dark brown fur---but the man's corpse on the
ground, the old woman who had gone insane, and the sight of the frozen
mob was only ever in monotone, in black and white. But there was just
one exception, in the dark grey that floated before his eyes. It was not
from the clouds. It was an eye colour. They were dark grey eyes that
glowed brightly and from deep within, brimming with vitality. It was the
colour which Shion had been drawn to, been beheld by, and ultimately had
never been able to forget for the rest of his life.

\emph{"I repeat. If you rebel, you shall be killed. Don't move."}

No one moved. They could not move. Only the wind blew freely.

"Shion." Nezumi grabbed his arm. "Don't lose it."

Shion gazed into Nezumi's eyes, and laid his own fingers over the ones
that grasped his bicep. He wasn't clinging out of desperation. He wasn't
giving in to complete reliance. He only wanted to make sure. \emph{This is
where my heart is. I was human when my heart was stolen by him, and I
was human when I longed to be by his side. And this fact won't change,
no matter what name I give to these feelings.}

In a reality so inhumane, almost too inhumane, the only thing one could
do to remain human was to refuse to abandon one's feelings for others,
and to hold onto one's own human soul. Shion clasped his hand tightly
around Nezumi's.

\emph{Nezumi, I want to stay human.}

Nezumi breathed out softly.

"Keep your sanity. You can do it, right?"

"I'm alright."

"Of course," Nezumi said reflectively. "You would be alright. I
shouldn't have worried."

\emph{"You will now be transported."}

The armoured trucks turned and changed directions. A large, black truck
loomed silently in its place.