% !TeX spellcheck = en_US

\chapter{A name for white darkness}

\myepigraph{My elder brother is a cannibal!\\
	I'm brother to a cannibal.\\
	Even though I'm to be the victim of cannibalism, I'm brother to a
	cannibal all the same!}{Lu Xun, \emph{Diary of a Madman}}

\lettrine{S}{hi-o-n}. She tried calling his name. Since being brought here, how many
times had she called it? No matter how many times she did, her voice
never reached him.~

Safu let out a deep, deep breath. The sound of her own sigh reached her
own ears very vividly. And it wasn't only her sighing: the faint sounds
of her own body as she shifted, her heartbeat, and even the name she'd
called out silently, all echoed back to her vividly with a clear
outline. On the contrary, her eyesight was always vague and closed off,
blankly white. It was like she was in a fog.

\emph{Where am I?} She let her gaze roam about.

It was a white world, like she was seeing through layers and layers of
lace curtains. A world enveloped in fog. When she first awoke, she had
thought for a fleeting instant that she'd wandered into a deep forest.
But she soon realized how different it was. The only thing here was the
white darkness that closed off her vision. There were no birds chirping
in the canopies; no bubbling brook, no swishing of the trees. There was
no fragrance of flowers, nor the smell of dirt. It was odourless,
soundless. Only the sounds of her own body and soul became clearer and
clearer by the day.

\emph{Inside a deep forest\el }

Safu sighed again. She had walked through a forest with Shion once. It
was a forest park in the centre of No. 6, however, so all animals and
plants were minutely scrutinized and managed by human hands. 'I don't
think a place like this should be called a forest,' Shion had said, and
grimaced in clear dislike.

\emph{Oh, I remember. How many years ago was it? I can remember it so clearly.}

Safu smiled. A feeling of happiness coursed through her body. It was
very warm, soft, and comforting. Every time she thought of Shion, every
time she revived the hours she spent with him, she could smile.

\emph{I remember. I was beside him, and I was very happy. Shion, don't you
think memories are amazing? The memories of being with you still bring
me happiness. Yes, it's true. I haven't forgotten a single thing. Your
tone of speech, your gaze, your gestures, your scent\el I haven't
forgotten anything.}

\emph{You told me once, while we were walking through the beech-tree block of
the Forest Park.}

"They call it a forest, but it's a place that's under human control. I
don't feel right calling it a forest. I wish they would at least let us
walk in the natural wood in the North Block. It's hard to get
permission, though."

"But this is your workplace too, isn't it?"

"That's why I can tell how much more it's being managed. I feel like
nature should be more unpredictable--- like something that surpasses human
intelligence. Safu, don't you feel anything wrong with this?"

"Hmm. Well, I don't feel much resistance really," she had pondered
aloud. "It's so beautiful here, after all." Safu let her gaze wander
amidst the numerous branches that framed her above her head. The beech
leaves were beginning to turn yellow. Catching the sunlight streaming
down from the clear autumn sky, they looked almost like they were
glowing.

"Oh, look!" she had said.

"Hm?"

"There was a squirrel. It went running along that branch."

"Beech trees bear fruit during this season, so animals come looking for
food."

"Can you eat the fruit?"

"Yeah. They're nuts, actually. They usually grow in twos or threes,
cased in a cupule."

"What's a cupule?"

"What you find in Mongolian oak fruits, and sawtooth oak\el called, uh,
acorns. What's attached to the bottom is part of it too."

"Oh, I think I know what you're talking about," Safu grinned. Shion
smiled too. His smile, glowing in the sunlight that streamed through the
beech trees, stung at her eyes. It stung in her heart. She had been
smiling then, but she had also been about to burst into tears.

\emph{We were walking alone together. But what did you talk about? Nuts?
Cupules? Can't you be a little more tactful with your conversation? Did
it ever occur to you to not say anything, and just snuggle up together,
and feel each other's breathing and warmth? Shion, didn't you want to
hold me? Didn't you want to love me?}

\emph{I suppose you didn't. You looked like you enjoyed being with me, though.
You laughed a lot, and you were more talkative than usual. Oh, yes yes.
It was only once, but you even said so out loud.}

"It's fun being with you, Safu."

\emph{I don't think you were lying. You're the kind of person who could never
lie.}

\emph{Shion, do you enjoy being with me?}

Yeah. A lot.

\emph{Wouldn't it be nice if we could be together forever?}

Sure we could. Safu, you're my most important---

\emph{You cared for me. You cherished me. But you didn't love me. You didn't
feel the kind of desire for me that burned your body with yearning.}

Safu, you're my most important friend.

\emph{You cruel person. So cruel, it's almost unbelievable. I don't think
anyone could be as gentle, innocent, and cruel as you.}

\emph{Shion, who are you in love with? Who do you burn with desire for?}

\emph{Knowing you, you would probably love her singly, devotedly, and
earnestly to the point of being absurd. You two would share both life
and death, but go walking towards life instead of death.}

\emph{Shion, who do you love? Who do you desire? Why can't it be me?}

The white curtains fluttered. A dark, hazy shadow appeared.

\emph{It's that man again.}

\emph{The man that smells like blood.}

"Hello, Safu." It looked like the man was raising his hand. "How do you
feel?" Even his voice was dripping with blood. She didn't want to
converse with him. She didn't want to speak. She didn't want him to come
closer.

"It looks like you can hear me just fine. But oh dear, what is this
response? Do you not like me, Safu?" The man chuckled. It was a muffled
and dark voice. Only his voice was laughing. His heart was not. "There's
nothing more sorrowful than being hated by you. I see, so you dislike my
voice? Goodness, what a horrible response."

"I can't\el see\el "

"Oh! Is that an audio response? So you feel like talking to me now,
Safu? I'm delighted to be able to have a conversation with you. Nothing
could delight me more. Come on, give it another try."

"I can't\el see. Just\el white."

"You can't see? Oh, yes, you probably wouldn't be able to. You haven't
completely recovered yet. Visual functions are the slowest to recover.
Almost---you're almost there, Safu. In a little bit, those hazy things
will become clear. Then you'll finally be able to look at yourself." The
man laughed again. This time, it was from his heart. A high-pitched,
somewhat vulgar laughter. It was chilling. Safu felt a foreboding
shiver.

"Ah, have I made you feel unpleasant again? Hm? These waves---Safu, is it
fear you're feeling rather than dislike?" The man drew nearer. His
fingers touched her.

"Stop\el go\el away\el "

"Safu, there is nothing to be afraid about. I don't intend to hurt you
at all. You're beautiful. If I said you're the most beautiful person I
know, it wouldn't be an overstatement. See, that's why I want to make
you happy."

"Ha\el ppy\el "

"Yes. Happy. You won't feel any suffering or sadness, and you'll never
contract a disease or have to groan in pain. You'll never age---no, in
fact, death will not even exist. I want to give you that kind of
happiness."

The man grew even more eloquent. The words streamed from his mouth as if
he were possessed.

"Safu, you're beautiful," he said. "I'll confess this truthfully. I
can't lie to beautiful people. Please don't be angry. At first, I only
wanted an elite sample. That was why I had you come here. It didn't
matter, as long as it was an elite. Oh, but a female one. Yes, a
female\el I needed a sample of a woman. But you were so beautiful, my
heart was stolen. I couldn't treat you in the same way I did all the
other samples. That's why you're right here, where I can reach you. See,
Safu, soon you'll stop fearing me, and begin to feel grateful towards
me."

"No\el no\el you're\el scary\el "

"Such an intelligent and beautiful person like you shouldn't whine like
an obstinate child. Say, weren't you a student specializing in cognitive
functions? I had the opportunity to read through the thesis you
submitted for your application for exchange students. It was about the
cortical column---on the functions of the finer structures within the
cerebral cortex, am I right? 'The Cortical Column as Functional Module:
The Mechanisms of Composite Information Processing' it was called. It
was quite interesting, though the development was rather awkward. But as
a student thesis, it was top-notch."

Another layer of white curtain was swept aside. The man turned from a
dark, shadowy figure to a human-shaped one.

"Oh? It looks like your eyesight is on the road to recovery as well. I'm
getting good numbers. Not only are you beautiful and intelligent, you're
also healthy. Supremely ideal. I'm very fortunate to have met someone as
ideal as you."

\emph{My eyesight is coming back? I can escape from this white world?}

No happiness welled up in Safu's heart. She felt no sense of freedom. On
the contrary, she was terrified. She was afraid of when all the curtains
had been drawn aside, when the fog cleared, what she would see, what she
would have to see.

\emph{Shion, I want to see you. I want to look at you. I want to hear your
voice. You are the only one I seek.}

\emph{Shion.}

---Safu.

She had heard him. She had heard his beloved voice calling her name.

"Hm? Hey, Safu. What's the matter? What is this response? Where did you
receive this stimulus?"

\emph{Shion.}

---Safu. Wait for me.

\emph{Shion.}

---I'll get there. I'll save you.

\emph{Shion\el }

\emph{Shion is nearby. He's close to me.}

A joyful thrill pierced through Safu's body. Hope was born. Hope was
strength. It was a searing energy that came alive, and coursed through
her whole body.

\emph{Shion, you are my hope. I'm waiting for you. I'll wait for you to come
to me.}

\emph{Shion.}

\mybreak

He was grasping a handful of hair. It was long and durable. He couldn't
tell what colour it was. He clutched at it like a lifeline, and climbed.
He was climbing a mountain of people piled and folded on top of each
other. He was going up, up, wedging his feet in, stepping on people's
heads, buttocks, shoulders, and legs to move forward.

Some raised a groan the moment Shion's foot pressed down on them. He
almost screamed. But it only stuck in his throat, and quivered there. A
corner of his head ached dully, and the muscles of his back were tense
and stiff as a board. Sweat glided down his back and chest. It drenched
his whole body.

He had been prepared for it.

From the moment he decided to infiltrate the Correctional Facility, he
had prepared himself. He had thought he did. But that resolve had been
blown into smithereens. It had shattered, leaving no trace. After
experiencing this hell, could he still say with certainty that he wanted
to go into the Correctional Facility? He asked himself over and over
inside his head, which only pounded with a dull pain.

\emph{So what'll you do, Shion?}

I'll do it, of course.

But he couldn't say it with certainty. He couldn't even reassure
himself.

What a fragile decision it was. What a half-hearted decision it had
been.

He lifted his face, and gazed at Nezumi's figure. The gap between them
seemed to be as wide as Heaven and Earth: Nezumi, who knew this hell and
yet was still here; and he, who was gasping from the difficulty of his
half-hearted and ignorant declaration. They were all too different.

It was no wonder if he was called a naive little boy, or scorned for it.
It was true.

His foot slipped. As he lunged and reached forward, he felt something
soft and malleable at his fingertips. He had grabbed someone's face, who
was lying sideways. His index finger dug into the person's nostril. The
pain in Shion's head grew worse. He felt dizzy. The strength was leaving
his hands and legs. \emph{Ah, I can't---}

"Shion!" He was grabbed by the wrist, and pulled up. "We're here."

"Here?"

"At the summit. Well, but that's only about half of the whole journey.
But for the time being, congratulations on a job well done."

\emph{The summit of a mountain of people, huh.}

"It's too bad we haven't brought lunch with us. Wanna take a break
anyway?"

"A break\el here?"

"If you know any other resting area, then there."

A tumult of groans rose up from below. They were, quite literally,
rising up from where he was standing.

"There are\el still people alive\el " Shion said falteringly.

"Probably quite a few. The ones who fell first probably didn't make it.
The ones that fell second, third, might've gotten away with broken
bones. If they're lucky. See, Shion, we were lucky to be in the second
group. If we were the first, we would've been smashed directly against
the floor."

Shion remembered what he felt at the moment of the fall. The sensation
of falling on top of human bodies. He had used the people in the first
group as a cushion, those unlucky people who had been smashed to the
floor, to lessen the impact of his own fall.

\emph{Can I even call that fortunate?}

"You okay?" Nezumi said. "If you're nauseous, it'll feel better if you
get it all out."

"Nezumi\el "

"Hm?"

"I'm sorry."

"Huh? Why're you apologizing?"

Shion covered his face with his hands. The stench of sweat and blood,
the groans of the dying people, enwrapped him whole. They dug into his
flesh, and corroded his bones.

\emph{This is all I can take. I can't bear any more.}

"I\el can't do it." He could only make it this far. This was the best he
could do. He couldn't move a single step more. If Nezumi hadn't grabbed
his wrist back there, he would have tumbled back down the slope. He
couldn't do anything alone.

"I'll\el only ever become a hindrance to you."

"What're you bringing up old news for? You've always been a hindrance.
You've never been anything more than that."

"Nezumi\el leave me here."

"You're staying alone?"

He nodded.

"You'll die, Shion."

"I know," he whispered.

"You won't die painlessly," Nezumi said. "I don't know how many days
you'll be like this for. It might be the dead of winter, but if these
corpses are left out, they'll start to rot. You'll either go insane in
the stench of decay, or you'll faint again and again from oxygen
deficiency, and weaken that way, or\el "

"Or\el die on my own."

"Shion, don't take death lightly. If you underestimate it, it'll come
back to bite you in the ass. Do you have some instantly effective poison
on you, huh? How're you gonna kill yourself here, without a knife to
slash your throat, without a rope to hang yourself? You can try biting
your tongue, or jumping off of here, but you won't die easily."

"You've---got a knife," Shion said hoarsely.

Nezumi's shoulder twitched.

"So that's what you meant."

Shion was grabbed roughly by his hair. His head was flung back, and a
knife was brought to his bared throat. He felt like the sharp blade
would slice through his skin just from taking a deep breath.

"Are you asking me to kill you?" Nezumi hissed.

Shion inhaled silently. What would happen if he got his throat slit
right here, by Nezumi's hand? Would his blood spurt forth, and colour
Nezumi crimson?

"Shion." Nezumi's voice shook. "Are you trying to make me kill you?"

"Huh?"

"Don't 'huh' me. I'm asking you if you're trying to make me kill more
people than I already have."

"Never---" Shion shook his head. Nezumi's fingers withdrew. "I would never
want that. I'd hate for you to."

A long sigh. The aged female dog at Inukashi's used to sigh in a very
similar way.

\emph{My goodness. What are we ever going to do with you, child?}

"Look, think about it," Nezumi said tersely. "If I slash your throat,
that's murder. If I give you the knife, I'm assisting your suicide.
Either way, I'll have to take the blame for your death. Are you ordering
me to take the brunt of it? And besides---"

Shion was grabbed by the hair, harder this time.

"Then what would you have memorized the layout of the Correctional
Facility for? We're just starting to need your brain the most. I'm not
gonna let you forfeit the match now. I won't allow it."

His hair was yanked mercilessly. The pain threw needles into his
delirious consciousness.

"Without you, it'll be nearly impossible to escape from here. If you
wanna die, I won't stop you. But do it after we get outta here. You
understand what I'm saying, right?"

"Pretty well."

"Then listen. It's just starting. Got it, Shion? I need you."

"Yeah."

Shion willed his legs to stand. He could do it, but barely.

"Good boy."

"Yeah."

"Let's get going, then."

"Okay." Shion had no idea where they were going next, whether they were
going to climb or descend. He didn't think of asking. He had no energy.
He could only muster all the strength he could, and follow Nezumi. If he
could be a necessary existence for him, then it was more attractive than
dying in one stroke. To feel like this meant he still had the will to
live. He still had\el the will. So his soul hadn't completely withered
away after all.

Nezumi whistled shortly. A clear, high note resounded in the darkness.
After the sound died away, a silence fell. Even the dying people's
groans were cut off.

\emph{Chit.}

"Huh?"

\emph{Cheep-cheep.}

A pair of small glowing dots appeared in the darkness. It was a colour
Shion remembered.

"Hamlet?" It was the colour of the little mouse's eyes. They were the
red stars at Shion's pillow as he got ready to go to bed; they were on
top of the lofty pile of books; under his bed, always twinkling.

"It's not Cravat or Tsukiyo, is it\el ?"

"I told you not to give funny names to my mice," Nezumi said in
annoyance. "And besides, what the hell would they be doing here?"

"You're right."

"But you're right about the mice part. It's a nameless mouse." Nezumi
whistled again. This time, it was a melody. The red lights disappeared
for a moment, and when Shion blinked again, they were right up close to
him. Nezumi unwound a thin rope from his wrist. He tossed it lightly to
the red lights.

"It's all yours."

\emph{Cheep-cheep-cheep.} The mouse squeaked. The light was gone---the mouse had
run off holding an end of the rope in its mouth.

"Oh---it's young."

"What'd you say?"

"The nameless mouse. It's younger than Hamlet and the rest, isn't it?"

"How can you tell? You couldn't even see the thing."

"Oh\el well, I just had a feeling. Like it was still young."

After a few seconds of silence, he heard Nezumi click his tongue.

"Geez, your instincts seem to sharpen in the weirdest moments. I dunno
if that makes you easy or hard to deal with."

"I only said what I felt."

"Hmph," Nezumi sniffed derisively, "talkative for someone who was about
to give in a minute ago, huh? Means you've still got strength to spare."

"You said you needed me. So I'm gonna try my best."

"God, you sound like a kid. I only need your brain. Soon you'll have to
run it full-throttle. Enjoy your holiday while you can. Here, take
this."

Shion was handed a rope. He could see it was woven with a special fibre.
It felt pliant and durable in his hands. Depending on how you used it,
the special fibre could be used to sling and lift over a ton of weight,
or cut cleanly through a single hair. The rope had been tied to
something, for it was taut.

"Tie this rope to your waist. Tie it tight, and then you're gonna fly."

"Fly?"

"Yeah, You're gonna fly through the darkness like a nightbird. Have you
tied it yet?"

"Yeah."

"Alright, we're gonna jump. Catch a breath." Shion was drawn closer, and
he flew, half-carried by Nezumi, through the air. The darkness swayed
all around him. He felt like he had become a pendulum. But his body soon
hit a wall. He smelled dirt.

"Hold onto the rope with both hands. Don't dangle, get a foothold on the
wall. Apply your rock-climbing skills, Shion."

"Sorry, I've never gone rock-climbing before." He told himself over and
over to calm down. The smell of dirt that tickled his nostrils gave him
courage. It wasn't blood, or vomit, or the stench of dying people. Shion
inhaled a breath of air. Nezumi climbed up ahead of him, as if to show
him by example.

"It's not much of a distance. Take your time on your way up. It's much
easier than climbing a mountain of people."

"You can say that again," Shion replied. But it was daunting task to
climb a wall that rose almost perpendicular from the ground. Shion felt
like he was struggling fruitlessly.

"Did the little mouse come up this way?" he asked.

"They've got their own routes. You really love mice, don't you? Here,
look, put your hand there, on the rock that's sticking out---yeah. Now
here: there's a groove, right? Stay like that, and lift your body up."

Guided by Nezumi's precise instructions, Shion tackled the wall with all
his concentration. It looked like Nezumi was only holding the rope with
one hand. Sometimes he swayed unsteadily. The rope was probably not long
enough for them both to tie around their waists.

\emph{I'm much worse than a hindrance: I could be endangering Nezumi's life.
That's how powerless I am.}

Shion was confronted with yet another reality.

\emph{I'm powerless. But---}

'I need you.'

He tasted the words in his mouth thoroughly. They were like an
aphrodisiac. He could feel it quenching his body. Shion dug his nails
into the wall of dirt, and continued inching his way up.

\myspace

His fingers touched something hard. The moment he noticed it, he felt
himself being pulled up. When he fell face-forward, out of breath, he
felt the same sensation of something hard on his cheek. It was also cold
to the touch.

\emph{Is it\el rock?}

\emph{Cheep-cheep-cheep!}

The lighthearted chirruping of little mice. He felt the small animals
scurrying over his back. Cravat and the rest would often scurry across
his back like this, in their bold demands for food or play.

Shion got up carefully. He cautiously tugged the rope bound around his
waist. The other end was secured tightly to a protruding rock. It was a
strange one; there was a round hole bored into the tip. The mouse had
slipped through this hole several times to bind the rope tightly. Maybe
it had been trained to do this. If it was, then was this rock also a
man-made object, placed like a moor for a ship? He untied the rope, and
coiled it around his arm.

He tried to hand the coil to Nezumi, but Nezumi didn't look up from
where he was squatting on the floor. His breathing was laboured, despite
how athletic he was. It was no surprise. He had looked out for Shion,
given him instructions, and supported him throughout their climb here.
It had probably taken many times the energy it would have cost him if he
had climbed up by himself. Shion's heart ached.

"Nezumi---I'm sorry. I---"

"Don't apologize." His voice, a little hoarser than usual, cut Shion
off. "You apologize for everything. I'm sorry, I'm sorry, I'm sorry.
What's apologizing gonna do to solve the problem? All it does is cut
your delicate and injured conscience some slack."

"Yeah."

"Don't use words to excuse your guilt. Treat them with more respect."

"Okay." He was right. No matter how many tens of thousands of apologies
he lined up, he wouldn't be able to solve a single thing. From now on,
he would swallow the words that threatened to spill all too easily from
his lips. Before speaking words of apology, he would silently bear the
weight of his guilt.

He watched Nezumi's profile, whose lips were parted in laboured pants,
making his shoulders rise and fall.

\emph{Some day, I'll return the favour. You said you needed me. I'll live up
to it. I'll put my life on the line to protect you.}

"Oh---Nezumi."

"Shut up. I told you to stop apologizing."

"No, I meant to say\el I can see your face."

"Idiot. Took you long enough to notice, didn't it? From here on, we'll
have a light. It's a small one, but still a light. A splendid gift,
don't you think?"

Shion looked around him. The place they were in was slightly more
spacious than a bed. The ground and walls were cobbled with stones of
all sizes, and a number of them glowed with a white light.

"These are\el LEDs\el "

"Yeah. Light-emitting diodes. I'm guessing familiar lighting for a No. 6
resident? It probably glows with a bit more flourish in No. 6, though."

"What are LEDs doing here---?" Shion said perplexedly. "The passage down
there only had incandescent bulbs. Nezumi, this is inside the
Correctional Facility, isn't it?"

"We haven't gotten inside yet, unfortunately."

"But---the wall we just climbed up was a natural one. It wasn't man-made."

"Oh, so you noticed?" Nezumi said with an impressed air.

"Even I could pick that up," Shion replied indignantly. "If it was
man-made, I wouldn't have been able to climb it, even with your help.
Either that, or it would have been much easier. But that wall was
neither. It had handholds and footholds, but only just enough for me to
manage the climb---not by myself, though."

"Are you still insulted that you couldn't climb up by yourself? Pretty
sensitive, aren't you? Take injury to your pride easily?"

"My pride practically aches right now," Shion said. "Nezumi, what is
this about? What is a natural cave doing directly connected to the
basement of the Correctional Facility, an execution grounds?"

Nezumi stood up. A mouse had appeared on his shoulder without him
noticing. It was grey and small. Its tail was a little longer than
Cravat's.

"This place is a naturally-occurring series of caves, huge and complex.
No. 6 decided to use part of it as its execution grounds. That's all
there is to it."

"But these rocks aren't natural. This place is man-made too, isn't it?
But it's completely different from the Correctional Facility. Which
means it was made by the hands of someone else---"

Nezumi's hand reached toward him. Before he could utter anything, it
clamped over his nose.

"You talk too much. Shut up and follow me."

"Okay. Right behind you."

"Shion, is your curiosity stirred just as easily as your pride? Your
eyes are positively glowing."

Stir it certainly did. Curiosity thudded with a steady heartbeat inside
Shion. What was there? Hell wasn't the only thing beyond this place.
There was something else, a world different from the hideous inferno.

\emph{What is it?}

\emph{What's waiting?}

Nezumi slowly walked down a steeply slanted slope. His back floated
dimly in the darkness.

A passage had been carved out of the boulders. The ceiling was low, and
it was impossible to get through unless you crouched. Nezumi stopped
once in a while to catch a deep breath, his shoulders sagging. He looked
like he was having considerable difficulty.

Just as Shion opened his mouth to ask if he was alright, Nezumi swayed,
and leaned heavily against the wall.

"Nezumi!"

He wondered if it was the same spell as last time. Nezumi would collapse
suddenly, and lose consciousness. Shion thrust his hands out, expecting
Nezumi to be overcome by the same fit. But Nezumi didn't collapse. Still
leaning against the wall, he only murmured:

"It's come again."

"Huh?"

"Never mind---"

"Can you walk?"

"Of course. I've got legs. And much better ones than yours at that."

Rejecting Shion's hand, Nezumi resumed his walk. Shion gave his hand,
which had been dangling without anyone to accept it, a little shake, and
moved forward as well.

"This is---"

He widened his eyes. They were, indeed, in the heart of a cavern. Rugged
boulders protruded in some places, but it was considerably spacious. It
was too dark to see into the corners. But it wasn't an inky darkness.
Although dim, there were lights. But they did not come from
light-emitting diodes.

"Candles?" There were a number of them lit in the crevices of the
boulders. Shion had encountered these lights for the first time in the
West Block.

"Nezumi, where---"

\emph{Is this?} he had planned to finish, but the words stuck in his throat.
Nezumi's profile was rigid. His throat slowly contracted as he
swallowed. It was rare to see Nezumi so on-edge.

"Something wrong? What's---"

"Shion, get down!"

Just as Nezumi yelled, Shion felt himself get shoved. He fell backwards
on his bottom. A black shadow whizzed past his nose.

\emph{Scritch. Scritch.}

He heard a sound like rusty cogwheels turning. It was a voice.

Nezumi swung his hand. A black shadow bounced and splayed at Shion's
feet.

"Whoa!" He bent over backwards. It was a grey rat, quite big. It looked
like it had come from the sewers.

\emph{Screech, screech, screech.}

One sewer rat after another attacked him. One leapt onto Shion's
shoulder, opened its mouth wide, and attempted to sink its teeth into
Shion's throat. He grabbed it and hurled it. The rat smelled dank. A
dull pain raced through his arm next. There was a rat latching onto it.
Shion's hands moved before he could feel fear.

"Damnit!" He battered his whole arm against the wall.

\emph{Screech, screech.}

The rusty, creaking sounds echoed. The rats were crying out in alarm.

Countless red lights were winking at him. From crevices in the boulders
all around, red eyes were looking down on Shion. He was being surrounded
by several dozens of sewer rats. Their crimson gazes were directed
unblinkingly at the two boys, as if they were waiting for the next
opportunity to attack.

"Shion, you alright?"

"Of course."

"Just to let you know, imitating a cat isn't gonna scare these guys
off."

"I figured as much. The cat would probably get scared off himself."

"That's some coarse welcome for someone they haven't seen in a while."

"Huh? In a while?"

Nezumi brought two fingers to his lips, and whistled. A variant melody,
dancing high and low, flowed forth. It was a song Shion had never heard
before. It made him think of a fog that drifted among a grove of trees
in the dark. A black-and-white movie played in his mind.

\emph{Scritch.}

A single sewer rat squeaked from somewhere nearby. It slowly approached
them. Nezumi gently extended a hand forth, and the rat nuzzled his
fingertips. Nezumi's fingers moved gently over its grey fur in a loving
caress.

\emph{Scritch, scritch, scritch.}

One more, then another, came down from the boulders. Nezumi's eyes
flitted to Shion for a moment. Shion nodded deeply as a sign of assent.
He crouched down, and extended his hand like Nezumi had done.

\emph{Scritch}.

A slightly smaller rat rubbed against his hand. Shion scratched it
between the ears.

Its red eyes narrowed. It was enjoying it.

\emph{Hey, he's not much different from Cravat.}

The little mice used to love being petted between the ears as well.
Every night before he went to sleep, they would always beg for it.
Inukashi's dogs were the same. They were always ecstatic when he gave
their fur a thorough brush.

"There there. There you go. Hey, wait. You want to be scratched too?"
Shion looked down to notice several rats already sitting in his lap.
They weren't as cute as the mice, of course. But they did not make him
afraid. There was no trace of the aggression that they had showed
before. More and more rats climbed into his lap, and it was starting to
get heavy.

"Look at you," Nezumi said, cutting his whistling off to shake his head
slightly, "you could give the Pied Piper a run for his money." Then he
raised his chin, and glared into the air. "Is this the last of your
welcoming procession?" It was a voice that rang out clearly. Nezumi's
beautiful voice echoed off the ceiling of boulders, and rang out still
further. It was like he was on a stage with top-class acoustics.

"Show yourself. Your sewer rats aren't gonna do any good."

A small rock rolled across the ground. The darkness bristled in the
crevices. As if to tear through it, a black mass came falling down. It
alighted without a sound.

The sewer rats scattered from Shion's lap. In a blink of an eye, they
melted out of sight into the darkness.

\emph{Is it a human\el ?}

It looked like a human clad in a black cloak. When the cloak flapped to
expose what was underneath, Shion stood up and held his breath.

A tall man of sturdy build was standing there. Everything about the man
was grey. The long hair that reached down to his waist and the colour of
his skin was grey. The colour of his eyes which stared back at him were
grey. But they weren't a lustrous dark grey like Nezumi's. They were the
colour of sand. Grey was also the colour of the desert. It rejected
life, and accepted the lives of others none too easily. It nurtured
nothing, and changed its shape with the wind. A vast and fruitless land.
Whereas Shion felt a vital energy from Nezumi, this man radiated an air
of a barren world.

"What did you return for?" The man spoke, barely moving his lips. Shion
felt a shiver run down his back, though he did not know why. He gripped
his own arm tightly.

"You came back. That means you must die."

"Let me see Rou." Nezumi took half a step forward. "I have something
important to discuss. Let me see him."

The man also took half a step forward. "You must die. Those are the
rules."

He was the desert after all. There was no trace of life in him. Shion's
chill got worse.

"You must die. Those are the rules." He felt an icy blast of wind coming
from the man. Was it a hallucination?

Nezumi exhaled slowly. The darkness shifted above his head.

Shion couldn't catch the moment when the man moved, partly because it
was dark. If they were immersed in inky darkness, the man's grey body
may have been visible even just a little. But this dusky darkness, with
only a candle as its source of light, allowed the man to blend easily
into the background, and he was almost impossible to see with Shion's
level of eyesight. But the man's movements would probably be difficult
to follow even under the blazing sun of noon. He was that swift. His
grey body glided and lunged at Nezumi. Nezumi rolled to the side barely
a moment earlier. The man's leg followed him, swinging upwards in a
kick, and Nezumi swatted it aside with his hand. The man only lost his
balance slightly before regaining his posture and lunging at him
soundlessly again.

A sewer rat clambered onto Shion's shoulder.

\emph{Screech. Screech. Screech.}

It raised its voice shrilly, and rubbed its paws together. Whether it
was merely spectating the fight between the two humans or cheering for
one of them, Shion didn't know; but its voice was strangely excited.

"Can you see what's going on?"

\emph{Screech-screech-screech.}

"You can see, huh. Nezumi---is Nezumi okay?" Shion squinted desperately
into the dim gloom. He could only squint. He could only watch.

It was always like this. It had always been like this. But---but I can't
just let it end at that now. I have to do something---anything.

The man had said Nezumi had to die. It wasn't mere intimidation.
Although the man's voice had been emotionless and flat, it had been full
of murderous intent. He was really intending to kill Nezumi.

\emph{Screech-screech! Skrit-skrit-chit.}

The sewer rat leaned forward and squeaked in an even higher voice.
Simultaneously, he heard the dull sound of flesh hitting flesh. Nezumi
sprawled at Shion's feet.

"Nezumi!"

"Idiot! Don't come closer!" Nezumi curled up and coughed. He hauled
himself up unsteadily.

"What's wrong?" The man asked from beyond the darkness, in the same flat
voice. "Softened up a lot, haven't you, during all the time you've spent
above ground?"

"Well, you might say I've---enjoyed my vacation a little---too much." He
could hear Nezumi gasping for air. Shion stepped forward.

"Fool. It's no wonder you can't fight me; you can barely even stand."

"Of course!" Shion was shouting. He wasn't able to make out the man
clearly. But he could still hurl words at him. "How much strength do you
think Nezumi had to use to even get here? Try doing the same, whoever
the hell you are, before acting high and mighty. Try climbing that
wall---\emph{with} a burden like me in tow."

He was met with silence. The sewer rat on Shion's shoulder flicked its
long tail lazily.

"What is he?"

"Just a burden," answered Nezumi.

"Why did you bring him here?"

"I want to introduce him to Rou."

"And then, what?"

"I want Rou to hear the story out."

"His story?"

"Mine."

"No one here will lend an ear to a fool like you, who's come crawling
back and doesn't even know to hide his shame."

"You don't know until you try." Nezumi drew up softly beside Shion. It
looked like Nezumi could see properly. For him, this dim light was
enough.

"Shion, listen," Nezumi whispered at his ear. "The gap in the boulders
right behind us. Narrow passage there. Jump into it. And run."

"And you?"

"Never mind me. Go!" Shion was shoved on his chest. He ran.

"Not so fast." The man's murderous intent bore down upon him like a
shockwave. Nezumi spoke a short command.

'Go'\el or was it 'run'?

Shion stopped and turned around. Two shadows were wrestling with each
other. He could see a blurry image through the darkness. He could
definitely see.

"Nezumi."

The man was straddling Nezumi, and had both hands around his throat.
Nezumi was writhing to get free. Shion breathed fast and shallow.

\emph{Nezumi is struggling?}

He had never seen Nezumi this trapped, struggling this hard.

\emph{You must die.}

That was what the man had said. He had definitely said it.

Shion lifted his wrist. The rope of special fibre was wound around it.
He wasn't thinking. His body had been cut away from his soul, his brain,
and was moving on its own. No---maybe it was his soul commanding him.

Kill him.

The sewer rat leapt off Shion's shoulder. It darted into the gap between
the boulders that Nezumi had told him to jump into. Shion didn't follow
it. He was going to turn his back on Nezumi's words.

\emph{Scree-scree-scree.}

The sewer rats screeched in every direction from their rocky perches.
Their voices were wrung in apprehension and fear. The man's movements
froze. His gaze scoured the area. His chin jerked upwards just slightly.

Shion leapt onto the man's back. He hooked the rope under the man's
chin, crossed it, and leaned backwards with all his weight.

\emph{Gah!}

The man writhed. Shion dug a foot into his shoulder, and tightened the
noose as far as it would go. Back when he had tried to strangle the
wretched man in the room adjacent to the execution grounds, he had only
had a vague notion of what he was doing, and his thought processes had
been mostly numbed. But it was different now. He was completely alert.
His conscious was crisp and clear. His intentions and thoughts were his
own.

\emph{I'll kill him.}

\emph{If you try to kill Nezumi, then you must be destroyed. You are destined
to be destroyed.}

He pulled tighter.

The man's body bent back like a bow.

"Shion!" A yell resounded. It was a scream. A strangled voice called his
name.

"Shion! Stop---stop, please---" Nezumi pounced on him from behind. "Stop,
I'm begging you. Shion."

"Huh---?"

A pair of hands cupped his face firmly.

"Can you hear my voice?"

"Oh---yeah."

"Let go. Hurry. Loosen your grip."

He did what he was told. The man rolled over, and tried unsuccessfully
to get up. He remained on his knees, coughing heavily. The air whistled
through his half-collapsed throat like a wind that whistled through a
wasteland.

"Shion---I told you before. You're not made out to be an executioner."
Nezumi picked up the rope, and gripped it in his hand. His lip was cut
and painted with his blood. The pair of red lips moved. "---or are you
saying this is salvation?"

"No."

"Then what? If you were trying to save me, it was none of your business.
Shion, don't ever pull a ridiculous stunt like this again. This isn't
something for you to do."

"It's punishment."

"What?"

"This is punishment."

"Punishment---what do you mean?"

"That man tried to kill you. So he paid the penalty."

"Shion, you---"

"I'll do the same thing again. If that man tries to kill you, I'll do
the exact same thing."

The man sat squatting on the ground, still wheezing, clutching his
throat.

"Who---is he?"

This time, Nezumi didn't answer. He looked down at Shion silently. His
fingers which held the rope were trembling.

"He choked me," the man said in disbelief. "And I didn't---I, out of all
people---I didn't notice his presence."

"Yeah---you sure didn't."

"I was choked from behind, and I couldn't escape."

"Yeah. You were flailing about like a rabbit in a trap."

"The rats were afraid of his presence."

"Yup."

The man shuddered. "Who\el is he?"

"He's a resident of No. 6."

"No. 6? ---What is a resident of No. 6 doing here?"

Nezumi exhaled shortly. "Let me speak to Rou. I'll tell him everything."

Shion sat listening to Nezumi and the man converse. His palms finally
began to throb in pain, from where the rope had dug in.

"Let us hear your story."

A voice rained down from above their heads.

Shion raised his face and looked around. There was a dark painted space
in the darkness where even the light of the candles didn't reach. The
voice was coming down from there. Just a sentence---

\emph{Let us hear your story.}

With those words, it disappeared. There was no human presence there.

"Much obliged," Nezumi sighed. The man stood up. He staggered and
disappeared between the boulders.

"Let's go then, Shion."

"Oh--- right." He stepped out into the darkness.

"Shion."

"Hm?"

"It's probably useless to say this, but---"

"Mm-hmm."

"I want you to stay as you are, Shion."

"Huh? What do you mean?"

"The Shion I know would never commit a sin. Never." \emph{Fight it}, Nezumi
murmured. "I want you to fight with yourself."

It was a plea. His tone was strained and imploring. Wasn't this the tone
of voice that Nezumi himself despised the most?

Shion closed his eyes.

Behind his eyelids, there was a darkness even deeper than the one that
spread before his eyes.