% !TeX spellcheck = en_US

\chapter{The city of light}

\lettrine{A}{fter their} meal, Nezumi placed a petri dish and a pair of tweezers in
front of Shion.

"I extracted this out of your incision. Try opening it up. This is
probably right in your field."

"My field?"

In the petri dish was something black and stringy, about two centimetres
long. Shion plucked it up with the tweezers. The slimy black object
dangled from them, and looked half-melted. Upon closer scrutiny, Shion
could make out evidence of something filmy at the end of it.

"These are― wings?"

"Looks like. I have no idea. There's one other thing I pulled out too,"
Nezumi added. "What do you have to say about this?"

It was another black lump. This one was hard, and resembled a seed.
There was a hole in it as if something had eaten its way out.

"A pupa― I think," said Shion slowly.

"Pupa? Like what moths and butterflies make themselves into? Oh wait,
butterflies make cocoons."

"Cocoons are the outer shell of pupae," Shion explained. "Embryo, larva,
pupa, and imago― most insects go through their development stages in
this order. This one... is probably some kind of bee."

"You can tell?"

"There are signs of wings beginning to form. The membranous qualities,
the fact that there are four of them... and more than anything―" Shion
swallowed. "I saw it with my own eyes― a black bee flying out of
Yamase-san's neck."

"And that bee and this black thing are the same thing?"

"If I'm not mistaken, probably. This one couldn't complete its
metamorphosis in the pupal stage. It managed to eat its way out of the
shell, but it couldn't become a fully grown imago. It failed."

"Why?"

\emph{Why?} He was right, why was that? Why was same bee that had hatched,
undergone metamorphosis and become an imago inside Yamase unable to
break out of its pupal stage here? Was it a coincidence, or― Shion shook
his head.

"I don't know. All I know is that this is a parasitic organism, and it
feeds off humans."

Nezumi stared unblinkingly at the petri dish.

"A parasite bee..." he muttered. "I thought bees only fed off flower
nectar."

"Those are just one species of bee, like the honey bee. Most bees ― or
wasp, in this case ― are hunters, and solitary by nature."

"And there are parasitic wasps too?"

Shion nodded. Nezumi's questions were simple and brief, and were easy to
answer from Shion's knowledge. But none of the questions were off the
mark. They tread lightly but accurately on the point of focus. With each
question he answered, Shion felt a growing uneasiness like he was being
backed into a corner. He felt like he would unwittingly slip and let
something horrific escape from his lips. \emph{But you can't be afraid}, he
told himself. He couldn't turn a blind eye and let things slip past him.
He couldn't pretend that nothing had happened, and refuse to enquire, to
take action. He stood in the position of one who had experienced it. He
had been host to the parasite, fought with it, and prevailed. And like a
symbol of this battle, he bore the red serpent on his body. Yes, this
was his imprint. Nezumi's face was peering into his. Shion returned his
gaze steadily, and spoke.

"There are said to be about 200,000 different species of parasitic
wasps. Hymenoptera such as bees and ants are highly specialized insects,
and there are still tens of thousands of species that are undocumented.
This is particularly so for parasitic wasps― or so I've heard."

"Which means we don't know what we're gonna get."

"We can't say what species for sure."

"But we can still predict."

"If we have any foundation for a basis of prediction," Shion answered.

"Why, \emph{you're} the best foundation there is," said Nezumi with mock
enthusiasm. "So how was it, being a host to a parasite wasp? Could you
tell if it was a new species?"

"You're really disagreeable sometimes, did you know that?" Shion replied
irritably.

"Well, you piss me off \emph{all the time}. 'We can't say what species for
sure', he says. Don't mess around. Don't you have any sense of danger?
These wasps are killing people."

"Most parasitic wasps do."

"What?"

"Wasps that are classified as parasites are actually more parasitoid. To
reach full growth, they only need to attach themselves to one prey...
their host. And ultimately, without fail, they consume and kill it."

Ultimately without fail, they consume and kill the host. It sounded even
more grotesque when put into words.

"Host? Like what kind?"

"There are lots. Moths, butterflies, ant larvae, fruits... a species of
ichneumonoideae called \emph{Rhysella approximator} lays eggs in the larva of
another species, xiphydriida, and makes it its host."

"So a wasp leeches off another wasp."

"Not only that, but another species of the same ichneumonoideae called
\emph{\emph{Pseudorhyssa alpestris}} lays eggs in the same xiphydriida right after the
\emph{Rhysella}, and \emph{its} larva eats both the larva of the \emph{Rhysella} \emph{and} the
xiphydriida."

"So they kill each other even if they're from the same species... wow, I
thought only humans killed their own kind. So?"

"Hm?"

"Are there parasite wasps that attach to humans as hosts?"

"I've never heard of any," replied Shion. "There are other organisms
that are parasitic to humans ― viruses, bacteria, ticks, fleas, and the
like. I've heard once of a warble fly that laid eggs in a boy's head,
and one of them invading his brain, but that was an unusual case, I
think... I've never heard of any wasps doing that. The question is,"
Shion said thoughtfully, "how was it able to lay eggs in a human body in
the first place? How did it pierce the skin with its ovipositor without
being noticed?"

"You have no memory of it?"

"No. I didn't feel any pain or itch. It never crossed my mind that I'd
been stung by a wasp."

"So they can lay their eggs without their host noticing at all."

"Not only that, they also grow with astonishing speed. And when they do,
they must excrete some sort of substance that rapidly accelerates ageing
in the host, and inevitably leads them to death. Even the process of
rigor mortis and dissipation gets sped up. And finally, as a full-grown
imago, the parasite wasp eats its way out of the body and escapes
outside."

There was a moment of silence.

Shion and Nezumi looked at each other, and exhaled at the same time.

"I'm surprised you lived through it."

"Yeah. I'm starting to get the cold sweats just thinking about it."

"There are too many things we don't know," said Nezumi. "Where did this
guy come from? What is it?"

"Hey―" Shion said suddenly. "Have there been any similar incidents like
that here?"

"No. I did a little research because it was nagging me too. There were
guys who got shot to death fighting, or people who got drunk and drowned
in a ditch, but no one who suddenly turned old and died. There's no
media control or censorship here like No. 6," Nezumi added, "so if
anything out of the ordinary happens, it should spread like wildfire."

"Then if it's happened in another Block―" suggested Shion. "The
Southeastern Blocks, maybe? That environment is probably the most suited
for a new species of insect to appear."

Nezumi shook his head slowly.

"I can't imagine that happening. If it did, the city should close all
the gates leading in. But they haven't shown any signs of doing that.
Produce is still being shipped in from the Southeastern Blocks as usual.
The North Block is the same."

"Then the wasp definitely must have come from No. 6.... I can't believe
it," Shion muttered to himself.

"Unbelievable― you're certainly right about that." Nezumi's fingers
lightly tapped the petri dish. His shoulders shook slightly.

"Nezumi?"

Nezumi's head was bowed, and a quiet chuckle escaped his lips. It soon
turned into howling laughter. It echoed in the underground room that
overflowed with books. Nezumi collapsed on the bed, holding his stomach
and laughing harder still. Shion lunged for a pitcher of water, and
emptied it on Nezumi's head.

"Hey!" Nezumi sprang up. "What the hell are you doing?"

"Are you alright?"

"\emph{Alright?} I'm soaking wet here."

"I just― I thought you were undergoing a fit of hysteria or something,
so I..."

"What do I have to throw a hysteric fit for?"

"Well, you started laughing randomly, I just thought..."

"I only laughed because it was funny."

"Funny? What is?"

Nezumi shook his head violently. Shion's face was pelted with water
droplets.

"It's hilarious, isn't it? Where did this thing originate? No. 6.
There's a mysterious man-eating wasp flying around in this utopian model
city, the \emph{Holy City}, if you will. This is city of the future, the
epitome of modern science. And it's being eaten by \emph{bees}. Hilarious."

"It's not something to laugh about. People are dying."

Nezumi stood up. He walked over to Shion, and drew up to him
face-to-face. Nezumi was right, Shion thought. He was tall. He easily
exceeded Shion in height by several centimetres.

"What?" Shion unconsciously took a step backwards. He drew himself up
and squared his shoulders as best he could in spite of the wall of books
behind him. He had seen something flash in Nezumi's grey eyes with a
savage, piercing glint. It was only for a fleeting instant, but he had
not missed it.

"Forgive my foolish question," Nezumi said in an expressionless voice.
At the same time, a set of fingers closed around Shion's throat.

"Have you killed anyone before?" Nezumi's thumb slowly dug deeper into
Shion's neck.

"Never..." Shion said faintly. "Of course I haven't..."

Nezumi's thin lip curled slightly in a cold smile.

"I would've figured. But keep this in mind. The wasp might kill its host
in order to keep itself alive, but humans can kill other humans for much
smaller reasons than that. And \emph{you} were almost killed by another human."

"I know."

"You liar. You don't know anything."

"I do know!" Shion said angrily, clenching Nezumi's wrist. "I know. If
I'd been taken to the Correctional Facility as planned, I would have
been made out to be the murderer in the wasp's place. At best, I would
have gotten a life sentence. At worst, I would have been executed..." He
paused for a moment, then continued determinedly. "The Bureau wanted to
buy more time. They needed time to decode the truth about Yamase-san's
cause of death― and by making me the suspect, they wanted to file it
away as a simple murder case for outside eyes. Am I right?"

Nezumi's fingers withdrew. The spot on Shion's neck burned where
Nezumi's thumb had dug in.

"Good answer, full marks," he said breezily. Then his tone dropped in
mock seriousness. "It seems this unbalanced young man, tumbled from the
ranks of the elite, engaged in this crime out of resentment for the
city. He allegedly concocted a special chemical to use repeatedly in
multiple criminal acts. Thanks to the efforts of the Security Bureau,
however, this young man has been put under arrest. We would like to
reassure the citizens of the city that they are perfectly safe. ―It was
probably scripted somewhere along those lines," he broke off. "What a
ridiculous farce. I'm guessing your knowledge and history fit the role
of 'dangerous criminal' perfectly."

"The City has full access to all the citizens' personal information,"
Shion answered. "It was probably easy to find a person to fit the role
they wanted."

"More like you were being marked from the beginning."

"Huh?"

"Ever since that day you helped me, the city's been marking you as a
cautionary suspect. They've been scrutinizing your daily life down to
every minute detail. Who you met with, what you talked about, what you
ate... so I thought this murder case was something the city devised to
arrest you. I was wrong, though, and we know that now."

"But why? For what purpose―"

"Because you're not a loyal citizen," Nezumi replied as he towelled his
hair off. His profile was delicately chiseled. It looked almost like an
artificial creation. It was all too different from a face that had skin
and blood coursing through it, and carried bodily warmth, with swells
and dimples of flesh or fat, the occasional eczema; a face that changed
with joy, anger, grief or mirth, shone with sweat, or stained with
tears. This was no human face― it looked like a doll that had been
crafted with utmost precision.

But even so, Shion thought, and clenched his fist. The wrist he had
grasped minutes ago had been warm, and throbbing with a steady pulse.

"You're spaced out again. Am I boring you?"

"Huh? Oh, no― of course not. I was just wondering what you meant by...
not loyal." Shion's face flushed, though he didn't know why. Nezumi
sniffed dismissively.

"That city only accepts people who pledge absolute loyalty to them. They
don't allow people who resist, object, or retaliate. They make sure any
foreign object is removed completely. That's how it's thrived up until
now."

"And I'm the foreign object this time."

"You're more than foreign to them― think about it. You housed a VC, you
held suspicions against the city for manipulating information, and you
saw the cruelty behind their fa\c{c}ade. As a citizen, you fail the test.
You're an unwanted candidate. The city was just waiting for the right
opportunity to get rid of you. ―Hey," Nezumi said abruptly. "Tell me,
what does the immune system do when a virus invades a human body?"

"Huh?" Shion was caught off-guard. "Well, first the natural killer
cells― that's a type of lymphocyte― find the cells that have been
infected with the virus, and destroy them. Then the ribonuclease become
active and suppress the spread of the virus. Next―"

"That's enough," Nezumi interrupted. "Geez, I set you off explaining
something, and you don't know when to stop. That's why people get pissed
off at you."

"You're the only one that seems to get irritated at me."

Nezumi ignored him and gave a short, derisive laugh.

"So basically, to the city, you're a virus. And that's why they tried to
erase you."

"I'm a human. I won't be erased that easily."

Nezumi sighed deeply in exasperation.

"It's easy for humans to kill other humans, you know."

Shion clenched his fists tightly again.

"But they can save people too."

"What?"

"You saved me. Nezumi," he said earnestly, "parasite wasps don't help
each other out. But people can save other people. Am I wrong?"

Nezumi smiled briefly, and his gaze slid away from Shion.

"You're as stupid as they come. Hopeless. Where did you think of that
sickening cliché? I told you, I'm only repaying my debt."

"And I told you, you've already paid enough."

"How generous of you to have such low estimations of my debt," said
Nezumi sarcastically.

"Then you must have had pretty high estimations."

Nezumi let out a long breath, and looked up at the ceiling. He bit his
lip in silence as if to grope for the right words. The mice gathered
around his feet.

"You don't understand," he said momentarily. "No amount of words would
probably make you understand. That day, four years ago, I'd mostly given
up. Giving up means the end of you. I knew that. But there was no way
anyone would help me, or lend me a hand― that's what I honestly thought.
I couldn't ask for help, I had nowhere to run.... I snuck into Chronos,
so tired I couldn't move, and I thought about how it was only a matter
of time until I was caught..." he paused, then spoke quietly. "I felt
so― humiliated. I wondered if the whole reason I'd been born was just to
die in humiliation like this.... don't laugh."

Shion would never have been able to. The sounds of that night four years
ago were echoing in his ears. The sounds of the wind, the trees, and the
whipping rain meshed and undulated, rising vivid and sharp in his mind.
And amidst the din and darkness, a sopping wet boy was curled up on the
floor.

"And then the window opened. You threw it open wide, didn't you. And
then you spread your arms open."

"Yeah, I remember. I felt really restless, and I wanted to scream."

"To me, it looked like you were calling, beckoning for me to come in. I
thought― this was unbelievable, and it was happening right this moment.
And you even left the window open when you ducked back inside."

"I was going to turn off the atmosphere control system."

"I don't care for what reason. That window you left recklessly open was
my stroke of luck. And the fact that you didn't call the Security Bureau
on me, but instead treated my wound and even gave me food was another
miracle. I found out for the first time that things like this could
happen. That a helping hand could be extended miraculously like that....
you were the first one that taught me. Like all of these―" Nezumi slowly
looked about his room.

"― These thousands of stories here, you taught me that sometimes we
encounter the most unexpected things. And that's why I was able to
survive...." he lapsed into momentary silence. "So you're right. There
are times when people are saved by other people. And you're the one that
taught me that. You were the only one that taught me that. The debt I
owe for that is high― unfortunately for me."

Nezumi's voice was so quiet it was almost a murmur, but it was deep and
clear, and rang pleasantly in Shion's ears. So that's what it was, Shion
thought, and spread his fingers as he looked as his palm. That night,
when he threw the window open with these hands, he had called in a
miracle along with the wind.

"Don't get too carried away," said Nezumi, his words quickly turning
brusque. "I'm giving you the guest treatment because I owe you. If you
get carried away and start acting cocky, I'm going to kick you out."

"Fine by me," said Shion mildly. "I don't know if you'll take my word
for it, but I'm not the type to get carried away too easily. But how did
you find out I was in danger?" he asked curiously. "It's not like you
were keeping constant watch over me these four years, right?"

Nezumi plucked a grey mouse up and held it out at Shion. It was the
smallest among all the mice.

"Take a close look."

Shion held the mouse in his palm, and brought it close to his face.

"Is this... a robot?"

"Pretty well-made, isn't it? It has a set of built-in sensors. This
thing is small enough that it can slip through the city's surveillance
net and move around quite a bit. Depends on the area, though."

"Did you make this?"

"Well, yeah," he said casually. "While I was away from No. 6, this guy
was the one sending me data about you."

Shion lightly closed his fingers around the mouse in his hand. It had
none of the warmth and softness that was characteristic of living
things. Conversely, he scooped up one of the mice scurrying about his
feet and held it in his palm too. This one had a faint but definite
warmth and pulse.

"I didn't know when or how the city was planning to get rid of you,"
Nezumi continued. "You're smart and young. You still had plenty of usage
value. I couldn't imagine that they would kick you out so easily. I
figured once they discovered how useful you could be, they'd take full
advantage of it. Writing you up as a murderer was probably a piece of
cake for them. You were their scapegoat," he sneered. "They were keeping
you enclosed in a corral until the ceremonial day, when they would drag
you out in front of everyone and make a flashy show of chopping your
head off."

"So I've gone from being a virus to a goat, huh. Not much of an
improvement."

"Hey, goats are cute. More lovable than you, anyway."

"I appreciate the compliment," said Shion unamusedly. "So this little
guy sensed the change going on around me and came to notify you."

"Yup. It started that day when that man died of unnatural causes at the
park where you worked. After that, the Bureau started stepping up their
surveillance on you. And like adding icing to the cake, your co-worker
got killed too. It was the perfect opportunity to put you under arrest."

"Surveillance― I didn't even know I was being watched."

"They do it so you don't notice. Once you do, it's too late."

"That's scary."

"You're noticing \emph{now}?" Nezumi sniffed in derision. Shion raked his bangs
up. He was confused― about what had happened, what was about to happen,
and what he was supposed to do from now on. He knew almost nothing. And
it was terrifying not to know. But there was one idea, although it was a
mere speculation, that had sparked in Shion's mind.

\mybreak

"Nezumi."

"Hm?"

"Could it be the park?"

"The what?"

"The Forest Park in the centre of the city. My workplace― could that be
where the parasite wasp originated?"

"Why?" said Nezumi. "That park is right in the middle of the city. It
might be a forest, but it's still artificial. All the wildlife is
managed and controlled by the city. If a parasite wasp sprung out of
nowhere, they'd notice."

"That's true, but... out of all places in the city, the park would be
the most adequate environment for a new species to appear. And all the
victims so far, including me, were in the park when it happened. Of
course―" Shion hesitated. "I don't know if there's been casualties
anywhere else― but I think part of the reason why the city suspected me
was because the incidents were concentrated in that location. But if
that's the case―"

"That monster must have been born there somehow without being noticed by
the control systems."

"It's plausible, right? And what's more, the park is where lots of
people gather."

"No shortage of hosts," said Nezumi grimly.

It was a park that was beautifully and conveniently crafted for the
citizens. If a species that preyed on humans actually did inhabit it,
then―

"Spring," Shion murmured.

Spring? Nezumi echoed in question.

"Once winter comes, the wasps will cease activity as they enter a
dormant stage. The eggs that have been laid already will probably pass
the winter as they are."

"Inside people's bodies."

"Yeah. And when spring comes, they'll be able to resume activity as an
imago. Then they'll hatch all at once." In a season abundant with
sunlight and flower blossoms, a mass of black wasps would simultaneously
break out of people's bodies to take flight. How many would they be? How
many people would be sacrificed?

"We have to do something."

"And how are you gonna 'do something' about it?" replied Nezumi bluntly.
"Don't even think about going back to the city. You'll be killed. You're
an amateur, you can't pull any fancy tricks like slipping past
surveillance. Ten-to-one, as soon as you step inside the city, you'll be
shot dead. We don't have a trump card to pull out, you know."

"Actually― I think we might."

Nezumi narrowed his eyes.

"I survived that wasp attack. There's a chance that I've developed
antibodies that resist the toxin. If I have, then it'll be possible to
make a serum out of my blood."

Nezumi shot an appalled look at Shion and hunched his shoulders
exaggeratedly.

"And then what're you gonna do? Go waltzing into the city's Health
Bureau and say 'Please check my blood. And if you like, please make a
serum out of it'? That's idiotic. They'll probably suck all your blood
out and throw you in the trash with the rest of their organic garbage.
Sure, what you're saying is impressive, but are you prepared to risk
losing your life for these people?"

"I don't want to die."

"Then don't think about useless things. Whether you have antibodies or
not, once you're caught, you're going to get killed anyway. It's just a
matter of how soon or how late."

"Then what should I do?"

"Don't do anything. Just leave them to fend for themselves."

Shion lifted his face.

"Leave them?" he asked quietly.

"Yeah. What a magnificent stage it'll be," Nezumi sneered. "You can
watch the Holy City crumble into ruin, glowing in the light of spring.
And you'll have the best seats in the house."

"Nezumi!" Shion raised his voice sharply.

"Whoa, don't go dumping water on me again."

"Are you under the impression that the West Block is safe from this?" he
said incredulously. "We're human beings, the same as them. There's no
knowing when the wasps might attack us too."

Nezumi fell silent. A crooked smile played on his lips.

"We're not the same."

"What―"

"The people inside the city sure don't see the residents of the West
Block as the same human beings. You still don't know what kind of place
this is, do you? This is the Holy City's garbage dump. No. 6 has thrived
by throwing everything it doesn't want out here. You should take a good
look and see for yourself."

"Nezumi..."

"This is just my hunch, but listen," he continued. "That monster is
probably only going to choose residents of No. 6 to be its host― the
people who have pushed everything dirty into the hands of others to live
in that perfectly hygienic environment, well-nourished and in excellent
health. Mr. Monster has gourmet tastes."

"How can you be so sure?"

"I have no clue about the biology of insects, Shion. But I'm probably
right in guessing that any bee, wasp, ant or grasshopper will appear
most in places where there's the most food. In terms of population
density, we're much higher than the city. But do you see any sign of the
monster here? No. Which means that there are simply no prey, no hosts
here. Right?"

Shion was at a loss for words. His thoughts were becoming tangled, and
there was a dull pain throbbing at the back of his head. Nezumi's hand
touched his cheek.

"Sorry―" he said softly. "I didn't mean to give you a hard time. I
forgot. You're from the other side, the inside of the wall."

"I don't understand what you mean by inside and outside."

"Of course you wouldn't," Nezumi said gently. "That's normal. You guys
have probably never tried to understand what was going on outside your
walls, have you? You probably weren't even curious about it. Oblivious,
arrogant, blissful people... But you, poor thing," he murmured. "You've
fallen off that pedestal."

\emph{Which means I can no longer be oblivious, arrogant or blissful anymore.
Is that what you want to say?} Shion let his gaze speak for him as he
looked Nezumi in the eye.

\emph{If arrogance is knowing nothing and never having tried to know, and if
my blissful life until now has been built upon this arrogance, then
sure, I don't mind throwing everything away. Falling off my pedestal
would be the best thing that could have happened to me.}

"Nezumi," he said steadily.

"Hm?"

"I want to know the truth. I want to know what's real, what's happening
to this world I'm living in. I want to see its true face."

Nezumi hunched his shoulders and flashed him a wry smile.

"Such youthful words."

"We're the same age."

"I have more life experience than you. Geez, I don't know who else would
rattle off a line as embarrassing as 'I want to know the truth'. Except
Hamlet, maybe."

"Who's that?"

"A prince of Denmark. I think you should balance out that knowledge bias
before working on knowing the truth. You really know next to nothing
about classics, huh?"

"Well, I've never needed them before..." frowned Shion. "The Arts
weren't encouraged much, so..."

Nezumi reached into the shelves and pulled out two books.~

"If what you're saying is true, then once winter comes, the commotion
will die down. Which means we have a moratorium until spring."

"Probably."

"Then there's no need to get worked up," he said airily. "Nothing will
come of it. So until you recover and you're well enough to move around,
you can read him these."

"Him?"

A brown mouse scurried up onto Shion's knee, and stood on its hind legs.

"He loves \emph{Macbeth}. The other is \emph{Faust}. Ever heard of it?"

"No."

Nezumi grimaced, and heaved an exaggerated sigh.

\poem{If feeling prompt not, if it doth not flow\\
	Fresh from the spirit's depths, with strong control\\
	Swaying to rapture every listener's soul,\\
	Idle your toil; the chase you may forego!}

"―is how it goes. You should give your brain a break and work on
training your soul. Your Mama used to read to you, right?"

"Yeah."

The mouse squeaked insistently.

"Oh, right. Speaking of Mama, I have a message from yours. I almost
forgot."

"Huh?"

A faint colour rose in Nezumi's cheeks as he obstinately turned aside.

"Well, since you managed not to die... I figured it wouldn't hurt to
tell your mother that you're over here now. "

"You went to see my mother?"

"Not me," he said brusquely, "I stayed in the underground tunnel. This
guy―"

The brown mouse tilted its head to one side.

"―He went for me, with the note in his mouth. One of the oldest tricks
in the book, but surprisingly, it got past surveillance without being
noticed."

"Thank you."

"Stop that." Nezumi pulled a face. "Don't give me that teary-eyed look.
Aren't you embarrassed at all?"

"I was talking to this little mouse here."

"Oh― well, then."

Shion really was grateful. Now that he knew how difficult it was to get
past the wall, he felt grateful from the bottom of his heart that Nezumi
had taken the same risk again just to deliver the message to his mother.
\emph{So this is what it means to gain knowledge.}

"Your mom's got some guts," Nezumi remarked. "She managed to give me a
reply without getting caught." Nezumi tossed him a rolled-up strip of
paper that was about half the size of his finger. There was a message
hastily scribbled onto it that he could barely read.

\memo{1}

"What does this mean?" He and Nezumi looked at each other in
bewilderment.

"It's a letter that your Mama wrote to her beloved son," said Nezumi.
"Don't you have any clue what it might be about?"

"Not really," replied Shion doubtfully. "'K' probably stands for my
mother's first name, but this... 'not sure'...?"

"It's probably an address. Not that building numbers would do any good
here.... Latch Building, huh. I guess I'll look into it."

"So that must mean my mother knows someone who lives in the West Block."
It was a surprise to him. He had never heard Karan utter a single word
about anyone who lived here. Nezumi snapped his fingers smartly.

"Oh― I know."

"Huh?"

"Maybe he's your dad."

"Fat chance," retorted Shion. "Look who's had one too many stories to
read. Aren't you embarrassed at all?"

Nezumi \emph{tsk}ed in disappointment.

"You're getting better at your comebacks. ―But, well, I guess you're
right. It's your typical script for a cheap melodrama. A father and son
reunite in tears after sixteen years of estrangement." Nezumi's voice
turned deep and burly.

"I've missed you, son."

"Me too, Father." Shion bounded into Nezumi's widespread arms. They
circled around his back. It was warm. For an instant, the frigid touch
of Yamase's dead body flashed back in his mind. But it was this warmth
here, not that coldness, that he wanted to remember; and Shion vowed
never to forget the heat of the body that was in his arms. He wished all
beings, himself included, could continue to be living beings. He didn't
want his life unfairly wrenched away from him. He could feel it― the
pleasure of living, breathing, and possessing a body of warm flesh― soak
into the depths of his core. Nezumi gently detached himself.

"You're getting better at picking up your cues," he said approvingly.

"I know. I've come pretty far in a short time, haven't I?"

"Quite an excellent pupil. Shall we go, then?"

"Where?"

"Outside."

Darkness had fallen outside. Here in the West Block, night and complete
darkness seemed synonymous. A chill wind nipped at Shion's skin.

"Look," Nezumi pointed. No. 6 was carved out in the darkness, bathed in
light as it glowed in the distance.

"It's always shining like that, morning, day, and night. Pretty, isn't
it."

"Yeah."

"But where you're going to be living from now on is here." The land was
sunken in darkness, with a sparse scattering of lights here and there.
They burned forlornly, and made the surrounding dark look even more inky
black. The clouds above broke, and the moon peeked out. It was a
crescent moon. A thin sliver, almost like a clipped nail, floated in the
empty sky.

Nezumi crouched down to pick something up.

"Look at this." It was a dead wasp.

"This looks like just a regular paper wasp."

"You were right, it looks like the season for wasp activity is over."

"By springtime..." Shion trailed off.

It was possible that the city would hold out somehow until spring. It
gave him a few months' grace period until the fatal judgment would fall.

"If you're serious about fighting the parasite wasps, I won't get in
your way," Nezumi said. "But if that means helping No. 6, I'm backing
out."

"Do you have a grudge against No. 6?"

There was no answer. The wind blew stronger. The canopies above creaked
and rustled as they swayed in the darkness.

"Shion."

"Hm?"

"That city where you were born and raised in― that's the biggest
parasite."

"Huh?"

"It latches onto the host, sucks out all its nutrients, and devours it
whole. That's the kind of city it is. A Parasite City... do you
understand what I'm saying?"

"No."

"You'll find out soon. You said you wanted to know the truth. But once
you know, you'll never be able to go back. I would prepare myself if I
were you."

"I've already come too far to go back anyway, wouldn't you think?"

"I guess so."

Nezumi's quiet laughter carried on the wind. His voice was dry and
hollow, as if to complement it.

"If you find out the truth, and still want to protect No. 6― then,"

In the darkness, Nezumi's face turned to his. Shion could feel his gaze.
He could almost see the grey of his eyes just as vividly.~

"Then you're my enemy too."

\emph{Boy, it's chilly out here. Let's head back in.} Nezumi's tone was light.
It was as if nothing had happened. He turned his back to Shion, and
began whistling as he descended the stairs.

"Nezumi."

The whistling stopped.

"You haven't told me your name yet."

"Nezumi it is, and Nezumi it shall be. Good enough."

"But it doesn't suit you. And it was a promise. You said you'd tell me
your name if I survived."

There was a soft laugh, which quickly turned into whistling again. The
door closed, and a silence settled over the darkness. Shion stood alone,
rooted to the spot. The wind caressed his white hair. He could hear a
dog barking somewhere in the distance.

He gazed up at the city that bejewelled itself in light. The Parasite
City. The city whose name Nezumi had spat with disgust was shimmering
and beautiful.

Shion averted his eyes from the light, and took a deep breath.

Then he descended slowly down the steps to the room below.