% !TeX spellcheck = en_US

\chapter{Those in the abyss}

\myepigraph{I was in it up to my neck by the time I realized the way things
	were going.\\ What could I do?\el if I refused to obey I would be
	killed. Or I could commit suicide.\\ On three different occasions I
	thought of resigning, but it was impossible.}{Wilhelm Keitel, \emph{The Nuremberg Interviews}}

\lettrine{T}{he darkness} was stabbing at him. Into his retina, his eardrums, his
skin, the darkness turned into needles that pricked at him viciously.

Shion sucked in a deep breath and filled his chest with air---no,
darkness. By doing so, he repressed his pain and trembling. He didn't
want to cower. He didn't want to let out a cry of fear. And he didn't
want Nezumi, who was beside him, to hear it.

\emph{Damnit if he ever hears me scream.}

He didn't want to expose his unsightly self to Nezumi's eyes. Shion
gulped in another breath, fully conscious of the pride within him which,
even in these circumstances, nagged persistently at him.

\emph{Hn.}

Nezumi sniffed derisively inches from his ear. At the same time, the arm
around Shion's waist grew tighter, pressing around his torso.

\emph{So much for trying to act tough}, he thought he heard Nezumi whisper. But
what actually reached his ears was:

"We're gonna fall."

It was a flat voice, stripped of all emotion. The emotionless voice
became a frigid wind that wrapped around Shion's body. With his sense of
pain, his fear, and his pride whipped away, for an instant, Shion was
empty. Like a cicada shedding its skin, he became a hollow cavern that
left only its outward appearance intact. He sometimes had this sensation
when listening to Nezumi's voice. He didn't mind it much. In fact, it
even felt refreshing. Exhilarating, even, to become empty.

When Shion tried to suck in his third breath, the floor disappeared from
beneath his feet. With a heavy \emph{thunk} it had split in two. It was like a
gallows. It almost felt strange that he wasn't feeling the rope digging
into his neck; hearing the sound of his cervical vertebrae cracking;
feeling his body swinging limply in the air.

They were falling. Falling, straight down---at least they were supposed to
be, but he couldn't grasp what was happening. He wasn't sure whether
they were falling, floating, or rising. He couldn't distinguish between
descent, suspension, or ascension. His senses were swallowed up by the
darkness that surrounded him on all sides.

An impact hit him. He felt his whole body slam into something hard. His
breath died on his lips. Whatever he had fallen on was slightly elastic,
absorbing and mediating the force enough to avoid spraining his muscles
or shattering his bones.

\emph{What did I land on---?}

He had no time to check. He was yanked forcefully.

"Roll."

He was half-shoved into a roll by Nezumi. He turned over and over,
thinking of nothing, feeling no fear. His shoulder hit something hard,
and he felt a pain followed by tingling. He had evidently hit a wall. As
he placed his palm on the floor to push himself up, he felt a
tremor---like vibrations, like strange rumbling.

"Stand up. Push yourself up against the wall."

Shion stood up, and huddled close to the wall, which was rough on the
surface---probably concrete. His thoughts, willpower, and senses were
half-numb. He could only barely manage to follow Nezumi's directions and
move as he was told. Nezumi's body overlapped his. It was hotter than
usual. But the heartbeat Shion felt against his back was not even
slightly out of rhythm. Crushed with such force, Shion couldn't help but
cry out.

"I can't breathe."

But his voice, which came out as a gasp, instantly dissolved in the
tremendous noise from behind them. He couldn't even tell if he had heard
his own voice.

"Nezumi."

He squirmed slightly.

"This---"

Never in his entire life had he heard sounds like this, voices like
these.

\emph{What is it? What are they?}

\emph{Groaning? Rumbling? Screaming?}

A booming, thick and heavy sound roared at Shion and pressed in on him
from all directions; it welled up from below, it came raining down from
up top; it twisted and tangled with itself. A piercing shriek rang out.
Then it rasped, cut off, and an eerie silence replaced it. But only for
an instant. And again, it welled up, it rained down\el 

These were not sounds of a human world. They were not mere noises.

"Nezumi!"

Unable to bear it anymore, Shion wrenched his body around. The force
pressing against him relaxed. The heat of Nezumi's body drew away. Shion
was grabbed by his hair, and turned around. His back was pressed against
the wall this time, and his hair yanked roughly.

His chin jerked up. Nezumi brought his lips to Shion's exposed ear, and
whispered as if to cram the words into it.

"Look if you want to. Listen if you wish. But---"

Nezumi's fingers released his hair, and slid down his neck. They traced
the red band of his scar.

"But you'll be haunted with nightmares for your whole life. Be prepared
for it."

\emph{Heh.} His short laugh, almost a mere breath, seeped into Shion's body. It
was a cold laugh. It may have been condescending. Nezumi freely
controlled the various ways in which he laughed. Normally, this would
have sparked Shion to anger. He would have reproached Nezumi, telling
him not to laugh like that.

None other than Nezumi had taught him: condemn from your heart those who
scorn, look down upon, and belittle themselves. He had taught him not
only to be angry, but to hone all of the emotions he possessed, whether
it was to cry, laugh, fear, reject, yearn, or love.

\emph{Don't let them go numb. Don't let them wither. Bare your fangs at all
that threatens to desecrate your humanness.}

Shion had definitely been taught. But right now, he was too overwhelmed
to be angry. His emotions were falling, sifting right through him.

"Nezumi\el what is this?"

"Reality." There was no hint of laughter left in his voice. "If you're
gonna look, see it through 'til the end. If you're gonna listen, don't
ever think of plugging your ears."

\emph{See this through\el all of this?}

Shion opened his mouth, and gasped for air.

Before his eyes was darkness. The bottom of this darkness was crawling
with people. To him, it looked like they were crawling. The darkness had
shades both dark and light, and his eyes, beginning to adjust, caught
the darkest shades. It was a lump of overlapped people. The people who
had been packed into the elevator had been smashed onto the floor, and
were now squirming, crawling.

There was a blood-curdling scream. A shadow came dropping down. Someone
who had been clinging onto some part of the elevator had finally spent
his strength. Shion couldn't tell whether it was a man or woman. Like
the roar of a beast, the scream echoed into the painted black darkness.

\emph{Thud.}

The sound of flesh hitting flesh. Its vibrations shook not his eardrums,
but his entire body, making his skin bristle.

Shion tried to remember. He tried to remember each and every one who had
been shut in with the elevator with him.

There was a man. There was a woman. There was an elderly lady with
mussed grey hair. There was a young girl with tanned skin. There was a
wiry merchant with sunken eyes. There was a deathly pale man, a
surviving member of the Disposers.

Wasn't there a mother holding her infant? Wasn't there a baby in that
mother's arms? There was. There certainly was.

Wrapped in a dirty white cloth, the infant was wriggling at his mother's
breast\el somewhere, in this mass of people---a stench came flowing into
his nostrils. It was like all of his senses, numb and dormant until now,
had opened themselves out to the outside world all at once.

He began sweating profusely. His teeth refused to come together, and
they chattered incessantly. The stench of blood, fecal matter, body
odour, assaulted his nostrils many times more viciously than inside the
cargo container. He heard people being crushed. People were being
crushed under the weight of others. Although it was a sound he was
hearing for the first time, he could tell it was the sound of human
destruction.

"This is hell," he heard himself utter weakly.

"This is reality," a mutter answered back. "This isn't any hell. This is
the reality of the world you've been living in, Shion."

A wave of nausea washed over him. Leaning heavily on the wall, Shion
covered his mouth with his hand. His stomach fluids spilled through his
clenched teeth. The sweat stung in his eyes. Behind his closed eyelids,
memories of his days in No. 6 floated and flashed by.

The roses of myriad colours that bloomed in the residences of Chronos;
the evening sky; the powder-blue walls of his classroom; Safu waving her
hand; early morning in Lost Town; the fragrance of bread that filled the
house; Karan with her back to him; a little girl's footsteps---'Good
morning, brother' 'Good morning, Lili'; Sampo's clunky round body; the
ladies' hat that Ippo had squashed by mistake---it had been decorated with
a pink flower pin---'\emph{Oh no}, Ippo, that's not good---' Yamase yelling; the
aroma of coffee at the café that he had stopped in with Safu; the tree
branches rustling and swishing in the breeze---oh, the green---it was so
vivid.

\emph{I want to go home.}

He longed for it achingly.

\emph{I want to go back to No. 6.}

He wanted to go back to the world within the walls. He wanted to return
to his peaceful, fulfilled, quiet world. Even if it was a land ornate in
falseness, he wanted to bury himself in beautiful artifice.

He gritted his teeth. He swallowed the stomach fluids inside his mouth.
Shion slowly raised his heavy head. His face was drenched with
perspiration.

"Nezumi\el " He mustered as much strength as he could into his legs, and
managed somewhat to keep himself upright. If he fell to his knees now,
he would never be able to get up. He would have to dig his heels in and
remain standing, even if he had to gasp for air. Nezumi would not extend
a hand to him. He would not support him. If Shion was going to curl up
here, if he was going to go mad, if he lost his ability to stand on his
own feet---there was nothing left for him ahead.

"What should I do next?" Shion managed to speak, albeit in a raspy
voice. He felt the presence in front of him give a short intake of
breath.

"Can you move?"

"I will."

If he didn't, he would die. And he could not. He had not come here to
die. \emph{I'm here to save her, to live. Don't forget that. I'm going to
survive this reality.} A crack ran through the cross-section of No. 6
that was drifting in the back of his eyelids. It tore apart into shreds.
It shattered and disappeared, along with his desire to flee and return.

Shion extended his hand, fully prepared to have it shaken off. His
fingertips felt a firm arm. He clenched his hand around it.

\emph{Nezumi.}

\emph{I'm not doing this to cling to your help.} He wanted it to get across.

\emph{I'm alright. I can move. I won't squat and curl up here.}

His clenched fingers were not shaken off. The cold and brittle arm only
twisted slightly. An answer came to his unspoken thoughts.

"I got it."

Almost at the same time, an orange light blinked behind Nezumi. Shion
widened his eyes. His heart trembled at the tiny, marble-sized light. He
felt like crying. His arm stretched forward, and his fingers clutched at
thin air.

"We're gonna run, following those lights. They'll stay on for a minute
and a half."

Miniature light bulbs were attached to the wall at equal intervals. They
were tiny, tiny lights, barely enough to water down the darkness that
lay thick upon them. But it was still light. There was still something
here that was not darkness.

"Let's go."

Nezumi turned his back to him, and broke into a run. Shion also stepped
out to run after him, but his foot slipped on something slimy. There was
a pool of blood at his feet.

"Fucking hell," he snarled without thinking. Something that wasn't quite
fear or shock was roaring in his chest, filling it up and pressing
against it; and at the bottom of it, a spark was lit. Wrath. The flames
of wrath circled its licking flames in a spiral, and came racing
upwards.

\emph{This is reality. Reality. Reality.}

"Goddamnit."

\emph{I'll never forgive it. I'll never forgive this reality.}

He moved forward. He moved forward, as if kicking the puddle of blood
out of the way. He desperately ran after the figure that was threatening
to melt into the darkness.

\emph{I'll survive. I'll live to destroy this reality.}

Shion's anger became heat that coursed through his body. He was filled
with energy right down to his toes. Nezumi turned around. It was too
dark to see the expression on his face. He swung back around, and
slackened his pace a little. Even in times like these, his movements
were still graceful.

The light bulbs flickered. Before them was a narrow walkway, wide enough
for one person to squeeze through. The walls were bare concrete.

"Move along the wall."

"Nezumi, where does this lead?"

"The execution grounds."

"Huh?"

"Whatever's behind you and in front of you, you might as well call them
execution grounds. The question is just how early or late the sentence
is gonna be delivered."

A motor was humming behind them. It was an outdated model that rattled
and screeched.

"Nezumi, wait. The elevator's moving again."

"Don't stop," Nezumi clicked his tongue irritably. "Keep moving forward.
Don't stop walking."

"But the elevator---"

Shion's lips trembled. A cold bead of sweat rolled down his spine.
Nezumi opened his mouth.

"But of course," he said stonily. "They're planning to cram all the
people they've hunted in this underground chamber."

"There's gonna be more people falling?"

"They don't fall, they get dropped. Same mechanics as a gallows. The
floor opens up. They fall to the bottom of the abyss. If they're lucky,
they'll break their neck and leave this world painlessly for good."

"We have to tell them about this passageway."

"Who?"

"Everyone. There are still people that can move. We have to tell those
people to escape here."

"And then what's gonna happen? Imagine."

"Huh\el ?"

"Yeah, there are people that can still move. Quite a few. But what'll
happen if they all trample over each other to rush into here?"

"Well\el "

A desperate mob would come swarming in. Each would jostle and shove,
vying to get into a passageway that was barely wide enough for one.

What would happen?

One would fall, and others would fall on top of him. The passage would
fill with more screams and groans.

"Now do you see?" Nezumi said. "Look behind you."

With a hand still on the wall, Shion turned around. Several shadows were
coming this way, dragging themselves across the ground.

"Only the people who've noticed this passage and are able to break away
get saved. Then they get to move to the next stage."

"Then this light---is that what it's---?"

Before he could finish his sentence, the light bulbs were extinguished.
They were again plunged into inky darkness. Then, there was a sound. The
air vibrated. The darkness trembled.

\emph{How many people were crammed into that elevator? Ten, fifteen, twenty\el 
more? But gee, you could probably only see a transport elevator like
that in a museum nowadays\el judging by the annoying noises, the
conveyor belt is probably worn pretty thin\el wait, I have a feeling
there might have been an elevator like that in Lost Town. Where was it
again? It made annoying noises\el }

He was slapped across the cheek. The pain stung in the inside of his
mouth. The empty rattling of his thoughts and perceptions returned to
their normal state. But it also meant that his conscience was being
pulled back into a hellish reality.

"Shion."

"Uh\el yeah?"

"There won't be a next time."

\emph{Next time, I'm leaving you behind. I'm not a saint who'll drag you along
if you space out. You said you could move. Then use your own legs to
escape.}

Shion wiped the sweat dripping from his chin with the back of his hand.

"Follow me. Don't get separated."

Nezumi turned his back to him again. It was so dark, and yet Shion could
see the outline of his figure clearly.

\emph{I won't leave you.}

He pressed a hand to his cheek, now hot and stinging.

\emph{I'll never leave you. I'll sink my teeth in, and latch on no matter
where you go.}

He would never lose sight of that back turned to him. He would crawl
across the ground to follow him if he had to. That was the only thing in
his mind. He had no room to think about No. 6, his mother, Safu, or the
parasite wasps. He slapped his own cheek this time. He finally knew
first-hand that pain could be a sign of being alive. His throbbing cheek
was telling him, \emph{you can live, you can still walk}.

Apparently the lights only reached a short distance in from the entrance
of the passage. It was relatively straight, and uniform in width. Just
this motion of continuous walking seemed to be awakening his thought
processes.

\emph{This passage---it's man-made.}

The thought occurred to him, and Shion smiled a little. He would never
have believed he could smile, but he felt the corners of his mouth
tugging up. It was a bitter smile, aimed at himself.

\emph{Of course it was man-made}, he was smiling at himself. This was the
Correctional Facility. It was a building into which No. 6 imprisoned the
people it deemed as criminals. Naturally, every path, every wall was
man-made. The scene that Shion had witnessed in the darkness just now
was the same. It wasn't hellish wreckage generated by some natural
disaster. Was it not a reality that had been created by human will?
Everything here was made by the human hand.

\emph{This is the reality of the world you live in.}

He repeated Nezumi's words in a corner of his mind.

\emph{This is the reality of the world I live in. Then who made it happen, and
for what purpose?}

He tried to visualize the mayor's face. He used to see photographs of
his gently-smiling face everywhere on the streets. He remembered seeing
him on television. \emph{"I don't like his ears. They're so vulgar."} That was
what his mother Karan had spat, but no one ever criticized the mayor of
No. 6. He had close to one-hundred percent support from the citizens.

\emph{Him---is it him? No, but\el is it possible for such a catastrophe to occur
under one person's command? None of the No. 6 residents knew of this
gruesome reality. Why don't they know? Why\el } his thoughts creaked
haltingly like the outdated elevator. They caused an unpleasant racket.
But he still had to keep thinking.

\emph{Why didn't any of them know?}

"Because they don't try to find out," Nezumi said, with his back still
turned to him. His feet stopped, and he twisted the top half of his body
to face Shion. Shion didn't know whether his eyes were getting used to
it, or if Nezumi himself was deflecting the darkness, but he could see
the expression on his face clearly.

"Nezumi, how did you know what I was thinking?"

He was genuinely surprised. He was so startled, he had almost lost his
train of thought for a moment. Nezumi shrugged.

"I told you before, didn't I? You're easy to understand\el well, parts
of you are. Everything else about you just baffles me."

Nezumi's tone of voice changed. It took on a hint of softness and rang
out clearly. It was a beautiful voice. Shion couldn't express what
exactly it was, or how it was so beautiful. He couldn't put it into
words, but he could feel the comfort slowly seep into him. It was like
the comfort of lying in soft grass. He even thought he caught a glimpse
of clear blue sky.

"You tired?"

"No, I can still walk."

"Hungry?"

"Huh?"

"I'm asking you if you're hungry."

"Oh, uh---no."

He tried to remember the last decent meal he had. He couldn't. But he
was not hungry. He didn't feel any desire at all to put anything into
his mouth. Considering what he had just slogged through, he wasn't so
tough that he could still feel hunger.

"I'm not hungry at all."

"But you're running low on energy, aren't you?"

"No---"

An arm reached out to him. Nezumi's fingertips lightly touched Shion's
chest in a soft and languid gesture. But Shion felt his body tipping
over.

\emph{Huh?}

He staggered, and fell down on his bottom. He had no strength in his
knees.

"See?" Nezumi said. "You can barely stand. At least make sure you can
assess the state you're in."

Shion was grabbed by the arm and pulled upright. A pain racked his
chest. His heart was palpitating; he couldn't breathe. He broke into a
sweat again.

"It's a considerable amount of trauma. Careful your heart doesn't decide
to quit. I don't think there are any doctors who are attentive enough to
come all the way here to examine you."

\emph{"Throw physic to the dogs, I'll none of it."}

"What was that?"

\poem{Canst thou not minister to mind diseas'd;\\
	Pluck from memory a rooted sorrow;\\
	Raze out the written troubles of the brain;\\
	And with some sweet oblivious antidote\\
	Cleanse the stuff'd bosom of that perilous stuff\\
	Which weighs upon the heart?}

Nezumi shifted uneasily. Shion could hear a deep sigh.

"Stop that, will you? The way you're butchering his lines, Macbeth is
probably spinning in his grave."

"Are you saying I'm not cut out for acting?"

"Astonishing lack of talent. You probably couldn't even be an extra in a
Shakespeare play. I'd advise you to give up any fruitless hopes, Shion."

"I guess I will. It's too bad, really."

"There's a good boy."

Shion was smiling. It was no ugly twist of the lips: he felt a faint but
genuine smile spread across his face. At the same time, he could feel an
expanse of sky spreading out over his head.

Invited along by Nezumi's voice, Shion had smiled, and seen the sky.

It was that deepest hue of blue he had seen, lying in the grassy field.
The colour of the heavens was spreading across the darkness. True, this
world was ridden with brutality and falseness. Indeed, it was rife with
it. But that wasn't the only thing that existed. Because, look---in this
world, and in people's souls, there definitely existed beautiful things
like the blue of the lofty skies.

Nezumi's voice became a bubbling spring that quenched Shion's body and
filled him to the brim. It was a strange voice. It melted the soul, and
regenerated people to life.

"Just a little more, and we'll be able to catch a breath."

Nezumi half-twisted to look at him. Shion could see a dim light over
Nezumi's shoulder. It didn't flicker like the light bulbs. It was dim,
but it wasn't the kind of dimness that made one uneasy about when the
light would go out.

"What's there?"

"A resting place. A temporary one."

"Resting place\el we can rest there, huh."

He had felt like he could go on walking forever. He thought he would
have to keep thinking like this, else they would not be able to escape.

\emph{But we can rest.}

He exhaled. He wanted to spring forward, but his knees were weak, and
walking was the best he could manage.

They emerged at the end of the passageway. Shion gulped. The scenery
changed abruptly.

It was a room with white walls and a white floor. It was quite spacious.
Thanks to the man-made light attached to the ceiling, the thick inky
darkness had lightened into a dusky evening shade. Although hazy,
Shion's vision could now capture things clearly.

Ahead of the passage, he could see a greyish door. There was no
furniture or windows in the room. There was no stench of blood, or
groaning voices. It was a white room, filled with nothing. There were a
few shadowy figures curled up in a corner of the room. They were
presumably the ones who had been crammed into the first elevator load,
and had managed to survive and make their way here.

Shion buckled near the entrance. All the strength was leaving his body.

"Don't go to sleep." Nezumi knelt down beside him. "We don't have time
for that."

"We're heading somewhere else again?"

"Why, it would be no fun if this was our final destination. I thought
you came here to see that certain cute girl of yours?"

\emph{Safu.}

He clenched his fists. He let his gaze dart around. Just as he thought,
he was not met with the gaze he was looking for. She had been kidnapped,
after all, by the Security Bureau, and imprisoned inside the
Correctional Facility.

"I wonder if Safu's safe?"

"Who knows?" Nezumi answered. "But if she's alive, she's probably in a
much better situation than we are. She might even be enjoying a
luxurious afternoon tea. If she's alive, that is."

"Safu is alive."

"You're trying to believe that she is. Your own selfish wishes."

"You must believe it too. If you didn't, you wouldn't have come with
me."

"Oh really?"

"Am I wrong?"

"Shion, why don't you rewire your brain once in a while to get out of
that naive thought pattern, hm?"

"Nezumi, but\el oh---"

Shion shut his mouth. A man was staggering across his path on unsteady
feet. He swayed forward, and crumpled face-first onto the floor. The man
behind him tripped over the body, and also fell. Neither of them moved.
However, Shion could tell that they were still breathing. Their fallen
backs were still rising and falling slightly. But the man who fell first
lay still moments later.

"Aren't you gonna help him?"

Shion fell silent this time in answer to Nezumi's question.

"What's wrong? Usually you'd be there in a flash, helping him up."

"I can't."

His hands and feet felt like they were tied to lead weights. Even moving
a finger took a large effort. It took all this energy to keep his body
standing. He wasn't able to extend a hand to to others. And besides\el 

If he reached out and helped the man up, what would he do then? He
wouldn't be able to treat his wounds, or console him in his grief, or
even give him water to drink.

Suddenly, the man let out a groan. Then he began coughing violently.
Once it passed, he groaned again. He was probably gravely wounded. His
groan was fraught with pain, as if his innards were being twisted.

"Somebody\el help me\el " The man moaned. He gasped for air like a
wounded animal. "Somebody\el please\el "

Shion plugged his ears. He closed his eyes. He knew he was being a
coward. Hadn't he learned so many times over how cowardly, how shameful
it was not trying to see, not trying to listen?

\emph{Look. Listen. Don't try to make excuses. Fight with anything that tries
to make you. Your enemies aren't only outside of you. They're inside
you, too. You have to fight with your own self who tries to avert your
eyes from what you don't want to see, and cover your ears from things
you don't want to hear.}

\emph{I know. I know, Nezumi. But I can't do it now. Right now, I'm more
powerless and fragile than anything. I can't bear seeing, or hearing,
any more.}

The man lifted his face. Their eyes met. To his utter misfortune, their
eyes had met. Shion shrank back. The man was dying. He was on the brink,
but unable to die completely, and writhing in the suffering of it.

"Help\el me\el "

Perhaps his bones were broken; perhaps his innards were crushed: bloody
foam was spilling out of the man's mouth. His whole body was convulsing
in small jerks. For the man, death was the only path out of his
suffering. But even Death was laughing scornfully at him. It would not
visit him so easily. His residual life came back to lash the man again
and again.

He came crawling towards them. His gaze never left Shion. His eyes were
like a murky swamp, and at the same time, like a bottomless cavern.

"Help me\el "

\emph{Please. Save me. Save me and raise me from this eternal suffering. Let
me rest---oh, please---let me be at peace.}

Shion swallowed the saliva in his mouth. Before he knew it, he was
kneeling down beside the man who was lying on his back. His long neck
protruded from his shirt which was reduced to rags. It was a thin,
stringy, pitiful neck. Even above ground, he had probably not led a
hospitable life. It was admirable for him to have come this far.

The man was looking only at Shion. A murky swamp, a bottomless cavern.
Its clouded depths reflected nothing, harboured nothing. His eyes did
not even blink. Only his bloodstained lips were moving.

"Why\el did I have to\el " he croaked.

Yes. What did this man ever do? Why did he have to go through something
like this? He was a West Block resident: why, for that reason solely,
did he have to be crushed like an insect? For what reason did he have to
endure so much suffering?

"Why\el why\el "

The man's lips never stopped moving. Wringing the last strength from his
body, he repeated his question, over and over and over.

\emph{Tell me. Why? Why? Why? Why?}

Shion, stooped above the man's face, slowly shook his head.

\emph{I can't answer that. I can't give you any answer at all.}

"I'm sorry," he whispered. If there was anything he could do, it was\el 

He put his fingers to the man's throat. It was damp, yet cold. All he
had to do was put a little strength into these fingers. His weakening
breathing would probably stop without any pain. Then he would be at
peace. \emph{If there's anything I could do, it would be to flex these
fingers, and choke him.}

On his palms, his fingers, he felt the sensation of raw flesh and bone.
His slight convulsions, and his pulse. The man's mouth opened, and
bloody foam and a groan poured forth. The tip of his tongue was
wiggling. Shion's arms trembled. He couldn't put any strength in them.

"Stop, that's enough."

He was pulled back by the shoulder. The neck slid from Shion's fingers
like it was coated in sticky ooze.

"He'll never go easily like that."

Shion turned around, and gazed at Nezumi. For an instant, a shadow
flitted across his glittering dark-grey eyes. It was a pitying shadow.

"Nezumi, I\el "

"You can't do it." A quivering sigh escaped his shapely lips. "I think
Executioner might be an even worse job for you than Actor."

Shoving Shion aside, Nezumi stepped forward. The man was lying on his
back, breathing raggedly. With every breath, there was a gurgling at the
back of his throat. His fingers bent, and clawed at the air. His
suffering was not allayed even a little. The man only lay and gurgled,
as if he had even lost the strength to writhe in pain. Nezumi knelt down
on one knee, crouched low, and whispered in his ear.

"Does it hurt?"

Only the sound of breathing answered him.

"It'll be alright. You'll feel better soon."

"Feel\el better\el "

"Yeah. You hung in there well. There won't be any more suffering for
you. Relax, and close your eyes."

"I committed\el a crime\el "

"A crime?"

"I beat\el a little child\el once\el "

"Mm-hmm."

"I tricked\el an elderly\el and st-stole\el money\el "

"Mm-hmm."

"I told lots\el and lots\el of lies\el "

"Mm-hmm."

"I b\el betrayed\el so\el many people\el "

Nezumi slid a pair of leather gloves on. Then, he gently stroked the
man's cheek.

"Good. I've heard everything. It's alright now, everything is forgiven."

"For\el given\el "

"Yeah. All your crimes are now forgiven. There's nothing to be afraid
of."

Nezumi's hand rested over the man's mouth and nose.

"You endured. You lived. I admire you from the bottom of my heart, and
dedicate a song to you."

"A song\el for me\el "

"For you."

With the bottom half of his face covered, the man narrowed his eyes. He
was smiling. Shion couldn't believe what he was seeing. He stared
transfixed at the man's softened eyes.

\emph{He's smiling.}

"Close your eyes softly. See, all the suffering\el it's going away."

A quiet melody flowed through the air. Soft, lilting, the sounds
overlapped. Shion felt like his own body was rising up. It was
weightless, like cotton fluff, and bobbed and drifted on the breeze.
Like a bird, he faced the stream of air, and soared. Released from
myriad things, he was free.

\emph{His song steals away souls that are struggling because they can't die.
Just like how the wind scatters flower petals, his song cuts the soul
away from the body.}

Inukashi had once said those words. It was not a lie. Indeed, his soul
was being led off. To some place that was not here, it was being carried
effortlessly. It was being thieved away.

\mybreak

The singing stopped. Silence wrapped around them. Shion had closed his
eyes without realizing. The silence seemed to gently urge him to lift
his eyelids. He opened his eyes to see Nezumi still on one knee, about
to take his hand off the man's face.

The man still had his eyes closed. His mouth was still stained with
blood, but it was no longer twisted in agony.

"Has he passed away?"

"Just now." Nezumi let out a long exhale, and slumped back against the
wall. He took off his gloves, and clenched them in his fist.

"Piece of shit," he heard Nezumi swear under his breath.

"Nezumi\el "

"Fucking, idiotic piece of shit."

"Who're you talking about?"

"You."

The pair of gloves whizzed towards him. As if they had a will of their
own, they attacked Shion, smacked him right on the face, and slid to the
ground.

"You're hopeless. Foolish, clumsy, useless beyond all hope."

"Yeah."

Shion picked the gloves up. Nezumi was right. He was foolish, clumsy,
and useless. Powerless, and unskilled. No matter how many insults were
hurled at him, he could only nod and agree.

"Not just you." Nezumi raked his bangs up, and looked down. "So am I,
and the guy that just died. We're all pieces of shit."

"You're not!" Shion leaned forward to face him. Nezumi lifted his face,
and furrowed his brow.

"We're the same. You and I."

"No we're not. We're totally different."

"How?"

Shion drew his chin back, and looked directly into the pair of grey
eyes.

"You saved him."

"Me? I just helped the guy stop breathing. Gave him a little push."

"Isn't that the same as giving him salvation?"

The rims of Nezumi's eyes quavered slightly.

"It's murder."

It was a word he had not expected to hear. Nezumi blinked slowly, just
once, in front of Shion's eyes, and extended a hand to him.

"Give me my gloves."

"Huh?"

"My gloves. Give them back to me."

"Oh---right."

With the leather gloves back in his hands, Nezumi clicked his tongue
irritably and muttered that they had gotten dirty.

"Now they've got that guy's blood and spit on it. These were my
favourite gloves."

"Nezumi\el what do you mean by murder?"

"Murder is murder," Nezumi answered brusquely. "What I did was kill that
man. I covered his mouth while he was still alive, and suffocated him.
People usually call that murder, Shion, just in case you didn't know."

"But thanks to you, he was saved. He was freed from suffering."

"So?"

"So---" Shion stammered, "so you saved him. Now he's at rest. He was
released from pain, he was able to repent his sins, and he was able to
go peacefully. What you did wasn't murder. It was salvation."

Nezumi leaned against the wall and blinked at him again.

"That's arrogant of you."

"Arrogant?"

"Yeah. That's arrogant of you, you know that? Arrogant enough to be able
to call killing someone 'salvation'. Who are you, Shion? God? Are you
mighty enough that you can preside over other people's deaths?"

"Nezumi, I just---"

"That man shouldn't have gone peacefully," Nezumi said savagely.

"Huh?"

"He should have kept suffering until he died. He should never have
repented his sins and gone in tranquility. He should have loathed and
cursed his unfair death, and he should have gasped his last breaths
writhing in pain. Look."

Nezumi jerked his chin.

"Just look at this room. Remember what the execution chamber back there
looked like. How could you leave this world peacefully after being
crushed, killed, and tormented like mere insects? You can't. Of course
you can't. Most people who get caught in the Hunt don't escape. They're
forced to die a gruesome death. And when those dying people leave, they
ought to leave strewing words of suffering and hatred everywhere. Then
at least their true feelings--- even if it's just deep resentment or
damnation\el They should never have their true feelings stolen from
them. A peaceful death would be a fake imitation. Getting treated like
bugs, getting abused, only to die smiling? What salvation, huh? That's
just a convenient excuse. It's a low, filthy excuse. Don't you agree?
There's only gruesome death here. I trust even \emph{you} would be getting the
picture by now, I hope?"

"Yeah\el "

"Do you really understand? Then---" Nezumi averted his eyes from Shion.
His grey eyes had only shifted a little, but Shion felt like a shadow
had been thrown over the light that had been shining on him dimly. It
was impossible, he knew, but he could feel it.

"Then restrain your arrogance. Respect death as it is. Don't think so
highly of yourself, and don't think you can be the one to give people a
painless death. Don't ever put your fingers around someone's throat
again."

Shion stretched both his palms. He could still feel man's neck on his
hands. His fingertips were shaking.

\emph{If these hands had power, if they had the power to bring a peaceful
death, if they had the power to steal souls away like Nezumi, what would
I have done?}

He asked himself, and Shion felt like his shaking fingers were answering
him.

\emph{I probably wouldn't have loosened my grip\el and if that's called
murder, then I would have become the murderer. But---but---could that really
be evil?}

"Nezumi."

"What?"

"Is it wrong to make excuses?"

"What?"

"Is it wrong to be released from suffering in the last moment of your
life? Is it wrong to die smiling?"

Whether it was just an excuse, or fake imitation, Shion, unlike Nezumi,
wasn't able to reject the fact that people wished a peaceful death, and
that there were those who wanted to grant that wish. Nezumi sighed.

"Shion, do you still not understand? If you think of the dozens---no,
hundreds by now, if you think of the people who have been killed
already\el what happens to those hundreds of lives, their hatred, their
resentment? Are you gonna make excuses, and pretend it never existed?"

"No. It wouldn't happen that way. That would never be tolerated. But
that's what the survivors are supposed to do. They live, they remember,
and they tell others. They tell the truth of what happened in this
place. It's a job for the survivors---for us. We'll engrave it into our
memory, and never forget. But---but at least---for those who are already
dying\el if only they could go without hatred, if only we could---"

"Grant them an eternal slumber?"

"Yeah."

"Idealistic, aren't you."

"I don't think it's wrong. I don't think what you did is murder, at
least. I just can't see it that way."

Nezumi's breathing quickened slightly. A shadow skimmed across his eyes.
His gaze darkened as he looked at Shion, and wavered along with his
breaths.

"Remembering is the role of the survivors, huh\el convenient, isn't it?
How can you be so sure that there'll even be survivors? No wait, I see,
you're already assuming you'll survive. Quite the optimist, aren't you,
young master?"

"We vowed together that we'd make it back alive."

"That we'd never die, no matter what?"

"Yeah. We'll live, and go back to that room together."

Back to that room. The basement room in which they lived flashed in the
back of Shion's mind. It was vivid, as if it were right before his eyes.
The numerous books he had taken a whole week to sort through; the
bookshelves, which covered the wall and reached to the ceiling; the
beautiful and lavishly-bound book---Nezumi had said it was a story of a
far-off land; the tattered and faded, though sturdy, chair; the pitiful
bed with its stiff mattress; the pot puffing steam over the heater; the
little mice scampering about the room. Cravat, Hamlet, Tsukiyo.

Shion clutched at his chest. He yearned for them so much, he felt dizzy.

\emph{I want to go back, to that place. I want to live those days once more.}
Those images did not shatter like the phantom vision of No. 6. It didn't
ripple and disappear. It stood firm, vivid and almost repulsively real.
It brought to him even the smell of the books, and the chattering of the
mice. The impulse to dig his nails into his skin and tear at himself,
pressed on his chest. He longed, and desperately so. He wanted to go
back.

That room was the only place he intended to return to alive.

Nezumi gave a little snap of his fingers.

"You should survive and write a reportage of your infiltration into the
Correctional Facility. Who knows, it might sell."

"You told me a while ago I wasn't meant to be a writer."

"Did I? It's quite the difficult task finding the right job for you. But
I do acknowledge that you have a way with handling dogs, and sorting
books, for one thing."

"Speaking of which, I think I left a half-finished book on your bed."

"What book?"

"It's a story that takes place in some faraway land. About a man who
sells his soul to the Devil."

"Ah." Nezumi closed his eyes for some moments, and muttered something
under his breath. "Shion," he said.

"Hm?"

"We've only just started this journey."

"I know. Everything lies ahead\el right?"

"I'm sure looking forward to it."

"To what?"

"Watching you," Nezumi replied. "Remembering is the role of the
survivors---your own words. I wonder how far you'd be able to act on them?
I'll be sure to watch carefully whether you seriously try to remember
everything you see from here on out, or force yourself to forget. I'll
see it right through to the end, when those lips go from spewing pretty
words to twisting into a scowl."

His tone was flat and regular. There was no hint of sarcasm, anger, or
irritation. Though devoid of all emotion, his voice, for some reason,
was heavy. Shion clenched his fingers, and posed a question.

"Do you not believe me?"

"If it's about your memorization abilities, then I have absolute faith
in that."

"Which means you have doubts when it comes to my own humanity."

"Quite a few."

Nezumi's fingers reached out and pinched Shion's chin. His eyes
narrowed, and their grey light intensified.

"I've always thought we could never live in harmony," he said, "that no
matter how much we lived together, how many experiences we shared, I
would end my life without ever having understood you. Shion, I'm going
to tell you the truth. Sometimes\el I feel hatred towards you to the
point that I want to kill you. Just happens sometimes."

"I knew that."

"You knew?"

"I kind of realized that you---hated me."

Nezumi's fingertips dug into his chin.

"You're like No. 6 itself. It flings pretty words and ideologies around,
but its true form is something hideous. Like a cruel devil shrouded in a
beautiful veil."

"And you're saying that's me?" Shion grabbed Nezumi's wrist, and
wrenched his fingers free from his chin. "Is that my true form, as you
see it?"

There was no answer. Shion gripped Nezumi's wrist tightly.

"I'm different from No. 6. Absolutely different. You don't realize
that."

He could feel Nezumi's pulse against his clenched fingers. He gripped
harder.

"How are you different?"

"I would never deceive you. I wouldn't wear any veil. I'm laying
everything before you, as who I really am."

"Shion, let go of my hand. It hurts."

"I'm laying it out right in front of you. Your eyes are the ones that
are too clouded to see. You cling to the idea of No. 6, and don't try to
see me without tying me to it. True form? You must be kidding me," he
spat. "When have you ever honestly tried to see me as who I am?"

His anger boiled, and its heat scalded his body.

\emph{You're the one who never tries to take that step towards me. If you hate
me so much you want to kill me, then why don't you? You only ever judge
my crimes, or loathe me through the lens of No. 6. If you could hurl
your emotions at me---me as a human being---then even if it was hatred so
potent it was murderous, I would accept it. I've steeled myself to
accept it.}

\emph{Why don't you understand that?}

Shion's anger passed its boiling point, and now frothed and steamed
fiercely. Nezumi shook his head as if to push him away.

"Let go." He extracted his wrist from Shion's fingers. "Geez, don't just
grip as hard as you can like that. That could've broken bones."

"You're not that delicate."

"I'm talking about your strength. If you had this kind of power, I wish
you'd use it when you actually need it. Look, it's all red."

Nezumi's extended wrist now bore faint red bands. Shion had been
gripping harder than he thought.

"Didn't know you had this much power, did you?" Nezumi asked.

"No, I didn't."

"See, you don't even know about yourself." Nezumi slid his gloves on,
hiding the reddened part of his wrist. "You don't know what kind of
human you are. Your Mama the talented baker probably doesn't know
either. She probably thinks you're a gentle and adorable, well-behaved
little boy."

"Not like you know either, right?"

"Me? Well, I dunno about that," he said lightly. "I probably know more
than you or your Mama, to say the least. Shion, you're right: I was too
caught up with No. 6 to see you clearly. But it's not always like that.
Sometimes---just occasionally---I feel like I've been able catch your tail,
grasp a piece of the human you really are."

"And that's when you want to kill me."

"No, no that's not it. I don't want to kill---rather\el "

"Rather?"

"I might even be---afraid."

"Afraid? What do you mean?"

Nezumi lapsed into silence. His lips moved slightly.

\emph{Monster.}

Was that the word his thin, shapely lips had moved to form?

Monster?

Agitated, Shion opened his mouth to prompt him again.

But there were footsteps. Several sets of them. They were slightly more
steady than the fallen man's. A couple men and a woman overtook them
from behind, and sank onto the floor in the middle of the room. They
were all out of breath, but were not on the verge of dying.

"It's all over," Nezumi said.

He meant that the task was complete. From the crowd of unfortunate
people caught up in the Hunt in the West Block, they had eliminated the
ones who had fallen on the way to the elevator; then, they had hurled
everyone into the dark depths of the underground. They had tossed them
away: the elderly, infants, men, and women, without distinction.

"Well, let's go, then."

"Huh?"

"Don't 'huh' me, I'm saying we have to move our chess piece forward.
Nothing will get done if we hang around chatting. About time anyway,
since we're probably both getting sick of it."

"Nezumi, wait. What you were saying bef---"

"That's enough."

Words were cut off by more words.

"Unfortunately this isn't exactly a situation where we can indulge in
idle conversation. Damnit," Nezumi swore, "I'm always thrown off track
when I'm with you. This is what I mean by piece of shit. Come on. We can
wait forever, but no one'll bring us afternoon tea. Break time is over.
Get moving."

"Where are we going?"

"We're going back along this passage, opposite of how we just came. Now
isn't that easy? I think even you might be able to manage it."

"Go back! What for?"

"To move forward."

Nezumi started walking. Shion followed behind him once again. The
passage reeked of blood. He wondered if odours could have weight to
them. The smell of blood that still flowed from the bodies was heavy,
and seemed to slither over the floor, and crawl up from his feet.

He realized he was getting used to this smell. Compared to when he had
walked down this path the first time, the queasiness in his chest and
the impulse to cover his nose were not as strong. He was getting used to
the smell of blood. Did that mean he was becoming stronger, or turning
numb?

Shion took wider steps as if to tear apart the stench that swathed him.

\emph{Monster.}

The word that had slipped voicelessly from Nezumi's lips: what did it
mean? Even if he asked, he would probably not get an answer.

Shion lifted his face. Nezumi was close enough that if he stretched, he
could touch his shoulder. The stench of blood grew thicker. The groans
and screams of people who could not die came pressing on him. Shion was
faced anew with the reality that he was standing at the brink of life
and death itself.

"Nezumi."

There was no answer. His right shoulder only rose slightly.

"On the floorplan of the Correctional Facility, apart from the
newly-built area, there was another large blank space underground,
wasn't there?"

"Yeah\el "

"Is this that blank space?"

"Yeah."

A clear answer bounced back to him.

"You knew about this place, didn't you?"

"What if I did?"

"Then what was the line that was extending further down from the space?"

This time, Nezumi did not even turn around. But his gait slackened.

"You noticed?" he said.

"Well, it seemed out of place\el "

It was an odd line. Especially because the map was filled with layers of
electric circuitry, barriers at equal intervals, and countless rooms
that made up the complicated interior structure of the Correctional
Facility, the two blanks were eye-catching. The first was the
newly-built area on the topmost floor; the other was this basement area.
From here, there was a white line drawn that extended still further
downwards. A straight line. It wasn't the symbol for a circuit or pipe;
in fact, it looked like a passageway. But there was nothing at the end
of it, not even a blank space. It abruptly ended in the middle. In the
Correctional Facility, every minute detail was carefully calculated to
cut off any possibility of escape; it was designed to maximize its
functionality in the most efficient way possible. Amidst all of that,
this line was a queer and unnatural existence.

Nezumi stopped. Turning only partly towards Shion, he threw a glance at
him.

"What do you think it is?"

"Is it something I would be able to figure out?"

"No. No matter how much you put your pitiful imagination to work, you
could probably never guess. I bet this place was off the radar of your
imagination too, by quite a bit."

If there was such a radar, it had long been shattered to pieces. He had
never imagined that a world like this could exist.

He had known nothing. But now, he knew.

The two blanks: with his flimsy imagination, he could not perceive what
could be on the topmost floor. But he understood now what was in the
basement. He knew now, down to the marrow of his bones. This place,
which had been a vacant space on the floorplan. was the Hell that the
Holy City had materialized in this world. No. 6 was a city state: this
meant that humans made it function. Then did that mean it was possible
for humans to become this brutal? Then how heartless could they
ultimately become? Then how could they stop themselves from becoming so?
Then\el 

Shion chewed his lip. While chewing, he gave his head a shake.

It was no good to think now---he had neither the time nor the strength.
But someday, someday surely, he would find the answer.

How heartless could humans become?

How could they stop themselves from becoming so?

Someday, he would seek it out.

Shion sucked in a breath, and smelled blood. He had confidence. The
confidence was firmly seated deep in his breast, that someday he would
grasp the answer with his own hands. Like an unshakable boulder, it
existed. It was also the conviction that no matter what situation may
befall him, he would still be able to keep a foothold and remain within
the range of humanity.

Nezumi was still twisted around, looking at Shion. Shion fixed his gaze
directly on Nezumi.

\emph{Yes, Nezumi. I'm confident. As long as I'm beside you, I can say with
conviction that I can remain human.}

"What?" Nezumi blinked. "What're you grinning about?"

"Grinning?" He brought a hand to his cheek. Sweat and blood had mingled,
dried, and left a crust on his skin. "Was I grinning?"

"You sure were. Really, would you smile in this kind of situation? I
thought you'd finally lost it."

"I'm still sane. Probably."

"I sure hope so. In a place like this, you could probably hop the border
between sanity and insanity with one leap."

"If I went mad, would you toss me away here?"

"Of course. I can't have you being more of a burden than you already
are."

"I figured as much."

\emph{Heh.} Nezumi's lip curled. He was also smiling, in this kind of
situation. It was a smile neither bitter nor cold. It was somewhat
mirthful, even.

"I wouldn't toss you away, Shion."

Shion drew his chin back a little. There was no way it would be followed
by any sugary line like, "I'll take you there if I have to carry you
myself."

"I'll slit your throat in one resolute stroke."

Still smiling, Nezumi lifted a single finger. His grey eyes were not
smiling at all. They were still, like the surface of a frozen lake.

Shion clutched at his throat without thinking. There was a scratch that
Nezumi had left a few days ago. He had made a shallow cut on his skin
with the tip of his knife. The scar from the wound, which had bled only
slightly and had closed up long ago, was thudding with a pulse.

"Relax," Nezumi drawled. "Even I take pity on people. I'll end it all in
an instant. I would never make you suffer."

"Thanks," Shion said, for want of anything else to say, still clutching
his throat. "That's kind of you."

"I'm always kind to you. Sometimes I think I'm spoiling you too much.
It's something I regret nowadays."

"It could be a temporary state of confusion."

"Huh?"

"Make sure you can distinguish whether I've actually gone mad or if I'm
suffering temporary confusion from shock. Then you can decide if you
still want to slit my throat. It shouldn't be too late for the
decision."

"If I have the time."

"Hey, wait a minute," Shion said indignantly. The scar was still
throbbing under his fingers.

If he was going to be killed by Nezumi, he had no complaints. True to
his promise, Nezumi would probably slash his throat without causing him
any pain or suffering at all. Shion had just seen for himself how
welcoming a peaceful death was. He would not complain. But he did not
want to die a meaningless death. He wanted to live and return to that
room, no matter what it took.

"It might be hard, but I want you to check for me, just in case.
Please."

"How?"

"Just throw water on me. If there's no water\el then no choice, I guess,
you can slap me across the face like you did back there. They say with
fits of hysteria, people can recover with a shock as little as that---"

"I'll give you a kiss."

"Huh?"

"Before I slit your throat, I'll give you a kiss," Nezumi said softly.
"You'll find out exactly how much better I am at giving farewell kisses.
Then you can go off to heaven."

"Nezumi\el "

He was probably bright red in the cheeks, right down to his ears. He
felt hot. Even his forehead was damp with sweat. Nezumi spoke in a
joking tone, but he was most likely not joking at all.

\emph{Whether you go mad, or get wounded, if you can't move anymore, then
that's the end of you. So I'll give you a farewell kiss, before I slit
your throat.}

A kiss of death. The innermost part of Shion's body pulsated in
response. He shook his head. No matter how seductive, he had to reject
anything that tried to lead him to death.

"That's no good. I need you to find another way, or else I'd be in
trouble."

"Why?"

"My panic attack would get worse."

Nezumi snapped his eyes open for an instant, then turned his face aside
to snort. Although he was trying not to laugh, his body shook with the
effort, and he couldn't quite restrain himself.

"You---" he gasped, "You really---don't get it, do you? To think you'd\el 
give me a serious answer\el I\el you're really dense."

"Is it that funny?"

"Couldn't have done better." Removing his gloves, Nezumi wiped at his
eyes with his fingers. "I would never have thought I'd\el laugh for real
in a place like this. Really funny."

"I didn't really mean it as a joke."

"Alright, Shion, spare me. I understand now. You'll never go insane,
yeah?" Wiping his eyes again, Nezumi drew a short breath. "Humans are
more prone to laughing than I thought. New discovery."

The smile vanished from Nezumi's face. With a stony expression that
reminded Shion of a mask, Nezumi slowly motioned with his chin.

"Let's go."

They were at the end of the passageway. They were standing in that place
again. It seemed as if the darkness had turned a deeper colour since
their last escape from it.

The mountain of casualties had grown higher. It was natural, since the
third group had added their numbers to the pile. But nevertheless, Shion
found himself backing away unconsciously. To think the mound of fallen
and crushed people would grow even larger\el 

"Hmm, I think this would do," Nezumi muttered, standing amongst the
torrent of darkness, stink, and the groans of people unable to die.
Shion felt a faint chill around his back.

"Nezumi, what are we about to---?"

"We're gonna climb."

"Climb?"

"Have you any experience with hiking or rock climbing?"

"Nezumi\el what are you talking about\el ? By climbing, surely you don't
mean---"

"I sure do mean it. There's gonna be no path. No signs, map, or portable
lights. You only have your body to depend on. Got it? Make sure you keep
up."

Nezumi swung a foot onto the black heap. Shion stood stock-still, with
his mouth hanging half-open.

"What are you waiting for? Hurry up." He could hear Nezumi's voice
raining down on his head. It didn't contain a smidgeon of irritation or
contempt, but the voice hurt him. He felt like he was being struck with
a whip.

\emph{I won't allow any hesitation. There's no option left for us to go back,
to delay, to look for another path. We have no choice but to move on.
And I won't allow you to hesitate here, Shion.}

\emph{I know. I know. I know.}

Shion reached out into the black heap. His fingers were shaking
violently. He couldn't grasp properly.

"Shion!"

He knew. He wasn't allowed to cower. He thrust his knuckle in his mouth,
and bit down hard. The shaking stopped. The sound of the earth rumbling
came from somewhere in the mound. He froze. It wasn't the earth
rumbling. They were the voices of people. This mound was made up of
people. \emph{Don't forget. Live, and commit everything to memory. Live
through it, and pass our story on.}

\emph{I won't let myself hesitate.}

He reached out. The trembling in his fingers had stopped completely.