% !TeX spellcheck = en_US

\chapter{A prayer yonder}

\myepigraph{Good fortune, then,\\
	To make me blest, or cursed'st among men!}{The Merchant of Venice Act II Scene I}

\lettrine{S}{hion}.

She tried to call to him. But her voice would not come out. Her tongue
would not move. Her arms and legs were heavy as if they had been bound
in shackles, and she could not get them free. Shion didn't turn around.
His back, clad in a white shirt, moved further and further away. Around
them was darkness. An inky black darkness spread out all around. There
was not even the smallest ray of light.

\emph{Shion, wait. You can't go.}

\emph{Turn around. Come back home. Don't go any further.}

The darkness shifted. It bristled slimily and reared like something
alive, and swallowed the retreating white back whole.

\emph{Shion!}

A shriek tore through her throat. Terror turned into vicious pain as it
raced through her whole body. She tried to leap into the darkness after
Shion, but her body would still not move. She couldn't take a single
step forward.

\emph{Someone---someone help me. Stop him.}

"Karan."

"Ma'am!"

She heard voices. Someone was holding her hand. She was shaken lightly.

"Karan, can you hear me? Can you hear my voice?"

"Ma'am, wake up!"

The voices had strength. The darkness was brushed away from her eyes,
and her vision lightened into a dim haze.

\emph{Oh---I hear you. I do hear you.}

Karan opened her eyes. Her vision was blurry, like there was a veil
being draped over it. Two hazy faces---one of a tan man and one of a
girl---were peering into her face. But they were fleeting. She felt like
if she blinked, they would ripple and shimmer, and disappear.

She could smell bread. Butter rolls, with ample butter kneaded into the
dough. Come evening, Lost Town residents would flock to Karan's bakery
for her affordable and delicious breads: labourers, after a long day's
toil; hungry students; children with loose change in their fists---for
these poor customers, she had set the oven to finish baking at 5 o'clock
sharp. It looked like the outdated oven had functioned properly---the
dozen or so butter rolls were finished and ready.

For Karan, the aroma of baking bread was the aroma of life itself. The
savoury smell, now long familiar to her nose, yanked Karan energetically
back into the real world.

The veil was thrown off. The outline of two faces flew clearly into her
vision.

"Lili\el Yoming\el "

"Looks like you've come to," Yoming heaved a relieved sigh. \emph{Thank
goodness}, his lips moved. "Can you get up? You don't have to force
yourself."

"Yes---I'm\el I'm fine."

Yoming supported her while she raised her upper body. She had been lying
on an old sofa in a corner of her workspace.

"I\el went unconscious\el "

"Yeah," Yoming said. "Behind the display case there, you just kind of
crumpled to the ground. I was so startled. My heart's still going a mile
a minute."

Yoming flashed a relieved smile. Karan tried to smile back, but her
cheeks were stiff, and didn't move the way she wanted them to.

"Ma'am!" Lili threw herself at Karan and clung to her neck. Her eyes
were brimming with tears. "Ma'am, you're okay, right? You're okay now?"

Lili pressed her cheek against Karan's neck. It was wet. The arms that
clung to her were trembling as well. The little girl's tears were warm.
They were almost hot. Normally she would gently embrace the little girl,
but Karan's arms would still not move as she wanted them to. They were
still heavy, and she felt like she was still clawing about in her dream.

\emph{Shion.}

She wanted to tear her hair out. She felt like she would go insane.
Right this moment, what if Shion was heading to a place where his
mother's hands could never reach? What if he was descending into the
depths of hell?

\emph{If he is, if that's really happening, what am I to do? What should I\el }

"Oh!" Lili gasped softly, and drew away from Karan. "They're little
mousies!"

A little brown mouse was sitting on the spice shelf. Another grey one
poked its furry face out from beside it.

"Hey, there's two." Lili raised two fingers. Were they siblings? The two
mice blinked their very similar grape-coloured eyes, and huddled
together.

One had brought her Shion's letter. But what about the other one?

"Lili, can you bring me a tiny piece of cheese from the fridge? It's in
the bottommost drawer."

"Okay."

Karan extended her hand up to the mice on the shelf, gently, but with as
much strength as she could. The tips of her fingers trembled. The two
mice looked at each other, and busily twitched their whiskers.

\emph{Cheep-cheep.}

One of them encouraged the other, and the encouraged one turned to face
Karan. It had such small eyes, but they were eyes that showed
intelligence. These mice possessed intellect. They could understand
human language and emotions.

Karan reached out further. She turned her palm upwards.

\emph{Cheep. Cheep.}

The grey one slipped forward. Without a minute of hesitation, it jumped
down onto her palm. It shook its head side-to-side, and spat a small
capsule out of its mouth. It was her second letter today.

"Ma'am, are you gonna give the cheese to the mousies?"

Karan nodded at Lili, and opened the capsule. It wasn't Shion's writing.
But she remembered seeing it before. It was the writing that had
extended a hand to Karan and pulled her up when she had been wallowing
in the depths of despair, after Shion was taken away by the Security
Bureau. It was the beautiful, flowing hand that showed its owner's
intelligence and resilient will. She could never forget this writing.

\memo{\nezumi}{Reunion will come.\hspace{1cm}Nezumi}

The short sentence didn't even add up to a tenth of his last note, but
Karan was able to heave a sigh of relief. A cool, soothing breeze blew
through her body. The obstruction in her chest, her airway, cleared
somewhat.

\emph{Oh, I can breathe.}

It was too early to despair. She could not lose hope yet.

"Nezumi\el " She found herself saying his name out loud. For an instant,
she felt like someone had put an arm around her shoulders. Although she
couldn't see it, she could feel strong and supple arms supporting her.

\emph{Reunion will come. Whatever happens, I will bring Shion back to you
alive. This I promise.}

She could hear a low voice whisper at her ear. She breathed deeply
again.

Nezumi was there. Always, at any time, he would be by Shion's side. Her
boy was not alone.

"Karan, what's that?"

Yoming was peering into Karan's hand.

"A letter."

"Letter? Do the mice deliver the post where you live?"

"They do," she smiled. "And it's handwritten, too. Isn't it so much more
delightful than electronic mail?"

Now she could smile. Yoming and Lili looked at each other, and the
corners of their mouths turned up as well. Lili, who was breaking the
cheese and feeding it to the two mice, came up to Karan and buried her
cheek into Karan's bosom. This time, Karan could finally put her arms
around her properly.

"I was scared," Lili mumbled tearfully. "I was scared that\el you
wouldn't move at all anymore\el like Daddy\el I was scared. Really
scared."

"Daddy? Did something happen to your Daddy, Lili?"

"My Daddy before. My real Daddy."

"What?"

Yoming shook his head slightly.

"Lili's current father is Renka's second husband---she remarried."

"So Getsuyaku-san is\el " Karan trailed off. "---I see."

She conjured to mind the long, thin face with drooping eyebrows. Now
that Yoming had mentioned it, she realized he and Lili were not alike at
all in facial structure or body type. But she never felt anything
strange about seeing them walking hand-in-hand, or coming to buy bread
together. They were a happy family, father and daughter who truly got
along. After Shion had disappeared, she felt a twinge of pain in her
heart at times when she saw Getsuyaku and Lili together. She was both
saddened and envious.

"Then Lili's father\el "

"He passed away a few years back."

"A little before you moved in here, ma'am," Lili chimed in. "But you
know, I love my new Daddy too. He's really funny. He always makes me
laugh."

Lili lifted her chin, and a grin spread across her face. It was a bright
smile of relief as she confirmed that Karan could speak properly, feeble
though it was.

"I never knew. Renka never mentioned anything."

"She probably didn't want to," Yoming said. "They're painful memories
for her."

The words had probably slipped without him knowing. Yoming gave a deep
sigh. Lili began to speak.

"One day when we were eating together, Daddy stopped moving. He said, 'I
can't breathe' and fell out of his chair. And I don't know why, but he
stopped moving after that."

Lili's body began to shake, as memories of her younger days began to
come back to her. Karan slid her gaze to Yoming. She questioned him with
her eyes.

\emph{What is this about?}

"Lili's father---died, before her eyes," Yoming said hesitantly, casting
his eyelashes down. "No," he then said momentarily. "He was murdered."

"Murdered!"

The frightful word overlapped with the image of Shion's retreating back.
Karan found herself clenching her fists so hard that her nails were
digging into her palms.

"Lili's father---his name was Suifu---was a construction worker, and a giant
of a man who was proud of his strength, and rightly too," Yoming said.

"Mommy says he was really kind, strong, and cool. He was really in love
with Mommy, right?"

Yoming smiled wryly.

"I think Renka's prettying it up a bit too much, even for a story to
tell her daughter. Suifu was a big drinker and a loose spender, so they
were always getting into fights. But, well, he was a nice guy, and
worked hard for his family. He was a boisterous one, and liked to sing.
When he'd get drunk, he'd always sing in that booming voice. Yeah," he
nodded. "He was a good guy. He certainly did love his family very much."

"But he was\el killed?"

"Indirectly."

"Indirectly\el " Karan repeated. "Yoming, will you explain in a way I can
understand?"

Yoming drew up a battered chair, and sat down. With his right hand, he
gently stroked Lili's hair. It was a gesture that showed how much Yoming
cared for and cherished his niece.

"Explain so you understand, huh\el if only it was as easy as that. There
are so many things I still don't know, that it's hard to even tell in
proper sequence."

Yoming always spoke in a muddled way, and often ended his sentences
awkwardly. But nevertheless, he groped for the right words, and began to
weave the story in fragments.

"Suifu, back then, was involved in the construction of a certain
building. He was a construction worker."

"A certain building\el "

"Yeah. But we still don't know what building it was. I heard even Suifu
didn't have an idea what it was. He used to be taken to the construction
site in a windowless van---he couldn't see anything outside."

"Then to silence him---?"

"No, Karan, that couldn't be it. Suifu took his assigned job seriously,
but he wasn't interested at all in what he was building. He didn't care
which part of the city this building was in, or what it was going to be
used for. Even if he was interested, it wasn't a kind of secret that a
construction worker could sniff out. It was put under skilful
concealment. Right after Suifu died, I did some footwork of my own
trying to find out where this brother-in-law of mine used to work, but
to no avail. Open disclosure doesn't exist in a city like this. If the
authorities wanted it concealed, there would be nothing we citizens
could do against it, anyway. There shouldn't have been any need to go as
far to kill Suifu to hide a secret."

"Then\el what did he die of?"

"Outwardly they're saying it was a heart attack. But I can't bring
myself to believe that Suifu could have had one. It's as likely as a
duck drowning in a pond."

"So it must mean there's something else to it."

"Yeah\el " Yoming sealed his lips gravely, and cast his gaze around the
room.

"It's alright," Karan reassured. "We're not being tapped."

"Is that so." Yoming paused. "I'm sorry," he said abruptly, "being all
furtive like this. It's shameful."

"No, not at all."

Were they really free from tapping devices? Frankly, Karan wasn't
completely sure. The authorities possessed enormous power. They could do
anything if they wished to. It should be no large feat for them to tap
all citizens' conversations and manage that information.

But even so.

Karan grasped the memo tightly in her hand.

She would accomplish nothing if she kept shrinking back from fear.
\emph{Instead of being afraid, sealing my lips, plugging my ears---let me speak,
let me listen.} She would say it out loud; she would tilt an ear to
listen. To her it seemed like it was the only option left.

Karan leaned forward determinedly to the man and his roundabout words.

"And this 'something else' that you were talking about?"

Yoming blinked just once. Then, he stared straight into Karan's eyes.

"All of this is speculation. But if I tell you, I might end up loading
you down with a burden."

"I want to hear about it, and this is from my own will."

She tried spurring Yoming on.

"You went and you investigated your own side of the truth. You said you
barely know anything, but knowing you, you've probably at least gotten a
clue. You've grasped \emph{something}, haven't you? A hint---it might be thinner
than a thread, but something to lead you to the truth?"

"You've expected too much from me," Yoming said heavily. "I didn't have
the power, courage, or method to do any of that\el but I can say that
the pay that Suifu received while he was working at that site was quite,
quite high. I heard it was double that of how much he usually gets.
Renka was surprised when she heard Suifu was getting 'special danger
compensation'. It's hard to imagine a construction site with danger risk
in a place like No. 6."

"Special danger compensation\el " Karan pondered. "For tearing something
down, or blowing it up\el "

"Or handling chemicals."

"Chemicals---you mean poison?"

"Or the equivalent. Something unknown: something even the scientists of
No. 6 wouldn't know the proper method of handling."

"I can't imagine anything that would fit."

"It's hard to. There's just not enough information."

"But Lili's father wasn't the only one working at the site, was he?"
Karan persisted. "Wouldn't we be able to find out more if we asked those
other people too?"

"That's the thing; I can't find any of them."

"You can't find them?"

"Yeah. They're missing---or maybe they didn't exist in the first place. In
other words, there were no other humans involved in the construction
other than Suifu."

"No other humans\el oh, then do you mean robots---"

"Yes. Robots. They were using construction robots."

Karan lifted her face, and gazed at the ceiling without really seeing
it. Shion used to operate robots, too. They were cleaning robots for the
park.

"They're really cute, but functionality-wise they've still got some ways
to go. Like just the other day: a lady had her hat blown away by the
wind, and the robot picked it up, which was perfectly fine. But the
robot couldn't control its grip, and ended up squashing the hat. The
lady was furious, can you imagine? So I think humans are still better
with small and delicate tasks. Human fingers are really amazing, you
know."

And he would wiggle his fingers lightly\el 

Karan screwed her eyes shut to forcefully scatter the memories of her
son from her mind. She spoke in the calmest voice she could muster.

"Lili's father must have been doing a job that robots couldn't do."

"Probably," Yoming conceded. "But Suifu wasn't a technician. He didn't
have any special technical skill. I mean, being the serious guy he is
deep-down, I'm sure he would have done a thorough job with anything that
was given to him, but\el I can't imagine what he could have been doing
amongst those robots."

"Fingertips?"

"Huh?"

"The difference between humans and task robots."

Shion's fingertips fluttered in her memories. They were deft fingertips.
They always skilfully performed the delicate work she asked him to do.
Once in a while, she even found herself gazing in admiration at their
dexterity.

\emph{You know mom, human fingers are really amazing.}

"Robots might be more useful for things like tearing down walls, or
carrying heavy things, but with smaller tasks that require more care\el 
for example, let's see\el using small tiles to make a complicated
pattern on the wall, or engraving letters into a pillar\el robots still
can't do that, right? It's the same with bread. If you want to make
bread that tastes the same and looks the same, a machine would be
enough. But celebration cakes, for example---where it's important for them
to look nice, and to match that person's taste---you'd have to make them
by hand if you wanted something good."

"But Suifu couldn't bake bread or cakes like you can. He didn't have the
skill to make patterns with tiles, or engrave lettering. He really
couldn't do anything special\el or at least, I don't think so."

"How about carrying things?"

"Carrying things?"

"Yes, important things\el like fragile items, or soft things\el things
that have to keep their shape, like a hat. Human hands would be more
suited for things like that."

"You're right. That might be it. Maybe Suifu was carrying some
highly-dangerous something-or-other, that couldn't be left to robots.
But\el even if that was true, I have no idea what that might be, or how
it could relate to those sudden deaths. No matter how much I rack my
brains, I can never get out of the range of speculation. In the end,
with nothing to work with, we can only keep asking the same questions
that will never have answers. We don't know anything for sure\el all we
know is that Suifu was involved in city construction work, and that he
died. That's it. Right, Karan?"

Yoming's tone of voice grew more leaden by the second, and dropped so
low she could barely hear him.

"This city devours people ruthlessly," Yoming growled. "Sometimes I
can't help but think so. It devours people that have fallen out of the
boundaries of the city's values; people whom they've deemed inferior to
their values; people who have objected against their values. They devour
them head-first, ripping them, strewing the bits, until they throw them
away."

"Mm\el " Karan answered vaguely.

"So in the end, a place like this, Lost Town, is like a cesspit for the
city: it's a gathering-place for people who have fallen out of the
city's criteria of value, inferior humans. No, they probably
deliberately made it this kind of gathering-place. It's a warehouse of
disposable people."

Karan felt an onset of shivers at Yoming's heavy, low voice, as well as
the words that were coming out of his mouth. She stole a glance at Lili.
Apparently weary of the adults' conversation, the little girl had moved
some paces away to play with the two mice. The brown and grey mice were
in Lili's lap, stuffing their cheeks with morsels of cheese. Whether
human or some other animal, small beings were always adorable. It was
the adult's job to protect these small and fragile bodies and minds,
with whatever it took.

That was what Karan believed. She didn't want to thrust the terror of
reality on Lili, still so young. Yes, one could not be blinded. One must
not be tricked. One had to be able see through the deceit and find real
truth. But this hardened will was something to be born by adults who
were old enough to withstand 'knowing'. Lili was still much too young.

"Lili."

The little girl turned towards Karan's voice with her large, black eyes.

"I don't think the cheese is enough to make those little mousies full. I
think there's a butter roll from yesterday left in a corner of the
display case. Will you give them half each?"

"You can give bread to mousies?"

"Yes. Will you give it to them as a reward? And could I ask you to watch
the store, too? If a customer comes in, I want you to give them a nice
greeting, and say, 'welcome!'. I promise I'll treat you to freshly-baked
butter rolls later."

"Yay! You know, I've always wanted to do a baker's job."

The mice were now perched on Lili's shoulder, evidently having become
close friends with her. They were a pair of smart mice: they could tell
which humans were dangerous, and which ones could be trusted.

"Ma'am, you know what?" Lili stood on her toes and brought her lips to
Karan's ear. "I'm gonna tell you a secret."

"Alright, what is it?"

"Mommy's gonna have a baby. I'm going to be a big sister."

"Oh my, Renka? That's fantastic. When?"

"When it gets warm, and lots of flowers start to bloom."

Yoming gave an exasperated smile.

"Hey, Lili, are you sure it was okay to just reveal Mommy's secret like
that?"

"Ma'am's allowed to know."

"I'm so glad," Karan said warmly. "Thank you for telling me. When the
baby is born, we'll have to celebrate with a giant cake. Alright, Lili,
you'll watch the store for me, right?"

"Yeah. I say 'welcome!' right? 'Welcome!'" With the mice sitting on her
shoulder, Lili left the room and made for the bakery counter. Yoming
gave yet another sigh.

"Right. I guess it's something we wouldn't want Lili to hear."

"Of course. To hear that your own father was treated like an object, and
that he lost his life as a result\el even if she were to find out
eventually, right now is too early."

Yoming slowly lifted his gaze from the exit into which Lili had
disappeared, and rested it back on Karan.

"Treated like an object---yes, Suifu was given the same treatment as the
robots. He wouldn't have been told how risky that job was. They must
have glossed it over with something vague, and dangled high wages under
his nose. Suifu wanted money. It was still only a short time after he'd
been fired from his former workplace for getting into a disagreement
with a colleague. If it was to support his family, he would have been
prepared to risk a few things to get a job. The authorities researched
all of that, of course, and chose Suifu for that reason. After all,
they've got complete access to citizen information. It was probably a
piece of cake for them to pick a suitable candidate. They needed someone
to handle a job with unknown dangers; someone who was used to heavy
lifting; someone who was responsible, and worked silently and
efficiently. A man without curiosity, inquisitiveness, or a sense of
suspicion. Someone who wouldn't mind risking danger for money---Suifu was
probably the perfect choice."

"So that's why his job and his sudden death must be related somehow.
You're sure of that."

"Yeah. I don't know how in the world they \emph{could} be related, but I
certainly believe they're connected to each other. Ask me why I think
so, and I'd say---"

"You'd say?"

"The ambulance. Suifu collapsed, and Renka, naturally, called the
ambulance. But she told me it came unusually quickly. She said it wasn't
even three minutes after she'd phoned them."

An ambulance arriving within three minutes---this was an extremely rare
occurrence in Lost Town; no, one could even say it was nonexistent.

The Holy City of No. 6 was an urban society built upon a rigid
hierarchy. With the mayor and his city policies at the apex, only a
handful of "chosen ones" reigned. They were named "elites", and lived in
the luxury residences of Chronos in a special district, blessed with an
undisturbed, excessive, and exceedingly comfortable life. The regular
citizens below them, although far from having a life like one in
Chronos, lived their daily lives supported by highly-developed medical
and scientific technologies, in happiness---or in what they were made to
think of as happiness. People like Karan who lived in Lost Town, even
farther from "elite", were not insured of any of the city's services and
aid that were normally available to regular citizens. They were treated
like sub-citizens. To borrow Yoming's words, Lost Town was like a
warehouse for disposable humans.

Emergency medical care was almost unattainable in Lost Town. Karan
remembered hearing that the number of ambulances and medical clinics
were less than a tenth of Chronos. This was regardless of the fact that
Lost Town had many more injured and ill patients than Chronos.

An ambulance had arrived in less than three minutes. What was the
meaning behind this almost miraculous occurrence?

"Do you mean that Lili's father was being placed under surveillance, so
that they could deal with it quickly if anything out-of-the-ordinary
happened?"

"It was probably Level 3 surveillance. Suifu started convulsing at the
dinner table, but by the time the ambulance arrived, he was already not
moving. I don't know whether he was still alive at this point, or if he
was already a corpse, because people from the Health and Hygiene Bureau
carried him off. Renka tried to accompany him in the ambulance, but she
was refused. They ordered her to stay at home."

"And after that, Lili's father\el "

"Two hours later, he came back as a cold body. A doctor that was sent
over by the Health and Hygiene Bureau explained that it was a heart
attack, but of course we could never believe that. I was at the scene
too, because I'd rushed over after getting Renka's call. I begged him to
explain in more detail, but it didn't do any good. The only thing that
happened was Suifu's ID card getting exchanged for a Confirmation of
Death card to permit his funeral."

"I see\el so that was what happened."

She knew she was giving a rather unthoughtful answer. But she had no
idea what kind of answer she could have given to Yoming's words---what
answer she ought to have given. It wasn't something she could just let
in one ear and out the other. But of course, easy words of consolation
and condolence were equally as inappropriate. Then what would she say,
and how? She couldn't help but hesitate. Her hesitation turned to
unease, and faintly took on a tinge of fear. Yoming's words further
coloured this fear deeply.

"When the doctor was leaving, what do you think he said to Renka? 'This
patient passed away almost without any pain at all,' he said. And true,
Suifu's dead face was peaceful. He was smiling like he was having some
nice dream. But Renka and Lili saw how his face was twisted in pain
before he collapsed. How could they ever believe that he'd died a
peaceful death?"

"So you're saying the Lili's father's dead face was \emph{made} to look
peaceful by some special method\el " Karan swallowed hard. Her own
parents included, all of the bodies that Karan had ever seen were always
smiling peacefully. Their faces were graced with smiles that made them
look like they had never experienced a single pain or hardship while
they were alive. Every dead face was beautiful. That was how she thought
they were supposed to be---that in No. 6, where palliative care was highly
developed, everyone was promised a calm and painless death.

It was a lie. It was all artificial. Here, even human deaths were
covered up and modified. All the circumstances and truths that clung to
each and every human death were scrubbed clean like tanned hide,
levelled, fixed up, and tucked away as a "peaceful death".

\emph{We're living in a world that is more disturbing than I could ever
fathom. And what if this disturbing nature was far beyond what my pallid
imagination could visualize\el ?}

"Whatever the case, Suifu's death is still shrouded in mystery. Renka's
remarried and managing to get on with her life. I'm---as you can probably
see---living day-to-day as an information-broker. I've been so caught up
with other tasks that a lot of times, I forget about Suifu. And I say
damnit to myself every time. Those are my days: gnashing my teeth,
reminding myself that I can't let myself forget about Suifu, and of
course my wife and son."

"There would be no way you would forget it," Karan reassured him, "if
Lili's father and your wife and son have been murdered by this city. You
wouldn't be able to, would you?"

"No. And that's the only thing I can do now: remember. Keep remembering.
I'll never forget all the people that were taken from me. But sometimes
I get a nasty chill when I think---what if the authorities catch me? And I
wonder, if they ever erased my memory\el "

Yoming peered closely at Karan's face. Her eyes were shadowed. It looked
as if despair had been poured into her eyes, and her gaze was swimming
in it.

"What do you mean, erase your memory?" she asked.

"Lobotomy. Cutting into my brain with a scalpel, and taking my memories
and thinking ability from me."

"Yoming, you're---" \emph{You're letting your thoughts run away with you. You're
being delusional.}

She couldn't say the rest of her words. Lobotomy---maybe it was possible.
After Shion disappeared, the Holy City shed mask after mask of artifice,
right before her eyes. Although she had only seen a small portion, what
Karan saw of No. 6 was not a Holy City; it was a remorseless
authoritarian city-state.

\emph{This city is trying to dominate people.}

They wanted to dominate without exception the minds, the bodies, of
everyone who lived in the city. They wanted to put their thoughts,
lives, and fates under relentless scrutiny, and dominate them.

Yes, it was like Yoming said. No. 6 devoured people. They tore through
any attempt to remain human, any soul, or will to resist, any wish, and
wolfed it all down. It was no Holy City. It was a rearing monster, gone
mad with desire for domination.

Had no one realized? Was everyone too fooled by their appearance of a
satisfactory and comfortable lifestyle to even notice the monstrous
figure? What stupidity\el 

Karan shook her head vigorously. These were not simply someone else's
problems. They were most certainly not.

"Karan, are you starting to feel ill again?" Yoming said with concern.
"You just fainted after all---you should rest a little. I'm sorry for
bringing up something like this."

Yoming looked sincerely apologetic. Karan shook her head firmly again.

"No, that's not it. I was just---remembering something."

"Hm? What?"

"Lili's asked me that before. Whether we're really happy or not."

Lili had once asked her.

"We're happy, right?"

It was quite a while back. It was after Karan had gone through the
struggle to open her bakery, and it was finally starting to operate
smoothly. Karan had murmured, \emph{hmm, well, I guess}, and cocked her head to
the side. She had been able to make baking, which she liked, into her
life's work. It wasn't much to live on, but at least she had an idea now
of how she and her son could make a living. Even after being revoked of
all their special privileges and being exiled from Chronos, they had
been able to acquire a stable life. It was during that time. Back then
she had no way of knowing that in a few years, a cruel separation from
Shion would be waiting for her. So in truth, if she was asked are you
happy, she could very well have nodded and said, \emph{why yes, I guess I am}.
Karan had indeed not thought of herself as unhappy at that time.

Karan's fall from Chronos to Lost Town didn't cause her much grief or
suffering. On the contrary, she was enjoying the lightness of her load,
having cast off her life insured of all amenities like food, clothing,
and shelter. Despite having to deal with treatment as a sub-citizen, she
was still within the walls of No. 6 as a resident of Lost Town. As long
as she didn't desire anything extravagant, she had nothing lacking in
her life. Clean water and food were easily accessible. Although
understaffed, there were medical clinics for Lost Town residents where
she could go to get examined. She had an abode that could withstand wind
and rain. She was free from any fears of malnutrition, starvation,
hypothermia, or genocide. Shion was by her side, and she had customers
who came to her bakery to buy her bread.

She was not unhappy at all.

She had not been able to agree promptly to Lili's question of whether
they were happy, not because of her own situation or state-of-mind, but
because of a shadow that had flitted across Lili's eyes. Perhaps it was
uncertainty. Perhaps Lili was uncertain, her emotions so unsettled, that
she had clung to the bakery madam, whom she loved and trusted.

"It's hard to say whether we're happy or not, in one word. There's a lot
of times where we're happy and we're not, when we're joyful or sad. Lots
of different feelings."

"Right?" Lili squeezed her fingers. "We have lots of different feelings,
right?"

"Right. You feel like that too, don't you Lili? Even during a single
day, sometimes you feel happy, and sometimes unhappy, right?"

"Yeah, I do. When I'm really hungry, and I get to eat your muffins,
ma'am, I feel happy. But when Mommy gets mad at me or when I get into a
fight with my friend and we can't say sorry and make up, I feel sad.
But\el "

"Hm?"

"But at school, the teacher says that everyone who lives in No. 6 is
happy. He says there's no one in No. 6 that's unhappy."

"You learned this in class?"

"Yeah. When the principal was saying his speech. He said outside of No.
6, the world is really tough and unhappy. And people die there every
day. They die because they don't have enough to eat, or because they
fight and hurt each other. He said people are like beasts, and they live
like beasts too. And compared to those people, No. 6 is heaven, and
everyone's happy."

By beast-like people, he probably meant the residents of the West Block.
It was such a scornful way to talk about people. To think that someone
involved in the education of children would call another human a
beast\el 

Karan knitted her brow. She crouched down, and looked Lili in the eye.

"But you didn't think so, Lili?"

"Hmm," Lili thought aloud. "I just felt kinda weird. Like this wiggly
feeling in my stomach. Because---because you know\el Mommy sometimes makes
a sad face because she's tired from work, or because we don't have
money. And Grandpa Saiton next door always looks painful because his
back hurts. So when he said everyone's happy, it just felt weird\el "

"And you didn't tell the principal this?"

Lili widened her eyes, shook her head vehemently.

"If I said that, the principal would be really angry at me. Sometimes
you get called to the office and they hit you with a whip."

"My goodness, with a whip! That's terrible\el "

"If you live in No. 6 and you don't think you're happy, it means you're
a bad kid. So they say, of course we should get whipped."

"\emph{Certainly not!}" Karan found herself saying shrilly. She placed a hand
on Lili's shoulder. "Lili, that's certainly not true. Not true at all."

"Ma'am\el "

Her heart grew restless. She could hear its fitful rustlings. She knew
she had to tell this young girl in front of her something important, but
she could not put it well into words. She felt frustrated at herself.

"Lili, you're still a child, and\el " She stopped. "No, even adults are
allowed to have all sorts of different thoughts. It's just not right if
everyone thinks and feels exactly the same, right? And---and---"

\emph{There are unhappy people in No. 6, too. Probably a lot more than I
think.}

It was something Karan knew first-hand. She had transferred from
Chronos, a place of chosen citizens, to Lost Town, a residence for
sub-citizens. She didn't think of that as any tragic fate, but she had
definitely seen with her eyes and experienced with her body the apex, as
well as the bottom, of the city-state of No. 6.

Indeed, there were unhappy people not only in Lost Town, but even in
Chronos---a place that was known far and wide as the ideal neighbourhood.
Yes, there were unhappy people, and many of them. But no one in that
area ever said 'I'm unhappy' out loud. Chronos had not a single person
who lamented difficulties with their household income, or those who
complained of physical ailments like Saiton. All residents were promised
a high and stable income, and they were in a position that granted them
access to the latest, most developed medical treatments at any hour of
the day. But yet there were still unhappy people.

"Whatever shall I do tomorrow?" she had heard someone mutter once.

She was an elderly lady who lived next door. However, "next-door" in
terms of Chronos was quite a distance because of the spacious yards
attached to each house. Periodically, gardeners from the city would come
to maintain the gardens (and also check up on and maintain the security
systems in the yard, which Karan didn't find out until much later), so
unlike Lost Town, where only a single wall separated one household from
the other, Karan wasn't accustomed to seeing her neighbours in person or
having conversations with them.

But Karan was on unusually good terms with this woman of over seventy,
and once in a while she would be invited over for tea. The woman's
husband, daughter, and grandchildren were all acknowledged as the
highest elites like Shion, and she was provided for and insured with
extremely favourable circumstances even compared to other residents of
Chronos. But despite that, she was neither arrogant nor condescending,
and often looked out for and lent a helping hand to Karan, who was
raising her son all by herself.

On that day, it was the same. On a sunny and temperate afternoon one day
in late autumn, the woman had invited Karan over for tea.

Smelling the fragrant aroma of black tea poured from the teapot, Karan
had been about to give an appreciative \emph{mmm} when the woman had mumbled
those words. Her voice was dry and brittle, like the foliage that danced
on the streets. It was dry, but heavy and gloomy.

"Whatever shall I do tomorrow?"

Karan slowly raised her gaze from the rose-patterned teacup, and stared
at the elegant, composed profile of the woman who had just spoken. The
words had reached Karan's ears, no problem. But the tone of her voice
clashed so much with the beautiful scenery, the lavish mansion, and the
fragrant tea, that she couldn't help but ask her to repeat.

"What was that?"

The elderly woman slowly let her gaze wander. Behind her ruby-studded
spectacles (almost solely a fashion item), her two eyes, set in the
wrinkles of her skin, blinked.

"I\el have no idea what I would like to do tomorrow."

"Do you mean you've got nothing to do?"

"I don't know\el what I want to do, Karan-san." Tears welled up in the
rims of her eyes.

"You don't know\el ?"

"There's nothing. It's just empty. And it makes me so afraid. I
especially despise mornings. They're utterly horrible. When I think that
it's the start of another empty day, I feel so terrified, so\el "

Karan, who had still been young, was perturbed by the elderly woman's
tearful face and her mumbled words. As if to prove that she wasn't
acting, the woman's shawl-clad shoulders were trembling.

"Ah---but---" Karan stammered. "As long as you're willing, I should think
you'd be able to do anything you like. So many things\el "

"Do you think so? I just have a feeling that it's going to be one empty
day after another until I die\el When I think about how I'll die
without having been able to do anything, I feel more fearful than
painful."

Karan rose out of her seat, and shook her head almost automatically.

"That's not true. Because, look---the decor of this room, or the way you
arrange tea---it's all so nice, and you're so good at it."

The elderly woman responded to Karan's awkward compliments with a serene
smile.

"You're a kind soul, Karan-san. But\el well, someday I suppose you'll
have a taste of the same fear I feel."

The pair of eyes behind the spectacles were not laughing at all. They
were like dark caverns. Karan remembered shivering. She had felt a chill
in this room, filled with extravagant furniture and maintained at
comfortable temperature levels all year long. The elderly woman's gaze
had been so vacant, so morose, that it had made her shudder. The woman
had plentiful time and wealth. Was she not in a position where all her
wishes could come true? Yet here she was, lamenting: how over-privileged
of her, how greedy\el Karan tried to mutter those words in her mind. But
both her heart and body shrank back from the morose and vacant look
before her. A despair enough to petrify someone was living behind those
spectacles, emitting a dull light. Karan drained her tea, and left
hastily. She remembered clearly how the dishes had clinked as she
replaced her cup on its saucer with trembling fingers.

Then not long after, on the edge of the changing seasons, the elderly
woman suddenly passed away. In her coffin and surrounded by the white
lilies which she always said she loved, the elderly woman with her eyes
closed had the same glowing skin as when she was living, and her face
was graced with a gentle smile. Karan felt like if she called her name,
the woman would answer.

"I've lived a very happy life. I'm thankful for everything about No. 6."

Those were her last words, according to the woman's daughter, who worked
at the Central Administration Bureau.

\standout{I've lived a very happy life.\\I'm thankful for everything about No. 6.}

"Your mother said this? Really?"

"Of course. Why wouldn't she? My mother lived a life lacking in nothing.
Wouldn't anyone think the same?"

"Well\el I was just wondering if you yourself were just under the
impression that\el "

"I?"

"Yes," Karan had said. "Have you ever thought that your mother may have
been unhappy?"

The daughter furrowed her brow, and a clear look of distaste swam in her
eyes. She gazed at Karan as if she were looking at a hideous beast, and
took half a step backwards.

"It's simply impossible that my mother could have been unhappy," she
snapped. "She has never spent a single day in that kind of state.
Wouldn't you know from common sense? I do hope you refrain from any more
rude comments."

She turned her back to Karan. Throughout the funeral, she kept her
distance. That was when Karan was certain that the elderly woman had
been unhappy. She had been struggling with her unhappiness that came
from being required to be happy---a life in which she was not allowed to
be sad.

\emph{Maybe\el }

Her heartbeat grew more frantic. In her mind rose the woman's face,
doll-like, surrounded by white lilies.

\emph{Maybe\el she killed herself---?}

She could not say it out loud. It was simply impossible for a resident
of Chronos to take her own life. It was unthinkable. They had been told
it was unthinkable.

Yet\el but\el if unhappiness existed despite the fact that it wasn't
supposed to, then couldn't there also be people who took their lives, on
the brink of despair with no other choice?

Karan tightly clutched her mourning gloves as the coffin was carried out
and whisked away to the cemetary.

\emph{I should have told Lili about the elderly lady.} Unhappiness was bound to
exist anywhere, whether it be Chronos or Lost Town. Karan felt like she
should have thought it out together with Lili---about why people were
unhappy; about how they could be happy again; what it was that they
could call real happiness. She should have talked it out with the little
girl---about her principal who forced happiness upon them; about the
elderly woman and her morose gaze; the pain of being whipped like
cattle. She should have reflected more intently on her own disquieted
soul, and the little girl's agitation. But Karan had not said anything,
and had done nothing.

"There are unhappy people everywhere. Just because he's the principal, I
don't think he has the right to say everyone has to be happy," she had
said, taking the most neutral way out. Just then, she had heard the
flour merchant calling from the back door with his rye and wheat flour.
Customers were trickling into the store.

"Thanks, ma'am. See you later."

And Lili had left. Karan pretended to be immersed in her work, and
pushed Lili, memories of her fear at the funeral, her thoughts of
happiness and unhappiness, clean out of her mind. She had not stopped to
think. She had even forgotten. Yoming had set his jaw and committed
everything to memory. But she had forgotten. She had never tried to
remember.

She herself was the fool, and no one else.

\emph{If I had been more wise, if I'd stopped to think a little harder, maybe
Shion wouldn't have had to go through what he did.}

It was not only Shion. Perhaps she had burdened Safu as well, with an
unfair and cruel fate. Karan chewed her lip hard.

\emph{Shion, Safu, be alive. Please, live on. Live to come home, and let me
apologize for my foolishness. Let me embrace you with these arms. Let me
beg for your forgiveness.}

She pressed the scrap of paper to her bosom, and prayed.

\memo{\nezumi}{Reunion will come.\hspace{1cm}Nezumi}

\emph{Nezumi, I pray to you. Please, let me see their faces again. Just one
more time.}

She heard Lili's tinkling laughter. It was lighthearted and carefree,
and punctuated with soft chirrups from the little mice.

\emph{Reunion will come.}

She murmured the words on the memo. She tried to hold back the tears
that were threatening to spill from her eyes. Crying wasn't going to
solve anything.

\emph{Right now, I can only send my prayers to you, whom I've yet to see.}

\emph{Reunion will come.}