% !TeX spellcheck = en_US

\chapter{Ring the alarum bell!}

\myepigraph{I gin to be aweary of the sun,\\
	And wish the estate o' the world were now undone.\\
	Ring the alarum bell! Blow, wind! come, wrack!\\
	At least we'll die with harness on our back.}{\emph{Macbeth}, Act V Scene V}

\lettrine{I}{ love you}\emph{, Shion. I love you more than anyone else.}

\myspace

Brains floated in the middle of the transparent columns.

Human brains.

How many? Ten, twenty, thirty\el perhaps more than fifty. There seemed
to be a light source at the base of the column, for the entirety of it
emitted a soft, white glow.

A scene he had never seen before. It was orderly, inorganic, and
sterile. Not a single stain marred the smooth floor. The chamber was
odourless and almost soundless. But that in itself was terrifying. Shion
felt that this scene was more terrifying than any he had seen until now.
He couldn't hear the tearful cries, the screams, or groans. There were
no corpses, no flowing blood, no faces distorted in agony. But this
scene here was so much more wicked than the picture of hell in the
basement that he had witnessed and burned into his memory.

Safu stood right inside this terrifying and wicked scene.

"Safu---"

Shion staggered as he tried to break into a run, and fell to his knees.
He had no strength in his legs. His heart pounded rapidly. His wounded,
bleeding, and exhausted body was crying out for mercy.

\emph{I can't go any further than this.}

He looked up. A stream of sweat travelled down his cheek and moistened
his mouth.

Safu still stood silently, gazing at Shion. She hadn't changed at all.
Nothing about her had changed: the length of her hair, her stature, her
unwavering gaze.

Lost Town, No. 6. They had made a hurried parting at the station. The
Safu he had seen then was standing in front of him now.

She didn't look worn out. She didn't look wounded.

"Safu\el you're safe." \emph{You're safe. You managed to stay safe. You
managed to live. We were able to see each other again, alive.}

\emph{I love you, Shion. I love you more than anyone else.}

Her confession had reached him through his ID card. A cutting-edge
communication device had mediated these flesh-and-blood feelings.

Her voice was coming back to him.

"Shion, you came." Safu's voice. A little low for a girl's, yet always
crisp and taut. He missed it.

It moved his heart. It squeezed his chest.

\emph{Oh, how I've missed it.}

\emph{Safu, we've been separated by a pretty long distance, haven't we? I feel
like we haven't seen each other for a century.}

"I knew. I believed you would come\el " Safu smiled. Then her face
crumpled into an expression both happy and tearful. "I was waiting all
this time. Waiting was all I could do. I could only wait for you
here\el "

"Mm-hmm."

Shion raised the upper half of his body, and took a deep breath.

"I knew I had to come sooner\el I'm sorry, Safu."

Safu shook her head, and cocked her head to one side. She blinked, and a
faint agitation crossed her eyes.

"Shion, your hair\el "

"Huh? Oh, this hair. Well, a lot of things happened, and\el I'll take my
time and tell you everything later." \emph{I'll tell you everything about what
I experienced while we were separated. There are so many things I want
you to hear, to listen to. One evening wouldn't be nearly enough to
cover everything.}

"You must have gone through so many hardships\el more difficult than I
can imagine. I'm sure that getting here wasn't the average stroll in the
park, was it? But you still came. For me\el that's more than enough.
Thank you, Shion. Thank you so much."

"Like her dying words or something," Nezumi muttered from his spot
beside Shion. It wasn't a cold voice. But it was flat and emotionless.

Safu's eyes moved slowly in response to the mutter, and fell on Nezumi.

"You must be Nezumi\el "

"Yeah."

"Nice to meet you. I've always wanted to take a look at you. I wanted to
know what kind of person you were."

"Here I am. Usually, I look better. This isn't the state I'd like a lady
to see me in, but unfortunately I didn't have the time to wash my face
or change into my good suit. Do forgive me." Nezumi also had his gaze
fixed on Safu. He stared at her without blinking.

"Safu, I have something I want to ask you."

"\el Alright."

"Are you the one who controlled the main computer to lead us here?"

There was no answer from Safu. A moment's silence passed. Shion looked
up at Nezumi, still on his knees.

\emph{Safu, control this Facility's computer? There's no way she could have.}

He swallowed the words just about to leave his mouth.

It couldn't be. But that was the only possible explanation.

Nezumi's grey eyes slid slightly aside.

"Yeah. That's the only explanation." His words tracing Shion's thoughts
almost exactly, Nezumi continued in an expressionless voice. "You said
so," he said to Shion, "you said someone was calling. Thanks to that
someone, we were able to get this far. Granted, this isn't the kind of
place I'd be terribly excited to see. But that aside, I can't think of
anyone else who'd be the precious sort to send us welcoming emissaries
from inside the Correctional Facility. She's the only possible person."

He had no choice but to nod. Shion himself had been feeling Safu calling
him. He had been urged on by this voice, and been led thus far.

But if that was the case, that meant Safu was somehow involved with the
core of the computer system.

But how? How was it made possible for her?

"Shion." Only Nezumi's lips moved as he called Shion's name. "How long
are you planning on sitting there for? You can wait for as long as you
like, but there won't be any coffee coming."

"Ah---"

Of course. What was he doing? He'd come this far: what was he doing
squatted on the ground?

He willed strength into his legs, and stood up. His feet were unsteady.
He managed to dig his heels in, but barely. Nezumi never tried to reach
out to him. Shion also had no intentions of clinging to the figure that
stood beside him.

They were wounded, exhausted, and had spilled the same amount of
blood---no, it must have been much more arduous for Nezumi.

Clinging was the last thing Shion wanted to do. Even if he were to lean
on Nezumi and manage to stand, taking the next step would probably prove
immensely difficult. If he could stand with his own strength, he would
be able to advance with his own strength as well.

Safu was still watching them. Her hands were clasped tightly together as
if in prayer, and she remained still.

"I wasn't me," was Safu's short answer. "I don't have that kind of
power."

Nezumi's brow furrowed slightly.

"I only thought it\el I only kept thinking in my heart that I wanted to
see Shion."

"Then who is it? Who brought us here?"

"Elyurias."

"Elyurias!" Nezumi and Shion cried in unison.

Elyurias.

They had heard the name from Rou, the elder who had long lived in the
underground realm. He was a man who had been involved in the foundation
of No. 6 as a city-state, and had lost both his legs to the parasite
wasp as its first sacrifice. He was an old and close friend of Shion's
mother, Karan.

Rou had said it.

\emph{Elyurias was a great sovereign. No, I am sure she still is. She probably
still reigns even now.}

Shion ran a hand over his pocket. The chip that Rou had given him was in
there. Once he rescued Safu safely from the Correctional Facility, he
wanted to take his time to decode it thoroughly. Here lay the answers to
the puzzle. The mystery of No. 6. The mystery of the underground realm.
And more than anything, the mysteries surrounding Nezumi. Answers
existed to these questions. There must also be considerable amounts of
information loaded onto the chip concerning Elyurias, the queen.

His heart raced slightly at the thought. But he had forgotten cleanly
about the chip after stepping into the Correctional Facility. He hadn't
even recalled it once. They had not had the time. He had been running
constantly, pushing the limits of his mind and body. One misstep, one
moment of decision could invert life and death. He had to survive even
one second longer---survive and move forward. This thought had occupied
his mind completely.

Elyurias.

To think that he would hear this name coming from Safu's mouth.

"Do you know Elyurias?" Nezumi's tone wavered for the first time. A
faint agitation crept into his voice.

"I don't. But\el she was the one who led you here. She awakened me
completely\el she taught me the truth."

"The truth," Nezumi repeated, as if to cross-examine her. "Truth, huh.
Safu, why did Elyurias or whoever it is invite us here?"

"I don't know."

"Where is Elyurias now?"

"I don't know\el but---"

"But?"

"But I think she must be\el very close. I have a feeling she is."

"Is that just your intuition, or---"

Safu shifted on the spot.

"Bombarding me with questions, aren't you, Nezumi?"

"I won't get any answers if I don't bombard you. We haven't come here to
have a leisurely chat. There's a pile of things we have to know, that we
ought to know. If you could just give us the answers, that's efficient
for all of us. Don't you think, Safu?"

"You're right. But I can't answer even half of what you want to know.
You're not looking for the kind of answers\el that you can obtain
easily, right?"

"So you're telling us to go out and search for ourselves if we want
answers." Nezumi exhaled. "Which means, to sum it up, you don't know
anything."

"I don't know anything about you, Nezumi. But I do know\el about Shion."

Safu exhaled as well. "Because I wished it. I wished strongly that I
would get to see Shion. Elyurias heard my wish. She told me\el "

Safu's lips trembled.

"I will grant your wish. I will bring you to the person you most want to
see\el that's what she said. And she didn't break her promise."

"So Elyurias can freely control the computer system?"

"I don't know. I don't know who she is, or where she is, or why she
started to talk to me all of a sudden\el I don't have a clear idea\el of
anything."

"She spoke? To you? From beside you?"

Safu refuted the suggestion.

\emph{No, not like that.}

"She\el spoke from inside me. When I was falling asleep, she called to
me directly."

"Wait, what do you mean by---"

"That's enough." Shion took hold of Nezumi's arm. Nezumi's slid his gaze
languidly from Shion's fingers to his face.

"It's alright, that's enough, Nezumi. We're not here to have a leisurely
chat, or to interrogate Safu."

\emph{We've come this far. Now we have to escape.}

\emph{There were two people up to this point, and from here on there will be
three.}

Nezumi continued to stare at Shion, and blinked.

"'Stand not upon the order of your going, but go at once,' huh. I
don't know how easy it'll be for us compared to the lords going home
from a banquet."

"That's awfully pessimistic of you."

"I'm careful. I don't do the naivety thing. It's probably known all over
by now that we're on this top floor. Scary old men might be storming up
from downstairs right this moment."

"Nezumi, there's only one route that leads here, and that's the elevator
we just came with. No one can enter unless that elevator moves. All the
facilities in this building are programmed into the computer system."

"And what makes you so sure that the system's gonna stay on our side?
Are you saying you can see when and where our situation is gonna
change?"

"Well---"

He was at a loss for an answer.

"We can't even put a finger on who or what this Elyurias person is.
Don't forget that. Think before trusting someone whom you don't even
know the truth about."

Nezumi was right. Neither Shion nor Nezumi had any definite information
about Elyurias. What they had was what Rou had told them, and what they
had heard from Safu.

He knew they could not cling to ambiguous things. They could not make a
blindly positive interpretation. It took firm resolve to believe in
another person. Trust was hollow without resolve. It was a fake,
papier-mache indulgence masked with a thin wrapper. And even a
millimetre of indulgence was enough to cost him his life.

"Safu," Shion spoke to the girl in front of him. "Could you take us to
the main computer\el the mother computer, it might be called\el the core
of the system?"

Safu nodded. There was no time for hesitation, anxiety, or prolonged
thought.

"Follow me." She turned her back, and started to walk.

"Let's go," Shion encouraged. Nezumi showed a slight hesitation.

"Can we trust her?"

"Safu?"

"Yeah. Can we just follow her innocently like this? Can you say for sure
that she won't betray us?"

"I can."

"And you're absolutely sure?" A cold smile played on Nezumi's lips.
Declaring absolute trust in someone was not a virtue for Nezumi; it was
closer to foolhardiness.

"Nezumi, I have three people I can trust one-hundred percent, no matter
what happens to me. Those people are Safu, my mother, and you."

\emph{I can believe them, no matter what. Believing has supported me. I don't
think it's naivety. A simple and superficial trust will corner a person
into trouble one day. But someone who can't trust anyone sincerely is
fragile. The only foothold they have is an unstable one on sand.}

\emph{I can believe, no matter what happens. I can keep on believing to the
end. That's resilience---it can't be anything else.}

"If\el If any one of these three were to betray me, then I would resign
myself to it. Even if I were to lose my life over it, I wouldn't have
any regrets. When I start doubting Safu, or my mother, or you\el when I
stop being able to believe in you, that's the same as annihilation for
me."

The smile vanished from Nezumi's face. The colour in his eyes darkened.
It made Nezumi look like someone in endless thought in search for the
truth, or a lost man wandering at his wit's end.

"Shion, you don't feel it?"

"Feel? Feel what?"

"Something off."

"Off\el about what?"

Nezumi watched Safu's back in silence.

"Alright, fine, we'll do as you wish. It seems like the only path open
to me is the one that follows yours, anyway. Took me long enough to
realize it, but I guess I have to steel myself if I want to get
anywhere."

"Does that mean you trust me?"

"Don't get carried away, idiot," spat Nezumi as he began to walk. It was
hard to tell that he had a bullet wound in his leg. Shion couldn't help
but drag his own foot. His wounded leg felt heavy, as if it were not his
own.

They moved further in amongst the transparent columns with Safu in the
lead. Some moments later, they hit a wall. It was white with a faint
tint of yellow, like the floor. The wall split open silently as Safu
stood in front of it.

"The inner chamber of the palace, huh?" Nezumi licked his lips.

Shion had opened his eyes widely, almost unconsciously holding his
breath.

It was a white, brightly-lit room. It was not particularly spacious. The
size was about the same as a floor or a living room of an average-sized
house in No. 6. The lights glowed brilliantly, illuminating every corner
of the room, which had no windows or furniture.

A column penetrated its centre. It was a size thicker than what he had
seen moments earlier. There was no brain floating in it, but there was a
pale silver sphere. It was covered in innumerable small projections, and
the tips of those projections blinked with lights every few seconds.
Some were blue, some were crimson, and yet others glowed a deep red.
Thin, clear tubes extended from some of the projections and spread
upwards in a tangle. It was too dark beyond that to see any further.

"This is the Mother."

"This is the Mother?"

Safu and Shion's voices overlapped.

"There's an identical model in the Moondrop. That one's the Grandmother,
and people call it Grandma. A research institution that was first
stationed in the Moondrop broke off as an independent organization and
moved to the Correctional Facility. That was because a version of
Grandma --- smaller, but with the same functions --- was complete. The
Mother. That was one reason."

"In the Correctional Facility, they could easily get their hands on test
subjects for their experiments. Human test subjects, to be exact. That
would be the second reason, right?"

Nezumi huffed.

"Either that, or they were starting to need larger quantities of them.
There was no way to acquire humans in bulk to use as lab rats. Not in
No. 6. Bringing in a large number of people from outside would also be a
hassle. But here, in the Correctional Facility, there would be no
problem. People were overflowing in the West Block. They only had to
switch the purpose of their Hunt, which was population control, to
securing test subjects. It can be for the granny or the mom, but I think
that might be a more likely reason for their little move than the
computer, don't you think?"

"You may be right." Safu closed her eyes for a short while. Once the
girl's black eyes disappeared from her bloodless face, she looked like a
doll.

"The Correctional Facility was\el always a place for human
experimentation. Many experiments involving living human bodies were
conducted over and over. Thanks to that, No. 6's medical technology saw
leaps and bounds in development\el And both you and I, Shion, received
the full benefits of it\el "

"Yeah\el that's right."

Shion turned back to Nezumi and asked him a question. His voice didn't
sound like his own, it was so raspy and unpleasant to the ears.

"Nezumi, that room\el that room with the passageway that led from the
underground chamber\el "

The bottom of the elevator had opened, fast becoming a gallows, and the
people were dashed to the ground along with their screams. The
underground chamber had become the first page in the book of hellish
horrors, and a narrow passageway from there had opened up into a room
that looked nearly like a cube. Nezumi had called it a "temporary
resting place".

"Yeah. Have you finally noticed? The structure from the underground
chamber to that room is designed to select lab rats. The people who were
able to reach that room were those who could bear the impact from
falling from the elevator, and escape on their own using the blinking
lights as a guide. They're lab rats with above-average strength in both
body and mind, and with a decent amount of intelligence. Superior lab
rats. If you're going to use lab rats, you might as well get the
stronger, more resistant ones. That's what they thought."

Safu made a small choked noise.

The eyes of a certain man rose in the back of Shion's mind. He did not
know the name nor the upbringing of the man who possessed those eyes.
The man had been struggling, unable to die, and had clung to Shion in
his suffering, and his eyes---his eyes were coming back to him.

Nezumi had been the one who saved that man. He had given the man a
peaceful death. Nezumi had called it murder, not salvation. Shion didn't
know. Like before, even now, Shion struggled to grasp the answer.

The only thing Shion could answer for certain was that that man was a
living human, not an experimental lab rat.

"Do you remember there being a door in that room?" Nezumi asked him.
Shion remembered. The room had been illuminated then, though somewhat
dimly. The light had stung at his eyes which had been used to the
darkness. He had seen a grey door beneath that light. He remembered.

"That door is where they come to collect the survivors, but it doesn't
lead into the Correctional Facility. It's from when the research
institution still used to be at the Moondrop. People were let out
through that door, then embedded with identification chips like
prisoners, and then sent to the city hall --- the Moondrop. The chip is a
safety measure in case someone escapes. But by placing the research
institution right inside the Correctional Facility, they removed all of
that extra work. Efficient, indeed, don't you think?"

"Identification chip\el " Something flared up in his mind. "Nezumi, you
got out through that door four years ago, didn't you? And you escaped
while you were being escorted to the Moondrop."

"Four years ago, huh\el it was a stormy day. I mark it down on my
calendar as the day I met a certain weirdo who opened his window in the
middle of a rainstorm. But now isn't the time to be taking a walk down
memory lane. Safu, you know the truth about the Correctional Facility.
Not only that, but about No. 6 itself. And Elyurias is the one who told
you about it, right?"

"Yes. She taught me the truth behind No. 6, the so-called Holy City, the
Utopia, even. \el But Shion, you weren't just taught. You saw with your
own eyes. You heard with your own ears."

"Only a part of it." Only a part of it. There were still an enormous
amount of things he didn't know, hadn't realized yet, still had to
ponder and think about.

Shion inhaled. He felt a faint pain deep within his chest. It wasn't a
physical pain. It was a small twinge inside his mind that had developed
unbeknownst to him. It throbbed every time he thought about No. 6.

No. 6 was no utopia. It was a ruthless and cruel city-state. For its
peace and prosperity, it shunned no kind of brutality. But, but, but\el 
Shion inhaled again, and pressed a hand to his chest.

What was No. 6? Was it not a country built by human hands?

\emph{I want you to believe this much. We tried to found an ideal city here, a
Paradise free of war and poverty\el where we could have gone wrong, I
don't know\el }

Rou's words. He was sure they weren't lies. No. 6 in its infancy had
still been based on the ideology and will of human beings.

A society without war, so that everyone could be happy.

Where did we go wrong?

Rou's thin, trembling voice and his words left a mark in Shion's heart
like a hot brand.

\emph{Where do people stray off the path? When do they begin to obey their
greed rather than their ideals? Or are ideals just prone to morphing
easily into greed? If so, then the same thing will happen in the future.
Even if No. 6 were to fall, a second, a third Holy City would be born.}

\emph{Where did we go wrong?}

\emph{Are human beings capable of creating a country without going astray?}

Shion shook his head. Now was not the time to be uncertain over his own
questions. He was not going to flee. He would face them squarely in the
near future. But now, he had to focus on the single task of overcoming
the wall before him.

He drew closer to the Mother.

A thin plastic board which looked like a control panel was attached to
the front of the round column. There were seven keys in each column and
fourteen in each row. They were white, marked with no numbers, letters,
or symbols. He tapped a key to test it out, but there was no response.
He let his fingers race across the control panel, typing whatever that
came to mind.

"How is it?" Nezumi peered at Shion's hands. "Does it look like you can
do something about it?"

"It's not working."

"Don't give up just yet. It shouldn't be hard to have Mama or Grandma in
the palm of your hand with your brains and skills. I think you're quite
a womanizer in that sense."

"You're expecting too much from me, Nezumi. I'm no match against her.
Forget coaxing her to like me, she's already elbowed me away because she
doesn't want anything to do with me."

Nezumi's eyes narrowed, and the dark grey light in them condensed.

"So the Mother didn't take a liking to you\el are you sure you can't do
it, Shion?"

"I can't. There seems to be a special authorization system, and you
can't get close to the Mother unless you clear it. It's too bad, but\el 
there's nothing more I can do."

"Mama is so strict. I can't help but sigh," Nezumi said, clicking his
tongue instead.

"Safu, how about you?"

"I can't, Shion. No one can can go near Mother, save one person."

"One person\el the mayor?"

"No. This person has no name for his profession. He created this
research institution, and presides over it\el he thinks he is the true
ruler of No. 6. The Mother is his creation, and it'll only obey him.
That's how it was made."

"How about this woman, Elyurias? Doesn't she have full control over the
Mother? That's why she was able to open and close the barriers when she
wanted, and operate the elevator, right?"

Nezumi and Shion looked at each other.

\emph{Yes, Elyurias. Maybe she can\el }

"Safu, does Elyurias still speak to you? Can you speak to her from your
end?"

He took one step closer to Safu.

Safu took one step back.

Now, Shion finally felt "something off", as Nezumi had mentioned
earlier.

\emph{Why doesn't she come closer?}

Safu always kept a set distance, and didn't try to narrow that gap.

"Safu?"

"Don't come!" Safu's words sounded close to a scream as they issued from
her lips. Shion watched the girl recoil, and felt his heart palpitating.
A flurry of unease started up in his chest.

\emph{Why?}

"Why are you running away, Safu?"

"Don't come close. Please. Shion\el "

A tear suddenly trickled down Safu's cheek.

"I was waiting\el waiting all this time. I wanted to see you, so, so
much\el that was all I hoped for\el "

"And we did see each other. I'm right in front of you, right now. I came
to save you and get you out of here. We came to escape the Correctional
Facility together."

He stepped forward and offered a hand.

"Safu, let's get out. Out of this building. Let's go together."

Safu jerked her chin up. She was chewing her lip in a desperate attempt
to contain her shaking. She shook her head, her face still drawn.

A gesture of rejection.

"Why!? Why are you refusing us?"

He tried to restrain himself, but he could not. His tone turned rough to
match the rise of his emotions.

\emph{Safu, let me hold you. Hold you with my own arms. I want to embrace you
to make up for all those years we spent apart. We've finally been able
to see each other. Words of every kind are whirling inside me, words to
say to you, to tell you, to apologize to you. Like a muddy stream. Like
a howling wind, they're ringing out.}

\emph{But why do you refuse? Why are you trying to flee from the hand I'm
offering you?}

"Safu, I---"

He was grabbed by the arm.

"Stop." Nezumi's fingers dug deeply into his skin. "Stop it. Don't get
any closer. Do as she says."

"Nezumi, even you---?"

Nezumi beheld Shion silently, still holding his arm. His gaze stopped
Shion from saying anything more. Shion swallowed the rest of his
sentence. His unspoken words became a muddy flow, a swift wind that
further agitated his heart. His breathing turned erratic from anxiety
and uncertainty. It was an entirely different type of unrest than what
he had felt at imagining the difficulty of all three of them escaping
the Correctional Facility together.

His body froze up at this unidentifiable fear.

"Safu, what do you want?" Nezumi asked. There was no hint of aggressive
pressure. His voice was soft, deep, and beautiful. "What do you want us
to do?"

Safu's expression relaxed somewhat.

"\el Will you grant my wish?"

"It's my command."

Safu drew a slight breath.

"Destroy the Mother."

Nezumi's fingers tightened their grip, but in the next instant, fell
from Shion's arm. Only the sensation of his strong grip remained.

"You're telling us to destroy this computer."

"Yes."

"I see\el well, if we could do that, that'd be more than I could ask
for. If we could, that is." Nezumi fished out a coin-shaped microbomb
from his jacket pocket, and held it between his fingers.

"If we set this guy to maximum power, it should be able to blow apart
the computer, no problem."

"It won't work."

Shion lightly touched the cylindrical column.

"The computer itself might be fragile, but the problem is with this
column. It's made of special plastic. I'm pretty sure that even a
missile hitting this thing wouldn't make it budge. It's like a glass
ball encased in a durable capsule. It's impossible to destroy it with a
coin bomb."

"You're a hundred percent sure."

"Yeah."

"A hundred percent impossible, and zero percent possible. Then we've got
nothing to go on."

"I can open the column."

Nezumi's gaze hardened at Safu's words.

"You can open the door to the Mother?"

"Not me."

"Elyurias?"

"Yes. She can do it. I'm sure she'll open it for you."

"If she can do so much already, it should be easy enough for her to stop
the Mother itself. You don't even need to rely on us."

"It needs will."

"Huh?"

"She said\el there needs to be human will."

Nezumi and Shion looked at each other blankly for a second or two.

"There needs to be human will in order to destroy it," Safu repeated.
She was like a medium announcing an oracle. Nezumi shifted uneasily.

"Those are Elyurias' words?"

"Yes."

"So she's saying she'll help, but the final decision has to come from
our will."

"Yes."

"But that means\el " Nezumi trailed off. Shion was nodding. He felt like
he had heard clearly what Nezumi had left unsaid.

\emph{That means Elyurias isn't human.}

It was probably true. He couldn't imagine a human in the flesh able to
manoeuvre through such a tight security system and infiltrate its
information routes, except for "him".

Elyurias wasn't a human. Then, what was she?

A god? A demon? A spirit of nature? Could she be---

"There needs to be human will in order to destroy it\el " Nezumi repeated
Safu's---no, Elyurias'--- words.

Safu closed her eyes, and murmured. "Humans are the only ones who
wilfully destroy things. It is something only humans can do\el so only
humans can destroy the Mother."

It was almost like an incantation.

Shion felt a chill.

Shion knew Safu as a person of frank speech, with a very strong sense of
reality. She could speak of hopes and dreams in realistic terms, not
fantastical ones; but reality did not bind her too strongly, for she
could still have hopes and dreams without being hindered by it. She was
sensitive, but not over-sensitive. Her mind was like a straight young
tree. It was upright, yet flexible.

She wasn't the kind of girl to repeat herself in a muffled murmur like
this. She was definitely not.

"Fine. We'll take it on." Nezumi's voice made Shion's eardrum tremble.
He was supposed to be used to hearing his voice, and yet it hit his
earlobes more vividly than ever.

Safu opened her eyes.

"\el Will you grant it?"

"If that's your wish."

\mybreak

"Thank you. I am grateful." Safu clasped her hands, and bowed her head.

"I don't need any thanks. Destroying the Mother is like shooting the
Correctional Facility through the heart. I could have wished with all my
might and still not gotten this opportunity. It's worth a try, if this
column will really open and expose the Mother, even for a moment."

Nezumi's eyes glittered. It was like the glitter of a finely-sharpened
knife.

The control panel lit up without warning. Words emerged in the air.
Nezumi gave a short whistle. He placed his fingers on the control panel.

"Unlocked, unlocked, unlocked\el heh, a miracle transformation from
haughty queen to meek lady. Now even I can handle her."

Shion's gaze was focused intently on Nezumi's fingertips. Every time,
and at any time, he couldn't help but admire those graceful movements.
To Shion, those fingers seemed to play a sweet melody, or breathe life
into a lively rhythm.

Every time, and at any time, he couldn't help but admire him\el But
this time, his heart was not drawn as strongly as usual.

The restless sounds of his heart refused to disappear. Instead, they
echoed even more strongly.

Nezumi's fingers stilled. A silver thread suddenly appeared in the
centre of the column. One, two, three, four. The silver threads
intersected to form a rectangle.

"The door," Nezumi said. "All you have to say now is 'open sesame'."
Perhaps even he was tense; Nezumi's voice was low and somewhat
heavy-sounding.

"Wait." Shion grabbed Nezumi's wrist. He could feel the other's body
heat and pulse on the palm of his hand. "Just wait for a second."

A shadow crossed Nezumi's eyes. A breath's length of silence.

"Shion, we don't have time to be wishy-washy and hesitant."

"I know. But wait, please\el Safu."

Safu's head was still bowed. Her shoulders clad in her black sweater
were trembling.

"Safu, you still haven't answered my question. Why are you refusing us?
Why aren't you coming any closer?"

"Shion\el "

"And that sweater\el your grandmother hand-knitted that, didn't she? The
last time I saw that was a long time ago. I probably wasn't even ten
then."

"You're right." Safu broke into a sudden smile. "You were the one to
speak to me first. You said it suited me. I was happy\el so happy.
Everyone else was laughing condescendingly at my hand-knitted sweater.
They were saying that you'd only find a wool sweater in a museum these
days. But you didn't laugh. You\el only you were loyal to your own
feelings and emotions, and to others, too. Shion\el I was able to meet
you in that bleak\el even lonely\el world of elite education. And that,
I think, is very---"

"Stop!" Shion overran Safu's words. "Why are you talking about past
memories? That's not what I want to hear. What I want to say is: why are
you still able to wear a sweater you got when you were ten? You've grown
taller since then, and your frame has changed, too. There's no way you
should be able to wear it. Or is that a new sweater that looks exactly
the same? But\el "

"I wanted you to remember." Safu interrupted Shion this time. "I wanted
you to remember me. You said this suited me\el so I wanted you to
remember me wearing this sweater."

"Remember? Are you telling me to turn you into a memory? Safu, what're
you talking about? You're not planning to come along with us?"

"Shion, leave it at that." Nezumi grasped his arm again. This time, he
held fast and yanked. It was enough power to make Shion stagger.

Shion tripped, and bumped into Nezumi. Nezumi did not budge.

"That's enough. This is as far as it goes."

"A far as what goes?"

"Don't corner her to distract yourself from your own uncertainty. That's
a cowardly thing to do."

Shion felt himself sweating. Nezumi's gaze stabbed at him.

"Me\el cowardly\el "

"Shion, you know already, don't you? There's no way you couldn't have
realized. And if you have realized\el don't avert your eyes from the
truth. Averting your eyes and running away isn't going to solve
anything. Nothing will change, and nothing will return to the way it
was."

It will solve nothing. Nothing will change. Nothing will return to the
way it was.

It was difficult to draw a breath. The sweat stung in his eyes.

"Shion, don't run away. At the very least, not now\el you can't run away
now."

He blinked. He caught Nezumi's gaze. He turned his head, and glanced at
Safu.

"\el You're saying she's not real\el that she's an illusion."

"She's what the Mother is showing us: a virtual reality. Your friend
doesn't exist in reality."

\emph{Doesn't exist in reality. What is that? What do those words mean?}

Shion was close to screaming. Terror welled up from the core of his
body. Safu had not run into his outstretched arms. She had not even
tried to touch Shion's fingertips.

She had not been able to. She was neither able to embrace nor be
embraced.

\emph{Doesn't exist in reality.}

\emph{An incorporeal}

\emph{~~~~~~~~~~~~~~~~~~~~~~~~~~~illusion.}

An incorporeal illusion.

Nezumi's tone became hurried, though only slightly. "At first I thought
it was a trap. But I changed my mind when I realized there would be no
point in setting a trap for us now. If it wanted to kill us, it had
hundreds, thousands of opportunities to do so. It had a reason to keep
us alive and bring us here. The Mother went as far as to borrow Safu's
body because it needed to tell us something\el that's what I was
thinking. What I didn't expect was that it would send us on the task of
killing the Mother itself."

"The Mother\el " Shion glanced at the sphere covered in protrusions.
"It's not the Mother," he shook his head. Nezumi's fingers loosened. "If
the Mother had created the virtual image, it would have recreated it
true to Safu. It wouldn't take the trouble to pull up the black sweater
from Safu's memories. Computers don't have emotions. But Safu chose that
sweater out of her own will. It wasn't the Mother\el Nezumi, the Mother
isn't the one showing Safu to us\el it's Safu herself."

"So Safu is using the Mother to project herself?"

"Yeah\el isn't that right, Safu? Or is this Elyurias' doing, too?" It
sounded so unlike his own voice. Like a cowering beast baring its fangs,
desperately raising its voice in aggression. That kind of growl. Twisted
and ugly, and fierce but intimidated.

"Yes\el Elyurias wakened me. Before then, I felt like I was drifting
through a dream\el just floating\el Elyurias awakened my consciousness,
and taught me what I could do. I\el can't overrule the Mother. But I can
use part of its functions\el that's all I can do."

"Where are you? Where are you in reality?"

"Nowhere." Safu's voice turned strained. "I don't exist anywhere
anymore."

"That's absurd. Then who made you, standing in front of me like this?
Didn't you?"

"I'm not here, Shion. I've already\el "

Safu took a step closer. Shion also advanced. He extended his arm
straight forward. It touched nothing. His fingers had reached Safu's
shoulder, but there was nothing there. Moments ago, he had felt Nezumi's
body heat and pulse. That warmth and movement was proof that he was
alive.

"I wanted to say good-bye to you. I wanted to say thank you. I was happy
all this time\el because you were there."

Safu looked up at Shion. A defiant glint shone in her eyes. "I loved
you."

"Safu---"

"That's my truth. It doesn't matter what you think of me. I loved you,
and only that is the truth."

\emph{Oh, that's Safu}, Shion thought. Firmly-grounded strength, a beautiful
resilience like that of a bird in flight: that was Safu.

"If I hadn't met you, I wouldn't have known what it was like to yearn
after someone. I would never have known what it meant to love\el I'm
glad I was able to know. I was born, and I was able to meet you. I don't
regret a single thing. Hm, well, that might be a little bravado. You did
tell me once that I had a bad habit putting on a brave face."

Safu's fingers touched Shion's cheek. He didn't feel it on his skin. But
he definitely did feel that Safu's fingers had touched him.

"Shion\el you think so, too, don't you?"

Safu threw a glance over Shion's shoulder at Nezumi, who was standing
behind him.

"You feel the same way I do, don't you? You're glad you were able to
know. You wouldn't be able to live anymore without knowing what yearning
and love is like."

"\el Yeah." \emph{You're right, Safu. I know. I came to know No. 6's true face,
and the fact that No. 6 existed within me, too. I came to know what it
was like for my heart to feel moved for someone, to yearn strongly for
someone. I can't go back to when I didn't know. I don't want to go back.
I would never want to go back to when I lived peacefully, knowing
nothing.}

Shion clenched his hand into a hard fist to repress his shaking. But
even his fist began to tremble.

"We don't have to go back. There's no need to. Safu, we just need to
start off from when we do know. We can start off right now, from this
place."

\emph{It's a starting point. A beginning, not an end. Right, Safu? We can go
on living together. Together\el }

His eyes fell on the tubes coming out of the Mother.

\emph{What is that connected to?}

\emph{What are those tubes for?}

"Please," Safu said, looking intently at Nezumi. "Destroy the Mother."

Nezumi didn't try to avoid Safu's gaze. He met it silently, and nodded
his assent. Safu breathed a sigh of relief. It was a breath of real
relief, from the bottom of her heart.

"Thank you so much\el "

"I'll fulfil the promise. I never break a promise made, no matter what
it is."

"Yes\el I know. You're that kind of person, aren't you?"

Nezumi faced the control panel again.

The section framed by silver lines glowed faintly red, and slid to the
side.

The door had opened.

Nezumi plunged his arm into the opening without a second of hesitation.
The control panel prevented him from leaning forward any further. The
Mother was out of reach by a very small distance.

"Tsukiyo."

A black mouse poked its head out from out of the folds of superfibre. It
looked about, then scurried swiftly up to Nezumi's shoulder.

"I'm counting on you."

Nezumi held out the coin-shaped bomb, and Tsukiyo took it in its mouth.

"Nezumi, wait, Wait, please!"

"Can't," Nezumi said flatly. "I'm going to destroy the Mother. I'm not
going to wait any longer."

"Don't. Wait, please. Wait. Let me check what's on the other end of
those tubes."

"There's no need."

His gaze collided with Nezumi's.

"\el Are you saying you know? Where Safu is\el and what's on the end of
those tubes\el "

"You should know, too. You saw it, after all."

It?

The expanse outside this room. It was like a cemetery with rows of
transparent gravestones. Gravestones, or coffins? A burial vessel, each
one with a human brain inside.

"Go."

Tsukiyo dashed off at its master's command. It leapt energetically
toward the Mother, and landed on top of it.

"Alright, good. Now wedge it right there."

Tsukiyo's movements were swift and smooth. It wedged the coin bomb
between two projections, lifted its head, and twitched its nose toward
Nezumi as if to wait for further orders.

"Good job."

Tsukiyo hopped into Nezumi's open palm. As he withdrew his arm, the door
to the Mother closed in the same silent way that it had opened.

Shion watched the events unfold before him stock-still, rooted to the
ground.

Nezumi's eyes looked past Shion.

"Done. Time limit is three minutes. That's the longest I can set the
timer for."

"Three minutes\el get away, quickly." Safu's tone and gaze tensed. Shion
looked from Nezumi to Safu.

"If we're going to escape, you're going to be coming with us."

"Shion, how many times will you make me repeat myself? I can't go. You
and Nezumi escape together."

"Safu."

"Go. You don't have a second to waste. Hurry."

When they were students, they had been required to present research for
their assignments once a month. When it was Safu's turn to present, some
students with the same research topic had made noise and disrupted her
on purpose. Even before Shion could stand up to admonish them, Safu had
looked straight at those students and thrown a sharp remark.

"You should be ashamed."

The boy who had been at the centre of the noise-making stood up, and
scowled exaggeratedly. "We should be ashamed? Are you insulting us?"

"I have no intention at all of insulting you. But regardless of the
content, listening to others' research presentations until the end is
common courtesy at the least, is it not? Even a three-year-old could do
it. But you can't. Something to be ashamed of, isn't it?"

Applause rose from various spots in the classroom. The boy bit his lip,
and resumed his seat in silence.

Her slightly flushed cheeks, her wilful gaze, the line of her
tightly-drawn chin---the same Safu from that day was standing right in
front of him. But he couldn't touch her. He couldn't even escape with
her.

\emph{That can't be.}

"If you're in here---" Shion made a fist, and punched the column as hard
as his strength allowed. "---I'll get you out. We're going together,
Safu."

\emph{No matter what you may look like.}

"Stop!" Safu shrieked. "Stop, stop. Anything but that!" She raised both
her hands as if to block Shion's vision. "Anything but that\el Shion,
please. Just don't\el don't do anything cruel like that\el don't."

Safu was truly afraid. Fear radiated from her words and her gaze.

"If I was going to be seen by you like this\el I would never have hoped
for you. I wouldn't have wished to see you again."

"But Safu\el "

"Shion, I'll say this again. I don't exist anymore, but I'm still
trapped. It's painful. Very. I can't--- I can't bear any more of this
humiliation. So please, destroy the Mother. Set me free."

He couldn't think.

Numerous white lines ran through his head, cutting off the circuits of
his thoughts.

"Come on." Nezumi pulled at his arm. "Safu, I want you to secure the
escape route for us until the very last minute."

"I will."

Safu broke into a run. She collided right into Shion. He instinctively
tried to embrace her, but her body passed through him with no impact
whatsoever. He didn't even feel a faint breeze.

\emph{I'm an illusion. Nothing more than a mirage.} This spoke to him more
meaningfully than a million words put together.

Suddenly, an alarm went off. It rang out across the entire Correctional
Facility.

\emph{Emergency alert. Emergency alert.}

\emph{Level 5, Level 5.}

\emph{Emergency evacuation. Emergency evacuation.}

He pursued Safu with Nezumi still holding his arm. Half of his mind had
ceased to work, and he could neither accept reality, nor make an
appropriate judgment. He couldn't even assess the current situation.

\emph{All three of us are escaping together. Me, Nezumi, Safu---three of us,
alive, in the flesh. We're running to stand underneath the sun again.
Yes, that has to be it.}

The cogwheels creaked in his head. Emitting a strange metallic sound,
they turned, stopped, turned backwards, and stopped again.

\emph{Creak creak creak, creak creak creak\el }

His torn thought circuits mended once, then were cut apart and scattered
asunder; then they solidified, and turned sticky.

\emph{All three of us are escaping. We'll be able to get out. We can get away.
We can go back to that place I yearn for again.}

\emph{I yearn, I yearn, I yearn, I yearn\el for that place that has burned
itself into my eyes, engraved itself into my soul. Not No. 6, of course,
but that room. The place that brought me back to life, and allowed me to
be born again.}

\emph{I want to show Safu that room, where Nezumi lives.}

\emph{Safu, you wouldn't believe this place. There's almost nothing in it
apart from books. There's a chair. There's a kerosene heater, a bed\el 
and the little mice. Just those. You'll probably stand there in
astonishment, open your eyes wide, and look around the place again and
again. You'd reach out and gently place your fingers on the piles of
books. And then\el and then, what would you do? Would you smile? Would
you cry out in awe? Would you be so overwhelmed that you would only
stand dazed?}

\emph{Then, I'd tell you: 'This was my starting point.'}

\emph{That room was where I started off. I took a cautious step out of the
bounds of my ignorance, led along by Nezumi. Like a baby who touches the
outside world for its first time, I stepped out into a world I didn't
know about. I want to show that place to you. I want you to see it, too.}

\emph{Oh, and Inukashi. I need to introduce Inukashi to you. He's the
greatest---such a jovial and wonderful person. You could probably get
friendly with him in no time. Inukashi can really understand, you know.
He can sniff out the true nature of people. No matter how well you
disguise yourself, he always notices the arrogance and foolishness under
your disguise.}

'I have a good nose, particularly when it comes to the smell of rot. It
can be meat, leftover food, or someone's rotten intentions, but I'll
smell it out in no time. Can't hide nothing from me.'

\emph{He said that to me once, and he's right. Inukashi will sniff out
anything. It's pretty amazing. And that's why I think he'll like you. He
definitely will. He'll twitch the tip of his nose, and he'll say:}

'Hmmm. Shion, this girl is pretty fresh. She looks good to eat. I know
for sure I wouldn't have to worry about getting food poisoning if I
did.'

\emph{And he'll smirk. He has a very rough way of speaking, and---yeah, it'll
probably surprise you until you get used to it\el but Inukashi never
lies. He won't turn against his own heart. He's someone you can trust
with your whole being. You'll come to understand and accept the way he
is.}

\emph{Ha ha, I can almost imagine you stretching your hand out to Inukashi,
and him taking it gingerly with a sullen look on his face. And I'd
probably be watching, trying not to laugh.}

\emph{Then, there's Rikiga-san. He's quite older, and he and my mother
actually knew each other. Isn't that a surprise?}

\emph{Rikiga-san also has a rough way of speaking. He also has bad drinking
habits. He's a big drinker, and he'll drink for almost the entire day.
Nezumi and Inukashi always tease him about that. But I listen to the way
they tease him, and it's sometimes so harsh I feel bad for him. It's
true that he drinks too much, though. But---how would I describe it?---he
has his own likeable traits. Rikiga-san has his own passions and
emotions, too, and I can feel them from him. He's the type of person
that doesn't exist in No. 6. You'd agree, right? There's no one in that
city who would show their emotions so openly. Nezumi says that all that
drinking has loosened Rikiga's stopper on his emotions to the point that
they're constantly gushing out into the open for everyone to see\el and
yes, Nezumi's got quite a sharp tongue too. One that would match
Inukashi's.}

\emph{There's also a girl named Kalan. That's right, she has the same name as
my mother. She's the first friend I made in the West Block. She's still
a little girl, but she's strong and smart with a sense of pride. She
loves picture books, and I've read them aloud to her lots of times. It
had been so long since I read picture books.}

\emph{And above all, I have to tell you about Nezumi. I want you to know about
him. Four years ago on a stormy night, I met him. Ever since then, I
feel like I've been captured by him. When I'm with him, I lose sight of
myself. No, that's not it. I'm illuminated vividly. Maybe I'm blinded
for an instant because that light is so bright. That's how much my
vision had deteriorated. It was so weak, I couldn't even discern myself,
my surroundings, or the truth. Safu, his---Nezumi's gaze and words pierce
me. They shoot through me, batter me, and save me. By his hands, I was
melted, wrought anew, and instilled with new life.}

\emph{Safu, Safu you are my one and only, irreplaceable friend. You're an
important friend, and no one else could compare.}

\emph{Is that word so cruel? Is the love you have for me, and the feelings I
have for you forever parallel, with no chance of intersecting?}

Why are you such a kid?

\emph{You seemed weary when you said that. And you're right. I'm so immature,
I'm embarrassed at myself. I can't restrain my emotions. If only I could
love you the way you wished me to\el my one and only, so dear to me\el }

The cogwheels turned. They continued to jerk, producing an unpleasant
sound.

\emph{Creak creak creak, creak creak creak\el }

\emph{All three of us are escaping. I know we can get out.}

They slipped hastily past the cylindrical columns. It was still and
quiet. Only two sets of footsteps---Nezumi's and Shion's---echoed.

The crimson door opened. They could see the deserted hallway. The three
doors were completely shut, and there was no sign of any human presence.

Safu's feet stopped.

"Go, hurry." She pointed straight at the elevator. "I'll operate it for
as long as I can, up to the time limit."

"Gotcha." Nezumi stepped into the hallway. He was still holding onto
Shion's arm.

"Safu, you too."

"This is as far as I'll go. Shion, thank you, and good-bye. Nezumi, you
as well." Safu smiled.

The door closed again.

"Safu, wait, Safu---"

"Shion."

He was grabbed by the shoulder, and forced to turn around. A fist dug
into his stomach.

"Gh---" he could hear himself emit a low groan. His body sank, and
collapsed into Nezumi's arms. He didn't lose consciousness, but for an
instant, his limbs went numb. He could not move.

He was being dragged to the elevator. He could feel Nezumi's laboured
breathing and the beating of his heart. The elevator opened as if to
summon them inside. Nezumi muttered something. Shion couldn't hear. He
tripped, staggered, and they tumbled into the elevator with Nezumi still
holding onto Shion.

The elevator descended rapidly.~

The security alarm was still going off.

\emph{Emergency alert. Emergency alert.}

\emph{Level 5. Level 5.}

\emph{Emergency evacuation. Emergency evacuation.}

\emph{All personnel, evacuate immediately.}

\emph{Level 5. Level 5.}

\emph{Emergency evacuation. Emergency evacuation.}

"---Safu," Shion choked, still thrown out onto the floor. Nezumi also
crouched, breathing raggedly.

\emph{I can't stand any more}, he thought. Both his body and soul had withered.
They were withered dry, yet so heavy. He felt like lead had been poured
into him, down to the tips of his hair. He couldn't move anything.

"Don't\el make noise yet." Nezumi's voice. It was coming from somewhere
high above his head. Echoing somewhere far, far in the distance.

\emph{Nezumi, what am I here for? Why am I here, collapsed in weakness, unable
to move? Where is Safu? Why did you leave her? Tell me. 'Don't cling
onto to others. Grasp your own answers,' you'd probably say. You scorn
people who cling to others too easily. I feel shame at my weakness. But
this time, please just tell me the answer. Give me the correct one.}

\emph{Why am I here? Why am I here, having left Safu behind? Tell me. Tell me,
Nezumi.}

\emph{I cling to you.}

The elevator came to an abrupt stop, and his body was thrown up by the
impact, and flung across the floor again. The door opened partway, and
then ceased to move. The lights went out.

He could hear thunder from far-off. A second impact hit him shortly
afterwards. It was much heavier than the first one.

\emph{Thunder? No. It's nothing like that. This is---}

An explosion jammed his ears. Darkness bore down on him.

Holding his hands over his ears, Shion raised a voiceless cry.

The elevator closed. It began its descent.

Safu stood silently, watching it leave.

Suddenly, a gentle voice rang out in her ears.

"It's you, Elyurias." Her eyes roved, but of course, she saw nothing.
She could not see, but she could feel.

\myspace

\emph{Safu, was this the right thing to do? Are you truly satisfied?}

\myspace

Safu tilted her head in uncertainty. She put a hand to her chest. Tears
sprang unexpectedly into her eyes.

\emph{I want to raise my voice and cry.}

\emph{Shion---Shion, you're gone.}

\emph{You came all the way here for me. I thought that would be enough, but
what am I feeling? What is this rush of emotion?}

\emph{Shion, Shion, why is he the one beside you? Why isn't it me? Why did
fate not allow me to live alongside you? If he wasn't here, would you
have loved me instead?}

\myspace

\emph{You may not have been able to live together, but you could have died
together.}

\myspace

Safu lifted her face, and clasped her hands together at her breast.

\myspace

\emph{Safu, you did not wish for that?}

\myspace

\emph{In truth, in truth, had I wished\el that you would die with me, that you
would expire here with me\el Shion?}

She shook her head. She did not wish for that. Even now, she did not
wish for it a tiny bit. She wanted him to be alive. She wanted him to
live, and change this world. She wanted him to create a world in which
no one was forced to die such an unfair death.

\emph{Shion, live. Live out your life. Please.}

"Elyurias, what will you do?"

\myspace

\emph{Me? What will I do\el ?}

\myspace

"Yes. You've been set free, too. What will you do from here?"

Laughter rang out. It sounded like the wind crossing a grassy plain.

\myspace

\emph{You watch and see what I will do.}

\myspace

Safu shuddered. It was no breeze from the plains; she felt like she was
being hit by a frigid wind mixed with sleet. A chill wind, signalling
the arrival of the coldest days of the winter.

\myspace

\emph{Safu, I liked you. Perhaps\el perhaps my meeting a human like you will
prove to mean very much to me.}

\myspace

"What do you mean?"

\myspace

\emph{I wonder what? Oh, it's time. I must go. Good-bye, Safu.}

\myspace

"Good-bye."

Yes, it was time. Safu closed her eyes. She felt the warm rays of the
sun and smelled the fragrance of the trees. She was able to let a faint
smile play on her lips.