% !TeX spellcheck = en_US

\chapter{The reason why}

\myepigraph{When people built the public office\\
	wasn't the reason why\\
	so it could take away their perils\\
	and create a bright and peaceful world?\\
	But the citizens suffer hardship, and the officials bloat with
	riches\\
	On the vast earth, not a single one\\
	of the citizens can voice their woe\\
	So they take to their brushes, and entrust it to song.}{Chinese folksong}

Safu let out a scream.

\emph{This is me?}

\emph{Why, why, why\el }

"Safu, are you awake? Good morning. How do you feel? Ah, I see all your
cognitive senses have returned to normal. Splendid."

\emph{This is me?}

\emph{No, this isn't me.}

\emph{This isn't me.}

"What are you talking about? Look. You are beautiful. Not only
beautiful---yes, soon you will have both beauty and power in your hands.
And immortal life. Brilliant, is it not?"

\emph{No. No.}

\emph{Help me.}

\emph{Turn me back.}

\emph{Turn me back to who I was.}

"Safu. You cannot let yourself get over-excited. It hurts, doesn't it?
Yes, when your emotions are agitated, it causes pain. Headaches. So,
calm. Calm down. Calm down, and think of the appropriate state you
should be in. Yes\el good girl. I will help you. Yes, calm down\el "

\emph{Shion\el }

\emph{Where is Shion?}

"Forget him. You have been reborn. Forget everything from before.
Everything. No people, no names, or memories are of use to you anymore,
Safu."

\emph{I don't want to forget.}

\emph{I can't forget.}

\emph{I\el won't forget.}

"You know, Safu, tomorrow is a festival. A day to celebrate the birth of
this city. A celebratory festival. It's called 'The Holy Celebration'.
You know about it too, I'm sure. You were a former citizen, after all."

\emph{Shion.}

\emph{Shion, where are you?}

"Festivals are utter foolishness. Everyone makes a senseless ruckus and
they don't even realize what they're celebrating for. Foolish, aren't
they? It would be troublesome if they weren't, however. Ha ha ha\el The
real Holy ones are right here. You and I. Shall we give a toast, Safu?
Will you have wine?"

\emph{I will not forget.}

\emph{I will not forget you.}

\emph{I would never be able to forget you.}

"Safu, why are you expressing sadness? I'm planning a very splendid gift
for you, you know. Soon. I will lead you to become an existence everyone
would admire."

\emph{I will keep remembering you.}

\emph{Because this is my own heart.}

\emph{I will not\el forget.}

"How troublesome. I thought you would be less of an obstinate child. I'm
a little disappointed, Safu. Very well, then. Soon you will see the
extent of my magnanimity. Then you will prostrate yourself and feel
gratitude for me. See, Safu? Oh, yes, we'll no longer need this name
anymore either. Let us throw it away. A new future is waiting for you,
after all. See? Doesn't it excite you just thinking about it?"

\emph{I will not throw away my soul.}

\emph{I will not lose my memories.}

\emph{My feelings will not be stolen from me.}

\emph{Shion,}

\emph{where\el }

"Come on. Come over here."

\emph{Shion, where are you?}

\myspace

Shion finished talking. He recalled, in as much detail as possible, the
past few years starting from the stormy night when he met Nezumi, to
where he stood today. He knew no amount of talking could tell his whole
story. He didn't have the confidence that he could accurately tell all
that had caused him such turmoil. But he told anyway. Rooting out the
buds of countless emotions that had begun to sprout in his soul, to the
best of his ability, he calmly and objectively told of his own
experiences, what he had seen and heard, the scenery which spread before
his eyes, and the sounds which had travelled through his eardrums. At
least he had meant to.

But still, his voice shook at the end. He couldn't help the plea from
creeping into his tone.

\emph{I am weak. So powerless. I can't even repress my emotions with my own
strength.}

He clenched his fist.

\emph{You knew, Shion. You've known this for a long time. You've been forced
to face the reality of how weak you really are, over and over, before
you came here. What's the use being afraid of your own powerlessness and
ignorance \emph{now}? You can be ashamed, but you can't be afraid. If you
falter, you won't be able to move forward again. You've come this far.
You can't turn back. You're not that weak.}

Shion took a deep breath, and continued his words.

"I want to help Safu. I'll do anything to get her out. That's what I've
come here for. Nezumi brought me here. I can't begin to imagine where
this is, or how I can infiltrate the Correctional Facility from here.
But no matter what, I have to accomplish it. That much I can be certain
of. And\el I'm the one that got Nezumi involved. Nezumi risked danger
for me\el that's also the truth."

The elder remained silent. They were wrapped in stillness. The silence
was heavy on them, and Shion felt like he could even feel his bones
creaking.

Beside him, Nezumi crouched. He picked up the shirt which had slid from
Shion's hand without him knowing, and handed it back to him.

"Thanks."

\emph{Heh.}

Nezumi chuckled.

"Your manners don't leave you in this situation either, do they, young
master? Maybe add 'ignorant brat who thinks highly of himself' to that
nickname, while you're at it."

"Me? Think highly of myself?"

"Yeah. I didn't come here for you. Don't flatter yourself too much,
young master."

Before Shion could respond, Nezumi turned aside. His expressionless
profile rejected Shion's gaze and words.

"Rou." The elder didn't respond to Nezumi's call. He remained unmoving,
with his eyes closed. He looked like he was either meditating, or
reciting a prayer in his head.

"Rou, there's nothing false about Shion's story. It's all truth. There
have been casualties in No. 6 from parasite wasps. Shion was spared. But
most of everyone else won't be. They all die strangely---" Here Nezumi
shut his mouth, and glanced at Shion. A shadow of doubt wavered in his
eyes, though only very slightly.

"Rou? Are you listening to me?"

The elder's head nodded slightly. "I am. Your voice projects well, and
reaches the ears of your listeners very clearly."

"Has it reached your heart?"

"Of course."

"Then I want you to answer me. I want you to tell me."

"The fate of No. 6?"

"No, I don't need to ask anyone to find that out. I know what's gonna
happen to it: destruction and extinction. I'll be the one to pull the
trigger."

"Then\el what do you wish to ask?"

"What the parasite wasps really are."

Shion let out a soft cry. He looked at Nezumi's profile wide-eyed, and
then shifted his gaze to the elder.

"You are telling me to divulge the truth about the parasite wasps?" the
elder said.

"Yeah."

"Why\el do you ask me this?"

"Because you know," Nezumi answered. "I have a feeling you do. I've been
thinking all this time: maybe, just maybe\el you know most of everything
I'd want to know." Nezumi exhaled. The stiff angles of his profile gave
way, and doubt shaded his face even more darkly.

"You know, because you were formerly of No. 6, as a citizen\el no, as a
creator. Am I wrong?"

This time, no voice escaped Shion's lips. It was caught in his throat.

\emph{Creator? This elderly man?}

"Is what I'm saying incorrect? Rou."

The elder didn't reply. Nezumi turned his face up at the ceiling. There
was only a pool of dusky gloom. But Nezumi blinked at it rapidly, as if
he were staring at something blinding. Then with an unusually languid
movement, he raised his arm up.

"This." He was holding a square piece of paper between his fingers. He
passed it to the elder. It was a photo, an outdated one that was still
printed on special photo paper.

"The alcoholic old man had it. Your mama's in it too," he said to Shion.
"I took the liberty of borrowing it from his files."

"Oh, that\el " It was one of the photos that had been mixed in with the
jumbled contents of several folders. They had been strewn about on the
floor when the two had last visited Rikiga from the directions on
Karan's memo. In the photo were his mother and her friends, several
decades younger. He remembered hearing Rikiga, a former journalist, say
that this was the photo he took the last time he ever entered into No.
6.

Back in those days, No. 6 hadn't been as closed off. There was no law
yet that required a city-issued permit to enter or exit, and it wasn't
like now where anyone who didn't possess a permit was prohibited from
entering under any reason or circumstance. The special gates and alloy
walls also hadn't been completed yet. Rikiga had said that it was still
a time when travelling to and from No. 6's surroundings had been
relatively easy.

"The young woman in the centre is Shion's mother. Her name is Karan."

"Karan."

"You know her, don't you? You're in the picture with her. Or have you
long forgotten her?"

"With her? This man, with my mother?" Shion was surprised. He could tell
his mouth was gaping open. He couldn't help but stare openly at the
snowy-haired elder. He knew how insolent his gaze was, but he could not
avert it.

\emph{He knows my mother?} To think that this man who had settled in these
underground caves, was called "elder" by the others, was connected to
Karan. It was unbelievable, if nothing else.

\emph{Unbelievable, how can that\el ?} For an instant, the surprise hit him so
hard he felt like the core of his brain was tingling.

Since meeting Nezumi, the boundaries of his world had broken. The world
he had lived in before had all but collapsed. Everything was full of
surprises. Things he had believed in, had never had a doubt about,
inverted and showed an opposite face. He experienced this heart-stopping
realization many, many times.

Astonishment, awe, stunned silence, perplexity, and pain. He had
experienced so many emotions and sensations. But he was also being
forced to come to terms with how ignorant he had been before he met
Nezumi, and how he had lived not knowing anything, and not trying to
know.

That was why it hurt. It hurt enough to make him gasp in pain. But even
so---he vowed not to hesitate at being surprised and perplexed.

Shion, in his own way, hoped to see the truth about himself and the
world he lived in. He had also resolved to see \emph{through} it all. He didn't
hesitate at being surprised or confounded; on the contrary, every time
he was surprised or confounded, he felt a layer peel away, and a new
facet of the world unfold before his eyes. He had even come to revere
the experience.

But this time, he was simply astonished. He fixed his eyes on the elder
with his mouth open. Nezumi's fingers touched his lips. Why were his
fingers always so cold? A feeling most distant from surprise or
perplexity flitted across the back of Shion's mind. Nezumi clicked his
tongue softly.

"Shut it. You have the most unbelievably idiotic expression on your face
right now."

"No way\el " Shion whispered. "\emph{This} is what's unbelievable\el Nezumi,
what's going on? How does my mother factor into this? This man and my
mother know each other\el what does it mean?"

"How should I know?" Nezumi retorted. "I'm asking you because I don't.
See that photo the alcoholic had: the one standing beside your mama is---"
Nezumi swallowed. "It's Rou."

The photo slid from the elder's fingers. It fluttered to the ground like
a flower petal.

"I was surprised too, when I first saw this photo," Nezumi said. "I
probably had the same kind of expression on my face, though probably not
as idiotic as yours."

Nezumi picked the photo up, and held it out for Shion to see. Shion
leaned forward, and squinted at it. It was a rather aged photograph.
Several young men and women were standing in front of a grey building.
Karan was standing in the middle of them. Her hair was grown out long,
and she was smiling shyly. Her smile still carried a sort of
girlishness. On her right was a tall man with a long face. He was
clutching a lab coat in one hand, and had gentle eyes. Even from the old
photo, Shion could make out the deep intellect that resided in those
eyes.

\emph{My godfather.} Nezumi had pointed at this man, and said those words. \emph{He's
my godfather.}

Shion knelt down in front of the elder.

"Please tell me." His voice was raspy. His throat was painfully parched.
"Please tell me the truth. That's all I ask."

The elder's torso swayed slightly. It reminded Shion of swaying silver
grasses. His white hair, which shone dully in the candle light, was
almost like the ears of the silver grasses themselves.

"Knowing the truth, and rescuing your friend: do you think the two are
connected, Shion?" Shion shook his head slowly in answer.

"I don't know." He answered truthfully. He really didn't know.

He had to do anything to rescue Safu even a minute sooner, a second
sooner. But what did he need? Did he \emph{need} to know the truth about the
parasite wasps, the relationship between his mother and the elder, and
No. 6's future\el did he really urgently need to know these things?
Shion didn't have an answer.

He did wish to know. He desperately yearned to know. But the most
important thing right now was to save Safu---was it not?

"I don't know\el Maybe my knowing the truth and rescuing Safu are two
completely different things. But\el "

"But?"

"But I---or should I say we---we residents of No. 6, including myself, have
been kept away from the truth all this time. We've lived our lives
hidden from the face of reality, the true form it embodies."

"You've just never tried to see it," Nezumi remarked, emotionless. "If
you squinted, you would have seen. If you searched for truth, you would
have found it. But you didn't. You got drunk and giddy on your false
idea of abundance, and settled yourselves into blissful laziness. You
didn't try to look through it to see reality. Your foolishness allowed
No. 6 to burgeon into the monster it is today."

"I'm sure you're right." Shion inhaled. Nezumi was right. \emph{But you know
what, Nezumi? In the time I've lived with you, I've been able to touch
the sprouting ears of truth. I touched them with my own hands. That was
my starting point. That's a truth in itself, too.}

\emph{I started off there, and now, I'm here.}

"Safu getting kidnapped, and parasite wasps appearing\el No. 6 turning
into a monster, all happened because we've averted our eyes from the
truth this whole time. The crime we've committed is grave; I've realized
that. But that's why I want to know. I want to see true form of the
world, with my very own eyes---"

Shion bit his lip. \emph{No}, he almost said out loud. It didn't feel right. It
wasn't that he had lied to the elder. But he had decorated his words.
Regret and resignation about the past weren't the only things that lay
behind the reason for his wanting to know the truth.

Curiosity. No, it wasn't such a casual feeling; it was a deep-rooted
desire. It roved in circles deep inside his chest.

It was intrigue towards a world his imagination could not render.
Interest in the unknown. And more than anything\el it was the
expectation that he could acquire some piece of knowledge that had to do
with Nezumi.

The part that Nezumi showed him was only a small fragment. In fact,
Nezumi had many faces which Shion could not see through. And he felt it,
painfully, everywhere, every time.

\emph{Where did you come from?}

\emph{Where were you born?}

\emph{How did you used to live until that stormy night when we met?}

\emph{What have you thought about, believed, and rejected in your life up
until then?}

\emph{And there's the promise of telling me your real name, which you haven't
fulfilled yet.}

His soul was stirring restlessly. It stirred from wanting to know, and
not for anyone else but himself. But he had put on an act. He had
pretended to be the friend, the innocent youth who longed to know the
truth.

His heart and words turned away from each other. How beautiful and
rational were the words that spilled from his mouth. They were rational
and beautiful to the point of sounding fake. His own words deceived his
heart.

He bit his lip. He chewed on it hard.

\emph{Can I only speak in these kinds of terms?}

\emph{Why can't I speak like Nezumi? I can only use empty, superficial words.
Why do I keep putting on an act? Why do I still speak, when I'm not even
prepared to reveal my true self?}

\emph{Even though I've lived by his side for months\el }

He had directed his gaze at Nezumi without even thinking. There was no
way he couldn't have noticed the decoration in Shion's words, but
Nezumi's profile showed no hint of disdain, scorn, or pity. He had
lowered his chin slightly, and was staring off into the dark void.

Nezumi never toyed with his words.

Safu was the same.

Like a flash of lightning in the night sky, an idea sparked in his mind.
Safu had never manipulated her words. At least, any words she had
directed at Shion were true. He had received her straight and earnest
words numerous times.

He realized he ought to be ashamed of himself. Both in the face of
Nezumi and Safu, he ought to be ashamed of himself.

"I\el want to know." He squeezed out each word painstakingly. "There are
too many things I don't know. That's why\el I want to find out. That's
it."

The elder's body swayed once again. "Just because you know, it does not
mean it will make you happy. You may end up wishing you had never known
at all. Such a reality may be waiting for you, Shion."

"I'm prepared for it." He would rather suffer from the knowledge than
being blissfully ignorant. He preferred the pain and hardship of truth
rather than fake happiness. With this as his fuel, he could move
forward. He couldn't keep leaning on this illusion, which didn't even
serve as a foothold.

He clutched his chest. He confirmed his feelings.

There was no doubt about it. \emph{My feelings are here within me. I am not
deceiving anyone.}

"I'm prepared. At least, I think I can prepare myself. Though---I can't
say for sure that I won't regret it\el I'll probably regret it a number
of times\el but I feel like it would be much better than going without
knowing. That much I feel is true\el so, ah, I\el " As soon as he tried
to speak in earnest, his tongue refused to co-operate. His words refused
to run smoothly as they had just moments before.

Earnest words were heavy things.

They bore the weight of the speaker's beliefs, emotions, and honest
feelings.

The elder suddenly smiled. At least to Shion, it seemed like he did. The
elder let his momentary smile fade, and slowly lowered his eyelids. He
fell silent.

"Rou, why are you silent?" Nezumi asked harshly in impatience. "Rou!"

"Elyurias." The elder's lips moved, and a whisper, like a breath,
escaped. It was a word Shion couldn't understand.

"Elyurias?" Nezumi furrowed his brow. Apparently, he hadn't understood
either.

"That is the name."

"Whose?"

"Hers."

"Her?"

"Nezumi, your eyes."

"Huh?"

"Close your eyes. Shion, you also."

Shion and Nezumi looked at each other. The elder's voice was low and
placid, and carried no hint of a command. But he found himself obeying
it nevertheless. He felt like he had let himself go limp on the gentle
flow of a river, and he was being born to the sea. Shion closed his
eyes.

"Elyurias," the elder whispered again. "She was a great sovereign. She
was a rare existence."

\emph{Elyurias\el }

Nezumi sucked in a breath from beside Shion.

"Looking back, it seems a thing of the distant past," the elder
continued. "It was still a time when this land\el yes, this land was
still without walls. Instead of walls, there was a lush green forest.
There were lakes, marshes, and grassy plains. Myriad things intertwined
and maintained a harmony. A paradise\el it may have been the last
remaining paradise on this planet. A paradise that had escaped the
destruction of humankind. A land of miracles. A place that could nurture
life and put death to rest. She resided there. She really existed. I was
the one who found her."

The elder's voice dropped even lower.

"Ah, no\el that is an arrogant way to put it. I did not find her. I met
her. We met by chance\el as if God had drawn us together. Elyurias---she
was a great sovereign. She would likely be one to this day. She still
reigns."

"Elyurias." Shion said the name under his breath, imitating the elder.
\emph{Elyurias.} It was a sound unfamiliar to his ear and tongue. He couldn't
imagine what kind of appearance or voice a person with that name would
have. Not to mention someone who was a "great sovereign"\el Shion cocked
his head in disbelief. It sounded too grandiose, too phony. He sensed
domination. Had a kingdom existed here in the past? Just like how No. 6
dominated this land now, this sovereign called Elyurias had governed
all\el 

'She', the elder had said. Then that would make her a queen. A paradise
governed by a queen? \emph{That sounds like a cheap drama. I find it hard to
believe.}

The air shifted just slightly. He heard a hoarse groan. As Shion lifted
his eyelids, the first thing that jumped into his vision was Nezumi
covering his face with his hands. He was about to buckle to his knees.

\mybreak

"Nezumi!" Nezumi collapsed into his outstretched arms. Shion felt the
heat and weight of his body. A low groan trickled through Nezumi's
fingers. \emph{It's the same. It's the same as last time.}

They had been talking about parasite wasps in their basement dwelling.
It was just when their conversation had moved from emergent viruses to
the mystery behind the parasite wasps. Nezumi had suddenly collapsed.

They had been drinking hot water. Shion remembered how Nezumi's cup had
slid out of his hand and bounced on a stack of books before rolling
across the floor.

"Nezumi---relax. Can you hear me?" Shion knelt down, supporting the boy's
body with his arms. If it was the same as last time, then there was no
need to panic. Nezumi had recovered just fine last time. If this time
was the same\el ~

"Ow!" A set of fingers dug fiercely into Shion's arm. Nezumi gasped, his
chest rising and falling. The tremor of his fingertips agitated Shion's
worry even more.

"Water," Shion muttered, glancing all around. No one moved. "Please,
give me water. Anyone."

"Will he die?" a voice asked from behind. It was flat and cold. It
belonged to Sasori, the sand-coloured man. He had drawn right up behind
them without Shion noticing.

"Will he die? Then there is no need to bring water." Contempt wafted
into Sasori's tone. "There is no need to give anything to the dying.
Furthermore, he is one who has once left. No need. At all."

Shion turned around. He looked up at the man who had concluded the
discussion with such terse words. \emph{No need.}

"Bring it," Shion commanded. As far as he could remember, he had never
given an order to someone in such an oppressive manner. But the words
didn't feel strange leaving his mouth.

"Bring water to me. Quickly."

Sasori shifted uneasily. The rims of his widened eyes twitched. A single
bead of sweat rolled down from a corner of his eye.

"Here." A wooden bowl was handed to him. It was about half-full with
water. A small, thin child was holding it out as if it were an offering.
"Mother told me to---take this."

"Thank you." Shion accepted the bowl from him. The child spun around,
and trotted away into the darkness.

\emph{Cheep-cheep.}

A small mouse scurried up onto Shion's shoulder. It stared at Shion's
hands, twitching its nose.

"Nezumi\el drink this." Supporting Nezumi's body with one arm, Shion
slowly tipped the water into his mouth. Nezumi's throat contracted. He
took a gulp.

"Nezumi, can you hear me?"

His eyelids lifted, and a pair of grey eyes peeked from underneath.
Shion thought they were beautiful. They were the colour of the sky at
the coming of morning. They absorbed light, yet released it softly at
the same time.

They were beautiful like the dawning sky.

A lightening sky at morning conjoined somewhere with the hope of life.
It was a glow that lauded people who had resolved to live, or at least
try to live, through today. That was why it was beautiful.

\emph{I've gotten so much hope from the beauty of these eyes.}

Shion clicked his tongue at himself. \emph{Idiot, now's not the time to be
admiring him.}

"---Shion."

"Are you awake? Drink the water slowly---there---all of it. Then take a deep
breath."

Nezumi obediently did as he was told. He drained the water, took a deep
breath, and exhaled.

"You alright?"

"Somewhat."

"Does you head hurt? Any nausea, or palpitation---"

"Ten."

"Huh?"

"Three plus seven is ten. And since I'm at it already, twenty-one."

"Oh\el three times seven." So Nezumi had remembered the questions Shion
had asked when he'd woken up last time. Shion stifled a chuckle. Yes,
reality was brutal and cruel. The past few hours had been filled with
human despair, death, and screams. It was dyed through with the colour
of terror, futility, and intense regret. But there had also been many
heartwarming moments, moments where his pulse had quickened and his
spirits had soared. Memories with Nezumi were always like that. They
always brought excitement and warmth to his heart.

\emph{Memories?}

Shion straightened his back, and put more strength into his arms. \emph{Why
did I just think 'memories', like he was someone of the past?} Nezumi
mumbled in Shion's arms.

"I heard the wind."

"Wind?"

"The wind was singing. I heard its song." Nezumi raised himself. "I've
heard it before. But this time it was\el it was clearer. It was a gentle
melody\el "

"What kind of song was it?"

"It was\el "

"Can you sing it?"

"Me? Hm\el well. I wonder if I can."

"Let me hear it."

Nezumi blinked, and his lips moved. A song with a lilting melody poured
forth.

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here\\
	Keep everything here, and\\
	Live in this place\\
	O soul, my heart, O love, my feelings true\\
	Return home here\\
	And stay}

The little mouse grew still on Shion's shoulder. It stopped moving as if
rooted to the spot, and quieted its breath. Humans all around did the
same. The people hidden in the darkness were also frozen in enthralment.
Their eyes were closed, and their bodies were lent fully to the song.
Everything grew still. It felt like even time had stopped. Nezumi's
voice, and his song, seemed to soak into them, enveloping them, rocking
them, and making them feel as if their bodies and souls were floating.

\poem{The wind steals the soul away, humans thieve the heart\\
	But here I will stay\\
	to keep singing\\
	Please\\
	Deliver my song\\
	Please\\
	Accept my song}

The song ceased, and someone let out a gentle sigh. He was not the only
one. Here and there in the darkness, soft sighs could be heard. Nezumi
slowly shook his head.

"I feel like I've heard it before. Like I've heard it over and over,
since a long time ago. Someone's taught me this song before."

Shion lifted his head and posed a question at the seated elder.

"Is this song somehow related with Elyurias?"

"Do you think so, child?"

"Yes." The moment he had blurted the answer, he felt certain. Nezumi and
Elyurias were connected. The elder narrowed his eyes, and his gaze
wandered in the air.

"It has been a long time since I heard it. I was convinced it had long
disappeared from this land. I see---there still remains a person who can
sing."

"The wind sings." Nezumi wiped his wet lips with the back of his hand.
"Or maybe someone's singing in the wind. And I\el hear it. I've come to
hear it."

The elder nodded. "Since when?"

"A little while ago. Yeah---a little while before the Hunt. This is the
third time. When it happens, my consciousness fades, like a stage in a
blackout\el and then green scenery appears\el and then\el "

Nezumi's eyes turned to Shion. His gaze wavered. Shion remembered that
stormy night, the night he and Nezumi had met. The boy had appeared
before him, soaked and blood-stained. He was so fragile, Shion had felt
like he would make the boy fall apart just by touching him. Drawn to
that fragility, and those vibrant eyes which were so much the opposite,
Shion had extended his hand.

"I'll treat your wound." Those words had escaped his lips without a
shadow of doubt, without resistance. He had felt like he had to do
something. He had felt like it was his duty to protect this boy. He had
never felt this protective of anyone, neither before nor after this
incident.

A sharp, vivid moment. One that had burned an imprint into his life.
Every time he recalled it, his heart quickened.

The fragility that had stirred Shion's protective instinct---the same
fragility that had been completely wiped clean when they reunited four
years later---returned into those eyes again.

His heart quickened.

"I don't know," Nezumi continued. "I was still young, and I was wading
through the grass. And I could see\el the sky."

"Right."

"An ultramarine sky. It was a really beautiful blue. And wings
buzzing\el and a song. I couldn't tell whether it was man's or woman's
voice. It was a strange voice. It almost sounded like the wind, crossing
the plains, or crawling across the ground, or showering down from the
heavens. I\el I was always just standing there\el listening to that
song\el "

A song of the wind which crawled across the ground, and showered from
above. \emph{Maybe\el }

"Was it a song of offering?" Shion said. It was mostly instinct. The
spark of an idea turned into words, and spilled from his lips. "A song
offered to Elyurias\el either to praise or appease her\el am I right?"

The elder's chest swelled and deflated. It looked like he was taking
several deep breaths. \emph{Is he agitated? Confused?}

"Sasori," the elder called. The sand-coloured man materialized like a
blot in the darkness. "Provide these two with food and rest."

"Rou---"

"They will probably not have much time to rest\el but that cannot be
helped. Provide them whatever they wish for, to the best of your
abilities."

"Why?" Sasori yelled angrily. "Why do you help them? Nezumi is one who
has once left this place. He left, vowing never to return again. He was
forbidden to return, was he not?"

"Yes."

"But he did return. Bringing a demon with him, nonetheless. Rou, can you
not understand? He is evil itself. He brings calamity and destruction."
Sasori's finger pointed squarely at Shion.

"Did you see his eyes just now? Those are the eyes of evil. The eyes of
wicked darkness. Nezumi is being puppeted by this demon."

"Now you listen." Shion was now feeling more than cross. "You've been
repeating yourself all this time. I only glared at you a little, and
you're making me sound like I'm some monster. Kind of rude, don't you
th---"

Sasori cut Shion off by shaking his head. His face contorted, as if
every word Shion uttered was a curse.

"The very picture of a monster. Rou, I am fine with Nezumi. If you
command me, I shall obey. I will provide him rest and food. But I cannot
do that for \emph{him}. If we do not kill him now, then he will bring
misfortune upon us. He may obliterate us entirely."

"Sasori." Nezumi stood up. "Sometimes poison and medicine can come from
the same plant. Sometimes you can't tell if it's going to be poison or
medicine until you drink it. Right?"

"\el What is your point?"

"There's no need to reveal Shion's so-called true identity, whether he's
a demon or not. His identity doesn't matter. Right now, all I care about
is that he's kept alive. That's all."

"Why?"

Nezumi's fingers grasped a handful of Shion's hair.

"Inside this head, Sasori, is information about the inner structure of
the Correctional Facility. The most up-to-date stuff. I can bet it's
probably as accurate as computer data. I wouldn't be able to destroy the
Correctional Facility without it."

"Destroy the Correctional Facility---" Shock spread across Sasori's face.
Just for an instant, it the expression made the sand-coloured man
actually look human. This man had shown the same reaction to Nezumi's
words as Rikiga and Inukashi did. \emph{Ah, I see}, Shion thought.

His skin and eyes were a strange colour, but those were the only
differences. This man was made of flesh. Blood coursed through his body,
and he gave off heat. He would feel pain if he was wounded, and he had
both emotions and intelligence. He was a human, just the same. Skin and
eye colour were such small differences, they didn't even seem to count.

"Surely you are not \emph{really} thinking of doing that?" he said in
disbelief.

"I am," Nezumi said promptly. "In fact, that's probably all I've been
thinking about. The Correctional Facility isn't just a prison. It's also
a research organization that's connected to the core of No. 6. If we
destroy it, it'll put a crack right in No. 6 itself, for sure. We're
going to use that crack as a foothold to throw No. 6 into its grave. And
to do that, I need Shion. I told you before, Sasori, I won't let you
kill him that easily."

The elder opened his mouth before Sasori could.

"There may already be a crack appearing."

"What? What do you mean?"

"No. 6 may disintegrate even before you strike a blow, because of
Elyurias."

"Rou!" Nezumi barked irritably. "Speak in a way I can understand. So far
you haven't clarified a single thing."

"Nezumi, perhaps it is fate that you have returned with Shion. Perhaps
it had already been decided beforehand."

"Beforehand?" Nezumi retorted. "Who the hell can decide how I'm going to
live? I'd like to see anyone try. I'll never bow down to cheap words
like God or Fate. That's enough, Rou. No more word-play. Stop your
mysterious nonsense and answer my question. You were involved in the
birth of No. 6, correct?"

"Yes."

"How?"

"Be seated. You too, Shion. Be at peace. I will give you water. You are
probably thirsty." Before the elder even finished his words, a pair of
slightly bigger bowls were being handed to them. They were filled with
clear water.

Shion felt a powerful thirst return to him.

He hadn't realized how badly he had wanted water. He felt like all the
moisture had been wrung out of him in the numerous experiences leading
up until now. He was so thirsty, he felt like his throat was chafing.
When he had fed Nezumi water earlier, he had not wanted any for himself.
He had completely forgotten his thirst. But now it was like his parched
state was a reaction to that; he felt like he was burning up.

"Water---" Shion held the bowl in both hands and greedily gulped it down.
It was cold and delicious, like the water that Nezumi had fed him over
and over during his battle with the wasp---the water that ran near
Inukashi's ruins. It had the same taste. It was delicious, and it
quenched him.

He drained it in a single draught. More water was poured into his empty
bowl. Shion was so grateful he felt he could cry.

"Good, isn't it?"

Shion found himself nodding vigorously in answer to Nezumi's question.
It was too good to put into words.

"There's an underground lake here. Lots of minerals. ---Geez, you must
have been thirsty."

Shion finally stopped to take a breath after he had had several bowls of
water. The elder must have been waiting for him, for now he opened his
mouth to speak.

"This will take a rather long time. I had intended not to tell anyone
for my whole life\el but I must tell it now. However, before that\el 
Nezumi."

Nezumi lifted his chin.

"There is a path leading to the Correctional Facility, but it is only
connected partway. The Facility has built a door from their side sealing
the way off. It has not been opened for decades."

"I know."

"There is no other way into the Correctional Facility unless you open
it. You know that too, I presume?"

"Naturally."

"It is impossible to open it from this side. Nor will it ever open from
the Facility's side. It absolutely will not happen."

"The thing with doors---" a wan smile spread across Nezumi's lips, "is
that you don't just wait for them to open politely by themselves. You
force them open."

"Have you a plan?"

"I'm not unprepared."

"I would not have expected you to act without some strategy. But I
cannot imagine how you would open the door."

"Shion." Nezumi crouched down, and put a firm hand on Shion's shoulder.
The startled mouse hastily hopped down out of his way. "The door we're
talking about: it's the only point on the map that connects the blank
space underground to ground-level. You know where it is, right?"

"Yeah." The floorplan appeared in his mind, the one of the Correctional
Facility that Nezumi had commanded Shion to memorize as if his life
depended on it.

"It's in location po1-z22. From the Facility's side, it was labelled
Point X."

"You remember the energy circuits which were connected to that point
too, right?"

"Yeah. It was a single circuit, an old system. There are no auxiliary
circuits."

"The unopenable door doesn't need a carefully-crafted backup system,"
Nezumi said. "Efficiency is paramount. Remove everything else that isn't
absolutely necessary. Both people and machinery." He chuckled. "Sounds
like something they would think of. But this is where it works to our
advantage."

Nezumi snapped his fingers.

"The unopenable door opens. We'll pry it open. Rou, we'll fight our own
battle. You have nothing to worry about."

"Only death is waiting."

"For us?"

"For many people. Many more people will likely die, more than you can
imagine. Perhaps you are the only ones who can stop that. Nezumi, fate
does exist. Fate has brought you together, and you are here because of
fate. It was fate that Elyurias and I met. Let us begin with that story
first. Listen well, and make haste, or else it will be too late. You
must hurry\el "

Then the elder began to speak. It was a story of No. 6.

Shion and Nezumi huddled together and grew still, like children
listening to their grandfather tell a tale of the past. Only their ears
strained hard to listen.

It was a story of No. 6.

A tale of destruction and creation.