% !TeX spellcheck = en_US

\chapter{Land's end}

\myepigraph{Humans were born from the eye of Ra.\\
	Ra was the creator of heaven, earth, and all things.\\
	Since he was the Sun, and also the ruler of the gods,\\
	it was decided that he would become the first King on earth.}{\emph{The Beginning of Heaven and Earth}, Egyptian myth}

\lettrine{I}{t was} blurry. Everything was veiled in a haze, and vague.

\emph{But I have to wake up\el }

Safu struggled to open her eyes. She bit her lip as hard as she could.
There was a slight pain. She could feel her sensations returning.

Safu realized that she was bound to a stretcher. A white door opened,
and she was carted inside. In her blurry vision, she could not make out
what was there. She felt her body gliding sideways.

"Ah, are we awake?" It was a man's voice. "No need to be, though. Let's
give you an anaesthetic, shall we? Then you can sleep again in peace."

"\emph{Where\el am I\el ?}"

"Care to take a guess?"

What's wrong with me? What happened---? I visited Shion's house, and then---

There was a man in a Security Bureau uniform.

\emph{'Are you Safu-san?'}

The shock in her neck. The numbness that had spread through her body.

Safu almost shrieked in terror. Her lips parted, but no sound came out.
Her voice was stuck at the back of her throat.

"\emph{Correc\el tional\el Facility\el }"

High-pitched laughter rang out. The man was laughing.

"Do you fancy the Correctional Facility? It seems you've taken a liking
to it. I know, once this surgery is over, you can live in your own
special suite until you die. I'll have it all arranged."

\emph{Surgery?}

"\emph{Surg\el }"

"Yes. You're lying on a surgical table." The man's voice was still
filled with mirth. A white glare filled her vision. Safu took it to be
the light of a surgical lamp. She was pierced with horror --- stronger
than the horror that had seized her when she had been apprehended by the
Security Bureau.

A tear spilled from her eye.

"There's nothing to cry about. There will be no pain, or discomfort.
Good night, now."

\emph{Shion. Shion. Shion.\\
	He'll save me. He'll rescue me, and get me out of here --- Shion.}

\mybreak

"Shion."

His name was called. Shion stopped his feet. His guard, a large dog,
gave a low growl.

"Rikiga-san."

Rikiga was exiting a shabby restaurant through its rickety glass door.
Shabby as it was, it was one of the more decent establishments in the
West Block's bazaar. Most establishments of these sort were clusters of
barrels and crates placed outside to sit on, and the dishes were all of
an unidentifiable origin. The stench of strong spirits and some
mysterious stew wafted out from these stands out into the street, and
Shion often found himself pinching his nose. But even so, starving
children and old beggars milled about the shops, some wandering in hopes
of receiving food, others staring fixedly at the adults bringing their
food to their mouths. A shop owner raised his voice angrily, splashing
water outside his storefront, and chased the people away as if they were
stray dogs or cats.

And in front of these starving people, those who had been able to get
their hands on the day's sustenance sank their teeth into their food,
dripped grease over their mouths, and licked their fingers.

To have money, and to have power.

To have food meant to fulfil these conditions.

Shion had learned this from these few days here. But he still could not
get used to it. He couldn't bear to look at the scene before him. He
couldn't help but avert his gaze, and look at the ground.

"If it makes you feel better, then give them a handout. But only if you
can fill the belly of every single person there," Nezumi had said. For
Shion at the present, it was an impossible task.

"What can you do with your half-hearted sympathy? You might be able to
save a handful of kids from starvation, for a short time. But that just
means you're creating two new types of people--- those who are starving,
and those who aren't. Let me tell you something interesting, Shion. It's
more excruciating for people who've filled their belly once to starve,
than for people who have never been full at all. Nothing is more harsh
than starvation after satiation. These kids here have never eaten until
they're full. They don't know what it's like to be satisfied. That's why
they can put up with it. Understand? There's nothing you can do here,
absolutely nothing."

Nezumi had spat those words, and strode out of the room. But before
that, he had stopped abruptly before the door, and turned around. A
brown dog was sprawled off to the side.

"So Inukashi's lent this dog to you as your bodyguard, huh? And I hear
your wages were a little more flush than usual. Looks like you've become
his favourite."

"He says he'll let me continue working for him. He asked me to clean the
guest rooms and take care of the dogs."

"And you took the job?"

"Of course," Shion replied enthusiastically. "I was so happy, I thanked
him over and over again."

Nezumi sneered.

"Will you look at that. Mr. No.~6 Elite is rejoicing over a
housecleaning and dogkeeping job. It should be interesting to see how
much lower you're going to stoop."

"I don't think I'm stooping," Shion said promptly. "You'd agree,
wouldn't you? You don't think this is stooping at all."

Nezumi's shapely face contorted slightly. He hunched his shoulders.

"Oh yeah, Shion. You got paid by Inukashi today, didn't you? Go out and
buy some dried meat and bread."

"At the market?"

"You don't know any other place to buy food, do you?" Nezumi said
sarcastically.

"Well---yeah, but\el "

"Dried meat and bread. Inspect it carefully when they give it to you.
Space out like you usually do, and you'll be stuck with a mouldy brick
of a loaf. And haggle. Haggle like no tomorrow. I'm off."

The door closed, and his footsteps faded into the distance.

He would have to buy dried meat and bread in front of those children.

Nezumi had told him to.

Dried meat, and bread.

Shion's stomach growled insistently. His mouth watered. He had had only
the slice of bread and fruits that Inukashi had given him at noon. He
was terribly hungry. He had not eaten any meat, nor soft bread, for
days.

His stomach growled, his mouth watered.

He wanted to eat. He wanted to sate his empty stomach.

Shion sighed, and pulled his hat further down over his head.

\emph{What can you do with your half-hearted sympathy?}

He recalled Nezumi's words again and again.

\emph{You're right. I can't do anything. I'm just pretending to pity those
kids to boost my self-respect. The truth is that I'm about to buy meat
and bread, right in front of those children, to satisfy my own hunger.
That's my true form --- that's the kind of person I am. Nezumi, is that
what you meant?}

There were a few coins in his pocket. It was his day's payment that he
had received from Inukashi.

"Part of that is a thank-you for treating my brother. I can't always pay
you this much." Inukashi had said this rather curtly, but Shion was
grateful for his kindness. It may have been quite a large amount for a
day's worth of work. But even so, it was enough to cover only a few
strips of dried meat and two or three loaves of mouldy bread. There was
almost no food left in their room, otherwise buried in books. He
wouldn't be able to live off Nezumi's goodwill forever. He had to secure
a means of providing for himself, however little it was.

Shion pushed the door open, and stepped outside. The dog slowly got to
its feet, and trailed after him. When Shion set foot into the market
street, it drew up to Shion's side and kept pace with him closely. He
was trained well. It was apparent that Inukashi had quite a hand with
his dogs. Shion smiled sheepishly as he caught himself, yet again, being
surprised or impressed like with so many other things since coming to
the West Block.

It was already dusk. Darkness was setting in, and the cooing and
bellowing of voices echoed even more loudly in the air. Under ripped
tents, and in front of barracks, people sold and bought things, ate, and
drank. As soon as the warmth of the afternoon slipped beneath the
horizon, the ground beneath them grew colder by the minute. Business was
probably booming at Inukashi's hotel. For those who had nowhere warm to
sleep, it was going to be an unpleasant night. Bare-breasted women
called out from the darkness of the alleyways, and old women clad in
rags huddled on the ground in the same darkness. Children trotted about,
nimbly threading through the crowd, and being yelled at occasionally.
And still people bought and sold, ate, and drank.

\poem{Don't know what waits for me tomorrow.\\
	But at least I've lived through today.\\
	So I'll eat. So I'll drink. Here, it's everything we've got.\\
	All the things I've said, can't enjoy 'em once I'm dead\\
	So I'm alive an' enjoyin' 'em today.\\
	That's everything. Here, it's everything. My everything.}

\clearpage

Someone was singing off-key. Shion paused, and tilted an ear to the
voice. He hugged the parcel of dried meat and bread that he had just
bought close to his chest. This clamour that seemed to rush at him and
overwhelm him --- this clamour, this jumble of noises that seemed to burst
out of the ground itself ---

It was all connected to those who had a strong attachment to life, and
the energy that they radiated. Here, everyone clung fast to life. They
greedily latched onto survival. Because nothing insured a tomorrow for
them, these people lived with even more desperation. This energy, this
clamour. It was something that didn't exist, wasn't allowed to exist, in
No.~6.

What feelings did Nezumi have as he walked through these streets?

"Brother."

A feeble voice called out to him. He turned to see a thin child robed in
faded cloth. He had long, matted hair, and a dirty face. Shion couldn't
tell whether it was a boy or a girl.

"Spare some bread for me," the child pleaded weakly, in a voice that was
barely a whisper. "I haven't eaten for three days. Please, just a
morsel."

The child's countenance reminded him of a little girl he got along with
back in Lost Town. Her name was Lili.

"A morsel\el "

A pair of tiny hands stretched toward him. Almost without a thought,
Shion was putting his hand into his parcel. As soon as he pulled out a
round roll, an impact slammed into his back. He had been shoved. He
staggered. As Shion lost his balance, a pair of small hands snatched the
parcel from Shion's arms. At the same time, he was shoved violently in
the back once more, and he fell to his knees.

"Run!"

The child shouted energetically, almost unrecognizable from the whisper
moments before. Several children yelled after him as they stormed past
Shion. The dog leapt forward swiftly and silently. He attacked the child
who had stolen the parcel. Screams rose from the group.

Still hugging the package of dried meat and bread in both hands, the
child crumpled to the ground. A few strips of meat and a piece of bread
fell out and scattered on the ground. The dog pinned the child down with
its legs, and bared its teeth.

"Stop it! Heel!" Shion had shouted without thinking. The dog obeyed,
closed its mouth, and looked up at Shion reproachfully. The child didn't
miss his chance. He sprang up, and broke into a sprint with the package
in his arms. He moved with the swiftness and agility of a wild animal.
In moments, his small back had disappeared into the throng. The other
children had also melted into the crowd, out of sight.

"Amazing\el "

Shion couldn't help but murmur at their cunning ways. Admittedly, he was
impressed. He soon realized that this was no time to be impressed, and
stooped to gather what was left of his meat and bread. What would Nezumi
say, after seeing it reduced to almost one-third of its original amount?
Would he say nothing, and shrug his shoulders? Would he sneer?

Shion shrugged off his coat and wrapped the bread and meat with it. He
would share this with Nezumi for dinner tonight. Those children would
probably do the same. They would share it amongst themselves, and each
have a tiny morsel of food for dinner. Naive, and meaningless sympathy.
He knew Nezumi would criticize him scathingly, but Shion was still a
little relieved.

At least tonight, those children would have food. Right now, he had no
power to free them from starvation. He couldn't do anything. But if his
meat and bread would stave off their empty stomachs even for a short
time--- wasn't that at least a little meaningful? It was acceptable enough
to give up because he was powerless to do anything. It was acceptable,
but it was arrogant. \emph{Wouldn't you think so, Nezumi?}

"Oy, you there, fella."

From a stall selling roasted kebabs, the female shopkeeper called over
to him in her raspy voice. "Will ya stop standin' in front o' my store
all dazed-like? Being a nuisance, you is. Disruptin' business!"

"Oh, I'm sorry," Shion bowed his head hastily in apology, but the shop
mistress was already busy dealing with other customers to notice him.
Here, no one looked out for other strangers. They simply weren't
interested. Whether there be robbery on the street, or a beggar dying,
or a fight breaking out, no one cared. It all blended into the scenery
of daily occurrences.

"Well, let's go home, then," Shion called over to the dog, and noticed
its jaws snapping as it was chewing something.

"Hey, wait a minute, don't tell me you're---"

The dog gulped the meat in its mouth, and looked up at him with a flash
of a grin.

"When did you manage to pick that meat up? A lot quicker than me, huh."

The dog lolled its pink tongue, licked its chops, and began trotting
briskly ahead of him. Shion was amused, though he wasn't sure why.

He had been following the dog for some time when he was stopped by
Rikiga. Outwardly, Rikiga's job was publishing lewd adult magazines. But
behind the scenes, he acted as a middleman for prostitutes, and that was
his livelihood. Among his patrons there were said to be higher officials
of No.~6 as well. In the words of Nezumi, it was from these kinds of
people that Rikiga cunningly weaselled great amounts money.

But he was also the man that Shion's mother Karan told him to go to for
help. According to Rikiga, a long time ago before No.~6 and the West
Block was been divided with a wall of special alloy, he had met and
fallen in love with Karan. But it was only he who had fallen in love,
and Karan had merely shown agreement toward the articles that Rikiga had
written as a journalist at that time.

"He's the prime example of a corrupted man." These were also Nezumi's
words, but Shion found he liked the somewhat aloof and fearless aura of
the man who had once loved his mother. This man wasn't completely
corrupted. He still had journalism in his bones. That was what Shion
felt.

Rikiga's face was beet-red from drunkenness, and even his eyes were
bloodshot. It looked like he had been drinking quite a bit.

"Rikiga-san, it's bad for your health if you don't lay off the alcohol a
little."

"You're so kind, Shion. I feel like Karan's the one reprimanding me. She
was just saying to me the other day, '\emph{Please, Rikiga, mind your
health.}'"

"The other day? My mother?"

"In my dream. Ever since seeing you, Karan's started appearing in my
dreams. And every single time I see her, she scolds me. Don't drink,
don't be reckless, don't lose sight of what your job should really be---"

A flush that was not from alcohol rose in Rikiga's cheeks. He turned his
face away as if to avoid Shion's gaze.

"Well, a dream's just a dream. Karan's moved on, gotten herself an
admirable son like you. I'm sure she's changed from when she was younger
--- in appearance, and heart too."

"She's aged," Shion conceded. "And she's gotten a little plump. ---But if
she were to see you again, Rikiga-san, I'm sure she'd say the same thing
she said to you in your dream. That's the kind of person she is."

Rikiga opened his mouth to say something, and then pursed his lips.

"All that about Karan--- it's--- it's alright. To tell you the truth, it's a
bit painful remembering\el " he trailed off before abruptly changing the
subject. "So are you alone today?"

"I'm with the dog."

"The one that's glaring at me suspiciously right now? You wouldn't wanna
bite me, mutt. Just so you know, my meat is soaked in booze, and it's
running in my veins. Sink your teeth into this, and you'll go belly-up
from alcohol poisoning."

The dog glanced up at the drunken man, twitched its nose disdainfully,
and scowled. Shion looked down and chuckled to himself.

"What's his problem?" Rikiga grumbled at the dog. "So, no one else with
you today apart from the dog?"

"Are you talking about Nezumi?"

"Yeah. That sarcastic smart-aleck of an actor. Geez, I don't think I've
met anyone as foul-mouthed as he is."

"But you were his fan, right?"

"I just didn't know his true identity, that's all. I mean, Eve is quite
enthralling onstage. I never would have guessed that he'd be such an
impolite asshole. The kid goes around saying whatever he wants, whenever
he wants. Hard to imagine how a beautiful face like that can be so brash
and brutal. Unbelievable, I tell ya."

"Nezumi only speaks the truth."

No matter how harsh or ruthless his words were, they never carried any
lies. That was why they became blades and spears that pierced Shion's
chest, and left a pain that he could not forget. It was a pain that he
would never have known if he had not met Nezumi. Every time the
countless pangs stirred restlessly deep in his chest, Shion felt
something in himself changing little by little. A part crumbled away,
while another part rebuilt itself; and yet another part would be born
anew. Each word from Nezumi, and the pain that accompanied it led Shion
to change, and kept urging him forward. Shion could vividly feel himself
being changed and shaped by the force of another.

"You know, Shion. If it gets too unbearable, you can stay over with me,"
Rikiga said as they walked side-by-side. His breath hit Shion's cheek,
and reeked of alcohol.

"Unbearable? What do you mean?"

"No, I understand," Rikiga said abruptly. "You don't have to hide it. I
can't imagine how it \emph{wouldn't} be unbearable living with Eve. I'm
guessing your living conditions are less-than-standard. Are you getting
enough to eat? Now, I think this highly unlikely, but if in some nasty
turn of events, you get influenced by Eve and your personality gets as
twisted as his--- hm," he grunted to himself. "Indeed. There's no way I
can let that happen to Karan's son. Come live at my place. I'll give you
enough to eat, and give you a warm bed to sleep in."

"No, that's alright. I'm fine."

"But Karan sent word to come to me for help, right?"

"Yes, but I don't want to be a burden on you, Rikiga-san," Shion
insisted. "I'm fine. I've managed until now, and I'll keep managing. And
I actually enjoy being around Nezumi."

"There's no way you'd enjoy being around an ass like him. You don't have
to put on a brave face. You're having a hard time, aren't you? Look,
you're not even wearing a sweater. You poor kid."

"Oh, no, I'm just using my sweater to wrap my meat and bread---"

But Rikiga wasn't listening to Shion's answer. He was glancing at his
surroundings, and nodding fervently to himself.

"I know a good store. Let's go there." He yanked Shion by the arm, and
walked into a shop that was lined with an enormous quantity of clothes.
It looked like a used-clothing shop, and there were garments even
hanging from the ceiling. The clothes ranged from well-worn to almost
new.

"G'day." A woman almost as large as the shopkeeper from the kebab stand
materialized out of the shadows of a mountain of clothes. As soon as she
noticed that Rikiga was her customer, she pasted a bright business smile
onto her face.

"Whah, Mr. Rikiga. Nice to see you again," she drawled. "If you're
looking for a dress to give to someone, we've got some very good ones,
we do. One of these would leave her pleased as punch, yessir."

"No, I'm not looking for women's clothes today," replied Rikiga. "Can
you find something warm that would look nice on this boy here?"

The woman's eyes narrowed, and her gaze raked Shion from head to toe.

"Whah, what an \emph{adorable} gentleman we have heah," she said
appreciatively. "And mah, what bee-yootiful hair. Is it fashionable with
young people these days?"

Shion pulled his wool hat further down over his eyes. His glossy white
hair stood out, even in the dim darkness of the shop. When the parasite
wasp had hatched inside him, as the price for his survival or some sort
of side-effect, Shion's hair had been drained of its colour in a single
night, and a red scar had appeared on his skin, snaking its way up from
his leg to his neck. He could hide his scar with clothing, but with his
hair, it wasn't so easy. His snowy hair and youthful face were an
unusual combination, and drew stares wherever he went. In the West
Block, it wasn't particularly out-of-place for young people to be
balding or have greying hair from malnutrition. There were many children
that had salt-and-pepper hair which would otherwise be more common to
those entering their senior years. But those like Shion, whose every
strand of hair was pure white and shiny, was a rarity.

"It's more transparent than white, I'd say. I think it looks way
prettier than before, to tell you the truth." Even Nezumi had said so,
while touching his hair with his fingertips.

"Is he your boy? Highly unlikely, Ah'd say," the women remarked, her
artificial smile still plastered to her face as she gazed at Shion. He
felt like he was being sized up. It was a little uncomfortable.

"Rikiga-san, um, I really don't need any winter clothes, can we just---"

"Nonsense," Rikiga interrupted. "Winters here are harsh. You've got
barely enough flesh on those bones to get you through. You need some
good, warm clothes to keep the cold out. Well?" he said impatiently to
the shopkeeper. "Are you going to put out some clothes or not? If you're
not, I'll take my business elsewhere."

Under Rikiga's glare, the woman sprang hastily into motion.

"Whah, of course Ah will. We've actually just gotten a shipment in. Just
a momen' now." The woman heaved an armload of clothes from behind a
dirty curtain.

"There y' go. Choose any one you like. They're all \emph{excellent} qualitay."

Shion had his doubts about whether they were of \emph{excellent qualitay} or
not, but there was certainly a variety of garments. There were
overcoats, half-coats, sweaters, heavy shawls, and sports jackets of
every size, material, and colour, all heaped high.

"Guess you just have to look in the right place," Shion muttered to
himself. Here was a wealth of clothing, where just down the road there
were people clad in rags, shivering in the cold. Even in a severely
impoverished place like the West Block, there was still a stark divide
between the poor and privileged.

"Shion, you don't need to be modest. Pick anything that catches your
eye."

"But Rikiga-san, there's no reason for you to be so good to me---"

"Don't worry about it. You're Karan's son--- and to me, that sort of feels
like you're my son too. Think of it as a kind of treat from your dad."

Shion blinked, and gazed into Rikiga's flushed face. It looked like his
drinking had done away with some of his inhibitions; what he was saying
now was probably close to how he truly felt. Perhaps Rikiga had lived
alone all this time in the West Block, with no family. And now, he was
trying to re-enact the sort of family life he never had, with the son of
a woman he had once loved. Freedom and loneliness. He had the cunning it
took to succeed in the underground business with No.~6 officials as his
patrons; but he had the frailty of one who had wearied of living too
long in solitude.

Humans were complex. They housed in themselves both resilience and
frailty; ying and yang; light and shadow; sacred and sinful. Here was
the true form of a human that Shion would never have been able to map
from the vast sea of knowledge he had acquired in No.~6.

What he knew of the human body --- of roughly 32,000 genes; approximately
100,000 different kinds of proteins; 300 million base sequences of DNA;
its neurons; collagen fibres; macrophages; the layered structure of
muscles; the volume of blood in circulation --- he didn't think any of it
a waste. He didn't think so at all. But \emph{understanding} a human being was
an entirely different dimension. It was impossible to grasp any of the
complexity or true form of a living being from systematic knowledge or
information that could be converted to numbers.

It was something that Shion had learned from his days of living with
Nezumi on this land.

"Well, in that case, I guess I'll choose freely."

"That's more like it," Rikiga said jovially. "Which one do you want?
Find anything you like?"

Shion pulled out a dark, heavy coat.

"I'll take this one. It looks warm."

"Are you sure you want something that dull? Alright, then pick a flashy
sweater. You're young, you'd look better in bright colours."

"No, really---" Shion protested, "I don't need so much."

"Nonsense. The coat by itself isn't going to keep you warm enough."

"Ah'd say so too mahself, sir," the woman chimed in. "Our sweaters are
\emph{very} warm, see. Whah don't you trah some on?"

The woman confidently yanked a sweater out of the pile. The mountain of
clothes collapsed, and spilled in an avalanche over the floor.

"Oh, mah. \emph{Well.} Ah \emph{do} apologize---"

Rikiga clicked his tongue in annoyance.

"\emph{What} are you doing?" he said irritably. "Now we can't even choose from
this mess. Ridiculous, huh, Shion." He paused. "Shion --- what's wrong?"

Although Rikiga had spoken right beside him, his words did not reach
Shion's ears. His gaze was glued to what had appeared underneath the
scattered garments. All sound and colour disappeared from around him,
and only that thing rose up into his vision.

It was a grey half-coat.

The soft colour, with a hint of blue; its premium quality obvious to the
touch; the large buttons on the cuffs of the sleeves --- he had seen them
before.

"This is---" His hand trembled as he grasped the coat. There was a rip in
the shoulder that had been sewn up crudely with black thread. There was
also a button missing, which looked like it had been torn off. His hands
shook violently. He wanted them to stop, but they would not.

"That one capture your fancy? Ah, but this is ladies' coat, see. The
very best qualitay, of course --- but maht be just a \emph{little} snug on you,
sir. Ah don't think it would fit. The last coat, the black one, that
would look much---"

"Where did you---"

"Ah beg your pardon?"

"I'm asking you where you got this from!" He was yelling. He had no
intention of intimidating the woman, but she raised her eyebrows in
surprise, and took a step backwards.

"This coat--- where--- where did you get it?"

"Shion!"

Rikiga clamped a hand on Shion's shoulder from behind. "What's wrong?
What are you getting all worked up for? What's wrong with the coat?"

Shion swallowed hard, and clenched the coat in his hands.

"This belongs to Safu."

"Safu? Who's that?"

"My friend. My\el very precious\el "

"Friend? You mean, from when you were still inside the city?"

"Yes."

"Are you sure it's not a mistake? There must be dozens of coats that
look like this."

Shion gritted his teeth in hopes of stopping the trembling in his
fingers, and shook his head from side to side.

It was no mistake. This was Safu's coat. It had been a gift from her
only blood relative, her grandmother, and even for a boy like Shion, he
could tell that it was an elegant and becoming piece that complimented
Safu's well-defined face.

"Your Grandma must really know you well, Safu. She always chooses things
that look the best on you," he had said.

"Yeah, I guess so. I mean, she's raised me all my life, after all. Hey,
Shion--- if you were to give me a coat, what kind would you give me?"

"What? I'm sorry, but my wages are never gonna be able to get you a coat
as nice as that one."

"I'm just saying, 'what if'? I want to know what you would choose."

"Hmm, tough question."

"Well, think hard. Solving difficult questions is your thing, isn't it?"

Last year, they had walked down a winter path holding this kind of
conversation. The rays of the winter sun had streamed through the bare
branches and shone down on Safu, making her coat glow dimly. That was
the first time he had thought his childhood friend looked beautiful. The
wintry sun, the warm smile, the grey coat. It was Safu's. He was sure of
it.

\textbf{\emph{Why--- what was this doing here? Why, why, why\el }}

"\emph{Why?}" Shion pressed urgently. "Where, and how did you get this coat?
Tell me, please. Now."

"Shion, calm down." Rikiga stepped out in front of Shion, and blocked
the woman's way. "So, what route did you ship this in through? Did it
find its way here from No.~6, or---"

The woman's face had long been wiped clean of its plastic smile.
Instead, it was filled with bold and disdainful suspicion.

"Whah, I \emph{never}. Here Ah am, bein' polite for \emph{you}, Mr. Rikiga, and what
do Ah get in return? Is it any of your business where Ah get mah things?
Or what is it--- plannin' to find all the faults you can with mah goods,
and get them for cheap, Ah suppose? This is no joking matter, no, this
\emph{is} not. Ah'm not laughing one bit."

"What the hell would I be doing wanting to make you laugh?" Rikiga
snapped. "I can assure you the chances of that is slimmer than a hair on
my head. Why aren't you talking? What are you being so cautious for?
It's that risky, is it, wherever you're getting these shipped from?"

The woman opened her wide mouth and let forth a stream of indignant
complaints.

"Tha's \emph{quite} enough. Ah'll have you know Ah run a \emph{decent} business 'round
these parts. If you've got somethin' to complain about, you can show
yourself the door. Git out, Ah say. Go home!"

Before she could finish, Rikiga had twisted her arm behind her back, and
pinned her down on the counter.

"What the hell are you doin'? You dirty littl' bastard!"

"If you don't want your arm broken, you better spit it out," Rikiga said
darkly. "How did you get this coat?"

"Ah got it from the waste disposal plant in No.~6. Picked it up 'cause
it was floatin' in the sewage. Thas' all, mercy, Jesus!" She winced in
pain.

"There was sewage coming out of that place? I don't think I've heard
anything about that."

"Thas' whah Ah'm sayin', it was a long time ago --- does it matter,
really? They threw 't away 'cause it was garbage, Ah'm free to do
whatever Ah want with it. It's nobody's business, 'specially not yours."

"You're lying!" Shion yelled. "That's a lie! This coat was important to
Safu. She would never throw it away!"

"What's the noise about?" A door at the back of the store opened, and a
man walked in. He was a giant --- at least two metres tall in height. It
looked like he weighed at least a hundred kilograms. His head was
completely bald, and his face was strangely twisted. Despite the season,
he was only clad in a short-sleeved T-shirt. Tattoos of a scorpion and
skull decorated his thick arms.

"You're back, and just in tahm. Will you kick these two out of here?"
The woman smiled contemptuously while still being pinned by Rikiga.
"Ah'll have you know that mah husband's got mighty strong muscles in
them arms. Could sure break a neck or two 'fore breakfast. Ah'd git
outta here if Ah were you, 'fore you end up dead."

Rikiga let go of the woman, and shrugged his shoulders casually.

"Well?" said the woman impatiently. "What're you dawdling for? Beat 'em
'til they can barely stand, go on."

The man remained silent. Then, without uttering a single word, he bowed
his head low.

"Long time no see, Conk," Rikiga said momentarily. "Didn't know you
settled down. So you're the hubby of a clothes-dealer now, huh?"

"Got married a month ago," the man mumbled.

"Well, well. Congratulations. Will you be kind and ask your beautiful
wife where she got this coat? She's got a lot of spunk, this madam of
yours. Having a hard time getting the truth out of her."

The man whom Rikiga called Conk stared intently at the coat in Shion's
hands, and turned to the woman.

"Tell Rikiga-san the truth."

"Whah, whas' gotten in to you all of a sudden? What do you have to
listen to them for?"

"Rikiga-san was good to me a long time ago. Hurry up. Say it."

Under Conk's threatening gaze, the woman's face twisted into a scowl.
Still scowling, she turned her face away huffily.

"Ah jus' bought it off some middleman. Ah dunno where \emph{he} maht've gotten
it."

Rikiga clicked his tongue.

"Liar. There's no way you wouldn't know where your merchandise came
from."

"Ah don't know what Ah don't know," the woman said stubbornly. "No way
Ah would."

Rikiga posed another question while restraining Conk, who had taken a
step forward with a clenched fist.

"Then tell me who that middleman is," he said. "I'll be able to figure
out the rest."

The woman didn't answer. Rikiga extracted a few bills from his breast
pocket, placed them in the woman's hand, and closed her fingers around
them.

"You were talking to yourself, and you let the middleman's name slip. We
just happened to overhear. We'll keep it that way. I won't cause you
trouble."

The woman glanced at the bills in her hand, and with her face still
turned aside, mumbled an answer.

"It's the dogkeeper. That weird squirt who uses his dogs to do
business."

The dog curled up at Shion's feet pricked its ears. Rikiga gave a low
growl.

"Inukashi, huh. Then it must've come from the Correctional Facility."

"Correctional Facility?" Shion echoed in disbelief.

"Yeah," said Rikiga. "I heard the kid passes prisoner's belongings along
to the underground market."

Shion's heart stopped. Or at least, it felt like it did. He couldn't
breathe. There was a dull ringing in his ears.

Correctional Facility, prisoners, Correctional Facility, prisoners,
Correctional Facility\el 

"Then Safu\el she's inside the Correctional Facility?"

"Most likely," Rikiga answered heavily. "And she probably hasn't been
invited cordially as a guest, either. She's probably been taken into
custody--- treated as a prisoner, no doubt."

Shion burst out of the store with the grey coat in his arms.

He had to see Inukashi immediately. He had to learn the truth from him.

"Shion!"

Behind him, Rikiga's yell scattered on the wind and dispersed
fruitlessly into the air.

\mybreak

The man was walking strangely, and he had been doing so for some time.
He stumbled on unsteady feet as if he were drunk.

Twelve-year-old Juse tilted his head in bewilderment as he dismounted
from his bicycle. Off to the left, he could see the apartment building
where he and his family lived. He was in a corner of a park, one of many
that dotted the residential area. Although it wasn't as large as the
Forest Park, it was nevertheless a peaceful alcove abundant in greenery.
Juse pushed his bicycle along --- a crossroad bike he had gotten for this
twelfth birthday from his father --- and followed the man with his gaze.
He couldn't help but be concerned; he couldn't just leave the man there.
His mother was always lamenting this habit of his. 'Don't get involved
in other people's business,' she would say. 'You seem to want to stick
your nose into everything, Juse. I wonder if you've gotten it from your
grandfather.' But if he \emph{had} gotten it from his grandfather, for Juse it
would have been the best thing he could ask for. He always thought so in
his heart.

Juse loved his grandfather. When Juse was still young, his grandfather,
who had once been a sailor, would always sit Juse on his lap and tell
him stories. He spoke of the sea, which Juse had never seen before; of
great white whales that were as big as mountains; lands that were
suspended year-round in snow and ice; flocks of tens of thousands of
butterflies that streamed across the sky in one large flowing mass;
giants that lived above the clouds; mysterious creatures that lived deep
beneath the sea; faeries; magic; ancient wars of the gods --- his mother
hated it, but there was a time in Juse's life when he became completely
engrossed in the stories that his grandfather would tell him.

He grew up, and not long after he began attending an institution
selected by the Education Bureau, he received a formal reprimand from
the instructor that he had delusional tendencies. He was told that this
was a concern for his future. His mother broke down in tears, and his
father reeled from the blow. Juse was streamed into the Special Program
and received special instruction for a full year. It was mandated to
him, and he was not given a choice. All the old books he had borrowed
from the shelves of his grandfather were disposed of. And a few months
later, his grandfather disappeared altogether. He had been taken to the
Twilight Cottage. Juse always heard from people how it was the greatest
happiness any elderly person could ask for, but he himself cried in bed
for many nights from the loneliness of never being able to see his
grandfather again. And on nights where he cried himself to sleep, he
always dreamt of the stories his grandfather used to tell him.

A year later, Juse had stopped talking about great white whales, or
faeries with transparent wings. The adults sighed breaths of relief. But
in the depths of the boy's soul, the stories remained secretly alive,
and breathed within him. He would never be able to wash them away.
Perhaps that was why he found himself still concerned about other
people, even now. He couldn't help but wonder, \emph{what does this person do?
What's he feeling right now?} But he had also acquired the sense not to
say it out loud.

"Oh---!" Juse cried out softly. The man had collapsed at the foot of a
beech tree. The man groaned in pain. Juse left his crossroad bike and
trotted to the man's side. He thought he saw something black fly away
from the man, who was lying face down. Juse didn't have the time to
check. The man's body had begun convulsing, but soon lay still.

"Um--- sir---"

Juse called out to him hesitantly. He peered into the man's face. The
next moment, Juse was screaming.