% !TeX spellcheck = en_US

\chapter{That which I say I saw}

\myepigraph{Gracious my lord,\\
	I should report that which I say I saw,\\
	But know not how to do it.}{\emph{Macbeth}, Act V Scene V}

\lettrine{T}{hey were} falling. Falling, almost straight down.

It was faster than anything Shion had imagined. He knew it was
impossible, but he heard the sound of the wind. It was the same wind
from that stormy night.

It was September 7, 2013---Shion's twelfth birthday. The Holy City of No.
6 had been directly hit by a hurricane. The rain was pounding on the
ground, and the wind was roaring. The trees in his yard careened wildly,
and leafy branches broke off and whipped through the air. It was an
extremely large and severe hurricane, a kind not seen in recent years,
but he was sure that no one living in Chronos felt threatened or
anxious. Shion and his mother, Karan, had been the same.

This was No. 6. A utopian city, the results of human wisdom and
cutting-edge technology. And in that utopia, Chronos was in the highest
ranks among the luxury residences, a town where only the chosen ones
were allowed to live. Mere natural disasters could not disturb it.

Everyone had believed so without a doubt. They had been allowed to
believe otherwise.

That stormy night, I opened my window.

\emph{Why?} he sometimes thought. \emph{Why did I open that window? Was it because I
was excited at nature's madness, and I was stimulated, or I was stirred
by a violent impulse---was that it? I certainly did open the window, and I
yelled. I screamed as if I were pouring out all of the ferocity inside
me. If I didn't scream, I felt like I would shatter to bits. In my own
way, I felt a fear that I would be entrapped and tamed into domesticity
by No. 6.}

\emph{A vague fear---maybe something that you wouldn't be acquainted with,
Nezumi.}

\emph{I felt like I was suffocating. I was scared. I wanted to scream.}

\emph{That was why I opened the window---wasn't it?}

\emph{No.}

\emph{That's not it.}

You called to me.

\emph{I heard that voice---your voice---calling me.}

\emph{It ducked through the wind, tore through the rain, and came to me.}

\emph{You called me, and I was called by you.}

\emph{That's why I opened the window. I flung it open wide to the outdoors.}

\emph{I extended my arms in search of you.}

\emph{Would you laugh? Would that breathtaking smile cross your face as you
sneer at me? Would you shake your head with exasperation in that
graceful way of yours?}

\emph{'Meaningless fancies. An intolerable mass of self-consciousness, like a
half-baked artist's work'---would you spit those words at me? You probably
would. Go on and laugh. You can dismiss them as my delusions; I don't
care.}

\emph{But it's the truth.}

\emph{You called me, and I listened. I reached out, and you caught my arm. I
opened the window so I could meet you.}

\emph{That's our truth, Nezumi.}

A noise was ringing in his ears. It wasn't the whirl of the wind. It was
the sound of sliding through a plastic tube. But what if this tube was
not a garbage chute, but a steep slope that led straight to Hell?

Suddenly his consciousness began to fade. All the wounds he had suffered
on his entire body grew hot and throbbed. The strength left him.

\emph{Going to Hell doesn't seem so bad when it's with you. Should I stop
resisting, then? Why don't I just give up on struggling, on fighting, on
wanting to live?}

\emph{If I let myself black out now, I'll be free from this pain, this
weariness.}

Shion closed his eyes. Darkness fanned out before him.

\emph{Just like this\el just like this\el }

"Ugh," Nezumi groaned softly. It stabbed Shion's eardrums. Like
lightning flaring up in a night sky, it tore the darkness away from his
consciousness.

\emph{Damnit.} Shion bit his lip and inflicted pain on himself. He scolded
himself severely. \emph{You bastard, what were you thinking? You can't give up
now. Live. Survive. We have a place to return to, and we have to get
there in one piece.}

He had made that vow. He had vowed to himself that he would protect
Nezumi through to the end, and survive this ordeal together.

His hand slipped. Nezumi's blood was caked on his palms. A black mouse
leapt out of his pocket and ran along the garbage chute wall. It wasn't
falling; it was definitely running.

\emph{Tsukiyo, I'm counting on you. Tell Inukashi that we're alive.}

Shion jammed both feet against the wall and gritted his teeth. He
focused all the strength in his body on his legs. His bones creaked.
Their falling speed decreased somewhat. His bones continued to creak as
if they were screaming from the pain.

\emph{Damnit, I won't give in yet.} Shion chewed his lip still harder. He did
not taste the blood. His tongue was already numbed to its rusty metallic
taste.

\emph{Inukashi---Inukashi, help us.}

\emph{Inukashi!}

\myspace

Rikiga fell into a fit of coughing. He recovered and breathed raggedly.

"Inukashi, I can't do it anymore. I'm at my limit."

"Limit of what?" Inukashi said tersely.

"I can't breathe. Are you planning on suffocating me like this?"

"What good is it to me if I suffocate you, old man? You gonna leave me a
giant inheritance? The most you'd probably leave behind is a pile of
empty booze bottles."

"Hmph. See if I even leave you that."

But even while griping, Rikiga did not try to flee. He was still
stacking mattresses under the opening of the garbage chute. With each
mattress he stacked, he had a coughing fit, gasped and wheezed, and
griped some more.

Smoke had saturated the hygiene management room. The collection area was
no exception; it was almost engulfed by thick, grey smoke. The dogs lay
low on their bellies, their breathing hushed. Even the little mice who
had been squeaking clamorously at each other were now huddled
motionless.

The limit---Rikiga was right, the limit was near. Inukashi himself was
choking on the smoke, and the air wasn't passing through his throat
well. His heart pounded frantically.

\emph{It hurts.}

\emph{The air is stuck in my throat.}

But he was not miserable. He was not in despair. On the contrary, a part
of his heart was pounding, soaring in anticipation.

\emph{What is this smoke? This hot air that blows at me from time to time? The
restless buzz that comes with its snarl?}

\emph{A clear precursor to destruction. The Correctional Facility is raising
its last dying shriek.}

Many times Inukashi felt like barking out of excitement. He wanted to
bark and howl until his throat trembled. Just once, he opened his mouth
wide, but he only choked on the smoke that rushed into his mouth.

He licked his lips while carrying the mattresses. \emph{If I can't bark, the
least I can do is lick my chops.}

What he thought was absolute was crumbling before his eyes.

\emph{Will you look at that. Is that what life is, Nezumi? Shion? If it is,
that means you guys taught me what it is to be alive. You never know
what happens. There's nothing absolute about what humans create.}

\emph{I won't thank you; you guys have caused me too much hassle. You'll never
hear a word of thanks come out of my mouth.}

\emph{But I owe you praise. I'll give you my best compliments. I'm actually
impressed that you guys turned out as decent as my dogs are. You guys
are really something. I have new regard for you. I'm impressed---just a
tiny bit.}

The smoke assaulted his eyes, his throat, and his nasal passage. A tear
rolled down his cheek. It was just the smoke stinging his eyes.

\emph{You come back, you hear me? If you don't, I can't praise you. Hurry,
hurry, while my breath can still last me. Hurry.}

\emph{Inukashi!} Someone called him. He whirled around. Rikiga was kneeling on
the floor. He was holding a white cloth to his mouth, and coughs were
racking his bent back.

"Call me?"

"---What?"

"Did you call me, old man?"

"What would I\el do that for?" Rikiga wheezed. "You want me to\el give
you one last kiss or something?"

"Knock it off. That's creepy, even for a joke."

"I'm\el past the point of\el caring whether it's creepy. Really, I
can't\el stand this anymore\el "

"That's a shame. My heart goes out to you, man. But it's a bit too late
to repent. A man as corrupted as you isn't gonna get any closer to
Heaven, no matter how hard you try."

"Damnit\el still smart-mouthing me\el are you?"

Explosions. Smoke pouring into the air. The dog with patched fur raised
its head. Terror swam in its eyes. But the dogs did not move. They did
not try to flee.

\emph{They're waiting for my orders.} They were waiting for Inukashi's command,
fighting their fear of death. Dogs never abandoned their master. They
never betrayed him.

\emph{I can't murder them like this.}

"Go." Inukashi pointed at the entrance door. "Escape by yourselves."

But the dogs did not get to their feet. They remained lying on their
stomachs, watching Inukashi.

"What? I'm telling you to leave. Get out of here, quickly." He met the
eyes of the patched dog. Its eyes were serene. The shadow of fear that
had crossed his eyes moments ago was wiped cleanly away.

"I see\el " \emph{You won't move if your master doesn't.}

"Aren't you gonna\el tell me?" Rikiga coughed and wheezed. "Aren't you
gonna\el tell me to run?"

"You? You can get the hell out of here if you want to. You wouldn't be
any use if you stayed."

"Inukashi."

"What?"

"Do you\el plan to die here?"

"Die? Why would I?"

"There's barely any\el chance that those two\el Shion and Eve\el are
going to come back. If you're gonna gamble on that slim chance\el if
you're gonna gamble and choose to stay\el that's like killing yourself."

\emph{No way. Heaven and earth can turn upside-down, but I'm never gonna kill
myself. I'd be missing the spectacle of a lifetime.} The destruction of
the Correctional Facility was only the beginning. It was only the
preamble. The devastation of No. 6 itself was what came next.

No. 6 was falling apart.

\emph{I'll get to see the very moment with my own eyes. And you're telling me
I intend to die? You must be kidding me. You bet I'll live to see No.
6's last. I'll thoroughly enjoy its final act.}

\emph{Heh heh heh.}

Lighthearted laughter rang at his ear. No, it was in his ear---inside his
head. Someone was laughing. It was carefree and joyful, yet an icy
laughter.

"Who is it?"

His gaze darted about instinctively and caught a small black shadow
passing by.

\emph{A bug?}

The shadow was soon swallowed up by the smoke as it disappeared. The
laughter ceased. \emph{Were they both hallucinations? There's no way a bug
could be flying around in this smoke.}

\emph{Shiver.} A chill ran down his spine.

\emph{Screech, screech, chit-chit!}

\emph{Cheep-cheep-cheep-cheep-cheep. Squeak!}

Suddenly, the mice began to cause a commotion. They raised their voices
again, but much higher this time, and dashed around on top of the
mattresses.

Inukashi held his breath.

A small object came tumbling out of the chute. It was not trash. It was
a small black mouse.

"Tsukiyo." Inukashi tried calling it. The black mouse flew through the
air; it leapt straight for Inukashi. It latched onto Inukashi's hastily
extended arm, and squeaked insistently.

\emph{Cheep cheep cheep cheep! Cheep cheep cheep cheep!}

It was Tsukiyo; there was no doubt about it. It was the same little
mouse that Inukashi himself had commanded to go to Nezumi. His blood
stirred. His body grew hot.

"Wake up, old man."

"Eh?"

Rikiga blinked feebly, still squatted on the ground. His eyes were
bleary and red. His face was sooty, his hair was mussed, and he looked
like he had aged a good decade.

"They're coming back."

"Eh?"

"Coming back. Hold onto the mattresses."

"R-Right." Rikiga got to his feet in a surprisingly swift move.

The wind was howling.

As Inukashi and Rikiga held the mattresses down, they felt a heavy
impact almost simultaneously. The mattress sank, almost sending
Inukashi's slender frame flying. He summoned all the strength in his
body to cling onto the mattress.

He had instinctively closed his eyes, but now he opened them carefully.
He saw two bodies lying in a heap.

"Shion, Eve!" Rikiga yelled before Inukashi could speak. "You alright?
Hey! You alright?"

"Gh\el " Shion's arm jerked. A part of his white hair was dyed with his
blood. Blood was streaming from his shoulder and his leg. His clothes
were torn, ripped, and hanging in places. Inukashi couldn't tell if the
dark flecks all over his clothes were from blood or the trash in the
chute.

\emph{Horrible.} Inukashi kept his eyes wide open as he swallowed his spit,
which smelled like smoke. \emph{You guys are a mess. I think even the undead
would look a bit better crawling out of their graves.}

"\el Inukashi." Shion lifted himself up and turned his face to Inukashi.
His cheeks were streaked---whether it was with sweat or tears, he didn't
know, but they engraved prominent marks on his skin.

"Shion, you're alive." \emph{You made it back alive.}

"Inukashi, save Nezumi\el "

"Nezumi? What about him? What---" Inukashi was barely able to hold in the
scream that threatened to burst from his throat.

Nezumi was lying on the mattress, totally still and unmoving. His
clothes were soiled reddish-black from his shoulder to his chest, and he
gave off the smell of blood.

"Nezumi, hey, what's wrong?" Inukashi asked tentatively, but there was
no answer. On his pale, bloodless face, only his lips were vividly red.
To Inukashi, they did not look human at all. Nezumi had always had a
face that was somewhat otherworldly, but the face in front of him was
one of a doll. A skillfully and meticulously crafted piece.

\emph{But dolls don't bleed.}

"To the hospital---hurry," Shion screamed, as if wringing the voice from
his throat. Explosions rocked the foundations of the building. The whole
room shook with its impact. A draft was coming in from somewhere, and
the smoke wavered and thinned slightly. The shaking did not stop.

"We need to get out of here! This place is coming down!" Rikiga yelled
as he wrenched Nezumi away from Shion's arms. He slung the boy over his
shoulder.

"Shion, can you run on your own?"

"I can."

"Right, then run. Get outside."

One more sound, more violent than before, rang out, and the door to the
Correctional Facility was blasted away.

"Run, run! This place won't hold much longer!"

Rikiga broke into a run, bearing Nezumi. Tsukiyo dove into Shion's
pocket, and the two mice, Hamlet and Cravat, leapt onto a dog's back.

"Get out, goddamnit! Get out of here!" Rikiga's bellows slammed into
him.

His back was blistering hot. Inukashi turned around to the flames
filling his vision. Beyond the blown-open door, the Correctional
Facility was burning.

\emph{The door blew apart? Wasn't the door between the Correctional Facility
and the Hygiene Management Room supposed to be made of some special
alloy that even a small missile couldn't penetrate? And it's been blown
apart like it's nothing?}

For less than half a second, he stood stupefied. Flames slithered. A
fire-coloured monster was writhing on the floor. It writhed and twisted
towards the corpse of the black dog and swallowed it whole. It was the
same dog that had been shot to death protecting Inukashi, but Inukashi
was unable to give it a proper burial.

\emph{Sorry.}

"Inukashi, hurry!" Shion grabbed his arm.

"Get out, get out! We have to get out of here!" Rikiga continued to
bellow. He seemed to be turning his yelling into energy to move forward.
Inukashi was pushed along by the heat and the hot air from behind, and
quite literally stumbled into the outdoors. Fresh air flowed into his
body.

\emph{Oh, I can finally breathe.}

"Not yet. We can't stop yet. Keep running." Shion's grip tightened.
Inukashi was dragged along by his arm. The gravel crunched under his
feet.

"Ow! Shion, that hurts! Stop---" Inukashi abruptly closed his mouth. His
eyes had met with Shion's.

His eyes, dark with a wash of purple, were the same as always. They were
completely unchanged. They were bloodshot, and the eyelids were swollen,
but they were Shion's eyes.

Yet Inukashi closed his mouth and felt his body stiffen. He did not know
why. The boy in front of him telling him to run seemed a complete
stranger. He was someone Inukashi did not know.

\emph{No. Those aren't Shion's eyes. Shion, what's gotten into you?}

But the confusion and foreboding vanished in an instant. Shion was
right---he could not fall to his knees just yet. His instincts sounded the
alarm. This physical sensation was much more reliable than any
cutting-edge security device.

\emph{Get out of here, run. Get out of here.}

Inukashi leapt to his feet, and ran as fast as he could. From behind, he
could hear the roar of a beast. Yes, those were not just explosions. A
monster was baying. It was raving madly.

\emph{Get out of here, run. Get out of here.}

\emph{Run and survive.}

Tsukiyo had crawled out of Shion's pocket and was clinging onto his
neck. It had opened its tiny round eyes as wide as it could, and was
staring over at Inukashi.

\emph{You're kinda cute.}

Dogs' eyes and mice's eyes were alike, and all such innocent beings were
loveable. Inukashi thought of Shionn. He had not forgotten about him for
a moment. He had only pushed the infant to a corner of his heart so as
not to remember him when he was not supposed to.

Shionn was innocence itself. He was so small, yet he had so much inside
him.

\emph{The dogs are probably managing alright. I left him with a dog that's
birthed and raised a ton of her own puppies. Apart from her, there are a
few other caring females in waiting. He's probably sleeping right now,
protected by his loving nurse.}

"Shionn, my baby," he murmured. Just then, Rikiga, who had been running
in front of him, disappeared. He heard a shout, and the sound of a body
falling over.

"Whoa!" Shion tripped over Rikiga's fallen body. In turn, Inukashi's
feet were swept from under him by Shion, and he was slammed to the
ground. The pain racked him to his very core.

He could not speak. Lying on his stomach on the ground, he could only
draw strained breaths. He could feel the frozen ground on his cheek. It
was soothing. It had not the iciness of winter, but a cold that
harboured a faint hint of warmth and softness.

Spring was coming. A late spring was starting to arrive in the West
Block.

No. 6 was probably fully furnished with flowering parks and streets
lined with cherry blossom trees, but one would be hard-pressed to find
even a single flowering tree in the West Block. But the weeds growing on
the shoulders of the road faithfully opened their petals year after
year. Flowers usually sparked no interest or intrigue in Inukashi since
they were not edible, but once in a while they pulled at his
heartstrings.

\emph{Oh, I've lived through another winter}, he would think. Then, for a
fleeting instant, in the back of his mind he saw faces of those who had
frozen to death that winter---the old beggar lady he had been familiar
with; the man who had hung around the ruins for a good while; the woman
who was so emaciated, it was hard to tell her age---but they disappeared
as quickly as they had come.

Spring was coming. Would those flowers bloom again on the side of the
road?

"Nezumi," Shion gasped. He lifted himself up, and crawled over to
Nezumi's side. "Nezumi, Nezumi. Can you hear me? Nezumi---"

Inukashi also lifted himself up. They were lying in the shadow of some
shrubbery. When was it that he had hidden himself here, witnessing
Getsuyaku being shot to death?

It felt like it had happened only minutes ago, but at the same time a
thousand years back.

"Nezumi, open your eyes. We're out. We were able to get out."

Shion's voice sounded like the wind that whistled through the ruins. It
was mournful. It froze the hearts and ears of those who listened.

Inukashi peered over Shion's shoulder at Nezumi's face, and compressed
his lips into a hard line.

\emph{Is he dead?} The statement pushed his lip up and threatened to spill out.
\emph{Shion, is Nezumi dead? Or is he just acting? Who's he playing? Macbeth,
Hamlet, or some other weird name that you guys used to mention?}

\emph{Hey, Shion. Don't tell me Nezumi is really---}

"Gh---" Nezumi's eyelashes trembled very slightly.

"He's alive," Shion shouted as he lifted Nezumi in his arms. "He's
alive! Hurry, to the hospital!"

\emph{Yeah, you're sure alive. You can't trick me, Nezumi. There's no way you
would be wiped out that easily.}

"Old man." Inukashi called to Rikiga, who was squatting on the ground.
His car was parked beyond the shrubs. It was a piece of junk, a step
away from scrap metal, but it could still chug along with a couple
passengers. They had taken this gasoline-fuelled car to get here, after
all.

"Old man, hurry up."

"---I know, but---"

Rikiga held a hand to his mouth, and stuck his head into the bushes. The
sound of retching reached them.

"Dumbass! This is no time to be puking! Hurry the hell up, come on!"

Inukashi grabbed the man by the belt of his trousers and dragged him out
of the bushes. Almost as if in answer, an even larger flame burst out of
the window of the Correctional Facility. It threw a bright light on the
surroundings. Black smoke formed a thick stream as it rose into the sky.
It engulfed and blacked out the stars.

\emph{Can you see these flames from No. 6, too? What would West Block
residents be thinking right now as they watch the flames burning the
night up?}

\emph{Look at it, it's falling. A place that used to mean Hell for us is
collapsing. It's gonna be wiped out, just like that, even quicker than
our marketplace.}

Rikiga got to his feet unsteadily. He wiped his mouth with the back of
his hand, and wiped the sweat on his brow while he was at it.

"Why do I\el have to go through this? Besides, you know, I---"

"Enough crap," Inukashi interrupted. "No one's listening. If you've got
time to bitch and moan, get the car moving."

"Moving where?" Rikiga snarled. "Eh? Answer me this, Inukashi. Where are
we going to take someone who's hurt so badly he's as good as dead?
Answer me, I'd like to see you try! If you can give me an answer, boy,
I'll take you wherever the hell you want."

Inukashi drew his chin back and fell silent. He could not answer.

He was not intimidated by Rikiga's angry outburst. He genuinely did not
know. 'To the hospital,' Shion had said, but there were no medical
facilities in the West Block. There were seedy witch doctors and
questionable medicine shops, to be sure, but they had all been blown
clean off their foundations during the Hunt. But even if they were still
around, they would probably not have been of much use.

Rikiga continued his furious tirade.

"Someone who's bled this much is going to need a decent amount of
medical equipment. Where do you suggest we find that, huh? Nowhere here,
for sure. You can scour the whole West Block and you won't find a single
damn syringe. You should know that best, Inukashi."

Inukashi looked down at Nezumi. His lips were parted slightly. He was
breathing. But---

\emph{This is the end, huh?} The strength withered in his legs, and he felt
like he would collapse. \emph{This is it, Nezumi. There's nothing more we can
do.}

\mybreak

"There is." Shion stood up. "There is a hospital."

Inukashi and Rikiga turned to each other. They peered into each other's
eyes.

"Hospital---? Where?" Rikiga asked in a hoarse, scratchy voice. Shion's
gaze slid to the side. On the other end of it was the special alloy
wall, illuminated brightly by the flames.

"Inside."

"No. 6!" Inukashi and Rikiga's voices overlapped.

"Yes. We'll find plenty of hospitals there."

"That's absurd!" Rikiga blurted. "How are we going to get inside? My car
won't even be able to pass the gates. They'll register it as a
suspicious vehicle and it'll get blown up within a few metres of even
entering. Impossible. Absolutely impossible. Wait, I know! Shion, how
did you escape from No. 6? Can't we go back in that way?"

Inukashi almost interjected in agreement. If Shion had come out that
way, perhaps he could get back in through it. \emph{That old man is a quick
thinker once the alcohol's gone out of him.}

But Shion shook his head firmly.

"We can't do that. That would take too much time. And Nezumi wouldn't
last on the strength he has left. We have an hour---we need to get him to
the hospital within an hour\el "

"But how are we going to manoeuvre through the gates?"

"We don't need to."

"What?"

"The Correctional Facility is destroyed. All its functions have shut
down. That means the gates mostly likely aren't operating, either."

"You're planning to enter No. 6 through the Correctional Facility's
private gates?"

"Yes."

"Shion, you\el do you know where the Correctional Facility's gates are?"

"I don't know for sure. I've heard, though, that they're directly
connected to the Correctional Facility."

Rikiga's throat contracted as he swallowed his saliva. Inukashi found
himself doing the same. The back of his throat burned from the smoke.

"You're right." Rikiga's voice grew even more hoarse. "You're absolutely
right. It's directly connected. About a hundred metres beyond the gates,
you'll find the back entrance of the Correctional Facility. That's where
you two were carried through during the Hunt. But you probably couldn't
see anything from inside the cargo container you were loaded into."

Inukashi realized he had unknowingly clenched his hand into a fist,
listening to Shion and Rikiga's conversation.

Getsuyaku had also been coming and going through those gates. Inukashi
had heard him complain countless times about being treated the same as
prisoners. Inukashi had given the man an offhand answer.

"Prisoners are killed once they get caught. They'll never come back out
through those gates again. But you're coming and going through them
every day. Not to mention you're getting paid to do it. That's way
different from being a prisoner."

"Well, I guess, now that you mention it. I wouldn't be able to go home
if I were just a prisoner, huh," Getsuyaku had shrugged and smiled
ruefully.

\emph{But in the end, he was the same. He was shot dead in the blink of an
eye, just the same as a prisoner. Even worse---like an insect.}

Inukashi remembered Getsuyaku's rueful smile. He closed his fist more
tightly.

"Then we can take the car to the gate from here, right?" Shion asked.

"We can if there are no obstacles along the way. No one is crazy enough
to get close to the Correctional Facility now, apart from you lot."

"Rikiga-san, lend me the keys to your car, please."

Shion extended his scratched and bloody hand. Rikiga's face twisted
visibly. Deep creases appeared between his eyebrows.

"What are you going to do with them?"

"I'm going to drive. You two can stay behind. The keys, quickly."

"Bullshit!" Rikiga bellowed angrily again. "Have your eyes rotted and
fallen out? Don't you see those flames? You idiot!"

The Correctional Facility barely remained standing, spewing flames and
black smoke. The alarms that had been ringing so loudly had died out
somewhere along the way, and only the ferocious wind sounded as it was
drawn in by the flames.

"We've barely gotten out of the Correctional Facility in one piece, and
you're going to prance right back in?" Rikiga said incredulously. "This
is no time for jokes. How many lives do you think you have?"

"I don't plan on going inside. The gates are outside of it."

"A hundred metres away. \emph{Only} a hundred metres. The gates aren't a safe
zone, you know."

"That's why I'm going. Usually we wouldn't be able to get through, but
right now, the gates are nothing but an opening."

"The car runs on gasoline. If you happen to drive into fire and it
catches---"

"Hand it over," Shion commanded in a low voice, cutting through Rikiga's
yelling. Commanded. That was indeed how the words came out. Shion had
neither snapped, nor yelled harshly. On the contrary, it was a quiet and
heavy utterance.

Rikiga retreated half a step.

"Hand over the keys."

It was the voice of a ruler giving orders to his subject---it was
unmistakable.

Rikiga rummaged through his pocket and extracted a worn silver keyring.
His fingertips were trembling.

"\el Stop it," said a voice even lower than Shion's. To Inukashi it
seemed to spring from the depths of the earth. A chill ran through his
spine. Nezumi had slowly lifted himself up.

"That's enough. Stop it."

Inukashi could hear his words clearly.

Nezumi's voice. Nezumi could use ten, twenty different voices, but what
Inukashi's ears had caught was unmistakably Nezumi's natural voice.

"Don't\el stay away, Shion."

Shion did not answer. He did not even try to look at Nezumi. Instead, he
bowed his head to Rikiga.

"Rikiga-san, please. Give me the keys. Please, I'm begging you." It was
not an order, but a plea.

This was the Shion that Inukashi knew. Intelligent, gentle, faithful,
airheaded and clumsy Shion.

"Just give it to him, old man," Inukashi said with a deep sigh. He
didn't know why he had sighed. There were a lot of things he couldn't
make sense of. He couldn't even understand himself.

"Shion, I'll go with ya." The words spilled out along with his sigh. He
surprised himself. \emph{Look at me. I'm so reluctant to put my life in
danger, I'm so desperate to survive, yet here I go saying 'I'll go with
you'. I can't believe myself sometimes. And what's worse is that it
isn't even a lie or bravado. I really mean it. I told him I'd go with
him, and I meant it. What on earth is wrong with me? I can't understand
myself. What's going on, what's going on, what's going on? Oh, hell.}

"Fine." Rikiga clicked his tongue. "If that's what you want to do, then
do as you will. You guys probably aren't the type to listen to your
elders, anyway."

"Don't lump me in with the airheaded young master, man," Inukashi
protested. "But, oh well. There you have it. The votes are in and it's
two to one for driving into No. 6. That's that. Too bad, Nezumi."

"Three to one." Rikiga clenched the keys. "I'm coming along for the
ride."

Inukashi blinked and glanced at Rikiga. The man also blinked repeatedly,
his eyes ringed with soot, dirt and sweat.

\emph{What on earth is wrong with me? Why did I say something like that? And I
actually meant it}, his facial expression seemed to say. Inukashi felt
like laughing and crying at the same time. \emph{What a weird feeling.} He felt
scared, yet exhilarated. Dismal, yet optimistic. \emph{Your heart can be weird
like that.}

"It's my precious car," Rikiga said. "I won't tolerate you trashing it.
Besides, I doubt you snot-faced kids would be able to drive. Young'uns
these days get better and better at mouthing off, but can't do anything
for themselves."

Rikiga mumbled complaint after complaint. It was most likely because he
would end up sighing if he didn't talk.

Rikiga's car was a minivan. It was dented everywhere, and the right side
mirror was bent. It was an outdated gasoline-fuelled model that could
easily have been displayed in a museum in No. 6.

But it had a sturdy frame, if anything. The engine also had a lot more
power than it looked. Being able to drive a car in the West Block was a
symbol of a certain level of wealth, and hence there was always a risk
of being ambushed by thieves on the road. Inukashi remembered listening
to Rikiga boast that for this reason, he had modified the car to be as
durable as a tank.

Inukashi sat in the passenger seat, while Shion sat in the back holding
Nezumi. The dogs climbed into the car last.

"Why do you have to bring your dogs? They'll stink up the car."

"They smell way better than your alcohol. My dogs are loyal to their
boss. They'll go wherever I go. Just like how these tiny mice are
faithful to their boss."

The mice were huddled together on the seat. They sat noiseless, as if
they had forgotten how to squeak.

"Dogs and mice, huh. That settles our destination, then: the zoo. Hmph,
what a fun drive this is going to be."

Rikiga turned the ignition. The engine sputtered comically, and the car
seemed to give itself a shake.

"Let's go. I'm going to floor the gas, so you better prepare
yourselves."

The car lurched forward. It continued to mount in speed as it made
straight for the Correctional Facility.

"Hey hey, old man. It seems like you're being a little reckless about
this."

"How can I not be? Look at what I'm doing. Damnit, what the \emph{hell} am I
doing? Why the hell am I doing this?"

"Because you're in love with Eve, duh."

"What?"

The back gates to the Correctional Facility had been thrown open.
Perhaps some people had escaped through them. These gates had always
been tightly closed, refusing all who came near, but now it was open and
exposed. Flames spiralled up behind them, and the building played its
melody of destruction. Inukashi could hardly believe that this wasn't an
illusion.

\emph{Is this reality?}

The gates to the Correctional Facility had opened, and the special alloy
door had been blown apart.

Things that were not supposed to be happening were happening. Things he
had believed would never happen---no, had been made to believe would not
happen---were inverted. There was no good or evil. No justice or
injustice.

\emph{This is reality.}

The car veered around the back gates, nearly scraping against them, and
gained speed. Inukashi saw the security gates beyond.

"What!?" Rikiga yelled. "What did you just say, Inukashi?"

"You were totally into Eve, old man. You're still a passionate fan,
aren't you? You're head over heels. Or else you wouldn't be able to
sprint like that while holding him. Those were some good moves out there
on the field, risking your life. Bravo."

"Knock it off. Once we get to a medical clinic, the first thing I'll do
is sew that mouth shut. Sew in that rotten tongue of yours while I'm at
it."

"Why, that's just splendid. An honour of honours to be able to get
treated at a clinic in No. 6."

"Say all the crap you want!" Rikiga gripped the steering wheel.

Inukashi snapped his eyes open, and shrank back. The gate was
approaching at an astonishing speed. No, they were approaching it.

"It's burning," he murmured. He had resolved not to voice it; he had
restrained himself from putting anything he saw into words. But he could
not help it.

The gates were burning.

They were engulfed in flames. Small explosions, still not as large as
the ones in the Correctional Facility, were ringing out. Fragments of
glass and metal battered the car ruthlessly. Each time, the car made an
unnerving \emph{bump-bump} sound. The sounds were like the car's screams
themselves.

\emph{It hurts. I'm scared. I'm gonna die.}

"It's burning." Once he put it into words, terror gripped his whole
body. It was like the roots of his hair were standing on end. But one
point of curiosity slipped through the wave of fear washing over him,
and clung to Inukashi persistently.

\emph{How can it crumble so easily?}

He understood that Shion and Nezumi had utterly destroyed the core of
the Correctional Facility. He was in awe at their accomplishment. But
there was something wrong with it. It happened too fast, too easily. \emph{Was
it always this fragile? Is it supposed to just collapse like that?} He
did not think for a bit anymore that No. 6 was an absolute existence, or
an omnipotent ruler. It was the same as that special alloy door. It had
bent out of shape, crumbled, and now lay in a disgraceful mess.

\emph{But---but this is No. 6 we're talking about here. An artificial city, the
epitome of human intelligence and scientific technology. The
Correctional Facility is another No. 6 that's supported its darker
workings. It's No. 6's bastard child, an evil spawn that's a spitting
image of its parent.}

Evil things often possessed evil powers. \emph{Couldn't it have stood its
ground somehow? Is it going to be defeated just like that, without a
choice?}

\emph{Heh heh heh.}

He heard it again. That lighthearted but terrifying laughter. It was
more frightening than the flames in front of him.

Inukashi screamed. Rikiga gave a shout beside him almost at the same
time. This one was from the fear of being on the brink.

"Ahhhhhh!!!"

They plunged into the wall of fire. The dogs continued to bark
incessantly. Inukashi did not close his eyes. He kept them open, and
watched the flames swallow them up. They were not a uniform colour. The
vermillion of sunset, the crimson of blood, the red of flowers all
blended together. They shone golden, then sank into a muddy red.

A part of the windshield shattered. Hot air blasted at them full-on in
the face. He smelled burning hair. The heat evaporated the moisture from
everything around them, and they began to shrivel up.

\emph{Oh, so we're gonna die here. So that's how it is}, he thought. \emph{I'm going
to die with them after all. In the end, I'm just\el }

"Elyurias," said a voice from the back seat. Inukashi could not tell if
it was Shion's or Nezumi's. He did not know what the word meant. Was it
an incantation? It sounded too strange to be someone's last utterance.
But then again, they were always strange, weird, ridiculous people from
the beginning. \emph{This doesn't surprise me now, but\el it's nagging at me.}

\emph{Elyurias? What the hell is that?}

His hair singed. His skin was being roasted. It was hot. \emph{Goddamnit, it's
hot.}

The flames wavered. They wavered, and seemed to retreat just slightly.
The heat also receded just slightly, and he could breathe a little.

\emph{Huh? Why?} Inukashi blinked. \emph{Are the flames retreating on their own? No
way. That's impossible. Absolutely impossible.}

"We're out! Rikiga roared with laughter. He laughed as if he had gone
mad. "We're out! Take that, bastards! We're out safe! Ha, ha, ha ha ha
ha ha ha! Take that! We've done it! Ha ha ha ha ha ha!"

Tense laughter echoed inside the car.

\emph{Ha ha ha ha ha! Ha ha ha ha ha! Ha ha ha ha ha!}

They had gotten through. He was right; they had certainly gotten
through.

The land around them wild and barren, with few grasses or trees. It was
no different from the West Block. But at least in this wasteland, there
was a straight, two-lane road. A lush, green forest probably awaited
them at the other end. In the dark, Inukashi could only make out a black
mass, but Inukashi's nose caught the rich, earthy smell of the trees.

Maintained roads and lush forests---all were things he could never see in
the West Block.

\emph{We've made it inside No. 6. I've stepped inside, for the first time in
my life.}

"Look at that. That was quite something. Ha ha ha ha ha! Only natural
for Almighty Mr. Rikiga! I'm quite the hero. Ha ha ha ha ha, I did it!
Take that, bastards! Hooray for Mr. Rikiga, hip-hip-hooray! Ha ha ha ha
ha!"

Rikiga's voice cracked even more, and whined in a higher pitch. Inukashi
swept up a liquor bottle that had been lying at his feet, and knocked
Rikiga over the head.

"Ow! What was that for?"

"I went easy on you. Your head hasn't cracked open, now, has it?"

"Idiot! How dare you act like that to a hero!"

"I calmed your hysterical fit. That's really sad, old man. Even my dogs
and the mice are calmer than you. What's so heroic about what you did?
You went on a reckless joy ride, and you jumped through fire. That's it.
Ugh, for shame."

"Shut up. Can a dog or a mouse drive a car? I'd like to see them try.
You think you've got a right to say whatever you want---"

Once Rikiga finished yelling to his heart's content, he gave a great
sigh.

"Shion, what are we going to do now?" he said. "I have no idea what it's
like inside No. 6. I've been away for ten years."

Inukashi could feel Shion shift in his seat.

"Lost Town is just a little ways in from here. The outskirts of No. 6
are beyond that forest, and further beyond that are the central
districts. The forest is there to hide the walls from the citizens."

"I see. So they can go on living without being reminded all the time
that they're surrounded by a wall."

"Yes."

"And how about medical facilities? Where should we go?"

"Go straight through the forest. There will be a fork, and if you turn
right, there should be a small clinic."

"Will that be good enough? Eve's hurt pretty badly, isn't he?"

"He's been pierced by a rifle bullet."

"Wouldn't you need a pretty sophisticated facility to treat that?"

"Maybe," Shion said. "But that clinic is the closest. They have a
surgery. You can only find fully-equipped facilities in the city centre.
We don't have time to go there, and this car might get caught in
inspections along the way. They get stricter as you get closer to the
centre. Also, you need a citizenship card to get into most medical
facilities."

"You don't have one?"

"I threw it away."

Shion paused for the length of a breath, and continued.

"It was a useless card to have, anyway. Lost Town residents aren't
allowed into most central facilities."

"You can't get in?"

"No. The type of ID you have---in other words, your position as a
citizen---decides what facilities you can use, where you can live, and
what you can ride. It's not only with clinics; Lost Town residents
aren't even allowed into the central facilities for daily shopping needs
or entertainment. When it comes to places with the best equipment, the
number of allowed people gets even smaller.

"That thorough about it, huh?" Rikiga commented. "I'd heard about it
before, of course, since I did business with high officials. I did get
the idea that there was some vague uncertainty and discontent brewing in
that city, and that a hierarchy was in place. But to think that such an
old-fashioned system was being enforced\el I would never have imagined.
What a surprise."

"High officials are elites close to the summit of the hierarchy. They
don't know what it looks like from the bottom."

Inukashi snorted.

Rikiga was right. He was surprised, or rather, struck dumb in amazement.
He was taken so off-guard, all he could do was growl.

\emph{So that city, No. 6 not only divided people inside and outside with a
wall, but they even sorted people within by creating more tiny
differences?}

The wealthy and the poor; the haves and have-nots; the superior and the
inferior; the strong and the weak---No. 6 drew countless lines that had
formerly never existed between humans, pruning and selecting to its
liking.

\emph{Why was such a system ever needed? Who needed it?} If you were unlucky,
you were dead. If you were lucky, you were alive. The line between good
and bad luck was the only thing that divided people in the West Block.

"And the hospital we're headed to right now doesn't need an ID card?"

"It does. There isn't any place in No. 6 that doesn't need an ID."

"Then---"

"The doctor at the clinic used to be a customer at my mother's store."

"Karan? Her store---a bakery, right?"

"Yes. He used to come once or twice a week to buy bread for lunch."

"What's his name?"

"I\el don't know. We all called him "doctor". That usually sufficed."

"You don't even know his name?" Rikiga said in disbelief. "Are you sure
you can trust this doc? Is he good-hearted enough to treat someone who
doesn't have an ID card? Who's not a citizen of No. 6?"

"I don't know. But he's our only chance."

Rikiga lapsed into silence. There was no time to waver or hesitate.

As they approached closer to the forest, the rich smell of vegetation
and earth grew stronger. Could anyone in No. 6 see the Correctional
Facility burning where they were, or was it blocked out of sight by the
forest?

\emph{He's so calm.} Inukashi thought about Shion. Shion's words were composed
and undisturbed. The usual Shion---he was not. If Shion were as he
normally was, he would be fraught with hesitation, fighting desperately
against his own heart.

When did he learn to repress all of his emotions and put on an act of
calmness? Had something in Shion changed, like a cloth that loses its
colour after being passed through water?

Inukashi licked the back of his hand. It was blistered from a burn.

He was afraid to turn around. If he turned around and focused his eyes,
he would see the bloodied figure of Nezumi, and inscrutable Shion. He
knew it was just his imagination, but he was afraid. The back of his
neck was so tense, he felt like it would seize up.

\emph{Well, I'll be damned if he changes.} He repeated inside his head while
licking the blister. \emph{Shion is Shion. He'll never change; I'll be damned
if he does. Just like I'll keep on being who I am, just like how I'll
never change, there's no way he'll ever change.}

The car entered the forest.

"Oh---!" Shion cried out softly. "The sky\el it's burning."

Rikiga also let out a muffled shout, and leaned out. The car swerved,
almost hitting the streetlights standing between the trees.

The sky was burning.

The sky, darkened even more deeply by the night, was coloured by the
flames. The Correctional Facility was not the only place. No. 6 itself
was spewing fire. Places across the city were being engulfed in flames.

\emph{What's going on?} Inukashi turned around, his mouth still hanging
half-open.

"Hey, what just happened?"

Shion sat frozen. He sat still, holding Nezumi in his arms without even
blinking. Only his lips moved imperceptibly.

"\el It's burning."

Far away, they heard the sound of a blast. It came from behind, not in
front---the direction they had just escaped from.

"The gate---" Inukashi fell speechless. No further words came out. He
closed his mouth, unable to believe his eyes.

\emph{What the hell is about to happen?} It was neither excitement nor
expectation. It was not fear. He was being toyed with by emotions that
he found hard to describe.

Shion spoke.

"We'll be out of the forest shortly. Then, we'll be in Lost Town."