% !TeX spellcheck = en_US

\chapter{But once}

\myepigraph{Cowards die many times before their deaths,\\
	The valiant never taste of death but once:\\
	Of all the wonders that I yet have heard,\\
	It seems to me most strange that men should fear,\\
	Seeing that death, a necessary end,\\
	Will come, when it will come.}{Shakespeare, \emph{Julius Caesar} Act II Scene II}

\lettrine{T}{he street} was filled with people.

Hundreds, thousands of people were running in the same direction. They
flowed like a giant river. But a large river would have meandered
gently; it would not be full of murderous intent. It would surge as
these people did now.

Karan stood with her back to the wall, watching the people go by. The
rows of small houses lining the street had all tightly shut their doors
and turned off their lights.

Were their residents huddled quietly inside, or were they somewhere in
this flow of people?

On her back she felt the cool emptiness of the abandoned houses.

"To the Moondrop!"

"We have a right to live, too!"

"Show us the mayor! Why are you pointing guns at your own people?"

"We won't stand for this!"

That was all Karan could pick up. The rest became angry yells, shouts,
calling cries and responses that mingled, twisted and tangled with each
other in the air.

The sheer energy of the sound was so great, Karan was seized by a
floating sensation. Karan dug her heels in, and pushed her back up
harder against the wall. If she didn't, she felt like she would be
pulled into this flow, this cyclone. Her body and her soul would be
carried away.

"Aghhh!!"

Suddenly she heard a scream that was a pitch higher than everything
else. It was very sudden. It pierced the roaring din and impaled her
eardrums.

A heavyset man standing diagonally in front of Karan fell on his side,
clutching his neck. For an instant, the people ceased their clamour.

"H-Help\el help me, someone\el help\el "

The man stood up, stumbled for a few steps, and collapsed again. His
hair turned white in seconds, and his body began to wither. The man
stopped moving.

"There it is. It's happened again. Another casualty!"

"We're going to be next!"

"Do something! We have to do something quickly!"

The buzz of the crowd shook the air, and people began to flow again. No
one tried to pick up the fallen man and carry him out of the crowd's
path. People stepped on him, over him, around him, and pressed forward.

Spring was still far-off, the night was still chilly, but beads of sweat
adorned everyone's face.

Karan also felt the sweat streaming down her cheek. She was unbearably
thirsty. She felt like she was fainting; her hands and feet were growing
numb, and she almost lost consciousness. She bit down on her lip.

\emph{I have to go back. Lili and everyone are waiting.}

With her back still to the wall, Karan edged her way back to her shop.
She moved against the flow of people.

The storefront was pitch-dark. She entered an alleyway and made for the
back. A light was on---in the storage room, which had doubled as Shion's
bedroom. Karan cleaned it every day so it would be ready anytime Shion
came home.

That room was lit.

\emph{Phew.} She let out a long breath that surprised even herself. Although it
was impossible for anyone to have heard it, the door to the storage room
opened just slightly. A small white face peeked out, and looked around
cautiously.

"Lili."

"Ma'am!"

Lili ran up to her. "I'm so glad you're back, ma'am. You know, I had
this feeling, I really did. Like you were outside. I could \emph{actually}
tell."

Karan embraced Lili's body tightly. She was almost brought to tears by
the softness and warmth of her small, young body.

"Was Madam Koka alright?"

"Yes\el "

"Was she crying?"

"Yes."

Karan had taken Koka back, the mother whose son had been shot to death.
Koka had sunk to the ground by her son's body with vacant eyes, as if
she had forgotten how to cry.

Every word of consolation was meaningless.

\emph{If Shion had gone through the same thing---} Just the thought of it racked
her chest. She could vividly feel Koka's despair. That was why Karan
could not find the right words to say to her.

"Ma'am Koka laughs, like, in this huuuuuge voice. And she laughs all the
time," Lili chattered.

"I know."

"Do you think she'll laugh for us again? Is she gonna be able to, ever?"

Lili's face clouded over. Karan could not answer. How could anyone stand
up again from the despair of losing her most beloved?

She softly placed her hand over her breast pocket. It contained three
letters. They were from Shion and from a boy called Nezumi. They were
scribbles, almost too short to be called letters.

\memo{\shion}{Mom, I'm sorry. Alive and well.}

\memo{\nezumi}{
	Shion is safe, worry not. Escaped to West Block.\vspace{-2ex}\\
	Be wary of Bureau surveillance.\vspace{-2ex}\\
	Any replies to this mouse. Brown brings news of safety,\vspace{-2ex}\\
	black brings news of change or abnormal occurrence. -Nezumi}

\memo{\nezumi}{Reunion will come.\hspace{1cm}Nezumi}

Words could not describe how much these letters had supported
her---supported her, and kept her alive.

\emph{What will Koka turn to for support to live on?} She didn't know. She
could not answer Lili's question.

"Ma'am?" Lili looked up at her. Karan nodded and flashed her a vague
smile.

\emph{I'm sorry, Lili. I've been alive for so much longer than you, and I
can't answer any of your questions.}

She heard a muffled sound in the room.

"Lili, where's Renka? Where's your mother?"

"Mommy's looking at the computer. Uncle Yoming is in there."

"Yoming?"

She held Lili's hand and walked inside. She closed the door and locked
it. The room doubled as storage, and there were sacks of flour, sugar,
and raisins piled high along with jars of honey and jam in rows.

In a far corner was Shion's bed, and beside that was an old desk.
Shion's desk. In the drawer was a half-written report that Shion was
planning to hand in.

Renka was crouched over the desk, engrossed in the monitor of the
outdated computer.

"Renka," Karan called. Renka twitched slightly and turned around. Her
bloodless face was illuminated by the dim light.

"Karan\el "

"Renka, what's wrong? Has something happened?"

"Karan, it's my brother." Renka straightened up awkwardly. "Look." She
pointed at the computer screen.

Yoming was there. His fist was raised, and his expression was fierce. He
was definitely Yoming, and yet he seemed a total stranger.

"Now is our time to stand!" he declared. "If we do not stand up now to
destroy everything, we will be slaves forever! Yes, slaves! You all must
realize by now how No. 6 has deceived us all this time! How much unfair
abuse we have suffered; how much exploitation we have endured! It has
always been this way. It has always been this way, comrades. This city's
horrific history is steeped in bloodshed. Let me tell you, comrades,
about the hundreds of lives that have been banished to eternal darkness
because they disputed the authorities; because they objected; because
they resisted. Let me bring everything to light. Look, comrades!"

Yoming swept his hand towards the wall behind him.

Countless faces appeared on it. Youth, the elderly, young boys and young
girls, even infants. A girl in her wedding dress; a muscular labourer; a
thoughtful elderly gentleman; a smiling elderly lady; a sleeping infant;
a girl running this way, laughing; a middle-aged woman with her eyes
cast down; a young doctor wearing a stethoscope---many, many faces
appeared before them.

Karan's heart thudded loudly.

\emph{Da-dum. Da-dum. Da-dum.}

Shion was there.

He was facing this way, with a slightly sheepish grin on his face. It
was his first birthday since coming to Lost Town, and Karan had taken a
picture.

"Aw, please, can we not take photos?"

"Why not? It's an occasion to remember."

"Fine, but no pictures outside."

"Oh, you're more bashful than I thought."

Such was the conversation that passed between them as she took the
picture.

"I want to know what kind of boy your son is. Can you tell me what he
looks like?"

Karan had shown Yoming that photo among others on his request. He had
copied the data without her even realizing.

"Look at these people," Yoming continued. "They are people who have been
taken away by the Security Bureau, never to return again. They are
people who have been murdered by No. 6. Unbeknownst to you, comrades,
the authorities have been obliterating anyone who poses an inconvenience
to them. You didn't know that, did you? No, you didn't. But I am not
blaming you, comrades. You have already come to know No. 6's true
identity. You now know what kind of people the authorities really are;
who the mayor really is. The question now is what we will do from here
on out.

Comrades, I am not talking about the past. I am talking about the
present. Even while we stand here now, fellow citizens are dying. They
are dying horrific deaths. A terrible disease is sweeping the city.
Already, many citizens---good and innocent citizens---have suffered at its
hands. But the authorities have failed to take action. Instead, they
have given themselves an effective vaccine and so are able to keep
living lives that they do not deserve.

Comrades, did you know? A considerable number of vaccines is still being
stored in the Moondrop. But the authorities are doing their best to hide
it. They won't give those vaccines to us citizens. They have paid
enormous expenses to develop them, and they don't want to hand them out
to just anyone---that's their standpoint. Have you ever heard of anything
so ridiculous?

Comrades, I disclose to you an even more shocking truth. All of this is
fact: this is something I have been investigating in secret for years.
This is the truth, and it is a horrific reality we must face. The upper
echelons of No. 6, including the mayor, have been predicting this
situation for many years---that a mysterious disease was going to spread
throughout No. 6. That was why they were developing a vaccine in secret,
while we citizens were kept in the dark. And when the situation becomes
dire, they are only interested in saving a select few. And look! Open
your eyes wide, and look at what is happening!"

Next, an image of a mob flashed across the white wall. They were people
who had crowded in protest around the Moondrop. They were all shouting
something, their expressions tense. A red ray of light streaked across
the corner of the screen. At once, every face took on an expression of
horror, and people frantically began to flee. Next, an image appeared of
soldiers at arms and several bloodied people collapsed in the square.
The video looked like it was from a hidden camera; the footage was
blurry and kept shaking sideways and diagonally.

"What is this, comrades? Do you know what this is called?"

Yoming's voice rang out, loud and pronounced.

"Yes. Our fellow people have been murdered. Killed like vermin. The
authorities have pointed their guns at their own citizens. Is that
something that ought to be forgiven? Of course not. We cannot let them
go for what they did.

Comrades, let us stand! Put the power of the government back into the
hands of the people. Take it away from the Moondrop, which has rotted
through completely. We will not stand to be trampled on anymore. We will
not be suppressed anymore. We are humans. Let us take back our freedom
and safety. To battle, to battle, to battle, comrades! We must rise up
in arms! Surround the Moondrop! Destroy No. 6! To battle, to battle, to
battle!"

It was a jarring cry. Renka turned the power off even before his yell
began to taper. Her legs curled under her as she dropped weakly to the
floor.

"It's been like this forever. About once every five minutes, my
brother's speech gets played."

Renka held her swelling belly, and her mouth twisted. The noise out on
the street grew even more agitated. It hit Karan and Renka like waves
crashing onto the shore.

\emph{To battle, to battle, to battle, to battle, to battle.}

\emph{Rise up, rise up, rise up, rise up.}

"Karan, what's gotten into my brother? Why is he saying things like
that? Why is he screaming?" Renka covered her face with her hands.

"Mommy." Lili huddled close to her, and placed a gentle hand on her
mother's knee. "Mommy, don't cry."

"I'm fine, Lili. I won't cry. But---but you know, Mommy is a little
scared." She then said to Karan, "My brother was such a gentle person,
but he\el he looked like a completely different person\el no, in fact,
he \emph{has} become a different person. He's changed ever since my
sister-in-law and her baby went missing after being abducted by the
authorities\el he's changed. From that day, the only thing in my
brother's heart has been---"

"Revenge."

Renka lifted her face at Karan's words, and opened her mouth slightly.
She looked like a gold fish with not enough air.

"Yoming wants revenge on No. 6. He's wants this city completely
destroyed."

"Yes," Renka answered. Her voice was croaky. "Yes, you're right, Karan.
My brother never said it. I never heard the word 'revenge' come out of
his mouth. But I \emph{knew}. I'm his little sister, after all. I could tell
how he'd changed, I could tell he had vowed in his heart to get revenge.
That's why, some day\el I was afraid this would happen. I was worried\el 
but scared. I was really scared."

Renka's lips trembled. Her large eyes turned watery, and she turned even
paler. Karan looked from Renka to the blank black screen.

\emph{Lies}, she thought vehemently. \emph{I won't say all, but half of Yoming's
speech is made of lies.}

Certainly, the authorities had placed its citizens under its vigilant
regime, and ruled them in a manipulative and ruthless way. It was true
that Karan and most of the citizens had been living blinded and
oblivious. Yes, many people had been sacrificed; an unidentifiable
disease \emph{was} spreading like wildfire; the authorities \emph{were} failing to
come up with any effective solution; they \emph{had} opened fire on citizens---it
was all true.

But his claim that the city had foreseen this situation---this
unfathomable, horrific situation---and had launched the development of a
vaccine---that was false. If by some chance this was true, there was no
reason for them not to vaccinate the citizens. If they had a store of
vaccines in the Moondrop, it was unthinkable for them to withhold it.

What good did it do No. 6 to kill its own citizens? If anything, it
would do more damage than good. They were in this situation precisely
because they had no vaccine to combat the disease. Right now, they were
in the middle of a worst-case scenario.

\emph{Besides---besides---Shion is not one of them. Shion will come home. Shion
isn't someone who is "never to return again". Yoming's words were half
truth, half lies. There is no vaccine in the Moondrop. That was a lie.
He's a perfect demagogue.}

Yoming was manipulating, encouraging, and agitating people's fears,
along with their long-festering suspicion and discontent towards No. 6.

\emph{Yoming, please don't. This is wrong.} She thought of Koka, who had
refused to move from her son's side. She remembered her unseeing vacant
eyes, frozen open from her overwhelming grief.

The soldiers had been the ones to shoot Koka's son to death. But Yoming
was part of the cause. Yoming was deeply involved with the brutal death
of a man who had been referred to affectionately as "Good Guy Appa".

The truth was noble, as long as it remained the truth. That was how it
made the world turn. But now, Yoming was not speaking the truth. He was
twisting it conveniently to match his intentions.

"My brother has changed," Renka said in despair. "It started gradually
after my sister-in-law went missing, and when this commotion began, he
changed completely."

"You're right," Karan said resignedly.

Yoming had been waiting. He had lain low, waiting for an opportunity---not
to flourish onto the scene, but to exact revenge on No. 6.

And this was the opportune moment.

"To battle, to battle, to battle, to battle!"

His cry rumbled deep in her ears. It stirred the soul like a magnificent
soundtrack.

Karan overlapped her hands over her chest.

\emph{No, Yoming. What you're doing is wrong. What will come of involving so
many of these nameless people? What will you try to create from their
sacrifice? Can you see them? Can you see each and every person's face as
they die bleeding? Have you ever tried to look at the life each of them
has lived, and the days that they've spent?}

\emph{Yoming, now is not the time to fight. We don't have a second to lose; we
have to find a way to deal with that unknown disease.}

\emph{We have to protect lives, not use and dispose of them. If you loved your
wife and your son, then you should respect life all the more.}

\emph{Do you---do you plan to cross that line?}

\emph{Please. Cast your thoughts not to the group, the people, the citizens,
but each and every person as their own! Make a place in your heart for
me, Renka, Lili, Koka, Getsuyaku, and all the people whose names you
don't know!}

\emph{You're a human, aren't you? You're not No. 6.}

"Karan," Renka said in a feeble voice.

"What is it?" Karan's voice also sounded faint to her own ears.

"You know\el I've wished for a long time that you and my brother would
be together."

"Why, Renka---"

"My brother liked you. I think he was in love with you. When the topic
would turn to you during dinner, he'd always turn very quiet. But he
looked so happy. I haven't seen my brother look so happy in a long
time."

"Renka\el "

"Then, someday you and my brother would get married, Shion would come
home, I would give birth to my baby, and Getsuyaku and Lili would visit
you so you could get a look at the baby, too. You and my brother and
Shion would kiss the baby in turns, congratulating it, and you, Karan,
would bake a cake to celebrate. Getsuyaku and I would stretch our
savings a little to give out "Fortune Bread" to everyone in Lost Town.
They'd be little rolls that you made, Karan, and we'd hand them out as a
symbol of our happiness. We'd package them in little bags, tied with a
cute ribbon\el We'd share a little bit of happiness with everyone. Both
Lili and the baby would wear a ribbon, too. I would put a white bib on
the baby, and a light pink apron on Lili. Lili would carry a basket full
of "Fortune Bread" and we would walk down the street. Everyone would
come up to greet us, saying, 'Congratulations, Renka. Congratulations,
Getsuyaku, Lili.'"

"Renka."

"That's all I wish for. That's not greedy at all. Is it, Karan? Is it
being greedy?"

"Of course not."

It was small---such a small wish.

"Then why won't it come true? Why does everything have to fall apart and
disappear? Why?" Unable to contain herself, Renka let a sob escape her
lips. Lili embraced her mother firmly with both arms.

A small, small wish. But it could not come true.

\mybreak

As long as they lived in No. 6, all their hopes were like towers of
sand. They melted away all too easily. \emph{Then, what are we to do? What
must we do so we can build our lives on firm ground instead of sand?}

\emph{If No. 6 isn't an idyllic city, then what is 'ideal' supposed to be? How
are we to create an entirely new world, so different from No. 6?}

"Renka, Yoming isn't working alone, is he?"

"No\el there must be other people who have gone through the same
thing---who have lost their family."

"And Yoming is with them, right? They must be acting together."

"Yes, I'm sure of it."

"Do you have any idea where they might be?"

After some moments of thought, Renka shook her head.

"No. It looks like they're in some basement studio. He would need proper
equipment to make that video clip."

"You're right. But neither of us know where that is. We have no way of
meeting Yoming."

"Karan," Renka held her hand out. Karan grasped it. "What will I do?
What should I do, Karan?"

Karan could feel a presence. It pressed upon her from the street.

\emph{To battle, to battle, to battle, to battle, to battle.}

\emph{Destroy it, destroy it, destroy it, destroy it.}

\emph{Kill, kill, kill, kill, kill.}

"Let's think about it, Renka." She cupped her hand gently around Renka's
belly. Then, she touched Lili's cheek.

"We still have hope."

"What?"

"Hope. The baby in your belly, and Lili---they are our hope. We have to do
our best so that these children will have a real world to live in.
Right, Renka? We have our children. Not all our hope has been taken from
us."

"Shion, too." Renka wiped her tears away and nodded. "Shion is our hope
too, isn't he? And a big one, too."

"Mm-hmm. Thank you, Renka."

"He's coming home soon," Lili blurted without warning. "Onii-chan's\footnote{Term of endearment meaning 'brother'}
coming home soon. I can tell."

"Why, Lili." Karan scooped Lili up and kissed her on the cheek.

"It's true," she insisted. "He's really coming home."

\emph{Shion is\el coming home.}

\emph{Please come back, Shion. And Safu, you too.}

\emph{Please come home safe.}

\emph{I pray for you.}

Her prayers led also to the boy named Nezumi, whom she had yet to meet.

\emph{I would love to meet you, Nezumi. I would love to see you, and thank
you. I want you to know how grateful I am for your support. Shion, Safu,
Nezumi. You, too, are my hope. My very large hope.}

\emph{Come home to me.}

\myspace

No. 6's city hall, known informally as the Moondrop, was surrounded.

The citizens crowded the square and overflowed into the streets. Each
shouted his own words of protest. Their voices melted into one, and
boomed so loudly it seemed to shake the canopies.

But no matter how loud the clamour got, it did not reach the mayor's
office. The office was on the highest floor of the building, with
soundproof walls and windows. Whatever happened outside never disturbed
the constant silence inside.

"Why? Why has something like this happened?" The silence was broken as
the mayor spun around and shook his fist.~

"Fennec, will you calm down?" the man in the lab coat answered. "You
should be the last to be agitated." He sank deeply into the leather
chair and crossed his legs.

\emph{Pitiful}, he thought as he mentally clicked his tongue. \emph{He has always
been like that. Ambitious but timid, and a coward.} The man switched his
legs and recrossed them.

But he has been able to come this far precisely because he is so timid
and cowardly. He opens his heart to no one. He trusts no one. He is
suspicious of everything and acts cautiously. A fennec indeed, the
world's smallest desert-dwelling fox.

The mayor paced the room. He flitted back and forth busily. The thick
carpet absorbed almost all of the noise generated by his footsteps.

"It wasn't supposed to be this way. Citizens are supposed to gather at
the Moondrop to celebrate the Holy Day and the greatness of No. 6, are
they not? To think it would turn out like---like this, I---how could such a
thing have happened?"

The man gave a deliberate sigh. The mayor stopped pacing, and deep
creases appeared on his brow as he looked over.

"Please, Fennec," the man said. "Compose yourself. All that's been
coming out of your mouth these days is 'why' and 'such a thing'. I'm
starting to get rather bored of it."

"Answer me. Why has this happened?" The mayor's voice grew strained. The
man gave another sigh.

"Because you haven't given it your all."

"I haven't?"

"Yes. You mobilized the army, but you only cleared them away with a
handful of firearms. Surely you wouldn't call that decisive action.
Nothing is more effective than the army when it comes to subduing the
imbecilic masses. That was not the right way to use them. You should
have used them with more flourish, more decision, and an iron finality."

"You're telling me to mass-murder my citizens?"

"They'll prostrate themselves to you before they get themselves killed.
They'll bow down in awe and fear. They'll tremble as their very hearts
are seized with regret for ever opposing you or No. 6. They will be like
neutered dogs. No matter how badly they are treated, they will never be
able to bite back. Fennec, it is not too late. Mobilize the army again,
and clear away the mob that is milling in the square. It may even be
wise to use the shockwave cannon, depending on the situation and the
course of events. You've already completed on-site testing in the West
Block, have you not?"

"That's almost like---" the mayor swallowed. "That's almost like a reign
of terror."

"Reign of terror? Absurd. I have told you before: you are the ruler of
No. 6. Its King. You reign over this country. You embody justice itself
and all its forms. Opposing you is the same as defiling justice. It is
only normal to use force to make them comply."

"\el Stop it," the mayor said weakly.

"Fennec, what are you afraid of? This is not like you. You have always
acted like the King that you are. You are conscious of your position as
the chosen one, and you have always lived under that notion."

"I have." The mayor slumped his shoulders, and dropped his gaze to his
feet. "I am the mayor. In No. 6's highest position of responsibility,
highest position of power. It's only natural. We were the ones that
built No. 6. We launched the revival project, and brought salvation to
the dying land and its people. We built a utopian city, the most
idyllic---most idyllic city possible by humankind."

"Precisely. You and I were both central members. In fact, only the two
of us truly understood the ideals that No. 6 strove for. The other
members were highly qualified, yes, but they lacked creativity. Or you
might say they severely lacked ambition, or an ability to observe the
changing times. But fortunately for us, we had those abilities, almost
in excess. That is why we have come this far."

"This far?" the mayor said sarcastically. "You mean being surrounded and
condemned by our citizens? Was our creativity and ambition and skill all
for \emph{this}?"

"This is only a temporary situation. It will conclude instantly if only
you would take effective measures."

"Effective measures? I've taken several."

"And those are?"

"There are people fanning the flames of this chaos. I've ordered the
Security Bureau to catch them as quickly as they can."

"Any ideas as to their location?"

"Not yet. They've gone underground."

"A clearly faulty plan. You should have obliterated all such dissidents
beforehand. You ought to have destroyed them to their very roots. And
what else have you done?"

"I used all sorts of mass media to broadcast my speech. I called on the
citizens to remain calm, not to panic easily or be influenced by false
rumours. I announced a state of emergency and put a lockdown order in
effect. I commanded people to stay inside until the order was lifted,
and announced that anyone deemed as a dissident would be arrested and
detained, regardless of whether he or she is a Chronos resident. I
listened to your warning, and I\el mobilized the army."

"Hm. Well, no big mistakes so far. This would have been resolved much
more quickly if you had used the army properly. But, well, small errors
can be remedied. Everything will go smoothly."

The mayor bent over and scrutinized the sitting man.

"Go smoothly? How? What part of this is going smoothly for you? The
citizens aren't retreating at all; in fact, they're out of control. No
matter how much the soldiers try to suppress them, it doesn't work. Do
you know why? Because casualty after casualty keeps occurring. Citizens
are still dying, one after another, for a reason no one can understand.
Everyone thinks that a new type of plague has suddenly broken out in the
city. They think we're hiding the vaccine somewhere. It's absurd,
absolutely absurd! That thing is no plague. It's because of \emph{them}. Why
are they going around killing citizens as they please? Why? I thought
they were supposed to act however we wanted them to. I thought we had
absolute rule over them!"

The wan smile vanished from the man's face. The corner of his mouth
twitched ever so slightly.

"Fennec, how many times will you make me repeat myself? Yes, true, this
was an unexpected happening. A random, totally unpredictable event. I
acknowledge that. I acknowledge too, of course, that my predictions were
much too optimistic. But this is not as dreadful as you make it out to
be. It is nothing more than a precursor---a precursor to Its awakening."

"You're saying this chaos is just a precursor?"

"Why, yes. It is a mere response to Its awakening. Which gives you an
idea of the enormous amount of energy this thing holds. Once It awakens
completely and comes under our control, we will be able to harness that
energy, and this chaos will calm."

"Are you\el really sure?"

"Have I ever lied or given you false information? I have always told the
truth. Fennec, you haven't forgotten, have you? I was the first to see
your true potential to blossom as a politician instead of a researcher."

"---I remember. You pushed for me to enter as a candidate for No. 6's
first mayor."

"Yes. You won that election, and you have reigned over No. 6 to this
day. And you will continue to. There is no need for an election. There
will be no need for the citizens to choose you of their own will.
Fennec, don't waver now. You have to act at all times like the mighty
man you are."

"A mighty man\el is that what I wanted to become?"

"What did you say?" the man said sharply.

"I certainly did want to create a utopia with our very own hands," the
mayor said pensively, "and I wasn't the only one. Back then, anyone who
was involved in the building of No. 6 should have felt the same. We all
spoke about how we would realize a utopian city here, embodying the
dreams of humankind. We talked about how we would be the ones to build
its foundations. Not a single person\el hoped to become an exalted man."

"A utopia cannot exist unless there is one to wield absolute power and
lead his people behind him. You should know this the best. Yes, the ones
with overwhelming power are the ones who draw the majority along with
them. If it weren't for that, No. 6 would not be called the utopia, the
Holy City that it is called today. It is a victory on the part of your
power and our ideology."

"Victory, you say."

"A complete victory," the man affirmed. "Some bumps along the way cannot
be helped. Once we overcome those, No. 6 will continue to engrave its
glorious history in time."

The mayor did not answer him. He clasped his hands behind his back, and
resumed walking.

"When will It awaken?"

"Soon."

"Soon? It isn't like you to be so vague. Be specific."

The man shrugged. \emph{Well, well. So he tells me to be specific. He must be
getting impatient. People tend to want specific numbers the more they
feel they are being cornered.}

"Let me see\el within twenty-four hours. All will be settled and
finished at this time tomorrow. Everything will be quiet and in its
right place."

"Twenty-four hours\el I can't wait that long. Within twenty hours, at
least\el no, twelve hours is the time limit."

"Impatient, are we, Fennec?"

"Impatient?" the mayor said incredulously. "How in the world could I be
otherwise in this situation? The city hall---the Moondrop---is being hemmed
in by citizens!"

The mayor's fist pounded the mahogany desk. The man shrugged one
shoulder slightly.

"Fennec, surely you don't think the Moondrop is still the heart of No.
6?"

The mayor froze.

"What? What did you just say?"

"No. 6's most important function now lies in the Correctional Facility.
The Moondrop has been reduced to a mere administrative body. It can be
surrounded by anything, for that matter, and nothing serious would come
of it. As long as we have the Correctional Facility, our No. 6 is in
safe hands."

The colour receded from the mayor's face. The tip of his tongue twitched
in his half-open mouth.

"What do you mean by that?"

"Mean? I just told you. The Correctional Facility is the heart and brain
of No. 6."

"What\el " the mayor croaked. His voice was overlapped by an electronic
chime. A man's long thin face appeared on the television screen embedded
in the wall. He was one of the secretaries under the mayor's direct
order.

"Mayor, there are fires happening throughout the city."

"So the rioters have found their way in to set them."

"That's one thing, but there's more. The emergency systems in all the
buildings are not functioning at all. In some buildings, I've heard that
the core computer itself has caught fire and exploded."

The man was rendered speechless. There was only the sound of his
wheezing breath whirling in his throat. \emph{What is this footage?} The man
let his throat rasp even more. \emph{Some kind of trick? A scene from some
cheap drama, what? What is he showing me this for?}

"The Correctional Facility is about to crumble!" The secretary's
high-pitched yell tore into him. The man, unable to endure it, took two,
three steps back.

"Wait, what's that shadow?" The mayor pushed the stumbling man back
upright again, and brought his face close to the screen.

"What is that?"

The man looked as well. It was a black shadow looming up clearly against
the flames.

"This\el isn't this a wasp? No, but\el wasps like this don't exist. They
simply don't." The mayor's jaw trembled.

The man's chin was also trembling. The tremor raced through his entire
body.

"Elyurias." The name slipped from his trembling lips. The mayor turned
around.

"Did you say Elyurias?"

"Yes. It is Elyurias. But, no---she is supposed to be more beautiful, more
demure. She is not supposed to be this---this enormous. She was supposed
to be controllable to my every whim."

\emph{Supposed to be. Supposed to be. Supposed to be. Supposed to be.}

The screen turned black as the video was cut off.

"Mayor, the citizens have gotten inside the Moondrop. Please, be
careful!" the secretary continued to yell from the other screen.

"This cannot be!" the man and mayor's voices overlapped.