% !TeX spellcheck = en_US

\chapter{Blackout}

\myepigraph{Did you come to me\\
	because I dropped off to sleep,\\
	tormented by love?\\
	If I had known I dreamed,\\
	I would not have awakened.}{Ono no komachi}

\lettrine[ante=``]{Y}{ou should} write a letter,'' Nezumi said, without looking up from his
book.

"A letter---to my mother?"

"If you have other pen pals, them too."

"Will you deliver them?"

"He will." A small mouse was perched on Nezumi's knee, cleaning its
whiskers.

"Thank you, Hamlet."

"You don't need to thank him. Every time he goes to see your Mama, he
gets to stuff himself with tasty bread. So he's in a good mood."

Shion scribbled a few words on a torn slip of paper. A score of letters.
Just a single line. What feelings would he instill in them?

He finished writing, and stuffed the slip into a capsule. Hamlet took it
in its mouth, and gave its tail a smart flick. Nezumi closed his book
with a snap. It was a beautiful book bound in blue, with white flower
petals scattered across the cover. Shion decided to ask him about it.

"What were you reading?"

"An ancient story from a country far, far away, at the ends of the
earth. A very ancient tale."

"A myth?"

"A tale about humans." Nezumi stood up, and slid the book back into the
shelf. The room filled with books was warm, thanks to the old heater. It
wasn't like when he was living in the luxury neighbourhood of Chronos in
No.~6, where he was protected by the atmosphere control system, and was
able to live in just the right temperature and humidity regardless of
the season, hour of the day, or the weather outside. There was no hope
of that kind of environment here, but he found the uneven heat of this
room much more comfortable than something controlled by machines. If he
was cold, he would don a blanket and draw closer to the heater. If he
was hot, he would back away, and shed his overcoat. That was all there
was to it. And he had not even known. He had learned, here, in this
room.

"Say---" Shion began, as he poured himself a cup of hot water that was
boiling on top of the heater. "Does it get hot here in the summer?"

Nezumi turned towards him from the bookcase, and narrowed his eyes.

"What about the summer?"

"Well, I mean---I figure since it's underground it would be pretty cool,
and since the books aren't mouldy, it probably doesn't get that humid
either\el but I was just wondering if it's comfortable."

"It's alright. Better than Inukashi's hotel."

"But what should we do with the heater?"

"Huh?"

"In the winter we can just use it like this, but it probably wouldn't do
in the summer, would it? But how else would we cook our food? We won't
be able to boil water, either." He handed a cup of hot water to Nezumi.
It was the only kind of drink available here.

"Are you telling me you're worrying about food for the summer \emph{now}?"

"I'm not worried, I was just wondering how---oh! You must cook outside.
Get a fire going, and cook the food there."

"Well---that's one way to do it."

"Ahh, I see," Shion hummed in a satisfied way. "Oh, but it must be a
hassle if it rains."

"Shion." Nezumi lifted his cup slightly. Shion could see a pair of dark
grey eyes looking at him through the rising steam.

"Are you planning to stay here in the summer, too? I mean, do you really
think you can?"

"As long as you don't kick me out."

"I'm not that pitiless. You can stay here as long as you like."

"Thanks. I'm relieved."

"Summer, huh," Nezumi said pensively. "Wonder what it would be like.
I've never thought that far ahead. ---Wonder if you'll still be here."

"I'm planning on it."

"Alive, you mean? Or would you be a handful of bones in an urn or
something?"

"No bones. I wouldn't wanna be buried in the ground, either." \emph{I want to
experience summer as a living being by your side. I want to live here,
in this room, buried in thousands of books. I want to feel the sweat
streaming down my body, and the sun's burning rays pricking at my skin.}

"Nezumi, I want to see summer here."

"Alive?"

"Alive."

"A modest wish. But it'll be hard to grant." Nezumi leaned back on the
bookcase, and abruptly changed the subject. "Shion, do you think the
commotion inside the city has something to do with the parasite wasps?"

Shion seated himself on the floor, and raised one knee. A mouse scurried
up on top of it. It was a third mouse, which Shion had named Tsukiyo\footnote{tsukiyo / \jp{ツキヨ}, Japanese for \emph{moonlit night}}
from the dark colour of its fur.

"Yeah, I do. I'm not quoting Fura-san, but I find it hard to believe
that an unknown disease would suddenly begin spreading inside No.~6."

"Really? It might be due to a new virus. Transmission via emergent
virus. Not impossible, is it?"

In 1980, the World Health Organization announced the complete
eradication of the smallpox virus. Ironically, in the following years, a
continuous stream of viruses unknown to humankind began to make their
appearance.

Ebola, HIV, the Sin Nombre, Nipah, Lassa, Hantan---to refer to such
viruses that cropped up continually, people used the blanket term
"emergent viruses".

Shion shook his head in disagreement.

"I don't think it's a virus."

"Why not?"

"Emergent viruses were originally naturally occurring parasites to
animals living in the tropical forests. Viruses probably only began
emerging from the sealed depths of the jungle because of
deforestation---that's how humankind came in contact with them. So what
I'm saying is that the viruses didn't come walking in themselves; it was
a result of mankind stepping into their territory. But No.~6 is
different. It's closed off, isolated. It runs its walls all around, and
doesn't mingle with other realms. They manage and inspect every little
thing that comes through the gates, right down to the nanometre scale. I
don't think it's possible for a virus to enter from outside."

"Awfully confident when it comes to these kinds of topics, aren't you?"
Nezumi said sourly. "But there are guys like that womanizer who come to
the West Block in secret. He could've picked up the virus here. That's
possible, isn't it?"

"Then there should be patients cropping up in the West Block as well.
Given the population density here, there should be double, triple the
number---all people who've suddenly collapsed, showing symptoms no one's
ever seen before. If such a situation actually arose, all the gates
would be closed. No one would be able to go into or out of the city."

"So you're sticking with the parasite wasp theory."

"Nezumi, I've seen it with my own eyes. Yamase-san collapsed, aged, and
died right in front of me. And afterwards, a wasp appeared out of
his---the base of his neck---his body. It was an unnatural death. I can't
think of any other cause. What's happening inside the city right now has
to have something to do with the parasite wasps."

"But where did those wasps come from? How can an insect that's several
centimetres long enter the Holy City that can weed out viruses only
electron microscopes can catch? They're not normal wasps. They plant
themselves in people's bodies and kill their host. They're skilled
hitmen---or hitwasps, I should probably say."

Nezumi fell silent. He cupped the warm mug in both hands, and looked
Shion in the eye.

"Shion---are you thinking of the same thing I am?"

"Probably."

"Say it."

His throat was dry. So dry, it hurt. Shion sipped a mouthful of hot
water, and swallowed it slowly.

"The wasps didn't come from outside."

He took another mouthful of water.

"They were inside No.~6 all along."

Nezumi also brought his cup to his lips. Perhaps his throat was dry as
well.

"You said something similar before---that maybe it originated in the
Forest Park. You said the admin system somehow overlooked the monster
when it was born."

"Yeah," Shion agreed. "I mean, seeing how there were already two
casualties in that park, including Yamase-san, I figured---but that sounds
way too unreal\el "

"So you're saying regular wasps that were living in the city suddenly
turned into man-eating ones. Is that what they call 'mutation'?"

"But it's a type of mutation that's never been seen before. But the fact
that they're still active in this cold---it's impossible in the natural
world."

It was impossible in the natural world. Then maybe---

"No way," Shion muttered to himself. "How could that---"

\emph{Thunk.} There was a dull noise. A cup grazed Shion's arm as it fell,
bounced off a book, and rolled on the floor.

"Huh?"

In a corner of his vision, Shion could see Nezumi falling forward. He
gradually crumpled to his knees, as if in slow motion.

"Nezumi!" Shion sprang forward to catch the falling body in his arms.
"Nezumi! Hang in there!"

Nezumi was heavy and completely limp. He was unable to keep his own body
standing. Shion couldn't believe it. His mind went blank---he couldn't
think of anything. He couldn't make a rational decision. He couldn't
take appropriate action.

"Nezumi, Nezumi!" He desperately kept calling his name, and and hugged
him tightly. He could feel the body tremble beneath his fingers. Through
the cracks of Nezumi's own fingers as he covered his face with his
hands, he could hear Nezumi groan.

"St---Stop it\el "

"Nezumi? What's wrong? Stay with me, Nezumi!"

"Stop---who\el who's\el " Nezumi's fingers latched onto Shion's arm and dug
in. They were shaking violently.

Shion slipped on the spilled water, and collapsed on the floor with
Nezumi still in his arms. A stack of books fell over, and the startled
mice darted out of sight.

"Nezumi, what's wrong? Tell me what's wrong."

\emph{Hang in there. Get a grip on yourself.} He told himself. But completely
arrested by fear, his own body was also shaking. Nezumi. Don't tell
me---not you too---

A wasp would come crawling out. It would come crawling out, breaking
through his smooth skin. If it did---if that happened---

"No!"

\emph{No. No. No. No. No. I can't bear it. If I lost you here, right now, I
wouldn't be able to stay sane. I would go mad. The world would turn
upside-down.}

\emph{No. No. No.}

Confusion inflated his fear, and ground his thought processes to a halt.

\emph{No. This is too much. What should I do? Someone---somebody, please---}

Nezumi's body began to burn. The perspiration that broke out moistened
Shion's hands.

"---Shion---" Nezumi called his name weakly between his groans.

"---help me\el "

Shion felt like he had been given a sharp slap. He was now wide awake.

\emph{Move. Move, before wailing and crying. Can't you do anything other than
hold him in your arms?}

He bit his lip, and willed strength into his arms. He laid Nezumi on the
floor, and tore his shirt open. He put a hand to the base of Nezumi's
neck. It was drenched with sweat, but there was no abnormality. There
was no stain or bulge. He pressed his ear to Nezumi's chest, and
listened to his heartbeat. He measured his pulse. It was quicker than
normal, but it was not erratic. There was no breathing trouble or
vomiting. There was probably zero danger of choking. And his
consciousness?

Shion squeezed Nezumi's hand, and leaned in towards him.

"Nezumi, can you hear my voice?"

\emph{Listen to me. Let my voice reach you. Open your eyes, and answer me.}

"I'll help you, I promise I will." \emph{I'll help you this time. So please.
Give me a response. I want you to answer me. No---I know you'll answer me.
You have to.}

"Nezumi!"

\mybreak

"It's a type of mutation that's never been seen before. But the fact
that they're still active in this cold---it's impossible in the natural
world." Shion abruptly clipped his words, and lapsed into silence as he
looked down. It looked like he was trying to settle into a contemplative
state.

\emph{Guess I better not disturb him.}

Nezumi thought to himself as he sipped his hot water. Whatever the case,
today was over. He couldn't predict what would happen tomorrow. But that
meant it was all the more meaningless to be dismal, fearful, or to brace
oneself for tomorrow. He didn't believe in any God. He knew right down
to the marrow of his bones how banal a word like "fate" was. He didn't
think of entrusting himself to a word like that. He would not be swept
up in its flow. If he gave up and abandoned his struggle, the only way
to go would be down. He would descend into death, or something worse.

So he would continue to rebel. How many years had passed since he had
decided to? But he would continue to rebel.

It meant that he would not abandon his will to fight, and that he would
hold his ground against a tomorrow he could not predict. It also meant
that at times, he would probably sink into deep contemplation like
Shion. It was certain that Shion was struggling and fighting in his own
earnest and singular way. It was clumsy, off-the-mark, and poorly
developed, but he was still fighting. He was taking his stance in his
own way. He wasn't trying to run away from battle. He had never run away
once. Inukashi was right---Nezumi was a little impressed.

Shion's white hair shimmered orange, lit by the light of the heater. He
never said it out loud, but Nezumi liked Shion's hair. He thought it was
much more beautiful than the black hair he had before.

Maybe he would give that hair a light caress before telling him he was
heading off to bed. He would disappear for the time being, so as not to
disturb Shion's struggle.

He reached out.

A flash of light pierced his head. His breath caught in his throat. A
wind, a turbulent gust whipped around the inside of his skull. His body
teetered. He was falling. Crumbling. His consciousness was being stolen
away.

"Nezumi!"

He heard Shion scream. Simultaneously, a song came flowing into his
ears. Someone was singing. Someone was singing a song that sounded like
murmurs of the wind---

"St---Stop it\el "

He wanted to plug his ears, but his hands would not move. He was being
dragged in. What was this? What was happening? An expanse of greenery
spread before him. He could feel the humid heat of the grass. Hot
vapours rose, filled with its grassy scent. Numerous trees nestled
together, and ferns grew in clumps. Layers and layers of tree leaves and
underbrush covered the ground in every shade of green. And he could hear
a song from far away. Song? Was it a song? It was. For sure---but what
mingled with its sound\el the buzzing of wings. Countless insects were
flying around.

This sound, this song, this scene---he had seen it before. Somewhere\el 

\emph{No, I'm being dragged in.}

"No!"

A scream tore through. Was it his own? He was clasping something. He was
being embraced by someone.

This was a lifeline. He would not let go, no matter what.

He used all his strength to dig his fingers in.

The firm sensation of flesh brought his consciousness a little closer to
the surface.

\emph{Shion.}

He clung desperately.

\emph{Shion---help me.}

\mybreak

The bluish-grey elevator doors were closing silently. The moment their
edges met as they closed completely, Fura let out a deep sigh. The
Security Bureau officials flanking him on both sides were as still as
stone statues.

"Why\el "

He knew it was useless to ask, but he couldn't bear to be silent.

"Why are you arresting me?"

Just as he thought, there was no reply. He posed a second question.

"Is this\el the Correctional Facility?"

His knees were shaking so badly, he could barely keep standing. This
morning, he had left the house as usual. His wife had seen him to the
door, with their son in her arms.

"The edge of your mouth still looks painful."

"It's nothing. You can't even tell."

"Silly you, falling down and getting yourself hurt like that."

"Don't tell anyone, now. I'd be so embarrassed if anyone found out I got
this from falling down the stairs at the park. I've been keeping this a
secret."

His wife's face suddenly grew concerned.

"Be careful. Thank goodness it was just a small wound this time. But
every time I think something might happen to you---I get chills all over."

"Nothing's going to happen to me. I have to get going now."

He had kissed his wife on the cheek, and gotten into the car that had
come to fetch him from the Central Administration Bureau. Just before he
got into the car, his wife had called him.

"Dear, you'll keep it in mind, won't you?"

"Keep in mind?"

"My going back to work. I'd like it to happen in the new year."

His wife had a career at the Traffic Administration Bureau. Since their
son had been recognized as an elite and guaranteed a perfect educational
environment, she had expressed a desire to return to her workplace and
resume her work.

"It should be no problem."

In No.~6, a woman who had given birth but desired to go back to work had
an almost-one-hundred-percent chance of obtaining support to achieve it.
Fura's direct superior was a woman with two children. When people were
given jobs, they were chosen not by gender but through judgment of their
individual skills.

"You should start making preparations for returning. If there's anything
I can help with, I'll be there to do it, of course."

"Thank you. That makes me so happy." His wife smiled. Their son wriggled
in her arms. He flailed his arms at Fura.

"Papa, a bug was flying."

"Huh?"

"A bug was flying. A black bug."

"When it's so cold outside? Ha ha, it would have to be a little warmer
for there to be any bugs flying around."

It was sunny, but a biting northern wind was blowing. Perhaps it would
snow in the afternoon. \emph{Maybe I'll leave work early today.}

He waved to his wife and son. The car glided forward. It was a morning
like any other. Other than the wound on his palm that throbbed with a
dull pain, there was nothing out of the ordinary. It was a morning like
any other.

Things began to change when they had passed through the gates of
Chronos. His car was stopped by Security Bureau officials, and he was
asked to comply.

"We're very sorry. On mayoral orders, we've been told to change your
destination." The two men were wearing uniforms from the Law Enforcement
division, and spoke in a polite but firm tone that left no room for
argument. Fura felt a violent chill run down his spine. It was a kind of
chill that had nothing to do with the frigid wind that swept by him.

"You will be transferring onto this car which we've prepared."

"Where\el will I be going?"

"The mayor is waiting."

"City Hall? Then there isn't any need for---"

"We will escort you there."

They transferred onto the Security Bureau car.

"If you will excuse my intrusion---" Vapid words of courtesy were followed
by something covering his eyes. A special eye-mask shut out all the
light from his vision, and Fura was plunged into a world of darkness.

At first he compared it to the darkness of the West Block, but quickly
changed his mind. It was much too different. The darkness of the West
Block was deeper, and more beautiful. It was a deep, deep darkness that
seemed to hide something in its depths. It was frightening and
unnerving, but nevertheless he was attracted to it. He was attracted to
the fact that it made him certain that there was something mysterious
lurking there. He had a healthy attachment for the women in the West
Block, but he had also gone beyond the walls out of a desire to
encounter that darkness. He was perhaps three when he had first felt
like there was something lurking in a dark corner of his yard. He was
scolded severely by his parents for saying so. \emph{There's nothing in this
world that we don't know about. Don't ever say something stupid like
that again.} His mother and father---usually so kind, almost too kind---had
both risen unrecognizably in anger, and chastised their son.

From then on, Fura never made mention of the thing that lurked in the
darkness. In time, he forgot about it. In the West Block he encountered
true darkness, and rejoiced even as he cowered at it. The sensations and
memories of his childhood, long buried, resurfaced again. He was
attracted to it. Yes, he had most certainly been attracted to that
place.

But would that become a threat to his life?

\emph{So my trips to the West Block must have been found out.}

\emph{But what would happen then? Rewriting records is a serious crime. If
it's been exposed, it wouldn't go without grave consequences.}

He would be stripped of all qualifications; his special privileges would
vanish; he would be exiled from Chronos.

He thought of a worst-case scenario. Fura's heart was unusually calm. He
had no attachment to his qualifications, privileges, or Chronos---not as
strong as the attachment he had for the darkness of the West Block. It
was strange. They were perplexing feelings which even he could not
explain.

A boy's face floated into his mind. A snowy-haired, odd boy. He had
announced clearly that he had no intention of returning to No.~6.

He had probably been able to declare it so firmly because of his age; he
was young, reckless, and ignorant. But even so---even if he was young and
foolish, was it possible to cast a place like No.~6 aside so easily?
That was the part he could not understand.

\emph{This is taking rather long.}

This was taking too much time for a trip to City Hall. With this amount
of travel time, they would have passed through the centre of the city a
long time ago.

"Wh---Where are we going?" His voice cracked nervously.

"The mayor is waiting."

"But haven't we passed the Moondrop already?"

"Quiet, please. If not---"

"If not, what?"

He heard a muffled chuckle. It was even more terrifying than threatening
words.

"T-Tell me the reason why I'm being escorted---the real reason. I'm
begging you, tell me."

"Quiet, please," the man on the right said. The man on the left tapped
Fura lightly on the shoulder.

It was a fair amount of time after that before the car finally came to a
stop. When it stopped, he was unloaded and seated in an electrical
wheelchair, still blindfolded. He was wheeled down a long hallway. It
was a very quiet place. He could only hear the subdued sound of the
motor of his wheelchair. The two Security Bureau officials made no sound
as they walked, perhaps due to some special footwear or because they had
been trained to walk silently. When Fura's eye-mask had been removed and
he had gotten up from his chair, the first thing that jumped into his
vision were the doors of an elevator about to close. Beyond the door he
could see a glass-paned room filled with men and women clad in white lab
coats.

\emph{A hospital? No\el this surely isn't---}

\emph{Why are you arresting me?}

\emph{Is this the Correctional Facility?}

He continued to pose questions that received no answer.

\emph{Tell me. Somebody.}

The elevator stopped.

It had descended---gone down.

Correctional Facility. Basement. A place newly-built. A new elevator.

He had abused the powers of his profession to rewrite records. He would
be held responsible, and receive a stern warning from the mayor himself.
Admonition. Punishment.

No, it was nothing like that. Not even half as forgiving.

Terror pierced his body.

"Let me go back!"

He twisted his body.

"Let me out of here. Let me out."

There was a jolt in the base of his neck. It was electric current. His
whole body went numb.

"I told you to be quiet."

He heard the Security Bureau official give another muffled chuckle.

\mybreak

"It looks like the preparations are complete," the man in the white lab
coat said as he turned around. The mayor of No.~6, the first in his
generation, brought his white porcelain mug to his lips, and sipped the
dark brown beverage inside.

"I see. Alright."

"Hmm? Something the matter? You look a little pale."

"I've been busy lately."

"Tired? That's not good. Exhaustion opens the door for all sorts of
ailments. I would advise you to be careful. I'll write you a
prescription later."

"Please."

"The project is almost finished. And until it's complete---no, even after
that---you have to stay healthy. Shall we go, then?"

The mayor put his mug down. It was a perfectly ordinary mug at first
glance, but upon closer examination one could see intricate patterns
engraved onto the back of the handle. It was a considerably expensive
item.

"You're sure you're going to do this?" The man in the lab coat gazed at
him in disbelief for a moment before letting his shoulders shake with
laughter.

"Of course."

"But unlike the girl before, this time---say, what have you done with that
girl?"

"Her? She's well. She's having a little trouble coming to, but soon
she'll be fully alert. She's a very beautiful girl, and I've taken a
liking to her. I'll treat her well."

"She might have been an elite, but she was still a student. The elite we
have in our hands this time is in an actual profession."

"He will be all the more useful because he's in a profession. In more
ways than one. And besides, he was a defective product, was he not,
according to your research? Despite pledging allegiance to our city, he
was exercising treason."

"Well, you're right about that---he was going out to the West Block
without a valid reason. He's recently gotten wounds on his face and
hand, which were probably received in the West Block as well. There are
strong suspicions that he's manipulated records. It most certainly is
treason, but---"

"He ought to be punished."

"In this sort of way?"

"Fennec." The man in the lab coat called the mayor by his old nickname.
\emph{Was it this man who gave me this nickname in my school days, after a
small desert-dwelling fox?}

The man stood in front of the mayor, and placed a hand on his shoulder.

"Fennec, you are going to be King."

The tall man bent forward slightly, and spoke a little faster.

"Your days of overseeing politics as mayor are over. From now on, you
will reign. As the absolute King, you are going to dominate this land."

"I know."

"Then why are you hesitating? Who cares about one or two defective
products?"

"You're right," the mayor relented.

"And this is a contribution. He is contributing to our good. It's an
honourable thing for the man as well."

The man in the lab coat muttered once again.

\emph{You will reign as the absolute King.}

The mayor nodded, and squared his shoulders. \emph{Let us go, then}, he said,
as he ushered the man in the lab coat out.

The room was bare. It was called Experiment Chamber I. Walls of special
alloy ran all around, and there were no windows. The only piece of
furniture was a single chair. A man was bound to it. Fear and confusion
swam in his eyes.

From this side of the wall, they could see everything that was going on
in the room. The man in the lab coat was tapping his fingers lightly on
a control panel with several buttons and lamps. His thin white fingers
moved rhythmically across the panel, keeping the beat, as if he was
playing a clavier.

\emph{Tap, tap, tap, ta-ta-tap, tap, tap, ta-ta---}

\emph{Is it some kind of musical piece? An unsightly switchboard, no matter
how many times I look at it. It looks like a misshapen toy. Couldn't he
have made it something more appealing to---}

"What now, Fennec?"

"What are you talking about?"

"As mayor, will you declare this man's sentence?"

"No, there's no need."

"The woeful criminal doesn't even understand what kind of situation he's
in. Look how terrified he is, the pitiful man. Won't you save him?"

"Save? What do you mean?"

"Give him a chance to acknowledge his crime, and beg God for
forgiveness."

The mayor gave a hearty scowl.

\emph{There he goes again, spouting strange things out of the blue. Has he
always had these odd tendencies?}

"Do you believe in God?"

"Of course not. But aren't there people who wish to obtain mercy from
God before taking their journey, peaceful at heart?"

"There might be. But those people don't exist in No.~6."

"I see. I haven't said anything offensive, I hope?"

"You wouldn't normally make that kind of joke."

"My apologies. Then let us begin."

His fingers, which had been tapping out a light rhythm only moments
before, moved almost carelessly this time to push a button. A part of
the wall turned into a white screen, where various numbers and lines
mapped themselves out.

"It's current data about the criminal on hand. His heart rate, brain
waves, stiffening in muscle tissue---various measurements of each body
part are recorded here."

"I see\el "

"In that room right now, there are waves being emitted at a frequency
beyond the level of human hearing. Sounds are essentially air
vibrations. For humans, those vibrations are transmitted through the
eardrum, malleus, incus, and stapes before they reach the cochlea. You
know that, right? And the range of frequencies that humans can
perceive---"

"Nothing is changing." Fennec stepped forward, and surveyed the scene in
the next room intently. There was no change. The man bound to the chair,
who had been gazing about uneasily, had just cast his eyes to his feet.

"There's nothing to fret about. It's starting. But this will take a
little time. Will you have a seat?"

"No."

"Then shall I treat you to a cup of coffee? I have the best blend of
beans."

"You're offering me to drink coffee? Here?"

"Would you prefer wine instead?"

"No---that's quite alright."

"It seems you're not in the mood to listen to my lecture."

"I'm sorry to disappoint, but I don't have much of an interest in organs
of the auditory system."

The man in the lab coat shrugged, and lapsed into silence. Nothing
happened.

"Are you sure there hasn't been some failure?" the mayor muttered in a
low voice.

"Me? Allow a failure to happen? A rather flat joke yourself, Fennec."

"But\el "

The lab coat's face stiffened. His bloodless face turned even paler, and
a vein in his temple twitched.

Ah yes---he remembered that the man hated the word "failure" more than
anything else. He detested the word as if it had the power to physically
harm him.

He changed the subject.

"So about the incidents that have been happening lately---they appear to
be quieting down for the time being. There have been no other reports."

"There will probably be no more of them in the future."

"Can I count on your word?"

"Of course."

"I'm counting on you. If those \emph{things} keep continuing their activities
in the city, things will get out of hand."

"Those were outlier cases."

"But why are outliers even occurring? And they're all occurring in
people who aren't registered to be samples."

"There must have been instances of carelessness in the preliminary
stages of the project. But it's nothing to be upset about. Outliers are
nothing more than outliers. ---Ah---"

"Hm?"

"It's happening." The man in the lab coat pointed.

The so-called criminal had grown rigid in his chair, his chest thrown
out and his head flung back. He was shaking his head from side to side,
screaming something.

"Would you like to hear the audio?" The lab coat asked him with a finger
poised over a green button.

"No, that's quite fine," Fennec replied hastily, shaking his head, yet
taking care not to make his agitation visible.

If he could, he would not have wanted to see something like this. He
wanted to leave this barren room and return to his office. \emph{My room, on
the top floor of the Moondrop. Exquisite furniture and a magnificent
view---indeed, a place most suited for me.}

"See, take a closer look. \emph{It} is coming out." The lab coat's voice was
trembling. His face wore a dreamy expression. The man in the chair was
no longer moving. How easily defeated he was. The man's hair had grown
white. The snowy strands fell softly to the floor, as if they had lost
the strength to hold on. Senile plaque was starting to dot his
translucent skin. Fennec could tell even from where he was standing.

"Let's zoom in. See," the man in the lab coat jerked his chin at the
monitor. A larger image of the man, his head bowed, filled the screen.
His eyes were wide open, and his mouth twisted; he had the face of one
who had lost his life even before he could decipher what was happening
to him. Brown spots were scattered all over his face, which was lined
with deep creases. His teeth, peeking out from his half-open mouth,
looked like they were about to fall out any minute. He looked like he
was nearing a hundred in age. And the base of his neck---there was a
darker stain there, swollen and stirring. All sound was blocked out in
this room. But for some reason, Fennec felt like he could hear the
sounds of human flesh being eaten through.

It came out.

Wings that shone silver. Antennae. Numerous, constantly moving legs. A
single bee had been born from a human body.

"We're going to capture you," the man in the lab coat muttered. His face
still wore a dreamy look. A clear bubble emerged from somewhere below
the chair. It was ball-shaped entrapment robot about ten centimetres in
diameter. Like a soap bubble, it floated up. It enveloped the bee just
as it took flight, and trapped it inside its spherical body.

"Success!" The lab coat cried. His eyes were bright with tears of joy.
"We've finally succeeded. Ah, I mean---no, this is just the first step to
success. But we've made certain progress, Fennec."

"Indeed. Congratulations."

"It's still not perfect---no, not near perfect. But success is still
success. A little more---just a little more, and they will be completely
under our control. Hatching, acceleration of development, eclosion, and
the laying of eggs. We'll control it all. We'll be able to move them
however we want. Brilliant. Finally, we've finally come this far."

The man in the lab coat clenched his hand into a fist, and paced
restlessly about the room. His cheeks flushed in excitement, while his
lips lost their colour.

"With our last sample, we couldn't control the eclosion phase. With the
male index case, and the male Park Administration worker, the best we
could do was predict the period of eclosion. It's been how many months
since then? In a mere few months, we've been able to get this far. Ah,
it's as if all those long hours were but a dream. Once we've come this
far, it's only a little more. A little more---"

\emph{Some say there is but a thin line that divides a genius and a madman.
I couldn't have said it any better.}

Fennec took his gaze off the man who was pacing and muttering to
himself, and glanced beyond the wall, inside Experiment Chamber I. He
thought "Execution Chamber" might be a better name for it.

The body was gone. It had been carted off to the autopsy room. The chair
had been stored away automatically as well, and the room was now a
barren, empty space. There were no remnants of death. It was a void.

"No, no, I mustn't overindulge in my happiness. Just because we can
perfectly control eclosion doesn't mean that it's free of any problems.
Of course---it's not like we have not had any problems. Ah, yes, we still
have one very large problem. Now, as for what to do with it---Fennec!"

The man's voice cracked in excitement as he barked the mayor's nickname.
Displeasure became little jabs that pricked at his skin irritatingly.

"What is it?"

"I need people."

"For samples?"

"I need those too."

"What type? How many?"

"This time, type doesn't matter. I want numbers."

"Do they have to be people from inside the city?"

"That doesn't matter. I want quantity, not quality. Numbers, Fennec."

"Perfect. I've scheduled a Clean-up."

"Brilliant! I'd like one soon, please. And manpower."

"Manpower\el "

"A capable workforce. I need staff that can be extensions of my own
limbs, but also have the highest levels of intelligence."

"Are the people you have at present not enough?"

"Far from enough. I need more intelligent individuals."

"That would be hard," the mayor said hesitantly. "There's a shortage of
elites as it is. If I transfer any more of them here, we would be
severely deficient overall."

"I want you to give this top priority," yelled the man in the lab coat.
At the same time, the lamp on the wall flashed.

"The preparations are complete in the autopsy room. I must go. What will
you do?"

"I'll go back to the Moondrop."

\emph{That is my proper place, after all.}

"I see. I'm counting on you, then. For both samples and manpower."

A section of the wall slid soundlessly open, and the man in the lab coat
walked out.

\emph{Do we really need him?}

A suspicion suddenly surfaced in his mind. It was so sudden, he had to
clutch his chest to calm his jagged breaths.

\emph{Do I really need him here? Is this project itself even needed? Can I not
rule this land without relying on him or his project?}

He took a few deep breaths to resume his normal breathing pattern. He
stared at the empty space before him.

\emph{How to dispose of the executed man?}

He thought.

Instead of publicizing it as an illness-related death, what would happen
if he announced that he had been executed? He would let it be seen and
known far and wide, what happened to those who broke the rules of the
Holy City of No.~6; those who tried to trick it; those who retaliated
and refused to submit obediently. He would not allow so much as a strand
of hair to rebel against him. He would make that attitude clear. He
would strengthen its enforcement. He would strengthen it enough so that
everyone would know. All suspicious individuals were to be arrested and
escorted away. If circumstances called for it, he could close the
congress.

What would happen? Would the citizens rebel? These were people who had
lived their lives devoid of anything like retaliation or objection: did
they still possess any mind or method to object? \emph{Would my beloved
citizens, as loyal as dogs, as powerless as kittens, dare to post a
rejection against my name?}

His lips curled, and a chuckle escaped them.

\emph{Impossible.}

\emph{There's no way that would happen. They will all cower in the face of
power, grovel, and obey me.}

"Mayor, your scheduled meeting is approaching," his secretary's voice
informed him from a speaker embedded in the city emblem.

"Very well."

"We have a car waiting for you."

"I'm coming."

\emph{But I can't get ahead of myself. We've come this far. There's nothing to
be over-excited about. I will make things proceed discreetly and
artfully.}

He walked towards the wall. The door opened, and he could see the
dimly-lit hallway beyond. It, too, was silver.