% !TeX spellcheck = en_US

\chapter{Your last embrace}

\myepigraph{O here\\
	Will I set up my everlasting rest\\
	And shake the yoke of inauspicious stars\\
	From this world-wearied flesh. Eyes, look your last.\\
	Arms, take your last embrace!}{\emph{Romeo and Juliet}, Act V Scene III}

\lettrine{A}{ white} light stabbed at his eyes.

It was blinding.

The light was overpowering.

The place overflowed with light, and glittered.

It was unmistakable---it was the world of No. 6.

\mybreak

Yes, No. 6 had always been like this. Brimming with light; releasing it.
\emph{I've returned.} Shion clenched his hand into a tight fist. He was thumped
on the back.

"Take a deep breath," Nezumi said. "Breathe out and get rid of all your
emotions. A split second of hesitation or excitement can cost you your
life. Keep your head."

"Got it. You too. Follow me, and don't fall behind." Suddenly, he felt
the urge to laugh. It tickled in his chest.

"What?" Nezumi drew his chin back. "What're you grinning about?"

"No\el just thinking about how great it feels to say 'follow me' to you.
Before, I was always the one to be told that."

"---You know, Shion, you're---" Nezumi closed his mouth mid-sentence, and
shook his head.

The door opened fully. The light hit them head-on.

"Let's go, Nezumi." Shion unclenched his fist, and glided out into the
white light.

\mybreak

\emph{He smiled?} Nezumi shook his head, and chewed his lip. He felt
suffocated, though only a little. \emph{How can he smile at a time like this?
And from the bottom of his heart, like he was really happy.} It wasn't
bravado. It wasn't fake. In a moment they would be stepping into the
Correctional Facility, and yet, Shion had smiled. He had been able to
smile.

\emph{Just thinking about how great it feels to say 'follow me' to you.}

\emph{What the hell? What are we, a couple of students making idle chatter and
laughing on the way home from school? Why? Why is it that you seem not
to feel nervous at all? Don't you understand what kind of situation
you're in right now?}

He could hurl as many insults as he liked. \emph{But}, Nezumi muttered under
his breath, \emph{but it's still amazing}. He couldn't help it; his feeling of
awe was stronger than his desire to insult the boy.

\emph{I can't smile like that. Give an innocent and carefree laugh---it's just
not gonna happen with me. Right now we're about to step into a danger
zone that might as well be a minefield. I can't spare the energy to
laugh.}

He wasn't afraid. He wasn't going to flinch. But he was tense. This
stance prepared him for battle. He needed this shift in mind and body so
that he could manoeuvre himself out of the way of an attacking enemy; so
that he could turn around and sink his fangs into the enemy's throat.
Shion had none of that. He didn't even have the fighting mentality.

Numerous times, Nezumi had felt frustrated at him. \emph{Where did you leave
your fangs and claws behind?} he would think. He had even slapped Shion's
cheek out of sheer frustration.

He had thought that Shion was frail. He was far weaker, far more fragile
than Nezumi. Like a newly-hatched chick, he was defenseless and
powerless\el he had not a single skill to survive in this harsh reality.
But that didn't mean that Nezumi scorned or looked down upon Shion.

On the contrary, he had felt that he needed to protect him. If he didn't
protect him with all the strength he had, Shion would not be able to
survive. He would be crushed. Nezumi had earnestly believed so once.

And he had utterly misunderstood. \emph{I made unfounded assumptions, and that
was my foolish mistake.} He had realized it long before.

Shion was not weak at all. That was why he had been able to come this
far. He had not been crushed; in fact, he was far from it: he had
survived stoutly. He had come crawling up with his own strength. He had
emerged from this brutal reality, stood on this ground, and even smiled.

\emph{Smiled, huh. That's right. You'll do things your way and I'll do it my
way, and we'll overcome this.}

He regulated his breathing.

\emph{It starts here, Shion.}

He couldn't predict in the faintest what was going to happen, what was
waiting for them.

\emph{An abyss?}

\emph{Or a miracle?}

\emph{A return alive, or no return at all?}

He couldn't predict what lay a pace away.

\emph{What's going to happen\el ?}

\emph{When we've run past the finish line, will you still be laughing? Will
you be smiling as you are, unchanged from now?}

"Let's go, Nezumi." Shion glided into the white light. He had to follow,
so as not to fall behind. Nezumi nodded, and stepped out into the light
after him.

Point X. It was marked as such on the floorplan. It was the door at
location po1-z22. It was the only point where the underground blank was
connected to ground-level.

When the door opened, it made a passage-way between the underground
realm and the Correctional Facility. There was a difference in air
pressure, perhaps, for there was a slight air flow.

Shion ran to the right. The floorplan that Fura had filled in for him
rose in his mind as if he were actually seeing it in front of him.

"Fifteen paces to the right. We're safe until there. There are no
sensors. Beyond that, we've got stairs."

"And there?"

"Laser beams: one on the second step, running 45 degrees; one on the
stairwell, 15 centimetres above the floor, running parallel; one on the
eleventh step running 60 degrees. As long as we don't touch those, the
surveillance won't go off."

"Hm. Pretty lax."

"Only up to here." This was the basement floor of the Correctional
Facility. Excluding Point X, there was no contact to outside areas, so
naturally, there were no windows or doors. Facility workers, personnel,
and visitors who had the appropriate identification chip and didn't need
to worry about the sensors came down by the stairs or elevator---the
legitimate route. But other than that, the only way to get here was
through the underground realm.

Adding to that fact, none of the departments here handled confidential
material, and the risks of infiltration were infinitely close to zero.
It was understandable for security to become lax.

No one had probably predicted that Point X, or location po1-z22 would
ever open.

"Nezumi."

"Hm?"

"How much time do you think we can buy?"

"One---no, at least two minutes."

\emph{Two minutes? Can we buy that much?} The change in Point X had probably
already been registered by the security system. Could they even buy two
minutes until the monitoring staff realized and took appropriate action?

"Inukashi's working his magic," Nezumi said. "It's probably a bit of a
hullabaloo up there."

"Hullabaloo?"

"You'll see in time. The joyous festivities are only beginning. Anyway,
we've got two full minutes. It's ours to use."

"Two minutes, huh."

"Feels like an eternity, doesn't it."

"Sure does," Shion said drily.

Second step, 45 degrees; stairwell, 15 centimetres parallel; eleventh
step, 60 degrees. They emerged at the top of the stairs. It took a bit
of time, since they couldn't just dash up. Approximately 1 minute, 06
seconds left.

From this floor began the ground-level part of the Correctional
Facility. There was an entrance hall, where the largest number of people
came and went. Personnel came through a different gate than that of
prisoners, and gathered on this floor. From here, they dispersed to
their respective workplaces. Everyone was cross-checked minutely at the
entrance, but once they were through, it seemed like inspection on the
rest of the floor wasn't as thorough. The higher the floors, the more
strict it became.

The top floor was where they were headed.

It was the deepest and furthest part of the Correctional Facility,
encircled by many layers of security networks. They were not headed for
the imprisonment facility, which protruded like a bump from the main
tower.

It was the furthest part of the Correctional Facility. That was where
Safu was.

Shion knew in his guts.

Safu was a certified elite. Such chosen ones were furnished with the
best educational environment from a young age. Investing ample time,
money, and labour into developing elites was a fundamental political
policy of No. 6.

Shion couldn't imagine No. 6 taking an elite that they had raised so
carefully to throw her into prison with the rest of the inmates. If she
had been arrested in connection with him, then his mother Karan wouldn't
have been safe, either.

But it had been Safu who had been taken, and not Karan.

Then it must mean that she was arrested not in connection with him, but
on the conditions that she herself fulfilled. The fact that she was
elite, perhaps, and without parents, or perhaps because she was female---

\emph{"Sample Collection Status---I remember there being a section like that in
the Health and Hygiene Bureau's data,"} Fura had said. Sample. Mock-up.
Specimen.

No. 6 was taking samples from within the city, and apparently in secret.
Citizens were being extracted, unbeknownst, to become specimens. There
was no way this wasn't related to the rumour of agitation and
abnormalities trickling out from inside the city.

Shion knew this too, in his guts.

If Safu was a sample who fulfilled their various requirements, then she
was valuable. They would probably need a suitable facility in which to
handle such a valuable sample.

That was why Safu had to be on the topmost floor, the Special section of
the furthest part of the Facility. He wasn't one-hundred percent sure,
but it was very likely.

Shion felt a violent chill.

Not at No. 6, but at himself.

\emph{How would I treat a valuable sample?} He felt a chill at how he was
turning this over in his mind coolly. He felt goosebumps form at his own
thoughts, which placed Safu in that position.

\emph{I need to be calm and rational. I need to be in this state of mind; it's
what I need most, especially in danger.}

\emph{Don't get distracted, don't get fooled, don't lose sight.}

Nezumi had taught him.

Being calm meant repressing the furor of his feelings. The restless
tides of his human emotions lurked constantly in his heart; and yet, he
had to suppress them inches from the surface. That was how it was. If he
let himself lose feeling and emotion completely, all that would remain
would be a heartless being.

\emph{But can I say that I'm not heartless? Maybe there's a part of me that's
gone completely cold, and I'm just mistaking it for calmness.}

He gritted his teeth.

\emph{Don't get distracted, don't get fooled, don't lose sight. And don't
wander.}

\emph{This isn't the time to be getting lost.}

There were hurried footsteps. Two sets. One was plodding and heavy, and
the other was light.

"Why does it smell so horrible? I can't stand it." Two men clad in white
coats came running down the stairs. Both of them had handkerchiefs held
to their noses. One man was heavyset and in his forties; the other man
was still young and scrawny.

Shion crouched in the shadow of the handrails. The men stopped right
before his eyes, and took deep breaths.

"I feel faint. What in heavens is this smell?" the middle-aged man
grumbled.

"Apparently the cleaning robots broke down. Instead of cleaning, they're
strewing trash everywhere, so I hear," answered the younger man, wiping
his brow. The middle-aged man was clearly not feeling well, for the
colour had receded from his face.

"It's impossible to get any work done in this. I feel like my nose is
going to fall off," complained the older man.

"Unbearable, isn't it? Do you suppose it's because of---you know, that?"

"That?"

"Today's the Holy Celebration. We're probably suffering some kind of
heavenly punishment because we're working on a holiday."

"It can't be helped. When you work for a research organization, you
can't always get your vacations by the calendar. But being rather
unscientific, aren't you, saying things like 'heavenly punishment'?"

"I guess." The man paused. "But these days, I find it suddenly occurs to
me that\el "

"Occurs to you? What does?"

"\el That maybe someday, the heavens are going to punish us. That if we
keep going like this, we'll eventually pay the penalty."

"What? And who do you suppose would be able to exact punishment on us?
Are you sure the smell hasn't short-circuited your brain?" the older man
said sardonically. "---You listen to me: even if you happen to have
unscientific thoughts, don't say them out loud. You'll earn the brand of
an ineligible citizen. And you can forget about your reputation as a
researcher."

The young man shrugged, and lapsed into silence.

Shion turned and signalled to Nezumi with his eyes. Nezumi acted at
almost the same time. Nezumi twisted the arm of the man in front of him,
and pressed a knife to his throat. Shion also burst out, and twisted the
young man's arm behind him.

"Wh-What---"

"Don't move. Don't make a sound. Make a noise, and I'll kill you."
Nezumi's voice was low, heavy, and cold. It was the voice of a murderer.
It agitated fear inside the person, and sealed any attempt at a
struggle.

Shion was yet again faced with the truth that Nezumi was an incredibly
talented actor.

"You too," he whispered in the young man's ear. It didn't go as well as
Nezumi. But Nezumi's voice and his silver knife played its part well.
The two of them showed no signs of struggling. They stood stock-still,
like wooden poles. Only their bodies trembled slightly.

"The door on the right," Shion said. "Hold the name tag on his chest up
to the sensor."

Nezumi nodded, and positioned the man in front of the door, with his arm
still twisted behind his back. The sensor embedded into the top part of
the door activated, and blinked on and off.

The door slid silently open.

"A change room," Nezumi said.

"Yeah."

"I see. A perfect hiding place for these gentlemen." Even before
finishing his sentence, Nezumi had spun around nimbly and had ground his
fist firmly into the man's stomach. Shion pushed the young man's body
forward. The man tripped over his own feet. The blade of Nezumi's hand
swung down upon his neck. It all happened in the blink of an eye.

The two men crumpled to the floor without uttering a single sound.

They stripped the men of their coats, and shoved them inside the
lockers. \emph{Like highway bandits}, Shion thought fleetingly. He didn't feel
strange about it, nor did he feel guilt. One more upper hand, one more
step forward. That was all he was setting out to do. He slid his arms
through the sleeves of the white coat.

"How do I look?" Nezumi twirled in his white lab coat.

"You look good."

"Thank you. They're a fine set of stage costumes. A little on the big
side, though. So? These name tags function as ID chips, then?"

"Yeah," Shion answered. "The door opened, so I think we can be sure
about that." He figured even No. 6 wouldn't embed each and every single
Facility employee with a chip. Embedding them inside the body would make
them incredibly difficult to retrieve. If they were to go through the
trouble, they would chip people who didn't need to get them retrieved:
first, prisoners; then, those with access to the most confidential
information---those who could access the top floor by their own will.

He had guessed that other personnel would use an identification item
which they could wear and take off easily, and could distinguish at a
glance.

His guess was right.

With these chips, they would go as far as they could go.

Shion and Nezumi made eye contact. No emotions swam in those grey eyes.
He felt somehow relieved. No matter what situation he was in, he would
have these unwavering eyes by his side. They had been like a sturdy
supporting pillar for Shion. All this time, they had supported him.

Shion closed the locker.

\emph{No, Shion. From here on out, you have to be the one to blaze the trail.
Instead of the stern, you have to be the prow.}

They exited out into the hallway. An odour permeated the place, which
smelled a lot like rotting garbage.

"Hey, what's going on? What's this smell?"

"The whole building is full of it."

"I feel faint. I think I'm going to throw up."

People burst into the hallways, or came clambering down the stairs,
holding their hands or handkerchiefs to their mouths. Some were deathly
pale. Others had a sheen of sweat on their foreheads, and still others
were close to tears.

Shion furrowed his brow, not at the stench, but at the commotion. It was
indeed a bad odour, but was it something to make such a fuss about?

The smell that wafted over the marketplace in the West Block was nothing
like this. It was a more concentrated, more vividly disgusting stench.
And everyone lived in it. They raged, harangued, drank, sometimes
laughed, and cried in it. They lived every day there.

But this, this was merely---

"They haven't any immunity, after all," Nezumi muttered, as if to sense
what was in Shion's heart.

\emph{No immunity. Well, I guess that's true.}

Disinfection, odour removal, humidity control---artificially building a
comfortable environment naturally meant the removal of everything
unpleasant. No. 6 had received its name as the Ideal City, the Holy
City, through purging and exterminating rubbish, refuse, bacteria,
viruses, smells, odours, and noise---all of it.

No. 6 had a standard frame, and did not tolerate anything or anyone who
crossed the boundaries of this frame. It concerned not only smells,
noise, and bacteria; it purged humans as well. It ruthlessly cut them
away. The majority of prisoners in this Correctional Facility were not
criminals in the real sense; they were merely people who had exceeded
the permissible bounds of the Holy City. They had not declared their
loyalty to the city, or they had raised an objection. They had not
complied. They had questioned its ways. There were probably a great
number of people who had been imprisoned on a charge of these crimes.
The rest were those who had committed crimes due to their poverty, or
out of want of food. And underground, the residents of the West Block
were groaning in pain.

Expel all undesirables without an exception.

This was the world of No. 6.

The result of the policy had shown itself in this small scene.

Any faint smell was enough for these sensitive people to react and
panic. It was a sign that the physical tolerance levels of the citizens,
like their city, were becoming dangerously low.

How fragile they were.

Had Nezumi perceived this fragility? It was a slight, almost
unnoticeable crack. But even a crack small enough to be overlooked could
be a trigger for collapse.

This frailty, this defect in its resistance, could be the wound that
would seal No. 6's fate.

Had Nezumi seen through all of this, too?

Shion didn't know.

He realized he barely knew anything about Nezumi. He thought he had
begun to see into his past, into how he had been raised, but---

He didn't know. He knew just as little as when they had first met.

Nezumi was almost like a deep forest.

No matter how far he waded in, he could never gaze out over its
entirety. Here, clumps of flowers bloomed; here, a bowed branch bore
fruits. Here, a spring gushed forth, and he could hear the gentle sound
of its flow. He had definitely seen these various scenes, but they were
mere parts of the deep, vast forest. Perhaps he would emerge from the
dense trees to be faced with a sheer cliff. Perhaps there lurked
man-eating beasts. Perhaps a scene totally unknown to him would stretch
before his eyes. He didn't know.

No matter how far he waded in, Nezumi never revealed his entirety to
him. The further he waded in, the more unfathomable it got.

\emph{I've wandered and gotten lost in an endless forest. I'm drifting, a
tangle of throbbing pain and dreamy ecstasy.}

\mybreak

There was a cotton handkerchief in Shion's coat pocket. He used it to
cover his nose and mouth. It wasn't to shield against the smell; it was
to hide his face. This way, the risk of being spotted would lessen.
Nezumi also pressed a white handkerchief to his mouth.

They climbed the stairs. The odour gradually grew stronger. Still, the
security alarms didn't go off.

A chime sounded, and his feet froze on the spot. A bead of sweat rolled
down his temple.

"Commencing odour removal. Commencing air filtering. Operational level
8.5. The air quality of the building will return to normal in
approximately two minutes, sixteen seconds."

The announcement was made by a mechanical voice imitating a female
contralto. A chubby man beside Shion let out a great puff of air. Shion
also breathed out quietly into his handkerchief.

"Good heavens, we're saved. It's torture, this smell."

"I don't think I can stand this for two whole minutes." Behind the man,
an equally chubby woman had twisted her face into a scowl. Her skin was
flawless, and her red pouting lips were strangely alluring. Shion and
Nezumi tried silently to slip by.

"Oh---hey, you there!" The man called at them. Shion's heart skipped a
beat.

\emph{Thump, thump. Thump, thump.}

His pulse was racing painfully. Sweat erupted on his face.

Nezumi twisted his neck around, his handkerchief still clamped over his
mouth.

"Yes?"

"Where are you going?"

"We're going\el back to work."

"Third floor?"

"Yes---third floor." Nezumi coughed lightly.

"The stench is horrible up there," the man said. "You'd be better off
going down. I'd suggest you avoid the area entirely for a while. I can't
imagine you could get any work done in that."

"---We can't really afford to leave. We're doing a rush job right now\el "

"Rush job? On the third floor?"

"Yes\el "

"But the third floor is for resource compilation and management systems.
What section of the third floor are you?"

"Hygiene Management," Shion answered. He traced the floorplan in his
head.

Third floor. He could guess judging by the layout of electric circuitry
that the General floors ended at the third. Starting from the fourth
Special floor, the circuitry spread into a fearfully complicated web.
The fourth floor was connected to the Surveillance Wing of the
prisoners. Mobile barriers were placed at equal intervals in the
hallways, and the number of sensors were over three times that of the
General floors.

The majority of Facility personnel could only access as far as the third
floor. They had no need to go further. What sections were laid out on
that third floor? The floorplan rose vividly in his mind. If he
remembered correctly, the Hygiene Management department was nestled in a
far corner of the third floor.

"The source of this smell still hasn't been identified," Shion said
hesitantly. "We Hygiene Management employees are in a bit of a panic
right now. We're not getting any data of foreign objects coming in from
outside, so there's a possibility that something has gone wrong inside
the building\el "

"Oh, really? According to Management Systems, there was a maintenance
problem with the cleaning robots, and they supposedly broke down and
started strewing trash everywhere. That's not it?"

"Ah, well, that's\el " He was at a loss for words. Nezumi answered in a
low, hoarse voice.

"The smell seems too strong for just that. We're doing an emergency
investigation into whether there was something mixed in with the
garbage. We've had no previous cases, after all\el we're fumbling, truth
be told."

"Hm. I see. Were there always young'uns like you in that section,
though?"

"We're not---that young," Shion stammered.

The man craned his neck to inspect him. "What happened to your hair?
It's gone all white."

Shion couldn't find any words to say. He had forgotten about his
hair---white, to the point of transparent. No doubt it was extremely
noticeable. If he said he was born with it, people would probably be
suspicious about never having seen him before.

\emph{What to do?}

"I, well\el I tried dyeing it\el "

"Oh, how pretty," the woman smiled. "It's \emph{very} pretty. So nice and
shiny. What did you use to get it to look like that? Tell me all about
it."

"Sara, stop flirting with him."

"Excuse me? \emph{Flirting?} How rude. I don't know why you can't be a little
more polite. Ugh, this \emph{smell}. I'm sick of it, and I'm sick of you, too."
The woman stalked off down the stairs.

"Wait---hey, Sara! What was that supposed to mean? Hey! Wait up, Sara.
Wait!" The man wiped the sweat off his brow as he followed after the woman.

"A romantic spat if I ever saw one. That guy supposedly tries to pick up
ladies in broad daylight. At work, no less." Nezumi shrugged. "Saved our
asses, though."

If the man had questioned them any further, they would have been in
trouble. Shion felt a coldness around his armpits.

"You've gotten pretty good at lying. But not quite polished enough on
the finish."

"Not as nearly as good as you. Looks like I'll need a lot more
training."

"Good call."

The third floor was white-walled and white-floored, and though it was
neat, it was eerily blank.

"So this Management Systems room?" Nezumi said.

"Left-hand side. It's a glass-panelled room. Nezumi, surveillance camera
right above you. Don't look up. Be careful. There's also a 360-degree
camera on the ceiling to your top-right after you enter the room."

"Roger that."

The odour removal and air-conditioning mechanics were well underway,
evidently, for the smell had dispersed considerably, and did not bother
them much. The confusion was beginning to settle.

The glass doors slid automatically open, and a thin man with a jutting
chin came out carrying a vacuum. He looked ill; there was a dead look in
his eyes, and he was horribly pale.

"I've done it\el I've actually done it," they heard the man mutter as he
passed them by. "I've done it\el but\el serves them right\el serves them
right\el "

"Get out of here quickly," Nezumi whispered to the man's back. The man
stopped in his tracks, and glanced furtively at Nezumi.

"Did you say something?"

"I told you to get out of here. Don't dally."

"You---"

"You've pulled it off admirably. A job well done." His tone was that of
a king congratulating a subject. The man blinked. His Adam's apple
slowly bobbed as he swallowed.

"Who\el are you?"

"I'm grateful. Now make a good getaway." Nezumi flashed the man a
seductive smile, and slowly set foot inside the Management Systems room.
He didn't look anything like he was in a rush. He had the footsteps of
an honest employee returning to his work.

The security alarm did not go off.

\emph{We're still good.} Shion clenched his hand into a fist. His palms were
sweaty. \emph{Things are going better than I thought. If they continue like
this, maybe we'd be able to pull it off.}

\emph{No, don't let your guard down. Even a slight moment of inattention could
cost us our lives.}

Following in Nezumi's footsteps, Shion also entered the room neither
hastily or cautiously, maintaining a perfectly ordinary step and speed.

It was spacious inside, and the room was sectioned off with clear walls
of reinforced plastic. The booth closest to where Shion and Nezumi had
entered was empty. There was no one there. The booth next to that also
showed no signs of anyone. They had probably fled, unable to bear the
smell. But the smell had now been mostly removed; people would be
returning soon.

"This must be the management division for ventilation. And---"

"The operating button for opening and closing Point X should be here,
too." Nezumi's gaze focused on the right-hand edge of the control panel.
A small, round button. It was a vivid, almost cheap-looking shade of
green. It looked almost out of place amongst the other switches and
touch panels. Shion stood in front of the control panel.

"Oh, yeah," Shion said. "The surveillance and management of all
entrances and openings take place beyond this wall, but the door to
Point X is the only thing that doesn't."

"Is that strange?"

"No. It's just as you said: that door is impenetrable. It will never
open. No. 6 never considered the chance of someone coming in through
that door. Of course, they never considered opening it from their side,
either. So this button for them was actually meaningless. That was why
it didn't matter where they put it. There was no need to keep watch on
it, anyway."

As he spoke, Shion tapped a large screen in the centre of the
control panel. Of course, he was concerned about his fingerprints being
lifted, but the screen wouldn't function if he didn't touch it directly.
Security measures would take effect, and it would lock itself.

"That's right," Nezumi answered. "It's indulgence. Indulgence that comes
from complacence. No. 6 thinks nothing in the world can threaten them.
Makes you laugh, doesn't it?"

Point X was created when Rou was placed in the underground settlement,
though at the time, it had probably been mere caverns. The caverns
themselves were to be his prison. Then, the Correctional Facility
gradually grew closer to its current form: a new, even more secure
imprisonment facility than the caves.

The underground caverns, Rou, and the other prisoners were forgotten.
Either that, or they were written off as people who had never existed.

Only the door remained.

The screen changed into a layout of the Correctional Facility's
ventilation system.

"Nezumi, look here." There were stairs leading from the fourth to the
fifth floor, and to the top floor as well.

Each step was 120 millimetres deep, and 240 millimetres high. It was
quite a steep slope. The stairs were also barely wide enough for one
adult to climb. It was more like a ladder than a set of stairs.

Nezumi peered in. "What's this?"

"Stairs for construction and maintenance. Everything is usually
computer-regulated, but once in while they would probably need some
manual labour. The stairs were probably made with that in mind. They
probably haven't been used much, though."

A soft exhale escaped Nezumi's lips.

"I didn't know there was something like this here. Did you know about
these stairs all along?"

"No, I only guessed," Shion said. "I noticed it when I first looked at
the floorplan. It was an unusual blank space."

"I didn't notice."

"It's in the wall. There was a narrow space between the outer and inner
walls. This particular part was wider than the rest."

"So you saw something that I overlooked."

"That's right."

\emph{Tsk.} The sound of a frustrated click of the tongue.

"And is that spot gonna welcome us in like an amusement park? There
aren't any anti-trespassing devices?"

"I don't know. This screen only shows ventilation-related systems. I
can't tell about anything else."

"You said it was a blank. So there's nothing written in there."

"No."

"Then how about a door? If there are stairs, there has to be a door that
leads to them."

"I don't know about that, either. There's nothing written here that
might pertain to that."

"Then we don't have a next move."

They did not have a next move. But they would have to move anyway. If
they couldn't use the central stairs or the elevator, this was the only
route that would take them to the top floor.

Shion had stared at the floorplan long enough until he felt his head
throb, memorizing the interior structure. This was the conclusion that
he had drawn as a result.

Their chips would not take them any higher. They would have to
set foot on these stairs, using any method they could. If only they
could bound up the steps in one dash. The mother computer was on the top
floor. They had to get there. They had to reach it, no matter what.

This was the only way.

In a way, the Correctional Facility was like a prototype of No. 6. All
information, activities, functions, and monitoring networks led back to
the mother computer. This meant that all the power was in the hands of
the single person who could control the Mother freely.

A perfect hierarchy, in which the king was the absolute summit---that was
what they were trying to create. It was an incredibly vast, yet foolish
ambition.

Humans could control machines. They could develop and refine devices,
and use them in any way they liked. But it was impossible for humans to
dominate other humans. Even empires which had proudly stood for a
thousand years, crumbled after that millennium. Humans could not
dominate other humans. The system would always break down.

Shion had learned this outside No. 6. The ones inside---those reigning
over No. 6---had evidently not. That was why they could continue to
believe in this illusion that they would conquer all.

They were foolish. But foolishness created a vulnerable opening. If they
could make contact with the mother computer, they would be able to find
out Safu's location, and they would be able to halt the Correctional
Facility's functions, if even momentarily.

With a centralized system like this one, where everything concentrated
into this one single point, then all they had to do was attack that one
spot.

No. 6's fragility had also revealed itself here.

Shion's fingers flitted about. The screens changed one after another.

The barriers on the fourth floor. They had to overcome those somehow.
They had to break through the open space before the walls closed in on
them and blocked their route off.

And to do that---

The inside of his head settled into a cold stillness. Only his fingers
kept moving, and finished one task, then another.

"Hey, there's something wrong here," yelled a man in the next booth.
Several workers had already returned. "The activity lamp for Point X is
on."

"Point X?"

"On location po1-z22. The door's been opened and closed. It's recorded
here."

A tall, young man tilted his head in perplexity. "Po1\el that's
underground. Did we ever have a door there? Are you sure it's not a
display error on the part of the computer? Maybe the smell was so bad,
even the computer couldn't handle it. Haha."

"This isn't a joking matter," the other snapped. The man closed his
mouth.

"Two minutes and forty seconds ago. That was just now. The door on Point
X opened right in the middle of that commotion."

"Is there something wrong with it opening? Doors are supposed to open,
aren't they?"

"It's not general entrance door. It's not an emergency exit, either. The
staff don't use this door."

"Oh. Then, where's the door supposed to lead?"

"I don't know. I've never heard of it. But this means that a door that
was never supposed to open has opened. This---"

Evidently the sound-proof setting was off, for the boys could hear the
muffled voices of the two men conversing.

"Our time's up." Nezumi undid the buttons of his lab coat. Shion stood
up as well.

Two minutes, forty seconds. It was much longer than they had
anticipated. It looked like Fortune had not abandoned them just yet.

"Oh---hey! You there." A grossly overweight mass of a man was standing in
front of them, blocking their way. "What are you doing there? Who are
you?"

Nezumi flung his coat at the man, which landed on the man's head and
draped over him. The man flailed his arms and staggered. Nezumi swept
his feet out from under him. The man fell sideways with a resounding
crash, and gave a muffled groan.

"Excuse me." Nezumi stepped over the man, and exited into the hallway.
Shion followed suit and hopped over the man's body.

"What was that?"

"Somebody---an intruder! Somebody help!"

"What? Has the emergency bell gone off?"

An agitated buzz rose from behind them.

"Nezumi, run up the stairs."

"Gotcha."

If the sensors caught any intruders, the security shutters would fall
automatically. Could they reach the fourth floor before all the shutters
went down?

The lighting on the stairs turned red. The shutters of special alloy
silently began to close.

They were fast.

"Shion, go in head-first."

Nezumi and Shion dived into the narrow space.