% !TeX spellcheck = en_US

\chapter{In my lusts}

\myepigraph{Who am I? A man seeking happiness.\\
	I sought it in my lusts and did not find it.\\
	And all who live as I did fail to find it.}{Tolstoy, \emph{Walk in the Light While There Is Light}}

\lettrine[ante=``]{I}{t was} summer, and I had just turned twenty when I was chosen as a core
member of the rebirth project.

When I was born, this planet was already in the midst of danger. Due to
numerous wars, pollution, and environmental destruction, over half of
the territory on earth had been devastated to the point of becoming
inhabitable for human life.

Global warming had sparked a spread of whole new contagious diseases;
weather patterns were abnormal and unpredictable; wars between nations
and tribes were neverending; nuclear weapons were being used.

By the time we realized it, humankind had driven itself to the verge of
extinction. We survivors only realized after being this close to the
edge that we had to reflect on the foolishness of our actions.

Our national framework had long crumbled away. So we thought, why not
live life over again? This time, let's live our lives proper, and not
make the same mistake.

The people who had managed to survive on this planet crossed the borders
of race, nationality and ethnic origin, and vowed to live humbly upon
the foundations of peace and harmony.

And so six cities were born.

There were not many regions left which were suitable for human life.
Half of humankind had died out. People gathered in those limited
regions, and gradually began to build their own cities.

There was once a city here as well. It was a beautiful city. There was
an almost miraculous amount of abundant nature still left intact on this
stretch of land. Admittedly, there was no ocean---but there were deep
forests, lakes and marshes, and plains. Yes: it was indeed miraculous.
It was a place of miracles, like the rose that blooms in the midst of
blasted pieces of rubble.

The city was established, and the people lived quietly, abiding by their
vow. I was born in that city. I was born, I grew up, and I became a
researcher. So did your mother, Shion.''

Having said so, the elder smiled.

"My mother?"

"Yes. Karan grew up in the same town, and she lived there too."

"What kind of relationship did you have with my mother?"

The elder's smile widened. It carried a hint of boyishness. "We were
childhood friends."

"Huh?"

"Karan and I were childhood friends. I was much older than her, but we
often played together. Karan was very skilled at climbing trees, and she
could scramble up any of them, no matter how big. It often made me
nervous, how daring she could be sometimes. Yes, I remember. She was a
beautiful and free-thinking girl. To think she is now a mother with a
grown son\el "

"I don't care about Shion's mother," Nezumi interrupted. "Or did you and
Karan fall in love, and was Shion born? Is that how it's gonna unfold?
That would be an interesting twist."

"Nezumi!" Shion said sharply.

Nezumi shrugged, throwing a glance at him. "Third-rate plays are usually
written like that. Rou, I want you to speed it up. You said so yourself:
we don't have time. There was a city, and you were born and raised
there, and became a researcher. Then you were chosen as a member of the
rebirth project. From there\el things started going haywire."

The elder drew a breath. "Is that what you think?"

"I do. Just look at the name, 'rebirth project'. It sounds phony
already. What are you gonna rebirth? What were you planning on reviving,
anyway? No wait, I already know the answer. The city got repaired,
albeit only barely. Life was getting back on track for most people. They
were freed from their days of being bedmates with death and extinction.
Then after a few more years down the road, you were ready to forget your
past mistakes. You wanted to abandon your vow, and dominate over the
land again. That was what the project was for. They were probably
gathering intelligent young people. It was the start of a project to
become more developed, more powerful, more wealthy. Am I right?"

Nezumi knitted his brow. Hatred and loathing were chiseled into his
refined profile. He spat the words from his mouth.

"Fools."

The elder's body trembled and grew rigid as if the word had struck him
like a whip.

"Repeating your past mistakes: it's the epitome of foolishness. But you
wanted to dominate. You contrived to make yourselves more plentiful by
using the people and things around you as stepping stones. As a result,
a hideous monster was born in a land that was once like a rose in the
ruins. That was No.~6."

\emph{More developed, more powerful, more wealthy. Was No.~6 what towered at
the end of this desire?} Shion also felt himself tremble.

"It was in a blink of an eye," the elder sighed. "The city grew at
astonishing speeds. Sometimes I wonder if it hadn't all been a
nightmare."

"It's reality. It's unmistakable, and you guys created it. Rou, weren't
the people at the centre of the rebirth project the same people who are
at the administrative core of No.~6 right now?"

"They were all there. Everyone was young and intelligent. Each one of
them had his own strong ideal."

"All the faces in this photo?"

"Yes. However, they are not the entire group. That---is from when Karan
came to visit my lab. I remember, the person who took this photo was a
young journalist who was here to do research. He also had his own ideals
and sense of duty as a journalist."

"Well, he's just an alcoholic geezer now. He probably has less sense of
duty left than the dirt under his nails. But even he's a hundred times
better than you people. He let the alcohol get to his head---but not his
ideologies. Each had his own strong ideal, huh? And this is where it
took everyone in the end?"

"Nezumi---I want you to believe this much. We tried to found an ideal city
here, a Paradise free of war and poverty\el where we could have gone
wrong, I don't know\el "

Nezumi laughed scornfully. "People can't become God. Humans can't create
Paradise. You guys thought you could be God, an almighty Creator. You
thought you were all-powerful. That moment is when you fell. You began
to corrupt. The cogwheels started turning backwards. You stopped paying
heed to people's feelings, and their suffering and brutality were no
longer in your line of sight. All you had was your greed to satisfy your
ideologies---no, your own selfish desires. In order to achieve that, you
thought you would be forgiven for doing anything. You didn't even need
to beg for forgiveness---begging was below you. What \emph{Paradise}? All you did
was create an arrogant and ruthless monster surrounded by alloy walls,
and turn everywhere else around it into Hell."

There was no heat in Nezumi's words. They rang out coldly, and at a
measured pace. But Shion could perceive the stormy emotions whipping
about inside Nezumi. He could hear the inferno raging.

"By the time I had realized it---" the elder said, "the change in No.~6
had already begun. The walls were built, which isolated it from its
surroundings. It leeched the wealth of everything around it, and tried
to sustain itself solely within its walls. An absolute authority was
born, and organizations to support that absolute authority sprang up and
established themselves."

"Were you too engrossed in your experiments to notice anything? That
doesn't make you any less guilty."

"Of course. My crime is grave. I was, after all\el on the side which
massacred your family and friends."

"\emph{What?}" Shion sat up without thinking. He looked back and forth at the
faces of Nezumi and the elder.

"So it's true," Nezumi murmured. His tone was almost the opposite of
before, somewhat frail and uncertain. "So it's true. That's how it is,
then. I knew that you'd been exiled from No.~6 and become part of the
underground people. I had a sneaking suspicion that you played a central
role in the birth of No.~6. But to think you were part of that
massacre\el I didn't want to think that could be true."

"Massacre? Nezumi, what's this about?"

"The history of No.~6. The Mao Massacre. Over a hundred people were
murdered."

"Mao Massacre\el "

"Bet you've never even heard of it."

"No, I haven't\el this is my first time."

"Nothing to be embarrassed about. No one knows about it, except for the
perpetrators and the victims. It's probably the incident in which No.~6
revealed its hideous rearing head for the first time. That's why it was
covered up. There are no records. But it's in my memory, and it'll never
fade. It's burned an image that'll never disappear."

"When did it happen?"

"Twelve years ago."

"Twelve years! So I was already born."

"Long born. You'd already been certified as an elite, and you would have
been living in your mansion in Chronos by that time. What an active and
adorable little boy you must have been."

Shion found himself grabbing Nezumi's arm.

"Tell me. What happened? Who got killed? Is it the Hunt? Is it something
that happened in the West Block?"

"No."

"Then, where?"

"In the forest."

"Forest? You mean the woods that spread to the north?"

Nezumi brushed Shion's fingers away. At the same time, he turned his
body and dug his own fingers into Shion's arm.

"Listen." Nezumi's breath was on his earlobe. It was cold. "I'll tell
you." His fingers drew away from Shion's arm and pressed against his
throat, slowly tracing the red mark that snaked around it.

"You have a red scar, a gift from the parasite wasp, right?"

"Not a gift I was happy to get."

"I have one too. A gift from No.~6, if you will."

"Huh?"

Nezumi cast off his shirt. He half-turned to show his back. Shion felt
his throat close up. His breath caught.

"Nezumi, this---"

There was a raised scar on the smooth skin between Nezumi's shoulders
and hips. It was about the size of an adult palm. That spot was coloured
pale pink, and was taut like a burn scar. It looked even more
out-of-place because of the smoothness of the skin around it. It looked
like a gigantic spider was splayed over his back.

"Keloids, huh\el "

"Yeah. Graciously given to me twelve years ago."

Shion stretched out his hand to touch the spot which looked like it
could be the spider's head. He slid his fingertip along the scar as if
to trace its outline. Nezumi did not resist. He stood like a statue as
if to give in to the movement of Shion's fingertips.

"I never\el noticed." Shion let out a sigh almost without thinking. Not
once four years ago, when he had treated the graze wound on Nezumi's
shoulder, nor in these past few months they spent together, did he
notice. Had Nezumi skilfully hidden it from him?

"Of course." Nezumi crouched suddenly, and retrieved his shirt. "What
reason do I have to show you? I'd have to get naked. You wouldn't wanna
be stark naked in front of me either, would you? Even though I've had
the privilege of seeing it once already."

"Well\el but\el " He wished Nezumi would have revealed it. He wished
Nezumi had revealed this scar earlier. He wanted Nezumi to speak about
the past which surrounded it. Shion didn't have the right to accuse him
of why he had hidden it up until now, and why he had said nothing. But
that was why he wanted Nezumi to open up and tell him. If only he had
earlier\el 

Shion knew he would have done so. He would expose his body, his mind,
his scars, and where his heart lay. He had done so before. \emph{Nezumi
doesn't trust me completely. He hasn't acknowledged me as someone who is
worth exposing everything to. What can I do to bridge this barrier
between us, this chasm?}

He gritted his teeth.

\emph{That's enough. This isn't the time to be wallowing in my emotions. This
isn't such a forgiving situation, I know that much.}

\emph{Keloids. Abnormal raising of the scar. Due to a burn?}

"We were burned," Nezumi said, as if he had seen right through Shion's
heart. His voice was brittle. It became a force of impact that slammed
into Shion.

"Burned?\el What do you mean, burned?"

"That's what happened. One day, some soldiers came in with firearms, and
cleared us out by burning us down."

Raging flames swirled before his eyes.

\emph{\textbf{They cleared us out by burning us down.}}

Nezumi stood in front of Shion, and began to speak. His tone was regular
and emotionless.

"My people, Shion---we were once called the Forest People. Even before
No.~6\el no, even before the Town of the Rose, which would become the
beginnings of No.~6, we lived in the forest, and it was our home. We
were in harmony---true harmony with the wind, the earth, the water and the
sky, and with animals and plants. For all of that time."

The elder raised his hand shakily.

"Yes, Shion. The Forest People used to inhabit this land. That is why so
much nature has managed to remain miraculously intact."

"What kind of people are the Forest People?" Shion's heart raced; he was
about to step further into Nezumi's truth.

"They are born in the forest, and they lived there," the elder said.
"They made the forest thrive, treated it with respect, and protected it.
They were able to converse with the wind, water, trees, and grasses, and
align their hearts with them. They lived in a totally opposite manner
from how we do. They did not wish for growth nor development; they only
lived quietly within the laws of nature. This land has always been
protected by these people\el that is how it has been."

The elder let out a long sigh, and lowered his head. As the sigh left
him, his body seemed to deflate and shrink in size.

"It was a lush forest\el there were all kinds of animals and plants,
large and small. Seasons passed, flowers bloomed, fruits ripened, leaves
thickened, and life pulsated as it was nurtured and passed on."

"And No.~6 destroyed it all." Nezumi's voice was now reduced to a
whisper. His beautiful murmur rocked Shion's eardrums and heart.

"Shion, you probably had no idea it was happening, but No.~6 was still
burgeoning when you were born. They tried to swallow every single piece
of land which was suitable for their habitation and make it their own.
They concluded that we were in the way. We were people of the forest---we
obeyed the laws of the forest, but refused to worship anything else. We
refused to become part of No.~6. Back then, the wall was finishing up at
a considerable speed. Only those on the inside of the silver wall were
to be treated like humans. As for those outside, they could invade it or
destroy it however they liked---that was becoming No.~6's stance. And in
accordance with it, they invaded the entire forest, and stole it from
us. You understand what I'm saying?"

"I do."

"Can you imagine what I'm going to say next?"

Shion nodded. He could feel his neck creak. "No.~6's army\el invaded
your village. They thought, if you weren't going to comply\el they would
destroy you all\el "

"Yeah. Nice, you've learned to see through things better."

Shion clutched at his chest. His heart wasn't just racing---it was
palpitating, and he couldn't breathe properly.

"And then, that time\el what were you doing\el ?"

"I was sleeping. It was nighttime. I was still young. I was too young\el 
to remember a lot of things. I don't remember my mother's face, nor my
father's voice. I just remember it was hot. And the viciousness of the
flames which devoured everything\el I remember. I remember it, Shion."

"They burned down\el the whole village."

"They burned it down and killed everyone off. Indiscriminately. They
burned down houses with people still in them, and shot those who tried
to flee. Can't you just see it? You've already experienced the Hunt. No.
6 has repeated that Hell many, many times."

He could see it. He could see vividly the scene of the massacre. Even
though he himself had been captured in the Hunt, thrown down into
darkness, come this far, always by Nezumi's side; even though he had
been amongst the abused, in the scene he watched now, Shion was on the
side that was perpetrating the murder. He was pointing the flamethrower
and the fire which spurted out of it at the elderly, children, men and
women.

Sweat soaked his skin. He felt ill.

"But you were saved. You suffered burns\el but you survived."

"An old woman---I don't know whether she was my real grandmother. But an
old woman took me in her arms, and made a desperate escape. Thanks to
her, I was able to survive."

"Your family, were they---"

"None of them lived."

He swallowed the spit in his mouth. It was bitter. Very bitter.

"So No.~6 invaded your forest, destroyed it, and went on extending its
territory."

"That's right. It was around where the airport is now. The woods that
dot the place are the remnants of the forest. They must've wanted land
to make a runway on. A few years after the massacre, No.~6's walls
stretched out into the form they are today."

A bead of sweat rolled down his cheek. There was still a bitter taste in
his mouth.

"There's more," Nezumi said. "It's about how I got imprisoned into this
underground part of the Correctional Facility."

"Right---let's hear it."

\emph{Heh.} Nezumi laughed without warning. It was a carefree, yet somehow
ironic smile, unique to Nezumi only.

"You don't look like you want to. You've gone all pale. Like a sheet."

"I'll listen. I want to. Nezumi, I want to hear your story until the
end. I think I have the obligation\el to hear it."

Nezumi's fingers pinched Shion's chin.

"Is that how you really feel?"

"I promised. I said I would never lie to you again. I'll keep the
promise. And---if it's possible\el "

"If what's possible?"

"I don't want to lie to myself, either."

"A fine challenge."

The fingers retreated. A smile graced the face which had fallen sombrely
a moment before. There was no more irony or coldness in his face. Shion
even thought it looked gentle. When he saw that smile, he felt the
strength suddenly leave him. He felt dizzy. He felt like the ground had
disappeared under his feet, like he was floating in the air. His whole
body grew cold.

He was fainting.

"Shion?"

"It's nothing." He spread his feet apart, and supported his crumbling
posture.

\emph{I'm not gonna fall here. Everything's starting. It's only starting. I
have to listen\el I have to hear him say the truth.} He closed his eyes.
Just as he expected, the raging inferno was still swirling behind his
eyelids. People rolled about on the ground, burning. He could even hear
the bloodcurdling screams and smell the stench of burning flesh.

\emph{Am I on the side of the murderers?}

\emph{Twelve years ago, I was in Chronos. In my comfortable room, I enjoyed
sumptuous meals, and slept in a clean bed. Even while Nezumi was being
burned and nearly killed, I was given everything, and was living a life
I didn't deserve.}

\emph{Who could say that this wasn't a sin? Even if I was a young child, I was
still living in the same world as those who were doing the massacring.
It's an immovable truth: I was on the side of No.~6, not Nezumi. Could
anyone say this wasn't a sin? Could I---and I'm not anyone---I'm no one.}

The darkness wavered. Nezumi's figure blurred. All sounds faded away.
Then, a pair of arms slid underneath his armpits.

"That's enough. Shion, this is as far as I'm gonna go." Nezumi tightened
his grip. The sensation brought Shion back to his senses.

"You're---well, I am too---we're both exhausted out of our wits. We've
managed to drag ourselves through this gruelling experience, not to
mention we were on our toes for the whole time. We're probably both as
tired as we can possibly get. It's alright. Rest. Take some time to wind
down. If you don't, your heart's gonna give."

"\el I can't\el hear any songs."

"Huh?"

"Even if I start to lose consciousness, I can't hear\el songs, like you
do\el "

"Shion."

"I can't\el do it."

"Shion, look at me."

He shifted his gaze, and looked up at the pair of grey eyes, which were
calm and peaceful.

"I told you before. I'm me, and you're you. We can't do the same things.
We can't be the same. But we can support each other like this. Both of
us. Back there, you supported me, and gave me water. You were probably
thirsty as hell yourself, but you saved every little drop for me.
Shion\el you were born inside the walls, and I've been living outside of
them. That's the reality of it, and we can't help it. No one can change
the fact. But when the other is about to fall, we stretch our hand out
without even thinking, and try to support him. We can't help it. We give
him water. We try to protect him. That's another truth about us."

"Nezumi\el "

"I didn't mean to make you feel guilty. I didn't mean to accuse you of
any crime. I---can't even imagine wanting to hurt you. I'm sorry. I should
have thought a little more about your situation."

Something hot pushed at the back of Shion's eyes. Even before he could
vocalize it, tears streamed down his face.

\emph{How embarrassing. How pathetic, to be crying like this.}

He clamped his teeth over his lip, and tried to hold the tears that
welled up. But sobs managed to push their way through between his
clenched teeth.

\emph{Don't be kind to me. Don't apologize. I wouldn't have minded if you
blamed me, hurt me, accused me of any crime. If you didn't, I would keep
taking advantage of it. I would lean on this reality you speak of, and I
would keep excusing myself to no end. I'm still that weak.}

He couldn't control his emotions. His nerves, which had been on-edge
until now, had a hard time bounding back once they gave way. They
ignored Shion's will as they let the tears fall freely.

"Don't cry." Nezumi's hand patted his back. "Don't you cry. You were
just a tiny kid. You're not to blame for anything. The guys who should
pay for their crime are the adults. The adults who gave birth to that
creature and let it grow this large should be the ones to pay the
penalty. Isn't that right, Rou?"

"Yes. The crime rests entirely with us."

"Then what's your personal crime? What have you committed?"

"I created the seed of the massacre."

It was like the air had frozen over. Nezumi's arms trembled softly
beneath Shion's armpits.

"That massacre was not carried out to acquire land for a runway. It was
to acquire Elyurias."

Elyurias. The great sovereign.

\mybreak

"We never had a sovereign, at least I don't remember there being one.
I've never even heard of the name before," Nezumi said.

"Naturally. I was the one who named her. Your people did not give her a
name, but you did revere her. You revered her as you did the other
trees, the sun, and the moon, and you feared her. Yes---you feared her.
She had power. She had a power that neither we nor you had---probably a
power no human could possess. That is why No.~6 desired her. They
desired her power. Nezumi---your people knew everything about her power,
and you feared and revered her. You never thought of using her as a
device for your own prosperity. That is the difference between your
people and us. However, I was not directly involved in that massacre.
Nevertheless, I know that is no excuse."

"Let's just hear the truth. What role did you play?"

"I---I met Elyurias in the forest, discovered her power, and reported it.
You could say I was entranced by her. I was obsessed with her, and I
submitted a massive research report about her. The upper echelons of No.
6 expressed a strong interest, and contributed generous research grants
to me. They called me a rare gem of a researcher. I had grown giddy with
fame and fortune. Oh---"

The elder's words trailed off. Just for a moment, his gaze wandered in
the air.

"What?"

"No\el I remember Karan saying to me around that time. She said she was
afraid of me. She said there was a frightening, dangerous sort of look
on my face. She said she was afraid of me, and she didn't know why\el it
was long afterwards when I finally realized why. Yes\el I had not
realized\el the change in myself, nor in No.~6\el I even laughed at
Karan's fear. I had not realized that I had thrown my ideals away, and
that I had wandered off the path I intended to walk. But---by that time,
the dominant organizations of No.~6 had already been formed, and they
were fast becoming concrete. A military was being assembled discreetly,
and a skillful system of controlling and dominating people was nearing
completion. I never knew---I had not realized in the slightest. I had
still believed\el I had still\el "

"\el that No.~6 was a utopian city?"

"Yes. A pacifist city with hopes of eternal peace at its foundation,
interacting with the world, armed with no weapons whatsoever. A city
that insured a humane life for each and every person; one that respected
each and every person as a human being. No.~6 and the world, science and
nature, ideal and reality would come together in harmony, with no
contradictions. I believed in it. I believed it, immersed myself in my
research, and\el brought tragedy. I never imagined that No.~6 would have
an army. I never imagined that they would mobilize their military and
invade the surrounding realms. When I learned of the truth of the
massacre, it was already a long, long time after the incident had
occurred\el but I panicked. It hit me with an impact enough to make my
body go rigid. It was then that I finally realized the meaning behind
Karan's words. I realized that I had been drunk with joy over the
superficial successes of my work, and had become one who couldn't feel,
one who was numb to the happenings around him, one who was more foolish
and dangerous than anyone could be. I realized this, and I appealed to
the uppers to clarify the truth of the massacre. It was my own way of
protesting."

Nezumi let his shoulders shake, as if he couldn't find anything more
funny about it.

"You thought they would listen to you?"

"I did."

"Naive."

"I had thought they were on my side. I had thought of them as my own
friends, fellow partners who shared the hope and ideology of creating a
utopian city---not politicans, not researchers."

"So you made a fiery objection. And the result of that was your arrest
and imprisonment as a rebel."

"That is about right\el they did not go so far as to kill me, however."

"Even they still had some pity left."

"No\el not that."

The elder slid his hand across his lap. "They probably decided that
there was no need to kill me after what my body had undergone. Shion."

"Yes."

"Look at this." The elder stuck his arm out, and rolled up the garment
covering it.

"\el "

Nezumi shifted in his spot beside Shion. Shion also held his breath, and
leaned forward. A red banded scar wound up the elder's arm from his
elbow to his shoulder. It meandered like Shion's, but the colour was a
little darker than his.

"This is\el from the parasite wasp\el "

"Now I can say so with certainty. Somewhere in my body, there are
probably remains of a wasp that could not hatch. At the time, I was
under house arrest by the authorities. I had collapsed suddenly in my
room and gone unconscious. When I recovered fully, these marks were on
my arm\el and both my legs had lost all functionality."

"Your legs\el "

"You lost the colour of your hair, I lost my legs. As the cost of
survival, I suppose. However, at the time, no one could grasp the exact
cause of this, including myself\el If the same thing happened now, I
would have made a good experimental specimen, perhaps, but at the time,
there was no such room for rational thought in the upper echelons. They
were immersed in the work of building governing organizations. The
Correctional Facility was still under construction. I managed to hang on
by a thread, losing my legs in exchange, and was housed in the
underground caves. And so they cast me off. Shion, I was the wasp's
first host, and one who survived."

"Then, Rou---" Nezumi lifted his chin, and directed his gaze straight up
at the elder. It was piercing, like an arrow.

\emph{Amazing.}

Nezumi was still in full control of himself. He was able regulate his
emotions and reason. Shion wiped his tears with the back of his hand,
and clenched it into a fist. Nezumi had said that they couldn't be the
same. Perhaps it was so. But he could still try to bring himself closer.

\emph{I want to be resilient like he is. I want to preserve myself. I want to
stay as who I am.}

\emph{I won't hope, or pray; I'm going to make a vow to myself. One day, I'll
become strong. I'll have the kind of strength that will keep me from
endlessly making excuses to myself.}

Nezumi pointed a finger to the heavens.

"Then, Rou, aren't the higher-ups gonna summon you sometime soon? Maybe
they've finally found out about the incidents occurring in the city, and
have got no idea what to do about it. It's about time their arrogant
gaze started seeing reality for what it is. Don't you think they'd come
to you for help?"

"That will not happen. All of my research was confiscated. They have
probably analyzed all they could. My power is now next to useless. I
have grown old. I will live the remainder of my life underground, and
die---that is my wish. I have neither the power nor will to change
reality. But I do know this much: what is about to happen in No.~6 is
many times more fearsome and destructive than you presume. Many people
will die. Neither I nor No.~6 can stop it. But you can."

"Stop it? The death and destruction? What do I have to stop it for? I
couldn't wish for a more splendid outcome."

"Nezumi, the citizens will be the ones dying. Children and adults will
die indiscriminately. Are you saying you will merely watch it happen?"

"What's wrong with that?"

"You said that Shion was not guilty of any crime. That is true. In just
the same way, with what crime could you accuse the children inside the
walls? If you will fold your arms and watch, knowing that children will
die\el if you will let it happen and do nothing\el you, and any who do
the same---"

The elder straightened his back, and returned Nezumi's gaze steadily.

"---are murderers."

Nezumi made a small strangled noise in his throat.

"It is not something for me to say. However, I must say it. Nezumi, you
are the survivor of a massacre. That is why you cannot stand on the side
of the murderers. You must not let yourself become the same as those
whom you hate."

"Gh---"

Nezumi fell silent. Shion stepped forward.

"What should we do? What \emph{can} we do?"

His mother was inside the city. There was also Lili, the girl from his
neighbourhood. There was her family. There was the student who came to
buy a roll every morning; there was the worker he exchanged greetings
with on the way to his job.

A fleeting resemblance of Kalan---the girl he had met in the West
Block---overlapped with Lili's face. He didn't know why.

\emph{I can't. I can't kill them.}

"I do not know," the elder said. "I cannot foresee what we can do to
prevent this tragedy. Nothing presents itself to me. You must act as
your hearts tell you to. You---your hearts---will be able to lead the people
away from destruction to salvation. To me that is how it seems, and I
cannot see it any other way. Shion."

"Yes."

"Take this." The elder slid his hand along his armrest. A small drawer
appeared. He plucked something small from it, and offered it to Shion,
giving another one of his numerous sighs. He looked like he had rapidly
aged. The boyish glint in his eye had faded.

"This is\el a chip."

"Yes. Almost the entirety of my research is in it. Parasite wasps,
Elyurias, the Forest People\el everything. After you have saved your
friend, please try to decode it."

"Me?"

"I entrust it to you. Now\el I am a little tired. I have not spoken this
much in a long time. I am tired. I wish to rest."

\emph{I entrust it to you. You must find the answer. Please find an answer---one
where no blood will be shed.} Shion heard the elder's unspoken words.

There were so many more mysteries: how this underground realm came to
be; how Nezumi found his way here; his reason for leaving; all the
things that happened which led up to their meeting---he itched to know,
but for now, he would suppress those words of questioning inside his
heart.

This was the time to act, not learn.

\emph{Cheep-cheep-cheep! Cheep-cheep-cheep!}

The mice were suddenly buzzing with noise. A rat at Shion's feet raised
its voice in apprehension.

\emph{Screech, screech!}

Shion had heard this voice before. It was---

"Tsukiyo. Nezumi, Tsukiyo's here."

"I know. Geez, how can you differentiate them like that?" Nezumi put his
fingers to his lips, and whistled shrilly.

\emph{Screech, screech!} A small black mouse came half-tumbling down the rocky
wall.

\emph{Skrit, skrit.} A sewer rat leapt up, and pounced on Tsukiyo.

"Stop!"

The sewer rat froze at Shion's command.

"He's not prey. He's one of us. Let him go." The sewer rat lifted its
paws which had been pinning Tsukiyo down. The black mouse leapt to its
feet as if on a spring, and scurried up Nezumi's body.

"Good, you made it. A message from Inukashi?"

Tsukiyo nodded. There were wounds all over its tiny body, and they were
beginning to bleed. Nezumi lent an ear to Tsukiyo's squeaking, and
swallowed.

"Looks like everything is ready to go above-ground. We have to act
quickly. Rou, I would have wanted to hear a little more of your story,
but it looks like we don't have time for that. We're gonna go."

"Then go you shall. Do you wish for anything?"

"Water and food. I'm so hungry, I feel like I'm gonna pass out."

"It will be prepared immediately. Sasori, give them whatever they wish."

"Before that---" Sasori drew up beside Nezumi. "Nezumi, I want to ask you
something."

"What?"

"Surely you are not thinking of blowing up the door with a micro-bomb?
If you do that, this place will collapse as well."

Nezumi furrowed his brow and looked at him in exaggerated bewilderment.
"Sasori, we've come through the back gates of the Correctional Facility
here. An old bomb detector is still a bomb detector, and that gate's got
them. We could get knives or small firearms past them, but not
micro-bombs. If we could, we would've sneaked in with at least a hundred
on our backs."

"Fine. As long as you do not bring us into this mess."

"You doubting me?"

"Who knows what you will do. You are dangerous."

"Hey, I thought Shion was the demon here?"

"Demons do not cry." Sasori glanced at Shion. "Demons do not cry\el like
that."

Shion felt his face burnt up at the man's words. He felt painfully
embarrassed.

"I found it strange," the man said. "To be able to cry so
unreservedly\el very strange."

"Well, no," Shion stammered, "I---I was just really tired, and\el my
nerves---stretched thin---that was it, really, it's not like I cry like that
all the time---"

The air shifted.

Sasori had laughed. It was the first smile Shion had seen on him.

"You are interesting. You may be, perhaps\el far more decent than
Nezumi."

A sewer rat sat on Shion's shoulder and nudged him with its nose.

"He says so too," the man said, indicating the rat. "He says you are
more decent."

"The hell is that supposed to mean?" Nezumi clicked his tongue. Then he
jerked his chin slightly.

"Let's go, Shion."

"Yeah."

"Rou. This is good-bye. It's probably the last I'll see of you. This
time, I won't come back."

"That is for the best. You are one who must live above-ground. You are
someone who must live in the light and wind. I pray that we will never
meet again. Ah, but you are not in need of prayers, perhaps?"

"I'm not."

"Oh---Rou, I'm going too," Shion said. "I wish I could have heard more of
your story."

"I trust that the rest will come through your own hands. Thanks to you,
I have been able to relive memories of Karan. But you do not need to
tell her about me. You should also forget about me yourself. This is
farewell, Shion."

"Good-bye. Thank you for everything."

They started walking.

When Shion turned around, the candle had already been extinguished.
Darkness shrouded all that was behind him.

\mybreak

The emergency lamp flashed and the buzzer rang.

The door to the Correctional Facility rolled up slowly in front of
Getsuyaku. He set a foot inside. White walls and a white hallway spread
before him, the picture of cleanliness itself.

"\emph{What} in the world is this, eh?" Getsuyaku was met with a torrent of
abuse as soon as he entered the monitoring room. "What's wrong with
these cleaning robots? They're spouting odours and strewing trash
everywhere instead of cleaning it up. Have you even maintained them
properly?" The man was practically a giant, almost one-and-a-half sizes
bigger than Getsuyaku in height and berth.

"I'm sorry. They've been acting up. I didn't even imagine something like
this would happen."

"Enough excuses. Clean it up, and quickly."

"Yes, sir."

"Oh, it \emph{stinks}," said a woman with long hair, grimacing as she pinched
her nose. "I can't work in this stench." She left the room, her voice
congested. She trampled Getsuyaku's toe on her way out, though whether
she had meant to do it or not, he didn't know. She gave him no apology,
nor did she even spare him a glance.

The room was divided by transparent walls into several sections. The
sections were arranged in accordance to priority level, and the higher
priority rooms were placed further in. Getsuyaku was in a space near the
door, commonly called the Mannequin. This section dealt mainly with
monitoring ventilation. It was a department relatively low on the
priority scale, and that was probably another reason why he had been let
in without much trouble.

"I'm very sorry." He went around with a vacuum, sucking up the trash
scattered over the floor.

"You're utterly useless. I can find a dozen replacements for janitors
like you, you know. Next time you mess up, you're fired on the spot.
Ugh, it smells horrible. I can't stand it. Hm? What are you looking at?"

"Nothing, sir." Getsuyaku lowered his eyes.

"Do you have something to say? A complaint? A Lost Town resident acting
high and mighty now, eh?"

Getsuyaku felt a firm kick in the shins. He staggered, and struck his
hip hard on a corner of a desk.

"Well? Don't just stand there. Hurry up and work!"

A wind was dancing inside his head. No, it was whirling fiercely. It was
whipping up a tremendous noise.

\emph{Damnit.} He was mumbling. \emph{Damnit, damnit, damnit, damnit.}

\emph{What makes him think he can be so arrogant? What have I done to be
insulted by him? I'm just doing my job. I've done my job all this
time---honest and hard work. ---Well, I might've done a little smuggling,
but still, I haven't caused anyone trouble. You guys would've been
buried in trash if it weren't for me. Don't like the smell? Dirty, you
say? It's all stuff you guys have produced. Don't give me this shit.
Treating me like a dog. It doesn't matter where I live; I'm still a
human. I'm no mongrel.}

His injured pride swelled into anger, and wiped clean from Getsuyaku's
breast any hint of uncertainty that had lodged itself there.

He saw a fleeting image of Inukashi's tan face.

\emph{They go around acting cocky like that, and they've got no idea how hard
your work is, and how much it's worth. They're looking down on you. So?
How about you give those cocky guys a piece of your mind? Not a bad
idea, is it?}

\emph{You're absolutely right, Inukashi. It's not bad at all.}

He threw a glance at the digital display on the wall. Within No.~6---and
this building was no exception---time passed by with not so much as a
0.1-second delay.

A capsule lay on the floor at his feet. It had not disintegrated.

\emph{Damn it all to hell.}

He stepped on it softly with his right foot. There was another one. He
did the same---

"What in the world---" The man stood up. His face was contorted. "What is
this horrid smell?"

"I have no idea\el " Getsuyaku replied vaguely, "it smells like rotting
meat\el I think it must've been mixed in with the garbage\el " He was
right. The smell was horrid. It wasn't an overpowering odour, but it was
enough to grate on his nerves. Even Getsuyaku, who was used to smelling
decay, felt ill.

"I can't stand it. Ugh---out of the way!" The man covered his mouth and
exited the room. He trampled Getsuyaku's foot on the way out, just like
the woman had.

"That hurts, what was that for?"

"Shut up. Move it!"

The man shoved his hand against Getsuyaku's chest. He staggered, and
bumped into the control panel.

\emph{Stop.} It was the designated time.

Getsuyaku pretended to hold his hip and groan in pain, and pressed the
green button on the far right. While he was at it, he pressed the
changer switch. Now, this stench would travel through the air ducts and
waft into the Facility. Getsuyaku didn't know what the green button was
supposed to do. He had only followed Inukashi's directions. He raised
himself unsteadily, and picked up the vacuum. He began to clean.

He was breaking out into a cold sweat.

How had he looked to the surveillance camera positioned in the middle of
the ceiling? Did his move seem unnatural?

\emph{I've done it.}

There was a melting capsule underneath the desk. Fumes rose up thickly.

Getsuyaku strengthened the grip in his trembling fingertips, and kept
hold of his vacuum hose.

\mybreak

\emph{Shion.\\
	I feel it. You're close by.}

\myspace

\emph{Shion.\\
	I can feel you.}

\myspace

\emph{Don't come. Please, don't come.\\
	I don't want to be seen by you.}

\myspace

\emph{Don't come, Shion.\\
	I really\\
	really\\
	want to see you.}

\mybreak

Another casualty. Over thirty in total, now. Social class, wealth,
history of illness, residence, sex, age, build, lifestyle, all
unrelated. Who was next---?

Fear, uncertainty, and agitation mounted inside No.~6.

"What are the authorities doing?"

"Investigate and disclose the causes."

"Why aren't you taking any effective measures?"

"Dispatch the medics, hurry."

"Mayor, your emergency press conference."

\emph{What has happened to our No.~6? Our city, our No.~6, what---}

\mybreak

Nezumi's fingers tapped the door connected to the Correctional Facility.
Safu was beyond this door.

"It's almost time. We'll be launching the flashy fireworks soon, Shion."

"Yeah."

"You nervous?"

"No. I've been thinking."

"What could you \emph{possibly} think of at a time like this?" Nezumi said
incredulously.

"I was thinking about Safu. I want to see her."

"No need to jump the gun."

"And---I was wondering, just for a tiny instant."

"What?"

"Whether it was possible to know everything about you."

"Idle thoughts, huh."

"You think so?"

Nezumi's fingers yanked at Shion's earlobe. A sharp pain shot through
it.

"Shion, listen. From here on out is your stage. Once the door opens,
we'll be inside the Correctional Facility. Get that brain working
full-throttle. I'm gonna be acting on your orders. You're my lifeline.
Don't you dare break."

"Of course I won't. You don't even need to say so."

Nezumi smiled wryly, and stretched his hand out palm-up. Shion placed
his own hand on top.

\emph{Click.}

There was a sound.

\emph{Click click click.}

The automatic locks were being released.

"Perfect. I need to give Inukashi a reward later."

\emph{Click click click. Creak.}

"Let's go, Shion."

"Right."

The door opened.

A white light stabbed at his eyes.

It was blinding.

The light was overpowering.

The place overflowed with light, and glittered.

It was unmistakable---it was the world of No.~6.