% !TeX spellcheck = en_US

\chapter{Leave every hope}

\myepigraph{Through me is the way into the woeful city;\\
	through me is the way into eternal woe;\\
	through me is the way among the lost people.\\
	Justice moved my lofty maker:\\
	the divine Power, the supreme Wisdom\\
	and the primal Love made me.\\
	Before me were no things created, unless eternal, and I eternal
	last.\\
	Leave every hope, ye who enter!}{Dante, \emph{The Divine Comedy Vol 1: The Inferno}, Canto III}

\lettrine{I}{t began} suddenly. No one would have been able to predict it.

It began suddenly, and amidst the crowd that had gathered in the square.
It began as when gas erupts after being compressed for a long time
underground.

\standout{The Holy Celebration Day, 2017.\\
	12:15 pm\\
	Front Square, City Hall (also known as The Moondrop)}

The wind blew icily and nipped at the skin, but the sun was bright. The
sky was clear, and was dyed a brilliant blue, appropriate for the
festivities. The hearts of the people were buoyant. They waved flags,
and all praised the Holy City.

"Our mighty No. 6."

The square in front of the city hall where the ceremonies were to be
held was bursting with people.

"It's hot," complained a woman in the stuffy crowd. She was young and
slender. "I feel like I'm going to suffocate, there's so many people."

"So true," her friend agreed beside her. She was short, with black hair.
She sighed as she dabbed the sweat off her nose. "Isn't it horrible, how
there's barely even space to walk? How disgusting to sweat in the
winter. I feel all sticky."

"Really, I don't believe it. We dressed up for nothing."

"I \emph{know}."

Both had barely any experience of sweating. They had always lived in
places where the temperature and humidity were adjusted just so for
maximum comfort. They couldn't stand the sweat that streamed under their
arms and down their backs. They found the heat of the jostling crowd
exceedingly unpleasant.

The black-haired woman pouted her painted lips.

"My supervisor said I absolutely had to participate in the ceremonies.
If I didn't, I would get my salary cut."

"Me too. Boss' orders. He said it's \emph{mandatory} that I show up. If it
wasn't, I definitely wouldn't be here."

"They'd know from your ID card if you didn't show up, wouldn't they? The
gates scan your citizenship number when you pass through them... and I
heard they notify your workplace afterwards."

The slender woman nodded gravely, and furrowed her brow. A bead of sweat
rolled down her cheek.

\emph{Oh, how unpleasant. I wish I could take a shower and freshen up.}

The black-haired woman continued loosing her stream of complaints.

"My younger sister is still a student, but she told me all of them have
to meet at school, and they get bussed over here."

"Really? They didn't have anything like that in our day, did they?"

"No. I heard it's just started this year. They want to confirm your
loyalty level to the city. My sister was complaining that if you don't
participate, you get negative points for your Activities column. You get
placed in Rank D. That means you wouldn't be able to get further
schooling, or land a job. I thought it was a bit harsh, don't you think
so?"

"It \emph{is}. They're practically forcing us. And speaking of which---it's a bit
much these days, isn't it? Everywhere you go lately, it's loyalty-level
this, loyalty-level that. I kind of find it weird---"

The slender woman was interrupted suddenly as somebody grabbed her by
the arm. White shirt, grey pants. He was a nondescript middle-aged man
with a strong build.

"Um, what---?" the woman began.

"What were you talking about just now?"

"Excuse me?"

"What were you two talking about just now?"

The two women looked at each other. Their hearts quickened. "W-We were
only talking about... you know, how hot it was... stuff like that..."

"Is that so? It rather sounded to me like you were expressing some
dissent, discontent towards the city. Am I wrong?" The man's narrow eyes
glinted. His words were courteous, but the light in his eyes was sharp
and fierce. It made the women cower. Fear pierced through their bodies.

The Security Bureau.

"N-No!" they protested. "Discontent---no---never, we would never say that.
We would never think of that. Not us, we would never..." The
black-haired woman clasped her trembling fingers to her breast. Tears
welled up in her eyes. \emph{Help me. Mom, Dad. Help me.}

"No matter. Will you kindly let me escort you two? We will have plenty
of time to hear your story later."

"How can you... that's not.. no..." Unable to bear it any longer, the
black-haired woman began to cry. The slender woman was also shaking.

"Kindly let us escort you." Another man in similar clothing materialized
and grabbed the woman's arm. His fingers were shockingly cold.

\emph{No---that's not fair, we were only having a conversation. We were only
saying our thoughts out loud.}

She was so stunned by the incident, no tears came. She could not cry
like her friend. The slender woman only trembled.

"Come, then." The man's eyes flashed incisively.

\emph{I'm scared. I'm so scared. Help me, Mom, Dad.}

---Mmgh.

There was a muffled groan. It had trickled from the man's mouth. His
eyes were bulging, wide open, and his mouth was opening and closing like
a fish. No voice came out. Only his lips moved. His hands tore at his
neck. His face began to discolour into a dark shade.

"Wh-What's the matter?"

The man with the cold fingers reached out towards her.

\emph{Ahhhh!!!}

The woman screamed. She felt like her shriek would tear her throat
apart. The black-haired woman had started screaming at almost the same
time.

\emph{"Oh God!"}

The man stopped moving. He stiffened, his eyes and mouth still open.
They could see inside his mouth.

\emph{Plunk.}

Something fell to the cobblestone with a soft sound. Something small and
white...

Teeth.

All the man's teeth were falling out of his mouth, one after another.
His hair was also falling out. Clumps of it turned white and scattered
all around. The man's eyes rolled back into his head as he fell
face-forward onto the ground. His body convulsed. A black stain spread
from his neck. It swelled into a bump, and then---

An incomparably stronger wave of fear came crashing down onto her. She
felt like she would go insane. Perhaps she was insane already. Perhaps
she had gone mad, and that was why she was seeing something that wasn't
supposed to exist. She had no other choice but to scream. She had to
raise her voice, and release her terror somehow. If not, her body would
swell and burst. She would shatter.

The woman breathed in.

\emph{Ahhhh!}

\emph{Eeeeek!}

Before the woman could open her mouth, shrieks and bellows welled up
from the rest of the crowd. Here and there, they rose and burst. Voices
of men, shrill screams of women, yells of young people, the clamouring
of the elderly---everything writhed, mingled and twisted around.

"\emph{Nooo!!}" The black-haired woman was frantically flapping her hands and
feet. She looked like she was doing a disturbing dance.
"Someone---someone's there. Inside me. Help---help me---!" Her teeth fell out
as she opened her mouth to scream.

\emph{Plunk, plunk, plunk.}

A stain was spreading from the black-haired woman's neck.

"It's poison!" someone was saying. "Run! We've been poisoned."

She heard another voice. It was saying, "we're all gonna die."

\emph{It's poison. Run. We're all gonna die. It's poison. Run. We're all gonna
die.}

The woman stepped over the fallen man, and tried to break into a run.
But before she did, she saw something glitter suddenly before her eyes.
\emph{A bug?} Someone shoved at her back. A fat woman tumbled and fell close
by. A mass of bodies stampeded over her ruthlessly.

\emph{This is Hell. I have to get out of here---quickly---right away.}
Unconsciously pressing a hand to her own neck, the woman leapt over the
bodies strewn on the ground, and broke into a desperate sprint.

\standout{The Holy Celebration Day, 2017.\\
	7:02 am -- Lost Town}

Karan was baking pastries. Cravats, in fact. She twisted the dough,
which had powdered almonds in it, into the shape of a necktie. She fried
it, flavoured it with orange curacao, and sprinkled it with icing sugar
as a finishing touch.

"It looks delicious," Lili said as she swallowed hungrily.

"And it is. Let me set aside ones I won't put out for the shop, and
we'll eat them together with some tea. Or would you prefer some warm
milk with that, Lili?"

"I want cold milk. I like cold milk better."

"Alright, we'll do that. Some nice iced milk, but not too much, or else
it'll give you a tummy-ache. But remember Lili, before that---"

"I have to help with the store, right?" she finished. "I'm gonna do a
really good job. I love being able to help with your store, ma'am. It's
exciting."

"Today's the Holy Celebration, so it'll be very busy."

"I know. First I say 'hello and welcome' right, and then I put the rolls
and muffins in the bag."

"Mm-hmm. And make sure to tell them, 'please feel free to use the trays
on the table by the entrance. You can put your items on them.' And if
the customers are children, or can't use their hands or legs, ask them,
'may I get that for you?'"

"'Hello, and welcome! Please feel free to use the... the..."

"Trays on the table, by the entrance."

"Trays on the table by the entrance. You can put your items on them. May
I get that for you?"

"Brilliant, Lili! That's the spirit. And don't forget to smile."

Lili's nostrils flared appreciatively. "It's easy to smile when it
smells so good. My cheeks just melt, like this." As she cupped her own
cheeks, a shadow flitted across Lili's eyes. Her tone dropped slightly
too.

"Ma'am?"

"Yes, darling."

"Can I take some of these pastries back to Daddy?"

"Of course. I'll leave some for both your Mommy and Daddy---why, Lili,
what's wrong? Has something happened to Renka?"

Karan had heard that Lili's mother Renka was pregnant with her second
child. Perhaps something had happened. Residents of the elite
residential area of Chronos would be promised thorough and meticulous
aid and treatment from specialized medical staff, from conception to
birth. However, a Lost Town resident could only dream of receiving
medical care at the level of Chronos residents. The mortality rates of
invalids, the elderly, and children were manyfold compared to Chronos.

Karan was not discontented with her life in Lost Town. But numerous
times, she found herself forced to face the fact that they were at the
very bottom of the rigid hierarchy which the city had created.

She felt her spine freeze.

She felt a chill not from the realization that they were at the bottom,
but at the very reality that people were dominating over other people
and reigning over them in this way. She also felt a chill at herself,
for not realizing this sooner.

Oh, how careless she had been.

Lili shook her head. Her fine, flaxen hair swished.

"It's not my Mommy. It's about Daddy."

"Getsuyaku-san? Has something happened to him?"

"He had to go to work, even though it's the Holy Celebration Day."

The Holy Celebration was one of No. 6's most revered holidays. Education
institutions and government organizations were closed as a matter of
course, as well as most city shops and offices. The majority of citizens
gathered in the square in front of city hall to listen raptly to the
mayor's speech, and to celebrate the birth and proliferation of No. 6.
Participation had been moving more toward mandatory since last year. By
making citizens pass through gates into the square, the city could tell
instantly if they did or did not participate in the ceremonies. Any
citizen who did not have a valid reason for not participating that fit
the criteria laid out by the authorities were investigated in detail.
Rumour said they were more like interrogations.

Karan felt that this city was becoming more suffocating by the day. But
still, many citizens participated in the festivities not because they
were forced, but because they wanted to. They gathered of their own
will, and waved their gold-embroidered flags of white cloth. \emph{Of their
own will} -- was this really so?

"Ma'am, the pastry." Lili was blinking. Karan realized she had been
clenching a cravat in her fist.

"Oh, dear, I've let one go to waste. So," she hastily resumed,
"Getsuyaku-san couldn't take the day off?"

"Nope..."

The Holy Celebration was a large event, but there were still many people
who went to work as usual, or else had no other choice but to go to
work. Karan was one of them. She could not live if she didn't work.
Cakes and sweet buns sold exceedingly well on celebratory days. On these
days "the cash came rolling in", to be vulgar about it. Karan had
planned to use this reason not to participate in the ceremonies this
year. On her Application for Non-Participation, which had to be
submitted beforehand, she had to fill in her job description, monthly
profits, and the predicted earnings if she opened her shop during the
holiday. She was also required to submit it in person to the reception
counter of the city. Although it was extra hassle, and although it would
have been much easier to just close her shop and participate, Karan
chose not to.

\emph{I can't let myself be pushed along down the easier path.}

She had always let herself be pushed into making the easier choice. She
had gotten out of practice of swimming against the current. She had let
her heart go numb, and been swallowed all too easily in the flow. Hadn't
she learned the hard way what the result of that had been?

Her son had been snatched away.

Her son's best friend had been snatched away.

Her most important things had been snatched from her suddenly and
unfairly. She would not let herself be washed away anymore. She had to
dig her heels in, or else she would be ashamed to look Shion or Safu in
the eye again. She would not be able to throw her arms around them
unreservedly when they came home. That was the last thing she wanted to
lose.

"Lili, are you lonely because your Daddy's not here? But I guess we
can't help it if it's his job, huh."

"No," Lili protested. She shook her head again. "Mommy already said we
can't help it. But that's not it. I'm not lonely because of Daddy. I get
to help you with your shop, ma'am, and it's exciting. All my friends
were jealous when I told them I got to work at a bakery---so I'm not
lonely, I'm just---I'm... I'm worried."

"About your father?"

Lili nodded.

"Why? Has something happened that's making you worry, Lili?"

"Not really," she said hesitantly. "Daddy always gives me a kiss on the
cheek before going to work. He said it makes him feel all happy inside.
He said it's kind of like a good-luck charm."

"My, isn't that nice of him."

"Yeah. He's the best. But today, he forgot. He went to work without
kissing me. He left by himself, while Mommy and me were talking in the
kitchen... he didn't even say he was leaving. He just left."

"Maybe he was busy."

"I dunno. But he didn't eat much breakfast either. Just half a slice of
bread and coffee. He was sighing, too. Like this." Lili slumped her
shoulders, and let out a huff of air.

Karan felt an outpouring of love for her.

Lili was concerned about her father, in her own way. 'Maybe he's
troubled about something, maybe he's tired'---she noticed these little
changes in her stepfather, her mother's second spouse, with a sharp eye.
And she was concerned about him. Lili had the experience of losing her
father right before her eyes at a young age. Did this kindness of hers
come from this experience?

"Lili..." Karan felt love for this tiny little soul. She crouched down
at eye-level to Lili, and stroked her flaxen hair. "Keep smiling. Your
smile is my good-luck charm. It makes me sad when I see you with that
frown, Lili."

"Ma'am... Daddy didn't kiss me today, but that's okay, right? God will
protect Daddy, won't He?"

"Of course. I know: why don't you give your Daddy a kiss this time when
he comes home, Lili?"

"Sure, I'll do that."

"Alright, let's open the store, shall we? Can you line the cravats on
the tray and put them out on the rack?"

\emph{Cheep-cheep.} She heard squeaking.

"Mr. Mouse! You're still here?" Lili chirped happily. A brown mouse was
twitching its nose from underneath the table. It placed its front paws
together, and bobbed its head up and down. Karan realized quickly that
it was a farewell gesture.

"You're going back to your master, then?" \emph{And back to my son?} Karan
broke off a piece from the pastry she had crushed in her fist earlier,
and placed it in front of the mouse. The mouse picked it up in its front
paws, and began to nibble at it without hesitation.

"Ma'am, look, the pastry and Mr. Mouse are the same colour."

"Oh. Come to think of it, they are. You have the same colour of fur as a
cravat."

\emph{Cheep cheep cheep.} The mouse raised its face and fixed its gaze on
Karan. It had beady grape-coloured eyes.

"Cravat... is that your name? Cravat?"

\emph{Cheep-cheep.} The mouse squeaked back as if to say, 'yes it is'.

"Cravat. What a nice name. Goodbye, then, Cravat. Please tell your
master that I'm thankful. That his words give me so much support... I'm
very, very thankful. Please tell him that." \emph{And if you can, please tell
Shion too. That I'm waiting---that Mom will always be waiting, and she'll
never give up. So tell him to come home alive.}

\memo{\nezumi}{Reunion will come.\hspace{1cm}Nezumi}

The short letter she had received from Nezumi. How much courage those
words had given her.

\memo{\nezumi}{Reunion will come.\hspace{1cm}Nezumi}

What a firm and valorous message it was. It had supported her crumbling
heart all this time. \emph{Nezumi, would I have the chance to embrace you?
Would I be able to take you in my arms along with Shion? I could keep
waiting, couldn't I, and believe that I can someday?}

Cravat finished his last morsel, touched his front paws together, and
bobbed his head. Then he scurried off into a corner of the room, and
quickly disappeared out of Karan's sight.

"There he goes." Lili frowned. "Is he gone forever?"

"No, we'll see him again. Certainly some other day. Right, let's open
the shop. It'll get busy, and I'm counting on you, Lili."

"Yes, Ms. Shopkeeper! Leave it to me." Lili swept into a theatrical bow.
Karan laughed as she opened the door of her shop. She could see the sky.
Its clear blue made her eyes water. The wind was freezing, but it looked
like it would be a sunny day. \emph{It looks like the weather will be great---}

She felt a chill. Goosebumps formed on her skin.

\emph{What? What is it?}

She clasped her hands together instinctively. It was cold. She felt like
her whole body was growing cold from the inside. It was only for a split
second, but she felt her face tense, and her hands and feet turn rigid.
The hairs on her body stood on end.

She felt her skin bristle. Again, and again. Something was closing in on
her, something she couldn't see.

A crowd of chattering people passed alongside her, city flags in hand.
They were participating in the walking rally from the Lost Town gates to
city hall. She saw several familiar faces. There were those who nodded
at Karan in acknowledgement; those who gazed at Karan curiously; those
who paused in their step to smell the aroma of fried pastries which was
wafting out onto the street. There was a father holding hands with his
child; young couples; an old woman with a hat perched upon her snowy
head.

They would walk to city hall, and from there take part in the
ceremonies. Midway through the route, all participants were supposedly
going to receive boxed lunches from the city bureau. Each and every face
bore a relaxed smile, like they were enjoying a picnic on a day off.

Karan could only stand still.

\emph{Shiver.}

She could feel the goosebumps rise on her skin like fizz. She shivered
as she looked up at the sky. It was clear and blue. The winter sky, like
a blue pane of glass, stretched out above her head. But there was
something there, in that sky. She could feel it.

She couldn't see it, or hear it. She could only feel.

Something was there.

Something was coming.

\standout{The Holy Celebration Day, 2017.\\
	Unknown time\\
	A room in the ruins, West Block.}

Inukashi awoke. He had fallen asleep without realizing it. How rare. \emph{I
wonder when I last slept like this.} It might even be when he was still a
baby, suckling on his mother dog's teat.

Death was always close by in the West Block, and violence and armed
robbery were daily occurrences. Thieves could come sneaking into the
ruins with weapons at any time. Even with his dogs there, he couldn't
relax. Inukashi had a good sense of the horrid environment in which he
lived, and the terror that lurked in it. That was why he never slept
deeply. His nerves were always honed to pick up any approaching danger
immediately, whether it be midnight or dawn. He was like a small wild
animal.

But he had fallen into a deep sleep just now. He couldn't believe
himself, that \emph{he} of all people had nodded off unawares, if even for a
short time.

\emph{Am I just tired?} He raked his bangs up. \emph{I'm just worn out from what's
about to happen---what I'm about to do. That's gotta be it. Even my
stomach started to hurt from nerves.}

\emph{I'm exhausted because of you guys, you know that? You good-for-nothings.
More unwanted than the plague.}

He tried hurling complaints at illusions of Shion and Nezumi. Nezumi
remained expressionless, but Shion hunched his shoulders apologetically.
Inukashi raked his bangs up again. He gave a great stretch, and swung
his neck around.

\emph{Hmm?}

His body felt lighter than he expected. He was famished, but not
painfully. He had slept well, and he felt like energy was coursing
through his body. \emph{So my body wanted sleep not because it was dead tired,
but because it wanted to store energy.}

\emph{Geez, self, you're serious about this, aren't you?} He clicked his tongue
unconsciously. The more he associated with Nezumi and Shion, the more
confused he became about where his honest opinions lay. Feelings that he
had kept at the very, very bottom of his heart simply slipped out. It
made him annoyed enough to click his tongue. Yet he welcomed it at the
same time.

\emph{So I'm pretty serious about this, then.} He tried whistling. The black
dog at his feet gave a twitch of its ear.

\emph{I've made the decision to fight the battle with them.} And that meant
believing. \emph{I guess it means... somewhere inside, I'm trying to believe
in them, in the future, and more than anything, in myself.}

An irritating guttural noise wrenched Inukashi away from his thoughts.
Rikiga was curled up in a blanket, snoring loudly. Several empty liquor
bottles were littered around him. It felt like every time he breathed
out, he released liquor-smelling fumes. It made him feel ill.

"Jesus. He's like the prime example of the adult you'd never want to
be." Inukashi sniffed disdainfully. He glanced at a corner of the room.
A purple blanket peeped out from between the sprawled dogs. Rikiga had
given it to him for the baby. Rikiga had proudly said he had picked it
to match Shionn's eyes, but Inukashi thought it was a garish, vulgar
shade of purple. Not even close to the colour of Shionn's eyes. He had
taken it gladly though, of course, since baby blankets were luxury items
that you couldn't exactly just "come across" in the West Block.

"Shionn?" The baby was silent. There wasn't even any sound of breathing.
Inukashi's heart began to palpitate.

\emph{Oy, come on...}

It was unusual for babies or toddlers to survive in a harsh environment
like the West Block. Starvation, hypothermia, disease, accident, and
infanticide. Sudden death, too. Death always wandered in search of prey,
changing form and shape each time. Powerless babies were prey to the
cuckoo bird of death.

"You're not dead, are ya? You gotta be kidding me." He scooped up the
blanket whole. Dark purple eyes, much like Shion's, sparkled at him.
Inukashi felt like he had glimpsed a deep darkness. It was a colour of
darkness that flashed momentarily from within the layers and layers of
black. Shionn blinked. His plump lips puckered as if he were demanding
milk. Inukashi eased his racing heart.

"Shionn, you're alive. Don't scare me like that."

The set of purple eyes shifted its gaze aside. Shionn twisted in
Inukashi's arms. Inukashi hastily readjusted his arms to avoid dropping
him. The baby neither laughed, nor cried---it only looked straight ahead
at something. Inukashi felt like he was holding a strange creature in
his arms.

"What's wrong? What're you looking at?"

Shionn's gaze was not directed this way; it was somewhere else,
somewhere far off. Inukashi didn't know where his gaze led.

"Shionn..." \emph{What's gotten into you? Why are you making eyes like that?
What can you see out there, Shionn?}

Fraught with uncertainties, Inukashi embraced the baby fiercely.

The wind made noises as it whistled past the ruins above.