% !TeX spellcheck = en_US

\chapter{I've done}

\myepigraph{"I've done with fancies, imaginary terrors and phantoms! Life is
real! haven't I lived just now? {[}...{]} The Kingdom of Heaven to her--
{[}...{]} Now for the reign of reason and light... and of will, and of
strength... and now we will see! We will try our strength!"}{-Dostoyevsky, \emph{Crime and Punishment}}

\lettrine{L}{ili was} sleeping. She breathed softly, lying on the tattered sofa at
the back of the shop.

She was in a fetal position, and with her furrowed brow and her pursed
lips, she looked anything but peaceful. Tear streaks still stood out on
her face. Out of anxiety, perhaps, she had curled up into a ball,
clutching tightly onto the blanket Karan had covered her with.

"Lili... poor thing." Karan smoothed the blanket's wrinkles out. Lili's
lips moved imperceptibly.

"Daddy... don't go," she mumbled in her sleep. Her fingers closed
tightly around a corner of the blanket.

Tears sprang into Karan's eyes, and she hurriedly pressed her fingers to
her tear ducts. Crying would not do anything. Tears had never solved
anything for her; she had wept herself dry when Shion had disappeared.

She had wept, and wept, and wept. Certainly, there were times when her
tears supported her. Sometimes, crying allowed her to change her mindset
and take a step towards tomorrow. She had numerous such experiences.
Karan had no intentions of dismissing or being ashamed of her tears.

But this time, it was different.

\emph{I have to protect this little girl. I can't sit here and cry. I have to
become stronger.}

Karan gently stroked Lili's hair. She had to protect Lili from any sort
of peril. \emph{I won't let her be sad any longer. I won't let her suffer. I
couldn't protect Shion; I couldn't protect Safu. But because of that, I
have to protect Lili with all it takes.}

\emph{I've been given almost no power at all: no power to change the world; no
power to ward off the rain of misfortune; no power to save the ones I
love. I am weak, but I am not powerless. There is still a little
strength left inside me. I'll use that strength to open my arms wide,
and become a shield to the ones weaker and more fragile than me.}

"Daddy... daddy... I'm scared."

Karan kissed Lili softly on her forehead. "Lili, it's okay. It's going
to be alright."

There was a knock.

Someone was knocking at the shop door in an apologetic but hurried
manner. Every time she heard a knock, Karan's heart used to soar at the
idea of Shion coming home. She used to be overcome with the urge to run
up to the door. Now, she was calm enough to tilt a cautious ear to the
sound of the door being struck.

It wasn't because she had lost hope. As a mother, her hope for her son's
return was firmly rooted in her heart.

\memo[0.45\textwidth]{8}

It was Nezumi's message. That short letter was hope itself. Hope brought
ease and resolution back to Karan. It bid her to be calm. It gave her
something to believe in.

\memo[0.45\textwidth]{8}

\emph{Yes, that's right. You'll definitely come home some day, Shion.
Definitely. Karan stood and crept up to the door.}

"Karan, aren't you home? It's me," said a somewhat tired male voice. It
was Yoming, the elder brother of Lili's mother, Renka. He was Lili's
only uncle and one of her few blood relatives.

"Hold on a minute, Yoming. I'll open it now." She pulled the blinds up
and unlocked the door. A tall man entered on unsteady feet. He looked
even more exhausted than he sounded.

"How's Renka?" she asked as she closed the door. The man had sunken into
a chair. According to him, Renka had worked herself into a panic over
worrying about her husband, who had not returned home from work.

"I gave her tranquilizers and finally got her to sleep. She cried and
screamed... it was horrible. I never imagined that she'd bawl like that.
She's a little tougher most of the time."

"She must be worried sick."

"You bet. No matter how long she kept waiting, Getsuyaku never came
home. He didn't show up on his usual bus, nor on the one after that.
This is the first time this has happened since they got married. She
figured something had happened to him, and she didn't know what to do.
It was all she could think about. I told her to calm down, but she
wouldn't listen to anything I said... it was a pity to watch."

"But someone would call if something happened at his workplace, right?
If there hasn't been a call, then..."

Yoming shook his head weakly. The bags under his eyes grew more
pronounced, and the creases deepened between his eyebrows.

"I don't know where he works. I have no idea where to call, or who to
ask questions to. Getsuyaku didn't even tell his own family where he was
working."

"His workplace? Even Renka doesn't know?"

"Yeah, she said she has no idea. She'd questioned Getsuyaku before, soon
after they'd gotten married, but he didn't give an answer. He said he
wasn't doing anything shady, but he couldn't say on corporate orders. He
begged her not to ask because he'd get fired for telling her. Renka said
she had no choice but to close her mouth after that. His salary wasn't
exactly high, but Getsuyaku made more than the average Lost Town
resident, and he used to hand it all to his wife. Renka eventually
stopped being bothered by Getsuyaku's workplace, and reckoned that he'd
tell her when the time was right. She had Lili, and another baby was on
the way. Sure, it bothered her, but a stable means of living was her
main concern. So she turned a blind eye. The result― this."

"But what kind of workplace would you have to keep secret from your own
family?"

"Where do you think?" Yoming looked up at Karan. A sharp light glinted
for a moment in his bloodshot eyes. Karan swallowed. Secrets,
concealment, silence.

"The Correctional Facility." As soon as the words slid off her tongue, a
bitter taste spread inside her mouth. She knew it was an illusion, but
it was bitter enough to make her shudder.

"Yes, that's what I think, too. I don't have evidence, but I'm almost
positive it's there. Getsuyaku was working at the Correctional Facility.
Of course, it probably wasn't such an important department. But a
workplace that needs to enforce a gag law right to the bottom rungs of
its organization... yeah, that place is the only possibility."

"But... even if Getsuyaku-san did work for the Correctional Facility, he
still came home every day at the same time, right?"

"Yeah. He left home and came back every day on the minute, like
clockwork. But today, no matter how long she waited, he never came home.
And on top of that..." Yoming hesitated to speak.

"Did something happen?"

Yoming extracted a small bag from his breast pocket, and emptied its
contents into the palm of his hand. Karan held her breath.

"Oh my, gold coins."

Three gold coins. One gold coin amounted to about half a year's worth of
wages for Lost Town residents. Three gold coins. It was an enormous sum.

"Getsuyaku gave them to her."

"Heavens, how did he come by such a large amount of money?"

"Renka asked him the same thing. But knowing her, she probably
interrogated him, more like."

"And Getsuyaku-san?"

"He didn't give her a clear answer. He said it wasn't shady money, and
kept repeating that it was legitimate payment. In the end, it was left
in the dark. It's just that... afterwards, Renka overheard him saying to
himself that it should be enough to sustain them for a good while.
Renka's insisting that Getsuyaku meant that they would be okay if he
disappeared. As for me, I don't think she's being delusional."

"Did Getsuyaku-san feel some kind of... premonition that something would
happen to him?"

"I suppose. Renka says he'd been acting strange these past couple of
days. He seemed to be lost and afraid of something, and there would
often be times like yesterday, when he'd be dazed and unresponsive."

"It seems like Lili had the same feeling. She was very worried about
Getsuyaku-san." Karan's voice trembled at the end of her words. Her
heart pounded frantically.

A large amount of money with no identifiable source; an utterance
predicting his failure to return; his inscrutable behaviour―it all
smelled of destruction. She could understand why Renka had become upset,
unable to bear her anxiety. Adding to this fact was that Renka had
witnessed her previous husband's sudden and mysterious death.

\emph{The same thing will happen again.}

That thought would make her fear and anxiety burgeon. Renka's household
with Getsuyaku was her small paradise, attained at last after a hard
struggle with her daughter. For her to have it wrenched from her, for
her to lose it all again―it was too cruel.

Yoming suddenly stood up. He began pacing inside the small store. His
footsteps echoed.

"Are they linked?" His footsteps almost drowned out his low voice, now
almost a mumble.

"Hm? What did you say?"

Yoming's feet stopped abruptly. He turned his body to stand in front of
Karan. His face was tense, but his flushed cheeks betrayed his
excitement.

"Is there a link between the incident with Getsuyaku and the incidents
in No. 6? What do you think, Karan?"

"No, why, there's no way―"

"―that could be true? Are you sure?" Yoming's eyes harboured a feverish
dull light. In a matter of minutes, his whole countenance had changed.
Or had Yoming simply showed a side of him he had kept hidden before?

"If Getsuyaku wasn't able to come home, it wasn't from personal reasons.
You know him; if it was, he would definitely contact his family somehow.
Right now, he's in a situation where he can't contact them even if he
wanted to. Maybe he's completely forbidden to make contact with anyone."

"You mean he's been detained somewhere?"

"Yes. But if he was detained, there would be some kind of notice to his
family from the Security Bureau. At least, that's how it's been up until
now. But there hasn't been any contact. If his workplace happened to be
the Correctional Facility... can't we say that maybe some abnormal
incident has occurred there?"

Correctional Facility. Safu was probably taken there, and Shion was
likely there as well.

"It's not only the Correctional Facility... hey, Karan. Right now, this
city, No. 6, is undergoing a huge shift. You feel it too, right?"

"Yes," Karan said hesitantly.

Yoming resumed walking. Click, click, click. His footsteps rang out more
loudly, more incessantly. "Holy City citizens are dropping dead left and
right. The authorities aren't trying to deal with it. In fact, they
can't. No one knows what to do. This is probably the first time
something like this has happened. No. 6 was the ultimate utopian city,
called Holy City by people, even―and it's crumbling. By tomorrow, it may
be completely gone."

"Yoming, you're getting ahead of yourself. It can't possibly be―"

"No, I know," Yoming interrupted Karan firmly, and a smile crossed his
lips. "There's a horror circling within this city, a horror no one's
experienced before. It's the horror of having your life threatened.
Soon, it'll turn into discontent towards the city authorities. In fact,
the discontent has swelled up so much, it's probably almost bursting by
now. Citizens were used to obeying and accepting the false prosperity
thrust upon them, but now they've woken up. They've woken up, and
realized what an unfair and confining world they've lived in. Yes, yes,
they've finally awoken. And they're nearly out of their wits panicking.
Goodness knows why they didn't try to wake up sooner. No one tried to
look at the truth."

"Yoming..." Karan took one step back. Yoming appeared not to notice
Karan's unease. He looked like he had forgotten about Getsuyaku and his
only younger sister, Renka, as well. Getsuyaku, Renka, Lili, and Karan.
Jarred by the tumult of his emotions, Yoming was not able to spare a
thought to any individual person around him.

Karan knew people with eyes like these.

It was a long, long time ago, when Karan was young. No. 6 had not even
developed its outline. Those people were carried away with their words
and ideals; their gazes smouldered with passion and their voices were
ablaze. They blinded others with their brilliance, but they were also
terrifying. Humans were nowhere to be found at the other end of their
heated gaze. They discoursed of ideals, but they were barely interested
in people. Perhaps they had not even realized that they no longer
regarded the existence of humans. They spoke of the foundation of the
ideal city as something of the near future, and yet humans never
factored into those thoughts... it was unnerving.

Karan gradually distanced herself from them. She was afraid of being
with them. She was afraid of their gaze. Those men were people who
gradually went on to build the foundation of No. 6, and yet she found
them terrifying, unnerving, and hard to relate to.

Terrifying, unnerving...

They had similar eyes. Those men discussed the creation of the utopian
city. The man in front of her spoke of its destruction. They stood on
opposite ends, and yet they had similar eyes.

"Karan, this is our opportunity. Our one in a thousand chances of
choking the life out of this artificial Holy City. Who knew it would
come so soon?" he chuckled. "Even heaven has turned its back on No. 6."

Yoming stopped and began to laugh out loud. Karan felt a chill. She felt
her back tense with cold.

"Yoming... what are you thinking? What are you planning to do?"

Yoming's eyes shifted aside, and his eyes trained on Karan.

"What am I trying to do? Hmm... well, Karan, I guess I can tell you
everything. You're almost like one of us anyway."

"One of you...?"

"There are many people like me in this city who have had their family
torn from them ruthlessly. You're one of those people too, aren't you?"

She had no choice but to answer 'yes'. She had certainly been ruthlessly
and suddenly torn apart from her son.

"It was almost impossible to make contact with each other because the
authorities were so strict with their surveillance. It's almost a
miracle that you and I were able to meet and talk freely like this. By
coincidence you happened to be friendly with Renka as a neighbour, and
that must've worked in our favour. But with this commotion, their
surveillance should be even more lax. The authorities have probably got
their hands full dealing with the emergency. We're going to penetrate
that gap. Just watch, Karan."

"Yoming!" Karan said shrilly. "Answer me. What are you planning to do?"

"Shh, don't raise your voice," Yoming warned. "Be cautious. We can't let
our guard down yet. Look here, listen carefully. Soon, I'm going to use
the electronic information network to call on the citizens. I'll tell
them: the authorities are going to watch their people die, and do
nothing about it. Instead of taking any effective steps to battle the
emergency, they're just twiddling their thumbs and watching their
citizens perish. Let's all storm the Moondrop. We have to drag the mayor
out. The higher-ups intend to give themselves a special vaccine so that
only they survive. We can't let that happen. That's what I'll say."

"Wait, what special vaccine? Does that exist?"

"I don't know."

"You don't know... you mean it doesn't exist, then?" Karan said
incredulously.

"We have no time to be worrying about whether it exists or not. But
don't you think it's a likely story?"

"That's much too vague to circulate... Yoming, do you plan on releasing
a false story to cause an uproar among the people?"

"Yes," said Yoming promptly. "The citizens' discontent is reaching an
all-time high. This will hit the spot. It's the last drop that'll burst
the entire dam. Karan, think about it: the majority of No. 6's citizens
are going to gather in droves to the Moondrop, their faces drawn in
anger and fear. What a sight it'll be. Just thinking about it makes me
shiver in glee."

"No, stop. You mustn't do that."

"I mustn't? Why not? Why are you saying things like that?"

"People will die." Karan looked straight into Yoming's face and spoke
slowly, as if to chew on each and every word. Her tongue felt heavy and
sluggish. A part of her head felt numb. "Many people will die. Yoming,
don't tell me you can't imagine what will happen. What will the
authorities do to that mob of people? You shouldn't even need to think
about it; they'll try to suppress them with brute force. No. 6―this
city-state―never, ever forgives people who rebel against it. They'll try
to suppress each and every person with the military... with military
force... Yoming, you understand, don't you? You understand, very, very
well."

Yoming looked away from Karan and sighed.

"But if tens of thousands of citizens storm in, even the authorities
will have no way to deal with it. Only an army would be able to handle
that."

"And what if they mobilize the army?" Karan raised her voice.

"Don't be foolish. No. 6 doesn't have an army. Every type of military
force is forbidden by the Babylon Treaty."

Yoming closed his mouth. His jaw was rigid and taut. Karan felt like
laughing.

No. 6, honour the treaty? How can you say such rubbish when you don't
even believe in it? Were you always the sort to speak so easily what you
didn't mean? Yoming, you told me once: this city devours people
ruthlessly. Weren't you fighting against the ruthless state who refused
to treat humans like humans? Weren't you fighting to honour people's
lives?

"People will die," she repeated. And she would repeat it as many times
as she had to. "If the civilians and the army collide, lots of... lots
of blood will be spilled. You can't let that happen. Yoming, think. All
those people who will die―they have families of their own. They have
people whom they love. They have family, like Lili here, or Renka. You
can't murder them."

"It can't be helped." Yoming's mutter put a stop to Karan's words. For a
moment, she didn't understand what had been said to her.

"What? What did you say?"

"Karan, the world is about to change. People will be sacrificed, but we
can't help it. Nothing will change if we keep fearing bloodshed."

"Yoming... are you insane?"

"Am I insane? Of course not. I'm not the one that's insane; it's them,
No. 6. I've got my wits about me, and I'm not afraid. Even if I were to
lose my life now, I'd have no regrets. I only have to accomplish what I
set out to do. Yes, I know my death won't be in vain. For the founding
of a new world, I would gladly offer my life. I'd become the stone upon
which the new world stands... a true hero."

\emph{Do you need sacrifice to found a new world? Must you offer up lives? A
world that seeks sacrificial offerings is just the same―just the same as
the Holy City you're so desperately trying to destroy. It's not new at
all. Not a single thing will change.}

She felt a tightness in her chest. Her breathing grew ragged, her words
were thrown into disarray, and she gasped for air.

"Do you think your wife... do you think she would have wanted you to
die... all those people to die?"

"My wife... you're right, I'll finally be able to avenge my wife and
son. They're probably overjoyed."

"Yoming, your wife wouldn't want revenge. I'm sure she definitely
wouldn't want you to die. Snap out of it, please. Peace won't come from
vengeance. Hatred only gives birth to more hatred. You have to keep
living."

Yoming's eyes hardened. Wrath flared within them.

"Karan... why are you stopping me? Are you not one of us? Are you siding
with No. 6?"

"No one said I was. I'm just―"

"Enough." Yoming strode swiftly to the door, and put a hand on the
doorknob. "Karan, I'm disappointed. I thought we could have understood
each other more. It's such a shame. I've lost hope in you."

"Yoming," Karan protested.

"In time, you'll realize how right I was. And when that time comes,
celebrate for me. I'll forgive you."

\emph{I'm right, I'm right. There is no way I could be wrong.} Once a man
completely believed that he was right, that he would never err, he was
already wrong.

"Look out for Lili and Renka for me. I probably won't be able to see
them for a while." The door opened. The wind blew in. She could see the
darkness. The sun had already set, and a breeze crawled across the
ground. The man's tall figure disappeared into the wind and darkness.
The door closed, and only the scent of nighttime remained.

Karan had crumpled to the floor. She covered her face with her hands,
and screwed her eyes shut. She felt dizzy. She felt ill.

"Ma'am," called a girl's thin voice. Lili had sat up on the sofa and was
watching Karan. "What's wrong?"

"Lili... no, it's nothing, dear."

"Really? Is there really nothing wrong?" Lili held her hands out. Karan
embraced her, blanket and all. Her tiny body was trembling.

"It's alright, it's alright. You have nothing to worry about. It'll be
alright," she murmured slowly as if in song. Lili's trembling stopped,
and her quick breathing calmed down again.

"Daddy isn't home yet."

"No, he isn't. He must have had a busy day at work."

"Ma'am, I'm gonna go home. I have to stay with Mommy. I can't leave poor
Mommy by herself."

"My, Lili." \emph{Yoming, do you see this? Your niece is so young, so weak,
and yet she's still concerned about her mother. In her own way, she's
trying to protect those who are important to her. There are many
children out there like Lili. We can't make them suffer. We can't take
their loved ones away. Please, let no one be killed. Don't die, Yoming.
Don't be killed.}

"Lili, your mother is asleep right now. Let her rest for a while. We'll
wait a bit, and then go and call on your mother, alright? For now, we
have to wait here for your father."

"Here at your bakery, ma'am?"

"Yes. We have bread here―fresh bread and milk, and a little fruit. I
know! Let's have a party with the three of us. When your father comes
home, he can join."

"A party?" Lili blinked. A faint blush crept into her cheeks. "I'd love
a party."

"Right? I can't bake a cake now, but I do have some muffins. I also have
some chocolate cookies left over, and I think I had some marshmallows,
too. Lili, would you arrange them on a plate nicely?"

"Yeah! I'll do it, I wanna do it!"

"Then I'll leave it up to you. We'll arrange everything nicely, get
prepared for the party, and then we'll go call on your mother together.
Renka would be happy, right?"

"She'll sure be happy!" Lili said ecstatically. "Mommy likes your
muffins as much as I do... oh, Cravat!"

"Hm? Cravats?" Karan instinctively glanced at the display case, which
had barely anything left inside. She had not sold out; rather, she had
not been able to bake a decent amount of pastries or bread in the first
place. Her usual supplier had not come. Stores everywhere had closed
their doors. She was running low on flour, sugar, butter, and oil. If
she continued without replenishing her stock, she would run out within a
few days. Karan had no choice but to close her shop.

The distribution chain was crumbling.

"Lili, I haven't made any cravats," she said aloud, and realized
immediately that Lili was not talking about the pastry. It was Cravat,
the small brown mouse.

"―No," Lili exhaled. Disappointment etched her face. "I thought I saw
Cravat, but it was just me."

"Do you want to see Cravat, Lili?"

"Yeah. I really like that little mouse. He has such beautiful eyes, and
he's so soft and warm when you hold him in your hand. I like him lots
and lots. Ma'am, where does Cravat live?"

"Hmm... I wonder where."

"You don't know either, ma'am?"

"I don't, unfortunately. I have no idea."

"Oh," Lili said. "You know, I really wanna go see Cravat's house. I feel
like it would be so much fun. There are probably lots of other little
mice beside Cravat, too, right?"

"Hmm, I think you're right. I feel like it would be like that."

\emph{Cravat's destination and his home―that's where my son is.}

\emph{Shion, what are you doing now? How are you doing? Are you with Nezumi?
You, Nezumi, and Safu are all alive, right? I can't do anything for you.
I know I'm undependable, but these hands don't reach far enough to touch
you.}

\emph{Live, Shion. Please cherish your life. Treat your life and the lives of
others with compassion.}

\memo[0.45\textwidth]{8}

\emph{Yes, of course. We will not be beaten. No matter how dire the situation,
we'll live to meet again.}

"Ma'am, I'll get the plates."

"That would be great, dear. I want you to get the big painted plate at
back of the cabinet. There are tea cups and a tea pot that match. Can
you find them?"

"I will. Leave it to me!" Lili bounded up to the cabinet on light feet.~

Karan placed a hand on her chest, and quietly took several deep breaths.

\emph{No matter what, we will survive. We'll reach the end of our lives, not
as glorious heroes whose names will remain beyond our time, but as ones
who have lived modestly. We'll hold in our hands a life not forced upon
us, but a life we decided for ourselves.}

\emph{That will be our victory.}

\emph{Right, Shion? Right, Nezumi?}

\mybreak

"How long do we have to stay like this for?" Rikiga stifled a yawn. He
fished out a flat metal bottle from his jacket pocket. The stench of
alcohol stung Inukashi's nose.

"That stinks. What's in there?" he asked as he pinched his nose.

"Do you want to know?" Rikiga flashed a vulgar grin, and lightly shook
the bottle. Inukashi could hear liquid sloshing inside.

"I don't even have to ask. It stinks of cheap booze. Ugh, that smell!
Makes me wanna throw up." He pulled his face into a scowl. It was no
act. The bottle was not even open, but the nauseating odour radiating
from it assaulted his nose.

"Don't ask if you already know," Rikiga said.

"I was bored, alright?" Inukashi retorted. "Unfortunately for me, the
only person I have to talk to is an alcoholic geezer. Can't start a
conversation without a topic, right? I'm doing a lot of work on my end
here."

"You have your dogs." Rikiga jerked his chin underneath the desk. A
large black dog was stretched out on the floor. In a corner of the room,
there were also three dogs lounging in various comfortable positions.
The small mice were curled up and asleep on the back of a black and
white patched dog. In a way, it was a peaceful pastoral scene.

Rikiga did not seem to take a liking to this, for he furrowed his brow
and growled.

"Take your choice of the dogs or the mice as your conversational pals.
They suit you."

"It's important for them to get their rest. I don't wanna disturb 'em."

"Hah, talking big, huh? As if this room wasn't small enough with the
dogs taking over the space. I'm human; why do I have to curl up in this
tiny chair?"

"It's a matter of rank."

"Rank?"

"I mean class. I'm just saying that my dogs are at a much higher level
than a drunk man blinded by greed."

"You go on saying what you will. You're just an underdog howling about
its loss." Rikiga shrugged, and emptied the contents of the bottle into
his mouth.

"Underdog? Old man, don't tell me you're waving your white flag already.
Let me tell you something: if we've come this far and we lose, it
means―" Inukashi cut himself off, and reached for the bag on top of the
desk. Rikiga glared at him with bloodshot eyes.

"If we lose, it means what? Stop being mysterious about it. Or have you
just forgotten how to speak like a proper human? Ha ha ha, Inukashi,
you're becoming closer to a dog every day. Soon you'll grow a tail, turn
furry, and start prowling around on your hands and feet. Ha ha ha!"

Inukashi glanced at Rikiga's flushed face, and clicked his tongue
softly.

"Become a dog? Bring it on. I couldn't wish for anything better. If I
could turn into a dog by praying, I'd pray to any God out there." He was
almost serious.

\emph{If I were to be reincarnated, would I choose to be a dog or a human?
What would I say if someone―or even God―asked me? I would probably
puzzle over it, unable to come up with an answer.}

He could not say that humans were loftier or more decent than dogs.
Inukashi knew of both the noble souls of dogs and the foolish hearts of
humans. Dogs only sought food enough to keep them alive, but human greed
knew no boundaries. Once a man's belly was full, he desired wealth; when
he had wealth, he desired more wealth and power.

Were not dogs more intelligent and sound in judgment? They knew when
they were fulfilled, whereas humans continued clawing for more and more.

Rikiga burped rudely.

"They're more intelligent than this old man, at least."

"Huh? Did you say something?"

"Nothing. I was just speaking in Dog."

"Hah. So, what was that? If we lose, what will happen to us?"

"We'll become like Getsuyaku."

Rikiga's hand froze, his bottle poised mid-air. Whiskey spilled from the
mouth and splashed on the floor.

"We'll turn into corpses and be dragged across ground," Inukashi
continued. "Or maybe we'll be dragged across the ground before we become
corpses. Either way, it doesn't make much of a difference. Right?"

"Right," Rikiga answered. He twisted the cap tightly on the bottle, and
tossed it back into his pocket. He seemed to be remembering Getsuyaku
getting shot through the chest, and his sagging cheeks began to tremble.

Rikiga was afraid of death. Inukashi didn't have the heart to sneer at
him and call him a coward. Inukashi was afraid of death as well. He was
afraid of it more than anything.

Getsuyaku had died almost immediately, with next to no suffering. In a
sense, his last moments were lucky. For Inukashi, who had seen countless
grisly deaths, a painless death was like a gift from heaven. If he was
going to die anyway, he wanted to die without pain. But if it was
possible for him to survive, he wanted to do anything he could to live.
If only death awaited at the end of his suffering, he wanted none of it.
But if suffering meant he could live, he could bear it. He would endure,
and live on.

He did not want to become like Getsuyaku.

\emph{I won't become like Getsuyaku. I won't let No. 6 kill me so easily. I'd
like to see them try to hunt me down.}

He drew the zipper on the bag, and examined its contents. Two foldable
automatic rifles. A few grenades and magazines of ammunition. All were
outdated secondhand items.

"Pathetic," Inukashi muttered under his breath with a sigh. Rikiga
didn't miss it.

"If you've got complaints about it, secure us some supplies yourself,"
he said indignantly. "How hard do you think I had to work to prepare
that many weapons, huh? Tell me where in the West Block I would be able
to buy the latest photon or electric gun, or a controlled-detonation
automatic microbomb. I'd like you to introduce me to those suppliers if
you've got contacts."

"Huh, well I thought getting weapons would be nothing with mighty Mr.
Rikiga's connections and networks. I guess I overestimated you. What a
disappointment."

"Oh, there's nothing that delights me more than Eve or you being
disappointed in me. I'm telling you never to expect anything from me
again. I'd rather all the the women in the world get sick of me than you
lot having expectations for me."

"No need to worry, the ladies are probably sick of you already."
Inukashi dismissed Rikiga's insult lightly, and began building the
automatic rifle.

"Inukashi."

"What?"

"Do you know how to use a gun?"

"We'll see."

"Have you... well, it doesn't even have to be a person. Have you ever
shot a dog or cat, even a rat?"

"I've been shot \emph{at} before, by the old butcher guy. It was when I nicked
a joint of meat. He flew into a rage and started firing his rifle. I
almost came away with a hole in my forehead. Thank heavens I didn't."

"Well, that's unfortunate," Rikiga replied sarcastically. "Maybe a few
holes would have aired out that brain of yours. Then you'd learn how to
speak to people properly."

"Hah, well, too bad for you. As you can see, my skull is still chock
full with brains. The old butcher, on the other hand, is probably
turning into a rotting hunk of meat under the rubble."

"Did he die during the Hunt?"

"Yeah. Looked like his arm was torn clean off. I don't think he'd ever
be able to fire a rifle with that."

Rikiga wiped his mouth with the back of his hand, and questioned
Inukashi again. "So, what about you? Have you ever fired a gun, even
once?"

"No."

Rikiga's pupils darted about. His uncertainty was apparent in his roving
gaze.

"How about you, old man? Have you ever gone on a long romp with any of
these ladies?"

"...I can't say I haven't. But let me tell you, my shooting skills are
no better than a blindfolded monkey."

"Stop being modest."

"Besides, why did Eve make us prepare this? This is the hygiene
management room. What does he plan to do, making us wait with these
weapons?"

Inukashi suddenly spun around, gun in hand. He aligned the sight with
the chest of the man sitting in front of him, and stood poised.

"This is it, old man."

"What? H-Hey, Inukashi, what's this about?"

"This is what it's about. Relax, I won't miss. I'll send you underground
in one shot."

"H-Hey, idiot, stop it. I said stop!" Rikiga yelled, and sprang to his
feet. His momentum made him stumble, and he fell to the floor.

"No, Inukashi. Have you gone insane? Stop!"

"Bang!" Inukashi pointed the barrel at the ceiling and grinned. "Oops. I
forgot to load it."

Rikiga looked up at him, curled up and gasping.

"Inukashi... don't you get carried away. What would you get out of
teasing me, anyway?"

"It kills time. I just wanted to give you a little scare. I didn't
realize you'd live up to my expectations this much. This is awesome."

"Stop messing around, damnit!" Rikiga said angrily. " I'm not going to
let some doggy boy get the better of me. I'm going home. I've had enough
of being alone with you in this stinking place. I can't take it. I'm
gone." He appeared serious, for he stood up and made for the door.

"If you take one step out that door―" Inukashi aimed his gun again.
"I'll shoot for real this time."

"It's not loaded."

"Know a joke when you hear one," Inukashi retorted. "Sure, I might not
have any shooting experience. But even a blindfolded monkey can hit its
target at point-blank range."

Rikiga clucked his tongue. \emph{Cluck cluck cluck.} Then he looked around, and
gave a sigh.

"It's dark." Rikiga's fat fingers felt for the light switch. The lights
came on; they were bright, too bright for Inukashi's eyes which were
used to being guided by the moon or a candle. He had barely any time to
blink when his gun was violently yanked from him. He staggered, took a
step forward, and was struck across the face. For a moment, his mind
went blank. This time, Inukashi was the one to land with his bottom on
the floor.

Rikiga began to shower him with abuse.

"You good-for-nothing brat," he roared. "As soon as I'm a little nice to
you, you start thinking you're entitled to everything."

The black dog snarled menacingly as it got to its feet. The other dogs
also acted swiftly. They circled around Rikiga, growling softly. The
mice huddled in a corner of the room with a steady eye on the
proceedings.

"Stupid mutts, don't underestimate us humans. Come at me, but before you
do, I'll blow a hole through your master's head."

"Wow, old man. Those were some moves. Almost as fast as Nezumi, I'd
say―but that would be giving you too much credit. Impressive. Ah, I see
you in a whole new light now. You're a fast drunkard, aren't ya?"

"Go on saying all the crap you want. I'm actually angry now. I'd feel so
much better if I could swing two or three punches into that face. Hmph,
you better watch yourself."

"Unfortunately―" Inukashi smiled wanly, and stuck his finger down the
barrel. "There aren't any bullets in here after all, Mr. Rikiga." Then
he whistled lightly. The tension in the dogs unravelled immediately, and
they rolled onto their sides on the spot. The black dog wagged its bushy
tail. No hint of its previous aggression remained.

"Did I go too far with my joke? Sorry, old man." He stood up and bowed
his head to Rikiga. His battered cheek still burned.

"Goodness..." Rikiga threw his gun down onto the desk, and collapsed
into a chair like a broken marionette. "What the hell are we doing here?
In a place like this... forced to do nothing... only to sit still and
wait..."

"Can't bear it?"

"If I said I couldn't, would you laugh?"

"Nah. I don't think I can bring myself to laugh, old man. I'm not in the
position to. Which means I feel the same way."

"How, now. You and I are at a consensus for the first time."

"You can say that again. This must be some kind of evil omen. It's bad
luck." Inukashi tried to make light of it, but his mood remained gloomy.
He had never expected waiting to be so hard.

They were to wait for Nezumi and Shion in this room, which had been
Getsuyaku's workplace.

That was all he knew right now. Inukashi couldn't even imagine how the
two would arrive here. Rikiga, of course, knew even less. Maybe even
Nezumi himself wasn't sure of the details. Yes―what if neither Nezumi
nor Shion arrived? What if they waited and waited, still waited, and
were fruitless in the end―? \emph{Stop it, don't even jinx yourself. This will
make me an underdog for sure. I don't want to be a loser before the
fight even begins.}

But it was hard.

How long did he have to wait? What was about to happen? It was hard to
wait without being able to predict the future. It was like being pricked
by countless transparent needles. It was like being broiled over an
illusory fire. His heart, which had been so jaunty when he had set foot
into the room, had now shrunken and shrivelled like an exhausted old
man. He was ashamed. He was embarrassed. He felt lame, and he knew he
was. But...

His heart was resolute; he had prepared himself; and yet this
purposeless passing of time made doubt creep into his decision and set
will. He didn't want to quote Rikiga, but he wanted to get out of here.
He was also worried about Shionn. It was almost time for him to wake up.

\emph{Shionn would probably cry if he woke up and didn't see me there. Oh man,
what if he's wailing for me? I wish he would just keep sleeping forever,
protected by the dogs, but of course things aren't always going to go
that well.}

He shook his head.

\emph{I can't think about Shionn. It'll make my heart weak. It'll make me want
to go running back home. I can't think of him now. Forget him. Forget.
Think... think of... Nezumi's letter.} He put a hand on his chest.

On Nezumi's scribbled note, there was but one message which ordered them
to prepare weapons to defend themselves with.

\memo{9}

Would that mean they would be faced with a fight? Would that fight be
with Security Bureau officials stationed at the Correctional Facility?
But there was no way Bureau officials would come all the way down to the
hygiene management room. The one man who had worked in this room had
been killed. He was already a corpse. No one would have business here.

He swallowed his saliva. \emph{Wait with utmost caution. Never let your guard
down.} Inukashi pounced on the wall switch, and turned the lights off.

"Hey, what was that for? Now I can't see anything," Rikiga complained.

"That was bad."

"Bad? What was?"

"The lights. We turned the lights on."

"So what? When it's dark, we turn on the lights. Electric lamps might be
a luxury in the West Block, but here in No. 6 they're commonplace."

"Dumbass, that's not what I'm talking about!" Inukashi said testily.
"What are we gonna do if someone saw that light?"

Even in the darkness, he could see Rikiga's features tense. Inukashi's
eyes were naturally used to the dark. \emph{Damnit, we didn't even need these
lights in the first place.}

"It'll be alright," Rikiga muttered. His voice was hoarse and hard to
hear, like he had forced it out of his throat. "No need to get so jumpy.
Stop acting like a lost rabbit. That light was on for maybe one, two
minutes max. Who the hell is going to care if the hygiene management
room burns down? You said it yourself: this place is like Paradise. It
doesn't even have surveillance cameras."

"It has been, up until now."

On one hand, Getsuyaku had been marked as a suspicious person, and had
been shot and killed. On the other, Nezumi and Shion had been able to
infiltrate the Correctional Facility successfully. This connection had
raised the question of whether the cleaning staff were on the same side
as the intruders, or whether they had collaborated together.

If that was so, was not this room more of a dangerous territory than a
Paradise? It was likely that surveillance had been tightened around the
area. It was very likely.

The black dog suddenly got to its feet. It cast its eyes around with a
low growl. Its gaze quickly trained on one point―the door. The door
connecting to the Correctional Facility. The black dog continued
growling at the metal door that only opened from the Facility side.

\emph{Shit.}

Inukashi snatched a gun and hurled it at Rikiga. Rikiga barely caught
the outdated carbine in his hands. His lips trembled.

"Inukashi... what's going on? What's going to happen?"

"A visitor, old man. An unwanted one at that."

\emph{Thud.} This time, there was a sound behind them. The entrance. He could
feel the moving presence of people through the worn grey door.

"A pincer attack. You must be kidding me." \emph{Shit, we've done it again.
We've made another mistake. A life-threatening one.} Inukashi chewed his
lip. He knew it was useless. He could chew his lip to shreds and it
would undo none of the mistakes they had made.

\emph{Inukashi, get moving.}

Nezumi's voice echoed in his ears.

\emph{A thousand regrets aren't going to open a path for you, but one act
will. Move. Just move.}

Why do I hear his voice? Even at a time like this―no, maybe it's because
we're in this situation that I hear it.

\emph{Move. Search for the path to life.}

Shut up, Nezumi. I've learned my own fair share of tricks to keep myself
alive.

He grasped the bag.

"This way."

He rammed his body into the door that led to the waste collection area.
The door did not budge. An alarm went off. The metal door was opening
up. He could see the tips of military boots.

"Inukashi, this." Rikiga touched the switch on the wall. The doors slid
sideways.

"Alright!" Inukashi roared to cheer himself on. The dogs swarmed into
the collection area behind Inukashi and Rikiga. Hamlet and Cravat wove
swiftly between their legs.

"Ugh, it smells." Rikiga broke into a coughing fit. He was right; there
was an odour. The stench of rotting meat juices filled the air. It was
no doubt the odour from the capsule that he had given Getsuyaku. The
capsule had been sucked in through a vacuum and brought to the
collection area along with other waste. If he had not been shot through
the chest, Getsuyaku would probably be sorting through this pile of
trash tomorrow. He would have been at his usual job.

"Makes me want to throw up," Rikiga groaned softly. A light flared
inside Inukashi's head. He swung around to see Security Bureau officials
with guns in hand beyond the glass. They had stormed into the small
room.

One, two, three, four... four people.

"Follow me, old man."

There was a small power shovel in a corner of the collection depot, near
the waste outlet. With this, Getsuyaku would deposit the waste onto the
conveyor belt and take it to the incinerator. Inukashi hid himself
behind the yellow-painted heavy machine.

The lights came on, illuminating everything with a glare.

\emph{Why do people from No. 6 hate darkness so much? Inukashi thought idly.
Why do they hate what they can't see, places light can't reach, and the
fact that darkness exists? Why do they try to illuminate it all?}

Security Bureau officials opened the door and stepped in. Suddenly, they
covered their noses and mouths with their hands and bent over double.

"What is this?"

"It stinks."

All four of them retreated. All of their faces were contorted. One of
them fell to his knees and vomited on the spot. Inukashi grinned in
satisfaction, and still grinning, aimed his gun.

\emph{Hah, what kind of Security Bureau officials are these? They've got huge
egos but no balls to go along with them. I can't believe they're making
such a fuss over a little smell. Hmph, so that makes them softies as
well as crazies. Makes me laugh. You guys should all go home and suck on
your mommy's nipple.}

He pulled the trigger.

An impact slammed into him. He felt like he had been hit hard in the
forehead. He tumbled backwards, and he felt a dull stinging from his
neck up.

"Horrible. What kind of aim have you got?" Rikiga shouted.

"Cut me some slack, it's my first time. Why don't you try shooting, old
man?"

"Never. I'm a pacifist through and through. I could never fire at other
humans, even if they're Bureau officials."

"I'd like to see you hit your target at least two, three times before
you make a sick joke like that."

The Security Bureau officials fled desperately from the stench. They
would probably not set foot into this place again without gas masks.

How fragile they were.

They were not civilians; they were specially trained Security Bureau
officials. Yet, they could not even endure a mild odour like this.

But at this point in time, Inukashi wanted to thank them rather than
scorn them for their fragility. The officials had bought them some time.
He was not foolish enough to be relieved, thinking that danger had
passed. But bought time was bought time. He could draw a breath.

\emph{But what'll I do with the time I bought?}

\emph{After I catch my breath, what'll I do next?}

He licked his bottom lip. His tongue ran across the dry membrane.

This room had only one entrance and exit: it was the door they had come
running through. The Security Bureau officials―their enemy―were
stationed outside. They were in a sealed room. There was no escape
route. \emph{Soon, those crazy softies are going to attack us. When that
happens―}

The more he thought about it, the more hopeless the situation seemed to
him. But Inukashi did not give up. \emph{We'll manage. There's no way we'll
end like this. Isn't that right, Nezumi?}

He didn't know whether he was believing in Nezumi or himself. But he
knew that he believed. He believed―so he did not give up.

\emph{We'll manage. We'll make do. We won't be finished off like this.}

"Inukashi." Rikiga grabbed his shoulder. "What are they planning to do?"

"Huh?"

Inukashi glanced at the small room, and inhaled sharply. He stood rooted
to the spot.

The Security Bureau officials were loading in an odd-looking device. It
was about as big as the black dog growling fiercely at his feet. One end
of it fanned out widely, and the other end narrowed to about a third of
the width. Numerous spiralled tubes extended from it, but Inukashi could
not see where they led. The body, as well as inside the mouth of the
machine was a colour between grey and blue, and shone in the light. It
reminded him of a highly- polished brass instrument.

"What's that? A huge trumpet?" Rikiga's face relaxed comically, but his
voice was a mixture of tension and fear. "They should have told me there
was going to be a recital. I would have worn my dress coat."

Inukashi was too on-edge to respond to Rikiga's joke. He couldn't
swallow the breath caught in his throat. The thudding of his heart rang
in his ears so loudly, he felt like his eardrums would burst.

Various scenes in the West Block came back to him vividly. It was right
after the Hunt. His surroundings were an expanse of rubble.

The market, where throngs of people moved to and fro among the barracks,
tents, and two-storey brick houses that lined the street, was razed
completely. All had turned to debris.

This destruction did not come from blasting explosives. There had been
no distinctive smell of gunpowder. He had also not seen any burns or
singes. There had been no embers, nor rising smoke. No. 6 had not used
firearms as it usually did for this Hunt. He even felt like No. 6 had
used a giant hand to crush the whole market.

But what had No. 6 used instead of a giant hand?

"Acoustic shockwaves."

Rikiga's ear twitched."Wait, what did you just say?"

"No. 6 used acoustic shockwaves for the Hunt. Like spleen whales do, or
sperm whales, or whatever they're called."

"What are acoustic shockwaves? Where did the whales come from? Can you
explain it in a way I can understand?"

"I can't. I'm just repeating what Nezumi's told me. Old man, you saw for
yourself what happened to the marketplace."

"Yeah―it was a clean sweep. The perfect model of a cleanup. And you're
saying they used acoustic shockwaves for that?"

"Yeah."

Rikiga's eyes opened wide. They bulged so much, Inukashi could count
each capillary running along his eyeball.

"Inukashi, so you're saying that weird trumpet―"

"It might be a smaller version of what they used in the West Block."

\emph{Might be? Hey, Inukashi, you can't fool yourself anymore. That has to be
a miniature sound cannon. That's what No. 6 was developing.}

"And―and they're going to fire that on us?" Rikiga bellowed.

"Don't ask me; ask them. They're the ones with the answers."

Rikiga growled still. Through the darkness, Inukashi could see his face
growing pale. Inukashi aimed his gun, and fired at the blue-grey weapon
of destruction before him. This time, he did not stagger. With great
effort, he held his ground and maintained his posture.

He could not discern where the bullet had hit. Perhaps it had not hit
anything. Perhaps it had flown away into the distance like a whimsical
crow.

"Couldn't you have attached an automatic target tracker?" he grumbled.

"Do you think the West Block would have such a luxury item?"

"Hah, I'm sure you pinched as many pennies as you could. Look what
you've ended up with: something slightly better than a toy."

"That's not the gun's fault. It's your aim."

They peeked out from behind the power shovel at the small room. The
Security Bureau officials were moving busily. They showed no signs of
retaliation. They did not fire a single shot back.

\emph{They don't need to.} They did not need to hit a wretched man right before
delivering his execution. That was probably their concept.

\emph{How compassionate of them. Brings tears to my eyes.}

"Inukashi, hey, Inukashi. What are we going to do? If we go on like
this, we'll be―" Rikiga yelled and ducked down. He cradled his head and
arranged himself in a defensive position. His whole body was shaking.

\emph{There's no way I'm gonna die here. I haven't been born into this world
to die in a place like this.}

Violent emotions churned in his chest. He had never thought about why he
had come into this world. Not once. It had seemed so trivial, he had
never felt the need to think about it. To Inukashi, finding a reason for
being born was nothing more than a foolish game. He had been born into
this world, and that was why he was going to live in it. That was it.
His life was no one's but his own.

\emph{I'm going to decide whether I throw this life away or protect it. It's
no one else's business.}

He fired wildly. \emph{Shooting skills? Go to hell.} The glass dividing the
room and the collection area shattered with a mighty crash. The Bureau
officials' panic was apparent.

The stench had become a torrent, tiding into the small room.

\emph{Move!} Nezumi's hand thumped his back. \emph{Move, Inukashi. Act in order to
live!}

\emph{Just what I was planning to do}, Inukashi answered in his head.

He sprinted up.

The black dog bounded past him and gave a great leap. It soared through
the broken window, making straight for the Bureau officials.