% !TeX spellcheck = en_US

\chapter{Nezumi's days}

\lettrine{T}{he clouds} shrouded the sun, and the land cooled quickly in the shadows.
The atmosphere lost heat rapidly and the daytime weather now seemed like
an illusion. The barrens were dotted with low shrubs and no tall trees;
if one stood on higher ground, one could probably look out across the
horizon.

The reddish soil lay exposed, and angular boulders sat here and there
across the land. It was the picture of ruin and fruitlessness itself.
But a number of shrubs harboured natural springs of clean water within
their depths. Those thickets were marked by their green colour, a shade
lusher than the others, and its bushes which yielded red fruit. The
fruit was about the size of an infant's fist and was much too tough to
eat, but its vivid colour was beautiful, and matched well with the
reddish-brown of the land and the green of the shrubbery.

Nezumi crouched by the spring and scooped up some water with his hands.

It was delicious. For someone who had journeyed across dry land, this
water was like a rejuvenating nectar that gave him strength and sped his
recovery.

``Hey, you guys want to take a break, too?'' Two little mice poked their
heads out of his jacket pocket. They climbed down Nezumi's leg, and once
they reached the ground they gave not so much a glance to the spring as
they pounced right onto the red fruit.

The skin of the fruit was too tough to bite for humans, but it seemed to
pose no difficulty for the rodents' incisors. The mice devoured a whole
fruit in moments, making cheerful crunching sounds all the while.

A mouse with light-brown fur---Shion had named it
Hamlet---looked up and tilted its head as if in inquiry.

``No, that's alright,'' Nezumi told him. ``I don't think I can handle
that fruit. You don't have to worry about me; I have a lot to eat.''

Apparently satisfied with its master's answer, Hamlet began nibbling at
the fruit again. Nezumi sipped another mouthful of water, then washed
his face. He shed his clothes and immersed his body in the spring.

It was far from a hot bath, but the cool water felt refreshing. The
spring was deeper than he thought: if he dove underwater, he could see
where the water sprang from the sandy bottom.

Several small fishes were swimming around in the shadows of the algae,
which swayed lazily along with the current and made him think of an
elegant dance.

Here was a world that was entirely different from the world
above-ground.

``Is it always peaceful underwater?''

How long ago had it been? Shion had murmured those words once, his gaze
hovering in the air.

\mybreak

It was in that room in the West Block. It was dawn. He remembered that
the steady rain had finally let up after three days, and the night had
brought a biting chill that blanketed the Block. But it was now starting
to lighten.

Just the day before, not long after the sun had gone down, Rikiga had
made a rare appearance at Nezumi's residence.

``Shion, I brought this for you to eat.'' Rikiga, who had braved the
cold and blustering winds to get here, placed a pointed emphasis on
``for you to eat'' as he handed a paper bag to Shion.

Shion peeked inside and emitted an exclamation of joy.

``Wow, this is amazing! White bread and meat!''

``There are also fresh vegetables and wine. Oh, and cheese. Quite a
feast, don't you think?''

``We can hold a banquet with this!'' Shion said in awe. ``Rikiga-san,
are you giving this all to us?''

Rikiga pursed his lips and shook his head. ``Not `us'. I'm giving it to
\emph{you}. Don't get that part mixed up. Understand, Shion? You're going to
eat this. You have absolutely no need to give it to a certain
serpent-tongued and cunning actor.''

``We'll all eat it together,'' Shion beamed. ``I've promised to have a
read-aloud with the kids tomorrow. I'll make a nice, hearty soup that we
can all eat together. It'll be a splendid lunch.''

Rikiga's face contorted. His expression was like that of someone whose
back itched terribly, but could not reach far enough to scratch it no
matter how hard he tried. Nezumi stifled a laugh behind his book.

``What? What's so funny, Eve?''

``Oh, nothing. I didn't mean to laugh. But if you must hear it out of
me, it was because you made such a cute face, old man, I couldn't help
but smile.''

Nezumi closed his book and stood up. He peered into the paper bag that
Shion held out for him, and gave a high whistle.

``My, my. This is much more than your average wooing gift. If you seek
you shall find, huh? Only a black market trader like you could pull this
off, Mr. Rikiga, sir.''

``Who are you calling a black market trader? I'm a bonafide
businessman.''

``A businessman who traffics women to No.~6 officials and charges
exorbitant amounts for it? Such philanthropic and saintly work you do. I
am ever so humbled.''

Rikiga bared his teeth and made a sour expression.

``Shion, look. You're free to take the meat and vegetables to make soup
or make them part of your interior decor, but whatever you do, don't let
him have a bite. Don't even let him smell it.''

Shion was not listening. His eyes were aglow as he laid out the contents
of the bag on the table.

``Nezumi's soup is top-class,'' he said.

Potatoes, onion, cabbage, carrots. All were fresh. The mice squeaked
incessantly from atop a pile of books.

``He barely uses any seasoning, but it's still so good,'' Shion
continued. ``With this many ingredients, we should be able to make the
best soup ever. Everyone will be so happy. Thank you, Rikiga-san.''

``Ah\el but, well, Shion. What I'm saying is that I went out of my way
to---''

``Before our meal, we'll say our graces to you, Rikiga-san. It won't be
a half-hearted ritual. I'm sure everyone will be truly thankful when
they say so. Right, Nezumi?''

``Of course. We'll say, `I am grateful and wish nothing but the best
from the bottom of my heart for this compassionate soul. I pray that his
sublime soul will forever be free of any hurt or pain,''' he said in the
voice of an innocent maiden. Rikiga had a soft spot for innocent, pure,
and unblemished things. Perhaps it was because he had internalized his
own corruption, or perhaps they were simply his fancy, but for whatever
reason, he couldn't help but be attracted to them.

Whether it was an innocent maiden or a prostitute on the corner; a noble
lady or loyal young man; a cunning merchant or an aged philosopher,
Nezumi could become whatever the other person wished. If only for a
short moment, he could show them an illusion of their desire with just
his voice.

Just now, he was certain that Rikiga had seen the countenance of an
untainted girl overlapped on his face. The eyes were connected to the
heart, and so could not help but see what they want to see more than
what is actually there. They also refused to acknowledge what they did
not want to see.

``Damnit! Just a third-rate actor and his tricks. Don't think you can
get away with mocking me, Eve.''

``I would never think of doing such a disgusting thing like manipulating
you to my every whim, old man.'' Nezumi shrugged.

\emph{That sneaky fox. He's as unpleasant as they come. Shion, why don't you
move in with me before he starts influencing you? Eve, if you don't
change your ways now, someday you'll pay for it. I know, next time I'll
bring some butter. For you, I mean, Shion. And I'll bring some fruits.
Make sure that bastard fox doesn't swipe them from you.}

Rikiga wrapped up a lengthy rant, then went home.

``He never shuts up,'' Nezumi grumbled. ``The right thing to do would be
to deliver his gifts and go straight home. He's the picture of
tactlessness, overstaying his welcome like that.''

``Well, I thought it was nice of him,'' Shion said. ``He came to deliver
all of this expensive stuff to us. It's ungrateful of you to speak ill
of him.''

``Hah,'' Nezumi scoffed. ``Some No.~6 official must have taken a liking
to a woman that the old man arranged for him. Old man got a handsome
load of goods as a reward for arranging that woman, except that stuff
wouldn't have been hard to come by in No.~6, anyway.''

``But he shared it with us instead of hoarding it for himself. He didn't
expect anything in return. I think it was a noble thing.''

``Noble? Are you kidding me?''

``Am I wrong?''

Nezumi smiled with only one side of his face. He found Shion's trusting
nature at once annoying and funny. His frankness and willingness to
trust were foreign to Nezumi. They were as meaningless as the frivolous
embellishments on a piece of clothing.

Rikiga had done it out of guilt.

He was ashamed that he made a business out of selling West Block women
to men from No.~6, and pocketing the money that came from it. On one
hand, it was a sign that Rikiga's heart had not yet been corrupted to
the core, but on the other hand, it was also a sign of his weakness.

Rikiga had wanted to absolve his guilt, his own weakness, by giving
Shion a part of what he had earned. He wanted to see Shion's carefree
smile, feel his joy, and draw some relief for himself. That was all
there was to it. Yet, Shion could not see through this facade.

\emph{Why does he believe in people so easily? How does he do it?
How does he keep doing it? It's a complete mystery.}

``Nezumi?'' Shion blinked at him uncertainly. ``What're you thinking
about?''

``Nothing, really\el oh, the wine wouldn't be a good idea for the kids.
Let's have it ourselves.''

``Sure. We'll have a bit of cheese and bread to go with. How about we
boil some potatoes, too?''

``Sounds great. This is going to be a wonderful night. Let me take back
what I said earlier---I am most sincerely grateful for Rikiga-san's
incredible generosity.''

``You're pretty material.''

``Call me \emph{liberated}. Now, I'll take care of the potatoes, then.''

``Nezumi, we only have mugs to drink out of.''

``Couldn't ask for better.''

``We're gonna drink wine out of mugs?''

``Hey, you don't have to force yourself. I'll have it all if you don't
want it.''

``In your dreams,'' Shion cut in. ``We're going to divide it equally in
half.''

They poured each other wine as they snacked on bread, cheese, and boiled
potatoes. The label on the bottle indicated that the wine was from the
western-most city of No. 3, and was quite an expensive pick. A gentle
sweetness crept up from the depths of its acidity. It was delicious.

Before long, the two had emptied the whole bottle between themselves.

``You can handle alcohol pretty well, can't you?'' Nezumi said.

``Impressed?'' Shion grinned cockily with a flushed face.

``Not impressed, really, just a bit surprised. I didn't know you were a
drinker.''

``This is the first time in my life.''

``\el What?''

``This is my first drink ever. I didn't expect it to taste so good,''
Shion said thoughtfully.

``Huh? Wait, Shion, are you alright? You just had half a bottle of wine.
You must be pretty drunk by now.''

``Mmmm, not really, no,'' Shion said contentedly. ``It just feels nice.
And now I feel so stupid for troubling myself over such little things.''

``What little things were you troubling yourself over?''

``Uh, let me see,'' Shion drawled, then chuckled. ``I can't remember. If
I can't remember, they must've not been that important in the first
place. Ha ha, cheers to no worries! Cheers to wine!''

``Shion---you're pretty drunk.''

``I \emph{am} drunk. I drank wine, didn't I? Of course I'd be drunk. Or is
there some law saying I'm not allowed to be drunk?'' Shion leaned so far
forward that their noses were practically touching.

``Shion\el please tell me you don't pick fights with people when you're
drunk.''

``Pick fights with people? What people? You?''

``We're the only two here apart from the mice.''

Shion stood up abruptly and put a hand on his hip.

``'We're the only two here apart from the mice.' Ha ha ha, how was it?
Wasn't that impression spot-on?''

``Impression of who?''

``You.''

``Not even a bit.''

``Liar! I sounded exactly like you.'' Shion stabbed a finger at Nezumi,
and drew a circle with it. ``You know, I think I've awakened to my
talent of doing impressions. Maybe I'm a miming prodigy. I \emph{must} be a
prodigy. The heavens have given me this amazing talent. `We're the only
two here apart from the mice.' Ha ha, see! I \emph{do} sound like you!''

``\el Is it fun imitating me?'' Nezumi said exasperatedly.

``It is.'' Shion crouched again and brought his nose right up to
Nezumi's. ``It's unbelievably fun. When I'm with you, everything is such
a joy to experience. Sometimes I wonder why it's so fun to be with
you.''

Nezumi tilted his face away, drew his chin back, and tried to smile
gently like a mother indulging her baby. The muscles around his cheeks
were tense and refused to co-operate.

``I see. Well, that's good for you, isn't it? Just great. But I think
you've let yourself be influenced a little too much by Inukashi's dogs.
We're humans here. We can communicate without having to rub noses.''

``'We're humans here. We can communicate without having to rub noses.'
Heh heh, how was that? Didn't it sound like you? But y'know, Nezumi,
people can't communicate as easily as you make it sound. Compared to the
number of things we understand, there're way more things we wish we
could unnerstan' but can't. A hundred times---a thousan' times more
things. Thas' juss how't is.''

``Shion\el you're starting to slur.''

``But iss great for dogs, innit? They juss hafta stick their noses
t'gether `n' go, \emph{sniff sniff} to unnerstan' each other. An' they lick
each other, too.''

``Don't you dare lick my face.''

``I won'. I might bite, though,'' Shion said, stretching out his last
syllable in a singsong voice.

``Knock it off, you drunk. Hurry up and go to sleep. Don't blame me if
you wake up tomorrow morning with a hangover. Besides, have you stopped
to think about how old you are? You're sixteen and you have no inkling
of how to drink\el Shion? Hey, Shion, what's wrong?''

Shion was leaning heavily on him. Nezumi could hear the sound of his
soft slumbering breathing.

``Geez, you must be kidding me,'' Nezumi muttered. ``Hey, don't fall
asleep here! I'm not gonna carry you to bed, you know.''

Nezumi shifted his weight. Shion shifted along with him, and they both
tumbled onto the floor. Shion's breathing did not so much as catch. It
continued on, even and regular.

``God,'' Nezumi grumbled. ``You stay awake just long enough to blabber
to your heart's content, then you're out like a light. I don't know if
you could get any more `typical drunk' than this.''

\emph{Cheep cheep cheep!} Cravat looked up from nibbling at a piece of cheese
and twitched his whiskers.

\emph{He's hopeless}, he seemed to say. He almost seemed to let out a sigh as
well.

Nezumi couldn't hold it in any longer. He burst out laughing.

He continued to laugh by himself, with Shion beside him.

\mybreak

He woke up.

He knew it was dawn because the air in the room had gotten even colder.
The chill tended to worsen just as the eastern skies were beginning to
lighten. This was also the hour when the highest number of invalids,
elderly, starving children, and physically weak people drew their last
breath.

Death slipped into the gap between the arrival of morning and the
leaving of night and stole people away. \emph{But even so}, Nezumi thought, \emph{the
frigid air and starvation are much more merciful servants of Death.
Much, much more merciful than ruthless violence.}

The scar on his back gave a great throb.

Ruthless---these hostile flames had burnt his back precisely because they
were ruthless. They had swallowed his family and turned everything to
ashes.

\emph{Throb, throb.} The restless pain crawled up his back. Nezumi got up and
regulated his breathing. He took a deep lungful of the frozen air that
summoned death, and exhaled. The cool air that slid down his airway was
a sign that he was alive. He was alive and warm, which was why he could
feel this cold.

\emph{Living people are warm.} Shion had taught him so. Shion had taught him
that living was to feel another's warmth right beside him, and to pass
on one's own warmth to another.

Nezumi raked a hand through his hair, then inhaled and exhaled deeply
one more time. For him, living had always been about revenge and nothing
else. His own survival, the fact that he was alive was revenge towards
No.~6. One day, one day not so far off, he would live and survive to
deliver the fatal blow to No.~6---that had always been the only thing on
his mind. He cared about nothing else. His hatred and loathing towards
No.~6 only mounted, never waned. But he did waver.

Revenge was not the only thing in his heart. There was also something
almost entirely different---something that existed completely unrelated to
No.~6.

Nezumi himself could not grasp what that something was.

\emph{That's why I waver.} He wavered as he wondered about himself after he had
fulfilled his revenge---would he be completely emptied, or would he still
be full? Would there still be a stubborn core of hatred left inside him?
He wavered.

If he wavered, he wandered. Wandering created a vulnerable opening.

Nezumi reached behind him and felt his back. The throbbing had subsided
considerably. Soon it would go away completely.

``Mm\el ''

Shion rolled over. Last night, Nezumi had dragged him to bed, and Shion
had continued to sleep without a sound, save for his breathing.

``You are \emph{so}---'' he murmured to Shion's sleeping face. ``So
high-main\-te\-nance, so hard to take care of\el just hopeless.''

Shion rolled over again. His eyelids fluttered, and slowly lifted. There
was no light source save for the dying embers in the stove. In nearly
inky darkness, Nezumi could see a faint white outline of Shion's profile
and hair.

``Nezumi\el did you say something?''

Despite the fact that he had just woken up, and that they were immersed
in darkness, Shion's vision had caught Nezumi squarely and his ears had
sensed his words.

``I was giving you my morning greetings. Good morning, your Highness.
How do you feel today? ---Something like that.''

``I feel\el not so bad.''

``Oh. Not hung over? Looks like you and booze will get along. If you
don't be careful, you'll turn out like the old man. Don't say I didn't
warn you.''

``You can't get hung over from wine. It's fruit-based, so it's gentle on
the body.''

``Is that true?''

``Yeah. I feel like I heard something along those lines from someone\el 
maybe it's just me.''

``Not very reliable, are you?''

``I'm not. I'm pretty unreliable---I've finally started to realize that.''

``So you've discovered yourself. Congratulations,'' Nezumi teased
without meaning it.

Shion always explored his own self thoroughly, diligently, and
persistently. He always tried to face off squarely with what was inside
of him.

And that was worthy of awe and praise, was it not?

Nezumi knew right down to his bones how difficult it was not to run away
from oneself. He even felt a sort of reverent fear towards this
high-maintenance, hard-to-take-care-of, hopeless boy.

Shion lifted the upper half of his body up and let his gaze wander in
the air.

``Nezumi.''

``Hm?''

``Do you think it's always peaceful underwater?''

``Wha?''

``Underwater. Like in the sea, or in a river, or in a lake\el is it
always peaceful in the water?''

``What're you talking about? Did you dream of something?''

``Yeah. It was the most vivid dream I've had in a while. I wonder if
it's because of the wine?''

``Was it a wine-coloured dream?''

``No\el I was swimming underwater, along the bottom. I could breathe
just fine. I just kept swimming on and on.'' Shion shifted and gave a
small sigh.

``And then?''

``That's it. I was just swimming. It was so quiet and beautiful, and I
felt so happy. It seemed like such a peaceful place, with no fighting or
invading\el ''

``Impossible.'' Nezumi smiled wanly in the dark. \emph{Naive, aren't you?}
``Of course there's fighting underwater. It's just as much of a
dog-eat-dog world as it is above ground. I thought you specialized in
ecology.''

``I was supposed to specialize in it.''

``Either way, it doesn't matter. I thought ecology was a field about the
interaction between organisms and their environment. Didn't you learn
that predation exists underwater, too?''

Shion shook his head. ``I know that. I'm not saying that it's Paradise
underwater. I just thought, since there are no humans\el ''

``So what?''

``There would be no meaningless fighting. There wouldn't be murder for
the sake of murder, or any atrocious killings.''

``That's what you were thinking about while you were swimming?''

``Yeah. It was so\el beautiful. It was sandy on the bottom, and it
stretched on and on. There were jade-coloured stones here and there in
the sand, and they would glimmer from time to time, though I didn't know
how. I reached out to pick one up, but I changed my mind.''

``Why?''

``The stone was so beautiful, I almost felt afraid to touch it. I felt
like if I touched it, the world would fall apart.''

``I didn't know you were such a romanticist,'' Nezumi commented.

``You sound like a blushing maiden.''

Shion squirmed. ``Yeah, I'm a little embarrassed, too. But I can't
really help it, can I? That's just how I felt. But I kind of regret it
now. If I was going to wake up anyway, I should have picked one up.''

Nezumi almost burst out into a laugh again. He wondered if he was losing
the ability to rein in his emotions.

``You should go back to sleep,'' he said. ``Maybe you'll be able to have
the same dream. Then, you could pick up as many rocks or coins as your
heart pleases.''

``I guess. Hey, Nezumi.''

``Hm?''

``We swam when we escaped No.~6, too, didn't we? But that time, I was
concentrating too much on swimming that I didn't have time to stop and
feel much.''

``We were swimming in sewage. That's completely different from what you
dreamed about.''

``But\el it's true that I've seen\el so many beautiful things\el here in
the West Block\el ''

Nezumi could hear the other boy lapse into quiet breathing as he fell
asleep. He could feel Shion's warmth. He felt like this warmth was all
he needed to get him through the frigid winter days.

\emph{What am I thinking? That's absurd.} Those who could not live by
themselves, those who could not stand up to fate on their own, simply
did not survive. It was how things worked in the West Block.

\emph{I don't need any warmth.}

Nezumi got up and filled a cup with water from their stores. He drained
it in one draught. The cool water slipped down through his body. Shion
muttered something unintelligible.

``Did you manage to pick one up?'' Nezumi said to him. There was no
answer. Only the heavy groan of the blowing wind echoed in the air.

\mybreak

The algae suddenly rippled. They were not languid movements like those
moments before; now, it bristled like a thin tree being blasted by the
wind.

It was an unsettling movement.

A silver fish burst out of the tangle of algae and sped past
Nezumi's line of vision. It was but an instant---but Nezumi could clearly
see it swallowing half of a little fish. Predator and prey. The eaters
and the eaten.

The disturbance was brief, and before long the tangle of algae returned
to its normal state and the little fish resumed swimming about as if
nothing had happened.

Nezumi found a blue stone on the waterbed. He picked it up without
hesitation. The stone was neither glittery nor beautiful. It was just a
crude, misshapen rock.

A breath escaped his lips and formed a jet of bubbles. Suddenly, he
couldn't breathe. Unless this was some kind of dream, he knew it was
impossible for a human like him to remain underwater for much longer.

Nezumi paddled the water and aimed for the surface.

The sun was apparently back out, for the surface of the water was
glowing white. A black shadow lay diagonally across the surface.

It was the shadow of a fallen tree. A dying tree had tipped over at the
roots, and was half-hanging into the water. Nezumi grasped a branch and
pulled himself up. Water rushed past his ears and his hair clung to his
neck and shoulders. He could let out a long exhale now. He filled his
chest with air.

The falling tree was still partly connected to its roots, and perhaps
due to that, its leaves were lush and its branches grew out in all
directions without showing signs of withering. Nezumi swung his leg over
the trunk, and took another breath. He had not expected a tree of this
size to be growing here. This unremarkable oasis in fact hid many
treasures within.

Something moved in the corner of his eye, around the area where he had
tossed his belongings. It seemed like a person.

\emph{Screek, screek!}

\emph{Scritch, scritch, scritch!}

The voices of the little mice turned harsh. They were baring their teeth
in apprehension at the suspicious shadow before them.

``Ow! Stop it! Ouch!'' yelled a voice. It belonged to a man. ``Jesus,
what the hell are these things? Go away! Go on, beat it! Stop biting me!
Damnit, I'm gonna roast you whole and eat you. Ow, my earlobe!''

Apparently the little mice had launched into their attack. The man's
cries grew shriller.

``Ow, ow, ow! Damnit, you bastards!''

The man attempted to flee, leaving curses in his wake. He swung his arm
around to brush off the mice. His hand firmly clutched Nezumi's
belongings.

Nezumi stood on the fallen tree and gripped the rock in his hand.

``Hey, thief.''

The man jumped and whirled around. Nezumi hurled the stone straight
towards his face. At the same time, he himself plunged into the water.
He swam towards the shore.

The man was kneeling on the grass, covering his face with both hands.
Blood was dripping from between his fingertips. Hamlet and Cravat leapt
onto his shoulder as Nezumi swiftly donned his clothes.

The little mice clamoured over each other as if making a passionate
claim.

``Right, I get it, I get it. You two did a good job.'' Nezumi petted
them both on the head with his finger. Cravat then dove into his pocket,
and Hamlet into his mop of wet hair.

``Ugh\el it hurts. My eyes\el I'm blinded! Help me!'' The man stretched
his bloody hand out into the air and flailed.

``I aimed for the middle of your forehead, and my aim is good. I've
never missed once. I'll go so far as to say I went easy on you.''

The man looked up at Nezumi with a hand still on his forehead.

``Went easy?'' he said incredulously.

``I sure did. I could have lodged that rock into your forehead. I showed
compassion to a thief. You should be thankful.''

The man took his hand away. Blood was spurting out of the centre of his
forehead and running down his face.

``You call this going easy?''

``Of course. No harm done to your skull or your brain. You just got a
little torn flesh there. It's almost too lenient a punishment for
theft.''

``Why, thank you,'' said the man sarcastically. ``I'll be sure to get my
brainwaves checked out at the hospital. Ugh, god, it hurts! It's
stinging!'' The man groaned as he washed his face. Then, he took out an
array of bottles in many sizes from the cloth bag slung over his
shoulder. Inside the bottles were liquids of every colour. The man
skilfully mixed some liquids together to produce a lilac-coloured,
slightly viscous solution which he soaked a cloth with and applied to
his wound.

``Hmm, this should do it. The wound should close up by tomorrow
morning.'' The man then wound the cloth around his forehead and grinned.
He was tanned, and deep creases lined his eyes and his mouth. There were
prominent white streaks in his shaggy head of hair. Yet his voice and
the glint in his eyes were lively---youthful, even.

His age was a mystery. It was hard to tell whether he was young or old,
but he was still a thief nonetheless.

``But let me say, boy---'' Once the man had put away the bottles into his
bag, he turned to Nezumi and began to talk to him with a smile. His tone
was much like that of a teacher lecturing his student on the principles
of higher learning.

``Now that I can get a closer look at you, I can see you're quite the
beauty. A beauty like you shouldn't be swimming naked in a place like
this. This place is dangerous---breeding grounds for vagabonds and rogues.
Swimming in this place with not a thread to clothe your body---why, you're
like a sweet lamb wandering amongst a pack of wolves. Caution is what's
needed, boy, caution.''

``Thank you, I didn't expect to be lectured by a thief. Good to know you
don't even feel guilty about what you did, old man.''

``Old man? Are you calling me an old man?''

``Well, it's not about me, is it? I'm neither an old man nor a thief.''

The man blinked. Twice. Thrice. Four times. Once he stopped
blinking, he burst out into laughter.

``Ha ha ha! That's funny! Ha ha ha ha! That was a good one! You have a
sharp tongue for such a pretty face. Ha ha ha! Ah, you're an interesting
one!'' he chortled. ``Ha---''

The man's laughter ceased. Nezumi had pressed a knife to his throat.

``What an irritating voice you have,'' Nezumi hissed. ``Why don't you
quiet down for a little---no, forever,'' he whispered into the man's ear
from behind. Nezumi knew well how much fear his whisper instilled to the
person at knifepoint. He also knew how effectively this fear was at
disabling the victim.

The man shuddered.

``Oh\el no, c-come on, wait a minute. You don't have to use a knife to
shut me up. Really, I'm honestly sorry. I'll apologize if I've offended
you. I'm sorry.''

Nezumi drew back and put away his knife. The man clutched his throat and
moved his lips. A long exhale hissed from between them.

``God, impatient despite your looks, aren't you? I thought you'd have a
more graceful manner.''

``I reserve my manners and grace for other people who are also graceful.
You're a thief. You tried to sneak away with a stranger's belongings. I
think you deserve a slash across the throat with a knife much more than
graceful manners.''

``Have you ever killed before?'' The man looked up at Nezumi from
beneath his eyebrows. ``Have you killed a man with that knife,
young'un?''

``I don't have any obligation to answer a thief.''

``No, don't misunderstand me. I wasn't trying to steal your things.''

Nezumi looked down at him expressionlessly.

``It's true,'' the man insisted. ``Believe me. Here, this is proof.''

The man thrust his hand into his cloth bag and began to take out one
item after another. There were several vials of medicine, a bag of cured
meat, a water jug, a wrapped loaf of bread, a hunk of cheese, rock salt,
and a small pouch. The man opened the pouch and showed it to Nezumi. It
was full to bursting with gold coins.

``See? Sorry to say this, but I'm a little more well off than you. I
don't \emph{need} to steal your things. I hope you understand now.''

``I don't understand at all.'' Nezumi shrugged just his right shoulder.

``I don't care how well-off you are. You still tried to walk away with
my stuff. That's the fact of the matter. That was theft and there's no
saying otherwise.''

``I guess it can't be helped if that's what you think I am. So this
wound,''---the man gently touched his forehead---''is my curse and mark of
Cain. I've already been through hell, whatnot with this wound on my
forehead and being bitten by mice. Can't you just take that and say I've
already paid my dues?''

``Awfully in your favour, that interpretation, isn't it?'' Nezumi slung
his load over his shoulder and smiled faintly. Suddenly, everything felt
foolish. Soon the sun would set. He had to secure a spot to sleep for
the night. There was no more time to waste with this smooth-talking
thief.

``Oh, leaving so soon?'' The man stood up. He was wiry and tall. He was
clad from top to bottom in rough, white cloth, and was wearing dirty
leather sandals.

``You bet I am. I'd rather not stay to chat with a thief.''

``I told you I'm not a thief. I just wanted to find something out.''

``Find out?''

``Yes, find out where you came from.''

``And what would you do with that information?''

The man straightened up. ``No, I just thought\el just maybe, that you
were from No.~6. It was just a thought.''

No.~6.

He had not expected to hear this name out here.

No.~6.

The artificial city which some called a utopia, which was supposed to
have been the embodiment of humankind's intellect and hopes, had quickly
transformed into a towering monster. The city had crumbled as if
succumbing to the weight of its own horrific ugliness.

\emph{Nezumi, I'll wait here for you. I'll keep waiting.}

Shion's voice echoed deep inside his ears.

``Aha, I see. So you \emph{are} from that city.'' The man jumped up and
attempted to grasp Nezumi's hand.

``Don't touch me.'' Nezumi batted away the arm that was offered to him.
He hadn't meant to do it with much force, but the man staggered back and
plunged one foot into the water.

``No need to be so hostile,'' the man said. ``It's just that if you \emph{are}
a resident of No.~6, there are a lot of things I'd like to ask you.''

``And I have less than a grain of sand's worth to say to you. I'm not a
citizen of No.~6.''

``But you know about it. Is it true that the city is destroyed now?''

The man's expression showed an obvious tension. The corners of his eyes
were turned up, and they twitched slightly.

``I hear rumours everywhere, but no one knows the truth. And I think you
know. I saw vacuum-packed rations and a lightweight LED
generator in your pack. That's from No.~6, isn't it? I can't think of
anywhere else you would get it.''

Before the day of Nezumi's departure, Karan and Shion had packed all
manners of things into Nezumi's bags, Karan with the face of a mother
seeing her son off, and Shion in stolid silence.

\emph{We really are saying good-bye.}

Nezumi had finally felt the reality of their parting in his flesh as he
watched Shion's profile, with the boy's lips pursed in a stiff, almost
grumpy, line.

\emph{Tomorrow, I'll be leaving. Shion will stay, and I will leave.}

Their two lives, connected almost miraculously four years ago, were now
parting and going their separate ways. Nezumi and Shion had lived
together for less than half a year. It was a very short period compared
to the days he had spent alone until then, and probably to the days that
were to follow. It was a brief, yet intense, period.

\emph{Would there be any period in the future more intense and finely-defined
than that period I spent with him?}

Nezumi shook his head. No.~6 had fallen. He had fulfilled what he had
set out for.

\emph{So it's fine.}

Shion was a person of the past. Although he would remain in Nezumi's
memories, never to disappear, he was not involved in Nezumi's present.

He had to draw a line. If he didn't he would not be able to move
forward. He would not be able to live the present if he was trapped in
the past.

He'd had enough. Enough of dragging the past behind him and
bearing its weight. He wanted no more of it.

``Come on, won't you answer me?'' A pleading tone crept into the man's
voice. ``I hear rumours. Lots of them. I hear that No.~6 has fallen, but
I've also heard that that's all a lie, and that city is still there,
still prospering. I can't tell if either story is true or false.''

``You can always see for yourself.''

The man drew his chin back and let his throat rumble.

``\el But No.~6 is such a distant land.''

``It's only about a six-month walk. That's pretty close.''

``Half a year\el just thinking about it makes me feel faint.'' The man
gave such a lengthy exhale that his body seemed to shrink a size.

``Aren't you a traveller, too, old man? Or don't tell me you've settled
in this wilderness?''

The man's lip curled revealing a part of his teeth, which were
surprisingly white. His tone and his voice carried none of the
piteousness of before.

``Oh, I wouldn't be so incredulous. It might be a more comfortable place
to live than you think.''

The earth was mostly uninhabitable by humans for the long-term, aside
from the six cities and their surroundings---it had been said so for
years.

People had built the six big cities in search of the right location,
land, and conditions for survival. Those who could not get inside had no
choice but to die, or to cling to their lives by hanging on margins of
the cities.

But after wandering the wilderness, Nezumi realized that not all of it
were badlands that inhibited any chance of survival. There was more
greenery, more oases than he saw back when he had wandered with the old
woman; there were even scattered streams, grassy fields, and marshlands.

It seemed as if the environment was recovering suddenly and rapidly,
though Nezumi could not tell if this improvement was the earth exerting
its inner strength or something that was simply temporary. Nezumi
figured no one would be able to tell.

But he did feel one thing: both the earth and humankind were resilient.

Humans were gathering near bodies of water and establishing small
settlements. They irrigated water and ploughed the fields, planted
seeds, tended cattle, produced children, and were attempting to rear
them. Although they were in extremely harsh conditions, they were
establishing lives that were separate from the six big cities.

\emph{Shion, the world is shifting. It's always moving and changing shape.
Have your eyes caught this change? Have your ears caught the sound of
this change, its movements in the womb?}

He spoke mentally to Shion, who was probably still in the midst of a
difficult battle in a newborn city.

``Oh, I know. How about this: why don't you stay over at my house
tonight, young'un? I'll give you a night's lodging as a way to apologize
for my rudeness. Will you sit down with me and tell me your story? It's
a small cottage, but I have a bed and a bath. It's a pretty good lodging
for these parts.''

``I won't take it.''

``Why not? It's a warm bed and a hot bath.''

``You could offer me a marble bathtub and I'd still refuse. I don't even
want to set foot into a thief's lodging.''

``As I said before, I'm not a thief. I'm No.~6's---'' the man abruptly shut
his mouth. Nezumi could hear the clear sounds of a horse's neigh and
human footsteps. There were several horses and men. The air suddenly
carried a scent of foreboding.

``Oh, no. They came after us.'' Colour fled from the man's face. In an
attempt to escape, he tripped over his feet and landed on his bottom.

``There, I see him! There he is!'' Three men appeared, wading through
the shrubbery. All three of them were of immense size. One was
tan-skinned, and the other two were fair-skinned with a hint of pink.

``We found you, fraud! Don't think you can get out of this alive.'' The
tan man raised a thick arm. His animal aggression was overwhelming.
``What the hell kind of elixir is this?'' he roared. ``It's just
coloured water! Stop fucking around.''

``Take him down!''

``Finish him off!''

The two fair-skinned men yelled at once. One of them had his grey hair
tied up like a horse's tail, and the other's head was shaven clean.

``You tricked us out of our money. I don't think anybody will have a
problem if you happen to get finished off.''

``W-Wait! Hold on a minute! You misunderstand me. That medicine is
really an elixir. Y-you must have made a mistake while you were
preparing it---''

``Shut up! Still got the balls to lie, huh?'' bellowed one.

``Rip his mouth apart and pull his tongue out so he can never speak
again! While you're at it, break two or three of his teeth!''

``Eeek!'' the man cried. ``P-Please, let's calm down and talk about this
without resorting to violence. I-I'll give you your money back!''

``Money?'' the tan man smirked. It made for a perfect stage villain's
face. ``Of course you'll give it back to us. I'll take my time with the
money after I'm finished with you.''

``Eeeek, help! C-Come on, young'un! Help me!'' The man looked at him
with pleading eyes.

``Hm? Who're you? Are you this fraudster's friend?'' The ponytail man's
eyes bulged as he glared at Nezumi.

``Never. I was just passing by. See ya.'' Nezumi turned his back on the
men. The last thing he wanted to do was get involved in a scuffle, much
less a dispute involving a thief.

``W-Wait! Please, don't leave me!''

``Shut up!''

He heard the dull sound of flesh hitting flesh behind him. He heard
someone collapse to the ground.

``St-Stop\el help me, please.''

``A fraudster like you should just own up to his crime, Shion.''

Nezumi's feet stopped.

``Did you say Shion?'' He turned around.

The man came crawling up to him, bleeding from the corner of his mouth.
He clung to Nezumi, pleading for help over and over.

``Is your name\el Shion?''

``I---it's what I call myself, but\el ''

``It's not your real name.''

``It's my son's name. H-He's an adorable baby, like an aster flower.''

``Your son's name?''

\emph{No way. Can it be?}

``Hey, kid.'' The man with the ponytail strode over to him. ``If you're
just a passerby, you better hand that man over to us and get going. Or
else---''

``Or else, what?''

The ponytail snapped his fingers as his face twisted into a grin.

``Or else you'll be buried in the wild right alongside him.''

``Oh, I think I'd like to decline, if you don't mind. I don't really
like being in the dirt.''

``Hey, fella.'' The tanned man twisted his face into the same kind of
vulgar grin. ``You're actually quite the looker up close. It's a waste
to put you underground. Why don't you come along with us? We'll give you
a good time.''

``What, you didn't realize I was beautiful until you looked at me up
close? I can see eyesight wasn't one of the things you were given, along
with looks.''

``What the hell did you say?''

Nezumi put his pack down and gave a small sigh. \emph{And so it goes in the
end. Shion, your name always gets me involved in some kind of conflict.
I hope you're aware of that.}

``Turning against us, huh, little bastard?''

``I wish I didn't have to.''

``Hah, well, that's fine. We'll just beat you up a little until you
quiet down. After we get rid of the fraudster, we'll have all the time
to enjoy with you.''

``Not the face, though. This one brings in the bucks.''

``I know that. Heh heh, we found ourselves a gem.'' The tanned man
licked his lips. Then he clenched his fist and lunged forward.

His movements were practiced and smooth, like one who was used to
violence and fighting.

Nezumi retreated a step and whistled. Hamlet burst out of his hair and
launched itself at the tanned face in front of it.

``Argh! What is it?!''

Before the tanned man could grasp Hamlet, Nezumi sank his knee into the
man's belly. The man's enormous tanned body fell to the ground without a
sound. Nezumi jumped over the fallen man and drew right up to the
ponytailed man.

``L-Little bastard---''

The ponytail bore down on him, his eyes bulging. Nezumi already had an
idea of the timing. He dodged the blow, slipped close to the man and
hammered the blade of his hand into the man's throat. The ponytail bent
over backwards before collapsing on his back. He, too, was unable to
raise so much as a cry.

``Oh, you've done it---'' The bald man, the last one remaining, drew a
dagger out. ``I'm gonna smash you.''

The bald man's movements were slightly less nimble than the other two.
Nezumi spun around so that he was behind him, and coiled his arm around
the man's neck, tightening his grip.

The dagger fell at his feet. Nezumi kicked it towards the spring. A
moment later, he heard a clear splash.

``A knife isn't something you just swing around. I suggest you get a
little more training.'' Nezumi tightened his headlock even more. All the
strength left the bald man's body. When Nezumi uncoiled his arm, the man
fell to his knees with a muffled gasp.

Hamlet scurried up to Nezumi's shoulder and chirruped softly.

He heard applause.

``Brilliant. I felt like I was watching a stage play. Amazing. Just
stunning. That was good work. Hey, what are you---''

Nezumi snatched the pouch of gold coins from the man's cloth bag and
placed it in the tanned man's hand. The tanned man groaned softly and
raised his head slightly.

``Sorry about that. Can you take this money as an apology for what he
did and write it off? Please.''

The tanned man blinked. He seemed to nod ever so slightly.

``H-Hey! That's too much. It's my money!''

``There'll be no grudges this way. Or would you rather these men follow
you around everywhere? Let me tell you that these types are tenacious.''

The man shrugged, and resumed clapping.

``I see. But anyway, you certainly did a brilliant job of cleaning them
up. I'm humbled.''

``Were you a citizen of No.~6?''

The man's hands froze. Without his smooth talk and clapping, the silence
seemed to ring in Nezumi's ears.

``Answer me. Did you live in that city?''

``\el Yes, I did. But I said my goodbyes a long, long time ago.''

``Why?''

``Why? Hmm, let's see. Because that city was fake, young'un. If it's
fake, it will always someday begin to unravel. I knew No.~6 would
probably begin to tighten its surveillance and become even more
domineering in its attempt to keep itself together. I didn't think I
could stand being suffocated like that.''

\emph{I see. So this man saw through No.~6's true form and its destiny.}

``And you escaped from the city alone, leaving your beloved little boy
behind.''

``I couldn't convince my wife to leave. She refused to leave No.~6 with
me. I don't think she could trust me completely.''

``That's shrewd judgement enough. If she had come with someone as
irresponsible as the likes of you, she would've been a pile of bones by
now.''

``Not exactly a polite one, are you? But anyway, is it true? Has No.~6
really been destroyed? It has, hasn't it? An artificial world like that
would never be able to exist in reality for long. It must have crumbled
from its foundations\el it's true, isn't it?''

``If it is, what do you plan to do?''

``I'm going home.''

``Home? To No.~6? It's pretty far-off.''

``Oh, six months of walking will get me there. It's not a big deal. You
said so yourself.''

``Yearning to see your wife and son again, huh, even after you abandoned
them once? Pretty selfish thing to do, I think.''

``No\el that's not all of it.'' The man fell silent for a while, then
raised his face determinedly. ``I owe you. You saved my life. So let me
tell you something. Come here.''

The man invited Nezumi out of the shrubbery. Three horses were tethered
and grazing. They were a dark brown colour.

``No one will overhear us here. Take this.'' The man drew a bag from
under his shirt. He had apparently kept it hanging around his neck. Both
the fabric and string of the bag were worn and faded.

``This\el ''

Inside was a rock a round smaller than the fruit on the bushes.

Nezumi did not even have to take a closer look to confirm. This was\el 

``Is this\el gold ore?''

``Yes. Listen to me: there are gold deposits in the area around No.~6. I
don't know how large the area is, but I think there's a considerable
amount of gold hidden there.''

``No way.''

``It's true. I discovered it when I was younger. I might look like this
now, but I was once a geologist. We investigated all soil around No.~6,
and this was part of the discovery.''

``But you put it under wraps and didn't report it.''

``Of course I did. Why would I have to report it, anyway? Gold would
never bring prosperity to No.~6. It would result in a hundred troubles
with not one good thing to make up for it.''

``I can see that.'' Nezumi felt a slight chill.

``As far as I know, the ore hasn't been discovered yet. I haven't heard
any rumours about any discovery. Besides, No.~6 is destroyed now, so the
place must be in the throes of confusion. Which means I can enter and
leave freely. I can even dig up gold in broad daylight and no one would
reprimand me.''

``Wait a minute. Where's this gold mine you're talking about?''

``A strip of land running from the north to the south. Part of it even
reaches the region that used to be called the Land of Mao. None of it is
visible above ground. The gold is slumbering away, deep inside the
earth. Plus---''

The man lowered his voice and continued in a low murmur, as if to build
tension.

``I can't say this is for sure yet, but\el there's also a possibility
that there's a huge deposit of rare metals right beneath No.~6. Nickel,
gallium, zirconium, niobium, indium\el I can't say much more, but what
do you think? Great news, isn't it?''

Nezumi's chill worsened slightly.

``\el It's great to hear as a fairy tale. This is how you've tricked
people all the way up until now, isn't it? As the fraudster that you
are.''

``I'm not a fraud. I'm the one who waits.''

``The one who waits?''

``Yes, I've been waiting---for No.~6's fall. And it seems like the time
has finally come. I have to make preparations to go back home. Hey, why
don't you come along with me? I couldn't ask for a better partner. Let's
go back to No.~6 and claim that enormous fortune for ourselves.

The man's eyes shone with a disgusting, slimy kind of light. It was not
the lively kind of light that illuminated the way forward. His eyes were
glowing dimly from their depths in an attempt to lure the prey close.

\emph{This man\el } Nezumi realized he had gritted his teeth. \emph{This man isn't
insane, nor is he trying to trick me. He's just telling the truth---at
least the truth as it appears to him.}

``And what do you plan to do with those riches? Enjoy a luxurious
retirement?'' \emph{No. That isn't what this man wants.}

``I'm going to buy it.''

``Buy what?''

``No.~6.''

For an instant, Nezumi's voice and breath caught in his throat. All he
could do was stare, bewildered, at the man.

``Buy No.~6? What do you mean?''

The man stowed the ore back in its pouch and smiled amiably.

``Listen, young man. If you plan on taking over the world, you won't be
needing armies, commandments, or thorough systems of surveillance and
control. You need wealth. Wealth is the single largest, most significant
weapon. No.~6 didn't quite get that part right. Well, the city was also
unlucky to have a foolish ruler.''

``You plan on becoming the ruler of No.~6 with wealth?''

``Oh, I don't know.'' The man cocked his head to the side. ``Who knows
what fate will bring? I'm not much of an ambitious person. I don't
aspire to be an emperor or a ruler.''

``Then why?''

``For fun. I can make a mess of people's lives with these two hands. It
would be jolly. Just jolly. No game could be better than this.''

``Wh\el '' Nezumi stared harder at the man. He was not like Shion.

Shion never looked at people's lives as something to toy with. He never
manipulated them for fun.

``No.~6---that city is finally on the road to rebuilding. They're trying
to establish a new city-state, and you're just going to make a mess of
it because you feel like it?''

``Rebuild? New? Impossible. It doesn't matter who gets involved and in
what manner. A state is a state. It'll eventually strengthen its
government and attempt to put people under its rule. That's the true
face of a state, and the history of humankind has proven that fact to
us. No.~6 can change its robe as many times as it likes, but it'll still
be No.~6, all the same. If there is any change, it would be whether the
person at the core of No.~6---its ruler---is foolish or intelligent. He'll
set his methods of rule in place: if he's foolish, he'll make it
obvious; if he's intelligent, he'll be nimble and discreet. The fool
would eventually destroy himself, but a man of decent intellect would
gradually gain complete hold of No.~6. Those are the types you should be
the most afraid of. So?''

``\el Huh?''

``What kind of person is involved in the rebuilding of No.~6? From your
point of view, is he foolish? Is he intelligent?''

Nezumi shook his head slowly. The base of his neck ached dully.

``He's very bright, and holds substantial intellect. I can't imagine him
becoming the type of ruler you were talking about.''

``Ah, you have high regard for him, I see. And you must know the man---he
is a man, right?---you must know him well?''

\emph{In a sense, I know him more than anyone else. And in a sense, I know
nothing at all.}

``And you also believe in him.''

\emph{I do believe in him. Nothing in the world would be worth believing if I
couldn't believe in Shion. I believe in him. But I was also afraid of
him, wasn't I?}

Nezumi fell silent. The man glanced at him and stepped forward.

``How about it? Come with me. I'm not quite sure about the rare metals,
but there's definitely gold.''

Nezumi took a firm step backwards.

``No thanks. I'll drift to wherever I want to go.''

``I see\el that's unfortunate.'' The man grimaced as if he were really
disappointed. ``But I guess there's nothing we can do. I'll be off,
then. I think I'll borrow this horse here. Considering how much gold I
paid back there, I don't think he'll mind if I take one horse.''

The man took hold of the reins of a grey horse and turned around.

``One last thing. People change, boy. That man you believe in will
change, too. Anyone who stands at the top of a state will change. If he
doesn't change, he'll be destroyed. You remember that.''

Nezumi touched the knife attached to his belt. \emph{Maybe if I finish this
man off here\el if I finish him off, I would nip a bud that would
otherwise bring harm to Shion.}

His fingers itched. Nezumi clasped his itching fingers.

\emph{I'll never forgive you for harming, much less killing, someone for me.}

\emph{Nezumi, don't kill him. Don't commit a crime for my sake.}

Shion was holding his arm back and pleading with him desperately.

\emph{\textbf{Nezumi, don't kill him.}}

\emph{That's right. That's what you would say. I know you would say that and
stop me. You've always been, and always will be, a naive do-gooder.}

\emph{Shion\el }

``Well, if the fates bring us together, let us meet again.'' The man
mounted the horse with a sweep, and dug his heels in. The grey horse
gave a whinny and started off. The man and the horse disappeared in a
cloud of dust.

The wind blew, making the bushes sway.

The clouds covered the sky as the land enrobed itself in the
darkness of nighttime.

\emph{Shion.}

A tiny crack appeared in the clouds, revealing deep purple sky.

A solitary star twinkled.

Far off into that sky was No.~6.

Nezumi yielded to the wind as he gazed intently up at that star.