% !TeX spellcheck = en_US

\chapter{This quintessence of dust}

\myepigraph{What a piece of work is a man, how noble in reason, how infinite in faculties,\\
	in form and moving how express and admirable, in action how like an angel,\\
	in apprehension how like a god --- the beauty of the world, the paragon of animals!\\
	And yet, to me, what is this quintessence of dust? Man delights not me\el}{\emph{Hamlet}, Act II Scene II}

\lettrine{T}{he doctor} was much older than how Shion remembered him. The tall,
liberal man used to come to Karan's shop once or twice a week to buy a
sandwich or meat pie. A handsome beard and moustache adorned his face,
and he spoke in a beautiful, clear baritone.

He had also once invited Shion to specialize in medicine and work at his
clinic.

"You'd have no problem with picking up the necessary specialized
knowledge and technique. I recommend taking the certification exam if
you're interested."

It was an attractive offer, but Shion did not take it up. There was no
way someone like him, who had been stripped of all his privileges and
exiled from Chronos, would be able to pass the exam. But he was happy
that the doctor had looked out for him---a stranger and a mere baker's
son---and offered him a path in medicine. He was also grateful.

In the months that Shion had not seen him, the doctor had transformed so
much he hardly looked like the same person. There were white streaks in
his beard and his hair, and he looked like he had shrunk a size. But in
terms of appearance, Shion admitted he had probably undergone a more
drastic change. His hair was completely white, and his face was smeared
with blood, dirt, and soot.

The small clinic in the outskirts of Lost Town was run by the doctor, a
nurse, and a nursing robot. The nurse screamed as the bloodied, dirty
group burst in. Shion yelled over her shriek.

"Doctor, please---please, he needs treatment!"

"You\el could you be---"

"The baker's son. Doctor, please. Treat him."

The doctor's eyes shifted to Nezumi. His gaze trained on the blood that
dripped from him.

"Prepare for an emergency operation."

The nurse sprang into action even before the doctor finished speaking.
She hastily disappeared into a room adjacent to the examination room. A
robot came pushing a stretcher.

{\sffamily "Please place the patient here."}

Shion laid Nezumi down on the stretcher.

"Nezumi," he called tentatively. His eyelids remained tightly closed.
"Nezumi\el "

{\sffamily "Please remove your arm. Please remove your arm from under the patient.
Now transporting the patient to the operating room."}

The robot urged him, but Shion's arms were stiff and unyielding, still
holding Nezumi as he had all this time. Only his fingertips shook
violently.

"Shion!" Inukashi grabbed his arms and yanked them for him.

{\sffamily "Now transporting the patient. Now transporting the patient. Entering
	emergency operating mode. Commencing oxygen intake. Commencing
	measurements. Now measuring blood pressure, pulse, heart rate, blood
	type."}

The doctor swiftly cut Nezumi's clothes away. Several pipes grew from
the robot's torso and connected to him.

{\sffamily "Transporting the patient. Transporting the patient."} The stretcher and
robot entered the operating room.

"Doctor." Shion grasped at the doctor's white coat. "Doctor, please\el 
save him. Please\el "

"Shion."

He did not expect to be called by his name. Shion lifted his face.

"I'm a doctor," the man said firmly. "If someone is in need of
treatment, I will do everything in my power to give it to him. But this
is Lost Town. I don't have the equipment it takes to perform delicate
surgery."

Shion knew. But as he had told Rikiga, he had no choice but to rely on
this doctor.

"I see that he's already gotten temporary treatment. Was that you?"

"Yes."

"What kind of wound is it?"

"A gunshot. A rifle bullet pierced him."

"Pierced, you say," the doctor muttered as he strode briskly into the
operating room. Shion bowed his head deeply to the man's retreating
back.

He felt faint. He sank to the floor.

"Shion\el " Inukashi sat beside him, and put an arm around his shoulders.
"Shion\el I just want to ask you, do you\el do you, by any chance, want
me to be with you?"

"Inukashi\el "

"Listen," Inukashi said brusquely, "I've never comforted anyone before.
I used to think it wasn't worth a crumb of bread. Still think so. But\el 
but if you want me to comfort you right now\el if I can comfort you
somehow by being here, then\el then, I'll be here."

Inukashi gently rubbed Shion's arm. The tension gradually loosened, and
blood began to course through his veins again. Shion closed his eyes,
and let his head droop onto Inukashi's chest.

He felt an almost imperceptible soft bump. If this was the usual case,
he would jump up in a confused panic. But right now, he only felt
soothed. Right here, there was a body to support him, arms to hold him,
a voice to murmur to him, and the warmth of another to comfort him. This
was happiness that could not command a price. Was it not?

"Inukashi\el thank you."

\emph{Oh, but\el } Shion bit his lip with his eyes still closed. \emph{But this is not
the warmth I long for. Not this body, these whispers, nor these arms.}

Something warm flitted over his eyelids. Inukashi had licked them.
Inukashi was gently licking off the blood that had dried and caked on
them. The little mice were curled up in Shion's lap, and the dogs had
lain down in a corner of the room.

"It'll be alright," Inukashi said. "There's no way he'd die. He's not
wuss enough to give in just yet. I've seen my share of bad people in the
West Block, but no one was as cunning, conniving, and dangerous as
Nezumi. I told ya before, didn't I, that the guy is the devil himself.
You just don't know his true face. And I'm still right. He's still the
devil he always was, and devils aren't done in so easily. Tomorrow,
he'll wake up as if nothing happened, and go right back to setting traps
for us. He's that kind of guy. He'll be alright, don't worry."

Shion opened his eyes, and lifted himself up.

"Inukashi, I'm grateful. Thank you so much."

"I was only insulting Nezumi, dumbass. What're you feeling grateful
about? You're a hopeless idiot, you know. Hopeless."

Inukashi turned aside obstinately. But he did not move away from Shion.

\emph{Ungh, nghoaaaar, nghoaaar.}

A snore rang out, making the very air of the room vibrate.

"Whoa! Will ya listen to that racket."

\emph{Nghoaaaar, nghoaaaar, nghoaaaar, ungh, ungh.}

Rikiga was fast asleep, lying on his back on a bench.

"Just now he was saying he wouldn't be able to sleep without some drinks
in him, and now look at the guy. Like a log. I'm surrounded by hopeless
people." Inukashi sighed theatrically. Then, he gave a short whistle.
The dogs got to their feet and approached. They nestled close to
Inukashi and Shion, and lay crouched on their bellies.

"These guys can make the best sleeping quarters out of any hole. It's
time for us to catch a wink, too."

"Yeah\el "

"We need to sleep, Shion." Inukashi pulled at Shion's shirt. "We won't
be able to fight tomorrow if we don't. You don't think our fight is over
yet, do you?"

He did not. Nothing had been solved yet. The fight would still continue
tomorrow. \emph{But if I lost Nezumi, if I had to face a tomorrow without him,
then I wouldn't be able to remain a soldier.}

\emph{You're weak. Unbelievably frail}, he could hear Nezumi say in derision.
\emph{Laugh at me, Nezumi. Look on me with contempt. Make fun of me. Give me a
scornful laugh, a cold laugh. I just want to hear your laughter. Let me
hear it, please.}

"Sleep," Inukashi said, almost like an order.

\mybreak

The Correctional Facility was burning. The flames roared up around it as
it crumbled. \emph{This is a dream}, his reason told him. \emph{You've escaped the
Correctional Facility. You're already in Lost Town, No.~6. That's
why---this must be a dream.}

\emph{This is an illusion.}

The flames roared. They were revoltingly real. He could clearly see the
tip of each writhing flame. His skin smarted at the scorching air that
blew at him. The acrid smell stung his nose.

\emph{This is a dream? This is an illusion? Absurd. This is unmistakably
reality.}

\emph{But does that mean I've come back again? Have I slipped back in time to
right after I escaped the Correctional Facility?}

The flames burned with even greater vigour. They roared, wavered, and
overlapped. He saw them stretch out into thin strips before a black
streak slashed through it.

Shion stood stock-still with his breath held. All confusion, agitation,
and astonishment fell away. He simply stood in a trance.

The black streak kept widening. The flames split into two.

"A wasp\el "

The rest failed to materialize as words.

It had a coal-black body, a slender curved torso, a long belly,
transparent wings embroidered with thin golden lines; golden antennae
and compound eyes; three simple eyes that shone a dull silver.

A giant wasp appeared out of the flames. It was a wasp, coloured
coal-black, gold, and silver---light and darkness. Shion took a step
backwards. Its beauty was almost terrifying. He was so overwhelmed, he
was almost brought to his knees.

\emph{What\el is this?}

"Elyurias," a mutter touched his earlobe.

"Nezumi."

Nezumi was standing right beside Shion. He stared unblinking at the
flames. No---he was not looking at the flames engulfing the Correctional
Facility, but at the enormous wasp. Nezumi was holding his ground
against it.

"Elyurias? This wasp?"

Nezumi did not answer. He did not stir. He was almost like a statue. For
an instant, the wasp in front of Shion faded in his consciousness.
Nezumi was standing there. His eyes were open wide. His profile
expressionless, but blood coursed through that face.

"Nezumi, you really did---" \emph{You really survived.}

Nezumi inhaled. His lips moved very slightly. A melody flowed forth.
Gentle music found life as it left Nezumi's lips.

Shion smelled the lush scent of greenery. The sound of the rustling
canopies reached his ears. He felt the beating of wings. The buzzing of
small insects echoed in his eardrums, until even that melted into music,
forming its ebb and flow.

His body was being lifted up. He no longer knew where he was. His body
and soul were suspended in Nezumi's music. Shion let his whole body
relax as he lent himself fully to it.

He could hear singing.

\clearpage

\poem{The wind steals the soul away, humans thieve the heart\\
	O earth, wind, and rain; O heavens, O light\\
	Keep everything here\\
	Keep everything here, and\\
	Live in this place\\
	O soul, my heart, O love, my feelings true\\
	Return home here\\
	And stay}

\poem{The wind steals the soul away, humans thieve the heart\\
	But here I will stay\\
	to keep singing\\
	Please\\
	Deliver my song\\
	Please\\
	Accept my song}

Shion had broken into a thin sheen of sweat in the midst of his ecstasy.
A bead of sweat slid down his forehead.

Suddenly, he was blasted by hot air.

He was slammed to the ground. Charred pieces of debris grazed his
cheeks, his body, as they bounced and tumbled across the ground.

"Don't get up." Nezumi's hand pressed on his back. "Keep lying low."

The wind kept blowing. Fragments of rock and debris rolled over the
ground in front of Shion as he lay face-down on the ground.

\elyurias{Chuckle chuckle chuckle.}

\elyurias{Chuckle chuckle chuckle.}

Laughter welled up from deep underground. Or was it raining down from
the heavens?

\elyurias{Chuckle chuckle chuckle.}

\elyurias{Chuckle chuckle chuckle.}

The wasp spread its wings wide open. The flames streamed sideways,
crawling across the ground.

\elyurias{Chuckle chuckle chuckle.}

\elyurias{Chuckle chuckle chuckle.}

The wasp took flight. It ascended to the sky without a sound, leaving
only the wind behind. A piercing buzz of wings rose all around.
Thousands of small black specks took flight after the giant wasp. The
swarm of them formed a wide band as they rose.

"Elyurias," Nezumi murmured again.

\mybreak

He couldn't breathe. There was something weighing down on his upper
torso.

Shion awoke. Inukashi's head was on his chest. He was asleep with his
ear pressed to Shion's chest as if to check his heartbeat. He was
breathing softly. Two dogs were nestled close on either side of them.

\emph{I see what he meant. You definitely wouldn't freeze to death like this.}

Another dog was curled up beside Rikiga. Despite his grumbling, Inukashi
had also looked out for Rikiga to make sure he didn't freeze. Perhaps
that explained why Rikiga's snores had turned into peaceful breathing.

They were in a small hospital room, Lost Town, No.~6. There was no
mistake: time had not turned back. But that was not a dream. What he had
seen was reality.

\emph{Elyurias---was that it? A wasp born from a cocoon of flames?}

Shion gingerly touched the nape of his neck. He thought about the wasp
that had tried to tear through that spot and crawl out of it. He thought
about Yamase. He thought about the thousands of wasps which had taken
flight in a dense black stream. If those were all parasitic, what would
become of No.~6?

He did not know.

He slipped a couch cushion under Inukashi's head, and stood up
stealthily so as not to wake him. He had probably only been asleep for a
short while---not more than thirty minutes. But his body felt surprisingly
light. Was it because he was relieved?

\emph{Nezumi survived.} He was certain. His heart, which was fraught with
tension until then, gradually began to unwind. Shion took several deep
breaths.

He was concerned about where the wasps were going, as well as what kind
of fate awaited No.~6. But his relief at not losing Nezumi trumped it
all.

He inhaled once more, deeply, and exhaled.

A computer was embedded in the doctor's desk. He pressed a button, and
the screen silently began to load. He dug into the pocket of his
sweater.

"There it is." The chip had been given to him by the man called Rou. He
wondered what was going to happen to that underground area now that the
Correctional Facility had crumbled. What had happened to Sasori? Or the
boy who had handed him a bowl of water? The girl who had stared at Shion
in wonder? And Safu?

Rou had said that the chip contained the entirety of his research, and
that he entrusted it to Shion.

"After you have saved your friend, please try to decode it." His voice
had been hoarse and feeble. \emph{After you have saved your friend\el }

\emph{Safu. I couldn't save her.} She had been his precious friend, and he had
abandoned her.

His last glimpse of Safu had been of her smiling. She looked a little
more mature than Shion remembered, and she was beautiful.

\emph{I couldn't save her. In the end, I couldn't save her.}

He made a fist and struck his chest. \emph{I've made another wound here. A
wound that'll ache for the rest of my life. I'll never forget. I won't
be able to forget.}

\emph{Safu. You're forever out of reach, no matter how strongly I feel for
you. But you'll still be in my heart. I'll continue to think of you, and
of what you left behind for me.}

He inserted the chip. He was not asked for a password. Shion bent
forward and stared intently at the screen.

Everything to do with No.~6 during their underground conversation with
Rou was written here. Elyurias, the Mao Massacre, the Forest People,
destruction, predation and parasitism\el 

As he read on, wading through the mix of unintelligible technical
language and numbers, he felt his fingertips growing colder.

Shion finished reading, and extracted the chip. His mind was half-numb
and in a daze.

\emph{So this was No.~6.}

\emph{This was Elyurias.}

The door of the operating room opened and the doctor walked out.

"Doctor." Shion stood up, and the man nodded at him.

"He'll be alright. He's hanging in there."

"Thank you so much, doctor. Thank you."

The doctor removed his mask and grinned.

"You mentioned that you were the one who stemmed his bleeding and gave
him temporary treatment?"

"Yes."

"You did a very nice job. He was also lucky that the bullet hadn't
remained in his body. It pierced him, but thankfully it just missed the
fatal spot. He's very fortunate, indeed."

"I told ya so."

Shion had not noticed Inukashi standing behind him. Inukashi had a hand
on his hip, and shot a quick glance at Shion.

"Nezumi has a notorious amount of good luck when it comes to getting out
of bad situations. You don't need to worry about him."

"And I think I need to worry about the rest of you," the doctor smiled
crookedly. "Where were you hit, Shion?"

"You know my name?"

"I do. It did make the headlines when you got arrested and taken to the
Correctional Facility."

"I see\el "

"Everyone who had any knowledge of you was surprised. I don't think
anyone could believe that you were the 'fallen elite turned murdering
monster' or the workplace murder suspect that the authorities made you
out to be."

"You too, doctor?"

"You could say that. I was more pained than surprised. I'd caught on
that the authorities were trying to paint a false picture of you as a
criminal."

The doctor then let out a long breath.

"It was the same with my younger brother," he said.

"Your brother?"

"Yes. We were far apart in age. Our father passed away early on, so I
raised him like a son. He was abducted by the Security Bureau five years
ago, when he was eighteen. Take a guess at why."

"Because he refused to declare his loyalty to No.~6?"

"Absolutely right. My brother refused to partake in the allegiance
ritual held at their school every morning. He didn't like being forced
to submit. I think it came from his youthful pride and sense of justice.
And as a human, it was normal for him to feel this way. My brother was
indeed a proper, normal adolescent. Maybe he was a little more
rebellious and stubborn than most. He was also a little inexperienced in
the ways of the world. My brother was summoned to the Moondrop the same
day, and he didn't come back until two weeks later."

"He came back?"

"He came back, but he was transformed. I don't mean dead---he was alive.
But he may as well have been dead. You could see no remnant of the
cheerful, active captain of the basketball team that he used to be. He
hardly spoke or responded to me, and just gazed blankly at the sky all
day, just vacantly stared\el He killed himself not long after coming
home. I can't even bear to think about what he must have gone through
during those two weeks. I said he killed himself, but in truth, he was
murdered by this city. Our mother collapsed from shock, and she never\el 
she passed away not more than three days later. Her will to live was
torn from her once she saw what her beloved son was reduced to. Our
mother may as well have been murdered, too. No, she I believe was. It
was definitely murder." The doctor nodded vehemently as if to convince
himself.

\emph{He killed himself.}

Shion recalled the doctor's words in his head again.

In the idyllic city of No.~6, cases of suicide were infinitely close to
zero. All citizens were promised blissful and peaceful lives. But what
an empty, artificial promise it was.

The doctor bit his lip as if to endure a throbbing pain. This man had
also suffered at the hands of No.~6. Already how many lives had the city
devoured?

Shion clenched his hand into a tight fist.

No.~6 did not permit people to be people, nor for each to be his own.

\emph{Why?} he almost screamed. \emph{Rou said so. He said he tried to construct a
utopia---one without war, discrimination, or unhappiness.}

\emph{When did it go wrong? What went wrong to transform it into such a
ruthless monster? What went wrong---?}

The doctor's face unravelled into a smile as his lips relaxed.

"But Karan was fearless. She continued to open her shop, bake bread, and
put it on the shelves. Every time I passed Karan's bakery, I couldn't
help but breathe in the delicious aroma of freshly-baked bread. She is
amazing for carrying on her daily work in spite of her loss. She
probably strongly believed that you were going to come home. I felt pity
for Karan, you know. I thought there was a slim chance, if there was
even one, that you were coming home. I believed if you did come back,
you would be just like my brother. But you did come back, and in one
piece. You came back proper."

"I did change in appearance, though."

"Appearances don't matter, as long as your soul isn't broken. That's
precisely No.~6's plan---to govern human souls. To rule the hearts, minds,
and even thoughts of people."

Inukashi stifled a huge yawn.

"So tell me what else is new. I thought this was obvious to you guys
already. For us West Block residents, No.~6 ain't no utopia. It's like a
bloated, fat vampire."

"A vampire\el I can see that." A smile spread across the doctor's face.
"And that vampire is writhing in pain from the changes occurring in its
body. To think---to think this day has come---ha ha ha! I wish I could have
shown this to my brother and mother! Ha ha ha ha!"

The doctor's laughter gradually gained momentum until it became a roar.
Inukashi furrowed his brow and recoiled.

"Hey, Shion. Is the doc okay? I mean, up here?" He pointed at his head.
"You sure he hasn't got something loose in there?"

"He saved Nezumi's life," Shion said sternly.

"Sure didn't do anything for me," retorted Inukashi.

The doctor was still laughing. Shion slowly enunciated his words as he
spoke at the man's trembling back.

"Doctor, can I see Nezumi?"

The laughter stopped. The doctor turned around. The echoes of his
laughter and the residue of his mirth still swam in his eyes.

"Nezumi? Ah, you mean that boy. What a peculiar name. Not his real name,
is it?"

"I don't think so."

"And what is?"

He had opened his mouth to say "I don't know" when the door to the
examination room opened a crack. A tall, thin man was edging his upper
body into view. A crow was perched on his shoulder. The mice gave a
terrified screech. One dove into Shion's pocket, while the other two
squeezed under the belly of a dog with patched fur.

"Yoming, what's the matter?" The doctor strode over to the man. Yoming
whispered something into his ear. The doctor's eyebrows rose
dramatically.

"The Correctional Facility!" The doctor's mouth gaped open. "The
Correctional Facility---is that even possible?"

Yoming answered him. Shion could not catch it. He didn't want to. Right
now, he was in no mood to listen.

\emph{I want to see Nezumi.} All of his thoughts concentrated into that one
point. His heart pounded in anticipation.

\emph{I want see him and know that he's alive.}

Shion put his hand on the operating room door.

"He's upstairs." The doctor pointed an index finger straight up at the
ceiling. "There's a recovery room on the second floor. Aria is attending
to him. There's a direct-route elevator in the operating room, too, but
I want you to use the stairs in the hallway."

"Thank you, doctor."

"Oh---wait a minute," the doctor said. "Don't tell me you've come from the
Correctional Facility---"

Shion did not hear the last of the doctor's sentence. He tore into the
hallway.

"Hey, wake up, old man! Looks like we're paying Nezumi a visit. We need
to get some flowers."

"Nnngh, what? Who said I ever wanted to go?"

"Quit talking in your sleep and wake the hell up."

Shion left Inukashi and Rikiga bickering behind him, and dashed up the
stairs. His legs faltered for a moment as he reached the corridor, dimly
lit by nighttime lights.

It reminded him of the long, straight corridor of the Correctional
Facility. But this atmosphere was not impregnated with fear; it did not
prick his skin as before.

He exhaled softly.

Only one room by the stairs had the lights on. Shion regulated his
breathing, and gently placed his hand on the door. It slid silently
open.

The room walls were painted a pale yellow. Across from him, darker
yellow curtains were drawn across what he supposed was a large window.

By the window, the nursing robot was making faint electronic sounds by
the bed. When Shion entered, it raised its arm as if to reject him.

{\sffamily "Resting. Resting. Not taking visitors. The patient is resting. Not
	taking visitors."}

I see, this robot must be Aria. He bent low to talk to the robot.

"Aria, thank you. I'm very grateful."

{\sffamily "Grateful. Grateful. Grateful."} The nursing robot's visual sensors
flashed, and turned from red to green. It seemed to have acknowledged
Shion's presence.

{\sffamily "Aria, I want you to let me see your patient. I want to see him really
	badly. I'll do anything."}

Aria's visual sensors stopped flashing---or rather, she stopped blinking.
Her green eyes were fixed on Shion.

"Want to see. Want to see. Request accepted. Request accepted."

Aria glided across the floor. She retracted her arm, and settled herself
in a corner of the room. She looked like a quirky but lovable piece of
interior decor. The dogs lay around her peacefully.

Nezumi was sleeping on the bed. He was connected to many tubes, and his
eyes were closed. A tinge of colour had returned to his cheeks, perhaps
thanks to a blood transfusion. His superfibre cloth was folded neatly
and placed beside the bed, no doubt by Aria.

Shion bent over Nezumi and took his pulse. It was faint, but regular.
Shion could definitely feel it. A sigh of relief escaped his lips.

"Nezumi\el " He felt his body unravel as he released a sigh.

\emph{He made it. He survived.} Shion knelt by the bed and buried his face in
the sheets. He could feel Nezumi's heartbeat. He wanted to raise his
voice and cry---as loudly as his voice would allow.

\emph{He's alive. He's alive. Nezumi's alive.}

"I could do with a few more winks." Rikiga yawned, showing a full array
of teeth.

"I'm hungry," Inukashi said. "And my dogs are hungry, too. It's all good
that Nezumi made it, but it ain't gonna be funny if we die from
starvation instead. Ah damnit, I'm starved!"

"If 'we' die? Don't lump me in with the likes of you."

"You've got nothing to do with it, old man. I'm talking about me and my
dogs. Hey, robot, uh---Aria, was it? Struck lucky with a pretty name,
haven't ya? Doesn't suit you at all. So, Ms. Aria, can you get us some
grub or what?"

{\sffamily "Grub. Grub. Grub. Cannot comprehend. Cannot comprehend."}

"I mean a meal. Patients and injured people still need to eat, right?"
Inukashi made a motion of wolfing something down.

{\sffamily "Meal. Understood. Understood."}

Aria's torso opened up. A row of three steaming paper cups appeared.
Inukashi whistled, and Rikiga swallowed hungrily.

"Two more, two more," Inukashi said."For my dogs. And some bread and
meat, if you've got any."

{\sffamily "No meat. Have bread."} Her torso opened again. Two more paper cups and
some rolls appeared.

"You're the best. I think I might fall in love with you. I'd give you a
huge kiss."

"I wouldn't do that," Rikiga said. "Think of the poor robot who has to
get a kiss from you. It would probably stop functioning. Don't turn such
a good girl into a lump of scrap metal. Hm? What's this?"

Rikiga furrowed his brow as he brought the cup away from his lips.

"It's bland. It may as well be hot water. And this bread\el it doesn't
taste like anything."

"It's hospital food, don't complain about it. Look how easy it was to
get hot soup and bread. Can't beat No.~6. In the West Block, you could
only dream of a feast like this. Right, Shion?"

"Yeah. It's really tasty." He was not simply going along with Inukashi.
He really found it delicious.

This taste almost matched that of the rich soup that Nezumi made on the
day he had escaped to the West Block---the day he had miraculously lived
through the wasp's attack.

It soaked into his body, quenched his soul, and revived him. Just one
cup of soup restored his confidence that he would live through another
day.

\emph{It's delicious.}

\emph{Nezumi, wake up. Wake up so you can sip this cup of soup. Look at me
again with those eyes full of life.}

"Mm\el " Nezumi shifted. The whiteness of the bandage around his shoulder
and chest stung Shion's eyes.

"Nezumi, Nezumi!" Shion called to him. He poured his soul into the name
he had called so many times before. Nezumi's eyelashes fluttered ever so
slightly.

"He's probably still knocked out from the anaesthesia," Rikiga said. "He
won't be waking up for a while. Hmm, but even a devil like him looks
like an angel when he's all quiet and asleep like this. Strange, isn't
it?" he murmured pensively.

"Hah, you still hung up on him, old man? How many times have you been
shafted because you were fooled by his looks?"

"I've been shafted enough times, with or without his good looks. By both
Eve and you." Rikiga sighed. "Am I just going to spend the rest of my
life being bossed around by rude, filthy brats? Just thinking about it
makes me depressed. I need a drink to stomach this. Lady Aria, you don't
happen to have some booze on you, do you?"

{\sffamily "Booze. Booze. Booze. Cannot comprehend. Unable to process your
request."}

"Alcohol. You know, I want something that'll hit me in the guts with
some oomph."

{\sffamily "We have: alcohol antiseptic. We have: disinfectant alcohol. We have:
sterilization alcohol. Which one do you need? Which one do you need?"}

"I don't need any of that. I don't need antisepsis, nor do I need to be
disinfected or sterilized. God, what a useless princess." Rikiga clicked
his tongue.

Inukashi turned aside and laughed discreetly. Shion also couldn't help
but twitch the corners of his mouth. Rikiga wore a wry smile. The three
glanced at each other and laughed for some time.

"I never expected you'd make it back like this," Inukashi murmured
thoughtfully after their laughter had died down.

"Me neither," Shion agreed.

"Not to mention that bonus work you guys did with the Correctional
Facility. I have a bit of a new regard for you, to tell you the truth. I
honestly never expected---had no clue how you'd pull it off. I thought you
guys would never be able to escape through the garbage chute."

"It's thanks to you and Rikiga-san, Inukashi."

"Thanks to us, huh. Say, Shion\el "

"Hm?"

"Didn't it ever cross your mind that we might not show up at the waste
depot? What if we pulled a no-show, or we showed up but left early---you
didn't think about that at all?"

Shion searched his soul for a moment at Inukashi's question. What had he
thought back then? He searched, then gave an answer.

"I didn't think of it at all." He gazed into Inukashi's eyes. "That
never even crossed my mind. I believed that you and Rikiga-san would be
there. Nezumi must have thought so, too. I'm sure he had solid belief in
you."

"Well, that's all great and nice for you, but let me say that we\el 
well, I dunno about the old man, but\el I don't owe nothing to you guys.
I didn't have an obligation to wait in there."

"Me neither," Rikiga chimed in. "I might have my share of grudges, but I
don't have any obligation or debts to owe, either." He clucked his
tongue repeatedly.

"Lemme tell you something, Shion," Inukashi stabbed a sharp-clawed index
finger in Shion's direction. "Don't think I got myself involved in this
hell of a mess for free. You guys owe me now. You best be prepared,
'cause I'm putting hefty interest on it."

"I'll have you know that I'm going to be sending out an invoice
addressed to Eve as well. He's made me spend quite a bit of money,
taking everything into account. I wouldn't be able to rest in peace if I
didn't get reimbursed for that at least."

Inukashi and Rikiga grimaced at the same time as if they had rehearsed
it. Shion suppressed a laugh and nodded solemnly. He didn't care how
astronomical the interest rate was, or how exorbitant the invoice was.
The two had stayed and waited for them. In that hygiene management room,
where life and death jostled each other, they had continued to wait,
believing that Shion and Nezumi would return alive.

He bit his lip.

Safu had also been waiting. She had been waiting for Shion. She was
probably waiting for him, not to say goodbye, but to escape together
with him.

\emph{I couldn't hold up my end.}

He had not been able to give her what Rikiga and Inukashi had given him.

"Hey, Shion." Inukashi hugged his knees and leaned closer. "Whaddaya
think is gonna happen to the West Block?"

"The West Block, huh\el "

"Yeah. No.~6 is spiralling into chaos, by the looks of it. The
Correctional Facility is gone. The gates are blown apart. Maybe that
wall---the wall that separates the West Block and No.~6---maybe that'll
break down too. Ya think?"

"Yeah. In fact, it most likely will."

Inukashi swallowed, and curled up just slightly.

"So, if that happens, I wonder what everyone in the West Block is gonna
do. How would they face people who've treated them like crap all this
time? Would they take their anger out on them? Would they storm into No.
6? Would they fight, or run away\el wonder what they'll do? When I think
about it, I just\el well, it makes my head spin."

"Mm-hmm\el " Inukashi was right. It made his head spin, too. A world
without walls: it was beyond his imagination. What would hold ground
there? Surely not just peace and open freedom. How would the West
Block's wind, swirling with hatred and anguish, blow against No.~6?

It simply exceeded his imagination.

"Turn the lights out," said a low, cutting voice.

"Wh---Eve, are you---?" Rikiga fell speechless.

Nezumi was sitting upright. His dark grey eyes glinted sharply. "Turn
off the lights. Quickly," he repeated.

Inukashi's nose twitched. He jumped to his feet, and pressed the
electric switch. All the lights were cut, and darkness fell over Shion's
vision like a veil.

"Nezumi, what---"

"Shh!"

Nezumi moved in the darkness. He pulled out all the tubes that were
inserted into his arm. He slipped to the floor and knelt down.

"Keep quiet. Don't even move."

Inukashi shivered.

Time passed. One minute, two minutes, three minutes\el suddenly, noise
erupted from downstairs. Footsteps, shouting, screaming, then gunshots.

"Run! It's the Security Bureau!"

"Don't move. Move, and we will shoot."

"Run! Get out of here!"

"All you traitors are under arrest."

"Kill them, it's no big matter."

"Their leader is getting away! Get him, and kill him!"

Those were the few words that Shion's ears managed to catch.

He curled up in the darkness.

He curled up and sat still, feeling Nezumi's warmth and breathing right
beside him.