% !TeX spellcheck = en_US

\chapter{A lie of truth, a truth of fiction}

\myepigraph{The King's ears are donkey's ears.\\
	Great furry donkey's ears.\\
	Moving, twitching donkey's ears.}{\emph{King Midas' Donkey Ears}, Greek myth}

\lettrine{N}{ezumi walked} slowly along the night path. Here, night and darkness were
synonymous with each other. After all natural light had faded, what was
left was a world of darkness. Everything became painted black.

Sometimes, a barrack would let a thin strip of light seep out of one of
its cracks, while barely keeping the wind and rain out. But the lights
were often extinguished not long after, and a frigid chill would reign
over the night, piercing through the darkness, the silence, and people's
clothes to reach their warm bodies underneath.

Even the white puffs of breath that escaped his lips faded into the
darkness. He turned his face up to the heavens. Countless stars were
winking in the clear night sky.

Tomorrow morning would probably be even colder than usual. And outside,
more people would freeze to death. A cruel fate to meet under a starry
sky. Even with a star-filled sky, no one called these winter nights
beautiful --- not on this land.

Nezumi stopped his feet, and gazed at the glittering city in the
distance. The city of light loomed in the darkness --- the Holy City of
No.~6.

The entire city glowed golden, and reminded him of the myth of King
Midas, who turned everything he touched into gold.

In the freezing darkness, Nezumi smiled wanly.

King Midas would acquire the golden touch, but in exchange for it he
would no longer be able to bring meat nor bread to his lips, and would
even turn his beloved daughter into a golden statue. He would then
finally realize his greed and his folly, and beg the gods for
forgiveness.

\emph{No.~6, what will you do? You, the city that looks down on us in our
darkness, and glitters in all its deception and artifice, will you too
grovel on the ground one day and beg for forgiveness? But there will be
no gods to grant you mercy. Clad in that golden robe of yours, you'll
crumble, burn to ashes, and perish. I'll live until the moment the
curtains fall on your finale. I'll keep living, and see the end with my
own eyes.}

Nezumi re-wrapped his superfibre cloth around himself, and began to
walk. A little mouse, one that Shion had named Hamlet, poked its head
out of the folds and chirruped softly.

Yes, he was going to live. Just as he had all the way up until now, he
was going to keep living, even if he had to crawl the earth on all
fours. He would shroud himself from any danger, sharpen his fangs,
polish his claws, and keep living until the moment that he would sink
his teeth into the other's throat, and tear it apart.

He would survive, keep living. He would.

Nezumi put a hand to the back pocket of his pants. Inside it was Karan's
memo.

\memo{\karan}{
	Safu was taken away by the Security Bureau.\\
	Help. -K}

He had not shown Shion yet. What was he to do with it? Nezumi was
suspended in his decision. He stood at a crossroads, unable to throw the
memo away, nor to pass it to Shion and turn his back on him, saying it
was none of his own business.

To be indecisive, to waver, and to be agitated --- he knew how dangerous
these were to him, almost painfully aware. Right or left; up or down;
fight or flight; abandon or protect --- the split second it took to make
the decision was the difference between life and death. He had never
once made the wrong choice. That was how he had survived up until now.

\emph{This memo is dangerous.} Then, all he had to do was throw it away. Along
with the indecision that would no doubt endanger his life, it was for
the best to entomb it all in darkness.

He knew the correct answer. But why wasn't he complying with it? Why was
he taking the trouble, even paying a large sum of money, to have
information collected about the Correctional Facility? \emph{What the hell am
I doing?}

His feet stopped.

Nezumi stood still, and trained his eyes onto the darkness. He was on a
slope sparsely populated with trees, a couple dozen metres away from his
underground abode.

"Who's there?" he spoke quietly. There was a dry rustling above him,
perhaps from a gust of wind that whistled through the bare branches. But
even more discreetly, there was a movement in the dark, the faint sound
of a step on the leaves.

"A little slow to notice, aren't ya?" There was a short bark of a laugh.
"Not like you, not like you at all. What were you daydreaming about?"

"Inukashi."

Inukashi's black hair and tan skin were convenient for blending into the
darkness. But it was careless of him not to have noticed his presence
until he had come this close. He was not himself today.

"Good thing it was only me. Who knows how many lives you'd need if you
were that dazed around anyone else, Eve." Inukashi called Nezumi by his
stage name, and gave another short laugh.

"Things aren't much safer with you around," Nezumi retorted. "Especially
if you're gonna be waiting at night to ambush me on the road." He took
half a step backwards. "What do you want, Inukashi? I find it hardly
likely you've been able to get the information this quickly."

Inukashi's tone of voice changed, and all sarcasm vanished from his
speech.

"We've got an emergency."

"Emergency?"

"Just now --- well, more like awhile ago --- Shion came to see me."

"Did he?" A jolt of unease raced through him, almost painfully.

"And not about his dog-washing job, either. He shoved a grey coat in my
face, and asked me if I got it from the Correctional Facility."

"Grey coat, huh\el women's?"

"Yeah. It was ripped at the shoulder, but it was a fine piece of
clothing. It came from a used-clothes dealer I sold stuff to. Stuff I
got smuggled out of the Correctional Facility."

\emph{It must belong to that girl--- Safu.} Nezumi turned aside, and drew a
breath.

"So?"

"\emph{So?}" Inukashi echoed incredulously. "You tell me. What's the script for
this act, huh, Nezumi? Shion says this coat belongs to his friend. Which
means his little friend is being kept prisoner in the Correctional
Facility. And earlier today, you gave me money to gather information
about the Correctional Facility. Don't tell me those aren't related ---
even a dog wouldn't fall for that lie. Are you planning to help Shion's
little friend out, is that what you're doing?"

Nezumi had no way to answer. He could neither affirm nor reject what
Inukashi had said.

"Of course not," Inukashi answered for him. "There's no way someone like
\emph{you} would throw his life away to help a complete stranger."

"What makes you think I'm gonna die in the process?"

On the other end of the darkness, Inukashi sucked in a deep breath.

"Are you half-asleep? This is the Correctional Facility we're talking
about. By some lucky fluke, you might be able to sneak in. But there's
no way you'd make it out alive. Nezumi, don't get any funny ideas."

"Goodness gracious, are you \emph{worried} about me? I'm shocked."

"I could care less about you," Inukashi snapped. "Whether one rat dies
or not isn't gonna make a difference. But what're you gonna do about
Shion, huh? Now he knows where his little friend's been taken. Being the
oblivious little boy he is, he probably thinks the Correctional Facility
is just some cushy Centre for Discipline, or whatever. He probably
figures all he has to do is hand in a Visitation Form to see his little
friend. If you don't stop him, the kid's gonna go. He's gonna go and ---
he's gonna get himself killed."

Inukashi fell silent, the darkness of the night seemed to deepen. Even
the wind was still --- the tree branches ceased to make even a faint
rustle.

"Is this what you've waited all this time to tell me?" Nezumi said
presently. "I ache to imagine what pains I must have put you through."

Nezumi stepped forward, and grabbed Inukashi by the shoulder before he
could slip away. As long as he had bearings on the other's presence, he
could more than easily predict all of his movements.

"It doesn't matter what Shion plans to do," Nezumi said quietly. "He's
not one of us, and it's none of our business."

"Then why the hell are you sniffing around behind his back?" Inukashi
replied accusingly. "Why do you need to gather information about the
Correctional Facility in secret?"

Nezumi stiffened his fingers and dug them harder into Inukashi's thin,
bony shoulder. Inukashi cried out in pain. Nezumi bent to bring his lips
near the other's ear.

"Don't stick your nose in things you have no business in," he whispered.
"You do the job you've been paid to do, and nothing else."

He let his hand go. Inukashi's small body swayed unsteadily.

"I only told Shion where the coat came from," he said. "I haven't told
him anything about what you've come to me for."

"Of course you haven't."

"Nezumi, Shion's gonna go alone," Inukashi said levelly. He feebly shook
the arm that was now numb all the way to his fingertips. "He thinks you
don't know anything about it. And he's gonna go alone, without telling
anyone. He's not gonna get you involved. You know that, right?"

"What makes you so sure? Are you Shion's Papa or something?"

"I don't have to be his Papa to know. You should know even better than
me what kind of person he is. That's why you're scuttling around in
secret, aren't you?"

"Shut up!" Nezumi had raised his voice in a snarl. His emotions whipped
about turbulently; his breathing came out irregular. Inukashi showed
almost no reaction.

"If he's so precious to you that you don't wanna lose him," Inukashi
said steadily, "protect him to the very end. And do whatever it takes to
protect him, you idiot, no matter how humiliating it is. You think you
can save face, huh? Keep it all hidden, and take care of it all on your
own? Stop fooling yourself."

"Inukashi!"

Inukashi sprang back a split second before Nezumi took a step forward.
Crouched on one knee, Inukashi laughed softly.

"You lose, Nezumi."

"What?"

"You've gotten yourself something you need to protect --- you lose. Those
are the rules in these parts. Better get to know them."

Nezumi kicked off the ground, and rounded in on Inukashi from the front.
He snared the other boy as he tried to get away, and pushed him to the
ground.

"What'd you say about losing?" he said fiercely. "That's enough bullshit
from you."

"I'm not bullshitting. Nezumi, if this was you a while ago, you wouldn't
have let yourself be provoked so easily. You wouldn't be walking around
at night lost in thought, either."

\emph{Let go}, Inukashi said in an eerily calm voice. He got up, and heaved a
sigh.

"Still don't realize, Nezumi?"

"Huh?"

A sharp whistle tore through the air. While he whistled, Inukashi took
several steps backwards.

In the darkness from all directions, countless small red dots of flame
glinted as they emerged. It didn't take Nezumi long to realize that they
were dogs' eyes. Before he knew it, he was surrounded by a pack of them.
Not one of them raised so much as a growl as they formed a ring and
advanced on him.

"Those ones are trained guard-dogs. You're not gonna get the same deal
you did in the afternoon." Inukashi's voice was further away now. "You
stepped right into that ring without even realizing it. Definitely not a
mistake you'd normally make, Nezumi. But there's your weakness. Forget
Shion --- look at you, you can't even protect yourself."

After a moment of silence, a short command sliced the air.

"Get him!"

The dogs sprang up. Dozens of lithe and deadly bodies flew over Nezumi's
head and came down upon him from above as he sat crouched on the ground.
He sprang to his feet, and aimed a kick straight upwards.

A yelp.

One dog broke the silence with its voice, and crumpled to the ground.
Before Nezumi could catch his breath, another one kicked off the ground.
It sank its teeth into Nezumi's arm, which he had wrapped with his
superfibre cloth just in time. Nezumi swung his entire arm around and
battered the dog to the ground. He rose, and regained his posture with a
tree at his back.

"Inukashi, if you're gonna keep up this stupid game, I'm not gonna go
easy on you either." Nezumi drew his knife from its leather sheath. He
caught his breath, and counted the little red flames.

Four more.

"So you don't care if your precious dogs get their throats slit, huh?"
he called out.

Inukashi's voice answered from the same spot as before.

"Let's see you try. That was just a warm-up. They're not gonna be all
polite this time and come at you one by one. This time, they're coming
all at once."

Even before Inukashi had finished his sentence, Nezumi was lunging in
the direction of his voice. At the same time, a searing pain tore across
his shoulder.

"Out of the way!" He rammed the butt of the knife between the dog's
eyes. Along with the sound of tearing fabric, the black dog went rolling
across the ground behind him.

"Inukashi!" Nezumi yanked Inukashi by his long hair, and dragged him
down. He pinned him to the ground, and pressed the knife to his tan
throat.

"Back your dogs down, or else---"

Inukashi laughed shortly.

"Or else what? You gonna kill me?"

"If you wish it so," Nezumi said coolly.

"You think you can kill me, when you haven't even managed to kill a
single dog?"

This time, it was Nezumi who gave a soft laugh.

"But I don't have a spare knife today."

"What?"

"Dog's blood dulls the blade. I saved it and kept it clean for you."

Inukashi's body twitched.

"Hey, cut that out, you jerk," he said nervously. "You try and kill me ---
my dogs'll jump you all at once. They'll tear you to pieces."

"Oh, I don't know about that. You're their boss, right? I've heard
before that dogs lose their will to fight if their boss gets defeated."

"Th---That's not true--- hey, really, cut it out. It's dangerous."

"Back your dogs down."

"Fine." Inukashi snapped his fingers. The dogs spun on their heels at
once, and disappeared into the darkness.

"I see. You've trained them well."

"Thanks for the compliment," Inukashi said sullenly. "Funny how it
doesn't seem to make me feel any better. So are you gonna get your heavy
ass off me or not? A love scene with you isn't exactly something I've
been itching to do lately."

"Don't worry," Nezumi said pleasantly, "it's the last thing I'd want to
be doing either. I wouldn't even do it if I got paid to on-stage."

After he had freed Inukashi and put away his knife, Nezumi posed his
question anew.

"What was all that for?"

Inukashi clucked his tongue while he brushed the leaves off his clothes.

"I took it upon myself to give you a private lesson."

"What?"

"The fact is, you're not as strong as you think. I just thought I'd
teach you that. You've got skill, though. Not many people can get that
far against me and my dogs."

"Why, thanks for the compliment. Funny how it's not making me feel
better."

"But you're not any superhuman or monster," Inukashi continued. "You're
just a human. And a man can only do so much by himself."

There was a dull pain in Nezumi's shoulder. Blood flowed in streams down
his arm.

A fleeting thought crossed Nezumi's mind. This was the same spot where
he had gotten the bullet wound which Shion had treated four years ago.

"Nezumi!"

He could hear Shion's voice calling him. The light of a lamp bobbed
nearer.

"Looks like the little lad has come to fetch you himself," Inukashi
snickered quietly. "Well, let me excuse myself then---" Then, somewhat
rushed, he added, "Nezumi, there's something weird going on inside No.
6."

"Weird?"

"I don't know the details. I've heard that there's some weird disease
going around, but I don't know for sure. I'm gonna look into it. And I'm
going to be getting information about the inside of the Correctional
Facility soon. It looks like things are starting to get busy for them
too. It's gonna get pretty interesting, I can smell it --- my dog's nose
is telling me. So---"

"So?"

"So count me in --- I'm gonna help you out."

Inukashi's hand reached out, and clapped Nezumi firmly on the shoulder.
A vicious pain shot through him. Nezumi groaned, and fell to his knees
with a hand pressed to his shoulder.

"See ya. I'll be in touch soon." Inukashi melted into the inky darkness
faster than his dogs had disappeared. As he faded, Shion's footsteps
approached nearer.

"Nezumi, did something happen?"

Shion held the lamp up to Nezumi as he got to his feet. His eyes widened
in alarm.

"What happened to you? You're bleeding!"

"I got attacked by a dog."

"A dog? Why?"

"It was just some mongrel. I guess it thought I was a cute little bunny
rabbit. What are \emph{you} doing here?"

Hamlet poked its head out from Shion's sweater pocket.

"He came to get me," Shion said. "I thought something might've happened
to you."

"So you came to help. With one lamp."

"Yeah." Shion brought the lamp closer to Nezumi's wound, and furrowed
his brow.

"We have to get this treated. Let's go home. Can you walk?"

"Of course."

Shion's slipped a hand under Nezumi's armpit, as if to support him.
Nezumi brushed him away, and began to walk ahead. His shoulder throbbed
painfully. But he wasn't about to cling onto the hand that was extended
to him. If he learned to lean on someone, he would never be able to walk
on his own again. The helping hand was always fickle, and disappeared
just as suddenly as it was offered. That was how things were.

Once they returned to their underground room, Shion sprang into action,
briskly taking the appropriate steps. He checked the wound, cleaned, and
disinfected it.

"You gonna sew it up again?"

"The wound isn't that bad this time, unfortunately," Shion said, in a
rare rueful grin as he closed the emergency kit. "Freaked out a bit,
didn't you, Nezumi? Thought you'd go through the same thing as four
years ago?"

"'A bit' is an overstatement. With you, I feel like I'd end up with
stitches for a bug bite."

"How rude," Shion smiled. "I still think the treatment I gave you four
years ago was the appropriate thing to do."

Four years ago, on that stormy night --- yes, on the night he had first
met Shion --- No.~6 had been in the midst of a hurricane. He still
remembered, ever so vividly, the window flung open as if to invite him
in; twelve-year-old Shion as he poked his face out; You're hurt, aren't
you? I'll treat your wound' --- words that he had never expected; the
satisfied smile that had spread over Shion's face the moment he had
completed the suture; the sweetness of the cocoa; the delicious taste of
the cherry cake; the comfort of the bed; the sound of quiet, slumbering
breaths right beside him as he awoke the next morning --- he couldn't
forget any of it, no matter how hard he tried. Even when he tried to
discard it, he could never quite bring himself to.

Each and every miraculous occurrence of that night still remained with
him as tangible sensations, never fading in the least over the four
years until now.

Did people call them memories? A mental record? Or did they call it
fate?

It was easy enough to laugh at people, calling them indulgent and weak,
when they accepted others unconditionally and tried to save them.
Indeed, as a result of taking Nezumi in, Shion had lost almost all of
his privileges and fortune.

How much easier things would have been if he was able to dismiss Shion
with a condescending laugh, this naive boy, this petri-dish elite who
had grown up oblivious to society. But it was too bitter to laugh at and
be done with. It was too vivid to forget. And to throw away, it was much
too heavy.

"Shion."

"Hm?"

"Do you really think so?"

Shion's hands stopped in the middle of winding a bandage.

"Four years ago. Do you really think it was the appropriate thing to
do?"

"Well, we were in pretty limited surroundings," Shion said slowly. "Back
then, though, that would have been the most I could do. Now, maybe I
would be able to sew it up a bit better." The long fingers of his
deft-looking hands moved as nimbly as they looked, winding the bandage
tightly and neatly.

"Not just about my injury. About the whole night."

After he had knotted the ends of the bandage with care, Shion studied
Nezumi's eyes.

"Your life turned 180 degrees that night. Can you still say, even now,
that what you did wasn't a mistake?"

"Yeah." His answer was so prompt, Nezumi was caught off-guard.

"You don't regret it?"

"No."

"Not even a bit?"

"No."

"Why?"

"Nezumi, I don't really understand what you're trying to ask. But I've
done a little thinking myself since moving to Lost Town. I wondered, if
I were to go back in time, and return to that night four years ago --- if
I were to return to before I met you, what would I do?"

Shion smiled sheepishly, and pushed the emergency kit to the back of the
shelf.

"I thought about it, over and over again. And every time, there was only
one answer. No matter how many times I'd return to that night, I'd do
the same thing again. I'd open the window, and wait for you."

"Even if you knew that your own ruin would be waiting beyond it?"

"But there wasn't any ruin," Shion replied softly. "I don't think my
being here like this has ruined me at all. Right, Cravat?"

The small brown mouse nodded from its perch atop a stack of books.

"That one's Hamlet, isn't it?"

"Hamlet's sleeping on the bed."

"Oh. Right. --- Geez, you had to go giving them stupid names, now it's
more confusing than before."

"The poor guys deserve names, it's the least you can do. Both of them
are smart and courageous. Like Hamlet today, when he let me know that
you were in danger."

"Well, he went to the wrong person. Even if you showed up, you wouldn't
be much help. It was alright this time because I'd already chased the
dogs away, but if I hadn't, you'd probably be the one sitting there with
a gaping wound."

"Yeah, well --- I guess you're right about that one."

Nezumi stood up, and grabbed Shion by the arm.

"Never do something like that again, you hear me? Whatever happens,
don't flatter yourself and think you can be any help to me."

Shion stared back at him with unblinking eyes. Nezumi lifted his chin,
and clenched his jaw.

"You're powerless, you remember that. You don't have the skill or the
mentality it takes to fight. You're like a chick that's fallen out of
its nest. You'd just chirp-chirp-chirp until you're eaten by a fox. So
do yourself a favour, and don't go walking into danger's path. Don't do
it, ever. Use your head. Put your so-called gifted brain into motion,
full-throttle, and use your judgment to assess the situation. Geez, I
don't know what the hell you were thinking, running out into the
darkness without even carrying a weapon."

"I wasn't."

"What?"

"I wasn't thinking at all, of the situation, or of danger. I was already
running before I could stop to think."

"That's why I'm saying, Shion, next time, don't ever do something as
foolish or reckless."

"Then what should I do?"

"Don't do anything. There's nothing you could do anyway. Pull a blanket
over your head or something, and stay quiet."

Shion dropped his gaze, and shook his head.

"I can't do that," he said quietly. "I can't stay there and sit still
when I know you're in trouble. I would've burst outside either way."

"You'd just be a hindrance."

"That's harsh," Shion said softly.

"It's the truth."

"Nezumi --- you're right," he relented. "I'm useless. I don't know how to
fight, and I would never be able to bring myself to hurt anyone."

"Yeah, and as a soldier, that would put you in the lowest rank. No ---
actually, you'd be a write-off. So don't even think about fighting. You
don't have the mental leverage to be worrying about other people. You
can't even protect yourself. So don't do anything. I'm begging you, just
don't go near any dangerous places."

\emph{What the hell am I saying?}

Nezumi clenched his jaw again.

What was he saying? What was he doing, getting serious about this? Was
he that bent on stopping Shion?

\emph{Shion's gonna go alone.}

Inukashi's low voice echoed in his ears.

Yes, Shion would probably go alone. \emph{He'd set out to a place with less
than one in a million chances of returning alive, and he'd go alone,
without begging for my help, without even telling me. He would go
silently, not knowing anything about fighting, not knowing the pain of
shedding blood or the chilling horrors of murderous intent. The useless,
big-headed, oblivious idiot.}

"But it's not about reasoning," Shion said quietly, puncturing the
silence.

"Huh? Did you say something?"

"It's not about reasoning, Nezumi. I know very well in my head that even
if I were to show up, I wouldn't be of any help to you --- I wouldn't be
able to save you. I know."

"Good for you. The grey matter in your head is about the only thing you
can boast about, anyway. And if your head knows, then take its advice."

"No."

Shion pursed his lips firmly, his expression defiant. It was the face of
one whose willpower ran strong and deep. It was Nezumi's first time
seeing Shion with a face like this.

"It's not about reasoning!" Shion said heatedly. "Back there, when
Hamlet came to call me, I was scared. I thought something had happened
to you. I thought you were going to die. Are you telling me I should've
just stopped and calculated in my head? Figured that it wouldn't do any
good if I went anyway, and just sat still? I could never do that. How
could I? How could I be cool and calm and think about whether I have or
don't have the strength, whether I can or can't help you? How could
anyone? Idiot!"

It was his second time being called an idiot by Shion. Both times,
Nezumi wasn't able to predict Shion's explosion of anger. The first
time, Nezumi had told Shion, 'Don't cry for other people. Don't get into
fights for other people. Fight and cry only for yourself.' Shion had
said that he didn't understand. It was true, he hadn't understood. For
this time, again, Shion had burst out into the darkness for a stranger.
Casting aside the reason which warned him of the risks, he had gone
running into the darkness. It was dangerous. Very dangerous. Nezumi had
been prepared for Shion to become shackles that bound his ankles. But
there was also the opposite. There was a possibility that he himself
would become the fetters that bound Shion's wrists.

This is why---

Nezumi averted his gaze from the boy in front of him.

\emph{This is why humans are troublesome. The more you involve yourself with
them, the tighter the shackles become. They hinder free movement. It
becomes harder to live only for yourself. Maybe we should never have
met. Maybe one day, Shion, you'd come to think so.}

Shion's shoulders rose and fell as he took a deep breath. He stuck his
lip out in a disgruntled manner.

"Nezumi, why aren't you saying anything?"

"No reason."

"Go on and laugh if you want to. You probably just think it's all
gibberish from someone who doesn't know a thing about the world, right?
Fine. Laugh to your heart's content. Go on, laugh."

"Wait a minute, Shion," Nezumi said hastily, "it's not like I'm mocking
you. I just, well\el I'm just saying it's dangerous to jump into danger
like that, without thinking about---"

"I know that!" Shion said hotly. "But I couldn't help it, alright, I was
worried sick. Or am I not even allowed to worry about you? Don't I even
have the right to be worried?"

"The right? Shion, you're not making sense."

"You're the one making me talk like this!"

Shion's fist pounded the bookcase. A mound of books collapsed. Cravat
gave an alarmed screech, and skittered into the folds of Nezumi's
clothes.

Shion blinked, and his cheeks flushed. He bent to pick up the books, and
mumbled an apology in a subdued voice.

"I'm sorry, I just --- I didn't mean to yell."

"I don't mind," Nezumi said lightly. "I must say it was quite alluring
to see you all worked up like that. Something I'd like to be treated to
again once in a while."

"It seems like I'm always worked up when I'm with you," Shion sighed.
"I'm surprised at how emotional I can get sometimes."

"You've always been an emotional person. You always choose feeling over
reason, and you're not ashamed to be truthful to your emotions. Four
years ago, it was the same. Even when you were a candidate for the elite
echelons of No.~6, you still obeyed your emotions and took me in."

"Yeah\el obeyed my emotions\el " he said pensively. "I guess you're
right."

Shion stacked the books neatly, and exhaled.

"But you know, Nezumi, I really don't regret it. I'm still glad that I
didn't turn my back on my feelings that night."

"I know."

"Huh?"

"I know you don't regret a single bit of what you did. I just asked on a
whim. I guess I was probably bored, or something."

He brought a hand to his shoulder. The bandages, which were old and
worn, and would have lost all elasticity by now, wrapped themselves
tightly around his shoulder and arm joint, and showed no signs of
loosening.

"I wouldn't have been able to dress my wound this well," Nezumi said
reflectively. "You might not be able to fight, but you can probably
treat people. Everyone has something. And probably---"

"Probably?"

"No, never mind. Say, I'm hungry, aren't you?"

Shion gazed at Nezumi, and gave a gentle smile.

"There's bread and meat on the table. Some stuff happened, and there's
only a little bit left, but it should be enough for dinner."

"What about you?"

"I'm going to sleep. Your wound is probably gonna keep you up tonight,
so you can have the bed to yourself. I'll sleep on the floor."

"How kind of you."

"Nezumi."

"Hm?"

"If I hadn't met you, I probably would never have realized what kind of
person I was, huh?"

"Why're you bringing this up now?"

Shion drew nearer to Nezumi as he sat in his chair, and looked him
straight in the eye.

"I would have grown up into a mild, rational, obedient adult, without
even knowing there were so many emotions inside of me. I would never
have known what it was like to cry, or get angry, or feel resistance
toward something. I met you, and I realized how much abundance I had.
And I'm proud that I know now."

Shion clipped his words, and hesitantly lowered his eyes.

"I'm glad I met you."

It came out as a whisper that he could barely catch. Shion bent down,
his eyes still lowered. His lips brushed lightly against Nezumi's.

A book fell somewhere with a soft \emph{whump}.

As Shion lifted his face again, Nezumi spoke.

"Not a thank-you kiss, is it?"

"It's a good-night kiss."

"Good-night, huh."

"I'm going to be shearing the dogs tomorrow," Shion said. "There are a
whole lot of them with long fur. Inukashi just leaves them, so their fur
gets all tangled and they're starting to get skin inflammation."

"I just got bitten by a dog, alright? I don't care if they have short
fur or long fur, I don't even want to hear about dogs right now."

Shion laughed out loud, and gave a casual wave of his hand.

"Good night, then."

"Yeah. Sweet dreams."

"You too."

Shion disappeared into the shadows of the books. Cravat crawled out from
Nezumi's clothes and scampered after him, perhaps intending to sleep
with him too.

"Good-night kiss, huh."

Nezumi traced his lips with his fingers, and slumped back in his chair.

"Some liar you are."

His gnawing hunger, exhaustion, and throbbing pain ebbed away. In its
place, something welled up from deep within. Sadness, loneliness --- it
wasn't quite either. What was it? A hot bead rolled down his cheek. It
took him a while to understand that they were tears. He had long
forgotten what it was like to cry.

It tasted salty, like over-salted soup.

Nezumi propped his knees up and put his head down on them. Slowly, he
swallowed the tears that seeped into his mouth.